### 2022-10-31 AppendixA.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\subsection*{The Space $L^2$}
Consider a measurable space $X$. The set of square integrable functions is called the $L^2$ space.\\

The inner product of $L^2$ is defined as 
\begin{eqnarray*}
	(f,g) = \int_X fg \ \ \ \ \textrm { for } f,g \in L2.
\end{eqnarray*}
The norm can be defined as $||f|| = (f,f)^{\frac{1}{2}}$ for each $f \in L^2(X)$. For reference, see \cite{Rud53}.\\

\textcolor{red}{***********************************************}\\

The space $C^m(a,b)$ is the space of functions with continuous derivatives up to order $m$ over the open interval (a,b).\\

The space $C^m[a,b]$ is the space of functions in $C^m(a,b)$, with existing right derivatives at $a$ and existing left derivatives at $b$, up to order m.\\

The space $C_0^m(a,b)$ contains all functions $f$ in $C^m[a,b]$ with the property that there exists numbers $a < \alpha < \beta < b$ such that $f$ is zero on $[a,\alpha] \cup [\beta, b]$.\\

The space $C^\infty(a,b)$ contains all functions in $C^m(a,b)$ for all $m$.\\

The space $C^\infty[a,b]$ contains all functions in $C^m[a,b]$ for all $m$.\\

The space $C_0^\infty(a,b)$ contains all functions in $C_0^m(a,b)$ for all $m$.\\

\textbf{Definition:} First Order Weak Derivative\\
Suppose $u \in L^2(a,b)$ and there exist a $v \in L^2(a,b)$ such that
\begin{eqnarray*}
	(u,\phi') = -(v,\phi) \ \textrm{ for each } \phi \in C^{\infty}_0(a,b)
\end{eqnarray*}
then $v$ is called the first order weak derivative of $u$ and is denoted by $Du$.\\

\textbf{Definition:} Higher Order Weak Derivative\\
Suppose $u \in L^2(a,b)$ and there exist a $v \in L^2(a,b)$ such that
\begin{eqnarray*}
	(u,\phi^{(m)}) = (-1)^{(m)}(v,\phi) \ \textrm{ for each } \phi \in C^{\infty}_0(a,b)
\end{eqnarray*}
then $v$ is called the m'th order weak derivative of $u$ and is denoted by $D^{(m)}u$.\\

Define inner product $$(u,v)_m = (u,v) + (Du,Dv) + ... + (D^mu ,D^mv)$$.

The space $W^1(a,b) \subset L^2(a,b)$ contains the functions with first order weak derivatives. $W^m(a,b)\subset L^2(a,b)$ contains the functions with weak derivatives up to order $m$. $W^m(a,b)$ is a Sobolev space with inner product $(u,v)_m$ and norm defined by 
\begin{eqnarray*}
	||u||_m = (u,u)^{\frac{1}{2}}_m.
\end{eqnarray*}

The space $H^1(a,b)$ is the closure of $C^1[a,b]$ in $W^1(a,b)$ with respect to the norm of $W^1(a,b)$. The space $H^m(a,b)$ is the closure of $C^m[a,b]$ in $W^m(a,b)$ with respect to the norm of $W^m(a,b)$.

\section*{Results for One-Dimensional Case}

\section*{Results for Higher-Dimensional Case}

\newtheorem{thmAH1}{Theorem}
\begin{thmAH1}
	The m'th order weak derivative $D^{(m)}u$ is uniquely determined.
\end{thmAH1}

\newtheorem{thmAH2}{Theorem}
\begin{thmAH2}
	$C^m(\bar{I}) \subset W^m(I)$ and if $u \in C^m(C^m(\bar{I})C^m(\bar{I})\bar{I})$, then $D^{(m)}u = u^{(m)}$. 
\end{thmAH2}

\end{document}

### 2022-10-31 AppendixB.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section*{One-Dimensional Case}
Consider the interval $[0,\ell]$. Divide the interval into $n$ elements $[x_{k-1},x_k]$. Each $x_i$ is called a node.
\subsection*{Piecewise Linear}
Denote the linear basis functions by $\phi_i$.

\subsubsection{Properties}
\begin{itemize}
	\item[-] The restriction of $\phi_i$ to an element is a linear polynomial.
	\item[-] $\phi_i = \in C^1_+[0, \ell]$
	\item[-] $\phi$ is piecewise linear.
	\item[-] $\phi_i(x_i) = 1$ and $\phi_i(x_j) = 0$ if $i \neq j$.
\end{itemize}

\subsection*{Hermite Piecewise Cubics}
The Hermite piecewise cubic basis functions has a continuous derivative. Thus any linear combination also have a continuous derivative. There are two types of Hermite cubics. Denote type one by $\phi_i^(1)$ and type two by $\phi_i^(2)$.\\

\subsubsection{Properties of Type One}
\begin{itemize}
	\item[-] The restriction of $\phi^{(1)}_i$ to an element is a cubic polynomial.
	\item[-] $\phi^{(1)}_i \in C^2_+[0,\ell]$
	\item[-] $(\phi^{(1)}_i)''$ is piecewise continuous with possible discontinuities at the nodes.
	\item[-] $\phi^{(1)}_i(x_i) = 1$ and $(\phi^{(1)}_i)' = 0$
	\item[-] $\phi^{(1)}_0(x) = 0$ if $x \notin [0,x_1)$, $\phi^{(1)}_n(x) = 0$ if $x \notin (x_{n-1},x_n]$ and for $i = 1,2,...,n-1$, $\phi^{(1)}_i(x) = 0$ if $x \notin (x_{i-1},x_{i+1})$
\end{itemize}

\subsubsection{Properties of Type Two}
\begin{itemize}
	\item[-] The restriction of $\phi^{(2)}_i$ to an element is a cubic polynomial.
	\item[-] $\phi^{(2)}_i \in C^2_+[0,\ell]$
	\item[-] $(\phi^{(2)}_i)''$ is piecewise continuous with possible discontinuities at the nodes.
	\item[-] $\phi^{(2)}_i(x_i) = 0$ and $(\phi^{(2)}_i)' = 1$
	\item[-] $\phi^{(2)}_0(x) = 0$ if $x \notin [0,x_1)$, $\phi^{(2)}_n(x) = 0$ if $x \notin (x_{n-1},x_n]$ and for $i = 1,2,...,n-1$, $\phi^{(2)}_i(x) = 0$ if $x \notin (x_{i-1},x_{i+1})$
\end{itemize}

\section*{Two-Dimensional Case}
Consider a rectangle $\Omega$ with length of sides $a$ and $b$, partitioned into smaller rectangles with length $\delta x$ and width $\delta y$. Each node is determined by $(x_i,y_i)$.
\subsection*{Piecewise Bi-Linear}
Denote the bilinear basis functions by $\phi_i$.

\subsubsection{Properties}
\begin{itemize}
	\item[-] The restriction of $\phi_i$ to an element is a bilinear polynomial. $\phi_i(x,y) = a + bx + cy + dxy$.
	\item[-] $\phi_i(x,\cdot) \in C^1_+[0,b]$ for each $x \in [0,a]$, and $\phi_i(\cdot,y) \in C^1_+[0,a]$ for each $x \in [0,b]$.
	\item[-] $\phi_i(x_i,y_i) = 1$ and $\phi_i = 0$ at any other node.
	\item[-] $0 < \phi_i < 1$ on each element having the node $(x_i,y_i)$ as a vertex. And $\phi_i = 0$ on every other node.
\end{itemize}

\end{document}

### 2022-10-31 Gedoen.tex
initial commit

\documentclass[a4paper,10pt]{article}
\usepackage{subfiles}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumitem}
\usepackage{amsfonts}
\usepackage{kantlipsum,graphicx}
\usepackage{graphicx} 
\usepackage{comment}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{comment}
\usepackage{booktabs}
\usepackage{xfrac}
\usepackage{floatrow}
\usepackage{multicol}
\usepackage{float}
\usepackage{tikz}
\definecolor{light-gray}{gray}{0.8}
\usepackage{graphicx}
\setlength\parindent{0pt}
\graphicspath{{images/2dwave/}{images/2dBeam/}}
\usepackage{xcolor}
\usepackage{pgfplots}

\begin{document}
\section*{Gedoen}

\subsection{Chapter 1}
\begin{itemize}
	\item Het 1.4.21 reg gemaak. Moet nog deur gaan en seker maak ek het dit ander plekke reg.
\end{itemize}

\subsection{Chapter 2}
\begin{itemize}
	\item Het verbeteringe aangebring.
\end{itemize}

\subsection{Appendix}
\begin{itemize}
	\item $L_2$ in gesit.
\end{itemize}

\end{document}

### 2022-10-31 References.tex
initial commit

\documentclass[main.tex]{subfiles}
\begin{document}
\begin{thebibliography}{AAA}
\bibitem[AL97]{An3} S S Antman and M Lanza de Christoforis, {\it Peculiar
instabilities due to the clamping of shearable rods}, Int. J.
Non-linear Mechanics $\mathbf{23}$ (31-54) 1997.

\bibitem[An76]{An1} S S Antman, {\it Ordinary differential eqautions of
non-linear elasticity~I: Foundations of the theories of non-linear
elastic rods and shells}, Archive for Rational Mechanics and
Analysis, $\mathbf{61}$, (307-351), 1976.

\bibitem[An96]{An2} S S Antman, {\it Dynamical Problems for Geometrically
Exact Theories of Nonlinearly Viscoelastic rods}, J. Nonlinear Sci.,
$\mathbf{6}$, 1-18, 1996.

\bibitem[BOC20]{Bochicchio2020} Bochiccho, I., Campo, M., Fernandez, J.R., Grazia Naso, M.,\ \textit{Analysis of a Thermoelastic Timoshenko Beam Model}, Acta Mechanica., (2020).

\bibitem[Bh09]{Bh} A Bhaskar, {\it Elastic waves in Timoshenko beams: the
`lost and found' of an eigenmode}, Proc. R. Soc. A $\mathbf{465}$
(239-255) 2009.

\bibitem[Co66]{Co} G R Cowper, {\it The shear coefficient in Timoshenko's beam
theory}, Journal of Applied Mechanics $\mathbf{33}$ (335-340) 1966.

\bibitem[CVV18]{VanRensburg18} Civin, D., van Rensburg, N.F.J., van der Merwe A.J.,\ \textit{Using energy methods to compare linear vibration models}, Applied Mathematics and Computation, \textbf{321}, (2018), 602-613.

\bibitem[Fung65]{Fung1965} Fung, Y C.,\ \textit{Foundations of Solid Mechanics}, Prentice-Hall Inc., Englewood Cliffs, (1965).

\bibitem[LC81]{LL} M Levinson and D W Cooke, {\it On the two frequency spectra of Timoshenko Beams}, Journal of
Sound and Vibration, $\mathbf{84(3)}$ (319-326), 1982.

\bibitem[LL91]{LL} J E Lagnese and G Leugering, {\it Uniform stabilization of
a nonliner beam by nonliner boundary feedback}, Journal of
Differential Equations, $\mathbf{91}$ (355-388), 1991.

\bibitem[LVV09]{LVV} A Labuschagne, N F J van Rensburg and A J van der Merwe,
{\it Comparison of linear  beam theories}, Mat. Comput. Model.,
$\mathbf{49}$,(20-30), 2009.

\bibitem[McK99]{McKenna97} McKenna, P.J.,\ \textit{Large Torsional Oscillations in Suspension Bridges Revisited: Fixing an Old Approximation}, American Mathematical Monthly, \textbf{106}(1), (1999), 1-18.

\bibitem[Rud53]{McKenna97} Walter, R.,\ \textit{Principles of Mathematical Analysis}, McGraw-Hill Book Company, Inc., New York-Toronto-London, (1953).

\bibitem[Sadd05]{Sadd} M H Sadd, {\it Elasticity. Theory, Applications and Numerics}, Academic Press, Burlington, (123-138), 2005

\bibitem[SR79]{SR} M Sapir and L Reiss, {\it Dynamic Buckling of a
Nonlinear Timoshenko Beam}, Siam J. Appl. Math., Vol
$\mathbf{37}$(2), (290-301), 1979.s

\bibitem[SV86]{SP6} J C Simo and L Vu-Quoc, {\it On the dynamics of
flexible beams under large overall motions - the plane case: Part
I}, Journal of Applied Mechanics {\bf 53}, (849-854), 1986.

\bibitem[SV87]{SP7} J C Simo and L Vu-Quoc, {\it The role of
nonlinear theories in transient dynamic analysis of flexible
structures}, Journal of Sound and Vibration {\bf 119}(3), 487-508,
1987.

\bibitem[SP06]{SP} N G Stephen and S Puchegger, {\it On the valid frequency
range of Timoshenko beam theory} J. Sound Vib. $\mathbf{297}$
(1082-1087) 2006.

\bibitem[Ti21]{Ti1} S Timoshenko *******

\bibitem[Ti37]{Ti2} S Timoshenko, {\it Vibration problems in engineering}
2nd Ed, 1937.

\bibitem[VV06]{VanRensburg06} van Rensburg, N.F.J., van der Merwe A.J.,\ \textit{Natural frequencies and modes of a Timoshenko beam}, Wave Motion, \textbf{44}, (2006), 58-69.

\bibitem[WU06]{Wu2006} Wu, Shen R.,\ \textit{Lumped Mass matrix in explicit finite element method for transient dynamics of elasticity}, Computer methods in applied mechanics and engineering, \textbf{195}, (2006), 5983-5994.

\end{thebibliography}
\end{document}

### 2022-10-31 files/Archive/Introduction.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\setcounter{chapter}{1}
\setcounter{section}{0}
\section{Introduction}

\textcolor{red}{**********Sit in introduction*************}

It is possible to derive a system of partial differential equations with corresponding boundary conditions but due to the complexity of the system, a different approach is considered. Consider the model problem in variational form.

We consider the {\bf variational form} of the vibration problem. This variational problem may be used to implement the {\bf finite element method}. The finite element method can be used to simulate vibrations of the elastic body for both dynamic and static problems and also calculate the natural frequencies and modes of the elastic body. Existence and uniqueness of solutions to the problem can also be investigated using a weak version of the variational form.

\subsubsection*{A Dynamic Problem}
Find a vector valued function $u \in C(\Omega)$ such that it satisfies the equations of motion and the constitutive equations. Since $u \in C(\Omega)$, $u$ satisfies the boundary conditions defined on $\Sigma$ and $\Gamma$.\\

Initial conditions for $u$ will need to be defined.

\subsubsection*{A Static Problem}
The static porblem is a special case of the dynamic problem  where $\partial_t^2 u = 0$. In this case, there are also no initial conditions.\\
\textcolor{red}{**************************}

\textcolor{red}{Research into the behaviour of suspension bridges is still a widely researched field by both engineers and mathematicians. This research started as several bridges suffered collapse. }

\subsubsection{Different Research Approaches}
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}
		\draw (3,2) -- (7,2);
		\draw (3,2) -- (3,1.9);
		\draw (7,2) -- (7,1.9);
		\node at (5,2.1) {Main Span};

		\draw[line width = 0.25mm] (0,0) -- (10,0);

		\draw[line width = 0.5mm] (1.4,0) -- (1.4,-0.5);
		\draw[line width = 2mm] (1.4,-0.5) -- (1.4,-0.7);

		\draw[line width = 0.5mm] (2.2,0) -- (2.2,-0.5);
		\draw[line width = 2mm] (2.2,-0.5) -- (2.2,-0.7);

		\draw[line width = 0.5mm] (8.6,0) -- (8.6,-0.5);
		\draw[line width = 2mm] (8.6,-0.5) -- (8.6,-0.7);

		\draw[line width = 0.5mm] (7.8,0) -- (7.8,-0.5);
		\draw[line width = 2mm] (7.8,-0.5) -- (7.8,-0.7);

		\draw[line width = 0.5mm] (3,1.5) -- (3,-0.5);
		\draw[line width = 2mm] (3,-0.5) -- (3,-0.7);

		\draw[line width = 0.5mm] (7,1.5) -- (7,-0.5);
		\draw[line width = 2mm] (7,-0.5) -- (7,-0.7);

		\draw (5,0.4) parabola (3,1.5);
		\draw (5,0.4) parabola (7,1.5) ;

		\draw (3,1.5) -- (0.2,-0.5);
		\draw (7,1.5) -- (9.8,-0.5);

		\draw[line width = 2mm] (0.2,-0.5) -- (0.2,-0.7);
		\draw[line width = 2mm] (9.8,-0.5) -- (9.8,-0.7);

		\draw[line width = 0.1mm] (5,0) -- (5,0.4);
		\draw[line width = 0.1mm] (5.25,0) -- (5.25,0.43);
		\draw[line width = 0.1mm] (5.5,0) -- (5.5,0.46);
		\draw[line width = 0.1mm] (5.75,0) -- (5.75,0.55);
		\draw[line width = 0.1mm] (6,0) -- (6,0.69);
		\draw[line width = 0.1mm] (6.25,0) -- (6.25,0.85);
		\draw[line width = 0.1mm] (6.5,0) -- (6.5,1);
		\draw[line width = 0.1mm] (6.75,0) -- (6.75,1.25);

		\draw[line width = 0.1mm] (4.75,0) -- (4.75,0.43);
		\draw[line width = 0.1mm] (4.5,0) -- (4.5,0.46);
		\draw[line width = 0.1mm] (4.25,0) -- (4.25,0.55);
		\draw[line width = 0.1mm] (4,0) -- (4,0.69);
		\draw[line width = 0.1mm] (3.75,0) -- (3.75,0.85);
		\draw[line width = 0.1mm] (3.5,0) -- (3.5,1);
		\draw[line width = 0.1mm] (3.25,0) -- (3.25,1.25);
	\end{tikzpicture}
	\caption{Side view of single span suspension bridge with conventional bridge on either sides of the main span.}
\end{figure}

\subsubsection{Motivation}

In most real-world applications, three-dimensional models are a natural choice. But it may not be the most efficient or practical choice. When considering the three-dimensional models, there is a limitation on the availability of computing power that is required for these models as well as the complexity of the models. This is especially true of systems of multiple three-dimensional models. Simplifications of the models are a great way around this limitation.\\

In many applications, especially engineering, one-dimensional models such as the Timoshenko beam model is used to a great extent for most beam type applications. To do this, some assumptions about the properties of the beam are required to be made. This brings into question the validity of using a one-dimensional model over a more realistic three-dimensional model.\\

In this essay, we consider three different models for a beam. A three-dimensional elastic solid is compared to a one-dimensional beam model, namely the Timoshenko beam model. As a natural intermediate step, we will also look at a two-dimensional elastic solid derived using an assumption of plane stress.\\

The comparisons of the models are made for a cantilever beam. The comparisons between the models are made by considering the modes and natural frequencies of the models. This is a valid comparison since the solution of a vibration problems can be written in terms of a linear combination of the eigenfunctions.\\

In Chapter 1, the models for a three-dimensional elastic solid, a two dimensional elastic solid as well as a one-dimensional Timoshenko beam model is presented. In Chapter 2, we look at the exsistance and uniqueness of solutions to these linear vibration models. Chapter 3 covers the convergence of the eigenvalue problems as well as a dynamic problem. This is neccessary since we intend to use the Finite Element Method in Chapter 5 to derive and solve a static problem and the eigenvalue problem for the two and three-dimensional models. For the one-dimensional Timoshenko model, seperation of variables can be applied to obtain the eigenvalues exactly and this is done in Chapter 4. In Chapter 4, we also look at the results of an article by [] that tested the validity of the Timoshenko beam model using an empirical test.

\textcolor{red}{************************************************}\\
\subsubsection*{Research rationale and motivation}
From small transverse vibration of a linearly elastic (flat) plate [Mindlin, 1951], to a fully non-linear shell model, numerous mathematical problems are possible. (The same remark is also true for beams.) In this research project, our focus is on the small vibrations but not sufficiently small to justify a linear model.\\

In the article of [Antman,1976], we see that the author takes a rigorous mathematical approach to obtain fully general theories of non-linearly elastic rods and shells from three-dimensional theories. In a follow up article [Antman,1996], open problems of nonlinear elastic rods are investigates and references are made to 4 articles of Simo and Vu-Quoc. Where [Antman,1976] follows a vigorous math approach, [Simo and Vu-Quoc,1987] follows an engineering approach. Their work however, received wide recognition and it is worthwhile to compare their articles to the work of [Antman,1976] and [Antman,1996].\\

\subsubsection*{Problem Identification}
In applications simplified models can be used with some additional but different assumptions and it leads to different models for the same real life problem. An example of where numerous models are used to study the same real world problem is the Tacoma Narrows Bridge disaster of 1940. [Gazzola, 2013] and [McKenna,1999] both derive models for this specific problem but with different approaches. Even though both authors agree on the shortcomings of many bridge models and that non-linear theories should be used, [Gazzola, 2013] insists on using a plate to model the bridge, while [McKenna,1999] uses a beam. This gives at least two different models for the same real world problem.\\

\subsubsection*{Research aims and objectives}
The main objective of this literature study is the comparison of such models, using either analysis or a finite element method simulation. Adding assumptions to a general model leads to many different simplified models that can be applied to the same situation. It is important to investigate the differences in these models and their applicability to real world problems.\\

Calculating solutions for these models will be useful for the comparison, but due to the complexities of the problems, numerical methods are used to obtain approximate solutions. The finite element method is generally accepted to be the best for elasto-mechanics. Appropriate articles will be used to ensure convergence of the solutions.\\

This study will also look at possible simplifications to the models through the addition of more assumptions. Examples of simplifications to models is the added assumption of rigidity of a beam model. This simplifies the model from a system of partial differential equations, to a system of ordinary differential equations.\\

This masters research is an in depth literature study with a main focus on model problems on shells and rods with attention given to:
\begin{itemize}
 \item Comparison of different models for the same problem either using analysis or numerical methods.
 \item Determining existence of solutions, given that the relevant articles are available.
 \item Convergence of finite element method when calculating solutions to the model problems.
\end{itemize}
\end{document}

### 2022-10-31 files/Archive/NRF.tex
initial commit

--- 2022-10-31 files/Archive/Introduction.tex
@@
 \setcounter{chapter}{1}
-\setcounter{section}{0}
-\section{Introduction}
-
-\textcolor{red}{**********Sit in introduction*************}
-
-It is possible to derive a system of partial differential equations with corresponding boundary conditions but due to the complexity of the system, a different approach is considered.
-Consider the model problem in variational form.
-
-We consider the {\bf variational form} of the vibration problem.
-This variational problem may be used to implement the {\bf finite element method}.
-The finite element method can be used to simulate vibrations of the elastic body for both dynamic and static problems and also calculate the natural frequencies and modes of the elastic body.
-Existence and uniqueness of solutions to the problem can also be investigated using a weak version of the variational form.
-
-\subsubsection*{A Dynamic Problem}
-Find a vector valued function $u \in C(\Omega)$ such that it satisfies the equations of motion and the constitutive equations.
-Since $u \in C(\Omega)$, $u$ satisfies the boundary conditions defined on $\Sigma$ and $\Gamma$.\\
-
-Initial conditions for $u$ will need to be defined.
-
-\subsubsection*{A Static Problem}
-The static porblem is a special case of the dynamic problem  where $\partial_t^2 u = 0$. In this case, there are also no initial conditions.\\
-\textcolor{red}{**************************}
-
-\textcolor{red}{Research into the behaviour of suspension bridges is still a widely researched field by both engineers and mathematicians. This research started as several bridges suffered collapse. }
-
-\subsubsection{Different Research Approaches}
-\begin{figure}[h!]
-	\centering
-	\begin{tikzpicture}
-		\draw (3,2) -- (7,2);
-		\draw (3,2) -- (3,1.9);
-		\draw (7,2) -- (7,1.9);
-		\node at (5,2.1) {Main Span};
-
-		\draw[line width = 0.25mm] (0,0) -- (10,0);
-
-		\draw[line width = 0.5mm] (1.4,0) -- (1.4,-0.5);
-		\draw[line width = 2mm] (1.4,-0.5) -- (1.4,-0.7);
-
-		\draw[line width = 0.5mm] (2.2,0) -- (2.2,-0.5);
-		\draw[line width = 2mm] (2.2,-0.5) -- (2.2,-0.7);
-
-		\draw[line width = 0.5mm] (8.6,0) -- (8.6,-0.5);
-		\draw[line width = 2mm] (8.6,-0.5) -- (8.6,-0.7);
-
-		\draw[line width = 0.5mm] (7.8,0) -- (7.8,-0.5);
-		\draw[line width = 2mm] (7.8,-0.5) -- (7.8,-0.7);
-
-		\draw[line width = 0.5mm] (3,1.5) -- (3,-0.5);
-		\draw[line width = 2mm] (3,-0.5) -- (3,-0.7);
-
-		\draw[line width = 0.5mm] (7,1.5) -- (7,-0.5);
-		\draw[line width = 2mm] (7,-0.5) -- (7,-0.7);
-
-		\draw (5,0.4) parabola (3,1.5);
-		\draw (5,0.4) parabola (7,1.5) ;
-
-		\draw (3,1.5) -- (0.2,-0.5);
-		\draw (7,1.5) -- (9.8,-0.5);
-
-		\draw[line width = 2mm] (0.2,-0.5) -- (0.2,-0.7);
-		\draw[line width = 2mm] (9.8,-0.5) -- (9.8,-0.7);
-
-		\draw[line width = 0.1mm] (5,0) -- (5,0.4);
-		\draw[line width = 0.1mm] (5.25,0) -- (5.25,0.43);
-		\draw[line width = 0.1mm] (5.5,0) -- (5.5,0.46);
-		\draw[line width = 0.1mm] (5.75,0) -- (5.75,0.55);
-		\draw[line width = 0.1mm] (6,0) -- (6,0.69);
-		\draw[line width = 0.1mm] (6.25,0) -- (6.25,0.85);
-		\draw[line width = 0.1mm] (6.5,0) -- (6.5,1);
-		\draw[line width = 0.1mm] (6.75,0) -- (6.75,1.25);
-
-		\draw[line width = 0.1mm] (4.75,0) -- (4.75,0.43);
-		\draw[line width = 0.1mm] (4.5,0) -- (4.5,0.46);
-		\draw[line width = 0.1mm] (4.25,0) -- (4.25,0.55);
-		\draw[line width = 0.1mm] (4,0) -- (4,0.69);
-		\draw[line width = 0.1mm] (3.75,0) -- (3.75,0.85);
-		\draw[line width = 0.1mm] (3.5,0) -- (3.5,1);
-		\draw[line width = 0.1mm] (3.25,0) -- (3.25,1.25);
-	\end{tikzpicture}
-	\caption{Side view of single span suspension bridge with conventional bridge on either sides of the main span.}
-\end{figure}
-
-\subsubsection{Motivation}
-
-In most real-world applications, three-dimensional models are a natural choice.
-But it may not be the most efficient or practical choice.
-When considering the three-dimensional models, there is a limitation on the availability of computing power that is required for these models as well as the complexity of the models.
-This is especially true of systems of multiple three-dimensional models.
-Simplifications of the models are a great way around this limitation.\\
-
-In many applications, especially engineering, one-dimensional models such as the Timoshenko beam model is used to a great extent for most beam type applications.
-To do this, some assumptions about the properties of the beam are required to be made.
-This brings into question the validity of using a one-dimensional model over a more realistic three-dimensional model.\\
-
-In this essay, we consider three different models for a beam.
-A three-dimensional elastic solid is compared to a one-dimensional beam model, namely the Timoshenko beam model.
-As a natural intermediate step, we will also look at a two-dimensional elastic solid derived using an assumption of plane stress.\\
-
-The comparisons of the models are made for a cantilever beam.
-The comparisons between the models are made by considering the modes and natural frequencies of the models.
-This is a valid comparison since the solution of a vibration problems can be written in terms of a linear combination of the eigenfunctions.\\
-
-In Chapter 1, the models for a three-dimensional elastic solid, a two dimensional elastic solid as well as a one-dimensional Timoshenko beam model is presented.
-In Chapter 2, we look at the exsistance and uniqueness of solutions to these linear vibration models.
-Chapter 3 covers the convergence of the eigenvalue problems as well as a dynamic problem.
-This is neccessary since we intend to use the Finite Element Method in Chapter 5 to derive and solve a static problem and the eigenvalue problem for the two and three-dimensional models.
-For the one-dimensional Timoshenko model, seperation of variables can be applied to obtain the eigenvalues exactly and this is done in Chapter 4.
-In Chapter 4, we also look at the results of an article by [] that tested the validity of the Timoshenko beam model using an empirical test.
-
-\textcolor{red}{************************************************}\\
+\setcounter{section}{1}
+\section{NRF Research Proposal}
+\subsection*{Finite Element Analysis of Model Problems for Elastic Rods and Shells}
 \subsubsection*{Research rationale and motivation}

### 2022-10-31 files/Archive/ThermoElasticBeam.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Modelling a Suspension Bridge: A Brief History}
A common and easy to understand concept of bridges are that ``The longer the bridge, the more pilots are needed''. But the foundation of bridges are expensive. Suspension bridges are a great solution, being able to span larger distances between pilots than conventional bridges. Since the construction of the first early suspension bridges, there have been multiple collapses. The Tacoma Bridge Narrows collapse being one of the most well-known. This has sparked curiosity in various disciplines such as applied mathematics and engineering.\\

Since the cables suspending the roadbed can only exert a force in a single direction, an asymmetric non-linearity occurs. A suspension bridge also consists of various structural parts. Therefore, the modelling of a suspension bridge can be a complex and difficult undertaking.

\section{Modelling a suspension bridge: An Engineering Example}
Consider a basic model for a suspension bridge given in [Yos04]. The bridge is a symmetric four-span suspension bridge. The study looks at the bending and torsional rigidity of the towers, the sag of the main cable and applied static loads.
\\

The bridge is divided into four parts, two main spans in the centre and two edge spans on either side. This configuration results in three supporting towers. The rigidity of the centre tower is determined by two parameters, $K_{tb}$ for the bending rigidity and $K_{tt}$ for the torsional rigidity. The force that the cables exert on the towers, are modelled as elastic springs. The parameter $K_c$ describes the force that the springs act on the towers. This value $K_c$ can act in both directions parallel to the span and is dependent on the length of the span.\\

Realistically, it is not possible for the main cable to have enough tension to remain horizontal. The main cable obtains the shape of a parabola. Any elastic elongation is assumed to be negligible. The reason for this is not given.\\

The transverse (vertical) deflection of the girder or roadbed, is mainly dependent of the shape of the parabola of the main cable. Any distortion in the main cable is reflected in the transverse motion of the girder. The maximum deflection occurs in the middle of a span.
\\

The roadbed is chosen as a ``streamlined twin-box girder'' which is a three dimensional structure which is aerodynamically stable. This is to counteract the well known effect that wind can have on these multi-span suspension bridges. The article of [Xu97] presents a similar supporting structure and reduces the structure to an equivalent beam.\\

\section{Simplified Mathematical Model for a Suspended Beam}
Consider the model of a basic single span suspension bridge. This specific model consists of a main span which is suspended, connected to a conventional bridge on either side. This is illustrated in Figure 7.1. \textcolor{red}{(Maputo-Katembe bridge)}.

\text{red}{*********Skuif dalk na chapter 1 as motiveering and verduidelik al die verskillende dele (beam, plate, membrane, roadbed, pilots, ens...}
\begin{figure}[h!]
 \centering
\begin{tikzpicture}
\draw (3,2) -- (7,2);
\draw (3,2) -- (3,1.9);
\draw (7,2) -- (7,1.9);
\node at (5,2.1) {Main Span};

\draw[line width = 0.25mm] (0,0) -- (10,0);

\draw[line width = 0.5mm] (1.4,0) -- (1.4,-0.5);
\draw[line width = 2mm] (1.4,-0.5) -- (1.4,-0.7);

\draw[line width = 0.5mm] (2.2,0) -- (2.2,-0.5);
\draw[line width = 2mm] (2.2,-0.5) -- (2.2,-0.7);

\draw[line width = 0.5mm] (8.6,0) -- (8.6,-0.5);
\draw[line width = 2mm] (8.6,-0.5) -- (8.6,-0.7);

\draw[line width = 0.5mm] (7.8,0) -- (7.8,-0.5);
\draw[line width = 2mm] (7.8,-0.5) -- (7.8,-0.7);

\draw[line width = 0.5mm] (3,1.5) -- (3,-0.5);
\draw[line width = 2mm] (3,-0.5) -- (3,-0.7);

\draw[line width = 0.5mm] (7,1.5) -- (7,-0.5);
\draw[line width = 2mm] (7,-0.5) -- (7,-0.7);

\draw (5,0.4) parabola (3,1.5);
\draw (5,0.4) parabola (7,1.5) ;

\draw (3,1.5) -- (0.2,-0.5);
\draw (7,1.5) -- (9.8,-0.5);

\draw[line width = 2mm] (0.2,-0.5) -- (0.2,-0.7);
\draw[line width = 2mm] (9.8,-0.5) -- (9.8,-0.7);

\draw[line width = 0.1mm] (5,0) -- (5,0.4);
\draw[line width = 0.1mm] (5.25,0) -- (5.25,0.43);
\draw[line width = 0.1mm] (5.5,0) -- (5.5,0.46);
\draw[line width = 0.1mm] (5.75,0) -- (5.75,0.55);
\draw[line width = 0.1mm] (6,0) -- (6,0.69);
\draw[line width = 0.1mm] (6.25,0) -- (6.25,0.85);
\draw[line width = 0.1mm] (6.5,0) -- (6.5,1);
\draw[line width = 0.1mm] (6.75,0) -- (6.75,1.25);

\draw[line width = 0.1mm] (4.75,0) -- (4.75,0.43);
\draw[line width = 0.1mm] (4.5,0) -- (4.5,0.46);
\draw[line width = 0.1mm] (4.25,0) -- (4.25,0.55);
\draw[line width = 0.1mm] (4,0) -- (4,0.69);
\draw[line width = 0.1mm] (3.75,0) -- (3.75,0.85);
\draw[line width = 0.1mm] (3.5,0) -- (3.5,1);
\draw[line width = 0.1mm] (3.25,0) -- (3.25,1.25);
\end{tikzpicture}
\caption{Side view of single span suspension bridge with conventional bridge on either sides of the main span.}
\end{figure}

\subsection{Reference Configuration}
In an attempt for a simplistic mathematical model of the main span of Figure 7.1, a Timoshenko beam suspended from an elastic string by multiple linear springs. The string is clamped at both ends and is assumed to be approximately parabolic-shaped. The beam is clamped elastically on both endpoints. The linear springs can only apply an upward force when stretched beyond their natural length and can not apply a force downward. It is assumed that there are enough linear springs distributed across the length of the beam and elastic string so that it can be modelled as a single distributed force acting on the entire length of the beam and the string.
\begin{figure}[h!]
 \centering
\begin{tikzpicture}
\draw[line width = 0.25mm] (1,0) -- (9,0);

\draw[line width = 0.5mm] (1,3) -- (1,0);

\draw[line width = 0.5mm] (9,3) -- (9,0);

\draw (5,1) parabola (1,3);
\draw (5,1) parabola (9,3) ;

% \draw[line width = 0.1mm] (5,0) -- (5,1);
% 
% % \draw[line width = 0.1mm] (5.5,0) -- (5.5,1.03);
% % \draw[line width = 0.1mm] (6,0) -- (6,1.1);
% % \draw[line width = 0.1mm] (6.5,0) -- (6.5,1.29);
% % \draw[line width = 0.1mm] (7,0) -- (7,1.5);
% % \draw[line width = 0.1mm] (7.5,0) -- (7.5,1.8);
% % \draw[line width = 0.1mm] (8,0) -- (8,2.1);
% % \draw[line width = 0.1mm] (8.5,0) -- (8.5,2.55);
% % 
% % \draw[line width = 0.1mm] (4.5,0) -- (4.5,1.03);
% % \draw[line width = 0.1mm] (4,0) -- (4,1.1);
% % \draw[line width = 0.1mm] (3.5,0) -- (3.5,1.29);
% % \draw[line width = 0.1mm] (3,0) -- (3,1.5);
% % \draw[line width = 0.1mm] (2.5,0) -- (2.5,1.8);
% % \draw[line width = 0.1mm] (2,0) -- (2,2.1);
% % % \draw[line width = 0.1mm] (1.5,0) -- (1.5,2.55);

\node at (1,-0.3) {(0,0)};
\node at (9,-0.3) {($\ell$,0)};
\node at (1,3.2) {(0,h)};
\node at (9,3.2) {($\ell$,h)};
\end{tikzpicture}
\caption{Side view of the main span.}
\end{figure}

Consider the beam and elastic string in their equilibrium state. Set $w(0,t)$ as the reference points for the system. The beam has length $\ell$, and the length of the string can be calculated .

\subsection{System of Equations}
\subsubsection{Equations of Motion}
For $x \in (0,\ell)$ and $t \in [0,T]$,
\begin{eqnarray}
\delta \partial^2_{t} u(x,t) - \partial_x V_s - k(w(x,t) - u(x,t))+ k_1 \partial_t u(x,t) = 0, \\
\rho A \partial^2_{t}w(x,t) - AG\kappa^2 \partial_xV(x,t) + k(w(x,t)-u(x,t)) + k_2\partial_t w(x,t) = 0,\\
\rho I \partial^2_{t}\phi(x,t) - EI \partial_{x} M(x,t) + AG\kappa^2V(x,t) = 0. 
\end{eqnarray}

\subsubsection{Constitutive Equations}
\begin{eqnarray}
        M &=& EI\partial_x \phi,\label{TGT_3}\\
        V &=& AG\kappa^2(\partial_x w - \phi)\label{TGT_4},\\
        V_s & = & Y\partial_x u
\end{eqnarray}

In this system, $\ell$ is the length of the beam. $w$ represents the transverse displacement of the beam's cross-section and the rotation of the cross-sections is given by $\phi$. $u$ is the vertical displacement of the elastic springs. $Y$ is the tension of the string and $\delta$ the mass per unit length. $E$ is Young's modulus, $I$ the area moment of inertia, $G$ the shear modulus, $A$ the cross-section of the beam and $\rho$ the density of the beam. $\kappa$ is the shear correction factor used with Timoshenko beam theory. $k$ represents the stiffness of the elastic spring connecting the elastic string and the beam. The terms with $k_1$ and $k_2$ represent damping terms.\\

\subsubsection{Dimensionless Equations}
The dimensionless form of the Timoshenko beam model is given is Section 1.3.4. The following dimensionless constants are introduced to add to Section 1.3.4 and allow equations (7.1) to (7.3) to be written in a dimensionless form.
\[P^* = ***, \,\, Y^* = ***, \,\, k^* = ***, \,\, k_1^* = *** \ \text{ and } \ k_2^* = ***.\]

Then the system of equations in dimensionless form is given using the original notation for convenience. 
\begin{eqnarray}
P \partial^2_{t} u(x,t) - Y\partial^2_x u(x,t) - k(w(x,t) - u(x,t))+ k_1 \partial_t u(x,t) = 0, \\
\partial^2_{t}w(x,t) - \partial^2_x w(x,t) + \partial_x\phi(x,t) + k(w(x,t)-u(x,t)) + k_2\partial_t w(x,t) = 0,\\
\frac{1}{\alpha} \partial^2_{t}\phi(x,t) - \frac{1}{\beta} \partial^2_{x} \phi(x,t) + \partial_x w(x,t) + \phi(x,t) = 0. 
\end{eqnarray}

\subsection{Boundary Conditions}
The beam is clamped elastically at the endpoints and the string is fixed at the endpoints.
\[u(0,t) = 0 \ \text{ and } \ u(1,t) = 0.\]
\[w(0,t) = 0 \ \text{ and } \ w(1,t) = 0.\]
\[\partial_x \phi(0,t) = \beta \mu\phi(0,t) \ \text{ and } \ \partial_x \phi(1,t)= \beta\mu\phi(1,t).\]

\section{Analysis of a Thermoelastic Timoshenko Beam Model}
In the article [Boc20], the authors attempt to model a single span of a suspension bridge. The bridge is modelled as a cable suspended Timoshenko beam system. The assumption for using a beam is that the length $\ell$ of the beam is large compared to the sectional dimensions so that they are negligible. In this system a beam is simply supported at the endpoints. A horizontal elastic string, representing  the main cable, is fixed at both endpoints above the beam and has the same length as the beam. A distributed force, simulating the connecting vertical cables, acts between the beam and the elastic string. This distributed force is modelled as an elastic spring, acting on the entire interval $(0,\ell)$. The beam also has thermal properties, allowing the beam to expand and contract due to temperature.\\

The system for the thermoelastic beam model is given, with updated notation. For $x \in (0,\ell)$ and $t \in [0,T]$,
\begin{eqnarray}
P \partial^2_{t} u(x,t) - Y\partial^2_x u(x,t) - k(w(x,t) - u(x,t))+ k_1 \partial_t u(x,t) = 0, \\
\textcolor{red}{\rho A \partial^2_{t}w(x,t) - AG\kappa^2 \partial_x[\partial_x w(x,t) + \phi(x,t)]} + k(w(x,t)-u(x,t)) + k_2\partial_t w(x,t) = 0,\\
\textcolor{red}{\rho I \partial^2_{t}\phi(x,t) - EI \partial^2_{x} \phi(x,t) + AG\kappa^2[\partial_x w(x,t) + \phi(x,t)]} - \mu\partial_x T(x,t) = 0,\\
\partial_t T(x,t) - \tau\partial_x^2T(x,t) - \mu \partial_{x}\partial_t\phi(x,t) = 0.
\end{eqnarray}
With boundary conditions:
\begin{eqnarray*}
 u(0,t) = w(0,t) = \phi(0,t) = T(0,t) = u(\ell,t) = w(\ell,t) = \partial_x \phi(\ell,t) = T(\ell,t) = 0
\end{eqnarray*}

In this system, $\ell$ is the length of the beam and the elastic string. $w$ represents the transverse displacement of the beam's cross-section and the rotation of the cross-sections is given by $\phi$. $u$ is the vertical displacement of the elastic string. $Y$ is the elastic modulus of the string and $P$ the mass material. $E$ is Young's modulus, $I$ the area moment of inertia, $G$ the shear modulus, $A$ the cross-section of the beam and $\rho$ the density of the beam. $\kappa$ is the shear correction factor used with Timoshenko beam theory. $k$ represents the stiffness of the elastic spring connecting the elastic string and the beam. $\mu$ is a coupling coefficient depending on the material properties. The terms with $k_1$ and $k_2$ represent damping terms, and $T$ is the thermal moment with $\tau$ the thermal diffusivity.\\

\begin{itemize}
 \item \textcolor{red}{Boundary conditions het 'n probleem}
 \item \textcolor{red}{Verduidelik nie hoekom die string horisontaal is en nie parabolies nie}
 \item \textcolor{red}{Parameters vir die elastic string moet uitgefigure word}
 \item \textcolor{red}{Dimensieloosheid}
\end{itemize}

************************Nog Net in gecopy**********************
\subsubsection{Dimensionless Equations}

Set \[\tau = \frac{t}{t_0}, \,\, \xi = \frac{x}{\ell}, \,\, u^*(\xi,\tau) = \frac{u(x,t)}{\ell} \ \text{ and } \ \phi^*(\xi, \tau) = \phi(x,t).\]

The dimensionless forms of the shear force, moment and load are \[ V^{*}(\xi,\tau) = \frac{V(x,t)}{AG\kappa^2}, \quad M^{*}(\xi,\tau) = \frac{M(x,t)}{A G\kappa^2 \ell} \,\,\, \ \text{and} \ \,\,\, Q^*(\xi,\tau) = \frac{Q(x,t)\ell}{A G\kappa^2}.\]

Choose $t_0$ the same as in Section 1.3.4, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]

We introduce the dimensionless constants
\begin{equation*}
\alpha = \frac{A \ell^2}{I} \,\,\, \text{and} \,\,\, \beta
=\frac{AG\kappa^2 \ell^2}{EI}.
\end{equation*}

We also have the relation $\gamma = \frac{\beta}{\alpha}$.\\
********************************************************\\

\section{An Elastically Clamped Beam Model}
Consider the following equations of motion and constitutive equations for a Cantilever Timoshenko Beam that is clamped elastically at both endpoints.
\subsubsection*{Equations of Motion}
\begin{eqnarray}
	\partial_t^2 w &=& \partial_x V - c_1\partial_t w  +q, \label{CT_1}\\
	\frac{1}{\alpha}\partial_t^2 \phi &=& V+\partial_xM. \label{CT_2}
\end{eqnarray}

\noindent
\subsubsection*{Constitutive Equations}
\begin{eqnarray}
	M &=& \frac{1}{\beta}\partial_x \phi +c_2 \partial_t \partial_x \phi,\label{CT_3}\\
	V&=& \partial_x w - \phi.\label{CT_4}
\end{eqnarray}
The terms with $c_1$ represents vicous damping, and the term with $c_2$ represents material damping.\\

\subsubsection{Boundary Conditions}
\noindent
The boundary conditions at the (elastically) clamped ends are
\begin{eqnarray}
   w(x,\cdot) &=&  0, \label{CT_5}\\
   M(x,\cdot) &=&  \mu \phi(x,\cdot). \label{CT_6}
\end{eqnarray} at $x = 0$ and $x = 1$.\\

With these boundary conditions, $\mu$ models the elastic interaction between the surface where the beam is attached and the beam itself. As $\mu$ increases, $\phi(0,t)$ decreases and similarly as $\mu$ decreases, $\phi(0,t)$ increases. This implies the the cross-section at $x=0$ will rotate less with a larger $\mu$ hence the elastic join is `more' rigid, and the cross-section will rotate more with a smaller $\mu$, hence a `more' elastic join.\\

Consider the general form of plane stress from section \ref{ssec:3D_Model:PlaneStress}. As mentioned in \cite{Fung65}, this is not a true two-dimensional model. Using the definition of strain \eqref{eq:3D_Model:Strain} and assuming plane stress parallel to the $e_1$-$e_2$ plane,
\begin{eqnarray}
	\varepsilon_{13} &=&  \frac{1}{2}\left( \frac{\partial u_1}{\partial x_3} + \frac{\partial u_3}{\partial x_1} \right) = 0,\label{e_1}\\
	\varepsilon_{23} &=& \frac{1}{2}\left( \frac{\partial u_2}{\partial x_3} + \frac{\partial u_3}{\partial x_2} \right) = 0,\label{e_2}\\
	\varepsilon_{33} &=& \frac{\partial u_3}{\partial x_3}.\label{e_3}
\end{eqnarray}
Hence $u_1$ and $u_2$ are functions of $x_1$, $x_2$ and $x_3$, and $u_3$ is linear function with respect to $x_3$. Therefore the model is still three-dimensional in the case of general plane stress. More assumptions are required to obtain a true two-dimensional model.\\

Assume that $\sigma_{3i} = 0$ for $i = 1,2,3$ (minimum assumption for plane stress). Also assume $u_1$ and $u_2$ are functions of $x_1$ and $x_2$ only, and that the strain component $\epsilon_{33} = 0$. From \eqref{e_1} - \eqref{e_3}, it follows that
\begin{eqnarray*}
	\frac{\partial u_3}{\partial x_i} & = & 0  \ \ \ \ \textrm{ for } i = 1,2,3 \textrm{ on } \Omega.
\end{eqnarray*} 
Therefore $u_3$ is a constant and the model is two-dimensional.

\subsubsection{Hooke's law in two-dimensions}
Using the components components \eqref{stress_comp} of the stress tensor $T$, Hooke's Law \eqref{eq:3D_Model:CE-D} in two-dimensions can be written as 
\begin{eqnarray}
	T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E}) I. 
\end{eqnarray}

\end{document}

### 2022-10-31 files/Chapter1/1DModel.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}

\section{Timoshenko beam models} \label{sec:1D_Model}

Consider the classical Timoshenko model for the vibration of a beam with no damping.

\subsection{Equations of motion and constitutive equations}\label{ssec:1D_Model:EquationsOfMotion+ConstitutiveEquation}
In this section we introduce the Timoshenko beam theory for the transverse vibration of a uniform beam. For a reference of the model, \cite{Inm94} and \cite{Fu65} were used.\\

Consider a beam defined on the interval $[0,\ell]$. Let $w$ represent the transverse displacement and $\phi$ a rotation of the cross-sections of the beam.

\subsubsection*{Equations of motion}\label{sssec:1D_Model:EquationOfMotion}
\begin{eqnarray}
	\rho A \partial_t^2 w &=& \partial_x V + Q, \label{eq:1D_Model:EquationOfMotion1}\\
	\rho I\partial_t^2 \phi  &=& V + \partial_x M. \label{eq:1D_Model:EquationOfMotion2}
\end{eqnarray}
In \eqref{eq:1D_Model:EquationOfMotion1} and \eqref{eq:1D_Model:EquationOfMotion2} $\rho$ denotes the density, $A$ is the area of a cross section, $I$ is the area moment of inertia, $M$ is the moment, $V$ is the shear force and $Q$ is an external force acting on the beam.

\subsubsection*{Constitutive equations}\label{sssec:1D_Model:ConstitutiveEquation}
\begin{eqnarray}
	M &=& EI\partial_x \phi, \label{eq:1D_Model:ConstitutiveEquations1}\\
	V &=& AG\kappa^2(\partial_x w - \phi), \label{eq:1D_Model:ConstitutiveEquations2}
\end{eqnarray}
$E$ is Young's modulus, $G$ the shear modulus and $\kappa^2$ the shear correction factor.

\subsubsection*{Dimensionless form}\label{sssec:1D_Model:DimensionlessForm}
As mentioned in subsection \ref{ssec:3D_Model:DimensionlessForm}, the same dimensionless scaling is used for all the models in this dissertation.\\

Set \[\tau = \frac{t}{t_0}, \,\, \xi = \frac{x}{\ell}, \,\, w^*(\xi,\tau) = \frac{w(x,t)}{\ell} \ \text{ and } \ \phi^*(\xi, \tau) = \phi(x,t).\]

The dimensionless forms of the shear force, moment and external force density are \[ V^{*}(\xi,\tau) = \frac{V(x,t)}{AG\kappa^2}, \quad M^{*}(\xi,\tau) = \frac{M(x,t)}{A G\kappa^2 \ell} \,\,\, \ \text{and} \ \,\,\, Q^*(\xi,\tau) = \frac{Q(x,t)\ell}{A G\kappa^2}.\]

Choose $t_0$ the same as in subsection \ref{ssec:3D_Model:DimensionlessForm}, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]

As in [VV06] and [LLV09] we use the dimensionless constants
\begin{equation*}
	\alpha = \frac{A \ell^2}{I} \,\,\, \text{and} \,\,\, \beta
	=\frac{AG\kappa^2 \ell^2}{EI}.
\end{equation*}

Interestingly, it turns out that 
\begin{eqnarray*}
	\frac{\beta}{\alpha} & = & \gamma
\end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in subsection \ref{ssec:3D_Model:DimensionlessForm}.\\

\textbf{Remark} Recall that in subsection \ref{ssec:3D_Model:DimensionlessForm} the constant $G\kappa^2$ was used for the scaling of the stresses.

\subsubsection*{Dimensionless equations of motion}\label{sssec:1D_Model:DimensionlessEquationsOfMotion}
\begin{eqnarray}
	\partial_{t}^{2} w &=& \partial_{x}V + Q, \label{eq:1D_Model:EquationOfMotion1D}\\
	\frac{1}{\alpha} \partial_{t}^{2} \phi &=& V + \partial_{x}M.\label{eq:1D_Model:EquationOfMotion2D}
\end{eqnarray}
\subsubsection*{Dimensionless constitutive equations}\label{sssec:1D_Model:DimensionlessConstitutiveEquations}
\begin{eqnarray}
	M &=& \frac{1}{\beta}\partial_x \phi, \label{eq:1D_Model:ConstitutiveEquations1D}\\
	V &=& \partial_x w-\phi. \label{eq:1D_Model:ConstitutiveEquations2D}
\end{eqnarray}
The original notation is retained for convenience.

\subsection{Boundary conditions}\label{ssec:1D_Model:BoundaryConditions}
The following boundary conditions are considered for the Timoshenko beam models in this dissertation.\\

\textbf{Clamped or built-in endpoint} - At the clamped end the boundary conditions are $w = 0$ and $\phi = 0$.\\

\textbf{Free endpoint} - At the free end the boundary conditions are $M = 0$ and $V = 0$.\\

\textbf{Pinned or hinged endpoint} - At the pinned endpoint the boundary conditions are $w = 0$ and $M = 0$.\\

\textbf{Suspended endpoint} - At the pinned endpoint the boundary conditions are $V = kw$ and $M = 0$. The parameter k is the elastic constant of the linear spring that suspends the beam.

\subsection{Boundary value problems}\label{ssec:1D_Model:ModelProblems}
The following model problems are used in this dissertation.

\subsubsection*{Problem T-1}\label{sssec:1D_Model:ProblemT1}
The beam is pinned at both endpoints.\\

{Boundary Conditions}\\
\begin{eqnarray*}
	w(0,\cdot) = 0, \ \ &M(0,\cdot) = 0, \label{eq:1D_Model:ProblemT1BC1}\\
	w(1,\cdot) = 0, \ \ &M(1,\cdot) = 0. \label{eq:1D_Model:ProblemT1BC2}
\end{eqnarray*}

\subsubsection*{Problem T-2}\label{sssec:1D_Model:ProblemT2}
The beam is clamped at the left endpoint where $x = 0$, and free-hanging where $x = 1$. (In this configuration, the beam is called a cantilever beam.)\\

{Boundary Conditions}\\
\begin{eqnarray*}
	w(0,\cdot) = 0, \ \ &\phi(0,\cdot) = 0, \label{eq:1D_Model:ProblemT2BC1}\\
	M(1,\cdot) = 0, \ \ &V(1,\cdot) = 0. \label{eq:1D_Model:ProblemT2BC2}
\end{eqnarray*}

\subsubsection*{Problem T-3}\label{sssec:1D_Model:ProblemT3}
The beam is suspended at both endpoints.

{Boundary Conditions}\\
\begin{eqnarray*}
	V(0,\cdot) = k w(0,\cdot), \ \ &M(0,\cdot) = 0, \label{eq:1D_Model:ProblemT3BC1}\\
	V(1,\cdot) = -kw(1,\cdot), \ \ &M(1,\cdot) = 0. \label{eq:1D_Model:ProblemT3BC2}
\end{eqnarray*}
\textbf{Remark:} These boundary conditions are only valid for $w$ ``small enough'' for the motion to remain linear. This is explained in more detail in Section 4.4.

\subsubsection*{Problem T-4}\label{sssec:1D_Model:ProblemT4}
The beam is free at both endpoints.
{Boundary Conditions}\\
\begin{eqnarray*}
	V(0,\cdot) = 0, \ \ &M(0,\cdot) = 0, \label{eq:1D_Model:ProblemT4BC1}\\
	V(1,\cdot) = 0, \ \ &M(1,\cdot) = 0. \label{eq:1D_Model:ProblemT4BC2}
\end{eqnarray*}
An example of a free-free beam is given in Section 4.5.

\subsection{Variational form}\label{ssec:1D_Model:VariationalForm}
Let $v, \psi \in C^1[0,1]$ be arbitrary functions. Multiply by these functions in equations \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion2D} and integrate over the interval $[0,1]$ to obtain:
\begin{eqnarray*}
	\int_{0}^{1} \partial_{t}^{2} w v &=& \int_{0}^{1}\partial_{x}V v  + \int_{0}^{1} Q v ,\\
	\int_{0}^{1}\frac{1}{\alpha} \partial_{t}^{2} \phi \psi  &=& \int_{0}^{1}V \psi  + \int_{0}^{1}\partial_{x}M \psi.
\end{eqnarray*}

Integration by parts yields
\begin{eqnarray*}
	\int_{0}^{1} \partial_{t}^{2} w v &=&  - \int_{0}^{1}V v'  + \int_{0}^{1} Q v + V(\cdot,t) v(\cdot) |_0^1,\\
	\int_{0}^{1}\frac{1}{\alpha} \partial_{t}^{2} \phi \psi  &=& \int_{0}^{1}V \psi - \int_{0}^{1}M \psi' + M(\cdot,t) \psi(\cdot) |_0^1.
\end{eqnarray*}

Substitute the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations2D} to obtain

\begin{eqnarray}
	\int_{0}^{1} \partial_{t}^{2} w v  &=& -\int_{0}^{1}(\partial_x w-\phi) v'  + \int_{0}^{1} Q v \nonumber\\
	& & + \left. \partial_x w(\cdot,t) v(\cdot) \right |_0^1 -\left. \phi(\cdot,t) v(\cdot) \right |_0^1, \label{TGT_13}\\
	\int_{0}^{1}\frac{1}{\alpha} \partial_{t}^{2} \phi \psi  &=&  \int_{0}^{1} (\partial_x w - \phi) \psi   - \frac{1}{\beta} \int_{0}^{1}\partial_x \phi \psi' \nonumber \\
	& &+ \frac{1}{\beta}\partial_x \phi(\cdot,t) \psi(\cdot) |_0^1 .\label{TGT_14}
\end{eqnarray}
\subsubsection{Function spaces}\label{sssec:1D_Model:FunctionSpace}
It is convenient to define the following function spaces:
\begin{eqnarray}
	F_0[0,1] & = & \left\{f \in C^1[0,1] \ | \ f(0) = f(1) = 0 \right\} \label{eq:1D_Model:FunctionSpace1}\\
	F_1[0,1] & = & \left\{g \in C^1[0,1] \ | \ g(0) = 0 \right\} \label{eq:1D_Model:FunctionSpace2}
\end{eqnarray}

\subsubsection{Test function spaces for different problems}\label{sssec:1D_Model:TestFunction}
Problem T-1
\begin{eqnarray*}
	T[0,1] &:=& F_0[0,1] \times C^1[0,1]
\end{eqnarray*}
Problem T-2
\begin{eqnarray*}
		T[0,1] &:=& F_1[0,1] \times F_1[0,1]
\end{eqnarray*}
Problem T-3 
\begin{eqnarray*}
	T[0,1] &:=&  C^1[0,1]\times C^1[0,1]
\end{eqnarray*}
Problem T-4
\begin{eqnarray*}
		T[0,1] &:=& C^1[0,1] \times C^1[0,1]
\end{eqnarray*}

\textbf{The variational problem of the pinned-pinned beam}\\

Using the test function space for Problem T-1, the equations \eqref{TGT_13} and \eqref{TGT_14} reduce to
\begin{eqnarray}
	\int_{0}^{1} \partial_{t}^{2} w v &=& -\int_{0}^{1}(\partial_x w - \phi) v' + \int_{0}^{1} Q v, \label{eq:1D_Model:ProblemT1V1}\\
	\int_{0}^{1}\frac{1}{\alpha} \partial_{t}^{2} \phi \psi &=&   \int_{0}^{1} (\partial_x w -\phi) \psi - \frac{1}{\beta} \int_{0}^{1}\partial_x \phi \psi'.\label{eq:1D_Model:ProblemT1V2}
\end{eqnarray}
for all $v, \psi \in T[0,1]$.

\subsubsection{Bilinear forms}
For $f,g \in T[0,1]$, define the bilinear forms
\begin{eqnarray}
	c(f,g) & = & \int_0^1  \partial_t^2 f_1 g_1 + \frac{1}{\alpha}\int_0^1  \partial_t^2 f_2g_2, \label{eq:1D_Model:Bilinear} \\ 
	b(f,g) & = &   \int_0^1 (f_1'-f_2)(g_1' - g_2) + \frac{1}{\beta}\int_0^1  f_2' g_2', \label{eq:1D_Model:Bilinear_c}
\end{eqnarray}
Define the integral
\begin{eqnarray}
	(f,g) &=& \int_{0}^1 fg \label{eq:1D_Model:Bilinear_int}
\end{eqnarray} for all $f,g \in L^2(0,1).$\\

\textbf{Remark}\\
$L^2(a,b)$ is the space of all square integrable functions on the interval $(a,b)$. The inner product is defined by $\displaystyle (f,g) = \int_a^b fg$, and the induced norm $\displaystyle ||f|| = \int_a^b f^2$. See the appendix for more information.\\

\textcolor{red}{***********Maak seker L2 is in die appendix!.}\\

\subsubsection*{Problem T-1V}\label{sssec:1D_Model:ProblemT1V}
Find a function ${u} = \langle w, \phi \rangle$ such that for all $t >0$, ${u} \in  T[0,1]$ satisfying
\begin{eqnarray}
	c(\partial_t^2 u,{\phi}) &=& -b({u},{\phi}) + (Q,{\phi})
\end{eqnarray} for each ${\phi} = \langle v, \psi \rangle \in T[0,1]$. \\

\textbf{The variational problem of the cantilever beam.}\\

Using the test function space for Problem T-2, the equations \eqref{TGT_13} and \eqref{TGT_14} reduce to
\begin{eqnarray}
	\int_{0}^{1} \partial_{t}^{2} w v &=& -\int_{0}^{1}(\partial_x w - \phi) v' + \int_{0}^{1} Q v, \label{eq:1D_Model:ProblemT1V1}\\
	\int_{0}^{1}\frac{1}{\alpha} \partial_{t}^{2} \phi \psi &=&   \int_{0}^{1} (\partial_x w -\phi) \psi - \frac{1}{\beta} \int_{0}^{1}\partial_x \phi \psi',\label{eq:1D_Model:ProblemT1V2}
\end{eqnarray}
for all $v, \psi \in T[0,1]$.\\

This variational form is the same as for the case of the pinned-pinned beam, Problem T-1 as discussed above. Therefore the bilinear forms \eqref{eq:1D_Model:Bilinear} and \eqref{eq:1D_Model:Bilinear_c} can be used.

\subsubsection*{Problem T-2V}\label{sssec:1D_Model:ProblemT1V}
Find a function ${u} = \langle w, \phi \rangle$ such that for all $t >0$, ${u} \in  T[0,1]$ satisfying
\begin{eqnarray}
	c(u,{\phi}) &=& -b({u},{\phi}) + (Q,{\phi}) \label{var_form_timo}
\end{eqnarray} for each ${\phi} = \langle v, \psi \rangle \in T[0,1]$. \\

\textbf{Remark} The formulation of Problem T-3V and Problem T-4V are the same. But there are some complications for Problem T-3V, which are discussed in Chapter 4.\\

The application for the Timoshenko beam theory are continued in Chapters 2,4 and 6. In Chapter 2, the cantilever beam is used an example to the existence theory. In Chapter 4, modal analysis is applied to the free-free and cantilever beam. The free-free and suspended beams are also used to discuss an empirical study. In Chapter 6, the cantilever beam is used in the comparison of our linear models.

\end{document}

### 2022-10-31 files/Chapter1/2DModel.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Two-dimensional model problem for an elastic solid} \label{sec:2D_Model}
\subsection{Introduction}
The following derivation of the two-dimensional model is based on my own work, using the textbook \cite{Sadd05} as a guide.\\

Assume that $\sigma_{3i} = 0$ for $i = 1, 2, 3$\textcolor{red}{;} $\partial_3 u_1 = 0$, $\partial_3 u_2 = 0$ ($u_1$ and $u_2$ are functions of $x_1$ and $x_2$), and the strain component $\varepsilon_{33} = 0$. Then using the definition of strain 
\begin{eqnarray}
	\partial_i u_3 = 0 \quad \textrm{ for } i = 1,2,3 \textrm{ on } \Omega.
\end{eqnarray}

It follows that $u_3$ is a constant on $\Omega$ and $u$ is a vector valued function in $R_2$ with two-dimensional stress and strain. The out of plane conditions for strain \eqref{plane_stress_neseccary_condition} falls away and Hooke’s law can be written in a two-dimensional form using the stress components (1.2.16) as $\displaystyle T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E})I.$\\

\subsection{Equations of motion and constitutive equations}\label{ssec:2D_Model:EquationsOfMotion+ConstitutiveEquations}
 The following equations of motion and constitutive equations follow from subsections \ref{ssec:3D_Model:DimensionlessForm} and 1.3.2.
\subsubsection{Equation of motion}\label{sssec:2D_Model:EquationOfMotion}
\begin{eqnarray}
	\partial_t^2 u & = & \textrm{div}T + Q, \label{eq:2D_Model:EM}
\end{eqnarray}
where
\begin{eqnarray}
	\textrm{div} T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} \\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22}
	\end{bmatrix}. \label{eq:2D_Model:DivT}
\end{eqnarray}
\subsubsection{Constitutive equation}\label{sssec:2D_Model:ConstitutiveEquation}
\begin{eqnarray}
	T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E}) I. \label{eq:2D_Model:CE}
\end{eqnarray}

\subsection{Model problem}\label{ssec:2D_Model:ModelProblem}
Suppose $\Omega \subset R_2$ is the reference configuration for a solid executing small vibrations. The boundary of $\Omega$ consists of two parts $\Sigma$ and $\Gamma$. The model problem is described as:
\begin{itemize}
    \item[] The equation of motion \eqref{eq:2D_Model:EM} and constitutive equation \eqref{eq:2D_Model:CE} are satisfied in $\Omega$.
	\item[] The displacement $u$ is specified on $\Sigma$;
	\item[] Traction $Tn$ is specified on $\Gamma$.
\end{itemize}

\subsubsection{Problem 2D-1}\label{sssec:2D_Model:Problem2D1}
Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:\\

Boundary Conditions:\\
\begin{eqnarray*}
	u & = & 0 \quad \textrm{ on } \Sigma,\\
	Tn & = & 0 \quad \textrm{ on } \Gamma.
\end{eqnarray*} with $n$ the outward unit normal.

\subsection{Variational form}\label{ssec:2D_Model:VariationalForm}
The steps to derive the variational form is almost identical to the case of the three-dimensional case. Therefore it is not shown again and only the differences are discussed. \\

Instead of volume integrals ($dV$) and surface integrals ($dS$), the two-dimensional model has area ($dA$) and line integrals ($ds$). Rather than the divergence formula, the divergence form of Green's formula is used to obtain the following result:
\begin{eqnarray*}
	\int_{\Omega} \textrm{div}(T)\cdot \phi \ dA & = & -\int_{\Omega} \textrm{Tr}(T\Phi) \ dA + \int_{\Gamma} Tn\cdot \phi ds.
\end{eqnarray*}

The general variational form of the two-dimensional model is given as
\begin{eqnarray*}
	\int_\Omega~ (\partial^2_t u) \cdot \phi~dA & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dA + \int_\Omega~ Q \cdot \phi~dA
	+ \int_\Gamma~Tn \cdot \phi~ds,
\end{eqnarray*}
with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.

\subsubsection{Bilinear forms and integral}\label{sssec:2D_Model:BilinearForm}
Define the bilinear forms
\begin{eqnarray}
	b(u,\phi) = \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dA \label{eq:2D_Model:Bilinear}
\end{eqnarray}
and
\begin{eqnarray}
	c(u,\phi) = \int_\Omega~ (\partial^2_t u) \cdot \phi~dA \label{eq:2D_Model:Bilinear_c}
\end{eqnarray}
with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.\\
Also define the integral
\begin{eqnarray}
	(f,g) &=& \int_{\Omega} f\cdot g \ dA \label{eq:2D_Model:Bilinear_int}
\end{eqnarray}

\subsubsection{Test functions for problem 2D-1}\label{sssec:2D_Model:TestFunctions2D1}
The test function space has the same definition of the test function space for Problem 3D-1. But since $\Omega \in R_2$, we have that $T(\Omega) \subset R_2$.
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
\end{eqnarray*}

\subsubsection{Problem 2D-1V}\label{sssec:2D_Model:Problem2D1V}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{eq:2D_Model:Problem2D1VEq}
\end{align}
for all $\phi \in T(\Omega)$.\\

 Applications are continued in Chapter 5 and 6. In Chapter 5, the finite element analysis is applied to a cantilever beam to solve the eigenvalue problem. In Chapter 6, a cantilever beam in used in the comparison of our linear models.

\end{document}

### 2022-10-31 files/Chapter1/3DModel.tex
initial commit

 \documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Model problem for a three-dimensional elastic solid} \label{sec:3D_Model}
In this section we introduces the linear theory for a three-dimensional elastic solid. The textbook of Fung \cite{Fung65} with some changes in the notation. \\

 The equation of motion and constitutive equation are given in subsection \ref{ssec:3D_Model:EquationOfMotion}. The dimensionless form of the equation of motion and constitutive equation are derived in subsection \ref{ssec:3D_Model:DimensionlessForm}. Model problems are presented in subsection \ref{ssec:3D_Model:ModelProblems}. The variational form for the vibration problem is given in section \ref{ssec:3D_Model:VariationalForm}. Plane stress is discussed in section \ref{ssec:3D_Model:PlaneStress} \\

\subsection{Equations of motion and constitutive equations} \label{ssec:3D_Model:EquationofMotion+ConstitutiveEquation}
Consider a vector valued function $u$ defined on domain $\Omega \subset {R}^3$ where $u$ describes the displacement of $\Omega$ in ${R}^3$.
\subsubsection{Equation of motion}\label{ssec:3D_Model:EquationOfMotion}
\begin{eqnarray}
	\rho\partial_t^2 u & = & \textrm{div}T + Q. \label{eq:3D_Model:EM}
\end{eqnarray}

In \eqref{eq:3D_Model:EM}, $\rho$ is the density of the elastic body, $T$ is the stress tensor with components $\sigma_{ij}$, $Q$ is an external body force acting on $\Omega$ and $\textrm{div}T$ is the divergence of the tensor $T$ and represented by
\begin{eqnarray}
	\textrm{div}  T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13}\\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23}\\
		\partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
	\end{bmatrix}. \label{eq:3D_Model:divT}
\end{eqnarray}

Only small vibrations are considered. This means that the local displacements and rotations are small and hence the stress tensor $T$ is symmetric. Let $\textrm{Tr}(T)$ denote the trace of the stress tensor T, that is
\begin{eqnarray}
	\textrm{Tr}(T) & = & \phi_{11} + \phi_{12} + \phi_{13}. \label{eq:stress_tensor_t}
\end{eqnarray}

\textbf{Remark} Some books prefer to use $\rho Q$ for the external body force, but $Q$ is also correct. $Q$ is then a force per unit volume.

\subsubsection*{Strain}\label{sssec:3D_Model:Strain}
Infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$ with components
\begin{eqnarray}
	\varepsilon_{ij} = \frac{1}{2}\left( \frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} \right). \label{eq:3D_Model:Strain}
\end{eqnarray}

In this dissertation, we only consider isotropic materials. As a consequence, the constitutive equation (Hooke's law) takes the following form.

\subsubsection*{Hooke's law in terms of $E$ and $\nu$}\label{sssec:3D_Model:Hooke'sLaw1}
\begin{eqnarray}
	\mathcal{E} = \left( \frac{1+\nu}{E} \right)T - \frac{\nu}{E}\textrm{Tr}(T)I,  \label{eq:3D_Model:HL}
\end{eqnarray} where $E$ is Young's Modulus and $\nu$ is Poisson's ratio.

\subsubsection*{Hooke's law in the alternative form}\label{sssec:3D_Model:Hooke'sLaw2}
If the principal stresses $\sigma_i$ are all non-zero, then Hooke's law can be written in the following form
\begin{eqnarray}
	T = \left( \frac{E}{1+\nu} \right)\mathcal{E} + \frac{\nu E}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \label{eq:3D_Model:CE}.
\end{eqnarray}
$\textrm{Tr}(\mathcal{E}) = \epsilon_{11} + \epsilon_{12} + \epsilon_{13}$ is the trace of the strain operator $\mathcal{E}$.\\

Hooke's Law \eqref{eq:3D_Model:CE} is the constitutive equation for the three-dimensional elastic model used in problems. Conditions for the problems to be well posed, is discussed in Chapter 2.

\subsection{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
The dimensionless form of the equation of motion and constitutive equation are derived in this subsection. Suppose $\ell$ represents some notable dimension (eg.the length) of the elastic body and $G$ the shear modulus of elasticity.\\

Set \[\tau = \frac{t}{t_0},\quad \xi_i = \frac{x_i}{\ell},\quad {u}^*(\xi,\tau) = \frac{1}{\ell}{u}(x,t), \quad Q^{*} = \ell G \kappa^2 Q, \]
\[ \text{and} \ \,\,\, \sigma_{ij}^*(\xi,\tau) = \frac{1}{G\kappa^2}\sigma_{ij}(x,t),\]

where $\kappa^2$ is a dimensionless constant and $t_0$ must be specified. A convenient choice for $t_0$ (see section \ref{sec:1D_Model}) is \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]

Substitution into \eqref{eq:3D_Model:EM} and yields
\begin{eqnarray*}
	\partial_{\tau} u^{*} = \textrm{div}T^* + Q^*.
\end{eqnarray*}
where $T^* = \sigma_{i,j}^*(\xi,\tau)$.\\

The dimensionless form of \eqref{eq:3D_Model:HL} and \eqref{eq:3D_Model:CE} are
\begin{eqnarray*}
	\mathcal{E} = \frac{G \kappa^2}{E} \left[ (1+\nu)T^* - \nu \textrm{Tr}(T^*)I \right]
\end{eqnarray*}

and
\begin{eqnarray*}
	T^* = \frac{E}{G \kappa^2} \left[\left( \frac{1}{1+\nu} \right)\mathcal{E} + \frac{\nu}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \right]
\end{eqnarray*}

Introduce a dimensionless constant
\begin{eqnarray*}
	\gamma= \frac{G\kappa^2}{E}.
\end{eqnarray*} Using this dimensionless constant, 
\begin{eqnarray}
	\mathcal{E} = \gamma(1+\nu)T^* - \gamma\nu \textrm{Tr}(T^*)I \label{DM_H_E} 
\end{eqnarray}
and
\begin{eqnarray}
	T^* = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I. \label{DM_H_T}
\end{eqnarray}

\textbf{Remark} The constant $G\kappa^2$ is introduced to allow for comparisons of the models in later chapters. The constant comes from the Timoshenko beam theory and is explained in section \ref{sec:1D_Model} \\

In the rest of section 1.2 the original notation is retained for convenience.

\subsubsection*{Equations of motion in dimensionless form}\label{sssec:3D_Model:EquationOfMotionDimensionless}
\begin{eqnarray}
	\partial_t^2 u & = & \textrm{div}T + Q \label{eq:3D_Model:EM-D}
\end{eqnarray}
with
\begin{eqnarray}
	\textrm{div}  T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13}\\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23}\\
		\partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
	\end{bmatrix}.\label{eq:3D_Model:divT-D}
\end{eqnarray}

\subsubsection*{Constitutive equations in dimensionless form}\label{sssec:3D_Model:ConstitutiveEquationsDimensionless}
\begin{eqnarray}
	T = \frac{1}{\gamma(1+\nu)} \mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \label{eq:3D_Model:CE-D}
\end{eqnarray}

\subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
Suppose $\Omega \subset R_3$ is the reference configuration for a solid executing small vibrations. The boundary of $\Omega$ can be divided into two distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be considered a model problem for a three-dimensional elastic body.
\begin{enumerate}
	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} is satisfied in $\Omega$;
	\item[] Hooke's law \eqref{eq:3D_Model:CE-D} is satisfied in $\Omega$;
	\item[] The displacement $u = u_\Sigma$ is specified on
	$\Sigma$;
	\item[] The traction $Tn = t_\Gamma$ is specified on
	$\Gamma$.
\end{enumerate}

The two model problems considered in this dissertation are described below.

\subsubsection{Problem 3D-1}\label{sssec:3D_Model:Problem3D1}
Find a vector valued function $u$, satisfying equations \eqref{eq:3D_Model:EM-D} to \eqref{eq:3D_Model:CE-D} and the following boundary conditions:\\

Boundary Conditions:
\begin{eqnarray*}
	u & = & 0 \quad \textrm{ on } \Sigma\\
	Tn & = & 0 \quad \textrm{ on } \Gamma
\end{eqnarray*} With $n$ the outward normal vector to $\Omega$.

\subsubsection{Problem 3D-2}\label{sssec:3D_Model:Problem3D2}
Find a vector valued function $u$, satisfying equations \eqref{eq:3D_Model:EM-D} to \eqref{eq:3D_Model:CE-D} and the following boundary conditions:\\

Boundary Conditions:
\begin{eqnarray*}
	Tn & = & 0 \quad \textrm{ on } \partial\Omega
\end{eqnarray*} With $n$ the unit outward normal vector.

\subsection{Variational form}\label{ssec:3D_Model:VariationalForm}
Let $\phi \in C({\Omega})$ be an arbitrary vector valued function. Multiplying $\phi$ to equation \eqref{eq:3D_Model:EM-D} and integrating over the domain $\Omega$ results in,

\begin{eqnarray*}
	\int_{\Omega} (\partial_t^2 u)\cdot \phi \ dV & = & \int_{\Omega} (\textrm{div} T)\cdot \phi \ dV + \int_{\Omega} Q \cdot \phi \ dV.
\end{eqnarray*}

Since the stress tensor T is symmetric, 
\begin{eqnarray*}
	\textrm{div}(T\phi) & = & (\textrm{div}T)\cdot \phi + \textrm{Tr}(T\Phi),
\end{eqnarray*}
where
\begin{eqnarray*}
	\Phi & = &
	\begin{bmatrix}
		\partial_1 \phi_1 & \partial_2 \phi_1 & \partial_3 \phi_1 \\
		\partial_1 \phi_2 & \partial_2 \phi_2 & \partial_3 \phi_2 \\
		\partial_1 \phi_3 & \partial_2 \phi_3 & \partial_3 \phi_3
	\end{bmatrix},
\end{eqnarray*}
and 
\begin{eqnarray*}
	\textrm{Tr}(T\Phi) & = & \sigma_{11} \partial_1\phi_1 + \sigma_{12}\partial_1 \phi_2 + \sigma_{13}\partial_1 \phi_3 + \sigma_{21}\partial_2 \phi_1 + \sigma_{22}\partial_2\phi_2 + \sigma_{23}\partial_2 \phi_3 \nonumber \\
	& & + \sigma_{31}\partial_3 \phi_1 + \sigma_{32}\partial_3\phi_2 + \sigma_{33}\partial_3 \phi_3.
	\label{Trc}
\end{eqnarray*}

Using the Divergence Theorem and the symmetry of T,
\begin{eqnarray*}
	\int_{\Omega} \textrm{div}(T\phi) \ dV & = & \int_{\partial \Omega} T\phi \cdot n \ dS,\\
	& = & \int_{\partial \Omega} Tn \cdot \phi \ dS.
\end{eqnarray*}

The divergence formula gives
\begin{eqnarray*}
	\int_{\Omega} \textrm{div}(T)\cdot \phi \ dV & = & -\int_{\Omega} \textrm{Tr}(T\Phi) \ dV + \int_{\partial \Omega} Tn\cdot \phi dS.
\end{eqnarray*}
Therefore,
\begin{align*}
	\int_{\Omega} (\partial_t^2 u)\cdot \phi \ dV = -\int_{\Omega} \textrm{Tr}(T\Phi) \ dV  + \int_{\Omega} Q\cdot\phi \ dV + \int_{\partial \Omega} Tn\cdot \phi \ dS.
\end{align*}
\\

The general variational form of the three-dimensional model is given as
\begin{eqnarray*}
	\int_\Omega~ (\partial^2_t u) \cdot \phi~dV & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dV + \int_\Omega~ Q \cdot \phi~dV
	+ \int_{\partial \Omega}~Tn \cdot \phi~dS,
\end{eqnarray*}
with $ \displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.\\

\subsubsection{Bilinear forms and integral}\label{sssec:3D_Model:BilinearForm}
Define the bilinear forms
\begin{eqnarray}
	b(u,\phi) = \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dV \label{eq:3D_Model:Bilinear}
\end{eqnarray}
and
\begin{eqnarray}
	c(u,\phi) = \int_\Omega~ (\partial^2_t u) \cdot \phi~dV \label{eq:3D_Model:Bilinear_c}
\end{eqnarray}
with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.\\

Also define the integral
\begin{eqnarray}
	(f,g) &=& \int_{\Omega} f\cdot g \ dV \label{eq:3D_Model:Bilinear_int}
\end{eqnarray}

\subsubsection{Test functions}\label{sssec:3D_Model:TestFunction}
Define the following set of test functions $T(\Omega)$ for Problem 3D-1 and Problem 3D-2:\\

Problem 3D-1
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}
\end{eqnarray*}

Problem 3D-2
\begin{eqnarray*}
	T(\Omega) & = &  C^1(\bar{\Omega})
\end{eqnarray*}

The variational problem of Problem 3D-1 is given as Problem 3D-1V.

\subsubsection{Problem 3D-1V}\label{sssec:3D_Model:Problem3D1V}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi), \label{eq:3D_Model:Problem3D1VEq}
\end{align}
for all $\phi \in T(\Omega)$\\

The well-posedness of the model is treated in Chapter 2, where Korn's inequality is presented. Applications are continued in Chapter 4, 5 and 6. In Chapter 4, a free-free three-dimensional beam is discussed as part of an empirical study. In Chapter 5, the finite element analysis is applied to a cantilever beam to solve the eigenvalue problem. In Chapter 6, a cantilever beam in used in the comparison of our linear models.

\subsection{Plane stress}\label{ssec:3D_Model:PlaneStress}
When the stresses in an elastic body act parallel to a single plane, it is referred to as plane stress.\\

Consider the right-hand orthonormal set $\left\{e_1, e_2, e_3\right\}$. Without loss of generality, assume the stresses act parallel to the $e_1$-$e_2$ plane i.e. $\sigma_{3i} = 0$ for all $i$. From Hooke's Law \eqref{DM_H_E} the following equations are obtained:

\begin{equation}
	\begin{aligned}
		\varepsilon_{11} & =  \gamma  ( \sigma_{11} - \nu \sigma_{22}) \qquad \qquad \varepsilon_{33} & = & - \gamma \nu (\sigma_{11} + \sigma_{22})\\
		\varepsilon_{22} & =   \gamma (\sigma_{22} - \nu\sigma_{11}) \qquad \qquad \varepsilon_{12} & = & \  \gamma (1+\nu) \sigma_{12} \label{strain_comp}
	\end{aligned}	
\end{equation}

and a sufficient condition
\begin{eqnarray}
	\varepsilon_{13} =  \varepsilon_{23} = 0.
\end{eqnarray}

After some manipulation, we verify the following equations for the stress components given in \cite{Fung65}.

\noindent
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)} ( \varepsilon_{11} + \nu\varepsilon_{22})\\
		\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)} (\nu \varepsilon_{11} + \varepsilon_{22}).
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray}
		\sigma_{12} & = & \frac{1}{\gamma(1+\nu)} \varepsilon_{12} \label{stress_comp}
	\end{eqnarray}
\end{minipage}\\

Another necessary strain condition for plane stress is found by substituting $\sigma_{11}$ and $\sigma_{22}$ from \eqref{stress_comp} into $\varepsilon_{33}$ in \eqref{strain_comp} to obtain
\begin{eqnarray}
	\varepsilon_{33} = -\frac{\nu}{1-\nu} (\varepsilon_{11} + \varepsilon_{22}).\label{plane_stress_neseccary_condition}
\end{eqnarray}

This is known as general plane stress. In this dissertation only a special case of general plane stress is considered in section \ref{sec:2D_Model}.

\end{document}

### 2022-10-31 files/Chapter1/NonlinearBeamTheory.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\setcounter{chapter}{1}
\setcounter{section}{6}
\begin{document}
\section{Rod Theory}
In the literature the word rod is often used for a one-dimensional
continuum for example linear and nonlinear beams but also hoses
..... ................ .............. Cosserat .........
[LA12]

J C Simo and L Vu-Quoc published a number of articles on beams and
plates. What is interesting to us here is [SV87] where they consider
``The role of nonlinear theories in transient dynamic analysis of
flexible structures". They state that large motion of beams and
plates has been studied since 1958 and consider 12 publications up
to 1986. The authors discuss shortcomings and wrong results in some
detail. What we also find interesting is that the article [Ant76] is
not mentioned.

It is clear from [Ant72] ~~ +  ~ [Ant76] that Antman follows a
rigorous mathematical approach to the theories on beams and plates.
Antman published a {\bf survey} article [Ant96] on nonlinearly
viscoelastic and elastic rods. According to him, some equations of
rods attained a form suitable for mathematical analysis in the ten
years preceding his 1996 paper. The articles he referred to were all
published by J C Simo and L Vu-Quoc. In our opinion this means that
he suggests a study of the connections between the two approaches
worth while.

A study of all the results mentioned above to ..................
.........\\ ................................................ \\
is beyond the scope of this literature study (especially since we
also aim to include detailed applications). ...................
\\ the aim of this study is comparison of different models for the
same application. A start is to restrict the study to planar motion
of a beam where the material is linearly elastic as in [VDB16].
\end{document}

### 2022-10-31 files/Chapter1/PlateModel.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
	\section{Reissner-Mindlin Plate Model} \label{sec:P_Model}
	Consider small vibrations of a plate. This motion can be described by using spherical coordinates. Assume that the plate has a two dimensional domain $\Omega \subset R_2$. For $r \geq 0$, the coordinates $x_1$ and $x_2$ can be rewritten as
	\[ x_1 = r \sin \phi \cos \theta, \]
	\[ x_2 = r \sin \phi \sin \theta. \]

	Let
	\[ r = \sqrt{q^2 + x_3^2},~~~\sin \phi = \frac{q}{r}~~~\textrm{and}~~~\cos \theta = \frac{x_3}{r}.\]
	and define the unit vectors
	\begin{eqnarray*}
		\bar e_r &=& \cos \theta ~\bar e_1 + \sin \theta ~\bar e_2,\\
		\bar e_n &=& \sin \phi~\bar e_r + \cos \psi~\bar e_3, \\
		\bar e_\phi &=& \cos \phi~\bar e_r - \sin \psi~\bar e_3.
	\end{eqnarray*}

	Any point on the plate can be described by
	\[ \bar{x} = x_1 \bar e_1 + x_2 \bar e_2 + x_3 \bar e_3 = q \bar e_r + x_3 \bar e_3. \]

	Let $w$ represent the displacement of the plate body and $\psi$ the angle between the material line and a line perpendicular to the plate. In the spherical coordinate form, the angle can easily be calculated for the directions of $\bar{e}_1$ and $\bar{e}_2$, i.e.
	\begin{eqnarray*}
		\psi_1 & = & \frac{q}{r} \bar{e}_r \cdot \bar{e}_1, \\
		\psi_2 & = & \frac{q}{r} \bar{e}_r \cdot \bar{e}_2.
	\end{eqnarray*}
	Define
	\begin{eqnarray*}
		{\psi} = \langle \psi_1 \  \psi_2\rangle = \langle \sin\phi \cos \theta \ \ \sin\phi \sin \theta\rangle.
	\end{eqnarray*}

	The plate model in consideration is restricted to a linear model. Therefore $\sin\phi$ can be approximated by $\phi$ such that
	\begin{eqnarray*}
		{\psi} = \langle \psi_1 \  \psi_2\rangle = \langle \phi \cos \theta \ \ \phi \sin \theta \rangle.
	\end{eqnarray*}

	The equations for the Reissner-Mindlin plate model is given in the next section. The model is restricted to the linear theory.

	\subsection{Equations of Motion and Constitutive Equations}\label{ssec:P_Model:EquationsOfMotion+ConstitutiveEquation}
	Consider a Reissner-Mindlin plate with reference configuration $\Omega \in R_2$. Let $u \in \Omega$ define the transverse motion of the plate model and $\psi = \langle \psi_1 \ \psi_2 \rangle$ the angle between the material line and a line perpendicular to the plate.

	\subsubsection*{Equations of Motion}\label{sssec:P_Model:EquationsOfMotion}
	\begin{eqnarray}
		\rho h \partial_t^2 w & = & \textrm{div} Q + q \label{eq:P_Model:EM1}\\
		\rho I \partial_t^2 {\psi} & = & \textrm{div} M - Q \label{P2}\label{eq:P_Model:EM1}
	\end{eqnarray}
	In these equations $\rho$ denotes the density of the plate, $\displaystyle I = \frac{h^3}{12}$ the length moment of inertia, $M$ the moment density and $Q$ the shear force density. The parameter $q$ is an external force acting on the plate. The moment density is defined as

	\begin{eqnarray*}
		M = 
		\begin{bmatrix}
			M_{11} & M_{12}\\
			M_{21} & M_{22}
		\end{bmatrix}.
	\end{eqnarray*}

	\subsubsection*{Constitutive Equations}\label{sssec:P_Model:ConstitutiveEquation}
	For the linear model, the constitutive equations are defined as:
	\begin{eqnarray}
		Q & = & \kappa^2 G h(\nabla w + \psi) \label{eq:P_Model:CE1} \\
		M_{11} & = & \frac{1}{2} D \left[2(\partial_1 \psi_1 + \nu \partial_2 \psi_2)\right]  \label{eq:P_Model:CE2}\\
		M_{12} =  M_{21} & = & \frac{1}{2} D \left[(1-\nu)(\partial_1 \psi_2 + \nu \partial_2 \psi_2)\right] \label{eq:P_Model:CE3} \\
		M_{22} & = & \frac{1}{2} D \left[2(\partial_2 \psi_2 + \nu \partial_1 \psi_1)\right] \label{eq:P_Model:CE4}
	\end{eqnarray}
	where $G$ is the shear modulus, $\kappa^2$ a shear correction factor and $D$ is a measure of stiffness for the plate and is defined by
	\begin{eqnarray*}
		D & = & \frac{EI}{1-\nu^2}
	\end{eqnarray*}
	where $E$ is Young's modulus and $\nu$ Poisson's ratio.\\

	In classical plate theory, $\psi = -\nabla w$ and the constitutive equation for $Q$ is excluded.

	\subsection{Dimensionless Form}\label{ssec:P_Model:DimensionlessForm}

	Set
	\[\tau = \frac{t}{t_0}, \,\, \quad \xi_1 = \frac{x_1}{\ell}, \,\, \quad \xi_2 = \frac{x_2}{\ell},\] 
	\[w^*(\xi,\tau) = \frac{w(x,t)}{\ell} \ \text{ and } \ {\psi}^*(\xi, \tau) = {\psi}(x,t).\]

	The dimensionless forms of the force density, moment density and load can be constructed as \[ Q^{*}(\xi,\tau) = \frac{Q(x,t)}{\ell G\kappa^2}, \quad M^{*}(\xi,\tau) = \frac{M(x,t)}{\ell^2 G\kappa^2} \,\,\, \ \text{and} \ \,\,\, q^*(\xi,\tau) = \frac{q(x,t)}{G\kappa^2}.\]

	Choose $t_0$ the same as in Section 1.3.4, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]

	The dimensionless constants are
	\[h = \frac{h}{\ell}, \,\, \quad I^* = \frac{h^3}{12} \ \text{ and } \  \beta = \frac{\ell^3G\kappa^2}{EI}.\]

	\subsubsection{Remark}
	Similar to the model in section \ref{ssec:3D_Model:DimensionlessForm}, the constant $G$ is introduced to allow for the comparison of models in later chapters. It will also be required that $\kappa$ is the same for the beam and plate models.

	\subsubsection{Dimensionless Equations of Motion}\label{sssec:P_Model:EquationsOfMotionD}
	\begin{eqnarray}
		h \partial_t^2 w & = & \textrm{div} Q + q \label{eq:P_Model:EM1D} \\
		I \partial_t^2 {\psi} & = & \textrm{div} M - Q \label{eq:P_Model:EM2D_chap1}
	\end{eqnarray}
	\subsubsection{Dimensionless Constitutive Equations}\label{sssec:P_Model:ConstitutiveEquationsD}
	\begin{eqnarray}
		Q & = & h(\nabla w + \psi) \label{eq:P_Model:CE1D}\\
		M_{11} & = & \frac{1}{2\beta(1-\nu^2)} \left[ 2(\partial_1\psi_1 + \nu \partial_2 \psi_2 \right] \label{eq:P_Model:CE2D}\\
		M_{12} = M_{21} & = & \frac{1}{2\beta(1-\nu^2)} \left[ (1-\nu)(\partial_1\psi_2 + \partial_2 \psi_1) \right] \label{eq:P_Model:CE3D}\\
		M_{11} & = & \frac{1}{2\beta(1-\nu^2)} \left[ 2(\partial_2 \psi_2 + \nu \partial_1 \psi_1)\right] \label{eq:P_Model:CE4D_chap1}
	\end{eqnarray}
	\subsection{Boundary Conditions}\label{ssec:P_Model:BoundaryConditions}
	The boundary conditions are applied along an edge of a plate. Let $n$ be the outward normal of the edge, and $\tau$ be a unit vector tangent to that edge.\\

	Some commonly used boundary (or edge) conditions are:\\

	Free Edge:
	\[Mn\cdot n = 0, \ \ Mn\cdot \tau = 0 \ \ \textrm{ and }\ Q\cdot n = 0 \]
	Soft Supported Edge:
	\[Mn\cdot n = 0, \ \ w = 0 \ \ \textrm{ and } \ Mn \cdot \tau = 0 \]
	Rigidly Supported Edge:
	\[Mn\cdot n = 0, \ \ w = 0 \ \ \textrm{ and } \ {\psi} \cdot \tau = 0 \]
	Soft Clamped Edge:
	\[w = 0, \ \ Mn \cdot \tau = 0 \ \ \textrm{ and } \ \psi \cdot n = 0 \]
	Rigidly Clamped Edge:
	\[w = 0, \ \ \psi_1 = 0 \ \ \textrm{ and } \ \psi_2 = 0 \]

	In this dissertation, only the free edge and rigidly clamped edge boundary conditions are considered.

	\subsection{Model Problems}\label{ssec:P_Model:ModelProblems}
	Let $\Omega \subset R_2$ denote reference configuration of the plate model. Following \cite{Wu05}, $\Omega$ is a rectangle.\\

	The boundary $\partial \Omega$ can be divided into 4 distinct parts. Denote any two opposing sides by $\Sigma_0$ and $\Sigma_1$ and the remaining two opposing sides by $\Gamma_0$ and $\Gamma_1$.

	\subsubsection{Problem P-1}\label{sssec:P_Model:ProblemP1}
	Consider a cantilever plate model. In this configuration, the plate is clamped at one edge and free hanging at the rest of the boundary. With out loss of generality, assume that the plate is clamped on the edge $\Sigma_0$.\\

	Find functions $w$ and $\psi$ satisfying equations \eqref{eq:P_Model:EM1D} to \eqref{eq:P_Model:CE4D_chap1}, the boundary conditions.\\

	Boundary Conditions\\
	\[w = 0,  \ \textrm{ and } \ \psi = \bar{0} \ \textrm{ on } \Sigma_0.\]
	\[Mn\cdot n = 0,\ \ \ Mn\cdot \tau = 0, \ \textrm{ and } \ Q \cdot n =0 \ \textrm{ on } \partial\Omega\setminus\Sigma_0.\]
	with $\tau$ a unit vector perpendicular to $n$.\\

	\subsubsection{Problem P-2}\label{sssec:P_Model:ProblemP2}
	Consider a plate model that is rigidly clamped on $\partial \Omega$. Find functions $w$ and $\psi$ satisfying equations \eqref{eq:P_Model:EM1D} to \eqref{eq:P_Model:CE4D_chap1}, the boundary conditions.\\

	Boundary Conditions\\
	\[w = 0,  \ \textrm{ and } \ \psi = \bar{0} \ \textrm{ on } \partial \Omega.\]

	\subsection{Variational Form}\label{ssec:P_Model:VariationalForm}
	Let $v \in C_2^1[0,1]$ and $w \in C^1[0,1] \times C^1[0,1]$ such that $w$ is a vector valued function. Multiplication these functions to \eqref{eq:P_Model:EM1D} and \eqref{eq:P_Model:EM2D} yields:
	\begin{eqnarray*}
		\int_\Omega h \partial_t^2 w v \ dA & = & \int_\Omega \textrm{div} (Q) v \ dA + \int_\Omega q v \ dA\\
		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & \int_\Omega \textrm{div} (M) \cdot \phi \ dA - \int_\Omega Q \cdot \phi \ dA
	\end{eqnarray*}

	Following from Green's Formulas, similar to section \ref{ssec:3D_Model:VariationalForm}, 
	\begin{eqnarray*}
		\int_\Omega \textrm{div}(Q) v \ dA & = & - \int_\Omega Q \cdot \nabla v \ dA + \int_{\partial\Omega} (Q\cdot n)v ds,\\
		\int_\Omega \textrm{div}(M) \cdot \phi \ dA & = & - \int_\Omega \textrm{Tr} (M \Phi) \ dA + \int_{\partial\Omega} M n \cdot \phi ds.
	\end{eqnarray*}
	$\textrm{Tr} (M \Phi)$ is the trace of the matrix $M \Phi$, $n$ is the normal vector to $\Omega$, and 
	\begin{eqnarray*}
		\Phi = 
		\begin{bmatrix}
			\partial_1\phi_1 & \partial_2\phi_1\\
			\partial_1\phi_2 & \partial_2\phi_2
		\end{bmatrix}.
	\end{eqnarray*}

	The variational form can be given as
	\begin{align}
		\int_\Omega h \partial_t^2 w v \ dA & = & - \int_\Omega Q \cdot \nabla v \ dA + \int_\Omega q v \ dA + \int_{\partial\Omega} (Q\cdot n)v ds, \label{P1}\\
		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & - \int_\Omega \textrm{Tr} (M \Phi) \ dA - \int_\Omega Q \cdot \phi \ dA + \int_{\partial\Omega} M n \cdot \phi ds. \label{P2}
	\end{align}

	Using the test function space for Problem P-1, the equations \eqref{P1} and \eqref{P2} reduce to
	\begin{eqnarray}
		\int_\Omega h \partial_t^2 w v \ dA & = & - \int_\Omega Q \cdot \nabla v \ dA + \int_\Omega q v \ dA, \label{eq:P_Model:ProblemP1V1}\\
		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & - b(\phi,v) - \int_\Omega Q \cdot \phi \ dA, \label{eq:P_Model:ProblemP1V2}
	\end{eqnarray}
	for all $v \in T_1(\bar{\Omega})$ and $\phi \in T_2(\bar{\Omega})$

	\subsubsection{Bilinear Forms and integral}\label{sssec:P_Model:BilinearForm}
	Let $u = \langle w, \psi \rangle$ and $\phi = \langle v, \phi \rangle$. Define the bilinear forms
	\begin{eqnarray*}
		b(u,\phi) & = & \int_\Omega Q \cdot \nabla v \ dA + \int_{\Omega} \textrm{Tr}(M\Phi) \ dA,
	\end{eqnarray*}
	and
	\begin{eqnarray}
		c(u,\phi) = \int_\Omega h (\partial_t^2 w) v \ dA + \int_\Omega I (\partial_t^2 \psi) \cdot \phi \ dA \label{eq:2D_Model:Bilinear_c}
	\end{eqnarray}
	Also define the integral
	\begin{eqnarray}
		(f,g) &=& -\int_{\Omega} f\cdot g \ dA \label{eq:2D_Model:Bilinear_int}
	\end{eqnarray}

	\subsubsection{Test Functions for Problem P-1}\label{sssec:P_Model:TestfunctionsP1}
	Define the following spaces $T_1(\bar{\Omega})$ and $T_2(\bar{\Omega})$ determined by the boundary conditions for $w$ and $\phi$
	\begin{eqnarray*}
		T_1(\bar{\Omega}) & = & \left \{v \in C^1(\bar{\Omega})\ | \ v = 0 \textrm{ on } \Sigma_0\right\},\\ 
		T_2(\bar{\Omega}) & = & \left \{ \phi = \left[ \phi_1 \ \phi_2 \right]^T \ | \ \phi_1, \phi_2 \in C^1(\bar{\Omega}), \ \phi_1 = \phi_2 = 0 \textrm{ on } \Sigma_0 \right\}.
	\end{eqnarray*}

	\subsubsection{Problem P-1V}\label{sssec:P_Model:ProblemP1V}
	Find a function $u = \langle w, \psi \rangle$, such that for all $t>0$, $u \in T_1({\bar{\Omega}}) \times T_2({\bar{\Omega}})$ and the following equations are satisfied
	\begin{eqnarray}
		c(u,\phi) &=& -b(u,\phi) + (Q,\phi), \label{eq:P_Model:ProblemP1V1}
	\end{eqnarray} with $\phi = \langle v, \phi \rangle  \in T_1({\bar{\Omega}}) \times T_2({\bar{\Omega}})$ an arbitrary function.\\

 Applications are continued in Chapter 5 and 6. In Chapter 5, the finite element analysis is applied to a cantilever plate to solve the eigenvalue problem. In Chapter 6, a cantilever plate in used in the comparison of our linear models.
\end{document}

	\textcolor{red}{Voel nie die dra iets by nie.}\\
\textbf{\sout{Remark}} \sout{Using the constitutive equations \eqref{eq:P_Model:CE2D} - \eqref{eq:P_Model:CE4D}, and the definition of the vectors $n$ and $\tau$, the following can be obtained to simplify the boundary conditions:}
\begin{eqnarray*}
	Mn\cdot n \neq 0 \  \textrm{ and } Mn\cdot \tau \neq 0 \textrm{ implies } \ \psi_1 = \psi_2 = 0 \\
	Mn\cdot n = 0 \  \textrm{ and } Mn\cdot \tau \neq 0 \textrm{ implies } \ \psi\cdot\tau = 0\\
	Mn\cdot n \neq 0 \  \textrm{ and } Mn\cdot \tau = 0 \textrm{ implies } \ \psi \cdot n = 0\\
	Mn\cdot n = 0 \ \textrm{ and } Mn\cdot \tau = 0 \textrm{ implies } \ \psi_1 \neq 0 \neq \psi_2
\end{eqnarray*}
\textcolor{red}{Equations kan ek nie dood trek nie, so ek los die nota hier.}
%\textbf{Remark:}\\
%The components of the moment desnity matrix $M$ are forces, and for any vector $v$, $Mv$ is also a vector.

### 2022-10-31 files/Chapter2/generalvibrationmodel.tex
initial commit

  \documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction} \label{sec:existence}
The models in this dissertation concern vibration of elastic bodies. These type of models have a similar variational form as the wave equation and are called second order hyperbolic type problems. This chapter discusses theory for the existence and uniqueness of solutions for these type of problems. The theoretical basis for modal analysis is also presented.\\

In this chapter we consider the work done by the authors of \cite{VV02} and \cite{VS19}. In these articles the authors prove the existence and uniqueness of solutions for general second order hyperbolic type problems. The problems in Chapter 1 are examples. The article \cite{VV02} concerns the case of a symmetric bilinear form $b$. The article \cite{VS19} extends this work where $b$ need not be symmetric. The article \cite{VV02} is sufficient for the models of this dissertation, while \cite{VS19} is only used where the notation is more convenient and to gain more insight.\\

Before the general theory is discussed, a model is presented to be used as an example to show the application of the theory. The model is a cantilever Timoshenko beam, denoted by Problem T-2 in Section \ref{ssec:1D_Model:ModelProblems}.\\

In Section \ref{ssec:1D_Model:VariationalForm}, the variational problem for the pinned-pinned beam is derived. The derivation of the cantilever beam model is similar, with a different test function space. Recall the variational problem for the cantilever beam Problem T-2V, with the test function space $\displaystyle T[0,1] = F_1[0,1] \times F_1[0,1]$. To determine the solvability of the problem, the weak variational problem is considered first.\\

To obtain the weak variational form of Problem T-2V some preparation is required. A natural setting for the problem is the product space $L^2(0,1)\times L^2(0,1)$, denoted by $X$. The inner product for $L^2(0,1)$ yields the inner product $\displaystyle (x_1,y_1) + (x_2,y_2)$ for $X$. The idea is to replace the pair $\langle w , \phi \rangle$ by a function $u$ ``of time only" and values $u(t)$ in the space $X$.\\

Define a function u with domain $J$, an interval of real numbers. The range of $u$ is contained in $X$:
\begin{eqnarray}
	u(t)(x) = \langle w(x,t), \phi(x,t) \rangle \label{def_of_u}
\end{eqnarray}

A derivative $u'$ for $u$ may be defined by 
\begin{eqnarray*}
	||\left(h^{-1} u(t+h)-u(t)\right)-u'(t)||_X \rightarrow 0.
\end{eqnarray*} Then $u''$ is defined by $u'' = (u')'$. Sometimes the derivatives are denoted by $\dot{u}$ and $\ddot{u}$.\\

Using the bilinear forms, $b$ and $c$ from Section 1.4, Problem T-2V can be rewritten in the following form
\begin{eqnarray}
	c(\ddot{u}(t),v) + b(u(t),v) & = & (Q(t),v) \label{eq:existence:PreWV}
\end{eqnarray} for each $v \in T[0,1]$.\\

To apply the theory from \cite{VV02}, complete function spaces are required. It is known that $L^2(0,1)$ is a complete function space and hence $X$ is complete.\\

 The Sobolev space $H^1(0,1)$ is all the functions in $L^2(0,1)$ with at least a first-order weak derivative. $H^1(0,1)$ is complete (see Appendix A).\\

  The test functions $T[0,1]$ do not form a complete space. Let $V(0,1)$ be the closure of {$F_1(0,1)$} in $H^1(0,1)$. The product space {$V(0,1)\times V(0,1)$} is denoted by $V$ and is complete. $V$ is called the energy space.\\

Using these complete product spaces and \eqref{eq:existence:PreWV}, the weak variational problem for the cantilever Timoshenko beam is defined as Problem T-2W.

\subsubsection{Problem T-2W}\label{sssec:existence:ProblemT2W}
Find a function $u$ such that $\forall \ t \in J$, $u(t) \in V$, $\ddot{u}(t) \in W$ and
\begin{eqnarray*}
	c(\ddot{u}(t),v) + b(u(t),v) & = & (Q(t),v)
\end{eqnarray*}
for all $v\in V$.\\

 The space X with the inner-product $c$ is denoted by $W$. $W$ is called the inertia space and in Section 2.3 it is shown that $c$ is an inner-product for $W$.\\

In the next section, the theory of the article \cite{VV02} is presented. In Section 2.3 the theory is applied to Problem T-2W.

\section{Existence and uniqueness of solutions}\label{sec:existence:ExistenceAndUniqueness}
The general weak variational problem is studied in this section. The following theory is from the article \cite{VV02}. To start, some notation is given, as well as the relations between various Hilbert spaces. The necessary assumptions are also stated.\\

As mentioned before, ideas and notation from \cite{VS19} are also used.

\subsection{The variational approach}\label{ssec:existence:VariationlApproach}
Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
\begin{itemize}
	\item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
	\item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
	\item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
\end{itemize}

The following notation is important for the theory that follows.\\

Let $J$ be a interval of real numbers containing zero. It can have one of the following forms $[0,\ T)$, $[0,\ \infty)$ or an arbitrary open interval. For any function $u$ on the interval $J$ and range in a Hilbert space Z, derivatives can be defined. A derivative $u'$ for $u$ may be defined by 
\begin{eqnarray*}
	||(h^{-1} u(t+h)-u(t))-u'(t)||_Z \rightarrow 0.
\end{eqnarray*} Then $u''$ is defined by $u'' = (u')'$.\\

\textbf{Notation}
\begin{itemize}
	\item[] $u\in C(J,Z)$ if $u$ is continuous on $J$ with respect to the norm of $Z$;

	\item[] $u'(t)\in Z$ if $u$ is differentiable with respect to the norm of $Z$;

	\item[] $u\in C^{k}(J,Z)$ if $u^{(k)}\in C(J,Z)$ .
\end{itemize}

\textbf{Remark} For Problem T-2, $Z$ can be $X$, $W$ or $V$.\\

Let $a$, $b$ and $c$ be bilinear forms where $a$ and $b$ are defined on $V$ and $c$ is defined on $W$. For the models in this dissertation, the bilinear form $b$ is symmetric.

\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
	Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
\begin{eqnarray}
	c(u''(t),v)+a(u'(t),v)+b(u(t),v)= (f(t),v)_{X} \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVar}
\end{eqnarray}
while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\\

This general variational form is applicable in all the models in this dissertation. In \cite{VV02}, a more general form is given that includes the possibility for damping terms in the models. Damping is not considered in this dissertation.

\subsubsection*{Assumptions} \label{sssec:existence:Assumptions}
The following assumptions are made in \cite{VV02} for the existence results.
\begin{itemize}
	\item[] \textbf{A1} - $V$ is dense in $W$ and $W$ is dense in $X$.

	\item[] \textbf{A2} - There exists a positive constant $C_{W}$ such that $\Vert w\Vert_{X} \leq C_{W}\Vert w\Vert_{W}$ for each $ w\in W$ and $c(\cdot,\ \cdot) =(\cdot,\ \cdot)_{W}$.

	\item[] \textbf{A3} - There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$ and $b(\cdot,\ \cdot) =(\cdot,\ \cdot)_{V}$.

	\item[] \textbf{A4} - The bilinear form $a$ is non-negative, symmetric and bounded on $V$, i.e. there exists a positive constant $K_a$ such that for $\displaystyle u,v \in V$, \[|a(u,v)| \leq K_a\Vert u \Vert_V \Vert v \Vert_V.\]
\end{itemize}

In general, the bilinear form $a$ in \textbf{A4} is defined on $V$. However it is possible for $a$ to be defined on the space $W$ and bounded by the norm $||\cdot||_W$, i.e. there exists a $k > 0$ so that
\begin{eqnarray}
	|a(u,v)| \leq k ||u||_W||v||_W \ \ \ \ \textrm{ for all } \ u,\ v \in W. \label{weak_damping}
\end{eqnarray} This is called \textbf{weak damping}. Note that \eqref{weak_damping} is trivially satisfied if $a = 0$.

\subsection{Main results for existence and uniqueness}\label{ssec:existence:MainResultsExistence}
To start, the main results of \cite{VV02} are presented. There are three existence theorems but Theorem 2 is important for this dissertation.

\newtheorem{Thmx}{Theorem}
\begin{Thmx}[{Main Result}]
	Suppose assumptions \textbf{A1}-\textbf{A4} hold. If, for $u_0 \in V$ and $u_1 \in V$, there exists some $y \in W$ such that 
	\begin{eqnarray}
		b(u_0,v) + a(u_1,v) = c(y,v) \ \ \ \ \textrm{ for all } \ v \in V, \label{bilinear_equation}
	\end{eqnarray}
	then for each $f \in C^1(J,X)$, there exists a unique solution $u \in C^1(J,V)\cap C^2(J,W)$ for Problem GVar.
\end{Thmx}

This theorem allows for a solution of the abstract variational problem Problem GVar, if the assumptions \textbf{A1}-\textbf{A4} is satisfied and the initial values $u_0$ and $u_1$ are admissible. It is not always easy to verify that \eqref{bilinear_equation} is satisfied.\\

 In \cite{VV02} the authors consider a special case of weak damping. Define a space $E_b \subset V$ where \[ E_b = \left\{x \in V \ | \ \textrm{there exists a } y \in W \textrm{ such that } c(y,v) = b(x,v) \textrm{ for all } v \in V\right\}.\] It is proved in \cite{VV02}  that $D(A) = E_b \times V$. Consequently if $u_1 \in V$ and $u_0 \in E_b$ the pair $u_0$, $u_1$ is admissible.

\newtheorem{Thm2n}[Thmx]{Theorem}
\begin{Thm2n}[Weak Damping]
	If $a$ is bounded with respect to the norm in $W$, then there exists a unique solution $u\in C^1(J,V)\cap C^2(J,W)$ for Problem GVar for each $u_0 \in E_b$. each $u_1 \in V$ and each $f\in C^1(J,X)$. 
\end{Thm2n}

\textbf{Remark} In general, the bilinear form $a$ is non-negative. However it is possible for $a$ to be positive definite on the space $V$ with respect to the norm $||\cdot||_V$, i.e. there exists a $c_a > 0$ so that
\begin{eqnarray*}
	a(v,v) \geq c_a ||v||^2_V \ \ \ \ \textrm{ for all } \ v \in V.
\end{eqnarray*} This is called strong damping. It is not considered in this dissertation.

\newtheorem{Thm3n}[Thmx]{Theorem}
\begin{Thm3n}[Strong Damping]
	If $a$ is positive definite on $V$, there exists a unique solution $u \in C^1([0,\infty),V)\cap C^2((0,\infty),W)$ for Problem GVar for any $u_0 \in V$, $u_1 \in W$ and any $f$ which is Lipschitz on $V$. If $f=0$, then $u \in C^1([0,\infty),V)\cap C^2([0,\infty),W)\cap C^\infty((0,\infty),V)$.
\end{Thm3n}

As mentioned, in the models of this dissertation, the bilinear form $a$ is identically zero. This automatically satisfy the weak damping condition and hence Theorem 2 may be applied.

\subsection{First order system} \label{ssec:existence:AbstractDifferentialEquation}

To prove the main results in \cite{VV02}, the authors introduce an equivalent first order system.\\

This variational form is rewritten as a first order system of differential equations. Let $y(t) = u'(t)$, then \[ c(y'(t),v)+a(y(t),v)+b(u(t),v)= (f(t),v)_{X}.\] To make this precise, a Hilbert space H is defined by $H:=V\times W$. For $x \in H$, $x = \langle x_1, x_2 \rangle$ with $x_1 \in V, x_2 \in W$. An inner product on $H$ is defined by
\begin{eqnarray*}
	(x,y)_H := b(x_1,y_1) + c(x_1,y_1) \ \textrm{for all} \ x,y \in H.
\end{eqnarray*}

Then the authors define an operator $\Lambda$ as a mapping on $H$ by $\Lambda y = -x$ when $-x_2 = y_1$ and $x_1 \in V$ such that 
\begin{eqnarray}
	b(x_1,v) + a(x_2,v) = c(y_2,v) \ \textrm{ for each } \ v \in V. \label{author_mapping}
\end{eqnarray}
The operator $A$ is defined in \cite{VV02} as $A = \Lambda^{-1}$ with $D(A) = \mathcal{R}(\Lambda)$.\\

From a result in \cite{VV02}, $x \in D(A)$ if and only if $x_1 \in V$, $x_2 \in V$ and there exists a $z \in W$ such that $b(x_1,v) + a(x_2,v) = c(z,v)$ for all $v \in V$. Furthermore $y = Ax$ if $y_1 = -x_2$ and \[b(x_1,v) + a(x_2,v) = c(y_2,v)\  \textrm{ for all } v \in V.\]

 This operator is used to rewrite the equation \eqref{eq:existence:ProblemGVar} of Problem GVar as a first order differential equation in the form
\begin{eqnarray}
	x' & = & Ax + f. \label{Cauchy}
\end{eqnarray}

To be more precise, the following problem is introduced.

\subsubsection*{Problem IVP}\label{sssec:existence:ProblemIVP}
Given a function $F:J\rightarrow H$, find a function $U\in C(J,\ H)$ such that for each $t\in J$, $U(t) \in D(A)$, $U(t) \in H$ and
\begin{eqnarray*}
	U(t)' & = & AU(t) + F(t),\\
	U(0) & = & U_0.
\end{eqnarray*}

 To link Problem IVP and Problem GVar, consider the following lemma from \cite{VV02}.

\newtheorem*{Prop}{Lemma 1}
\begin{Prop}
	Suppose $F(t) = \langle 0, f(t) \rangle$ for each $t\in J$.
	\begin{itemize}
		\item[a)] If $u$ is a solution of Problem GVar, then $U = \langle u, u' \rangle$ is a solution of Problem IVP, with $U_0 = \langle u_0, u_1 \rangle$.
		\item[b)] If $U$ is a solution of Problem IVP with $U_0 = \langle u_0, u_1 \rangle$, then the first component $u = U_1$ of $U$ is a solution for Problem GVar.
	\end{itemize}
\end{Prop}

Semi-group theory is used in \cite{VV02} to investigate the solvability of Problem IVP and obtain a solution for Problem IVP. It is also important to mention that in \cite{VV02}, the authors provide the necessary result that shows the function $F$ is uniquely defined by $f$.\\

As mentioned before, if $a = 0$ then the inequalities in \eqref{weak_damping} hold trivially. However, the operator A is defined by the operator $\Lambda$ and in the definition of $\Lambda$, the form $a$ is used (see \eqref{author_mapping}).\\

\vspace{10mm}
 derivation of this linear operator remains unchanged as presented in \cite{VV02} for $a$ identically zero.\\
 \vspace{10mm}

  To apply Theorem 2, the admissible initial conditions are $u_0 \in E_b$ and $u_1 \in V$. As mentioned $\langle u_0, u_1 \rangle \in D(A)$. From semigroup theory, it follows that $u(t) \in D(A)$ for each $t$. Therefore $u(t) \in E_b$ and $u'(t) \in V$ for each $t$.\\

\textcolor{red}{Volgende Rondte}\\
 Using the assumptions \textbf{A1}-\textbf{A4}, they prove that this linear operator $A$ is an infinitesimal generator of a $C_0$-semigroup of contractions and the domain of $A$ is dense in $H$.

\section{Application: Timoshenko beam model}\label{sec:existence:Application}
In this section the theory of \cite{VV02} (presented in Section \ref{sec:existence:ExistenceAndUniqueness}) is applied to Problem T-2W. This is an continuation of the example from section \ref{sec:existence}.\\

Recall the spaces defined in Section \ref{sec:existence}:
\begin{itemize}
	\item[] $X = L^2(0,1)\times L^2(0,1)$ with inner product $(\cdot,\cdot)_X$ and induced norm $||\cdot||_X$.
	\item[] $W = X$ with inner product $c$ and induced norm $||\cdot||_W$.
	\item[] $V  = V(0,1)\times V(0,1)$ with inner product $b$ and induced norm $||\cdot||_V$.
\end{itemize}

\textcolor{red}{ALLES NOG NIE BEWYS NIE - moet nog doen}

 To apply the theory, Problem T-2W must satisfy assumptions \textbf{A1}-\textbf{A4} and the initial values must be admissible.

\subsubsection{Assumption A1}\label{sssec:existence:AssumptionA1}
It is clear that $W$ is dense in $X$. (The set $W = X$).\\

Let $u \in C_0^\infty(0,1)$. Then $u(0) = u(1) = 0$ and therefore $u \in T(0,1)$ and $C_0^\infty(0,1) \subset T(0,1)$. Recall that $V(0,1)$ is the closure of $T(0,1)$ in $H^1(0,1)$.\\

So it follows that $C_0^\infty(0,1) \subset V(0,1) \subset H^1(0,1)$. And since $C_0^\infty(0,1)$ is dense in $L_2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L_2(0,1)$. Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.

\subsubsection{Assumption A2}\label{sssec:existence:AssumptionA2}
	From the definition of the bilinear form $c$, 
\begin{eqnarray*}
	c(f,f) & = & \int_0^1  (f_1)^2 + \frac{1}{\alpha}\int_0^1  (f_2)^2 = ||f_1||^2 + \frac{1}{\alpha}||f_2||^2.\\
\end{eqnarray*}
From this, the following inequalities can be obtained: 
\begin{eqnarray*}
	\min\left\{1, \frac{1}{\alpha}\right\} ||f||_{X}^2 \leq	c(f,f)	\leq \max\left\{1, \frac{1}{\alpha}\right\} ||f||_{X}^2.\\
\end{eqnarray*}

Since $c$ is a bilinear form and by the inequality above, $c$ is a inner-product for $W$. The norm of $W$ can be defined as $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$. Let $C_1 = \min\left\{1, \frac{1}{\alpha}\right\}$ and $C_2 = \max\left\{1, \frac{1}{\alpha}\right\}$. Then
\begin{eqnarray}
C_1||x||_X \leq ||x||_W \leq C_2||x||_X \label{C}
\end{eqnarray} for all $x \in X$.\\

 To prove \textbf{Assumption A3}, some preparation is required. Consider the following proposition for a Poincar\'e-Type inequality for the one-dimensional case.
\newtheorem*{Poincare}{Proposition 1}
\begin{Poincare}
	Suppose that $f \in C^1[a,b]$, and $f(0) = 0$. Then $||f|| \leq (b-a)||f'||$
\end{Poincare}
\begin{proof}
	Let $f \in C^1(0,1)$ such that $f(0) = 0$. By the Fundamental Theorem of Calculus,
	\begin{eqnarray*}
		|f(x)| = \left|\int_0^x f'(s) \ ds\right| \leq \int_0^x |f'(s)| \ ds.
	\end{eqnarray*}
	Since $x$ is arbitrary, 
		\begin{eqnarray*}
		||f||_{\sup} \leq \int_0^1 |f'(s)| ds. 
	\end{eqnarray*}
Also for $f,g \in C^1(0,1)$,
	\begin{eqnarray}
	\left| \int_a^b fg \right| & \leq & ||f||\ ||g|| \ \ \ \ \textrm{ by Cauchy-Swartz Inequality.} \label{CSI}
	\end{eqnarray}
	Choose $g = 1$ then since $||f|| \leq ||f||_{\sup} \sqrt{b-a}$, the result follows.
\end{proof}

\newtheorem*{Poincare_2}{Corollary}
\begin{Poincare_2}
	Suppose that $f \in H^1(a,b)$, and $f(0) = 0$. Then $||f|| \leq (b-a)||f'||$
\end{Poincare_2}

To show that assumption \textbf{A3} holds, it is required to show that there exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.\\

Let $f \in V$, then $f_1(0) = f_2(0) = 0$.
\begin{eqnarray}
	b(f,f) & = &   \int_0^1 (f_1'-f_2)^2 + \frac{1}{\beta}\int_0^1  (f_2')^2 \nonumber\\
	& = & ||f_1' - f_2||^2 + \frac{1}{\beta}||f_2'||^2 \nonumber\\
	& \geq & \min\left\{1 ,\ \frac{1}{\beta} \right\} \left( ||f_1' - f_2||^2 + ||f_2'||^2\right) \label{b}
\end{eqnarray}

 Using the Corollary, and from the definition of the norm $||\cdot||_X$, the following Poincar\'e-Type inequality for the norm $||\cdot||_X$ can be obtained.
\begin{eqnarray*}
	||f||_X^2 & \leq & ||f_1'||^2 + ||f_2'||^2 \\
	& = & ||f_1'||^2 -||f_2||^2 + ||f_2'||^2 +||f_2||^2\\
	& \leq & 2||f_1'-f_2||^2 + 2||f_2'||^2.
\end{eqnarray*} \sout{by Proposition 2 and the reverse triangle inequality.}\\

Using \eqref{b} and the inequality above, it follows that
\begin{eqnarray}		
	b(f,f)	& \geq & \frac{1}{2}\min\left \{1, \frac{1}{\beta}\right \} ||f||_{X}^2. \label{b2}
\end{eqnarray} for all $f \in V$.\\

Since $b$ is the bilinear form for $V$ and $W = X$, \eqref{b2} is equivalent to \[||v||^2_V \geq C^{\frac{1}{2}}_V ||v||^2_W\] for all $v \in V$ with $\displaystyle C^{\frac{1}{2}}_V = \frac{1}{2}\min\left \{1, \frac{1}{\beta}\right \} > 0$. It follows that $\displaystyle||v||_W \leq C_V||v||_V$ for all $v \in V$.\\

\sout{Since $b$ is a bilinear form and from the inequality above, $b$ is a inner-product for $V$. Using the inequality \eqref{C} results in $||v||^2_V \geq  C_3 ||w||_{W}^2$ for all $v \in V$, $w \in W$. With $C_3 =\frac{1}{2}\min\left \{1, \frac{1}{\beta}\right \} > 0$. The result follows by taking the square on both sides of the inequality.}\\

Consider \textbf{Assumption A4}. In Problem T-2W, it is clear that the bilinear form $a$ is identically zero. As mentioned before... \textcolor{red}{As mentioned before, if $a = 0$, the weak damping as well as assumption \textbf{A4} is satisfied.}\\

\section{Modal analysis}\label{sec:existence:ModalAnalysis}
\subsection{Timoshenko beam}
In this dissertation, the eigenvalues and eigenvectors of the models presented are required. To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration. And to understand how modal analysis is applied, a Timoshenko beam is used as an example. Specifically, Problem T-1.\\

Consider the partial differential equations of a pinned-pinned Timoshenko beam (obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}).
\begin{eqnarray*}
	\partial^{2}_{t} w &=& \partial_{x}(\partial_{x} w - \phi), \label{eq:1D_Model:ModalPDE1}\\
	\gamma \partial^{2}_{t} \phi &=& \beta (\partial_{x} w - \phi) + \partial_{x}(\partial_{x}\phi),\label{eq:1D_Model:ModalPDE2}
\end{eqnarray*}
with boundary conditions
\begin{eqnarray*}
	w(0,t) = 0, & &	\	 w(1,t) = 0. \label{eq:1D_Model:ModalBC1}\\
	M(0,t) = 0, & &	\	M(1,t) = 0, \label{eq:1D_Model:ModalBC2}
\end{eqnarray*}
The boundary conditions of the moments can be written in terms of $\phi$ using the constitutive equation \eqref{eq:1D_Model:ConstitutiveEquations1D}:
\begin{eqnarray*}
	\partial_{x}\phi(0,t) = 0, & & \partial_{x}\phi(1,t) = 0. \label{MA_4}
\end{eqnarray*}
Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ with $\phi(x,t) = T(t)\tilde{\phi}(x)$. Simple substitution confirms that this trial solution satisfies the partial differential equations and the boundary conditions for Problem T-1.\\

The method of separation of variables leads to an eigenvalue problem. For the pinned-pinned beam, this eigenvalue problem is referred to as Problem T-1E.
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in \mathbb{R}$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.\\

The solution to Problem T-1E is a pair of functions $\langle \tilde{w} \ \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$.\\

The eigenvalues for the pinned-pinned beam model is the first example in [VV06]. In this dissertation, the pinned-pinned model problem is referred to as Problem T-1 (eigenvalue problem Problem T-1E). Obviously, since $\langle 0 \ 1\rangle$ satisfies the boundary conditions, it is an eigenfunction with corresponding eigenvalue $\alpha$. In [VV06] the authors proved the following theorem.

\newtheorem{ThmVV06}{Theorem}
\begin{ThmVV06}
	If $\langle u \ \phi\rangle$ is a nonconstant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions. $A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$. Also all eigenvalues less than $\alpha$ are simple eigenvalues.
\end{ThmVV06}

Suppose the function $T$ satisfies the following differential equation
\begin{eqnarray}
	\ddot{T} + \lambda T = 0, \label{eq:1D_Model:ModalAnalysisT}
\end{eqnarray} with $\lambda$ an eigenvalue.\\

The variational eigenvalue problem for Problem T-1E can be obtained using similar steps to how Problem T-1V is obtained. This variational eigenvalue problem is referred to as Problem T-1EV

\subsubsection*{Problem T-1EV}\label{sssec:1D_Model:ProblemT1EV}
Find a pair of functions $\tilde{w}$ and $\tilde{\phi}$ such that for all $t >0$, $\langle \tilde{w}\ \tilde{\phi}\rangle \in  T[0,1]$ and satisfying the equations
\begin{eqnarray*}
	\int_0^1 \lambda \tilde{w} v &=& -\int_0^1 \tilde{w}'v'  + \int_0^1 \tilde{\phi} v',\\
	\int_0^1 \lambda \tilde{\phi} \psi &=& -\int_0^1\alpha \tilde{w}' \psi + \int_0^1\alpha \tilde{\phi} \psi - \int_0^1\frac{1}{\gamma}\tilde{\phi}' \psi'.
\end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$.\\

\textcolor{red}{Res moet dalk out of skuif.*******************************}\\
It is now possible to test the trial solutions $w(x,t) = T(t)\tilde{w}(x)$ and $\phi(x,t) = T(t)\tilde{\phi}(x)$. Consider the right hand side of the variational form of Problem T-1V with $Q=0$. Then substituting the pair of trial solutions:
\begin{eqnarray*}
	-\int_{0}^{1}\partial_x w v'  + \int_{0}^{1} \phi v' &=& -T\int_{0}^{1} \tilde{w}' v'  + T\int_{0}^{1} \tilde{\phi} v',\\
	- \int_{0}^{1} \alpha \partial_x w \psi + \int_{0}^{1} \alpha \phi \psi - \frac{1}{\gamma} \int_{0}^{1}\partial_x \phi \psi' &=& - T\int_{0}^{1} \alpha \tilde{w}' \psi + T\int_{0}^{1} \alpha \tilde{\phi} \psi - \frac{1}{\gamma} T\int_{0}^{1} \tilde{\phi}' \psi'.
\end{eqnarray*}
Similarly for the left hand side and using \eqref{eq:1D_Model:ModalAnalysisT}:
\begin{eqnarray*}
	\int_{0}^{1} \partial_{t}^{2} w v &= \int_0^1 \ddot{T} \tilde{w} v &= T\int_0^1 \lambda \tilde{w} v,\\
	\int_{0}^{1} \partial_{t}^{2} \phi \psi &= \int_0^1 \ddot{T} \tilde{\phi} \psi &= T \int_0^1 \lambda \tilde{\phi} \psi.
\end{eqnarray*}

This shows that the pair of trial solutions $\langle {w} \ {\phi} \rangle$ are solutions of the variational problem Problem T-1V with $\langle \tilde{w} \ \tilde{\phi} \rangle$ the eigenvalues with corresponding eigenvalue $\lambda$ from the variational eigenvalue problem Problem T-1EV. This was accomplished without using the method of separation of variables and thus avoiding any contention on division by zero.\\

It is well known that the eigenvalue problem like Problem T-1EV has infinitely many solutions $\langle \tilde{w}_n \ \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$. For Problem T-1 (Problem T-2 and Problem T-4 also), $\lambda_n > 0$ for all $n > 0$. A convenient reference is [VV06].\\

Corresponding to this sequence of eigenvalues, we have a sequence of solutions $(T_n(t))$:
\begin{eqnarray}
	T_n(t)=A_n\cos(\sqrt{\lambda_n}t)+B_n\sin(\sqrt{\lambda_n}t), \label{eq:1D_Model:ModalAnalysisTn}
\end{eqnarray}
(with $A_n$ and $B_n$ arbitrary constants) for the ordinary differential equation \eqref{eq:1D_Model:ModalAnalysisT}.\\

As a consequence, the system of partial differential equations of Problem T-1 has a sequence of solutions $(w_n,\phi_n)$ such that
\begin{eqnarray*}
	w_n(x,t) & = & T_n(t)\tilde{w}_n(t), \\
	\phi_n(x,t) & = & T_n(t)\tilde{\phi}_n(x).,
\end{eqnarray*} satisfying the boundary conditions. These solutions are referred to as the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.\\

The formal series solution for Problem T-1 is 
\begin{eqnarray*}
	\langle u \ \phi \rangle = \sum_{n=1}^{\infty} T_n(t)\langle u_n(x) \ \psi_n(x)\rangle.
\end{eqnarray*}

The article [VV06] provides a rigorous method to solving the eigenvalue problem for Timoshenko beam models of different boundary conditions. This method and examples form [VV06] is discussed in Chapter 4.

\subsection{General vibration problem}

	\textbf{********* MOET [CVV18] in bronnelys sit}\\

Consider Problem XX in Section 2.2 \textbf{*** Sy reference is \eqref{GV_PB1}}\\

Given $g \in C((a,b);W)$, find $u$ such that for each $t > 0$, $u(t) \in V$, $u \in C^2((a,b);W)$ and
\begin{eqnarray*}
	c(u''(t),v) + b(u(t),v) = c(g(t),v).
\end{eqnarray*}

Now suppose there exists $\lambda$ and $x \in V$, $x \neq 0$ such that
\begin{eqnarray*}
	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
\end{eqnarray*}

Then, $u(t) = T(t)x$ is a solution of the homogeneous problem
\begin{eqnarray*}
	c(u''(t),v) + b(u(t),v) = 0
\end{eqnarray*}
if and only if
\begin{eqnarray}
T''  + \lambda T = 0.
\end{eqnarray}

General solution $T(t) = c_1 \sin(\omega t) + c_2 \cos(\omega t)$ with $\omega = \sqrt{\lambda}$.\\

The function $u$ is a natural mode of vibration and $\omega$ natural angular frequency. Natural frequency is $\frac{\omega}{2 \pi}$.

\subsection*{Series solution}\label{ssec:existence:SeriesSolution}
Next we consider the question: When is the formal series solution valid for the vibration problem **(1)** with initial values $u(0) = u_0$ and $u'(0) = u_1$?\\

Consider the partial sum $u^{N}(t) = \sum_{n=1}^{N} T_{n}(t)w_n$. Let
\begin{eqnarray*}
	u_0^{N} = \sum_{n=1}^{N} A^*_n w_n \ \ \textrm{ and } \ \ u_{1}^{N} =\sum_{n=1}^{N} B^*_n w_n
\end{eqnarray*} where $A^*_n = T_n(0)$ and $B^*_n = T'_n(0)$.\\

\textbf{Assumption A5} The embedding of $V$ into $W$ is compact.

\end{document}

\textcolor{red}{Voorstel:}\\
\textcolor{red}{*********************}\\
Using these complete product spaces, \eqref{def_of_u} and the variational form \eqref{var_form_timo} defined in Section \ref{ssec:1D_Model:VariationalForm}, the weak variational form for the cantilever Timoshenko beam is defined as Problem T-2W.\\
\textcolor{red}{*********************}

\begin{proof}
	Suppose $f,g \in \mathbb{R}[a,b]$. Then
	\begin{eqnarray}
		\left| \int_a^b fg \right| & \leq & ||f||\ ||g|| \ \ \ \ \textrm{ by Cauchy-Swartz Inequality.} \label{CSI}
	\end{eqnarray}

	Suppose that $x^*$ is the zero of $u$ on the interval $[a,b]$. Then since $u \in C^1[0,1]$, by the Fundamental Theorem of Calculus
	\begin{eqnarray*}
		u(x) = \int_{x^*}^x u' \ \ \ \ \textrm{or} \ \ \ \ \ u(x) = -\int^{x^*}_x u'
	\end{eqnarray*}

	So by \eqref{CSI} with $g = 1$, it follows that $|u(x)| \leq ||u'||\sqrt{b-a}$. So it is clear that $||u'||\sqrt{b-a}$ is an upper bound for $|u|$, hence
	\begin{eqnarray}
		||u||_{\sup} \leq ||u'||\sqrt{b-a} \label{sup}
	\end{eqnarray}

	It is easy to show that $||u|| \leq \sqrt{b-a} ||u||_{\sup}$. It then follows from \eqref{sup} that $||u|| \leq (b-a) ||u'||$.
\end{proof}

### 2022-10-31 files/Chapter3/dynamicconvergence.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
In this chapter, two convergence results for the Finite Element Method (FEM) is discussed. The first result is the convergence of the Galerkin approximation for second order hyperbolic type problems, from the article \cite{BV13}. The second result is from the textbook \cite{SF97} regarding the convergence of the eigenvalues and eigenfunctions for a one-dimensional vibration problem, using the Finite Element Method.

\section{Convergence of the Galerkin approximation}
In the article \cite{BV13}, the authors investigate the convergence of the Galerkin approximation for second order hyperbolic type problems. The article \cite{BV18} extends \cite{BV13} by including general damping and damping at the endpoints. For the models in Chapter 1, \cite{BV13} is sufficient and \cite{BV18} was read for more insight and improved notation.\\

In Section 2.2, a general variational problem Problem GVar from \cite{VV02} is given. The authors of \cite{BV13} use the same general variational problem.

\subsubsection*{Problem GVar}
Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
\begin{eqnarray}
	c(u''(t),v)+a(u'(t),v)+b(u(t),v)= (f(t),v)_{X} \ \ \ \ \textrm{for each} \ v \in V, \label{GV_PB1}
\end{eqnarray}
while $u(0)=u_{0}$, $u'(0)=u_{1}$.\\

It is assumed that the assumptions \textbf{A1}-\textbf{A4} from Section 2.2 are satisfied such that Problem GVar has a unique solution.\\

To start, the authors of \cite{BV13} formulate the Galerkin Approximation of Problem GVar.

\subsection{Galerkin approximation}
 Recall from Chapter 2 that $V$ is the closure of the test function space $T$ in the Hilbert space $H$.\\

 Suppose $S^h$ is a finite n-dimensional subspace of V. Let $\{\phi_1, \ \phi_2,...,\phi_n\}$ be a set of linear independent basis functions such that $S^h = \textrm{span}(\{\phi_1, \phi_2, ..., \phi_n \})$ and $\phi_i \in C^{(1)}$ for all $i$.\\

For any function $w_h$ in $S^h$, $w_h$ can be expressed as a linear combination
\begin{eqnarray*}
	w_h = \sum_{j=1}^n w_j \phi_j.
\end{eqnarray*} Define a vector valued function $\bar{w} = \langle w_1 \ w_2 \ ... \ w_n \rangle$ for each $w_h \in S^h$. Denote the problem of solving the Galerkin Approximation of Problem GVar, by Problem GVar$^h$.

\subsubsection*{Problem GVar$^h$}
Given a function $f: J \rightarrow X$, find a function $u_h \in C^2(J)$ such that for each $t\in J$
\begin{eqnarray}
 c(u_h''(t),v)+a(u_h'(t),v)+b(u_h(t),v)= (f(t),v)_{X} \ \ \ \ \textrm{for each} \ v \in S^h, \label{DC_E2} 
\end{eqnarray}
with the initial values $u_h(0)=u^h_{0}$ and $u'_h(0)=u^h_{1}$. The initial conditions $u^h_{0}$ and $u^h_{1}$ are projections of $u_0$ and $u_1$ into the finite dimensional space $S^h$.\\

If the function $f$ is continuous, then Problem GVar$^h$ is equivalent to a system of second order differential equations. The following theorem from \cite{BV13} proves that if $f$ is continuous, then problem Problem GVar$^h$ has a unique solution.

\newtheorem{DC_Thm2}{Theorem}
\begin{DC_Thm2} \label{DC_THM2}
	If $f \in C(J,X)$, then there exists a unique solution $u_h \in C^2(J)$ for Problem GVar$^h$ for each $u_0^h$ and $u_1^h$ in $S^h$. If $f = 0$ then $u_h \in C^2((-\infty, \infty))$.
\end{DC_Thm2}

\subsection{Error estimates}
Given that the assumptions \textbf{A1}-\textbf{A4} of Section 2 is satisfied, and $f$ is continuous, there exists unique solutions for  Problem GVar and Problem GVar$^h$. It remains only to show that the solution of Problem GVar$^h$ denoted by $u^h$ converges to the solution of Problem GVar denoted by $u$ as $h$ is decreased.\\

Suppose $u$ is a solution of Problem GVar and $u^h$ is a solution of Problem GVar$^h$. Define the error $e^h$ by 
\begin{eqnarray*}
	e^h(t) = u(t) - u^h(t).
\end{eqnarray*}

In \cite{BV13}, a projection $P$ is defined so that $Pu \in V$. The error is then split using this projection. Let $e(t) = Pu(t)- u_h(t)$ and $e_p(t) = u(t) - Pu(t)$ so that 
\begin{eqnarray}
	e^h(t) = e_p(t) +e(t) \label{Error}
\end{eqnarray}

The authors of \cite{BV13} use interpolation theory to determine the error $e_p$. However to obtain an error estimate for $e$ is not trivial. The approach of the authors is to use Finite Element Analysis to obtain an error estimate for $e$.

\subsection{Main result}

The following two assumptions are made in \cite{BV13}.
\subsubsection*{Assumptions}
\begin{itemize}
	\item[] \textbf{B1} - The solution $u \in C(J,V)$ of Problem GVar$^h$ has the property that $(Pu) \in C^2(J)$.

	\item[] \textbf{B2} - There exists a subspace $H$ of $V$ and a positive integer $\alpha$ such that if $w \in H$, then $$\inf_{v\in S^{h}}||w-v||_V \leq \hat{C} h^\alpha|||w|||_H,$$ where $|||w|||_H$ is a norm or a semi-norm for $H$.
\end{itemize}

\newtheorem*{DC_Thm5}{Theorem 3}
\begin{DC_Thm5}
	Error estimate\\
	If $f\in C^{2}([0,T],X)$, then
	\begin{eqnarray*}
		\Vert u_{h}(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & 7T^{2}\tau^{2}\max\Vert u_{h}^{(4)}\Vert_{W}+7T\tau^{2}\max\Vert u_{h}'''\Vert_{W}\\
		& & + \sqrt{2K_{a}}\tau^{4}\max\Vert u_{h}'''\Vert_{W}
	\end{eqnarray*}
	for each $t\in(0,\ T)$.
\end{DC_Thm5}

\subsection{System of ordinary differential equations}
Consider the standard FEM matrices defined by
\begin{eqnarray*}
	K_{ij} & = & b(\phi_j, \phi_i)\\
	C_{ij} & = & a(\phi_j, \phi_i)\\
	M_{ij} & = & c(\phi_j, \phi_i)\\
	F_{i}(t) & = & b(f(t), \phi_i)_X
\end{eqnarray*}

Using these matrices, Problem GVar$^h$ is rewritten as a system of ordinary differential equations.
\subsubsection*{Problem ODE}
Find a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	M\bar{u}'' + C \bar{u}' + K\bar{u} = F(t) \ \ \ \textrm{ with } \bar{u}(0) = \bar{u}^h_0 \textrm{ and }  \bar{u}(1) = \bar{u}^h_1 \label{ODE}
\end{eqnarray}
The function $F(t)$ is the interpolation of the function $f(x,t)$ into the discrete space $S^h$. \\

The following propositions are given in \cite{BV13}. The proof of Theorem 1 follows from these two propositions.

\newtheorem{DC_Prop2}{Proposition}
\begin{DC_Prop2}
	Suppose $M, K, C, F,\bar{d}$  and $\bar{v}$ are defined as above. Then, the function $u_{h}$ is a solution of Problem $G^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
\end{DC_Prop2}

Since the matrix $M$ is invertible, \eqref{ODE} can be rewritten as $\bar{u}'' + M^{-1}C\bar{u}' + M^{-1}K \bar{u} = M^{-1}F(t)$. Using the theory of linear differential equations, a unique solution for Problem ODE can be found. This proves Proposition 2.

\newtheorem{DC_Prop3}[DC_Prop2]{Proposition}
\begin{DC_Prop3}
	If $F\in C(J)$, then Problem ODE has a unique solution for each pair of vectors $\bar{d}$ and $\bar{v}.$
\end{DC_Prop3}

The \cite{BV13}, the authors first investigate a semi-discrete Galerkin approximation. In this semi-discrete approximation, $x$ is discretised and $t$ remains continuous. Results for the semi-discrete approximation are required for the results of the fully-discrete approximation.\\

The results for the semi-discrete problem are necessary, since later in \eqref{error_e} it will be shown that the error $e(t)$ can be split up into a semi-discrete term and a fully-discrete term.

\sout{Before the fully discrete Galerkin Scheme is investigated, a result from \cite{BV13} on semi-discrete error estimates is required.}\\
\subsection{Semi-discrete error estimate}

Define the projection $P$ such that for any function $u$, 
\begin{eqnarray*}
	(Pu)(t) = Pu(t) \ \ \ \textrm{ for all } t \in (0,T).
\end{eqnarray*}

The authors of \cite{BV13} introduce two assumptions.
\subsubsection*{Assumptions} 
\begin{itemize}
	\item[] \textbf{E1} - The solution $u$ of Problem GVar has the property that $(Pu) \in C^2(0,T)$.

	\item[] \textbf{E2} -There exists a subspace $H$ of $V$ and a positive integer $\alpha$ such that if $w\in H,$ then
	\begin{eqnarray*}
		\inf_{v\in S^{h}}\Vert w-v\Vert_{V}\leq\hat{C}h^{\alpha}|||w|||_{H},
	\end{eqnarray*}
	where $|||w|||_{H}$ is a norm or semi-norm for $H.$
\end{itemize}

From Theorem 1, it follows that the solution $u$ of Problem GVar satisfies $u \in C^1([0,T]; V) \cap C^2((0,T);V)$. \textcolor{red}{This is a weak assumption made in \cite{BV13}.}\\

\sout{The following is a weak assumption in \cite{BV13}: The solution $u$ of Problem GVar satisfies $u \in C^1([0,T]; V) \cap C^2((0,T);V)$. This follows from Theorem 1 and is a necessary assumption in [BSV17].}\\

Let $\Pi$ denote the interpolation operator such that $u_0^h = \Pi u_0$ and $u_1^h = \Pi u_1$.

\newtheorem*{DC_Thm4}{Theorem 2}
\begin{DC_Thm4}
	Suppose Assumption E2 holds and $u_{0}^{h}=\Pi u_{0}$ and $u_{1}^{h}=\Pi u_{1}.$ If the solution $u$ of Problem $GVar$ satisfies Assumption El, $u(t)\in H$ and $u'(t)\in H$, then
	\begin{eqnarray*}
		\Vert u(t)-u_{h}(t)\Vert_{W} & \leq & C_{b} \hat{C}h^{\alpha}|||u(t)|||_{H}+\sqrt{2}C_{b}\hat{C}h^{\alpha}(3T\max|||u'(t)|||_{H}\\
		& & +3K_{a}T\max|||u(t)|||_{H}+(2+3K_{a}T)|||u_{0}|||_{H} \\
		& & +3T|||u_{1}|||_{H}) ,
	\end{eqnarray*} for each $t\in[0, T].$
\end{DC_Thm4}

\subsection{Fully discrete Galerkin finite element approximation}
Consider the time interval $J = [0,T]$. Divide $J$ into $N$ steps with length $\tau = \frac{T}{N}$. Each interval can be expressed as $[t_{k-1}, \ t_k]$ for $k = 1,...,N$. Denote the approximation of $u_h$ on the interval $[t_{k-1}, \ t_k]$ by $u_k^h$, i.e. $u_h(t_k) = u_k^h$ for each $k$.\\

\sout{The goal the fully-discrete approximation as given by \cite{BV13} is to find an estimate between Problem GVar and Problem GVar$^h$, which can be expressed as}

The error $e(t)$, can now be expressed as
\begin{eqnarray}
	e(t_k) = u(t_k) - u^h_k & = & [u(t_k)-u_h(t_k)] + [u_h(t_k) - u^h_k]. \label{error_e}
\end{eqnarray}

From Theorem 2 of the semi-discrete problem an error estimate for $[u(t_k)-u_h(t_k)]$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $[u_h(t_k) - u^h_k]$. Since the dimension of $S^h$ is not fixed, the equivalence of norms cannot be used, and therefore this error estimate for $[u_h(t_k) - u^h_k]$ should also be with respect to the norm of $W$.

\sout{In Theorem 2, Section 3.1.3 it is shown that \cite{BV13} obtained an error estimate for $[u(t_k)-u_h(t_k)]$ with respect to the norm of $W$. The authors explain that an estimate for $[u_h(t_k) - u^h_k]$ should also be with respect to the norm $W$ since the dimension of $S^h$ is not fixed and hence the equivalence of the relevant norms cannot be used.}\\

\subsubsection{Notation}
For any sequence $\{x_k\} \in R_n$,
\begin{eqnarray*}
	\delta_{t}x_{k}& = &\tau^{-1}[x_{k+1}-x_{k}],\\
	x_{k+\frac{1}{2}} & = & \frac{1}{2}[x_{k+1}+x_{k}].
\end{eqnarray*}

Let Problem GVar$^h$-D denote the fully discrete form of Problem GVar$^h$.
\subsubsection*{Problem GVar$^\mathbf{{h}}$-D}
Find a sequence $\{u_{k}^{h}\}\subset S^{h}$ such that for $k=0,1,2$, . . . , $N-1,$
\begin{eqnarray}
	\delta_{t}u_{k}^{h}\ & = & v_{k+\frac{1}{2}},\\
	c(\delta_{t}v_{k},\ \psi)+a(v_{k+\frac{1}{2}},\ \psi)+b(u_{k+\frac{1}{2}}^{h},\ \psi) & = & \frac{1}{2}([f(t_{k})+f(t_{k+1})],\ \psi)_{X} \nonumber \\ \label{PP}
\end{eqnarray}
for each $\psi\in S^{h}$, while $u_{0}^{h}=u_{h}(0)=d^{h}$ and $v_{0}=u_{h}'(0)=v^{h}$.\\

\textcolor{red}{Haal uit************************************************}\\
The article \cite{BV13} proves the following proposition. This proposition proves that Problem GVar$^h$-D is well defined.

\newtheorem{DC_Prop4}[DC_Prop2]{Proposition}
\begin{DC_Prop4}
	Problem $GVar^{h}-D$ has a unique solution for any pair of vectors $d^{h}$ and $v^{h}$ in $S^{h}$.
\end{DC_Prop4}

In the proof of Proposition 3, the authors of \cite{BV13} show that \eqref{PP} in Problem GVar$^h$-D can be rewritten as
\begin{eqnarray}
	c(v_k+1,\phi) + \frac{\tau}{2} a(v_{k+1},\phi) + \frac{\tau^2}{4} a(v_{k+1},\phi) & = & c(v_k,\phi) - \frac{\tau}{2} a(v_k,\phi) \nonumber \\  &&
	 - \frac{\tau^2}{4}b(v_k,\phi) - \tau b(u_k,\phi) \nonumber\\
	 &&+\frac{\tau}{2}([f(t_k)+f(t_{k+1})],\phi)_X.\nonumber \\ \label{PPP}
\end{eqnarray} for each $\phi \in S^h$.\\

Using \eqref{PPP} and the definition of the standard finite element matrices, Problem GVar$^h$-D can be reformulated into a algorithm for the Finite Element Method. This is the fully discrete form of Problem GVar and is represented in Problem FD.\\
\textcolor{red}{******************************************************}\\

Further results and the standard Finite Element Matrices, let the authors of \cite{BV13} rewrite Problem GVar$^\mathbf{{h}}$-D into an algorithm for the Finite Element Method. This is represented as Problem FD

\subsubsection*{Problem FD}
Find a sequence $\{\bar{u}_{k}\}\subset R_{n}$ such that for each $k,$
\begin{eqnarray*}
	\bar{u}_{k+1}\ & = & \bar{u}_{k}+\tau\bar{v}_{k+\frac{1}{2}},\\
	(M + \frac{\tau}{2}C+\frac{\tau^{2}}{4}K)\bar{v}_{k+1} & = & (M- \frac{\tau}{2}C-\frac{\tau^{2}}{4}K)\bar{v}_{k}-\tau K\bar{u}_{k}+\frac{\tau}{2}[F(t_{k})+F(t_{k+1})]
\end{eqnarray*}
with $\bar{u}_{0}=\bar{d}$ and $\bar{v}_{0}=\bar{v}.$\\

In this form, the problem is fully discrete. This form also allow the authors of \cite{BV13} to obtain an error estimate for the fully-discrete problem.

\subsubsection{Error estimate for the fully discrete problem}

\textcolor{red}{Haal uit*****************************}\\
There error estimate for $[u_h(t_k) - u^h_k]$ can now be determined. Recall that $\tau = \frac{T}{N}$. Subsituting $t = t_k$ and $t = t_k+1$ in Problem GVar$^h$ results in
\begin{eqnarray*}
	c( \tau^{-1}[v_{h}(t_{k+1})-v_{h}(t_{k})], \psi)+\frac{1}{2}a([v_{h}(t_{k+1})+v_{h}(t_{k})], \psi)+\frac{1}{2}b([u_{h}(t_{k+1})+u_{h}(t_{k})], \psi) \\
	=\frac{1}{2}([f(t_{k+1})+f(t_{k})], \psi)_{X}+c(\rho_{k}, \psi)
\end{eqnarray*}
where $v_{h}(t)=u_{h}'(t)$ and
\begin{eqnarray*}
	\rho_{k}=\tau^{-1}[v_{h}(t_{k+1})-v_{h}(t_{k})]-\frac{1}{2}[v_{h}'(t_{k+1})+v_{h}'(t_{k})].
\end{eqnarray*}

The authors in \cite{BV13} denote the following errors
\begin{eqnarray*}
	e_{k}=u_{h}(t_{k})-u_{k} \ \ \ \ \textrm{ and } \ \ \ \ q_{k}=u_{h}'(t_{k})-v_{k}.
\end{eqnarray*} In the authors approach, $e_0$ and $q_0$ are zero.

\newtheorem*{DC_Lem3}{Lemma 2}
\begin{DC_Lem3}
	Stability
	\begin{eqnarray*}
		\max\Vert e_{n}\Vert_{W}^{2}\leq 8T\tau\sum_{n=0}^{N-1}\Vert\epsilon_{n}\Vert_{W}^{2}+2\tau^{4}\Vert\rho_{0}\Vert_{W}^{2}+(8\tau^{2}+2\tau^{4}K_{a})\Vert\sigma_{0}\Vert_{W}^{2}.
	\end{eqnarray*}
\end{DC_Lem3}

Using this lemma, \cite{BV13} proves the following error estimate.\\
\textcolor{red}{*************************************}

Recall that $\displaystyle \tau = \frac{T}{N}$. The error estimate for the term $[u_h(t_k) - u^h_k]$ with respect to the norm of $W$ as proven by the authors of \cite{BV13} is presented here as Theorem 3.

Finally, Theorem 2 of the semi-discrete problem and Theorem 3 of the fully discrete problem gives an error estimate for the error $e(t)$. Consequently, the error estimate $e^h(t) = u(t) - u^h(t)$ is obtained.

\end{document}

Define the error $e_h$ as the error between the solutions of Problem GVar and Problem GVar$^h$, i.e.
\begin{eqnarray}
	e_h(t) = u(t)-u_h(t). \label{Error}
\end{eqnarray}

Since $u$ is unknown, the error $e_h$ cannot be calculated directly. Instead the authors of \cite{BV13} derive estimate for this error using projections.***  \\

Define a projection operator $P_h$ by
\begin{eqnarray*}
	b(u - P_hu, v) = 0 \ \ \ \textrm{ for all } v \in S^h.
\end{eqnarray*}

Define the projection $P$ such that for any function $u$, 
\begin{eqnarray*}
	(Pu)(t) = Pu(t) \ \ \ \textrm{ for all } t \in (0,T).
\end{eqnarray*}

Same a \cite{BV13}, $P_h$ is renamed to $P$ for convenience. $P_h$ will be used when it is needed to differentiate between $P$ and $P_h$. Define the following errors $e_p$ and $e$ by
\begin{eqnarray*}
	e(t) & = & Pu(t) - u_h(t),\\
	e_p(t) & = & u(t) - Pu(t).
\end{eqnarray*}
Then \eqref{Error} can be rewritten as
\begin{eqnarray*}
	e_h(t) = e(t) - e_p(t).
\end{eqnarray*}

Estimates for the norm of $e_p$ is obtained in \cite{BV13} using approximation theory. It is only left to find an estimate for $e(t)$. The approach of \cite{BV13} is to estimate the error $e$ using the projection error $e_p$ and errors for the initial conditions.

\subsubsection*{Assumptions} 
The following assumptions are made in \cite{BV13} for the convergence results.
\begin{itemize}
	\item[] \textbf{E1} - The solution $u$ of Problem GVar has the property that $(Pu) \in C^2(0,T)$.

	\item[] \textbf{E2} - The solution $u$ of Problem GVar satisfies $u \in C^1([0,T]; V) \cap C^2((0,T);V)$.
\end{itemize}

\subsubsection{Remark}
- Assumption \textbf{E2} is a weak assumption and follows from the existence theorem, Theorem 1 of Section 2.2. In [BSV17], \textbf{E2} is no longer a weak assumption but a necessary assumption. *****\\

From this Proposition in \cite{BV13} the general variational problem in terms of the errors $e_h$ and $e$.
\newtheorem{DC_Prop1}{Proposition}
\begin{DC_Prop1}
	If $u$ is a solution of Problem GVar and satisfies Assumption E1, then
	\begin{eqnarray*}
		c(e_h''(t),v)+a(e_h'(t),v)+b(e_h(t),v) = 0 \ \ \ \ \textrm{for each} \ v \in S^h.
	\end{eqnarray*}
\end{DC_Prop1}

\subsection{Fundamental estimate}
The authors of \cite{BV13} use the form of Proposition 1, to give a generalization of an estimate for the error $e(t)= Pu(t)- u_h(t)$.

\newtheorem{DC_Lem2}{Lemma}
\begin{DC_Lem2}
	If the solution $u$ of Problem $GVAr$ satisfies Assumption El, then for $t\in[0,\ T],$
	\begin{eqnarray*}
		\Vert e(t)\Vert_{W}\ &\leq\ & \sqrt{2}(\Vert e(0)\Vert_{W}+3T\Vert e_{h}'(0)\Vert_{W}+3\int_{0}^{T}\Vert e_{p}'(t)\Vert_{W}\\
		& & +3K_{a}T\Vert e_{h}(0)\Vert_{W}+3K_{a}\int_{0}^{T}\Vert e_{p}(t)\Vert_{W})
	\end{eqnarray*}
\end{DC_Lem2}

Similarly, for $a = 0$ (weak damping as explained in Section 2.2), the following corollary is obtained in a similar proof to Lemma 1.
\newtheorem{DC_Cor1}{Corollary}
\begin{DC_Cor1}
	If the solution $u$ of Problem $GVar$ with $a=0$ satisfies Assumption $El$, then for $t\in[0, T],$
	\begin{eqnarray*}
		\Vert e(t)\Vert_{W} & \leq  & \sqrt{2}\Vert e(0) \Vert_W + 2T\Vert e_h'(0) \Vert_W + 4 \sqrt{T} \max\limits_{t \in [0,T]} \Vert e_p'(t) \Vert_W.
	\end{eqnarray*}
\end{DC_Cor1}

\subsection{Convergence and error estimated for the semi-discrete approximation}
Consider Problem GVar$^h$ with discretised space and continuous time variables. This is known as a semi-discrete problem. This is a natural intermediate step between a continuous and a fully discrete problem.\\

\newtheorem*{DC_Thm3}{Theorem 2}
\begin{DC_Thm3}
	If the solution $u$ of Problem $G$ satisfies Assumption Al, then
	\begin{eqnarray}
		\Vert u(t)-u_{h}(t)\Vert_{W} & \leq & \Vert e_{p}(t)\Vert_{W}+\sqrt{2}(\Vert Pu_{0}-u_{0}\Vert_{W}+3T\Vert u_{1}-u_{1}^{h}\Vert_{W}+3\int_{0}^{T}\Vert e_{p}'(t)\Vert_{W} \nonumber \\
		& & +(1+3K_{a}T) \Vert u_{0}-u_{0}^{h}\Vert_{W}+3K_{a}\int_{0}^{T}\Vert e_{p}(t)\Vert_{W}) \label{DC_E7}
	\end{eqnarray}
	for each $t\in[0,\ T].$
\end{DC_Thm3}
\begin{comment}
\begin{proof}
From (3.2), $\Vert u(t)-u_{h}(t)\Vert_{W}\leq\Vert e_{p}(t)\Vert_{W}+\Vert e(t)\Vert_{W}$.\\

The result follows from Lemma 4.1 since $\Vert Pu_{0}-u_{0}^{h}\Vert_{W}\leq\Vert Pu_{0}-u_{0}\Vert+\Vert u_{0}-u_{0}^{h}\Vert.$
\end{proof}
\end{comment}

To be able to use Theorem in application, it is necessary to be able to estimate an element in $V$ with an element in $S^h$. Suppose $h$ is related to the dimension n of $S^h$ such that $h \rightarrow 0$ as $n \rightarrow \infty$.\\

Another assumption is introduced by \cite{BV13}.

\subsubsection*{Assumption E3}
There exists a subspace $H$ of $V$ and a positive integer $\alpha$ such that if $w\in H,$ then
\begin{eqnarray*}
	\inf_{v\in S^{h}}\Vert w-v\Vert_{V}\leq\hat{C}h^{\alpha}|||w|||_{H},
\end{eqnarray*}
where $|||w|||_{H}$ is a norm or semi-norm for $H.$\\

Using this assumption, the projection errors in Theorem 2 can be expressed as 
\begin{eqnarray*}
	||e'_p(t)||_W & \leq & C_b \hat{C} h^\alpha |||u'(t)|||_H,\\
	||u_0 - u_0^h||_W & \leq & C_b \hat{C} h^\alpha |||u_0|||_H,
\end{eqnarray*} if $u^h_0$ and $u^h_1$ are chosen as $Pu_0$ and $Pu_1$. However choosing $u^h_0$ and $u^h_1$ in this form is not possible in general. Let $\Pi$ denote the interpolation operator such that $u_0^h = \Pi u_0$ and $u_1^h = \Pi u_1$.

\newtheorem*{DC_Thm4}{Theorem 3}
\begin{DC_Thm4}
	Suppose Assumption E3 holds and $u_{0}^{h}=\Pi u_{0}$ and $u_{1}^{h}=\Pi u_{1}.$ If the solution $u$ of Problem $GVar$ satisfies Assumption El, $u(t)\in H$ and $u'(t)\in H$, then
	\begin{eqnarray*}
		\Vert u(t)-u_{h}(t)\Vert_{W} & \leq & C_{b} \hat{C}h^{\alpha}|||u(t)|||_{H}+\sqrt{2}C_{b}\hat{C}h^{\alpha}(3T\max|||u'(t)|||_{H}\\
		& & +3K_{a}T\max|||u(t)|||_{H}+(2+3K_{a}T)|||u_{0}|||_{H} \\
		& & +3T|||u_{1}|||_{H}) ,
	\end{eqnarray*} for each $t\in[0, T].$
\end{DC_Thm4}

### 2022-10-31 files/Chapter3/femconvergence.tex
initial commit

s\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Convergence of eigenvalues in Finite Element Analysis}
This section looks at the work of the authors of the textbook [SF97].

\subsection{Eigenvalue problem for vibration problem}
Consider the general variational problem Problem GVar from section 2.2.1
\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
	Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
\begin{eqnarray}
	c(u''(t),v)+a(u'(t),v)+b(u(t),v)= (f(t),v)_{X} \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVar}
\end{eqnarray}
while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\\

\textcolor{red}{Haal uit**********************************}\\
The following spaces are also defined in section 2.2.1:
\begin{itemize}
	\item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
	\item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
	\item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
\end{itemize} The inner product of the function space $L^2$ is given by $(\cdot, \cdot)$ with induced norm $||\cdot||_{L^2}$.\\

Define a Hilbert space $H = V \times W$, with inner product defined by
\begin{eqnarray*}
	(x,y)_H := b(x_1,y_1) + c(x_1,y_1) \ \ \ \ \textrm{for all} \ x,y \in H.
\end{eqnarray*} $V$ is obviously a linear subspace of $H$, and it is assumed that $(\cdot,\cdot)_V  = b(\cdot,\cdot)$. $V$ is also the closure of the test function space $T$.\\
\textcolor{red}{**********************************}\\

Recall form Section 2.2, $V$ is the energy space with inner-product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$. For the Timoshenko beam theory, $V$ is the closure of the test-function space $T$. It is assumed that $b(\cdot,\cdot) = (\cdot,\cdot)_V$.\\

Denote the eigenvalue problem of Problem GVar by Problem GVarE. This eigenvalue problem can be formulated as follow

\subsubsection{Problem GVarE} Find $\lambda \in \mathbb{R}$ and $u \in V$ such that
\begin{eqnarray*}
	b(u(t),v) = \lambda c( u(t), v ) \ \ \ \ \textrm{ for all  } v\in V.
\end{eqnarray*}

\subsection{Interpolation theorem}
Consider the Interpolation Theorem for Finite Elements from the textbook [ORXX].\\

\sout{Consider the following theorem for Finite Elements from the textbook [ORXX]. This theorem is called The Interpolation Theorem for Finite Elements.}

\newtheorem*{Interpolation}{Theorem}
\begin{Interpolation}[The Interpolation Theorem for Finite Elements] 
	Let $\Omega$ be an open bounded domain in $\mathcal{R}^n$ satisfying the cone condition. Let $k$ be a fixed integer and $m$ an integer such that $0\leq m \leq k+1$. Let $\Pi \in L(H^{k+1}(\Omega), H^{m}(\Omega))$ be such that
	\begin{eqnarray}
	    \Pi u = u \ \ \ \ \textrm{ for all } u \in \mathcal{P}_k(\Omega)
	\end{eqnarray}
	Then for any $u \in H^{k+1}(\Omega)$ and for sufficiently small $h$, there exists positive a constant $C$, independent of $u$ and $h$, such that
	\begin{eqnarray}
	    ||u - \Pi u||_{H^m(\Omega)} \leq C \frac{h^{k+1}}{p^m} |u|_H^{k+1}(\Omega)
	\end{eqnarray}
	where $|u|_H^{k+1}(\Omega)$ is the seminorm.
\end{Interpolation} ************what is p?

This theorem provides an error estimate for the projection of $u$ in a Sobolev space. By proving this theorem, the authors in [ORXX] show the accuracy of the finite element interpolations of functions $u$ defined in a Sobolev space $H^{k+1}(\Omega)$ into a finite dimensional subspace $S^h(\Omega)$, with the projection defined by $\Pi u$.\\

\subsection{Eigenvalue problem for our models*********}
For this dissertation, the result can be simplified and need not be so general. The basis functions used in this dissertation are called Hermite-Cubic basis functions. Therefore the focus can be restricted to functions in an n-dimensional polynomial space.\\
**********Wys hoe function spaces H, V, W verander na polynomial spcaes!!************

\subsubsection{Notation}
Define the linear interpolation operator as
\begin{eqnarray*}
	\Pi f &=& f_{I},
\end{eqnarray*} such that
\begin{eqnarray*}
	\Pi (f+g) &=& \Pi f + \Pi g, \\
	\Pi (\alpha f) &=& \alpha \Pi f.
\end{eqnarray*}
%\newpage

Define the reference interval $I_{e} = [a, a+h]$. The following notation,
\begin{eqnarray*}
	\left[\Pi u \right]_{I_{e}} &=& \Pi_{e} \left[u\right]_{I_{e}},
\end{eqnarray*} implies that $\Pi u$ restricted to the interval $I_{e}$ must equal $\Pi_{e} u$.\\

Define the following set and integers.
\begin{itemize}
	\item[] $\mathcal{P}_{j}(I_{e}):$ the set of all polynomials on the interval $I_{e}$ of degree at most $j$.\\

	\item[] $r(\Pi_{e})$: If the range of $\Pi_{e}$ is contained in $\mathcal{P}_{j}(I_{e})$ and $k\leq j$ is the largest integer such that $\Pi_{e} f = f$ for each $f\in\mathcal{P}_{j}(I_{e})$, then $r(\Pi_{e}) = k$.\\

	\item[] $s(\Pi_{e})$: the integer $s(\Pi_{e})$ is the largest order derivative used in the definition of $\Pi_{e}$.
\end{itemize}
\textbf{Interpolation Theorem} Suppose there exists an integer $k$ such that for each element
\begin{eqnarray*}
	s(\Pi_{e}) + 1 \leq & k & \leq r(\Pi_{e}) + 1
\end{eqnarray*}
Then there exists a constant C such that for any $u\in C^{k}_{+}(I)$ we have
\begin{eqnarray*}
	||(\Pi u)^{(m)} - u^{(m)}|| & \leq & Ch^{k-m}||u^{(k)}|| \ \ \textrm{ for } m = 0,1,...,k
\end{eqnarray*}

In this form, the theory of convergence of the eigenvalues for our models can be investigated. For this theory, consider another textbook [SF73]. In this textbook, the authors prove the convergence of of the eigenvalues using the interpolation theorem. The results of the authors of [SF73] is discussed here, in the notation followed in throughout this dissertation.

\subsection{Convergence of the eigenvalues}
From the brief introduction of modal analysis in section 1.xxx, it is clear that the solution of the eigenvalue problem is an infinite sequence of eigenvalues with corresponding eigenfunctions (eigenvectors in this case). Therefore assume the eigenvalues can be ordered, i.e. $\lambda_{1} \leq \lambda_{2} \leq \lambda_{3} \leq ...$. Denote the corresponding eigenvectors by $u_{i}$ and scale the eigenvectors such that $||u_{i}|| = 1$ for all $i$. Fix $m\in\mathbb{N}$ and consider a finite dimensional ordered subset of the eigenvalues $\lambda_{1} \leq \lambda_{2} \leq \lambda_{3} \leq ... \leq \lambda_{m}$.\\

For each of the models in this dissertation, the set of test functions are defined as $T$. Now take the set of admissible basis functions $\left\{ \phi_{i} \in T \ | \ i = 1,2,...,m\right\}$, and define a finite dimensional subspace $S^{h} := span(\left\{\phi_{i}\in T \ | \ i = 1,2,...,m\right\})$ of V. From this finite dimensional subspace, the following set of eigenvalues $\lambda^{h}_{1} \leq \lambda^{h}_{2} \leq \lambda^{h}_{3} \leq ... \leq \lambda^{h}_{m}$, also ordered, with corresponding normalized eigenvectors $u^{h}_{i}$ for each i are obtained.\\

The following definitions from [SF73] are required for the theory.\\
\textbf{Rayleigh Quotient:}
\begin{align*}
	R(v) = \frac{b(v,v)}{( v,v )}
\end{align*}

\textbf{minmax Principle:} Let T denote the class of subspaces of V that has dimension j. Then
\begin{align*}
\lambda_{j} = \min\limits_{s\in T} \max\limits_{v\in S}R(v)
\end{align*}\\

\textbf{Rayleigh-Ritz Projection:} If $u \in V$, then $Pu$ is its component in the subspace $S^{h}$:
\begin{align*}
b(u-Pu,v^{h}) = 0 \ \ \ \ \forall \ v^{h} \in S^{h}
\end{align*}

Now since the space $S^{h}$ is a finite subspace of T, any subspace of $S^{h}$ will also be a subspace of T. So the minmax principle applies to $S^{h}$. So we then get a lower bound for the approximate eigenvalues
\begin{align*}
\lambda_{i} \leq \lambda_{i}^{h}
\end{align*}

Let $E_{j} \subset T$ denote the eigenspace spanned by $\left\{u_{1},u_{2},...,u_{j}\right\}$ for $j = 1,2,...,m$. Then we consider the subspaces $S_{j}$ where
\begin{align*}
S_{j} = PE_{j} \ \ \textrm{ for } j = 1,2,...,m
\end{align*}
The elements $Py_{i}$ of $E_{j}$ are the projections of the exact eigenvectors to the space $S^{h}$ but are not necessarily equal to the eigenvector's approximations $u^{h}_{i}$. But it can proved that they are close.\\

Let $B_{m} = \left\{u\in E_{m} \ | \ ||u|| = 1\right\}$ and define $\mu_{m} = \inf\left\{ ( Pu,Pu) \ | \ \in B_{m} \right\}$.\\

\textbf{Proposition 7.1:} $\mu_{m} > 0$ if and only if $\dim S_{m} = m$\\

\begin{comment}
\textbf{Proof:} Suppose that $\dim S_{m} < m$, then the set of projected eigenvalues $\left\{Py_{1}, Py_{2},...,Py_{m}\right\}$ is a linearly dependent set. So then there exists a $u \in B_{m}$ such that $Pu = 0$. Then $\mu_{m} = 0$. So the result follows by the contra-positive. \qed \\

So we from here on assume that $S^{h}$ is such that $\dim S_{m} = m$.\\
\end{comment}

\textbf{Proposition 7.2:} $\lambda^{h}_{m} \leq \max\left\{R(Pu) \ | \ u \in B_{m} \right\}$\\

\begin{comment}
\textbf{Proof:} The minmax principle gives $\lambda_{m}^{h} \leq \max\left\{R(v) \ | \ v \in S_{m} \right\}$ since $\dim S_{m} = m$.\\

Now we take an arbitrary $v \in S_{m}$, $v \neq 0$. Then there exists a $u \in E_{m}$ such that $Py = v$. Since $u \in E_{m}$, we have that $\frac{1}{||u||}u \in B_{m}$ and

\begin{eqnarray*}
R(\frac{1}{||u||}u) &=& \frac{b\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)}{\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)}\\
					&=& \frac{b(u,u)}{(u,u)}\\
					&=& R(u)
\end{eqnarray*}
So then we have that
\begin{eqnarray*}
\lambda_{m}^{h} &\leq & \max\left\{R(v) \ | \ v \in S_{m} \right\}\\
					&=& \max\left\{R(Pu) \ | \ u \in E_{m} \right\}\\
					&=& \max\left\{R(Pu) \ | \ u \in B_{m} \right\}
\end{eqnarray*}\qed
\end{comment}
%\newpage

\textbf{Lemma 7.1:} $\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}$\\

\begin{comment}
\textbf{Proof:} Let $Y = \sum_{i=1}^{m} c_{i}u_{i}$.
\begin{eqnarray*}
b(u,u) &=& b\left(\sum_{i=1}^{m} c_{i}u_{i},\sum_{j=1}^{m} c_{j}u_{j}\right)\\
		&=& \sum_{i=1}^{m} c_{i}\sum_{j=1}^{m} c_{j} b(u_{i},u_{j})
\end{eqnarray*}
\textbf{RTP:} $\left\{u_{1},u_{2},...,u_{m}\right\}$ is orthonormal.\\
Pick any $i,j \in \mathbb{N}$ such that $i,j \leq m$. Let arbitrary $v_{i},v_{j} \in V$ be arbitrary, then
\begin{eqnarray*}
	b(u_{i},u_{i}) &=& \lambda_{i}( u_{i},u_{i})\\
	b(u_{j},u_{j}) &=& \lambda_{j}( u_{j},u_{j})
\end{eqnarray*}
Now we pick $u_{i} = u_{j}$ and $u_{j} = u_{i}$. Then
\begin{eqnarray*}
	b(u_{i},u_{j}) &=& \lambda_{i}( u_{i},u_{j})\\
	b(u_{j},u_{i}) &=& \lambda_{j}( u_{j},u_{i})
\end{eqnarray*}
Then using the symmetry of $b(\cdot,\cdot)$ and $( \cdot, \cdot )$, and subtracting, we get
\begin{eqnarray*}
 0 &=& (\lambda_{i} - \lambda_{j})( u_{i}, u_{j} )
\end{eqnarray*}
So if $i \neq j$, $\lambda_{i} \neq \lambda_{j}$. Thus we must have that $u_{i}$ and $u_{j}$ are orthogonal. And since by the way $u_{i}$ is defined, $||u_{i}|| = 1$. So thus $\left\{u_{1},u_{2},...,u_{m}\right\}$ is orthonormal.\\

So then $b(u,u) = \sum_{i=1}^{m} c_{i}^{2} \lambda_{i} \leq \lambda_{m}\sum_{i=1}^{m} c_{i}^{2} =\lambda_{m} ||u||^{2}$ for all $u \in E_{m}$.\\
And since $B_{m} \subset E_{m}$, we have $b(Pu,Pu) \leq \lambda_{m}$ for all $u\in B_{m}$\\

So now from the definition of $\mu_{m}^{h}$ and the Rayleigh quotient, we have
\begin{eqnarray*}
	R(Pu) &=& \frac{b(Pu,Pu)}{(Pu,Pu)}\\
		&=& \frac{b(Pu,Pu)}{||Pu||^{2}}\\
		&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}
\end{eqnarray*}
This together with Proposition 7.1 gives
\begin{eqnarray*}
	\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}
\end{eqnarray*}\qed
\end{comment}

Now since $\lambda_{i}^{h} \geq \lambda_{i}$ and by Lemma 7.1, we must then have that $0 < \mu_{m}^{h} \leq 1$. Now define the error estimate as
\begin{eqnarray*}
\sigma_{m}^{h} = 1 - \mu_{m}^{h}
\end{eqnarray*}

%\newpage

\textbf{Corollary 7.1:} $0 \leq \sigma_{m}^{h} < 1$ and $\lambda_{m}^{h} - \lambda_{m} \leq \lambda_{m}^{h}\sigma_{m}^{h}$\\

\begin{comment}
\textbf{Proof:}
\begin{eqnarray*}
\lambda_{m}^{h} & \leq & \frac{\lambda_{m}}{\mu_{m}^{h}} \ \ \textrm { (by Lemma 7.1)} \\
\lambda_{m}^{h}\mu_{m}^{h}& \leq & \lambda_{m} \\
-\lambda_{m}& \leq & -\lambda_{m}^{h}\mu_{m}^{h} \\
\lambda_{m}^{h} -\lambda_{m}& \leq & \lambda_{m}^{h} -\lambda_{m}^{h}\mu_{m}^{h}\\
\lambda_{m}^{h} -\lambda_{m}& \leq & \lambda_{m}^{h}\sigma_{m}^{h}
\end{eqnarray*}\qed

So from this Corollary 7.1, we see that to prove that our approximate eigenvalues converge to the exact eigenvalues. The only thing then left to prove is  that $\sigma_{m}^{h} \rightarrow 0$ as $h \rightarrow 0$.\\
\\

\textbf{Proposition 7.1} $\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}$\\

\textbf{Proof:}  Let $u \in B_{m}$. Then
\begin{eqnarray*}
||u - Pu||^{2} &=& ( u - Pu, u - Pu ) \\
				&=& ( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ) \\
				&=& 2( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ) - ( u, u )\\
				&=& 2( u, u - Pu ) + ( Pu, Pu ) - ( u, u )\\
( u, u ) - ( Pu, Pu )  & = & 2( u, u - Pu ) - ||u - Pu||^{2}	
\end{eqnarray*}
Now since $u \in B_{m}$, $<u,u> = 1$. So we have
\begin{eqnarray*}
1 - ||Pu||^{2}  & = & 2( u, u - Pu ) - ||u - Pu||^{2}	
\end{eqnarray*}
Now the right hand side, $1 - ||Pu||^{2} \leq 1 - \mu_{m}^{h} = \sigma_{m}^{h}$ for all $u \in B_{m}$. So then we must have that
\begin{eqnarray*}
\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}
\end{eqnarray*}\qed
\end{comment}

Next we introduce some new notation to ease the writing. For any $u \in E_{m}$, let $u^{*} = \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}$ where $u = \sum_{i=1}^{m} c_{i}u_{i}$.\\

%\newpage

\textbf{Proposition 7.3:} For any $u \in E_{m}$
\begin{eqnarray*}
( u, u - Pu ) = b(u^{*} - Pu^{*}, u -Pu)
\end{eqnarray*}

\begin{comment}
\textbf{Proof:} For any $i = 1,2,...,m$, we have that
\begin{eqnarray*}
\lambda_{i}( u_{i},u-Pu ) &=&  b(u_{i}, u-Pu)\\
									&=& b(u_{i}, u-Pu) - b(u-Pu,Pu_{i}) \ \textrm{ (by definition of Rayleigh-Ritz Projection)}\\
									&=&  b(u_{i}, u-Pu) - b(Pu_{i},u-Pu)\\
									&=&  b(u_{i}-Pu_{i}, u-Pu)
\end{eqnarray*}
So multiplying by $c_{i}\lambda_{i}^{-1}$ and summation over i gives:
\begin{eqnarray*}
\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}\lambda_{i}( u_{i},u-Pu ) &=& \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}b(u_{i}-Pu_{i}, u-Pu)\\
									&=& b(\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}-\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}Pu_{i}, u-Pu)\\
									&=& b(u^{*}-Pu^{*}, u-Pu)
\end{eqnarray*}
So $( u,u-Pu ) = b(u^{*}-Pu^{*}, u-Pu)$.\qed\\
\end{comment}

\textbf{Lemma 7.2:} $\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$\\

\begin{comment}
\textbf{Proof:} From Proposition 7.1, we have
\begin{eqnarray*}
\sigma_{m}^{h} &=& \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \} \\
				&\leq & \max\left\{ 2( u,u-Pu ) \ | \ u \in B_{m} \right \}
\end{eqnarray*} since $||u-Pu||^{2} \geq 0$.\\
\end{comment}

Using Proposition 7.3
\begin{eqnarray*}
\sigma_{m}^{h} &\leq & \max\left\{ 2b(u^{*} - Pu^{*}, u -Pu) \ | \ u \in B_{m} \right \}			
\end{eqnarray*}
Now
\begin{eqnarray*}
b(u^{*} - Pu^{*}, u -Pu) & \leq & ||u^{*} - Pu^{*}||||u -Pu|| \ \textrm{ (Schwartz inequality)} \\
\end{eqnarray*}
Thus  $\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$. \qed

%\newpage

\textbf{Proposition 7.3:} For any $\epsilon > 0$, there exists a $\delta >0$ such that for $h<\delta$,
\begin{eqnarray*}
||u^{*} - Pu^{*}|| < \epsilon \ \textrm{ for each } u \in B_{m}\\
||u - Pu|| < \epsilon \ \textrm{ for each } u \in B_{m}
\end{eqnarray*}

\begin{comment}
\textbf{Proof:}
Suppose we have a set of basis functions $\Phi \subset S^{h}$ such that each element in $\Phi$ has order k, i.e. for each $v \in \Phi$, $v^{(k)} = 0$. Now from the definition of the Rayleigh-Ritz Projection, we have that $Pu$ is the closest element in $S^{h}$ to $u$. In particular, $||u-Pu||\leq ||u-\Pi u||$, where $\Pi u$ is the interpolant of $u$ into $S^{h}$.\\

Now from, we use the Approximation Theorem, so that we have
\begin{eqnarray*}
||u - \Pi u|| \leq Ch^{k}||u^{(k)}||
\end{eqnarray*}
So for any $\epsilon > 0$, we can find a $\delta$ such that if $h<\delta$ then
\begin{eqnarray*}
||u - Pu|| \leq ||u - \Pi u|| \leq \epsilon
\end{eqnarray*}
A similar argument for $||u^{*} - Pu^{*}||$ proves the theorem.
\qed
\\
\end{comment}

\textbf{Lemma 7.4:} For any $\epsilon >0$ there exists a $\delta > 0$ such that
\begin{eqnarray*}
\sigma_{m}^{h} < \epsilon \ \textrm{ if } \ h < \delta
\end{eqnarray*}

\begin{comment}
\textbf{Proof:} For any $\epsilon > 0$ there exists a $\delta > 0$ such that if $h<\delta$, then
\begin{eqnarray*}
||u-Pu|| < \epsilon \ \textrm{ for each } \ u \in B_{m}
\end{eqnarray*}
This, together with Lemma 7.2 and Proposition 7.4 gives the result.\qed\\
\end{comment}

\textbf{Lemma 7.5:} There exists a $\delta > 0$ such that for $h < \delta$
\begin{eqnarray*}
\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}
\end{eqnarray*}

\begin{comment}
\textbf{Proof:}
Using Lemma 7.4, choose $\delta$ such that $\sigma_{m}^{h} < \frac{1}{2}$. Then by Lemma 7.1 gives that $\lambda_{m}^{h} < 2\lambda_{m}$. So we have that
$\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}$.
\qed
\end{comment}

\subsection{Convergence of the eigenfunctions}
So from Lemma 7.4, it is that if $h \rightarrow 0$, we will get convergence in the eigenvalues. The next step is now to use this, to show convergence in the eigenvectors.\\

\textbf{Lemma 7.6:}
\begin{eqnarray*}
b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& \lambda_{m}( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h} ) + \lambda_{m}^{h} - \lambda_{m}
\end{eqnarray*}

\begin{comment}
\textbf{Proof:}
\begin{eqnarray*}
b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& b(u_{m},u_{m}) - 2b(u_{m},u^{h}_{m}) + b(u^{h}_{m},u^{h}_{m}) \\
								&=& \lambda_{m} ( u_{m}, u_{m} ) - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h}( u_{m}^{h},u_{m}^{h} )\\
								&=&  \lambda_{m} - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} \\
								&=& 2\lambda_{m} - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} - \lambda_{m}\\
								&=& \lambda_{m}( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) + \lambda_{m}^{h} - \lambda_{m}
\end{eqnarray*}
\qed
\end{comment}

We have already shown that $\lambda_{m}^{h} \rightarrow \lambda_{m}$. So it remains only to show that $( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$

Now we have the possibility that an eigenvalue, say $\lambda_{m}$ has multiplicity $r>1$. This implies that there are at least two eigenfunctions that correspond to this eigenvalue.\\

The Euler-Bernoulli beam however, only has a repeated eigenvalue if we consider the free-free boundary conditions. Then the beam would have a zero eigenvalue with multiplicity more than 1. Our model, however, does not have repeated eigenvalues. So we may assume that all the eigenvalues has multiplicity $r=1$.\\

\textbf{Lemma 7.7:} For all m and j
\begin{eqnarray*}
(\lambda_{j}^{h} - \lambda_{m}) ( Pu_{m}, u_{j}^{h}) = \lambda_{m} ( u_{m}-Pu_{m},u_{j}^{h} )
\end{eqnarray*}

\begin{comment}
\textbf{Proof:}
Since the term $\lambda_{m}( Pu,u^{h}_{j})$ appears on both sides of the equation, it is only required to show that
\begin{eqnarray*}
\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& \lambda_{m} ( u, u_{j}^{h} )
\end{eqnarray*}
Now
\begin{eqnarray*}
\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& b(Pu,u_{j}^{h})\\
\lambda_{m} ( u, u_{j}^{h} ) &=& b(u,u_{j}^{h})
\end{eqnarray*} Since $u$ and $u_{j}^{h}$ are both eigenfunctions.\\

Then equality follows from the definitions of the projection P.
\qed
\end{comment}

The set $\left\{u_{1}^{h},u_{2}^{h},...,u_{N}^{h}\right\}$ then forms an orthonormal basis for $S^{h}$. So we can then write a projection $Pu_{m}$ as:
\begin{eqnarray}
Pu_{m} &=& \sum_{j=1}^{N} ( P u_{m} ,u_{j}^{h}) u_{j}^{h} \label{CV1}
\end{eqnarray}

From Lemma 7.8, we see that $( P_{m},u_{j}^{h} )$ is small if $\lambda_{m}^{h}$ is not close to $\lambda_{j}$. So then (\ref{CV1}) tells us then that $Pu_{m}$ is close to $u_{m}^{h}$. This will allow us to estimate $Pu_{m} - u_{m}^{h}$.\\

Since we have convergence in our eigenvalues, it follows that $\exists \rho > 0$ and $\exists \delta > 0$ such that if $h<\delta$ we have that
\begin{eqnarray}
|\lambda_{m} - \lambda_{j}^{h}| &>& \rho \ \ \textrm{ for all } \ j = 1,2,...,N
\end{eqnarray}
Therefore
\begin{eqnarray}
\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|} &\leq & \rho \ \ \textrm{ for all } \ j = 1,2,...,N
\end{eqnarray}

\textbf{Lemma 7.8:}
\begin{eqnarray*}
||Pu - QPu||^{2} &\leq & {\rho}^{2} ||u_{m} - Pu_{m}||^{2}
\end{eqnarray*}

\begin{comment}
\textbf{Proof:}

Now using Lemma 7.7:
\begin{eqnarray*}
||Pu - \beta u_{m}^{h}||^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}\\
				&\leq & \rho^{2} \sum_{j\neq m} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2} \\
				&\leq & \rho^{2} \sum_{j=1}^{N} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2} \\
				& = & \rho^{2} ||u - Pu||^{2}\\
\end{eqnarray*}
\qed
\end{comment}

\textbf{Lemma 7.9:}
\begin{eqnarray*}
||u_{m} - \beta u_{m}^{h}|| &\leq & \left(1+\rho\right)||u_{m}-Pu_{m}||
\end{eqnarray*}

\begin{comment}
\textbf{Proof:}
\begin{eqnarray*}
||u_{m} - \beta u_{m}^{h}|| & \leq & ||u_{m}-Pu_{m}|| + ||Pu_{m} - \beta u_{m}^{h}|| \\
			& \leq & \left(1+\rho\right)||u_{m}-Pu_{m}|| \ \ \textrm{ (by Lemma 7.8)}
\end{eqnarray*}
\qed
\end{comment}

So again using the Approximation Theorem, we have that $||u_{m} - \beta u_{m}^{h}||\leq Ch^{k}||u^{k}||$.\\

\textbf{Proposition 7.4:}
\begin{eqnarray*}
||u_{m} -  u_{m}^{h}|| &\leq & 2||u_{m}-\beta u^{h}_{m}||
\end{eqnarray*}

\begin{comment}
\textbf{Proof:}
\begin{eqnarray*}
||u_{m} - u_{m}^{h}|| &=& ||u_{m} - \beta u_{m}^{h} + \beta u_{m}^{h} - u_{m}^{h}|| \\
					& \leq & ||u_{m} - \beta u_{m}^{h}|| + ||\beta u_{m}^{h} - u_{m}^{h}|| \\
					& = & 2||u_{m} - \beta u_{m}^{h}||	
\end{eqnarray*}
\qed
\end{comment}

Therefore we have that $||u_{m} -  u_{m}^{h}|| \leq Ch^{k}||u^{k}||$. So for any $\epsilon >0$ , we can find a $\delta >0$ so that if $h < \delta$, we have that $||u_{m} -  u_{m}^{h}|| < \epsilon$.

Finally, for elastic beam models like the Euler-Bernoulli beam model, the norm $||.||$ is the energy norm defined as
\begin{eqnarray*}
||u|| &=& \left(\int u^{2}\right)^{\frac{1}{2}}
\end{eqnarray*}

So clearly then we have that $u_{m}^{h} \rightarrow u_{m}$ as $h \rightarrow 0$.

\section{Example}
What moet hier kom?\\

dalk timoshenko beam sal beter wees met plaat of 2d model.\\

Consider a variational problem for a cantilever two-dimensional beam, with a reference configuration $\Omega$. In section \ref{sssec:2D_Model:Problem2D1}, the derivation of this variational problem is referred to as Problem 2D-1V.

\subsubsection{Problem 2D-1V}\label{sssec:2D_Model:Problem2D1V}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
\begin{align}
	\int_{\Omega} (\partial_t^2 u)\cdot \phi \ dA = -b(u,\phi) - \int_{\Omega} Q\cdot\phi \ dA \label{eq:2D_Model:Problem2D1VEq}
\end{align}
for all $\phi \in T(\Omega)$.\\

With the test function space defined as
\subsubsection{Test functions}
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
\end{eqnarray*}

\subsection{Weak variational form}
For all $f,g \in T(\Omega)$ and $h \in C(\Omega)$, define the bilinear forms
\begin{eqnarray*}
	c(f,g) & = & \iint_\Omega f \cdot g \ dA, \\
\end{eqnarray*}
and integral
\begin{eqnarray*}
	(h,g) & = & \iint_\Omega h \cdot g \ dA. \\
\end{eqnarray*}
Recall from section  that the bilinear form $b$ is defined as
\begin{eqnarray*}
	b(u,\phi) & = & \frac{1}{\gamma(1-\nu^2)}\iint_{\Omega} (\partial_1 u_1 \partial_1 \phi_1 + \partial_2 u_2 \partial _2 \phi_2 + \nu\partial_1 u_1 \partial_2\phi_2 + \nu \partial_2 u_2 \partial_1 \phi_1 ) \ dA \\
	& + & \frac{1}{2\gamma(1+\nu)}\iint_{\Omega} (\partial_1 u_2 \partial_1 \phi_2 + \partial_1 u_2 \partial_2 \phi_1 + \partial_2 u_1 \partial_1\phi_2 + \partial_2 u_1 \partial_2\phi_1) \ dA.
\end{eqnarray*}

Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)$. Denote $X = L^2(0,1)\times L^2(0,1)$. The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.

\subsubsection{Problem 2D-1W}
Find a function $u$ such that for all $t>0$, $u(t) \in V$ and $u''(t) \in W$, satisfying the following equation
\begin{eqnarray}
	c(u''(t),v) + b(u(t),v) & = & (Q(t),v)_X \ \ \ \textrm{ for each } v \in V.
\end{eqnarray}

\end{document}

### 2022-10-31 files/Chapter4/CantileverBeam.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Cantilever beam} \label{sec:Timo:Cantilever}
Consider a cantilever Timoshenko beam model (Problem T-3 as defined in section \ref{ssec:1D_Model:ModelProblems}). The eigenvalue problem of Problem T-3 is denoted by Problem T-3E. This section serves as an example of the application of the theory from [VV02].\\

Consider the general solutions of the eigenvalue problem for the three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$. Imposing the boundary conditions $x = 0$ results the following constants:
\begin{align}
	C = & \frac{\mu(\lambda-\omega^2)}{\omega(\lambda+\mu^2)}A  \  &\textrm{ and } \ D = -B  \ \textrm{ if } \lambda < \alpha \label{A1}\\
	C = & \frac{\omega}{\lambda - \omega^2}A  \  &\textrm{ and } \ D = -B  \ \textrm{ if } \lambda = \alpha \label{A2}\\
	C = & -\frac{\omega(\lambda-\theta^2)}{\theta(\lambda-\omega^2)}A  \  &\textrm{ and } \ D = -B  \ \textrm{ if } \lambda > \alpha \label{A3}
\end{align}
The boundary conditions at $x = 1$ reduces the general solution to the following two-dimensional homogeneous system for each of the three cases.

\begin{align}
	\begin{bmatrix}
		M_{11}(\lambda) & M_{12}(\lambda)\\
		M_{21}(\lambda) & M_{22}(\lambda)
	\end{bmatrix}
	\begin{bmatrix}
		A\\
		B
	\end{bmatrix}
	= 
	\begin{bmatrix}
		0\\
		0
	\end{bmatrix}
\label{eq:Timo:Cantilever:SystemOfEquations}
\end{align}

To obtain non-zero solutions, the determinant of the coefficient matrix $M$ is set to zero, ie. $\textrm{det}(M) = 0$, and is called the frequency equation after simplification. The frequency equations for all three cases is given in [VV06] and is presented below.\\
%freq not defined. freq when simplified and by authors

Case $\lambda < \alpha$:\\
\begin{align}
	\left(\frac{\lambda + \mu^2}{\lambda - \omega^2} + \frac{\lambda - \omega^2}{\lambda + \mu^2} \right) \cosh (\mu) \cos (\omega) + \left(\frac{\omega}{\mu} - \frac{\mu}{\omega}\right) \sinh (\mu) \sin (\omega) - 2 = 0 \label{Freq1}
\end{align}

Case $\lambda = \alpha$:\\
\begin{align}
	\left(\frac{\alpha}{\alpha - \omega^2} + \frac{\alpha - \omega^2}{\alpha} \right) \cos (\omega) + \omega \sin (\omega) - 2 = 0 \label{Freq2}
\end{align}

Case $\lambda > \alpha$:\\
\begin{align}
	\left(\frac{\lambda + \theta^2}{\lambda - \omega^2} + \frac{\lambda - \omega^2}{\lambda + \theta^2} \right) \cos (\theta) \cos (\omega) + \left(\frac{\omega}{\theta} - \frac{\theta}{\omega}\right) \sin (\theta) \sin (\omega) - 2 = 0 \label{Freq3}
\end{align}

Inspection of the system of equations \eqref{eq:Timo:Cantilever:SystemOfEquations}, shows that the coefficient matrix is never zero for the case of the cantilever beam. It follows that all the eigenvalues are simple eigenvalues. This is mentioned in [VV06].

\subsection{Calculating the eigenvalues}
The solutions of the frequency equations \eqref{Freq1} - \eqref{Freq2} can be calculated using simple numerical methods. Using interval division, the eigenvalues are calculated accurate to at least 4 significant digits.
\FloatBarrier
\begin{table}[htbp]
	\centering
	\caption{First 8 eigenvalues, with $\gamma = 0.25$.}
	\begin{tabular}{|c||c|c|c|}
		\hline
		\multicolumn{4}{|c|}{Cantilever Beam Eigenvalues}\\
		\hline
		{i} & {$\alpha = 1200$} & {$\alpha = 4800$} & {$\alpha = 10800$} \\
		\hline
		1     & 0.04043 & 0.01025 & 0.004569 \\
		2     & 1.427 & 0.3914 & 0.1772 \\
		3     & 9.657 & 2.937 & 1.361 \\
		4     & 31.06 & 10.62 & 5.08 \\
		5     & 70.51 & 27.02 & 13.4 \\
		6     & 130.8 & 55.63 & 28.67 \\
		7     & 213.4 & 99.54 & 53.36 \\
		8     & 318.7 & 161.2 & 89.85 \\
		\hline
	\end{tabular}%
	\label{tab:addlabel}%
\end{table}%
\FloatBarrier

\textbf{Remark:} For interval division, the frequency equations are sketched to determine intervals to isolate the solutions. Another method that requires less user involvement is the bisection method. The advantage of the interval method is that the number of solutions within any given interval can be determined visually before the method is applied.

\subsection{Example of mode shapes}
Substituting a calculated eigenvalue $\lambda_k$ back into \eqref{eq:Timo:Cantilever:SystemOfEquations}, the values for $A_k$ and $B_k$ can be calculated by solving the system. But since $\textrm{det}(M) =0$, there are infinity many solutions of $[A_k \ B_k]^T$ for each $k$. So either one of $A_k$ or $B_k$ can be chosen freely and the other is depended on the choice. The modal shapes are sketched below in Figure 4.1 (modal shapes for $u$) and Figure 4.2 (modal shapes for $\phi$) corresponding to the eigenvalue $\lambda_k$ with $A_k = 1$, $\alpha = 1200$ and $\gamma = 0.25$.
\FloatBarrier
\begin{figure}[h!]

	\makebox[\textwidth][c]{
		\centering
		\begin{minipage}[b]{0.7\linewidth}
			\includegraphics[width=1\linewidth]{Cant1.png}
			\subcaption{ $\lambda_1 = 0.04043$, $B_1 = -1.368$}
			\label{fig:minipage2}
		\end{minipage}
		\begin{minipage}[b]{0.7\linewidth}
			\includegraphics[width=1\linewidth]{Cant2.png}
			\subcaption{$\lambda_2 = 1.427$, $B_2 = -0.9768$}
			\label{fig:minipage1}
		\end{minipage}
	}

	\makebox[\textwidth][c]{
		\centering
		\begin{minipage}{.7\textwidth}
			\centering
			\includegraphics[width=1\linewidth]{Cant3.png}
			\subcaption{$\lambda_3 = 9.657$, $B_3 = -1.002$}
			\label{fig:minipage1}
		\end{minipage}
		\begin{minipage}{.7\textwidth}
			\centering
			\includegraphics[width=1\linewidth]{Cant4.png}
			\subcaption{$\lambda_4 = 31.06$, $B_4 = -0.9997$}
			\label{fig:minipage2}
		\end{minipage}
	}
	\caption{Sketch of $w$ for the first 4 mode shapes of the cantilever beam. $\alpha = 1200$ and $\gamma = 0.25$ with $A_k = 1$.}
\end{figure}
\FloatBarrier

\begin{figure}[h!]

	\makebox[\textwidth][c]{
		\centering
		\begin{minipage}[b]{0.7\linewidth}
			\includegraphics[width=1\linewidth]{Cant21.png}
			\subcaption{ $\lambda_2 = 1.427$, $B_1 = -0.9768$}
			\label{fig:minipage2}
		\end{minipage}
		\begin{minipage}[b]{0.7\linewidth}
			\includegraphics[width=1\linewidth]{Cant31.png}
			\subcaption{$\lambda_3 = 9.657$, $B_2 = -1.002$}
			\label{fig:minipage1}
		\end{minipage}
	}

	\caption{Sketch of $\phi$ for mode shapes 2 and 3 of the cantilever beam. $\alpha = 1200$ and $\gamma = 0.25$ with $A_k = 1$.}
\end{figure}

\FloatBarrier
\textbf{Remark:} The sketch of $\phi$ for the first mode shape is similar to the sketch of $w$ and is therefore omitted.\\
\FloatBarrier

The results obtained for the Cantilever beam model are the same as the results in [VV06]. The motivation for this model is Chapter 6. The work of this section will be used for comparisons to a two and three-dimensional cantilever beam model.

\end{document}

### 2022-10-31 files/Chapter4/CantileverTimo.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\noindent
\section{Cantilever Timoshenko beam with tip-body}
\sout{This section discusses the technical report [DBVXX] on a cantilever Timoshenko beam with a tip body and elastic boundary interfaces. Most papers on a similar topic focus on the analysis of vibration modes, stabilization and optimal control of vibrations. The goal of [DBVXX] is to realistically model the interface between the endpoint of a beam and the attached tip body. Few publications consider this modelling.}\\

\sout{In this section, the finite element analysis and some numerical simulations for the model are presented. These numerical simulations are to show that the model behaves in a realistic manner.}\\

This section discusses a technical report [DBVXX]. In this technical report the authors models a cantilever Timoshenko beam with a tip body and elastic boundary conditions. This model can be seen as a motivation of the importance of investigating the validity of the Timoshenko beam theory.\\

This section discusses the model as presented in [DBVXX] as well as adding to the numerical results.

\subsection{The model problem}
Consider the dimensionless equations of motion \ref{eq:1D_Model:EquationOfMotion1D} and \ref{eq:1D_Model:EquationOfMotion2D} and constitutive equations \ref{eq:1D_Model:ConstitutiveEquations1D} and \ref{eq:1D_Model:ConstitutiveEquations2D} of a Timoshenko beam, as given in section \ref{sec:1D_Model}. The model in [DBVXX] adds two damping terms to these equations.

{Equations of Motion}
\begin{eqnarray}
	\partial_t^2 w &=& \partial_x V - c_1\partial_t w  + q, \label{CT_1}\\
	\frac{1}{\alpha}\partial_t^2 \phi &=& V+\partial_xM. \label{CT_2}
\end{eqnarray}

\noindent
{Constitutive Equations}
\begin{eqnarray}
	M &=& \frac{1}{\beta}\partial_x \phi +c_2 \partial_t \partial_x \phi,\label{CT_3}\\
	V&=& \partial_x w - \phi.\label{CT_4}
\end{eqnarray}

The term with $c_1$ models viscous damping and the term with $c_2$ models material damping.

\subsubsection{Boundary conditions}
It is assumed that the beam is elastically clamped at the endpoint $x=0$ and the tip-body is elastically clamped at the endpoint $x=1$.\\

The boundary conditions at the (elastically) clamped end $x=0$ are
\begin{eqnarray}
   w(0,t) &=&  0, \label{CT_5}\\
   M(0,t) &=&  \mu \phi(0,t). \label{CT_6}
\end{eqnarray}
The parameter $\mu > 0$ models the elastic interaction between the surface where the beam is attached and the beam itself. As $\mu$ increases, $\phi(0,t)$ decreases and similarly as $\mu$ decreases, $\phi(0,t)$ increases. Thus as $\mu$ increases, the join becomes ``more rigid" as the rotation of the cross-section is decreased. Obviously for a decrease in $mu$ the join becomes ``less rigid".\\

At the other endpoint where the tip body is attached, the following interface conditions derived by the authors of [DBVXX]
\begin{eqnarray}
- V(1,t) &=& m \partial_t^2 w(1,t) + md \ddot \theta(t) + k_1 \partial_t w(1,t) + k_1 d \dot \theta(t), \label{CT_7}\\
 -M(1,t) &=& J \ddot \theta(t) + d k_2 \dot \theta(t)- dV(1,t), \label{CT_8}\\
M(1,t) &=& \gamma (\theta(t)- \phi(1,t)). \label{CT_9}
\end{eqnarray}
In these equations, $m$ is the mass of the tip body, $J$ the moment of inertia about the centre of mass, $\theta$ represents the rotation of the tip- body, the terms with $k_1$ and $k_2$ are damping terms and $\gamma$ a parameter representing the elastic interaction between the tip body and the endpoint of the beam.\\

Similar to $\mu$, as $\gamma$ increases, $\theta(t) - \phi(1,t)$ decreases, hence the interaction is `more' rigid. And as $\gamma$ decreases, $\theta(t) - \phi(1,t)$ increases, so the interaction is `more' elastic. It is assumed that $\gamma > 0$.

\subsubsection{Remark}
The well-posedness of the model as well as the existence of unique solutions is investigated in [DBVXX].

\subsection{Variational form}
Let $f,g \in C[0,1]$. Multiplication and integration by parts results in
\begin{eqnarray}
\int_0^1~ \partial^2_t w(\cdot,t) f &=&  - \int_0^1~ V(\cdot,t)f' - c_1\int_0^1 \partial_t w(\cdot,t)f + \int_0^1q(\cdot,t)f \nonumber \\
& &+~V(1,t)f(1)~-~V(0,t)f(0), \label{CT_10}\\
 \int_0^1~ \frac{1}{\alpha}~\partial^2_t \phi(\cdot,t) g  &=& -\int_0^1~M(\cdot,t)g' + \int_0^1~ V(\cdot,t)g \nonumber\\
& & + M(1,t)g(1) -  M(0,t)g(0), \label{CT_11}
\end{eqnarray}

Let $h \in C[0,1]$. Multiply and integration gives:

\begin{eqnarray}
 \int_0^1 V(\cdot,t)h &=& \int_0^1 \partial_x wh - \int_0^1\phi h. \label{CT_12}
\end{eqnarray}

\subsubsection{Remark}
Integration by parts is not applied to equation \eqref{CT_12}. This results in the Mixed Finite Element Method.

Substituting the boundary conditions results in the following variational form
\begin{align}
\int_0^1~ \partial^2_t w(\cdot,t) f &=  - \int_0^1~ V(\cdot,t)f' - c_1\int_0^1 \partial_t w(\cdot,t)f + \int_0^1q(\cdot,t)f \nonumber \\
&  -(m \partial_t^2 w(1,t) +  md \ddot \theta(t) + k_1 \partial_t w(1,t)+ k_1 d \dot \theta(t))f(1) \nonumber\\
&~-~V(0,t)f(0), \label{CT_13}\\
 \int_0^1~ \frac{1}{\alpha}~\partial^2_t \phi(\cdot,t) g & = -\int_0^1\dfrac{1}{\beta} \partial_x \phi(\cdot,t)g' - c_2 \int_0^1 \partial_t \partial_x \phi(\cdot,t)g' +\int_0^1~V(\cdot,t)g \nonumber\\
 &  +\gamma \big(\theta(t) - \phi(1,t)\big)g(1) - \mu \phi(0,t)g(0), \label{CT_14}\\
 \int_0^1 V(\cdot,t)h &= \int_0^1 \partial_x wh - \int_0^1\phi h. \label{CT_15}
\end{align}

\subsubsection{Interface equation}
For the interface between the beam and tip body, the authors of [DBVXX] derive a differential equation for the interface at the tip body. Multiply the interface equation \eqref{CT_7} by d and add equation \eqref{CT_8} to obtain
\begin{align}
 J\ddot{\theta}(t) + dk_2\dot{\theta}(t) + dm\partial_t^2w(1,t) + md^2\ddot{\theta}(t) + dk_1\partial_tw(1,t) + k_1d^2\dot{\theta}(t)\nonumber \\
 = - \gamma(\theta(t)-\phi(1,t)) \label{CT_16}
\end{align}

\subsubsection*{Test functions}
The test function space can be defined as
\begin{align}
T[0,1] = \left\{ f \in C[0,1] ~~ | ~~ f(0)= 0~\right\} \label{CT_17}
\end{align}

Using the test function space and the variational form, it is possible to define a variational problem. Denote this problem by Problem Var.

\subsubsection{Problem Var} Find the functions $w$, $\phi$, $V$ and $\theta$ such that $\langle w(\cdot,t), \phi(\cdot,t) \rangle \in T[0,1] \times C^1[0,1]$, $V(\cdot,t) \in C^1[0,1]$ and $\theta(t) \in \mathbb{R}$ for all $t>0$ and the following equations hold:
\begin{align}
\int_0^1 \partial^2_t w(\cdot,t) f \ dx  & =   \int_0^1~ V(\cdot,t) f' \ dx - c_1\int_0^1 \partial_t w(\cdot,t)f \ dx + \int_0^1q(\cdot,t)f \ dx \nonumber \\
 &  -(m \partial_t^2 w(1,t) +  md \ddot \theta(t) + k_1 \partial_t w(1,t) + k_1 d \dot \theta(t))f(1), \label{CT_18}\\
\int_0^1 \frac{1}{\alpha}~\partial^2_t \phi(\cdot,t) g \ dx  &= -\int_0^1\dfrac{1}{\beta} \partial_x \phi(\cdot,t)g' \ dx - c_2 \int_0^1 \partial_t \partial_x \phi(\cdot,t)g' \ dx + \int_0^1 V(\cdot,t)g \ dx \nonumber \\
 &  +\gamma \big(\theta(t) - \phi(1,t)\big)g(1) - \mu \phi(0,t)g(0), \label{CT_19}\\
\int_0^1 V(\cdot,t)h \ dx &= \int_0^1 \partial_x w(\cdot,t)h \ dx - \int_0^1 \phi(\cdot,t)h \ dx,  \label{CT_20}
\end{align}
with the interface equation,
\begin{align}
(J+ md^2) \ddot \theta(t)+ (k_1d^2 + d k_2) \dot \theta(t)  + dm \partial_t^2 w(1,t)
  + dk_1 \partial_t w(1,t) \nonumber\\
  =  -\gamma \big(\theta(t) - \phi(1,t)\big),  \label{CT_21}
\end{align}

for all $f \in T[0,1]$ and $g,h \in C^1[0,1]$.\\

\subsection{Galerkin approximation}
Create a set of n+1 linear basis functions $\delta_i$, where $\delta_i \in C[0,1]$ for $i = 0,1,2,...,n$. Let $S_0 = \textrm{span}\left\{\delta_0,\delta_1,\delta_2,...,\delta_n\right\}$ and $S = \textrm{span}\left\{\delta_1,\delta_2,\delta_3,...,\delta_n\right\}$.

\subsubsection{Problem G}
Find the functions $w^h$, $\phi^h$, $V^h$ and $\theta^h$ such that $w^h(\cdot,t) \in S$,  $\phi^h(\cdot,t),V^h(\cdot,t) \in S_0$ and $\theta^h(t) \in \mathbb{R}$ for all $t>0$ and the following equations hold:

\begin{align}
\int_0^1 \partial^2_t w^h(\cdot,t) \delta_i \ dx & =   \int_0^1 V^h(\cdot,t) \delta_i' \ dx - c_1 \int_0^1 \partial_t w^h(\cdot,t) \delta_i \ dx + \int_0^1 q(\cdot,t) \delta_i \ dx \nonumber \\
 & -(m \partial_t^2 w^h(1,t) +  md \ddot \theta^h(t)k_1 \partial_t w^h(1,t) + k_1 d \dot \theta^h(t))\delta_i(1), \\
\frac{1}{\alpha} \int_0^1 \partial^2_t \phi^h(\cdot,t) \delta_i \ dx & = -\dfrac{1}{\beta}\int_0^1\partial_x \phi^h(\cdot,t)\delta_i' \ dx - c_2 \int_0^1 \partial_t \partial_x \phi^h(\cdot,t) \delta_i' \ dx + \int_0^1 V^h(\cdot,t) \delta_i \ dx \nonumber \\
 & +\gamma \big(\theta^h(t) - \phi^h(1,t)\big)\delta_i(1) - \mu \phi^h(0,t)\delta_i(0),\\
\int_0^1 V^h(\cdot,t),\delta_i \ dx &= \int_0^1 \partial_x w^h(\cdot,t) \delta_i \ dx -  \int_0^1 \phi^h(\cdot,t) \delta_i \ dx, 
\end{align}
for $i = 0,1,2,...,n+1$.\\

And the interface equation,
\begin{align}
(J+ md^2) \ddot \theta^h(t)+ (k_1 d^2 + d k_2) \dot \theta^h(t)  + dm \partial_t^2 w^h(1,t)
  + dk_1 \partial_t w^h(1,t) \nonumber\\
  =  -\gamma \big(\theta^h(t) - \phi^h(1,t)\big).
\end{align}

\subsection{System of ordinary differential equations}
Consider the following standard Finite Element matrices
\begin{align*}\label{ch6_eq10}
M_{ij} = \int_0^1 \delta_j \delta_i, ~K_{ij} = \int_0^1 \delta'_j\delta'_i ~\textrm{and} ~L_{ij} = \int_0^1 \delta_j\delta'_i.
\end{align*}

Using the matrices $M$, $K$ and $L$, Problem G can be rewritten as a system of ordinary differential equations. This system is referred to as Problem ODE.

\subsubsection{Problem ODE}
Find the functions $\bar{w} \in S$, $\bar{\phi}, \bar{V} \in S_0$ and $\theta^h \in \mathbb{R}$ such that
\begin{align}
M_w\ddot{\bar{w}} = L_w\bar{V} -\big(m \ddot{w}_{n+1}(t) + k_1 \dot{w}_{n+1}(t) \big)\delta_i(1) + M^* \bar{q}(t) + \bar{q}_I,\\
\label{sys2}
\frac{1}{\alpha} M \ddot{\bar{\phi}} = -\frac{1}{\beta} K\bar{\phi} + M\bar{V} + \tilde{G},\\
\label{sys2.1}
\bar{0} = -M\bar{V} + L^T\bar{w} - M\bar{V}.
\end{align}

With the interface equation
\begin{align} \label{sys3} \nonumber
(J+md^2) \ddot \theta^h(t) &+ (d k_2+ d^2 k_1 ) \dot \theta^h(t)  + dm {\ddot w}_{n+1}(t) +  dk_1 {\dot w}_{n+1}(t)\\
  =&  -\gamma \big(\theta^h(t) - {\phi}_{n+1}(t)\big).
\end{align} and $\bar{q}_I$ the interpolation of the function $q$ over the basis functions.

\subsection{Numerical results}
These equations can be rewritten in a general form for a system of ordinary differential equations
\begin{align}
	A\ddot{\bar{u}} &= B\dot{\bar{u}} + C\bar{u} + D
\end{align}
and
\begin{align}
	a \ddot{\theta} & = b \dot{\theta} + c \theta + d
\end{align} with $\bar{u} = \langle \bar{w}, \bar{\phi}, \bar{V} \rangle$.\\

A finite difference scheme can be applied to find $\bar{u}$ and $\theta$ numerically. An example of a scheme that can be used is the Central Difference Average Acceleration finite difference method. The following results were obtained by implementing a MATLAB program.\\

The beam is excited using a periodic forcing function $q(t) = 0.1 \sin(\frac{\pi}{4}t)$ to induce motion. The damping parameters are set to $c_1 = 0$, $c_2 = 0$, $k_1 = 0.1$ and $k_2 = 1$.

\newpage
\FloatBarrier
\subsubsection{Case: Control}
Consider the control case as presented in [DBVXX].\\

 The maximum displacement is $u$ is 0.07694. And the maximum angle of cross-section at tip-body is 0.005552.

\begin{figure}[!hb]
\makebox[\textwidth]{
\centering
 \includegraphics[scale=0.3]{../../images/TimoshenkoTipBody/ControlMotion.png}
 \caption{Motion of the beam with $\mu = 0.5$, $\gamma = 0.5$, $m = 0.1$}\label{CLB_F5}}
\end{figure}

\begin{table}[!hb]
\makebox[\textwidth]{
\renewcommand{\arraystretch}{1}
    \begin{tabular}{|c||c||c||c||}
        \hline
         t & $\phi(1)$ & $\theta$ & $\phi(1) - \theta$\\ 
        \hline
        0  & 0 & 0 & 0 \\
        2  & -0.002020353467526 & -0.000027406615955 & -0.001992946851571 \\
        4  & -0.000596779278874 & -0.000134256143882 & -0.000462523134992 \\
        6  & 0.004742324601643 	& -0.000810001256052 & 0.005552325857694 \\
        8  & 0.000059161424311 	& -0.001289328238416 & 0.001348489662727 \\
        10 & -0.003024749574431 & -0.000359603287124 & -0.002665146287307 \\
        \hline 
        \end{tabular}
        \caption{Angle of the beam and tip-body at time $t$ and their relative error.}\label{CLB_T1}}
\end{table}

\FloatBarrier
\subsubsection{Case: Decrease $\gamma$}
For this case, the parameter $\gamma$ is decreased. Compared to the control case, the maximum angle achieved of the cross-section at the tip body is increased.\\

The maximum displacement is $u$ is 0.07801. And the maximum angle of cross-section at tip-body is 0.02676.

\begin{figure}[!hb]
	\makebox[\textwidth]{
		\centering
		\includegraphics[scale=0.3]{../../images/TimoshenkoTipBody/ControlMotion_gam.png}
		\caption{Motion of the beam with $\mu = 0.5$, $\gamma = 0.1$, $m = 0.1$}\label{CLB_F5}}
\end{figure}

\begin{table}[!hb]
	\makebox[\textwidth]{
		\renewcommand{\arraystretch}{1}
		\begin{tabular}{|c||c||c||c||}
			\hline
			t & $\phi(1)$ & $\theta$ & $\phi(1) - \theta$\\ 
			\hline
			0  & 0 & 0 & 0 \\
			2  & -0.008968780504176 & -0.000034622649348 & -0.008934157854828 \\
			4  & -0.003421432704948 & -0.000247657709436 & -0.003173774995512 \\
			6  & 0.025401485816257 	& -0.001090880083035 & 0.026492365899293 \\
			8  & 0.004576031105634 	& -0.002083479267232 & 0.006659510372866 \\
			10 & -0.015386157002644 & -0.002074203805624 & -0.013311953197020 \\
			\hline 
		\end{tabular}
		\caption{Angle of the beam and tip-body at time $t$ and their relative error.}\label{CLB_T1}}
\end{table}

\FloatBarrier
\subsubsection{Case: Decrease $\mu$}
For this case, the parameter $\mu$ is decreased. Compared to the control case, the maximum displacement of the beam achieved during motion is increased..\\

The maximum displacement is $u$ is 0.08017. And the maximum angle of cross-section at tip-body is 0.005854.

\begin{figure}[!hb]
	\makebox[\textwidth]{
		\centering
		\includegraphics[scale=0.3]{../../images/TimoshenkoTipBody/ControlMotion_mu.png}
		\caption{Motion of the beam with $\mu = 0.1$, $\gamma = 0.5$, $m = 0.1$}\label{CLB_F5}}
\end{figure}

\begin{table}[!hb]
	\makebox[\textwidth]{
		\renewcommand{\arraystretch}{1}
		\begin{tabular}{|c||c||c||c||}
			\hline
			t & $\phi(1)$ & $\theta$ & $\phi(1) - \theta$\\ 
			\hline
			0  & 0 & 0 & 0 \\
			2  & -0.0020146527231596 & -0.000026854667752 & -0.001987798055407 \\
			4  & -0.000919770985602 & -0.000102876004834 & -0.000816894980768 \\
			6  & 0.005023665668264 	& -0.000752726666843 & 0.005776392335107 \\
			8  & 0.000210040029687 	& -0.001352805739549 & 0.001562845769236 \\
			10 & -0.003254467815569 & -0.000453217154384 & -0.002801250661185 \\
			\hline 
		\end{tabular}
		\caption{Angle of the beam and tip-body at time $t$ and their relative error.}\label{CLB_T1}}
\end{table}

\FloatBarrier
\subsubsection{Case: Increase $m$}
For this case, the parameter $m$ is increased. This parameter represents the weight of the tip body. Compared to the control case, the maximum displacement of the beam achieved during motion is decreased. Lag in the motion of the beam can also be seen in Figure \ref{lag}. \\

The maximum displacement is $u$ is 0.04813. And the maximum angle of cross-section at tip-body is 0.007164.

\begin{figure}[!hb]
	\makebox[\textwidth]{
		\centering
		\includegraphics[scale=0.3]{../../images/TimoshenkoTipBody/ControlMotion_m.png}
		\caption{Motion of the beam with $\mu = 0.5$, $\gamma = 0.5$, $m = 0.5$}\label{lag}}
\end{figure}

\begin{table}[!hb]
	\makebox[\textwidth]{
		\renewcommand{\arraystretch}{1}
		\begin{tabular}{|c||c||c||c||}
			\hline
			t & $\phi(1)$ & $\theta$ & $\phi(1) - \theta$\\ 
			\hline
			0  & 0 & 0 & 0 \\
			2  & -0.001872928034631 & 0.000860073660995 & -0.002733001695626 \\
			4  & 0.000838496309022 & 0.002376699454088 & -0.001538203145066 \\
			6  & 0.000527590593005 	& -0.006558345806040 & 0.007085936399045 \\
			8  & -0.000248514461727 	& -0.0009904383205016 & 0.000741923858774 \\
			10 & -0.000030840351397 & 0.003708628513388 & -0.003739468864785 \\
			\hline 
		\end{tabular}
		\caption{Angle of the beam and tip-body at time $t$ and their relative error.}\label{CLB_T1}}
\end{table}

\end{document}

### 2022-10-31 files/Chapter4/FreeFreeTimo.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Free-free timoshenko beam}\label{sec:Timo:Free}
Consider a free-free Timoshenko beam model (Problem T-4 in section \ref{ssec:1D_Model:ModelProblems}).The eigenvalue problem of Problem T-4 is denoted by Problem T-4E. Similar to the previous section, this section serves as an example of the application of the theory from [VV02].\\

Consider the general solutions of the eigenvalue problem for the three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$. Imposing the boundary conditions $x = 0$ results the following:

\begin{align}
	C  =&  \frac{\omega}{\mu}A &\textrm{ and } \ D = \frac{ \mu^2+\lambda}{\omega^2-\lambda}B \ \ \ \textrm{ if } \lambda < \alpha \label{A1}\\
	C = & \frac{\omega}{\lambda}A \ &\textrm{ and } \ D = \frac{\alpha}{\omega^2-\lambda}B  \ \textrm{ if } \lambda = \alpha \label{A2}\\
	C= &-\frac{\omega}{\theta}A \ &\textrm{ and } \ D = -\frac{\theta^2-\lambda}{\omega^2 - \lambda}B  \ \textrm{ if } \lambda > \alpha \label{A3}
\end{align}
The boundary conditions at $x = 1$ gives the following homogeneous system of equations for each of the three cases.
\begin{align}
	\begin{bmatrix}
		M_{11}(\lambda) & M_{12}(\lambda)\\
		M_{21}(\lambda) & M_{22}(\lambda)
	\end{bmatrix}
	\begin{bmatrix}
		A\\
		B
	\end{bmatrix}
	= 
	\begin{bmatrix}
		0\\
		0
	\end{bmatrix}
	\label{eq:Timo:Free:SystemOfEquations}
\end{align}

The entries of the coefficient matrix for each separate case is presented below.

{If $\lambda < \alpha$}
\begin{align*}
	&M_{11}(\lambda) = \sinh(\mu)(\lambda+\mu^2) + \frac{\omega(\lambda - \omega^2)}{\mu}\sin(\omega)&\\
	&M_{12}(\lambda) = (\lambda+\mu^2)(\cosh(\mu)-\cos(\omega))& \\
	&M_{21}(\lambda) = \frac{\lambda}{\mu}(\cos(\omega) - \cosh(\mu))&\\
	&M_{22}(\lambda) =\frac{\lambda^2+\lambda\mu^2}{\omega(\lambda-\omega^2)}\sin(\omega) - \frac{\lambda }{\mu}\sinh(\mu)&
\end{align*}

{If $\lambda = \alpha$}
\begin{align*}
	&M_{11}(\lambda) = \frac{\omega\left(\lambda - \omega^2\right)}{\lambda}\sin(\omega)&\\
	&M_{12}(\lambda)=\alpha-\alpha\cos(\omega)&\\
	&M_{21}(\lambda)=\frac{\omega^2}{\lambda}\cos(\omega)+\cos(\omega)\frac{\left(\lambda - \omega^2\right)}{\lambda} - 1 &\\
	&M_{22}(\lambda)=-\alpha+\left(\frac{\alpha}{\omega}+\frac{\alpha\omega}{\lambda-\omega^2}\right)\sin(\omega)&
\end{align*}

{If $\lambda > \alpha$}
\begin{align*}
	&M_{11}(\lambda) = \left(\lambda - \theta^2\right)\sin(\theta) - \frac{\omega  \left(\lambda - \omega^2\right)}{\theta}\sin(\omega)&\\
	&M_{12}(\lambda) = \left(\lambda - \omega^2\right)(\cos(\omega) - \cos(\theta))&\\
	&M_{21}(\lambda)=-\frac{\lambda}{\theta}(\cos(\omega)-\cos(\theta))&\\
	&M_{22}(\lambda)=\frac{\lambda^2-\lambda\theta^2}{\omega(\lambda-\omega^2)}\sin(\omega)-\frac{\lambda}{\theta}\sin(\theta)&
\end{align*}

The frequency equations can be determined by simplifying the equation $$M_{11}(\lambda)M_{22}(\lambda)-M_{12}(\lambda)M_{21}(\lambda) = 0$$
for each case. To retain readability, the frequency equations are not written out.

\subsection{Calculating the eigenvalues}
Using interval division, the eigenvalues are calculated accurate to at least 4 significant digits.
\FloatBarrier
\begin{table}[htbp]
	\centering
	\caption{First 8 eigenvalues, with $\gamma = 0.25$.}
	\begin{tabular}{|c||c|c|c|}
		\hline
		\multicolumn{4}{|c|}{Free-Free Beam Eigenvalues}\\
		\hline
		{i} & {$\alpha = 1200$} & {$\alpha = 4800$} & {$\alpha = 10800$} \\
		\hline
		1     & 1.544 & 0.4088 & 0.1837 \\
		2     & 10.26 & 2.989 & 1.372 \\
		3     & 33.41 & 10.88 & 5.139 \\
		4     & 76.16 & 27.82 & 13.59 \\
		5     & 141.3 & 57.49 & 29.15 \\
		6     & 229.7 & 103.2 & 54.38 \\
		7     & 341.2 & 167.4 & 91.75 \\
		8     & 475.0   & 252.2 & 143.5 \\
		\hline
	\end{tabular}%
	\label{tab:addlabel}%
\end{table}%
\FloatBarrier

\subsection{Example of mode shapes}
 Figure 4.3 (modal shapes for $u$) and Figure 4.4 (modal shapes for $\phi$) show examples of the modal shapes corresponding to the eigenvalue $\lambda_k$ with $A_k = 1$, $\alpha = 1200$ and $\gamma = 0.25$.
\FloatBarrier
\begin{figure}[h!]

	\makebox[\textwidth][c]{
		\centering
		\begin{minipage}[b]{0.7\linewidth}
			\includegraphics[width=1\linewidth]{Free1.png}
			\subcaption{ $\lambda_1 = 1.544$, $B_1 = -1.022$}
			\label{fig:minipage2}
		\end{minipage}
		\begin{minipage}[b]{0.7\linewidth}
			\includegraphics[width=1\linewidth]{Free2.png}
			\subcaption{$\lambda_2 = 10.26$, $B_2 = -0.9982$}
			\label{fig:minipage1}
		\end{minipage}
	}

	\makebox[\textwidth][c]{
		\centering
		\begin{minipage}{.7\textwidth}
			\centering
			\includegraphics[width=1\linewidth]{Free3.png}
			\subcaption{$\lambda_3 = 33.41$, $B_3 = -1.000$}
			\label{fig:minipage1}
		\end{minipage}
		\begin{minipage}{.7\textwidth}
			\centering
			\includegraphics[width=1\linewidth]{Free4.png}
			\subcaption{$\lambda_4 = 76.16$, $B_4 = -0.9999$}
			\label{fig:minipage2}
		\end{minipage}
	}
	\caption{Sketch of $w$ of the first 4 mode shapes of the free-free beam. $\alpha = 1200$ and $\gamma = 0.25$ with $A_k = 1$.}
\end{figure}
\FloatBarrier
\begin{figure}[h!]

	\makebox[\textwidth][c]{
		\centering
		\begin{minipage}[b]{0.7\linewidth}
			\includegraphics[width=1\linewidth]{Free21.png}
			\subcaption{ $\lambda_2 = 1.544$, $B_1 = -1.022$}
			\label{fig:minipage2}
		\end{minipage}
		\begin{minipage}[b]{0.7\linewidth}
			\includegraphics[width=1\linewidth]{Free31.png}
			\subcaption{$\lambda_3 = 10.26$, $B_2 = -0.9982$}
			\label{fig:minipage1}
		\end{minipage}
	}

	\caption{Sketch of $\phi$ for the first two mode shapes of the free-free beam. $\alpha = 1200$ and $\gamma = 0.25$ with $A_k = 1$.}
\end{figure}
\FloatBarrier

The motivation for the free-free beam in this dissertation is section 4.6. In this section, an article is discussed in which the eigenvalues of a free-free Timoshenko beam are compared to empirical results from an experiment conducted in [SP06].

\end{document}

### 2022-10-31 files/Chapter4/ModalAnalysisTimo.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}

\section{Eigenvalue problem}\label{sec:Timo:EigenvalueProblem}
In section \ref{ssec:1D_Model:Modal} the idea of modal analysis is explored using a Timoshenko beam as an example. In this section, we look at the work of the authors of [VV06]. The authors gives a method to calculate the eigenvalues and eigenfunctions for the Timoshenko beam theory.\\

Consider a general eigenvalue problem for the Timoshenko beam theory.

\sout{The next step is to find a method to {easily} calculate the eigenvalues and eigenvectors for the Timoshenko beam models {theory}}.\\

\sout{For this section, the work of the authors of [VV06] is discussed. {Consider the article [VV06].} In this article the authors present a method to calculate the exact eigenvalues and eigenvectors for the Timoshenko beam theory}.\\

\sout{To discuss the work of [VV06], a general eigenvalue problem is required. So consider only the differential equations of an eigenvalue problem for a Timoshenko beam. The reader can refer to Problem T-1E in section \ref{ssec:1D_Model:Modal} for a more specific example of the derivation of the eigenvalue problems for the Timoshenko beam theory.}

\sout{In section \ref{ssec:1D_Model:Modal}, the eigenvalue for Problem T-1 is given as Problem T-1E. }
\textcolor{red}{Probleem se naam verander vanaf Differential equations for the eigenvalue problem}
\subsubsection{General eigenvalue problem} \label{sssec:Timo:EigenvalueProblem}
Find functions $u$ and $\phi$ and a real number $\lambda$ satisfying the following equations
\begin{eqnarray}
-u'' + \phi' &=& \lambda u, \label{eq:Timo:EigenvalueProblem1}\\
-\alpha u' + \alpha\phi - \frac{1}{\gamma}\phi'' &=& \lambda\phi.\label{eq:Timo:EigenvalueProblem2}
\end{eqnarray}

Recall from section \ref{sec:1D_Model}, $u$ represents the transverse motion of the beam, $\phi$ is the angle of rotation of the cross-section of the beam, $\alpha$ and $\gamma$ are dimensionless constants defined in section 1.5 and $\lambda$ represents the eigenvalue. \\

The authors of [VV06] first derive a general solution for the system of ordinary differential equations \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2}. In [VV06] the authors show that for the Timoshenko models in this dissertation $\lambda$ non-negative. Assume that the solution is of the form $\langle u, \phi \rangle = e^{mx}\bar{w}$ where $m\in \mathbb{R}$ or $m\in \mathbb{C}$. Substitution into \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2} yields:
\begin{eqnarray*}
-m^{2}e^{mx}w_{1}+me^{mx}w_{2}&=&\lambda e^{mx}w_{1},\\
-\frac{1}{\gamma}m^{2}e^{mx}w_{2}-\alpha me^{mx}w_{1}+\alpha e^{mx}w_{2}&=&\lambda e^{mx}w_{2}.
\end{eqnarray*}

From these equations it can be concluded that $e^{mx}\bar{w}$ is a solution of the system if and only if the pair $\langle m,\bar{w} \rangle$ is a solution of the linear system:

\begin{equation}
\begin{bmatrix}
-m^{2}-\lambda & m\\
-\alpha m & -\frac{1}{\gamma}m^{2}+(\alpha- \lambda)
\end{bmatrix}
\begin{bmatrix}
w_{1}\\w_{2}
\end{bmatrix}
=
\begin{bmatrix}
0\\0
\end{bmatrix}. \label{eq:Timo:SolutionEigenvalueProblem}
\end{equation}

Let $A$ denote the coefficient matrix of \eqref{eq:Timo:SolutionEigenvalueProblem}. For a nontrivial solution of $\bar{w}$, it is required that the determinant of matrix $A$ is $0$.
\begin{align*}
\textrm{det}(A)=m^{4}+\lambda(1+\gamma)m^{2}+\gamma\lambda(\lambda-\alpha)=0. \label{TE7}
\end{align*}

This equation is called the characteristic equation. The characteristic equation is quadratic with respect to $m^2$. The roots of the characteristic equation can be expressed as
\begin{align}
m^{2}=-\frac{1}{2}\lambda(1+\gamma)(1\pm\sqrt{\Delta}),
\end{align}
where
\begin{align}
\Delta=1-\frac{4\gamma}{(1+\gamma)^{2}}\left(1-\frac{\alpha}{\lambda}\right)=\frac{4\gamma}{(1+\gamma)^{2}}\frac{\alpha}{\lambda}+\frac{(1-\gamma)^{2}}{(1+\gamma)^{2}}.
\end{align}

It is clear that $\Delta>0$, since $\lambda$, $\alpha$ and $\gamma$ are all positive. Therefore $m^{2}$ will always be real, and have distinct roots.\\

Consider the case where $m^{2} = 0$, which occurs when $\lambda = \alpha$. Then the matrix A simplifies to
\begin{equation*}
\begin{bmatrix}
	\alpha & 0\\
	0&0
	\end{bmatrix}.
\end{equation*}

In  this case it is easy to find two linearly independent solutions:
\begin{eqnarray*}
\left[u(x) \ \phi(x)\right]^{T} = \left[0 \ 1 \right]^{T} \ \ \textrm{ and } \ \ \left[u(x) \ \phi(x)\right]^{T} = \left[1 \ \alpha x \right]^{T}.
\end{eqnarray*}

Now if $m^{2} \neq 0$, we consider the system $A\bar{w}=0$ with $w_{1} = m$ and $w_{2} = m^{2} + \lambda$. From [VV06], the parameters $\omega$, $\mu$ and $\theta$ are uniquely determined by $\lambda$.
\begin{eqnarray}
	\omega^2 & = & \frac{1}{2}\lambda(1+\gamma)(\Delta^{\frac{1}{2}}+1) \ \textrm{ for } \lambda >0\\
	\mu^2 & = & \frac{1}{2}\lambda(1+\gamma)(\Delta^{\frac{1}{2}}-1) \ \textrm{ for } \lambda < \alpha\\
	\theta^2 & = & \frac{1}{2}\lambda(1+\gamma)(1-\Delta^{\frac{1}{2}}) \ \textrm{ for } \lambda > \alpha
\end{eqnarray}

 The three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$ are considered separately by the authors of [VV06]. The general solution from [VV06] for each case is presented below.

\subsubsection{Case $\boldsymbol{\lambda<\alpha}$}

Denote the roots of (\ref{TE7}) by $\pm \mu$ and $\pm \omega i$. Thus the general solution is given by
\begin{eqnarray*}
\begin{bmatrix}
u(x)\\ \phi(x)
\end{bmatrix}
&=&
A
\begin{bmatrix}
\sinh (\mu x) \\ \frac{\lambda+\mu^{2}}{\mu}\cosh (\mu x)
\end{bmatrix}
+
B
\begin{bmatrix}
\cosh (\mu x) \\ \frac{\lambda+\mu^{2}}{\mu}\sinh (\mu x)
\end{bmatrix}
+
C
\begin{bmatrix}
\sin (\omega x) \\ -\frac{\lambda-\omega^{2}}{\omega}\cos (\omega x)
\end{bmatrix}\\
&&
+
D
\begin{bmatrix}
\cos (\omega x) \\ \frac{\lambda-\omega^{2}}{\omega}\sin (\omega x)
\end{bmatrix}.
\end{eqnarray*}

\subsubsection{Case $\boldsymbol{ \lambda=\alpha}$}

In this case the roots of (\ref{TE7}) are $0$ with multiplicity 2, and $\pm \omega i$. The general solution is
\begin{eqnarray*}
	\begin{bmatrix}
		u(x)\\ \phi(x)
	\end{bmatrix}
	=
	A
	\begin{bmatrix}
		0 \\1
	\end{bmatrix}
	+
	B
	\begin{bmatrix}
		1 \\ \alpha x
	\end{bmatrix}
	+
	C
	\begin{bmatrix}
		\sin (\omega x) \\ -\frac{\lambda-\omega^{2}}{\omega}\cos (\omega x)
	\end{bmatrix}
	+
	D
	\begin{bmatrix}
		\cos (\omega x) \\ \frac{\lambda-\omega^{2}}{\omega}\sin (\omega x)
	\end{bmatrix}.\label{T9}
\end{eqnarray*}

\subsubsection{Case $\boldsymbol{\lambda>\alpha}$}

All the roots of (\ref{TE7}) are complex. Denote them by $\pm \theta i$ and $\pm \omega i$. The general solution is
\begin{eqnarray*}
\begin{bmatrix}
u(x)\\ \phi(x)
\end{bmatrix}
&=&
A
\begin{bmatrix}
\sin (\theta  x) \\-\frac{\lambda-\theta^{2}}{\theta}\cos (\theta x)
\end{bmatrix}
+
B
\begin{bmatrix}
\cos (\theta x) \\ \frac{\lambda-\theta^{2}}{\theta}\sin (\theta x)
\end{bmatrix}
+
C
\begin{bmatrix}
\sin (\omega x) \\ -\frac{\lambda-\omega^{2}}{\omega}\cos (\omega x)
\end{bmatrix}\\
&&
+
D
\begin{bmatrix}
\cos (\omega x) \\ \frac{\lambda-\omega^{2}}{\omega}\sin (\omega x)
\end{bmatrix}.\label{T10}
\end{eqnarray*}

The next step is to determine the solution of the general eigenvalue problem. The strategy to obtain the eigenvalues and eigenvectors are described in detail in [VV06] using an example. A summary of the strategy is presented here.\\

From the general solutions for $u$ and $\phi$, the eigenvalues and eigenfunctions can be determined by imposing the boundary conditions of the model problem. The boundary conditions at $x=0$ reduces the solution space of four dimensions to a solution space of dimension at least two. The boundary condition at $x=1$ is then substituted which results in a homogeneous system of linear equations.
\begin{eqnarray*}
A \bar{b} = \bar{0}
\end{eqnarray*}

 This system has either the zero solution or infinitely many solutions. To ensure a non-zero solution, the determinant of the coefficient matrix $A$ of the system of equations is set equal to 0. The equation $\textrm{det}(A) = 0$ is called the frequency equation. The frequency equation has infinitely many solutions and each solution corresponds to an eigenvalue.\\

 For each eigenvalue, a unique solution for the pair $\bar{b}$ can be obtained. A eigenfunction for $u$ and $\phi$ is obtained using $\bar{b}$ and corresponds to the relevant eigenvalue.\\

The following two sections provide examples of this strategy applied to beam models. These examples are also in [VV06].

**sluit af***
******NB Verduidelik $\alpha$
\end{document}
%obvisouly the solution space is 4 dimensional . bc at 0 makes it at most two.

### 2022-10-31 files/Chapter4/SP06.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{SP06}
Consider a study by Stephen and Puchegger in 2006, article [SP06]. This study investigated the validity of the Timoshenko beam theory by hand of empirical and numerical data. The approach of the study is to compare the natural frequencies of a Timoshenko beam, to that of a three-dimensional elastic beam. The authors conducted comparisons between the models using theoretical methods as well as results from an empirical study on a physical beam, conducted by the authors.\\

The authors decided on a free-free beam configuration, as it is the easiest to achieve in the physical experiment. The natural frequencies of the Timoshenko beam theory was obtained by using frequency equations from an article by Levison and Cooke [LC81]. In theoretical approach of the three-dimensional beam, two methods were considered. A commercial finite elements method (ANSYS), and a resonant ultrasound spectroscopy (RUS) technique.\\

This section discusses the results of [SP06].

\subsection{Mathematical models}
Let $\Omega$ be the reference configuration of a free-free beam with square cross-section. The authors of [SP06] do not formulate the models in the article. Consider Problem T-4 from section \ref{ssec:1D_Model:ModelProblems} for the free-free Timoshenko beam and Problem 3D-2 from section \ref{ssec:3D_Model:ModelProblems} for the free-free three-dimensional beam. The model problems are given here again for the reader's convenience.

\subsubsection*{Problem T-4}
Find a function $u$, satisfying the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D}- \eqref{eq:1D_Model:EquationOfMotion2D} and constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D}- \eqref{eq:1D_Model:ConstitutiveEquations2D}.\\

{Free-Free Boundary Conditions:}
\begin{eqnarray}
	V(0,\cdot) = 0, \ \ &M(0,\cdot) = 0, \label{BC_1}\\
	V(1,\cdot) = 0, \ \ &M(1,\cdot) = 0. \label{BC_2}
\end{eqnarray}

\subsubsection{Problem 3D-2}
Find a vector valued function $u$, satisfying the equation of motion \eqref{eq:3D_Model:EM-D} and constitutive equation \eqref{eq:3D_Model:CE-D}. Let $\Omega$ represent the reference configuration of the beam with a square cross-section.
\begin{eqnarray*}
	\Omega := \left\{ \bar{x} = \langle x,y,z \rangle \in \mathbb{R} \ | \ 0 \leq x \leq 1, \ -\frac{h}{2} \leq y, z \leq \frac{h}{2}  \right\}
\end{eqnarray*}

with $h$ the height and width of the beam. $\partial \Omega$ denotes the boundary of $\Omega$. \\

{Free-Free Boundary Conditions:}\\
\begin{eqnarray*}
	Tn & = & 0 \quad \textrm{ on } \partial\Omega.
\end{eqnarray*} with $n$ a outward normal vector.

\subsection{Experimental setup}
Next the experiment conducted by [SP06] is discussed. A short, aluminium alloy beam with near square cross-section is suspended at both ends. The beam is suspended by carbon fibre loops.

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.25mm] (2,0) -- (7,2);
		\draw[line width = 0.25mm] (2,1) -- (7,3);
		\draw[line width = 0.25mm] (1,1) -- (6,3);

		\draw[line width = 0.25mm] (2,0) -- (2,1);
		\draw[line width = 0.25mm] (1,0) -- (1,1);
		\draw[line width = 0.25mm] (2,0) -- (1,0);
		\draw[line width = 0.25mm] (2,1) -- (1,1);

		\draw[line width = 0.25mm] (6,3) -- (7,3);
		\draw[line width = 0.25mm] (7,3) -- (7,2);

		\draw(2.1,0) parabola (2.5,4);
		\draw(1,0.1) parabola (0.6,4);

		\draw(6.9,1.9) parabola (7.4,4.9);
		\draw[line width = 0.15mm] (5.7,2.9) -- (5.5,4.9);

	\end{tikzpicture}
	\caption{Sketch of beam suspended at the end-points by carbon fibre loops.}
\end{figure} 
\FloatBarrier

To vibrate the beam, the authors of [SP06] excited the carbon fibre loops and the frequencies were measured using two piezoelectric transducers. During the vibration, the beam will be momentarily free at both endpoints. The natural frequencies were obtained by sweeping through frequencies until a resonance was found.\\

The measured parameters of the beam is given in [SP06]. Since the physical beam is only nearly square, the plane has two distinct planes. The plane of the beam with a larger diameter is referred to as the stiff plane and the plane of the beam with smaller diameter is referred to as the flexible plane, by [SP06].\\

For the flexible plane $\alpha = \pm 190$ and for the stiff plane $\alpha = \pm 189$. The parameter $\gamma = 0.2830$. The natural frequencies $f_k$ is defined as 
\begin{eqnarray*}
	f_k = \sqrt{\frac{\lambda_k}{2\pi}}
\end{eqnarray*} with $\lambda_k$ the $k$'th eigenvalue. These natural frequencies $f_k$ are dimensionless, and can be scaled back by multiplying the natural frequency $f_k$ by $t_0=\ell\sqrt{\frac{\rho}{G\kappa^2}}$, as defined in Chapter 1.\\

The cut-off frequency given in [SP06] can be expressed as
\begin{eqnarray*}
	\omega_{co} = \sqrt{\frac{\kappa^2 A G}{\rho I}} = \frac{\alpha}{t_0}
\end{eqnarray*}
with the dimensionless cut-off frequency $\alpha$.

\subsection{Results from SP06}
The following table contains relevant results are obtained by [SP06]. 
% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
	\makebox[\textwidth]{
	\caption{Results from [SP06] (excluding RUS).}
	\begin{tabular}{||c|c|cc|cc|c||}
		\hline
		{n} & {Measured} & {3D FEM} & {\% Error} & {Timoshenko Beam} & {\% Error} & Side \\
		\hline
		1     & 27359.6 & 27417.6 & 0,21\% & 27407.1 & 0,17\% & Flexible \\
		  	  & 27423.8 & 27515.6 & 0,33\% & 27505.3 & 0,30\% & Stiff \\
		2     & 60862   & 60882.0 & 0,03\% & 60851.1 & -0,02\% & Flexible \\
		 	  & 61098.3 & 61022.0 & -0,12\% & 60992.1 & -0,17\% & Stiff \\
		3     & 97609.5 & 97734.4 & 0,13\% & 97796.0 & 0,19\% & Flexible \\
			  & 97852.4 & 97881.5 & 0,03\% & 97945.4 & 0,09\% & Stiff \\
		4     & 161494 & 131658 & 0,12\% & 132277 & 0,60\% & Flexible \\
			  & 131732 & 131675 & -0,04\% & 132308 & 0,44\% & Stiff \\
		5     & 161352 & 161390 & 0,02\% & 163547 & 1,36\% & Stiff \\
			  & 161538 & 161517 & -0,01\% & 163611 & 1,31\% & Flexible \\
		6     & 165183 & 164887 & -0,18\% & 169108 & 2,38\% & Stiff \\
			  & 165598 & 165398 & -0,12\% & 169634 & 2,44\% & Flexible \\
		7     & 194863 & 194933 & 0,04\% & 202352 & 3,84\% & Flexible \\
		   	  & 194973 & 195032 & 0,03\% & 202115 & 3,66\% & Stiff \\
		8     & 195869 & 195977 & 0,06\% & 203319 & 3,80\% & Stiff \\
			  & 195908 & 196097 & 0,10\% & 203518 & 3,88\% & Flexible \\
		9     & 213501 &       &       & 241202 & 12,97\% & Flexible \\
			  & 213635 &       &       & 241067 & 12,84\% & Stiff \\
  {10 and 11} & 220556 &       &       & 247954 & 12,42\% & Flexible \\
			  & 220702 &       &       & 281542 & 27,57\% & Flexible \\
			  & 221010 &       &       & 247782 & 12,11\% & Stiff \\
			  & 221092 &       &       & 281408 & 27,28\% & Stiff \\
		\hline
	\end{tabular}%
	\label{tab:addlabel}%
}
\end{table}%

\FloatBarrier

Table 4.3 shows that the Timoshenko model compares well to the measured results from the experiment. The first 8 natural frequencies for the stiff and flexible planes are very close to the natural frequencies of the three-dimensional and physical beam.\\

\textcolor{red}{Onseker oor die***************}\\
In [LC81], a single frequency equation for the free-free beam is given. From the work in section \ref{sec:Timo:EigenvalueProblem}, it has been shown that there can be up to three-different frequency equations depending on $\alpha$. As the $\alpha$ for this beam is very small, the eigenvalues 9 and above will not be considered in this dissertation.\\
\textcolor{red}{Onseker oor die***************}
\end{document}

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.3mm] (0,0) -- (7,0);

		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});	
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

	\end{tikzpicture}
	\caption{Visual representation of beam suspended at the end-points by carbon fibre loops.}
\end{figure} 
\FloatBarrier

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.3mm] (0,1) -- (7,1);
		\draw[line width = 0.3mm] (0,-1) -- (7,-1);
		\draw[line width = 0.3mm] (7,-1) -- (7,1);
		\draw[line width = 0.3mm] (0,-1) -- (0,1);

		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});

		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

		\draw[scale=0.5, domain=1:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=2:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
		\draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
		\draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

	\end{tikzpicture}
	\caption{Visual representation of beam suspended at the end-points by carbon fibre loops.}
\end{figure} 
\FloatBarrier

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.3mm] (0,0.1) -- (7,0.1);
		\draw[line width = 0.3mm] (0,-0.1) -- (7,-0.1);
		\draw[line width = 0.3mm] (7,-0.1) -- (7,0.1);
		\draw[line width = 0.3mm] (0,-0.1) -- (0,0.1);

		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});

		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
		\draw[scale=0.5, domain=-3:0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
		\draw[scale=0.5, domain=-3:1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
		\draw[scale=0.5, domain=-3:2.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});

		\draw[scale=0.5, domain=0.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
		\draw[scale=0.5, domain=1.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
		\draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});

		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

	\end{tikzpicture}
	\caption{Visual representation of beam suspended at the end-points by carbon fibre loops.}
\end{figure} 
\FloatBarrier

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.3mm] (-0.5,1) -- (6.5,1);
		\draw[line width = 0.3mm] (-0.5,-1) -- (6.5,-1);
		\draw[line width = 0.3mm] (6.5,-1) -- (6.5,1);
		\draw[line width = 0.3mm] (-0.5,-1) -- (-0.5,1);

		\draw[line width = 0.3mm] (0.5,1.5) -- (7.5,1.5);
		\draw[line width = 0.3mm] (7.5,-0.5) -- (7.5,1.5);

		\draw[line width = 0.3mm] (-0.5,1) -- (0.5,1.5);
		\draw[line width = 0.3mm] (6.5,1) -- (7.5,1.5);
		\draw[line width = 0.3mm] (6.5,-1) -- (7.5,-0.5);

		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});

		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
		\draw[scale=0.5, domain=2:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});

		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
		\draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
		\draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

	\end{tikzpicture}
	\caption{Visual representation of beam suspended at the end-points by carbon fibre loops.}
\end{figure} 
\FloatBarrier

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.3mm] (-0.1,1) -- (6.9,1);
		\draw[line width = 0.3mm] (-0.1,-1) -- (6.9,-1);
		\draw[line width = 0.3mm] (6.9,-1) -- (6.9,1);
		\draw[line width = 0.3mm] (-0.1,-1) -- (-0.1,1);

		\draw[line width = 0.3mm] (0.1,1.1) -- (7.1,1.1);
		\draw[line width = 0.3mm] (7.1,-0.9) -- (7.1,1.1);

		\draw[line width = 0.3mm] (-0.1,1) -- (0.1,1.1);
		\draw[line width = 0.3mm] (6.9,1) -- (7.1,1.1);
		\draw[line width = 0.3mm] (6.9,-1) -- (7.1,-0.9);

		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});

		\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
		\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

		\draw[scale=0.5, domain=0.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
		\draw[scale=0.5, domain=1.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

		\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
		\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
		\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
		\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
		\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
		\draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
		\draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

	\end{tikzpicture}
	\caption{Visual representation of beam suspended at the end-points by carbon fibre loops.}
\end{figure} 
\FloatBarrier

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.3mm] (-0.8,0.1) -- (6.2,0.1);
		\draw[line width = 0.3mm] (-0.8,-0.1) -- (6.2,-0.1);
		\draw[line width = 0.3mm] (6.2,-0.1) -- (6.2,0.1);
		\draw[line width = 0.3mm] (-0.8,-0.1) -- (-0.8,0.1);

		\draw[line width = 0.3mm] (0.8,0.9) -- (7.8,0.9);
		\draw[line width = 0.3mm] (7.8,0.7) -- (7.8,0.9);

		\draw[line width = 0.3mm] (-0.8,0.1) -- (0.8,0.9);
		\draw[line width = 0.3mm] (6.2,0.1) -- (7.8,0.9);
		\draw[line width = 0.3mm] (6.2,-0.1) -- (7.8,0.7);

		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

		\draw[scale=0.5, domain=-3:-1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
		\draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});

		\draw[scale=0.5, domain=-3:-0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
		\draw[scale=0.5, domain=-3:0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
		\draw[scale=0.5, domain=-3:1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
		\draw[scale=0.5, domain=-3:2.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

	\end{tikzpicture}
	\caption{Visual representation of beam suspended at the end-points by carbon fibre loops.}
\end{figure} 
\FloatBarrier

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.3mm] (-0.8,-0.1) -- (6.2,-0.1);
		\draw[line width = 0.3mm] (0.8,0.7) -- (7.8,0.7);
		\draw[line width = 0.3mm] (-0.8,-0.1) -- (0.8,0.7);
		\draw[line width = 0.3mm] (6.2,-0.1) -- (7.8,0.7);

		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

		\draw[scale=0.5, domain=-3:-1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
		\draw[scale=0.5, domain=2:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});

		\draw[scale=0.5, domain=-3:-0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
		\draw[scale=0.5, domain=-3:0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
		\draw[scale=0.5, domain=-3:1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
		\draw[scale=0.5, domain=-3:2.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

	\end{tikzpicture}
	\caption{Visual representation of beam suspended at the end-points by carbon fibre loops.}
\end{figure} 
\FloatBarrier

### 2022-10-31 files/Chapter4/SuspendedBeamModel.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\setcounter{chapter}{4}
\section{Suspended beam model}
The suspended Timoshenko beam model is referred to as Problem T-3 in this \ref{ssec:1D_Model:ModelProblems}. The beam is suspended at both endpoints by linear springs. The boundary conditions of Problem T-3 as given in section \ref{ssec:1D_Model:ModelProblems} can be rewritten by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations2D}.

	\[\partial_{x}w(0,\cdot) - \phi(0,\cdot) = kw(0,\cdot)  \ \ \ \textrm{and} \ \ \ \partial_{x}\phi(0,\cdot) = 0\]
	\[\partial_{x}w(1,\cdot) - \phi(1,\cdot) = -kw(0,\cdot) \ \  \ \textrm{and} \ \ \ \partial_{x}\phi(1,\cdot) = 0\]

The linear springs are allowed to take the weight of the beam and the system settles in a equilibrium state. The elongation of the springs from their natural length is denoted by $h$. The displacement from this equilibrium state should be considered.\\

Let $\langle w^* \ \phi^*\rangle$ represent the solution of the model problem, and $\langle w^e \ \phi^e \rangle$ the solution to the equilibrium problem. Define $\langle w \ \phi\rangle = \langle(w^*-w^e) \ \ (\phi^*-\phi^e)\rangle$ such that it represents the deviation of the beam from the equilibrium solution. Substitution verifies that $\langle w \ \phi\rangle$ satisfies the partial differential equation and boundary conditions.\\

If the beam is suspended by cables, in their loaded state they can be considered as linear springs. However if $w > h$ then the cables are no longer supporting the beam. The problem then becomes non-linear. Assume that the motion is small enough so that the problem remains linear.

\subsubsection{Variational problem}
Find $w,\phi$ such that for all $t>0$, $\langle w,\phi \rangle \in C[0,1]\times C[0,1]$ and
\begin{eqnarray*}
	\int_{0}^{1} \partial_{t}^{2} wv + \frac{1}{\alpha}\int_{0}^{1}  \partial_{t}^{2} \phi \psi &=& \int_{0}^{1} (\partial_{x}w - \phi)(\psi -v')  - \frac{1}{\beta}\int_{0}^{1}\partial_{x}\phi \psi'\\
	& & - kv(1)w(1,t) - kv(0)w(0,t)
\end{eqnarray*} for all $v,\psi \in C[0,1]$.\\

This model is required for explanation in Section 4.6.

\begin{comment}

\subsubsection{Modal Analysis}
The boundary conditions at $x = 0$ results in the following solutions for the constants of the general solution of the eigenvalue problem:
\begin{align}
	C  =  \frac{\omega}{\mu}A - k\frac{\omega}{\lambda} \left(1+\frac{\mu^{2}+\lambda}{\omega^2-\lambda}\right)B & \textrm{ and } \ D = \frac{ \mu^2+\lambda}{\omega^2-\lambda}B \ \ \ \textrm{ if } \lambda < \alpha \label{A1}\\
	C = \frac{\omega}{\lambda}A + k\frac{\omega}{\lambda}\left(1+\frac{\alpha}{\lambda - \omega^2}\right)B  \ & \textrm{ and } \ D = \frac{\alpha}{\omega^2-\lambda}B  \ \textrm{ if } \lambda = \alpha \label{A2}\\
	C=-\frac{\omega}{\theta}A+k\frac{\omega}{\lambda}\left(1-\frac{\theta^2-\lambda}{\omega^2-\lambda}\right)B  \ & \textrm{ and } \ D = -\frac{\theta^2-\lambda}{\omega^2 - \lambda}B  \ \textrm{ if } \lambda > \alpha \label{A3}
\end{align}

The boundary conditions at $x = 1$ gives the following homogeneous system of equations with the entries of the coefficient matrix given below.
\begin{align}
	\begin{bmatrix}
		M_{11}(\lambda) & M_{12}(\lambda)\\
		M_{21}(\lambda) & M_{22}(\lambda)
	\end{bmatrix}
	\begin{bmatrix}
		A\\
		B
	\end{bmatrix}
	= 
	\begin{bmatrix}
		0\\
		0
	\end{bmatrix}
	\label{Mat}
\end{align}

{If $\lambda < \alpha$}
\begin{align*}
&M_{11}(\lambda) = \sinh(\mu)(\lambda+\mu^2) + \frac{\omega(\lambda - \omega^2)}{\mu}\sin(\omega)&\\
&M_{12}(\lambda) = - k\frac{\omega(\mu^2+\omega^2)}{\lambda}\sin(\omega) + (\lambda+\mu^2)(\cosh(\mu)-\cos(\omega))& \\
&M_{21}(\lambda) = k\sinh(\mu) + k\frac{\omega}{\mu}\sin(\omega) +  \frac{\lambda}{\mu}(\cos(\omega) - \cosh(\mu))&\\
&M_{22}(\lambda) =\frac{\lambda^3+\lambda^2\mu^2-k^2\omega^4-k^2\mu^2\omega^2}{\lambda\omega(\lambda-\omega^2)}\sin(\omega) - \frac{\lambda }{\mu}\sinh(\mu) -k\frac{\lambda+\omega^2+2\mu^2}{(\lambda-\omega^2)}\cos(\omega) -k\cosh(\mu)&
\end{align*}

{If $\lambda = \alpha$}
\begin{align*}
&M_{11}(\lambda) = \frac{\omega\left(\lambda - \omega^2\right)}{\lambda}\sin(\omega)&\\
&M_{12}(\lambda)=\alpha-\alpha\cos(\omega)-k\frac{\omega}{\lambda}\left(\frac{\alpha}{\omega^2+\lambda}+1\right)(\lambda-\omega^2)\sin(\omega)&\\
&M_{21}(\lambda)=\frac{\omega^2}{\lambda}\cos(\omega)+\cos(\omega)\frac{\left(\lambda - \omega^2\right)}{\lambda} + k\sin(\omega)\frac{\omega}{\lambda} - 1 &\\
&M_{22}(\lambda) = k-\alpha-k\left(1-\frac{\alpha}{\lambda-\omega^2}-\frac{\alpha }{\omega^2+\lambda}\right)\cos(\omega)+\left(\frac{\alpha}{\omega}-k^2\frac{\omega}{\lambda}+\frac{\alpha\omega}{\lambda-\omega^2}-k^2\frac{\alpha\omega}{\lambda(\omega^2+\lambda)}\right)\sin(\omega)&
\end{align*}

{If $\lambda > \alpha$}
\begin{align*}
&M_{11}(\lambda) = \left(\lambda - \theta^2\right)\sin(\theta) - \frac{\omega  \left(\lambda - \omega^2\right)}{\theta}\sin(\omega)&\\
&M_{12}(\lambda) =  - k\frac{\omega(\omega^2- \theta^2)}{\lambda}\sin(\omega) + \left(\lambda - \omega^2\right)(\cos(\omega) - \cos(\theta))&\\
&M_{21}(\lambda)=k\frac{\omega}{\theta}\sin(\omega)-k\sin(\theta)-\frac{\lambda}{\theta}(\cos(\omega)-\cos(\theta))&\\
&M_{22}(\lambda)=\frac{\lambda^3-\lambda^2\theta^2-k^2\omega^4+k^2\omega^2\theta^2}{\lambda\omega(\lambda-\omega^2)}\sin(\omega)-\frac{\lambda}{\theta}\sin(\theta) + k\cos(\theta)-k\frac{\lambda-2\theta^2+\omega^2}{(\lambda-\omega^2)}\cos(\omega)&
\end{align*}

The frequency equations can be determined by simplifying the equation $$M_{11}(\lambda)M_{22}(\lambda)-M_{12}(\lambda)M_{21}(\lambda) = 0.$$
\end{comment}
\end{document}

### 2022-10-31 files/Chapter5/PlateModel.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Cantilever plate model}\label{sec:FEM:Plate}
Consider a rectangular cantilever Reissner-Mindlin plate.

\subsubsection{Reference configuration for a rectangular plate}
Let $\left\{e_1,e_2\right\}$ be a right-handed orthonormal basis for $R^2$. Denote the elastic body as $\Omega \in R^2$ with the reference point $(0,0)$. For a rectangular plate, 
\begin{eqnarray*}
	\Omega = \left \{ x \in R_2 \ | \ 0 \leq x_1 \leq 1, \ 0 \leq x_2 \leq b \right \}.
\end{eqnarray*} 
Let $\partial \Omega$ denote the boundary of plate. The boundary $\partial \Omega$ can be divided into four distinct lines.\\

\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\Sigma_0:& \quad x_1 &= 0\\
		\Sigma_1:& \quad x_1 &= 1
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\Gamma_0:& \quad x_2 &= 0\\
		\Gamma_1:& \quad x_2 &= b
	\end{eqnarray*}
\end{minipage}\\

\textcolor{red}{*****************************}\\
Since the plate is a rectangular shape in $R^2$, one would easily try to use the reference configuration as the two-dimensional elastic body in section 5.2. However for the plate model, the space $R^2$ can be considered perpendicular to the space for the two-dimensional elastic body in section 5.2.\\
\textcolor{red}{*****************************}

\subsubsection{Cantilever plate model}
Consider a rectangular plate clamped rigidly to a surface at the edge $\Sigma_0$. The plate is free hanging on the remaining edges and there is not external force acting on the plate. The plate is be modelled using the Reissner-Mindlin plate theory that is presented in section \ref{ssec:P_Model:ModelProblems} as Problem P-1.\\

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.3mm] (-0.8,-0.1) -- (6.2,-0.1);
		\draw[line width = 0.3mm] (0.8,0.7) -- (7.8,0.7);
		\draw[line width = 0.3mm] (-0.8,-0.1) -- (0.8,0.7);
		\draw[line width = 0.3mm] (6.2,-0.1) -- (7.8,0.7);

		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

		\draw[scale=0.5, domain=-3:-1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
		\draw[scale=0.5, domain=2:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});

		\draw[scale=0.5, domain=-3:-0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
		\draw[scale=0.5, domain=-3:0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
		\draw[scale=0.5, domain=-3:1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
		\draw[scale=0.5, domain=-3:2.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

		\node at (7.2,0.1) {$b$};
		\node at (3.2,-0.27) {$\ell = 1$};

		%\node at (6.5,0.3) {$\Sigma_1$};
		%\node at (0.51,0.3) {$\Sigma_0$};
		%\node at (3.2,0.05) {$\Gamma_0$};
		%\node at (3.6,0.5) {$\Gamma_1$};
		%\node at (-0.7,-0.3) {$(0,0)$};

		\draw[line width = 0.1mm,->] (9,1) -- (10,1.6);
		\draw[line width = 0.1mm,->] (9,1) -- (10.3,1);
		\node at (9.2,1.4) {$e_2$};
		\node at (9.6,0.8) {$e_1$};

		\draw[line width = 0.2mm] (0.8,0.7) -- (7.8,0.7);
		\draw[line width = 0.2mm] (-0.8,-0.1) -- (0.8,0.7);
		\draw[line width = 0.2mm] (6.2,-0.1) -- (7.8,0.7);

	\end{tikzpicture}
	\caption{Two-dimensional Cantilever Plate}
\end{figure} 
\FloatBarrier

In section \ref{ssec:P_Model:ModelProblems} the variational problem for the cantilever Reissner-Mindlin plate is defined by Problem P-1V. For convenience, the relevant results from section \ref{ssec:P_Model:ModelProblems} are repeated.

\subsubsection{Problem P-1V}
Find a function $u = \langle w, \psi \rangle$, such that for all $t>0$, $u \in T_1({\bar{\Omega}}) \times T_2({\bar{\Omega}})$ and the following equations are satisfied
\begin{eqnarray}
	c(u,\phi) &=& -b(u,\phi) + (Q,\phi), \label{eq:P_Model:ProblemP1V1}
\end{eqnarray} with $\phi = \langle v, \phi \rangle  \in T_1({\bar{\Omega}}) \times T_2({\bar{\Omega}})$ an arbitrary function.\\

With the test function spaces
\begin{eqnarray*}
	T_1(\bar{\Omega}) & = & \left \{v \in C^1(\bar{\Omega})\ | \ v = 0 \textrm{ on } \Sigma_0\right\},\\ 
	T_2(\bar{\Omega}) & = & \left \{ \phi = \left[ \phi_1 \ \phi_2 \right]^T \ | \ \phi_1, \phi_2 \in C^1(\bar{\Omega}), \ \phi_1 = \phi_2 = 0 \textrm{ on } \Sigma_0 \right\}.
\end{eqnarray*}

The bilinear forms and integral function defined by

\begin{eqnarray*}
	b(u,\phi) & = & \int_\Omega \boldsymbol{Q} \cdot \nabla v \ dA + \int_{\Omega} \textrm{Tr}(M\Phi) \ dA,\\
	c(u,\phi) & = & \int_\Omega h (\partial_t^2 w) v \ dA + \int_\Omega I (\partial_t^2 \psi) \cdot \phi \ dA \\
	(f,g) &=& -\int_{\Omega} f\cdot g \ dA \label{eq:2D_Model:Bilinear_int}
\end{eqnarray*}

Using the definition of the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten as follows.

\subsubsection{Constitutive Equations}
\begin{eqnarray}
	\boldsymbol{Q} & = & h(\nabla w + \boldsymbol{\psi}) \label{eq:P_Model:CE1D}\\
	M_{11} & = & \frac{1}{2\beta(1-\nu^2)} \left[ 2(\partial_1\psi_1 + \nu \partial_2 \psi_2 \right] \label{eq:P_Model:CE2D}\\
	M_{12} = M_{21} & = & \frac{1}{2\beta(1-\nu^2)} \left[ (1-\nu)(\partial_1\psi_2 + \partial_2 \psi_1) \right] \label{eq:P_Model:CE3D}\\
	M_{11} & = & \frac{1}{2\beta(1-\nu^2)} \left[ 2(\partial_2 \psi_2 + \nu \partial_1 \psi_1)\right] \label{eq:P_Model:CE4D}
\end{eqnarray}

\textcolor{red}{CHECK!!!}
\subsubsection{Bilinear Form}
\begin{eqnarray*}
b(u,\phi) & = & \int_\Omega \boldsymbol{Q} \cdot \nabla v \ dA + \int_{\Omega} \textrm{Tr}(M\Phi) \ dA,\\
	& + & \frac{1}{\beta(1-\nu^2)}\int_{\Omega} (\partial_1\psi_1 + \nu\partial_2\psi_2)\partial_1\phi_1+ (\partial_2\psi_2 + \nu\partial_1\psi_1)\partial_2\phi_2 \ dA,\\
	& + & \frac{1}{2\beta(1+\nu)}\int_{\Omega} (\partial_1\psi_2+\partial_2\psi_1)(\partial_1\phi_2+\partial_2\psi_1) \ dA.\\
\end{eqnarray*}

\subsection{Weak variational form}
Similar to Section 2.1, the weak variational form for Problem P-1 can be derived from Problem P-1V.
\subsubsection{Bilinear forms}
From the bilinear form, we have
\begin{eqnarray*}
	b(f_2,g_2) & = & \frac{1}{\beta(1-\nu^2)}\iint_{\Omega} (\partial_1f_{2,1} + \nu\partial_2f_{2,2})\partial_1g_{2,1}+ (\partial_2f_{2,2} + \nu\partial_1f_{2,1})\partial_2g_{2,2} \ dA,\\
	& + & \frac{1}{2\beta(1+\nu)}\iint_{\Omega} (\partial_1f_{2,2}+\partial_2f_{2,1})(\partial_1g_{2,2}+\partial_2 g_{2,1}) \ dA
\end{eqnarray*}

For all $f,g \in T_1(\Omega)\times T_2(\Omega) $, define the bilinear forms
\begin{eqnarray*}
	c(f,g) & = & h(f_1,g_1)_{\Omega} + I(f_2,g_2)_{R_2} \\
	b^*(f,g) & = & b(f_2,g_2) + h(\nabla f_1 + f_2, \nabla g_1 + g_2)_{R_2}
\end{eqnarray*}
where the integrals are defined by
\begin{eqnarray*}
	(f_1,g_1)_{\Omega} & = & \iint_\Omega f_1 g_1 \ dA,\\
	(f,g)_{R_2} & = & \iint_\Omega f \cdot g \ dA.
\end{eqnarray*}

Define $V_1(0,1)$ as the closure of $T_1(0,1)$ in $H^1(0,1)$ and $V_2(0,1)$ as the closure of $T_2(0,1)$ in $H^1(0,1)^2$.\\

Denote the space $X = L^2(0,1)\times L^2(0,1)^2$ as a setting for Problem P-1V. A natural inner product for $X$ is $(f,g)_X = (f_1,g_1)_{\Omega} + (f_2,g_2)_{R_2}$.  Define $W$ as the space $X$ with the inner product $c$ and $V = V_1(0,1) \times V_2(0,1)$

\subsubsection{Problem Plate-1W}
Find a function $u$ such that for all $t>0$, $u(t) \in V$, $u'(t) \in V$ and $u''(t) \in W$, satisfying the following equation
\begin{eqnarray}
	c(u''(t),v) + b^*(u(t),v) & = & (f(t),v)_{\Omega} \ \ \ \textrm{ for each } v \in V,
\end{eqnarray} with $u(0)= u_0 = \langle w_0, \boldsymbol\psi_0 \rangle$, and $u'(0)= u_1 = \langle w_1, \boldsymbol\psi_1 \rangle$.\\

\subsubsection{Existence and uniqueness}
\textcolor{red}{XXXXXXXXXXXXXXXXXXXXX}
Section 2.2 provides the necessary theory for the existence and uniqueness of solutions for second order hyperbolic equations. The assumptions \textbf{A1}, \textbf{A2} and \textbf{A4} are similar to Section 2.3. So it is only required to show that $b$ is an inner product for $V$ and that there exists a positive number $C_V$ such that
\begin{eqnarray*}
	\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}
\end{eqnarray*} for each $v \in V$.\\

However, this is not as simple as the example in Section 2.4. ****Reference 'n article wat na dit kyk.***

\subsection{Galerkin approximation}
Divide the reference configuration $\Omega$ into a rectangular grid of elements, such that there are $n = n_1 \times n_2$ nodes.\\

For the plate model, two different definitions for basis functions are required.\\

First consider a set of $n$-dimensional linear independent basis functions, defined by the set 
\begin{eqnarray*}
	\left\{\delta^*_1, \delta^*_2, ..., \delta^*_n\right\}.
\end{eqnarray*}
In this set, each $\delta^*$ is a cubic function. The subset of functions that satisfies the conditions of the test function space $T_1(\bar{\Omega})$ are the admissible basis functions for $T_1(\bar{\Omega})$. These admissible basis functions can be renumbered and expressed as the set $\left\{\delta^*_1, \delta^*_2, ..., \delta^*_{k_1}\right\}$ for some $k_1 \leq 2n$.\\

Next consider a set of $n$-dimensional linear independent basis functions, defined by the set
\begin{eqnarray*}
	\left\{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \right\}.
\end{eqnarray*} These functions $\phi_j$ are cubic basis functions. Denote each element in this set by $\delta_i$. The subset of functions that satisfies the conditions of the test function space $T_2(\bar{\Omega})$ are the admissible basis functions for $T_2(\bar{\Omega})$. These admissible basis functions can be renumbered and expressed as the set $\left\{\delta_1, \delta_2, ..., \delta_{k_2}\right\}$ for some $k_2 \leq 2n$.\\

Define the two spaces
\begin{eqnarray*}
	S^h_1 & = & \textrm{span}\left(\left\{\delta^*_i \ | \ i = 1,2,...,k_1 \right\} \right),\\
	S^h_2 & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k_2 \right\} \right).
\end{eqnarray*}
For each function $u^h \in S_1^h$ and each function $\psi^h \in S_2^h$, $u^h$ can be expressed as
\begin{eqnarray*}
	w^h = \sum_{i = 1}^{k} w_i(t) \delta^*_{i}(x)
\end{eqnarray*} and $\psi^h$ can be expressed as
\begin{eqnarray*}
	\psi^h = \sum_{i = 1}^{k} \psi_i(t) \delta_{i}(x)
\end{eqnarray*}

Problem P1-V can now be rewritten into a Galerkin Approximation, denoted by Problem P-1G.

\subsubsection{Problem P-1G}
Find a function $u^h = \langle w^h, \psi^h \rangle$, such that for all $t>0$, $u^h \in S_1^h \times S_1^h$ and the following equations are satisfied
\begin{eqnarray}
	c(u^h,\phi_{i,j}) &=& -b(u^h,\phi_{i,j}) + (Q^I,\phi_{i,j}), \label{eq:P_Model:ProblemP1V1}
\end{eqnarray} with $\phi_{i,j} = \langle v_i, \phi_j \rangle$ for $i = 1,2,...,k_1$ and $j = 1,2,...,k_2$

\textcolor{red}{INTERPOLATION TERM}

\subsection{System of ordinary differential equations}
The standard FEM matrices $K_{11}$ to $K_{22}$ and $M_F$ where presented in section \ref{ssec:2DFEM:DE}. In addition, the following standard FEM matrices are also required.

\subsubsection{FEM matrices}
\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		{L_{1}}_{ij} & = & \iint_{\Omega} \phi_j \partial_1\phi_i
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		{L_{2}}_{ij} & = & \iint_{\Omega} \phi_j \partial_2\phi_i
	\end{eqnarray*}
\end{minipage}

for $i,j = 1,2,...,p$.\\

Define the following matrices:\\
\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\mathbf{K11} & = & hK_{11}-hK_{22}\\
		\mathbf{K12} & = & hL_1\\
		\mathbf{K13} & = & hL_2\\
		\mathbf{K21} & = & hL_1^T\\
		\mathbf{K22} & = & AK_{11}+BK_{22}+h\mathbf{M}
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{0.8\linewidth}
	\begin{eqnarray*}
		\mathbf{K23} & = & A\nu K_{12}+BK_{21}\\
		\mathbf{K31} & = & hL_2^T\\
		\mathbf{K32} & = & A\nu K_{21}+BK_{12}\\
		\mathbf{K33} & = & AK_{22}+BK_{11}+h\mathbf{M}
	\end{eqnarray*}
\end{minipage}\\

with $A = \frac{1}{\beta(1-\nu^2)}$ and $B = \frac{1}{2\beta(1+\nu)}$.\\

Using the standard FEM matrices and the matrices $\mathbf{K11}$ to $\mathbf{K33}$, the following concatenated matrices are defined.

\begin{eqnarray}
	\begin{aligned}
		K & = &
		\begin{bmatrix}
			\mathbf{K11} & \mathbf{K12} & \mathbf{K13}\\
			\mathbf{K21} & \mathbf{K22} & \mathbf{K23}\\
			\mathbf{K31} & \mathbf{K32} & \mathbf{K33}
		\end{bmatrix}
	\end{aligned}
	\ \ \ \ \ \ \ \ \
	\begin{aligned}
		M & = &
		\begin{bmatrix}
			h\mathbf{M} & {O} & {O}\\
			{O} & I\mathbf{M} & {O}\\
			{O} & {O} & I\mathbf{M}
		\end{bmatrix}\label{3DB_23}
	\end{aligned}\label{eq:PFEM:K+M}
\end{eqnarray}

\begin{eqnarray}
	M_f & = &
	\begin{bmatrix}
		{M_F} & {O_F} & {O_F}\\
		{O_F} & {M_F} & {O_F}\\
		{O_F} & {O_F} & {M_F}
	\end{bmatrix}\label{eq:PFEM:M}
\end{eqnarray}
The matrices ${O}$ and ${O_F}$ are the zero matrices of the same size as $\mathbf{M}$ and $\mathbf{M_f}$ respectively.\\

Using \eqref{eq:PFEM:K+M} and \eqref{eq:PFEM:M}, Problem P-1G is rewritten as a system of ordinary differential equations. This system is referred to as Problem P-1ODE
\subsubsection{Problem P-1ODE}
Find function $\bar{u} \in S_1^h\times S_2^h$ such that
\begin{eqnarray}
	M\ddot{\bar{u}} & = & K\bar{u} + M_{f}Q^I \label{Plate_FEM_M}
\end{eqnarray}
With $\bar{u}$ in the form $\bar{u} = \langle w, \partial_x w, \partial_y w, \partial_{xy} w, \psi_1, \partial_x \psi_1, \partial_y \psi_1, \partial_{xy} \psi_1, \psi_2, \partial_x \psi_2, \partial_y \psi_2, \partial_{xy} \psi_2 \rangle$.

\subsection{Eigenvalue problem}

The equation \eqref{Plate_FEM_M} is the same form as in section \ref{2dFEM_EP} for the two-dimensional elastic body. Therefore the derivation of the eigenvalue problem is identical. Denote the eigenvalue problem for Problem P-1 by Problem P-1E.
\subsubsection{Problem P-1E}
Find a vector function $u$ and a number $\lambda$ such that
\begin{eqnarray}
	\lambda M{u} & = & K{u}.
\end{eqnarray}

\end{document}
\subsubsection{Accuracy of the eigenvalues}
Recall that there are $n = (n_1+1)(n_2+1)$ elements for a choice of positive integers $n_1$ and $n_2$. Table 5.1 and 5.2 show that increasing the number of elements, the accuracy of the eigenvalues increase.\\

Fix $h = 1/20$.

\begin{table}[htbp]
	\makebox[\textwidth]{
		\caption{Relative error of first 50 eigenvalues of Problem P-1. Bi-Cubic basis functions.}
		\begin{tabular}{|lc|cccccc|}
			\hline
			\multicolumn{8}{|c|}{Relative Error of Eigenvalues} \\
			\hline
			\multicolumn{2}{|c|}{$n_1$} & {20} & {25} & {30} & {35} & {40} & {45} \\
			\hline
			\hline
			{d = 0.25} & n     & {126} & {208} & {279} & {360} & {451} & {598} \\
			& Error & 7.993 $\times 10^{-3}$ & 2.699$\times 10^{-3}$ & 6.686$\times 10^{-4}$ & 2.713$\times 10^{-4}$ &
			1.246$\times 10^{-4}$ & 7.545$\times 10^{-5}$ \\
			\hline
			{d = 0.5} & n     & {231} & {364} & {496} & {684} & {861} & {1104} \\
			& Error & 2.656$\times 10^{-3}$ & 8.026$\times 10^{-4}$ & 2.379$\times 10^{-4}$ & 1.159$\times 10^{-4}$ & 4.225$\times 10^{-5}$ & - \\
			\hline
			{d =1} & n     & {441} & {676} & {961} & {1296} & {1681} & {2116} \\
			& Error & 1.255$\times 10^{-3}$ & 3.285$\times 10^{-4}$ & 1.228$\times 10^{-4}$ & 5.225$\times 10^{-6}$ & -     & - \\
			\hline
			{d = 1.25} & n     & {546} & {858} & {1209} & {1620} & {2091} & {2668} \\
			& Error & 8.608$\times 10^{-4}$ & 2.677$\times 10^{-4}$ & 9.040$\times 10^{-5}$ & -     & -     & - \\
			\hline
		\end{tabular}%
		\label{tab:addlabel}%
	}
\end{table}%

\FloatBarrier

In Table 5.1, the ratio between $n_1$ and $n_2$ are kept so that $\Delta x_1$ and $\Delta x_2$ are equal for all elements. So for any $n_1$, $n_2 = \lceil d n_1 \rceil$.\\

Table 5.1 shows that using bi-cubic basis functions, an accuracy of at least 4 significant digits can be obtained with minimal elements. It also shows that the number of elements have to be increased as the parameter $d$ is increased.

\subsubsection{Eigenvalues and eigenfunctions}
Fix $b =1$. Table 5.1 shows examples of the eigenvalues. The greater the ratio between $b$ and $h$ with $b>h$, the smaller the first eigenvalues become.
\begin{table}[!h]
	\centering
	\renewcommand{\arraystretch}{1.05}
	\begin{tabular}{|l||l|l|l|}
		\hline
		\multicolumn{4}{|l|}{Cantilever Plate Eigenvalues with $b = 1$.} \\ \hline
		i        & $h = 1/10$       & $h  = 1/20$      & $h = 1/30$      \\ \hline
		1        & 0.0336           & 0.00845          & 0.00381         \\
		2        & 0.186            & 0.0496           & 0.0224          \\ 
		3        & 1.15             & 0.313            & 0.142          \\
		4        & 1.86             & 0.506            & 0.230           \\
		5        & 2.28             & 0.643            & 0.294            \\
		6        & 6.45             & 1.92             & 0.887            \\
		7        & 8.37             & 2.50             & 1.15            \\
		8        & 9.29             & 2.74             & 1.26            \\
		9        & 10.8             & 3.29             & 1.53            \\
		10       & 17.4             & 5.49             & 2.58            \\ \hline
	\end{tabular}
	\caption{First 10 eigenvalues of a cantilever plate, with $b = 1$ and varying values for $h$.}
\end{table}

\subsubsection{Shapes of modes/eigenfunctions**}
Figure 5.1 show examples of several mode shapes of a cantilever plate model.
\begin{figure}[h!]
	\centering
	\begin{minipage}[b]{0.4\linewidth}
		\includegraphics[width=60mm]{BeamType.png}
		\subcaption{Beam Type}
		\label{fig:minipage1}
	\end{minipage}
	\quad
	\begin{minipage}[b]{0.4\linewidth}
		\includegraphics[width=60mm]{2DType.png}
		\subcaption{2-Dimensional Wave}
		\label{fig:minipage2}
	\end{minipage}
	\quad
	\begin{minipage}[b]{0.4\linewidth}
		\includegraphics[width=60mm]{TwistType.png}
		\subcaption{Twisting}
		\label{fig:minipage2}
	\end{minipage}
	\quad
	\begin{minipage}[b]{0.4\linewidth}
		\includegraphics[width=60mm]{TransverseType.png}
		\subcaption{Transverse Waves along y-Axis}
		\label{fig:minipage2}
	\end{minipage}
	\caption{Examples of possible mode shapes of the cantilever plate model.}
\end{figure}

\section{Example: Plate-Beam System}
An example of the use of a plate model, consider the plate-beam system as given in [LVV09]. Consider a thin rectangular plate. Suppose that the plate is rigidly supported at the endpoints $\Sigma_0$ and $\Sigma_1$. The plate is supported by beams at the endpoints $\Gamma_0$ and $\Gamma_1$. The beams are simply supported at their endpoints. There are no external forces acting on the plate or beams. This model can be mathematically expressed as a Reissner-Mindlin-Timoshenko model.\\

Consider the equations for the Reissner-Mindlin plate model \eqref{P_DE_1}-\eqref{P_DE_6} in Section 1.6.
\subsubsection{Boundary Conditions}
The boundary conditions at the rigidly supported edges $\Sigma_0$ and $\Sigma_1$ are
\[Mn\cdot n = 0, \ \ w = 0 \ \ \textrm{ and } \ \boldsymbol{\psi} \cdot \tau = 0 \]
with $n$ the unit normal vector. The boundary conditions for the beams are
\begin{eqnarray*}
	w_b = 0 \ \ \textrm{ and } \ \ M_b = 0
\end{eqnarray*} at $x_1 = 0$ and $x_1 = 1$.

\subsubsection{Interface Conditions}
The plate is supported at the edges $\Gamma_0$ and $\Gamma_1$ by two beams. The interface of the displacement and angle of cross-sections between the plate and beam is given by
\[w_b(x_1,t) = w(x_1,0,t) \ \textrm{ on } \ \Gamma_0, \ w_b(x_1,t) = w(x_1,b,t) \ \textrm{ on } \ \Gamma_1, \]
\[\phi_b(x_1,t) = -\psi(x_1,0,t) \ \textrm{ on } \ \Gamma_0, \ \phi_b(x_1,t) = -\psi(x_1,b,t) \ \textrm{ on } \ \Gamma_1, \]
where subscript $b$ denotes the values of the beam.\\

The interface of the force and moment densities are given by,
\begin{eqnarray*}
	Q \cdot n & = & -P, \\
	Mn \cdot \tau & = & L, \\
	Mn \cdot n & = & 0.
\end{eqnarray*} $\tau$ is a unit vector perpendicular to $n$. $L$ is a moment density transmitted from the plate to the beam. $P$ is a force density transmitted from the plate to the beam.

\subsection{Variational Form}
Number the beams $b_0$ as the beam supporting the edge $\Gamma_0$ and $b_1$ as the beam supporting the edge $\Gamma_1$. The dimensionless equations of the plate model remains as equations \eqref{P_DE_1}-\eqref{P_DE_6}. The equations for the beams includes dimensionless constants $\eta_1$ and $\eta_2$ that accounts for the material and geometric properties of the beams and plate. The equations also include moment density $L$ and force density $P$.

\subsubsection*{Equations of Motion}
\begin{eqnarray*}
	\partial_{t}^{2} w &=& \frac{1}{\eta_1}(\partial_{x}V + P), \label{TGT_5}\\
	\frac{1}{\alpha} \partial_{t}^{2} \phi &=& \frac{1}{\eta_1}(V + \partial_{x}M+L),\label{TGT_6}
\end{eqnarray*}
\subsubsection*{Constitutive Equations}
\begin{eqnarray*}
	M &=& \frac{\eta_2}{\beta}\partial_x \phi, \label{TGT_7}\\
	V &=& \eta_2(\partial_x w-\phi). \label{TGT_8}
\end{eqnarray*}
The dimensionless constants are $\eta_1 = \displaystyle \left(\frac{\rho_b}{\rho}\right)\left(\frac{A}{\ell^2}\right)$ and $\eta_2 = \displaystyle \left(\frac{G_b}{G}\right)\left(\frac{\kappa^2_b}{\kappa^2}\right)\left(\frac{A}{\ell^2}\right)$.

\subsubsection{Test Functions}
\begin{eqnarray*}
	T_1(\Omega) & = & \left\{v \in C^1(\Omega) \ | \ v = 0 \ \textrm{ on } \Sigma_0 \textrm { and } \Sigma_1\right\}\\
	T_2(\Omega) & = & \left\{\phi = \langle \phi_1, \ \phi_2\rangle \ | \ \phi_1,\phi_2 \in C^1(\Omega), \ \ \phi_2 = 0 \ \textrm{ on } \Sigma_0 \textrm { and } \Sigma_1\right\}\\
	T_b([0,1]) & = & \left\{v \in C^1[0,1] \ | \ v(0)  = v(1) = 0\right\}
\end{eqnarray*}
\subsection{Bilinear Form}

\subsubsection{Variational Problem}
The body $\Omega$ is also divided into an $n_1 \times n_2$ rectangular grid.  For each solution $w$ of Problem P-1V let $w^h$ denote the projection of $u$ into the finite dimensional space $S_1^h$ and $\psi^h$ denote the projection of $\psi$ into the finite dimensional space $S_2^h$. Each function $w^h$ in $S_1^h$ and $\psi^h = \langle \psi_1^h, \psi_2^h \rangle$ in $S_2^h$ can be expressed as
\begin{eqnarray*}
	w^h(\bar{x},t) = \sum_{i = 1}^{k_1} w(x_i^*,t) \delta_{i},
\end{eqnarray*}
and for each function $\psi^h$ in $S^h_2$,
\begin{eqnarray*}
	\psi_1^h(\bar{x},t)  =  \sum_{i = 1}^{k_2} \psi_{1}(x_i^*,t) \delta_{i}^* \ \ \ \ \textrm{ and } \ \ \psi_2^h(\bar{x},t)  =  \sum_{i = 1}^{k_2} \psi_{2}(x_i^*,t) \delta_{i}^*.
\end{eqnarray*}

Suppose $\langle u , \phi \rangle$ is a solution for Problem P-1V and $\langle u^h, \phi^h \rangle$ is a projection of $\langle u, \phi \rangle$ onto the finite dimensional space $S_1^h\times S_2^h$. Then Problem P-1V can be rewritten into a Galerkin Approximation, denoted by Problem P-1G

Find functions $w^h$ and $\psi^h$, such that for all $t>0$, $w^h \in S^h_1$ and $\psi^h \in S^h_2$, satisfying the following equations
\begin{eqnarray}
	\iint_\Omega h \partial_t^2 w^h v_i \ dA & = & - \iint_\Omega Q^h \cdot \nabla v_i \ dA + \iint_\Omega q_I v_i \ dA, \\
	\iint_\Omega I \partial_t^2 \psi^h \cdot \phi_i \ dA & = & - \iint_\Omega b(\psi^h,\phi_i) \ dA - \iint_\Omega Q^h \cdot \phi_i \ dA.
\end{eqnarray}
for $i = 1,2,...,p$. $q_I$ is the interpolant of the function $q$ over the discretized domain.

### 2022-10-31 files/Chapter6/2D_FEM.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
In this chapter, the Finite Element Method (FEM) is applied to the two- and three-dimensional cantilever beams as well as a Reissner-Mindlin cantilever plate. The aim of this chapter is to obtain a numerical formula to calculate the eigenvalues and eigenvectors for these models. This chapter serves as preparation for Chapter 6.\\

The outline of the chapter is as follows.
\begin{itemize}
	\item[] Section \ref{sec:FEM:2D} is the FEM for a two-dimensional cantilever body.
	\item[] Section \ref{sec:FEM:3D} is the FEM for a three-dimensional cantilever body. 
	\item[] Section \ref{sec:FEM:Plate} is the FEM for A Reissner-Mindlin cantilever plate model. 
\end{itemize}

\section{Two-dimensional cantilever body} \label{sec:FEM:2D}
Consider a two-dimensional cantilever elastic body, with a rectangular cross-section.

\subsubsection{Reference configuration for rectangular cross-section}
Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$. Denote the elastic body by $\Omega \in R_2$, with $(0,0)$ as the reference point. For a rectangular cross-section, $\Omega$ can be described as
\begin{eqnarray*}
	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines as follows:

\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\Sigma_0:& \quad x_1 &= 0\\
		\Sigma_1:& \quad x_1 &= 1
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\Gamma_1:& \quad x_2 &= -{h}/{2}\\
		\Gamma_2:& \quad x_2 &= {h}/{2}
	\end{eqnarray*}
\end{minipage}

\subsubsection{Cantilever elastic body}
Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries This is referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
\FloatBarrier
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.4mm] (0,0.5) -- (7,0.5);
		\draw[line width = 0.4mm] (0,-0.5) -- (7,-0.5);
		\draw[line width = 0.4mm] (7,-0.5) -- (7,0.5);
		\draw[line width = 0.4mm] (0,-0.5) -- (0,0.5);

		\draw[line width = 0.1mm] (0,1.5) -- (0,-1.5);

		\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.3);
		\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.1);
		\draw[line width = 0.1mm] (0,1.1) -- (-0.2,0.9);
		\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.7);
		\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.5);
		\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.3);
		\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.1);
		\draw[line width = 0.1mm] (0,0.1) -- (-0.2,-0.1);
		\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.3);
		\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.5);
		\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.7);
		\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.9);
		\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1.1);
		\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.3);
		\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.5);

		\node at (7.3,0) {$h$};
		\draw[-stealth] (7.3,0.2) -- (7.3,0.5);
		\draw (7.2,0.5) -- (7.4,0.5);
		\draw[-stealth] (7.3,-0.2) -- (7.3,-0.5);
		\draw (7.2,-0.5) -- (7.4,-0.5);

		\node at (3.5,-0.8) {$1$};
		\draw[stealth-] (0,-0.8) -- (3.3,-0.8);
		\draw[stealth-] (7,-0.8) -- (3.7,-0.8);
		\draw (7,-0.9) -- (7,-0.7);

		\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
		\draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
		\node at (9.7,0.8) {$e_1$};
		\node at (8.8,1.5) {$e_2$};

		\node at (-0.6,0) {$(0,0)$};
		\node at (0,0)[circle,fill,inner sep=1.5pt]{};

	\end{tikzpicture}
	\caption{A cantilever two-dimensional elastic body.}
\end{figure} 
\FloatBarrier

In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is defined by Problem 2D-1V. For convenience, the relevant results from section \ref{ssec:2D_Model:VariationalForm} are repeated.
\subsubsection{Problem 2D-1V}\label{sssec:2D_Model:Problem2D1VChp5}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{eq:2D_Model:Problem2D1VEqChp5}
\end{align}
for all $\phi \in T(\Omega)$.\\

With the test function space 
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
\end{eqnarray*}
The bilinear forms and integral function defined by
\begin{eqnarray}
	b(u,\phi) & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dA, \label{eq:2D_Model:BilinearChp5}\\
	c(\partial_t^2 u,\phi) & = & \int_\Omega~ (\partial^2_t u) \cdot \phi~dA, \label{eq:2D_Model:Bilinear_cChp5}\\
	(f,g) &=& \int_{\Omega} f\cdot g \ dA, \label{eq:2D_Model:Bilinear_intChp5}
\end{eqnarray}
with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.\\

Using the definition of the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten as follows.

\subsubsection{Constitutive equations:}
\begin{eqnarray}
	\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_1 u_1 + \nu \partial_2 u_2) \label{CE1} \\
	\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_2 u_2 + \nu \partial_1 u_1) \label{CE2} \\
	\sigma_{12} & = & \frac{1}{2\gamma(1+\nu)}(\partial_1 u_2 + \partial_2 u_1) \label{CE3}
\end{eqnarray}

\subsubsection{Bilinear form:}
\begin{align}
	b(u,\phi) & = & \frac{1}{\gamma(1-\nu^2)}\int_{\Omega} (\partial_1 u_1 \partial_1 \phi_1 + \partial_2 u_2 \partial _2 \phi_2 + \nu\partial_1 u_1 \partial_2\phi_2 + \nu \partial_2 u_2 \partial_1 \phi_1 ) \ dA \nonumber\\
	& + & \frac{1}{2\gamma(1+\nu)}\int_{\Omega} (\partial_1 u_2 \partial_1 \phi_2 + \partial_1 u_2 \partial_2 \phi_1 + \partial_2 u_1 \partial_1\phi_2 + \partial_2 u_1 \partial_2\phi_1) \ dA.
\end{align}

This form of the bilinear form $b$ is more useful than the general form in \eqref{eq:2D_Model:BilinearChp5} to apply the Finite Element Method.

\subsection{Weak variational form}
Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)$. Denote $X = L^2(0,1)\times L^2(0,1)$. The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.

\subsubsection{Problem 2D-1WV}
Find a function $u$ such that $\forall \ t > 0$, $u \in V$ with $\partial_t^2 u \in W$ and
\begin{eqnarray*}
	c(u,v) + b(u,v) & = & (Q,v)
\end{eqnarray*}
for all $v\in V$.

\subsection{Galerkin approximation}\label{2d_FEM_G}
Divide the reference configuration $\Omega$ into a rectangular grid of elements, such that there are $n = n_1\times n_2$ nodes.\\

Define a set of $n$-dimensional linear independent basis functions. For the two dimensional model, the basis functions can be defined by the set $$\left\{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \right\}.$$ For this dissertation, we use bi-cubic functions $\phi_i$, however simpler bi-linear functions can also be used. For easier notation, denote each of these basis functions by $\delta_i$.\\

The functions in this set that satisfies the conditions of the test function space $T(\Omega)$ are called the admissible basis functions. The admissible basis functions for this model can be renumbered and expressed as the set $\left \{\delta_1, \delta_2,..., \delta_k \right\}$ for some $k \leq 2n$.\\

Define the space
\begin{eqnarray*}
S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right)
\end{eqnarray*}

For each function $u^h \in S^h$, $u^h$ can be expressed as
\begin{eqnarray*}
	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x)
\end{eqnarray*}

Problem 2D-1V can now be rewritten into a Galerkin Approximation, denoted by Problem 2D-1G.

\subsubsection{Problem 2D-1G}
Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
\begin{eqnarray*}
	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I \cdot \phi_i)
\end{eqnarray*} for $i = 1,2,...,k$.\\

\textbf{Remarks:}
\begin{itemize}
	\item[] $Q^I$ is scalar vector that is the result of interpolating the function $Q$ over the rectangular grid. i.e. $Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.
\end{itemize}

\subsection{System of differential equations}\label{ssec:2DFEM:DE}

Consider the following standard Finite Element Method matrices
\subsubsection{FEM matrices}
\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\mathbf{M}_{j,i} & = & \int_{\Omega} \phi_i \phi_j ~dA \\
		\mathbf{{K}_{11}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_1\phi_j~dA\\
		\mathbf{{K}_{22}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_2\phi_j~dA
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\mathbf{{K}_{12}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_1\phi_j~dA\\
		\mathbf{{K}_{21}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_2\phi_j~dA
	\end{eqnarray*}
\end{minipage}
for $i,j = 1,2,...,k$.\\

And 
\begin{eqnarray*}
	{M_{F}}_{j,i} = \int_{\Omega}  \phi_i \phi_j~dA
\end{eqnarray*} for $i = 1,2,...,k$ and for $j =1,2,...,2n$.\\

Define the following matrices:
\begin{eqnarray*}
	K_1 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{11}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{22}} \label{eq:2DFEM:K1} \\
	K_2 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{21}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{12}}\label{eq:2DFEM:K2}\\
	K_3 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{12}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{21}}\label{eq:2DFEM:K3}\\
	K_4 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{22}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{11}}\label{eq:2DFEM:K4}
\end{eqnarray*}

Using the standard FEM matrices and matrices $K_1$-$K_4$, the following concatenated matrices are defined.
\begin{eqnarray}
	\begin{aligned}
		K = 
		\begin{bmatrix}
			K1 & K2\\
			K3 & K4
		\end{bmatrix}
	\end{aligned}
	\ \ \ \ \ \ \ \ \
	\begin{aligned}
		M_f = 
		\begin{bmatrix}
			M_{F} & O_{F}\\
			O_{F} & M_{F}
		\end{bmatrix}
	\end{aligned}\label{eq:2DFEM:K+M}
\end{eqnarray}

\begin{eqnarray}
	M = 
	\begin{bmatrix}
		\mathbf{M} & O \\
		O & \mathbf{M}
	\end{bmatrix}\label{eq:2DFEM:M}
\end{eqnarray}

The matrices ${O}$ and ${O_f}$ are the zero matrices of the same size as $\mathbf{M}$ and ${M_f}$ respectively.\\

Using \eqref{eq:2DFEM:K+M} and \eqref{eq:2DFEM:M}, Problem 2D-1G is rewritten as a system of ordinary differential equations. This system is referred to as Problem 2D-1ODE.

\subsubsection{Problem 2D-1ODE}
Find a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	M\ddot{\bar{u}} & = & K\bar{u} + M_{f}Q^I.
\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \langle u, \partial_1 u, \partial_2 u, \partial_{12} u \rangle$.

\subsubsection{Remark}
This form of $\bar{u}$ is determined by the Hermite cubic basis functions.

\subsection{Eigenvalue problem}\label{2dFEM_EP}
For the eigenvalue problem, assume that $M_{f}Q^I = 0$ so that 
\begin{eqnarray}
		M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
\end{eqnarray}
It is known that a system of ordinary differential equations have a general solution of the form $e^{rt}$. Suppose that $\bar{w} = e^{\lambda t} \bar{u}$ is a solution for \eqref{eq:2DFEM:M2}. In this solution, $\lambda$ is an eigenvalue and $\bar{u}$ a corresponding eigenfunction. Substitution into \eqref{eq:2DFEM:M2} results in
\begin{eqnarray*}
	M\lambda e^{\lambda t}\bar{u} & = & Ke^{\lambda t}\bar{u}.
\end{eqnarray*}
Since $e^{\lambda t} > 0$ for all values of $\lambda t$, we can cancel it from both sides of the equation and formulate the eigenvalue problem Problem 2D-1E.

\subsubsection{Problem 2D-1E}
Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	M\lambda{\bar{u}} & = & K\bar{u}.
\end{eqnarray}

Now the eigenvalue problem can be solve using a finite difference method.

\end{document}

Divide the reference configuration $\Omega$ into $n_1\times n_2$ nodes in a rectangular grid.\\

Consider a set of 
For this dissertation, we consider bi-cubic basis functions, however bi-linear basis functions can also be used.

Consider a $n$-dimensional set of linearly independent two-dimensional scalar valued functions, denoted $\delta_i$. In this dissertation, these functions are chosen as bi-cubic functions, however simpler bi-linear functions can also be used.\\

The functions in the set that satisfies the conditions of the test function space $T(\Omega)$ are called the admissible basis functions. Number these admissible basis functions $\delta_1, \delta_2,...,\delta_k$ for some $k \leq n$.

Let $S^h$ be a $2k$-dimensional subset of $T(\Omega)$ such that
\begin{eqnarray*}
	S^h & = & \textrm{span}\left \{[\delta_1 \ 0], [\delta_2 \ 0],...,[\delta_k \ 0],[0 \ \delta_1],[0 \ \delta_2],...,[0 \ \delta_k] \right\}.
\end{eqnarray*}

Let $S^h$ be a $2k$-dimensional subset of $T(\Omega)$ such that
\begin{eqnarray*}
	S^h & = & \textrm{span}\left \{[\delta_1 \ 0], [\delta_2 \ 0],...,[\delta_k \ 0],[0 \ \delta_1],[0 \ \delta_2],...,[0 \ \delta_k] \right\}.
\end{eqnarray*}

he body $\Omega$ is divided into an $n_1\times n_2$ rectangular grid. Let $x_i^* = \langle x_1, x_2 \rangle \in \Omega$ where $\delta_{i}(x_1,x_2) = 1$. Define $\bar{x} = \langle x_1^*, x_2^*,...,x_k^* \rangle$. For each solution $u$ of Problem 2D-1V let $u^h$ denote the projection of $u$ into the finite dimensional space $S^h$. Each function $u^h=\langle u_1^h,u_2^h\rangle$ in S$^h$ can be expressed as
\begin{eqnarray*}
	u_1^h(\bar{x},t) = \sum_{i = 1}^{k} u_{1}(x_i^*,t) \delta_{i}(\bar{x}) \ \ \textrm{ and } \ u_2^h(\bar{x},t) = \sum_{i = 1}^{k} u_{2}(x_i^*,t) \delta_{i}(\bar{x}).
\end{eqnarray*}

### 2022-10-31 files/Chapter6/3D_FEM.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}

\section{Three-dimensional elastic model}\label{sec:FEM:3D}
Consider a three-dimensional cantilever elastic body, with a rectangular cross-section.

\subsubsection{Reference configuration for rectangular cross-section}
Let $\{e_1,e_2,e_3\}$ be a right-handed orthonormal basis for $R^3$. Denote the elastic body as $\Omega \in R^3$ with $(0,0,0)$ the reference point. For a rectangular cross-section, $\Omega$ can be described as
\begin{eqnarray*}
	\Omega = \left\{ x \in R^3 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} , \ -\frac{b}{2} \leq x_3 \leq \frac{b}{2}\right \}
\end{eqnarray*}
Let $\partial \Omega$ denote the boundary of the body. Divide $\partial \Omega$ into the six distinct flat surfaces as follows:

\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\Sigma_0:& \quad x_1 &= 0\\
		\Sigma_1:& \quad x_1 &= 1\\
		\Gamma_1:& \quad x_3 &= -{b}/{2} 
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\Gamma_2:& \quad x_2 &= -{h}/{2}\\
		\Gamma_3:& \quad x_3 &= {b}/{2}\\
		\Gamma_4:& \quad x_2 &= {h}/{2} 
	\end{eqnarray*}
\end{minipage}

\subsubsection{Cantilever elastic body}
Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma_0$ and free-hanging at all the other sides. This is referred to as Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.
\FloatBarrier
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.4mm] (-0.5,1) -- (6.5,1);
		\draw[line width = 0.4mm] (-0.5,-1) -- (6.5,-1);
		\draw[line width = 0.4mm] (6.5,-1) -- (6.5,1);
		\draw[line width = 0.4mm] (-0.5,-1) -- (-0.5,1);

		\draw[line width = 0.4mm] (0.5,1.5) -- (7.5,1.5);
		\draw[line width = 0.4mm] (7.5,-0.5) -- (7.5,1.5);

		\draw[line width = 0.4mm] (-0.5,1) -- (0.5,1.5);
		\draw[line width = 0.4mm] (6.5,1) -- (7.5,1.5);
		\draw[line width = 0.4mm] (6.5,-1) -- (7.5,-0.5);

		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+4});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+2.5});

		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+2});
		\draw[scale=0.5, domain=2:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+2});

		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+1});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+0.5});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-0.5});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-1});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-1.5});
		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-2});
		\draw[scale=0.5, domain=-3:1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-2.5});
		\draw[scale=0.5, domain=-3:2, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-4});

		%\node at (6.9,1) {$b$};
		%\node at (6.65,0) {$h$};
		%\node at (3.2,-1.2) {$\ell = 1$};

		\draw[line width = 0.1mm,->] (9,1) -- (10,1.6);
		\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
		\draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
		\node at (9.3,1.4) {$e_3$};
		\node at (9.7,0.8) {$e_1$};
		\node at (8.8,1.5) {$e_2$};

		\node at (7.7,0.5) {$h$};
		\draw[-stealth] (7.7,0.7) -- (7.7,1.5);
		\draw (7.6,1.5) -- (7.8,1.5);
		\draw[-stealth] (7.7,0.3) -- (7.7,-0.5);
		\draw (7.6,-0.5) -- (7.8,-0.5);

		\node at (3,-1.2) {$1$};
		\draw[stealth-] (-0.5,-1.2) -- (2.8,-1.2);
		\draw[stealth-] (6.5,-1.2) -- (3.2,-1.2);
		\draw (6.5,-1.3) -- (6.5,-1.1);
		\draw (-0.5,-1.3) -- (-0.5,-1.1);

		\node at (7.2,-0.9) {$b$};
		\draw[stealth-] (7.7,-0.5) -- (7.35,-0.75);
		\draw[stealth-] (6.5,-1.2) -- (7,-0.95);

		\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
		\draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
		\node at (9.7,0.8) {$e_1$};
		\node at (8.8,1.5) {$e_2$};

		\node at (-0.6,0) {$(0,0)$};
		\node at (0,0)[circle,fill,inner sep=1.5pt]{};

		%\node at (-1.4,-1.3) {$(0,-\frac{h}{2},-\frac{b}{2})$};
		%\node at (-1.4,1) {$(0,\frac{h}{2},-\frac{b}{2})$};
		%\node at (0.5,1.8) {$(0,\frac{h}{2},\frac{b}{2})$};

		%\node at (6,-1.3) {$(1,-\frac{h}{2},-\frac{b}{2})$};
		%\node at (6.3,0.7) {$(1,\frac{h}{2},-\frac{b}{2})$};
		%\node at (7.5,1.8) {$(1,\frac{h}{2},\frac{b}{2})$};
		%\node at (8.4,-0.4) {$(1,-\frac{h}{2},\frac{b}{2})$};

	\end{tikzpicture}
	\caption{Cantilever Three-Dimensional Elastic Body with Rectangular Cross-Section.}
\end{figure} 
\FloatBarrier

In section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3D-1V. For convenience, the relevant results from section \ref{ssec:3D_Model:VariationalForm} are repeated.

\subsubsection{Problem 3D-1V}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
\begin{align}
	c(u,\phi) = -b(u,\phi) - (Q,\phi) \label{3DB_20}
\end{align}
for all $\phi \in T(\Omega)$.\\

With the test function space
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C(\Omega) \ | \ \phi = 0 \ \textrm{ on } \ \Sigma_0 \right\}.
\end{eqnarray*}

The bilinear forms and integral function are defined by
\begin{eqnarray}
	b(u,\phi) &=& \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dV,\\
	c(u,\phi) &=& \int_\Omega~ (\partial^2_t u) \cdot \phi~dV, \\
	(f,g) &=& \int_{\Omega} f\cdot g \ dV, \\
\end{eqnarray}
with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.\\

Using the definition of the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten as follows.
\subsubsection*{Constitutive equations}
\begin{eqnarray*}
	\sigma_{11} & = &  \frac{1}{\gamma(1+\nu)}\partial_1 u_1 + \frac{\nu}{\gamma (1+\nu)(1-2\nu)}(\partial_1 u_1 +  \partial_2 u_2 + \partial_3 u_3)\label{3DB_3}\\
	\sigma_{22} & = &  \frac{1}{\gamma(1+\nu)}\partial_2 u_2 + \frac{\nu}{\gamma (1+\nu)(1-2\nu)}(\partial_1 u_1 +  \partial_2 u_2 + \partial_3 u_3)\label{3DB_4}\\
	\sigma_{33} & = &  \frac{1}{\gamma(1+\nu)}\partial_3 u_3 + \frac{\nu}{\gamma (1+\nu)(1-2\nu)}(\partial_1 u_1 +  \partial_2 u_2 + \partial_3 u_3)\label{3DB_5}\\
	\sigma_{23} & = &  \frac{1}{2\gamma(1+\nu)}(\partial_3 u_2 + \partial_2 u_3)\label{3DB_6}\\
	\sigma_{31} & = &  \frac{1}{2\gamma(1+\nu)}(\partial_3 u_1 + \partial_1 u_3)\label{3DB_7}\\
	\sigma_{12} & = &  \frac{1}{2\gamma(1+\nu)}(\partial_2 u_1 + \partial_1 u_2)\label{3DB_8}
\end{eqnarray*}

\subsubsection{Bilinear Form}
\begin{align*}
	b(u,\phi)  &=  \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dV \nonumber\\
	 &=  \int_{\Omega} \sigma_{11} \partial_1\phi_1 + \sigma_{12}\partial_1 \phi_2 + \sigma_{13}\partial_1 \phi_3 + \sigma_{21}\partial_2 \phi_1 + \sigma_{22}\partial_2\phi_2 + \sigma_{23}\partial_2 \phi_3 ~dV
\end{align*}

In this form, the bilinear form $b$ is more useful for applications than the general form.

\subsection{Weak variational form}

\subsubsection{Bilinear form}
Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)\times H^1(0,1)$. Denote $X = L^2(0,1)\times L^2(0,1)\times L^2(0,1)$. The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.

\subsubsection{Problem 3D-1W}
Find a function $u$ such that for all $t>0$, $u(t) \in V$ and $u''(t) \in W$, satisfying the following equation
\begin{eqnarray}
	c(u,v) + b(u,v) & = & (Q,v) \ \ \ \textrm{ for each } v \in V.
\end{eqnarray}

\subsection{Galerkin approximation}
Divide the reference configuration $\Omega$ into a grid of rectangular prismatic elements, such that there are $n = n_1 \times n_2 \times n_3$ nodes. These rectangular prismatic elements are also known as brick shaped elements as described by \cite{Wu06}. This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.\\

Define a set of $n$-dimensional linear independent basis functions. For the three-dimensional model, the basis functions can be defined by the set
\begin{eqnarray*}
 \{\langle\phi_1, 0 , 0\rangle, \langle\phi_2, 0, 0\rangle,...,\langle\phi_{n}, 0, 0 \rangle,\\
	\langle 0,\phi_1 ,0 \rangle,\langle 0 ,\phi_2,0\rangle,...,\langle 0,\phi_{n},0\rangle,\\
	\langle 0,0,\phi_1 \rangle,\langle 0,0,\phi_2\rangle,...,\langle 0,0,\phi_{n}\rangle \}.
\end{eqnarray*}

For this dissertation, we use tri-cubic functions $\phi_i$. For a simplification, tri-linear functions can also be used instead. For easier notation, denote each of the basis functions in the set by $\delta_i$.\\

The functions that satisfy the conditions of the test function space $T(\Omega)$ are called the admissible basis functions. The admissible basis functions for this model can be renumbered and expressed as the set $\left\{\delta_1, \delta_2, ..., \delta_k \right\}$ for some $k \leq 3n$.\\

Define the space
\begin{eqnarray*}
	S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right)
\end{eqnarray*}

For each function $u^h \in S^h$, $u^h$ can be expressed as
\begin{eqnarray*}
	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x)
\end{eqnarray*}

Problem 3D-1V can now be rewritten into a Galerkin Approximation, denoted by Problem 3D-1G.

\subsubsection{Problem 3D-1G}
Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
\begin{eqnarray*}
	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I \cdot \phi_i)
\end{eqnarray*} for $i = 1,2,...,k$.\\

\subsection{System of ordinary differential equations}
Consider the following standard Finite Element Method matrices.

\subsubsection{FEM matrices}
\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\mathbf{M}_{ij} & = & \int_{\Omega} \phi_j \phi_i \ dV \ \\
		{K_{11}}_{ij} & = & \int_{\Omega} \partial_1\phi_j \partial_1\phi_i \ dV \  \\
		{K_{12}}_{ij} & = & \int_{\Omega} \partial_1\phi_j \partial_2\phi_i \ dV \ \\
		{K_{13}}_{ij} & = & \int_{\Omega} \partial_1\phi_j \partial_3\phi_i \ dV \ 
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		{K_{22}}_{ij} & = & \int_{\Omega} \partial_2\phi_j \partial_2\phi_i \ dV \  \\
		{K_{23}}_{ij} & = & \int_{\Omega} \partial_2\phi_j \partial_3\phi_i \ dV \ \\
		{K_{33}}_{ij} & = & \int_{\Omega} \partial_3\phi_j \partial_3\phi_i \ dV \ \\
	\end{eqnarray*}
\end{minipage}
for $i,j = 1,2,...,k.$\\

And

\begin{eqnarray*}
	\mathbf{M_f}_{ij} & = & \int_{\Omega} \phi_j \phi_i \ dV
\end{eqnarray*}
for $i = 1,2,...,k$ and for $j = 1,2,...,3n.$\\

The remaining matrices can be defined as
\begin{eqnarray*}
	{K_{21}} & = & {K_{12}}^{T},\\
	{K_{31}} & = & {K_{13}}^{T}, \\
	{K_{32}} & = & {K_{23}}^{T}. \\
\end{eqnarray*}

Define the following matrices:\\
\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\mathbf{K11} & = & \left(C_1 + C_2 \right) K_{11} + C_3 K_{22} + C_3 K_{33}\\
		\mathbf{K12} & = & C_3 K_{12} + C_2 K_{21}\\
		\mathbf{K13} & = & C_3 K_{13} + C_2 K_{31}\\
		\mathbf{K21} & = & C_3 K_{21} + C_2 K_{12}\\
		\mathbf{K22} & = & \left(C_1 + C_2 \right) K_{22} + C_3 K_{11} + C_3 K_{33}
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{0.8\linewidth}
	\begin{eqnarray*}
		\mathbf{K23} & = & C_3 K_{23} + C_2 K_{32}\\
		\mathbf{K31} & = & C_3 K_{31} + C_2 K_{13}\\
		\mathbf{K32} & = & C_3 K_{32} + C_2 K_{23}\\
		\mathbf{K33} & = & \left(C_1 + C_3 \right) K_{33} + C_3 K_{11} + C_3 K_{22}
	\end{eqnarray*}
\end{minipage}\\

with $C_1 = \frac{1}{\gamma(1+\nu)}$, $C_2 =  \frac{\nu}{\gamma (1+\nu)(1-2\nu)}$ and $C_3 =  \frac{1}{2\gamma(1-2\nu)}$.\\

Using the standard FEM matrices and the matrices $K11$ to $K33$, the following concatenated matrices are defined:\\

\begin{eqnarray}
	\begin{aligned}
		K = 
		\begin{bmatrix}
			\mathbf{K11} & \mathbf{K12} & \mathbf{K13}\\
			\mathbf{K21} & \mathbf{K22} & \mathbf{K23}\\
			\mathbf{K31} & \mathbf{K32} & \mathbf{K33}
		\end{bmatrix}
	\end{aligned}
	\ \ \ \ \ \ \ \ \
	\begin{aligned}
		M  = 
		\begin{bmatrix}
			\mathbf{M} & {O} & {O}\\
			{O} & \mathbf{M} & {O}\\
			{O} & {O} & \mathbf{M}
		\end{bmatrix}
	\end{aligned}\label{eq:3DFEM:K+M}
\end{eqnarray}

\begin{eqnarray}
	M_f & = &
	\begin{bmatrix}
		\mathbf{M_f} & {O_f} & {O_f}\\
		{O_f} & \mathbf{M_f} & {O_f}\\
		{O_f} & {O_f} & \mathbf{M_f}
	\end{bmatrix}\label{eq:3DFEM:M}
\end{eqnarray}
The matrices ${O}$ and ${O_f}$ are the zero matrices of the same size as $\mathbf{M}$ and $\mathbf{M_f}$ respectively.\\

Using \eqref{eq:3DFEM:K+M} and \eqref{eq:3DFEM:M}, Problem 3D-1G is rewritten as a system of ordinary differential equations. This system is referred to as Problem 3D-1ODE

\subsubsection{Problem 3D-1ODE}
Find a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	M\ddot{\bar{u}} & = & K\bar{u} + M_{f}Q^I. \label{3D_M}
\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \langle u, \partial_1 u, \partial_2 u, \partial_3 u, \partial_{11} u, \partial_{12}u, \partial_{13}u,\partial_{22}u,\partial_{23}u, \partial_{33}u,$\\$ \partial_{111}u, \partial_{112}u, \partial_{113}u, \partial_{121}u, \partial_{122}u, \partial_{123}u, \partial_{133}u,\partial_{223}u,\partial_{233}u,\partial_{333}u \rangle$. \textcolor{red}{beter manier om voor te stel?}

\subsection{Eigenvalue problem}
The equation \eqref{3D_M} is the same form as in section \ref{2dFEM_EP} for the two-dimensional elastic body. Therefore the derivation of the eigenvalue problem is identical. Denote the eigenvalue problem for Problem 3D-1 by Problem 3D-1E.

\subsubsection{Problem 3D-1E}
Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	M\lambda{\bar{u}} & = & K\bar{u}.
\end{eqnarray}
\end{document}

Consider a set of $n$ linear independent three-dimensional scalar valued functions $\delta_i$. In this dissertation, these functions are tri-cubic basis functions (an extension of Hermite cubics from the two-dimensional model into three-dimensions). The functions $\delta_i$ satisfying the conditions of the test function space $T(\Omega)$ are called the admissible basis functions. Since there are a finite number if admissible basis functions, they can be numbered $\delta_1, \delta_2,...,\delta_k$.\\

Let $S^h$ be a $3k$-dimensional subset of $T(\Omega)$ where
\begin{eqnarray*}
	S^h & = & \textrm{span}(\left\{\langle \delta_i, 0,  0\rangle \ | \ i = 1,2,...,p \right\} \cup \left\{\langle 0, \delta_i, 0\rangle \ | \ i = 1,2,...,p \right\}\\
	&& \quad \quad \quad \quad \quad  \cup \left\{\langle 0, 0, \delta_i\rangle \ | \ i = 1,2,...,p \right\} ).
\end{eqnarray*}

The body $\Omega$ is divided into an $n_1 \times n_2 \times n_3$ grid consisting of rectangular prism shaped elements. This is described as ``bricked-shaped'' elements in [WuXX]. Let $x^*_i = \langle x_1,x_2,x_3\rangle \in \Omega$ where $\delta_i(x_1,x_2,x_3) = 1$. Define $\bar{x} = \langle x_1^*,x_2^*,...,x_k^* \rangle$.  For each solution $u$ of Problem 3D-1V let $u^h$ denote the projection of $u$ into the finite dimensional space $S^h$. Each function $u^h=\langle u_1^h,u_2^h,u_3^h\rangle$ in S$^h$ can be expressed as
\begin{eqnarray*}
	w_1^h(\bar{x},t) = \sum_{i = 1}^{p} w_{1}(x_i^*,t) \delta_{i}(\bar{x}), \ \ \ w_2^h(\bar{x},t) = \sum_{i = 1}^{p} w_{2}(x_i^*,t) \delta_{i}(\bar{x})\\
	\ \ \   \textrm{ and }  w_3^h(\bar{x},t) = \sum_{i = 1}^{p} w_{3}(x_i^*,t) \delta_{i}(\bar{x}).
\end{eqnarray*}

Then Problem 3D-1V can be rewritten into a Galerkin Approximation, denoted by Problem 3D-1G

### 2022-10-31 files/Chapter7/Beam-Main_Rig_2.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of the Timoshenko beam model}
This section is a literature study of the article \cite{LVV09}. The goal of the authors is to show that for practical applications, the solution of the Timoshenko beam model is close to the solution of a two-dimensional beam model. This is referred to as the validity of the Timoshenko beam model in this dissertation.\\

For practical applications, it would be preferred to compare the Timoshenko beam model to a more realistic three-dimensional model. But the authors of \cite{LVV09} explain that this will introduce complexities. \textcolor{red}{What complexities?} To mitigate some of the complexities, the two-dimensional model is used as an intermediate step.\\

Where \cite{LVV09} differs from most other research, is that the boundary conditions are also taken into consideration. The authors of \cite{LVV09} use a cantilever beam configuration for their investigation.\\

To compare the two models, the authors compare the natural frequencies of the models. From modal analysis, it is known that a solution of a second order hyperbolic type problem is a linear combination of the eigenvalues and eigenfunctions of the model. Therefore it is sufficient to compare the eigenvalues and eigenfunctions to determine the validity of the different dimensional models.\\

\subsection{The models}
Consider the cantilever Timoshenko beam model problem Problem T-2 from section \ref{ssec:1D_Model:ModelProblems} and the cantilever two-dimensional beam model problem Problem 2D-1 from section \ref{ssec:2D_Model:ModelProblem}.\\

Figure 6.1 shows the two beams side-by-side for a visual guide.

\begin{figure}[h!]\label{fig:compare:1D+2D}
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\caption{Side by side comparison of the beams.}
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\begin{center}
					\begin{tikzpicture}
					\draw[line width = 0.4mm] (0,0) -- (6,0);

					\node at (2.7,-0.25) {$\ell = 1$};

					\draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
					\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
					\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
					\draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
					\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
					\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
					\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
					\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
					\draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);

					\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
					\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
					\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
					\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
					\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
					\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
					\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
					\draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);

					%\node at (3.2,-0.2) {$\ell = 1$};
					\end{tikzpicture}
				\end{center}
				\subcaption{Timoshenko Cantilever Beam}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\begin{center}
					\begin{tikzpicture}
						\draw[line width = 0.4mm] (0,0.2) -- (6,0.2);
						\draw[line width = 0.4mm] (0,-0.2) -- (6,-0.2);
						\draw[line width = 0.4mm] (6,-0.2) -- (6,0.2);
						%\draw[line width = 0.4mm] (0,-0.2) -- (0,0.2);

						%\draw[line width = 0.1mm,->] (6,2) -- (7.4,2);
						%\draw[line width = 0.1mm,->] (6,2) -- (6,0.9);
						%\node at (6.7,1.8) {$e_1$};
						%\node at (5.8,1.4) {$e_2$};

						\node at (6.2,0) {$h$};
						\node at (2.7,-0.45) {$\ell = 1$};

						\draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
						\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
						\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
						\draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
						\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
						\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
						\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
						\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
						\draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);

						\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
						\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
						\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
						\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
						\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
						\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
						\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
						\draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);

						%\node at (3.2,-0.3) {$\ell = 1$};

					\end{tikzpicture}
				\end{center}
				\subcaption{Two-Dimensional Cantilever Beam}
			\end{minipage}
		}
	}
\end{figure}

The parameter $h$ is the height of the two-dimensional beam. Recall the dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ from section \ref{sssec:1D_Model:DimensionlessForm}. For the Timoshenko beam model with a rectangular cross-section, the area moment of inertial is 
\begin{eqnarray*}
	I = \frac{h^3b}{12}.
\end{eqnarray*}

After substitution, the following relation ship between $\alpha$ and $h$ is found
\begin{eqnarray*}
	h = \sqrt{\frac{12}{\alpha}}.
\end{eqnarray*}
The parameter $\alpha$ can be chosen in such a way that the beams have equal dimensions.

\subsection{Accuracy of the numerical eigenvalues}
For the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} reference an another article \cite{VV06}. In this article \cite{VV06}, a method is described to obtain the eigenvalues and eigenfunctions of a (cantilever) Timoshenko beam. This method also allows for the eigenvalues to be obtained to a desired level of accuracy (using a numerical method such as interval division). In this dissertation, \cite{VV06} is discussed in section \ref{sec:Timo:EigenvalueProblem}.\\

For the two-dimensional beam, the Finite Element Method is used to calculate the eigenvalues and eigenfunctions. In \cite{LVV09} the authors used piecewise bi-cubic basis functions and a grid size large enough to ensure that the eigenvalues are accurate to 3 significant digits.\\

\begin{figure}[H]
	\begin{center}
		\scalebox{1.4}{
			\includegraphics[scale=0.4]{Convergence.png}
			\caption{Maximum relative error of the first 10 eigenvalues of the two-dimensional beam.}
			\label{fig:conv}
		}
	\end{center}	
\end{figure}

Figure \ref{fig:conv} show the maximum relative error of the first 10 eigenvalues of the two-dimensional beam. In \cite{LVV09}, the authors use a grid size of $40 \times 10$ with $h= 1/10$ (or $\alpha = 1200$) and $h = 1/5$ (or $\alpha = 300$).\\

 Figure \ref{fig:conv} show that this can be improved significantly. For each case of $h$, the grid size is calculated as $n \times \max\left\{\lceil\frac{n}{h}\rceil,10\right\}$. This ensures that the nodes are distributed somewhat evenly relative to the length-width ratio. For this chapter, the results of the Timoshenko beam and two-dimensional beam are given accurate up to 5 significant digits.

\subsection{Comparing the shape of the eigenfunctions}
Before the eigenvalues of the beams can be compared, a method is required to be able to match the eigenvalues. In \cite{LVV09} the authors compare the modal shapes of the Timoshenko beam model to the modal shapes of the two-dimensional model.\\

Similar modal shapes implies that the eigenvalues can be matched up and compared. Eigenvalues relating to the shapes of the Timoshenko beams modes are called beam-type eigenvalues by \cite{LLV09}.

\subsubsection{Shapes relating to beam-type eigenvalues}
The following are examples of beam-type mode shapes for the displacement $w$ for the cantilever two-dimensional beam and cantilever Timoshenko beam. The figures are presented side-by-side.

\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{Beam1.jpg}
				\subcaption{2D Beam Type - $\lambda_6 = 21.911$}
				\label{fig:minipage2}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{1DBeam2.png}
				\subcaption{Timoshenko - $\lambda_5 = 21.794$}
				\label{fig:minipage1}
			\end{minipage}
	}}
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{Beam2.jpg}
				\subcaption{2D Beam Type - $\lambda_7 = 45.711$}
				\label{fig:minipage2}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{1DBeam1.png}
				\subcaption{Timoshenko - $\lambda_6 = 45.390$}
				\label{fig:minipage1}
			\end{minipage}
			\caption{Modal shapes of the displacement $w$ for the beam-type 2D body and the Timoshenko beam with $\alpha = 4800$ ($h = 1/20$).}
		}
	}
\end{figure}
\FloatBarrier

\subsubsection{Shapes relating to non-beam type eigenvalues}
The following are examples of non beam-type mode shapes for the displacement $w$ of the cantilever two-dimensional beam.
\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{NotBeam1.jpg}
				\subcaption{Non-Beam Type - $\lambda_4 = 7.7077$}
				\label{fig:minipage2}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{NotBeam2.jpg}
				\subcaption{Non-Beam Type - $\lambda_8 = 69.344$}
				\label{fig:minipage1}
			\end{minipage}
			\caption{Modal shapes of the displacement $w$ for the non-beam type 2D body with $h = 1/20$.}
		}
	}
\end{figure}
\FloatBarrier

Using this method all the relevant eigenvalues in this section were matched. The non-beam type eigenvalues are highlighted in gray in the tables.

\subsubsection{Shapes of the cross-section}
The Timoshenko beam theory differs from other one-dimensional beam theories by also including shear. It is assumed that the cross-sections need not remain perpendicular to the neutral axis of the beam. The cross-sections remain straight.\\

For the two-dimensional body, the shape of the cross-section of beam type eigenfunctions can deform into an a s-shape. Figure \ref{fig:s} shows an exaggerated representation of the s-shaped deformation. This is also given and explained in \cite{LVV09}.
\FloatBarrier
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}[scale=1.2]

	\draw[line width = 0.4mm] (0,1) -- (7,1);
	\draw[line width = 0.4mm] (0,-1) -- (7,-1);
	\draw[line width = 0.4mm] (7,-1) -- (7,1);
	\draw[line width = 0.4mm] (0,-1) -- (0,1);

	\draw[line width = 0.1mm,dashed] (3.5,1) -- (3.5,-1);

	\draw[thick] plot [smooth,tension=0.9] coordinates{(3.3,1) (3.7,0.5) (3.5,0) (3.3,-0.5) (3.7,-1)};

	\draw[line width = 0.2mm,red] (3.3,1) -- (3.7,-1);

\end{tikzpicture}
	\caption{S-shape deformation and average rotation.}\label{fig:s}
\end{figure}
The red line in figure \ref{fig:s} show how the average rotation of the cross-section is calculated in \cite{LVV09}.
\FloatBarrier

\subsubsection{Direct comparison of mode shapes}
Figure \ref{fig:w} shows the displacement $w$ of the cantilever Timoshenko beam and the cantilever two-dimensional beam directly compared.

\begin{figure}[ht!]
	\scalebox{.8}{
		\makebox[\textwidth]{
			\centering
			\centering
			\includegraphics[scale=0.4]{1Dv2D.png}
			\caption{Comparison of the displacement $w$ mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
			\label{fig:w}}}
\end{figure}
\FloatBarrier

Similarly Figure \ref{fig:phi} shows the direct comparison of the angle of the cross-section of the cantilever Timoshenko beam and the two-dimensional beam. The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s}.

\FloatBarrier
\begin{figure}[ht!]
	\scalebox{.8}{
		\makebox[\textwidth]{
			\centering
			\centering
			\includegraphics[scale=0.4]{1Dv2Dphi.png}
			\caption{Comparison of the angle $\phi$ (best fit for 2D Beam) mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
			\label{fig:phi}}}
\end{figure}
\FloatBarrier

Figures \ref{fig:w} and \ref{fig:phi} show that for $\alpha = 4800$, the mode shapes are very close, even for the eigenvalues 8 (for Timoshenko beam) and 10 (for the two-dimensional beam). The authors of \cite{LVV09} obtained similar results for $\alpha = 300$ for the eigenvalues 6 (for Timoshenko beam) and 9 (for the two-dimensional beam). Therefore a direct comparison of the mode shapes are feasible for short and long beams.

\subsubsection{Remark}
Due to the fact that any multiple of an eigenfunction is still an eigenfunction, the figures can be scaled. This is why no scale is indicated on the y-axis in \cite{LVV09}. Figures \ref{fig:w} and \ref{fig:phi} were scaled by eye.

\subsection{Comparing the eigenvalues}
\subsubsection{Results of [LVV09]}
The following table contains the results form \cite{LVV09} as well as the corresponding results obtained in this dissertation.
\begin{table}[!ht]
	\centering
	\caption{Results from [LVV09] and results obtained in this dissertation. $0^a$ indicates a 0 as a result of rounding. $\alpha = 1200$}
	\begin{tabular}{|c|c|c|c||c|c|c|c|}
		\hline
		\multicolumn{4}{|c||}{Results from [LVV09]} & \multicolumn{4}{c|}{Dissertation} \\ \hline \hline
		~ & 2D & Timo & RE & ~ & 2D & Timo & RE  \\ \hline
		1 & 0.0317 & 0.0316 & 0.00315 & 1 & 0.031713 & 0.031639 & 0.0023407  \\ 
		2 & 1.14 & 1.14 & $0^a$ & 2 & 1.1413 & 1.1365 &  0.0042050 \\ 
		3 & 7.72 & - & ~ & 3 & 7.7161 & - &   \\ 
		4 & 7.92 & 7.86 & 0.00758 & 4 & 7.918 & 7.8617 & 0.0071116    \\ 
		5 & 26.2 & 25.9 & 0.0115 & 5 & 26.148 & 25.869 & 0.010669  \\ 
		6 & 60.8 & 59.9 & 0.0148 & 6 & 60.816 & 59.946 & 0.014303  \\ 
		7 & 69.3 & - & ~ & 7 & 69.344 & - &    \\ 
		8 & 115 & 113 & 0.0174 & 8 & 115.28 & 113.23 &  0.017787  \\ 
		9 & 192 & 188 & 0.0208 & 9 & 191.57 & 187.55 &  0.020999  \\ 
		10 & 192 & - &  & 10 & 192.03 & - &   \\ 
		11 & 291 & 284 & 0.0241 & 11 & 290.76 & 283.81 &  0.023899  \\ \hline
	\end{tabular}\label{Results_LVV09}
\end{table}

In Table \ref{Results_LVV09}, the results from \cite{LVV09} and the respective results from this dissertation is given. This table shows that the results of \cite{LVV09} can be replicated with more significant digits.\\

Interestingly, with the improved accuracy over \cite{LVV09}, the relative errors remain similar in Table \ref{Results_LVV09}. It is possible that the higher level of accuracy will only benefit larger eigenvalues. Larger eigenvalues are however not of interest for practical applications. The 2nd relative error of \cite{LVV09} however could not be duplicated.

\subsection{Comparison of the eigenvalues}
In \cite{LVV09}, two values for $\alpha$ are considered. For $\alpha = 1200$, the Timoshenko beam has a length to width ratio of $1:10$. For $\alpha = 300$, the Timoshenko beam has length to width ratio of $1:5$. These two values represent a ``long slender'' beam and a ``short'' beam.\\

In Table \ref{tab:Timo}, the eigenvalues of the Timoshenko beam are compared to the first 20 eigenvalues of the two-dimensional beam. The eigenvalues are calculated for different values of $\alpha$.\\

\begin{table}[h!]
	\scalebox{.8}{
	\makebox[\textwidth]{
	\caption{Eigenvalues of a Timoshenko cantilever beam vs the eigenvalues of a cantilever two-dimensional elastic body. RE - Relative Error}
	\begin{tabular}{|cccc||cccc||cccc||cccc|}
		\hline
		\multicolumn{16}{|c|}{Comparison of Eigenvalues} \\
		\hline\hline
		\multicolumn{4}{|c||}{ $h = 1/5$ or $\alpha = 300$}       & \multicolumn{4}{c||}{$h =1/10$ or $\alpha = 1200$}      & \multicolumn{4}{c||}{$h = 1/20$ or $\alpha = 4800$}      & \multicolumn{4}{c|}{$h = 1/30$ or $\alpha = 10800$} \\
		\hline
		{i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} \\
		\hline
		{1}&0.12151&1&0.12092&1&0.031713&1&0.031639&1&0.008013&1&0.008004&1&0.003568&1&0.003565\\
		{2}&3.5460&2&3.5071&2&1.1413&2     & 1.1365 & 2     & 0.30756 & 2     & 0.30705 & 2     & 0.13869 & 2     & 0.13855 \\
		\cellcolor{lightgray}{3} & \cellcolor{lightgray}{7.7311} &       & {-} & \cellcolor{lightgray}{3}     & \cellcolor{lightgray}{7.7161} &       & {-} & 3     & 2.3273 & 3     & 2.3213 & 3     & 1.0698 & 3     & 1.0683 \\
		{4} & 20.225 & 3     & 19.869 & 4     & 7.9180 & 3     & 7.8617 & \cellcolor{lightgray}{4}     & \cellcolor{lightgray}{7.7077} &       & {-} & 4     & 4.0140 & 4     & 4.0058 \\
		{5} & 56.109 & 4     & 54.766 & 5     & 26.148 & 4     & 25.869 & 5     & 8.5086 & 4     & 8.4762 & \cellcolor{lightgray}{5}     & \cellcolor{lightgray}{7.7047} &       & {-} \\
		\cellcolor{lightgray}{6} & \cellcolor{lightgray}{69.164} &       & {-} & 6     & 60.816 & 5     & 59.946 & 6     & 21.911 & 5     & 21.794 & 6     & 10.655 & 5     & 10.625 \\
		{7} & 114.03 & 5     & 110.75 & \cellcolor{lightgray}{7}     & \cellcolor{lightgray}{69.344} &       & {-} & 7     & 45.711 & 6     & 45.390 & 7     & 22.975 & 6     & 22.890 \\
		{8} & {189.17} &  6     & {186.50} & 8     & 115.28 & 6     & 113.23 & \cellcolor{lightgray}{8}     & \cellcolor{lightgray}{69.344} &       & {-} & 8     & 43.113 & 7     & 42.909 \\
		\cellcolor{lightgray}{9} & \cellcolor{lightgray}{192.61} &      &  & {9}     & {191.57} &   7  & {187.55} & 9     & 82.887 & 7     & 82.154 & \cellcolor{lightgray}{9}     & \cellcolor{lightgray}{69.331} &       & {-} \\
		{10} & 285.85 & 7     & 277.64 & \cellcolor{lightgray}{10}    & \cellcolor{lightgray}{192.03} &      & {-} & 10    & 136.03 & 8     & 134.58 & 10    & 73.230 & 8     & 72.803 \\
		{11} & 328.40 & 8     & 330.29 & 11    & 290.76 & 8     & 283.81 & \cellcolor{lightgray}{11}    & \cellcolor{lightgray}{192.48} &       & {-} & 11    & 115.41 & 9     & 114.61 \\
		\cellcolor{lightgray}{12} & \cellcolor{lightgray}{357.08} &       & {-} & \cellcolor{lightgray}{12}    & \cellcolor{lightgray}{374.45} &       & {-} & 12    & 207.29 & 9     & 204.69 & 12    & 171.61 & 10    & 170.20 \\
		{13} & 397.33 & 9     & 394.02 & 13    & 413.20 & 9     & 402.27 & 13    & 298.38 & 10    & 294.10 & \cellcolor{lightgray}{13}    & \cellcolor{lightgray}{192.52} &       & {-} \\
		{14} & 442.00   & 10    & 439.52 & 14    & 558.67 & 10    & 542.65 & \cellcolor{lightgray}{14}    & \cellcolor{lightgray}{376.83} &       & {-} & 14    & 243.56 & 11    & 241.26 \\
		\cellcolor{lightgray}{15} & \cellcolor{lightgray}{533.71} &       & {-} & \cellcolor{lightgray}{15}    & \cellcolor{lightgray}{614.11} &       & {-} & 15    & 410.63 & 11    & 404.01 & 15    & 332.83 & 12    & 329.28 \\
		{16} & 538.97 & 11    & 541.55 & 16    & 726.26 & 11    & 704.15 & 16    & 545.03 & 12    & 535.32 & \cellcolor{lightgray}{16}    & \cellcolor{lightgray}{377.16} &       & {-} \\
		\cellcolor{lightgray}{17} & \cellcolor{lightgray}{596.06} &       & {-} & \cellcolor{lightgray}{17}    & \cellcolor{lightgray}{906.28} &       & {-} & \cellcolor{lightgray}{17}    & \cellcolor{lightgray}{621.95} &       & {-} & 17    & 440.77 & 13    & 435.51 \\
		{18} & 602.77 & 12    & 596.09 & 18    & 913.69 & 12    & 884.92 & 18    & 702.30 & 13    & 688.64 & 18    & 568.51 & 14    & 561.04 \\
		\cellcolor{lightgray}{19} & \cellcolor{lightgray}{657.87} &       & {-} & 19    & 1113.7 & 13    & 1080.1 & 19    & 882.95 & 14    & 864.40 & \cellcolor{lightgray}{19}    & \cellcolor{lightgray}{623.05} &       & {-} \\
		{20} & 717.37 & 13    & 731.74 & \cellcolor{lightgray}{20}    & \cellcolor{lightgray}{1218.0}  &       & {-} & \cellcolor{lightgray}{20}    & \cellcolor{lightgray}{927.18} &       & {-} & 20    & 717.04 & 15    & 706.74 \\
		\hline
		\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{3.1718\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{3.1486\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{2.1018\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{1.4361\%} \\
		\hline
	\end{tabular}%
	\label{tab:Timo}%
}
}
\end{table}%
\FloatBarrier

The authors of \cite{LVV09} show that for $\alpha = 300$ the eigenvalues compare very well up to the 20th two-dimensional eigenvalue. This is also apparent for other values of $\alpha$ as Table \ref{tab:Timo} shows. In fact, the accuracy of the eigenvalues increases as $\alpha$ increases. The authors of \cite{LVV09} also mention that for $\alpha = 100$, the results are very good for the first 10 eigenvalues.\\

Interestingly, the number of non-beam type eigenvalues within the first few eigenvalues decreases as $\alpha$ increases (or more relevant for the two-dimensional beam: as $h$ decreases).\\

Overall, the relevant conclusions of \cite{LVV09} is verified. For practical applications of beam models, the Timoshenko beam can be used. Preferably for long slender beams as Table \ref{tab:Timo} shows. The authors also mention that nature of the disturbance should also be taken into consideration, mainly because the models are linear.\\

 The short comings of \cite{LVV09} is that damping is not considered. This is mentioned by the authors of \cite{LVV09}, but will not be addressed in this dissertation. Further work is to extend \cite{LVV09} to a three-dimensional comparison. This is investigated further in this chapter.\\

\section{Validity of the two-dimensional elastic model}
This section continues the work of the article \cite{LVV09}. As mentioned by the authors of \cite{LVV09}, a comparison using a three-dimensional beam is desired. The two-dimensional beam model is an intermediate step to be able to investigate the validity of the Timoshenko beam model using a three-dimensional beam model as a reference. As mentioned by the authors, this will avoid some complexities.\\

The approach for this section remain similar to the previous section and the work of \cite{LVV09}. The eigenvalues for both models are calculated using FEM. The eigenvalues are then matched by sketching and comparing the mode shapes. Similar shapes indicate the the eigenvalues are comparable. The eigenvalues are then compared to determine how close the solutions of the models are.\\

As seen in the previous section, the two-dimensional model has eigenvalues not relating to beam type eigenvalues. There will also be eigenvalues not relating to beam type eigenvalues in this section. The results will include some of these eigenvalues, but the focus of our investigation remain with beam problems.

\subsection{The models}
Consider a cantilever two-dimensional beam, referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.\\

Figure \ref{fig:2Dv3D} shows the two beams side-by-side.

\FloatBarrier
\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\caption{Side-by-side comparison of the beams.}
			\label{fig:2Dv3D}
			\centering
			\begin{minipage}[b]{0.7\linewidth}
				\begin{tikzpicture}
					\draw[line width = 0.3mm] (0,1) -- (7,1);
					\draw[line width = 0.3mm] (0,-1) -- (7,-1);
					\draw[line width = 0.3mm] (7,-1) -- (7,1);
					\draw[line width = 0.3mm] (0,-1) -- (0,1);

					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});

					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

					\draw[scale=0.5, domain=1:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=2:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
					\draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
					\draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

					\node at (7.2,0) {$h$};
					\node at (3.2,-1.2) {$\ell = 1$};
				\end{tikzpicture}
				\subcaption{Two-Dimensional Elastic Body}
			\end{minipage}
			\begin{minipage}[b]{0.7\linewidth}
				\begin{tikzpicture}
					\draw[line width = 0.3mm] (-0.1,1) -- (6.9,1);
					\draw[line width = 0.3mm] (-0.1,-1) -- (6.9,-1);
					\draw[line width = 0.3mm] (6.9,-1) -- (6.9,1);
					\draw[line width = 0.3mm] (-0.1,-1) -- (-0.1,1);

					\draw[line width = 0.3mm] (0.1,1.1) -- (7.1,1.1);
					\draw[line width = 0.3mm] (7.1,-0.9) -- (7.1,1.1);

					\draw[line width = 0.3mm] (-0.1,1) -- (0.1,1.1);
					\draw[line width = 0.3mm] (6.9,1) -- (7.1,1.1);
					\draw[line width = 0.3mm] (6.9,-1) -- (7.1,-0.9);

					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});

					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

					\draw[scale=0.5, domain=0.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
					\draw[scale=0.5, domain=1.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
					\draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
					\draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

					\node at (6.95,1.25) {$b$};
					\node at (6.78,0) {$h$};
					\node at (3.2,-1.2) {$\ell = 1$};

				\end{tikzpicture}
				\subcaption{Three-Dimensional Elastic Body}

			\end{minipage}
		}
	}
\end{figure}
\FloatBarrier

For both models the parameter $h$ represents the width of the beams. The three-dimensional model also have depth $b$. Intuitively, the two-dimensional beam should compare well the the three-dimensional beam if $b$ is small.

\subsection{Accuracy of the numerical eigenvalues}
In the previous section, the accuracy of the two-dimensional beam's eigenvalues were investigated. This can be done similarly for the three-dimensional beam. The eigenvalues are also calculated using the Finite Element Method. Using piecewise tri-cubic basis functions, the following results were obtained.\\

****************INSERT GRAPHIC**************\\

\subsection{Comparing the mode shapes}
As in \cite{LVV09}, the shape of the modes are compared. Similar mode shapes implies that the eigenvalues are comparable. Results for both beam and non-beam type eigenvalues are included. The focus still remains on beam type eigenvalues.

\subsubsection{Mode shapes relating to beam type eigenvalues.}
Figure \ref{fig:beam-2dv3d} show some examples of beam type mode shapes for the displacement $u$. These are shapes that can be obtained from the Timoshenko beam model.

\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{3D12.png}
				\subcaption{3D Beam Type - $\lambda_{12} = 2.3293$}
				\label{fig:minipage2}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{2D3.png}
				\subcaption{2D Beam Type - $\lambda_3 = 2.3273$}
				\label{fig:minipage1}
			\end{minipage}
	}}
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{3D22.png}
				\subcaption{3D Beam Type - $\lambda_{24} = 21.929$}
				\label{fig:minipage2}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{2D6.png}
				\subcaption{2D Beam Type - $\lambda_6 = 21.911$}
				\label{fig:minipage1}
			\end{minipage}
			\caption{Mode shapes of the displacement $w$ with $h=1/20$.}
			\label{fig:beam-2dv3d}
	}}
\end{figure}
\FloatBarrier

\subsubsection{Mode shapes relating to non-beam type eigenvalues that are present in the two-dimensional model.}
Figure \ref{fig:nonbeam-2dv3d} show examples of mode shapes relating to non-beam type eigenvalues for the displacement $u$. These mode shapes are the non-beam type eigenvalues found in both the two-dimensional beam and the three-dimensional beam model.

\FloatBarrier
\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{3D33.png}
				\subcaption{3D Non-Beam Type - $\lambda_{33} = 69.374$}
				\label{fig:minipage2}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{2D8.png}
				\subcaption{2D Non-Beam Type - $\lambda_8 = 69.344$}
				\label{fig:minipage1}
			\end{minipage}
			\caption{Mode shapes of the displacement $w$ with $h=1/20$.}
			\label{fig:nonbeam-2dv3d}
	}}
\end{figure}
\FloatBarrier

\subsubsection{Mode shapes relating to non-beam type eigenvalues that are not present in the two-dimensional model.}
Figure \ref{fig:nonbeam-2dv3d} show examples of mode shapes relating to non-beam type eigenvalues for the displacement $u$ which are not present in the two-dimensional model. These mode shapes only appear in the three-dimensional beam.
\FloatBarrier
\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{3DNonBeam10.png}
				\subcaption{Non-2D Type - $\lambda_{10} = xx$}
				\label{fig:minipage2}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{3DNonBeam11.png}
				\subcaption{Non-2D Type - $\lambda_{11} = xx$}
				\label{fig:minipage11}
			\end{minipage}
			\caption{Mode shapes of the displacement $w$ with $\alpha = 4800$.}

	}}
\end{figure}
\FloatBarrier

Figure \ref{fig:minipage11} looks similar to the beam type eigenvalues, however the shape is in the $x-z$ axis.\\

\subsection{Comparing the eigenvalues}
The eigenvalues can now be compared. In the upcoming tables, the eigenvalues of the two-dimensional beam are compared to the eigenvalues of the three-dimensional beam. For each case of $h$, different values of $b$ are given.\\

Eigenvalues relating to non-beam type eigenvalues that are present in both the two-dimensional and three-dimensional beam, are highlighted in grey. The other non-beam type eigenvalues that are only found in the three-dimensional beam, are omitted from the tables. The original numbering is maintained.\\

The two cases for $h$ are $h = 1/5$ for a short beam and $1/20$ for a slender beam. For now, the investigation is restricted to values where $b \leq h$.

\begin{table}[htbp]
	\scalebox{.8}{
	\makebox[\textwidth]{
		\caption{Comparsion of Eigenvalues with $h = 1/5$.}
		\begin{tabular}{|cc|cc|cc|cc||cc|}
			\hline
			\multicolumn{10}{|c|}{Eigenvalues} \\
			\hline
			\hline
			i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
			\hline
			{2} & 0.12307 & {2} & 0.12234 & {2} & 0.12198 & {3} & 0.12178 & 1     & 0.12151 \\
			{3} & 3.5773 & {5} & 3.5630 & {6} & 3.5558 & {8} & 3.5519 & 2     & 3.5460 \\
			\rowcolor{lightgray}{5} & 7.7799 & {6} & 7.7596 & {8} & 7.7471 & {11} & 7.7401 & 3     & 7.7311 \\
			{8} & 20.334 & {9} & 20.283 & {11} & 20.26 & {14} & 20.247 & 4     & 20.225 \\
			{10} & 56.247 & {12} & 56.173 & {15} & 56.156 & {22} & 56.142 & 5     & 56.109 \\
			\rowcolor{lightgray}{11} & 69.197 & {14} & 69.319 & {17} & 69.281 & {24} & 69.238 & 6     & 69.164 \\
			{14} & 114.03 & {16} & 114.01 & {20} & 114.05 & {29} & 114.06 & 7     & 114.03 \\
			\rowcolor{lightgray}{17} & 187.01 & {19} & 189.14 & {25} & 189.37 & {36} & 189.34 & 8     & 189.17 \\
			{18} & 192.21 & {20} & 192.41 & {26} & 192.58 & {37} & 192.63 & 9     & 192.61 \\
			{21} & 284.76 & {23} & 285.43 & {31} & 285.74 & {42} & 285.84 & 10    & 285.85 \\
			{23} & 327.57 & {26} & 328.24 & {35} & 328.37 & {46} & 328.40 & 11    & 328.40 \\
			\rowcolor{lightgray}{25} & 347.77 & {28} & 356.44 & {36} & 357.30 & {50} & 357.33 & 12    & 357.08 \\
			{27} & 393.69 & {30} & 396.84 & {38} & 397.28 & {53} & 397.37 & 13    & 397.33 \\
			{30} & 434.46 & {34} & 441.05 & {41} & 441.81 & {57} & 441.99 & 14    & 442.00 \\
			\rowcolor{lightgray}{31} & 523.65 & {36} & 534.04 & {43} & 534.17 & {63} & 534.03 & 15    & 533.71 \\
			{34} & 550.51 & {37} & 537.82 & {44} & 538.86 & {64} & 539.06 & 16    & 538.97 \\
			\rowcolor{lightgray}{37} & 590.86 & {41} & 587.43 & {48} & 594.17 & {65} & 595.58 & 17    & 596.06 \\
			{39} & 590.86 & {42} & 600.52 & {49} & 602.25 & {67} & 602.69 & 18    & 602.77 \\
			\rowcolor{lightgray}{42} & 646.21 & {44} & 657.22 & {50} & 658.04 & {71} & 658.06 & 19    & 657.87 \\
			{44} & 711.07 & {46} & 714.62 & {53} & 717.10 & {73} & 717.51 & 20    & 717.37 \\
			\hline
			\hline
			\multicolumn{2}{|c|}{Max RE: \  2.6069\%} &\multicolumn{2}{c|}{Max RE: \ 1.4469\%}  & \multicolumn{2}{c|}{Max RE: \  0.38192\%}  & \multicolumn{2}{c||}{Max RE: \ 0.22301\%}& \multicolumn{2}{c|}{-} \\
			\hline
		\end{tabular}%
		\label{tab:2v3_1}%
	}}
\end{table}%
\FloatBarrier
Table \ref{tab:2v3_1} show that the eigenvalues of the two-dimensional model compare very well to the three-dimensional model.  The maximum relative error decreases significantly as $b$ is decreased. Even with $b = h$ the maximum relative error is still less than $2.7\%$. \\

Table \ref{tab:2Dv3D_1_breakup} gives more information on the maximum relative error by separating the beam type and non-beam type eigenvalues.

% Table generated by Excel2LaTeX from sheet 'Sheet2'
\begin{table}[htbp]
	\centering
	\caption{****$h = 1/5$}
	\begin{tabular}{|c|cccc|}
		\hline
		\multicolumn{5}{|c|}{Maximum Relative Error} \\
		\hline
		\hline
		& {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
		\hline
		Beam Type & 2.1420 \% & 0.6804 \% & 0.38192 \% & 0.22301 \% \\
		Non-Beam Type & 2.6069 \% & 1.4469 \% & 0.31546 \% & 0.11680 \% \\
		\hline
	\end{tabular}%
	\label{tab:2Dv3D_1_breakup}%
\end{table}%

From Table \ref{tab:2Dv3D_1_breakup}, it is clear that indeed for beam type eigenvalues, a short two-dimensional beam compares very well to a short three-dimensional beam.\\

\begin{table}[ht]
	\scalebox{.8}{
	\makebox[\textwidth]{
	\caption{Comparsion of Eigenvalues with $h = 1/20$. The non beam-type eigenvalues are highlighted or omitted.}
	\begin{tabular}{|cc|cc|cc|cc||cc|}
		\hline
		\multicolumn{10}{|c|}{Eigenvalues} \\
		\hline
		\hline
		i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
		\hline
		{2} & 0.008043 & {2} & 0.008029 & {2} & 0.008023 & {3} & 0.00802 & {1} & {0.008013} \\
		{3} & 0.3087 & {4} & 0.30816 & {5} & 0.30794 & {7} & 0.30785 & {2} & {0.30757} \\
		{5} & 2.3357 & {8} & 2.3316 & {9} & 2.3300  & {12} & 2.3293 & {3} & {2.3273} \\
		\rowcolor{lightgray}{8} & 7.7217 & {10} & 7.7156 & {13} & 7.7124 & {16} & 7.7111 & {4} & {7.7077} \\
		{10} & 8.5387 & {11} & 8.5238 & {14} & 8.5182 & {18} & 8.516 & {5} & {8.5086} \\
		{11} & 21.986 & {14} & 21.948 & {18} & 21.934 & {24} & 21.929 & {6} & {21.911} \\
		{14} & 45.863 & {18} & 45.781 & {21} & 45.756 & {30} & 45.746 & {7} & {45.712} \\
		\rowcolor{lightgray}{17} & 69.444 & {19} & 69.408 & {25} & 69.385 & {33} & 69.374 & {8} & {69.344} \\
		{18} & 83.149 & {22} & 82.999 & {27} & 82.960 & {36} & 82.944 & {9} & {82.887} \\
		{21} & 136.44 & {25} & 136.19 & {31} & 136.14 & {42} & 136.12 & {10} & {136.03} \\
		\rowcolor{lightgray}{23} & 192.62 & {27} & 192.62 & {35} & 192.58 & {47} & 192.56 & {11} & {192.48} \\
		{25} & 207.87 & {29} & 207.5 & {36} & 207.43 & {48} & 207.41 & {12} & {207.29} \\
		{27} & 299.14 & {33} & 298.63 & {41} & 298.56 & {55} & 298.53 & {13} & {298.38} \\
		\rowcolor{lightgray}{30} & 376.68 & {35} & 377.01 & {44} & 377.01 & {58} & 376.98 & {14} & {376.83} \\
		{31} & 411.58 & {37} & 410.89 & {46} & 410.83 & {61} & 410.81 & {15} & {410.63} \\
		{34} & 546.15 & {40} & 545.27 & {50} & 545.24 & {66} & 545.23 & {16} & {545.03} \\
		\rowcolor{lightgray}{37} & 620.77 & {42} & 622.02 & {53} & 622.19 & {69} & 622.18 & {17} & {621.95} \\
		{39} & 703.55 & {44} & 702.49 & {54} & 702.29 & {71} & 702.53 & {18} & {702.31} \\
		{42} & 884.27 & {47} & 883.02 & {59} & 883.14 & {82} & 883.19 & {19} & {882.96} \\
		\rowcolor{lightgray}{44} & 923.68 & {49} & 926.88 & {60} & 927.43 & {86} & 927.50 & {20} & {927.18} \\
		\hline
		\hline
		\multicolumn{2}{|c|}{Max RE: \  0.37701\%} &\multicolumn{2}{c|}{Max RE: \ 0.19893\%}  & \multicolumn{2}{c|}{Max RE: \  0.12393\%}  & \multicolumn{2}{c||}{Max RE: \ 0.092843\%}& \multicolumn{2}{c|}{-} \\
		\hline
	\end{tabular}%
	\label{tab:2v3_2}%
}}
\end{table}%
\FloatBarrier

In Table \ref{tab:2v3_2}, the eigenvalues are again compared for $h = 1/20$. The maximum relative error shows very impressive results for this case. The maximum relative error is less than $0.4\%$ and the maximum relative error decreases as $b$ is decreased.\\

\begin{table}[htbp]
	\centering
	\caption{*****$h = 1/20$}
	\begin{tabular}{|c|cccc|}
		\hline
		\multicolumn{5}{|c|}{Maximum Relative Error} \\
		\hline
		\hline
		& {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
		\hline
		Beam Type & 0.37701 \% & 0.19893 \% & 0.12393 \% & 0.092843 \% \\
		Non-Beam Type & 0.37682 \% & 0.10218 \% & 0.061213 \% & 0.043601 \% \\
		\hline
	\end{tabular}%
	\label{tab:2v3_2_split}%
\end{table}%
\FloatBarrier

Separating the errors of the beam-type eigenvalues and the non-beam type eigenvalues in Table \ref{tab:2v3_2_split}, just reaffirms the results.\\

Restricting the models where $b \leq h$ yielded great results. It has been shown that the two-dimensional beam compares very well the the three-dimensional beam. The comparison also improves for smaller values of $h$. This is a similar result as seen with the work of \cite{LVV09} in the previous section.

\subsection{$b > h$}
Now we can ask the question what happens if $b > h$. Of course for very large values of $b$, the question should be asked is if the beam model is still relevant. Therefore, the investigation will look at an incremental increase of $b$, without making assumptions on the relevancy of a beam model.\\

\FloatBarrier
\begin{table}[htbp]
	\scalebox{.8}{
	\makebox[\textwidth]{
		\caption{$h = 1/20$}
		\begin{tabular}{|cc|cc|cc||cc|}
			\hline
			\multicolumn{8}{|c|}{Eigenvalues} \\
			\hline
			\hline
			i     & {b = 2h} & i     & {b = 4h} & i     & {b = 8h} & j     & 2D \\
			\hline
			{2} & 0.008076 & {1} & 0.008162 & {1} & 0.008324 & 1     & 0.008013 \\
			{3} & 0.30995 & {3} & 0.31298 & {3} & 0.31738 & 2     & 0.30757 \\
			{5} & 2.3462 & {5} & 2.3737 & {6} & 2.4116 & 3     & 2.3273 \\
			\rowcolor{lightgray}{8} & 7.7312 & {8} & 7.7471 & {9} & 7.7711 & 4     & 7.7077 \\
			{10} & 8.5841 & {9} & 8.7082 & {10} & 8.7929 & 5     & 8.5086 \\
			{11} & 22.124 & {12} & 22.491 & {14} & 23.222 & 6     & 21.911 \\
			{14} & 46.195 & {14} & 47.003 & {18} & 47.921 & 7     & 45.712 \\
			\rowcolor{lightgray}{17} & 69.454 & {17} & 69.281 & {22} & 72.307 & 8     & 69.344 \\
			{18} & 83.822 & {18} & 85.218 & {24} & 80.607 & 9     & 82.887 \\
			{21} & 137.43 & {21} & 138.58 & {32} & 140.97 & 10    & 136.03 \\
			\hline
			\hline
			\multicolumn{2}{|c|}{Max RE: \  1.1289\%} &\multicolumn{2}{c|}{Max RE: \ 2.8261\%}  & \multicolumn{2}{c|}{Max RE: \  5.9821\%} & \multicolumn{2}{c|}{-} \\
			\hline
		\end{tabular}%
		\label{tab:b>h}%
	}}
\end{table}
\FloatBarrier
In Table \ref{tab:b>h}, $h = 1/20$ was chosen since it was the beam case investigated in the previous section and $b$ is increased by a factor of $2$. And here we see that the maximum relative error increases almost by a factor of $2$ for each case. Note also that this table only shows the first 10 eigenvalues.\\

There is also an increase of non-beam type eigenvalues that are only present in the three-dimensional model.\\

In Table \ref{tab:b>h-split}, the maximum relative error of the beam-type and non-beam type eigenvalues are separated.
\FloatBarrier
\begin{table}[htbp]
	\centering
	\caption{$\alpha = 4800$}
	\begin{tabular}{|c|ccc|}
		\hline
		\multicolumn{4}{|c|}{Maximum Relative Error} \\
		\hline
		\hline
		& {b = 2h} & {b = 4h} & {b = 8h} \\
		\hline
		Beam Type & 1.1289 \% & 2.8261 \% & 5.9821 \% \\
		Non-Beam Type & 0.30521 \% & 0.51096 \% & 4.2734 \% \\
		\hline
	\end{tabular}%
	\label{tab:b>h-split}%
\end{table}%
\FloatBarrier

From Table \ref{tab:b>h-split}, it is clear that as $b$ increases, the maximum relative error of the beam type eigenvalues increases and the two-dimensional model compares less to the three-dimensional model.\\

In this section, it has been shown that the two-dimensional beam compares very well to the three-dimensional beam, in practical beam problems. Practical beam problems imply that $b \leq h$. The models also compare much better if $h$ is smaller. For values of  $b > h$, the use of a beam model should be questioned.\\

For $b > h$, another model might be presented. In the next section, a Reisner-Mindlin plate model is investigated.
\end{document}

\begin{figure}[h!]\label{fig:compare:1D+2D}
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\caption{Side by side comparison of the beams.}
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\begin{tikzpicture}
					\draw[line width = 0.3mm] (0,0) -- (7,0);

					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});	
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

					%\node at (3.2,-0.2) {$\ell = 1$};
				\end{tikzpicture}
				\subcaption{Timoshenko Cantilever Beam}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\begin{tikzpicture}
					\draw[line width = 0.2mm] (0,0.1) -- (7,0.1);
					\draw[line width = 0.2mm] (0,-0.1) -- (7,-0.1);
					\draw[line width = 0.2mm] (7,-0.1) -- (7,0.1);
					\draw[line width = 0.2mm] (0,-0.1) -- (0,0.1);

					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});

					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
					\draw[scale=0.5, domain=-3:0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
					\draw[scale=0.5, domain=-3:1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
					\draw[scale=0.5, domain=-3:2.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});

					\draw[scale=0.5, domain=0.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
					\draw[scale=0.5, domain=1.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
					\draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});

					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

					\draw[line width = 0.1mm,->] (6,2) -- (7.4,2);
					\draw[line width = 0.1mm,->] (6,2) -- (6,0.9);
					\node at (6.7,1.8) {$e_1$};
					\node at (5.8,1.4) {$e_2$};

					\node at (7.2,0) {$h$};
					%\node at (3.2,-0.3) {$\ell = 1$};

				\end{tikzpicture}
				\subcaption{Two-Dimensional Cantilever Beam}
			\end{minipage}
		}
	}
\end{figure}

### 2022-10-31 files/Chapter7/Beam.tex
initial commit

--- 2022-10-31 files/Chapter7/Beam-Main_Rig_2.tex
@@
 This section is a literature study of the article \cite{LVV09}.
-The goal of the authors is to show that for practical applications, the solution of the Timoshenko beam model is close to the solution of a two-dimensional beam model.
-This is referred to as the validity of the Timoshenko beam model in this dissertation.\\
+The goal of \cite{LVV09} to show that the one-dimensional Timoshenko beam theory, is a feasible model to use in practical applications of beams.
+In the real world, a beam is a three-dimensional model.
+Therefore it is important to validate the use of the Timoshenko beam theory in practical applications.\\
 
-For practical applications, it would be preferred to compare the Timoshenko beam model to a more realistic three-dimensional model.
-But the authors of \cite{LVV09} explain that this will introduce complexities.
-\textcolor{red}{What complexities?} To mitigate some of the complexities, the two-dimensional model is used as an intermediate step.\\
+In mathematical terms, the validity of the Timoshenko beam theory is described as how well the solutions of the Timoshenko beam theory compare to more realistic, higher-dimensional models.
+It is obvious that a three-dimensional beam model is a better approximation of a real world beam.
+But the Timoshenko beam theory is less complex and more widely used.\\
 
-Where \cite{LVV09} differs from most other research, is that the boundary conditions are also taken into consideration.
-The authors of \cite{LVV09} use a cantilever beam configuration for their investigation.\\
+The authors of \cite{LVV09} use a two-dimensional cantilever beam, to validate the use of a cantilever Timoshenko beam for practical importance.
+Although a direct comparison to a three-dimensional beam would be preferred, the authors state that this would introduce complexities.
+A two-dimensional model is therefore used as an intermediate step.\\
+
+Where \cite{LVV09} differs from most other research, is that the boundary conditions are also taken into consideration.\\
 
@@
 From modal analysis, it is known that a solution of a second order hyperbolic type problem is a linear combination of the eigenvalues and eigenfunctions of the model.
-Therefore it is sufficient to compare the eigenvalues and eigenfunctions to determine the validity of the different dimensional models.\\
+Therefore it is sufficient to compare the eigenvalues and eigenfunctions to compare the solutions and comment on the validity of the models.\\
 
 \subsection{The models}
-Consider the cantilever Timoshenko beam model problem Problem T-2 from section \ref{ssec:1D_Model:ModelProblems} and the cantilever two-dimensional beam model problem Problem 2D-1 from section \ref{ssec:2D_Model:ModelProblem}.\\
+Recall the cantilever Timoshenko beam model from section \ref{ssec:1D_Model:ModelProblems}, referred to as Problem T-2 and the cantilever two-dimensional beam model from section \ref{ssec:2D_Model:ModelProblem}, referred to as Problem 2D-1.
+In \cite{LVV09} it is assumed that the beams have a rectangular cross-section.\\
 
-Figure 6.1 shows the two beams side-by-side for a visual guide.
+Figure 6.1 shows the two beams side-by-side.
 
@@
 
-The parameter $h$ is the height of the two-dimensional beam.
-Recall the dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ from section \ref{sssec:1D_Model:DimensionlessForm}.
-For the Timoshenko beam model with a rectangular cross-section, the area moment of inertial is
+In Chapter 1, the following parameters were established.
+The parameter $h$ is the height of the two-dimensional beam and for the Timoshenko dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ was found.\\
+
+For the Timoshenko beam model with a rectangular cross-section, the area moment of inertial is calculated as
 \begin{eqnarray*}
@@
 
-After substitution, the following relation ship between $\alpha$ and $h$ is found
+After substitution, the following relationship between $\alpha$ and $h$ is found
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-The parameter $\alpha$ can be chosen in such a way that the beams have equal dimensions.
+Using this relationship, $\alpha$ can be chosen in such a way that the beams have equal lateral dimensions.
 
 \subsection{Accuracy of the numerical eigenvalues}
-For the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} reference an another article \cite{VV06}.
-In this article \cite{VV06}, a method is described to obtain the eigenvalues and eigenfunctions of a (cantilever) Timoshenko beam.
-This method also allows for the eigenvalues to be obtained to a desired level of accuracy (using a numerical method such as interval division).
-In this dissertation, \cite{VV06} is discussed in section \ref{sec:Timo:EigenvalueProblem}.\\
+The calculate the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} use the article \cite{VV06}.
+This article was discussed in section \ref{sec:Timo:EigenvalueProblem} in this dissertation.
+It is important to note that the method described in \cite{VV06} allows us to find the eigenvalues of a cantilever Timoshenko beam accurate to a desired level, using numerical methods like interval division.\\
 
-For the two-dimensional beam, the Finite Element Method is used to calculate the eigenvalues and eigenfunctions.
+A different approach is needed for the two-dimensional beam.
+In section \ref{sec:FEM:2D}, the Finite Element Method was used to obtain a numerical formula to solve the eigenvalue problem Problem 2D-1E.
 In \cite{LVV09} the authors used piecewise bi-cubic basis functions and a grid size large enough to ensure that the eigenvalues are accurate to 3 significant digits.\\
@@
 \subsection{Comparing the shape of the eigenfunctions}
-Before the eigenvalues of the beams can be compared, a method is required to be able to match the eigenvalues.
-In \cite{LVV09} the authors compare the modal shapes of the Timoshenko beam model to the modal shapes of the two-dimensional model.\\
+Before the eigenvalues can be compared, a method is required to be able to match the eigenvalues of the two different models.
+The authors of \cite{LVV09} match the modal shapes of the eigenfunctions.
+The corresponding eigenvalues can then be matched.\\
 
-Similar modal shapes implies that the eigenvalues can be matched up and compared. Eigenvalues relating to the shapes of the Timoshenko beams modes are called beam-type eigenvalues by \cite{LLV09}.
+The eigenvalues of the Timoshenko beam, are referred to by the authors as beam-type eigenvalues.
 
 \subsubsection{Shapes relating to beam-type eigenvalues}
-The following are examples of beam-type mode shapes for the displacement $w$ for the cantilever two-dimensional beam and cantilever Timoshenko beam. The figures are presented side-by-side.
+The following figures are examples of beam-type mode shapes for the displacement $w$.
 
@@
 \subsubsection{Shapes relating to non-beam type eigenvalues}
-The following are examples of non beam-type mode shapes for the displacement $w$ of the cantilever two-dimensional beam.
+The following figures are examples of non beam-type mode shapes for the displacement $w$. These mode shapes are not present in the cantilever Timoshenko beam model and are not beam related. 
 \begin{figure}[h!]
@@
 
-Using this method all the relevant eigenvalues in this section were matched. The non-beam type eigenvalues are highlighted in gray in the tables.
+The existence of these non-beam type eigenvalues imply that there are eigenvalues in the two-dimensional model, that are not in the Timoshenko beam model.
+This is an example of the complexities that arise when comparing models of different dimensions.
 
 \subsubsection{Shapes of the cross-section}
-The Timoshenko beam theory differs from other one-dimensional beam theories by also including shear.
-It is assumed that the cross-sections need not remain perpendicular to the neutral axis of the beam.
-The cross-sections remain straight.\\
+The Timoshenko beam theory improve some one-dimensional beam theories such as the Euler-Bernoulli beam theory by also including the effect of shear.
+In the Timoshenko beam theory it is assumed that the cross-sections need not remain perpendicular to the neutral axis of the beam.
+The cross-sections however remain a straight line.\\
 
-For the two-dimensional body, the shape of the cross-section of beam type eigenfunctions can deform into an a s-shape.
-Figure \ref{fig:s} shows an exaggerated representation of the s-shaped deformation.
-This is also given and explained in \cite{LVV09}.
+For the two-dimensional beam, the shape of the cross-section can deform into a s-shape. This is explained in \cite{LVV09} and a similar figure in \cite{LVV09} is given here.
 \FloatBarrier
@@
 \end{tikzpicture}
-	\caption{S-shape deformation and average rotation.}\label{fig:s}
+	\caption{S-shape deformation of the cross-section.}\label{fig:s}
 \end{figure}
-The red line in figure \ref{fig:s} show how the average rotation of the cross-section is calculated in \cite{LVV09}.
+
+Note that figure \ref{fig:s} shows an exaggerated example of the deformation of a cross-section.
+The red line shows how the average rotation of a cross-section is calculated in \cite{LVV09}.
+This average rotation can be used to compare the rotation of the cross-section of the two-dimensional beam to the rotation of the cross-section of the Timoshenko beam.
 \FloatBarrier
@@
 \subsubsection{Direct comparison of mode shapes}
-Figure \ref{fig:w} shows the displacement $w$ of the cantilever Timoshenko beam and the cantilever two-dimensional beam directly compared.
+Figure \ref{fig:w} shows the displacement of the material lines of the cantilever Timoshenko beam and the cantilever two-dimensional beam, compared directly.
 
@@
 Similarly Figure \ref{fig:phi} shows the direct comparison of the angle of the cross-section of the cantilever Timoshenko beam and the two-dimensional beam.
-The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s}.
+The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s} and \cite{LVV09}.
 
@@
 
-Figures \ref{fig:w} and \ref{fig:phi} show that for $\alpha = 4800$, the mode shapes are very close, even for the eigenvalues 8 (for Timoshenko beam) and 10 (for the two-dimensional beam).
-The authors of \cite{LVV09} obtained similar results for $\alpha = 300$ for the eigenvalues 6 (for Timoshenko beam) and 9 (for the two-dimensional beam).
-Therefore a direct comparison of the mode shapes are feasible for short and long beams.
+In \cite{LVV09} the authors obtained similar results for $\alpha=300$, which represents a short beam.
+Both figures \ref{fig:w} and \ref{fig:phi} were calculated with5 $\alpha = 4800$, which represents a longer, narrower beam.
 
 \subsubsection{Remark}
-Due to the fact that any multiple of an eigenfunction is still an eigenfunction, the figures can be scaled.
-This is why no scale is indicated on the y-axis in \cite{LVV09}.
-Figures \ref{fig:w} and \ref{fig:phi} were scaled by eye.
+The mode shapes were scaled to obtain figures \ref{fig:w} and \ref{fig:phi}. Therefore no scale is shown on the y-axis.
 
@@
 \section{Validity of the two-dimensional elastic model}
-This section continues the work of the article \cite{LVV09}.
-As mentioned by the authors of \cite{LVV09}, a comparison using a three-dimensional beam is desired.
-The two-dimensional beam model is an intermediate step to be able to investigate the validity of the Timoshenko beam model using a three-dimensional beam model as a reference.
-As mentioned by the authors, this will avoid some complexities.\\
+In this section, the validity of a two-dimensional cantilever beam is investigated.
+A three-dimensional cantilever beam is the model we'll use the measure.
+Recall that the two-dimensional model is an intermediate step between a Timoshenko beam and a three-dimensional beam.\\
 
-The approach for this section remain similar to the previous section and the work of \cite{LVV09}.
-The eigenvalues for both models are calculated using FEM.
-The eigenvalues are then matched by sketching and comparing the mode shapes.
-Similar shapes indicate the the eigenvalues are comparable.
-The eigenvalues are then compared to determine how close the solutions of the models are.\\
+In Chapter 1, models for a two-dimensional cantilever elastic body, as well as a three-dimensional cantilever elastic body is given.
+In Chapter 5, the Finite Element Method is applied to these models to obtain a formula to numerically calculate the eigenvalues and eigenfunctions of each of the models.\\
 
-As seen in the previous section, the two-dimensional model has eigenvalues not relating to beam type eigenvalues.
-There will also be eigenvalues not relating to beam type eigenvalues in this section.
-The results will include some of these eigenvalues, but the focus of our investigation remain with beam problems.
+This section follows the same strategy as the previous section by comparing the eigenvalues and eigenfunctions of the models to determine the validity of the two-dimensional model.
+This investigation remains focussed on beam type problems.
 
 \subsection{The models}
-Consider a cantilever two-dimensional beam, referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.\\
+Recall a cantilever two-dimensional beam, referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.\\
 
@@
 
+For different values of $h$ and $b$, the first 30 eigenvalues are calculated with increasing grid sizes. The maximum relative error between the sets of eigenvalues are then calculated and graphed.\\
+
 ****************INSERT GRAPHIC**************\\
@@
 \subsection{Comparing the mode shapes}
-As in \cite{LVV09}, the shape of the modes are compared.
-Similar mode shapes implies that the eigenvalues are comparable.
-Results for both beam and non-beam type eigenvalues are included.
-The focus still remains on beam type eigenvalues.
+In this section, the mode shapes of the two dimensional and three-dimensional beam are compared.
+Recall that beam-type eigenvalues are defined by \cite{LVV09} as any eigenvalue for which it's corresponding mode shape is similar to the mode shapes obtained in the Timoshenko beam theory.
 
 \subsubsection{Mode shapes relating to beam type eigenvalues.}
-Figure \ref{fig:beam-2dv3d} show some examples of beam type mode shapes for the displacement $u$. These are shapes that can be obtained from the Timoshenko beam model.
+Figure \ref{fig:beam-2dv3d} show some examples of beam type mode shapes for the displacement $u$.
 
@@
 Figure \ref{fig:nonbeam-2dv3d} show examples of mode shapes relating to non-beam type eigenvalues for the displacement $u$.
-These mode shapes are the non-beam type eigenvalues found in both the two-dimensional beam and the three-dimensional beam model.
 

### 2022-10-31 files/Chapter7/Introduction.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
This chapter is an investigation into the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate. Validity in this context refer to how well the solutions compare to the solutions of more realistic higher dimensional models.\\

The chapter consists of three main parts.

\begin{itemize}
	\item[-] Section 7.2: Comparison between the cantilever Timoshenko beam and cantilever two-dimensional beam.
	\item[-] Section 7.3: Comparison between the cantilever two-dimensional beam and cantilever three-dimensional beams.
	\item[-] Section 7.4: Comparison between the cantilever Reissner-Mindlin plate and cantilever three-dimensional plate.
\end{itemize}

In Section 7.2, the work in \cite{LVV09} is discussed and the numerical results are verified. In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. More results not given in  [LVV09] are also calculated, to be used in the sections following.

Section 7.3 is a natural extension of the article \cite{LVV09}. In this section, the validity of a two-dimensional beam model is investigated. The results of the two-dimensional beam are compared to a three-dimensional beam. The two-dimensional beam thus serves are an intermediate step to validate the Timoshenko beam model.

 extends the work of \cite{LVV09} to a comparison of a cantilever two-dimensional beam to a cantilever three-dimensional beam.\\

Section 7.4 extends the work of \cite{LVV09} to plate models. Specifically a comparison of a cantilever two-dimensional Reissner-Mindlin plate to a cantilever three-dimensional plate.\\

\subsubsection{Parameters}
All the models in this dissertation are made of the same isotropic material and have square cross-section. Therefore for all the models, the elastic modulus $\displaystyle G = \frac{E}{2(1+\nu)}$. The shear correction factor is chosen as $\kappa^2 = 5/6$ and Poisson's ratio $\nu = 0.3$.\\

\end{document}

This is the same idea as done in the article [LVV09]. To make the comparison between models of different dimensions, the eigenvalues and eigenfuctions of the models are considered. If the eigenvalues and eigenfunctions compare well, it can be assumed that the solution to the model problem would also compare well. The reason for this is explained in Section 1.5.5. And since the Fourier coefficients in the solution decreases very rapidly, only the first few eigenvalues and eigenfunctions need to be considered.\\

Section 6.2 looks at some of the results obtained in [LVV09]. The results for the Euler-Bernoulli beam theory is excluded a the article has sufficient results. The idea of Section 6.2 is to verify the conclusions obtained in [LVV09]. The results of the section also aggregate the work of the article by examining different values for the parameter $\alpha$.\\

Section 6.3 extends the work of [LVV09] by examining the comparison between a two-dimensional and three-dimensional cantilever beam model. The authors' opinion is that a comparison between a two-dimensional and three-dimensional model would be less problematic than comparing the one-dimensional (Timoshenko) beam model to a three-dimensional model. The two-dimensional model can be seen as an intermediate step.

\subsubsection{Parameters}
For all models, the parameters are chosen as $\nu = 0.3$, and $\kappa^2 = 5/6$. It is assumed that all models are made from the same isotropic material, hence $G = \frac{E}{2(1+\nu)}$. Since the beams have a rectangular cross-section, for the Timoshenko beam model the area moment of inertia can be calculated as
\begin{eqnarray*}
	I & = & \frac{h^3b}{12}.
\end{eqnarray*}
The dimensionless constant $\alpha$, given in Section 1.5.1, gives the following relationship between the beam's height, length and the value of $\alpha$:
\begin{eqnarray*}
	\frac{h}{\ell}  & = & \sqrt{\frac{12}{\alpha}}
\end{eqnarray*}
This equation show that the ratio of the height of the beam and the length is dependant on the value of the parameter $\alpha$. The parameter $\alpha$ only appears in the one-dimensional beam model. But for continuity will be used for all models in this chapter to determine the ratio of length to height of the models.

\subsubsection{Remark:}
\begin{itemize}
	\item[--] All results in this chapter are given to 3 significant digits.
	\item[--] ****b does not depend on $\alpha$
\end{itemize}

**********************Needs work******************\\
The comparisons in this Chapter are as follow:
\begin{itemize}
	\item[] Section 7.2: The Timoshenko cantilever beam (Problem T-2) and two-dimensional cantilever beam (Problem 2D-1).
	\item[] Section 7.3: The two-dimensional cantilever beam (Problem 2D-1) and three-dimensional cantilever beam(Problem 3D-1)
	\item[] Section 7.4: The Reisner-Mindlin cantilever plate (Problem P-1) and three-dimensional cantilever plate (Problem 3D-1)
\end{itemize}

For the first part of this chapter, the work of the authors of \cite{LVV09} are discussed. The authors of

This chapter is a discussion and an extension of the work of the authors of \cite{LVV09}. In \cite{LVV09}, the authors examined the validity of a cantilever Timoshenko beam using a cantilever two-dimensional beam as a reference.\\

After the discussion of \cite{LVV09}, the work of the authors is extended to investigate the validity of a cantilever two-dimensional beam using a cantilever three-dimensional beam as a reference. Finally the validity of a cantilever Reissner-Mindlin plate is investigated using a cantilever three-dimensional plate model as reference. The structure and idea of the authors of \cite{LVV09} is used a guide throughout this chapter.\\

The chapter is divided into the following sections:\\

### 2022-10-31 files/Chapter7/Plate.tex
initial commit

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Validity of the Reissner-Mindlin plate model}
In this section, the validity of a cantilever Reissner-Mindlin plate is investigates with reference to a three-dimensional plate model. In the previous section, it was shown that the beam models do not compare well when the parameter $b$ is ``too-large''. A plate model might be a better option.\\

Similarly to how the Timoshenko beam theory improves on the Euler-Bernoulli beam theory, the Reissner-Mindlin plate theory improves on classical plate theory by including the effect of shear stress. The Reisner-Mindlin plate theory is a two-dimensional theory. Therefore it is of interest to investigate the validity of such a plate model.Using \cite{LVV09} as a guide, the validity a cantilever Reisner-Mindlin plate model is investigated.\\

 Figure \ref{fig:plate_sbs} shows the two cantilever plates side by side.
\FloatBarrier
\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\caption{Side by side visualization of the cantilever plates.}
			\label{fig:plate_sbs}
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\begin{tikzpicture}
					\draw[line width = 0.3mm] (-0.8,-0.1) -- (6.2,-0.1);
					\draw[line width = 0.3mm] (0.8,0.7) -- (7.8,0.7);
					\draw[line width = 0.3mm] (-0.8,-0.1) -- (0.8,0.7);
					\draw[line width = 0.3mm] (6.2,-0.1) -- (7.8,0.7);

					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

					\draw[scale=0.5, domain=-3:-1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
					\draw[scale=0.5, domain=2:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});

					\draw[scale=0.5, domain=-3:-0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
					\draw[scale=0.5, domain=-3:0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
					\draw[scale=0.5, domain=-3:1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
					\draw[scale=0.5, domain=-3:2.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

					\node at (7.2,0.1) {$b$};
					\node at (3.2,-0.27) {$\ell = 1$};

					\draw[line width = 0.2mm] (0.8,0.7) -- (7.8,0.7);
					\draw[line width = 0.2mm] (-0.8,-0.1) -- (0.8,0.7);
					\draw[line width = 0.2mm] (6.2,-0.1) -- (7.8,0.7);
				\end{tikzpicture}
				\subcaption{Timoshenko Cantilever Beam}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\begin{tikzpicture}
					\draw[line width = 0.3mm] (-0.8,0.1) -- (6.2,0.1);
					\draw[line width = 0.3mm] (-0.8,-0.1) -- (6.2,-0.1);
					\draw[line width = 0.3mm] (6.2,-0.1) -- (6.2,0.1);
					\draw[line width = 0.3mm] (-0.8,-0.1) -- (-0.8,0.1);

					\draw[line width = 0.3mm] (0.8,0.9) -- (7.8,0.9);
					\draw[line width = 0.3mm] (7.8,0.7) -- (7.8,0.9);

					\draw[line width = 0.3mm] (-0.8,0.1) -- (0.8,0.9);
					\draw[line width = 0.3mm] (6.2,0.1) -- (7.8,0.9);
					\draw[line width = 0.3mm] (6.2,-0.1) -- (7.8,0.7);

					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

					\draw[scale=0.5, domain=-3:-1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
					\draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});

					\draw[scale=0.5, domain=-3:-0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
					\draw[scale=0.5, domain=-3:0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
					\draw[scale=0.5, domain=-3:1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
					\draw[scale=0.5, domain=-3:2.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

					\node at (6.85,0.6) {$b$};
					\node at (6,0) {$h$};
					\node at (3.2,-0.3) {$\ell = 1$};

					\draw[line width = 0.1mm,->] (9,1) -- (10,1.6);
					\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
					\draw[line width = 0.1mm,->] (9,1) -- (9,-0.1);
					\node at (9.2,1.4) {$e_3$};
					\node at (9.7,0.8) {$e_1$};
					\node at (8.8,0.4) {$e_2$};
				\end{tikzpicture}
				\subcaption{Two-Dimensional Cantilever Beam}

			\end{minipage}
		}
	}
\end{figure}
\FloatBarrier

Both the Reissner-Mindlin plate and the three-dimensional plate model has a parameter $b$ representing the depth of the plate. The three-dimensional model also have a parameter $h$ representing the width of the plate model.

\subsection{Comparing the mode shapes}
\FloatBarrier
\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{Plate2.png}
				\subcaption{Plate - $\lambda_5 = 0.643$}
				\label{fig:minipage2}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{3D2.png}
				\subcaption{3D Model - $\lambda_5 = 0.645$}
				\label{fig:minipage1}
			\end{minipage}
	}}
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}{.8\textwidth}
				\centering
				\includegraphics[width=1\linewidth]{Plate1.png}
				\subcaption{Plate - $\lambda_6 = 1.92$}
				\label{fig:minipage1}
			\end{minipage}
			\begin{minipage}{.8\textwidth}
				\centering
				\includegraphics[width=1\linewidth]{3D1.png}
				\subcaption{3D Model - $\lambda_7 = 1.92$}
				\label{fig:minipage2}
			\end{minipage}
	}}
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{Plate3.png}
				\subcaption{Plate - $\lambda_8 = 2.74$}
				\label{fig:minipage1}
			\end{minipage}
			\quad
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{3D3.png}
				\subcaption{3D Model - $\lambda_8 = 2.74$}
				\label{fig:minipage2}
			\end{minipage}
	}}
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{Plate4.png}
				\subcaption{Plate - $\lambda_{12} = 8.96$ (Side view)}
				\label{fig:minipage2}
			\end{minipage}
			\quad
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{3D4.png}
				\subcaption{3D Model - $\lambda_{14} = 9.01$ (Side view)}
				\label{fig:minipage2}
			\end{minipage}
			\caption{Comparison of Mode Shapes of the 3D model and the plate model. $b = 1/20$, $d = 1$.}
	}}
\end{figure}

\FloatBarrier

Let $b= 1$ and $\alpha= 4800$ so that $h= \frac{1}{2}$.\\

\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}{.8\textwidth}
				\centering
				\includegraphics[width=1\linewidth]{3Dnp1.png}
				\subcaption{3D Model - $\lambda_{6} = 1.35$ (Top view)}
				\label{fig:minipage1}
			\end{minipage}
			\begin{minipage}{.8\textwidth}
				\centering
				\includegraphics[width=1\linewidth]{3Dnp2.png}
				\subcaption{3D Model - $\lambda_{13} = 7.80$ (Top view)}
				\label{fig:minipage2}
			\end{minipage}
	}}
	\caption{Examples of non-plate mode shapes.}
\end{figure}

\subsection{Comparing the eigenvalues}
Tables \ref{tab:Table_plate_1} and \ref{tab:Table_plate_1} compare the eigenvalues of a cantilever Reissner-Mindlin plate model to the eigenvalues of a cantilever three-dimensional plate model. The different widths of plates considered are $b = 0.25$ and $b = 1$. These cases represent a slightly and very wide plate models. In each of the tables, the parameter $h$ representing the height is decreased.

\FloatBarrier
\begin{table}[htbp]
	\scalebox{.8}{
	\makebox[\textwidth]{
		\caption{Comparison of eigenvalues of the cantilever Reissner-Mindlin and three-dimensional plates.}
		\begin{tabular}{|cccc||cccc||cccc||cccc|}
			\hline
			\multicolumn{16}{|c|}{Comparison of Eigenvalues, $b = 0.25$} \\
			\hline\hline
			\multicolumn{4}{|c||}{$h = 1/5$}       & \multicolumn{4}{c||}{$h =1/10$}      & \multicolumn{4}{c||}{$h = 1/20$}      & \multicolumn{4}{c|}{$h = 1/30$} \\
			\hline
			{i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} \\
			\hline
			1     & 0.12348 & 1     & {0.12249} & 1     & 0.032327 & 1     & 0.032184 & 1     & 0.008207 & 1     & 0.008186 & 1     & 0.003663 & 1     & 0.003656 \\
			2     & 0.18638 &       & -     & 2     & 0.18531 &       & {-} & 2     & 0.18476 &       & {-} & 2     & 0.14204 & 2     & 0.14173 \\
			3     & 2.4151 & 2     & {2.3954} & 3     & 1.161 & 2     & 1.1537 & 3     & 0.31436 & 2     & 0.31341 & 3     & 0.18456 &       & {-} \\
			4     & 3.5856 & 3     & {3.5368} & 4     & 1.3155 & 3     & 1.31  & 4     & 0.44696 & 3     & 0.44582 & 4     & 0.21514 & 3     & 0.21454 \\
			5     & 4.785 &       & -     & 5     & 4.7697 &       & {-} & 5     & 2.3862 & 4     & 2.3767 & 5     & 1.1001 & 4     & 1.0971 \\
			6     & 7.7889 &       & -     & 6     & 7.7674 & 4     & 7.9816 & 6     & 4.1984 & 5     & 4.1857 & 6     & 2.0374 & 5     & 2.0313 \\
			7     & 20.37 & 4     & {19.969} & 7     & 8.056 &       & {-} & 7     & 4.7615 &       & {-} & 7     & 4.1509 & 6     & 4.1367 \\
			8     & 21.722 & 5     & {21.537} & 8     & 12.034 & 5     & 11.972 & 8     & 7.7543 &       & {-} & 8     & 4.7585 &       & {-} \\
			9     & 25.181 &       & -     & 9     & 25.147 &       & {-} & 9     & 8.7609 & 6     & 8.7132 & 9     & 6.2078 & 7     & 6.1864 \\
			10    & 56.321 & 6     & {54.887} & 10    & 26.608 & 6     & 26.266 & 10    & 12.598 & 7     & 12.548 & 10    & 7.7495 &       & {-} \\
			11    & 60.267 & 7     & {59.71} & 11    & 34.438 & 7     & 34.197 & 11    & 22.619 & 8     & 22.456 & 11    & 11.064 & 8     & 11.015 \\
			12    & 65.513 &       & -     & 12    & 61.829 & 8     & 60.801 & 12    & 25.128 &       & {-} & 12    & 13.734 & 9     & 13.678 \\
			13    & 69.031 &       & -     & 13    & 65.518 &       & {-} & 13    & 27.297 & 9     & 27.155 & 13    & 23.854 & 10    & 23.724 \\
			14    & 114.09 & 8     & {110.7} & 14    & 69.133 & 9     & 69.548 & 14    & 47.123 & 10    & 46.695 & 14    & 25.121 &       & {-} \\
			15    & 117.88 & 9     & {116.66} & 15    & 70.211 &       & {-} & 15    & 50.515 & 11    & 50.174 & 15    & 26.054 & 11    & 25.927 \\
			16    & 127.05 &       & -     & 16    & 116.78 & 10    & 114.43 & 16    & 65.523 &       & {-} & 16    & 36.259 & 12    & 36.15 \\
			17    & 184.46 & 10    & {185.78} & 17    & 121.43 & 11    & 119.94 & 17    & 69.089 &       & {-} & 17    & 41.973 & 13    & 41.807 \\
			18    & 191.91 & 11    & {191.47} & 18    & 127.23 &       & {-} & 18    & 71.563 & 12    & 71.166 & 18    & 44.95 & 14    & 44.685 \\
			19    & 193.03 &       & -     & 19    & 178.27 & 12    & 175.79 & 19    & 81.444 & 13    & 80.894 & 19    & 45.798 & 15    & 45.507 \\
			20    & 193.71 &       & -     & 20    & 186.06 & 13    & 187.28 & 20    & 84.785 & 14    & 84.064 & 20    & 54.838 & 16    & 54.573 \\
			\hline
			\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{2.9764\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{2.7585\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{0.90845\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{0.63525\%} \\
			\hline
		\end{tabular}%
		\label{tab:Table_plate_1}%
	}}
\end{table}%
\FloatBarrier

The results in Table \ref{tab:Table_plate_1} show that the cantilever Reissner-Mindlin plate model compare very well to the cantilever three-dimensional plate. For $h = 1/5$ the plate can be considered ``thick'', and the maximum relative error is less than $3\%$. This relative error decreases significantly as $h$ decreases.\\

As $b$ decreases, there are also more eigenvalues of the cantilever the Reissner-Mindlin plate relating to the first 20 eigenvalues of the cantilever three-dimensional plate. Table
\ref{tab:Table_plate_1_1} shows some more results for different values of $b$ without presenting the eigenvalues.

\FloatBarrier
\begin{table}[htbp]
	\centering
	\caption{Maximum relative error of the first 10 comparable eigenvalues with b = 0.25.}
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\multicolumn{6}{|c|}{Max Relative Error } \\ 
		\hline 
		\hline
		b = 1/2 & b = 1/5 & b = 1/10 & b = 1/20 & b = 1/30 & b = 1/50\\ \hline
		3.4514\% & 2.9764 \% & 2.7585 \% & 0.90845 \% & 0.63525 \% & 0.50397 \% \\ \hline
	\end{tabular}%
	\label{tab:Table_plate_1_1}%
\end{table}%

\FloatBarrier
\begin{table}[htbp]
	\scalebox{.8}{
	\makebox[\textwidth]{
		\caption{Comparison of eigenvalues of the cantilever Reissner-Mindlin and three-dimensional plates.}
		\begin{tabular}{|cccc||cccc||cccc||cccc|}
			\hline
			\multicolumn{16}{|c|}{Comparison of Eigenvalues, $b = 1$} \\
			\hline\hline
			\multicolumn{4}{|c||}{$h = 1/5$}       & \multicolumn{4}{c||}{$h =1/10$}      & \multicolumn{4}{c||}{$h = 1/20$}      & \multicolumn{4}{c|}{$h = 1/30$} \\
			\hline
			{i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} \\
			\hline
			1     & 0.12869 & 1     & {0.12743} & 1     & 0.033784 & 1     & 0.033626 & 1     & 0.008565 & 1     & 0.008543 & 1     & 0.003817 & 1     & {0.00381} \\
			2     & 0.62189 & 2     & {0.61703} & 2     & 0.18635 & 2     & 0.18562 & 2     & 0.049829 & 2     & 0.04957 & 2     & 0.022511 & 2     & {0.022405} \\
			3     & 1.3638 &       & -     & 3     & 1.1603 & 3     & 1.153 & 3     & 0.31428 & 3     & 0.31315 & 3     & 0.14192 & 3     & {0.14156} \\
			4     & 3.5808 & 3     & {3.5289} & 4     & 1.3579 &       & {-} & 4     & 0.50842 & 4     & 0.50676 & 4     & 0.23035 & 4     & {0.22969} \\
			5     & 5.8165 & 4     & {5.7694} & 5     & 1.864 & 4     & 1.8577 & 5     & 0.64595 & 5     & 0.64297 & 5     & 0.29502 & 5     & {0.29394} \\
			6     & 6.6048 & 5     & {6.5216} & 6     & 2.2928 & 5     & 2.2792 & 6     & 1.3555 &       & {-} & 6     & 0.8928 & 6     & {0.88735} \\
			7     & 7.8455 &       & -     & 7     & 6.4973 & 6     & 6.4546 & 7     & 1.9293 & 6     & 1.9157 & 7     & 1.156 & 7     & {1.1527} \\
			8     & 9.8027 &       & -     & 8     & 7.8167 &       & {-} & 8     & 2.5089 & 7     & 2.4975 & 8     & 1.265 & 8     & {1.261} \\
			9     & 17.03 & 6     & {16.802} & 9     & 8.4533 & 7     & 8.3671 & 9     & 2.7486 & 8     & 2.7369 & 9     & 1.3543 &       & - \\
			10    & 21.225 & 7     & {20.743} & 10    & 9.3453 & 8     & 9.2873 & 10    & 3.3087 & 9     & 3.2903 & 10    & 1.5352 & 9     & {1.529} \\
			11    & 23.935 & 8     & {23.552} & 11    & 9.8009 &       & {-} & 11    & 5.5365 & 10    & 5.4914 & 11    & 2.598 & 10    & {2.5803} \\
			12    & 24.694 &       & -     & 12    & 10.925 & 9     & 10.827 & 12    & 5.9696 & 11    & 5.9246 & 12    & 2.8161 & 11    & {2.7997} \\
			13    & 27.187 & 9     & {26.69} & 13    & 17.599 & 10    & 17.447 & 13    & 7.8024 &       & {-} & 13    & 4.2654 & 12    & {4.2474} \\
			14    & 28.844 &       & -     & 14    & 18.596 & 11    & 18.407 & 14    & 9.0173 & 12    & 8.9573 & 14    & 4.6674 & 13    & {4.6415} \\
			15    & 32.373 &       & -     & 15    & 24.729 &       & {-} & 15    & 9.8006 & 13    & 9.838 & 15    & 4.9397 & 14    & {4.9143} \\
			16    & 41.288 & 10    & {40.519} & 16    & 27.4  & 12    & 27.021 & 16    & 9.9172 &       & {-} & 16    & 5.7243 & 15    & {5.6803} \\
			17    & 42.082 & 11    & {41.246} & 17    & 28.81 &       & {-} & 17    & 10.365 & 13    & 10.286 & 17    & 6.6585 & 16    & {6.6025} \\
			18    & 51.427 &       & -     & 18    & 30.737 & 13    & 30.413 & 18    & 11.934 & 14    & 11.817 & 18    & 7.2935 & 17    & {7.2474} \\
			19    & 56.963 & 12    & {56.1} & 19    & 30.83 & 14    & 30.413 & 19    & 13.915 & 15    & 13.767 & 19    & 7.7966 &       & - \\
			20    & 57.741 &       & -     & 20    & 32.414 &       &       & 20    & 15.109 & 16    & 14.974 & 20    & 9.7996 &       & - \\
			\hline
			\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{2.2695\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{1.3816\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{1.0657\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{0.84102\%} \\
			\hline
		\end{tabular}%
		\label{tab:Table_plate_2}%
	}}
\end{table}%
\FloatBarrier

Similarly, Table \ref{tab:Table_plate_2} also show that a cantilever Reissner-Mindlin plate compares very well to a cantilever three-dimensional plate for $b=1$ which can be considered a wide plate.\\

Table \ref{tab:Table_plate_2_2} presents some more results without showing all the eigenvalues.

\FloatBarrier
\begin{table}[htbp]
	\centering
	\caption{Maximum relative error of the first 10 comparable eigenvalues with d=1.}
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\multicolumn{6}{|c|}{Max Relative Error } \\ 
		\hline 
		\hline
		b = 1/2 & b = 1/5 & b = 1/10 & b = 1/20 & b = 1/30 & b = 1/50\\ \hline
		3.9342\% & 2.2695 \% & 1.3816 \% & 1.0657 \% & 0.84101 \% & 0.38181 \% \\ \hline
	\end{tabular}%
	\label{tab:addlabel}%
\end{table}%

\end{document}

### 2022-10-31 files/Introduction.tex
initial commit

\documentclass[../main.tex]{subfiles}
\begin{document}
This dissertation is a literature study that focusses on the comparison of popular simplified models to more complex three-dimensional versions of the models. This comparison is restricted the eigenvalues and eigenfunctions of the different models.\\

\textbf{Motivation and Problem Identification}\\
From small transverse vibration of a linearly elastic (flat) plate [Mindlin, 1951], to a fully non-linear shell model, numerous mathematical problems are possible. (The same remark is also true for beams.) In this research project, our focus is on the small vibrations but not sufficiently small to justify a linear model.\\

In the article of [Antman,1976], we see that the author takes a rigorous mathematical approach to obtain fully general theories of non-linearly elastic rods and shells from three-dimensional theories. In a follow up article [Antman,1996], open problems of nonlinear elastic rods are investigates and references are made to 4 articles of Simo and Vu-Quoc. Where [Antman,1976] follows a vigorous math approach, [Simo and Vu-Quoc,1987] follows an engineering approach. Their work however, received wide recognition and it is worthwhile to compare their articles to the work of [Antman,1976] and [Antman,1996].\\

In applications simplified models can be used with some additional but different assumptions and it leads to different models for the same real life problem. An example of where numerous models are used to study the same real world problem is the Tacoma Narrows Bridge disaster of 1940. [Gazzola, 2013] and [McKenna,1999] both derive models for this specific problem but with different approaches. Even though both authors agree on the shortcomings of many bridge models and that non-linear theories should be used, [Gazzola, 2013] insists on using a plate to model the bridge, while [McKenna,1999] uses a beam. This gives at least two different models for the same real world problem.\\

\textbf{Research Methodology}\\
The main objective of this literature study is the comparison of such models, using either analysis or a finite element method simulation. Adding assumptions to a general model leads to many different simplified models that can be applied to the same situation. It is important to investigate the differences in these models and their applicability to real world problems.\\

Calculating solutions for these models will be useful for the comparison, but due to the complexities of the problems, numerical methods are used to obtain approximate solutions. The finite element method is generally accepted to be the best for elasto-mechanics. Appropriate articles will be used to ensure convergence of the solutions.\\

This study will also look at possible simplifications to the models through the addition of more assumptions. Examples of simplifications to models is the added assumption of rigidity of a beam model. This simplifies the model from a system of partial differential equations, to a system of ordinary differential equations.\\

This masters research is an in depth literature study with a main focus on model problems on shells and rods with attention given to:
\begin{itemize}
	\item Comparison of different models for the same problem either using analysis or numerical methods.
	\item Determining existence of solutions, given that the relevant articles are available.
	\item Convergence of finite element method when calculating solutions to the model problems.
\end{itemize}

The term validity in this case will refer to how well the solutions of the models compare to a ``realistic'' model. Ideally one would want to compare the models to a perfectly realistic model. But since no such realistic model truly exists, some simplifications have to be made. For this dissertation, the three-dimensional models are the most realistic, while the one-dimensional are the least realistic. The two-dimensional models can be seen as an intermediate step between the one and three-dimensional models.\\

As seen in \ref{ssec:1D_Model:Modal}, the solutions of second order hyperbolic type problems can be expressed as a linear combination of the eigenvalues and eigenfunctions. So to be able to compare the different models of this dissertation, it is sufficient to compare the eigenvalues and the shapes of the eigenfunctions.\\

This idea to determine the validity of the models follows form the work done in [LVV08]. In this article, the authors compared a Timoshenko cantilever beam to a two-dimensional cantilever beam. The comparison was made by comparing the eigenvalues as well as comparing some of the mode shapes. The authors were able to show that the Timoshenko model compares very well to the two-dimensional beam model. The work of [LVV08] is revisited in this chapter and extended to a three-dimensional cantilever beam and also plate theory.\\

The eigenvalues and eigenfunctions for the Timoshenko beam are calculated using the method for [VV06] (this was discussed in \ref{sec:Timo:EigenvalueProblem}). The frequency equation is sketched and the eigenvalues are found using interval division. This insures that no eigenvalues are skipped and the accuracy can be determined to a desired level. Other methods can also be used to obtain the eigenvalues. The method presented in [VV06] also allows the mode shapes to be determined if the eigenvalues are found. The results for the Timoshenko beam in this section are accurate up to 5 significant digits.\\

The eigenvalues and eigenfunctions for the two and three-dimensional models and the Reissner-Mindlin plate model are calculated using the Finite Element Method. For each model, the eigenvalue problem is described in Chapter 5. The first 30 eigenvalues are accurate to at least 5 significant digits. The rest of the eigenvalues are accurate to at least 4 significant digits.\\

To be able to match the eigenvalues of the different models for the comparison, the modal shapes are sketched and their shapes are compared. Similar shapes will imply that the eigenvalues can be compared. In this chapter, the eigenvalues relating to the mode shape of the Timoshenko beam model is referred to as ``beam-type'' eigenvalues. Similarly eigenvalues relating to the mode shape of the Reissner-Mindlin plate model is referred to as ``plate-type'' eigenvalues.

\textcolor{red}{*****************test*************}\\
Since the cross-section is square, the area moment of inertia for the Timoshenko beam and the plate model can be calculated. For the Timoshenko beam model, the area moment of inertial is 
\begin{eqnarray*}
	I = \frac{h^3b}{12}.
\end{eqnarray*}

Using the definition if the dimensionless parameter $\alpha$, the following relationship between $\alpha$ and $h$ is found
\begin{eqnarray*}
	h = \sqrt{\frac{12}{\alpha}}
\end{eqnarray*}

\textcolor{red}{******************************}

\end{document}

### 2022-10-31 files/Overview.tex
initial commit

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Overview}
\begin{itemize}
	\item Chapter 1: Models, Dimensionless, Variational Forms, Modal Analysis
	\item Chapter 2: Example Weak Variational, Existence and Uniqueness from [VV02], Application to example
	\item Chapter 3: Example Galerkin, Convergence of Galerkin [BV13], Application to example, Convergence of Eigenvalues using FEM
	\item Chapter 4: Eigenvalues of Timo [VV06], Example of applications on models, Emperical Study of validity [SP06], Cantilever with Tip-Body (Example why need validity)
	\item Chapter 5: FEM of 2D, 3D, and Plate
	\item Chapter 6: Validity of 1D, Validity of 2D, Validity of Plate
	\item Chapter 7: Conclusion
\end{itemize}

In chapter 1, word al die modelle gegee wat in die dissertation gebruik word. Die modelle word in dimenielose form herskryf. Die modelle is dan herskryd in variational form wat gebruik gaan word vir die res van die verhandeling. Modal analysis word ook in chapter 1 verduidelik in hand vn 'n voorbeeld.\\

 In Chapter 2 word die werk van die artikel [VV02] gebruik om na die existence and uniqueness of solutions van second order hyperbolic equations te kyk. Die cantilever beam word as 'n voorbeeld gebruik om die werk te verduidelik.\\

 Chapter 3 kyk na die convergence van die FEM. Dit volg die werk van die artikel [XX]. Die methode van die artikel is om error estimates vir die fully discrete vartiational problem (Galerkin Approximation) te bepaal. In die tweede deel van chapter 3, word daar na die convergence van die eigenvalues en eigenvectors in die FEM gekyk. Dit volg die werk van die handboek [XX] en word in beter notation oorgeskryf.\\

 Chapter 4 fokus op the Timoshenko beam. Eerste word daar gekyk na die eigenvalue problem van die Timoshenko beam theory. Die artikel [VV06] gee die nodige werk om die eigenvalues en eigenvectors exactly uit te werk. Die methode word dan op 'n free-free beam en ook 'n cantilever beam toe gepas waar die eiewaarde uitgewerk word en ook die eigenfunctions geskets word. Daar is dan navorsing gedoen deur [SP06] wat gekyk het hoe goed 'n Timoshenko beam theory vergelyk met 'n 3D en 'n regte balk. Die navorsing wys dat die Timoshenko goed vergelyk die die regte balk in 'n free-free configuration. Die navorsing van [SP06] word discuss en gebruik dit as motiveering vir verdere numeriese simulation. Laaste deel in chapter 4 is 'n voorbeeld van 'n Timoshenko beam in 'n model wat meer real world application het. Dit is in die tegniese report van [XX]. Die werk in die chapter oor die tip body balk is net gefokus op die numeriese simulation.\\

 Chapter 5 gaan oor die plaat model. Die chapter doen die FEM analiese van die cantilever model. Die chapter le oook die reference configuration uit vir 'n rectangular plate model en adress die shear correction factor. Kan moontlik deel word van die volgende chapter.\\

 Chapter 6 is dieselfde as die vorige chapter Die chapter hanteer die FEM analise vir die twee en drie dimensionele elastic bodies. Die reference configuration is vir 'n rectangular form vir beide sodat dit later gebruik kan word indie volgende chapter. Die chapter gee ook die eigenvalue problems en wys wys dat die regte accuracy kan obtained word die die eiewaardes numeries uit te werk.\\

 Die laaste chapter hanteer die hoof numeriese werk van die verhandeling. Die die chapter word die validityvna die timoshenko beam asook die plaat model ondersoek. Eerste word die timoshenko beam met 'n twee-D beam vergelyk. Die is dieselfde as die artikel [XX]. So dieselfde werk word gedoen as die artikel, maar met aner waardes. Die werk word dan extend deur die twee-D model te vergelyk met die 3D model. Die modelle is elastic bodies, so daar work ook apart na die beam-type en non-beam type dele gekyk. Die eiewaardes word vergelyk met verskillende diktes va die 3D model en dan word daar gekyk na die eiefunksies se forms. Dan 
\end{document}

### 2022-10-31 summary.tex
initial commit

\documentclass[main.tex]{subfiles}
\begin{document}
\begin{center}
	\large \textbf{Summary}
\end{center}
This dissertation is a literature study, investigating the Finite Element Analysis of multidimensional and simplified beam and plate models. The Timoshenko beam and Reissner-Mindlin plate theories are popular theories used in mathematics and engineering. An example of ongoing research using these theories is the study of suspension bridges. The articles \cite{McK99}, \cite{BOC20} are examples of mathematical studies while \cite{SV86} follows an engineering approach.\\

 This dissertation is a literature study on the Finite Element Analysis 
 \begin{itemize}
	\item Considering linear mathematical model s for elastic beams and plates.
	\item Focus is on the one-dimensional Timoshenko beam theory and two-dimensional Reissner-Mindlin plate theory
	\item Also require two and three-dimensional beam models and a three-dimensional plate model
	\item Models are used in variational form (Chapter 1)
	\item Existence and uniqueness of solutions (Chapter 2)
	\item Convergence of FEM (Chapter 3)
	\item Chapter 4: - Timoshenko beam theory - Modal analysis - Examples of calculating eigenvalues and eigenvectors - Emperical study - Tipbody model with numerical results.
	\item Chapter 5: FEM applied to cantilever 3D, 2D and plate elastic bodies
	\item Chapter 6: Validity of Timo and Reissner-Mindlin Models
\end{itemize}

\end{document}

### 2022-11-02 files/Chapter3/dynamicconvergence.tex
Chapter 3 work on first part

@@
 \ w_n \rangle$ for each $w_h \in S^h$.
-Denote the problem of solving the Galerkin Approximation of Problem GVar, by Problem GVar$^h$.
+The problem of solving the Galerkin Approximation is denoted by Problem GVar$^h$.
 
@@
 However to obtain an error estimate for $e$ is not trivial.
-The approach of the authors is to use Finite Element Analysis to obtain an error estimate for $e$.
+The approach of the authors is to use Finite Element Analysis to obtain an error estimate for $e$.\\
 
+Now we look at the main results of \cite{BV13}.
 \subsection{Main result}
@@
 
-\newtheorem*{DC_Thm5}{Theorem 3}
+To solve the error estimate $e$, the following theorem is proved in \cite{BV13}.
+
+\newtheorem*{DC_Thm5}{Theorem 2}
 \begin{DC_Thm5}
-	Error estimate\\
+	{Main Result}\\
 	If $f\in C^{2}([0,T],X)$, then
@@
 \end{DC_Thm5}
+
+As mentioned before, the authors use Finite Element Analysis to obtain an error estimate for $e$. What follows is a discussion of the approach used in \cite{BV13}.
 
@@
 
-Using these matrices, Problem GVar$^h$ is rewritten as a system of ordinary differential equations.
+Using these matrices, Problem GVar$^h$ is rewritten as a system of ordinary differential equations denoted by Problem ODE.
 \subsubsection*{Problem ODE}
@@
 \end{eqnarray}
-The function $F(t)$ is the interpolation of the function $f(x,t)$ into the discrete space $S^h$. \\
+The function $F$ is the interpolation of the function $f$ into the discrete space $S^h$.\\
 
-The following propositions are given in \cite{BV13}. The proof of Theorem 1 follows from these two propositions.
+The following propositions for Problem ODE are given in \cite{BV13}.
 
@@
 \begin{DC_Prop2}
-	Suppose $M, K, C, F,\bar{d}$  and $\bar{v}$ are defined as above. Then, the function $u_{h}$ is a solution of Problem $G^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
+	If $F\in C(J)$, then Problem ODE has a unique solution for each pair of vectors $\bar{d}$ and $\bar{v}.$
 \end{DC_Prop2}
 
-Since the matrix $M$ is invertible, \eqref{ODE} can be rewritten as $\bar{u}'' + M^{-1}C\bar{u}' + M^{-1}K \bar{u} = M^{-1}F(t)$.
+Since the set $\{\phi_1, \ \phi_2,...,\phi_n\}$ is a linearly independent basis for $S^h$, the bilinear form $c$ is positive definite on $S^h$.
+Therefore, the matrix $M$ is invertible.
+The equation \eqref{ODE} of Problem ODE can be rewritten as $\bar{u}'' + M^{-1}C\bar{u}' + M^{-1}K \bar{u} = M^{-1}F(t)$.
 Using the theory of linear differential equations, a unique solution for Problem ODE can be found.
-This proves Proposition 2.
+This proves Proposition 1.\\
+
+Proposition 2 provides a link between the solution of Problem ODE and the solution of Problem GVar$^h$.
 
@@
 \begin{DC_Prop3}
-	If $F\in C(J)$, then Problem ODE has a unique solution for each pair of vectors $\bar{d}$ and $\bar{v}.$
+	Suppose $M, K, C, F,\bar{d}$ and $\bar{v}$ are defined as above. Then, the function $u_{h}$ is a solution of Problem GVar$^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
 \end{DC_Prop3}
 
-The \cite{BV13}, the authors first investigate a semi-discrete Galerkin approximation.
-In this semi-discrete approximation, $x$ is discretised and $t$ remains continuous.
-Results for the semi-discrete approximation are required for the results of the fully-discrete approximation.\\
+Consider the time interval $J = [0,T]$.
+Divide $J$ into $N$ steps with length $\tau = \frac{T}{N}$.
+Each interval can be expressed as $[t_{k-1}, \ t_k]$ for $k = 1,...,N$.
+Denote the approximation of $u_h$ on the interval $[t_{k-1}, \ t_k]$ by $u_k^h$, i.e.
+$u_h(t_k) = u_k^h$ for each $k$.\\
 
-The results for the semi-discrete problem are necessary, since later in \eqref{error_e} it will be shown that the error $e(t)$ can be split up into a semi-discrete term and a fully-discrete term.
+The error $e(t)$, can now be expressed as
+\begin{eqnarray}
+	e(t_k) = u(t_k) - u^h_k & = & [u(t_k)-u_h(t_k)] + [u_h(t_k) - u^h_k]. \label{error_e}
+\end{eqnarray}
 
-\sout{Before the fully discrete Galerkin Scheme is investigated, a result from \cite{BV13} on semi-discrete error estimates is required.}\\
+In \eqref{error_e}, the authors divide the error $e$ into a semi-discrete term and a fully discrete term. The two terms are investigated separately in \cite{BV13}.
+
 \subsection{Semi-discrete error estimate}

### 2022-11-03 files/Chapter3/dynamicconvergence.tex
Fixing missing work in Chapter 3.

@@
 
-To start, the authors of \cite{BV13} formulate the Galerkin Approximation of Problem GVar.
+Before we can look at the results of \cite{BV13}, some preparation is required. To start, the authors of \cite{BV13} formulate the Galerkin Approximation of Problem GVar.
 
@@
 	w_h = \sum_{j=1}^n w_j \phi_j.
-\end{eqnarray*} Define a vector valued function $\bar{w} = \langle w_1 \ w_2 \ ...
-\ w_n \rangle$ for each $w_h \in S^h$.
-The problem of solving the Galerkin Approximation is denoted by Problem GVar$^h$.
+\end{eqnarray*} Define a vector valued function $\bar{w} = \langle w_1,w_2,...,w_n \rangle$ for each $w_h \in S^h$. The problem of solving the Galerkin Approximation is denoted by Problem GVar$^h$.
 
@@
 
-\subsection{Error estimates}
+\subsection{System of ordinary differential equations}
+Consider the standard FEM matrices defined by
+\begin{eqnarray*}
+	K_{ij} & = & b(\phi_j, \phi_i)\\
+	C_{ij} & = & a(\phi_j, \phi_i)\\
+	M_{ij} & = & c(\phi_j, \phi_i)\\
+	F_{i}(t) & = & b(f(t), \phi_i)
+\end{eqnarray*}
+
+Using these matrices, Problem GVar$^h$ is rewritten as a system of ordinary differential equations denoted by Problem ODE.
+\subsubsection*{Problem ODE}
+Find a function $\bar{u} \in S^h$ such that
+\begin{eqnarray}
+	M\bar{u}'' + C \bar{u}' + K\bar{u} = F(t) \ \ \ \textrm{ with } \bar{u}(0) = \bar{u}^h_0 \textrm{ and }  \bar{u}(1) = \bar{u}^h_1 \label{ODE}
+\end{eqnarray}
+The function $F$ is the interpolation of the function $f$ into the discrete space $S^h$.\\
+
+The following propositions for Problem ODE are given in \cite{BV13}.
+
+\newtheorem{DC_Prop2}{Proposition}
+\begin{DC_Prop2}
+	If $F\in C(J)$, then Problem ODE has a unique solution for each pair of vectors $\bar{u}^h_0$ and $\bar{u}^h_1$
+\end{DC_Prop2}
+
+Since the set $\{\phi_1, \ \phi_2,...,\phi_n\}$ is a linearly independent basis for $S^h$, the bilinear form $c$ is positive definite on $S^h$.
+Therefore, the matrix $M$ is invertible.
+The equation \eqref{ODE} of Problem ODE can be rewritten as $\bar{u}'' + M^{-1}C\bar{u}' + M^{-1}K \bar{u} = M^{-1}F(t)$.
+Using the theory of linear differential equations, a unique solution for Problem ODE can be found.
+This proves Proposition 1.\\
+
+Proposition 2 provides a link between the solution of Problem ODE and the solution of Problem GVar$^h$.
+
+\newtheorem{DC_Prop3}[DC_Prop2]{Proposition}
+\begin{DC_Prop3}
+	Suppose $M, K, C, F,\bar{u}^h_0$ and $\bar{u}^h_1$ are defined as above.
+Then, the function $u_{h}$ is a solution of Problem GVar$^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
+\end{DC_Prop3}
+
+\subsection{Error estimates}\label{e_est}
 Given that the assumptions \textbf{A1}-\textbf{A4} of Section 2 is satisfied, and $f$ is continuous, there exists unique solutions for  Problem GVar and Problem GVar$^h$.
@@
 
+Consider the time interval $J = [0,T]$.
+Divide $J$ into $N$ steps with length $\tau = \frac{T}{N}$.
+Each interval can be expressed as $[t_{k-1}, \ t_k]$ for $k = 1,...,N$.
+Denote the approximation of $u_h$ on the interval $[t_{k-1}, \ t_k]$ by $u_k^h$, i.e.
+$u_h(t_k) = u_k^h$ for each $k$.\\
+
+The error $e$, can now be expressed as
+\begin{eqnarray}
+	e(t_k) = u(t_k) - u^h_k & = & [u(t_k)-u_h(t_k)] + [u_h(t_k) - u^h_k]. \label{error_e}
+\end{eqnarray}
+
+In \eqref{error_e}, the authors divide the error $e$ into a semi-discrete term and a fully discrete term. The two terms are investigated as seperate problems in \cite{BV13}.\\
+
 Now we look at the main results of \cite{BV13}.
 \subsection{Main result}
-
-The following two assumptions are made in \cite{BV13}.
-\subsubsection*{Assumptions}
-\begin{itemize}
-	\item[] \textbf{B1} - The solution $u \in C(J,V)$ of Problem GVar$^h$ has the property that $(Pu) \in C^2(J)$.
-
-	\item[] \textbf{B2} - There exists a subspace $H$ of $V$ and a positive integer $\alpha$ such that if $w \in H$, then $$\inf_{v\in S^{h}}||w-v||_V \leq \hat{C} h^\alpha|||w|||_H,$$ where $|||w|||_H$ is a norm or a semi-norm for $H$.
-\end{itemize}
-
-To solve the error estimate $e$, the following theorem is proved in \cite{BV13}.
 
@@
 
-As mentioned before, the authors use Finite Element Analysis to obtain an error estimate for $e$. What follows is a discussion of the approach used in \cite{BV13}.
+\subsection{Obtaining the error estimate}
+In this section we will show how the error estimate in Theorem 2 is obtained in \cite{BV13}.\\
 
-\subsection{System of ordinary differential equations}
-Consider the standard FEM matrices defined by
+The following two assumptions are made in \cite{BV13}.
+
+\subsubsection*{Assumptions}
+\begin{itemize}
+	\item[] \textbf{B1} - The solution $u \in C(J,V)$ of Problem GVar$^h$ has the property that $(Pu) \in C^2(J)$.
+
+	\item[] \textbf{B2} - There exists a subspace $H$ of $V$ and a positive integer $\alpha$ such that if $w \in H$, then $$\inf_{v\in S^{h}}||w-v||_V \leq \hat{C} h^\alpha|||w|||_H,$$ where $|||w|||_H$ is a norm or a semi-norm for $H$.
+\end{itemize}
+
+The projection $P$ in section \eqref{e_est} is defined in \cite{BV13} as
 \begin{eqnarray*}
-	K_{ij} & = & b(\phi_j, \phi_i)\\
-	C_{ij} & = & a(\phi_j, \phi_i)\\
-	M_{ij} & = & c(\phi_j, \phi_i)\\
-	F_{i}(t) & = & b(f(t), \phi_i)_X
+	b(u-P_hu,v) = 0 \ \ \ \textrm{ for all } v \in V.
 \end{eqnarray*}
 
-Using these matrices, Problem GVar$^h$ is rewritten as a system of ordinary differential equations denoted by Problem ODE.
-\subsubsection*{Problem ODE}
-Find a function $\bar{u} \in S^h$ such that
+From assumption \textbf{B1}, $Pu \in C^2(J)$ and by the definition $P$, $P$ is a projection with respect to the inner product $b$.\\
+
+Subtracting \eqref{GV_PB1} from \eqref{DC_E2} gives
+\begin{eqnarray*}
+	c(u''(t)-u''_h(t),v) + a(u'(t)-u'_h(t),v) + b(u(t)-u_h(t),v) = 0
+\end{eqnarray*}
+
+Using the definition of the error $e^h$ while also adding and subtracting $Pu(t)$ in the bilinear form $b$, we can write
+\begin{eqnarray*}
+	c(e''(t),v) + a(e'(t),v) + b(u(t) - Pu(t),v) + b(Pu(t) +u_h(t),v)- = 0
+\end{eqnarray*}
+
+It then follows from the definitions of the error $e$ and the projection $P$ that 
+\begin{eqnarray*}
+	c(e''(t),v) + a(e'(t),v) + b(e(t),v) = 0
+\end{eqnarray*}
+
+In \cite{BV13}, this is presented as a proposition.
+\newtheorem{DC_Prop1}{Proposition}
+\begin{DC_Prop1}
+	If $u$ is the solution of Problem GVar and $u$ satisfies assumption \textbf{B1}, then
+
 	\begin{eqnarray}
-	M\bar{u}'' + C \bar{u}' + K\bar{u} = F(t) \ \ \ \textrm{ with } \bar{u}(0) = \bar{u}^h_0 \textrm{ and }  \bar{u}(1) = \bar{u}^h_1 \label{ODE}
+		c(e''(t),v) + a(e'(t),v) + b(e(t),v) = 0 \ \ \ \textrm{ for all } v \in V.
 	\end{eqnarray}
-The function $F$ is the interpolation of the function $f$ into the discrete space $S^h$.\\
+\end{DC_Prop1}
 
-The following propositions for Problem ODE are given in \cite{BV13}.
+Using this proposition, the authors of \cite{BV13} derive a generalized error estimate for the error $e = Pu - u_h$.
 
-\newtheorem{DC_Prop2}{Proposition}
-\begin{DC_Prop2}
-	If $F\in C(J)$, then Problem ODE has a unique solution for each pair of vectors $\bar{d}$ and $\bar{v}.$
-\end{DC_Prop2}
+\newtheorem{lem_1}{Lemma}
+\begin{lem_1}
+	If $u$ is the solution of Problem GVar and $u$ satisfies assumption \textbf{B1}, then
+	\begin{eqnarray}
+		\Vert e(t)\Vert_{W} \leq \sqrt{2} \left( \Vert e(0) \Vert_W + 3T\Vert e'_h(0) \Vert_W + 3 \int_o^T \Vert e'_p(t)\Vert_W + 3K_\alpha T \Vert e_h(0) \Vert_W + 3K_\alpha \int_0^T \Vert e_p(t) \Vert_W \right).
+	\end{eqnarray}
+\end{lem_1}
 
-Since the set $\{\phi_1, \ \phi_2,...,\phi_n\}$ is a linearly independent basis for $S^h$, the bilinear form $c$ is positive definite on $S^h$.
-Therefore, the matrix $M$ is invertible.
-The equation \eqref{ODE} of Problem ODE can be rewritten as $\bar{u}'' + M^{-1}C\bar{u}' + M^{-1}K \bar{u} = M^{-1}F(t)$.
-Using the theory of linear differential equations, a unique solution for Problem ODE can be found.
-This proves Proposition 1.\\
+In chapter 2, it was explained that the models of this dissertation have weak damping, i.e.
+$a = 0$.
+Therefore, the error estimate in Lemma 1 can be simplified.
+This is given in \cite{BV13} as a corollary.
 
-Proposition 2 provides a link between the solution of Problem ODE and the solution of Problem GVar$^h$.
+\newtheorem{col_1}{Corollary}
+\begin{col_1}
+	If $u$ is the solution of Problem GVar with $a = 0$ and $u$ satisfies assumption \textbf{B1}, then
+	\begin{eqnarray}
+		\Vert e(t)\Vert_{W} \leq \sqrt{2} \Vert e(0) \Vert_W + 4\sqrt{T}\max_{t \in [0,T]} \Vert e'_p(t) \Vert_W.
+	\end{eqnarray}
+\end{col_1}
 
-\newtheorem{DC_Prop3}[DC_Prop2]{Proposition}
-\begin{DC_Prop3}
-	Suppose $M, K, C, F,\bar{d}$ and $\bar{v}$ are defined as above. Then, the function $u_{h}$ is a solution of Problem GVar$^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
-\end{DC_Prop3}
-
-Consider the time interval $J = [0,T]$.
-Divide $J$ into $N$ steps with length $\tau = \frac{T}{N}$.
-Each interval can be expressed as $[t_{k-1}, \ t_k]$ for $k = 1,...,N$.
-Denote the approximation of $u_h$ on the interval $[t_{k-1}, \ t_k]$ by $u_k^h$, i.e.
-$u_h(t_k) = u_k^h$ for each $k$.\\
-
-The error $e(t)$, can now be expressed as
-\begin{eqnarray}
-	e(t_k) = u(t_k) - u^h_k & = & [u(t_k)-u_h(t_k)] + [u_h(t_k) - u^h_k]. \label{error_e}
-\end{eqnarray}
-
-In \eqref{error_e}, the authors divide the error $e$ into a semi-discrete term and a fully discrete term. The two terms are investigated separately in \cite{BV13}.
-
-\subsection{Semi-discrete error estimate}
+\subsection{Semi-discrete problem}
 
@@
 \end{eqnarray*}
-
-The authors of \cite{BV13} introduce two assumptions.
-\subsubsection*{Assumptions} 
-\begin{itemize}
-	\item[] \textbf{E1} - The solution $u$ of Problem GVar has the property that $(Pu) \in C^2(0,T)$.
-
-	\item[] \textbf{E2} -There exists a subspace $H$ of $V$ and a positive integer $\alpha$ such that if $w\in H,$ then
-	\begin{eqnarray*}
-		\inf_{v\in S^{h}}\Vert w-v\Vert_{V}\leq\hat{C}h^{\alpha}|||w|||_{H},
-	\end{eqnarray*}
-	where $|||w|||_{H}$ is a norm or semi-norm for $H.$
-\end{itemize}
 

### 2022-11-03 files/Chapter3/dynamicconvergence.tex
adding to chapter 3

@@
 \subsection{Obtaining the error estimate}
-In this section we will show how the error estimate in Theorem 2 is obtained in \cite{BV13}.\\
-
-The following two assumptions are made in \cite{BV13}.
+In this section we will show how the error estimate in Theorem 2 is obtained in \cite{BV13}.The following two assumptions are made in \cite{BV13}.
 
@@
 	\begin{eqnarray}
-		\Vert e(t)\Vert_{W} \leq \sqrt{2} \left( \Vert e(0) \Vert_W + 3T\Vert e'_h(0) \Vert_W + 3 \int_o^T \Vert e'_p(t)\Vert_W + 3K_\alpha T \Vert e_h(0) \Vert_W + 3K_\alpha \int_0^T \Vert e_p(t) \Vert_W \right).
+		\Vert e(t)\Vert_{W} &\leq& \sqrt{2} \biggl( \Vert e(0) \Vert_W + 3T\Vert e'_h(0) \Vert_W + 3 \int_o^T \Vert e'_p(t)\Vert_W\nonumber \\ 
+		&& + 3K_\alpha T \Vert e_h(0) \Vert_W + 3K_\alpha \int_0^T \Vert e_p(t) \Vert_W \biggr). \label{fundamental_estimate}
 	\end{eqnarray}
@@
 	\begin{eqnarray}
-		\Vert e(t)\Vert_{W} \leq \sqrt{2} \Vert e(0) \Vert_W + 4\sqrt{T}\max_{t \in [0,T]} \Vert e'_p(t) \Vert_W.
+		\Vert e(t)\Vert_{W} \leq \sqrt{2} \Vert e(0) \Vert_W + 2T||e'_h(0)||_W + 4\sqrt{T}\max_{t \in [0,T]} \Vert e'_p(t) \Vert_W.
 	\end{eqnarray}
@@
 
-\subsection{Semi-discrete problem}
+\subsubsection{Semi-discrete problem}
+The estimate \eqref{fundamental_estimate} in Lemma 1 is equivalent to
+\begin{eqnarray*}
+	\Vert u(t) - u_h(t) \Vert_{W} &\leq& \sqrt{2} \biggl( \Vert u(0) - u_h(0) \Vert_W + 3T\Vert e'_h(0) \Vert_W + 3 \int_o^T \Vert e'_p(t)\Vert_W\nonumber \\ 
+	&& + 3K_\alpha T \Vert e_h(0) \Vert_W + 3K_\alpha \int_0^T \Vert e_p(t) \Vert_W \biggr).
+\end{eqnarray*}
 

### 2022-11-08 files/Chapter3/dynamicconvergence.tex
klein verbeteringe

@@
 
-Before we can look at the results of \cite{BV13}, some preparation is required. To start, the authors of \cite{BV13} formulate the Galerkin Approximation of Problem GVar.
+Before the theory of \cite{BV13} can be discussed, some preparation is required.
+First the Galerkin approximation is for Problem GVar is derived.
+Then a equivalent system of ordinary differential equations is derived using the Finite Element Method.
+The problem is then discussed followed by the solution of \cite{BV13}.\\
 

### 2022-11-08 files/Chapter6/2D_FEM.tex
klein verbeteringe

@@
 The aim of this chapter is to obtain a numerical formula to calculate the eigenvalues and eigenvectors for these models.
-This chapter serves as preparation for Chapter 6.\\
+This chapter is preparation for Chapter 6.\\
 
@@
 \begin{itemize}
-	\item[] Section \ref{sec:FEM:2D} is the FEM for a two-dimensional cantilever body.
-	\item[] Section \ref{sec:FEM:3D} is the FEM for a three-dimensional cantilever body. 
-	\item[] Section \ref{sec:FEM:Plate} is the FEM for A Reissner-Mindlin cantilever plate model. 
+	\item[] Section \ref{sec:FEM:2D} FEM for a two-dimensional cantilever body.
+	\item[] Section \ref{sec:FEM:3D} FEM for a three-dimensional cantilever body. 
+	\item[] Section \ref{sec:FEM:Plate} FEM for A Reissner-Mindlin cantilever plate model. 
 \end{itemize}
@@
 \subsubsection{Cantilever elastic body}
-Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$.
-The body is free-hanging on the other boundaries This is referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
+Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries This is Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
 \FloatBarrier
@@
 In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is defined by Problem 2D-1V.
-For convenience, the relevant results from section \ref{ssec:2D_Model:VariationalForm} are repeated.
+For convenience, some results from section \ref{ssec:2D_Model:VariationalForm} are repeated here.
+
 \subsubsection{Problem 2D-1V}\label{sssec:2D_Model:Problem2D1VChp5}
@@
 
-This form of the bilinear form $b$ is more useful than the general form in \eqref{eq:2D_Model:BilinearChp5} to apply the Finite Element Method.
-
 \subsection{Weak variational form}
@@
 \begin{eqnarray*}
-S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right)
+S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right).
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x)
+	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x).
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I \cdot \phi_i)
+	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I, \phi_i)
 \end{eqnarray*} for $i = 1,2,...,k$.\\
@@
 \begin{itemize}
-	\item[] $Q^I$ is scalar vector that is the result of interpolating the function $Q$ over the rectangular grid. i.e. $Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.
+	\item[] $Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$. i.e. $Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.
 \end{itemize}

### 2022-11-08 files/Chapter2/generalvibrationmodel.tex
improvements chapter 2

@@
 The product space {$V(0,1)\times V(0,1)$} is denoted by $V$ and is complete.
-$V$ is called the energy space.\\
+It is called the energy space.\\
 
@@
 \end{eqnarray*}
-for all $v\in V$.\\
+for all $v\in V$. The initial conditions $u(0) = u_0$ and $\dot{u}(0)=u_1$ must be specified.\\
 
@@
 \begin{Thm2n}[Weak Damping]
-	If $a$ is bounded with respect to the norm in $W$, then there exists a unique solution $u\in C^1(J,V)\cap C^2(J,W)$ for Problem GVar for each $u_0 \in E_b$.
-each $u_1 \in V$ and each $f\in C^1(J,X)$.
+	If $a$ is bounded with respect to the norm in $W$, then there exists a unique solution $u\in C^1(J,V)\cap C^2(J,W)$ for Problem GVar for each $u_0 \in E_b$. each $u_1 \in V$ and each $f\in C^1(J,X)$.
 \end{Thm2n}
@@
 
-As mentioned before, if $a = 0$ then the inequalities in \eqref{weak_damping} hold trivially.
-However, the operator A is defined by the operator $\Lambda$ and in the definition of $\Lambda$, the form $a$ is used (see \eqref{author_mapping}).\\
-
-\vspace{10mm}
- derivation of this linear operator remains unchanged as presented in \cite{VV02} for $a$ identically zero.\\
- \vspace{10mm}
+As mentioned before, if $a = 0$ then the inequality in \eqref{weak_damping} hold trivially.
+However, the operator A is defined by the operator $\Lambda$ and in the definition of $\Lambda$, the form $a$ is used (see \eqref{author_mapping}).
+It is proved in \cite{VV02} that equation \eqref{author_mapping} is uniquely solvable and hence $\Lambda$ is well defined.
+The proof remains unchanged as presented for $a$ identically zero.\\
 
 To apply Theorem 2, the admissible initial conditions are $u_0 \in E_b$ and $u_1 \in V$.
-As mentioned $\langle u_0, u_1 \rangle \in D(A)$.
-From semigroup theory, it follows that $u(t) \in D(A)$ for each $t$.
+As mentioned above, this implies $\langle u_0, u_1 \rangle \in D(A)$.
+From semigroup theory, it follows that $U(t) \in D(A)$ for each $t$.
 Therefore $u(t) \in E_b$ and $u'(t) \in V$ for each $t$.\\
 
-\textcolor{red}{Volgende Rondte}\\
- Using the assumptions \textbf{A1}-\textbf{A4}, they prove that this linear operator $A$ is an infinitesimal generator of a $C_0$-semigroup of contractions and the domain of $A$ is dense in $H$.
+Using the assumptions \textbf{A1}-\textbf{A4}, it is proved in \cite{VV02} that the linear operator $A$ is an infinitesimal generator of a $C_0$-semigroup of contractions and the domain of $A$ is dense in $H$ (see Section \ref{sec:existence:ModalAnalysis}).
 
@@
 
-\textcolor{red}{ALLES NOG NIE BEWYS NIE - moet nog doen}
+To apply the theory, Problem T-2W must satisfy assumptions \textbf{A1}-\textbf{A4} and the initial values must be admissible. We must show that the assumptions are satisfied.\\
 
- To apply the theory, Problem T-2W must satisfy assumptions \textbf{A1}-\textbf{A4} and the initial values must be admissible.
+To prove \textbf{Assumption A1}, observe that $W$ is dense in $X$. (The set $W = X$).\\
 
-\subsubsection{Assumption A1}\label{sssec:existence:AssumptionA1}
-It is clear that $W$ is dense in $X$. (The set $W = X$).\\
-
-Let $u \in C_0^\infty(0,1)$. Then $u(0) = u(1) = 0$ and therefore $u \in T(0,1)$ and $C_0^\infty(0,1) \subset T(0,1)$. Recall that $V(0,1)$ is the closure of $T(0,1)$ in $H^1(0,1)$.\\
-
+Let $u \in C_0^\infty(0,1)$.
+Then $u(0) = u(1) = 0$ and therefore $u \in T(0,1)$ and $C_0^\infty(0,1) \subset T(0,1)$.
+Recall that $V(0,1)$ is the closure of $T(0,1)$ in $H^1(0,1)$.
 So it follows that $C_0^\infty(0,1) \subset V(0,1) \subset H^1(0,1)$.
 And since $C_0^\infty(0,1)$ is dense in $L_2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L_2(0,1)$.
-Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.
+Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.\\
 
-\subsubsection{Assumption A2}\label{sssec:existence:AssumptionA2}
-	From the definition of the bilinear form $c$, 
+Consider \textbf{Assumption A2}. From the definition of the bilinear form $c$,
 \begin{eqnarray*}
@@
 \begin{Poincare_2}
-	Suppose that $f \in H^1(a,b)$, and $f(0) = 0$. Then $||f|| \leq (b-a)||f'||$
+	Suppose that $f \in H^1(a,b)$, and $f(0) = 0$. Then $||f|| \leq (b-a)||f'||$.
 \end{Poincare_2}
+\begin{proof}
+a
+\end{proof}
 
-To show that assumption \textbf{A3} holds, it is required to show that there exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.\\
+There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
+\begin{proof}
+	Let $f \in V$, then $f_1(0) = f_2(0) = 0$. Using the Corollary, and from the definition of the norm $||\cdot||_X$, the following inequality for the norm $||\cdot||_X$ can be obtained.
+	\begin{eqnarray*}
+		||f||_X^2 & \leq & ||f_1'||^2 + ||f_2'||^2 \\
+		& = & ||f_1'||^2 -||f_2||^2 + ||f_2'||^2 +||f_2||^2\\
+		& \leq & 2||f_1'-f_2||^2 + 2||f_2'||^2.
+	\end{eqnarray*}
 
-Let $f \in V$, then $f_1(0) = f_2(0) = 0$.
+	It follow from the inequality \eqref{C} that
+	\begin{eqnarray}
+		\Vert f \Vert_{W}^2 \leq 2C_2||f_1'-f_2||^2 + 2C_2||f_2'||^2. \label{f}
+	\end{eqnarray}
+
 	\begin{eqnarray}
@@
 
- Using the Corollary, and from the definition of the norm $||\cdot||_X$, the following Poincar\'e-Type inequality for the norm $||\cdot||_X$ can be obtained.
+	Now combine the inequalities \eqref{f} and \eqref{b},
 	\begin{eqnarray*}
-	||f||_X^2 & \leq & ||f_1'||^2 + ||f_2'||^2 \\
-	& = & ||f_1'||^2 -||f_2||^2 + ||f_2'||^2 +||f_2||^2\\
-	& \leq & 2||f_1'-f_2||^2 + 2||f_2'||^2.
-\end{eqnarray*} \sout{by Proposition 2 and the reverse triangle inequality.}\\
-
-Using \eqref{b} and the inequality above, it follows that
-\begin{eqnarray}		
-	b(f,f)	& \geq & \frac{1}{2}\min\left \{1, \frac{1}{\beta}\right \} ||f||_{X}^2. \label{b2}
-\end{eqnarray} for all $f \in V$.\\
-
-Since $b$ is the bilinear form for $V$ and $W = X$, \eqref{b2} is equivalent to \[||v||^2_V \geq C^{\frac{1}{2}}_V ||v||^2_W\] for all $v \in V$ with $\displaystyle C^{\frac{1}{2}}_V = \frac{1}{2}\min\left \{1, \frac{1}{\beta}\right \} > 0$.
-It follows that $\displaystyle||v||_W \leq C_V||v||_V$ for all $v \in V$.\\
-
-\sout{Since $b$ is a bilinear form and from the inequality above, $b$ is a inner-product for $V$.
-Using the inequality \eqref{C} results in $||v||^2_V \geq  C_3 ||w||_{W}^2$ for all $v \in V$, $w \in W$.
-With $C_3 =\frac{1}{2}\min\left \{1, \frac{1}{\beta}\right \} > 0$.
-The result follows by taking the square on both sides of the inequality.}\\
+		||f||_W^2 \leq Kb(f,f)
+	\end{eqnarray*} for all $f \in V$.
+\end{proof}
 
@@
 In Problem T-2W, it is clear that the bilinear form $a$ is identically zero.
-As mentioned before...
-\textcolor{red}{As mentioned before, if $a = 0$, the weak damping as well as assumption \textbf{A4} is satisfied.}\\
+As mentioned before, if $a = 0$, the weak damping as well as assumption \textbf{A4} is satisfied.
+Also, as explained in Section \ref{sec:existence:ExistenceAndUniqueness} the constuction of the operator $A$ is not affected.\\
 
@@
 \subsection{Timoshenko beam}
-In this dissertation, the eigenvalues and eigenvectors of the models presented are required.
  To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration.
 And to understand how modal analysis is applied, a Timoshenko beam is used as an example.
-Specifically, Problem T-1.\\
+Specifically, Problem T-1.
+\textcolor{red}{******* WHY NOT T-2???}\\
 
@@
 \end{eqnarray*}
-Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ with $\phi(x,t) = T(t)\tilde{\phi}(x)$.
-Simple substitution confirms that this trial solution satisfies the partial differential equations and the boundary conditions for Problem T-1.\\
+Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ with $\phi(x,t) = T(t)\tilde{\phi}(x)$. \\
 
@@
 The solution to Problem T-1E is a pair of functions $\langle \tilde{w} \ \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$.\\
+
+Suppose the function $T$ satisfies the following differential equation
+\begin{eqnarray}
+	\ddot{T} + \lambda T = 0, \label{eq:1D_Model:ModalAnalysisT}
+\end{eqnarray} with $\lambda$ an eigenvalue.\\
+
+Simple substitution confirms that the trial solution satisfies the partial differential equations and the boundary conditions for Problem T-1.\\
+
+Corresponding to this sequence of eigenvalues, we have a sequence of solutions $(T_n(t))$:
+\begin{eqnarray}
+	T_n(t)=A_n\cos(\sqrt{\lambda_n}t)+B_n\sin(\sqrt{\lambda_n}t), \label{eq:1D_Model:ModalAnalysisTn}
+\end{eqnarray}
+(with $A_n$ and $B_n$ arbitrary constants) for the ordinary differential equation \eqref{eq:1D_Model:ModalAnalysisT}.\\
 
@@
 
-Suppose the function $T$ satisfies the following differential equation
-\begin{eqnarray}
-	\ddot{T} + \lambda T = 0, \label{eq:1D_Model:ModalAnalysisT}
-\end{eqnarray} with $\lambda$ an eigenvalue.\\
-
 The variational eigenvalue problem for Problem T-1E can be obtained using similar steps to how Problem T-1V is obtained. This variational eigenvalue problem is referred to as Problem T-1EV
@@
 \end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$.\\
-
-\textcolor{red}{Res moet dalk out of skuif.*******************************}\\
-It is now possible to test the trial solutions $w(x,t) = T(t)\tilde{w}(x)$ and $\phi(x,t) = T(t)\tilde{\phi}(x)$.
-Consider the right hand side of the variational form of Problem T-1V with $Q=0$.
-Then substituting the pair of trial solutions:
-\begin{eqnarray*}
-	-\int_{0}^{1}\partial_x w v'  + \int_{0}^{1} \phi v' &=& -T\int_{0}^{1} \tilde{w}' v'  + T\int_{0}^{1} \tilde{\phi} v',\\
-	- \int_{0}^{1} \alpha \partial_x w \psi + \int_{0}^{1} \alpha \phi \psi - \frac{1}{\gamma} \int_{0}^{1}\partial_x \phi \psi' &=& - T\int_{0}^{1} \alpha \tilde{w}' \psi + T\int_{0}^{1} \alpha \tilde{\phi} \psi - \frac{1}{\gamma} T\int_{0}^{1} \tilde{\phi}' \psi'.
-\end{eqnarray*}
-Similarly for the left hand side and using \eqref{eq:1D_Model:ModalAnalysisT}:
-\begin{eqnarray*}
-	\int_{0}^{1} \partial_{t}^{2} w v &= \int_0^1 \ddot{T} \tilde{w} v &= T\int_0^1 \lambda \tilde{w} v,\\
-	\int_{0}^{1} \partial_{t}^{2} \phi \psi &= \int_0^1 \ddot{T} \tilde{\phi} \psi &= T \int_0^1 \lambda \tilde{\phi} \psi.
-\end{eqnarray*}
-
-This shows that the pair of trial solutions $\langle {w} \ {\phi} \rangle$ are solutions of the variational problem Problem T-1V with $\langle \tilde{w} \ \tilde{\phi} \rangle$ the eigenvalues with corresponding eigenvalue $\lambda$ from the variational eigenvalue problem Problem T-1EV.
-This was accomplished without using the method of separation of variables and thus avoiding any contention on division by zero.\\
 
@@
 
-Consider Problem XX in Section 2.2 \textbf{*** Sy reference is \eqref{GV_PB1}}\\
+Consider Problem GVar in Section 2.2.\\
 
-Given $g \in C((a,b);W)$, find $u$ such that for each $t > 0$, $u(t) \in V$, $u \in C^2((a,b);W)$ and
-\begin{eqnarray*}
-	c(u''(t),v) + b(u(t),v) = c(g(t),v).
-\end{eqnarray*}
-
-Now suppose there exists $\lambda$ and $x \in V$, $x \neq 0$ such that
+Suppose there exists a number $\lambda$ and $x \in V$, $x \neq 0$ such that
 \begin{eqnarray*}

### 2022-11-11 files/Chapter5/PlateModel.tex
Checked Chapter 5

@@
 \end{eqnarray*}
-Let $\partial \Omega$ denote the boundary of plate. The boundary $\partial \Omega$ can be divided into four distinct lines.\\
+Let $\partial \Omega$ denote the boundary of plate. The boundary $\partial \Omega$ can be divided into four distinct lines.
 
@@
 
-\textcolor{red}{*****************************}\\
-Since the plate is a rectangular shape in $R^2$, one would easily try to use the reference configuration as the two-dimensional elastic body in section 5.2.
-However for the plate model, the space $R^2$ can be considered perpendicular to the space for the two-dimensional elastic body in section 5.2.\\
-\textcolor{red}{*****************************}
+\textbf{Remark} The mathematical definition of $R_2$ is the same as the two-dimensional beam.
+Practically, it is not the same.
+The plate model is a horisontal two-dimensional plane, and the two-dimensional beam is a vertical two-dimensional plane.
 
@@
 		\node at (7.2,0.1) {$b$};
-		\node at (3.2,-0.27) {$\ell = 1$};
+		\draw[-stealth] (7.25,0.2) -- (8.1,0.7);
+		\draw (8,0.7) -- (8.2,0.7);
+		\draw[-stealth] (7,0.05) -- (6.7,-0.15);
+		\draw (6.6,-0.15) -- (6.8,-0.15);
+
+		\node at (3.2,-0.3) {$1$};
+		\draw[stealth-] (-0.8,-0.3) -- (3,-0.3);
+		\draw[stealth-] (6.2,-0.3) -- (3.3,-0.3);
+		\draw (6.2,-0.2) -- (6.2,-0.4);
 
@@
 
-\textcolor{red}{CHECK!!!}
 \subsubsection{Bilinear Form}
@@
 \end{eqnarray} with $\phi_{i,j} = \langle v_i, \phi_j \rangle$ for $i = 1,2,...,k_1$ and $j = 1,2,...,k_2$
-
-\textcolor{red}{INTERPOLATION TERM}
 

### 2022-11-15 files/Overview.tex
Overview v1

@@
 \begin{document}
+
+\section{Comparison of models}
+\subsection{Introduction}
+\subsection{Model problem for a three-dimensional elastic solid}
+\subsubsection{Equations of motion and constitutive equations}
+\textbf{Equation of motion}
+\subsubsection{Dimensionless form}
+\subsubsection{Model problems}
+\textbf{Problem 3D-1}\\
+\textbf{Problem 3D-2}
+\subsubsection{Variational form}
+\textbf{Bilinear forms and integral}\\
+\textbf{Test functions}\\
+\textbf{Problem 3D-1V}
+\subsubsection{Plane stress}
+\subsection{Two-dimensional model problem for an elastic solid}
+\subsubsection{Introduction}
+\subsubsection{Equations of motion and constitutive equations}
+\textbf{Equation of motion}\\
+\textbf{Constitutive equation}
+\subsubsection{Model problem}
+\textbf{Problem 2D-1}
+\subsubsection{Variational form}
+\textbf{Bilinear forms and integral}\\
+\textbf{Test functions for problem 2D-1}\\
+\textbf{Problem 2D-1V}
+\subsection{Timoshenko beam models}
+\subsubsection{Equations of motion and constitutive equations}
+\subsubsection{Boundary conditions}
+\subsubsection{Boundary value problems}
+\subsubsection{Variational form}
+\textbf{Function spaces}\\
+\textbf{Test function spaces for different problems}\\
+\textbf{Bilinear forms}
+\subsection{Reissner-Mindlin Plate Model}
+\subsubsection{Equations of Motion and Constitutive Equations}
+\subsubsection{Dimensionless Form}
+\textbf{Remark}\\
+\textbf{Dimensionless Equations of Motion}\\
+\textbf{Dimensionless Constitutive Equations}
+\subsubsection{Boundary Conditions}
+\subsubsection{Model Problems}
+\textbf{Problem P-1}\\
+\textbf{Problem P-2}
+\subsubsection{Variational Form}
+\textbf{Bilinear Forms and integral}\\
+\textbf{Test Functions for Problem P-1}\\
+\textbf{Problem P-1V}
+\subsection{Rod Theory}
+\section{Mathematical analysis of vibration problems}
+\subsection{Introduction}
+\textbf{Problem T-2W}
+\subsection{Existence and uniqueness of solutions}
+\subsubsection{The variational approach}
+\subsubsection{Main results for existence and uniqueness}
+\subsubsection{First order system}
+\subsection{Application: Timoshenko beam model}
+\subsection{Modal analysis}
+\subsubsection{Timoshenko beam}
+\subsubsection{General vibration problem}
+\section{Finite element theory}
+\subsection{Introduction}
+\subsection{Convergence of the Galerkin approximation}
+\subsubsection{Galerkin approximation}
+\subsubsection{System of ordinary differential equations}
+\subsubsection{Error estimates}
+\subsubsection{Main result}
+\subsubsection{Obtaining the error estimate}
+\textbf{Semi-discrete problem}
+\subsubsection{Fully discrete Galerkin finite element approximation}
+\textbf{Notation}\\
+\textbf{Error estimate for the fully discrete problem}
+\subsection{Convergence of eigenvalues in Finite Element Analysis}
+\subsubsection{Eigenvalue problem for vibration problem}
+\textbf{Problem GVarE}
+\subsubsection{Interpolation theorem}
+\subsubsection{Eigenvalue problem for our models*********}
+\textbf{Notation}
+\subsubsection{Convergence of the eigenvalues}
+\subsubsection{Convergence of the eigenfunctions}
+\subsection{Example}
+\textbf{Problem 2D-1V}\\
+\textbf{Test functions}
+\subsubsection{Weak variational form}
+\textbf{Problem 2D-1W}
+\section{Timoshenko beam model}
+\subsection{Introduction}
+\subsection{Eigenvalue problem}
+\textbf{General eigenvalue problem}\\
+\textbf{Case $\bm {\lambda <\alpha }$}\\
+\textbf{Case $\bm { \lambda =\alpha }$}\\
+\textbf{Case $\bm {\lambda >\alpha }$}
+\subsection{Cantilever beam}
+\subsubsection{Calculating the eigenvalues}
+\subsubsection{Example of mode shapes}
+\subsection{Free-free timoshenko beam}
+\subsubsection{Calculating the eigenvalues}
+\subsubsection{Example of mode shapes}
+\subsection{Suspended beam model}
+\textbf{Variational problem}
+\subsection{SP06}
+\subsubsection{Mathematical models}
+\textbf{Problem 3D-2}
+\subsubsection{Experimental setup}
+\subsubsection{Results from SP06}
+\subsection{Cantilever Timoshenko beam with tip-body}
+\subsubsection{The model problem}
+\textbf{Boundary conditions}\\
+\textbf{Remark}
+\subsubsection{Variational form}
+\textbf{Remark}\\
+\textbf{Interface equation}\\
+\textbf{Problem Var}
+\subsubsection{Galerkin approximation}
+\textbf{Problem G}
+\subsubsection{System of ordinary differential equations}
+\textbf{Problem ODE}
+\subsubsection{Numerical results}
+\textbf{Case: Control}\\
+\textbf{Case: Decrease $\gamma $}\\
+\textbf{Case: Decrease $\mu $}\\
+\textbf{Case: Increase $m$}
+\section{Finite element method}
+\subsection{Introduction}
+\subsection{Two-dimensional cantilever body}
+\textbf{Reference configuration for rectangular cross-section}\\
+\textbf{Cantilever elastic body}\\
+\textbf{Problem 2D-1V}\\
+\textbf{Constitutive equations:}\\
+\textbf{Bilinear form:}
+\subsubsection{Weak variational form}
+\textbf{Problem 2D-1WV}
+\subsubsection{Galerkin approximation}
+\textbf{Problem 2D-1G}
+\subsubsection{System of differential equations}
+\textbf{FEM matrices}\\
+\textbf{Problem 2D-1ODE}\\
+\textbf{Remark}
+\subsubsection{Eigenvalue problem}
+\textbf{Problem 2D-1E}
+\subsection{Three-dimensional elastic model}
+\textbf{Reference configuration for rectangular cross-section}\\
+\textbf{Cantilever elastic body}\\
+\textbf{Problem 3D-1V}\\
+\textbf{Bilinear Form}
+\subsubsection{Weak variational form}
+\textbf{Bilinear form}\\
+\textbf{Problem 3D-1W}
+\subsubsection{Galerkin approximation}
+\textbf{Problem 3D-1G}
+\subsubsection{System of ordinary differential equations}
+\textbf{FEM matrices}\\
+\textbf{Problem 3D-1ODE}
+\subsubsection{Eigenvalue problem}
+\textbf{Problem 3D-1E}
+\subsection{Cantilever plate model}
+\textbf{Reference configuration for a rectangular plate}\\
+\textbf{Cantilever plate model}\\
+\textbf{Problem P-1V}\\
+\textbf{Constitutive Equations}\\
+\textbf{Bilinear Form}
+\subsubsection{Weak variational form}
+\textbf{Bilinear forms}\\
+\textbf{Problem Plate-1W}\\
+\textbf{Existence and uniqueness}
+\subsubsection{Galerkin approximation}
+\textbf{Problem P-1G}
+\subsubsection{System of ordinary differential equations}
+\textbf{FEM matrices}\\
+\textbf{Problem P-1ODE}
+\subsubsection{Eigenvalue problem}
+\textbf{Problem P-1E}
+\section{Validity of cantilever beam and plate models}
+\subsection{Introduction}
+\textbf{Parameters}
+\subsection{Validity of the Timoshenko beam model}
+\subsubsection{The models}
+\subsubsection{Accuracy of the numerical eigenvalues}
+\subsubsection{Comparing the shape of the eigenfunctions}
+\textbf{Shapes relating to beam-type eigenvalues}\\
+\textbf{Shapes relating to non-beam type eigenvalues}\\
+\textbf{Shapes of the cross-section}\\
+\textbf{Direct comparison of mode shapes}\\
+\textbf{Remark}
+\subsubsection{Comparing the eigenvalues}
+\textbf{Results of [LVV09]}
+\subsubsection{Comparison of the eigenvalues}
+\subsection{Validity of the two-dimensional elastic model}
+\subsubsection{The models}
+\subsubsection{Accuracy of the numerical eigenvalues}
+\subsubsection{Comparing the mode shapes}
+\textbf{Mode shapes relating to beam type eigenvalues.}\\
+\textbf{Mode shapes relating to non-beam type eigenvalues that are present in the two-dimensional model.}\\
+\textbf{Mode shapes relating to non-beam type eigenvalues that are not present in the two-dimensional model.}
+\subsubsection{Comparing the eigenvalues}
+\subsubsection{$b > h$}
+\subsection{Validity of the Reissner-Mindlin plate model}
+\subsubsection{Comparing the mode shapes}
+\subsubsection{Comparing the eigenvalues}
 \section{Overview}
+\subsection{Overview}
+\section{Conclusion}
+\subsection{Overview}
+\textbf{Properties}\\
+\textbf{Properties of Type One}\\
+\textbf{Properties of Type Two}\\
+\textbf{Properties}
+\subsection{Introduction}
+\textbf{Different Research Approaches}\\
+\textbf{Motivation}
+\subsection{NRF Research Proposal}
+\subsection{Modelling a Suspension Bridge: A Brief History}
+\subsection{Modelling a suspension bridge: An Engineering Example}
+\subsection{Simplified Mathematical Model for a Suspended Beam}
+\subsubsection{Reference Configuration}
+\subsubsection{System of Equations}
+\textbf{Equations of Motion}\\
+\textbf{Constitutive Equations}\\
+\textbf{Dimensionless Equations}
+\subsubsection{Boundary Conditions}
+\subsection{Analysis of a Thermoelastic Timoshenko Beam Model}
+\textbf{Dimensionless Equations}
+\subsection{An Elastically Clamped Beam Model}
+\textbf{Boundary Conditions}\\
+\textbf{Hooke's law in two-dimensions}
+
 \begin{itemize}

### 2022-11-16 files/Chapter7/Introduction.tex
Started with overview

@@
 In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
-More results not given in  [LVV09] are also calculated, to be used in the sections following.
+More results not given in  [LVV09] are also calculated, to be used in the sections following.\\
 
@@
 The results of the two-dimensional beam are compared to a three-dimensional beam.
-The two-dimensional beam thus serves are an intermediate step to validate the Timoshenko beam model.
-
- extends the work of \cite{LVV09} to a comparison of a cantilever two-dimensional beam to a cantilever three-dimensional beam.\\
+The two-dimensional beam thus serves are an intermediate step to validate the Timoshenko beam model.\\
 
@@
 
-\subsubsection{Parameters}
+\subsubsection{Global parameters}
 All the models in this dissertation are made of the same isotropic material and have square cross-section.

### 2022-11-16 files/Overview.tex
Started with overview

@@
 \section{Comparison of models}
-\subsection{Introduction}
 \subsection{Model problem for a three-dimensional elastic solid}
-\subsubsection{Equations of motion and constitutive equations}
-\textbf{Equation of motion}
-\subsubsection{Dimensionless form}
-\subsubsection{Model problems}
-\textbf{Problem 3D-1}\\
-\textbf{Problem 3D-2}
-\subsubsection{Variational form}
-\textbf{Bilinear forms and integral}\\
-\textbf{Test functions}\\
-\textbf{Problem 3D-1V}
-\subsubsection{Plane stress}
+
+Models for a three-dimensional elastic solid is presented.
+These models are a cantilever and a free-free elastic body.
+A dimensionless variational form of the cantilever model is derived.
+General plane stress is discussed.
+
 \subsection{Two-dimensional model problem for an elastic solid}
-\subsubsection{Introduction}
-\subsubsection{Equations of motion and constitutive equations}
-\textbf{Equation of motion}\\
-\textbf{Constitutive equation}
-\subsubsection{Model problem}
-\textbf{Problem 2D-1}
-\subsubsection{Variational form}
-\textbf{Bilinear forms and integral}\\
-\textbf{Test functions for problem 2D-1}\\
-\textbf{Problem 2D-1V}
+
+A model for a two-dimensional elastic solid is presented.
+The model is a cantilever elastic body.
+This model is a special case of plane stress of a three-dimensional elastic body.
+The model is given in a dimensionless variational form by simplification of the three-dimensional model.
+
 \subsection{Timoshenko beam models}
-\subsubsection{Equations of motion and constitutive equations}
-\subsubsection{Boundary conditions}
-\subsubsection{Boundary value problems}
-\subsubsection{Variational form}
-\textbf{Function spaces}\\
-\textbf{Test function spaces for different problems}\\
-\textbf{Bilinear forms}
+
+Models for a one-dimensional beam are presented using the Timoshenko beam theory.
+Four different models are presented.
+The models are a cantilever, free-free, pinned-pinned and a suspended beam.
+A dimensionless variational form for the models are derived.
+
 \subsection{Reissner-Mindlin Plate Model}
-\subsubsection{Equations of Motion and Constitutive Equations}
-\subsubsection{Dimensionless Form}
-\textbf{Remark}\\
-\textbf{Dimensionless Equations of Motion}\\
-\textbf{Dimensionless Constitutive Equations}
-\subsubsection{Boundary Conditions}
-\subsubsection{Model Problems}
-\textbf{Problem P-1}\\
-\textbf{Problem P-2}
-\subsubsection{Variational Form}
-\textbf{Bilinear Forms and integral}\\
-\textbf{Test Functions for Problem P-1}\\
-\textbf{Problem P-1V}
+
+Models for a Reissner-Mindlin plate are presented. The models are a cantilever and a rigidly clamped plate. A dimensionless variational form for the cantilever model is derived.
+
 \subsection{Rod Theory}
+**************
+
 \section{Mathematical analysis of vibration problems}
-\subsection{Introduction}
-\textbf{Problem T-2W}
+
+This chapter is a discussion and example of application of the theory presented in \cite{VV02}.
+This article concerns the existence and uniqueness of solutions of second order hyperbolic type problems.
+Like the models in this dissertation.\\
+
+As an example to explain the theory, the a weak variational form of a cantilever Timoshenko beam is used.\\
+
+This chapter also concerns the idea of modal analysis. This is a method to find the natural frequencies of a system. This method is used later in the dissertation.
+
 \subsection{Existence and uniqueness of solutions}
+
 \subsubsection{The variational approach}
+
+A general variational problem is defined. Specific Hilbert spaces are defined as well as notation. The four assumptions from \cite{VV02} is given.
+
 \subsubsection{Main results for existence and uniqueness}
+The main results from \cite{VV02} is presented. This includes cases for strong and weak damped systems. The models in this dissertation all have weak damping.
+
 \subsubsection{First order system}
+The general variational problem is rewritten for a first order system.
+To obtain this first order system, a operator $A$ is defined.
+The authors prove that this operator is a infinitesimal generator of a $C_0$-semigroup of contractions with a domain in the Hilbert space $H$.\\
+
+The existence and uniqueness results for the first order system is easily proven with an initial value problem.
+The authors also prove that a solution of the first order system is also a solution to the general variational problem.
+
 \subsection{Application: Timoshenko beam model}
+The theory is applied to a cantilever Timoshenko beam model. Using the weak variational form, the four assumptions from \cite{VV02} is proven.
+
 \subsection{Modal analysis}
+*****************************************************************
+
 \subsubsection{Timoshenko beam}
@@
 \section{Finite element theory}
-\subsection{Introduction}
+
 \subsection{Convergence of the Galerkin approximation}
+In this chapter, two convergence results relating to the Finite Element Method is presented.
+The first result is a convergence result for the Galerkin approximation of a second order hyperbolic type problem.
+This is presented in \cite{BV13}.\\
+
+The second result is from the textbook \cite{SF97}.
+This results concerns the convergence of the eigenvalues and eigenfunctions of a one-dimensional second order hyperbolic type problem when using the Finite Element Method.
+
 \subsubsection{Galerkin approximation}
+The general variational problem is identical to the one in \cite{VV02} presented in chapter 2. It is assumed that the the general variational problem has a unique solution.\\
+
+The Galerkin approximation for the general variational problem is derived. Uniqueness of a solution to the Galerkin approximation is proven if $f$ is continuous.\\
+
 \subsubsection{System of ordinary differential equations}
+
+Continuing with to apply the Finite Element Method, the Galerkin approximation is rewritten as a system of ordinary differential equations. The system is a linear system.\\
+
 \subsubsection{Error estimates}
+Suppose $u$ is a solution to the general variational problem and $u^h$ is a solution to the Galerkin approximation.
+The goal of \cite{BV13} is to prove that $u^h$ converges to $u$ in $H$ as $h\rightarrow 0$.\\
+
+A error estimate is defined by the authors. The error estimate is split into two parts. A semi-discrete part and a fully discrete part. The two parts are investigated separately.\\
+
 \subsubsection{Main result}
+
+The main result of \cite{BV13} is presented. Two assumptions of \cite{BV13} are also given.
+
 \subsubsection{Obtaining the error estimate}
-\textbf{Semi-discrete problem}
-\subsubsection{Fully discrete Galerkin finite element approximation}
-\textbf{Notation}\\
-\textbf{Error estimate for the fully discrete problem}
+
+In this subsection, the approach of the authors are discussed. First a error estimate for the semi-discrete problem is obtained.*****\\
+
 \subsection{Convergence of eigenvalues in Finite Element Analysis}
+*****************************************************************
+
 \subsubsection{Eigenvalue problem for vibration problem}
@@
 \section{Timoshenko beam model}
-\subsection{Introduction}
+
+In this chapter, the Timoshenko beam theory is explored further.
+
 \subsection{Eigenvalue problem}
+In the first three sections, the idea of modal analysis is applied to the Timoshenko beam theory.
+The first section follows the work of \cite{VV06}.
+In this article, the authors present a method of calculating the eigenvalues and eigenfunctions.
 \textbf{General eigenvalue problem}\\
@@
 \subsection{Cantilever beam}
+This is an example of the application of the theory on a cantilever Timoshenko beam.
 \subsubsection{Calculating the eigenvalues}
@@
 \subsection{Free-free timoshenko beam}
+
+This is an example of the application of the theory on a free-free Timoshenko beam.
+
 \subsubsection{Calculating the eigenvalues}
@@
 \subsection{Suspended beam model}
+The idea of a suspended Timoshenko is also discuss briefly.\\
 \textbf{Variational problem}
 \subsection{SP06}
+In the next section, an empirical study of the Timoshenko beam is discussed.
+In the article \cite{SP06} the authors obtained the eigenvalues of a Timoshenko beam, by analyzing the natural frequencies of a real world beam.
+Their findings are compared to various theoretical models.\\
 \subsubsection{Mathematical models}
@@
 \subsection{Cantilever Timoshenko beam with tip-body}
+Last an example of the Timoshenko beam in application is presented. This section is a study of a technical report on a cantilever Timoshenko beam with elastic interfaces and a tip body.
 \subsubsection{The model problem}
@@
 \section{Finite element method}
-\subsection{Introduction}
 \subsection{Two-dimensional cantilever body}
@@
 \section{Validity of cantilever beam and plate models}
-\subsection{Introduction}
 \textbf{Parameters}
@@
 \textbf{Properties}
-\subsection{Introduction}
+\textbf{Different Research Approaches}\\
+\textbf{Motivation}
+\subsection{NRF Research Proposal}
+\subsection{Modelling a Suspension Bridge: A Brief History}
+\subsection{Modelling a suspension bridge: An Engineering Example}
+\subsection{Simplified Mathematical Model for a Suspended Beam}
+\subsubsection{Reference Configuration}
+\subsubsection{System of Equations}
+\textbf{Equations of Motion}\\
+\textbf{Constitutive Equations}\\
+\textbf{Dimensionless Equations}
+\subsubsection{Boundary Conditions}
+\subsection{Analysis of a Thermoelastic Timoshenko Beam Model}
+\textbf{Dimensionless Equations}
+\subsection{An Elastically Clamped Beam Model}
+\textbf{Boundary Conditions}\\
+\textbf{Hooke's law in two-dimensions}
+
+******************************************************************\\
+
+\section{Comparison of models}
+\subsection{Model problem for a three-dimensional elastic solid}
+\subsubsection{Equations of motion and constitutive equations}
+\textbf{Equation of motion}
+\subsubsection{Dimensionless form}
+\subsubsection{Model problems}
+\textbf{Problem 3D-1}\\
+\textbf{Problem 3D-2}
+\subsubsection{Variational form}
+\textbf{Bilinear forms and integral}\\
+\textbf{Test functions}\\
+\textbf{Problem 3D-1V}
+\subsubsection{Plane stress}
+\subsection{Two-dimensional model problem for an elastic solid}
+\subsubsection{Equations of motion and constitutive equations}
+\textbf{Equation of motion}\\
+\textbf{Constitutive equation}
+\subsubsection{Model problem}
+\textbf{Problem 2D-1}
+\subsubsection{Variational form}
+\textbf{Bilinear forms and integral}\\
+\textbf{Test functions for problem 2D-1}\\
+\textbf{Problem 2D-1V}
+\subsection{Timoshenko beam models}
+\subsubsection{Equations of motion and constitutive equations}
+\subsubsection{Boundary conditions}
+\subsubsection{Boundary value problems}
+\subsubsection{Variational form}
+\textbf{Function spaces}\\
+\textbf{Test function spaces for different problems}\\
+\textbf{Bilinear forms}
+\subsection{Reissner-Mindlin Plate Model}
+\subsubsection{Equations of Motion and Constitutive Equations}
+\subsubsection{Dimensionless Form}
+\textbf{Remark}\\
+\textbf{Dimensionless Equations of Motion}\\
+\textbf{Dimensionless Constitutive Equations}
+\subsubsection{Boundary Conditions}
+\subsubsection{Model Problems}
+\textbf{Problem P-1}\\
+\textbf{Problem P-2}
+\subsubsection{Variational Form}
+\textbf{Bilinear Forms and integral}\\
+\textbf{Test Functions for Problem P-1}\\
+\textbf{Problem P-1V}
+\subsection{Rod Theory}
+\section{Mathematical analysis of vibration problems}
+\textbf{Problem T-2W}
+\subsection{Existence and uniqueness of solutions}
+\subsubsection{The variational approach}
+\subsubsection{Main results for existence and uniqueness}
+\subsubsection{First order system}
+\subsection{Application: Timoshenko beam model}
+\subsection{Modal analysis}
+\subsubsection{Timoshenko beam}
+\subsubsection{General vibration problem}
+\section{Finite element theory}
+\subsection{Convergence of the Galerkin approximation}
+\subsubsection{Galerkin approximation}
+\subsubsection{System of ordinary differential equations}
+\subsubsection{Error estimates}
+\subsubsection{Main result}
+\subsubsection{Obtaining the error estimate}
+\textbf{Semi-discrete problem}
+\subsubsection{Fully discrete Galerkin finite element approximation}
+\textbf{Notation}\\
+\textbf{Error estimate for the fully discrete problem}
+\subsection{Convergence of eigenvalues in Finite Element Analysis}
+\subsubsection{Eigenvalue problem for vibration problem}
+\textbf{Problem GVarE}
+\subsubsection{Interpolation theorem}
+\subsubsection{Eigenvalue problem for our models*********}
+\textbf{Notation}
+\subsubsection{Convergence of the eigenvalues}
+\subsubsection{Convergence of the eigenfunctions}
+\subsection{Example}
+\textbf{Problem 2D-1V}\\
+\textbf{Test functions}
+\subsubsection{Weak variational form}
+\textbf{Problem 2D-1W}
+\section{Timoshenko beam model}
+\subsection{Eigenvalue problem}
+\textbf{General eigenvalue problem}\\
+\textbf{Case $\bm {\lambda <\alpha }$}\\
+\textbf{Case $\bm { \lambda =\alpha }$}\\
+\textbf{Case $\bm {\lambda >\alpha }$}
+\subsection{Cantilever beam}
+\subsubsection{Calculating the eigenvalues}
+\subsubsection{Example of mode shapes}
+\subsection{Free-free timoshenko beam}
+\subsubsection{Calculating the eigenvalues}
+\subsubsection{Example of mode shapes}
+\subsection{Suspended beam model}
+\textbf{Variational problem}
+\subsection{SP06}
+\subsubsection{Mathematical models}
+\textbf{Problem 3D-2}
+\subsubsection{Experimental setup}
+\subsubsection{Results from SP06}
+\subsection{Cantilever Timoshenko beam with tip-body}
+\subsubsection{The model problem}
+\textbf{Boundary conditions}\\
+\textbf{Remark}
+\subsubsection{Variational form}
+\textbf{Remark}\\
+\textbf{Interface equation}\\
+\textbf{Problem Var}
+\subsubsection{Galerkin approximation}
+\textbf{Problem G}
+\subsubsection{System of ordinary differential equations}
+\textbf{Problem ODE}
+\subsubsection{Numerical results}
+\textbf{Case: Control}\\
+\textbf{Case: Decrease $\gamma $}\\
+\textbf{Case: Decrease $\mu $}\\
+\textbf{Case: Increase $m$}
+\section{Finite element method}
+\subsection{Two-dimensional cantilever body}
+\textbf{Reference configuration for rectangular cross-section}\\
+\textbf{Cantilever elastic body}\\
+\textbf{Problem 2D-1V}\\
+\textbf{Constitutive equations:}\\
+\textbf{Bilinear form:}
+\subsubsection{Weak variational form}
+\textbf{Problem 2D-1WV}
+\subsubsection{Galerkin approximation}
+\textbf{Problem 2D-1G}
+\subsubsection{System of differential equations}
+\textbf{FEM matrices}\\
+\textbf{Problem 2D-1ODE}\\
+\textbf{Remark}
+\subsubsection{Eigenvalue problem}
+\textbf{Problem 2D-1E}
+\subsection{Three-dimensional elastic model}
+\textbf{Reference configuration for rectangular cross-section}\\
+\textbf{Cantilever elastic body}\\
+\textbf{Problem 3D-1V}\\
+\textbf{Bilinear Form}
+\subsubsection{Weak variational form}
+\textbf{Bilinear form}\\
+\textbf{Problem 3D-1W}
+\subsubsection{Galerkin approximation}
+\textbf{Problem 3D-1G}
+\subsubsection{System of ordinary differential equations}
+\textbf{FEM matrices}\\
+\textbf{Problem 3D-1ODE}
+\subsubsection{Eigenvalue problem}
+\textbf{Problem 3D-1E}
+\subsection{Cantilever plate model}
+\textbf{Reference configuration for a rectangular plate}\\
+\textbf{Cantilever plate model}\\
+\textbf{Problem P-1V}\\
+\textbf{Constitutive Equations}\\
+\textbf{Bilinear Form}
+\subsubsection{Weak variational form}
+\textbf{Bilinear forms}\\
+\textbf{Problem Plate-1W}\\
+\textbf{Existence and uniqueness}
+\subsubsection{Galerkin approximation}
+\textbf{Problem P-1G}
+\subsubsection{System of ordinary differential equations}
+\textbf{FEM matrices}\\
+\textbf{Problem P-1ODE}
+\subsubsection{Eigenvalue problem}
+\textbf{Problem P-1E}
+\section{Validity of cantilever beam and plate models}
+\textbf{Parameters}
+\subsection{Validity of the Timoshenko beam model}
+\subsubsection{The models}
+\subsubsection{Accuracy of the numerical eigenvalues}
+\subsubsection{Comparing the shape of the eigenfunctions}
+\textbf{Shapes relating to beam-type eigenvalues}\\
+\textbf{Shapes relating to non-beam type eigenvalues}\\
+\textbf{Shapes of the cross-section}\\
+\textbf{Direct comparison of mode shapes}\\
+\textbf{Remark}
+\subsubsection{Comparing the eigenvalues}
+\textbf{Results of [LVV09]}
+\subsubsection{Comparison of the eigenvalues}
+\subsection{Validity of the two-dimensional elastic model}
+\subsubsection{The models}
+\subsubsection{Accuracy of the numerical eigenvalues}
+\subsubsection{Comparing the mode shapes}
+\textbf{Mode shapes relating to beam type eigenvalues.}\\
+\textbf{Mode shapes relating to non-beam type eigenvalues that are present in the two-dimensional model.}\\
+\textbf{Mode shapes relating to non-beam type eigenvalues that are not present in the two-dimensional model.}
+\subsubsection{Comparing the eigenvalues}
+\subsubsection{$b > h$}
+\subsection{Validity of the Reissner-Mindlin plate model}
+\subsubsection{Comparing the mode shapes}
+\subsubsection{Comparing the eigenvalues}
+\section{Overview}
+\subsection{Overview}
+\section{Conclusion}
+\subsection{Overview}
+\textbf{Properties}\\
+\textbf{Properties of Type One}\\
+\textbf{Properties of Type Two}\\
+\textbf{Properties}
 \textbf{Different Research Approaches}\\

### 2022-11-17 files/Overview.tex
Some additions to overview

@@
 \subsection{Cantilever beam}
-This is an example of the application of the theory on a cantilever Timoshenko beam.
-\subsubsection{Calculating the eigenvalues}
-\subsubsection{Example of mode shapes}
+This is an example of the application of the theory on a cantilever Timoshenko beam. In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.\\
+
 \subsection{Free-free timoshenko beam}
 
-This is an example of the application of the theory on a free-free Timoshenko beam.
+This is an example of the application of the theory on a free-free Timoshenko beam.In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.\\
 
-\subsubsection{Calculating the eigenvalues}
-\subsubsection{Example of mode shapes}
 \subsection{Suspended beam model}
 The idea of a suspended Timoshenko is also discuss briefly.\\
-\textbf{Variational problem}
+
 \subsection{SP06}
@@
 Their findings are compared to various theoretical models.\\
-\subsubsection{Mathematical models}
-\textbf{Problem 3D-2}
-\subsubsection{Experimental setup}
-\subsubsection{Results from SP06}
+
 \subsection{Cantilever Timoshenko beam with tip-body}
-Last an example of the Timoshenko beam in application is presented. This section is a study of a technical report on a cantilever Timoshenko beam with elastic interfaces and a tip body.
-\subsubsection{The model problem}
-\textbf{Boundary conditions}\\
-\textbf{Remark}
-\subsubsection{Variational form}
-\textbf{Remark}\\
-\textbf{Interface equation}\\
-\textbf{Problem Var}
-\subsubsection{Galerkin approximation}
-\textbf{Problem G}
-\subsubsection{System of ordinary differential equations}
-\textbf{Problem ODE}
-\subsubsection{Numerical results}
-\textbf{Case: Control}\\
-\textbf{Case: Decrease $\gamma $}\\
-\textbf{Case: Decrease $\mu $}\\
-\textbf{Case: Increase $m$}
+Last an example of the Timoshenko beam in application is presented. This section is a study of a technical report on a cantilever Timoshenko beam with elastic interfaces and a tip body.\\
+
+The variational form is derived. Then the Galerkin apporximation is given and a numerical formula for calculting the solution of the problem is given as a resut of the Finite Element Method.\\
+
+The numerical results in this section give some assurance that the model behaves as expected.
+The numerical results also contribute to the technical report.
+Various parameters are manipluated to see how the model behaves.
+The results are given in tables and figures.\\
+
 \section{Finite element method}
+This chapter is preparation for the last chapter in this dissertation.
+The finite element method is applied to a cantilever version of each of the models in this dissertation.
+The goal of the chapter is to get a numerical formula to solve the eigenvalue problem for each model.
+The Timoshenko beam model is excluded from this chapter since an exact methd is already presented in chapter 4.\\
+
 \subsection{Two-dimensional cantilever body}
-\textbf{Reference configuration for rectangular cross-section}\\
-\textbf{Cantilever elastic body}\\
-\textbf{Problem 2D-1V}\\
-\textbf{Constitutive equations:}\\
-\textbf{Bilinear form:}
-\subsubsection{Weak variational form}
-\textbf{Problem 2D-1WV}
-\subsubsection{Galerkin approximation}
-\textbf{Problem 2D-1G}
-\subsubsection{System of differential equations}
-\textbf{FEM matrices}\\
-\textbf{Problem 2D-1ODE}\\
-\textbf{Remark}
-\subsubsection{Eigenvalue problem}
-\textbf{Problem 2D-1E}
+
+The model is assumed to have a rectangular cross-section and is in a cantilever configuration.
+The Galerkin approximation is derived and applying the finite element method, a numerical formula for solving the model problem is given.\\
+
+In this numerical formula, the model problem is a system of linear equations. This system can be changed to obtain a numerical formula for teh eigenvalue problem.\\
+
 \subsection{Three-dimensional elastic model}
-\textbf{Reference configuration for rectangular cross-section}\\
-\textbf{Cantilever elastic body}\\
-\textbf{Problem 3D-1V}\\
-\textbf{Bilinear Form}
-\subsubsection{Weak variational form}
-\textbf{Bilinear form}\\
-\textbf{Problem 3D-1W}
-\subsubsection{Galerkin approximation}
-\textbf{Problem 3D-1G}
-\subsubsection{System of ordinary differential equations}
-\textbf{FEM matrices}\\
-\textbf{Problem 3D-1ODE}
-\subsubsection{Eigenvalue problem}
-\textbf{Problem 3D-1E}
+Similar to above.
+
 \subsection{Cantilever plate model}
-\textbf{Reference configuration for a rectangular plate}\\
-\textbf{Cantilever plate model}\\
-\textbf{Problem P-1V}\\
-\textbf{Constitutive Equations}\\
-\textbf{Bilinear Form}
-\subsubsection{Weak variational form}
-\textbf{Bilinear forms}\\
-\textbf{Problem Plate-1W}\\
-\textbf{Existence and uniqueness}
-\subsubsection{Galerkin approximation}
-\textbf{Problem P-1G}
-\subsubsection{System of ordinary differential equations}
-\textbf{FEM matrices}\\
-\textbf{Problem P-1ODE}
-\subsubsection{Eigenvalue problem}
-\textbf{Problem P-1E}
+Similar to above.
+
 \section{Validity of cantilever beam and plate models}

### 2022-11-19 files/Overview.tex
Overview v1.2

--- 2022-11-15 files/Overview.tex
@@
 \section{Comparison of models}
-\subsection{Introduction}
+This chapter introduces the models used in this dissertation.
+
+\subsection{Model problem for a three-dimensional elastic solid}
+
+Two models for a three-dimensional elastic solid are presented.
+These models are a cantilever and a free-free elastic body.
+A dimensionless variational form of the cantilever model is derived.
+General plane stress is discussed.
+
+\subsection{Two-dimensional model problem for an elastic solid}
+
+A model for a two-dimensional elastic solid is presented.
+The model is a cantilever elastic body.
+This model is a special case of plane stress of a three-dimensional elastic body.
+The model is given in a dimensionless variational form by simplification of the three-dimensional model.
+
+\subsection{Timoshenko beam models}
+
+Four models for a one-dimensional beam are presented using the Timoshenko beam theory are presented.
+The models are a cantilever, free-free, pinned-pinned and a suspended beam.
+A dimensionless variational form for the models are derived.
+
+\subsection{Reissner-Mindlin Plate Model}
+
+Two models for a Reissner-Mindlin plate are presented. The models are a cantilever and a rigidly clamped plate. A dimensionless variational form for the cantilever model is derived.
+
+\subsection{Rod Theory}
+**************
+
+\section{Mathematical analysis of vibration problems}
+
+This chapter is a discussion and example of application of the theory presented in the article \cite{VV02}.
+This article concerns the existence and uniqueness of solutions of second order hyperbolic type problems.
+The models in this dissertation as such problems.\\
+
+This chapter also concerns the idea of modal analysis. This is a method to find the natural frequencies of a system. This method is used later in the dissertation.
+
+\subsection{Existence and uniqueness of solutions}
+This section is a discussion of the theory presented in the article \cite{VV02}.
+
+\subsubsection{The variational approach}
+
+The authors define a general variational problem. This problem is defined on specific Hilbert spaces. Four assumptions are made in the article as well as some notation introduced.
+
+\subsubsection{Main results for existence and uniqueness}
+The main resuls of the article are given in this section.
+The results include existence and uniqueness of solutions for strong and weak damped models.
+The models in this dissertation are all weakly damped.
+
+\subsubsection{First order system}
+To prove the results, the approach of the authors are as follows.\\
+
+The general variational problem is rewritten for a first order system of differential equations.
+This system is defined on a Hilbert space $H$.
+A operator $A$ is defined, and using the assumptions the authors prove that the operator $A$ is an infinitesimal generator of a $C_0$-semigroup of contractions with a domain in $H$.\\
+
+Using this operator the authors rewrite the system of differential into the form $\displaystyle x' = Ax + f$.
+To be more precise, the system of first order system of differential equations can be written as an initial value problem.\\
+
+The existence and uniqueness results for the first order system is easily proven with an initial value problem.
+The authors also prove that a solution of the first order system is also a solution to the general variational problem.\\
+
+Using semi-group theory, a unnique solution for the initial value problem can be proved.
+The authors also provide the link between the solutions of the initial value problem and the general variational form.
+Thus proving the required results.
+
+\subsection{Application: Timoshenko beam model}
+As an example of the application of the theory, the weak variational form for the cantilever Timshenko beam is introduced. This weak variational problem is defined on complete product spaces.\\
+
+The four assumptions of \cite{LVV09} are proved for this example model.
+
+\subsection{Modal analysis}
+*****************************************************************
+
+\subsubsection{Timoshenko beam}
+\subsubsection{General vibration problem}
+\section{Finite element theory}
+
+\subsection{Convergence of the Galerkin approximation}
+In this Chapter, two convergence results related to the Finite Element Method is presented.
+This first result is the convergence of the Galerkin approximation of a second order hyperbolic type problem, presented in the article \cite{BV13}.\\
+
+The second result concerns the convergence of the eigenvalue and eigenfunctions of a one-dimensional second order hyperbolic type problem when applying the Finite Element Method.
+This is presented in the textbook \cite{SF97}.
+
+\subsubsection{Galerkin approximation}
+In this section, the authors use the same general variational problem as presented in \cite{VV02} (Chapter 2). The authors assume that this general variational problem has a unique solution.\\
+
+To start, the Galerkin approximation for the general variational problem is derived. The a unique solution is proved in \cite{BV13} when the forcing function $f$ is continuous.\\
+
+\subsubsection{System of ordinary differential equations}
+
+Using the Finite Element Method matrices, the Galerkin approximation is rewritten as a system of ordinary differential equations.
+
+\subsubsection{Error estimates}
+Given that $u$ is a solution of the general variational problem, and $u^h$ is a solution to the Galerkin approximation, the authors define the error $e^h = u - u^h$.\\
+
+The in \cite{BV13} the authors prove that this error can be made arbitrarily small by choosing a sufficiently small $h$, such that $u^h \rightarrow u$ as $h \rightarrow 0$.
+\cite{BV18} extends \cite{BV13} to include damping.\\
+
+To obtain the error estimate, the authors split the error into two parts. The first part is a semi-dicrete problem and the second is a discrete problem. These two problems are investigated seperately.
+
+\subsubsection{Main result}
+
+In this section, the main results of \cite{BV13} are presented. The two assumptions made by the authors are also given.
+
+\subsubsection{Obtaining the error estimate}
+
+In this section, the approach of the authors for determining the error estimates for the semi-discrete and fully discrete problems are presented.\\
+
+\subsection{Convergence of eigenvalues in Finite Element Analysis}
+*****************************************************************
+
+\subsubsection{Eigenvalue problem for vibration problem}
+\textbf{Problem GVarE}
+\subsubsection{Interpolation theorem}
+\subsubsection{Eigenvalue problem for our models*********}
+\textbf{Notation}
+\subsubsection{Convergence of the eigenvalues}
+\subsubsection{Convergence of the eigenfunctions}
+\subsection{Example}
+\textbf{Problem 2D-1V}\\
+\textbf{Test functions}
+\subsubsection{Weak variational form}
+\textbf{Problem 2D-1W}
+\section{Timoshenko beam model}
+
+In this chapter, the Timoshenko beam theory is explored further. In the first three sections, the theory and two examples of \cite{VV06} are given. 
+\subsection{Eigenvalue problem}
+
+In this article \cite{VV06}, the authors present a method for finding the exact eigenvalues and eigenfunctions for the Timoshenko beam theory.
+The method provides solutions for three cases where $\lambda <\alpha$, $\lambda =\alpha$ and $\lambda >\alpha$.\\
+
+\subsection{Cantilever beam}
+This is an example of the application of the theory on a cantilever Timoshenko beam. In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.
+
+\subsection{Free-free timoshenko beam}
+
+This is an example of the application of the theory on a free-free Timoshenko beam.In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.
+
+\subsection{Suspended beam model}
+The idea of a suspended Timoshenko is also discuss briefly.
+
+\subsection{SP06}
+In this section this section, the article \cite{SP06} is discussed.
+In this section, the authors obtain eigenvalues of a free-free Timoshenko beam by vibrating and measuring the natural frequencies of a real beam.
+This empirical data is then compared to the theoretical results of various methods, including the Finite Element Method.
+
+\subsection{Cantilever Timoshenko beam with tip-body}
+
+In this last section, a example of the application of the Timoshenko beam model is presented.
+This section is a study of a technical report.
+In this report, the authors present a model for a cantilever Timoshenko beam with a tip body and elastic interfaces.
+This section also expands the numerical results of the report.\\
+
+The variational form of the model is derived, and the Galerkin approximation follows. The Mixed Finite Element Method is applied to the model.\\
+
+Using the Finite Element Method, the solution of the model is numerically calculated.
+Various results are given for different values of the parameters.
+The numerical results and figures confirms that the model behaves as expected.
+
+\section{Finite element method}
+This chapter is preperation for the final chapter in this dissertation.
+The finite element method to a cantilever version of each of the models in this dissertation.
+The goal of the chapter is to get a numerical formula to solve the eigenvalue problem for each model.
+The Timoshenko beam model is excluded from this chapter since an exact methd is already presented in chapter 4 (\cite{VV02}).\\
+
+\subsection{Two-dimensional cantilever body}
+
+The model is assumed to have a rectangular cross-section and is in a cantilever configuration.
+The Galerkin approximation is derived and applying the finite element method, a numerical formula for solving the model problem is given.\\
+
+In this numerical formula, the model problem is a system of linear equations. This system can be changed to obtain a numerical formula for teh eigenvalue problem.\\
+
+\subsection{Three-dimensional elastic model}
+Similar to above.
+
+\subsection{Cantilever plate model}
+Similar to above.
+
+\section{Validity of cantilever beam and plate models}
+
+In this chapter, the validity of the models in this dissertation is investigated using numerical results.
+Specifically the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate is investigated.\\
+
+In this case, the term validity refers to how well the model compares to a more realistic model.\\
+
+All models are assumed to have a rectangular cross-section, are in a cantilever configuration and are made of the same isotropic material.\\
+
+\subsection{Validity of the Timoshenko beam model}
+This first section, is a discussion of the article \cite{LVV09}.
+In this article, the authors investigate the validity of the Timoshenko beam model.
+The authors compare the Timoshenko beam model to a more realistic two-dimensional beam model.\\
+
+The comparison is made with the eigenvalues and eigenfunctions. From modal analysis it is known that the solution of the models are linear combinations of the eigenvalues and eigenfunctions.\\
+
+The two-dimensional model also have eigenvalues that do not have a corresponding eigenvalue in the Timoshenko beam model. The authors call all matching eigenvalues beam-type eigenvalues.\\
+
+The authors show that the Timoshenko beam model compare well to the two-dimensional model for long and short beams.
+The results of the article are verified and extra results are also calculated for the rest of this chapter.\\
+
+\subsection{Validity of the two-dimensional elastic model}
+
+In this section, the aricle \cite{LVV09} is extended to verify the validity of the two-dimensional elastic model.
+The two-dimensional elastic model is compared to a more realistic three-dimensional model.\\
+
+The two dimensional model serves as a intermediate step between the Timoshenko beam model and the three-dimensional model.\\
+
+The same approach of \cite{LVV09} is used to compare the two models. The result show that the two-dimensional model compare very well to the three-dimensional model, especially for beam problems.
+
+\subsection{Validity of the Reissner-Mindlin plate model}
+
+The last section takes the idea of \cite{LVV09} and extends it to the Reissner-Mindlin plate model. The Reissner-Mindlin plate model is compared to a more realistic three-dimensional plate model.\\
+
+******************************************************************\\
+
+\section{Comparison of models}
 \subsection{Model problem for a three-dimensional elastic solid}
@@
 \subsection{Two-dimensional model problem for an elastic solid}
-\subsubsection{Introduction}
 \subsubsection{Equations of motion and constitutive equations}
@@
 \section{Mathematical analysis of vibration problems}
-\subsection{Introduction}
 \textbf{Problem T-2W}
@@
 \section{Finite element theory}
-\subsection{Introduction}
 \subsection{Convergence of the Galerkin approximation}
@@
 \section{Timoshenko beam model}
-\subsection{Introduction}
 \subsection{Eigenvalue problem}
@@
 \textbf{Properties}
-\subsection{Introduction}
 \textbf{Different Research Approaches}\\

### 2022-11-23 files/Overview.tex
Overview 2.0
paragraphs

@@
 \begin{document}
+
+\section{Overview}
+
+\subsubsection{Comparison of models}
+This chapter introduces the models used in this dissertation.
+
+Two models for a three-dimensional elastic solid are presented.
+These models are a cantilever and a free-free elastic body.
+A dimensionless variational form of the cantilever model is derived.
+General plane stress is discussed.
+A model for a two-dimensional elastic solid is presented.
+The model is a cantilever elastic body.
+This model is a special case of plane stress of a three-dimensional elastic body.
+The model is given in a dimensionless variational form by simplification of the three-dimensional model.
+Four models for a one-dimensional beam are presented using the Timoshenko beam theory are presented.
+The models are a cantilever, free-free, pinned-pinned and a suspended beam.
+A dimensionless variational form for the models are derived.
+Two models for a Reissner-Mindlin plate are presented.
+The models are a cantilever and a rigidly clamped plate.
+A dimensionless variational form for the cantilever model is derived.
+(ROD THEORY?)
+
+\subsubsection{Mathematical analysis of vibration problems}
+
+This chapter is a discussion and example of application of the theory presented in the article \cite{VV02}.
+This article concerns the existence and uniqueness of solutions of second order hyperbolic type problems.
+The models in this dissertation as such problems.
+This chapter also concerns the idea of modal analysis.
+This is a method to find the natural frequencies of a system.
+This method is used later in the dissertation.
+This section is a discussion of the theory presented in the article \cite{VV02}.
+The authors define a general variational problem.
+This problem is defined on specific Hilbert spaces.
+Four assumptions are made in the article as well as some notation introduced.
+The main resuls of the article are given in this section.
+The results include existence and uniqueness of solutions for strong and weak damped models.
+The models in this dissertation are all weakly damped.
+To prove the results, the approach of the authors are as follows.
+The general variational problem is rewritten for a first order system of differential equations.
+This system is defined on a Hilbert space $H$.
+A operator $A$ is defined, and using the assumptions the authors prove that the operator $A$ is an infinitesimal generator of a $C_0$-semigroup of contractions with a domain in $H$.
+Using this operator the authors rewrite the system of differential into the form $\displaystyle x' = Ax + f$.
+To be more precise, the system of first order system of differential equations can be written as an initial value problem.
+The existence and uniqueness results for the first order system is easily proven with an initial value problem.
+The authors also prove that a solution of the first order system is also a solution to the general variational problem.
+Using semi-group theory, a unnique solution for the initial value problem can be proved.
+The authors also provide the link between the solutions of the initial value problem and the general variational form.
+Thus proving the required results.
+As an example of the application of the theory, the weak variational form for the cantilever Timshenko beam is introduced.
+This weak variational problem is defined on complete product spaces.
+The four assumptions of \cite{LVV09} are proved for this example model.
+(Modal Analysis)
+
+\subsubsection{Finite element theory}
+
+In this Chapter, two convergence results related to the Finite Element Method is presented.
+This first result is the convergence of the Galerkin approximation of a second order hyperbolic type problem, presented in the article \cite{BV13}.
+The second result concerns the convergence of the eigenvalue and eigenfunctions of a one-dimensional second order hyperbolic type problem when applying the Finite Element Method.
+This is presented in the textbook \cite{SF97}.
+In this section, the authors use the same general variational problem as presented in \cite{VV02} (Chapter 2).
+The authors assume that this general variational problem has a unique solution.
+To start, the Galerkin approximation for the general variational problem is derived.
+The a unique solution is proved in \cite{BV13} when the forcing function $f$ is continuous.
+Using the Finite Element Method matrices, the Galerkin approximation is rewritten as a system of ordinary differential equations.
+Given that $u$ is a solution of the general variational problem, and $u^h$ is a solution to the Galerkin approximation, the authors define the error $e^h = u - u^h$.
+The in \cite{BV13} the authors prove that this error can be made arbitrarily small by choosing a sufficiently small $h$, such that $u^h \rightarrow u$ as $h \rightarrow 0$.
+\cite{BV18} extends \cite{BV13} to include damping.
+To obtain the error estimate, the authors split the error into two parts.
+The first part is a semi-dicrete problem and the second is a discrete problem.
+These two problems are investigated seperately.
+In this section, the main results of \cite{BV13} are presented.
+The two assumptions made by the authors are also given.
+In this section, the approach of the authors for determining the error estimates for the semi-discrete and fully discrete problems are presented.\\
+
+(Convergence of eigenvalues in Finite Element Analysis)
+
+\subsubsection{Timoshenko beam model}
+
+In this chapter, the Timoshenko beam theory is explored further.
+In the first three sections, the theory and two examples of \cite{VV06} are given.
+In this article \cite{VV06}, the authors present a method for finding the exact eigenvalues and eigenfunctions for the Timoshenko beam theory.
+The method provides solutions for three cases where $\lambda <\alpha$, $\lambda =\alpha$ and $\lambda >\alpha$.
+This is an example of the application of the theory on a cantilever Timoshenko beam.
+In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.
+This is an example of the application of the theory on a free-free Timoshenko beam.In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.
+The idea of a suspended Timoshenko is also discuss briefly.
+In this section this section, the article \cite{SP06} is discussed.
+In this section, the authors obtain eigenvalues of a free-free Timoshenko beam by vibrating and measuring the natural frequencies of a real beam.
+This empirical data is then compared to the theoretical results of various methods, including the Finite Element Method.
+In this last section, a example of the application of the Timoshenko beam model is presented.
+This section is a study of a technical report.
+In this report, the authors present a model for a cantilever Timoshenko beam with a tip body and elastic interfaces.
+This section also expands the numerical results of the report.
+The variational form of the model is derived, and the Galerkin approximation follows.
+The Mixed Finite Element Method is applied to the model.
+Using the Finite Element Method, the solution of the model is numerically calculated.
+Various results are given for different values of the parameters.
+The numerical results and figures confirms that the model behaves as expected.
+
+\subsubsection{Finite element method}
+This chapter is preperation for the final chapter in this dissertation.
+The finite element method to a cantilever version of each of the models in this dissertation.
+The goal of the chapter is to get a numerical formula to solve the eigenvalue problem for each model.
+The Timoshenko beam model is excluded from this chapter since an exact methd is already presented in chapter 4 (\cite{VV02}).
+The model is assumed to have a rectangular cross-section and is in a cantilever configuration.
+The Galerkin approximation is derived and applying the finite element method, a numerical formula for solving the model problem is given.
+In this numerical formula, the model problem is a system of linear equations.
+This system can be changed to obtain a numerical formula for teh eigenvalue problem.\\
+
+\subsubsection{Validity of cantilever beam and plate models}
+
+In this chapter, the validity of the models in this dissertation is investigated using numerical results.
+Specifically the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate is investigated.
+In this case, the term validity refers to how well the model compares to a more realistic model.
+All models are assumed to have a rectangular cross-section, are in a cantilever configuration and are made of the same isotropic material.
+This first section, is a discussion of the article \cite{LVV09}.
+In this article, the authors investigate the validity of the Timoshenko beam model.
+The authors compare the Timoshenko beam model to a more realistic two-dimensional beam model.
+The comparison is made with the eigenvalues and eigenfunctions.
+From modal analysis it is known that the solution of the models are linear combinations of the eigenvalues and eigenfunctions.
+The two-dimensional model also have eigenvalues that do not have a corresponding eigenvalue in the Timoshenko beam model.
+The authors call all matching eigenvalues beam-type eigenvalues.
+The authors show that the Timoshenko beam model compare well to the two-dimensional model for long and short beams.
+The results of the article are verified and extra results are also calculated for the rest of this chapter.
+In this section, the aricle \cite{LVV09} is extended to verify the validity of the two-dimensional elastic model.
+The two-dimensional elastic model is compared to a more realistic three-dimensional model.
+The two dimensional model serves as a intermediate step between the Timoshenko beam model and the three-dimensional model.
+The same approach of \cite{LVV09} is used to compare the two models.
+The result show that the two-dimensional model compare very well to the three-dimensional model, especially for beam problems.
+The last section takes the idea of \cite{LVV09} and extends it to the Reissner-Mindlin plate model.
+The Reissner-Mindlin plate model is compared to a more realistic three-dimensional plate model.\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-11-24 files/Overview.tex
Overview v2.1

@@
 \subsubsection{Comparison of models}
-This chapter introduces the models used in this dissertation.
-
-Two models for a three-dimensional elastic solid are presented.
-These models are a cantilever and a free-free elastic body.
-A dimensionless variational form of the cantilever model is derived.
-General plane stress is discussed.
-A model for a two-dimensional elastic solid is presented.
-The model is a cantilever elastic body.
-This model is a special case of plane stress of a three-dimensional elastic body.
-The model is given in a dimensionless variational form by simplification of the three-dimensional model.
-Four models for a one-dimensional beam are presented using the Timoshenko beam theory are presented.
-The models are a cantilever, free-free, pinned-pinned and a suspended beam.
-A dimensionless variational form for the models are derived.
-Two models for a Reissner-Mindlin plate are presented.
-The models are a cantilever and a rigidly clamped plate.
-A dimensionless variational form for the cantilever model is derived.
+The first chapter introduces the models used in this dissertation.
+The models are of different dimensions.
+The first model is a three dimensional elastic body.
+The model problems for the three-dimensional body is a cantilever and a free-free body.
+A general case of plane stress is also discussed.
+Making assumptions on plane stress, results into a two-dimensional model.
+This model is a special case of plane stress.
+For the one-dimensional case, the Timoshenko beam theory is considered.
+Four different models problems are used in this disseration.
+These model problems are a cantilever, a free-free beam, a pinned-pinned beam and a suspended beam.
+Lastly a Reissner Mindlin plate theory is considered.
+The model problems for the plate theory are a cantilever plate and a rigidly clamped plate.
+For each of the models problems, the boundary conditions are presented and the variational form is derived.
+The variational form of each problem is mainly used in this dissertation.
 (ROD THEORY?)
@@
 This article concerns the existence and uniqueness of solutions of second order hyperbolic type problems.
-The models in this dissertation as such problems.
-This chapter also concerns the idea of modal analysis.
-This is a method to find the natural frequencies of a system.
-This method is used later in the dissertation.
-This section is a discussion of the theory presented in the article \cite{VV02}.
-The authors define a general variational problem.
-This problem is defined on specific Hilbert spaces.
-Four assumptions are made in the article as well as some notation introduced.
-The main resuls of the article are given in this section.
+The models in this dissertation are such problems.
+In the article \cite{VV02}, the authors define a general variational problem on specific Hilbert spaces.
+To obtain the main results of the article, four assumptions are made.
 The results include existence and uniqueness of solutions for strong and weak damped models.
 The models in this dissertation are all weakly damped.
-To prove the results, the approach of the authors are as follows.
 The general variational problem is rewritten for a first order system of differential equations.
@@
 The authors also prove that a solution of the first order system is also a solution to the general variational problem.
-Using semi-group theory, a unnique solution for the initial value problem can be proved.
+Using semi-group theory, a unique solution for the initial value problem can be proved.
 The authors also provide the link between the solutions of the initial value problem and the general variational form.
 Thus proving the required results.
-As an example of the application of the theory, the weak variational form for the cantilever Timshenko beam is introduced.
-This weak variational problem is defined on complete product spaces.
-The four assumptions of \cite{LVV09} are proved for this example model.
-(Modal Analysis)
+As an example to apply the theory, a cantilever Timoshenko beam is used.
+The weak variational form is derived.
+In this weak variational form, the product spaces can be made complete.
+The four assumptions of \cite{VV02} is then proved to hold for the example.
+(Modal Analysis ?)
 
@@
 
-In this Chapter, two convergence results related to the Finite Element Method is presented.
-This first result is the convergence of the Galerkin approximation of a second order hyperbolic type problem, presented in the article \cite{BV13}.
-The second result concerns the convergence of the eigenvalue and eigenfunctions of a one-dimensional second order hyperbolic type problem when applying the Finite Element Method.
-This is presented in the textbook \cite{SF97}.
-In this section, the authors use the same general variational problem as presented in \cite{VV02} (Chapter 2).
-The authors assume that this general variational problem has a unique solution.
-To start, the Galerkin approximation for the general variational problem is derived.
-The a unique solution is proved in \cite{BV13} when the forcing function $f$ is continuous.
-Using the Finite Element Method matrices, the Galerkin approximation is rewritten as a system of ordinary differential equations.
-Given that $u$ is a solution of the general variational problem, and $u^h$ is a solution to the Galerkin approximation, the authors define the error $e^h = u - u^h$.
-The in \cite{BV13} the authors prove that this error can be made arbitrarily small by choosing a sufficiently small $h$, such that $u^h \rightarrow u$ as $h \rightarrow 0$.
-\cite{BV18} extends \cite{BV13} to include damping.
-To obtain the error estimate, the authors split the error into two parts.
-The first part is a semi-dicrete problem and the second is a discrete problem.
-These two problems are investigated seperately.
-In this section, the main results of \cite{BV13} are presented.
-The two assumptions made by the authors are also given.
-In this section, the approach of the authors for determining the error estimates for the semi-discrete and fully discrete problems are presented.\\
+In this chapter, two convergence results relating to the Finite Element Method are discussed.
+The first result is the convergence of the Galerkin approximation for vibration problems.
+This is presented in the article \cite{BV13.} For this result, the general variational form of chapter 2 is used.
+The Galerkin approximation of this general variational problem can be derived, as well as an initial value problem using the standard Finite Element Analysis matrices.
+The article \cite{BV13} derive an error estimate for the solution of the general vartiational problem and the solution to it's Galerkin approximation.
+To obtain this error estimate, the authors make two assumptions, and split the problem into a semi-discrete and a fully discrete problem.
+Following the assumptions, the authors prove error estimates for the semi-dicrete and the fully-discrete problem.\\
 
-(Convergence of eigenvalues in Finite Element Analysis)
+The second result concerns the convergence of the eigenvalues and eigenfunctions with the Finite Element Method for one-dimensional vibration problems.
+This is a result form the textbook \cite{SF97}.**********
 
@@
 
-In this chapter, the Timoshenko beam theory is explored further.
-In the first three sections, the theory and two examples of \cite{VV06} are given.
-In this article \cite{VV06}, the authors present a method for finding the exact eigenvalues and eigenfunctions for the Timoshenko beam theory.
-The method provides solutions for three cases where $\lambda <\alpha$, $\lambda =\alpha$ and $\lambda >\alpha$.
-This is an example of the application of the theory on a cantilever Timoshenko beam.
-In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.
-This is an example of the application of the theory on a free-free Timoshenko beam.In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.
-The idea of a suspended Timoshenko is also discuss briefly.
-In this section this section, the article \cite{SP06} is discussed.
+Tis chapter explores the idea of the Timoshenko beam theory further.
+The article \cite{VV06} presents a method of finding the exact eigenvalues and eigenfunctions for a Timoshenko beam.
+The method uses modal analysis to solve a general eigenvalue problem.
+This results in three different cases of possible solutions for the general eigenvalue problem.
+Using these cases, the eigenvalues and eigenfunctions can be calculated.
+The authors also present some examples.
+two examples are verified in this chapter.
+The cantilever and free-free beam.
+For both the eigenvalues are calculated and compared to the results of \cite{VV06}.
+Some examples of modal shapes are also graphed.
+The idea of a suspended beam is breifly discussed.
+Next the article \cite{SP06} is discussed.
 In this section, the authors obtain eigenvalues of a free-free Timoshenko beam by vibrating and measuring the natural frequencies of a real beam.
@@
 This chapter is preperation for the final chapter in this dissertation.
-The finite element method to a cantilever version of each of the models in this dissertation.
+The finite element method is applied to the models of this dissertation.
+Specifically, it is applied to the Cantilever model problem of the three-dimensional and two-dimensional elastic bosies, as well as the cantilever plate model.
+The cantilever Timoshenko beam model is excluded since chapter 4 provides an exact method to calculate the eigenvalues and eigenfunctions.
+Each of the models are assumed to have a rectangular cross-section and is made of the same isotropic material.
+
+to a cantilever version of each of the models in this dissertation.
 The goal of the chapter is to get a numerical formula to solve the eigenvalue problem for each model.

### 2022-11-24 files/Overview.tex
Overview v2.2

@@
 Each of the models are assumed to have a rectangular cross-section and is made of the same isotropic material.
-
-to a cantilever version of each of the models in this dissertation.
-The goal of the chapter is to get a numerical formula to solve the eigenvalue problem for each model.
-The Timoshenko beam model is excluded from this chapter since an exact methd is already presented in chapter 4 (\cite{VV02}).
-The model is assumed to have a rectangular cross-section and is in a cantilever configuration.
-The Galerkin approximation is derived and applying the finite element method, a numerical formula for solving the model problem is given.
-In this numerical formula, the model problem is a system of linear equations.
-This system can be changed to obtain a numerical formula for teh eigenvalue problem.\\
+For each model, a reference configuration is defined.
+The Galerkin approximation can then be derived and using the Finite Element Method, a system of oridinary differential equations can be obatined.
+At this point is it easy to derive a eigenvalue problem for each of the models.
+This eigenvalue problem can be solved using numerical methods.
 
@@
 All models are assumed to have a rectangular cross-section, are in a cantilever configuration and are made of the same isotropic material.
-This first section, is a discussion of the article \cite{LVV09}.
+The first section, is a discussion of the article \cite{LVV09}.
 In this article, the authors investigate the validity of the Timoshenko beam model.
@@
 
+*******************************************************************************
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-12-20 files/Chapter3/dynamicconvergence.tex
added some work on chapter 3

--- 2022-11-03 files/Chapter3/dynamicconvergence.tex
@@
 
-In Section 2.2, a general variational problem Problem GVar from \cite{VV02} is given. The authors of \cite{BV13} use the same general variational problem.
+In Section 2.2, a general variational problem, called Problem GVar, which is identical to the one in \cite{VV02} is given. From this model, a Galerkin Approximation can be derived.
 
@@
 
-Before we can look at the results of \cite{BV13}, some preparation is required. To start, the authors of \cite{BV13} formulate the Galerkin Approximation of Problem GVar.
+Before the main theory of \cite{BV13} can be discussed, some preparation is required.
+First the Galerkin approximation is for Problem GVar is derived.
+Then a equivalent system of ordinary differential equations is derived using the Finite Element Method.\\
 
@@
 \end{DC_Thm2}
+
+This theorem is presented in \cite{BV13}.
 
@@
 
-Now we look at the main results of \cite{BV13}.
 \subsection{Main result}
+
+The main result proving the convergence of the solution of the Galerkin Approximation is given in \cite{BV13} as follows.
 
@@
 	{Main Result}\\
-	If $f\in C^{2}([0,T],X)$, then
+	If $f\in C^{2}([0,T]4,X)$, then
 	\begin{eqnarray*}
@@
 
+The parameter $\tau$ is some number in $(0,T)$. The constant $K_\alpha$ is the constant defined in assumption \textbf{A4} of Section 2.2.1.
+
 \subsection{Obtaining the error estimate}
-In this section we will show how the error estimate in Theorem 2 is obtained in \cite{BV13}.The following two assumptions are made in \cite{BV13}.
+In this section we will show how the error estimate in Theorem 2 is obtained by the authors of \cite{BV13}.\\
 
+The following two assumptions are made in \cite{BV13}.
 \subsubsection*{Assumptions}
@@
 \begin{eqnarray*}
-	b(u-P_hu,v) = 0 \ \ \ \textrm{ for all } v \in V.
+	b(u-Pu,v) = 0 \ \ \ \textrm{ for all } v \in V.
 \end{eqnarray*}
@@
 	If $u$ is the solution of Problem GVar and $u$ satisfies assumption \textbf{B1}, then
-
 	\begin{eqnarray}

### 2023-01-17 files/Chapter3/femconvergence.tex
fem covergence update

@@
-s\documentclass[../../main.tex]{subfiles}
+\documentclass[../../main.tex]{subfiles}
 \begin{document}
 \section{Convergence of eigenvalues in Finite Element Analysis}
-This section looks at the work of the authors of the textbook [SF97].
+In this section, the work in the textbook \cite[p.228-236]{SF73} is discussed.\\
 
-\subsection{Eigenvalue problem for vibration problem}
-Consider the general variational problem Problem GVar from section 2.2.1
-\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
-	Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
-\begin{eqnarray}
-	c(u''(t),v)+a(u'(t),v)+b(u(t),v)= (f(t),v)_{X} \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVar}
-\end{eqnarray}
-while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\\
+Let $H$ be a Hilbert space with the inner product $(\cdot,\cdot)$ and induced norm $||\cdot||$.
+Let $V$ be a linear subspace of $H$, with inner product defined by the bilinear form $b(\cdot,\cdot)$.
+It is assumed that this bilinear form $b$ is symmetric.
 
-\textcolor{red}{Haal uit**********************************}\\
-The following spaces are also defined in section 2.2.1:
+\subsection{General eigenvalue problem}
+Find a function $u \in H$ and number $\lambda \in \mathcal{R}$ such that
+\begin{equation}
+	b(u,v) = \lambda (u,v) \label{GEVP}
+\end{equation} for some $v \in V$.
+
+\subsection{Preparatory theory and notation}
+Some theory is required that is presented in \cite{SF73}.\\
+
+\textbf{Rayleigh quotient}
+\begin{equation*}
+	R(v) = \frac{b(v,v)}{(v,v)} \ \text { for } v \in V.
+\end{equation*}
+
+\textbf{minmax Principle}\\
+Let T denote the class of subspaces of $V$ that jas dimension $j$. Then
+\begin{equation*}
+	\lambda_j = \min_{s\in T}\max_{v \in S} R(v).
+\end{equation*}
+
+\textbf{Rayleigh-Ritz Projection}\\
+If $u \in V$, then $Pu$ is its component in the subspace $S^h$.
+\begin{equation*}
+	b(u-Pu,v^h) = 0 \ \text{ for all } v \in S^h.
+\end{equation*}
+
+Consider a interpolation operator $\Pi$. This projection is linear, i.e.
+\begin{align*}
+	\Pi(f + g) & = \Pi f + \Pi g,\\
+	\Pi(\alpha f) & = \alpha \Pi f \ \text{ for a constant } \alpha. 
+\end{align*}
+
+Define the interval $I_e = [a, a+h]$.
+A necessary condition is for the operator $\Pi$ is that when $\Pi u$ is restricted to the interval $I_e$, this must equal the projection of $u$ restricted to the interval $I_e$.
+This can be written as
+\begin{equation*}
+	\left[ \Pi u \right]_{I_{e}} = \Pi_e [u]_{I_{e}}.
+\end{equation*}
+
+The following notation is introduced.
 \begin{itemize}
-	\item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
-	\item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
-	\item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
-\end{itemize} The inner product of the function space $L^2$ is given by $(\cdot, \cdot)$ with induced norm $||\cdot||_{L^2}$.\\
+	\item[] $\mathcal{P}_j(I_e)$: Is the set of all polynomials on the interval $I_e$ of degree at most $j$.
+	\item[] $r(\Pi_e)$: If the range of $\Pi_e$ is contained in $\mathcal{P}_j(I_e)$ and $k<j$ is the largest integer such that $\Pi_e f = f$ for each $f \in \mathcal{P}_j(I_e)$, then $r(\Pi_e) = k$.
+	\item[] $s(\Pi_e)$: Is a integer and the largest order derivative used in the definition of $\Pi_e$.
+\end{itemize}
 
-Define a Hilbert space $H = V \times W$, with inner product defined by
-\begin{eqnarray*}
-	(x,y)_H := b(x_1,y_1) + c(x_1,y_1) \ \ \ \ \textrm{for all} \ x,y \in H.
-\end{eqnarray*} $V$ is obviously a linear subspace of $H$, and it is assumed that $(\cdot,\cdot)_V  = b(\cdot,\cdot)$. $V$ is also the closure of the test function space $T$.\\
-\textcolor{red}{**********************************}\\
-
-Recall form Section 2.2, $V$ is the energy space with inner-product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
-For the Timoshenko beam theory, $V$ is the closure of the test-function space $T$.
-It is assumed that $b(\cdot,\cdot) = (\cdot,\cdot)_V$.\\
-
-Denote the eigenvalue problem of Problem GVar by Problem GVarE. This eigenvalue problem can be formulated as follow
-
-\subsubsection{Problem GVarE} Find $\lambda \in \mathbb{R}$ and $u \in V$ such that
-\begin{eqnarray*}
-	b(u(t),v) = \lambda c( u(t), v ) \ \ \ \ \textrm{ for all  } v\in V.
-\end{eqnarray*}
-
-\subsection{Interpolation theorem}
-Consider the Interpolation Theorem for Finite Elements from the textbook [ORXX].\\
-
-\sout{Consider the following theorem for Finite Elements from the textbook [ORXX]. This theorem is called The Interpolation Theorem for Finite Elements.}
-
+From the textbook \cite{ORXX}, the following approximation for finite elements is given verbatim:
 \newtheorem*{Interpolation}{Theorem}
@@
 	where $|u|_H^{k+1}(\Omega)$ is the seminorm.
-\end{Interpolation} ************what is p?
+\end{Interpolation}
 
-This theorem provides an error estimate for the projection of $u$ in a Sobolev space.
-By proving this theorem, the authors in [ORXX] show the accuracy of the finite element interpolations of functions $u$ defined in a Sobolev space $H^{k+1}(\Omega)$ into a finite dimensional subspace $S^h(\Omega)$, with the projection defined by $\Pi u$.\\
+For the requirements of this dissertation, this is too general and can be simplified with assumptions.
+The first assumption is a reiteration that the eigenvalue problem is one-dimensional.
+Another assumption is that the basis of $S^h$ consists of polynomials.
+With these assumptions, the semi-norm $|u|_H$ is equal to the norm $||u||$.
+This approximation theorem can be rewritten as
+\newtheorem{Interpolation_2}{Theorem}
+\begin{Interpolation_2}
+	Suppose there exists an integer $k$ such that for each element
+	\begin{equation*}
+		s(\Pi_e) + 1 \leq k \leq r(\Pi_e) +1.
+	\end{equation*}
+	Then there exists a constant $C$ such that for any $u \in C^k_+(I)$,
+	\begin{equation*}
+		||(\Pi u)^(m) - u^(m)|| \leq C h^{k-m} || u^(k)|| \ \text{ for } m = 0,1,...,k.
+	\end{equation*}
+\end{Interpolation_2}
 
-\subsection{Eigenvalue problem for our models*********}
-For this dissertation, the result can be simplified and need not be so general.
-The basis functions used in this dissertation are called Hermite-Cubic basis functions.
-Therefore the focus can be restricted to functions in an n-dimensional polynomial space.\\
-**********Wys hoe function spaces H, V, W verander na polynomial spcaes!!************
+It is well known that the eigenvalues of a eigenvalue problem such as \eqref{GEVP} form an infinite sequence $(\lambda_i)$.
+Assume that the eigenvalues $\lambda_i$ can be ordered $\lambda_1 \leq \lambda_2 \leq \lambda_3 \leq ...$ and denote the corresponding eigenfunctions $u_i$.\\
 
-\subsubsection{Notation}
-Define the linear interpolation operator as
+Since any multiple of a eigenfunction is still an eigenfunction, the eigenfunctions can be normalized so that $||u_i|| = 1$ for all $i$.\\
+
+Fix $m \in \mathbb{N}$.
+Let $\left\{ \phi_i \in V | i = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
+Define $S^h := \text{span}\left\{\phi_i \in V | i = 1,2,...,m\right\}$.\\
+
+Since $S^h$ is finite dimensional, the ordering of the eigenvalues still hold.
+The eigenvalues in the space $S^h$ is denoted as $\lambda_i^h$ with corresponding normalized eigenfunction $u^h_i$ for $i = 1,2,...,m$.\\
+
+The space $S^h$ is a finite dimensional subspace of $V$.
+Therefore any subspace of $S^h$ will also be a subspace of $V$.
+So the minmax principle applies and a lower bound for the eigenvalues can be found:
+\begin{equation}
+	\lambda_i \leq \lambda_i^h.
+\end{equation}
+
+\subsection{Estimating the eigenvalues.}
+Let $E_j \in V$ denote the eigenspace spanned by the exact eigenvalues $\left\{u_1,u_2,...,u_j \right\}$ for $j = 1,2,...,m$.\\
+
+Then consider the subspace $S_j$ where
+\begin{equation*}
+	S_j = PE_j \ \text{ for } j = 1,2,...,m.
+\end{equation*} The elements $Py_i$ are the projections of the eigenfunctions $u_i$ into the space $S^h$.
+These projections $Py_i$ are not necessarily equal to $u^h_j \in S^h$, but it can be shown that they are close.\\
+
+Let $B_m = \left\{u \in e_m \ | \ ||u|| = 1 \right\}$ and define $\mu_m = \inf\left\{(Pu,Pu \ | \ u \in B_m)\right\}$.\\
+
+The next steps in the textbook \cite{SF73} contains proofs with multiple results. In an attempt to better understand the results, the proofs are broken up into smaller proofs.\\
+
+The first step to obtain estimates for the eigenvalues, it to show that the elements of $B_m$ are linearly independent.
+
+\newtheorem{Prop_1}{Proposition}
+\begin{Prop_1}
+ $\mu_{m} > 0$ if and only if $\dim S_{m} = m$.
+\end{Prop_1}
+\begin{proof}
+	To show that the dimension of $S_m = m$, suppose that the elements of $B_m$ are linearly dependent.
+Then there exists a $u \in B_m$ such that $Pu = 0$ and consequently $\mu_m = 0$.
+The result follows from the contra-positive.
+\end{proof}
+
+\newtheorem{Prop_2}[Prop_1]{Proposition}
+\begin{Prop_2}
+	$\lambda^{h}_{m} \leq \max R(Pu) \ \text{ for } u \in B_{m}$\\
+\end{Prop_2}
+\begin{proof}
+	Since $\dim S_{m} = m$, following from the minmax principle
+	\begin{equation*}
+		\lambda_m^h \leq \max R(v) \ \text{ for } v \in S_m.
+	\end{equation*}
+
+	Take an arbitrary nonzero $v \in S_m$. Then there exists a $Py \in E_m$ such that $v = Py$.\\
+
+	Now we take an arbitrary $v \in S_{m}$, $v \neq 0$.
+Then there exists a $u \in E_{m}$ such that $Py = v$.
+This $Py$ is the projection into $S_m$ of some $u \in E_m$ (which is also $\displaystyle \frac{1}{||u||}u \in B_m$).\\
+
+	Next a linearity property for $R$ can be proven. 
 	\begin{eqnarray*}
-	\Pi f &=& f_{I},
-\end{eqnarray*} such that
+	R(\frac{1}{||u||}u) &=& \frac{b\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)}{\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)},\\
+						&=& \frac{b(u,u)}{(u,u)},\\
+						&=& R(u).
+	\end{eqnarray*}
+	So finally,
 	\begin{eqnarray*}
-	\Pi (f+g) &=& \Pi f + \Pi g, \\
-	\Pi (\alpha f) &=& \alpha \Pi f.
+	\lambda_{m}^{h} &\leq & \max R(v) \ \text{ for } \ v \in S_{m},\\
+						&=& \max R(Pu) \ \text{ for } \ u \in E_{m},\\
+						&=& \max R(Pu) \ \text{ for } \ u \in B_{m}.
 	\end{eqnarray*}
+\end{proof}
+
 %\newpage
+In the textbook, the authors show that the eigenfunctions are orthogonal. But they do so using matrix representations of the eigenvalue problem. A different method can be used to show this.\\
 
-Define the reference interval $I_{e} = [a, a+h]$. The following notation,
+Pick any $i,j \in \mathbb{N}$ such that $i,j \leq m$. Let $v_{i},v_{j} \in V$ be arbitrary, then
 \begin{eqnarray*}
-	\left[\Pi u \right]_{I_{e}} &=& \Pi_{e} \left[u\right]_{I_{e}},
-\end{eqnarray*} implies that $\Pi u$ restricted to the interval $I_{e}$ must equal $\Pi_{e} u$.\\
+	b(u_{i},u_{i}) &=& \lambda_{i}( u_{i},u_{i}),\\
+	b(u_{j},u_{j}) &=& \lambda_{j}( u_{j},u_{j}).
+\end{eqnarray*}
+Now pick $u_{i} = u_{j}$ and $u_{j} = u_{i}$. Then
+\begin{eqnarray*}
+	b(u_{i},u_{j}) &=& \lambda_{i}( u_{i},u_{j}),\\
+	b(u_{j},u_{i}) &=& \lambda_{j}( u_{j},u_{i}).
+\end{eqnarray*}
+Then using the symmetry of $b(\cdot,\cdot)$ and $( \cdot, \cdot )$, and subtracting,
+\begin{eqnarray*}
+	0 &=& (\lambda_{i} - \lambda_{j})( u_{i}, u_{j} )
+\end{eqnarray*}
+So if $i \neq j$ then $\lambda_{i} \neq \lambda_{j}$.\\
 
-Define the following set and integers.
-\begin{itemize}
-	\item[] $\mathcal{P}_{j}(I_{e}):$ the set of all polynomials on the interval $I_{e}$ of degree at most $j$.\\
+Therefore $u_{i}$ and $u_{j}$ must be orthogonal. And as mentioned previously, $||u|| = 1$.
 
-	\item[] $r(\Pi_{e})$: If the range of $\Pi_{e}$ is contained in $\mathcal{P}_{j}(I_{e})$ and $k\leq j$ is the largest integer such that $\Pi_{e} f = f$ for each $f\in\mathcal{P}_{j}(I_{e})$, then $r(\Pi_{e}) = k$.\\
-
-	\item[] $s(\Pi_{e})$: the integer $s(\Pi_{e})$ is the largest order derivative used in the definition of $\Pi_{e}$.
-\end{itemize}
-\textbf{Interpolation Theorem} Suppose there exists an integer $k$ such that for each element
+\newtheorem{Lem_1}{Lemma}
+\begin{Lem_1}
+	$\displaystyle \lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}$
+\end{Lem_1}
+\begin{proof}
+	Consider the linearity of the bilinear form $b$, and fact that any $u \in E_m$ can be expressed as a linear combination $u = \sum_{i=1}^{m} c_{i}u_{i}$. Then
 	\begin{eqnarray*}
-	s(\Pi_{e}) + 1 \leq & k & \leq r(\Pi_{e}) + 1
-\end{eqnarray*}
-Then there exists a constant C such that for any $u\in C^{k}_{+}(I)$ we have
-\begin{eqnarray*}
-	||(\Pi u)^{(m)} - u^{(m)}|| & \leq & Ch^{k-m}||u^{(k)}|| \ \ \textrm{ for } m = 0,1,...,k
+	b(u,u) &=& b\left(\sum_{i=1}^{m} c_{i}u_{i},\sum_{j=1}^{m} c_{j}u_{j}\right),\\
+			&=& \sum_{i=1}^{m} c_{i}\sum_{j=1}^{m} c_{j} b(u_{i},u_{j}).
 	\end{eqnarray*}
 
-In this form, the theory of convergence of the eigenvalues for our models can be investigated.
-For this theory, consider another textbook [SF73].
-In this textbook, the authors prove the convergence of of the eigenvalues using the interpolation theorem.
-The results of the authors of [SF73] is discussed here, in the notation followed in throughout this dissertation.
+	The summation parameters can be merged into a single parameter. Then
+	\begin{eqnarray*}
+		b(u,u)  & = & \sum_{i=1}^{m} c_{i}^{2} \lambda_{i} u_i,\\
+				& \leq & \lambda_{m}\sum_{i=1}^{m} c_{i}^{2} u_i,\\
+				& = & \lambda_{m}||u||^2.
+	\end{eqnarray*} for all $u \in B_m$.\\
 
-\subsection{Convergence of the eigenvalues}
-From the brief introduction of modal analysis in section 1.xxx, it is clear that the solution of the eigenvalue problem is an infinite sequence of eigenvalues with corresponding eigenfunctions (eigenvectors in this case).
-Therefore assume the eigenvalues can be ordered, i.e.
-$\lambda_{1} \leq \lambda_{2} \leq \lambda_{3} \leq ...$.
-Denote the corresponding eigenvectors by $u_{i}$ and scale the eigenvectors such that $||u_{i}|| = 1$ for all $i$.
-Fix $m\in\mathbb{N}$ and consider a finite dimensional ordered subset of the eigenvalues $\lambda_{1} \leq \lambda_{2} \leq \lambda_{3} \leq ...
-\leq \lambda_{m}$.\\
+	$b(u,u) = \sum_{i=1}^{m} c_{i}^{2} \lambda_{i} \leq \lambda_{m}\sum_{i=1}^{m} c_{i}^{2} =\lambda_{m} ||u||^{2}$ for all $u \in E_{m}$.\\
+	And since $B_{m} \subset E_{m}$, we have $b(Pu,Pu) \leq \lambda_{m}$ for all $u\in B_{m}$\\
 
-For each of the models in this dissertation, the set of test functions are defined as $T$.
-Now take the set of admissible basis functions $\left\{ \phi_{i} \in T \ | \ i = 1,2,...,m\right\}$, and define a finite dimensional subspace $S^{h} := span(\left\{\phi_{i}\in T \ | \ i = 1,2,...,m\right\})$ of V.
-From this finite dimensional subspace, the following set of eigenvalues $\lambda^{h}_{1} \leq \lambda^{h}_{2} \leq \lambda^{h}_{3} \leq ...
-\leq \lambda^{h}_{m}$, also ordered, with corresponding normalized eigenvectors $u^{h}_{i}$ for each i are obtained.\\
-
-The following definitions from [SF73] are required for the theory.\\
-\textbf{Rayleigh Quotient:}
-\begin{align*}
-	R(v) = \frac{b(v,v)}{( v,v )}
-\end{align*}
-
-\textbf{minmax Principle:} Let T denote the class of subspaces of V that has dimension j. Then
-\begin{align*}
-\lambda_{j} = \min\limits_{s\in T} \max\limits_{v\in S}R(v)
-\end{align*}\\
-
-\textbf{Rayleigh-Ritz Projection:} If $u \in V$, then $Pu$ is its component in the subspace $S^{h}$:
-\begin{align*}
-b(u-Pu,v^{h}) = 0 \ \ \ \ \forall \ v^{h} \in S^{h}
-\end{align*}
-
-Now since the space $S^{h}$ is a finite subspace of T, any subspace of $S^{h}$ will also be a subspace of T.
-So the minmax principle applies to $S^{h}$.
-So we then get a lower bound for the approximate eigenvalues
-\begin{align*}
-\lambda_{i} \leq \lambda_{i}^{h}
-\end{align*}
-
-Let $E_{j} \subset T$ denote the eigenspace spanned by $\left\{u_{1},u_{2},...,u_{j}\right\}$ for $j = 1,2,...,m$. Then we consider the subspaces $S_{j}$ where
-\begin{align*}
-S_{j} = PE_{j} \ \ \textrm{ for } j = 1,2,...,m
-\end{align*}
-The elements $Py_{i}$ of $E_{j}$ are the projections of the exact eigenvectors to the space $S^{h}$ but are not necessarily equal to the eigenvector's approximations $u^{h}_{i}$.
-But it can proved that they are close.\\
-
-Let $B_{m} = \left\{u\in E_{m} \ | \ ||u|| = 1\right\}$ and define $\mu_{m} = \inf\left\{ ( Pu,Pu) \ | \ \in B_{m} \right\}$.\\
-
-\textbf{Proposition 7.1:} $\mu_{m} > 0$ if and only if $\dim S_{m} = m$\\
-
-\begin{comment}
-\textbf{Proof:} Suppose that $\dim S_{m} < m$, then the set of projected eigenvalues $\left\{Py_{1}, Py_{2},...,Py_{m}\right\}$ is a linearly dependent set.
-So then there exists a $u \in B_{m}$ such that $Pu = 0$.
-Then $\mu_{m} = 0$.
-So the result follows by the contra-positive.
-\qed \\
-
-So we from here on assume that $S^{h}$ is such that $\dim S_{m} = m$.\\
-\end{comment}
-
-\textbf{Proposition 7.2:} $\lambda^{h}_{m} \leq \max\left\{R(Pu) \ | \ u \in B_{m} \right\}$\\
-
-\begin{comment}
-\textbf{Proof:} The minmax principle gives $\lambda_{m}^{h} \leq \max\left\{R(v) \ | \ v \in S_{m} \right\}$ since $\dim S_{m} = m$.\\
-
-Now we take an arbitrary $v \in S_{m}$, $v \neq 0$. Then there exists a $u \in E_{m}$ such that $Py = v$. Since $u \in E_{m}$, we have that $\frac{1}{||u||}u \in B_{m}$ and
-
+	So now from the definition of $\mu_{m}^{h}$ and the Rayleigh quotient, we have
 	\begin{eqnarray*}
-R(\frac{1}{||u||}u) &=& \frac{b\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)}{\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)}\\
-					&=& \frac{b(u,u)}{(u,u)}\\
-					&=& R(u)
+		R(Pu) &=& \frac{b(Pu,Pu)}{(Pu,Pu)}\\
+			&=& \frac{b(Pu,Pu)}{||Pu||^{2}}\\
+			&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}
 	\end{eqnarray*}
-So then we have that
+	This together with Proposition 7.1 gives
 	\begin{eqnarray*}
-\lambda_{m}^{h} &\leq & \max\left\{R(v) \ | \ v \in S_{m} \right\}\\
-					&=& \max\left\{R(Pu) \ | \ u \in E_{m} \right\}\\
-					&=& \max\left\{R(Pu) \ | \ u \in B_{m} \right\}
-\end{eqnarray*}\qed
-\end{comment}
-%\newpage
-
-\textbf{Lemma 7.1:} $\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}$\\
-
+		\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}
+	\end{eqnarray*}
+\end{proof}
 \begin{comment}

### 2023-01-17 files/Overview.tex
added some work on chapter 3
fem covergence update

--- 2022-11-23 files/Overview.tex
@@
 
-\subsubsection{Comparison of models}
-This chapter introduces the models used in this dissertation.
+\subsubsection*{Comparison of models}
 
-Two models for a three-dimensional elastic solid are presented.
-These models are a cantilever and a free-free elastic body.
-A dimensionless variational form of the cantilever model is derived.
-General plane stress is discussed.
-A model for a two-dimensional elastic solid is presented.
-The model is a cantilever elastic body.
-This model is a special case of plane stress of a three-dimensional elastic body.
-The model is given in a dimensionless variational form by simplification of the three-dimensional model.
-Four models for a one-dimensional beam are presented using the Timoshenko beam theory are presented.
-The models are a cantilever, free-free, pinned-pinned and a suspended beam.
-A dimensionless variational form for the models are derived.
-Two models for a Reissner-Mindlin plate are presented.
-The models are a cantilever and a rigidly clamped plate.
-A dimensionless variational form for the cantilever model is derived.
-(ROD THEORY?)
+In the first chapter, the various models of this dissertation are presented. The models consist of
 
-\subsubsection{Mathematical analysis of vibration problems}
+The models consist of three-dimensional, two-dimensional and one-dimensional models.
+For the three-dimensional model, a cantilever and a free-free elsatic body are used.
+The general case of plane stress is also discussed.
+As a result of a special case of plane stress, a two-dimensional cantilever elastic body is obtained.
+For the one dimensional model, the Timoshenko beam theory is considered.
+The beam models for the Timoshenko beam are a cantilever, free-free, pinned-pinned and a suspended beam models.
+Finally a Reissner-Mindlin plate model is given.
+For this plate, the models are a cantilever and a rigidly clamped plate.
+The variational form of the models are derived.
 
-This chapter is a discussion and example of application of the theory presented in the article \cite{VV02}.
-This article concerns the existence and uniqueness of solutions of second order hyperbolic type problems.
-The models in this dissertation as such problems.
-This chapter also concerns the idea of modal analysis.
-This is a method to find the natural frequencies of a system.
-This method is used later in the dissertation.
-This section is a discussion of the theory presented in the article \cite{VV02}.
-The authors define a general variational problem.
-This problem is defined on specific Hilbert spaces.
-Four assumptions are made in the article as well as some notation introduced.
-The main resuls of the article are given in this section.
-The results include existence and uniqueness of solutions for strong and weak damped models.
-The models in this dissertation are all weakly damped.
-To prove the results, the approach of the authors are as follows.
-The general variational problem is rewritten for a first order system of differential equations.
-This system is defined on a Hilbert space $H$.
-A operator $A$ is defined, and using the assumptions the authors prove that the operator $A$ is an infinitesimal generator of a $C_0$-semigroup of contractions with a domain in $H$.
-Using this operator the authors rewrite the system of differential into the form $\displaystyle x' = Ax + f$.
-To be more precise, the system of first order system of differential equations can be written as an initial value problem.
-The existence and uniqueness results for the first order system is easily proven with an initial value problem.
-The authors also prove that a solution of the first order system is also a solution to the general variational problem.
-Using semi-group theory, a unnique solution for the initial value problem can be proved.
-The authors also provide the link between the solutions of the initial value problem and the general variational form.
-Thus proving the required results.
-As an example of the application of the theory, the weak variational form for the cantilever Timshenko beam is introduced.
-This weak variational problem is defined on complete product spaces.
-The four assumptions of \cite{LVV09} are proved for this example model.
-(Modal Analysis)
-
-\subsubsection{Finite element theory}
-
-In this Chapter, two convergence results related to the Finite Element Method is presented.
-This first result is the convergence of the Galerkin approximation of a second order hyperbolic type problem, presented in the article \cite{BV13}.
-The second result concerns the convergence of the eigenvalue and eigenfunctions of a one-dimensional second order hyperbolic type problem when applying the Finite Element Method.
-This is presented in the textbook \cite{SF97}.
-In this section, the authors use the same general variational problem as presented in \cite{VV02} (Chapter 2).
-The authors assume that this general variational problem has a unique solution.
-To start, the Galerkin approximation for the general variational problem is derived.
-The a unique solution is proved in \cite{BV13} when the forcing function $f$ is continuous.
-Using the Finite Element Method matrices, the Galerkin approximation is rewritten as a system of ordinary differential equations.
-Given that $u$ is a solution of the general variational problem, and $u^h$ is a solution to the Galerkin approximation, the authors define the error $e^h = u - u^h$.
-The in \cite{BV13} the authors prove that this error can be made arbitrarily small by choosing a sufficiently small $h$, such that $u^h \rightarrow u$ as $h \rightarrow 0$.
-\cite{BV18} extends \cite{BV13} to include damping.
-To obtain the error estimate, the authors split the error into two parts.
-The first part is a semi-dicrete problem and the second is a discrete problem.
-These two problems are investigated seperately.
-In this section, the main results of \cite{BV13} are presented.
-The two assumptions made by the authors are also given.
-In this section, the approach of the authors for determining the error estimates for the semi-discrete and fully discrete problems are presented.\\
-
-(Convergence of eigenvalues in Finite Element Analysis)
-
-\subsubsection{Timoshenko beam model}
-
-In this chapter, the Timoshenko beam theory is explored further.
-In the first three sections, the theory and two examples of \cite{VV06} are given.
-In this article \cite{VV06}, the authors present a method for finding the exact eigenvalues and eigenfunctions for the Timoshenko beam theory.
-The method provides solutions for three cases where $\lambda <\alpha$, $\lambda =\alpha$ and $\lambda >\alpha$.
-This is an example of the application of the theory on a cantilever Timoshenko beam.
-In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.
-This is an example of the application of the theory on a free-free Timoshenko beam.In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.
-The idea of a suspended Timoshenko is also discuss briefly.
-In this section this section, the article \cite{SP06} is discussed.
-In this section, the authors obtain eigenvalues of a free-free Timoshenko beam by vibrating and measuring the natural frequencies of a real beam.
-This empirical data is then compared to the theoretical results of various methods, including the Finite Element Method.
-In this last section, a example of the application of the Timoshenko beam model is presented.
-This section is a study of a technical report.
-In this report, the authors present a model for a cantilever Timoshenko beam with a tip body and elastic interfaces.
-This section also expands the numerical results of the report.
-The variational form of the model is derived, and the Galerkin approximation follows.
-The Mixed Finite Element Method is applied to the model.
-Using the Finite Element Method, the solution of the model is numerically calculated.
-Various results are given for different values of the parameters.
-The numerical results and figures confirms that the model behaves as expected.
-
-\subsubsection{Finite element method}
-This chapter is preperation for the final chapter in this dissertation.
-The finite element method to a cantilever version of each of the models in this dissertation.
-The goal of the chapter is to get a numerical formula to solve the eigenvalue problem for each model.
-The Timoshenko beam model is excluded from this chapter since an exact methd is already presented in chapter 4 (\cite{VV02}).
-The model is assumed to have a rectangular cross-section and is in a cantilever configuration.
-The Galerkin approximation is derived and applying the finite element method, a numerical formula for solving the model problem is given.
-In this numerical formula, the model problem is a system of linear equations.
-This system can be changed to obtain a numerical formula for teh eigenvalue problem.\\
-
-\subsubsection{Validity of cantilever beam and plate models}
-
-In this chapter, the validity of the models in this dissertation is investigated using numerical results.
-Specifically the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate is investigated.
-In this case, the term validity refers to how well the model compares to a more realistic model.
-All models are assumed to have a rectangular cross-section, are in a cantilever configuration and are made of the same isotropic material.
-This first section, is a discussion of the article \cite{LVV09}.
-In this article, the authors investigate the validity of the Timoshenko beam model.
-The authors compare the Timoshenko beam model to a more realistic two-dimensional beam model.
-The comparison is made with the eigenvalues and eigenfunctions.
-From modal analysis it is known that the solution of the models are linear combinations of the eigenvalues and eigenfunctions.
-The two-dimensional model also have eigenvalues that do not have a corresponding eigenvalue in the Timoshenko beam model.
-The authors call all matching eigenvalues beam-type eigenvalues.
-The authors show that the Timoshenko beam model compare well to the two-dimensional model for long and short beams.
-The results of the article are verified and extra results are also calculated for the rest of this chapter.
-In this section, the aricle \cite{LVV09} is extended to verify the validity of the two-dimensional elastic model.
-The two-dimensional elastic model is compared to a more realistic three-dimensional model.
-The two dimensional model serves as a intermediate step between the Timoshenko beam model and the three-dimensional model.
-The same approach of \cite{LVV09} is used to compare the two models.
-The result show that the two-dimensional model compare very well to the three-dimensional model, especially for beam problems.
-The last section takes the idea of \cite{LVV09} and extends it to the Reissner-Mindlin plate model.
-The Reissner-Mindlin plate model is compared to a more realistic three-dimensional plate model.\\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection*{Mathematical analysis of vibration problems}
+\subsubsection*{Finite element theory}
+\subsubsection*{Timoshenko beam model}
+\subsubsection*{Finite element method}
+\subsubsection*{Validity of cantilever beam and plate models}
 
@@
 \subsubsection{Main results for existence and uniqueness}
-The main resuls of the article are given in this section.
+The main results of the article are given in this section.
 The results include existence and uniqueness of solutions for strong and weak damped models.

### 2023-01-17 files/Chapter1/3DModel.tex

@@
 \section{Model problem for a three-dimensional elastic solid} \label{sec:3D_Model}
-In this section we introduces the linear theory for a three-dimensional elastic solid. The textbook of Fung \cite{Fung65} with some changes in the notation. \\
+In this section we introduces the linear theory for a three-dimensional elastic
+solid. The textbook of Fung \cite{Fung65} is used with some changes in the
+notation. \\
 
- The equation of motion and constitutive equation are given in subsection \ref{ssec:3D_Model:EquationOfMotion}.
-The dimensionless form of the equation of motion and constitutive equation are derived in subsection \ref{ssec:3D_Model:DimensionlessForm}.
-Model problems are presented in subsection \ref{ssec:3D_Model:ModelProblems}.
-The variational form for the vibration problem is given in section \ref{ssec:3D_Model:VariationalForm}.
-Plane stress is discussed in section \ref{ssec:3D_Model:PlaneStress} \\
+The equation of motion and constitutive equation are given in subsection
+\ref{ssec:3D_Model:EquationOfMotion}. The dimensionless form of the equation of
+motion and constitutive equation are derived in subsection
+\ref{ssec:3D_Model:DimensionlessForm}. Model problems are presented in
+subsection \ref{ssec:3D_Model:ModelProblems}. The variational form for the
+vibration problem is given in section \ref{ssec:3D_Model:VariationalForm}.
+Plane stress is discussed in section \ref{ssec:3D_Model:PlaneStress}
 
 \subsection{Equations of motion and constitutive equations} \label{ssec:3D_Model:EquationofMotion+ConstitutiveEquation}
-Consider a vector valued function $u$ defined on domain $\Omega \subset {R}^3$ where $u$ describes the displacement of $\Omega$ in ${R}^3$.
+Consider a vector valued function $u$ defined on domain $\Omega \subset {R}^3$
+where $u$ describes the displacement of $\Omega$ in ${R}^3$.
 \subsubsection{Equation of motion}\label{ssec:3D_Model:EquationOfMotion}
@@
 
-In \eqref{eq:3D_Model:EM}, $\rho$ is the density of the elastic body, $T$ is the stress tensor with components $\sigma_{ij}$, $Q$ is an external body force acting on $\Omega$ and $\textrm{div}T$ is the divergence of the tensor $T$ and represented by
+In \eqref{eq:3D_Model:EM}, $\rho$ is the density of the elastic body, $T$ is
+the stress tensor with components $\sigma_{ij}$, $Q$ is an external body force
+acting on $\Omega$ and $\textrm{div}T$ is the divergence of the tensor $T$ and
+represented by
 \begin{eqnarray}
@@
 	\begin{bmatrix}
-		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13}\\
-		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23}\\
+		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13} \\
+		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23} \\
 		\partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
@@
 
-Only small vibrations are considered.
-This means that the local displacements and rotations are small and hence the stress tensor $T$ is symmetric.
-Let $\textrm{Tr}(T)$ denote the trace of the stress tensor T, that is
+Only small vibrations are considered. This means that the local displacements
+and rotations are small. Hence the stress tensor $T$ is symmetric. Let
+$\textrm{Tr}(T)$ denote the trace of the stress tensor $T$, that is
 \begin{eqnarray}
@@
 \subsubsection*{Strain}\label{sssec:3D_Model:Strain}
-Infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$ with components
+Infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$, with components
 \begin{eqnarray}
@@
 
-In this dissertation, we only consider isotropic materials. As a consequence, the constitutive equation (Hooke's law) takes the following form.
+In this dissertation, we only consider isotropic materials. As a consequence,
+the constitutive equation (Hooke's law) takes the following form.
 
@@
 
-Hooke's Law \eqref{eq:3D_Model:CE} is the constitutive equation for the three-dimensional elastic model used in problems. Conditions for the problems to be well posed, is discussed in Chapter 2.
+Hooke's Law \eqref{eq:3D_Model:CE} is the constitutive equation for the
+three-dimensional elastic model used in problems. Conditions for the problems
+to be well posed, are discussed in Chapter 2.
 
 \subsection{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
-The dimensionless form of the equation of motion and constitutive equation are derived in this subsection.
-Suppose $\ell$ represents some notable dimension (eg.the length) of the elastic body and $G$ the shear modulus of elasticity.\\
+The dimensionless form of the equation of motion and constitutive equation are
+derived in this subsection. Suppose $\ell$ represents some notable dimension
+(e.g.the length) of the elastic body and $G$ the shear modulus of elasticity.\\
 
@@
 
-where $\kappa^2$ is a dimensionless constant and $t_0$ must be specified. A convenient choice for $t_0$ (see section \ref{sec:1D_Model}) is \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]
+where $\kappa^2$ is a dimensionless constant and $t_0$ must be specified. A
+convenient choice for $t_0$ (see section \ref{sec:1D_Model}) is \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]
 
@@
 \subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
-Suppose $\Omega \subset R_3$ is the reference configuration for a solid executing small vibrations.
-The boundary of $\Omega$ can be divided into two distinct parts, referred to as $\Sigma$ and $\Gamma$.
-The following will be considered a model problem for a three-dimensional elastic body.
+Suppose $\Omega \subset R_3$ is the reference configuration for a solid
+executing small vibrations. The boundary of $\Omega$ can be divided into two
+distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be
+considered a model problem for a three-dimensional elastic body.
 \begin{enumerate}
@@
 \subsubsection{Problem 3D-1}\label{sssec:3D_Model:Problem3D1}
-Find a vector valued function $u$, satisfying equations \eqref{eq:3D_Model:EM-D} to \eqref{eq:3D_Model:CE-D} and the following boundary conditions:\\
+Find a vector valued function $u$, satisfying equations
+\eqref{eq:3D_Model:EM-D} to \eqref{eq:3D_Model:CE-D} and the following boundary
+conditions:\\
 
@@
 \subsubsection{Problem 3D-2}\label{sssec:3D_Model:Problem3D2}
-Find a vector valued function $u$, satisfying equations \eqref{eq:3D_Model:EM-D} to \eqref{eq:3D_Model:CE-D} and the following boundary conditions:\\
+Find a vector valued function $u$, satisfying equations
+\eqref{eq:3D_Model:EM-D} to \eqref{eq:3D_Model:CE-D} and the following boundary
+conditions:\\
 
@@
 \subsection{Variational form}\label{ssec:3D_Model:VariationalForm}
-Let $\phi \in C({\Omega})$ be an arbitrary vector valued function. Multiplying $\phi$ to equation \eqref{eq:3D_Model:EM-D} and integrating over the domain $\Omega$ results in,
+Let $\phi \in C({\Omega})$ be an arbitrary vector valued function. Multiplying
+$\phi$ to equation \eqref{eq:3D_Model:EM-D} and integrating over the domain
+$\Omega$ results in,
 
 \begin{eqnarray*}
-	\int_{\Omega} (\partial_t^2 u)\cdot \phi \ dV & = & \int_{\Omega} (\textrm{div} T)\cdot \phi \ dV + \int_{\Omega} Q \cdot \phi \ dV.
+	\int_{\Omega} (\partial_t^2 u)\cdot \phi \ dV & = & \int_{\Omega} (\textrm{div} T)\cdot \phi \ dV
+	+ \int_{\Omega} Q \cdot \phi \ dV.
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-	\textrm{Tr}(T\Phi) & = & \sigma_{11} \partial_1\phi_1 + \sigma_{12}\partial_1 \phi_2 + \sigma_{13}\partial_1 \phi_3 + \sigma_{21}\partial_2 \phi_1 + \sigma_{22}\partial_2\phi_2 + \sigma_{23}\partial_2 \phi_3 \nonumber \\
-	& & + \sigma_{31}\partial_3 \phi_1 + \sigma_{32}\partial_3\phi_2 + \sigma_{33}\partial_3 \phi_3.
+	\textrm{Tr}(T\Phi) & = & \sigma_{11} \partial_1\phi_1 + \sigma_{12}\partial_1 \phi_2 + \sigma_{13}\partial_1 \phi_3 + \sigma_{21}\partial_2 \phi_1 + \sigma_{22}\partial_2\phi_2 + \sigma_{23}\partial_2 \phi_3 \nonumber \\ & & + \sigma_{31}\partial_3 \phi_1 + \sigma_{32}\partial_3\phi_2 + \sigma_{33}\partial_3 \phi_3.
 \label{Trc}
@@
 \begin{eqnarray*}
-	\int_{\Omega} \textrm{div}(T\phi) \ dV & = & \int_{\partial \Omega} T\phi \cdot n \ dS,\\
-	& = & \int_{\partial \Omega} Tn \cdot \phi \ dS.
+	\int_{\Omega} \textrm{div}(T\phi) \ dV & = & \int_{\partial \Omega} T\phi \cdot n \ dS,\\ & = & \int_{\partial \Omega} Tn \cdot \phi \ dS.
 \end{eqnarray*}
@@
 \begin{align*}
-	\int_{\Omega} (\partial_t^2 u)\cdot \phi \ dV = -\int_{\Omega} \textrm{Tr}(T\Phi) \ dV  + \int_{\Omega} Q\cdot\phi \ dV + \int_{\partial \Omega} Tn\cdot \phi \ dS.
+	\int_{\Omega} (\partial_t^2 u)\cdot \phi \ dV = -\int_{\Omega} \textrm{Tr}(T\Phi) \ dV +
+	\int_{\Omega} Q\cdot\phi \ dV + \int_{\partial \Omega} Tn\cdot \phi \ dS.
 \end{align*}
@@
 \begin{eqnarray*}
-	\int_\Omega~ (\partial^2_t u) \cdot \phi~dV & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
-	\textrm{Tr}(\Phi) ~dV + \int_\Omega~ Q \cdot \phi~dV
-	+ \int_{\partial \Omega}~Tn \cdot \phi~dS,
+	\int_\Omega~ (\partial^2_t u) \cdot \phi~dV & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+
+	c_2\textrm{Tr}({\cal E}) \textrm{Tr}(\Phi) ~dV + \int_\Omega~ Q \cdot \phi~dV +
+	\int_{\partial \Omega}~Tn \cdot \phi~dS,
 \end{eqnarray*}
@@
 \subsubsection{Test functions}\label{sssec:3D_Model:TestFunction}
-Define the following set of test functions $T(\Omega)$ for Problem 3D-1 and Problem 3D-2:\\
+Define the following set of test functions $T(\Omega)$ for Problem 3D-1 and
+Problem 3D-2:\\
 
@@
 
-The well-posedness of the model is treated in Chapter 2, where Korn's inequality is presented.
-Applications are continued in Chapter 4, 5 and 6.
-In Chapter 4, a free-free three-dimensional beam is discussed as part of an empirical study.
-In Chapter 5, the finite element analysis is applied to a cantilever beam to solve the eigenvalue problem.
-In Chapter 6, a cantilever beam in used in the comparison of our linear models.
+The well-posedness of the model is treated in Chapter 2, where Korn's
+inequality is presented. Applications are continued in Chapter 4, 5 and 6. In
+Chapter 4, a free-free three-dimensional beam is discussed as part of an
+empirical study. In Chapter 5, the finite element analysis is applied to a
+cantilever beam to solve the eigenvalue problem. In Chapter 6, a cantilever
+beam in used in the comparison of our linear models.
 
 \subsection{Plane stress}\label{ssec:3D_Model:PlaneStress}
-When the stresses in an elastic body act parallel to a single plane, it is referred to as plane stress.\\
+When the stresses in an elastic body act parallel to a single plane, it is
+referred to as plane stress.\\
 
-Consider the right-hand orthonormal set $\left\{e_1, e_2, e_3\right\}$.
-Without loss of generality, assume the stresses act parallel to the $e_1$-$e_2$ plane i.e.
-$\sigma_{3i} = 0$ for all $i$.
-From Hooke's Law \eqref{DM_H_E} the following equations are obtained:
+Consider the right-hand orthonormal set $\left\{e_1, e_2, e_3\right\}$. Without
+loss of generality, assume the stresses act parallel to the $e_1$-$e_2$ plane
+i.e. $\sigma_{3i} = 0$ for all $i$. From Hooke's Law \eqref{DM_H_E} the
+following equations are obtained:
 
@@
 	\begin{aligned}
-		\varepsilon_{11} & =  \gamma  ( \sigma_{11} - \nu \sigma_{22}) \qquad \qquad \varepsilon_{33} & = & - \gamma \nu (\sigma_{11} + \sigma_{22})\\
+		\varepsilon_{11} & =  \gamma  ( \sigma_{11} - \nu \sigma_{22}) \qquad \qquad \varepsilon_{33} & = & - \gamma \nu (\sigma_{11} + \sigma_{22})          \\
 		\varepsilon_{22} & =   \gamma (\sigma_{22} - \nu\sigma_{11}) \qquad \qquad \varepsilon_{12}   & = & \  \gamma (1+\nu) \sigma_{12} \label{strain_comp}
@@
 
-After some manipulation, we verify the following equations for the stress components given in \cite{Fung65}.
+After some manipulation, we verify the following equations for the stress
+components given in \cite{Fung65}.
 
@@
 
-Another necessary strain condition for plane stress is found by substituting $\sigma_{11}$ and $\sigma_{22}$ from \eqref{stress_comp} into $\varepsilon_{33}$ in \eqref{strain_comp} to obtain
+Another necessary strain condition for plane stress is found by substituting
+$\sigma_{11}$ and $\sigma_{22}$ from \eqref{stress_comp} into
+$\varepsilon_{33}$ in \eqref{strain_comp} to obtain
 \begin{eqnarray}
@@
 
-This is known as general plane stress. In this dissertation only a special case of general plane stress is considered in section \ref{sec:2D_Model}.
+This is known as general plane stress. In this dissertation only a special case
+of general plane stress is considered in section \ref{sec:2D_Model}.
 

### 2023-01-17 files/Overview.tex

--- 2022-11-24 files/Overview.tex
@@
 The authors also present some examples.
-two examples are verified in this chapter.
+Two examples are verified in this chapter.
 The cantilever and free-free beam.

### 2023-01-18 files/Chapter3/femconvergence.tex
Chapter 3 end 95%

@@
 
-\newtheorem{Prop_2}[Prop_1]{Proposition}
+\newtheorem{Prop_2}[Prop_1]{Proposition} \label{Prop_2}
 \begin{Prop_2}
@@
 
-\newtheorem{Lem_1}{Lemma}
+\newtheorem{Lem_1}{Lemma} \label{Lem_1}
 \begin{Lem_1}
-	$\displaystyle \lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}$
+	$\displaystyle \lambda_{m}^{h} \leq \frac{\lambda_{m}}{u_{m}^{h}}$
 \end{Lem_1}
@@
 
-	$b(u,u) = \sum_{i=1}^{m} c_{i}^{2} \lambda_{i} \leq \lambda_{m}\sum_{i=1}^{m} c_{i}^{2} =\lambda_{m} ||u||^{2}$ for all $u \in E_{m}$.\\
-	And since $B_{m} \subset E_{m}$, we have $b(Pu,Pu) \leq \lambda_{m}$ for all $u\in B_{m}$\\
+	And since $B_{m} \subset E_{m}$, $b(Pu,Pu) \leq \lambda_{m}$ for all $u\in B_{m}$\\
 
-	So now from the definition of $\mu_{m}^{h}$ and the Rayleigh quotient, we have
+	Using the Rayleigh quotient, and the definition of $\mu_{m}^{h}$, 
 	\begin{eqnarray*}
-		R(Pu) &=& \frac{b(Pu,Pu)}{(Pu,Pu)}\\
-			&=& \frac{b(Pu,Pu)}{||Pu||^{2}}\\
-			&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}
+		R(Pu) &=& \frac{b(Pu,Pu)}{(Pu,Pu)},\\
+			&=& \frac{b(Pu,Pu)}{||Pu||^{2}},\\
+			&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}.
 	\end{eqnarray*}
-	This together with Proposition 7.1 gives
+
+	Together with Proposition \ref{Prop_2} it follows that
 	\begin{eqnarray*}
-		\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}
+		\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}.
 	\end{eqnarray*}
 \end{proof}
-\begin{comment}
-\textbf{Proof:} Let $Y = \sum_{i=1}^{m} c_{i}u_{i}$.
+
+Following Lemma \ref{Lem_1}, and since $\lambda_{i}^{h} \geq \lambda_{i}$ it follows that $0 < \mu_{m}^{h} \leq 1$. It is now possible to define the error estimate as given in \cite{SF73}:
 \begin{eqnarray*}
-b(u,u) &=& b\left(\sum_{i=1}^{m} c_{i}u_{i},\sum_{j=1}^{m} c_{j}u_{j}\right)\\
-		&=& \sum_{i=1}^{m} c_{i}\sum_{j=1}^{m} c_{j} b(u_{i},u_{j})
-\end{eqnarray*}
-\textbf{RTP:} $\left\{u_{1},u_{2},...,u_{m}\right\}$ is orthonormal.\\
-Pick any $i,j \in \mathbb{N}$ such that $i,j \leq m$. Let arbitrary $v_{i},v_{j} \in V$ be arbitrary, then
-\begin{eqnarray*}
-	b(u_{i},u_{i}) &=& \lambda_{i}( u_{i},u_{i})\\
-	b(u_{j},u_{j}) &=& \lambda_{j}( u_{j},u_{j})
-\end{eqnarray*}
-Now we pick $u_{i} = u_{j}$ and $u_{j} = u_{i}$. Then
-\begin{eqnarray*}
-	b(u_{i},u_{j}) &=& \lambda_{i}( u_{i},u_{j})\\
-	b(u_{j},u_{i}) &=& \lambda_{j}( u_{j},u_{i})
-\end{eqnarray*}
-Then using the symmetry of $b(\cdot,\cdot)$ and $( \cdot, \cdot )$, and subtracting, we get
-\begin{eqnarray*}
- 0 &=& (\lambda_{i} - \lambda_{j})( u_{i}, u_{j} )
-\end{eqnarray*}
-So if $i \neq j$, $\lambda_{i} \neq \lambda_{j}$.
-Thus we must have that $u_{i}$ and $u_{j}$ are orthogonal.
-And since by the way $u_{i}$ is defined, $||u_{i}|| = 1$.
-So thus $\left\{u_{1},u_{2},...,u_{m}\right\}$ is orthonormal.\\
-
-So then $b(u,u) = \sum_{i=1}^{m} c_{i}^{2} \lambda_{i} \leq \lambda_{m}\sum_{i=1}^{m} c_{i}^{2} =\lambda_{m} ||u||^{2}$ for all $u \in E_{m}$.\\
-And since $B_{m} \subset E_{m}$, we have $b(Pu,Pu) \leq \lambda_{m}$ for all $u\in B_{m}$\\
-
-So now from the definition of $\mu_{m}^{h}$ and the Rayleigh quotient, we have
-\begin{eqnarray*}
-	R(Pu) &=& \frac{b(Pu,Pu)}{(Pu,Pu)}\\
-		&=& \frac{b(Pu,Pu)}{||Pu||^{2}}\\
-		&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}
-\end{eqnarray*}
-This together with Proposition 7.1 gives
-\begin{eqnarray*}
-	\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}
-\end{eqnarray*}\qed
-\end{comment}
-
-Now since $\lambda_{i}^{h} \geq \lambda_{i}$ and by Lemma 7.1, we must then have that $0 < \mu_{m}^{h} \leq 1$. Now define the error estimate as
-\begin{eqnarray*}
-\sigma_{m}^{h} = 1 - \mu_{m}^{h}
+	\sigma_{m}^{h} = 1 - \mu_{m}^{h}.
 \end{eqnarray*}
 
-%\newpage
-
-\textbf{Corollary 7.1:} $0 \leq \sigma_{m}^{h} < 1$ and $\lambda_{m}^{h} - \lambda_{m} \leq \lambda_{m}^{h}\sigma_{m}^{h}$\\
-
-\begin{comment}
-\textbf{Proof:}
+\newtheorem{Cor_1}{Corollary}
+\begin{Cor_1}
+	$0 \leq \sigma_{m}^{h} < 1$ and $\lambda_{m}^{h} - \lambda_{m} \leq \lambda_{m}^{h}\sigma_{m}^{h}$
+\end{Cor_1}
+\begin{proof}
+	Starting with the result of Lemma \ref{Lem_1},
 	\begin{eqnarray*}
-\lambda_{m}^{h} & \leq & \frac{\lambda_{m}}{\mu_{m}^{h}} \ \ \textrm { (by Lemma 7.1)} \\
+		\lambda_{m}^{h} & \leq & \frac{\lambda_{m}}{\mu_{m}^{h}}\\
 		\lambda_{m}^{h}\mu_{m}^{h}& \leq & \lambda_{m} \\
@@
 		\lambda_{m}^{h} -\lambda_{m}& \leq & \lambda_{m}^{h}\sigma_{m}^{h}
-\end{eqnarray*}\qed
+		\end{eqnarray*}
+\end{proof}
 
-So from this Corollary 7.1, we see that to prove that our approximate eigenvalues converge to the exact eigenvalues.
-The only thing then left to prove is  that $\sigma_{m}^{h} \rightarrow 0$ as $h \rightarrow 0$.\\
-\\
+This corollary give a error estimate for the eigenvalues.
+To prove the convergence of the eigenvalues, it is necessary to prove that the error estimate $\sigma_{m}^{h}$ converges to zero as $h \rightarrow 0$.\\
 
-\textbf{Proposition 7.1} $\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}$\\
+\newtheorem{Prop_3}[Prop_1]{Proposition} \label{Prop_3}
+\begin{Prop_3}
+	$\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}$
+\end{Prop_3}
+\begin{proof}
+	Let $u \in B_{m}$. Then
+	\begin{eqnarray*}
+		||u - Pu||^{2} &=& ( u - Pu, u - Pu ), \\
+						&=& ( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ), \\
+						&=& 2( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ) - ( u, u ),\\
+						&=& 2( u, u - Pu ) + ( Pu, Pu ) - ( u, u ).\\
+	\end{eqnarray*}
+	Rewriting gives
+	\begin{eqnarray*}
+		( u, u ) - ( Pu, Pu )  & = & 2( u, u - Pu ) - ||u - Pu||^{2}.
+	\end{eqnarray*}
 
-\textbf{Proof:}  Let $u \in B_{m}$. Then
+	Since $u \in B_{m}$, $||u||^{2} = 1$. So then
 	\begin{eqnarray*}
-||u - Pu||^{2} &=& ( u - Pu, u - Pu ) \\
-				&=& ( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ) \\
-				&=& 2( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ) - ( u, u )\\
-				&=& 2( u, u - Pu ) + ( Pu, Pu ) - ( u, u )\\
-( u, u ) - ( Pu, Pu )  & = & 2( u, u - Pu ) - ||u - Pu||^{2}	
+		1 - ||Pu||^{2}  & = & 2( u, u - Pu ) - ||u - Pu||^{2}.
 	\end{eqnarray*}
-Now since $u \in B_{m}$, $<u,u> = 1$. So we have
-\begin{eqnarray*}
-1 - ||Pu||^{2}  & = & 2( u, u - Pu ) - ||u - Pu||^{2}	
-\end{eqnarray*}
-Now the right hand side, $1 - ||Pu||^{2} \leq 1 - \mu_{m}^{h} = \sigma_{m}^{h}$ for all $u \in B_{m}$. So then we must have that
+
+	On the right hand side, $1 - ||Pu||^{2} \leq 1 - \mu_{m}^{h} = \sigma_{m}^{h}$ for all $u \in B_{m}$. So then it must be that
 	\begin{eqnarray*}
 	\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}
-\end{eqnarray*}\qed
-\end{comment}
+	\end{eqnarray*}
+\end{proof}
 
-Next we introduce some new notation to ease the writing. For any $u \in E_{m}$, let $u^{*} = \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}$ where $u = \sum_{i=1}^{m} c_{i}u_{i}$.\\
+Proposition \ref{Prop_3} is a result given in \cite{SF73} without explaining how it is derived.\\
 
-%\newpage
+Introduce some new notation for ease of writing. For any $u \in E_{m}$, let $u^{*} = \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}$ where $u = \sum_{i=1}^{m} c_{i}u_{i}$.\\
 
-\textbf{Proposition 7.3:} For any $u \in E_{m}$
+\newtheorem{Prop_4}[Prop_1]{Proposition} \label{Prop_4}
+\begin{Prop_4}
+	For any $u \in E_{m}$
 		\begin{eqnarray*}
@@
 		\end{eqnarray*}
+\end{Prop_4}
+\begin{proof}
+	For any $i = 1,2,...,m$,
+	\begin{eqnarray*}
+	\lambda_{i}( u_{i},u-Pu ) &=&  b(u_{i}, u-Pu),\\
+								&=& b(u_{i}, u-Pu) - b(u-Pu,Pu_{i}) \ \textrm{ (Rayleigh-Ritz Projection)},\\
+								&=&  b(u_{i}, u-Pu) - b(Pu_{i},u-Pu),\\
+								&=&  b(u_{i}-Pu_{i}, u-Pu).
+	\end{eqnarray*}
+	Multiplying by $c_{i}\lambda_{i}^{-1}$ and summation over i gives:
+	\begin{eqnarray*}
+	\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}\lambda_{i}( u_{i},u-Pu ) &=& \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}b(u_{i}-Pu_{i}, u-Pu),\\
+								&=& b(\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}-\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}Pu_{i}, u-Pu),\\
+										&=& b(u^{*}-Pu^{*}, u-Pu).
+	\end{eqnarray*}
+	Therefore $( u,u-Pu ) = b(u^{*}-Pu^{*}, u-Pu)$.
+\end{proof}
 
-\begin{comment}
-\textbf{Proof:} For any $i = 1,2,...,m$, we have that
+\newtheorem{Lem_2}[Lem_1]{Lemma} \label{Lem_2}
+\begin{Lem_2}
+	$\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$
+\end{Lem_2}
+\begin{proof}
+	From Proposition \ref{Prop_3},
 	\begin{eqnarray*}
-\lambda_{i}( u_{i},u-Pu ) &=&  b(u_{i}, u-Pu)\\
-									&=& b(u_{i}, u-Pu) - b(u-Pu,Pu_{i}) \ \textrm{ (by definition of Rayleigh-Ritz Projection)}\\
-									&=&  b(u_{i}, u-Pu) - b(Pu_{i},u-Pu)\\
-									&=&  b(u_{i}-Pu_{i}, u-Pu)
+		\sigma_{m}^{h} & = & \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}, \\
+					& \leq & \max\left\{ 2( u,u-Pu ) \ | \ u \in B_{m} \right\}. \\
 	\end{eqnarray*}
-So multiplying by $c_{i}\lambda_{i}^{-1}$ and summation over i gives:
+
+	From Proposition \ref{Prop_4}, 
 	\begin{eqnarray*}
-\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}\lambda_{i}( u_{i},u-Pu ) &=& \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}b(u_{i}-Pu_{i}, u-Pu)\\
-									&=& b(\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}-\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}Pu_{i}, u-Pu)\\
-									&=& b(u^{*}-Pu^{*}, u-Pu)
+		\sigma_{m}^{h} = \max\left\{ 2 b(u^{*}-Pu^{*}, u-Pu) \ | \ u \in B_{m} \right\}.
 	\end{eqnarray*}
-So $( u,u-Pu ) = b(u^{*}-Pu^{*}, u-Pu)$.\qed\\
-\end{comment}
 
-\textbf{Lemma 7.2:} $\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$\\
+	Using the Schwartz inequality,
+	\begin{eqnarray*}
+		b(u^{*} - Pu^{*}, u -Pu) & \leq & ||u^{*} - Pu^{*}||||u -Pu||.
+	\end{eqnarray*}
 
-\begin{comment}
-\textbf{Proof:} From Proposition 7.1, we have
+	Finally,
 	\begin{eqnarray*}
-\sigma_{m}^{h} &=& \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \} \\
-				&\leq & \max\left\{ 2( u,u-Pu ) \ | \ u \in B_{m} \right \}
-\end{eqnarray*} since $||u-Pu||^{2} \geq 0$.\\
-\end{comment}
+		\sigma_{m}^{h} & \leq & \max\left\{ 2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}.
+	\end{eqnarray*}
+\end{proof}
 
-Using Proposition 7.3
-\begin{eqnarray*}
-\sigma_{m}^{h} &\leq & \max\left\{ 2b(u^{*} - Pu^{*}, u -Pu) \ | \ u \in B_{m} \right \}			
-\end{eqnarray*}
-Now
-\begin{eqnarray*}
-b(u^{*} - Pu^{*}, u -Pu) & \leq & ||u^{*} - Pu^{*}||||u -Pu|| \ \textrm{ (Schwartz inequality)} \\
-\end{eqnarray*}
-Thus  $\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$. \qed
-
-%\newpage
-
-\textbf{Proposition 7.3:} For any $\epsilon > 0$, there exists a $\delta >0$ such that for $h<\delta$,
+\newtheorem{Prop_5}[Prop_1]{Proposition} \label{Prop_5}
+\begin{Prop_5}
+	For any $\epsilon > 0$, there exists a $\delta >0$ such that for $h<\delta$,
 	\begin{eqnarray*}
@@
 	\end{eqnarray*}
+\end{Prop_5}
+\begin{proof}
+	Consider a set of basis functions $\Phi \subset S^h$ such that $\phi^(k) = 0$ for each $\phi \in \Phi$.\\
 
-\begin{comment}
-\textbf{Proof:}
-Suppose we have a set of basis functions $\Phi \subset S^{h}$ such that each element in $\Phi$ has order k, i.e.
-for each $v \in \Phi$, $v^{(k)} = 0$.
-Now from the definition of the Rayleigh-Ritz Projection, we have that $Pu$ is the closest element in $S^{h}$ to $u$.
-In particular, $||u-Pu||\leq ||u-\Pi u||$, where $\Pi u$ is the interpolant of $u$ into $S^{h}$.\\
+	From the Rayleigh-Ritz Projection, $Pu$ is the closest element in $S^h$ to $u$. In particular, $||u-Pu||\leq ||u-\Pi u||$, where $\Pi u$ is the interpolation of $u$ into $S^h$.\\
 
-Now from, we use the Approximation Theorem, so that we have
+	From the Approximation Theorem, is follows that
 	\begin{eqnarray*}
@@
 	\end{eqnarray*}
-So for any $\epsilon > 0$, we can find a $\delta$ such that if $h<\delta$ then
+
+	So for any $\epsilon > 0$, a $\delta$ can be found such that if $h<\delta$ then
 	\begin{eqnarray*}
@@
 	A similar argument for $||u^{*} - Pu^{*}||$ proves the theorem.
-\qed
-\\
-\end{comment}
+\end{proof}
 
-\textbf{Lemma 7.4:} For any $\epsilon >0$ there exists a $\delta > 0$ such that
+\newtheorem{Lem_3}[Lem_1]{Lemma} \label{Lem_3}
+\begin{Lem_3}
+	For any $\epsilon >0$ there exists a $\delta > 0$ such that
 	\begin{eqnarray*}
@@
 	\end{eqnarray*}
-
-\begin{comment}
-\textbf{Proof:} For any $\epsilon > 0$ there exists a $\delta > 0$ such that if $h<\delta$, then
+\end{Lem_3}
+\begin{proof}
+	For any $\epsilon > 0$ there exists a $\delta > 0$ such that if $h<\delta$, then
 	\begin{eqnarray*}
@@
 	\end{eqnarray*}
-This, together with Lemma 7.2 and Proposition 7.4 gives the result.\qed\\
-\end{comment}
+	This result, together with Lemma \ref{Lem_2} and Proposition \ref{Prop_5} gives the result.
+\end{proof}
 
-\textbf{Lemma 7.5:} There exists a $\delta > 0$ such that for $h < \delta$
+\newtheorem{Lem_4}[Lem_1]{Lemma} \label{Lem_4}
+\begin{Lem_4}
+	There exists a $\delta > 0$ such that for $h < \delta$
 	\begin{eqnarray*}
@@
 	\end{eqnarray*}
+\end{Lem_4}
+\begin{proof}
+	Using Lemma \ref{Lem_3}, choose $\delta$ such that $\sigma_{m}^{h} < \frac{1}{2}$. Then by Lemma \ref{Lem_1} gives that $\lambda_{m}^{h} < 2\lambda_{m}$.\\
 
-\begin{comment}
-\textbf{Proof:}
-Using Lemma 7.4, choose $\delta$ such that $\sigma_{m}^{h} < \frac{1}{2}$. Then by Lemma 7.1 gives that $\lambda_{m}^{h} < 2\lambda_{m}$. So we have that
-$\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}$.
-\qed
-\end{comment}
+	So $\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}$.
+\end{proof}
+
+The convergence of the eigenvalues are now proved.\\
 
 \subsection{Convergence of the eigenfunctions}
-So from Lemma 7.4, it is that if $h \rightarrow 0$, we will get convergence in the eigenvalues. The next step is now to use this, to show convergence in the eigenvectors.\\
+The next step is to show the convergence of the eigenfunctions. First consider the following result.
 
-\textbf{Lemma 7.6:}
+\newtheorem{Lem_5}[Lem_1]{Lemma} \label{Lem_5}
+\begin{Lem_5}
 	\begin{eqnarray*}
@@
 		\end{eqnarray*}
-
-\begin{comment}
-\textbf{Proof:}
+\end{Lem_5}
+\begin{proof}
 	\begin{eqnarray*}
@@
 		\end{eqnarray*}
-\qed
-\end{comment}
+\end{proof}
 
-We have already shown that $\lambda_{m}^{h} \rightarrow \lambda_{m}$. So it remains only to show that $( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$
+It has been shown that the eigenvalues converge to the exact eigenvalues as $h \rightarrow 0$.
+So from this result, it only remains to show that $( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$.\\
 
-Now we have the possibility that an eigenvalue, say $\lambda_{m}$ has multiplicity $r>1$. This implies that there are at least two eigenfunctions that correspond to this eigenvalue.\\
+At this point, another assumption must be made.
+Assume that there are not eigenvalues with multiplicity more than 1.
+In other words, all the eigenvalues correspond only to one eigenfunction.
+In \cite{SF73}, the authors mention that for repeated eigenvalues, then the eigenfunctions can be chosen so that the main convergence results hold.
+This case is ommited in this dissertation.\\
 
-The Euler-Bernoulli beam however, only has a repeated eigenvalue if we consider the free-free boundary conditions.
-Then the beam would have a zero eigenvalue with multiplicity more than 1.
-Our model, however, does not have repeated eigenvalues.
-So we may assume that all the eigenvalues has multiplicity $r=1$.\\
-
-\textbf{Lemma 7.7:} For all m and j
+\newtheorem{Lem_6}[Lem_1]{Lemma} \label{Lem_6}
+\begin{Lem_6}
+	For all m and j
 	\begin{eqnarray*}
@@
 	\end{eqnarray*}
-
-\begin{comment}
-\textbf{Proof:}
+\end{Lem_6}
+\begin{proof}
 	Since the term $\lambda_{m}( Pu,u^{h}_{j})$ appears on both sides of the equation, it is only required to show that
 	\begin{eqnarray*}
-\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& \lambda_{m} ( u, u_{j}^{h} )
+		\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& \lambda_{m} ( u, u_{j}^{h} ).	
 	\end{eqnarray*}
-Now
+	Since both $u$ and $u_{j}^{h}$ are eigenfunctions, then
 	\begin{eqnarray*}
@@
 		\lambda_{m} ( u, u_{j}^{h} ) &=& b(u,u_{j}^{h})
-\end{eqnarray*} Since $u$ and $u_{j}^{h}$ are both eigenfunctions.\\
+	\end{eqnarray*}
 
 	Then equality follows from the definitions of the projection P.
-\qed
-\end{comment}
+\end{proof}
 
-The set $\left\{u_{1}^{h},u_{2}^{h},...,u_{N}^{h}\right\}$ then forms an orthonormal basis for $S^{h}$. So we can then write a projection $Pu_{m}$ as:
+The set $\left\{u_{1}^{h},u_{2}^{h},...,u_{N}^{h}\right\}$ forms an orthonormal basis for $S^{h}$. The projection $Pu_{m}$ can be written as:
 \begin{eqnarray}
-Pu_{m} &=& \sum_{j=1}^{N} ( P u_{m} ,u_{j}^{h}) u_{j}^{h} \label{CV1}
+	Pu_{m} &=& \sum_{j=1}^{N} ( P u_{m} ,u_{j}^{h}) u_{j}^{h}. \label{CV1}
 \end{eqnarray}
 
-From Lemma 7.8, we see that $( P_{m},u_{j}^{h} )$ is small if $\lambda_{m}^{h}$ is not close to $\lambda_{j}$.
-So then (\ref{CV1}) tells us then that $Pu_{m}$ is close to $u_{m}^{h}$.
-This will allow us to estimate $Pu_{m} - u_{m}^{h}$.\\
+From Lemma \ref{Lem_6}, it follows that $( P_{m},u_{j}^{h} )$ is small if $\lambda_{m}^{h}$ is not close to $\lambda_{j}$.
+Therefore (\ref{CV1}) tells us that $Pu_{m}$ is close to $u_{m}^{h}$.
+The estimate for $Pu_{m} - u_{m}^{h}$ will follow from this result.\\
 
-Since we have convergence in our eigenvalues, it follows that $\exists \rho > 0$ and $\exists \delta > 0$ such that if $h<\delta$ we have that
+Following the convergence of the eigenvalues, $\exists \rho > 0$ and $\exists \delta > 0$ such that if $h<\delta$,
 \begin{eqnarray}
-|\lambda_{m} - \lambda_{j}^{h}| &>& \rho \ \ \textrm{ for all } \ j = 1,2,...,N
+|\lambda_{m} - \lambda_{j}^{h}| &>& \rho \ \ \textrm{ for all } \ j = 1,2,...,N.
 \end{eqnarray}
@@
 \begin{eqnarray}
-\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|} &\leq & \rho \ \ \textrm{ for all } \ j = 1,2,...,N
+\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|} &\leq & \rho \ \ \textrm{ for all } \ j = 1,2,...,N.
 \end{eqnarray}
 
-\textbf{Lemma 7.8:}
+\newtheorem{Lem_7}[Lem_1]{Lemma} \label{Lem_7}
+\begin{Lem_7}
 	\begin{eqnarray*}
@@
 	\end{eqnarray*}
+\end{Lem_7}
+\begin{proof}
 
-\begin{comment}
-\textbf{Proof:}
+Using Lemma \ref{Lem_6}:
+\begin{eqnarray*}
+||Pu - \beta u_{m}^{h}||^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2},\\
+				&\leq & \rho^{2} \sum_{j\neq m} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
+				&\leq & \rho^{2} \sum_{j=1}^{N} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
+				& = & \rho^{2} ||u - Pu||^{2}.\\
+\end{eqnarray*}
+\end{proof}
 
-Now using Lemma 7.7:
-\begin{eqnarray*}
-||Pu - \beta u_{m}^{h}||^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}\\
-				&\leq & \rho^{2} \sum_{j\neq m} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2} \\
-				&\leq & \rho^{2} \sum_{j=1}^{N} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2} \\
-				& = & \rho^{2} ||u - Pu||^{2}\\
-\end{eqnarray*}
-\qed
-\end{comment}
-
-\textbf{Lemma 7.9:}
+\newtheorem{Lem_8}[Lem_1]{Lemma} \label{Lem_8}
+\begin{Lem_8}
 	\begin{eqnarray*}
@@
 	\end{eqnarray*}
-
-\begin{comment}
-\textbf{Proof:}
+\end{Lem_8}
+\begin{proof}
 	\begin{eqnarray*}
 	||u_{m} - \beta u_{m}^{h}|| & \leq & ||u_{m}-Pu_{m}|| + ||Pu_{m} - \beta u_{m}^{h}|| \\
-			& \leq & \left(1+\rho\right)||u_{m}-Pu_{m}|| \ \ \textrm{ (by Lemma 7.8)}
+				& \leq & \left(1+\rho\right)||u_{m}-Pu_{m}|| \ \ \textrm{ (by Lemma \ref{Lem_7})}
 	\end{eqnarray*}
-\qed
-\end{comment}
+\end{proof}
 
-So again using the Approximation Theorem, we have that $||u_{m} - \beta u_{m}^{h}||\leq Ch^{k}||u^{k}||$.\\
+So again using the Approximation Theorem, it follows that $||u_{m} - \beta u_{m}^{h}||\leq Ch^{k}||u^{k}||$.\\
 
-\textbf{Proposition 7.4:}
+\newtheorem{Lem_9}[Lem_1]{Lemma} \label{Lem_9}
+\begin{Lem_9}
 	\begin{eqnarray*}
@@
 	\end{eqnarray*}
+\end{Lem_9}
+\begin{proof}
+	\begin{eqnarray*}
+	||u_{m} - u_{m}^{h}|| &=& ||u_{m} - \beta u_{m}^{h} + \beta u_{m}^{h} - u_{m}^{h}||, \\
+						& \leq & ||u_{m} - \beta u_{m}^{h}|| + ||\beta u_{m}^{h} - u_{m}^{h}||, \\
+						& = & 2||u_{m} - \beta u_{m}^{h}||.	
+	\end{eqnarray*}
+\end{proof}
 
-\begin{comment}
-\textbf{Proof:}
-\begin{eqnarray*}
-||u_{m} - u_{m}^{h}|| &=& ||u_{m} - \beta u_{m}^{h} + \beta u_{m}^{h} - u_{m}^{h}|| \\
-					& \leq & ||u_{m} - \beta u_{m}^{h}|| + ||\beta u_{m}^{h} - u_{m}^{h}|| \\
-					& = & 2||u_{m} - \beta u_{m}^{h}||	
-\end{eqnarray*}
-\qed
-\end{comment}
+Therefore t $||u_{m} -  u_{m}^{h}|| \leq Ch^{k}||u^{k}||$. So for any $\epsilon >0$ , a $\delta >0$ can be found such that if $h < \delta$, $||u_{m} -  u_{m}^{h}|| < \epsilon$.
 
-Therefore we have that $||u_{m} -  u_{m}^{h}|| \leq Ch^{k}||u^{k}||$. So for any $\epsilon >0$ , we can find a $\delta >0$ so that if $h < \delta$, we have that $||u_{m} -  u_{m}^{h}|| < \epsilon$.
-
-Finally, for elastic beam models like the Euler-Bernoulli beam model, the norm $||.||$ is the energy norm defined as
-\begin{eqnarray*}
-||u|| &=& \left(\int u^{2}\right)^{\frac{1}{2}}
-\end{eqnarray*}
-
-So clearly then we have that $u_{m}^{h} \rightarrow u_{m}$ as $h \rightarrow 0$.
-
-\section{Example}
-What moet hier kom?\\
-
-dalk timoshenko beam sal beter wees met plaat of 2d model.\\
-
-Consider a variational problem for a cantilever two-dimensional beam, with a reference configuration $\Omega$.
-In section \ref{sssec:2D_Model:Problem2D1}, the derivation of this variational problem is referred to as Problem 2D-1V.
-
-\subsubsection{Problem 2D-1V}\label{sssec:2D_Model:Problem2D1V}
-Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
-\begin{align}
-	\int_{\Omega} (\partial_t^2 u)\cdot \phi \ dA = -b(u,\phi) - \int_{\Omega} Q\cdot\phi \ dA \label{eq:2D_Model:Problem2D1VEq}
-\end{align}
-for all $\phi \in T(\Omega)$.\\
-
-With the test function space defined as
-\subsubsection{Test functions}
-\begin{eqnarray*}
-	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
-\end{eqnarray*}
+******************************\\
+WAT IS N en WAT IS $\beta$?\\
+********************************\\
 

### 2023-01-24 files/Chapter3/femconvergence.tex
chapter 3 last section finished

@@
 \section{Convergence of eigenvalues in Finite Element Analysis}
-In this section, the work in the textbook \cite[p.228-236]{SF73} is discussed.\\
+In this section, the work in the textbook \cite[p.228-236]{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for clarity.\\
 
@@
 Let $V$ be a linear subspace of $H$, with inner product defined by the bilinear form $b(\cdot,\cdot)$.
-It is assumed that this bilinear form $b$ is symmetric.
+It is assumed that this bilinear form $b$ is symmetric.\\
+
+The following eigenvalue is given in \cite{SF73}. It is important to note that the problem is limited to one-dimensional problems.
 
@@
 
-\subsection{Preparatory theory and notation}
-Some theory is required that is presented in \cite{SF73}.\\
+\subsection{Preliminary theory and notation}
+Some theory is required before the main results can be proven. The theory is from \cite{SF73}.\\
 
@@
 \end{equation*}
+
+\subsubsection{The approximation theorem}
 
@@
 
-From the textbook \cite{ORXX}, the following approximation for finite elements is given verbatim:
+From the textbook \cite{ORXX}, the following approximation theorem for finite elements is given verbatim:
 \newtheorem*{Interpolation}{Theorem}
@@
 
-For the requirements of this dissertation, this is too general and can be simplified with assumptions.
+For the requirements of this dissertation, this can be simplified with assumptions.
 The first assumption is a reiteration that the eigenvalue problem is one-dimensional.
@@
 \end{Interpolation_2}
+
+This will be referred to as the approximation theorem in this section.\\
+
+\subsubsection*{Properties of eigenvalues}
 
@@
 \subsection{Convergence of the eigenfunctions}
-The next step is to show the convergence of the eigenfunctions. First consider the following result.
+The next step is to show the convergence of the eigenfunctions. The problem can be formulated using the following result.
 
@@
 
+To simplify the notation, let $\beta = (Pu_m,Pu_m^h)$.
+
 \newtheorem{Lem_7}[Lem_1]{Lemma} \label{Lem_7}
@@
 	\begin{eqnarray*}
-		||Pu - QPu||^{2} &\leq & {\rho}^{2} ||u_{m} - Pu_{m}||^{2}
+		||Pu - \beta Pu^h_m||^{2} &\leq & {\rho}^{2} ||u_{m} - Pu_{m}||^{2}
 	\end{eqnarray*}
 \end{Lem_7}
+\begin{comment}
 \begin{proof}
@@
 				&\leq & \rho^{2} \sum_{j=1}^{N} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
-				& = & \rho^{2} ||u - Pu||^{2}.\\
+				& = & \rho^{2} ||u_m - Pu_m||^{2}.\\
 \end{eqnarray*}
 \end{proof}
+\end{comment}
 
@@
 \end{Lem_8}
+\begin{comment}
 \begin{proof}
@@
 \end{proof}
+\end{comment}
+
+The proofs for lemma's \ref{Lem_7} and \ref{Lem_8} are given in \cite{SF73}.\\
 
@@
 Therefore t $||u_{m} -  u_{m}^{h}|| \leq Ch^{k}||u^{k}||$. So for any $\epsilon >0$ , a $\delta >0$ can be found such that if $h < \delta$, $||u_{m} -  u_{m}^{h}|| < \epsilon$.
-
-******************************\\
-WAT IS N en WAT IS $\beta$?\\
-********************************\\
-
-\subsection{Weak variational form}
-For all $f,g \in T(\Omega)$ and $h \in C(\Omega)$, define the bilinear forms
-\begin{eqnarray*}
-	c(f,g) & = & \iint_\Omega f \cdot g \ dA, \\
-\end{eqnarray*}
-and integral
-\begin{eqnarray*}
-	(h,g) & = & \iint_\Omega h \cdot g \ dA. \\
-\end{eqnarray*}
-Recall from section  that the bilinear form $b$ is defined as
-\begin{eqnarray*}
-	b(u,\phi) & = & \frac{1}{\gamma(1-\nu^2)}\iint_{\Omega} (\partial_1 u_1 \partial_1 \phi_1 + \partial_2 u_2 \partial _2 \phi_2 + \nu\partial_1 u_1 \partial_2\phi_2 + \nu \partial_2 u_2 \partial_1 \phi_1 ) \ dA \\
-	& + & \frac{1}{2\gamma(1+\nu)}\iint_{\Omega} (\partial_1 u_2 \partial_1 \phi_2 + \partial_1 u_2 \partial_2 \phi_1 + \partial_2 u_1 \partial_1\phi_2 + \partial_2 u_1 \partial_2\phi_1) \ dA.
-\end{eqnarray*}
-
-Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)$.
-Denote $X = L^2(0,1)\times L^2(0,1)$.
-The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.
-
-\subsubsection{Problem 2D-1W}
-Find a function $u$ such that for all $t>0$, $u(t) \in V$ and $u''(t) \in W$, satisfying the following equation
-\begin{eqnarray}
-	c(u''(t),v) + b(u(t),v) & = & (Q(t),v)_X \ \ \ \textrm{ for each } v \in V.
-\end{eqnarray}
-
 \end{document}

### 2023-01-30 files/Chapter7/Beam.tex
Redoing code in python

@@
 The goal of \cite{LVV09} to show that the one-dimensional Timoshenko beam theory, is a feasible model to use in practical applications of beams.
-In the real world, a beam is a three-dimensional model.
-Therefore it is important to validate the use of the Timoshenko beam theory in practical applications.\\
+In the real world, a beam is a complex three-dimensional model.
+Therefore it is important to validate the accuracy of a simlified theory like the Timoshenko beam theory for practical applications.\\
 
@@
 \section{Validity of the two-dimensional elastic model}
-In this section, the validity of a two-dimensional cantilever beam is investigated.
-A three-dimensional cantilever beam is the model we'll use the measure.
-Recall that the two-dimensional model is an intermediate step between a Timoshenko beam and a three-dimensional beam.\\
+In this section, the validity of a two-dimensional cantilever beam is investigated. This is a natural extension of the work in \cite{LVV09}. The authors mentioned this.\\
 
-In Chapter 1, models for a two-dimensional cantilever elastic body, as well as a three-dimensional cantilever elastic body is given.
-In Chapter 5, the Finite Element Method is applied to these models to obtain a formula to numerically calculate the eigenvalues and eigenfunctions of each of the models.\\
+The model that will be considered is the two-dimensional elastic body defined in Chapter 1. The investigation will focus on the results relating to beam type problems.
 
-This section follows the same strategy as the previous section by comparing the eigenvalues and eigenfunctions of the models to determine the validity of the two-dimensional model.
-This investigation remains focussed on beam type problems.
+and eigenfunctions of the models to determine the validity of the two-dimensional model. This investigation remains focussed on beam type problems.
 

### 2023-01-30 code/Timoshenko_beam.py

@@ -1,0 +1,103 @@
+import numpy
+import sympy
+
+A = sympy.Symbol('A')
+B = sympy.Symbol('B')
+C = sympy.Symbol('C')
+D = sympy.Symbol('D')
+x = sympy.Symbol('x')
+m = sympy.Symbol('m')
+o = sympy.Symbol('o')
+a = sympy.Symbol('a')
+l = sympy.Symbol('l')
+k = sympy.Symbol('k')
+t = sympy.Symbol('t')
+
+class TimoshenkoBeam(object):
+    def __init__(self,alpha) -> None:
+        self.nu = 0.3
+        self.gamma = 1/(2*(1+self.nu))*5/5
+        self.alpha = alpha
+        self.u_0 = None
+        self.u_1 = None
+        self.p_0 = None
+        self.p_1 = None
+
+    @property
+    def delta(self):
+        return 4*self.gamma/(1+self.gamma)**2*self.alpha/l + (1-self.gamma)**2/(1+self.gamma)**2
+
+    @property
+    def omega_squared(self):
+        return 1/2*l*(1+self.gamma)*(self.delta**(1/2)+1)
+
+    @property
+    def mu_squared(self):
+        return 1/2*l*(1+self.gamma)*(self.delta**(1/2)-1)
+
+    @property
+    def theta_squared(self):
+        return 1/2*l*(1+self.gamma)*(1-self.delta**(1/2))
+
+    def u(self, size_of_lam):
+        if size_of_lam == 'less':
+            return A*sympy.sinh(m*x) + B*sympy.cosh(m*x) + C*sympy.sinh(o*x) + D*sympy.cosh(o*x)
+        elif size_of_lam == 'equal':
+            return B + C*sympy.sin(o*x) + D*sympy.cos(o*x)
+        elif size_of_lam == 'greater':
+            return A*sympy.sin(t*x) + B*sympy.cos(t*x) + C*sympy.sin(o*x) + D*sympy.cos(o*x)
+
+    def p(self, size_of_lam):
+        if size_of_lam == 'less':
+            return A*(l+m**2)/(m*sympy.cosh(m*x)) + B*(l+m**2)/(m*sympy.sinh(m*x)) + C*(-l+o**2)/(o*sympy.cosh(o*x)) + D*(l-o**2)/(o*sympy.sinh(o*x))
+        elif size_of_lam == 'equal':
[…]

### 2023-02-01 files/Chapter7/Beam.tex
2d beam validity started

@@
 In the real world, a beam is a complex three-dimensional model.
-Therefore it is important to validate the accuracy of a simlified theory like the Timoshenko beam theory for practical applications.\\
+So a three-dimensional model would be a good approximation and better than a one-dimensional model.
+It is therefore important to validate the accuracy of a simlified theory like the Timoshenko beam theory.\\
 
-In mathematical terms, the validity of the Timoshenko beam theory is described as how well the solutions of the Timoshenko beam theory compare to more realistic, higher-dimensional models.
-It is obvious that a three-dimensional beam model is a better approximation of a real world beam.
-But the Timoshenko beam theory is less complex and more widely used.\\
+In the article, the authors validate the Timoshenko beam theory by comparing it to a more realistic, two-dimensional model.
+The authors use a cantilever beam as a model.
+Although a direct comparison to a three-dimensional beam would be preferred, the authors state that this would introduce complexities.
+The two-dimensional model is an intermediate step.\\
 
-The authors of \cite{LVV09} use a two-dimensional cantilever beam, to validate the use of a cantilever Timoshenko beam for practical importance.
-Although a direct comparison to a three-dimensional beam would be preferred, the authors state that this would introduce complexities.
-A two-dimensional model is therefore used as an intermediate step.\\
-
-Where \cite{LVV09} differs from most other research, is that the boundary conditions are also taken into consideration.\\
+Where \cite{LVV09} differs from most other research into the validity of the Timoshenko beam theory, is that the boundary conditions are also taken into consideration.\\
 
@@
 \subsection{The models}
+In the article, the authors use a cantilever configuration for the two models. Therefore the models presented here are also cantilever models.\\
+
 Recall the cantilever Timoshenko beam model from section \ref{ssec:1D_Model:ModelProblems}, referred to as Problem T-2 and the cantilever two-dimensional beam model from section \ref{ssec:2D_Model:ModelProblem}, referred to as Problem 2D-1.
@@
 
-In Chapter 1, the following parameters were established.
+In Chapter 1, the following parameters were defined.
 The parameter $h$ is the height of the two-dimensional beam and for the Timoshenko dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ was found.\\
@@
 \section{Validity of the two-dimensional elastic model}
-In this section, the validity of a two-dimensional cantilever beam is investigated. This is a natural extension of the work in \cite{LVV09}. The authors mentioned this.\\
+In this section, the validity of a two-dimensional cantilever beam is investigated. This is a natural extension of the work in \cite{LVV09}. This was mentioned by the authors.\\
 
-The model that will be considered is the two-dimensional elastic body defined in Chapter 1. The investigation will focus on the results relating to beam type problems.
+As mentioned before, the two-dimensional model is used as a intermediate step between the Timoshenko and three-dimensional beam.
+The same method as in \cite{LVV09} will be used to investigate the validity of the two-dimensional model.\\
 
-and eigenfunctions of the models to determine the validity of the two-dimensional model. This investigation remains focussed on beam type problems.
+The models for the two-dimensional and three-dimensional beams are defined in section \ref{ssec:2D_Model:ModelProblem} and \ref{ssec:3D_Model:ModelProblems} respectively.
+These models are elastic bodies and not specifically beam models.
+Therefore it is expected to find eigenvalue and eigenfunction pairs that does not relate to beam type problems.
+This was already seen with the two-dimensional model in the previous section.
+These not beam type eigenvalues are calculated in this section, however the focus still remains on beam type problems.\\
 
@@
 The three-dimensional model also have depth $b$.
-Intuitively, the two-dimensional beam should compare well the the three-dimensional beam if $b$ is small.
+Intuitively, from the figure, the two-dimensional beam should compare better to the three-dimensional beam for smaller $b$.
 

### 2023-02-15 files/Chapter7/Beam.tex
Added new figure example
Reviewing results for 2d and 3d beam

@@
 \end{figure}
+
+\begin{tikzpicture}
+\begin{axis}[width=0.9\textwidth,
+			 xlabel=Iteration Number,
+			 ylabel=Error,
+			 ymode=log,
+			 legend pos=south east]
+\addplot[color=blue, mark=o] coordinates {
+    (1,0.1)
+    (2,0.05)
+    (3,0.01)
+    (4,0.005)
+};
+\addlegendentry{$h=1/5$}
+
+\addplot[color=red, mark=o] coordinates {
+    (1,0.2)
+    (2,0.1)
+    (3,0.05)
+    (4,0.02)
+};
+\addlegendentry{$h=1/10$}
+
+\addplot[color=green, mark=o] coordinates {
+    (1,0.2)
+    (2,0.1)
+    (3,0.05)
+    (4,0.02)
+};
+\addlegendentry{$h=1/20$}
+
+\addplot[color=black, mark=o] coordinates {
+    (1,0.3)
+    (2,0.3)
+    (3,0.03)
+    (4,0.03)
+};
+\addlegendentry{$h=1/30$}
+
+\end{axis}
+\end{tikzpicture}
 
@@
 \section{Validity of the two-dimensional elastic model}
-In this section, the validity of a two-dimensional cantilever beam is investigated. This is a natural extension of the work in \cite{LVV09}. This was mentioned by the authors.\\
+In this section, the validity of a two-dimensional cantilever beam is investigated. This is an extension of the work in \cite{LVV09}, as mentioned in the article.\\
 
-As mentioned before, the two-dimensional model is used as a intermediate step between the Timoshenko and three-dimensional beam.
+As explained before, the two-dimensional model is used as a intermediate step between the Timoshenko and three-dimensional beam.
 The same method as in \cite{LVV09} will be used to investigate the validity of the two-dimensional model.\\
@@
 \subsection{Accuracy of the numerical eigenvalues}
-In the previous section, the accuracy of the two-dimensional beam's eigenvalues were investigated.
-This can be done similarly for the three-dimensional beam.
-The eigenvalues are also calculated using the Finite Element Method.
+Similar to how the eigenvalues and eigenfunctions of the two-dimensional model calculated in the previous section, the eigenvalues and eigenfunctions can be calculated for the three-dimensional model.
+The numerical formula to calculate the eigenvalues and eigenfunctions are derived in section \ref{sec:FEM:3D}.\\
+
 Using piecewise tri-cubic basis functions, the following results were obtained.\\
 
-For different values of $h$ and $b$, the first 30 eigenvalues are calculated with increasing grid sizes. The maximum relative error between the sets of eigenvalues are then calculated and graphed.\\
+\begin{tikzpicture}
+	\begin{axis}[width=0.9\textwidth,
+				 xlabel=Iteration Number,
+				 ylabel=Error,
+				 ymode=log,
+				 legend pos=south east]
+	\addplot[color=blue, mark=o] coordinates {
+		(1,0.1)
+		(2,0.05)
+		(3,0.01)
+		(4,0.005)
+	};
+	\addlegendentry{$h=1/5$}
 
-****************INSERT GRAPHIC**************\\
+	\addplot[color=red, mark=o] coordinates {
+		(1,0.2)
+		(2,0.1)
+		(3,0.05)
+		(4,0.02)
+	};
+	\addlegendentry{$h=1/10$}
+
+	\addplot[color=green, mark=o] coordinates {
+		(1,0.2)
+		(2,0.1)
+		(3,0.05)
+		(4,0.02)
+	};
+	\addlegendentry{$h=1/20$}
+
+	\addplot[color=black, mark=o] coordinates {
+		(1,0.3)
+		(2,0.3)
+		(3,0.03)
+		(4,0.03)
+	};
+	\addlegendentry{$h=1/30$}
+
+	\end{axis}
+	\end{tikzpicture}
 
 \subsection{Comparing the mode shapes}
-In this section, the mode shapes of the two dimensional and three-dimensional beam are compared.
-Recall that beam-type eigenvalues are defined by \cite{LVV09} as any eigenvalue for which it's corresponding mode shape is similar to the mode shapes obtained in the Timoshenko beam theory.
+Identical to the method used in \cite{LVV09} and the previous section, the eigenvalues of the two models can be matched by comparing the mode shapes.
+As mentioned earlier, it is expected that there will be mode shapes not related to beam type problems, and also mode shapes that the three-dimensional model do not share with the two-dimensional model.\\
+
+In this section, examples of the different mode shapes are shown.
 
@@
 				\includegraphics[width=1\linewidth]{3DNonBeam10.png}
-				\subcaption{Non-2D Type - $\lambda_{10} = xx$}
+				\subcaption{Non-2D Type - $\lambda_{10}$}
 				\label{fig:minipage2}
@@
 				\includegraphics[width=1\linewidth]{3DNonBeam11.png}
-				\subcaption{Non-2D Type - $\lambda_{11} = xx$}
+				\subcaption{Non-2D Type - $\lambda_{11}$}
 				\label{fig:minipage11}
@@
 The eigenvalues can now be compared.
-In the upcoming tables, the eigenvalues of the two-dimensional beam are compared to the eigenvalues of the three-dimensional beam.
-For each case of $h$, different values of $b$ are given.\\
+In the tables of this subsection, the eigenvalues of the two-dimensional beam are compared to the eigenvalues of the three-dimensional beam.
+Since there are two parameters to consider, $h$ and $b$, only a few cases are considered.\\
 
-Eigenvalues relating to non-beam type eigenvalues that are present in both the two-dimensional and three-dimensional beam, are highlighted in grey.
-The other non-beam type eigenvalues that are only found in the three-dimensional beam, are omitted from the tables.
-The original numbering is maintained.\\
+The three-dimensional beam has more eigenvalues than the two-dimensional beam for the range considered in this investigation.
+Since the interest is in the comparison of the two models, the eigenvalues of the three-dimensional that are not present in the two-dimensional beam are omitted from the tables.\\
 
-The two cases for $h$ are $h = 1/5$ for a short beam and $1/20$ for a slender beam. For now, the investigation is restricted to values where $b \leq h$.
+The eigenvalues for beam type problems, the main focus of this investigation, are highlighted in the tables.\\
+
+The cases considered are similar to the cases in \cite{LVV09}, a short beam and a slender beam.
+For the short beam, $h = 1/5$ and for the slender beam, $h = 1/20$.
+The parameter $b$ will be varied to test the accuracy.
+For now the results are restricted to $b \leq h$.
+The other cases will be discussed later.\\
+
+\subsubsection*{Case $b < h$:}
 

### 2023-02-15 code/Timoshenko_beam.py
python code

@@ -1,5 +1,6 @@
 import numpy
 import sympy
+import time
 
 A = sympy.Symbol('A')
 B = sympy.Symbol('B')
@@ -87,6 +88,7 @@ class TimoshenkoBeam(object):
             return L
         
     def determinant(self, L):
+        L = L.simplify()
         return L.det()
             
 class CantileverTimoshenkoBeam(TimoshenkoBeam):
@@ -96,8 +98,13 @@ class CantileverTimoshenkoBeam(TimoshenkoBeam):
         self.p_0 = 0
 
 if __name__ == "__main__":
+    start_time = time.time()
     cantileverbeam = CantileverTimoshenkoBeam(alpha = 1200)
     L = cantileverbeam.calculate_matrix()
-    function = cantileverbeam.determinant(L)
+    L.simplify()
+    #function = cantileverbeam.determinant(L)
+    print('Time taken: ', time.time()-start_time)
+    function = numpy.prod(list(L.eigenvals().keys()))
+    print('Time taken: ', time.time()-start_time)
     print(function)
     

### 2023-03-18 TODO.tex
added todo

\documentclass{article}

\begin{document}

\title{Meesters TODO List}
\author{Rudi du Toit}
\date{\today}
\maketitle

\section*{TODO}

\subsection*{Done}
\begin{itemize}
\item Chapter 3.3 Convergence of Eigenvalues and Eigenfunctions oor gedoen. Dit was my teorie deel van die honneurs.
\end{itemize}

\subsection*{In Progress/Need to do}
\begin{itemize}
\item Overview/Summary is op papier en moet dit die komende week afhandel en in die LaTeX format kry.
\item Laaste hoofstuk met numeriese resultate het ek eers op sy gesit toe ek aan chapter 3.3 gewerk het. Moet nou net die kommentaar oor die resultate na kyk.
\end{itemize}

\end{document}

### 2023-03-18 files/Chapter2/generalvibrationmodel.tex
quick save
Overview v1
Noe real changes
Notes on section 2.4.2
Added to section 2.4.2

@@
 \documentclass[../../main.tex]{subfiles}
+
 \begin{document}
+
 \section{Introduction} \label{sec:existence}
@@
 \begin{proof}
-a
+	\textcolor{red}{Inlas 41A. Inlas 41B. Theorem 1.}
 \end{proof}
@@
 
-\textbf{********* MOET [CVV18] in bronnelys sit}\\
+\textcolor{red}{CVV18 moet in die subsection verwys word.}\\
 
@@
 
-\textbf{Assumption A5} The embedding of $V$ into $W$ is compact.
+\textbf{Assumption A5} The embedding of $V$ into $W$ is compact.\\
+
+\textcolor{red}{************************************}\\
+\textcolor{red}{VOORSTEL:}
+
+Consider Problem GVar defined in Section 2.2.\\
+
+Suppose there exists a number $\lambda$ and $x \in V$, $x \neq 0$ such that
+\begin{eqnarray}
+	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V. \label{eq:1D_Model:ModalAnalysisEquation}
+\end{eqnarray}
+
+\textcolor{red}{Following the method of seperation of variables,} $u(t) = T(t)x$ is a solution of the homogeneous problem
+\begin{eqnarray}
+	c(u''(t),v) + b(u(t),v) = 0
+\end{eqnarray}
+if and only if
+\begin{eqnarray}
+	T''  + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
+\end{eqnarray}
+
+\textcolor{red}{A general solution for \eqref{eq:1D_Model:ModalAnalysisT} is} $T(t) = c_1 \sin(\omega t) + c_2 \cos(\omega t)$ with $\omega = \sqrt{\lambda}$.\\
+
+The function $u$ is a natural mode of vibration and $\omega$ natural angular frequency. Natural frequency is $\frac{\omega}{2 \pi}$.\\
+
+From \cite{CVV18}, it follows that a formal series solution for \eqref{eq:1D_Model:ModalAnalysisEquation} can be expressed as
+\begin{eqnarray}
+	u(t) = \sum_{n=1}^{\infty} T_n(t)x_n \label{eq:1D_Model:ModalAnalysisSeriesSolution}
+\end{eqnarray}
+
+The following question is considered: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$?
+To answer this question, consider \cite{CVV18}.\\
+
+\subsubsection{Validity of series solution}
+Consider the partial sum $u^{N}(t) = \sum_{n=1}^{N} T_{n}(t)w_n$. Let
+\begin{eqnarray*}
+	u_0^{N} = \sum_{n=1}^{N} A^*_n w_n \ \ \textrm{ and } \ \ u_{1}^{N} =\sum_{n=1}^{N} B^*_n w_n
+\end{eqnarray*} where $A^*_n = T_n(0)$ and $B^*_n = T'_n(0)$.\\
+
+In \cite{CVV18}, the validity of the series solution is proved using the energy norms. The energy $\mathcal{E}$ a function $u$ given by
+\begin{eqnarray}
+	\mathcal{E} (t) = \frac{1}{2} b(u(t), u(t)) + \frac{1}{2} c(u'(t), u'(t)). \label{eq:1D_Model:ModalAnalysisEnergy}
+\end{eqnarray}
+
+The partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions to Problem GVar.\\
+
+In \cite{CVV18}, a error function is defined $u^E_N = u - u^N$. Following the initial conditions, $u^E_N = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.\\
+
+Let $\mathcal{E}$ denote the energy of the error function $u^E_N$.
+In \cite{CVV18} it is proven that $\mathcal{E}(t) \leq \mathcal{E}(0)$.
+Using this inequality it follows that, \[||u(t) -  u^N(t)||_V^2 + ||u'(t) - (u^N)'(t)||^2_W \leq ||u_0 - u^N_0||_V^2 + ||u_1 - u^N_1||_W^2.
+\]
+
+The authors of \cite{CVV18} prove that $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$.
+Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$.\\
+
+It follows that the partial series solution converges to the solution $u$ as the initial conditions $u_0^N$ and $u_1^N$ converges to $u_0$ and $u_1$ respectively.\\
+
+\subsubsection{Comparison of models}
+In a later chapter of this dissertation, different dimensional models are compared with each other.
+Since the formal series solution is a linear combination of eigenvalues and eigenfunctions, it is only required to compare the eigenvalues and eigenfunctions of the different models.\\
+
+Using the results of this subsection, it can be shown that for specific initial conditions, the formal series solution is valid for the different models.
+So if the two models are disturbed in the exact same way, the formal series solution is valid for both models, and hence the eigenvalues and eigenfunctions can be used to compare the models.\\
 

### 2023-03-21 files/Chapter2/generalvibrationmodel.tex
notes on discussion

@@
 
+Kan sien met substituting, meer
+
+MODAL solution\\
+
 Suppose the function $T$ satisfies the following differential equation
@@
 Simple substitution confirms that the trial solution satisfies the partial differential equations and the boundary conditions for Problem T-1.\\
+
+As w en phi kan 2.4.1 en () dan sal .... nie nodig nie. Probeer so ver as moontlik nie seperation of variables gebruik nie. Se eerder oof w en phi is sin en cos\\
 
@@
 In [VV06] the authors proved the following theorem.
+
+Los voorlopig hier.\\
 
@@
 
-\subsection{General vibration problem}
+\subsection{General vibration problem new}
+\subsection{General vibration problem old}
 
-\textcolor{red}{CVV18 moet in die subsection verwys word.}\\
+\textcolor{red}{CVV18 word verwys, kyk onder}\\
 
@@
 
+nie seperation of variables nie, eers question dan cvv. Kry modal solutions, kan ons dit nou gebruik om algemene solution te kry?
 \textcolor{red}{Following the method of seperation of variables,} $u(t) = T(t)x$ is a solution of the homogeneous problem
@@
 \subsubsection{Comparison of models}
+Hele disseratoin gaan oor comparison of models. \\
+
 In a later chapter of this dissertation, different dimensional models are compared with each other.

### 2023-03-22 files/Chapter2/generalvibrationmodel.tex
Partial work

@@
 \begin{proof}
-	\textcolor{red}{Inlas 41A. Inlas 41B. Theorem 1.}
+	\textcolor{red}{Inlas 41A.}
 \end{proof}
 
+\newtheorem{Theorem_1}{Theorem}
+\begin{Theorem_1}
 There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
+\end{Theorem_1}
+
 \begin{proof}
@@
 And to understand how modal analysis is applied, a Timoshenko beam is used as an example.
-Specifically, Problem T-1.
-\textcolor{red}{******* WHY NOT T-2???}\\
+Specifically, Problem T-1 as it is easy to illustrate the idea of modal analysis.\\
 
@@
 
-The solution to Problem T-1E is a pair of functions $\langle \tilde{w} \ \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$.\\
-
-Kan sien met substituting, meer
-
-MODAL solution\\
+Solutions to Problem T-1E is a pair of functions $\langle \tilde{w} \ \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$.
+Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are modal solutions of the differential equations and satisfy the boundary conditions.\\
 
@@
 \end{eqnarray} with $\lambda$ an eigenvalue.\\
-
-Simple substitution confirms that the trial solution satisfies the partial differential equations and the boundary conditions for Problem T-1.\\
-
-As w en phi kan 2.4.1 en () dan sal .... nie nodig nie. Probeer so ver as moontlik nie seperation of variables gebruik nie. Se eerder oof w en phi is sin en cos\\
 
@@
 \subsection{General vibration problem new}
+In the previous section In this subsection, is an investigation of the validity of a series solution for a general vibration problem.
+Specifically, the validity of the series solution given some initial conditions.\\
+
+Suppose there exists a number $\lambda$ and $x \in V$, $x \neq 0$ such that
+\begin{eqnarray*}
+	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
+\end{eqnarray*}
+
 \subsection{General vibration problem old}

### 2023-03-26 files/Chapter2/generalvibrationmodel.tex
Veranderinge soos oor die foom

@@
 \begin{proof}
-	\textcolor{red}{Inlas 41A.}
+	\textcolor{red}{Inlas 41A. Nie seker wat 41A verwys in die veranderinge nie. Kom die ander deel reg maak}
 \end{proof}
@@
 As mentioned before, if $a = 0$, the weak damping as well as assumption \textbf{A4} is satisfied.
-Also, as explained in Section \ref{sec:existence:ExistenceAndUniqueness} the constuction of the operator $A$ is not affected.\\
+Also, as explained in Section \ref{sec:existence:ExistenceAndUniqueness} the constuction of the operator $A$ is not affected.
 
@@
 And to understand how modal analysis is applied, a Timoshenko beam is used as an example.
-Specifically, Problem T-1 as it is easy to illustrate the idea of modal analysis.\\
+Specifically, Problem T-1 as it is easy to illustrate the idea of modal analysis.
 
-Consider the partial differential equations of a pinned-pinned Timoshenko beam (obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}).
+Consider the partial differential equations of a pinned-pinned Timoshenko beam (obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}):
 \begin{eqnarray*}
@@
 \begin{eqnarray*}
-	w(0,t) = 0, & &	\	 w(1,t) = 0. \label{eq:1D_Model:ModalBC1}\\
-	M(0,t) = 0, & &	\	M(1,t) = 0, \label{eq:1D_Model:ModalBC2}
+	w(0,t) = 0, & &	\	 w(1,t) = 0, \label{eq:1D_Model:ModalBC1}\\
+	M(0,t) = 0, & &	\	M(1,t) = 0. \label{eq:1D_Model:ModalBC2}
 \end{eqnarray*}
@@
 \end{eqnarray*}
-Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ with $\phi(x,t) = T(t)\tilde{\phi}(x)$. \\
+Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ with $\phi(x,t) = T(t)\tilde{\phi}(x)$.
 
-The method of separation of variables leads to an eigenvalue problem. For the pinned-pinned beam, this eigenvalue problem is referred to as Problem T-1E.
+\textcolor{red}{Commonly at this point, the method of seperation of variables is applied.
+This splits the partial differential equation into an eigenvalue problem and a differential equation.
+Instead of using this method, a formulation of the eigenvalue problem and differential equation will be assumed and we'll show that they satisfy the trial solutions.}\sout{The method of separation of variables leads to an eigenvalue problem.}
+
+For the pinned-pinned beam, the eigenvalue problem is referred to as Problem T-1E.
 \subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
@@
 	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
-\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.\\
+\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.
 
-Solutions to Problem T-1E is a pair of functions $\langle \tilde{w} \ \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$.
-Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are modal solutions of the differential equations and satisfy the boundary conditions.\\
+Solutions to Problem T-1E is a pair of functions $\langle \tilde{w}, \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$.
+\textcolor{red}{Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are solutions of the differential equations and satisfy the boundary conditions.}
 
@@
 	\ddot{T} + \lambda T = 0, \label{eq:1D_Model:ModalAnalysisT}
-\end{eqnarray} with $\lambda$ an eigenvalue.\\
+\end{eqnarray} with $\lambda$ an eigenvalue.
+
+\textcolor{red}{Die deel copy vanaf later in die section}
+
+\textcolor{red}{********************************************************}
+
+It is well known that the eigenvalue problem like Problem T-1E has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
+For the pinned-pinned beam (Problem T-1), $\lambda_n > 0$ for all $n > 0$ (this is also true for Problem T-2 and Problem T-4).
+A convenient reference is \cite{VV06}.
 
@@
 \begin{eqnarray}
-	T_n(t)=A_n\cos(\sqrt{\lambda_n}t)+B_n\sin(\sqrt{\lambda_n}t), \label{eq:1D_Model:ModalAnalysisTn}
+	T_k(t)=A_n\cos(\sqrt{\lambda_n}t)+B_n\sin(\sqrt{\lambda_n}t), \label{eq:1D_Model:ModalAnalysisTn}
 \end{eqnarray}
-(with $A_n$ and $B_n$ arbitrary constants) for the ordinary differential equation \eqref{eq:1D_Model:ModalAnalysisT}.\\
+(with $A_n$ and $B_n$ arbitrary constants) for the ordinary differential equation \eqref{eq:1D_Model:ModalAnalysisT}.
 
-The eigenvalues for the pinned-pinned beam model is the first example in [VV06].
+Combining these solutions give solutions in the form the trial solutions:
+\begin{eqnarray*}
+	w_n(x,t) & = & T_n(t)\tilde{w}_n(t), \\
+	\phi_n(x,t) & = & T_n(t)\tilde{\phi}_n(x).
+\end{eqnarray*} 
+Substitution show that these solutions does indeed satisfy the differential equations with the boundary conditions.
+These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.
+
+Therefore the formal series solution for Problem T-1 is
+\begin{eqnarray*}
+	\langle u, \phi \rangle = \sum_{n=1}^{\infty} T_n(t)\langle u_n(x), \phi_n(x)\rangle.
+\end{eqnarray*}
+
+**********Conclusion of the section**********
+
+\textcolor{red}{********************************************************}
+
+The eigenvalues for the pinned-pinned beam model is the first example in \cite{VV06}.
 In this dissertation, the pinned-pinned model problem is referred to as Problem T-1 (eigenvalue problem Problem T-1E).
 Obviously, since $\langle 0 \ 1\rangle$ satisfies the boundary conditions, it is an eigenfunction with corresponding eigenvalue $\alpha$.
-In [VV06] the authors proved the following theorem.
+In \cite{VV06} the authors proved the following theorem.
 
-Los voorlopig hier.\\
+\textcolor{red}{Los theorem voorlopig hier. Alles onder die theorem is soortgelyk aan wat hier bo is. Was gedoen op die variational form van Problem T1.}\\
 
@@
 For Problem T-1 (Problem T-2 and Problem T-4 also), $\lambda_n > 0$ for all $n > 0$.
-A convenient reference is [VV06].\\
+A convenient reference is \cite{VV06}.\\
 
@@
 \end{eqnarray*} satisfying the boundary conditions.
-These solutions are referred to as the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.\\
+These solutions are referred to as the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.
 
@@
 
-The article [VV06] provides a rigorous method to solving the eigenvalue problem for Timoshenko beam models of different boundary conditions.
-This method and examples form [VV06] is discussed in Chapter 4.
+The article \cite{VV06} provides a rigorous method to solving the eigenvalue problem for Timoshenko beam models of different boundary conditions.
+This method and examples form \cite{VV06} is discussed in Chapter 4.
 
 \subsection{General vibration problem new}
-In the previous section In this subsection, is an investigation of the validity of a series solution for a general vibration problem.
-Specifically, the validity of the series solution given some initial conditions.\\
+Using the pinned-pinned beam as an example, in the previous section it was shown that a formal series solution can be derived that satisfies the boundary conditions.
+In this section, a more general vibration problem is considered that also includes initial conditions.
 
@@
 \end{eqnarray*}
+
+Then, $u(t) = T(t)x$ is a solution of the homogeneous problem
+\begin{eqnarray*}
+	c(u''(t),v) + b(u(t),v) = 0
+\end{eqnarray*}
+if and only if
+\begin{eqnarray}
+	T''  + \lambda T = 0.
+\end{eqnarray}
+
+Then the formal series solution for the boundary value problem is
+\begin{eqnarray}
+	u(t) = \sum_{n=1}^{\infty} T_n(t)x_n. \label{eq:1D_Model:ModalAnalysisSeriesSolution}
+\end{eqnarray}
+
+This is a generalisation of the formal series solution for Problem T-1.
+This also means that the formal series solution satisfies the partial differential equation and the boundary conditions.
+However, it is not yet known if the formal series solution satisfies the initial conditions.
+
+\subsubsection{Validity of series solution}
+Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$?
+To answer this question, consider the article \cite{CVV18}.
+
+Denote the partial sum $u^{N}(t) = \sum_{n=1}^{N} T_{n}(t)w_n$. Let
+\begin{eqnarray*}
+	u_0^{N} = \sum_{n=1}^{N} A^*_n w_n \ \ \textrm{ and } \ \ u_{1}^{N} =\sum_{n=1}^{N} B^*_n w_n
+\end{eqnarray*} where $A^*_n = T_n(0)$ and $B^*_n = T'_n(0)$.
+
+In \cite{CVV18}, the validity of the series solution is proved using the energy norms, where the energy $\mathcal{E}$ a function $u$ given by
+\begin{eqnarray}
+	\mathcal{E} (t) = \frac{1}{2} b(u(t), u(t)) + \frac{1}{2} c(u'(t), u'(t)). \label{eq:1D_Model:ModalAnalysisEnergy}
+\end{eqnarray}
+
+The partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions to Problem GVar.
+
+In \cite{CVV18}, a error function is defined $u^E_N = u - u^N$. Following the initial conditions, $u^E_N = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.
+
+Let $\mathcal{E}$ denote the energy of the error function $u^E_N$.
+In \cite{CVV18} it is proven that $\mathcal{E}(t) \leq \mathcal{E}(0)$.
+Using this inequality it follows that, \[||u(t) -  u^N(t)||_V^2 + ||u'(t) - (u^N)'(t)||^2_W \leq ||u_0 - u^N_0||_V^2 + ||u_1 - u^N_1||_W^2.
+\]
+
+The authors of \cite{CVV18} prove that $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$.
+Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$.
+
+It follows that the partial series solution converges to the solution $u$ as the initial conditions $u_0^N$ and $u_1^N$ converges to $u_0$ and $u_1$ respectively.
+
+\subsubsection{Comparison of models}
+In this dissertation, we are trying to compare different models for use in applications.
+Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.\\
+
+The validity of the formal series solution with initial conditions is required to investigate the vibration of the models.
+This ensured that if the models are disturbed in the exact same way, the formal series solution is valid, and therefore the comparison can be made.
+
+\textcolor{red}{****************OLD*************}
+
+Hele dissertation gaan oor comparison of models.
+
+In a later chapter of this dissertation, different dimensional models are compared with each other.
+Since the formal series solution is a linear combination of eigenvalues and eigenfunctions, it is only required to compare the eigenvalues and eigenfunctions of the different models.\\
+
+Using the results of this subsection, it can be shown that for specific initial conditions, the formal series solution is valid for the different models.
+So if the two models are disturbed in the exact same way, the formal series solution is valid for b
 
@@
 \begin{eqnarray}
-	T''  + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
+	T''  + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT1}
 \end{eqnarray}

### 2023-04-01 files/Chapter2/generalvibrationmodel.tex
notes

@@
 Consider the partial differential equations of a pinned-pinned Timoshenko beam (obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}):
-\begin{eqnarray*}
-	\partial^{2}_{t} w &=& \partial_{x}(\partial_{x} w - \phi), \label{eq:1D_Model:ModalPDE1}\\
-	\gamma \partial^{2}_{t} \phi &=& \beta (\partial_{x} w - \phi) + \partial_{x}(\partial_{x}\phi),\label{eq:1D_Model:ModalPDE2}
-\end{eqnarray*}
+\begin{eqnarray}
+	  \partial^2_{x} w - \partial_{x}\phi &=& \partial^{2}_{t} w, \label{eq:1D_Model:ModalPDE1}\\
+	  \alpha\partial_{x} w - \alpha\phi + \frac{1}{\gamma}\partial^2_{x}\phi &=&  \partial^{2}_{t} \phi,\label{eq:1D_Model:ModalPDE2}
+\end{eqnarray}
 with boundary conditions
@@
 \end{eqnarray*}
-Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ with $\phi(x,t) = T(t)\tilde{\phi}(x)$.
+Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ and $\phi(x,t) = T(t)\tilde{\phi}(x)$.
+Substituting these trial solutions in \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} yields
+\begin{eqnarray*}
+	T(t)\tilde{w}''(x) - T(t)\tilde{\phi}'(x) &=& T''(t)\tilde{w}(x),\\
+	  \alpha T(t)\tilde{w}'(x) - \alpha T(t)\tilde{\phi}(x) + \frac{1}{\gamma}T(t)\tilde{\phi}''(x) &=&  T''(t)\tilde{\phi}(x).
+\end{eqnarray*}
+Dividing by $T(t)$,
+\begin{eqnarray*}
+	\tilde{w}''(x) - \tilde{\phi}'(x) &=& \frac{T''(t)}{T(t)}\tilde{w}(x),\\
+	  \alpha \tilde{w}'(x) - \alpha \tilde{\phi}(x) + \frac{1}{\gamma}\tilde{\phi}''(x) &=&  \frac{T''(t)}{T(t)}\tilde{\phi}(x).
+\end{eqnarray*}
 
-\textcolor{red}{Commonly at this point, the method of seperation of variables is applied.
-This splits the partial differential equation into an eigenvalue problem and a differential equation.
-Instead of using this method, a formulation of the eigenvalue problem and differential equation will be assumed and we'll show that they satisfy the trial solutions.}\sout{The method of separation of variables leads to an eigenvalue problem.}
+Therefore $\displaystyle \frac{T''(t)}{T(t)}$ must be a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. Then the function $T$ satisfies the following differential equation
+\begin{eqnarray}
+	\ddot{T} + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
+\end{eqnarray}
 
-For the pinned-pinned beam, the eigenvalue problem is referred to as Problem T-1E.
+The following problem is also obtained and is called an eigenvalue problem. \sout{For the pinned-pinned beam, this eigenvalue problem is referred to as Problem T-1E.}
 \subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
@@
 Solutions to Problem T-1E is a pair of functions $\langle \tilde{w}, \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$.
-\textcolor{red}{Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are solutions of the differential equations and satisfy the boundary conditions.}
+Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are solutions of the differential equations and satisfy the boundary conditions.
 
-Suppose the function $T$ satisfies the following differential equation
-\begin{eqnarray}
-	\ddot{T} + \lambda T = 0, \label{eq:1D_Model:ModalAnalysisT}
-\end{eqnarray} with $\lambda$ an eigenvalue.
-
-\textcolor{red}{Die deel copy vanaf later in die section}
-
-\textcolor{red}{********************************************************}
-
-It is well known that the eigenvalue problem like Problem T-1E has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
+\sout{It is well known} that the eigenvalue problem like Problem T-1E has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
 For the pinned-pinned beam (Problem T-1), $\lambda_n > 0$ for all $n > 0$ (this is also true for Problem T-2 and Problem T-4).
@@
 
-**********Conclusion of the section**********
-
-\textcolor{red}{********************************************************}
-
 The eigenvalues for the pinned-pinned beam model is the first example in \cite{VV06}.
@@
 In \cite{VV06} the authors proved the following theorem.
-
-\textcolor{red}{Los theorem voorlopig hier. Alles onder die theorem is soortgelyk aan wat hier bo is. Was gedoen op die variational form van Problem T1.}\\
 
@@
 \begin{eqnarray*}
-	\int_0^1 \lambda \tilde{w} v &=& -\int_0^1 \tilde{w}'v'  + \int_0^1 \tilde{\phi} v',\\
-	\int_0^1 \lambda \tilde{\phi} \psi &=& -\int_0^1\alpha \tilde{w}' \psi + \int_0^1\alpha \tilde{\phi} \psi - \int_0^1\frac{1}{\gamma}\tilde{\phi}' \psi'.
-\end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$.\\
-
-It is well known that the eigenvalue problem like Problem T-1EV has infinitely many solutions $\langle \tilde{w}_n \ \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
-For Problem T-1 (Problem T-2 and Problem T-4 also), $\lambda_n > 0$ for all $n > 0$.
-A convenient reference is \cite{VV06}.\\
-
-Corresponding to this sequence of eigenvalues, we have a sequence of solutions $(T_n(t))$:
-\begin{eqnarray}
-	T_n(t)=A_n\cos(\sqrt{\lambda_n}t)+B_n\sin(\sqrt{\lambda_n}t), \label{eq:1D_Model:ModalAnalysisTn}
-\end{eqnarray}
-(with $A_n$ and $B_n$ arbitrary constants) for the ordinary differential equation \eqref{eq:1D_Model:ModalAnalysisT}.\\
-
-As a consequence, the system of partial differential equations of Problem T-1 has a sequence of solutions $(w_n,\phi_n)$ such that
-\begin{eqnarray*}
-	w_n(x,t) & = & T_n(t)\tilde{w}_n(t), \\
-	\phi_n(x,t) & = & T_n(t)\tilde{\phi}_n(x).,
-\end{eqnarray*} satisfying the boundary conditions.
-These solutions are referred to as the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.
-
-The formal series solution for Problem T-1 is
-\begin{eqnarray*}
-	\langle u \ \phi \rangle = \sum_{n=1}^{\infty} T_n(t)\langle u_n(x) \ \psi_n(x)\rangle.
-\end{eqnarray*}
-
-The article \cite{VV06} provides a rigorous method to solving the eigenvalue problem for Timoshenko beam models of different boundary conditions.
-This method and examples form \cite{VV06} is discussed in Chapter 4.
+	 -\int_0^1 \tilde{w}'v'  + \int_0^1 \tilde{\phi} v' &=& \int_0^1 \lambda \tilde{w} v ,\\
+	 -\int_0^1\alpha \tilde{w}' \psi + \int_0^1\alpha \tilde{\phi} \psi - \int_0^1\frac{1}{\gamma}\tilde{\phi}' \psi' &=& \int_0^1 \lambda \tilde{\phi} \psi .
+\end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$.
 
 \subsection{General vibration problem new}
-Using the pinned-pinned beam as an example, in the previous section it was shown that a formal series solution can be derived that satisfies the boundary conditions.
-In this section, a more general vibration problem is considered that also includes initial conditions.
+\textcolor{red}{Introduction***}
 
-Suppose there exists a number $\lambda$ and $x \in V$, $x \neq 0$ such that
-\begin{eqnarray*}
+Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. Assume there is no damping and no forcing.
+
+\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
+Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
+\begin{eqnarray}
+	c(u''(t),v)+b(u(t),v) = 0 \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
+\end{eqnarray}
+with $u(0)=u_{0}$, $u'(0)=u_{1}$.\\
+
+Consider a trial solution $u(t) = T(t)x$ with $x \in V$ and $x \neq 0$.
+
+Similar to the example of the pinned-pinned beam in the previous section, substitution shows that this trial solution is a solution to \eqref{eq:existence:ProblemGVarHom} if and only if you can find a real number $\lambda$ such that
+\begin{eqnarray}
+	T''  + \lambda T = 0,
+\end{eqnarray}
+and there exists a $x \in V$ with $x \neq 0$ such that
+\begin{eqnarray}
 	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
-\end{eqnarray*}
-
-Then, $u(t) = T(t)x$ is a solution of the homogeneous problem
-\begin{eqnarray*}
-	c(u''(t),v) + b(u(t),v) = 0
-\end{eqnarray*}
-if and only if
-\begin{eqnarray}
-	T''  + \lambda T = 0.
 \end{eqnarray}

### 2023-04-15 files/Chapter2/generalvibrationmodel.tex
chapter 2 + 4

@@
 
-The following problem is also obtained and is called an eigenvalue problem. \sout{For the pinned-pinned beam, this eigenvalue problem is referred to as Problem T-1E.}
+If such a $\lambda$ exists, it leads to the following problem called an eigenvalue problem.
 \subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
@@
 
+\textcolor{red}{Due to this periodicity of these solutions for} the eigenvalue problem Problem T-1E, it has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
+The vector $\langle 0, 1 \rangle$ also satisfies the eigenvalue problem with boundary conditions.
+This solution is called the constant solution.
+
+A systematic approach to get the eigenvalues and eigenfunctions is given in \cite{VV06}.
+This is discussed in in Section 4.2.
+The following theorem is derived from \cite{VV06} and confirms the validity of our trial solutions for the eigenvalue problem.
+
+\newtheorem{ThmVV06}{Theorem}
+\begin{ThmVV06}
+	If $\langle u \ \phi\rangle$ is a non-constant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions.
+$A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$.
+Also all eigenvalues less than $\alpha$ are simple eigenvalues.
+The solution $\langle 0, 1 \rangle$ is a constant solution of Problem T-1E.
+\end{ThmVV06}
+
+\textcolor{red}{**************OLD VERSION******************}
+
 \sout{It is well known} that the eigenvalue problem like Problem T-1E has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
@@
 A convenient reference is \cite{VV06}.
+
+The eigenvalues for the pinned-pinned beam model is the first example in \cite{VV06}.
+In this dissertation, the pinned-pinned model problem is referred to as Problem T-1 (eigenvalue problem Problem T-1E).
+Obviously, since $\langle 0 \ 1\rangle$ satisfies the boundary conditions, it is an eigenfunction with corresponding eigenvalue $\alpha$.
+In \cite{VV06} the authors proved the following theorem.
+
+\newtheorem{ThmVV06_2}{Theorem}
+\begin{ThmVV06_2}
+	If $\langle u \ \phi\rangle$ is a nonconstant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions.
+$A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$.
+Also all eigenvalues less than $\alpha$ are simple eigenvalues.
+\end{ThmVV06_2}
+
+\textcolor{red}{********************************}
 
@@
 
-Combining these solutions give solutions in the form the trial solutions:
+Combining the solutions of the eigenvalue problem with the solution \eqref{eq:1D_Model:ModalAnalysisTn} yields:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-
-The eigenvalues for the pinned-pinned beam model is the first example in \cite{VV06}.
-In this dissertation, the pinned-pinned model problem is referred to as Problem T-1 (eigenvalue problem Problem T-1E).
-Obviously, since $\langle 0 \ 1\rangle$ satisfies the boundary conditions, it is an eigenfunction with corresponding eigenvalue $\alpha$.
-In \cite{VV06} the authors proved the following theorem.
-
-\newtheorem{ThmVV06}{Theorem}
-\begin{ThmVV06}
-	If $\langle u \ \phi\rangle$ is a nonconstant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions.
-$A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$.
-Also all eigenvalues less than $\alpha$ are simple eigenvalues.
-\end{ThmVV06}
 

### 2023-04-15 files/Chapter4/ModalAnalysisTimo.tex
chapter 2 + 4

@@
 \section{Introduction}
-
+An example of modal analysis on a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}.
+In this section, more general theory for modal analysis of te Timoshenko beam theory is discuss, as well as some more examples of the application of the theory.
 \section{Eigenvalue problem}\label{sec:Timo:EigenvalueProblem}
@@
 In this section, we look at the work of the authors of [VV06].
-The authors gives a method to calculate the eigenvalues and eigenfunctions for the Timoshenko beam theory.\\
+The authors gives a method to calculate the eigenvalues and eigenfunctions for the Timoshenko beam theory.
 
@@
 
-\sout{The next step is to find a method to {easily} calculate the eigenvalues and eigenvectors for the Timoshenko beam models {theory}}.\\
+\sout{The next step is to find a method to {easily} calculate the eigenvalues and eigenvectors for the Timoshenko beam models {theory}}.
 
 \sout{For this section, the work of the authors of [VV06] is discussed.
-{Consider the article [VV06].} In this article the authors present a method to calculate the exact eigenvalues and eigenvectors for the Timoshenko beam theory}.\\
+{Consider the article [VV06].} In this article the authors present a method to calculate the exact eigenvalues and eigenvectors for the Timoshenko beam theory}.
 
@@
 Recall from section \ref{sec:1D_Model}, $u$ represents the transverse motion of the beam, $\phi$ is the angle of rotation of the cross-section of the beam, $\alpha$ and $\gamma$ are dimensionless constants defined in section 1.5 and $\lambda$ represents the eigenvalue.
-\\
 

### 2023-04-15 files/Chapter2/generalvibrationmodel.tex
temp changes, pulling

--- 2023-04-01 files/Chapter2/generalvibrationmodel.tex
@@
 
-Therefore $\displaystyle \frac{T''(t)}{T(t)}$ must be a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. Then the function $T$ satisfies the following differential equation
+Therefore $\displaystyle \frac{T''(t)}{T(t)}$ is a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. This can also be written as the following differential equation
 \begin{eqnarray}
@@
 
-The following problem is also obtained and is called an eigenvalue problem. \sout{For the pinned-pinned beam, this eigenvalue problem is referred to as Problem T-1E.}
+To determine if such a number $\lambda$ exists, the following eigenvalue problem is considered.
+
 \subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}

### 2023-04-15 files/Chapter2/generalvibrationmodel.tex

--- 2023-04-15 files/Chapter2/generalvibrationmodel.tex
@@
 \section{Modal analysis}\label{sec:existence:ModalAnalysis}
-\subsection{Timoshenko beam}
+\subsection{Timoshenko beam}\label{subsec:Timoshenko_Modal_Analsis}
 To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration.
@@
 
-If such a $\lambda$ exists, it leads to the following problem called an eigenvalue problem.
+To determine if such a number $\lambda$ exists, consider the following eigenvalue problem.
 \subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
@@
 \end{eqnarray*} 
-Substitution show that these solutions does indeed satisfy the differential equations with the boundary conditions.
+Substitution show that these solutions does indeed satisfy the differential equations \ref{eq:1D_Model:ModalPDE1} and \ref{eq:1D_Model:ModalPDE2} with the boundary conditions.
 These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.

### 2023-04-15 files/Chapter4/ModalAnalysisTimo.tex

@@
 \section{Eigenvalue problem}\label{sec:Timo:EigenvalueProblem}
-In section \ref{ssec:1D_Model:Modal} the idea of modal analysis is explored using a Timoshenko beam as an example.
-In this section, we look at the work of the authors of [VV06].
-The authors gives a method to calculate the eigenvalues and eigenfunctions for the Timoshenko beam theory.
+This section is a discussion of a systematic method to solve the eigenvalue problem for the Timoshenko beam theory. The article discussed is \cite{VV06}.
 
-Consider a general eigenvalue problem for the Timoshenko beam theory.
-
-\sout{The next step is to find a method to {easily} calculate the eigenvalues and eigenvectors for the Timoshenko beam models {theory}}.
-
-\sout{For this section, the work of the authors of [VV06] is discussed.
-{Consider the article [VV06].} In this article the authors present a method to calculate the exact eigenvalues and eigenvectors for the Timoshenko beam theory}.
-
-\sout{To discuss the work of [VV06], a general eigenvalue problem is required.
-So consider only the differential equations of an eigenvalue problem for a Timoshenko beam.
-The reader can refer to Problem T-1E in section \ref{ssec:1D_Model:Modal} for a more specific example of the derivation of the eigenvalue problems for the Timoshenko beam theory.}
-
-\sout{In section \ref{ssec:1D_Model:Modal}, the eigenvalue for Problem T-1 is given as Problem T-1E. }
-\textcolor{red}{Probleem se naam verander vanaf Differential equations for the eigenvalue problem}
+Consider a general eigenvalue problem for a Timoshenko beam Problem.
 \subsubsection{General eigenvalue problem} \label{sssec:Timo:EigenvalueProblem}
@@
 
-The authors of [VV06] first derive a general solution for the system of ordinary differential equations \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2}.
-In [VV06] the authors show that for the Timoshenko models in this dissertation $\lambda$ non-negative.
+The authors of \cite{VV06} first derive a general solution for the system of ordinary differential equations \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2}.
+In \cite{VV06} the authors show that for the Timoshenko models in this dissertation $\lambda$ non-negative.
 Assume that the solution is of the form $\langle u, \phi \rangle = e^{mx}\bar{w}$ where $m\in \mathbb{R}$ or $m\in \mathbb{C}$.
@@
 Now if $m^{2} \neq 0$, we consider the system $A\bar{w}=0$ with $w_{1} = m$ and $w_{2} = m^{2} + \lambda$.
-From [VV06], the parameters $\omega$, $\mu$ and $\theta$ are uniquely determined by $\lambda$.
+From \cite{VV06}, the parameters $\omega$, $\mu$ and $\theta$ are uniquely determined by $\lambda$.
 \begin{eqnarray}
@@
 
- The three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$ are considered separately by the authors of [VV06]. The general solution from [VV06] for each case is presented below.
+ The three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$ are considered separately by the authors of \cite{VV06}.
+The general solution from \cite{VV06} for each case is presented below.
 
@@
 The next step is to determine the solution of the general eigenvalue problem.
-The strategy to obtain the eigenvalues and eigenvectors are described in detail in [VV06] using an example.
+The strategy to obtain the eigenvalues and eigenvectors are described in detail in \cite{VV06} using an example.
 A summary of the strategy is presented here.\\
@@
 
-The following two sections provide examples of this strategy applied to beam models. These examples are also in [VV06].
+In \cite{VV06}, the steps are explained using the example of a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}.
+For $\lambda < \alpha$ the general solution reduces to $\langle u , \phi \rangle = \langle \sin, \cos \rangle$.
+For $\lambda > \alpha$, the general solution also reduces to $\langle u , \phi \rangle = \langle \sin, \cos \rangle$.
+For $\lambda = \alpha$, the general solution reduces to $\langle u , \phi \rangle = \langle 0, 1 \rangle$.\\
+
+This is proved rigourously in \cite{VV06} and also proved Theorem 1 in section \ref{subsec:Timoshenko_Modal_Analsis}.
+
+The following two sections provide examples of this strategy applied to beam models. These examples are also in \cite{VV06}.
 

### 2023-04-18 Gedoen.tex
Overview 2.0
chap 2.4 and chap 4.2

@@
 
-\subsection{Chapter 1}
-\begin{itemize}
-	\item Het 1.4.21 reg gemaak. Moet nog deur gaan en seker maak ek het dit ander plekke reg.
-\end{itemize}
+Het gefokus om eerder klein veranderinge te maak.
+So lyk dalk na min veranderinge maar het probeer mooi dink oor als.
+Daar is nog wat ek more aan gaan werk, maar is kleiner goed soos seker maak die references na equations/sections is als reg.
+\subsubsection*{Section 2.4}
+Het gefokus om die verduideliking te verbeter.
+Ek weet prof het gese die eigenvalue problem moet voor die differential equation van $T$ wees, maar ek het nie die volgorder verander nie.
+EK het gevoel dit gaan baie meer verander en dan mag ek dalk grooter foute maak.
+So e het dit gelos, en probeer die verduideliking reg maak.
 
-\subsection{Chapter 2}
-\begin{itemize}
-	\item Het verbeteringe aangebring.
-\end{itemize}
+Ek het dan van die klein veranderinge ook gemaak.
 
-\subsection{Appendix}
-\begin{itemize}
-	\item $L_2$ in gesit.
-\end{itemize}
+\subsubsection*{Section 4.1}
+Het 'n eenvoudige inleiding gemaak wat section 2.4 link.
+
+\subsubsection*{Section 4.2}
+Aan die einde net die werk oor die pinned pinned beam by gesit. Het dit net gehou soos prof versuidelik het, en nog nie op die regte plek gesit nie.
+
+Het ook goed in die begin wat dood getrek was uit gehaal
 

### 2023-04-18 files/Chapter2/generalvibrationmodel.tex
chap 2.4 and chap 4.2

@@
 
-Therefore $\displaystyle \frac{T''(t)}{T(t)}$ is a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. This can also be written as the following differential equation
+Therefore $\displaystyle \frac{T''(t)}{T(t)}$ is a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. This can also be written as the following differential equation,
 \begin{eqnarray}
@@
 Solutions to Problem T-1E is a pair of functions $\langle \tilde{w}, \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$.
-Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are solutions of the differential equations and satisfy the boundary conditions.
+Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are possible solutions of the differential equations and satisfy the boundary conditions.
 
-\textcolor{red}{Due to this periodicity of these solutions for} the eigenvalue problem Problem T-1E, it has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
+Due to this periodicity of these solutions for the eigenvalue problem Problem T-1E, it has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
 The vector $\langle 0, 1 \rangle$ also satisfies the eigenvalue problem with boundary conditions.
@@
 
-A systematic approach to get the eigenvalues and eigenfunctions is given in \cite{VV06}.
+A systematic approach to obtain the eigenvalues and eigenfunctions is given in \cite{VV06}.
 This is discussed in in Section 4.2.
-The following theorem is derived from \cite{VV06} and confirms the validity of our trial solutions for the eigenvalue problem.
+From \cite{VV06}, the following theorem can be derived and confirms the validity of our trial solutions for the eigenvalue problem.
 
@@
 \begin{ThmVV06}
-	If $\langle u \ \phi\rangle$ is a non-constant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions.
+	If $\langle u, \phi\rangle$ is a non-constant eigenfunction of Problem T-1E, then $\langle u, \phi\rangle = \langle\sin k \pi x, A_k \cos k \pi x\rangle$ which satisfies the boundary conditions.
 $A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$.
+If $\langle u, \phi\rangle$ is a constant eigenfunction of Problem T1-E, then  $\langle u, \phi\rangle = \langle 0, 1 \rangle$.
 Also all eigenvalues less than $\alpha$ are simple eigenvalues.
-The solution $\langle 0, 1 \rangle$ is a constant solution of Problem T-1E.
 \end{ThmVV06}
@@
 \subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
-Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
+Find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
 \begin{eqnarray}
@@
 \end{eqnarray}
-with $u(0)=u_{0}$, $u'(0)=u_{1}$.\\
+with $u(0)=u_{0}$, $u'(0)=u_{1}$.
 
@@
 
-Similar to the example of the pinned-pinned beam in the previous section, substitution shows that this trial solution is a solution to \eqref{eq:existence:ProblemGVarHom} if and only if you can find a real number $\lambda$ such that
+Substitution shows that this trial solution is a solution to \eqref{eq:existence:ProblemGVarHom} if and only if you can find a real number $\lambda$ such that 
 \begin{eqnarray}
@@
 However, it is not yet known if the formal series solution satisfies the initial conditions.
+
+\textcolor{red}{*************** Need to check everything below this ******************}
 

### 2023-04-18 files/Chapter4/ModalAnalysisTimo.tex
chap 2.4 and chap 4.2

@@
 The strategy to obtain the eigenvalues and eigenvectors are described in detail in \cite{VV06} using an example.
-A summary of the strategy is presented here.\\
+A summary of the strategy is presented here.
 
@@
 The equation $\textrm{det}(A) = 0$ is called the frequency equation.
-The frequency equation has infinitely many solutions and each solution corresponds to an eigenvalue.\\
+The frequency equation has infinitely many solutions and each solution corresponds to an eigenvalue.
 
- For each eigenvalue, a unique solution for the pair $\bar{b}$ can be obtained. A eigenfunction for $u$ and $\phi$ is obtained using $\bar{b}$ and corresponds to the relevant eigenvalue.\\
+ For each eigenvalue, a unique solution for the pair $\bar{b}$ can be obtained. A eigenfunction for $u$ and $\phi$ is obtained using $\bar{b}$ and corresponds to the relevant eigenvalue.
+
+\textcolor{red}{Die moet net op die regte plek gesit word.}
+
+\textcolor{red}{**********************************************}
 
 In \cite{VV06}, the steps are explained using the example of a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}.
-For $\lambda < \alpha$ the general solution reduces to $\langle u , \phi \rangle = \langle \sin, \cos \rangle$.
-For $\lambda > \alpha$, the general solution also reduces to $\langle u , \phi \rangle = \langle \sin, \cos \rangle$.
-For $\lambda = \alpha$, the general solution reduces to $\langle u , \phi \rangle = \langle 0, 1 \rangle$.\\
+The authors  For $\lambda < \alpha$ the general solution reduces to $\langle u(x) , \phi(x) \rangle = \langle \sin(k \pi x), A_k \cos(k \pi x) \rangle$.
+For $\lambda > \alpha$, the general solution also reduces to $\langle u(x) , \phi(x) \rangle = \langle \sin(k \pi x), A_k  \cos(k \pi x) \rangle$.
+For $\lambda = \alpha$, the general solution reduces to $\langle u(x) , \phi(x) \rangle = \langle 0, 1 \rangle$.
 
-This is proved rigourously in \cite{VV06} and also proved Theorem 1 in section \ref{subsec:Timoshenko_Modal_Analsis}.
+This is proved rigourously in \cite{VV06} and also proves Theorem 1 in section \ref{subsec:Timoshenko_Modal_Analsis}.
+
+\textcolor{red}{**********************************************}
 

### 2023-04-19 files/Chapter2/generalvibrationmodel.tex
general vibration problem

@@
 
-Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. Assume there is no damping and no forcing.
+Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. In this section, assume there is no damping and no forcing.
 
 \subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
-Find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
+Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
 \begin{eqnarray}
@@
 \end{eqnarray}
-with $u(0)=u_{0}$, $u'(0)=u_{1}$.
+with initial conditions $u(0)=u_{0}$ and $u'(0)=u_{1}$.
 
-Consider a trial solution $u(t) = T(t)x$ with $x \in V$ and $x \neq 0$.
+To try and find a solution to this problem, consider a trial solution $u(t) = T(t)x$ with $x \in V$ and $x \neq 0$. Substituting this trial solution into \eqref{eq:existence:ProblemGVarHom} results in
+\begin{eqnarray*}
+	b(T(t)x,v) = - c(T''(t)x,v).  \label{eq:existence:ProblemGVarHom:Substitution}
+\end{eqnarray*}
+
+Due to the linearity of the bilinear form, this equation can be rewritten as
+\begin{eqnarray*}
+	T(t)b(x,v) = - T''(t)c(x,v).
+\end{eqnarray*}
+
+Dividing both sides by $T(t)$ gives
+\begin{eqnarray*}
+	b(x,v) = - \frac{T''(t)}{T(t)}c(x,v).
+\end{eqnarray*}
+
+Therefore $\frac{T''(t)}{T(t)}$ must be a constant.
+Suppose that $\frac{T''(t)}{T(t)} = -\lambda$.
+The existence of such a $\lambda$ is uncertain at this point.
+To investigate the existence of such a $\lambda$, consider the following eigenvalue problem.
+
+Find a real number $\lambda$ and a $x \in V$ with $x \neq 0$ such that
+\begin{eqnarray*}
+	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
+\end{eqnarray*}
+
+A solution to the eigvalue problem consists of an eigenvalue $\lambda$ with corresponding eigenvector $x$.
+
+The article \cite{CVV18} is a convenient reference to show that the eigenvalue problem has a solution if the following assumption is satisfied:
+
+\begin{itemize}
+	\item[] \textbf{A5} - The embedding of $V$ into $W$ is compact.
+\end{itemize}
+
+(Note that this assumption expands on the assumptions already made in Section 2.2.)
+
+Buidling on assumption \textbf{A5}, the authors of \cite{CVV18} prove that there exists a eigenvalue $\lambda$ and a corresponding eigenvector $x$ such that the eigenvalue problem has a solution.
+The authors also prove that the eigenvalues are positive, and the corresponding eigenvectors are orthogonal in $W$ (the bilinear form $c$).
+In fact it is also orthogonal with respect to the bilinear form $b$, hence
+\begin{eqnarray*}
+	b(x_i, x_j) = \lambda_i c(x_i, x_j) = 0, \ \ \ \ \textrm{ for each } \ i \neq j.
+\end{eqnarray*}
+
+The sequence of eigenvalues ${\lambda_i}$ is an infinite sequence with $\lambda_n \rightarrow \infty$ as $n \rightarrow \infty$.
+The sequence of eigenvectors ${x_i}$ forms an orthogonal basis in $W$, which means that any element of $W$ can be represented as a linear combination of the eigenvectors.
+
+\textcolor{red}{Onseker oor die volgede deel oor die Fourier Coefficients. Moet net nog daaroor dink.}
+
+Following this result, the authors explain that any $u \in V$ can be represented as a linear combination of the eigenvectors $x_i$ with coefficients $a_i$.
+These coefficients are Fourier coefficients of $u$ with respect to the basis $x_i$.
+Therefore, for any $u \in V$,
+\begin{eqnarray*}
+	u = \sum_{i=1}^{\infty} a_i x_i. = \sum_{i=1}^{\infty} c(u, x_i)x_i
+\end{eqnarray*}
+
+Now that the eigenvalue problem has a solution, the following ordinary differentiable equation can be considered,
+\begin{eqnarray*}
+	T'' + \lambda T = 0. 
+\end{eqnarray*}
+
+Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
+\begin{flalign*}
+	T_n(t) &= e^{-r_nt}\left[ A_n \cos(\omega_n t) + B_n \sin(\omega_n t) \right],\\
+	T_n(t) &= e^{-r_nt}\left[ A_n + B_n t) \right],\\
+	T_n(t) &= e^{-r_nt}\left[ A_n \cosh(\mu_n t) + B_n \sinh(\mu_n t) \right].
+\end{flalign*}
+
+Then the formal series solution for the boundary value problem is
+\begin{eqnarray}
+	u(t) = \sum_{n=1}^{\infty} T_n(t)x_n. \label{eq:1D_Model:ModalAnalysisSeriesSolution}
+\end{eqnarray}
+
+***********************************************
 

### 2023-04-24 work_plan.tex
workplan

\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{amsmath, amssymb}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{float}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{wasysym} % for checkboxes

\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\titleformat{\section}{\normalfont\Large\bfseries}{\thesection.}{1em}{}
\titleformat{\subsection}{\normalfont\large\bfseries}{\thesubsection}{1em}{}

\title{Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates}
\author{Rudi du Toit}
\date{}

\begin{document}

\maketitle

\noindent
\textbf{Supervisor:} \\
Prof. J. van Rensburg \\
Email: jvrnf2013@gmail.com \\

\noindent
\textbf{Co-supervisor:} \\
Dr. M. Labuschagne  \\
Email: madelein.labuschagne@up.ac.za \\

\section*{Current Status of the Thesis}
The dissertation is mainly complete, and in the review phase. There are a few sections in which the theory is being updated.

\section*{Work Plan}
\subsection*{22-04-2023 - 30-04-2023}
\subsubsection*{Article work}
\begin{itemize}[label=\Square]
  \item Task 0.1: Reading articles.
\end{itemize}

\subsubsection*{Chapter 1: Comparison of models}
\begin{itemize}[label=\Square]
  \item Task 1.1: Review equation and section references.
\end{itemize}

\subsubsection*{Chapter 2: Mathematical analysis of vibration problems}
\begin{itemize}[label=\Square]
  \item Task 2.1: General vibration problems
  \item Task 2.2: Add series solution to the eiegenvalue problem
\end{itemize}

\subsubsection*{Chapter 3: Finite element theory}
\begin{itemize}[label=\Square]
  \item Task 3.1: Apply suggestion from chapter 2 onto chapter 3 ahead of review.
\end{itemize}

\subsubsection*{Chapter 4: Timoshenko beam model}
\begin{itemize}[label=\Square]
  \item Task 4.1: Expand the general solutions of the eigenvalue problem and link it to chapter 2.
\end{itemize}

\subsubsection*{Chapter 5: Finite element method}
\begin{itemize}[label=\Square]
  \item Task 5.1: Self review of Chapter 5.
\end{itemize}

\subsubsection*{Chapter 6: Validity of cantilever beam and plate models}
\begin{itemize}[label=\Square]
  \item Task 6.1: Self review of Chapter 6.
  \item Task 6.2: Re-calculate the numerical results for the three-dimensional beam and two-dimensional plate model.
  \item Task 6.3: Finish the comparison of the three-dimensional beam and two-dimensional plate model.
\end{itemize}

\subsubsection*{Chapter 7: Conclusion}
\begin{itemize}[label=\Square]
  \item Task 6.1: Second draft of the conclusion and summary.
\end{itemize}

\section*{Additional Notes and Remarks}
This week is a focus week on completing some task that have been set a side for some time. It is also necessary just to read up on articles.

\section*{Submission Deadlines}
\begin{itemize}
\item First draft submission: July 2023
\item Feedback from supervisor and co-supervisor: June 2023
\item Final draft submission: TBC
\item Defense date: TBC
\end{itemize}

\end{document}

### 2023-04-24 files/Chapter2/generalvibrationmodel.tex
Voorstel soos epos

@@
 The existence of such a $\lambda$ is uncertain at this point.
-To investigate the existence of such a $\lambda$, consider the following eigenvalue problem.
+So we consider the following eigenvalue problem.
 
@@
 
-(Note that this assumption expands on the assumptions already made in Section 2.2.)
+This assumption expands on the assumptions \textbf{A1}-\textbf{A4} already made in Section 2.2.
 
-Buidling on assumption \textbf{A5}, the authors of \cite{CVV18} prove that there exists a eigenvalue $\lambda$ and a corresponding eigenvector $x$ such that the eigenvalue problem has a solution.
+Building these assumptions, the authors of \cite{CVV18} prove that there exists a eigenvalue $\lambda$ and a corresponding eigenvector $x$ such that the eigenvalue problem has a solution.
 The authors also prove that the eigenvalues are positive, and the corresponding eigenvectors are orthogonal in $W$ (the bilinear form $c$).
@@
 The sequence of eigenvalues ${\lambda_i}$ is an infinite sequence with $\lambda_n \rightarrow \infty$ as $n \rightarrow \infty$.
-The sequence of eigenvectors ${x_i}$ forms an orthogonal basis in $W$, which means that any element of $W$ can be represented as a linear combination of the eigenvectors.
+The sequence of normalized eigenvectors ${x_i}$ forms an orthonormal basis in $W$, which means that the sequence is complete (or total) in $W$.
 
-\textcolor{red}{Onseker oor die volgede deel oor die Fourier Coefficients. Moet net nog daaroor dink.}
-
-Following this result, the authors explain that any $u \in V$ can be represented as a linear combination of the eigenvectors $x_i$ with coefficients $a_i$.
-These coefficients are Fourier coefficients of $u$ with respect to the basis $x_i$.
+Following this result, the authors explain that any $u \in V$, the eigenvector series for $u$ converges to $u$.
+These coefficients $a_i$ are generalized Fourier coefficients of $u$ with respect to the basis $x_i$.
 Therefore, for any $u \in V$,
@@
 \end{eqnarray}
-
-***********************************************
-
-Substitution shows that this trial solution is a solution to \eqref{eq:existence:ProblemGVarHom} if and only if you can find a real number $\lambda$ such that 
-\begin{eqnarray}
-	T''  + \lambda T = 0,
-\end{eqnarray}
-and there exists a $x \in V$ with $x \neq 0$ such that
-\begin{eqnarray}
-	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
-\end{eqnarray}
-
-Then the formal series solution for the boundary value problem is
-\begin{eqnarray}
-	u(t) = \sum_{n=1}^{\infty} T_n(t)x_n. \label{eq:1D_Model:ModalAnalysisSeriesSolution}
-\end{eqnarray}
-
-This is a generalisation of the formal series solution for Problem T-1.
-This also means that the formal series solution satisfies the partial differential equation and the boundary conditions.
-However, it is not yet known if the formal series solution satisfies the initial conditions.
-
-\textcolor{red}{*************** Need to check everything below this ******************}
 

### 2023-04-26 files/Chapter2/generalvibrationmodel.tex
Chapter 3

@@
 \subsection{General vibration problem new}
-\textcolor{red}{Introduction***}
-
-Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. In this section, assume there is no damping and no forcing.
+This section is a discussion of a general vibration problem.
+The discussion will refer to the article \cite{CVV18}.
+Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}.
+The authors of \cite{CVV18} do take damping into consideration, which is not covered in this dissertation.
+Assume there is no damping and no forcing.
 
@@
 
-A solution to the eigvalue problem consists of an eigenvalue $\lambda$ with corresponding eigenvector $x$.
+A solution to the eigenvalue problem consists of an eigenvalue $\lambda$ with corresponding eigenvector $x$.
 
@@
 
-Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
-\begin{flalign*}
-	T_n(t) &= e^{-r_nt}\left[ A_n \cos(\omega_n t) + B_n \sin(\omega_n t) \right],\\
-	T_n(t) &= e^{-r_nt}\left[ A_n + B_n t) \right],\\
-	T_n(t) &= e^{-r_nt}\left[ A_n \cosh(\mu_n t) + B_n \sinh(\mu_n t) \right].
-\end{flalign*}
+Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions as given in \cite{CVV18}:
+\begin{flalign}
+	T_n(t) &= e^{-r_nt}\left[ A_n \cos(\omega_n t) + B_n \sin(\omega_n t) \right] \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
+	T_n(t) &= e^{-r_nt}\left[ A_n + B_n t \right] \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
+	T_n(t) &= e^{-r_nt}\left[ A_n \cosh(\mu_n t) + B_n \sinh(\mu_n t) \right] \quad \textrm{ if } \lambda < 0. \label{lambda_3}
+\end{flalign}
 
-Then the formal series solution for the boundary value problem is
+From assumptions \textbf{A2} and \textbf{A3}, the bilinear forms $b$ and $c$ are positive definite.
+And since we assumed that there is no damping ($a=0$), $\lambda$ cannot be negative.
+Therefore, the only possible solutions for $T_n(t)$ is \eqref{lambda_1} and \eqref{lambda_2}.
+
+Then combining the solutions of the eigenvalue problem and the differential equation, the formal series solution for the boundary value problem is
 \begin{eqnarray}

### 2023-04-26 files/Chapter3/dynamicconvergence.tex
Chapter 3

@@
 \section{Introduction}
-In this chapter, two convergence results for the Finite Element Method (FEM) is discussed.
-The first result is the convergence of the Galerkin approximation for second order hyperbolic type problems, from the article \cite{BV13}.
-The second result is from the textbook \cite{SF97} regarding the convergence of the eigenvalues and eigenfunctions for a one-dimensional vibration problem, using the Finite Element Method.
+In this chapter, two important convegence results of the Finite Element Method (FEM) is discussed.
+The first result looks at the convergence of the Galerkin approximation for second order hyperbolic type problems, as presented in \cite{BV13}.
+The second result, from the textbook \cite{SF97}, examines the convergence of eigenvalues and eigenfunctions for a one-dimensional vibration problem, using the Finite Element Method.
 
@@
 In the article \cite{BV13}, the authors investigate the convergence of the Galerkin approximation for second order hyperbolic type problems.
-The article \cite{BV18} extends \cite{BV13} by including general damping and damping at the endpoints.
-For the models in Chapter 1, \cite{BV13} is sufficient and \cite{BV18} was read for more insight and improved notation.\\
+The article \cite{BV18} extends the work of \cite{BV13} by including general damping and damping at the endpoints.
+For the models in Chapter 1, \cite{BV13} is sufficient while \cite{BV18} provides more insight and improved notation.
 
-In Section 2.2, a general variational problem, called Problem GVar, which is identical to the one in \cite{VV02} is given. From this model, a Galerkin Approximation can be derived.
+In Section 2.2, Problem GVar is presented and identical to the problem in \cite{BV13}. The problem is repeated here for convenience.
 
@@
 \end{eqnarray}
-while $u(0)=u_{0}$, $u'(0)=u_{1}$.\\
+while $u(0)=u_{0}$, $u'(0)=u_{1}$.
 
-It is assumed that the assumptions \textbf{A1}-\textbf{A4} from Section 2.2 are satisfied such that Problem GVar has a unique solution.\\
+Assume that the assumptions \textbf{A1}-\textbf{A4} from Section 2.2 are satisfied ensuring that Problem GVar has a unique solution.
 
-Before the main theory of \cite{BV13} can be discussed, some preparation is required.
+Before the theory of \cite{BV13} can be discussed, some preliminary work is necessary.
+The structure of this section is as follows.
 First the Galerkin approximation is for Problem GVar is derived.
-Then a equivalent system of ordinary differential equations is derived using the Finite Element Method.\\
+Then a equivalent system of ordinary differential equations is derived using the Finite Element Method.
+Finally, the convergence of the Galerkin approximation is discussed using the work of the article \cite{BV13}.
 
-\subsection{Galerkin approximation}
-Recall from Chapter 2 that $V$ is the closure of the test function space $T$ in the Hilbert space $H$.\\
+\subsection{Galerkin approximation of Problem GVar}
+Recall from Chapter 2 that $V$ is the closure of the test function space $T$ in the Hilbert space $H$.
 
 Suppose $S^h$ is a finite n-dimensional subspace of V.
-Let $\{\phi_1, \ \phi_2,...,\phi_n\}$ be a set of linear independent basis functions such that $S^h = \textrm{span}(\{\phi_1, \phi_2, ..., \phi_n \})$ and $\phi_i \in C^{(1)}$ for all $i$.\\
+Let $\{\phi_1, \ \phi_2,...,\phi_n\}$ be a set of linear independent basis functions such that $S^h = \textrm{span}(\{\phi_1, \phi_2, ..., \phi_n \})$ and $\phi_i \in C^{(1)}$ for all $i$.
 
@@
 \end{eqnarray}
-with the initial values $u_h(0)=u^h_{0}$ and $u'_h(0)=u^h_{1}$. The initial conditions $u^h_{0}$ and $u^h_{1}$ are projections of $u_0$ and $u_1$ into the finite dimensional space $S^h$.\\
+with the initial values $u_h(0)=u^h_{0}$ and $u'_h(0)=u^h_{1}$. The initial conditions $u^h_{0}$ and $u^h_{1}$ are projections of $u_0$ and $u_1$ into the finite dimensional space $S^h$.
 
@@
 
-This theorem is presented in \cite{BV13}.
+This theorem is presented and proved in \cite{BV13}.
 
@@
 \end{eqnarray}
-The function $F$ is the interpolation of the function $f$ into the discrete space $S^h$.\\
+The function $F$ is the interpolation of the function $f$ into the discrete space $S^h$.
 
-The following propositions for Problem ODE are given in \cite{BV13}.
+The following propositions related to Problem ODE are given in \cite{BV13}.
 
@@
 \end{DC_Prop2}
-
-Since the set $\{\phi_1, \ \phi_2,...,\phi_n\}$ is a linearly independent basis for $S^h$, the bilinear form $c$ is positive definite on $S^h$.
-Therefore, the matrix $M$ is invertible.
-The equation \eqref{ODE} of Problem ODE can be rewritten as $\bar{u}'' + M^{-1}C\bar{u}' + M^{-1}K \bar{u} = M^{-1}F(t)$.
-Using the theory of linear differential equations, a unique solution for Problem ODE can be found.
-This proves Proposition 1.\\
-
-Proposition 2 provides a link between the solution of Problem ODE and the solution of Problem GVar$^h$.
 
@@
 
+Since the set $\{\phi_1, \ \phi_2,...,\phi_n\}$ forms a linearly independent basis for $S^h$, the bilinear form $c$ is positive definite on $S^h$.
+Consequently, the matrix $M$ is invertible.
+The equation \eqref{ODE} can therefore be rewritten as $\bar{u}'' + M^{-1}C\bar{u}' + M^{-1}K \bar{u} = M^{-1}F(t)$.
+Using the theory of linear differential equations, a unique solution for Problem ODE can be found, proving Proposition 1.
+
+Proposition 2 provides a link between the solution of Problem ODE and the solution of Problem GVar$^h$.
+
 \subsection{Error estimates}\label{e_est}
 Given that the assumptions \textbf{A1}-\textbf{A4} of Section 2 is satisfied, and $f$ is continuous, there exists unique solutions for  Problem GVar and Problem GVar$^h$.
-It remains only to show that the solution of Problem GVar$^h$ denoted by $u^h$ converges to the solution of Problem GVar denoted by $u$ as $h$ is decreased.\\
+It remains only to show that the solution of Problem GVar$^h$ denoted by $u^h$ converges to the solution of Problem GVar denoted by $u$.
 
-Suppose $u$ is a solution of Problem GVar and $u^h$ is a solution of Problem GVar$^h$. Define the error $e^h$ by
-\begin{eqnarray*}
-	e^h(t) = u(t) - u^h(t).
-\end{eqnarray*}
+Let $u$ be the solution of Problem GVar and $u^h$ be the solution of Problem GVar$^h$. The authors of \cite{BV13} define the following error,
+
+\begin{eqnarray}
+	e^h(t) = u(t) - u^h(t). \label{Error}
+\end{eqnarray}
 

### 2023-04-26 files/Chapter4/ModalAnalysisTimo.tex
Chapter 3

@@
 An example of modal analysis on a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}.
-In this section, more general theory for modal analysis of te Timoshenko beam theory is discuss, as well as some more examples of the application of the theory.
+In this chapter, more general theory for modal analysis of te Timoshenko beam theory is discussed, as well as some more examples of the application of the theory.
+
 \section{Eigenvalue problem}\label{sec:Timo:EigenvalueProblem}
@@
 
+\textcolor{red}{*****************SUGGESTION****************************}
+
+\subsubsection*{Stragety for determining the eigenvalues and eigenvectors}
+
+The authors of \cite{VV06} provide a detailed example of the application of the above strategy to for determining the eigenvalues and eigenvectors.
+The example used is a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}.
+
+The strategy can be summarized as follows:
+
+From the general solutions for $u$ and $\phi$, the eigenvalues and eigenfunctions can be determined by imposing the boundary conditions at $x=0$ to reduce the solution space of four dimensions to a solution space of dimension at least two.
+
+The boundary condition at $x=1$ is then substituted which results in a homogeneous system of linear equations of the form
+\begin{eqnarray*}
+A \bar{b} = \bar{0}.
+\end{eqnarray*}
+
+This system either has the zero solution or infinitely many solutions.
+To ensure the zero solution, the determinant of the matrix $A$ is set to zero.
+This equation $\textrm{det}(A) = 0$ is called the frequency equation.
+
+The frequency equation has infinitely many solutions.
+Each of the solutions corresponds to a eigenvalue with a unique vector $\bar{b}$.
+The eigefunctions can then be obtained by substituting the vector $\bar{b}$ into the general solution for $u$ and $\phi$.
+
+\subsubsection*{Pinned-pinned beam}
+
+Returning back to the example of the pinned-pinned beam, we present some of the results from \cite{VV06}:
+
+For $\lambda < \alpha$ the general solution reduces to $\langle u(x) , \phi(x) \rangle = \langle \sin(k \pi x), A_k \cos(k \pi x) \rangle$.
+
+For $\lambda = \alpha$, the general solution reduces to $\langle u(x) , \phi(x) \rangle = \langle 0, 1 \rangle$.
+
+For $\lambda > \alpha$, the general solution also reduces to $\langle u(x) , \phi(x) \rangle = \langle \sin(k \pi x), A_k  \cos(k \pi x) \rangle$.
+
+A rigourous proof of the above results can be found in \cite{VV06}. These results also prove the Theorem 1 presented in section \ref{subsec:Timoshenko_Modal_Analsis}.
+
+\textcolor{red}{*****************OLD alles onder moontlik weg vat****************************}
+
 The next step is to determine the solution of the general eigenvalue problem.
@@
 
-From the general solutions for $u$ and $\phi$, the eigenvalues and eigenfunctions can be determined by imposing the boundary conditions of the model problem.
-The boundary conditions at $x=0$ reduces the solution space of four dimensions to a solution space of dimension at least two.
-The boundary condition at $x=1$ is then substituted which results in a homogeneous system of linear equations.
+From the general solutions for $u$ and $\phi$, the eigenvalues and eigenfunctions can be determined by imposing the boundary conditions at $x=0$ to reduce the solution space of four dimensions to a solution space of dimension at least two.
+
+The boundary conditions at $x=1$ is then substituted which results in a homogeneous system of linear equations of the form
 \begin{eqnarray*}
@@
 \end{eqnarray*}
+This system either has the zero
 

### 2023-04-28 files/Chapter2/generalvibrationmodel.tex
Saving model

@@
 
-Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions as given in \cite{CVV18}:
+Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
 \begin{flalign}
-	T_n(t) &= e^{-r_nt}\left[ A_n \cos(\omega_n t) + B_n \sin(\omega_n t) \right] \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
-	T_n(t) &= e^{-r_nt}\left[ A_n + B_n t \right] \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
-	T_n(t) &= e^{-r_nt}\left[ A_n \cosh(\mu_n t) + B_n \sinh(\mu_n t) \right] \quad \textrm{ if } \lambda < 0. \label{lambda_3}
+	T_n(t) &=  A_n \cos(\omega_n t) + B_n \sin(\omega_n t) \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
+	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
+	T_n(t) &=  A_n \cosh(\mu_n t) + B_n \sinh(\mu_n t) \quad \textrm{ if } \lambda < 0. \label{lambda_3}
 \end{flalign}
-
-From assumptions \textbf{A2} and \textbf{A3}, the bilinear forms $b$ and $c$ are positive definite.
-And since we assumed that there is no damping ($a=0$), $\lambda$ cannot be negative.
-Therefore, the only possible solutions for $T_n(t)$ is \eqref{lambda_1} and \eqref{lambda_2}.
 

### 2023-04-30 files/Chapter2/generalvibrationmodel.tex
Chapter 2.4.2 and 4.2

@@
 And to understand how modal analysis is applied, a Timoshenko beam is used as an example.
-Specifically, Problem T-1 as it is easy to illustrate the idea of modal analysis.
+Specifically, Problem T-1 as the boundary conditions makes it easy to illustrate the idea of modal analysis.
+A systematic approach to modal analysis for the Timoshenko beam theory is discussed in Chapter 4.
 
@@
 Solutions to Problem T-1E is a pair of functions $\langle \tilde{w}, \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$.
-Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are possible solutions of the differential equations and satisfy the boundary conditions.
+Substitution  that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are possible solutions of the differential equations and satisfy the boundary conditions.
 
-Due to this periodicity of these solutions for the eigenvalue problem Problem T-1E, it has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
-The vector $\langle 0, 1 \rangle$ also satisfies the eigenvalue problem with boundary conditions.
+Due to the periodicity of these solutions, the eigenvalue problem has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
+Another solution is the vector $\langle 0, 1 \rangle$ which also satisfies the eigenvalue problem with boundary conditions.
 This solution is called the constant solution.
@@
 A systematic approach to obtain the eigenvalues and eigenfunctions is given in \cite{VV06}.
-This is discussed in in Section 4.2.
-From \cite{VV06}, the following theorem can be derived and confirms the validity of our trial solutions for the eigenvalue problem.
+This is discussed in more detail in Section \ref{sec:Timo:EigenvalueProblem}.
+To verify the trial solutions for Problem T-1E, the following theorem can be derived from \cite{VV06}.
 
@@
 
-\textcolor{red}{**************OLD VERSION******************}
-
-\sout{It is well known} that the eigenvalue problem like Problem T-1E has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
-For the pinned-pinned beam (Problem T-1), $\lambda_n > 0$ for all $n > 0$ (this is also true for Problem T-2 and Problem T-4).
-A convenient reference is \cite{VV06}.
-
-The eigenvalues for the pinned-pinned beam model is the first example in \cite{VV06}.
-In this dissertation, the pinned-pinned model problem is referred to as Problem T-1 (eigenvalue problem Problem T-1E).
-Obviously, since $\langle 0 \ 1\rangle$ satisfies the boundary conditions, it is an eigenfunction with corresponding eigenvalue $\alpha$.
-In \cite{VV06} the authors proved the following theorem.
-
-\newtheorem{ThmVV06_2}{Theorem}
-\begin{ThmVV06_2}
-	If $\langle u \ \phi\rangle$ is a nonconstant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions.
-$A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$.
-Also all eigenvalues less than $\alpha$ are simple eigenvalues.
-\end{ThmVV06_2}
-
-\textcolor{red}{********************************}
+\begin{proof}
+	See Section 4.2.
+\end{proof}
 
@@
 
+\textcolor{red}{**************OLD VERSION******************}
+
+\sout{It is well known} that the eigenvalue problem like Problem T-1E has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
+For the pinned-pinned beam (Problem T-1), $\lambda_n > 0$ for all $n > 0$ (this is also true for Problem T-2 and Problem T-4).
+A convenient reference is \cite{VV06}.
+
+The eigenvalues for the pinned-pinned beam model is the first example in \cite{VV06}.
+In this dissertation, the pinned-pinned model problem is referred to as Problem T-1 (eigenvalue problem Problem T-1E).
+Obviously, since $\langle 0 \ 1\rangle$ satisfies the boundary conditions, it is an eigenfunction with corresponding eigenvalue $\alpha$.
+In \cite{VV06} the authors proved the following theorem.
+
+\newtheorem{ThmVV06_2}{Theorem}
+\begin{ThmVV06_2}
+	If $\langle u \ \phi\rangle$ is a nonconstant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions.
+$A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$.
+Also all eigenvalues less than $\alpha$ are simple eigenvalues.
+\end{ThmVV06_2}
+
+\textcolor{red}{********************************}
+
 \subsection{General vibration problem new}
@@
 The discussion will refer to the article \cite{CVV18}.
+In this article, the authors take damping into consideration, which is not covered in this dissertation.
 Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}.
-The authors of \cite{CVV18} do take damping into consideration, which is not covered in this dissertation.
 Assume there is no damping and no forcing.
@@
 \begin{flalign}
-	T_n(t) &=  A_n \cos(\omega_n t) + B_n \sin(\omega_n t) \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
+	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
 	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
-	T_n(t) &=  A_n \cosh(\mu_n t) + B_n \sinh(\mu_n t) \quad \textrm{ if } \lambda < 0. \label{lambda_3}
+	T_n(t) &=  A_n \cosh(\sqrt{-\lambda_n} t) + B_n \sinh(\sqrt{-\lambda_n} t) \quad \textrm{ if } \lambda < 0. \label{lambda_3}
 \end{flalign}

### 2023-05-07 files/Chapter2/generalvibrationmodel.tex
Some local chamges

@@
 Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$?
-To answer this question, consider the article \cite{CVV18}.
+To answer this question, we refer to the article \cite{CVV18}.
+
+In article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ a function $u$ given by
+\begin{eqnarray}
+	\mathcal{E} (t) = \frac{1}{2} b(u(t), u(t)) + \frac{1}{2} c(u'(t), u'(t)). \label{eq:1D_Model:ModalAnalysisEnergy}
+\end{eqnarray}
+
+The authors also prove that for all $t>0$, $\mathcal{E}(t) \leq \mathcal{E}(0)$.
 
@@
 
-In \cite{CVV18}, the validity of the series solution is proved using the energy norms, where the energy $\mathcal{E}$ a function $u$ given by
-\begin{eqnarray}
-	\mathcal{E} (t) = \frac{1}{2} b(u(t), u(t)) + \frac{1}{2} c(u'(t), u'(t)). \label{eq:1D_Model:ModalAnalysisEnergy}
-\end{eqnarray}
+Substitution shows that these partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions to Problem GVar.
 
-The partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions to Problem GVar.
-
-In \cite{CVV18}, a error function is defined $u^E_N = u - u^N$. Following the initial conditions, $u^E_N = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.
+The authors then define an error function $u^E_N = u - u^N$.
+Since both $u$ and $u^N$ satisfies Problem GVar, so does this error function with the following the initial conditions, $u^E_N(0) = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.
 
 Let $\mathcal{E}$ denote the energy of the error function $u^E_N$.
-In \cite{CVV18} it is proven that $\mathcal{E}(t) \leq \mathcal{E}(0)$.
-Using this inequality it follows that, \[||u(t) -  u^N(t)||_V^2 + ||u'(t) - (u^N)'(t)||^2_W \leq ||u_0 - u^N_0||_V^2 + ||u_1 - u^N_1||_W^2.
+Since $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ it follows that, \[||u(t) -  u^N(t)||_V^2 + ||u'(t) - (u^N)'(t)||^2_W \leq ||u_0 - u^N_0||_V^2 + ||u_1 - u^N_1||_W^2.
 \]
 
-The authors of \cite{CVV18} prove that $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$.
+The authors of \cite{CVV18} prove that both $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$.
 Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$.
@@
 \subsubsection{Comparison of models}
+
 In this dissertation, we are trying to compare different models for use in applications.
-Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.\\
+Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.
 
 The validity of the formal series solution with initial conditions is required to investigate the vibration of the models.
-This ensured that if the models are disturbed in the exact same way, the formal series solution is valid, and therefore the comparison can be made.
+This ensured that if the models are disturbed in the exact same way, the formal series solution remains valid, and a fair comparison can be made.
 

### 2023-05-07 files/Chapter4/ModalAnalysisTimo.tex
Some local chamges

@@
 
-\textcolor{red}{Die moet net op die regte plek gesit word.}
-
-\textcolor{red}{**********************************************}
-
-In \cite{VV06}, the steps are explained using the example of a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}.
-The authors  For $\lambda < \alpha$ the general solution reduces to $\langle u(x) , \phi(x) \rangle = \langle \sin(k \pi x), A_k \cos(k \pi x) \rangle$.
-For $\lambda > \alpha$, the general solution also reduces to $\langle u(x) , \phi(x) \rangle = \langle \sin(k \pi x), A_k  \cos(k \pi x) \rangle$.
-For $\lambda = \alpha$, the general solution reduces to $\langle u(x) , \phi(x) \rangle = \langle 0, 1 \rangle$.
-
-This is proved rigourously in \cite{VV06} and also proves Theorem 1 in section \ref{subsec:Timoshenko_Modal_Analsis}.
-
-\textcolor{red}{**********************************************}
-
 The following two sections provide examples of this strategy applied to beam models. These examples are also in \cite{VV06}.

### 2023-05-07 files/Chapter2/generalvibrationmodel.tex
local changes

--- 2023-04-30 files/Chapter2/generalvibrationmodel.tex
@@
 
-\textcolor{red}{**************OLD VERSION******************}
-
-\sout{It is well known} that the eigenvalue problem like Problem T-1E has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
-For the pinned-pinned beam (Problem T-1), $\lambda_n > 0$ for all $n > 0$ (this is also true for Problem T-2 and Problem T-4).
-A convenient reference is \cite{VV06}.
-
-The eigenvalues for the pinned-pinned beam model is the first example in \cite{VV06}.
-In this dissertation, the pinned-pinned model problem is referred to as Problem T-1 (eigenvalue problem Problem T-1E).
-Obviously, since $\langle 0 \ 1\rangle$ satisfies the boundary conditions, it is an eigenfunction with corresponding eigenvalue $\alpha$.
-In \cite{VV06} the authors proved the following theorem.
-
-\newtheorem{ThmVV06_2}{Theorem}
-\begin{ThmVV06_2}
-	If $\langle u \ \phi\rangle$ is a nonconstant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions.
-$A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$.
-Also all eigenvalues less than $\alpha$ are simple eigenvalues.
-\end{ThmVV06_2}
-
-\textcolor{red}{********************************}
-
 \subsection{General vibration problem new}
@@
 In this article, the authors take damping into consideration, which is not covered in this dissertation.
-Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}.
-Assume there is no damping and no forcing.
+
+Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. Assume there is no damping and no forcing.
 
@@
 \begin{flalign}
-	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
-	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
-	T_n(t) &=  A_n \cosh(\sqrt{-\lambda_n} t) + B_n \sinh(\sqrt{-\lambda_n} t) \quad \textrm{ if } \lambda < 0. \label{lambda_3}
+	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda_n > 0, \label{lambda_1}\\
+	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda_n = 0, \label{lambda_2}\\
+	T_n(t) &=  A_n \cosh(\sqrt{-\lambda_n} t) + B_n \sinh(\sqrt{-\lambda_n} t) \quad \textrm{ if } \lambda_n < 0. \label{lambda_3}
 \end{flalign}
@@
 
-\textcolor{red}{****************OLD*************}
+\end{document}
 
-Hele dissertation gaan oor comparison of models.
+\textcolor{red}{Voorstel:}\\
+\textcolor{red}{*********************}\\
+Using these complete product spaces, \eqref{def_of_u} and the variational form \eqref{var_form_timo} defined in Section \ref{ssec:1D_Model:VariationalForm}, the weak variational form for the cantilever Timoshenko beam is defined as Problem T-2W.\\
+\textcolor{red}{*********************}
 
-In a later chapter of this dissertation, different dimensional models are compared with each other.
-Since the formal series solution is a linear combination of eigenvalues and eigenfunctions, it is only required to compare the eigenvalues and eigenfunctions of the different models.\\
+\begin{proof}
+	Suppose $f,g \in \mathbb{R}[a,b]$. Then
+	\begin{eqnarray}
+		\left| \int_a^b fg \right| & \leq & ||f||\ ||g|| \ \ \ \ \textrm{ by Cauchy-Swartz Inequality.} \label{CSI}
+	\end{eqnarray}
 
-Using the results of this subsection, it can be shown that for specific initial conditions, the formal series solution is valid for the different models.
-So if the two models are disturbed in the exact same way, the formal series solution is valid for b
+	Suppose that $x^*$ is the zero of $u$ on the interval $[a,b]$. Then since $u \in C^1[0,1]$, by the Fundamental Theorem of Calculus
+	\begin{eqnarray*}
+		u(x) = \int_{x^*}^x u' \ \ \ \ \textrm{or} \ \ \ \ \ u(x) = -\int^{x^*}_x u'
+	\end{eqnarray*}
+
+	So by \eqref{CSI} with $g = 1$, it follows that $|u(x)| \leq ||u'||\sqrt{b-a}$. So it is clear that $||u'||\sqrt{b-a}$ is an upper bound for $|u|$, hence
+	\begin{eqnarray}
+		||u||_{\sup} \leq ||u'||\sqrt{b-a} \label{sup}
+	\end{eqnarray}
+
+	It is easy to show that $||u|| \leq \sqrt{b-a} ||u||_{\sup}$. It then follows from \eqref{sup} that $||u|| \leq (b-a) ||u'||$.
+\end{proof}
 
@@
 
+\textcolor{red}{****************OLD*************}
+
+Hele dissertation gaan oor comparison of models.
+
+In a later chapter of this dissertation, different dimensional models are compared with each other.
+Since the formal series solution is a linear combination of eigenvalues and eigenfunctions, it is only required to compare the eigenvalues and eigenfunctions of the different models.\\
+
+Using the results of this subsection, it can be shown that for specific initial conditions, the formal series solution is valid for the different models.
+So if the two models are disturbed in the exact same way, the formal series solution is valid for b
+
 \subsubsection{Comparison of models}
@@
 
-\end{document}
+\textcolor{red}{**************OLD VERSION******************}
 
-\textcolor{red}{Voorstel:}\\
-\textcolor{red}{*********************}\\
-Using these complete product spaces, \eqref{def_of_u} and the variational form \eqref{var_form_timo} defined in Section \ref{ssec:1D_Model:VariationalForm}, the weak variational form for the cantilever Timoshenko beam is defined as Problem T-2W.\\
-\textcolor{red}{*********************}
+\sout{It is well known} that the eigenvalue problem like Problem T-1E has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
+For the pinned-pinned beam (Problem T-1), $\lambda_n > 0$ for all $n > 0$ (this is also true for Problem T-2 and Problem T-4).
+A convenient reference is \cite{VV06}.
 
-\begin{proof}
-	Suppose $f,g \in \mathbb{R}[a,b]$. Then
-	\begin{eqnarray}
-		\left| \int_a^b fg \right| & \leq & ||f||\ ||g|| \ \ \ \ \textrm{ by Cauchy-Swartz Inequality.} \label{CSI}
-	\end{eqnarray}
+The eigenvalues for the pinned-pinned beam model is the first example in \cite{VV06}.
+In this dissertation, the pinned-pinned model problem is referred to as Problem T-1 (eigenvalue problem Problem T-1E).
+Obviously, since $\langle 0 \ 1\rangle$ satisfies the boundary conditions, it is an eigenfunction with corresponding eigenvalue $\alpha$.
+In \cite{VV06} the authors proved the following theorem.
 
-	Suppose that $x^*$ is the zero of $u$ on the interval $[a,b]$. Then since $u \in C^1[0,1]$, by the Fundamental Theorem of Calculus
-	\begin{eqnarray*}
-		u(x) = \int_{x^*}^x u' \ \ \ \ \textrm{or} \ \ \ \ \ u(x) = -\int^{x^*}_x u'
-	\end{eqnarray*}
+\newtheorem{ThmVV06_2}{Theorem}
+\begin{ThmVV06_2}
+	If $\langle u \ \phi\rangle$ is a nonconstant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions.
+$A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$.
+Also all eigenvalues less than $\alpha$ are simple eigenvalues.
+\end{ThmVV06_2}
 
-	So by \eqref{CSI} with $g = 1$, it follows that $|u(x)| \leq ||u'||\sqrt{b-a}$. So it is clear that $||u'||\sqrt{b-a}$ is an upper bound for $|u|$, hence
-	\begin{eqnarray}
-		||u||_{\sup} \leq ||u'||\sqrt{b-a} \label{sup}
-	\end{eqnarray}
-
-	It is easy to show that $||u|| \leq \sqrt{b-a} ||u||_{\sup}$. It then follows from \eqref{sup} that $||u|| \leq (b-a) ||u'||$.
-\end{proof}
+\textcolor{red}{********************************}

### 2023-05-11 files/Chapter2/generalvibrationmodel.tex
fixed chapter 2

--- 2023-05-07 files/Chapter2/generalvibrationmodel.tex
@@
 Specifically, Problem T-1 as the boundary conditions makes it easy to illustrate the idea of modal analysis.
-A systematic approach to modal analysis for the Timoshenko beam theory is discussed in Chapter 4.
+A detailed approach to modal analysis for the Timoshenko beam theory is discussed in Chapter 4.
 
-Consider the partial differential equations of a pinned-pinned Timoshenko beam (obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}):
+Consider the partial differential equations of a pinned-pinned Timoshenko beam, obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}:
 \begin{eqnarray}
@@
 
-\textcolor{red}{**************OLD VERSION******************}
-
-\sout{It is well known} that the eigenvalue problem like Problem T-1E has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
-For the pinned-pinned beam (Problem T-1), $\lambda_n > 0$ for all $n > 0$ (this is also true for Problem T-2 and Problem T-4).
-A convenient reference is \cite{VV06}.
-
-The eigenvalues for the pinned-pinned beam model is the first example in \cite{VV06}.
-In this dissertation, the pinned-pinned model problem is referred to as Problem T-1 (eigenvalue problem Problem T-1E).
-Obviously, since $\langle 0 \ 1\rangle$ satisfies the boundary conditions, it is an eigenfunction with corresponding eigenvalue $\alpha$.
-In \cite{VV06} the authors proved the following theorem.
-
-\newtheorem{ThmVV06_2}{Theorem}
-\begin{ThmVV06_2}
-	If $\langle u \ \phi\rangle$ is a nonconstant eigenfunction of Problem T-1E, then $\langle u \ \phi\rangle = \langle\sin k \pi x \ A_k \cos k \pi x\rangle$ which satisfies the boundary conditions.
-$A_k$ is a constant depending on the integer $k$ and the eigenvalue $\lambda_k$.
-Also all eigenvalues less than $\alpha$ are simple eigenvalues.
-\end{ThmVV06_2}
-
-\textcolor{red}{********************************}
-
-\subsection{General vibration problem new}
+\subsection{General vibration problem}
 This section is a discussion of a general vibration problem.
@@
 
-Therefore $\frac{T''(t)}{T(t)}$ must be a constant.
-Suppose that $\frac{T''(t)}{T(t)} = -\lambda$.
+Therefore $\displaystyle -\frac{T''(t)}{T(t)}$ must be a non-negative constant.
+Suppose that $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$.
 The existence of such a $\lambda$ is uncertain at this point.
@@
 \begin{eqnarray*}
-	u = \sum_{i=1}^{\infty} a_i x_i. = \sum_{i=1}^{\infty} c(u, x_i)x_i
+	u = \sum_{i=1}^{\infty} a_i x_i. = \sum_{i=1}^{\infty} c(u, x_i)x_i.
 \end{eqnarray*}
@@
 \begin{flalign}
-	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
-	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
-	T_n(t) &=  A_n \cosh(\sqrt{-\lambda_n} t) + B_n \sinh(\sqrt{-\lambda_n} t) \quad \textrm{ if } \lambda < 0. \label{lambda_3}
+	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda_n > 0, \label{lambda_1}\\
+	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda_n = 0. \label{lambda_2}
 \end{flalign}
@@
 Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$?
-To answer this question, we refer to the article \cite{CVV18}.
+To answer this question, we can again refer to the article \cite{CVV18}.
 
@@
 In this dissertation, we are trying to compare different models for use in applications.
+These comparisons are made in Chapter 4 and 6.
 Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.

### 2023-05-15 files/Chapter3/dynamicconvergence.tex
Chapter 2.4.2 and 4.2
Chapter 7

@@
 \subsection{Error estimates}\label{e_est}
-Given that the assumptions \textbf{A1}-\textbf{A4} of Section 2 is satisfied, and $f$ is continuous, there exists unique solutions for  Problem GVar and Problem GVar$^h$.
-It remains only to show that the solution of Problem GVar$^h$ denoted by $u^h$ converges to the solution of Problem GVar denoted by $u$.
+Under the assumptions \textbf{A1}-\textbf{A4} of Section 2 and continuity of $f$, there exists unique solutions for Problem GVar and Problem GVar$^h$.
+The next step is to show that the solution of Problem GVar$^h$ converges to the solution of Problem GVar.
+This is proven the main result of \cite{BV13}.
 
@@
 
-The authors of \cite{BV13} use interpolation theory to determine the error $e_p$.
-However to obtain an error estimate for $e$ is not trivial.
-The approach of the authors is to use Finite Element Analysis to obtain an error estimate for $e$.\\
+The authors of \cite{BV13} mention that interpolation theory can be used to determine the error $e_p$.
+However to obtain an error estimate for $e$ is not as trivial.
+This is where the authors use the Finite Element Analysis, which is used to obtain an error estimate for $e$.
 
@@
 Denote the approximation of $u_h$ on the interval $[t_{k-1}, \ t_k]$ by $u_k^h$, i.e.
-$u_h(t_k) = u_k^h$ for each $k$.\\
+$u_h(t_k) = u_k^h$ for each $k$.
 

### 2023-05-15 files/Chapter7/Beam.tex
Chapter 7

@@
 \section{Validity of the Timoshenko beam model}
+In the article \cite{LVV09}, the authors show that the Timoshenko beam theory is a feasible model to use in practical applications of beams.
+In this section, the article is studied and the results are replicated.
+
+Where \cite{LVV09} differs from most other research into the validity of the Timoshenko beam theory, is that the boundary conditions are also taken into consideration.
+
 This section is a literature study of the article \cite{LVV09}.
@@
 So a three-dimensional model would be a good approximation and better than a one-dimensional model.
-It is therefore important to validate the accuracy of a simlified theory like the Timoshenko beam theory.\\
+It is therefore important to validate the accuracy of a simlified theory like the Timoshenko beam theory.
 
@@
 The two-dimensional model is an intermediate step.\\
-
-Where \cite{LVV09} differs from most other research into the validity of the Timoshenko beam theory, is that the boundary conditions are also taken into consideration.\\
 

### 2023-05-15 files/Chapter7/Introduction.tex
Chapter 7

@@
 \section{Introduction}
-This chapter is an investigation into the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate.
-Validity in this context refer to how well the solutions compare to the solutions of more realistic higher dimensional models.\\
+This chapter is an investigation into the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate model for practical applications.
+Validity in this context refers to how well the solutions of the model compare to the solutions of more realistic higher-dimensional model.
 
@@
 
-\begin{itemize}
-	\item[-] Section 7.2: Comparison between the cantilever Timoshenko beam and cantilever two-dimensional beam.
-	\item[-] Section 7.3: Comparison between the cantilever two-dimensional beam and cantilever three-dimensional beams.
-	\item[-] Section 7.4: Comparison between the cantilever Reissner-Mindlin plate and cantilever three-dimensional plate.
-\end{itemize}
+Section 7.2 is a discussion and a verification of numerical results of the work done in \cite{LVV09} In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
+We also include some extra results for different values of the parameter $\alpha$.
 
-In Section 7.2, the work in \cite{LVV09} is discussed and the numerical results are verified.
-In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
-More results not given in  [LVV09] are also calculated, to be used in the sections following.\\
+Section 7.3 is a natural extension of the article \cite{LVV09} which is mentioned by the authors.
+In this section, the validity of the two-dimensional beam model use in Section 7.2 is investigated.
+The results of the two-dimensional beam are compared to a three-dimensional beam.
 
-Section 7.3 is a natural extension of the article \cite{LVV09}.
-In this section, the validity of a two-dimensional beam model is investigated.
-The results of the two-dimensional beam are compared to a three-dimensional beam.
-The two-dimensional beam thus serves are an intermediate step to validate the Timoshenko beam model.\\
+The two-dimensional beam is an intermediate step to validate the Timoshenko beam model.
+A direct comparison between the one and three dimensional would be preferred, but the authors of \cite{LVV09} mention that this will introduce complexities, which will be discussed in more detail in the numerical results.
 
-Section 7.4 extends the work of \cite{LVV09} to plate models. Specifically a comparison of a cantilever two-dimensional Reissner-Mindlin plate to a cantilever three-dimensional plate.\\
+Section 7.4 extends the work of \cite{LVV09} further to plate models. Specifically a comparison of a cantilever two-dimensional Reissner-Mindlin plate to a cantilever three-dimensional plate.
 
@@
 
+\subsubsection{Global Parameters}
+The models in this Chapter (and this dissertation) assume the use of an identical isotropic material with, a rectangular cross-section.
+These are defined in global parameters shared by all the models.
+The parameters are as follows:
+
+\begin{itemize}
+    \item Elastic modulus ($G$): This is calculated using the formula $G = \frac{E}{2(1+\nu)}$, where $E$ is the modulus of elasticity and $\nu$ is Poisson's ratio.
+
+    \item Shear correction factor ($\kappa^2$): This is set to $5/6$, which is common for rectangular cross-sections.
+
+    \item Poisson's ratio ($\nu$): This is set to $0.3$, a typical value for materials like steel used in engineering.
+\end{itemize}
+
+The consistent use of these parameters across all models helps to ensure that any differences in the results can be attributed to the model structures themselves, rather than variations in the material or geometric properties.
 \end{document}

### 2023-06-25 files/Chapter1/1DModel.tex
Overview v1
Veranderinge 10-06

@@
 
-\subsection{Equations of motion and constitutive equations}\label{ssec:1D_Model:EquationsOfMotion+ConstitutiveEquation}
-In this section we introduce the Timoshenko beam theory for the transverse vibration of a uniform beam. For a reference of the model, \cite{Inm94} and \cite{Fu65} were used.\\
+    \subsection{Equations of motion and constitutive equations}\label{subsec:equationsofmotion+constitutiveequation}
+    In this section we introduce the Timoshenko beam theory for the transverse vibration of a uniform beam.
+    For a reference of the model~\cite{Inm94}, and~\cite{Fu65} were used.\\
 
-Consider a beam defined on the interval $[0,\ell]$. Let $w$ represent the transverse displacement and $\phi$ a rotation of the cross-sections of the beam.
+    Consider a beam defined on the interval $[0,\ell]$.
+    Let $w$ represent the transverse displacement and $\phi$ a rotation of the cross-sections of the beam.
 
     \subsubsection*{Equations of motion}\label{sssec:1D_Model:EquationOfMotion}
-\begin{eqnarray}
+    \begin{align}
         \rho A \partial_t^2 w &=& \partial_x V + Q, \label{eq:1D_Model:EquationOfMotion1}\\
         \rho I\partial_t^2 \phi  &=& V + \partial_x M. \label{eq:1D_Model:EquationOfMotion2}
-\end{eqnarray}
-In \eqref{eq:1D_Model:EquationOfMotion1} and \eqref{eq:1D_Model:EquationOfMotion2} $\rho$ denotes the density, $A$ is the area of a cross section, $I$ is the area moment of inertia, $M$ is the moment, $V$ is the shear force and $Q$ is an external force acting on the beam.
+    \end{align}
+    In~\eqref{eq:1D_Model:EquationOfMotion1} and \eqref{eq:1D_Model:EquationOfMotion2} $\rho$ denotes the density, $A$ is the area of a cross section, $I$ is the area moment of inertia, $M$ is the moment, $V$ is the shear force and $Q$ is an external force acting on the beam.
 
@@
     \end{eqnarray}
+
     \subsubsection{Function spaces}\label{sssec:1D_Model:FunctionSpace}
@@
     \begin{eqnarray}
-	(f,g) &=& \int_{0}^1 fg \label{eq:1D_Model:Bilinear_int}
+    (f,g)
+        &=& \int_{0}^1 fg \label{eq:1D_Model:Bilinear_int}
     \end{eqnarray} for all $f,g \in L^2(0,1).$\\
@@
 See the appendix for more information.\\
-
-\textcolor{red}{***********Maak seker L2 is in die appendix!.}\\
 

### 2023-06-25 files/Chapter2/generalvibrationmodel.tex
Veranderinge 10-06

@@
 The test functions $T[0,1]$ do not form a complete space.
-Let $V(0,1)$ be the closure of {$F_1(0,1)$} in $H^1(0,1)$.
-The product space {$V(0,1)\times V(0,1)$} is denoted by $V$ and is complete.
+Let $V(0,1)$ be the closure of {$F_1(0,1)$} in $H^1(0,1)$ (see Section 1.4.4).
+It follows that $V(0,1)$ is complete and the product space {$V(0,1)\times V(0,1)$} denoted by $V$ is complete.
 It is called the energy space.\\
@@
 
-Let $a$, $b$ and $c$ be bilinear forms where $a$ and $b$ are defined on $V$ and $c$ is defined on $W$. For the models in this dissertation, the bilinear form $b$ is symmetric.
+Let $a$, $b$ and $c$ be bilinear forms where $a$ and $b$ are defined on $V$ and $c$ is defined on $W$.
+For the models in this dissertation, the bilinear forms $b$ and $c$ are symmetric.
+Furthermore, $b(\cdot, \cdot) = (\cdot, \cdot)_V$ and $c(\cdot, \cdot) = (\cdot, \cdot)_W$.
 
@@
 
-	\item[] \textbf{A2} - There exists a positive constant $C_{W}$ such that $\Vert w\Vert_{X} \leq C_{W}\Vert w\Vert_{W}$ for each $ w\in W$ and $c(\cdot,\ \cdot) =(\cdot,\ \cdot)_{W}$.
+	\item[] \textbf{A2} - There exists a positive constant $C_{W}$ such that $\Vert w\Vert_{X} \leq C_{W}\Vert w\Vert_{W}$ for each $ w\in W$.
 
-	\item[] \textbf{A3} - There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$ and $b(\cdot,\ \cdot) =(\cdot,\ \cdot)_{V}$.
+	\item[] \textbf{A3} - There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
 
@@
 In \cite{VV02} the authors consider a special case of weak damping.
-Define a space $E_b \subset V$ where \[ E_b = \left\{x \in V \ | \ \textrm{there exists a } y \in W \textrm{ such that } c(y,v) = b(x,v) \textrm{ for all } v \in V\right\}.\] It is proved in \cite{VV02}  that $D(A) = E_b \times V$.
-Consequently if $u_1 \in V$ and $u_0 \in E_b$ the pair $u_0$, $u_1$ is admissible.
+Define a space $E_b \subset V$ where \[ E_b = \left\{x \in V \ | \ \textrm{there exists a } y \in W \textrm{ such that } c(y,v) = b(x,v) \textrm{ for all } v \in V\right\}.\] It is proved in \cite{VV02}  that condition (2.2.3) is satisfied if $u_1 \in V$ and $u_0 \in E_b$ (the pair $u_0$, $u_1$ is admissible).
 
@@
 
-Since $c$ is a bilinear form and by the inequality above, $c$ is a inner-product for $W$.
-The norm of $W$ can be defined as $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.
+Since $c$ is a bilinear form and by the inequality above, $c$ is an inner-product for $W$.
+The norm of $W$ is defined as $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.
 Let $C_1 = \min\left\{1, \frac{1}{\alpha}\right\}$ and $C_2 = \max\left\{1, \frac{1}{\alpha}\right\}$.
@@
 \begin{Poincare}
-	Suppose that $f \in C^1[a,b]$, and $f(0) = 0$. Then $||f|| \leq (b-a)||f'||$
+	Suppose that $f \in C^1[a,b]$, and $f(a) = 0$. Then\\ $\displaystyle ||f|| \leq (b-a)||f'||$.
 \end{Poincare}
 \begin{proof}
-	Let $f \in C^1(0,1)$ such that $f(0) = 0$. By the Fundamental Theorem of Calculus,
+	Let $f \in C^1(a,b)$ such that $f(a) = 0$. By the Fundamental Theorem of Calculus,
 	\begin{eqnarray*}
-		|f(x)| = \left|\int_0^x f'(s) \ ds\right| \leq \int_0^x |f'(s)| \ ds.
+		|f(x)| = \left|\int_a^x f'(s) \ ds\right| \leq \int_a^x |f'(s)| \ ds.
 	\end{eqnarray*}
@@
 	\begin{eqnarray*}
-		||f||_{\sup} \leq \int_0^1 |f'(s)| ds.
+		||f||_{\sup} \leq \int_a^b |f'(s)| ds.
 	\end{eqnarray*}
-	Also for $f,g \in C^1(0,1)$,
+	Also for $f,g \in C^1(a,b)$,
 	\begin{eqnarray}
@@
 \begin{Poincare_2}
-	Suppose that $f \in H^1(a,b)$, and $f(0) = 0$. Then $||f|| \leq (b-a)||f'||$.
+	Suppose that $f \in H^1(a,b)$, and $f(a) = 0$. Then $||f|| \leq (b-a)||f'||$.
 \end{Poincare_2}
 \begin{proof}
-	\textcolor{red}{Inlas 41A. Nie seker wat 41A verwys in die veranderinge nie. Kom die ander deel reg maak}
+	There exists a sequence $(g_n) \subset C^1[a,b]$ such that $||g_n -f|| \rightarrow 0$ and $||g'_n-f'||\rightarrow 0$.
+
+	Therefore $\displaystyle \frac{||f||}{||f'||} = \lim_{n\ \rightarrow \infty} \frac{||g_n||}{||g'_n||} \leq (b-a)$.
 \end{proof}
@@
 \begin{proof}
-	Let $f \in V$, then $f_1(0) = f_2(0) = 0$. Using the Corollary, and from the definition of the norm $||\cdot||_X$, the following inequality for the norm $||\cdot||_X$ can be obtained.
+	Let $f \in V$, then $f_1(0) = f_2(0) = 0$. Following from the corollary, $||f_1|| \leq ||f_1'||$ and $||f_2|| \leq ||f_2'||$. Therefore,
 	\begin{eqnarray*}
-		||f||_X^2 & \leq & ||f_1'||^2 + ||f_2'||^2 \\
-		& = & ||f_1'||^2 -||f_2||^2 + ||f_2'||^2 +||f_2||^2\\
-		& \leq & 2||f_1'-f_2||^2 + 2||f_2'||^2.
+		||f_1'|| & = & ||f_1 + f_2 - f_2||,\\
+				 & \leq & ||f_1 + f_2|| + ||f_2||.\\
+		||f_1'||^2 & \leq & 2||f_1 + f_2||^2 +||f_2'||^2.
+	\end{eqnarray*}
+
+	Hence from the definition of the norm $||\cdot||_X$, and again from the corollary,
+	\begin{eqnarray*}
+		||f||_X^2 & = & ||f_1||^2 + ||f_2||^2,\\
+				  & \leq & 2||f_1 + f_2||^2 + 2||f_2'||^2.
 	\end{eqnarray*}
@@
 
+	But we also have
 	\begin{eqnarray}
-		b(f,f) & = &   \int_0^1 (f_1'-f_2)^2 + \frac{1}{\beta}\int_0^1  (f_2')^2 \nonumber\\
-		& = & ||f_1' - f_2||^2 + \frac{1}{\beta}||f_2'||^2 \nonumber\\
-		& \geq & \min\left\{1 ,\ \frac{1}{\beta} \right\} \left( ||f_1' - f_2||^2 + ||f_2'||^2\right) \label{b}
+		b(f,f) & = &   \int_0^1 (f_1'-f_2)^2 + \frac{1}{\beta}\int_0^1  (f_2')^2, \nonumber\\
+		& = & ||f_1' - f_2||^2 + \frac{1}{\beta}||f_2'||^2, \nonumber\\
+		& \geq & \min\left\{1 ,\ \frac{1}{\beta} \right\} \left( ||f_1' - f_2||^2 + ||f_2'||^2\right). \label{b}
 	\end{eqnarray}
@@
 	\begin{eqnarray*}
-		||f||_W^2 \leq Kb(f,f)
+		||f||_W^2 \leq Kb(f,f),
 	\end{eqnarray*} for all $f \in V$.
@@
 
-Therefore $\displaystyle \frac{T''(t)}{T(t)}$ is a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. This can also be written as the following differential equation,
+Therefore $\displaystyle \frac{T''(t)}{T(t)}$ is constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. This can also be written as the following differential equation,
 \begin{eqnarray}
@@
 Solutions to Problem T-1E is a pair of functions $\langle \tilde{w}, \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$.
-Substitution  that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are possible solutions of the differential equations and satisfy the boundary conditions.
+Substitution of $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ show that they are solutions of the differential equations and satisfy the boundary conditions.
 
-Due to the periodicity of these solutions, the eigenvalue problem has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$.
-Another solution is the vector $\langle 0, 1 \rangle$ which also satisfies the eigenvalue problem with boundary conditions.
-This solution is called the constant solution.
+Clearly the eigenvalue problem has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding eigenvalues $\lambda_n$.
+Another solution is the vector $\langle \tilde{w}, \tilde{\phi} \rangle= \langle 0, 1 \rangle$ which also satisfies the eigenvalue problem with boundary conditions.
 
@@
 
-Corresponding to this sequence of eigenvalues, we have a sequence of solutions $(T_n(t))$:
+Corresponding to this sequence of eigenfunctions, we have a sequence of solutions $(T_n(t))$:
 \begin{eqnarray}
-	T_k(t)=A_n\cos(\sqrt{\lambda_n}t)+B_n\sin(\sqrt{\lambda_n}t), \label{eq:1D_Model:ModalAnalysisTn}
+	T_n(t)=A_n\cos(\sqrt{\lambda_n}t)+B_n\sin(\sqrt{\lambda_n}t), \label{eq:1D_Model:ModalAnalysisTn}
 \end{eqnarray}
@@
 \end{eqnarray*} 
-Substitution show that these solutions does indeed satisfy the differential equations \ref{eq:1D_Model:ModalPDE1} and \ref{eq:1D_Model:ModalPDE2} with the boundary conditions.
+Substitution show that these solutions does indeed satisfy the differential equations \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} with the boundary conditions.
 These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.
@@
 \subsection{General vibration problem}
-This section is a discussion of a general vibration problem.
+This section is a discussion of the general vibration problem GVar.
 The discussion will refer to the article \cite{CVV18}.
@@
 \end{eqnarray}
-with initial conditions $u(0)=u_{0}$ and $u'(0)=u_{1}$.
+with initial conditions $u_{0}$ and $u_{1}$.
 
@@
 
-Therefore $\displaystyle -\frac{T''(t)}{T(t)}$ must be a non-negative constant.
+Therefore $\displaystyle -\frac{T''(t)}{T(t)}$ must be constant.
 Suppose that $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$.
@@
 
-The article \cite{CVV18} is a convenient reference to show that the eigenvalue problem has a solution if the following assumption is satisfied:
+The article \cite{CVV18} is a convenient reference to show that the eigenvalue problem has a solution if the following assumption, aditional to \textbf{A1}, \textbf{A2}, \textbf{A3} and \textbf{A4},  is satisfied:
 
@@
 
-This assumption expands on the assumptions \textbf{A1}-\textbf{A4} already made in Section 2.2.
+(This assumption expands on the assumptions \textbf{A1}-\textbf{A4} already made in Section 2.2.)
 
-Building these assumptions, the authors of \cite{CVV18} prove that there exists a eigenvalue $\lambda$ and a corresponding eigenvector $x$ such that the eigenvalue problem has a solution.
-The authors also prove that the eigenvalues are positive, and the corresponding eigenvectors are orthogonal in $W$ (the bilinear form $c$).
-In fact it is also orthogonal with respect to the bilinear form $b$, hence
+Using these assumptions, the authors of \cite{CVV18} prove that there exists a complete orthonormal sequence of eigenvectors for the eigenvalue problem with a corresponding sequence of eigenvalues.
+These eigenvalues are positive and the orthogonality is with respect to the bilinear form $c$.
+In fact it is also orthogonal with respect to the bilinear form $b$,
 \begin{eqnarray*}
@@
 
-The sequence of eigenvalues ${\lambda_i}$ is an infinite sequence with $\lambda_n \rightarrow \infty$ as $n \rightarrow \infty$.
-The sequence of normalized eigenvectors ${x_i}$ forms an orthonormal basis in $W$, which means that the sequence is complete (or total) in $W$.
+Also the sequence of normalized eigenvectors ${x_i}$ forms an orthonormal basis in $W$ and sequence of eigenvalues ${\lambda_i}$ is an infinite sequence with $\lambda_n \rightarrow \infty$ as $n \rightarrow \infty$.
 
-Following this result, the authors explain that any $u \in V$, the eigenvector series for $u$ converges to $u$.
-These coefficients $a_i$ are generalized Fourier coefficients of $u$ with respect to the basis $x_i$.
+Following these results from \cite{CVV18}, for any $u \in V$, $\displaystyle u = \sum_{i=1}^{\infty} a_i x_i$.
+These coefficients $a_i$ are generalized Fourier coefficients of $u$ with respect to the eigenvectors $x_i$.
 Therefore, for any $u \in V$,
@@
 
-Now that the eigenvalue problem has a solution, the following ordinary differentiable equation can be considered,
+Now that the eigenvalue problem has many solutions, the following ordinary differentiable equation can be considered,
 \begin{eqnarray*}
-	T'' + \lambda T = 0. 
+	T_n'' + \lambda T_n = 0. 
 \end{eqnarray*}
 
-Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
+Since this differential equation is a simple second order differential equation, $T_n(t)$ has the following possible solutions:
 \begin{flalign}
-	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda_n > 0, \label{lambda_1}\\
-	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda_n = 0. \label{lambda_2}
+	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda_n > 0, \label{lambda_1}
 \end{flalign}
@@
 Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$?
-To answer this question, we can again refer to the article \cite{CVV18}.
+To answer this question, we again refer to the article \cite{CVV18}.
 
-In article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ a function $u$ given by
+In the article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ a function $u$ given by
 \begin{eqnarray}
@@
 \end{eqnarray}
+
+*****************Voorstel*****************************
+
+Then,
+\begin{eqnarray*}
+	\mathcal{E}'(t) & = & b(u(t), u'(t)) + c(u'(t), u''(t)),\\
+					& = & 0 \ \ \ \ \ \ \ \textrm{ following from \eqref{eq:existence:ProblemGVarHom}}. 
+\end{eqnarray*}
+
+Therfore $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$. For the case of weak damping, it can be proved that $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ which is the case of \cite{CVV18}.
+
+Denote the partial sum $u^{N}(t) = \sum_{n=1}^{N} T_{n}(t)w_n$. Let
+\begin{eqnarray*}
+	u_0^{N} = \sum_{n=1}^{N} T_n(0) w_n \ \ \textrm{ and } \ \ u_{1}^{N} =\sum_{n=1}^{N} T'_n(0) w_n.
+\end{eqnarray*}
+
+Substitution shows that these partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions to Problem GVar.
+
+The authors then define an error function $u^E_N = u - u^N$.
+Since both $u$ and $u^N$ satisfies Problem GVar, so does this error function with the following the initial conditions, $u^E_N(0) = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.
+
+Let $\mathcal{E}$ denote the energy of the error function $u^E_N$.
+Since $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$ it follows that, \[||u(t) -  u^N(t)||_V^2 + ||u'(t) - (u^N)'(t)||^2_W = ||u_0 - u^N_0||_V^2 + ||u_1 - u^N_1||_W^2.
+\]
+
+\textcolor{red}{Nie seker wat ek hier moet doen met die Fourier coefficients nie.}
+
+*****************************************************
+
+\textcolor{red}{**************** OU WEERGAWE******************************}
 
@@
 
+\textcolor{red}{**********************************************}
+
 It follows that the partial series solution converges to the solution $u$ as the initial conditions $u_0^N$ and $u_1^N$ converges to $u_0$ and $u_1$ respectively.
@@
 
-In this dissertation, we are trying to compare different models for use in applications.
+In this dissertation, the stated objectives were to compare different models for use in applications.
 These comparisons are made in Chapter 4 and 6.

### 2023-06-25 files/Chapter3/dynamicconvergence.tex
Veranderinge 10-06

@@
 \documentclass[../../main.tex]{subfiles}
+\insubfile{\AtEndDocument{\bibliography{../../references.bib}}}
+
 \begin{document}
 \section{Introduction}
-In this chapter, two important convegence results of the Finite Element Method (FEM) is discussed.
-The first result looks at the convergence of the Galerkin approximation for second order hyperbolic type problems, as presented in \cite{BV13}.
-The second result, from the textbook \cite{SF97}, examines the convergence of eigenvalues and eigenfunctions for a one-dimensional vibration problem, using the Finite Element Method.
+In this chapter, two important convergence results of the Finite Element Method
+(FEM) is discussed. The first result looks at the convergence of the Galerkin
+approximation for second order hyperbolic type problems, as presented
+in~\cite{BV13}. The second result, from the textbook~\cite{SF97}, examines the
+convergence of eigenvalues and eigenfunctions for a one-dimensional vibration
+problem, using the Finite Element Method.
 
-\section{Convergence of the Galerkin approximation}
-In the article \cite{BV13}, the authors investigate the convergence of the Galerkin approximation for second order hyperbolic type problems.
-The article \cite{BV18} extends the work of \cite{BV13} by including general damping and damping at the endpoints.
-For the models in Chapter 1, \cite{BV13} is sufficient while \cite{BV18} provides more insight and improved notation.
+\section{Convergence of the Galerkin approximation}\label{sec:convergence-of-the-galerkin-approximation}
+In the article \cite{BV13}, the authors investigate the convergence of the
+Galerkin approximation for second order hyperbolic type problems. The article
+\cite{BV18} extends the work of \cite{BV13} by including general damping and
+damping at the endpoints. For the models in Chapter 1, \cite{BV13} is
+sufficient while \cite{BV18} provides more insight and improved notation.
 
-In Section 2.2, Problem GVar is presented and identical to the problem in \cite{BV13}. The problem is repeated here for convenience.
+In Section 2.2, Problem GVar is presented and identical to the problem in
+\cite{BV13}. The problem is repeated here for convenience.
 
@@
 
-Assume that the assumptions \textbf{A1}-\textbf{A4} from Section 2.2 are satisfied ensuring that Problem GVar has a unique solution.
+Assume that the assumptions \textbf{A1}-\textbf{A4} from Section 2.2 are
+satisfied ensuring that Problem GVar has a unique solution.
 
-Before the theory of \cite{BV13} can be discussed, some preliminary work is necessary.
-The structure of this section is as follows.
-First the Galerkin approximation is for Problem GVar is derived.
-Then a equivalent system of ordinary differential equations is derived using the Finite Element Method.
-Finally, the convergence of the Galerkin approximation is discussed using the work of the article \cite{BV13}.
+Before the theory of \cite{BV13} can be discussed, some preliminary work is
+necessary. The structure of this section is as follows. First the Galerkin
+approximation is for Problem GVar is derived. Then a equivalent system of
+ordinary differential equations is derived using the Finite Element Method.
+Finally, the convergence of the Galerkin approximation is discussed using the
+work of the article \cite{BV13}.
 
-\subsection{Galerkin approximation of Problem GVar}
-Recall from Chapter 2 that $V$ is the closure of the test function space $T$ in the Hilbert space $H$.
+\subsection{Galerkin approximation of Problem GVar}\label{subsec:galerkin-approximation-of-problem-gvar}
+Recall from Chapter 2 that $V$ is the closure of the test function space $T$ in
+the Hilbert space $H$.
 
-Suppose $S^h$ is a finite n-dimensional subspace of V.
-Let $\{\phi_1, \ \phi_2,...,\phi_n\}$ be a set of linear independent basis functions such that $S^h = \textrm{span}(\{\phi_1, \phi_2, ..., \phi_n \})$ and $\phi_i \in C^{(1)}$ for all $i$.
+Suppose $S^h$ is a finite n-dimensional subspace of V. Let $\{\phi_1, \
+	\phi_2,...,\phi_n\}$ be a set of linear independent basis functions such that
+$S^h = \textrm{span}(\{\phi_1, \phi_2, ..., \phi_n \})$ and $\phi_i \in
+	C^{(1)}$ for all $i$.
 
@@
 
-If the function $f$ is continuous, then Problem GVar$^h$ is equivalent to a system of second order differential equations.
-The following theorem from \cite{BV13} proves that if $f$ is continuous, then problem Problem GVar$^h$ has a unique solution.
+If the function $f$ is continuous, then Problem GVar$^h$ is equivalent to a
+system of second order differential equations. The following theorem from
+\cite{BV13} proves that if $f$ is continuous, then problem Problem GVar$^h$ has
+a unique solution.
 
@@
 
-Using these matrices, Problem GVar$^h$ is rewritten as a system of ordinary differential equations denoted by Problem ODE.
-\subsubsection*{Problem ODE}
+Using these matrices, Problem GVar$^h$ is rewritten as a system of ordinary
+differential equations denoted by Problem ODE. \subsubsection*{Problem ODE}
 Find a function $\bar{u} \in S^h$ such that
@@
 
-Since the set $\{\phi_1, \ \phi_2,...,\phi_n\}$ forms a linearly independent basis for $S^h$, the bilinear form $c$ is positive definite on $S^h$.
-Consequently, the matrix $M$ is invertible.
-The equation \eqref{ODE} can therefore be rewritten as $\bar{u}'' + M^{-1}C\bar{u}' + M^{-1}K \bar{u} = M^{-1}F(t)$.
-Using the theory of linear differential equations, a unique solution for Problem ODE can be found, proving Proposition 1.
+Since the set $\{\phi_1, \ \phi_2,...,\phi_n\}$ forms a linearly independent
+basis for $S^h$, the bilinear form $c$ is positive definite on $S^h$.
+Consequently, the matrix $M$ is invertible. The equation \eqref{ODE} can
+therefore be rewritten as $\bar{u}'' + M^{-1}C\bar{u}' + M^{-1}K \bar{u} =
+	M^{-1}F(t)$. Using the theory of linear differential equations, a unique
+solution for Problem ODE can be found, proving Proposition 1.
 
-Proposition 2 provides a link between the solution of Problem ODE and the solution of Problem GVar$^h$.
+Proposition 2 provides a link between the solution of Problem ODE and the
+solution of Problem GVar$^h$.
 
@@
 
-Let $u$ be the solution of Problem GVar and $u^h$ be the solution of Problem GVar$^h$. The authors of \cite{BV13} define the following error,
+Let $u$ be the solution of Problem GVar and $u^h$ be the solution of Problem
+GVar$^h$. The authors of \cite{BV13} define the following error,
 
@@
 
-In \cite{BV13}, a projection $P$ is defined so that $Pu \in V$. The error is then split using this projection. Let $e(t) = Pu(t)- u_h(t)$ and $e_p(t) = u(t) - Pu(t)$ so that
+In \cite{BV13}, a projection $P$ is defined so that $Pu \in V$. The error is
+then split using this projection. Let $e(t) = Pu(t)- u_h(t)$ and $e_p(t) = u(t)
+	- Pu(t)$ so that
 \begin{eqnarray}
@@
 
-In \eqref{error_e}, the authors divide the error $e$ into a semi-discrete term and a fully discrete term. The two terms are investigated as seperate problems in \cite{BV13}.\\
+In \eqref{error_e}, the authors divide the error $e$ into a semi-discrete term
+and a fully discrete term. The two terms are investigated as seperate problems
+in \cite{BV13}.\\
 
@@
 
-The main result proving the convergence of the solution of the Galerkin Approximation is given in \cite{BV13} as follows.
+The main result proving the convergence of the solution of the Galerkin
+Approximation is given in \cite{BV13} as follows.
 
@@
 
-The parameter $\tau$ is some number in $(0,T)$. The constant $K_\alpha$ is the constant defined in assumption \textbf{A4} of Section 2.2.1.
+The parameter $\tau$ is some number in $(0,T)$. The constant $K_\alpha$ is the
+constant defined in assumption \textbf{A4} of Section 2.2.1.
 
 \subsection{Obtaining the error estimate}
-In this section we will show how the error estimate in Theorem 2 is obtained by the authors of \cite{BV13}.\\
+In this section we will show how the error estimate in Theorem 2 is obtained by
+the authors of \cite{BV13}.\\
 
@@
 
-From assumption \textbf{B1}, $Pu \in C^2(J)$ and by the definition $P$, $P$ is a projection with respect to the inner product $b$.\\
+From assumption \textbf{B1}, $Pu \in C^2(J)$ and by the definition $P$, $P$ is
+a projection with respect to the inner product $b$.\\
 
@@
 
-Using the definition of the error $e^h$ while also adding and subtracting $Pu(t)$ in the bilinear form $b$, we can write
+Using the definition of the error $e^h$ while also adding and subtracting
+$Pu(t)$ in the bilinear form $b$, we can write
 \begin{eqnarray*}
@@
 
-It then follows from the definitions of the error $e$ and the projection $P$ that
+It then follows from the definitions of the error $e$ and the projection $P$
+that
 \begin{eqnarray*}
@@
 
-Using this proposition, the authors of \cite{BV13} derive a generalized error estimate for the error $e = Pu - u_h$.
+Using this proposition, the authors of \cite{BV13} derive a generalized error
+estimate for the error $e = Pu - u_h$.
 
@@
 
-In chapter 2, it was explained that the models of this dissertation have weak damping, i.e.
-$a = 0$.
-Therefore, the error estimate in Lemma 1 can be simplified.
-This is given in \cite{BV13} as a corollary.
+In chapter 2, it was explained that the models of this dissertation have weak
+damping, i.e. $a = 0$. Therefore, the error estimate in Lemma 1 can be
+simplified. This is given in \cite{BV13} as a corollary.
 
@@
 
-From Theorem 1, it follows that the solution $u$ of Problem GVar satisfies $u \in C^1([0,T]; V) \cap C^2((0,T);V)$. \textcolor{red}{This is a weak assumption made in \cite{BV13}.}\\
+From Theorem 1, it follows that the solution $u$ of Problem GVar satisfies $u
+	\in C^1([0,T]; V) \cap C^2((0,T);V)$. \textcolor{red}{This is a weak assumption
+	made in \cite{BV13}.}\\
 
@@
 
-Let $\Pi$ denote the interpolation operator such that $u_0^h = \Pi u_0$ and $u_1^h = \Pi u_1$.
+Let $\Pi$ denote the interpolation operator such that $u_0^h = \Pi u_0$ and
+$u_1^h = \Pi u_1$.
 
@@
 \subsection{Fully discrete Galerkin finite element approximation}
-Consider the time interval $J = [0,T]$.
-Divide $J$ into $N$ steps with length $\tau = \frac{T}{N}$.
-Each interval can be expressed as $[t_{k-1}, \ t_k]$ for $k = 1,...,N$.
-Denote the approximation of $u_h$ on the interval $[t_{k-1}, \ t_k]$ by $u_k^h$, i.e.
-$u_h(t_k) = u_k^h$ for each $k$.\\
+Consider the time interval $J = [0,T]$. Divide $J$ into $N$ steps with length
+$\tau = \frac{T}{N}$. Each interval can be expressed as $[t_{k-1}, \ t_k]$ for
+$k = 1,...,N$. Denote the approximation of $u_h$ on the interval $[t_{k-1}, \
+			t_k]$ by $u_k^h$, i.e. $u_h(t_k) = u_k^h$ for each $k$.\\
 
@@
 
-From Theorem 2 of the semi-discrete problem an error estimate for $[u(t_k)-u_h(t_k)]$ with respect to the norm of $W$ was obtained.
-The authors of \cite{BV13} then proceed to obtain an error estimate for $[u_h(t_k) - u^h_k]$.
-Since the dimension of $S^h$ is not fixed, the equivalence of norms cannot be used, and therefore this error estimate for $[u_h(t_k) - u^h_k]$ should also be with respect to the norm of $W$.
+From Theorem 2 of the semi-discrete problem an error estimate for
+$[u(t_k)-u_h(t_k)]$ with respect to the norm of $W$ was obtained. The authors
+of \cite{BV13} then proceed to obtain an error estimate for $[u_h(t_k) -
+			u^h_k]$. Since the dimension of $S^h$ is not fixed, the equivalence of norms
+cannot be used, and therefore this error estimate for $[u_h(t_k) - u^h_k]$
+should also be with respect to the norm of $W$.
 
@@
 Let Problem GVar$^h$-D denote the fully discrete form of Problem GVar$^h$.
-\subsubsection*{Problem GVar$^\mathbf{{h}}$-D}
-Find a sequence $\{u_{k}^{h}\}\subset S^{h}$ such that for $k=0,1,2$, . . . , $N-1,$
+\subsubsection*{Problem GVar$^\mathbf{{h}}$-D} Find a sequence
+$\{u_{k}^{h}\}\subset S^{h}$ such that for $k=0,1,2$, . . . , $N-1,$
 \begin{eqnarray}
@@
 
-In the proof of Proposition 3, the authors of \cite{BV13} show that \eqref{PP} in Problem GVar$^h$-D can be rewritten as
+In the proof of Proposition 3, the authors of \cite{BV13} show that \eqref{PP}
+in Problem GVar$^h$-D can be rewritten as
 \begin{eqnarray}
@@
 
-Using \eqref{PPP} and the definition of the standard finite element matrices, Problem GVar$^h$-D can be reformulated into a algorithm for the Finite Element Method.
-This is the fully discrete form of Problem GVar and is represented in Problem FD.\\
+Using \eqref{PPP} and the definition of the standard finite element matrices,
+Problem GVar$^h$-D can be reformulated into a algorithm for the Finite Element
+Method. This is the fully discrete form of Problem GVar and is represented in
+Problem FD.\\
 \textcolor{red}{******************************************************}\\
 
-Further results and the standard Finite Element Matrices, let the authors of \cite{BV13} rewrite Problem GVar$^\mathbf{{h}}$-D into an algorithm for the Finite Element Method.
-This is represented as Problem FD
+Further results and the standard Finite Element Matrices, let the authors of
+\cite{BV13} rewrite Problem GVar$^\mathbf{{h}}$-D into an algorithm for the
+Finite Element Method. This is represented as Problem FD
 
@@
 
-In this form, the problem is fully discrete. This form also allow the authors of \cite{BV13} to obtain an error estimate for the fully-discrete problem.
+In this form, the problem is fully discrete. This form also allow the authors
+of \cite{BV13} to obtain an error estimate for the fully-discrete problem.
 
@@
 
-Recall that $\displaystyle \tau = \frac{T}{N}$.
-The error estimate for the term $[u_h(t_k) - u^h_k]$ with respect to the norm of $W$ as proven by the authors of \cite{BV13} is presented here as Theorem 3.
+Recall that $\displaystyle \tau = \frac{T}{N}$. The error estimate for the term
+$[u_h(t_k) - u^h_k]$ with respect to the norm of $W$ as proven by the authors
+of \cite{BV13} is presented here as Theorem 3.
 
-Finally, Theorem 2 of the semi-discrete problem and Theorem 3 of the fully discrete problem gives an error estimate for the error $e(t)$.
-Consequently, the error estimate $e^h(t) = u(t) - u^h(t)$ is obtained.
+Finally, Theorem 2 of the semi-discrete problem and Theorem 3 of the fully
+discrete problem gives an error estimate for the error $e(t)$. Consequently,
+the error estimate $e^h(t) = u(t) - u^h(t)$ is obtained.
 
@@
 
-Define the error $e_h$ as the error between the solutions of Problem GVar and Problem GVar$^h$, i.e.
+Define the error $e_h$ as the error between the solutions of Problem GVar and
+Problem GVar$^h$, i.e.
 \begin{eqnarray}
@@
 
-Since $u$ is unknown, the error $e_h$ cannot be calculated directly. Instead the authors of \cite{BV13} derive estimate for this error using projections.***  \\
+Since $u$ is unknown, the error $e_h$ cannot be calculated directly. Instead
+the authors of \cite{BV13} derive estimate for this error using projections.***
+\\
 
@@
 
-Same a \cite{BV13}, $P_h$ is renamed to $P$ for convenience. $P_h$ will be used when it is needed to differentiate between $P$ and $P_h$. Define the following errors $e_p$ and $e$ by
+Same a \cite{BV13}, $P_h$ is renamed to $P$ for convenience. $P_h$ will be used
+when it is needed to differentiate between $P$ and $P_h$. Define the following
+errors $e_p$ and $e$ by
 \begin{eqnarray*}
@@
 
-Estimates for the norm of $e_p$ is obtained in \cite{BV13} using approximation theory.
-It is only left to find an estimate for $e(t)$.
-The approach of \cite{BV13} is to estimate the error $e$ using the projection error $e_p$ and errors for the initial conditions.
+Estimates for the norm of $e_p$ is obtained in \cite{BV13} using approximation
+theory. It is only left to find an estimate for $e(t)$. The approach of
+\cite{BV13} is to estimate the error $e$ using the projection error $e_p$ and
+errors for the initial conditions.
 
@@
 
-From this Proposition in \cite{BV13} the general variational problem in terms of the errors $e_h$ and $e$.
-\newtheorem{DC_Prop1}{Proposition}
+From this Proposition in \cite{BV13} the general variational problem in terms
+of the errors $e_h$ and $e$. \newtheorem{DC_Prop1}{Proposition}
 \begin{DC_Prop1}
@@
 \subsection{Fundamental estimate}
-The authors of \cite{BV13} use the form of Proposition 1, to give a generalization of an estimate for the error $e(t)= Pu(t)- u_h(t)$.
+The authors of \cite{BV13} use the form of Proposition 1, to give a
+generalization of an estimate for the error $e(t)= Pu(t)- u_h(t)$.
 
@@
 
-Similarly, for $a = 0$ (weak damping as explained in Section 2.2), the following corollary is obtained in a similar proof to Lemma 1.
+Similarly, for $a = 0$ (weak damping as explained in Section 2.2), the
+following corollary is obtained in a similar proof to Lemma 1.
 \newtheorem{DC_Cor1}{Corollary}
@@
 Consider Problem GVar$^h$ with discretised space and continuous time variables.
-This is known as a semi-discrete problem.
-This is a natural intermediate step between a continuous and a fully discrete problem.\\
+This is known as a semi-discrete problem. This is a natural intermediate step
+between a continuous and a fully discrete problem.\\
 
@@
 
-	The result follows from Lemma 4.1 since $\Vert Pu_{0}-u_{0}^{h}\Vert_{W}\leq\Vert Pu_{0}-u_{0}\Vert+\Vert u_{0}-u_{0}^{h}\Vert.$
+	The result follows from Lemma 4.1 since $\Vert
+		Pu_{0}-u_{0}^{h}\Vert_{W}\leq\Vert Pu_{0}-u_{0}\Vert+\Vert
+		u_{0}-u_{0}^{h}\Vert.$
 \end{proof}
@@
 
-To be able to use Theorem in application, it is necessary to be able to estimate an element in $V$ with an element in $S^h$.
-Suppose $h$ is related to the dimension n of $S^h$ such that $h \rightarrow 0$ as $n \rightarrow \infty$.\\
+To be able to use Theorem in application, it is necessary to be able to
+estimate an element in $V$ with an element in $S^h$. Suppose $h$ is related to
+the dimension n of $S^h$ such that $h \rightarrow 0$ as $n \rightarrow
+	\infty$.\\
 

### 2023-07-21 Gedoen.tex
redo v1"

--- 2022-10-31 Gedoen.tex
@@
 
-\subsection{Chapter 1}
+\section{Section 2.3}
 \begin{itemize}
-	\item Het 1.4.21 reg gemaak. Moet nog deur gaan en seker maak ek het dit ander plekke reg.
+    \item[-] Page 42 - $(a+b)^2 \leq 2a^2 +2b^2$ verander na $(a+b)^2 < 2a^2 + 2b^2$
+    \item[-] Page 42 - It follows that... was display, verander na in-line en ook die volgorde was nie dieselfde nie.
+    \item[-] Page 42 - Hence het nie 'n komma gehad nie
 \end{itemize}
 
-\subsection{Chapter 2}
+\section{Section 2.4.2}
 \begin{itemize}
-	\item Het verbeteringe aangebring.
-\end{itemize}
-
-\subsection{Appendix}
-\begin{itemize}
-	\item $L_2$ in gesit.
+    \item[-] Page 48 - Problem GVar is korrek vernader na die equation ref, die woord `satisfies' het wel weg geraak. Nou terug gesit.
 \end{itemize}

### 2023-07-21 files/Chapter2/generalvibrationmodel.tex
redo v1"

@@
 Let $V(0,1)$ be the closure of {$F_1(0,1)$} in $H^1(0,1)$ (see Section 1.4.4).
-It follows that $V(0,1)$ is complete and the product space {$V(0,1)\times V(0,1)$} denoted by $V$ is complete.
+It follows that $V(0,1)$ is complete and the product space {$V(0,1)\times V(0,1)$}, denoted by $V$, is complete.
 It is called the energy space.\\
@@
 	\begin{eqnarray*}
-		||f_1'|| & = & ||f_1 + f_2 - f_2||,\\
-				 & \leq & ||f_1 + f_2|| + ||f_2||.\\
-		||f_1'||^2 & \leq & 2||f_1 + f_2||^2 +||f_2'||^2.
+		||f_1'|| & = & ||f_1' - f_2 + f_2||,\\
+				 & \leq & ||f_1' - f_2|| + ||f_2||,\\
+				 & \leq & ||f_1' - f_2|| + ||f_2'||.
 	\end{eqnarray*}
 
-	Hence from the definition of the norm $||\cdot||_X$, and again from the corollary,
+	It follows that $||f_1'||^2 \leq 2||f_1' - f_2||^2 + 2||f_2'||^2$, since $\displaystyle (a+b)^2 \leq 2a^2 + 2b^2$. Hence, from the definition of the norm $||\cdot||_X$, and again from the corollary,
 	\begin{eqnarray*}
 		||f||_X^2 & = & ||f_1||^2 + ||f_2||^2,\\
-				  & \leq & 2||f_1 + f_2||^2 + 2||f_2'||^2.
+				  & \leq & ||f_1'||^2 + ||f_2'||^2,\\
+				  & \leq & 2||f_1' - f_2||^2 + 3||f_2'||^2.
 	\end{eqnarray*}
 
-	It follow from the inequality \eqref{C} that
+	It follows from the inequality \eqref{C} that
 	\begin{eqnarray}
-		\Vert f \Vert_{W}^2 \leq 2C_2||f_1'-f_2||^2 + 2C_2||f_2'||^2. \label{f}
+		\Vert f \Vert_{W}^2 \leq 2C_2||f_1'-f_2||^2 + 3C_2||f_2'||^2. \label{f}
 	\end{eqnarray}
@@
 
-	Now combine the inequalities \eqref{f} and \eqref{b},
+	Now combine the inequalities \eqref{f} and \eqref{b}. There exists a positive constant $C_V$ such that
 	\begin{eqnarray*}
-		||f||_W^2 \leq Kb(f,f),
+		||f||_W^2 \leq C_V b(f,f),
 	\end{eqnarray*} for all $f \in V$.
@@
 Substitution show that these solutions does indeed satisfy the differential equations \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} with the boundary conditions.
-These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.
+These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (and consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.
 
@@
 \end{eqnarray}
-with initial conditions $u_{0}$ and $u_{1}$.
+with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.
 
@@
 
-*****************Voorstel*****************************
-
 Then,
@@
 
-Denote the partial sum $u^{N}(t) = \sum_{n=1}^{N} T_{n}(t)w_n$. Let
+Denote the partial sum $u^{N}(t) = \sum_{n=1}^{N} T_{n}(t)w_n$. Ideally
 \begin{eqnarray*}
-	u_0^{N} = \sum_{n=1}^{N} T_n(0) w_n \ \ \textrm{ and } \ \ u_{1}^{N} =\sum_{n=1}^{N} T'_n(0) w_n.
+	u_0^{N} = \sum_{n=1}^{N} T_n(0) w_n \ \ \textrm{ and } \ \ u_{1}^{N} =\sum_{n=1}^{N} T'_n(0) w_n,
 \end{eqnarray*}
+but $T_n$ is not uniquely defined by the differential equation.
 
-Substitution shows that these partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions to Problem GVar.
+Substitution shows that these partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions for \eqref{eq:existence:ProblemGVarHom} in Problem GVar.
 
 The authors then define an error function $u^E_N = u - u^N$.
-Since both $u$ and $u^N$ satisfies Problem GVar, so does this error function with the following the initial conditions, $u^E_N(0) = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.
+Since both $u$ and $u^N$ satisfies \eqref{eq:existence:ProblemGVarHom}, so does this error function with the following the initial conditions, $u^E_N(0) = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.
 
-Let $\mathcal{E}$ denote the energy of the error function $u^E_N$.
-Since $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$ it follows that, \[||u(t) -  u^N(t)||_V^2 + ||u'(t) - (u^N)'(t)||^2_W = ||u_0 - u^N_0||_V^2 + ||u_1 - u^N_1||_W^2.
-\]
+Let $\mathcal{E}$ denote the energy of the error function $u^E_N$. Since $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$ it follows that, 
+\begin{eqnarray}
+	||u(t) -  u^N(t)||_V^2 + ||u'(t) - (u^N)'(t)||^2_W = ||u_0 - u^N_0||_V^2 + ||u_1 - u^N_1||_W^2. \label{eq:inequality}
+\end{eqnarray}
 
-\textcolor{red}{Nie seker wat ek hier moet doen met die Fourier coefficients nie.}
+Now, $u_0$ and $u_1$ are given in Problem GVar.
+Therefore the generalized Fourier coefficients for $u_0$ and $u_1$ must be used to compute $u_0^N$ and $u_1^N$.
+These Fourier coefficients are $\displaystyle u_0^N = \sum_{n=1}^{N} b(u_0, w_n)w_n$ and $\displaystyle u_1^N = \sum_{n=1}^{N} c(u_1, w_n)w_n$.
 
-*****************************************************
+Then $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$. Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$ by \eqref{eq:inequality}.
 
-\textcolor{red}{**************** OU WEERGAWE******************************}
-
-The authors also prove that for all $t>0$, $\mathcal{E}(t) \leq \mathcal{E}(0)$.
-
-Denote the partial sum $u^{N}(t) = \sum_{n=1}^{N} T_{n}(t)w_n$. Let
-\begin{eqnarray*}
-	u_0^{N} = \sum_{n=1}^{N} A^*_n w_n \ \ \textrm{ and } \ \ u_{1}^{N} =\sum_{n=1}^{N} B^*_n w_n
-\end{eqnarray*} where $A^*_n = T_n(0)$ and $B^*_n = T'_n(0)$.
-
-Substitution shows that these partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions to Problem GVar.
-
-The authors then define an error function $u^E_N = u - u^N$.
-Since both $u$ and $u^N$ satisfies Problem GVar, so does this error function with the following the initial conditions, $u^E_N(0) = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.
-
-Let $\mathcal{E}$ denote the energy of the error function $u^E_N$.
-Since $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ it follows that, \[||u(t) -  u^N(t)||_V^2 + ||u'(t) - (u^N)'(t)||^2_W \leq ||u_0 - u^N_0||_V^2 + ||u_1 - u^N_1||_W^2.
-\]
-
-The authors of \cite{CVV18} prove that both $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$.
-Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$.
-
-\textcolor{red}{**********************************************}
-
-It follows that the partial series solution converges to the solution $u$ as the initial conditions $u_0^N$ and $u_1^N$ converges to $u_0$ and $u_1$ respectively.
+It follows that the partial sums of the series solution converges to the solution $u$ as the initial conditions $u_0^N$ and $u_1^N$ converges to $u_0$ and $u_1$ respectively.
 
@@
 Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.
+This is explained in detail in \cite{CVV18}.
 
 The validity of the formal series solution with initial conditions is required to investigate the vibration of the models.
-This ensured that if the models are disturbed in the exact same way, the formal series solution remains valid, and a fair comparison can be made.
+This ensured that if the models are disturbed in the exact same way, the formal series solution remains valid, and a comparison can be made.
 

### 2023-07-21 files/Chapter3/dynamicconvergence.tex
redo v1"

@@
 \documentclass[../../main.tex]{subfiles}
-\insubfile{\AtEndDocument{\bibliography{../../references.bib}}}
-
 \begin{document}
@@
 \subsubsection*{Problem GVar}
-Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
+Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to
+$\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
 \begin{eqnarray}
@@
 
-\subsection{Galerkin approximation of Problem GVar}\label{subsec:galerkin-approximation-of-problem-gvar}
 Recall from Chapter 2 that $V$ is the closure of the test function space $T$ in
 the Hilbert space $H$.
-
-Suppose $S^h$ is a finite n-dimensional subspace of V. Let $\{\phi_1, \
-	\phi_2,...,\phi_n\}$ be a set of linear independent basis functions such that
-$S^h = \textrm{span}(\{\phi_1, \phi_2, ..., \phi_n \})$ and $\phi_i \in
-	C^{(1)}$ for all $i$.
-
-For any function $w_h$ in $S^h$, $w_h$ can be expressed as a linear combination
-\begin{eqnarray*}
-	w_h = \sum_{j=1}^n w_j \phi_j.
-\end{eqnarray*} Define a vector valued function $\bar{w} = \langle w_1,w_2,...,w_n \rangle$ for each $w_h \in S^h$. The problem of solving the Galerkin Approximation is denoted by Problem GVar$^h$.
 
@@
 
+Let $u$ be the solution of Problem GVar and $u^h$ be the solution of Problem GVar$^h$.
+ The authors of \cite{BV13} define the following error,
 \begin{eqnarray}
@@
 \begin{eqnarray}
-	e^h(t) = e_p(t) +e(t) \label{Error}
+	e^h(t) = e_p(t) +e(t). \label{Error}
 \end{eqnarray}
 
-The authors of \cite{BV13} mention that interpolation theory can be used to determine the error $e_p$.
+According to the authors of~\cite{BV13}, interpolation theory can be used to determine the error $e_p$.
 However to obtain an error estimate for $e$ is not as trivial.
-This is where the authors use the Finite Element Analysis, which is used to obtain an error estimate for $e$.
+This is where the use of the Finite Element Analysis comes in.
+
+To simplify the proof, the problem is divided into a semi-discrete problem and a fully discrete problem.
 
@@
 \begin{eqnarray*}
-	c(e''(t),v) + a(e'(t),v) + b(u(t) - Pu(t),v) + b(Pu(t) +u_h(t),v)- = 0
+	c(e_h''(t),v) + a(e_h'(t),v) + b(u(t) - Pu(t),v) + b(Pu(t) +u_h(t),v)- = 0.
 \end{eqnarray*}
@@
 
-In \cite{BV13}, this is presented as a proposition.
+This equation \eqref{DC_E3} is presented in \cite{BV13} as a proposition.
 \newtheorem{DC_Prop1}{Proposition}
@@
 	\begin{eqnarray}
-		c(e''(t),v) + a(e'(t),v) + b(e(t),v) = 0 \ \ \ \textrm{ for all } v \in V.
+		c(e_h''(t),v) + a(e_h'(t),v) + b(e(t),v) = 0 \ \ \ \textrm{ for all } v \in V.
 	\end{eqnarray}
@@
 	\begin{eqnarray}
-		\Vert e(t)\Vert_{W} \leq \sqrt{2} \Vert e(0) \Vert_W + 2T||e'_h(0)||_W + 4\sqrt{T}\max_{t \in [0,T]} \Vert e'_p(t) \Vert_W.
+		\Vert e_(t)\Vert_{W} \leq \sqrt{2} \Vert e(0) \Vert_W + 2T||e'_h(0)||_W + 4\sqrt{T}\max_{t \in [0,T]} \Vert e'_p(t) \Vert_W.
 	\end{eqnarray}
 \end{col_1}
+
+\begin{proof}
+	Assume that there is no damping other than the weak damping, i.e. $a = 0$. The the equation in proposition 1 becomes
+	\begin{eqnarray*}
+		c(e_h''(t),v) + b(e(t),v) = 0 \ \ \ \textrm{ for all } v \in V.
+	\end{eqnarray*}
+
+	If $v \in S^h[0,T]$, then 
+	\begin{eqnarray*}
+		c(e_h''(t),v(t)) + b(e(t),v(t)) = 0.
+	\end{eqnarray*}
+
+	Let $v'(t) = c(t)$, then 
+	\begin{flalign}
+		\frac{d}{dt}\left[\frac{1}{2}c(e,e)-\frac{1}{2}b(v,v)-c(e_h,v) \right] &= c(e',e) - b(e,v)- c(e''_h, v)-c(e_h',v')\nonumber\\
+		&= c(e'_p,e). \label{DC_E4}
+	\end{flalign}
+
+	Choose $v(\tau) = 0$ for some $\tau \in [0,T]$, and integrate \eqref{DC_E4} between $0$ and $\tau$ to obtain
+	\begin{eqnarray*}
+		a
+	\end{eqnarray*}
+
+\end{proof}
 
@@
 \begin{eqnarray}
-	e(t_k) = u(t_k) - u^h_k & = & [u(t_k)-u_h(t_k)] + [u_h(t_k) - u^h_k]. \label{error_e}
+	e(t_k) = u(t_k) - u^h_k & = & [u(t_k)-u_h(t_k)] + [u_h(t_k) - u^h_k]. \label{error_ek}
 \end{eqnarray}
@@
 \subsubsection{Notation}
+For any sequence $\{x_k\} \in R_n$,
 For any sequence $\{x_k\} \in R_n$,
@@
 the error estimate $e^h(t) = u(t) - u^h(t)$ is obtained.
+
+The parameter $\tau$ is some number in $(0,T)$. The constant $K_\alpha$ is the constant defined in assumption \textbf{A4} of Section 2.2.1.
 

### 2023-07-29 files/Chapter2/generalvibrationmodel.tex
chapter2

@@
 
-In this dissertation, the stated objectives were to compare different models for use in applications.
+In this dissertation, the objective is to compare different linear beam and plate models for use in applications.
+The first of the comparisons are in Section \ref{sec:SP06}.
+This section is a discussion of the article \cite{SP06} comparing a Timoshenko beam model and a three dimensional beam model to empirical results.
+The authors of this article use the natural frequencies (equivalently the eigenvalues) to compare the different models.\\
+
+Chapter 6 is a discussion and extension of the article \cite{LVV09}.
+This article compares a Timoshenko beam model to a two-dimensional beam model.
+This is then extended to a comparison of a two-dimensional beam model to a three-dimensional beam model as well as a comparison of a two-dimensional plate model to a three-dimensional plate model.
+
 These comparisons are made in Chapter 4 and 6.

### 2023-08-31 files/Chapter7/Beam.tex
day before

@@
 \section{Validity of the Timoshenko beam model}
-In the article \cite{LVV09}, the authors show that the Timoshenko beam theory is a feasible model to use in practical applications of beams.
-In this section, the article is studied and the results are replicated.
+In the article \cite{LVV09}, the authors show that a cantilever Timoshenko beam model can be a feasible model to replace a more realistic two-dimensional model for use in application.
+They also show that the dimensions of the beam will determine how well the one-dimensional Timoshenko beam compares to the two-dimensional beam.
+In this section, the results of the article is discussed, replicated and extended with more testcases.
 
 Where \cite{LVV09} differs from most other research into the validity of the Timoshenko beam theory, is that the boundary conditions are also taken into consideration.
+The article serves as an intermediate step to comparing a Timoshenko beam to a three-dimensional beam.
 
-This section is a literature study of the article \cite{LVV09}.
-The goal of \cite{LVV09} to show that the one-dimensional Timoshenko beam theory, is a feasible model to use in practical applications of beams.
-In the real world, a beam is a complex three-dimensional model.
-So a three-dimensional model would be a good approximation and better than a one-dimensional model.
-It is therefore important to validate the accuracy of a simlified theory like the Timoshenko beam theory.
-
-In the article, the authors validate the Timoshenko beam theory by comparing it to a more realistic, two-dimensional model.
-The authors use a cantilever beam as a model.
-Although a direct comparison to a three-dimensional beam would be preferred, the authors state that this would introduce complexities.
-The two-dimensional model is an intermediate step.\\
-
-To compare the two models, the authors compare the natural frequencies of the models.
-From modal analysis, it is known that a solution of a second order hyperbolic type problem is a linear combination of the eigenvalues and eigenfunctions of the model.
-Therefore it is sufficient to compare the eigenvalues and eigenfunctions to compare the solutions and comment on the validity of the models.\\
+The authors use a cantilever beam with rectangular cross-section.
 
 \subsection{The models}
-In the article, the authors use a cantilever configuration for the two models. Therefore the models presented here are also cantilever models.\\
-
 Recall the cantilever Timoshenko beam model from section \ref{ssec:1D_Model:ModelProblems}, referred to as Problem T-2 and the cantilever two-dimensional beam model from section \ref{ssec:2D_Model:ModelProblem}, referred to as Problem 2D-1.
@@
 \subsection{Accuracy of the numerical eigenvalues}
-The calculate the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} use the article \cite{VV06}.
+To calculate the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} use the article \cite{VV06}.
 This article was discussed in section \ref{sec:Timo:EigenvalueProblem} in this dissertation.
-It is important to note that the method described in \cite{VV06} allows us to find the eigenvalues of a cantilever Timoshenko beam accurate to a desired level, using numerical methods like interval division.\\
+Using this article, the eigenvalues for the Timoshenko beam model can be numerically calculated to a desired accuracy level.
 
 A different approach is needed for the two-dimensional beam.
-In section \ref{sec:FEM:2D}, the Finite Element Method was used to obtain a numerical formula to solve the eigenvalue problem Problem 2D-1E.
-In \cite{LVV09} the authors used piecewise bi-cubic basis functions and a grid size large enough to ensure that the eigenvalues are accurate to 3 significant digits.\\
+The Finite Element Method is applied to the eigenvalue problem described in section \ref{sec:FEM:2D}.
+The following shows the rate of convergence of the first 20 eigenvalues using FEM and bi-cubic basis functions.
 
@@
 		\scalebox{1.4}{
-			\includegraphics[scale=0.4]{Convergence.png}
-			\caption{Maximum relative error of the first 10 eigenvalues of the two-dimensional beam.}
+			\includegraphics[scale=0.7]{Convergence.png}
+			\caption{Rate of convergence of the first 20 eigenvalues.}
 			\label{fig:conv}
@@
 \end{figure}
-
-\begin{tikzpicture}
-\begin{axis}[width=0.9\textwidth,
-			 xlabel=Iteration Number,
-			 ylabel=Error,
-			 ymode=log,
-			 legend pos=south east]
-\addplot[color=blue, mark=o] coordinates {
-    (1,0.1)
-    (2,0.05)
-    (3,0.01)
-    (4,0.005)
-};
-\addlegendentry{$h=1/5$}
-
-\addplot[color=red, mark=o] coordinates {
-    (1,0.2)
-    (2,0.1)
-    (3,0.05)
-    (4,0.02)
-};
-\addlegendentry{$h=1/10$}
-
-\addplot[color=green, mark=o] coordinates {
-    (1,0.2)
-    (2,0.1)
-    (3,0.05)
-    (4,0.02)
-};
-\addlegendentry{$h=1/20$}
-
-\addplot[color=black, mark=o] coordinates {
-    (1,0.3)
-    (2,0.3)
-    (3,0.03)
-    (4,0.03)
-};
-\addlegendentry{$h=1/30$}
-
-\end{axis}
-\end{tikzpicture}
-
+\textcolor{red}{FIX THIS}
 Figure \ref{fig:conv} show the maximum relative error of the first 10 eigenvalues of the two-dimensional beam.

### 2023-08-31 files/Chapter7/Introduction.tex
day before

@@
 \section{Introduction}
-This chapter is an investigation into the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate model for practical applications.
-Validity in this context refers to how well the solutions of the model compare to the solutions of more realistic higher-dimensional model.
+This chapter is an investigation into the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate model when used in application.
+Validity in this context refers to how well the solutions of a model compare to the solutions of a more realistic, higher-dimensional model.
 

### 2023-09-12 files/Chapter7/Introduction.tex
Introduction chapter 6

@@
 \section{Introduction}
-This chapter is an investigation into the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate model when used in application.
+This chapter is an investigation into the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin.
 Validity in this context refers to how well the solutions of a model compare to the solutions of a more realistic, higher-dimensional model.
+The application of the models are limited to beam-type and plate-type problems.
 
@@
 
-Section 7.2 is a discussion and a verification of numerical results of the work done in \cite{LVV09} In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
-We also include some extra results for different values of the parameter $\alpha$.
+Section 7.2 is a discussion and a replication of numerical results of the work done in the article \cite{LVV09}.
+In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
+Extra results are included in this section to verify the conclusions of the authors of \cite{LVV09}.
+The results of this section are also used as a reference for the rest of the chapter.
 

### 2023-09-13 files/Chapter7/Introduction.tex
parameters

@@
 
-Section 7.3 is a natural extension of the article \cite{LVV09} which is mentioned by the authors.
-In this section, the validity of the two-dimensional beam model use in Section 7.2 is investigated.
-The results of the two-dimensional beam are compared to a three-dimensional beam.
+Section 7.3 is a extension of the article \cite{LVV09} to a comparison of a cantilever two-dimensional beam to a cantilever three-dimensional beam.
+This extension is mentioned by the authors of \cite{LVV09}.
+This is an investigation into the validity of a two-dimensional beam model, and is an intermediate step to validate the Timoshenko beam model against a three-dimensional beam model.
+A direct comparison is not considered due to the complexities involved, which is discussed in more detail in the numerical results.
 
-The two-dimensional beam is an intermediate step to validate the Timoshenko beam model.
-A direct comparison between the one and three dimensional would be preferred, but the authors of \cite{LVV09} mention that this will introduce complexities, which will be discussed in more detail in the numerical results.
+Section 7.4 extends the work of \cite{LVV09} further to plate models.
+This extension follows the same idea as the previous sections, and originates from non-beam type behaviour observed in the three-dimensional beam models.
+In this section, a cantilever two-dimensional Reisner-Mindlin plate model is compared to a cantilever three-dimensional plate model.
 
-Section 7.4 extends the work of \cite{LVV09} further to plate models. Specifically a comparison of a cantilever two-dimensional Reissner-Mindlin plate to a cantilever three-dimensional plate.
-
-\subsubsection{Global parameters}
-All the models in this dissertation are made of the same isotropic material and have square cross-section.
-Therefore for all the models, the elastic modulus $\displaystyle G = \frac{E}{2(1+\nu)}$.
-The shear correction factor is chosen as $\kappa^2 = 5/6$ and Poisson's ratio $\nu = 0.3$.\\
-
-\subsubsection{Global Parameters}
-The models in this Chapter (and this dissertation) assume the use of an identical isotropic material with, a rectangular cross-section.
-These are defined in global parameters shared by all the models.
-The parameters are as follows:
+\subsection{Global parameters}
+All the models in this dissertation are assumed to be made of the same isotropic material and have a square cross-section. The parameters are as follows:
 
@@
 
-The consistent use of these parameters across all models helps to ensure that any differences in the results can be attributed to the model structures themselves, rather than variations in the material or geometric properties.
+These paremeters are used in all the models, and their consistency helps to ensure that any differences in the results can be attributed to the model structures themselves, rather than variations in the material or geometric properties.
+
+Since our models are all dimensionless, all of the beams and plates have a length of $\ell = 1$.
+We'll use $h$ to describe the height of the beams and plates, and $b$ to describe the width of the beams and plates.
+
+\subsection{Model specific parameters}
+The following parameters are not shared over all the models.
+These parameters can be unique to a model, or can be shared between some models but not all.
+These parameters mostly affect the geometry of the models.
+
+\subsubsection{Timoshenko beam}
+In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is introduced.
+\begin{eqnarray*}
+	\alpha = \frac{A\ell^2}{I}
+\end{eqnarray*}
+
+The model is in a dimensionless form, therefore the length of the beam is $\ell = 1$.
+Since we assumed a square cross-section, the area of the cross-section can be calculated as $\displaystyle A = hb$.
+The area moment of inertia can also be calculated as $\displaystyle I = \frac{h^3b}{12}$.
+
+Substituting these values into the equation for $\alpha$ gives the following relationship between the height of the beam and the parameter $\alpha$
+\begin{eqnarray*}
+	\alpha & = & \frac{12}{h^2},
+\end{eqnarray*}
+or equivalently,
+\begin{eqnarray*}
+	h & = & \sqrt{\frac{12}{\alpha}}.
+\end{eqnarray*}
+
+Using this parameter, the height of the beam can be set to any value.
+Some examples of values for $\alpha$ and the corresponding height of the beam that can be expected in this chapter, are given in Table \ref{tab:alphaheight} below.
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|c|c|}
+		\hline
+		$\alpha$ & $h$\\
+		\hline
+		$100$ & $\approx 0.35$ \\
+		$300$ & $1/5$ \\
+		$1200$ & $1/10$ \\
+		$4800$ & $1/20$ \\
+		$9600$ & $\approx 0.035$ \\
+		$10800$ & $1/30$ \\
+		\hline
+	\end{tabular}
+	\caption{Values of $\alpha$ and the corresponding height of the beam.}
+	\label{tab:alphaheight}
+\end{table}
+
+\subsubsection{Two-dimensional beam}
+
+For the two-dimensional beam, only the height parameter $h$ is required. The width of the beam is assumed to be finite, constant and small.
+
+\subsubsection{Three-dimensional beam}
+The three-dimensional beam is the most complex model and has two parameters to consider, the height $h$ and the width $b$.
+
+For beam type problems, one would assume that the width of the beam not much larger than the height of the beam. The numerical results will show that this guess is correct.
+
+For plate type problems, the width of the plate is assumed to be much larger than the height of the plate. This assumption is also verified in the numerical results.
+
+\subsubsection{Two-dimensional plate}
+The two-dimensional plate model is the most different model from the rest of the models.
+The two-dimensional plate model is a Reissner-Mindlin plate model, and is derived in section \ref{sec:reissnermindlinplate}.
+The model has two parameters, the height $h$ and the width $b$.
+
+% Need to explain the two parameters.
+
 \end{document}

### 2023-09-30 files/Chapter7/Introduction.tex
intro change

@@
 
-Section 7.2 is a discussion and a replication of numerical results of the work done in the article \cite{LVV09}.
+Section 7.2 is a discussion of the work and a replication of numerical results of/ the article \cite{LVV09}.
 In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
-Extra results are included in this section to verify the conclusions of the authors of \cite{LVV09}.
 The results of this section are also used as a reference for the rest of the chapter.

### 2023-09-30 files/Chapter6/Introduction.tex
cleanup chapter 6

--- 2022-10-31 files/Archive/Introduction.tex
@@
 \begin{document}
-\setcounter{chapter}{1}
-\setcounter{section}{0}
 \section{Introduction}
 
-\textcolor{red}{**********Sit in introduction*************}
-
-It is possible to derive a system of partial differential equations with corresponding boundary conditions but due to the complexity of the system, a different approach is considered.
-Consider the model problem in variational form.
-
-We consider the {\bf variational form} of the vibration problem.
-This variational problem may be used to implement the {\bf finite element method}.
-The finite element method can be used to simulate vibrations of the elastic body for both dynamic and static problems and also calculate the natural frequencies and modes of the elastic body.
-Existence and uniqueness of solutions to the problem can also be investigated using a weak version of the variational form.
-
-\subsubsection*{A Dynamic Problem}
-Find a vector valued function $u \in C(\Omega)$ such that it satisfies the equations of motion and the constitutive equations.
-Since $u \in C(\Omega)$, $u$ satisfies the boundary conditions defined on $\Sigma$ and $\Gamma$.\\
-
-Initial conditions for $u$ will need to be defined.
-
-\subsubsection*{A Static Problem}
-The static porblem is a special case of the dynamic problem  where $\partial_t^2 u = 0$. In this case, there are also no initial conditions.\\
-\textcolor{red}{**************************}
-
-\textcolor{red}{Research into the behaviour of suspension bridges is still a widely researched field by both engineers and mathematicians. This research started as several bridges suffered collapse. }
-
-\subsubsection{Different Research Approaches}
-\begin{figure}[h!]
-	\centering
-	\begin{tikzpicture}
-		\draw (3,2) -- (7,2);
-		\draw (3,2) -- (3,1.9);
-		\draw (7,2) -- (7,1.9);
-		\node at (5,2.1) {Main Span};
-
-		\draw[line width = 0.25mm] (0,0) -- (10,0);
-
-		\draw[line width = 0.5mm] (1.4,0) -- (1.4,-0.5);
-		\draw[line width = 2mm] (1.4,-0.5) -- (1.4,-0.7);
-
-		\draw[line width = 0.5mm] (2.2,0) -- (2.2,-0.5);
-		\draw[line width = 2mm] (2.2,-0.5) -- (2.2,-0.7);
-
-		\draw[line width = 0.5mm] (8.6,0) -- (8.6,-0.5);
-		\draw[line width = 2mm] (8.6,-0.5) -- (8.6,-0.7);
-
-		\draw[line width = 0.5mm] (7.8,0) -- (7.8,-0.5);
-		\draw[line width = 2mm] (7.8,-0.5) -- (7.8,-0.7);
-
-		\draw[line width = 0.5mm] (3,1.5) -- (3,-0.5);
-		\draw[line width = 2mm] (3,-0.5) -- (3,-0.7);
-
-		\draw[line width = 0.5mm] (7,1.5) -- (7,-0.5);
-		\draw[line width = 2mm] (7,-0.5) -- (7,-0.7);
-
-		\draw (5,0.4) parabola (3,1.5);
-		\draw (5,0.4) parabola (7,1.5) ;
-
-		\draw (3,1.5) -- (0.2,-0.5);
-		\draw (7,1.5) -- (9.8,-0.5);
-
-		\draw[line width = 2mm] (0.2,-0.5) -- (0.2,-0.7);
-		\draw[line width = 2mm] (9.8,-0.5) -- (9.8,-0.7);
-
-		\draw[line width = 0.1mm] (5,0) -- (5,0.4);
-		\draw[line width = 0.1mm] (5.25,0) -- (5.25,0.43);
-		\draw[line width = 0.1mm] (5.5,0) -- (5.5,0.46);
-		\draw[line width = 0.1mm] (5.75,0) -- (5.75,0.55);
-		\draw[line width = 0.1mm] (6,0) -- (6,0.69);
-		\draw[line width = 0.1mm] (6.25,0) -- (6.25,0.85);
-		\draw[line width = 0.1mm] (6.5,0) -- (6.5,1);
-		\draw[line width = 0.1mm] (6.75,0) -- (6.75,1.25);
-
-		\draw[line width = 0.1mm] (4.75,0) -- (4.75,0.43);
-		\draw[line width = 0.1mm] (4.5,0) -- (4.5,0.46);
-		\draw[line width = 0.1mm] (4.25,0) -- (4.25,0.55);
-		\draw[line width = 0.1mm] (4,0) -- (4,0.69);
-		\draw[line width = 0.1mm] (3.75,0) -- (3.75,0.85);
-		\draw[line width = 0.1mm] (3.5,0) -- (3.5,1);
-		\draw[line width = 0.1mm] (3.25,0) -- (3.25,1.25);
-	\end{tikzpicture}
-	\caption{Side view of single span suspension bridge with conventional bridge on either sides of the main span.}
-\end{figure}
-
-\subsubsection{Motivation}
-
-In most real-world applications, three-dimensional models are a natural choice.
-But it may not be the most efficient or practical choice.
-When considering the three-dimensional models, there is a limitation on the availability of computing power that is required for these models as well as the complexity of the models.
-This is especially true of systems of multiple three-dimensional models.
-Simplifications of the models are a great way around this limitation.\\
-
-In many applications, especially engineering, one-dimensional models such as the Timoshenko beam model is used to a great extent for most beam type applications.
-To do this, some assumptions about the properties of the beam are required to be made.
-This brings into question the validity of using a one-dimensional model over a more realistic three-dimensional model.\\
-
-In this essay, we consider three different models for a beam.
-A three-dimensional elastic solid is compared to a one-dimensional beam model, namely the Timoshenko beam model.
-As a natural intermediate step, we will also look at a two-dimensional elastic solid derived using an assumption of plane stress.\\
-
-The comparisons of the models are made for a cantilever beam.
-The comparisons between the models are made by considering the modes and natural frequencies of the models.
-This is a valid comparison since the solution of a vibration problems can be written in terms of a linear combination of the eigenfunctions.\\
-
-In Chapter 1, the models for a three-dimensional elastic solid, a two dimensional elastic solid as well as a one-dimensional Timoshenko beam model is presented.
-In Chapter 2, we look at the exsistance and uniqueness of solutions to these linear vibration models.
-Chapter 3 covers the convergence of the eigenvalue problems as well as a dynamic problem.
-This is neccessary since we intend to use the Finite Element Method in Chapter 5 to derive and solve a static problem and the eigenvalue problem for the two and three-dimensional models.
-For the one-dimensional Timoshenko model, seperation of variables can be applied to obtain the eigenvalues exactly and this is done in Chapter 4.
-In Chapter 4, we also look at the results of an article by [] that tested the validity of the Timoshenko beam model using an empirical test.
-
-\textcolor{red}{************************************************}\\
-\subsubsection*{Research rationale and motivation}
-From small transverse vibration of a linearly elastic (flat) plate [Mindlin, 1951], to a fully non-linear shell model, numerous mathematical problems are possible.
-(The same remark is also true for beams.) In this research project, our focus is on the small vibrations but not sufficiently small to justify a linear model.\\
-
-In the article of [Antman,1976], we see that the author takes a rigorous mathematical approach to obtain fully general theories of non-linearly elastic rods and shells from three-dimensional theories.
-In a follow up article [Antman,1996], open problems of nonlinear elastic rods are investigates and references are made to 4 articles of Simo and Vu-Quoc.
-Where [Antman,1976] follows a vigorous math approach, [Simo and Vu-Quoc,1987] follows an engineering approach.
-Their work however, received wide recognition and it is worthwhile to compare their articles to the work of [Antman,1976] and [Antman,1996].\\
-
-\subsubsection*{Problem Identification}
-In applications simplified models can be used with some additional but different assumptions and it leads to different models for the same real life problem.
-An example of where numerous models are used to study the same real world problem is the Tacoma Narrows Bridge disaster of 1940.
-[Gazzola, 2013] and [McKenna,1999] both derive models for this specific problem but with different approaches.
-Even though both authors agree on the shortcomings of many bridge models and that non-linear theories should be used, [Gazzola, 2013] insists on using a plate to model the bridge, while [McKenna,1999] uses a beam.
-This gives at least two different models for the same real world problem.\\
-
-\subsubsection*{Research aims and objectives}
-The main objective of this literature study is the comparison of such models, using either analysis or a finite element method simulation.
-Adding assumptions to a general model leads to many different simplified models that can be applied to the same situation.
-It is important to investigate the differences in these models and their applicability to real world problems.\\
-
-Calculating solutions for these models will be useful for the comparison, but due to the complexities of the problems, numerical methods are used to obtain approximate solutions.
-The finite element method is generally accepted to be the best for elasto-mechanics.
-Appropriate articles will be used to ensure convergence of the solutions.\\
-
-This study will also look at possible simplifications to the models through the addition of more assumptions.
-Examples of simplifications to models is the added assumption of rigidity of a beam model.
-This simplifies the model from a system of partial differential equations, to a system of ordinary differential equations.\\
-
-This masters research is an in depth literature study with a main focus on model problems on shells and rods with attention given to:
-\begin{itemize}
- \item Comparison of different models for the same problem either using analysis or numerical methods.
- \item Determining existence of solutions, given that the relevant articles are available.
- \item Convergence of finite element method when calculating solutions to the model problems.
-\end{itemize}
 \end{document}

### 2023-09-30 files/Chapter6/Validity_Timo.tex
chapter 6v2

--- 2023-08-31 files/Chapter7/Beam.tex
@@
 \begin{document}
-\section{Validity of the Timoshenko beam model}
-In the article \cite{LVV09}, the authors show that a cantilever Timoshenko beam model can be a feasible model to replace a more realistic two-dimensional model for use in application.
-They also show that the dimensions of the beam will determine how well the one-dimensional Timoshenko beam compares to the two-dimensional beam.
-In this section, the results of the article is discussed, replicated and extended with more testcases.
+\section{Validity of a Cantilever Timoshenko beam} \label{sec:validity-of-a-cantilever-timoshenko-beam}
 
-Where \cite{LVV09} differs from most other research into the validity of the Timoshenko beam theory, is that the boundary conditions are also taken into consideration.
-The article serves as an intermediate step to comparing a Timoshenko beam to a three-dimensional beam.
+In this section, the validity of the Timoshenko beam model is investigated.
+Specifically, the validity of a cantilever Timoshenko beam model, using a cantilever two-dimensional beam model as a reference.
+This is a discussion and a replication of numerical results of the work done in the article \cite{LVV09}.
 
-The authors use a cantilever beam with rectangular cross-section.
+The article \cite{LVV09} is titled `Comparison of linear beam theories'.
+In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
+\textcolor{red}{Give a brief summary of the article here, linking to whatever has already been discussed in the literature review.}
 
 \subsection{The models}
-Recall the cantilever Timoshenko beam model from section \ref{ssec:1D_Model:ModelProblems}, referred to as Problem T-2 and the cantilever two-dimensional beam model from section \ref{ssec:2D_Model:ModelProblem}, referred to as Problem 2D-1.
-In \cite{LVV09} it is assumed that the beams have a rectangular cross-section.\\
+The following two models are the focus of this section and the models that are used in the article \cite{LVV09}.
+From section \ref{ssec:1D_Model:ModelProblems}, the cantilever Timoshenko beam model, referred to as Problem T-2.
+From section \ref{ssec:2D_Model:ModelProblem}, the cantilever two-dimensional beam model, referred to as Problem 2D-1.\\
 
-Figure 6.1 shows the two beams side-by-side.
+Figure \ref{fig:compare:1D+2D} shows the two beams side-by-side.
 
-\begin{figure}[h!]\label{fig:compare:1D+2D}
+\begin{figure}[h!]
 	\scalebox{.8}{
@@
 	}
+\end{figure}\label{fig:compare:1D+2D}
+
+As mentioned in the introduction, the height of the two beams can be set to be the same by considering the parameter $\alpha$ for the Timoshenko beam model and the parameter $h$ for the two-dimensional beam model.
+
+\subsection{Calculating the eigenvalues and eigenvectors}
+In section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided.
+And in section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.
+These can also be obtained to a desired level of accuracy.
+
+For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method.
+In section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived.
+Specifically, section \ref{2dFEM_EP} derived the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.
+
+\subsubsection{Problem 2D-1E}
+Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
+\begin{eqnarray}
+	K\bar{u} & = & M\lambda{\bar{u}},
+\end{eqnarray} where $M$ and $K$ are the standard Finite Element Method matrices defined in section \ref{sec:FEM:2D}.
+
+In this form, the eigenvalue problem is a system of ordinary differential equations, and can be solved using a numerical method.
+
+\subsubsection{Accuracy of the eigenvalues}
+Solving \textbf{Problem 2D-1E} with a numerical method, requires a quick investigation into the rate of convergence so that the accuracy of the eigenvalues can be established.
+Chapter \ref{ch:finite-element-theory} provides the necessary theory on the existence of solutions as well as the proof of convergence of the Finite Element Method.
+
+\begin{figure}[H]
+    \centering
+    \begin{adjustbox}{center}
+        \includegraphics[scale=0.7]{Convergence.png}
+    \end{adjustbox}
+    \caption{Rate of convergence of the first 20 eigenvalues.}
+    \label{fig:conv_2d_eig}
 \end{figure}
 
-In Chapter 1, the following parameters were defined.
-The parameter $h$ is the height of the two-dimensional beam and for the Timoshenko dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ was found.\\
+Figure \ref{fig:conv_2d_eig} shows the rate of convergence of the first 20 eigenvalues of the two-dimensional beam. Each color represents a spesific eigenvalue.
 
-For the Timoshenko beam model with a rectangular cross-section, the area moment of inertial is calculated as
-\begin{eqnarray*}
-	I = \frac{h^3b}{12}.
-\end{eqnarray*}
+The number of elements are chosen so that at least the first 10 eigenvalues are accurate to 5 significant digits.
 
-After substitution, the following relationship between $\alpha$ and $h$ is found
-\begin{eqnarray*}
-	h = \sqrt{\frac{12}{\alpha}}.
-\end{eqnarray*}
-Using this relationship, $\alpha$ can be chosen in such a way that the beams have equal lateral dimensions.
+\subsection{Comparing the mode shapes}
+Recall from the introduction, that the investigation is focussed on beam-type problems.
+The two-dimensional model is for an elastic body, and not specific to a beam, like the Timoshenko beam model.
+Therefore there are non-beam type behaviour that can be expected from the two-dimensional model.
+This is also be reflected in the eigenvalues of the two-dimensional model.
 
-\subsection{Accuracy of the numerical eigenvalues}
-To calculate the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} use the article \cite{VV06}.
-This article was discussed in section \ref{sec:Timo:EigenvalueProblem} in this dissertation.
-Using this article, the eigenvalues for the Timoshenko beam model can be numerically calculated to a desired accuracy level.
-
-A different approach is needed for the two-dimensional beam.
-The Finite Element Method is applied to the eigenvalue problem described in section \ref{sec:FEM:2D}.
-The following shows the rate of convergence of the first 20 eigenvalues using FEM and bi-cubic basis functions.
-
-\begin{figure}[H]
-	\begin{center}
-		\scalebox{1.4}{
-			\includegraphics[scale=0.7]{Convergence.png}
-			\caption{Rate of convergence of the first 20 eigenvalues.}
-			\label{fig:conv}
-		}
-	\end{center}	
-\end{figure}
-\textcolor{red}{FIX THIS}
-Figure \ref{fig:conv} show the maximum relative error of the first 10 eigenvalues of the two-dimensional beam.
-In \cite{LVV09}, the authors use a grid size of $40 \times 10$ with $h= 1/10$ (or $\alpha = 1200$) and $h = 1/5$ (or $\alpha = 300$).\\
-
- Figure \ref{fig:conv} show that this can be improved significantly.
-For each case of $h$, the grid size is calculated as $n \times \max\left\{\lceil\frac{n}{h}\rceil,10\right\}$.
-This ensures that the nodes are distributed somewhat evenly relative to the length-width ratio.
-For this chapter, the results of the Timoshenko beam and two-dimensional beam are given accurate up to 5 significant digits.
-
-\subsection{Comparing the shape of the eigenfunctions}
-Before the eigenvalues can be compared, a method is required to be able to match the eigenvalues of the two different models.
-The authors of \cite{LVV09} match the modal shapes of the eigenfunctions.
-The corresponding eigenvalues can then be matched.\\
-
-The eigenvalues of the Timoshenko beam, are referred to by the authors as beam-type eigenvalues.
+Therefore a method is required to compare and match the eigenvalues of the two models.
+In \cite{LVV09}, the authors compare the mode shapes of the two models, to match up the eigenvalues.
+Recall \textcolor{red}{****} that eigenvalues relating to the mode shapes similar to the mode shapes of the Timoshenko beam, are called beam type eigenvalues.
+The other eigenvalues are called non-beam type eigenvalues.
+This naming convention is used by the authors of \cite{LVV09}.
 
@@
 
-The existence of these non-beam type eigenvalues imply that there are eigenvalues in the two-dimensional model, that are not in the Timoshenko beam model.
-This is an example of the complexities that arise when comparing models of different dimensions.
-
-\subsubsection{Shapes of the cross-section}
+\subsubsection{Shape of the cross-sections}
 The Timoshenko beam theory improve some one-dimensional beam theories such as the Euler-Bernoulli beam theory by also including the effect of shear.
-In the Timoshenko beam theory it is assumed that the cross-sections need not remain perpendicular to the neutral axis of the beam.
+For Timoshenko beam theory it is assumed that the cross-sections need not remain perpendicular to the neutral axis of the beam.
 The cross-sections however remain a straight line.\\
 
-For the two-dimensional beam, the shape of the cross-section can deform into a s-shape. This is explained in \cite{LVV09} and a similar figure in \cite{LVV09} is given here.
+For the two-dimensional beam, the shape of the cross-section can deform into a s-shape.
+This is explained in \cite{LVV09} and a similar figure in \cite{LVV09} is given here.
+This is a difference between the two models that are inherent to their definitions.\\
+
 \FloatBarrier
@@
 \end{tikzpicture}
-	\caption{S-shape deformation of the cross-section.}\label{fig:s}
+	\caption{S-shape deformation of the cross-section of the two-dimensional beam.}\label{fig:s}
 \end{figure}
+\FloatBarrier
 
 Note that figure \ref{fig:s} shows an exaggerated example of the deformation of a cross-section.
-The red line shows how the average rotation of a cross-section is calculated in \cite{LVV09}.
-This average rotation can be used to compare the rotation of the cross-section of the two-dimensional beam to the rotation of the cross-section of the Timoshenko beam.
-\FloatBarrier
+The red line shows how the authors of \cite{LVV09} calculated the average rotation of a cross-section of the two-dimensional beam.
+This average rotation can be used to compare the rotation of the cross-section of the two-dimensional beam to the rotation of the cross-section of the Timoshenko beam given by $\phi$.
 
 \subsubsection{Direct comparison of mode shapes}
-Figure \ref{fig:w} shows the displacement of the material lines of the cantilever Timoshenko beam and the cantilever two-dimensional beam, compared directly.
+Figure \ref{fig:w} directly compares a mode shape of the Timoshenko beam to a mode shape of the two-dimensional beam.
+For the two-dimensional model, the center line of the displacement of the beam is shown.
+For the Timoshenko beam, the displacement $w$ is shown.
 
@@
 
-Similarly Figure \ref{fig:phi} shows the direct comparison of the angle of the cross-section of the cantilever Timoshenko beam and the two-dimensional beam.
-The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s} and \cite{LVV09}.
+Similarly, figure {fig:phi} directly compares the angle of the cross-section of the Timoshenko beam and the two-dimensional beam.
+The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s}.
 
@@
 
-In \cite{LVV09} the authors obtained similar results for $\alpha=300$, which represents a short beam.
-Both figures \ref{fig:w} and \ref{fig:phi} were calculated with5 $\alpha = 4800$, which represents a longer, narrower beam.
+These figures are examples that show how similar the mode shapes of the two models are.
+This specific example is for $\alpha = 4800$, which represents a long, narrow beam.
+The authors of \cite{LVV09} obtained similar results for $\alpha=300$, which represents a short and fat beam.
 
-\subsubsection{Remark}
-The mode shapes were scaled to obtain figures \ref{fig:w} and \ref{fig:phi}. Therefore no scale is shown on the y-axis.
+\subsubsection{Remark:} Note that the overall shape is more important than the actual fit.
+This is because any multiple of a eigenvector is still an eigenvector.
+The mode shapes were specifically scaled to obtain figures \ref{fig:w} and \ref{fig:phi}.
 
 \subsection{Comparing the eigenvalues}
-\subsubsection{Results of [LVV09]}
-The following table contains the results form \cite{LVV09} as well as the corresponding results obtained in this dissertation.
+Using this method of comparing the mode shapes, the eigenvalues can now be matched up and compared.
+
+\subsubsection{Some results from [LVV09]}
+The following table contains results from \cite{LVV09} verbatim to 3 significant digits, as well as the replicated results to 5 significant digits.
+
 \begin{table}[!ht]
 	\centering
-	\caption{Results from [LVV09] and results obtained in this dissertation. $0^a$ indicates a 0 as a result of rounding. $\alpha = 1200$}
+	\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
 	\begin{tabular}{|c|c|c|c||c|c|c|c|}
@@
 		1 & 0.0317 & 0.0316 & 0.00315 & 1 & 0.031713 & 0.031639 & 0.0023407  \\ 
-		2 & 1.14 & 1.14 & $0^a$ & 2 & 1.1413 & 1.1365 &  0.0042050 \\ 
+		2 & 1.14 & 1.14 & $0^*$ & 2 & 1.1413 & 1.1365 &  0.0042050 \\ 
 		3 & 7.72 & - & ~ & 3 & 7.7161 & - &   \\ 
@@
 
-In Table \ref{Results_LVV09}, the results from \cite{LVV09} and the respective results from this dissertation is given.
-This table shows that the results of \cite{LVV09} can be replicated with more significant digits.\\
+This table shows that the results obtained in this dissertation are very similar to the results obtained in \cite{LVV09}. This is for a specific case where $\alpha = 1200$.
 
-Interestingly, with the improved accuracy over \cite{LVV09}, the relative errors remain similar in Table \ref{Results_LVV09}.
-It is possible that the higher level of accuracy will only benefit larger eigenvalues.
-Larger eigenvalues are however not of interest for practical applications.
-The 2nd relative error of \cite{LVV09} however could not be duplicated.
-
-\subsection{Comparison of the eigenvalues}
-In \cite{LVV09}, two values for $\alpha$ are considered.
-For $\alpha = 1200$, the Timoshenko beam has a length to width ratio of $1:10$.
-For $\alpha = 300$, the Timoshenko beam has length to width ratio of $1:5$.
-These two values represent a ``long slender'' beam and a ``short'' beam.\\
-
-In Table \ref{tab:Timo}, the eigenvalues of the Timoshenko beam are compared to the first 20 eigenvalues of the two-dimensional beam. The eigenvalues are calculated for different values of $\alpha$.\\
+In the following table, the eigenvalues for different values of $\alpha$ are compared.
 
@@
 	\makebox[\textwidth]{
-	\caption{Eigenvalues of a Timoshenko cantilever beam vs the eigenvalues of a cantilever two-dimensional elastic body. RE - Relative Error}
+	\caption{Eigenvalues of a Timoshenko cantilever beam vs the eigenvalues of a cantilever two-dimensional elastic body. *RE is the relative error.}
 	\begin{tabular}{|cccc||cccc||cccc||cccc|}
@@
 
-The authors of \cite{LVV09} show that for $\alpha = 300$ the eigenvalues compare very well up to the 20th two-dimensional eigenvalue.
-This is also apparent for other values of $\alpha$ as Table \ref{tab:Timo} shows.
-In fact, the accuracy of the eigenvalues increases as $\alpha$ increases.
-The authors of \cite{LVV09} also mention that for $\alpha = 100$, the results are very good for the first 10 eigenvalues.\\
+This table shows that the eigenvalues compare very well.
+The non-beam type eigenvalues are highlighted in grey.
+For a short fat beam ($\alpha = 300$), the maximum relative error for the first 20 two-dimensional eigenvalues is just over $3\%$, while for a long thin beam ($\alpha = 10800$), the maximum relative error is just over $1\%$.
+This shows that as the beam becomes longer and thinner, the Timoshenko beam is better approximation of the two-dimensional beam.
+But overall the Timoshenko beam compares very well.
 
-Interestingly, the number of non-beam type eigenvalues within the first few eigenvalues decreases as $\alpha$ increases (or more relevant for the two-dimensional beam: as $h$ decreases).\\
+This table also shows that as the beam gets more narrow, there are less non-beam type eigenvalues within the first few eigenvalues.This would also indicate that the Timoshenko beam would be a better approximation of the two-dimensional beam as the beam gets more narrow since the two-dimensional model behaves `more like a beam'.
 
-Overall, the relevant conclusions of \cite{LVV09} is verified.
-For practical applications of beam models, the Timoshenko beam can be used.
-Preferably for long slender beams as Table \ref{tab:Timo} shows.
-The authors also mention that nature of the disturbance should also be taken into consideration, mainly because the models are linear.\\
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \begin{axis}[
+            title={Relative Error of Eigenvalues for Different Values of Alpha},
+            xlabel={Eigenvalue},
+            ylabel={Relative Error (\%)},
+            legend pos=north east,
+            grid=major,
+        ]
+        % Alpha = 300
+        \addplot coordinates {
+            (1,0.4875) (2,1.1106) (3,0) (4,1.7895) (5,2.4560) (6,0) (7,2.9630) (8,1.4324) (9,0) (10,2.9530)
+            (11,0.5735) (12,0) (13,0.8375) (14,0.5643) (15,0) (16,0.4757) (17,0) (18,1.1240) (19,0) (20,1.9740)
+        };
+        \addlegendentry{\(\alpha = 300\)}
 
- The short comings of \cite{LVV09} is that damping is not considered.
-This is mentioned by the authors of \cite{LVV09}, but will not be addressed in this dissertation.
-Further work is to extend \cite{LVV09} to a three-dimensional comparison.
-This is investigated further in this chapter.\\
+        % Alpha = 1200
+        \addplot coordinates {
+            (1,0.2337) (2,0.4217) (3,0) (4,0.7198) (5,1.0738) (6,1.4507) (7,0) (8,1.6244) (9,2.1618) (10,0)
+            (11,2.4560) (12,0) (13,2.7265) (14,0) (15,0) (16,5.2392) (17,0) (18,3.2823) (19,3.0864) (20,0)
+        };
+        \addlegendentry{\(\alpha = 1200\)}
 
-\section{Validity of the two-dimensional elastic model}
-In this section, the validity of a two-dimensional cantilever beam is investigated. This is an extension of the work in \cite{LVV09}, as mentioned in the article.\\
+        % Alpha = 4800
+        \addplot coordinates {
+            (1,0.1125) (2,0.1661) (3,0.2574) (4,0) (5,0.3824) (6,0.5373) (7,0.7065) (8,0) (9,0.9950) (10,1.0740)
+            (11,0) (12,1.2680) (13,1.4507) (14,0) (15,0) (16,1.8120) (17,0) (18,1.9850) (19,2.1618) (20,0)
+        };
+        \addlegendentry{\(\alpha = 4800\)}
 
-As explained before, the two-dimensional model is used as a intermediate step between the Timoshenko and three-dimensional beam.
-The same method as in \cite{LVV09} will be used to investigate the validity of the two-dimensional model.\\
-
-The models for the two-dimensional and three-dimensional beams are defined in section \ref{ssec:2D_Model:ModelProblem} and \ref{ssec:3D_Model:ModelProblems} respectively.
-These models are elastic bodies and not specifically beam models.
-Therefore it is expected to find eigenvalue and eigenfunction pairs that does not relate to beam type problems.
-This was already seen with the two-dimensional model in the previous section.
-These not beam type eigenvalues are calculated in this section, however the focus still remains on beam type problems.\\
-
-\subsection{The models}
-Recall a cantilever two-dimensional beam, referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.\\
-
-Figure \ref{fig:2Dv3D} shows the two beams side-by-side.
-
-\FloatBarrier
-\begin{figure}[h!]
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\caption{Side-by-side comparison of the beams.}
-			\label{fig:2Dv3D}
-			\centering
-			\begin{minipage}[b]{0.7\linewidth}
-				\begin{tikzpicture}
-					\draw[line width = 0.3mm] (0,1) -- (7,1);
-					\draw[line width = 0.3mm] (0,-1) -- (7,-1);
-					\draw[line width = 0.3mm] (7,-1) -- (7,1);
-					\draw[line width = 0.3mm] (0,-1) -- (0,1);
-
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
-
-					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
-					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
-
-					\draw[scale=0.5, domain=1:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
-					\draw[scale=0.5, domain=2:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
-
-					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
-					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
-					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
-					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
-					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
-					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
-					\draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
-					\draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});
-
-					\node at (7.2,0) {$h$};
-					\node at (3.2,-1.2) {$\ell = 1$};
-				\end{tikzpicture}
-				\subcaption{Two-Dimensional Elastic Body}
-			\end{minipage}
-			\begin{minipage}[b]{0.7\linewidth}
-				\begin{tikzpicture}
-					\draw[line width = 0.3mm] (-0.1,1) -- (6.9,1);
-					\draw[line width = 0.3mm] (-0.1,-1) -- (6.9,-1);
-					\draw[line width = 0.3mm] (6.9,-1) -- (6.9,1);
-					\draw[line width = 0.3mm] (-0.1,-1) -- (-0.1,1);
-
-					\draw[line width = 0.3mm] (0.1,1.1) -- (7.1,1.1);
-					\draw[line width = 0.3mm] (7.1,-0.9) -- (7.1,1.1);
-
-					\draw[line width = 0.3mm] (-0.1,1) -- (0.1,1.1);
-					\draw[line width = 0.3mm] (6.9,1) -- (7.1,1.1);
-					\draw[line width = 0.3mm] (6.9,-1) -- (7.1,-0.9);
-
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
-
-					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
-					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
-					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
-
-					\draw[scale=0.5, domain=0.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
-					\draw[scale=0.5, domain=1.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
-					\draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
-
-					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
-					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
-					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
-					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
-					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
-					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
-					\draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
-					\draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});
-
-					\node at (6.95,1.25) {$b$};
-					\node at (6.78,0) {$h$};
-					\node at (3.2,-1.2) {$\ell = 1$};
-
-				\end{tikzpicture}
-				\subcaption{Three-Dimensional Elastic Body}
-
-			\end{minipage}
-		}
-	}
-\end{figure}
-\FloatBarrier
-
-For both models the parameter $h$ represents the width of the beams.
-The three-dimensional model also have depth $b$.
-Intuitively, from the figure, the two-dimensional beam should compare better to the three-dimensional beam for smaller $b$.
-
-\subsection{Accuracy of the numerical eigenvalues}
-Similar to how the eigenvalues and eigenfunctions of the two-dimensional model calculated in the previous section, the eigenvalues and eigenfunctions can be calculated for the three-dimensional model.
-The numerical formula to calculate the eigenvalues and eigenfunctions are derived in section \ref{sec:FEM:3D}.\\
-
-Using piecewise tri-cubic basis functions, the following results were obtained.\\
-
-\begin{tikzpicture}
-	\begin{axis}[width=0.9\textwidth,
-				 xlabel=Iteration Number,
-				 ylabel=Error,
-				 ymode=log,
-				 legend pos=south east]
-	\addplot[color=blue, mark=o] coordinates {
-		(1,0.1)
-		(2,0.05)
-		(3,0.01)
-		(4,0.005)
+        % Alpha = 10800
+        \addplot coordinates {
+            (1,0.0841) (2,0.1009) (3,0.1287) (4,0.2052) (5,0.3824) (6,0.2817) (7,0.3725) (8,0.4712) (9,0) (10,0.5940)
+            (11,0.7005) (12,0.8140) (13,0.9307) (14,0) (15,0) (16,1.8120) (17,1.2150) (18,1.9850) (19,2.1618) (20,2.8860)
         };
-	\addlegendentry{$h=1/5$}
-
-	\addplot[color=red, mark=o] coordinates {
-		(1,0.2)
-		(2,0.1)
-		(3,0.05)
-		(4,0.02)
-	};
-	\addlegendentry{$h=1/10$}
-
-	\addplot[color=green, mark=o] coordinates {
-		(1,0.2)
-		(2,0.1)
-		(3,0.05)
-		(4,0.02)
-	};
-	\addlegendentry{$h=1/20$}
-
-	\addplot[color=black, mark=o] coordinates {
-		(1,0.3)
-		(2,0.3)
-		(3,0.03)
-		(4,0.03)
-	};
-	\addlegendentry{$h=1/30$}
+        \addlegendentry{\(\alpha = 10800\)}
 
@@
     \end{tikzpicture}
+    \caption{Plot of the relative error for each eigenvalue and each value of \(\alpha\).}
+    \label{fig:relative_error_plot}
+\end{figure}
 
-\subsection{Comparing the mode shapes}
-Identical to the method used in \cite{LVV09} and the previous section, the eigenvalues of the two models can be matched by comparing the mode shapes.
-As mentioned earlier, it is expected that there will be mode shapes not related to beam type problems, and also mode shapes that the three-dimensional model do not share with the two-dimensional model.\\
-
-In this section, examples of the different mode shapes are shown.
-
-\subsubsection{Mode shapes relating to beam type eigenvalues.}
-Figure \ref{fig:beam-2dv3d} show some examples of beam type mode shapes for the displacement $u$.
-
-\begin{figure}[h!]
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{3D12.png}
-				\subcaption{3D Beam Type - $\lambda_{12} = 2.3293$}
-				\label{fig:minipage2}
-			\end{minipage}
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{2D3.png}
-				\subcaption{2D Beam Type - $\lambda_3 = 2.3273$}
-				\label{fig:minipage1}
-			\end{minipage}
-	}}
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{3D22.png}
-				\subcaption{3D Beam Type - $\lambda_{24} = 21.929$}
-				\label{fig:minipage2}
-			\end{minipage}
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{2D6.png}
-				\subcaption{2D Beam Type - $\lambda_6 = 21.911$}
-				\label{fig:minipage1}
-			\end{minipage}
-			\caption{Mode shapes of the displacement $w$ with $h=1/20$.}
-			\label{fig:beam-2dv3d}
-	}}
-\end{figure}
-\FloatBarrier
-
-\subsubsection{Mode shapes relating to non-beam type eigenvalues that are present in the two-dimensional model.}
-Figure \ref{fig:nonbeam-2dv3d} show examples of mode shapes relating to non-beam type eigenvalues for the displacement $u$.
-
-\FloatBarrier
-\begin{figure}[h!]
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{3D33.png}
-				\subcaption{3D Non-Beam Type - $\lambda_{33} = 69.374$}
-				\label{fig:minipage2}
-			\end{minipage}
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{2D8.png}
-				\subcaption{2D Non-Beam Type - $\lambda_8 = 69.344$}
-				\label{fig:minipage1}
-			\end{minipage}
-			\caption{Mode shapes of the displacement $w$ with $h=1/20$.}
-			\label{fig:nonbeam-2dv3d}
-	}}
-\end{figure}
-\FloatBarrier
-
-\subsubsection{Mode shapes relating to non-beam type eigenvalues that are not present in the two-dimensional model.}
-Figure \ref{fig:nonbeam-2dv3d} show examples of mode shapes relating to non-beam type eigenvalues for the displacement $u$ which are not present in the two-dimensional model.
-These mode shapes only appear in the three-dimensional beam.
-\FloatBarrier
-\begin{figure}[h!]
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{3DNonBeam10.png}
-				\subcaption{Non-2D Type - $\lambda_{10}$}
-				\label{fig:minipage2}
-			\end{minipage}
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{3DNonBeam11.png}
-				\subcaption{Non-2D Type - $\lambda_{11}$}
-				\label{fig:minipage11}
-			\end{minipage}
-			\caption{Mode shapes of the displacement $w$ with $\alpha = 4800$.}
-
-	}}
-\end{figure}
-\FloatBarrier
-
-Figure \ref{fig:minipage11} looks similar to the beam type eigenvalues, however the shape is in the $x-z$ axis.\\
-
-\subsection{Comparing the eigenvalues}
-The eigenvalues can now be compared.
-In the tables of this subsection, the eigenvalues of the two-dimensional beam are compared to the eigenvalues of the three-dimensional beam.
-Since there are two parameters to consider, $h$ and $b$, only a few cases are considered.\\
-
-The three-dimensional beam has more eigenvalues than the two-dimensional beam for the range considered in this investigation.
-Since the interest is in the comparison of the two models, the eigenvalues of the three-dimensional that are not present in the two-dimensional beam are omitted from the tables.\\
-
-The eigenvalues for beam type problems, the main focus of this investigation, are highlighted in the tables.\\
-
-The cases considered are similar to the cases in \cite{LVV09}, a short beam and a slender beam.
-For the short beam, $h = 1/5$ and for the slender beam, $h = 1/20$.
-The parameter $b$ will be varied to test the accuracy.
-For now the results are restricted to $b \leq h$.
-The other cases will be discussed later.\\
-
-\subsubsection*{Case $b < h$:}
-
-\begin{table}[htbp]
-	\scalebox{.8}{
-	\makebox[\textwidth]{
-		\caption{Comparsion of Eigenvalues with $h = 1/5$.}
-		\begin{tabular}{|cc|cc|cc|cc||cc|}
-			\hline
-			\multicolumn{10}{|c|}{Eigenvalues} \\
-			\hline
-			\hline
-			i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
-			\hline
-			{2} & 0.12307 & {2} & 0.12234 & {2} & 0.12198 & {3} & 0.12178 & 1     & 0.12151 \\
-			{3} & 3.5773 & {5} & 3.5630 & {6} & 3.5558 & {8} & 3.5519 & 2     & 3.5460 \\
-			\rowcolor{lightgray}{5} & 7.7799 & {6} & 7.7596 & {8} & 7.7471 & {11} & 7.7401 & 3     & 7.7311 \\
-			{8} & 20.334 & {9} & 20.283 & {11} & 20.26 & {14} & 20.247 & 4     & 20.225 \\
-			{10} & 56.247 & {12} & 56.173 & {15} & 56.156 & {22} & 56.142 & 5     & 56.109 \\
-			\rowcolor{lightgray}{11} & 69.197 & {14} & 69.319 & {17} & 69.281 & {24} & 69.238 & 6     & 69.164 \\
-			{14} & 114.03 & {16} & 114.01 & {20} & 114.05 & {29} & 114.06 & 7     & 114.03 \\
-			\rowcolor{lightgray}{17} & 187.01 & {19} & 189.14 & {25} & 189.37 & {36} & 189.34 & 8     & 189.17 \\
-			{18} & 192.21 & {20} & 192.41 & {26} & 192.58 & {37} & 192.63 & 9     & 192.61 \\
-			{21} & 284.76 & {23} & 285.43 & {31} & 285.74 & {42} & 285.84 & 10    & 285.85 \\
-			{23} & 327.57 & {26} & 328.24 & {35} & 328.37 & {46} & 328.40 & 11    & 328.40 \\
-			\rowcolor{lightgray}{25} & 347.77 & {28} & 356.44 & {36} & 357.30 & {50} & 357.33 & 12    & 357.08 \\
-			{27} & 393.69 & {30} & 396.84 & {38} & 397.28 & {53} & 397.37 & 13    & 397.33 \\
-			{30} & 434.46 & {34} & 441.05 & {41} & 441.81 & {57} & 441.99 & 14    & 442.00 \\
-			\rowcolor{lightgray}{31} & 523.65 & {36} & 534.04 & {43} & 534.17 & {63} & 534.03 & 15    & 533.71 \\
-			{34} & 550.51 & {37} & 537.82 & {44} & 538.86 & {64} & 539.06 & 16    & 538.97 \\
-			\rowcolor{lightgray}{37} & 590.86 & {41} & 587.43 & {48} & 594.17 & {65} & 595.58 & 17    & 596.06 \\
-			{39} & 590.86 & {42} & 600.52 & {49} & 602.25 & {67} & 602.69 & 18    & 602.77 \\
-			\rowcolor{lightgray}{42} & 646.21 & {44} & 657.22 & {50} & 658.04 & {71} & 658.06 & 19    & 657.87 \\
-			{44} & 711.07 & {46} & 714.62 & {53} & 717.10 & {73} & 717.51 & 20    & 717.37 \\
-			\hline
-			\hline
-			\multicolumn{2}{|c|}{Max RE: \  2.6069\%} &\multicolumn{2}{c|}{Max RE: \ 1.4469\%}  & \multicolumn{2}{c|}{Max RE: \  0.38192\%}  & \multicolumn{2}{c||}{Max RE: \ 0.22301\%}& \multicolumn{2}{c|}{-} \\
-			\hline
-		\end{tabular}%
-		\label{tab:2v3_1}%
-	}}
-\end{table}%
-\FloatBarrier
-Table \ref{tab:2v3_1} show that the eigenvalues of the two-dimensional model compare very well to the three-dimensional model.
-The maximum relative error decreases significantly as $b$ is decreased.
-Even with $b = h$ the maximum relative error is still less than $2.7\%$.
-\\
-
-Table \ref{tab:2Dv3D_1_breakup} gives more information on the maximum relative error by separating the beam type and non-beam type eigenvalues.
-
-% Table generated by Excel2LaTeX from sheet 'Sheet2'
-\begin{table}[htbp]
-	\centering
-	\caption{****$h = 1/5$}
-	\begin{tabular}{|c|cccc|}
-		\hline
-		\multicolumn{5}{|c|}{Maximum Relative Error} \\
-		\hline
-		\hline
-		& {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
-		\hline
-		Beam Type & 2.1420 \% & 0.6804 \% & 0.38192 \% & 0.22301 \% \\
-		Non-Beam Type & 2.6069 \% & 1.4469 \% & 0.31546 \% & 0.11680 \% \\
-		\hline
-	\end{tabular}%
-	\label{tab:2Dv3D_1_breakup}%
-\end{table}%
-
-From Table \ref{tab:2Dv3D_1_breakup}, it is clear that indeed for beam type eigenvalues, a short two-dimensional beam compares very well to a short three-dimensional beam.\\
-
-\begin{table}[ht]
-	\scalebox{.8}{
-	\makebox[\textwidth]{
-	\caption{Comparsion of Eigenvalues with $h = 1/20$. The non beam-type eigenvalues are highlighted or omitted.}
-	\begin{tabular}{|cc|cc|cc|cc||cc|}
-		\hline
-		\multicolumn{10}{|c|}{Eigenvalues} \\
-		\hline
-		\hline
-		i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
-		\hline
-		{2} & 0.008043 & {2} & 0.008029 & {2} & 0.008023 & {3} & 0.00802 & {1} & {0.008013} \\
-		{3} & 0.3087 & {4} & 0.30816 & {5} & 0.30794 & {7} & 0.30785 & {2} & {0.30757} \\
-		{5} & 2.3357 & {8} & 2.3316 & {9} & 2.3300  & {12} & 2.3293 & {3} & {2.3273} \\
-		\rowcolor{lightgray}{8} & 7.7217 & {10} & 7.7156 & {13} & 7.7124 & {16} & 7.7111 & {4} & {7.7077} \\
-		{10} & 8.5387 & {11} & 8.5238 & {14} & 8.5182 & {18} & 8.516 & {5} & {8.5086} \\
-		{11} & 21.986 & {14} & 21.948 & {18} & 21.934 & {24} & 21.929 & {6} & {21.911} \\
-		{14} & 45.863 & {18} & 45.781 & {21} & 45.756 & {30} & 45.746 & {7} & {45.712} \\
-		\rowcolor{lightgray}{17} & 69.444 & {19} & 69.408 & {25} & 69.385 & {33} & 69.374 & {8} & {69.344} \\
-		{18} & 83.149 & {22} & 82.999 & {27} & 82.960 & {36} & 82.944 & {9} & {82.887} \\
-		{21} & 136.44 & {25} & 136.19 & {31} & 136.14 & {42} & 136.12 & {10} & {136.03} \\
-		\rowcolor{lightgray}{23} & 192.62 & {27} & 192.62 & {35} & 192.58 & {47} & 192.56 & {11} & {192.48} \\
-		{25} & 207.87 & {29} & 207.5 & {36} & 207.43 & {48} & 207.41 & {12} & {207.29} \\
-		{27} & 299.14 & {33} & 298.63 & {41} & 298.56 & {55} & 298.53 & {13} & {298.38} \\
-		\rowcolor{lightgray}{30} & 376.68 & {35} & 377.01 & {44} & 377.01 & {58} & 376.98 & {14} & {376.83} \\
-		{31} & 411.58 & {37} & 410.89 & {46} & 410.83 & {61} & 410.81 & {15} & {410.63} \\
-		{34} & 546.15 & {40} & 545.27 & {50} & 545.24 & {66} & 545.23 & {16} & {545.03} \\
-		\rowcolor{lightgray}{37} & 620.77 & {42} & 622.02 & {53} & 622.19 & {69} & 622.18 & {17} & {621.95} \\
-		{39} & 703.55 & {44} & 702.49 & {54} & 702.29 & {71} & 702.53 & {18} & {702.31} \\
-		{42} & 884.27 & {47} & 883.02 & {59} & 883.14 & {82} & 883.19 & {19} & {882.96} \\
-		\rowcolor{lightgray}{44} & 923.68 & {49} & 926.88 & {60} & 927.43 & {86} & 927.50 & {20} & {927.18} \\
-		\hline
-		\hline
-		\multicolumn{2}{|c|}{Max RE: \  0.37701\%} &\multicolumn{2}{c|}{Max RE: \ 0.19893\%}  & \multicolumn{2}{c|}{Max RE: \  0.12393\%}  & \multicolumn{2}{c||}{Max RE: \ 0.092843\%}& \multicolumn{2}{c|}{-} \\
-		\hline
-	\end{tabular}%
-	\label{tab:2v3_2}%
-}}
-\end{table}%
-\FloatBarrier
-
-In Table \ref{tab:2v3_2}, the eigenvalues are again compared for $h = 1/20$.
-The maximum relative error shows very impressive results for this case.
-The maximum relative error is less than $0.4\%$ and the maximum relative error decreases as $b$ is decreased.\\
-
-\begin{table}[htbp]
-	\centering
-	\caption{*****$h = 1/20$}
-	\begin{tabular}{|c|cccc|}
-		\hline
-		\multicolumn{5}{|c|}{Maximum Relative Error} \\
-		\hline
-		\hline
-		& {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
-		\hline
-		Beam Type & 0.37701 \% & 0.19893 \% & 0.12393 \% & 0.092843 \% \\
-		Non-Beam Type & 0.37682 \% & 0.10218 \% & 0.061213 \% & 0.043601 \% \\
-		\hline
-	\end{tabular}%
-	\label{tab:2v3_2_split}%
-\end{table}%
-\FloatBarrier
-
-Separating the errors of the beam-type eigenvalues and the non-beam type eigenvalues in Table \ref{tab:2v3_2_split}, just reaffirms the results.\\
-
-Restricting the models where $b \leq h$ yielded great results.
-It has been shown that the two-dimensional beam compares very well the the three-dimensional beam.
-The comparison also improves for smaller values of $h$.
-This is a similar result as seen with the work of \cite{LVV09} in the previous section.
-
-\subsection{$b > h$}
-Now we can ask the question what happens if $b > h$.
-Of course for very large values of $b$, the question should be asked is if the beam model is still relevant.
-Therefore, the investigation will look at an incremental increase of $b$, without making assumptions on the relevancy of a beam model.\\
-
-\FloatBarrier
-\begin{table}[htbp]
-	\scalebox{.8}{
-	\makebox[\textwidth]{
-		\caption{$h = 1/20$}
-		\begin{tabular}{|cc|cc|cc||cc|}
-			\hline
-			\multicolumn{8}{|c|}{Eigenvalues} \\
-			\hline
-			\hline
-			i     & {b = 2h} & i     & {b = 4h} & i     & {b = 8h} & j     & 2D \\
-			\hline
-			{2} & 0.008076 & {1} & 0.008162 & {1} & 0.008324 & 1     & 0.008013 \\
-			{3} & 0.30995 & {3} & 0.31298 & {3} & 0.31738 & 2     & 0.30757 \\
-			{5} & 2.3462 & {5} & 2.3737 & {6} & 2.4116 & 3     & 2.3273 \\
-			\rowcolor{lightgray}{8} & 7.7312 & {8} & 7.7471 & {9} & 7.7711 & 4     & 7.7077 \\
-			{10} & 8.5841 & {9} & 8.7082 & {10} & 8.7929 & 5     & 8.5086 \\
-			{11} & 22.124 & {12} & 22.491 & {14} & 23.222 & 6     & 21.911 \\
-			{14} & 46.195 & {14} & 47.003 & {18} & 47.921 & 7     & 45.712 \\
-			\rowcolor{lightgray}{17} & 69.454 & {17} & 69.281 & {22} & 72.307 & 8     & 69.344 \\
-			{18} & 83.822 & {18} & 85.218 & {24} & 80.607 & 9     & 82.887 \\
-			{21} & 137.43 & {21} & 138.58 & {32} & 140.97 & 10    & 136.03 \\
-			\hline
-			\hline
-			\multicolumn{2}{|c|}{Max RE: \  1.1289\%} &\multicolumn{2}{c|}{Max RE: \ 2.8261\%}  & \multicolumn{2}{c|}{Max RE: \  5.9821\%} & \multicolumn{2}{c|}{-} \\
-			\hline
-		\end{tabular}%
-		\label{tab:b>h}%
-	}}
-\end{table}
-\FloatBarrier
-In Table \ref{tab:b>h}, $h = 1/20$ was chosen since it was the beam case investigated in the previous section and $b$ is increased by a factor of $2$.
-And here we see that the maximum relative error increases almost by a factor of $2$ for each case.
-Note also that this table only shows the first 10 eigenvalues.\\
-
-There is also an increase of non-beam type eigenvalues that are only present in the three-dimensional model.\\
-
-In Table \ref{tab:b>h-split}, the maximum relative error of the beam-type and non-beam type eigenvalues are separated.
-\FloatBarrier
-\begin{table}[htbp]
-	\centering
-	\caption{$\alpha = 4800$}
-	\begin{tabular}{|c|ccc|}
-		\hline
-		\multicolumn{4}{|c|}{Maximum Relative Error} \\
-		\hline
-		\hline
-		& {b = 2h} & {b = 4h} & {b = 8h} \\
-		\hline
-		Beam Type & 1.1289 \% & 2.8261 \% & 5.9821 \% \\
-		Non-Beam Type & 0.30521 \% & 0.51096 \% & 4.2734 \% \\
-		\hline
-	\end{tabular}%
-	\label{tab:b>h-split}%
-\end{table}%
-\FloatBarrier
-
-From Table \ref{tab:b>h-split}, it is clear that as $b$ increases, the maximum relative error of the beam type eigenvalues increases and the two-dimensional model compares less to the three-dimensional model.\\
-
-In this section, it has been shown that the two-dimensional beam compares very well to the three-dimensional beam, in practical beam problems.
-Practical beam problems imply that $b \leq h$.
-The models also compare much better if $h$ is smaller.
-For values of  $b > h$, the use of a beam model should be questioned.\\
-
-For $b > h$, another model might be presented. In the next section, a Reisner-Mindlin plate model is investigated.
 \end{document}
-
-\begin{figure}[h!]\label{fig:compare:1D+2D}
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\caption{Side by side comparison of the beams.}
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\begin{tikzpicture}
-					\draw[line width = 0.3mm] (0,0) -- (7,0);
-
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});	
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});
-
-					%\node at (3.2,-0.2) {$\ell = 1$};
-				\end{tikzpicture}
-				\subcaption{Timoshenko Cantilever Beam}
-			\end{minipage}
-			\begin{minipage}[b]{0.8\linewidth}
-				\begin{tikzpicture}
-					\draw[line width = 0.2mm] (0,0.1) -- (7,0.1);
-					\draw[line width = 0.2mm] (0,-0.1) -- (7,-0.1);
-					\draw[line width = 0.2mm] (7,-0.1) -- (7,0.1);
-					\draw[line width = 0.2mm] (0,-0.1) -- (0,0.1);
-
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
-
-					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
-					\draw[scale=0.5, domain=-3:0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
-					\draw[scale=0.5, domain=-3:1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
-					\draw[scale=0.5, domain=-3:2.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
-
-					\draw[scale=0.5, domain=0.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
-					\draw[scale=0.5, domain=1.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
-					\draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
-
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});
-
-					\draw[line width = 0.1mm,->] (6,2) -- (7.4,2);
-					\draw[line width = 0.1mm,->] (6,2) -- (6,0.9);
-					\node at (6.7,1.8) {$e_1$};
-					\node at (5.8,1.4) {$e_2$};
-
-					\node at (7.2,0) {$h$};
-					%\node at (3.2,-0.3) {$\ell = 1$};
-
-				\end{tikzpicture}
-				\subcaption{Two-Dimensional Cantilever Beam}
-			\end{minipage}
-		}
-	}
-\end{figure}

### 2023-10-01 files/Chapter5/3D_FEM.tex
cleanup chapter 6
second part chapter 6

--- 2022-10-31 files/Chapter6/3D_FEM.tex
@@
 In section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3D-1V.
-For convenience, the relevant results from section \ref{ssec:3D_Model:VariationalForm} are repeated.
+For convenience, some results from section \ref{ssec:3D_Model:VariationalForm} are repeated here.
 
@@
 
-\subsubsection{Problem 3D-1E}
+\subsubsection{Problem 3D-1E}\label{3dFEM_EP}
 Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that

### 2023-10-01 files/Chapter6/Introduction.tex

@@
 \section{Introduction}
+This chapter is an investigation into the validity of a cantilever Timoshenko beam model and a cantilever Reissner-Mindlin plate model.
+Validity in this context refers to how well the solutions of a model compare to the solutions of a more realistic, higher-dimensional model.
+The investigation and application of the models are restricted to beam-type and plate-type problems.
+
+The following is a summary of the work covered in this chapter.
+
+Section \ref{sec:validity-of-a-cantilever-timoshenko-beam} is a discussion of the article \cite{LVV09}.
+In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
+This is an investigation into the validity of the Timoshenko beam model.
+The results of the article are replicated and the conclusions are verified.
+This chapter also include extra results to expand and add to the results of the article.
+The results of this section are also used as a referencefor the rest of the chapter.
+
+Section 7.3 extends the work of \cite{LVV09} further to a comparison of a cantilever two-dimensional beam to a cantilever three-dimensional beam.
+It is an investigation into the validity of the two-dimensional beam model.
+This extention is suggested by the authors of \cite{LVV09}.
+Although a direct comparison between the Timoshenko beam and the three-dimensional beam is preffered, there are complexities involved that makes this comparison difficult.
+Some of these complexities are discussed in more detail in the numerical results.
+The authors of \cite{LVV09} therefore suggest that the two-dimensional beam model is used as an intermediate step to validate the Timoshenko beam.
+
+Section 7.4 extends the work of \cite{LVV09} further to plate models.
+This extention follows the same idea as the previous sections, and originates from non-beam type behaviour observed in the three-dimensional beam model in Section 7.3.
+In this section, a cantilever two-dimensional Reisner-Mindlin plate model is compared to a cantilever three-dimensional plate model.
+Same as in the other sections, it is an investigation into the validity of the Reisner-Mindlin plate model.
+
+\subsection{Global parameters and configuration}
+All the models in this dissertation are assumed to be made of the same isotropic material and have a square cross-section. The parameters are as follows:
+
+\begin{itemize}
+  \item Elastic modulus ($G$): This is calculated using the formula $G = \frac{E}{2(1+\nu)}$, where $E$ is the modulus of elasticity and $\nu$ is Poisson's ratio.
+
+  \item Shear correction factor ($\kappa^2$): This is set to $5/6$, which is common for rectangular cross-sections.
+
+  \item Poisson's ratio ($\nu$): This is set to $0.3$, a typical value for materials like steel used in engineering.
+\end{itemize}
+
+These global parameters are used in all the models, and their consistency helps to ensure that any differences in the results can be attributed to the model structures themselves, rather than variations in the material or geometric properties.
+
+Since our models are all dimensionless, all of the beams and plates have a length of $\ell = 1$.
+We'll use $h$ to describe the height of the beams and plates, and $b$ to describe the width of the beams and plates.
+
+\subsection{Model specific parameters}
+The following are parameters that are not shared over all the models.
+These parameters can be unique to a model, or can be shared between some but not all of the models.
+These parameters mostly affect the geometry of the models.
+
+\subsubsection{Timoshenko beam}
+In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
+introduced. The paramater is given here again for convenience,
+\begin{eqnarray*}
+	\alpha = \frac{A\ell^2}{I}.
+\end{eqnarray*}
+
+The model is in a dimensionless form, therefore the length of the beam is $\ell = 1$.
+Since we assumed a square cross-section, the area of the cross-section can be calculated as $\displaystyle A = hb$.
+The area moment of inertia can also be calculated as $\displaystyle I = \frac{h^3b}{12}$.
+
+Substituting these values into the equation for $\alpha$ gives the following relationship between the height of the beam and the parameter $\alpha$,
+\begin{eqnarray}
+	\alpha & = & \frac{12}{h^2}, \label{eq:alpha-h-relationship}
+\end{eqnarray}
+or equivalently,
+\begin{eqnarray}
+	h & = & \sqrt{\frac{12}{\alpha}}. \label{eq:h-alpha-relationship}
+\end{eqnarray}
+
+These equations \eqref{eq:alpha-h-relationship} or \eqref{eq:h-alpha-relationship} describe the relationship between the height of the beam and the parameter $\alpha$.
+Using this relationship, the height of the beam model can be set by considering the value of $\alpha$.
+
+Some examples of values for $\alpha$ and the corresponding height of the beam that can be expected in this chapter, are given in Table \ref{tab:alphaheight} below.
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|c|c|}
+		\hline
+		$\alpha$ & $h$\\
+		\hline
+		$100$ & $\approx 0.35$ \\
+		$300$ & $1/5$ \\
+		$1200$ & $1/10$ \\
+		$4800$ & $1/20$ \\
+		$9600$ & $\approx 0.035$ \\
+		$10800$ & $1/30$ \\
+		\hline
+	\end{tabular}
+	\caption{Values of $\alpha$ and the corresponding height of the beam.}
+	\label{tab:alphaheight}
+\end{table}
+
+\subsubsection{Two-dimensional beam}
+
+For the two-dimensional beam, only the height parameter $h$ is required. The width of the beam $b$ is ommitted in this model, since the two-dimensional beam is a special case of plane stress.
+
+This special case of plane stress, simplifies the three-dimensional model (see section \ref{sec:2D_Model} In application, this two-dimensional beam can be interpreted as a vertical slice of the three-dimensional beam, where the width of the slice is infinitesimally small.
+Therefore there is no width parameter $b$ for the two-dimensional beam.
+
+\subsubsection{Three-dimensional beam}
+
+The three-dimensional beam is the most complex, realistic model and has two parameters to consider, the height $h$ and the width $b$.
+This model is also used for both the beam-type and plate-type problems.
+
+For beam-type problems, one would assume that the width of the beam not much larger than the height of the beam. The numerical results will show that this assumption is correct.
+
+On the other hand, for plate-type problems, the width of the plate is assumed to be much larger than the height of the plate. This assumption is also verified in the numerical results.
+
+\subsubsection{Reisner-Mindlin plate}
+The Reisner-Mindlin plate model is the most different model compared to the rest of the models in this dissertation.
+The Reisner-Mindlin plate model is derived in section \ref{sec:reissnermindlinplate}.
+The model has two parameters, the height $h$ and the width $b$.
+
+\subsection{Beam type and plate type problems}
+The investigation of this chapter, and this dissertation focuses on beam-type and plate-type problems. \textcolor{red}{**************expand**********}
 

### 2023-10-01 files/Chapter6/Validity_2D.tex

--- 2023-08-31 files/Chapter7/Beam.tex
@@
 \begin{document}
-\section{Validity of the Timoshenko beam model}
-In the article \cite{LVV09}, the authors show that a cantilever Timoshenko beam model can be a feasible model to replace a more realistic two-dimensional model for use in application.
-They also show that the dimensions of the beam will determine how well the one-dimensional Timoshenko beam compares to the two-dimensional beam.
-In this section, the results of the article is discussed, replicated and extended with more testcases.
+\section{Validity of a Two-dimensional beam} \label{sec:validity-of-a-cantilever-timoshenko-beam}
+This section is an extention of section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and the article \cite{LVV09}.
+As seen in the previous section, the two-dimensional model does have some characteristics that are not related to beam-type problems.
+This is also true for the three-dimensional model.
 
-Where \cite{LVV09} differs from most other research into the validity of the Timoshenko beam theory, is that the boundary conditions are also taken into consideration.
-The article serves as an intermediate step to comparing a Timoshenko beam to a three-dimensional beam.
-
-The authors use a cantilever beam with rectangular cross-section.
+The results in this section will show that the three-dimensional model has a lot of non-beam type eigenvalues.
+It is due to this reason, the authors of \cite{LVV09} suggested to use the two-dimensional model as an intermediate step.
+The the previous section, the validity of a cantilever Timoshenko beam was investigated using a cantilever two-dimensional beam as a reference.
+In this section, the validity of a cantilever two-dimensional beam will be investigated using a cantilever three-dimensional beam as a reference.
 
 \subsection{The models}
-Recall the cantilever Timoshenko beam model from section \ref{ssec:1D_Model:ModelProblems}, referred to as Problem T-2 and the cantilever two-dimensional beam model from section \ref{ssec:2D_Model:ModelProblem}, referred to as Problem 2D-1.
-In \cite{LVV09} it is assumed that the beams have a rectangular cross-section.\\
-
-Figure 6.1 shows the two beams side-by-side.
-
-\begin{figure}[h!]\label{fig:compare:1D+2D}
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\caption{Side by side comparison of the beams.}
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\begin{center}
-					\begin{tikzpicture}
-					\draw[line width = 0.4mm] (0,0) -- (6,0);
-
-					\node at (2.7,-0.25) {$\ell = 1$};
-
-					\draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
-					\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
-					\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
-					\draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
-					\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
-					\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
-					\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
-					\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
-					\draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);
-
-					\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
-					\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
-					\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
-					\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
-					\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
-					\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
-					\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
-					\draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
-
-					%\node at (3.2,-0.2) {$\ell = 1$};
-					\end{tikzpicture}
-				\end{center}
-				\subcaption{Timoshenko Cantilever Beam}
-			\end{minipage}
-			\begin{minipage}[b]{0.8\linewidth}
-				\begin{center}
-					\begin{tikzpicture}
-						\draw[line width = 0.4mm] (0,0.2) -- (6,0.2);
-						\draw[line width = 0.4mm] (0,-0.2) -- (6,-0.2);
-						\draw[line width = 0.4mm] (6,-0.2) -- (6,0.2);
-						%\draw[line width = 0.4mm] (0,-0.2) -- (0,0.2);
-
-						%\draw[line width = 0.1mm,->] (6,2) -- (7.4,2);
-						%\draw[line width = 0.1mm,->] (6,2) -- (6,0.9);
-						%\node at (6.7,1.8) {$e_1$};
-						%\node at (5.8,1.4) {$e_2$};
-
-						\node at (6.2,0) {$h$};
-						\node at (2.7,-0.45) {$\ell = 1$};
-
-						\draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
-						\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
-						\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
-						\draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
-						\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
-						\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
-						\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
-						\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
-						\draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);
-
-						\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
-						\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
-						\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
-						\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
-						\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
-						\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
-						\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
-						\draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
-
-						%\node at (3.2,-0.3) {$\ell = 1$};
-
-					\end{tikzpicture}
-				\end{center}
-				\subcaption{Two-Dimensional Cantilever Beam}
-			\end{minipage}
-		}
-	}
-\end{figure}
-
-In Chapter 1, the following parameters were defined.
-The parameter $h$ is the height of the two-dimensional beam and for the Timoshenko dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ was found.\\
-
-For the Timoshenko beam model with a rectangular cross-section, the area moment of inertial is calculated as
-\begin{eqnarray*}
-	I = \frac{h^3b}{12}.
-\end{eqnarray*}
-
-After substitution, the following relationship between $\alpha$ and $h$ is found
-\begin{eqnarray*}
-	h = \sqrt{\frac{12}{\alpha}}.
-\end{eqnarray*}
-Using this relationship, $\alpha$ can be chosen in such a way that the beams have equal lateral dimensions.
-
-\subsection{Accuracy of the numerical eigenvalues}
-To calculate the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} use the article \cite{VV06}.
-This article was discussed in section \ref{sec:Timo:EigenvalueProblem} in this dissertation.
-Using this article, the eigenvalues for the Timoshenko beam model can be numerically calculated to a desired accuracy level.
-
-A different approach is needed for the two-dimensional beam.
-The Finite Element Method is applied to the eigenvalue problem described in section \ref{sec:FEM:2D}.
-The following shows the rate of convergence of the first 20 eigenvalues using FEM and bi-cubic basis functions.
-
-\begin{figure}[H]
-	\begin{center}
-		\scalebox{1.4}{
-			\includegraphics[scale=0.7]{Convergence.png}
-			\caption{Rate of convergence of the first 20 eigenvalues.}
-			\label{fig:conv}
-		}
-	\end{center}	
-\end{figure}
-\textcolor{red}{FIX THIS}
-Figure \ref{fig:conv} show the maximum relative error of the first 10 eigenvalues of the two-dimensional beam.
-In \cite{LVV09}, the authors use a grid size of $40 \times 10$ with $h= 1/10$ (or $\alpha = 1200$) and $h = 1/5$ (or $\alpha = 300$).\\
-
- Figure \ref{fig:conv} show that this can be improved significantly.
-For each case of $h$, the grid size is calculated as $n \times \max\left\{\lceil\frac{n}{h}\rceil,10\right\}$.
-This ensures that the nodes are distributed somewhat evenly relative to the length-width ratio.
-For this chapter, the results of the Timoshenko beam and two-dimensional beam are given accurate up to 5 significant digits.
-
-\subsection{Comparing the shape of the eigenfunctions}
-Before the eigenvalues can be compared, a method is required to be able to match the eigenvalues of the two different models.
-The authors of \cite{LVV09} match the modal shapes of the eigenfunctions.
-The corresponding eigenvalues can then be matched.\\
-
-The eigenvalues of the Timoshenko beam, are referred to by the authors as beam-type eigenvalues.
-
-\subsubsection{Shapes relating to beam-type eigenvalues}
-The following figures are examples of beam-type mode shapes for the displacement $w$.
-
-\begin{figure}[h!]
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{Beam1.jpg}
-				\subcaption{2D Beam Type - $\lambda_6 = 21.911$}
-				\label{fig:minipage2}
-			\end{minipage}
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{1DBeam2.png}
-				\subcaption{Timoshenko - $\lambda_5 = 21.794$}
-				\label{fig:minipage1}
-			\end{minipage}
-	}}
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{Beam2.jpg}
-				\subcaption{2D Beam Type - $\lambda_7 = 45.711$}
-				\label{fig:minipage2}
-			\end{minipage}
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{1DBeam1.png}
-				\subcaption{Timoshenko - $\lambda_6 = 45.390$}
-				\label{fig:minipage1}
-			\end{minipage}
-			\caption{Modal shapes of the displacement $w$ for the beam-type 2D body and the Timoshenko beam with $\alpha = 4800$ ($h = 1/20$).}
-		}
-	}
-\end{figure}
-\FloatBarrier
-
-\subsubsection{Shapes relating to non-beam type eigenvalues}
-The following figures are examples of non beam-type mode shapes for the displacement $w$. These mode shapes are not present in the cantilever Timoshenko beam model and are not beam related. 
-\begin{figure}[h!]
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{NotBeam1.jpg}
-				\subcaption{Non-Beam Type - $\lambda_4 = 7.7077$}
-				\label{fig:minipage2}
-			\end{minipage}
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{NotBeam2.jpg}
-				\subcaption{Non-Beam Type - $\lambda_8 = 69.344$}
-				\label{fig:minipage1}
-			\end{minipage}
-			\caption{Modal shapes of the displacement $w$ for the non-beam type 2D body with $h = 1/20$.}
-		}
-	}
-\end{figure}
-\FloatBarrier
-
-The existence of these non-beam type eigenvalues imply that there are eigenvalues in the two-dimensional model, that are not in the Timoshenko beam model.
-This is an example of the complexities that arise when comparing models of different dimensions.
-
-\subsubsection{Shapes of the cross-section}
-The Timoshenko beam theory improve some one-dimensional beam theories such as the Euler-Bernoulli beam theory by also including the effect of shear.
-In the Timoshenko beam theory it is assumed that the cross-sections need not remain perpendicular to the neutral axis of the beam.
-The cross-sections however remain a straight line.\\
-
-For the two-dimensional beam, the shape of the cross-section can deform into a s-shape. This is explained in \cite{LVV09} and a similar figure in \cite{LVV09} is given here.
-\FloatBarrier
-\begin{figure}[h!]
-	\centering
-	\begin{tikzpicture}[scale=1.2]
-
-	\draw[line width = 0.4mm] (0,1) -- (7,1);
-	\draw[line width = 0.4mm] (0,-1) -- (7,-1);
-	\draw[line width = 0.4mm] (7,-1) -- (7,1);
-	\draw[line width = 0.4mm] (0,-1) -- (0,1);
-
-	\draw[line width = 0.1mm,dashed] (3.5,1) -- (3.5,-1);
-
-	\draw[thick] plot [smooth,tension=0.9] coordinates{(3.3,1) (3.7,0.5) (3.5,0) (3.3,-0.5) (3.7,-1)};
-
-	\draw[line width = 0.2mm,red] (3.3,1) -- (3.7,-1);
-
-\end{tikzpicture}
-	\caption{S-shape deformation of the cross-section.}\label{fig:s}
-\end{figure}
-
-Note that figure \ref{fig:s} shows an exaggerated example of the deformation of a cross-section.
-The red line shows how the average rotation of a cross-section is calculated in \cite{LVV09}.
-This average rotation can be used to compare the rotation of the cross-section of the two-dimensional beam to the rotation of the cross-section of the Timoshenko beam.
-\FloatBarrier
-
-\subsubsection{Direct comparison of mode shapes}
-Figure \ref{fig:w} shows the displacement of the material lines of the cantilever Timoshenko beam and the cantilever two-dimensional beam, compared directly.
-
-\begin{figure}[ht!]
-	\scalebox{.8}{
-		\makebox[\textwidth]{
-			\centering
-			\centering
-			\includegraphics[scale=0.4]{1Dv2D.png}
-			\caption{Comparison of the displacement $w$ mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
-			\label{fig:w}}}
-\end{figure}
-\FloatBarrier
-
-Similarly Figure \ref{fig:phi} shows the direct comparison of the angle of the cross-section of the cantilever Timoshenko beam and the two-dimensional beam.
-The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s} and \cite{LVV09}.
-
-\FloatBarrier
-\begin{figure}[ht!]
-	\scalebox{.8}{
-		\makebox[\textwidth]{
-			\centering
-			\centering
-			\includegraphics[scale=0.4]{1Dv2Dphi.png}
-			\caption{Comparison of the angle $\phi$ (best fit for 2D Beam) mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
-			\label{fig:phi}}}
-\end{figure}
-\FloatBarrier
-
-In \cite{LVV09} the authors obtained similar results for $\alpha=300$, which represents a short beam.
-Both figures \ref{fig:w} and \ref{fig:phi} were calculated with5 $\alpha = 4800$, which represents a longer, narrower beam.
-
-\subsubsection{Remark}
-The mode shapes were scaled to obtain figures \ref{fig:w} and \ref{fig:phi}. Therefore no scale is shown on the y-axis.
-
-\subsection{Comparing the eigenvalues}
-\subsubsection{Results of [LVV09]}
-The following table contains the results form \cite{LVV09} as well as the corresponding results obtained in this dissertation.
-\begin{table}[!ht]
-	\centering
-	\caption{Results from [LVV09] and results obtained in this dissertation. $0^a$ indicates a 0 as a result of rounding. $\alpha = 1200$}
-	\begin{tabular}{|c|c|c|c||c|c|c|c|}
-		\hline
-		\multicolumn{4}{|c||}{Results from [LVV09]} & \multicolumn{4}{c|}{Dissertation} \\ \hline \hline
-		~ & 2D & Timo & RE & ~ & 2D & Timo & RE  \\ \hline
-		1 & 0.0317 & 0.0316 & 0.00315 & 1 & 0.031713 & 0.031639 & 0.0023407  \\ 
-		2 & 1.14 & 1.14 & $0^a$ & 2 & 1.1413 & 1.1365 &  0.0042050 \\ 
-		3 & 7.72 & - & ~ & 3 & 7.7161 & - &   \\ 
-		4 & 7.92 & 7.86 & 0.00758 & 4 & 7.918 & 7.8617 & 0.0071116    \\ 
-		5 & 26.2 & 25.9 & 0.0115 & 5 & 26.148 & 25.869 & 0.010669  \\ 
-		6 & 60.8 & 59.9 & 0.0148 & 6 & 60.816 & 59.946 & 0.014303  \\ 
-		7 & 69.3 & - & ~ & 7 & 69.344 & - &    \\ 
-		8 & 115 & 113 & 0.0174 & 8 & 115.28 & 113.23 &  0.017787  \\ 
-		9 & 192 & 188 & 0.0208 & 9 & 191.57 & 187.55 &  0.020999  \\ 
-		10 & 192 & - &  & 10 & 192.03 & - &   \\ 
-		11 & 291 & 284 & 0.0241 & 11 & 290.76 & 283.81 &  0.023899  \\ \hline
-	\end{tabular}\label{Results_LVV09}
-\end{table}
-
-In Table \ref{Results_LVV09}, the results from \cite{LVV09} and the respective results from this dissertation is given.
-This table shows that the results of \cite{LVV09} can be replicated with more significant digits.\\
-
-Interestingly, with the improved accuracy over \cite{LVV09}, the relative errors remain similar in Table \ref{Results_LVV09}.
-It is possible that the higher level of accuracy will only benefit larger eigenvalues.
-Larger eigenvalues are however not of interest for practical applications.
-The 2nd relative error of \cite{LVV09} however could not be duplicated.
-
-\subsection{Comparison of the eigenvalues}
-In \cite{LVV09}, two values for $\alpha$ are considered.
-For $\alpha = 1200$, the Timoshenko beam has a length to width ratio of $1:10$.
-For $\alpha = 300$, the Timoshenko beam has length to width ratio of $1:5$.
-These two values represent a ``long slender'' beam and a ``short'' beam.\\
-
-In Table \ref{tab:Timo}, the eigenvalues of the Timoshenko beam are compared to the first 20 eigenvalues of the two-dimensional beam. The eigenvalues are calculated for different values of $\alpha$.\\
-
-\begin{table}[h!]
-	\scalebox{.8}{
-	\makebox[\textwidth]{
-	\caption{Eigenvalues of a Timoshenko cantilever beam vs the eigenvalues of a cantilever two-dimensional elastic body. RE - Relative Error}
-	\begin{tabular}{|cccc||cccc||cccc||cccc|}
-		\hline
-		\multicolumn{16}{|c|}{Comparison of Eigenvalues} \\
-		\hline\hline
-		\multicolumn{4}{|c||}{ $h = 1/5$ or $\alpha = 300$}       & \multicolumn{4}{c||}{$h =1/10$ or $\alpha = 1200$}      & \multicolumn{4}{c||}{$h = 1/20$ or $\alpha = 4800$}      & \multicolumn{4}{c|}{$h = 1/30$ or $\alpha = 10800$} \\
-		\hline
-		{i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} \\
-		\hline
-		{1}&0.12151&1&0.12092&1&0.031713&1&0.031639&1&0.008013&1&0.008004&1&0.003568&1&0.003565\\
-		{2}&3.5460&2&3.5071&2&1.1413&2     & 1.1365 & 2     & 0.30756 & 2     & 0.30705 & 2     & 0.13869 & 2     & 0.13855 \\
-		\cellcolor{lightgray}{3} & \cellcolor{lightgray}{7.7311} &       & {-} & \cellcolor{lightgray}{3}     & \cellcolor{lightgray}{7.7161} &       & {-} & 3     & 2.3273 & 3     & 2.3213 & 3     & 1.0698 & 3     & 1.0683 \\
-		{4} & 20.225 & 3     & 19.869 & 4     & 7.9180 & 3     & 7.8617 & \cellcolor{lightgray}{4}     & \cellcolor{lightgray}{7.7077} &       & {-} & 4     & 4.0140 & 4     & 4.0058 \\
-		{5} & 56.109 & 4     & 54.766 & 5     & 26.148 & 4     & 25.869 & 5     & 8.5086 & 4     & 8.4762 & \cellcolor{lightgray}{5}     & \cellcolor{lightgray}{7.7047} &       & {-} \\
-		\cellcolor{lightgray}{6} & \cellcolor{lightgray}{69.164} &       & {-} & 6     & 60.816 & 5     & 59.946 & 6     & 21.911 & 5     & 21.794 & 6     & 10.655 & 5     & 10.625 \\
-		{7} & 114.03 & 5     & 110.75 & \cellcolor{lightgray}{7}     & \cellcolor{lightgray}{69.344} &       & {-} & 7     & 45.711 & 6     & 45.390 & 7     & 22.975 & 6     & 22.890 \\
-		{8} & {189.17} &  6     & {186.50} & 8     & 115.28 & 6     & 113.23 & \cellcolor{lightgray}{8}     & \cellcolor{lightgray}{69.344} &       & {-} & 8     & 43.113 & 7     & 42.909 \\
-		\cellcolor{lightgray}{9} & \cellcolor{lightgray}{192.61} &      &  & {9}     & {191.57} &   7  & {187.55} & 9     & 82.887 & 7     & 82.154 & \cellcolor{lightgray}{9}     & \cellcolor{lightgray}{69.331} &       & {-} \\
-		{10} & 285.85 & 7     & 277.64 & \cellcolor{lightgray}{10}    & \cellcolor{lightgray}{192.03} &      & {-} & 10    & 136.03 & 8     & 134.58 & 10    & 73.230 & 8     & 72.803 \\
-		{11} & 328.40 & 8     & 330.29 & 11    & 290.76 & 8     & 283.81 & \cellcolor{lightgray}{11}    & \cellcolor{lightgray}{192.48} &       & {-} & 11    & 115.41 & 9     & 114.61 \\
-		\cellcolor{lightgray}{12} & \cellcolor{lightgray}{357.08} &       & {-} & \cellcolor{lightgray}{12}    & \cellcolor{lightgray}{374.45} &       & {-} & 12    & 207.29 & 9     & 204.69 & 12    & 171.61 & 10    & 170.20 \\
-		{13} & 397.33 & 9     & 394.02 & 13    & 413.20 & 9     & 402.27 & 13    & 298.38 & 10    & 294.10 & \cellcolor{lightgray}{13}    & \cellcolor{lightgray}{192.52} &       & {-} \\
-		{14} & 442.00   & 10    & 439.52 & 14    & 558.67 & 10    & 542.65 & \cellcolor{lightgray}{14}    & \cellcolor{lightgray}{376.83} &       & {-} & 14    & 243.56 & 11    & 241.26 \\
-		\cellcolor{lightgray}{15} & \cellcolor{lightgray}{533.71} &       & {-} & \cellcolor{lightgray}{15}    & \cellcolor{lightgray}{614.11} &       & {-} & 15    & 410.63 & 11    & 404.01 & 15    & 332.83 & 12    & 329.28 \\
-		{16} & 538.97 & 11    & 541.55 & 16    & 726.26 & 11    & 704.15 & 16    & 545.03 & 12    & 535.32 & \cellcolor{lightgray}{16}    & \cellcolor{lightgray}{377.16} &       & {-} \\
-		\cellcolor{lightgray}{17} & \cellcolor{lightgray}{596.06} &       & {-} & \cellcolor{lightgray}{17}    & \cellcolor{lightgray}{906.28} &       & {-} & \cellcolor{lightgray}{17}    & \cellcolor{lightgray}{621.95} &       & {-} & 17    & 440.77 & 13    & 435.51 \\
-		{18} & 602.77 & 12    & 596.09 & 18    & 913.69 & 12    & 884.92 & 18    & 702.30 & 13    & 688.64 & 18    & 568.51 & 14    & 561.04 \\
-		\cellcolor{lightgray}{19} & \cellcolor{lightgray}{657.87} &       & {-} & 19    & 1113.7 & 13    & 1080.1 & 19    & 882.95 & 14    & 864.40 & \cellcolor{lightgray}{19}    & \cellcolor{lightgray}{623.05} &       & {-} \\
-		{20} & 717.37 & 13    & 731.74 & \cellcolor{lightgray}{20}    & \cellcolor{lightgray}{1218.0}  &       & {-} & \cellcolor{lightgray}{20}    & \cellcolor{lightgray}{927.18} &       & {-} & 20    & 717.04 & 15    & 706.74 \\
-		\hline
-		\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{3.1718\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{3.1486\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{2.1018\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{1.4361\%} \\
-		\hline
-	\end{tabular}%
-	\label{tab:Timo}%
-}
-}
-\end{table}%
-\FloatBarrier
-
-The authors of \cite{LVV09} show that for $\alpha = 300$ the eigenvalues compare very well up to the 20th two-dimensional eigenvalue.
-This is also apparent for other values of $\alpha$ as Table \ref{tab:Timo} shows.
-In fact, the accuracy of the eigenvalues increases as $\alpha$ increases.
-The authors of \cite{LVV09} also mention that for $\alpha = 100$, the results are very good for the first 10 eigenvalues.\\
-
-Interestingly, the number of non-beam type eigenvalues within the first few eigenvalues decreases as $\alpha$ increases (or more relevant for the two-dimensional beam: as $h$ decreases).\\
-
-Overall, the relevant conclusions of \cite{LVV09} is verified.
-For practical applications of beam models, the Timoshenko beam can be used.
-Preferably for long slender beams as Table \ref{tab:Timo} shows.
-The authors also mention that nature of the disturbance should also be taken into consideration, mainly because the models are linear.\\
-
- The short comings of \cite{LVV09} is that damping is not considered.
-This is mentioned by the authors of \cite{LVV09}, but will not be addressed in this dissertation.
-Further work is to extend \cite{LVV09} to a three-dimensional comparison.
-This is investigated further in this chapter.\\
-
-\section{Validity of the two-dimensional elastic model}
-In this section, the validity of a two-dimensional cantilever beam is investigated. This is an extension of the work in \cite{LVV09}, as mentioned in the article.\\
-
-As explained before, the two-dimensional model is used as a intermediate step between the Timoshenko and three-dimensional beam.
-The same method as in \cite{LVV09} will be used to investigate the validity of the two-dimensional model.\\
-
-The models for the two-dimensional and three-dimensional beams are defined in section \ref{ssec:2D_Model:ModelProblem} and \ref{ssec:3D_Model:ModelProblems} respectively.
-These models are elastic bodies and not specifically beam models.
-Therefore it is expected to find eigenvalue and eigenfunction pairs that does not relate to beam type problems.
-This was already seen with the two-dimensional model in the previous section.
-These not beam type eigenvalues are calculated in this section, however the focus still remains on beam type problems.\\
-
-\subsection{The models}
-Recall a cantilever two-dimensional beam, referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.\\
+The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in section \ref{ssec:2D_Model:ModelProblem}.
+From section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D-1.
 
@@
 
-For both models the parameter $h$ represents the width of the beams.
-The three-dimensional model also have depth $b$.
-Intuitively, from the figure, the two-dimensional beam should compare better to the three-dimensional beam for smaller $b$.
+\subsection{Calculating the eigenvalues}
+Similar to calculating the eiegnvalues of the two-dimensional beam, to calculate the eigenvalues of the three-dimensional beam, the Finite Element Method is used.
+In section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived.
+Section \ref{3dFEM_EP} gives the following eigenvalue problem for the three-dimensional beam:
 
-\subsection{Accuracy of the numerical eigenvalues}
-Similar to how the eigenvalues and eigenfunctions of the two-dimensional model calculated in the previous section, the eigenvalues and eigenfunctions can be calculated for the three-dimensional model.
-The numerical formula to calculate the eigenvalues and eigenfunctions are derived in section \ref{sec:FEM:3D}.\\
+\subsubsection{Problem 3D-1E}
+Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
+\begin{eqnarray}
+	K\bar{u} & = & M\lambda{\bar{u}},
+\end{eqnarray} where $K$ and $M$ are the standard Finite Element Matrices for tri-cubic basis functions. The definition of the matrices are given in section \ref{sec:FEM:3D}.
 
-Using piecewise tri-cubic basis functions, the following results were obtained.\\
+\subsubsection{Accuracy of the eigenvalues}
+Figure \ref{fig:conv_3d_eig} show the rate of convergence of the first 20 eigenvalues of Problem 3D-1E.
 
-\begin{tikzpicture}
-	\begin{axis}[width=0.9\textwidth,
-				 xlabel=Iteration Number,
-				 ylabel=Error,
-				 ymode=log,
-				 legend pos=south east]
-	\addplot[color=blue, mark=o] coordinates {
-		(1,0.1)
-		(2,0.05)
-		(3,0.01)
-		(4,0.005)
-	};
-	\addlegendentry{$h=1/5$}
+\begin{figure}[H]
+    \centering
+    \begin{adjustbox}{center}
+        \includegraphics[scale=0.7]{Convergence.png}
+    \end{adjustbox}
+    \caption{Rate of convergence of the first 20 eigenvalues.}
+    \label{fig:conv_3d_eig}
+\end{figure}
+\textcolor{red}{Update this figure.}
 
-	\addplot[color=red, mark=o] coordinates {
-		(1,0.2)
-		(2,0.1)
-		(3,0.05)
-		(4,0.02)
-	};
-	\addlegendentry{$h=1/10$}
-
-	\addplot[color=green, mark=o] coordinates {
-		(1,0.2)
-		(2,0.1)
-		(3,0.05)
-		(4,0.02)
-	};
-	\addlegendentry{$h=1/20$}
-
-	\addplot[color=black, mark=o] coordinates {
-		(1,0.3)
-		(2,0.3)
-		(3,0.03)
-		(4,0.03)
-	};
-	\addlegendentry{$h=1/30$}
-
-	\end{axis}
-	\end{tikzpicture}
+Similar to the two-dimensional case, the number of elements can be chosen so that at least the first 10 eigenvalues are accurate to 5 significant digits.
 
 \subsection{Comparing the mode shapes}
-Identical to the method used in \cite{LVV09} and the previous section, the eigenvalues of the two models can be matched by comparing the mode shapes.
-As mentioned earlier, it is expected that there will be mode shapes not related to beam type problems, and also mode shapes that the three-dimensional model do not share with the two-dimensional model.\\
-
-In this section, examples of the different mode shapes are shown.
+The method to match up the eigenvalues remains the same as in the previous section.
+Since the three-dimensional model is more complex, there are more mode shapes that do no appear in the Timoshenko model or two-dimensional model.
+The focus remains on beam-type problems, so the mode shapes relating to beam type problems are most important.
 
@@
 
-Figure \ref{fig:minipage11} looks similar to the beam type eigenvalues, however the shape is in the $x-z$ axis.\\
+\subsection{Comparing the eigenvalues}
+The eigenvalues of the two models can now be compared. Recall from the introduction, that the two-dimensional and three-dimensional models have different paramaters.
 
-\subsection{Comparing the eigenvalues}
-The eigenvalues can now be compared.
-In the tables of this subsection, the eigenvalues of the two-dimensional beam are compared to the eigenvalues of the three-dimensional beam.
-Since there are two parameters to consider, $h$ and $b$, only a few cases are considered.\\
+The two-dimensional model has the single paramater $h$ representing the height of the beam.
+The three-dimensional model has two parameters, $h$ and $b$, representing the height and width of the beam respectively.
 
-The three-dimensional beam has more eigenvalues than the two-dimensional beam for the range considered in this investigation.
-Since the interest is in the comparison of the two models, the eigenvalues of the three-dimensional that are not present in the two-dimensional beam are omitted from the tables.\\
-
-The eigenvalues for beam type problems, the main focus of this investigation, are highlighted in the tables.\\
-
-The cases considered are similar to the cases in \cite{LVV09}, a short beam and a slender beam.
-For the short beam, $h = 1/5$ and for the slender beam, $h = 1/20$.
-The parameter $b$ will be varied to test the accuracy.
-For now the results are restricted to $b \leq h$.
-The other cases will be discussed later.\\
-
-\subsubsection*{Case $b < h$:}
-
-\begin{table}[htbp]
-	\scalebox{.8}{
-	\makebox[\textwidth]{
-		\caption{Comparsion of Eigenvalues with $h = 1/5$.}
-		\begin{tabular}{|cc|cc|cc|cc||cc|}
-			\hline
-			\multicolumn{10}{|c|}{Eigenvalues} \\
-			\hline
-			\hline
-			i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
-			\hline
-			{2} & 0.12307 & {2} & 0.12234 & {2} & 0.12198 & {3} & 0.12178 & 1     & 0.12151 \\
-			{3} & 3.5773 & {5} & 3.5630 & {6} & 3.5558 & {8} & 3.5519 & 2     & 3.5460 \\
-			\rowcolor{lightgray}{5} & 7.7799 & {6} & 7.7596 & {8} & 7.7471 & {11} & 7.7401 & 3     & 7.7311 \\
-			{8} & 20.334 & {9} & 20.283 & {11} & 20.26 & {14} & 20.247 & 4     & 20.225 \\
-			{10} & 56.247 & {12} & 56.173 & {15} & 56.156 & {22} & 56.142 & 5     & 56.109 \\
-			\rowcolor{lightgray}{11} & 69.197 & {14} & 69.319 & {17} & 69.281 & {24} & 69.238 & 6     & 69.164 \\
-			{14} & 114.03 & {16} & 114.01 & {20} & 114.05 & {29} & 114.06 & 7     & 114.03 \\
-			\rowcolor{lightgray}{17} & 187.01 & {19} & 189.14 & {25} & 189.37 & {36} & 189.34 & 8     & 189.17 \\
-			{18} & 192.21 & {20} & 192.41 & {26} & 192.58 & {37} & 192.63 & 9     & 192.61 \\
-			{21} & 284.76 & {23} & 285.43 & {31} & 285.74 & {42} & 285.84 & 10    & 285.85 \\
-			{23} & 327.57 & {26} & 328.24 & {35} & 328.37 & {46} & 328.40 & 11    & 328.40 \\
-			\rowcolor{lightgray}{25} & 347.77 & {28} & 356.44 & {36} & 357.30 & {50} & 357.33 & 12    & 357.08 \\
-			{27} & 393.69 & {30} & 396.84 & {38} & 397.28 & {53} & 397.37 & 13    & 397.33 \\
-			{30} & 434.46 & {34} & 441.05 & {41} & 441.81 & {57} & 441.99 & 14    & 442.00 \\
-			\rowcolor{lightgray}{31} & 523.65 & {36} & 534.04 & {43} & 534.17 & {63} & 534.03 & 15    & 533.71 \\
-			{34} & 550.51 & {37} & 537.82 & {44} & 538.86 & {64} & 539.06 & 16    & 538.97 \\
-			\rowcolor{lightgray}{37} & 590.86 & {41} & 587.43 & {48} & 594.17 & {65} & 595.58 & 17    & 596.06 \\
-			{39} & 590.86 & {42} & 600.52 & {49} & 602.25 & {67} & 602.69 & 18    & 602.77 \\
-			\rowcolor{lightgray}{42} & 646.21 & {44} & 657.22 & {50} & 658.04 & {71} & 658.06 & 19    & 657.87 \\
-			{44} & 711.07 & {46} & 714.62 & {53} & 717.10 & {73} & 717.51 & 20    & 717.37 \\
-			\hline
-			\hline
-			\multicolumn{2}{|c|}{Max RE: \  2.6069\%} &\multicolumn{2}{c|}{Max RE: \ 1.4469\%}  & \multicolumn{2}{c|}{Max RE: \  0.38192\%}  & \multicolumn{2}{c||}{Max RE: \ 0.22301\%}& \multicolumn{2}{c|}{-} \\
-			\hline
-		\end{tabular}%
-		\label{tab:2v3_1}%
-	}}
-\end{table}%
-\FloatBarrier
-Table \ref{tab:2v3_1} show that the eigenvalues of the two-dimensional model compare very well to the three-dimensional model.
-The maximum relative error decreases significantly as $b$ is decreased.
-Even with $b = h$ the maximum relative error is still less than $2.7\%$.
-\\
-
-Table \ref{tab:2Dv3D_1_breakup} gives more information on the maximum relative error by separating the beam type and non-beam type eigenvalues.
-
-% Table generated by Excel2LaTeX from sheet 'Sheet2'
-\begin{table}[htbp]
-	\centering
-	\caption{****$h = 1/5$}
-	\begin{tabular}{|c|cccc|}
-		\hline
-		\multicolumn{5}{|c|}{Maximum Relative Error} \\
-		\hline
-		\hline
-		& {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
-		\hline
-		Beam Type & 2.1420 \% & 0.6804 \% & 0.38192 \% & 0.22301 \% \\
-		Non-Beam Type & 2.6069 \% & 1.4469 \% & 0.31546 \% & 0.11680 \% \\
-		\hline
-	\end{tabular}%
-	\label{tab:2Dv3D_1_breakup}%
-\end{table}%
-
-From Table \ref{tab:2Dv3D_1_breakup}, it is clear that indeed for beam type eigenvalues, a short two-dimensional beam compares very well to a short three-dimensional beam.\\
-
-\begin{table}[ht]
-	\scalebox{.8}{
-	\makebox[\textwidth]{
-	\caption{Comparsion of Eigenvalues with $h = 1/20$. The non beam-type eigenvalues are highlighted or omitted.}
-	\begin{tabular}{|cc|cc|cc|cc||cc|}
-		\hline
-		\multicolumn{10}{|c|}{Eigenvalues} \\
-		\hline
-		\hline
-		i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
-		\hline
-		{2} & 0.008043 & {2} & 0.008029 & {2} & 0.008023 & {3} & 0.00802 & {1} & {0.008013} \\
-		{3} & 0.3087 & {4} & 0.30816 & {5} & 0.30794 & {7} & 0.30785 & {2} & {0.30757} \\
-		{5} & 2.3357 & {8} & 2.3316 & {9} & 2.3300  & {12} & 2.3293 & {3} & {2.3273} \\
-		\rowcolor{lightgray}{8} & 7.7217 & {10} & 7.7156 & {13} & 7.7124 & {16} & 7.7111 & {4} & {7.7077} \\
-		{10} & 8.5387 & {11} & 8.5238 & {14} & 8.5182 & {18} & 8.516 & {5} & {8.5086} \\
-		{11} & 21.986 & {14} & 21.948 & {18} & 21.934 & {24} & 21.929 & {6} & {21.911} \\
-		{14} & 45.863 & {18} & 45.781 & {21} & 45.756 & {30} & 45.746 & {7} & {45.712} \\
-		\rowcolor{lightgray}{17} & 69.444 & {19} & 69.408 & {25} & 69.385 & {33} & 69.374 & {8} & {69.344} \\
-		{18} & 83.149 & {22} & 82.999 & {27} & 82.960 & {36} & 82.944 & {9} & {82.887} \\
-		{21} & 136.44 & {25} & 136.19 & {31} & 136.14 & {42} & 136.12 & {10} & {136.03} \\
-		\rowcolor{lightgray}{23} & 192.62 & {27} & 192.62 & {35} & 192.58 & {47} & 192.56 & {11} & {192.48} \\
-		{25} & 207.87 & {29} & 207.5 & {36} & 207.43 & {48} & 207.41 & {12} & {207.29} \\
-		{27} & 299.14 & {33} & 298.63 & {41} & 298.56 & {55} & 298.53 & {13} & {298.38} \\
-		\rowcolor{lightgray}{30} & 376.68 & {35} & 377.01 & {44} & 377.01 & {58} & 376.98 & {14} & {376.83} \\
-		{31} & 411.58 & {37} & 410.89 & {46} & 410.83 & {61} & 410.81 & {15} & {410.63} \\
-		{34} & 546.15 & {40} & 545.27 & {50} & 545.24 & {66} & 545.23 & {16} & {545.03} \\
-		\rowcolor{lightgray}{37} & 620.77 & {42} & 622.02 & {53} & 622.19 & {69} & 622.18 & {17} & {621.95} \\
-		{39} & 703.55 & {44} & 702.49 & {54} & 702.29 & {71} & 702.53 & {18} & {702.31} \\
-		{42} & 884.27 & {47} & 883.02 & {59} & 883.14 & {82} & 883.19 & {19} & {882.96} \\
-		\rowcolor{lightgray}{44} & 923.68 & {49} & 926.88 & {60} & 927.43 & {86} & 927.50 & {20} & {927.18} \\
-		\hline
-		\hline
-		\multicolumn{2}{|c|}{Max RE: \  0.37701\%} &\multicolumn{2}{c|}{Max RE: \ 0.19893\%}  & \multicolumn{2}{c|}{Max RE: \  0.12393\%}  & \multicolumn{2}{c||}{Max RE: \ 0.092843\%}& \multicolumn{2}{c|}{-} \\
-		\hline
-	\end{tabular}%
-	\label{tab:2v3_2}%
-}}
-\end{table}%
-\FloatBarrier
-
-In Table \ref{tab:2v3_2}, the eigenvalues are again compared for $h = 1/20$.
-The maximum relative error shows very impressive results for this case.
-The maximum relative error is less than $0.4\%$ and the maximum relative error decreases as $b$ is decreased.\\
-
-\begin{table}[htbp]
-	\centering
-	\caption{*****$h = 1/20$}
-	\begin{tabular}{|c|cccc|}
-		\hline
-		\multicolumn{5}{|c|}{Maximum Relative Error} \\
-		\hline
-		\hline
-		& {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
-		\hline
-		Beam Type & 0.37701 \% & 0.19893 \% & 0.12393 \% & 0.092843 \% \\
-		Non-Beam Type & 0.37682 \% & 0.10218 \% & 0.061213 \% & 0.043601 \% \\
-		\hline
-	\end{tabular}%
-	\label{tab:2v3_2_split}%
-\end{table}%
-\FloatBarrier
-
-Separating the errors of the beam-type eigenvalues and the non-beam type eigenvalues in Table \ref{tab:2v3_2_split}, just reaffirms the results.\\
-
-Restricting the models where $b \leq h$ yielded great results.
-It has been shown that the two-dimensional beam compares very well the the three-dimensional beam.
-The comparison also improves for smaller values of $h$.
-This is a similar result as seen with the work of \cite{LVV09} in the previous section.
-
-\subsection{$b > h$}
-Now we can ask the question what happens if $b > h$.
-Of course for very large values of $b$, the question should be asked is if the beam model is still relevant.
-Therefore, the investigation will look at an incremental increase of $b$, without making assumptions on the relevancy of a beam model.\\
-
-\FloatBarrier
-\begin{table}[htbp]
-	\scalebox{.8}{
-	\makebox[\textwidth]{
-		\caption{$h = 1/20$}
-		\begin{tabular}{|cc|cc|cc||cc|}
-			\hline
-			\multicolumn{8}{|c|}{Eigenvalues} \\
-			\hline
-			\hline
-			i     & {b = 2h} & i     & {b = 4h} & i     & {b = 8h} & j     & 2D \\
-			\hline
-			{2} & 0.008076 & {1} & 0.008162 & {1} & 0.008324 & 1     & 0.008013 \\
-			{3} & 0.30995 & {3} & 0.31298 & {3} & 0.31738 & 2     & 0.30757 \\
-			{5} & 2.3462 & {5} & 2.3737 & {6} & 2.4116 & 3     & 2.3273 \\
-			\rowcolor{lightgray}{8} & 7.7312 & {8} & 7.7471 & {9} & 7.7711 & 4     & 7.7077 \\
-			{10} & 8.5841 & {9} & 8.7082 & {10} & 8.7929 & 5     & 8.5086 \\
-			{11} & 22.124 & {12} & 22.491 & {14} & 23.222 & 6     & 21.911 \\
-			{14} & 46.195 & {14} & 47.003 & {18} & 47.921 & 7     & 45.712 \\
-			\rowcolor{lightgray}{17} & 69.454 & {17} & 69.281 & {22} & 72.307 & 8     & 69.344 \\
-			{18} & 83.822 & {18} & 85.218 & {24} & 80.607 & 9     & 82.887 \\
-			{21} & 137.43 & {21} & 138.58 & {32} & 140.97 & 10    & 136.03 \\
-			\hline
-			\hline
-			\multicolumn{2}{|c|}{Max RE: \  1.1289\%} &\multicolumn{2}{c|}{Max RE: \ 2.8261\%}  & \multicolumn{2}{c|}{Max RE: \  5.9821\%} & \multicolumn{2}{c|}{-} \\
-			\hline
-		\end{tabular}%
-		\label{tab:b>h}%
-	}}
-\end{table}
-\FloatBarrier
-In Table \ref{tab:b>h}, $h = 1/20$ was chosen since it was the beam case investigated in the previous section and $b$ is increased by a factor of $2$.
-And here we see that the maximum relative error increases almost by a factor of $2$ for each case.
-Note also that this table only shows the first 10 eigenvalues.\\
-
-There is also an increase of non-beam type eigenvalues that are only present in the three-dimensional model.\\
-
-In Table \ref{tab:b>h-split}, the maximum relative error of the beam-type and non-beam type eigenvalues are separated.
-\FloatBarrier
-\begin{table}[htbp]
-	\centering
-	\caption{$\alpha = 4800$}
-	\begin{tabular}{|c|ccc|}
-		\hline
-		\multicolumn{4}{|c|}{Maximum Relative Error} \\
-		\hline
-		\hline
-		& {b = 2h} & {b = 4h} & {b = 8h} \\
-		\hline
-		Beam Type & 1.1289 \% & 2.8261 \% & 5.9821 \% \\
-		Non-Beam Type & 0.30521 \% & 0.51096 \% & 4.2734 \% \\
-		\hline
-	\end{tabular}%
-	\label{tab:b>h-split}%
-\end{table}%
-\FloatBarrier
-
-From Table \ref{tab:b>h-split}, it is clear that as $b$ increases, the maximum relative error of the beam type eigenvalues increases and the two-dimensional model compares less to the three-dimensional model.\\
-
-In this section, it has been shown that the two-dimensional beam compares very well to the three-dimensional beam, in practical beam problems.
-Practical beam problems imply that $b \leq h$.
-The models also compare much better if $h$ is smaller.
-For values of  $b > h$, the use of a beam model should be questioned.\\
-
-For $b > h$, another model might be presented. In the next section, a Reisner-Mindlin plate model is investigated.
 \end{document}
-
-\begin{figure}[h!]\label{fig:compare:1D+2D}
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\caption{Side by side comparison of the beams.}
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\begin{tikzpicture}
-					\draw[line width = 0.3mm] (0,0) -- (7,0);
-
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});	
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});
-
-					%\node at (3.2,-0.2) {$\ell = 1$};
-				\end{tikzpicture}
-				\subcaption{Timoshenko Cantilever Beam}
-			\end{minipage}
-			\begin{minipage}[b]{0.8\linewidth}
-				\begin{tikzpicture}
-					\draw[line width = 0.2mm] (0,0.1) -- (7,0.1);
-					\draw[line width = 0.2mm] (0,-0.1) -- (7,-0.1);
-					\draw[line width = 0.2mm] (7,-0.1) -- (7,0.1);
-					\draw[line width = 0.2mm] (0,-0.1) -- (0,0.1);
-
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
-
-					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
-					\draw[scale=0.5, domain=-3:0.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
-					\draw[scale=0.5, domain=-3:1.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
-					\draw[scale=0.5, domain=-3:2.5, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
-
-					\draw[scale=0.5, domain=0.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
-					\draw[scale=0.5, domain=1.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
-					\draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
-
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
-					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});
-
-					\draw[line width = 0.1mm,->] (6,2) -- (7.4,2);
-					\draw[line width = 0.1mm,->] (6,2) -- (6,0.9);
-					\node at (6.7,1.8) {$e_1$};
-					\node at (5.8,1.4) {$e_2$};
-
-					\node at (7.2,0) {$h$};
-					%\node at (3.2,-0.3) {$\ell = 1$};
-
-				\end{tikzpicture}
-				\subcaption{Two-Dimensional Cantilever Beam}
-			\end{minipage}
-		}
-	}
-\end{figure}

### 2023-10-01 files/Chapter6/Validity_2D.tex
v2 chapter 7.2, started 7.3

@@
 \begin{document}
-\section{Validity of a Two-dimensional beam} \label{sec:validity-of-a-cantilever-timoshenko-beam}
+\section{Validity of a Two-dimensional beam} \label{sec:validity-of-a-2d-beam}
 This section is an extention of section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and the article \cite{LVV09}.
@@
 \subsection{Calculating the eigenvalues}
-Similar to calculating the eiegnvalues of the two-dimensional beam, to calculate the eigenvalues of the three-dimensional beam, the Finite Element Method is used.
+Similar to calculating the eigenvalues of the two-dimensional beam, to calculate the eigenvalues of the three-dimensional beam, the Finite Element Method is used.
 In section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived.
 Section \ref{3dFEM_EP} gives the following eigenvalue problem for the three-dimensional beam:
+
+\subsubsection{Problem 2D-1E}
+Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
+\begin{eqnarray}
+	K\bar{u} & = & M\lambda{\bar{u}},
+\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices for bi-cubic basis functions. The definition of the matrices are given in section \ref{sec:FEM:2D}.
 
@@
 	K\bar{u} & = & M\lambda{\bar{u}},
-\end{eqnarray} where $K$ and $M$ are the standard Finite Element Matrices for tri-cubic basis functions. The definition of the matrices are given in section \ref{sec:FEM:3D}.
+\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices for tri-cubic basis functions. The definition of the matrices are given in section \ref{sec:FEM:3D}.
 
@@
 
-The two-dimensional model has the single paramater $h$ representing the height of the beam.
+The two-dimensional model has the single parameter $h$ representing the height of the beam.
 The three-dimensional model has two parameters, $h$ and $b$, representing the height and width of the beam respectively.
+There are thus infinite possibilities for combinations of parameters that can be considered.
+However only a small number of combinations need to be considered to show that the two-dimensional model is a good approximation of the three-dimensional model.
+
+For $h$, the values used in the previous section will be used.
+These values covers a range of beam shapes from a short fat beam, to a long slender beam with respect to the length to height ratio.
+For a short and fat beam, consider $h = 1/5$ and for a long and slender beam, consider $h = 1/20$.
+
+For $b$, two different cases will be considered. The first case is for $b <= h$, and the $b>h$. Incremental increase/decrease of $b$ will then be used to compare the models.
+
+In all of the tables to follow, the non-beam type eigenvalues that are not present in the two-dimensional model are omitted.
+The beam and non-beam type eigenvalues that both models share are included, with the non-beam type eigenvalues highlighted in grey.
+
+\subsubsection*{Case $b < h$:}
+Intuitively, for this case the two-dimensional model should be a good approximation of the three-dimensional model when considering the shape and definition of the two-dimensional model.
+
+Table \ref{ab:2v3_1} below compares the eigenvalues of the models for a beam with a small length to height ratio of $h=1/5$ with decreasing values of $b$.
+
+\begin{table}[htbp]
+	\scalebox{.8}{
+	\makebox[\textwidth]{
+		\caption{Comparsion of Eigenvalues with $h = 1/5$, with decreasing $b$ and $b < h$.}
+		\begin{tabular}{|cc|cc|cc|cc||cc|}
+			\hline
+			\multicolumn{10}{|c|}{Eigenvalues} \\
+			\hline
+			\hline
+			i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
+			\hline
+			{2} & 0.12307 & {2} & 0.12234 & {2} & 0.12198 & {3} & 0.12178 & 1     & 0.12151 \\
+			{3} & 3.5773 & {5} & 3.5630 & {6} & 3.5558 & {8} & 3.5519 & 2     & 3.5460 \\
+			\rowcolor{lightgray}{5} & 7.7799 & {6} & 7.7596 & {8} & 7.7471 & {11} & 7.7401 & 3     & 7.7311 \\
+			{8} & 20.334 & {9} & 20.283 & {11} & 20.26 & {14} & 20.247 & 4     & 20.225 \\
+			{10} & 56.247 & {12} & 56.173 & {15} & 56.156 & {22} & 56.142 & 5     & 56.109 \\
+			\rowcolor{lightgray}{11} & 69.197 & {14} & 69.319 & {17} & 69.281 & {24} & 69.238 & 6     & 69.164 \\
+			{14} & 114.03 & {16} & 114.01 & {20} & 114.05 & {29} & 114.06 & 7     & 114.03 \\
+			\rowcolor{lightgray}{17} & 187.01 & {19} & 189.14 & {25} & 189.37 & {36} & 189.34 & 8     & 189.17 \\
+			{18} & 192.21 & {20} & 192.41 & {26} & 192.58 & {37} & 192.63 & 9     & 192.61 \\
+			{21} & 284.76 & {23} & 285.43 & {31} & 285.74 & {42} & 285.84 & 10    & 285.85 \\
+			{23} & 327.57 & {26} & 328.24 & {35} & 328.37 & {46} & 328.40 & 11    & 328.40 \\
+			\rowcolor{lightgray}{25} & 347.77 & {28} & 356.44 & {36} & 357.30 & {50} & 357.33 & 12    & 357.08 \\
+			{27} & 393.69 & {30} & 396.84 & {38} & 397.28 & {53} & 397.37 & 13    & 397.33 \\
+			{30} & 434.46 & {34} & 441.05 & {41} & 441.81 & {57} & 441.99 & 14    & 442.00 \\
+			\rowcolor{lightgray}{31} & 523.65 & {36} & 534.04 & {43} & 534.17 & {63} & 534.03 & 15    & 533.71 \\
+			{34} & 550.51 & {37} & 537.82 & {44} & 538.86 & {64} & 539.06 & 16    & 538.97 \\
+			\rowcolor{lightgray}{37} & 590.86 & {41} & 587.43 & {48} & 594.17 & {65} & 595.58 & 17    & 596.06 \\
+			{39} & 590.86 & {42} & 600.52 & {49} & 602.25 & {67} & 602.69 & 18    & 602.77 \\
+			\rowcolor{lightgray}{42} & 646.21 & {44} & 657.22 & {50} & 658.04 & {71} & 658.06 & 19    & 657.87 \\
+			{44} & 711.07 & {46} & 714.62 & {53} & 717.10 & {73} & 717.51 & 20    & 717.37 \\
+			\hline
+			\hline
+			\multicolumn{2}{|c|}{Max RE: \  2.6069\%} &\multicolumn{2}{c|}{Max RE: \ 1.4469\%}  & \multicolumn{2}{c|}{Max RE: \  0.38192\%}  & \multicolumn{2}{c||}{Max RE: \ 0.22301\%}& \multicolumn{2}{c|}{-} \\
+			\hline
+		\end{tabular}%
+		\label{tab:2v3_1}%
+	}}
+\end{table}%
+\FloatBarrier
+Table \ref{tab:2v3_1} show that the two-dimensional modes compares well to the three-dimensional beam for $b<=h$.
+As the width decreases, the two-dimensional model becomes a better approximation of the three-dimensional model.
+
+Table \ref{tab:2Dv3D_1_breakup} breaks up the maximum relative error for the beam type and non-beam type eigenvalues. The conclusion still holds.
+
+% Table generated by Excel2LaTeX from sheet 'Sheet2'
+\begin{table}[htbp]
+	\centering
+	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/5$.}
+	\begin{tabular}{|c|cccc|}
+		\hline
+		\multicolumn{5}{|c|}{Maximum Relative Error} \\
+		\hline
+		\hline
+		& {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
+		\hline
+		Beam Type & 2.1420 \% & 0.6804 \% & 0.38192 \% & 0.22301 \% \\
+		Non-Beam Type & 2.6069 \% & 1.4469 \% & 0.31546 \% & 0.11680 \% \\
+		\hline
+	\end{tabular}%
+	\label{tab:2Dv3D_1_breakup}%
+\end{table}%
+
+Table \ref{tab:2v3_2} below is similar to Table \ref{tab:2v3_1} but compares the eigenvalues of the models for a beam with a large length to height ratio of $h=1/20$ with decreasing values of $b$.
+
+\begin{table}[ht]
+	\scalebox{.8}{
+	\makebox[\textwidth]{
+	\caption{Comparsion of Eigenvalues with $h = 1/20$, with decreasing $b$ and $b < h$.}
+	\begin{tabular}{|cc|cc|cc|cc||cc|}
+		\hline
+		\multicolumn{10}{|c|}{Eigenvalues} \\
+		\hline
+		\hline
+		i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
+		\hline
+		{2} & 0.008043 & {2} & 0.008029 & {2} & 0.008023 & {3} & 0.00802 & {1} & {0.008013} \\
+		{3} & 0.3087 & {4} & 0.30816 & {5} & 0.30794 & {7} & 0.30785 & {2} & {0.30757} \\
+		{5} & 2.3357 & {8} & 2.3316 & {9} & 2.3300  & {12} & 2.3293 & {3} & {2.3273} \\
+		\rowcolor{lightgray}{8} & 7.7217 & {10} & 7.7156 & {13} & 7.7124 & {16} & 7.7111 & {4} & {7.7077} \\
+		{10} & 8.5387 & {11} & 8.5238 & {14} & 8.5182 & {18} & 8.516 & {5} & {8.5086} \\
+		{11} & 21.986 & {14} & 21.948 & {18} & 21.934 & {24} & 21.929 & {6} & {21.911} \\
+		{14} & 45.863 & {18} & 45.781 & {21} & 45.756 & {30} & 45.746 & {7} & {45.712} \\
+		\rowcolor{lightgray}{17} & 69.444 & {19} & 69.408 & {25} & 69.385 & {33} & 69.374 & {8} & {69.344} \\
+		{18} & 83.149 & {22} & 82.999 & {27} & 82.960 & {36} & 82.944 & {9} & {82.887} \\
+		{21} & 136.44 & {25} & 136.19 & {31} & 136.14 & {42} & 136.12 & {10} & {136.03} \\
+		\rowcolor{lightgray}{23} & 192.62 & {27} & 192.62 & {35} & 192.58 & {47} & 192.56 & {11} & {192.48} \\
+		{25} & 207.87 & {29} & 207.5 & {36} & 207.43 & {48} & 207.41 & {12} & {207.29} \\
+		{27} & 299.14 & {33} & 298.63 & {41} & 298.56 & {55} & 298.53 & {13} & {298.38} \\
+		\rowcolor{lightgray}{30} & 376.68 & {35} & 377.01 & {44} & 377.01 & {58} & 376.98 & {14} & {376.83} \\
+		{31} & 411.58 & {37} & 410.89 & {46} & 410.83 & {61} & 410.81 & {15} & {410.63} \\
+		{34} & 546.15 & {40} & 545.27 & {50} & 545.24 & {66} & 545.23 & {16} & {545.03} \\
+		\rowcolor{lightgray}{37} & 620.77 & {42} & 622.02 & {53} & 622.19 & {69} & 622.18 & {17} & {621.95} \\
+		{39} & 703.55 & {44} & 702.49 & {54} & 702.29 & {71} & 702.53 & {18} & {702.31} \\
+		{42} & 884.27 & {47} & 883.02 & {59} & 883.14 & {82} & 883.19 & {19} & {882.96} \\
+		\rowcolor{lightgray}{44} & 923.68 & {49} & 926.88 & {60} & 927.43 & {86} & 927.50 & {20} & {927.18} \\
+		\hline
+		\hline
+		\multicolumn{2}{|c|}{Max RE: \  0.37701\%} &\multicolumn{2}{c|}{Max RE: \ 0.19893\%}  & \multicolumn{2}{c|}{Max RE: \  0.12393\%}  & \multicolumn{2}{c||}{Max RE: \ 0.092843\%}& \multicolumn{2}{c|}{-} \\
+		\hline
+	\end{tabular}%
+	\label{tab:2v3_2}%
+}}
+\end{table}%
+\FloatBarrier
+
+Table \ref{tab:2v3_2} shows that the two-dimensional beam compares very well to the three-dimensional beam.
+For this long and slender beam, the two-dimensional model is an exellent approximation, and the approximation improves as the width $b$ decreases.
+
+Table \ref{tab:2v3_2_split} breaks up the maximum relative error for the beam type and non-beam type eigenvalues. The conclusion still holds.
+
+\begin{table}[htbp]
+	\centering
+	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$}
+	\begin{tabular}{|c|cccc|}
+		\hline
+		\multicolumn{5}{|c|}{Maximum Relative Error} \\
+		\hline
+		\hline
+		& {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
+		\hline
+		Beam Type & 0.37701 \% & 0.19893 \% & 0.12393 \% & 0.092843 \% \\
+		Non-Beam Type & 0.37682 \% & 0.10218 \% & 0.061213 \% & 0.043601 \% \\
+		\hline
+	\end{tabular}%
+	\label{tab:2v3_2_split}%
+\end{table}%
+\FloatBarrier
+
+From these results, it is clear that the two-dimensional model compares very well to the three-dimensional model for $b<=h$.
+The two-dimensional model is an excellent approximation for long and slender beams, and the approximation improves as the width $b$ decreases.
+
+For applications, very small values of the width $b$ are not always realistic, however the cases $b = h$ and $b=1/2h$ are realistic or close to realistic.
+And for these cases, the two-dimensional model still compare very well.
+
+\subsubsection*{Case $b > h$:}
+In this section, the case where $b > h$ is investigated. Similar to the previous case, the two cases of $h = 1/5$ and $h = 1/20 $ are considered, and the width $b$ is increased incrementally.
+
+\textcolor{red}{Results for $h = 1/5$}
+
+In Table \ref{tab:b>h}, the height of the beam is set to $h=1/20$, which was the best case when $b<h$.
+
+\FloatBarrier
+\begin{table}[htbp]
+	\scalebox{.8}{
+	\makebox[\textwidth]{
+		\caption{Comparsion of Eigenvalues with $h = 1/20$, with increasing $b$ and $b > h$}
+		\begin{tabular}{|cc|cc|cc||cc|}
+			\hline
+			\multicolumn{8}{|c|}{Eigenvalues} \\
+			\hline
+			\hline
+			i     & {b = 2h} & i     & {b = 4h} & i     & {b = 8h} & j     & 2D \\
+			\hline
+			{2} & 0.008076 & {1} & 0.008162 & {1} & 0.008324 & 1     & 0.008013 \\
+			{3} & 0.30995 & {3} & 0.31298 & {3} & 0.31738 & 2     & 0.30757 \\
+			{5} & 2.3462 & {5} & 2.3737 & {6} & 2.4116 & 3     & 2.3273 \\
+			\rowcolor{lightgray}{8} & 7.7312 & {8} & 7.7471 & {9} & 7.7711 & 4     & 7.7077 \\
+			{10} & 8.5841 & {9} & 8.7082 & {10} & 8.7929 & 5     & 8.5086 \\
+			{11} & 22.124 & {12} & 22.491 & {14} & 23.222 & 6     & 21.911 \\
+			{14} & 46.195 & {14} & 47.003 & {18} & 47.921 & 7     & 45.712 \\
+			\rowcolor{lightgray}{17} & 69.454 & {17} & 69.281 & {22} & 72.307 & 8     & 69.344 \\
+			{18} & 83.822 & {18} & 85.218 & {24} & 80.607 & 9     & 82.887 \\
+			{21} & 137.43 & {21} & 138.58 & {32} & 140.97 & 10    & 136.03 \\
+			\hline
+			\hline
+			\multicolumn{2}{|c|}{Max RE: \  1.1289\%} &\multicolumn{2}{c|}{Max RE: \ 2.8261\%}  & \multicolumn{2}{c|}{Max RE: \  5.9821\%} & \multicolumn{2}{c|}{-} \\
+			\hline
+		\end{tabular}%
+		\label{tab:b>h}%
+	}}
+\end{table}
+\FloatBarrier
+
+In Table \ref{tab:b>h}, $h = 1/20$, it is clear that even the beams with a larger lenght to width ratio, the two-dimensional model compares less well to the three-dimensional model as $b$ increases.
+
+Table \ref{tab:b>h-split}, again splits the beam and non-beam type maximum relative errors.
+
+\FloatBarrier
+\begin{table}[htbp]
+	\centering
+	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$}
+	\begin{tabular}{|c|ccc|}
+		\hline
+		\multicolumn{4}{|c|}{Maximum Relative Error} \\
+		\hline
+		\hline
+		& {b = 2h} & {b = 4h} & {b = 8h} \\
+		\hline
+		Beam Type & 1.1289 \% & 2.8261 \% & 5.9821 \% \\
+		Non-Beam Type & 0.30521 \% & 0.51096 \% & 4.2734 \% \\
+		\hline
+	\end{tabular}%
+	\label{tab:b>h-split}%
+\end{table}%
+\FloatBarrier
+
+From these result it is clear the the two-dimensional beam compares less well to the three-dimensional beam if the width $b$ is `too much' larger than the height $h$.
+
+Overall the results show that there are cases where the two-dimensional model compares very well to the three-dimensional model and can be used as a substitute.
+The best case is when the beam has a large length to height ratio, and the width is equal to less than the height.
+
+When the width gets larger than the height of the beam, the two-dimensional model starts to compare less well, and the comparison degrades as this difference increases further.
+
+For practical applications, when cantilever body has a larger width than height, the use of a beam model must be brought into question.
+A different model, like a plate model might be a better choice.
+In the next section, the validity of the Reissner-Mindlin plate mode is investigated using the same methodology used so far in this chapter, and in \cite{LVV09}.
 

### 2023-10-01 files/Chapter6/Validity_Plate.tex
v2 chapter 7.2, started 7.3

--- 2022-10-31 files/Chapter7/Plate.tex
@@
 \begin{document}
-\section{Validity of the Reissner-Mindlin plate model}
-In this section, the validity of a cantilever Reissner-Mindlin plate is investigates with reference to a three-dimensional plate model.
-In the previous section, it was shown that the beam models do not compare well when the parameter $b$ is ``too-large''.
-A plate model might be a better option.\\
+\section{Validity of a Reissner-Mindlin plate} \label{sec:validity-of-a-plate}
 
-Similarly to how the Timoshenko beam theory improves on the Euler-Bernoulli beam theory, the Reissner-Mindlin plate theory improves on classical plate theory by including the effect of shear stress.
-The Reisner-Mindlin plate theory is a two-dimensional theory.
-Therefore it is of interest to investigate the validity of such a plate model.Using \cite{LVV09} as a guide, the validity a cantilever Reisner-Mindlin plate model is investigated.\\
+In this section, the validity of a cantilever Reisner-Mindlin plate model is investigated.
+The idea of the model comes from the beam models in the previous section failing to approximate a cantilever elastic body with a width much larger than it's height.
+The process of determining the validity of the model follows the same ideas and methodology as in the previous sections, that is established in \cite{LVV09}.
+
+Similarly to how the Timoshenko beam theory improves on the Euler-Bernoulli beam theory by including the shear forces, so does the Reissner-Mindlin plate models improve on classic plate models.
+The Reissner-Mindlin plate model is a two-dimensional model, and therefore is it of value to investigate the validity of the model using a three-dimensional plate model as a reference.
+
+\subsection{The models}
+Form section \ref{ssec:P_Model:ModelProblems}, the cantilever Reissner-Mindlin plate model is given, and is referred to as Problem P-1.
+The three-dimensional model is the same as used in the previous section, and is referred to as Problem 3D-1 defined in section \ref{ssec:3D_Model:ModelProblems}.
 
 Figure \ref{fig:plate_sbs} shows the two cantilever plates side by side.
+
 \FloatBarrier
 \begin{figure}[h!]
-	\scalebox{.8}{
+	\scalebox{.7}{
 		\makebox[\textwidth][c]{
@@
 				\end{tikzpicture}
-				\subcaption{Timoshenko Cantilever Beam}
+				\subcaption{Reissner-Mindlin cantilever plate}
 			\end{minipage}
@@
 
-					\draw[line width = 0.1mm,->] (9,1) -- (10,1.6);
-					\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
-					\draw[line width = 0.1mm,->] (9,1) -- (9,-0.1);
-					\node at (9.2,1.4) {$e_3$};
-					\node at (9.7,0.8) {$e_1$};
-					\node at (8.8,0.4) {$e_2$};
+					% \draw[line width = 0.1mm,->] (9,1) -- (10,1.6);
+					% \draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
+					% \draw[line width = 0.1mm,->] (9,1) -- (9,-0.1);
+					% \node at (9.2,1.4) {$e_3$};
+					% \node at (9.7,0.8) {$e_1$};
+					% \node at (8.8,0.4) {$e_2$};
 				\end{tikzpicture}
-				\subcaption{Two-Dimensional Cantilever Beam}
+				\subcaption{Three-dimensional cantilever plate}
 
@@
 
-Both the Reissner-Mindlin plate and the three-dimensional plate model has a parameter $b$ representing the depth of the plate.
-The three-dimensional model also have a parameter $h$ representing the width of the plate model.
+\subsection{Calculating the eigenvalues}
+The eigenvalues for both models are calculated using the Finite Element Method.
+For the plate model, the Finite Element Method is derived in \ref{sec:FEM:Plate} and for the three-dimensional model, the Finite Element Method is derived in \ref{sec:FEM:3D}.
+
+\subsubsection{Problem P-1E}
+Find a vector function $u$ and a number $\lambda$ such that
+\begin{eqnarray}
+	K{u} & = & M\lambda{u}, 
+\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices for bi-cubic basis functions. The definition of the matrices are given in \ref{sec:FEM:Plate}.
+
+\subsubsection{Problem 3D-1E}
+Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
+\begin{eqnarray}
+	K\bar{u} & = & M\lambda{\bar{u}},
+\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices for tri-cubic basis functions. The definition of the matrices are given in section \ref{sec:FEM:3D}.
+
+\subsubsection{Accuracy of the eigenvalues}
+Figure \ref{fig:conv_3d_eig} show the rate of convergence of the first 20 eigenvalues of Problem 3D-1E.
+
+\begin{figure}[H]
+    \centering
+    \begin{adjustbox}{center}
+        \includegraphics[scale=0.7]{Convergence.png}
+    \end{adjustbox}
+    \caption{Rate of convergence of the first 20 eigenvalues.}
+    \label{fig:conv_3d_eig}
+\end{figure}
+\textcolor{red}{Update this figure.}
+
+The number of elements can be chosen so that at least the first 10 eigenvalues are accurate to 5 significant digits.
 
 \subsection{Comparing the mode shapes}
-\FloatBarrier
-\begin{figure}[h!]
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{Plate2.png}
-				\subcaption{Plate - $\lambda_5 = 0.643$}
-				\label{fig:minipage2}
-			\end{minipage}
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{3D2.png}
-				\subcaption{3D Model - $\lambda_5 = 0.645$}
-				\label{fig:minipage1}
-			\end{minipage}
-	}}
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\centering
-			\begin{minipage}{.8\textwidth}
-				\centering
-				\includegraphics[width=1\linewidth]{Plate1.png}
-				\subcaption{Plate - $\lambda_6 = 1.92$}
-				\label{fig:minipage1}
-			\end{minipage}
-			\begin{minipage}{.8\textwidth}
-				\centering
-				\includegraphics[width=1\linewidth]{3D1.png}
-				\subcaption{3D Model - $\lambda_7 = 1.92$}
-				\label{fig:minipage2}
-			\end{minipage}
-	}}
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{Plate3.png}
-				\subcaption{Plate - $\lambda_8 = 2.74$}
-				\label{fig:minipage1}
-			\end{minipage}
-			\quad
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{3D3.png}
-				\subcaption{3D Model - $\lambda_8 = 2.74$}
-				\label{fig:minipage2}
-			\end{minipage}
-	}}
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\centering
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{Plate4.png}
-				\subcaption{Plate - $\lambda_{12} = 8.96$ (Side view)}
-				\label{fig:minipage2}
-			\end{minipage}
-			\quad
-			\begin{minipage}[b]{0.8\linewidth}
-				\includegraphics[width=1\linewidth]{3D4.png}
-				\subcaption{3D Model - $\lambda_{14} = 9.01$ (Side view)}
-				\label{fig:minipage2}
-			\end{minipage}
-			\caption{Comparison of Mode Shapes of the 3D model and the plate model. $b = 1/20$, $d = 1$.}
-	}}
-\end{figure}
-
-\FloatBarrier
-
-Let $b= 1$ and $\alpha= 4800$ so that $h= \frac{1}{2}$.\\
-
-\begin{figure}[h!]
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\centering
-			\begin{minipage}{.8\textwidth}
-				\centering
-				\includegraphics[width=1\linewidth]{3Dnp1.png}
-				\subcaption{3D Model - $\lambda_{6} = 1.35$ (Top view)}
-				\label{fig:minipage1}
-			\end{minipage}
-			\begin{minipage}{.8\textwidth}
-				\centering
-				\includegraphics[width=1\linewidth]{3Dnp2.png}
-				\subcaption{3D Model - $\lambda_{13} = 7.80$ (Top view)}
-				\label{fig:minipage2}
-			\end{minipage}
-	}}
-	\caption{Examples of non-plate mode shapes.}
-\end{figure}
 
 \subsection{Comparing the eigenvalues}
-Tables \ref{tab:Table_plate_1} and \ref{tab:Table_plate_1} compare the eigenvalues of a cantilever Reissner-Mindlin plate model to the eigenvalues of a cantilever three-dimensional plate model.
-The different widths of plates considered are $b = 0.25$ and $b = 1$.
-These cases represent a slightly and very wide plate models.
-In each of the tables, the parameter $h$ representing the height is decreased.
-
-\FloatBarrier
-\begin{table}[htbp]
-	\scalebox{.8}{
-	\makebox[\textwidth]{
-		\caption{Comparison of eigenvalues of the cantilever Reissner-Mindlin and three-dimensional plates.}
-		\begin{tabular}{|cccc||cccc||cccc||cccc|}
-			\hline
-			\multicolumn{16}{|c|}{Comparison of Eigenvalues, $b = 0.25$} \\
-			\hline\hline
-			\multicolumn{4}{|c||}{$h = 1/5$}       & \multicolumn{4}{c||}{$h =1/10$}      & \multicolumn{4}{c||}{$h = 1/20$}      & \multicolumn{4}{c|}{$h = 1/30$} \\
-			\hline
-			{i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} \\
-			\hline
-			1     & 0.12348 & 1     & {0.12249} & 1     & 0.032327 & 1     & 0.032184 & 1     & 0.008207 & 1     & 0.008186 & 1     & 0.003663 & 1     & 0.003656 \\
-			2     & 0.18638 &       & -     & 2     & 0.18531 &       & {-} & 2     & 0.18476 &       & {-} & 2     & 0.14204 & 2     & 0.14173 \\
-			3     & 2.4151 & 2     & {2.3954} & 3     & 1.161 & 2     & 1.1537 & 3     & 0.31436 & 2     & 0.31341 & 3     & 0.18456 &       & {-} \\
-			4     & 3.5856 & 3     & {3.5368} & 4     & 1.3155 & 3     & 1.31  & 4     & 0.44696 & 3     & 0.44582 & 4     & 0.21514 & 3     & 0.21454 \\
-			5     & 4.785 &       & -     & 5     & 4.7697 &       & {-} & 5     & 2.3862 & 4     & 2.3767 & 5     & 1.1001 & 4     & 1.0971 \\
-			6     & 7.7889 &       & -     & 6     & 7.7674 & 4     & 7.9816 & 6     & 4.1984 & 5     & 4.1857 & 6     & 2.0374 & 5     & 2.0313 \\
-			7     & 20.37 & 4     & {19.969} & 7     & 8.056 &       & {-} & 7     & 4.7615 &       & {-} & 7     & 4.1509 & 6     & 4.1367 \\
-			8     & 21.722 & 5     & {21.537} & 8     & 12.034 & 5     & 11.972 & 8     & 7.7543 &       & {-} & 8     & 4.7585 &       & {-} \\
-			9     & 25.181 &       & -     & 9     & 25.147 &       & {-} & 9     & 8.7609 & 6     & 8.7132 & 9     & 6.2078 & 7     & 6.1864 \\
-			10    & 56.321 & 6     & {54.887} & 10    & 26.608 & 6     & 26.266 & 10    & 12.598 & 7     & 12.548 & 10    & 7.7495 &       & {-} \\
-			11    & 60.267 & 7     & {59.71} & 11    & 34.438 & 7     & 34.197 & 11    & 22.619 & 8     & 22.456 & 11    & 11.064 & 8     & 11.015 \\
-			12    & 65.513 &       & -     & 12    & 61.829 & 8     & 60.801 & 12    & 25.128 &       & {-} & 12    & 13.734 & 9     & 13.678 \\
-			13    & 69.031 &       & -     & 13    & 65.518 &       & {-} & 13    & 27.297 & 9     & 27.155 & 13    & 23.854 & 10    & 23.724 \\
-			14    & 114.09 & 8     & {110.7} & 14    & 69.133 & 9     & 69.548 & 14    & 47.123 & 10    & 46.695 & 14    & 25.121 &       & {-} \\
-			15    & 117.88 & 9     & {116.66} & 15    & 70.211 &       & {-} & 15    & 50.515 & 11    & 50.174 & 15    & 26.054 & 11    & 25.927 \\
-			16    & 127.05 &       & -     & 16    & 116.78 & 10    & 114.43 & 16    & 65.523 &       & {-} & 16    & 36.259 & 12    & 36.15 \\
-			17    & 184.46 & 10    & {185.78} & 17    & 121.43 & 11    & 119.94 & 17    & 69.089 &       & {-} & 17    & 41.973 & 13    & 41.807 \\
-			18    & 191.91 & 11    & {191.47} & 18    & 127.23 &       & {-} & 18    & 71.563 & 12    & 71.166 & 18    & 44.95 & 14    & 44.685 \\
-			19    & 193.03 &       & -     & 19    & 178.27 & 12    & 175.79 & 19    & 81.444 & 13    & 80.894 & 19    & 45.798 & 15    & 45.507 \\
-			20    & 193.71 &       & -     & 20    & 186.06 & 13    & 187.28 & 20    & 84.785 & 14    & 84.064 & 20    & 54.838 & 16    & 54.573 \\
-			\hline
-			\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{2.9764\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{2.7585\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{0.90845\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{0.63525\%} \\
-			\hline
-		\end{tabular}%
-		\label{tab:Table_plate_1}%
-	}}
-\end{table}%
-\FloatBarrier
-
-The results in Table \ref{tab:Table_plate_1} show that the cantilever Reissner-Mindlin plate model compare very well to the cantilever three-dimensional plate.
-For $h = 1/5$ the plate can be considered ``thick'', and the maximum relative error is less than $3\%$.
-This relative error decreases significantly as $h$ decreases.\\
-
-As $b$ decreases, there are also more eigenvalues of the cantilever the Reissner-Mindlin plate relating to the first 20 eigenvalues of the cantilever three-dimensional plate. Table
-\ref{tab:Table_plate_1_1} shows some more results for different values of $b$ without presenting the eigenvalues.
-
-\FloatBarrier
-\begin{table}[htbp]
-	\centering
-	\caption{Maximum relative error of the first 10 comparable eigenvalues with b = 0.25.}
-	\begin{tabular}{|c|c|c|c|c|c|}
-		\hline
-		\multicolumn{6}{|c|}{Max Relative Error } \\ 
-		\hline 
-		\hline
-		b = 1/2 & b = 1/5 & b = 1/10 & b = 1/20 & b = 1/30 & b = 1/50\\ \hline
-		3.4514\% & 2.9764 \% & 2.7585 \% & 0.90845 \% & 0.63525 \% & 0.50397 \% \\ \hline
-	\end{tabular}%
-	\label{tab:Table_plate_1_1}%
-\end{table}%
-
-\FloatBarrier
-\begin{table}[htbp]
-	\scalebox{.8}{
-	\makebox[\textwidth]{
-		\caption{Comparison of eigenvalues of the cantilever Reissner-Mindlin and three-dimensional plates.}
-		\begin{tabular}{|cccc||cccc||cccc||cccc|}
-			\hline
-			\multicolumn{16}{|c|}{Comparison of Eigenvalues, $b = 1$} \\
-			\hline\hline
-			\multicolumn{4}{|c||}{$h = 1/5$}       & \multicolumn{4}{c||}{$h =1/10$}      & \multicolumn{4}{c||}{$h = 1/20$}      & \multicolumn{4}{c|}{$h = 1/30$} \\
-			\hline
-			{i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} \\
-			\hline
-			1     & 0.12869 & 1     & {0.12743} & 1     & 0.033784 & 1     & 0.033626 & 1     & 0.008565 & 1     & 0.008543 & 1     & 0.003817 & 1     & {0.00381} \\
-			2     & 0.62189 & 2     & {0.61703} & 2     & 0.18635 & 2     & 0.18562 & 2     & 0.049829 & 2     & 0.04957 & 2     & 0.022511 & 2     & {0.022405} \\
-			3     & 1.3638 &       & -     & 3     & 1.1603 & 3     & 1.153 & 3     & 0.31428 & 3     & 0.31315 & 3     & 0.14192 & 3     & {0.14156} \\
-			4     & 3.5808 & 3     & {3.5289} & 4     & 1.3579 &       & {-} & 4     & 0.50842 & 4     & 0.50676 & 4     & 0.23035 & 4     & {0.22969} \\
-			5     & 5.8165 & 4     & {5.7694} & 5     & 1.864 & 4     & 1.8577 & 5     & 0.64595 & 5     & 0.64297 & 5     & 0.29502 & 5     & {0.29394} \\
-			6     & 6.6048 & 5     & {6.5216} & 6     & 2.2928 & 5     & 2.2792 & 6     & 1.3555 &       & {-} & 6     & 0.8928 & 6     & {0.88735} \\
-			7     & 7.8455 &       & -     & 7     & 6.4973 & 6     & 6.4546 & 7     & 1.9293 & 6     & 1.9157 & 7     & 1.156 & 7     & {1.1527} \\
-			8     & 9.8027 &       & -     & 8     & 7.8167 &       & {-} & 8     & 2.5089 & 7     & 2.4975 & 8     & 1.265 & 8     & {1.261} \\
-			9     & 17.03 & 6     & {16.802} & 9     & 8.4533 & 7     & 8.3671 & 9     & 2.7486 & 8     & 2.7369 & 9     & 1.3543 &       & - \\
-			10    & 21.225 & 7     & {20.743} & 10    & 9.3453 & 8     & 9.2873 & 10    & 3.3087 & 9     & 3.2903 & 10    & 1.5352 & 9     & {1.529} \\
-			11    & 23.935 & 8     & {23.552} & 11    & 9.8009 &       & {-} & 11    & 5.5365 & 10    & 5.4914 & 11    & 2.598 & 10    & {2.5803} \\
-			12    & 24.694 &       & -     & 12    & 10.925 & 9     & 10.827 & 12    & 5.9696 & 11    & 5.9246 & 12    & 2.8161 & 11    & {2.7997} \\
-			13    & 27.187 & 9     & {26.69} & 13    & 17.599 & 10    & 17.447 & 13    & 7.8024 &       & {-} & 13    & 4.2654 & 12    & {4.2474} \\
-			14    & 28.844 &       & -     & 14    & 18.596 & 11    & 18.407 & 14    & 9.0173 & 12    & 8.9573 & 14    & 4.6674 & 13    & {4.6415} \\
-			15    & 32.373 &       & -     & 15    & 24.729 &       & {-} & 15    & 9.8006 & 13    & 9.838 & 15    & 4.9397 & 14    & {4.9143} \\
-			16    & 41.288 & 10    & {40.519} & 16    & 27.4  & 12    & 27.021 & 16    & 9.9172 &       & {-} & 16    & 5.7243 & 15    & {5.6803} \\
-			17    & 42.082 & 11    & {41.246} & 17    & 28.81 &       & {-} & 17    & 10.365 & 13    & 10.286 & 17    & 6.6585 & 16    & {6.6025} \\
-			18    & 51.427 &       & -     & 18    & 30.737 & 13    & 30.413 & 18    & 11.934 & 14    & 11.817 & 18    & 7.2935 & 17    & {7.2474} \\
-			19    & 56.963 & 12    & {56.1} & 19    & 30.83 & 14    & 30.413 & 19    & 13.915 & 15    & 13.767 & 19    & 7.7966 &       & - \\
-			20    & 57.741 &       & -     & 20    & 32.414 &       &       & 20    & 15.109 & 16    & 14.974 & 20    & 9.7996 &       & - \\
-			\hline
-			\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{2.2695\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{1.3816\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{1.0657\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{0.84102\%} \\
-			\hline
-		\end{tabular}%
-		\label{tab:Table_plate_2}%
-	}}
-\end{table}%
-\FloatBarrier
-
-Similarly, Table \ref{tab:Table_plate_2} also show that a cantilever Reissner-Mindlin plate compares very well to a cantilever three-dimensional plate for $b=1$ which can be considered a wide plate.\\
-
-Table \ref{tab:Table_plate_2_2} presents some more results without showing all the eigenvalues.
-
-\FloatBarrier
-\begin{table}[htbp]
-	\centering
-	\caption{Maximum relative error of the first 10 comparable eigenvalues with d=1.}
-	\begin{tabular}{|c|c|c|c|c|c|}
-		\hline
-		\multicolumn{6}{|c|}{Max Relative Error } \\ 
-		\hline 
-		\hline
-		b = 1/2 & b = 1/5 & b = 1/10 & b = 1/20 & b = 1/30 & b = 1/50\\ \hline
-		3.9342\% & 2.2695 \% & 1.3816 \% & 1.0657 \% & 0.84101 \% & 0.38181 \% \\ \hline
-	\end{tabular}%
-	\label{tab:addlabel}%
-\end{table}%
 

### 2023-10-02 files/Chapter6/Validity_Plate.tex
new version
chapter 6 finished excluding new data that is still needed

@@
 \subsection{Comparing the mode shapes}
+Similar to the previous sections, the mode shapes of the two models are compared, to be able to match up the eigenvalues.
+
+\subsubsection{Mode shapes relating to plate type eigenvalues}
+Figure \ref{fig:plate_mode_shapes} shows examples of mode shapes relating to plate-type eigenvalues. The plate models has many different shapes.
+
+\FloatBarrier
+\begin{figure}[h!]
+	\scalebox{.8}{
+		\makebox[\textwidth][c]{
+			\centering
+			\begin{minipage}[b]{0.8\linewidth}
+				\includegraphics[width=1\linewidth]{Plate2.png}
+				\subcaption{Plate - $\lambda_5 = 0.643$}
+				\label{fig:minipage2}
+			\end{minipage}
+			\begin{minipage}[b]{0.8\linewidth}
+				\includegraphics[width=1\linewidth]{3D2.png}
+				\subcaption{3D Model - $\lambda_5 = 0.645$}
+				\label{fig:minipage1}
+			\end{minipage}
+	}}
+	\scalebox{.8}{
+		\makebox[\textwidth][c]{
+			\centering
+			\begin{minipage}{.8\textwidth}
+				\centering
+				\includegraphics[width=1\linewidth]{Plate1.png}
+				\subcaption{Plate - $\lambda_6 = 1.92$}
+				\label{fig:minipage1}
+			\end{minipage}
+			\begin{minipage}{.8\textwidth}
+				\centering
+				\includegraphics[width=1\linewidth]{3D1.png}
+				\subcaption{3D Model - $\lambda_7 = 1.92$}
+				\label{fig:minipage2}
+			\end{minipage}
+	}}
+	\scalebox{.8}{
+		\makebox[\textwidth][c]{
+			\centering
+			\begin{minipage}[b]{0.8\linewidth}
+				\includegraphics[width=1\linewidth]{Plate3.png}
+				\subcaption{Plate - $\lambda_8 = 2.74$}
+				\label{fig:minipage1}
+			\end{minipage}
+			\quad
+			\begin{minipage}[b]{0.8\linewidth}
+				\includegraphics[width=1\linewidth]{3D3.png}
+				\subcaption{3D Model - $\lambda_8 = 2.74$}
+				\label{fig:minipage2}
+			\end{minipage}
+	}}
+	\scalebox{.8}{
+		\makebox[\textwidth][c]{
+			\centering
+			\begin{minipage}[b]{0.8\linewidth}
+				\includegraphics[width=1\linewidth]{Plate4.png}
+				\subcaption{Plate - $\lambda_{12} = 8.96$ (Side view)}
+				\label{fig:minipage2}
+			\end{minipage}
+			\quad
+			\begin{minipage}[b]{0.8\linewidth}
+				\includegraphics[width=1\linewidth]{3D4.png}
+				\subcaption{3D Model - $\lambda_{14} = 9.01$ (Side view)}
+				\label{fig:minipage2}
+			\end{minipage}
+			\caption{Comparison of mode shapes relating to plate-type models. $b = 1/20$, $d = 1$.}
+	}}
+\end{figure}\label{fig:plate_mode_shapes}
+
+\FloatBarrier
+
+\subsubsection{Mode shapes relating to non-plate type eigenvalues}
+Figure \ref{fig:non_plate_mode_shapes} shows examples of mode shapes not relating to plate-type eigenvalues.
+
+\begin{figure}[h!]
+	\scalebox{.8}{
+		\makebox[\textwidth][c]{
+			\centering
+			\begin{minipage}{.8\textwidth}
+				\centering
+				\includegraphics[width=1\linewidth]{3Dnp1.png}
+				\subcaption{3D Model - $\lambda_{6} = 1.35$ (Top view)}
+				\label{fig:minipage1}
+			\end{minipage}
+			\begin{minipage}{.8\textwidth}
+				\centering
+				\includegraphics[width=1\linewidth]{3Dnp2.png}
+				\subcaption{3D Model - $\lambda_{13} = 7.80$ (Top view)}
+				\label{fig:minipage2}
+			\end{minipage}
+	}}
+	\caption{Comparison of mode shapes not relating to plate-type models. $b = 1/20$, $d = 1$.}
+\end{figure} \label{fig:non_plate_mode_shapes}
 
 \subsection{Comparing the eigenvalues}
+The eigenvalues of the two plate models can now be compared.
+For both the models, there are two parameters to consider for the height $h$ and width $b$.
+For realistic applications, the width of the plate is larger than its height.
+
+For the comparisons, the investigation will consider a plate with small width $b = 0.25$, a plate of width equal to lenght $b = 1$ and a wide plate $1.75$.
+For each case, decreasing values of the height $h$ will be considered.
+
+\FloatBarrier
+\begin{table}[htbp]
+	\scalebox{.8}{
+	\makebox[\textwidth]{
+		\caption{Comparison of eigenvalues with $b = 0.25$, with decreasing values of $h$.}
+		\begin{tabular}{|cccc||cccc||cccc||cccc|}
+			\hline
+			\multicolumn{16}{|c|}{Comparison of Eigenvalues, $b = 0.25$} \\
+			\hline\hline
+			\multicolumn{4}{|c||}{$h = 1/5$}       & \multicolumn{4}{c||}{$h =1/10$}      & \multicolumn{4}{c||}{$h = 1/20$}      & \multicolumn{4}{c|}{$h = 1/30$} \\
+			\hline
+			{i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} \\
+			\hline
+			1     & 0.12348 & 1     & {0.12249} & 1     & 0.032327 & 1     & 0.032184 & 1     & 0.008207 & 1     & 0.008186 & 1     & 0.003663 & 1     & 0.003656 \\
+			2     & 0.18638 &       & -     & 2     & 0.18531 &       & {-} & 2     & 0.18476 &       & {-} & 2     & 0.14204 & 2     & 0.14173 \\
+			3     & 2.4151 & 2     & {2.3954} & 3     & 1.161 & 2     & 1.1537 & 3     & 0.31436 & 2     & 0.31341 & 3     & 0.18456 &       & {-} \\
+			4     & 3.5856 & 3     & {3.5368} & 4     & 1.3155 & 3     & 1.31  & 4     & 0.44696 & 3     & 0.44582 & 4     & 0.21514 & 3     & 0.21454 \\
+			5     & 4.785 &       & -     & 5     & 4.7697 &       & {-} & 5     & 2.3862 & 4     & 2.3767 & 5     & 1.1001 & 4     & 1.0971 \\
+			6     & 7.7889 &       & -     & 6     & 7.7674 & 4     & 7.9816 & 6     & 4.1984 & 5     & 4.1857 & 6     & 2.0374 & 5     & 2.0313 \\
+			7     & 20.37 & 4     & {19.969} & 7     & 8.056 &       & {-} & 7     & 4.7615 &       & {-} & 7     & 4.1509 & 6     & 4.1367 \\
+			8     & 21.722 & 5     & {21.537} & 8     & 12.034 & 5     & 11.972 & 8     & 7.7543 &       & {-} & 8     & 4.7585 &       & {-} \\
+			9     & 25.181 &       & -     & 9     & 25.147 &       & {-} & 9     & 8.7609 & 6     & 8.7132 & 9     & 6.2078 & 7     & 6.1864 \\
+			10    & 56.321 & 6     & {54.887} & 10    & 26.608 & 6     & 26.266 & 10    & 12.598 & 7     & 12.548 & 10    & 7.7495 &       & {-} \\
+			11    & 60.267 & 7     & {59.71} & 11    & 34.438 & 7     & 34.197 & 11    & 22.619 & 8     & 22.456 & 11    & 11.064 & 8     & 11.015 \\
+			12    & 65.513 &       & -     & 12    & 61.829 & 8     & 60.801 & 12    & 25.128 &       & {-} & 12    & 13.734 & 9     & 13.678 \\
+			13    & 69.031 &       & -     & 13    & 65.518 &       & {-} & 13    & 27.297 & 9     & 27.155 & 13    & 23.854 & 10    & 23.724 \\
+			14    & 114.09 & 8     & {110.7} & 14    & 69.133 & 9     & 69.548 & 14    & 47.123 & 10    & 46.695 & 14    & 25.121 &       & {-} \\
+			15    & 117.88 & 9     & {116.66} & 15    & 70.211 &       & {-} & 15    & 50.515 & 11    & 50.174 & 15    & 26.054 & 11    & 25.927 \\
+			16    & 127.05 &       & -     & 16    & 116.78 & 10    & 114.43 & 16    & 65.523 &       & {-} & 16    & 36.259 & 12    & 36.15 \\
+			17    & 184.46 & 10    & {185.78} & 17    & 121.43 & 11    & 119.94 & 17    & 69.089 &       & {-} & 17    & 41.973 & 13    & 41.807 \\
+			18    & 191.91 & 11    & {191.47} & 18    & 127.23 &       & {-} & 18    & 71.563 & 12    & 71.166 & 18    & 44.95 & 14    & 44.685 \\
+			19    & 193.03 &       & -     & 19    & 178.27 & 12    & 175.79 & 19    & 81.444 & 13    & 80.894 & 19    & 45.798 & 15    & 45.507 \\
+			20    & 193.71 &       & -     & 20    & 186.06 & 13    & 187.28 & 20    & 84.785 & 14    & 84.064 & 20    & 54.838 & 16    & 54.573 \\
+			\hline
+			\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{2.9764\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{2.7585\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{0.90845\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{0.63525\%} \\
+			\hline
+		\end{tabular}%
+		\label{tab:Table_plate_1}%
+	}}
+\end{table}%
+\FloatBarrier
+
+Table \ref{tab:Table_plate_1} shows that the narrow plate model compares well the to three-dimensional model.
+Also note that as the height $h$ decreases, the number of plate type eigenvalues within the first 20 eigenvalues increases.
+
+The next table, table \ref{tab:Table_plate_2}, shows the comparison of the eigenvalues for a plate of width equal to its length, $b = 1$.
+
+\FloatBarrier
+\begin{table}[htbp]
+	\scalebox{.8}{
+	\makebox[\textwidth]{
+		\caption{Comparison of eigenvalues with $b = 1$, with decreasing values of $h$.}
+		\begin{tabular}{|cccc||cccc||cccc||cccc|}
+			\hline
+			\multicolumn{16}{|c|}{Comparison of Eigenvalues, $b = 1$} \\
+			\hline\hline
+			\multicolumn{4}{|c||}{$h = 1/5$}       & \multicolumn{4}{c||}{$h =1/10$}      & \multicolumn{4}{c||}{$h = 1/20$}      & \multicolumn{4}{c|}{$h = 1/30$} \\
+			\hline
+			{i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} \\
+			\hline
+			1     & 0.12869 & 1     & {0.12743} & 1     & 0.033784 & 1     & 0.033626 & 1     & 0.008565 & 1     & 0.008543 & 1     & 0.003817 & 1     & {0.00381} \\
+			2     & 0.62189 & 2     & {0.61703} & 2     & 0.18635 & 2     & 0.18562 & 2     & 0.049829 & 2     & 0.04957 & 2     & 0.022511 & 2     & {0.022405} \\
+			3     & 1.3638 &       & -     & 3     & 1.1603 & 3     & 1.153 & 3     & 0.31428 & 3     & 0.31315 & 3     & 0.14192 & 3     & {0.14156} \\
+			4     & 3.5808 & 3     & {3.5289} & 4     & 1.3579 &       & {-} & 4     & 0.50842 & 4     & 0.50676 & 4     & 0.23035 & 4     & {0.22969} \\
+			5     & 5.8165 & 4     & {5.7694} & 5     & 1.864 & 4     & 1.8577 & 5     & 0.64595 & 5     & 0.64297 & 5     & 0.29502 & 5     & {0.29394} \\
+			6     & 6.6048 & 5     & {6.5216} & 6     & 2.2928 & 5     & 2.2792 & 6     & 1.3555 &       & {-} & 6     & 0.8928 & 6     & {0.88735} \\
+			7     & 7.8455 &       & -     & 7     & 6.4973 & 6     & 6.4546 & 7     & 1.9293 & 6     & 1.9157 & 7     & 1.156 & 7     & {1.1527} \\
+			8     & 9.8027 &       & -     & 8     & 7.8167 &       & {-} & 8     & 2.5089 & 7     & 2.4975 & 8     & 1.265 & 8     & {1.261} \\
+			9     & 17.03 & 6     & {16.802} & 9     & 8.4533 & 7     & 8.3671 & 9     & 2.7486 & 8     & 2.7369 & 9     & 1.3543 &       & - \\
+			10    & 21.225 & 7     & {20.743} & 10    & 9.3453 & 8     & 9.2873 & 10    & 3.3087 & 9     & 3.2903 & 10    & 1.5352 & 9     & {1.529} \\
+			11    & 23.935 & 8     & {23.552} & 11    & 9.8009 &       & {-} & 11    & 5.5365 & 10    & 5.4914 & 11    & 2.598 & 10    & {2.5803} \\
+			12    & 24.694 &       & -     & 12    & 10.925 & 9     & 10.827 & 12    & 5.9696 & 11    & 5.9246 & 12    & 2.8161 & 11    & {2.7997} \\
+			13    & 27.187 & 9     & {26.69} & 13    & 17.599 & 10    & 17.447 & 13    & 7.8024 &       & {-} & 13    & 4.2654 & 12    & {4.2474} \\
+			14    & 28.844 &       & -     & 14    & 18.596 & 11    & 18.407 & 14    & 9.0173 & 12    & 8.9573 & 14    & 4.6674 & 13    & {4.6415} \\
+			15    & 32.373 &       & -     & 15    & 24.729 &       & {-} & 15    & 9.8006 & 13    & 9.838 & 15    & 4.9397 & 14    & {4.9143} \\
+			16    & 41.288 & 10    & {40.519} & 16    & 27.4  & 12    & 27.021 & 16    & 9.9172 &       & {-} & 16    & 5.7243 & 15    & {5.6803} \\
+			17    & 42.082 & 11    & {41.246} & 17    & 28.81 &       & {-} & 17    & 10.365 & 13    & 10.286 & 17    & 6.6585 & 16    & {6.6025} \\
+			18    & 51.427 &       & -     & 18    & 30.737 & 13    & 30.413 & 18    & 11.934 & 14    & 11.817 & 18    & 7.2935 & 17    & {7.2474} \\
+			19    & 56.963 & 12    & {56.1} & 19    & 30.83 & 14    & 30.413 & 19    & 13.915 & 15    & 13.767 & 19    & 7.7966 &       & - \\
+			20    & 57.741 &       & -     & 20    & 32.414 &       &       & 20    & 15.109 & 16    & 14.974 & 20    & 9.7996 &       & - \\
+			\hline
+			\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{2.2695\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{1.3816\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{1.0657\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{0.84102\%} \\
+			\hline
+		\end{tabular}%
+		\label{tab:Table_plate_2}%
+	}}
+\end{table}%
+\FloatBarrier
+
+Table \ref{tab:Table_plate_2} shows that the plate model compares slightly less well than the case where $b=0.25$, but the comparison is still very good.
+Again it seems that as $h$ decreases, the number of plate-type eigenvalues within the first 20 eigenvalues increases, and in this case there are more than the previous case.
 

### 2023-10-02 files/Overview.tex
chapter 6 finished excluding new data that is still needed

@@
 \begin{document}
+
+\section{Summary}
+
+\subsubsection{Chapter 1}
+This dissertation is a literature study that investigates the validity of different linear models.
+The term validity in this dissertation means how well a model compares to a more realistic model for real world applications.
+The first chapter of the dissertation introduces the models.
+The main model is the Timoshenko beam theory.
+
+\subsubsection{Chapter 2}
+\subsubsection{Chapter 3}
+\subsubsection{Chapter 4}
+\subsubsection{Chapter 5}
+\subsubsection{Chapter 6}
+
+\end{document}
 

### 2023-10-04 files/Overview.tex
Overview v1

@@
 The main model is the Timoshenko beam theory.
+The other models are a two-dimensional elastic model, a three-dimensional elastic model and a Reissner-Mindlin plate model.
+The goal of this disseration to validate the use of the Timoshenko beam model and the Reissner-Mindlin plate model in applications.
+These models are simplified one-dimensional beam and two-dimensional plate models.
+But more realistic models exists, such as a two-dimensional and three-dimensional beam model and a three-dimensional plate model.
+Using modal analysis, it is shown that the solutions of the models can be represented as a linear combination of the eigenvalues and eigenfunctions.
+Therefore it is only required to compare the eigenvalues and eigenfunctions of the models to determine the difference of the solutions.
 
 \subsubsection{Chapter 2}
+In this section, the existence and solutions for a general vibration problem is investigated.
+The main article that is discussed is \cite{VV02}.
+In this article, the authors define a general vibration problem.
+The authors state four assumptions that need to be satified.
+Under these four assumptions, it can be shown that for the general vibration problem there exists a linear operator A, which is an infinitesimal generator of a $C_0$-semigroup of contractions with a domain in the problem space.
+This operator allows the general vibration problem to be rewritten as a system of first order differential equations $\displaystyle x' = Ax + f$.
+This differential equations are rewritten into an initial value problem which can be proven using semi-group theory to have a unique solution.
+The authors then provide the necessary proofs to show that a solution of the initial value problem is also a solution of the general vibration problem.
+An example of the application of this theory is provided using a cantilever Timoshenko beam.
+
 \subsubsection{Chapter 3}

### 2023-10-07 files/Chapter6/Validity_Plate.tex
summary

@@
     \begin{adjustbox}{center}
-        \includegraphics[scale=0.7]{Convergence.png}
+        \includegraphics[scale=0.4]{Plate accuracy_no_legend.png}
     \end{adjustbox}
@@
 \end{figure}
-\textcolor{red}{Update this figure.}
 
@@
 
+\FloatBarrier
+\begin{table}[htbp]
+	\scalebox{.8}{
+	\makebox[\textwidth]{
+		\caption{Comparison of eigenvalues with $b = 1.75$, with decreasing values of $h$.}
+		\begin{tabular}{|cccc||cccc||cccc||cccc|}
+			\hline
+			\multicolumn{16}{|c|}{Comparison of Eigenvalues, $b = 1.75$} \\
+			\hline\hline
+			\multicolumn{4}{|c||}{$h = 1/5$}       & \multicolumn{4}{c||}{$h =1/10$}      & \multicolumn{4}{c||}{$h = 1/20$}      & \multicolumn{4}{c|}{$h = 1/30$} \\
+			\hline
+			{i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} \\
+			\hline
+			1 & 0.13062 & 1 & 0.12939 & 1 & 0.034245 & 1 & 0.034079 & 1 & 0.0086697 & 1 & 0.32670086456 & 1 & 0.0038626 & 1 & 0.0038541\\
+			2 & 0.32016 & 2 & 0.31779 & 2 & 0.089872 & 2 & 0.089508 & 2 & 0.023395 & 2 & 0.023323 & 2 & 0.010507 & 2 & 0.010475\\
+			3 & 1.2496 & 3 & 1.2422 & 3 & 0.36964 & 3 & 0.36841 & 3 & 0.098072 & 3 & 0.097745 & 3 & 0.044239 & 3 & 0.044074\\
+			4 & 1.9808 &  & - & 4 & 1.2274 & 4 & 1.2188 & 4 & 0.33233 & 4 & 0.33118 & 4 & 0.15003 & 4 & 0.14964\\
+			5 & 3.7675 & 4 & 3.7086 & 5 & 1.352 & 5 & 1.3465 & 5 & 0.36764 & 5 & 0.36652 & 5 & 0.16657 & 5 & 0.16605\\
+			6 & 4.2021 & 5 & 4.1631 & 6 & 1.6994 & 6 & 1.6894 & 6 & 0.4647 & 6 & 0.4632 & 6 & 0.21059 & 6 & 0.21002\\
+			7 & 5.2022 & 6 & 5.1381 & 7 & 1.9763 &  & - & 7 & 0.79935 & 7 & 0.79606 & 7 & 0.3656 & 7 & 0.36423\\
+			8 & 7.6603 & 7 & 7.9399 & 8 & 2.8259 & 7 & 2.8076 & 8 & 1.2445 & 8 & 1.2411 & 8 & 0.56685 & 8 & 0.56529\\
+			9 & 8.0445 &  & - & 9 & 4.4507 & 8 & 4.4294 & 9 & 1.5708 & 9 & 1.563 & 9 & 0.72384 & 9 & 0.72032\\
+			10 & 9.0791 &  & - & 10 & 5.3923 & 9 & 5.3539 & 10 & 1.9739 &  & - & 10 & 1.1585 & 10 & 1.1545\\
+			11 & 10.135 &  & - & 11 & 7.6371 &  & 0 & 11 & 2.5137 & 10 & 2.5015 & 11 & 1.2513 & 11 & 1.2466\\
+			12 & 12.888 & 8 & 12.736 & 12 & 8.4707 & 10 & 8.3817 & 12 & 2.708 & 11 & 2.6947 & 12 & 1.4005 & 12 & 1.3927\\
+			13 & 14.506 & 9 & 14.302 & 13 & 9.0612 & 11 & 8.9704 & 13 & 3.0153 & 12 & 2.9984 & 13 & 1.4449 & 13 & 1.4393\\
+			14 & 14.892 &  & - & 14 & 9.0682 & 12 & 9.9347 & 14 & 3.137 & 13 & 3.1246 & 14 & 1.6806 & 14 & 1.6738\\
+			15 & 19.395 &  & - & 15 & 10.018 & 13 & 10.605 & 15 & 3.6118 & 14 & 3.5928 & 15 & 1.973 &  & -\\
+			16 & 21.265 & 10 & 20.79 & 16 & 10.131 &  & - & 16 & 5.1287 & 15 & 5.0977 & 16 & 2.4081 & 15 & 2.3958\\
+			17 & 22.512 & 11 & 22.038 & 17 & 10.683 &  & - & 17 & 5.6368 & 16 & 5.6009 & 17 & 2.6419 & 16 & 2.6253\\
+			18 & 25.193 & 12 & 24.775 & 18 & 11.806 & 14 & 11.682 & 18 & 6.5069 & 17 & 6.4687 & 18 & 3.0386 & 17 & 3.0189\\
+			19 & 27.783 & 13 & 27.322 & 19 & 14.893 &  & - & 19 & 7.6243 & 18 & 7.6617 & 19 & 3.6563 & 18 & 3.6342\\
+			20 & 28.461 & 14 & 27.851 & 20 & 16.275 & 15 & 16.1 & 20 & 7.7152 &  & - & 20 & 4.3466 & 19 & 4.3267\\
+			\hline
+			\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{3.6499\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{9.5565\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{0.63674\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{0.64798\%} \\
+			\hline
+		\end{tabular}
+		\label{tab:Table_plate_3}
+	}}
+\end{table}
+\FloatBarrier
+
+Table \ref{tab:Table_plate_3} that for a wide plate with $b=1.75$, the models do compare very well.
+However it seems like the height of the plate does no longer have a significant effect on the accuracy of the eigenvalues.
+What can be seen is that as het height decreases, the number of plate type eigenvalues within the first 20 eigenvalues increases quite significant.
+
 \end{document}

### 2023-10-07 files/Overview.tex
summary

@@
 \subsubsection{Chapter 3}
+In this chapter, some theory for the Finite Element Method is discussed.
+This chapter contains two parts, that covers two different results.
+The first result is the convergence of the Galerkin approximation of a general vibration problem.
+This result is presented in the article \cite{BV13}.
+The second result concerns the convergence of the eigenvalues and eigenfunctions of a one-dimensional vibration problem when applying the Finite Element Method.
+This result is presented in the textbook \cite{SF97}.
+In the first section, the authors continue with the general vibration problem that is used in chapter 2.
+The general vibration problem has a solution as shown in chapter 2.
+The Galerkin Approximation is derived from the general vibration probelm and is rewritten into a system of ordinary differential using the Finite Element Method.
+This oridinary differential equation can be proven to have a unique solution.
+The main results of \cite{BV13} shows that this solution of the Galerkin Approximation converges to the solution of the general vibration problem.
+The approach of the authors is to calculate the error estimates.
+The error is split into two parts, a semi-discrete and a fully discrete problem.
+Two assumptions are added to the assumptions from chapter 2.
+Using these assumptions, the authors obtain error estimates for the semi-discrete and fully discrete problems.
+
+The second part of the chapter considers work done in a textbook \cite{SF97}.
+
 \subsubsection{Chapter 4}

### 2023-10-09 files/Overview.tex
Summary v1

@@
 The second part of the chapter considers work done in a textbook \cite{SF97}.
+The specific work discussed, covers the convergence of the eigenvalues and eigenfunctions of a one-dimensional vibration problem when applying the Finite Element Method.
+The authors consider a general eigenvalue problem.
+Then using the Rayleigh-quotient, from the Rayleigh-Ritz method, as well as an approximation theorem from \cite{ORXX}, the main result is proven.
+The specific work done in this section is updating the notation of the textbook, as well as expanding some results so that the results are easier to understand.
 
 \subsubsection{Chapter 4}
+This chapter is a focus on the main model theory of this disseration, the Timoshenko beam theory.
+The first section is a discussion of modal analysis applied to the Timoshenko beam theory, and specifically a discussion of the article \cite{VV06}.
+In this article, the authors present a method to calculate the exact eigenvalues and eigenfunctions of a Timoshenko beam.
+This method considers the boundary conditions, which differs from most other research.
+Starting with a general eigenvalue problem for a Timoshenko beam model, the authors derive a general solution for this problem.
+The authors then explain the method by hands of an example by applying the method to a cantilever beam model.
+The next sections of this chapter also then looks at examples of applying the method, first to a cantilever beam model, and then to a free-free beam model.
+The focus of these applications are to show that the method works and that the numerical results can be obtained easily.
+Similar numerical results will be required in chapter 6.
+The next section is a short discussion on a suspended beam model, afterwards an interesting article \cite{SP06} is discussed.
+In this article, the authors investigate the validity of the Timoshenko beam theory, by comparing the eigenvalues (natural frequencies) for a emperically mesasured beam, to a Timoshenko beam and a three-dimensional beam using Finite Element Analysis.
+The specific model used is a free-free beam.
+The emperical results are obtained by vibrating a suspended steel beam and measuring the natural frequencies.
+These results are then compared to the theoretical results.
+Finally the chapter finished by looking at an interesting model of a cantilever beam with a tip-body with elastic interfaces.
+These results combine modal analysis and looks at the behavior of the model.
+This section serves as an example of how useful the Timoshenko beam theory can be in a complex model.
+
 \subsubsection{Chapter 5}
+In this chapter, the Finite Element Method is applied to cantilever two-dimensional,and three-dimensional cantilever beams and a cantilever Reissner-Mindlin plate.
+The aim of this section is to obtain a numerical formula to calculate the eigenvalues and eigenfunctions of the models.
+The results of these formulas will be used in chapter 6.
+The Finite Element Method need not be applied to the Timoshenko beam theory, as chapter 4 provides an alternative method.
+For all the models, the Finite Element Method is applied using bi-cubic or tri-cubic basis functions to improve the rate of convergence and reduce the processing required to obtain accurate results.
+
 \subsubsection{Chapter 6}
+In this chapter, the main comparisons of the models are conducted.
+The first section is a discussion of the article \cite{LVV09}.
+Each section in this chapter follows the same structure as this article.
+In this article, the authors investigate the validity of a cantilever Timoshenko beam models, by comparing it to a two-dimensional cantilever Timoshenko beam model.
+To make this comparison, the authors compare the eigenvalues and eigenfunctions of the models.
+But since the two-dimensional model is more complex, there are `non-beam type' eigenvalues.
+These are eigenvalue that are not in the Timoshenko beam theory, and does not relate to beam type problems.
+To be able to find the beam type eigenvalues that can be compared, the authors compare the mode shapes.
+This allows the eigenvalues to be matched up.
+The results of the article show that the Timoshenko beam model compares very well to the two-dimensional beam.
+The comparison improves when the application is for a long and slender beam.
+The results of the article are verified and more results are added to extend the article and also to be using the the following sections.
+But in real-world applications, a beam is a three-dimensional model.
+Therefore it would be better to use a three-dimensional model to investigate the validity of the Timoshenko beam theory.
+The authors of \cite{LVV09} mentions this, and suggests using the two-dimensional model as an intermediate step to avoid complexities.
+So in the second section of this chapter, the validity of the two-dimensional model is investigated using the three-dimensional model as a reference.
+The results show that the two-dimensional model also compares very well to the three-dimensional model.
+Similar to the one-dimensional case, the results improve for a long and slender beam, and also if the width of the three-dimensional beam is not larger than the height of the beam.
+When increasing the width past the size of the height, the two-dimensional model is less accurate.
+This shape does however bring into question the use of a beam model, and something like a plate model might be better suited.
+In the last section, the validiy of the Reissner-Mindlin plate model is investigated.
+Similar to how the Timoshenko beam theory improves on the Euler-Bernoulli beam theory, the Reissner-Mindlin plate theory improves on the classical plate theory.
+The numerical results do show that this Reissner-Mindlin plate model compares well to a three-dimensional plate model, also when the dimensions of the models are realistic for application.
 

### 2023-10-14 files/Chapter5/2D_FEM.tex
chapter 5 fixes

--- 2022-11-08 files/Chapter6/2D_FEM.tex
@@
 \section{Introduction}
-In this chapter, the Finite Element Method (FEM) is applied to the two- and three-dimensional cantilever beams as well as a Reissner-Mindlin cantilever plate.
-The aim of this chapter is to obtain a numerical formula to calculate the eigenvalues and eigenvectors for these models.
-This chapter is preparation for Chapter 6.\\
+In this chapter, the Finite Element Method (FEM) is applied to the models of this dissertation, presented in chapter 1.
+The goal of this chapter is to obtain numerical formulas that can be used to calculate the eigenvalues and eigenvectors for the models.
+This is in preperation of chapter 6, where the eigenvalues and eigenvectors of the models are compared.
+
+In chapter 4, a method was discussed to obtain the eigenvalues and eigenvectors for the Timoshenko beam model.
+Therefore it is not neccesary to apply the Finite Element Method on the Timoshenko model to obtain the eigenvalues and eigenvectors.
+The Finite Element Mehtod is applied to the two-dimensional and three-dimensional models.
 
@@
 \begin{itemize}
-	\item[] Section \ref{sec:FEM:2D} FEM for a two-dimensional cantilever body.
-	\item[] Section \ref{sec:FEM:3D} FEM for a three-dimensional cantilever body. 
-	\item[] Section \ref{sec:FEM:Plate} FEM for A Reissner-Mindlin cantilever plate model. 
+	\item[] Section \ref{sec:FEM:2D} FEM for a cantilever two-dimensional elastic body. This is problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
+	\item[] Section \ref{sec:FEM:3D} FEM for a cantilever three-dimensional elastic body. This is problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.
+	\item[] Section \ref{sec:FEM:Plate} FEM for a cantilever Reissner-Mindlin plate. This is problem P-1 in section \ref{ssec:P_Model:ModelProblems}.
 \end{itemize}
 
-\section{Two-dimensional cantilever body} \label{sec:FEM:2D}
-Consider a two-dimensional cantilever elastic body, with a rectangular cross-section.
+\section{A cantilever two-dimensional body} \label{sec:FEM:2D}
+Consider a cantilever two-dimensional elastic body, with a rectangular cross-section.
 
-\subsubsection{Reference configuration for rectangular cross-section}
+\subsubsection{Reference configuration for rectangular cross-section}\label{sssec:2D_Model:RefConf}
 Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$.
-Denote the elastic body by $\Omega \in R_2$, with $(0,0)$ as the reference point.
-For a rectangular cross-section, $\Omega$ can be described as
+Denote the elastic body by $\Omega \in R_2$, with $(0,0)$ as the point of reference.
+For a rectangular cross-section, the body $\Omega$ can be described as,
 \begin{eqnarray*}
 	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
-\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines as follows:
+\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines (or edges) as follows:
 
@@
 	\begin{eqnarray*}
-		\Sigma_0:& \quad x_1 &= 0\\
-		\Sigma_1:& \quad x_1 &= 1
+		\Sigma:& \quad x_1 &= 0\\
+		\Gamma_3:& \quad x_1 &= 1
 	\end{eqnarray*}
@@
 
+In this configuration, the body is clamped rigidly to the surface at $x_1 = 0$ denoted as $\Sigma$ and the body is free-hanging on the other boundaries denoted by $\Gamma$.
+
 \subsubsection{Cantilever elastic body}
-Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries This is Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
+Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$.
+The body is free-hanging on the other boundaries.
+Recall this is Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
 \FloatBarrier
@@
 
+		% Add Σ at x_1 = 0
+		\node at (-1.4,0) {$\Sigma$};
+
+		% Add Γ₁ at x_2 = -h/2
+		\node at (3.5,-1.2) {$\Gamma_1$};
+
+		% Add Γ₂ at x_2 = h/2
+		\node at (3.5,0.9) {$\Gamma_2$};
+
+		% Add Γ₃ at x_1 = 1
+		\node at (8,0) {$\Gamma_3$};
+
 	\end{tikzpicture}
@@
 
-In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is defined by Problem 2D-1V.
-For convenience, some results from section \ref{ssec:2D_Model:VariationalForm} are repeated here.
+In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2D-1V.
+Some of the results from section \ref{sec:2D_Model} are repeated here for convenience.
+Using the reference configuration, these results are rewritten from a general form to a model specific form.
 
@@
 \end{align}
-for all $\phi \in T(\Omega)$.\\
-
-With the test function space 
+for all $\phi \in T(\Omega)$. With the test function space 
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-The bilinear forms and integral function defined by
+
+The bilinear forms and integral function is defined by
 \begin{eqnarray}
@@
 \end{eqnarray}
-with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.\\
+with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.
 
-Using the definition of the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten as follows.
+Using the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten into a model specific form.
 
@@
 
+See chapter 2 for the existence theory.
+
 \subsection{Galerkin approximation}\label{2d_FEM_G}
-Divide the reference configuration $\Omega$ into a rectangular grid of elements, such that there are $n = n_1\times n_2$ nodes.\\
+To be able to apply the Finite Element Method to Problem 2D-1V, the body $\Omega$ needs to be discretised.
+This is done by dividing the body $\Omega$ into discrete shapes, called elements.
+There are various types of shapes of elements that can be used.
+Since the body $\omega$ is has a rectangular cross-section, rectangular are the simplist elements to use.
+
+Divide the reference configuration $\Omega$ into a grid of rectangular elements, such that there are $n = n_1\times n_2$ nodes.
 
 Define a set of $n$-dimensional linear independent basis functions.
-For the two dimensional model, the basis functions can be defined by the set $$\left\{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \right\}.$$ For this dissertation, we use bi-cubic functions $\phi_i$, however simpler bi-linear functions can also be used.
-For easier notation, denote each of these basis functions by $\delta_i$.\\
+For the two dimensional model, the basis functions can be defined by the set $$B = \left\{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \right\}.$$
 
-The functions in this set that satisfies the conditions of the test function space $T(\Omega)$ are called the admissible basis functions.
-The admissible basis functions for this model can be renumbered and expressed as the set $\left \{\delta_1, \delta_2,..., \delta_k \right\}$ for some $k \leq 2n$.\\
+These functions are chosen as bi-cubic functions $\phi_i$.
+Simpler bi-linear functions can also be used, however the use of the bi-cubic basis functions results in faster convergence and also the benefit of obtaining the derivatives of the solution at the expense of more complexity.
+
+The subset of basis functions $B$ that satisfies all the conditions of the test function space $T(\Omega)$ are called the admissible basis functions.
+Denote the admissible basis functions by $\delta_j$, where each $\delta_j$ is a unique element of $B$.
+The admissible basis functions can be numbered and expressed as the set $A = \left \{\delta_1, \delta_2,..., \delta_k \right\}$ for some $k \leq 2n$.\\
 
@@
 
-Problem 2D-1V can now be rewritten into a Galerkin Approximation, denoted by Problem 2D-1G.
+Substitution of $u^h$ into Problem 2D-1V, results in the following Galerkin Approximation, denoted by Problem 2D-1G.
 
@@
 	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I, \phi_i)
-\end{eqnarray*} for $i = 1,2,...,k$.\\
-
-\textbf{Remarks:}
-\begin{itemize}
-	\item[] $Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$. i.e. $Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.
-\end{itemize}
+\end{eqnarray*} for $i = 1,2,...,k$.
+$Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$.
+i.e.
+$Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.
 
@@
 \end{minipage}
-for $i,j = 1,2,...,k$.\\
+for $i,j = 1,2,...,k$.
 
@@
 	{M_{F}}_{j,i} = \int_{\Omega}  \phi_i \phi_j~dA
-\end{eqnarray*} for $i = 1,2,...,k$ and for $j =1,2,...,2n$.\\
+\end{eqnarray*}
+
+for $i = 1,2,...,k$ and for $j =1,2,...,2n$.
 
@@
 
-The matrices ${O}$ and ${O_f}$ are the zero matrices of the same size as $\mathbf{M}$ and ${M_f}$ respectively.\\
+The matrices ${O}$ and ${O_f}$ are the zero matrices of the same size as $\mathbf{M}$ and ${M_f}$ respectively.
 
@@
 
-\subsubsection{Remark}
-This form of $\bar{u}$ is determined by the Hermite cubic basis functions.
+\textbf{Remark} This form of $\bar{u}$ is determined by the use of the bi-cubic basis functions.
 
@@
 \end{eqnarray}
-
-Now the eigenvalue problem can be solve using a finite difference method.
 

### 2023-10-14 files/Chapter5/3D_FEM.tex
chapter 5 fixes

@@
 
-\section{Three-dimensional elastic model}\label{sec:FEM:3D}
-Consider a three-dimensional cantilever elastic body, with a rectangular cross-section.
+In this section, a similar approach is applied to the three-dimensional elastic body.
+
+\section{A cantilever three-dimensional body}\label{sec:FEM:3D}
+Consider a cantilever three-dimensional elastic body, with a rectangular cross-section.
 
@@
 Let $\{e_1,e_2,e_3\}$ be a right-handed orthonormal basis for $R^3$.
-Denote the elastic body as $\Omega \in R^3$ with $(0,0,0)$ the reference point.
-For a rectangular cross-section, $\Omega$ can be described as
+Denote the elastic body as $\Omega \in R^3$ with $(0,0,0)$ the point of reference.
+For a rectangular cross-section, the body $\Omega$ can be described as
 \begin{eqnarray*}
@@
 	\begin{eqnarray*}
-		\Sigma_0:& \quad x_1 &= 0\\
-		\Sigma_1:& \quad x_1 &= 1\\
+		\Sigma:& \quad x_1 &= 0\\
+		\Gamma_5:& \quad x_1 &= 1\\
 		\Gamma_1:& \quad x_3 &= -{b}/{2} 
@@
 
+Using this notation, the boundary conditions are similar to the two-dimensional model in section \ref{sssec:2D_Model:RefConf}, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.
+
 \subsubsection{Cantilever elastic body}
-Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma_0$ and free-hanging at all the other sides.
-This is referred to as Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.
+Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma$ and free-hanging at all the other sides.
+This is Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.
 \FloatBarrier
@@
 In section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3D-1V.
-For convenience, some results from section \ref{ssec:3D_Model:VariationalForm} are repeated here.
+This general form can now be rewritten as in a model specific form using the reference configuration.
+For convenience, some of the results from section \ref{sec:3D_Mode} are repeated here.
 
@@
 
-Using the definition of the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten as follows.
+Using the definition of the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten in the following model specific forms: 
 \subsubsection*{Constitutive equations}
@@
 
-In this form, the bilinear form $b$ is more useful for applications than the general form.
-
 \subsection{Weak variational form}
@@
 
+See chapter 2 for the existence theory.
+
 \subsection{Galerkin approximation}
+As mentioned in the previous section, section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised.
+This is model, three-dimensional elements shapes are required.
+The elements used in this dissertation are rectangular prismatic elements.
+These elements are also known as brick shaped elements as described by \cite{Wu06}.
+This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.\
+
 Divide the reference configuration $\Omega$ into a grid of rectangular prismatic elements, such that there are $n = n_1 \times n_2 \times n_3$ nodes.
-These rectangular prismatic elements are also known as brick shaped elements as described by \cite{Wu06}.
-This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.\\
 
@@
 \begin{eqnarray*}
- \{\langle\phi_1, 0 , 0\rangle, \langle\phi_2, 0, 0\rangle,...,\langle\phi_{n}, 0, 0 \rangle,\\
+ B = \{\langle\phi_1, 0 , 0\rangle, \langle\phi_2, 0, 0\rangle,...,\langle\phi_{n}, 0, 0 \rangle,\\
 	\langle 0,\phi_1 ,0 \rangle,\langle 0 ,\phi_2,0\rangle,...,\langle 0,\phi_{n},0\rangle,\\
@@
 \end{eqnarray*}
+
+For the this three-dimensional model, tri-cubix basis functions are used.
+These basis functions are an extension of the Hermite cubic basis functions from the two-dimensional model.
+Although this is more complex than using tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.\\
 
@@
 
-The functions that satisfy the conditions of the test function space $T(\Omega)$ are called the admissible basis functions.
-The admissible basis functions for this model can be renumbered and expressed as the set $\left\{\delta_1, \delta_2, ..., \delta_k \right\}$ for some $k \leq 3n$.\\
+Similar to \ref{2d_FEM_G}, denote the admissible basis functions by $\delta_j$, where each $\delta_j$ is a unique element of $B$ satisfying all the conditions of the test function space $T(\Omega)$.
+The admissible basis functions are numbered and expressed as the set $A = \left\{\delta_1, \delta_2, ..., \delta_k \right\}$ for some $k \leq 3n$.\\
 
@@
 
-Problem 3D-1V can now be rewritten into a Galerkin Approximation, denoted by Problem 3D-1G.
+Substituting $u^h$ into Problem 3D-1V, results in the following Galerkin approximation, denoted by Problem 3D-1G.
 
@@
 	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I \cdot \phi_i)
-\end{eqnarray*} for $i = 1,2,...,k$.\\
+\end{eqnarray*} for $i = 1,2,...,k$.
+$Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$.
+i.e.
+$Q^I_{i,j, h} = Q(x_i,x_j, x_h)$ for $i = 1,2,...,n_1$, $j = 1,2,...,n_2$ and $h = 1,2,...,n_3$.
 
@@
 	M\ddot{\bar{u}} & = & K\bar{u} + M_{f}Q^I. \label{3D_M}
-\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \langle u, \partial_1 u, \partial_2 u, \partial_3 u, \partial_{11} u, \partial_{12}u, \partial_{13}u,\partial_{22}u,\partial_{23}u, \partial_{33}u,$\\$ \partial_{111}u, \partial_{112}u, \partial_{113}u, \partial_{121}u, \partial_{122}u, \partial_{123}u, \partial_{133}u,\partial_{223}u,\partial_{233}u,\partial_{333}u \rangle$.
-\textcolor{red}{beter manier om voor te stel?}
+\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \partial^i_1u \partial^j_2u \partial^k_3u$ for $i,j,k = 0,1,2,3$.
 
 \subsection{Eigenvalue problem}
-The equation \eqref{3D_M} is the same form as in section \ref{2dFEM_EP} for the two-dimensional elastic body.
-Therefore the derivation of the eigenvalue problem is identical.
-Denote the eigenvalue problem for Problem 3D-1 by Problem 3D-1E.
+The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in section \ref{2dFEM_EP}.
 
@@
 \end{eqnarray}
+
 \end{document}

### 2023-10-23 files/Overview.tex
ssummary

@@
 The numerical results do show that this Reissner-Mindlin plate model compares well to a three-dimensional plate model, also when the dimensions of the models are realistic for application.
+
+\subsection*{500 Word Summary}
+This dissertation is a literature study into the comparison of different dimensional linear model.
+This comparison is an investigation of the validity of lower dimensional models in practical appplications.
+
+This dissertation embarks on a critical examination and comparative analysis of various linear mechanical models, principally assessing their applicability and accuracy in replicating real-world scenarios.
+The term "validity" in this context refers to how precisely a model, such as the Timoshenko beam theory or the Reissner-Mindlin plate model, emulates more detailed and complex models in practical applications.
+The methodological approach pivots around modal analysis, which allows model solutions to be represented as a linear combination of eigenvalues and eigenfunctions, facilitating a systematic comparison between different models primarily through their respective eigenvalues and eigenfunctions.
+
+In Chapter 1, the fundamental models under scrutiny are introduced, including the pivotal Timoshenko beam theory.
+The chapter seeds the research question concerning the efficacy and applicability of simplified models compared to their complex two-dimensional and three-dimensional counterparts, aiming to validate the practical use of simplified models through a systematic comparative approach.
+
+Chapter 2 delves into general vibration problems, building upon referenced scholarly works.
+It involves exploring the theoretical framework, involving a linear operator "A" and its relationship with the $C_0$-semigroup, to transfigure the general vibration problem into a system of first-order differential equations, which, through semi-group theory, enables the derivation of a unique solution.
+
+Chapter 3 dives into the Finite Element Method (FEM) and its theoretical underpinnings, bifurcating its exploration into two primary results concerning the Galerkin approximation's convergence and eigenvalue and eigenfunction convergence in a one-dimensional vibration problem within the FEM framework.
+The chapter seamlessly integrates theory and practical applicability, demonstrating how theoretical advancements lead to robust model solutions through innovative approaches.
+
+Chapter 4 spotlights the Timoshenko beam theory, elucidating its application and methodology via modal analysis and hands-on examples.
+A unique approach to calculating exact eigenvalues and eigenfunctions considering boundary conditions is unveiled, moving away from standard research practices.
+It blends theoretical discussions with practical examples and culminates by examining a complex model of a cantilever beam with a tip-body and elastic interfaces, demonstrating the Timoshenko beam theory's practical utility.
+
+In Chapter 5, the FEM is applied to two-dimensional and three-dimensional cantilever beams and a cantilever Reissner-Mindlin plate, aiming to derive numerical formulas for the eigenvalues and eigenfunctions of the models, which will be utilized in Chapter 6.
+The methods engage bi-cubic or tri-cubic basis functions to optimize the convergence rate and minimize computational requirements.
+
+Chapter 6 orchestrates a comprehensive comparison and validation of the models discussed.
+It methodically outlines comparative analyses of the Timoshenko beam model against two-dimensional and three-dimensional models, examining their eigenvalues and eigenfunctions for validity.
+The comparisons span different beam and plate configurations, culminating in an analysis that validates the Reissner-Mindlin plate model against a three-dimensional plate model, affirming its reliability in realistic application dimensions.
+
+In essence, this dissertation offers a rigorous, comparative exploration of linear models, primarily the Timoshenko beam theory and Reissner-Mindlin plate model, juxtaposing them against more complex models, and spotlighting their effectiveness and limitations across various practical contexts through detailed theoretical and practical explorations.
 

### 2023-10-23 files/Overview.tex
Summary 500 words

--- 2023-10-09 files/Overview.tex
@@
 \begin{document}
+
+\section{500-word summary}
+This dissertation is a literature study that investigates the validity of different linear models in application.
+Validity in this context refers to how well simplified lower dimensional models compare to more realistic higher dimensional models.
+This dissertation will investigate the validity of the Timoshenko beam theory and the Reissner-Mindlin plate theory.
+The higher dimensional models are a two- and three-dimensional beam and a three-dimensional plate.
+In the first chapter, the models are provided.
+
+Next, a discussion of the existence and uniqueness of solutions for a general vibration problem.
+The article discussed provide four assumptions, and prove there exists an infinitesimal generator of a $C_0$-semigroup of contractions, that rewrites the problem into an initial value problem, with a unique solution.
+The authors then prove this is also a solution of the general vibration problem.
+An application of this theory is demonstrated using a cantilever Timoshenko beam.
+
+Thereafter a discussion of two theoretical results for the Finite Element Method.
+The first result is from an article where the convergence of the Galerkin Approximation is proved.
+A Galerkin Approximation of the general vibration problem is derived.
+Using the Finite Element Method, this Galerkin Approximation is rewritten into an initial value problem, that has a unique solution.
+The authors show that there exists error estimates that approximate the error between the general vibration problem and the initial value problem.
+The next result is from a textbook on the convergence of the eigenvalues and eigenvectors of a one-dimensional vibration problem.
+This section rewrites the textbook's results with updated notation, aiming for greater clarity and understanding.
+
+The forth chapter discusses results for the Timoshenko beam theory.
+First an article is examined that provides a method to calculate the exact eigenvalues and eigenvectors.
+The method is then applied to a cantilever and a free-free beam model.
+Next is a discussion of an empirical study, that compares the natural frequencies of a physical free-free beam to the theoretical results of the Timoshenko beam theory.
+Finally an extension on a technical report of a cantilever Timoshenko beam with a tip-body and elastic interfaces.
+This model serves as an example of the application of the Timoshenko theory in a complex model and adds to the article by expanding the numerical results.
+
+In the fifth chapter, the Finite Element Method is applied to the two and three-dimensional models of this dissertation.
+The goal of this chapter is to obtain a numerical formula that can be used to calculate the eigenvalues and eigenvectors of the models in preparation for the final chapter where the models are compared.
+
+The last chapter compares the eigenvalues and eigenvectors of the models.
+The approach is based on an article where a cantilever Timoshenko beam model is compared to a cantilever two-dimensional model.
+The article is discussed and results replicated.
+The article is then extended to a comparison of a two-dimensional model to a three-dimensional model.
+Finally, a cantilever Reissner-Mindlin plate model is compared to a cantilever three-dimensional plate model.
+
+\textcolor{red}{493 Words}
 

### 2023-10-26 files/Overview.tex
title

@@
 
-\section{500-word summary}
-This dissertation is a literature study that investigates the validity of different linear models in application.
-Validity in this context refers to how well simplified lower dimensional models compare to more realistic higher dimensional models.
-This dissertation will investigate the validity of the Timoshenko beam theory and the Reissner-Mindlin plate theory.
-The higher dimensional models are a two- and three-dimensional beam and a three-dimensional plate.
-In the first chapter, the models are provided.
-
-Next, a discussion of the existence and uniqueness of solutions for a general vibration problem.
-The article discussed provide four assumptions, and prove there exists an infinitesimal generator of a $C_0$-semigroup of contractions, that rewrites the problem into an initial value problem, with a unique solution.
-The authors then prove this is also a solution of the general vibration problem.
-An application of this theory is demonstrated using a cantilever Timoshenko beam.
-
-Thereafter a discussion of two theoretical results for the Finite Element Method.
-The first result is from an article where the convergence of the Galerkin Approximation is proved.
-A Galerkin Approximation of the general vibration problem is derived.
-Using the Finite Element Method, this Galerkin Approximation is rewritten into an initial value problem, that has a unique solution.
-The authors show that there exists error estimates that approximate the error between the general vibration problem and the initial value problem.
-The next result is from a textbook on the convergence of the eigenvalues and eigenvectors of a one-dimensional vibration problem.
-This section rewrites the textbook's results with updated notation, aiming for greater clarity and understanding.
-
-The forth chapter discusses results for the Timoshenko beam theory.
-First an article is examined that provides a method to calculate the exact eigenvalues and eigenvectors.
-The method is then applied to a cantilever and a free-free beam model.
-Next is a discussion of an empirical study, that compares the natural frequencies of a physical free-free beam to the theoretical results of the Timoshenko beam theory.
-Finally an extension on a technical report of a cantilever Timoshenko beam with a tip-body and elastic interfaces.
-This model serves as an example of the application of the Timoshenko theory in a complex model and adds to the article by expanding the numerical results.
-
-In the fifth chapter, the Finite Element Method is applied to the two and three-dimensional models of this dissertation.
-The goal of this chapter is to obtain a numerical formula that can be used to calculate the eigenvalues and eigenvectors of the models in preparation for the final chapter where the models are compared.
-
-The last chapter compares the eigenvalues and eigenvectors of the models.
-The approach is based on an article where a cantilever Timoshenko beam model is compared to a cantilever two-dimensional model.
-The article is discussed and results replicated.
-The article is then extended to a comparison of a two-dimensional model to a three-dimensional model.
-Finally, a cantilever Reissner-Mindlin plate model is compared to a cantilever three-dimensional plate model.
-
-\textcolor{red}{493 Words}
-
-\section{Summary}
+\section{Overview}
 
@@
 The other models are a two-dimensional elastic model, a three-dimensional elastic model and a Reissner-Mindlin plate model.
-The goal of this disseration to validate the use of the Timoshenko beam model and the Reissner-Mindlin plate model in applications.
+The goal of this dissertation to validate the use of the Timoshenko beam model and the Reissner-Mindlin plate model in applications.
 These models are simplified one-dimensional beam and two-dimensional plate models.
 But more realistic models exists, such as a two-dimensional and three-dimensional beam model and a three-dimensional plate model.
-Using modal analysis, it is shown that the solutions of the models can be represented as a linear combination of the eigenvalues and eigenfunctions.
-Therefore it is only required to compare the eigenvalues and eigenfunctions of the models to determine the difference of the solutions.
+Using modal analysis (see chapter 2), it is shown that the solutions of the models can be represented as a linear combination of the eigenvalues and eigenfunctions.
+Using this idea, it is only required to compare the eigenvalues and eigenfunctions of the models to be able to compare the difference between the solutions.
+In chapter 1, the models of the dissertation is given.
+They are given in a dimensionless form, and also the variational forms are derived.
+Model problems are then defined by including boundary conditions.
+These model problems are the models used in the rest of the dissertation.
 
 \subsubsection{Chapter 2}
-In this section, the existence and solutions for a general vibration problem is investigated.
+In this section, the existence of a unique solutions for a general vibration problem is investigated.
 The main article that is discussed is \cite{VV02}.
@@
 \subsubsection{Chapter 3}
-In this chapter, some theory for the Finite Element Method is discussed.
-This chapter contains two parts, that covers two different results.
+In this chapter, some theoretical results for the Finite Element Method is discussed.
+This chapter contains two parts, that covers two results.
 The first result is the convergence of the Galerkin approximation of a general vibration problem.
@@
 This result is presented in the textbook \cite{SF97}.
-In the first section, the authors continue with the general vibration problem that is used in chapter 2.
-The general vibration problem has a solution as shown in chapter 2.
-The Galerkin Approximation is derived from the general vibration probelm and is rewritten into a system of ordinary differential using the Finite Element Method.
+In the first section, the authors continue with the general vibration problem that is used in chapter 2, as well as the assumptions made in chapter 2.
+Hence there is a unique solution.
+The Galerkin Approximation for the general vibration problem is derived and is rewritten into a system of ordinary differential using the Finite Element Method.
 This oridinary differential equation can be proven to have a unique solution.
-The main results of \cite{BV13} shows that this solution of the Galerkin Approximation converges to the solution of the general vibration problem.
+The goal of \cite{BV13} is to show that the solution for the general vibration problem and the solution for the Galerkin Approximation can be made arbitrarily close by choosing a sufficiently small $h$.
 The approach of the authors is to calculate the error estimates.
 The error is split into two parts, a semi-discrete and a fully discrete problem.
-Two assumptions are added to the assumptions from chapter 2.
+Two new assumptions are added to the assumptions from chapter 2.
 Using these assumptions, the authors obtain error estimates for the semi-discrete and fully discrete problems.
+This result shows that the error can be made arbitrarily small by choosing a sufficiently small $h$.
 
@@
 The next sections of this chapter also then looks at examples of applying the method, first to a cantilever beam model, and then to a free-free beam model.
-The focus of these applications are to show that the method works and that the numerical results can be obtained easily.
-Similar numerical results will be required in chapter 6.
+The examples shows the use of the method, and is preperation for chapter 6 where these results are required for the comparison of the models.
 The next section is a short discussion on a suspended beam model, afterwards an interesting article \cite{SP06} is discussed.
-In this article, the authors investigate the validity of the Timoshenko beam theory, by comparing the eigenvalues (natural frequencies) for a emperically mesasured beam, to a Timoshenko beam and a three-dimensional beam using Finite Element Analysis.
-The specific model used is a free-free beam.
-The emperical results are obtained by vibrating a suspended steel beam and measuring the natural frequencies.
-These results are then compared to the theoretical results.
+In this article, the authors investigate the validity of the Timoshenko beam theory, by comparing the eigenvalues (natural frequencies) for a physical beam, to a Timoshenko beam and a three-dimensional beam using Finite Element Analysis.
+The authors suspended the beam, and vribrated the beam to induce a free-free beam and measure the natural frequencies.
+These emperical results are then compared to the theoretical results.
+This result, together with the results in chapter 6, give a good picture to the validity of the Timoshenko beam theory.
 Finally the chapter finished by looking at an interesting model of a cantilever beam with a tip-body with elastic interfaces.
 These results combine modal analysis and looks at the behavior of the model.
-This section serves as an example of how useful the Timoshenko beam theory can be in a complex model.
+This section is an example of the usefullness of the Timoshenko beam theory.
+A similar model using a more realistic two- or three-dimensional model will be very complex.
 
@@
 The results of these formulas will be used in chapter 6.
-The Finite Element Method need not be applied to the Timoshenko beam theory, as chapter 4 provides an alternative method.
+The Finite Element Method is not applied to the Timoshenko beam theory, as chapter 4 provides an alternative method.
 For all the models, the Finite Element Method is applied using bi-cubic or tri-cubic basis functions to improve the rate of convergence and reduce the processing required to obtain accurate results.
+Each section ends with a eigenvalue problem for the models that can be easily applied to a computer program to calculate the eigenvalues and eigenvectors for the models.
+These numerical formulas will be used to obtain the results in chapter 6.
 
@@
 The numerical results do show that this Reissner-Mindlin plate model compares well to a three-dimensional plate model, also when the dimensions of the models are realistic for application.
+
+\section{500-word summary}
+This dissertation is a literature study that investigates the validity of different linear models for applications.
+Validity in this context refers to how well simplified lower dimensional models compare to more realistic higher dimensional models.
+This dissertation will investigate the validity of the Timoshenko beam theory and the Reissner-Mindlin plate theory, with focus on the Timoshenko theory.
+The higher dimensional models are a two- and three-dimensional beam models and a three-dimensional plate model.
+
+In the first chapter, the models are provided.
+Then a discussion follows of the existence and uniqueness of solutions for a general vibration problem.
+The article discussed provide necessary four assumptions, and prove there exists an infinitesimal generator of a $C_0$-semigroup of contractions, that rewrites the problem into an initial value problem, with a unique solution.
+The authors then prove this is also a solution of the general vibration problem.
+An application of this theory is demonstrated using a cantilever Timoshenko beam.
+
+Thereafter of two theoretical results for the Finite Element Method is discussed, one from an article and one from a textbook.
+The first result looks at the convergence of the Galerkin Approximation for vibration problems.
+Using the Finite Element Method, this Galerkin Approximation is rewritten into an initial value problem, that has a unique solution.
+The authors show that there exists error estimates that approximate the error between the general vibration problem and the initial value problem.
+The next result is on the convergence of the eigenvalues and eigenvectors of a one-dimensional vibration problem.
+This section rewrites the textbook's results with updated notation, aiming for greater clarity and understanding.
+
+Next the focus turns to the Timoshenko beam theory.
+First an article is examined that provides a method to calculate the exact eigenvalues and eigenvectors.
+The method is then applied to a cantilever and a free-free beam model.
+Next is a discussion of an empirical study, that compares the natural frequencies of a physical free-free beam to the theoretical results of the Timoshenko beam theory.
+Finally an extension on a technical report of a cantilever Timoshenko beam with a tip-body and elastic interfaces.
+This model serves as an example of the application of the Timoshenko theory in a complex model and adds to the article by expanding the numerical results.
+
+The attention is then turned to application where the Finite Element Method is applied to the two and three-dimensional models of this dissertation.
+The goal of this chapter is to obtain a numerical formula that can be used to calculate the eigenvalues and eigenvectors of the models in preparation for the final chapter where the models are compared.
+
+The final chapter compares the eigenvalues and eigenvectors of the models.
+The approach is based on an article where a cantilever Timoshenko beam model is compared to a cantilever two-dimensional model.
+The article is discussed and results replicated.
+The article is then extended to a comparison of a two-dimensional model to a three-dimensional model.
+Finally, a cantilever Reissner-Mindlin plate model is compared to a cantilever three-dimensional plate model.
+
+\textcolor{red}{500 Words}
 

### 2023-10-28 files/Chapter4/ModalAnalysisTimo.tex
chapter 4

@@
 An example of modal analysis on a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}.
-In this chapter, more general theory for modal analysis of te Timoshenko beam theory is discussed, as well as some more examples of the application of the theory.
+In this chapter, more general theory for modal analysis of te Timoshenko beam theory is discussed, as well as more examples of the application of the theory.
 
@@
 
-\textcolor{red}{*****************SUGGESTION****************************}
-
-\subsubsection*{Stragety for determining the eigenvalues and eigenvectors}
+\subsubsection*{Strategy for determining the eigenvalues and eigenvectors}
 
@@
 
-\textcolor{red}{*****************OLD alles onder moontlik weg vat****************************}
-
-The next step is to determine the solution of the general eigenvalue problem.
-The strategy to obtain the eigenvalues and eigenvectors are described in detail in \cite{VV06} using an example.
-A summary of the strategy is presented here.
-
-From the general solutions for $u$ and $\phi$, the eigenvalues and eigenfunctions can be determined by imposing the boundary conditions at $x=0$ to reduce the solution space of four dimensions to a solution space of dimension at least two.
-
-The boundary conditions at $x=1$ is then substituted which results in a homogeneous system of linear equations of the form
-\begin{eqnarray*}
-A \bar{b} = \bar{0}
-\end{eqnarray*}
-This system either has the zero
-
- This system has either the zero solution or infinitely many solutions.
-To ensure a non-zero solution, the determinant of the coefficient matrix $A$ of the system of equations is set equal to 0.
-The equation $\textrm{det}(A) = 0$ is called the frequency equation.
-The frequency equation has infinitely many solutions and each solution corresponds to an eigenvalue.
-
- For each eigenvalue, a unique solution for the pair $\bar{b}$ can be obtained. A eigenfunction for $u$ and $\phi$ is obtained using $\bar{b}$ and corresponds to the relevant eigenvalue.
-
-The following two sections provide examples of this strategy applied to beam models. These examples are also in \cite{VV06}.
-
-**sluit af***
-******NB Verduidelik $\alpha$
 \end{document}

### 2023-10-28 files/Chapter4/SP06.tex
chapter2
chapter 4

@@
 \begin{document}
-\section{SP06}
-Consider a study by Stephen and Puchegger in 2006, article [SP06].
+\section{Empirical and numerical examination of a Timoshenko beam} \label{sec:SP06}
+Consider a study by Stephen and Puchegger in 2006, article \cite{SP06}.
 This study investigated the validity of the Timoshenko beam theory by hand of empirical and numerical data.
 The approach of the study is to compare the natural frequencies of a Timoshenko beam, to that of a three-dimensional elastic beam.
-The authors conducted comparisons between the models using theoretical methods as well as results from an empirical study on a physical beam, conducted by the authors.\\
+The authors conducted comparisons between the models using theoretical methods as well as results from an empirical study on a physical beam, conducted by the authors.
 
-The authors decided on a free-free beam configuration, as it is the easiest to achieve in the physical experiment.
-The natural frequencies of the Timoshenko beam theory was obtained by using frequency equations from an article by Levison and Cooke [LC81].
+The authors decided on a free-free beam configuration.
+The natural frequencies of the Timoshenko beam theory was obtained by using frequency equations from an article by Levison and Cooke \cite{LC81}.
 In theoretical approach of the three-dimensional beam, two methods were considered.
-A commercial finite elements method (ANSYS), and a resonant ultrasound spectroscopy (RUS) technique.\\
+A commercial finite elements method (ANSYS), and a resonant ultrasound spectroscopy (RUS) technique.
 
-This section discusses the results of [SP06].
+This section discusses the results of \cite{SP06}.
 
@@
 Let $\Omega$ be the reference configuration of a free-free beam with square cross-section.
-The authors of [SP06] do not formulate the models in the article.
+The authors of \cite{SP06} do not formulate the models in the article.
 Consider Problem T-4 from section \ref{ssec:1D_Model:ModelProblems} for the free-free Timoshenko beam and Problem 3D-2 from section \ref{ssec:3D_Model:ModelProblems} for the free-free three-dimensional beam.
-The model problems are given here again for the reader's convenience.
+The boundary conditions and reference configurations of the model problems are given below.
 
 \subsubsection*{Problem T-4}
-Find a function $u$, satisfying the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D}- \eqref{eq:1D_Model:EquationOfMotion2D} and constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D}- \eqref{eq:1D_Model:ConstitutiveEquations2D}.\\
+Find a function $u$, satisfying the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D}- \eqref{eq:1D_Model:EquationOfMotion2D} and constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D}- \eqref{eq:1D_Model:ConstitutiveEquations2D}.
 
@@
 \subsection{Experimental setup}
-Next the experiment conducted by [SP06] is discussed. A short, aluminium alloy beam with near square cross-section is suspended at both ends. The beam is suspended by carbon fibre loops.
+Next the experiment conducted by \cite{SP06} is discussed. A short, aluminium alloy beam with near square cross-section is suspended at both ends. The beam is suspended by carbon fibre loops.
 
@@
 
-To vibrate the beam, the authors of [SP06] excited the carbon fibre loops and the frequencies were measured using two piezoelectric transducers.
+To vibrate the beam, the authors of \cite{SP06} excited the carbon fibre loops and the frequencies were measured using two piezoelectric transducers.
 During the vibration, the beam will be momentarily free at both endpoints.
-The natural frequencies were obtained by sweeping through frequencies until a resonance was found.\\
+The natural frequencies were obtained by sweeping through frequencies until a resonance was found.
 
-The measured parameters of the beam is given in [SP06].
+The measured parameters of the beam is given in \cite{SP06}.
 Since the physical beam is only nearly square, the plane has two distinct planes.
-The plane of the beam with a larger diameter is referred to as the stiff plane and the plane of the beam with smaller diameter is referred to as the flexible plane, by [SP06].\\
+The plane of the beam with a larger diameter is referred to as the stiff plane and the plane of the beam with smaller diameter is referred to as the flexible plane, by \cite{SP06}.
 
@@
 \end{eqnarray*} with $\lambda_k$ the $k$'th eigenvalue.
-These natural frequencies $f_k$ are dimensionless, and can be scaled back by multiplying the natural frequency $f_k$ by $t_0=\ell\sqrt{\frac{\rho}{G\kappa^2}}$, as defined in Chapter 1.\\
+These natural frequencies $f_k$ are dimensionless, and can be scaled back by multiplying the natural frequency $f_k$ by $t_0=\ell\sqrt{\frac{\rho}{G\kappa^2}}$, as defined in Chapter 1.
 
-The cut-off frequency given in [SP06] can be expressed as
+The cut-off frequency given in \cite{SP06} can be expressed as
 \begin{eqnarray*}
@@
 \subsection{Results from SP06}
-The following table contains relevant results are obtained by [SP06]. 
+The following table contains relevant results are obtained by \cite{SP06}. 
 % Table generated by Excel2LaTeX from sheet 'Sheet1'
@@
 	\makebox[\textwidth]{
-	\caption{Results from [SP06] (excluding RUS).}
+	\caption{Results from \cite{SP06} (excluding RUS).}
 	\begin{tabular}{||c|c|cc|cc|c||}
@@
 Table 4.3 shows that the Timoshenko model compares well to the measured results from the experiment.
-The first 8 natural frequencies for the stiff and flexible planes are very close to the natural frequencies of the three-dimensional and physical beam.\\
+The first 8 natural frequencies for the stiff and flexible planes are very close to the natural frequencies of the three-dimensional and physical beam.
 

### 2023-11-01 files/Overview.tex
overview v2

@@
 \subsubsection{Chapter 1}
-This dissertation is a literature study that investigates the validity of different linear models.
+This dissertation is a literature study to investigate the validity of different linear models for beams and plates.
 The term validity in this dissertation means how well a model compares to a more realistic model for real world applications.
 The first chapter of the dissertation introduces the models.
-The main model is the Timoshenko beam theory.
-The other models are a two-dimensional elastic model, a three-dimensional elastic model and a Reissner-Mindlin plate model.
-The goal of this dissertation to validate the use of the Timoshenko beam model and the Reissner-Mindlin plate model in applications.
+The simplest model is the Timoshenko model.
+The other models are a two-dimensional elastic beam model, a three-dimensional elastic beam model and a Reissner-Mindlin plate model.
+The aim in this dissertation to validate the use of the Timoshenko beam model and the Reissner-Mindlin plate model in applications.
 These models are simplified one-dimensional beam and two-dimensional plate models.
 But more realistic models exists, such as a two-dimensional and three-dimensional beam model and a three-dimensional plate model.
-Using modal analysis (see chapter 2), it is shown that the solutions of the models can be represented as a linear combination of the eigenvalues and eigenfunctions.
+Using modal analysis (see Chapter 2), it is shown that the solutions of the models can be represented as a linear combination of the modal solutions.
 Using this idea, it is only required to compare the eigenvalues and eigenfunctions of the models to be able to compare the difference between the solutions.
-In chapter 1, the models of the dissertation is given.
-They are given in a dimensionless form, and also the variational forms are derived.
+In Chapter 1, the models of the dissertation is given (they are given in a dimensionless form).
 Model problems are then defined by including boundary conditions.
 These model problems are the models used in the rest of the dissertation.
+Also the variational forms are derived which enables us to see the similarity between the models.
 
 \subsubsection{Chapter 2}
+First, a variational form for a model problem of a cantilever Timoshenko beam given.
+This model problem in variational form is then extended to complete function spaces, and in turn a weak variational problem is obtained.
+This weak variational problem is used as an example to explain the main theory of the chapter, from the article \cite{VV02}.
+In this article, the authors present a general weak variational form.
+The weak variational form of all the model problems of this dissertation are special cases of this general weak variational problem.
+The assumptions and results can be formulated and applied to all the applications.
+
 In this section, the existence of a unique solutions for a general vibration problem is investigated.
@@
 The authors consider a general eigenvalue problem.
-Then using the Rayleigh-quotient, from the Rayleigh-Ritz method, as well as an approximation theorem from \cite{ORXX}, the main result is proven.
+Then using the Rayleigh-quotient, from the Rayleigh-Ritz method, as well as an approximation theorem from \cite{OR97}, the main result is proven.
 The specific work done in this section is updating the notation of the textbook, as well as expanding some results so that the results are easier to understand.
@@
 The examples shows the use of the method, and is preperation for chapter 6 where these results are required for the comparison of the models.
-The next section is a short discussion on a suspended beam model, afterwards an interesting article \cite{SP06} is discussed.
+The next section is a short discussion on a suspended beam model, afterwards an important article \cite{SP06} is discussed.
 In this article, the authors investigate the validity of the Timoshenko beam theory, by comparing the eigenvalues (natural frequencies) for a physical beam, to a Timoshenko beam and a three-dimensional beam using Finite Element Analysis.
@@
 Finally the chapter finished by looking at an interesting model of a cantilever beam with a tip-body with elastic interfaces.
-These results combine modal analysis and looks at the behavior of the model.
+These results combine modal analysis and look at the behavior of the model.
 This section is an example of the usefullness of the Timoshenko beam theory.
-A similar model using a more realistic two- or three-dimensional model will be very complex.
+A similar model using realistic two- or three-dimensional model will be very challenging.
 
@@
 In this chapter, the Finite Element Method is applied to cantilever two-dimensional,and three-dimensional cantilever beams and a cantilever Reissner-Mindlin plate.
-The aim of this section is to obtain a numerical formula to calculate the eigenvalues and eigenfunctions of the models.
+The aim of this section is to obtain an algorithm to calculate the eigenvalues and eigenfunctions of the models.
 The results of these formulas will be used in chapter 6.
@@
 Each section ends with a eigenvalue problem for the models that can be easily applied to a computer program to calculate the eigenvalues and eigenvectors for the models.
-These numerical formulas will be used to obtain the results in chapter 6.
+These algorithms will be used to obtain the results in chapter 6.
 

### 2023-11-02 files/Overview.tex
overview v2

@@
 The weak variational form of all the model problems of this dissertation are special cases of this general weak variational problem.
-The assumptions and results can be formulated and applied to all the applications.
+Therefore the assumptions and results can be formulated and applied to all the applications.
+The article gives four assumptions.
+Under these assumptions it is shown that the general vibration problem has a unique solution using semi-group theory.
+Next the theory is applied to the example weak variational problem for the cantilever Timoshenko beam, by showing that the assumptions hold.
 
-In this section, the existence of a unique solutions for a general vibration problem is investigated.
-The main article that is discussed is \cite{VV02}.
-In this article, the authors define a general vibration problem.
-The authors state four assumptions that need to be satified.
-Under these four assumptions, it can be shown that for the general vibration problem there exists a linear operator A, which is an infinitesimal generator of a $C_0$-semigroup of contractions with a domain in the problem space.
-This operator allows the general vibration problem to be rewritten as a system of first order differential equations $\displaystyle x' = Ax + f$.
-This differential equations are rewritten into an initial value problem which can be proven using semi-group theory to have a unique solution.
-The authors then provide the necessary proofs to show that a solution of the initial value problem is also a solution of the general vibration problem.
-An example of the application of this theory is provided using a cantilever Timoshenko beam.
+Finally the concept of modal analysis is introduced, which is fundamental to this dissertation.
+The idea of modal analysis is explained by hands of another example, again using a cantilever Timoshenko beam.
+Then the general case is discussed, following \cite{CVV18}.
+Given a general vibration problem, an eigenvalue problem and a differential equation is derived.
+An additional assumption is introduced by \cite{CVV18}.
+Under this assumption, the eigenvalue problem has infinite many solutions, and that the solution of the general vibration problem is an infinite series of the eigenvectors and general Fourier coefficients.
+Solving the differential equation, shows that these Fourier coeffiencients are periodic and a formal series solution for the general vibration problem (which is a boundary value problem) is obtained.
+This formal series solution is then shown to also be valid for a general initial value problem.
+This general case is applicable to all the models in this dissertation.
+
+Being able to express the solution of a model problem as a linear combination of the eigenvalues and eigenfunctions in a formal series solution, is fundamental to this dissertation.
+This means that the solutions of models will compare well if the eigenvalues and eigenfunctions compare well.
+The validity of the formal series solution is also a requirement as it ensures that the comparisons remain valid, as long as the models are disturbed in the same way.
 
 \subsubsection{Chapter 3}
-In this chapter, some theoretical results for the Finite Element Method is discussed.
-This chapter contains two parts, that covers two results.
+In this chapter, some theory for the Finite Element Method is discussed.
+This chapter contains two parts, that covers two different results.
 The first result is the convergence of the Galerkin approximation of a general vibration problem.
@@
 This result is presented in the textbook \cite{SF97}.
-In the first section, the authors continue with the general vibration problem that is used in chapter 2, as well as the assumptions made in chapter 2.
-Hence there is a unique solution.
-The Galerkin Approximation for the general vibration problem is derived and is rewritten into a system of ordinary differential using the Finite Element Method.
+In the first section, the authors continue with the general vibration problem that is used in chapter 2.
+The general vibration problem has a solution as shown in chapter 2.
+The Galerkin Approximation is derived from the general vibration probelm and is rewritten into a system of ordinary differential using the Finite Element Method.
 This oridinary differential equation can be proven to have a unique solution.
-The goal of \cite{BV13} is to show that the solution for the general vibration problem and the solution for the Galerkin Approximation can be made arbitrarily close by choosing a sufficiently small $h$.
+The main results of \cite{BV13} shows that this solution of the Galerkin Approximation converges to the solution of the general vibration problem.
 The approach of the authors is to calculate the error estimates.
 The error is split into two parts, a semi-discrete and a fully discrete problem.
-Two new assumptions are added to the assumptions from chapter 2.
+Two assumptions are added to the assumptions from chapter 2.
 Using these assumptions, the authors obtain error estimates for the semi-discrete and fully discrete problems.
-This result shows that the error can be made arbitrarily small by choosing a sufficiently small $h$.
 
@@
 \subsubsection{Chapter 4}
-This chapter is a focus on the main model theory of this disseration, the Timoshenko beam theory.
+This chapter is a focus on the main model theory of this dissertation, the Timoshenko beam theory.
 The first section is a discussion of modal analysis applied to the Timoshenko beam theory, and specifically a discussion of the article \cite{VV06}.
@@
 \section{500-word summary}
-This dissertation is a literature study that investigates the validity of different linear models for applications.
+This dissertation is a literature study that investigates the validity of different linear models in application.
 Validity in this context refers to how well simplified lower dimensional models compare to more realistic higher dimensional models.
-This dissertation will investigate the validity of the Timoshenko beam theory and the Reissner-Mindlin plate theory, with focus on the Timoshenko theory.
-The higher dimensional models are a two- and three-dimensional beam models and a three-dimensional plate model.
+This dissertation will investigate the validity of the Timoshenko beam theory and the Reissner-Mindlin plate theory.
+The higher dimensional models are a two- and three-dimensional beam and a three-dimensional plate.
+In the first chapter, the models are provided.
 
-In the first chapter, the models are provided.
-Then a discussion follows of the existence and uniqueness of solutions for a general vibration problem.
-The article discussed provide necessary four assumptions, and prove there exists an infinitesimal generator of a $C_0$-semigroup of contractions, that rewrites the problem into an initial value problem, with a unique solution.
+Next, a discussion of the existence and uniqueness of solutions for a general vibration problem.
+The article discussed provide four assumptions, and prove there exists an infinitesimal generator of a $C_0$-semigroup of contractions, that rewrites the problem into an initial value problem, with a unique solution.
 The authors then prove this is also a solution of the general vibration problem.
@@
 
-Thereafter of two theoretical results for the Finite Element Method is discussed, one from an article and one from a textbook.
-The first result looks at the convergence of the Galerkin Approximation for vibration problems.
+Thereafter a discussion of two theoretical results for the Finite Element Method.
+The first result is from an article where the convergence of the Galerkin Approximation is proved.
+A Galerkin Approximation of the general vibration problem is derived.
 Using the Finite Element Method, this Galerkin Approximation is rewritten into an initial value problem, that has a unique solution.
 The authors show that there exists error estimates that approximate the error between the general vibration problem and the initial value problem.
-The next result is on the convergence of the eigenvalues and eigenvectors of a one-dimensional vibration problem.
+The next result is from a textbook on the convergence of the eigenvalues and eigenvectors of a one-dimensional vibration problem.
 This section rewrites the textbook's results with updated notation, aiming for greater clarity and understanding.
 
-Next the focus turns to the Timoshenko beam theory.
+The forth chapter discusses results for the Timoshenko beam theory.
 First an article is examined that provides a method to calculate the exact eigenvalues and eigenvectors.
@@
 
-The attention is then turned to application where the Finite Element Method is applied to the two and three-dimensional models of this dissertation.
+In the fifth chapter, the Finite Element Method is applied to the two and three-dimensional models of this dissertation.
 The goal of this chapter is to obtain a numerical formula that can be used to calculate the eigenvalues and eigenvectors of the models in preparation for the final chapter where the models are compared.
 
-The final chapter compares the eigenvalues and eigenvectors of the models.
+The last chapter compares the eigenvalues and eigenvectors of the models.
 The approach is based on an article where a cantilever Timoshenko beam model is compared to a cantilever two-dimensional model.
@@
 
-\textcolor{red}{500 Words}
+\textcolor{red}{493 Words}
 
@@
 For the one-dimensional case, the Timoshenko beam theory is considered.
-Four different models problems are used in this disseration.
+Four different models problems are used in this dissertation.
 These model problems are a cantilever, a free-free beam, a pinned-pinned beam and a suspended beam.

### 2023-11-02 files/Overview.tex
Overview v2

@@
 This result is presented in the textbook \cite{SF97}.
-In the first section, the authors continue with the general vibration problem that is used in chapter 2.
-The general vibration problem has a solution as shown in chapter 2.
+In the first section, the authors continue with the general vibration problem that is used in Chapter 2.
+The general vibration problem has a solution as shown in Chapter 2.
 The Galerkin Approximation is derived from the general vibration probelm and is rewritten into a system of ordinary differential using the Finite Element Method.
@@
 The error is split into two parts, a semi-discrete and a fully discrete problem.
-Two assumptions are added to the assumptions from chapter 2.
+Two assumptions are added to the assumptions from Chapter 2.
 Using these assumptions, the authors obtain error estimates for the semi-discrete and fully discrete problems.
@@
 The first result is the convergence of the Galerkin approximation for vibration problems.
-This is presented in the article \cite{BV13.} For this result, the general variational form of chapter 2 is used.
+This is presented in the article \cite{BV13.} For this result, the general variational form of Chapter 2 is used.
 The Galerkin approximation of this general variational problem can be derived, as well as an initial value problem using the standard Finite Element Analysis matrices.

### 2023-11-04 files/Overview.tex
overview v2

@@
 The simplest model is the Timoshenko model.
-The other models are a two-dimensional elastic beam model, a three-dimensional elastic beam model and a Reissner-Mindlin plate model.
+The other models are a two-dimensional elastic beam model, three-dimensional elastic beam and plate models and a Reissner-Mindlin plate model.
 The aim in this dissertation to validate the use of the Timoshenko beam model and the Reissner-Mindlin plate model in applications.
@@
 These model problems are the models used in the rest of the dissertation.
-Also the variational forms are derived which enables us to see the similarity between the models.
+The variational forms are also derived which enables us to see the similarity between the models and the general theory.
 
@@
 First, a variational form for a model problem of a cantilever Timoshenko beam given.
-This model problem in variational form is then extended to complete function spaces, and in turn a weak variational problem is obtained.
-This weak variational problem is used as an example to explain the main theory of the chapter, from the article \cite{VV02}.
+This model problem in variational form is then extended to complete function spaces, and a weak variational problem is obtained.
+This weak variational problem is used as an example to explain the main theory of this chapter which is from the article \cite{VV02}.
 In this article, the authors present a general weak variational form.
 The weak variational form of all the model problems of this dissertation are special cases of this general weak variational problem.
-Therefore the assumptions and results can be formulated and applied to all the applications.
+Therefore the assumptions and results can be formulated and applied to all the applications in this dissertation.
 The article gives four assumptions.
 Under these assumptions it is shown that the general vibration problem has a unique solution using semi-group theory.
-Next the theory is applied to the example weak variational problem for the cantilever Timoshenko beam, by showing that the assumptions hold.
+The theory is then applied to the example by proving that the assumptions hold.
 
 Finally the concept of modal analysis is introduced, which is fundamental to this dissertation.
-The idea of modal analysis is explained by hands of another example, again using a cantilever Timoshenko beam.
-Then the general case is discussed, following \cite{CVV18}.
-Given a general vibration problem, an eigenvalue problem and a differential equation is derived.
-An additional assumption is introduced by \cite{CVV18}.
-Under this assumption, the eigenvalue problem has infinite many solutions, and that the solution of the general vibration problem is an infinite series of the eigenvectors and general Fourier coefficients.
-Solving the differential equation, shows that these Fourier coeffiencients are periodic and a formal series solution for the general vibration problem (which is a boundary value problem) is obtained.
-This formal series solution is then shown to also be valid for a general initial value problem.
-This general case is applicable to all the models in this dissertation.
+First idea of modal analysis is explained by hands of another example, again using a cantilever Timoshenko beam.
+Then the general case is discussed that follows the article \cite{CVV18}.
+Given a general vibration problem, it is split into two problems by introducing a trial solution.
+It can then be verified that these two problems are the eigenvalue problem and a differential equation.
+An additional assumption (additional to the assumptions of \cite{VV02}) is introduced by \cite{CVV18}.
+Under this assumption, the eigenvalue problem has infinite many solutions, and the solution of the general vibration problem is an infinite series of the eigenvectors and general Fourier coefficients.
+Solving the differential equation, shows that these Fourier coefficients are periodic and a formal series solution for the general vibration problem (which is a boundary value problem) is obtained.
+This formal series solution is then shown to also be valid for a initial value problem.
+This general case is also applicable to all the models in this dissertation.
 
-Being able to express the solution of a model problem as a linear combination of the eigenvalues and eigenfunctions in a formal series solution, is fundamental to this dissertation.
-This means that the solutions of models will compare well if the eigenvalues and eigenfunctions compare well.
-The validity of the formal series solution is also a requirement as it ensures that the comparisons remain valid, as long as the models are disturbed in the same way.
+This theory is crucial for this dissertation.
+It ensures that the solutions of the models will compare well if the eigenvalues and eigenfunctions compare well.
+Therefore for the comparisons in Chapter 4 and 6, it is only required to compare the eigenvalues and eigenfunctions.
+The validity of the formal series solution is also important as it ensures that the comparisons remain valid, as long as the models are disturbed in the same way.
 
 \subsubsection{Chapter 3}
+\textcolor{red}{Nie seker hoekom prof gese het nie BV13 nie? Ook nie seker hoekom SF97 dood getrek was nie.}
+
 In this chapter, some theory for the Finite Element Method is discussed.
-This chapter contains two parts, that covers two different results.
-The first result is the convergence of the Galerkin approximation of a general vibration problem.
-This result is presented in the article \cite{BV13}.
-The second result concerns the convergence of the eigenvalues and eigenfunctions of a one-dimensional vibration problem when applying the Finite Element Method.
-This result is presented in the textbook \cite{SF97}.
+This chapter contains two parts, that covers two different theoretical results.
+The first is on the convergence of the Galerkin approximation of a general vibration problem.
+This theory is presented in the article \cite{BV13}.
+The second part concerns the convergence of the eigenvalues and eigenfunctions of a one-dimensional vibration problem when applying the Finite Element Method.
+This theory is presented in the textbook \cite{SF97}.
+
 In the first section, the authors continue with the general vibration problem that is used in Chapter 2.
@@
 The examples shows the use of the method, and is preperation for chapter 6 where these results are required for the comparison of the models.
+
 The next section is a short discussion on a suspended beam model, afterwards an important article \cite{SP06} is discussed.
@@
 Finally the chapter finished by looking at an interesting model of a cantilever beam with a tip-body with elastic interfaces.
-These results combine modal analysis and look at the behavior of the model.
+These results combine modal analysis and investigates at the behavior of the model.
 This section is an example of the usefullness of the Timoshenko beam theory.
@@
 \subsubsection{Chapter 5}
-In this chapter, the Finite Element Method is applied to cantilever two-dimensional,and three-dimensional cantilever beams and a cantilever Reissner-Mindlin plate.
+In this chapter, the Finite Element Method is applied to cantilever two-dimensional elastic body, cantilever three-dimensional elastic body and a cantilever Reissner-Mindlin plate.
 The aim of this section is to obtain an algorithm to calculate the eigenvalues and eigenfunctions of the models.
-The results of these formulas will be used in chapter 6.
 The Finite Element Method is not applied to the Timoshenko beam theory, as chapter 4 provides an alternative method.
@@
 Each section ends with a eigenvalue problem for the models that can be easily applied to a computer program to calculate the eigenvalues and eigenvectors for the models.
-These algorithms will be used to obtain the results in chapter 6.
+This is in preparation of Chapter 6 where the eigenvalues and eigenfunctions are calculated and compared.
 
 \subsubsection{Chapter 6}
-In this chapter, the main comparisons of the models are conducted.
+In this chapter, the main comparisons of the models are conducted. All of the sections follow the same idea and struture as the article \cite{LVV09}.
+
 The first section is a discussion of the article \cite{LVV09}.
-Each section in this chapter follows the same structure as this article.
-In this article, the authors investigate the validity of a cantilever Timoshenko beam models, by comparing it to a two-dimensional cantilever Timoshenko beam model.
-To make this comparison, the authors compare the eigenvalues and eigenfunctions of the models.
-But since the two-dimensional model is more complex, there are `non-beam type' eigenvalues.
-These are eigenvalue that are not in the Timoshenko beam theory, and does not relate to beam type problems.
-To be able to find the beam type eigenvalues that can be compared, the authors compare the mode shapes.
-This allows the eigenvalues to be matched up.
-The results of the article show that the Timoshenko beam model compares very well to the two-dimensional beam.
-The comparison improves when the application is for a long and slender beam.
-The results of the article are verified and more results are added to extend the article and also to be using the the following sections.
+In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model.
+The authors compare the models by comparing the eigenvalues and eigenfunctions (see Chapter 2 on modal analysis).
+The two-dimensional model is more complex and there are eigenvalues that are not shared between the models.
+The authors use the mode shapes to match up the eigenvalues.
+The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues.
+The authors also consider different shapes of beams, from a short fat beam to a long slender beam.
+The results show that the models compare very well, even for a short and fat beam.
+As the beam gets more slender, the comparison improves.
+In this section some of the results of the article are discussed and replicated.
+
 But in real-world applications, a beam is a three-dimensional model.
-Therefore it would be better to use a three-dimensional model to investigate the validity of the Timoshenko beam theory.
-The authors of \cite{LVV09} mentions this, and suggests using the two-dimensional model as an intermediate step to avoid complexities.
-So in the second section of this chapter, the validity of the two-dimensional model is investigated using the three-dimensional model as a reference.
-The results show that the two-dimensional model also compares very well to the three-dimensional model.
-Similar to the one-dimensional case, the results improve for a long and slender beam, and also if the width of the three-dimensional beam is not larger than the height of the beam.
-When increasing the width past the size of the height, the two-dimensional model is less accurate.
-This shape does however bring into question the use of a beam model, and something like a plate model might be better suited.
-In the last section, the validiy of the Reissner-Mindlin plate model is investigated.
-Similar to how the Timoshenko beam theory improves on the Euler-Bernoulli beam theory, the Reissner-Mindlin plate theory improves on the classical plate theory.
-The numerical results do show that this Reissner-Mindlin plate model compares well to a three-dimensional plate model, also when the dimensions of the models are realistic for application.
+Therefore it would be more suited to use a three-dimensional model to investigate the validity of the Timoshenko beam theory.
+This is mentioned by the authors of \cite{LVV09}.
+Their suggestion is to use the two-dimensional model as an intermediate step, to avoid complexities.
+Therefore the validity of the two-dimensional model is investigated, using a three-dimensional beam model as a reference.
+Again the results so that the comparison relies on the shape of the beams.
+The two-dimensional model compares well to the three-dimensional beam if the beam is not very wide.
+
+If the width of the beam is very large, the use of a beam model can be questioned.
+A plate model might be more suited.
+Therefore the last section of this chapter investigates the validity of the Reissner-Mindlin plate model.
+The Reissner-Mindlin plate model is compared to a three-dimensional plate model.
+The results show that the Reissner-Mindlin plate model compares well to the three-dimensional plate model.
+This is also true for a wide plate.
+
+Overall the models compare very well, as long as the shape of the model is realistic.
+
+\end{document}
 
@@
 \textcolor{red}{493 Words}
-
-\end{document}
 

### 2023-11-04 files/Chapter2/generalvibrationmodel.tex
presentation
Chapter 4 + 5 review

@@
 
-\subsubsection{Validity of series solution}
+\subsection{Validity of series solution}
 Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$?
@@
 
-\subsubsection{Comparison of models}
+\subsection{Comparison of models}
 
@@
 This section is a discussion of the article \cite{SP06} comparing a Timoshenko beam model and a three dimensional beam model to empirical results.
-The authors of this article use the natural frequencies (equivalently the eigenvalues) to compare the different models.\\
+The authors of this article use the natural frequencies (equivalently the eigenvalues) to compare the different models.
 
@@
 These comparisons are made in Chapter 4 and 6.
-Being able to express the solutions of the models as a formal series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.
+Being able to express the solutions as a valid series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.
 This is explained in detail in \cite{CVV18}.
 
-The validity of the formal series solution with initial conditions is required to investigate the vibration of the models.
-This ensured that if the models are disturbed in the exact same way, the formal series solution remains valid, and a comparison can be made.
+In \cite{CVV18}, the authors consider a beam model and wave equation model for a vibrating string.
+Suppose that for the same initial conditions, $u_b$ and $u_w$ are the exact solution.
+A comparison of the exact solutions are not possible, but the partial sums can be compared if the bounds for the errors $u_b - u^N_b$ and $u_w - u^N_w$ can be guaranteed.
 

### 2023-11-04 files/Chapter4/CantileverTimo.tex
Chapter 4 + 5 review

@@
 \section{Cantilever Timoshenko beam with tip-body}
-\sout{This section discusses the technical report [DBVXX] on a cantilever Timoshenko beam with a tip body and elastic boundary interfaces.
-Most papers on a similar topic focus on the analysis of vibration modes, stabilization and optimal control of vibrations.
-The goal of [DBVXX] is to realistically model the interface between the endpoint of a beam and the attached tip body.
-Few publications consider this modelling.}\\
 
-\sout{In this section, the finite element analysis and some numerical simulations for the model are presented. These numerical simulations are to show that the model behaves in a realistic manner.}\\
+\textcolor{red}{MOONTLIK UIT HAAL.}
 
@@
 In this technical report the authors models a cantilever Timoshenko beam with a tip body and elastic boundary conditions.
-This model can be seen as a motivation of the importance of investigating the validity of the Timoshenko beam theory.\\
+This model can be seen as a motivation of the importance of investigating the validity of the Timoshenko beam theory.
 

### 2023-11-04 files/Chapter5/2D_FEM.tex
Chapter 4 + 5 review

@@
 \section{Introduction}
-In this chapter, the Finite Element Method (FEM) is applied to the models of this dissertation, presented in chapter 1.
-The goal of this chapter is to obtain numerical formulas that can be used to calculate the eigenvalues and eigenvectors for the models.
-This is in preperation of chapter 6, where the eigenvalues and eigenvectors of the models are compared.
+In this chapter, the Finite Element Method (FEM) is applied to the models of this dissertation, presented in Chapter 1.
+The goal of this chapter is to obtain an algorithm that can be used to calculate the eigenvalues and eigenvectors for the models.
+This is in preparation of chapter 6, where the eigenvalues and eigenvectors of the models are compared.
 
 In chapter 4, a method was discussed to obtain the eigenvalues and eigenvectors for the Timoshenko beam model.
-Therefore it is not neccesary to apply the Finite Element Method on the Timoshenko model to obtain the eigenvalues and eigenvectors.
-The Finite Element Mehtod is applied to the two-dimensional and three-dimensional models.
+Therefore it is not necessary to apply the Finite Element Method on the Timoshenko model to obtain the eigenvalues and eigenvectors.
+The Finite Element Method is applied to the two-dimensional and three-dimensional models.
 
@@
 \subsubsection{Cantilever elastic body}
-Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$.
-The body is free-hanging on the other boundaries.
-Recall this is Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
+Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
 \FloatBarrier
@@
 
-See chapter 2 for the existence theory.
+See Chapter 2 for the existence theory.
 
@@
 There are various types of shapes of elements that can be used.
-Since the body $\omega$ is has a rectangular cross-section, rectangular are the simplist elements to use.
+Since the body $\omega$ is has a rectangular cross-section, rectangular elements are the simplest elements to use.
 
@@
 \subsection{Eigenvalue problem}\label{2dFEM_EP}
-For the eigenvalue problem, assume that $M_{f}Q^I = 0$ so that 
+For the eigenvalue problem, assume that there is no external force, $M_{f}Q^I = 0$, so that 
 \begin{eqnarray}
@@
 \end{eqnarray}
-It is known that a system of ordinary differential equations have a general solution of the form $e^{rt}$.
+It is known that a system of ordinary differential equations has a general solution of the form $e^{rt}$.
 Suppose that $\bar{w} = e^{\lambda t} \bar{u}$ is a solution for \eqref{eq:2DFEM:M2}.

### 2023-11-04 files/Chapter5/3D_FEM.tex
Chapter 4 + 5 review

@@
 This general form can now be rewritten as in a model specific form using the reference configuration.
-For convenience, some of the results from section \ref{sec:3D_Mode} are repeated here.
+For convenience, some of the results from section \ref{sec:3D_Model} are repeated here.
 
@@
 \begin{eqnarray*}
-	T(\Omega) & = & \left\{ \phi \in C(\Omega) \ | \ \phi = 0 \ \textrm{ on } \ \Sigma_0 \right\}.
+	T(\Omega) & = & \left\{ \phi \in C(\Omega) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
 \end{eqnarray*}
@@
 As mentioned in the previous section, section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised.
-This is model, three-dimensional elements shapes are required.
+For this is three-dimensional body, three-dimensional elements shapes are required.
 The elements used in this dissertation are rectangular prismatic elements.
-These elements are also known as brick shaped elements as described by \cite{Wu06}.
-This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.\
+These elements are also known as `brick-shaped' elements and is described in \cite{Wu06}.
+This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.
 
@@
 These basis functions are an extension of the Hermite cubic basis functions from the two-dimensional model.
-Although this is more complex than using tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.\\
+Although this is more complex than using tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
 
-For this dissertation, we use tri-cubic functions $\phi_i$.
-For a simplification, tri-linear functions can also be used instead.
-For easier notation, denote each of the basis functions in the set by $\delta_i$.\\
-
-Similar to \ref{2d_FEM_G}, denote the admissible basis functions by $\delta_j$, where each $\delta_j$ is a unique element of $B$ satisfying all the conditions of the test function space $T(\Omega)$.
-The admissible basis functions are numbered and expressed as the set $A = \left\{\delta_1, \delta_2, ..., \delta_k \right\}$ for some $k \leq 3n$.\\
+Recall that the admissible basis functions, are all the basis functions that satisfies all the conditions of the test function space $T(\Omega)$.
+Denote the admissible basis functions by $\delta_j$, with each $\delta_j$ a unique element of $B$.
+The set of admissible basis functions can then be expressed as $A = \left\{\delta_1, \delta_2,...
+, \delta_k\right\}$ with $k \leq 3n$.
 

### 2023-11-04 files/Chapter5/PlateModel.tex
v2 chapter 7.2, started 7.3
Chapter 4 + 5 review

@@
 \section{Cantilever plate model}\label{sec:FEM:Plate}
-Consider a rectangular cantilever Reissner-Mindlin plate.
+Consider a rectangular cantilever Reissner-Mindlin plate model with a rectangular cross-section.
 
 \subsubsection{Reference configuration for a rectangular plate}
-Let $\left\{e_1,e_2\right\}$ be a right-handed orthonormal basis for $R^2$. Denote the elastic body as $\Omega \in R^2$ with the reference point $(0,0)$. For a rectangular plate,
+Let $\left\{e_1,e_2\right\}$ be a right-handed orthonormal basis for $R^2$.
+Although this basis seems identical to the two-dimensional beam in section \ref{sssec:2D_Model:RefConf}, it is fact different.
+It would be more appropriate to use $e_1$ and $e_3$ for this plate model.
+However the use of $e_1$ and $e_2$ is kept to reiterate that this is in fact a two-dimensional model.
+
+Denote the elastic body as $\Omega \in R^2$ with the reference point $(0,0)$. For a rectangular plate,
 \begin{eqnarray*}
@@
 	\end{eqnarray*}
-\end{minipage}\\
+\end{minipage}
 
-\textbf{Remark} The mathematical definition of $R_2$ is the same as the two-dimensional beam.
-Practically, it is not the same.
-The plate model is a horisontal two-dimensional plane, and the two-dimensional beam is a vertical two-dimensional plane.
+Similar to the two and three-dimensional cantilever models, this notation implies that the plate is clamped at $\Sigma$ and free hanging at $\Gamma$.
 
 \subsubsection{Cantilever plate model}
-Consider a rectangular plate clamped rigidly to a surface at the edge $\Sigma_0$.
-The plate is free hanging on the remaining edges and there is not external force acting on the plate.
-The plate is be modelled using the Reissner-Mindlin plate theory that is presented in section \ref{ssec:P_Model:ModelProblems} as Problem P-1.\\
+Consider a rectangular Reissner-Mindlin plate clamped rigidly to a surface at $\Sigma$ and free hanging on the remaining edges.
+This plate model is presented in section \ref{ssec:P_Model:ModelProblems} as Problem P-1.
 
@@
 	\end{tikzpicture}
-	\caption{Two-dimensional Cantilever Plate}
+	\caption{Two-dimensional cantilever Reissner-Mindlin plate}
 \end{figure}
@@
 Similar to Section 2.1, the weak variational form for Problem P-1 can be derived from Problem P-1V.
+
 \subsubsection{Bilinear forms}
@@
 	c(u''(t),v) + b^*(u(t),v) & = & (f(t),v)_{\Omega} \ \ \ \textrm{ for each } v \in V,
-\end{eqnarray} with $u(0)= u_0 = \langle w_0, \boldsymbol\psi_0 \rangle$, and $u'(0)= u_1 = \langle w_1, \boldsymbol\psi_1 \rangle$.\\
+\end{eqnarray} with $u(0)= u_0 = \langle w_0, \boldsymbol\psi_0 \rangle$, and $u'(0)= u_1 = \langle w_1, \boldsymbol\psi_1 \rangle$.
 
-\subsubsection{Existence and uniqueness}
-\textcolor{red}{XXXXXXXXXXXXXXXXXXXXX}
-Section 2.2 provides the necessary theory for the existence and uniqueness of solutions for second order hyperbolic equations.
-The assumptions \textbf{A1}, \textbf{A2} and \textbf{A4} are similar to Section 2.3.
-So it is only required to show that $b$ is an inner product for $V$ and that there exists a positive number $C_V$ such that
-\begin{eqnarray*}
-	\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}
-\end{eqnarray*} for each $v \in V$.\\
-
-However, this is not as simple as the example in Section 2.4. ****Reference 'n article wat na dit kyk.***
+See Chapter 2 for the existence theory.
 
 \subsection{Galerkin approximation}
-Divide the reference configuration $\Omega$ into a rectangular grid of elements, such that there are $n = n_1 \times n_2$ nodes.\\
+To discretise the body $\Omega$, the same shapes as in section \ref{ssec:2D_Model:Galerkin} are used.
 
-For the plate model, two different definitions for basis functions are required.\\
+Divide the reference configuration $\Omega$ into a rectangular grid of elements, such that there are $n = n_1 \times n_2$ nodes.
 
-First consider a set of $n$-dimensional linear independent basis functions, defined by the set
-\begin{eqnarray*}
-	\left\{\delta^*_1, \delta^*_2, ..., \delta^*_n\right\}.
-\end{eqnarray*}
-In this set, each $\delta^*$ is a cubic function.
-The subset of functions that satisfies the conditions of the test function space $T_1(\bar{\Omega})$ are the admissible basis functions for $T_1(\bar{\Omega})$.
-These admissible basis functions can be renumbered and expressed as the set $\left\{\delta^*_1, \delta^*_2, ..., \delta^*_{k_1}\right\}$ for some $k_1 \leq 2n$.\\
+Define a set of $n$-dimensional linear independent basis functions.
+The basis functions can be defined by the set $$B = \left\{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \right\}.$$
 
-Next consider a set of $n$-dimensional linear independent basis functions, defined by the set
-\begin{eqnarray*}
-	\left\{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \right\}.
-\end{eqnarray*} These functions $\phi_j$ are cubic basis functions.
-Denote each element in this set by $\delta_i$.
-The subset of functions that satisfies the conditions of the test function space $T_2(\bar{\Omega})$ are the admissible basis functions for $T_2(\bar{\Omega})$.
-These admissible basis functions can be renumbered and expressed as the set $\left\{\delta_1, \delta_2, ..., \delta_{k_2}\right\}$ for some $k_2 \leq 2n$.\\
+These basis functions are bi-cubic basis functions.
+
+Since there are two test function spaces, $T_1(\Omega)$ and $T_2(\Omega)$, two different sets of admissible basis functions are required.
+Denote the admissible basis functions for $T_1(\Omega)$ by $\delta^1_j$ where each $\delta^1_j$ is a unique element of B.
+The set of admissible basis functions that satisfies $T_1(\Omega)$ can be defined as $A_1 = \left\{\delta^1_1, \delta^1_2,..., \delta^1_{k_1} \right\}$ for a $k_1 \leq 2n$.
+Similarly for $T_2(\Omega)$, the set of admissible basis functions can be defined as $A_2 = \left\{\delta^2_1, \delta^2_2,..., \delta^2_{k_2} \right\}$ for a $k_2 \leq 2n$.
 
@@
 \begin{eqnarray*}
-	S^h_1 & = & \textrm{span}\left(\left\{\delta^*_i \ | \ i = 1,2,...,k_1 \right\} \right),\\
-	S^h_2 & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k_2 \right\} \right).
+	S^h_1 & = & \textrm{span}\left(\left\{\delta^1_i \ | \ i = 1,2,...,k_1 \right\} \right),\\
+	S^h_2 & = & \textrm{span}\left(\left\{\delta^2_i \ | \ i = 1,2,...,k_2 \right\} \right).
 \end{eqnarray*}
@@
 
-Problem P1-V can now be rewritten into a Galerkin Approximation, denoted by Problem P-1G.
+Substitution of $u^h$ and $\psi^h$ into Problem P-1V, results in the following Galerkin approximation, denoted by Problem P-1G.
 
@@
 \subsection{System of ordinary differential equations}
-The standard FEM matrices $K_{11}$ to $K_{22}$ and $M_F$ where presented in section \ref{ssec:2DFEM:DE}. In addition, the following standard FEM matrices are also required.
+The standard FEM matrices $K_{11}$, $K_{12}$, $K_{21}$, $K_{22}$ and $M_F$ where presented in section \ref{ssec:2DFEM:DE}.
+Even though the definition of $R_2$ is different in section \ref{sec:FEM:2D}, the definition of the matrices are the same and are not repeated here.
+
+In addition to these matrices, the following standard FEM matrices are also required.
 
@@
 
-for $i,j = 1,2,...,p$.\\
+for $i,j = 1,2,...,p$.
 
-Define the following matrices:\\
+Define the following matrices:
+
 \noindent\begin{minipage}{.5\linewidth}
@@
 
-with $A = \frac{1}{\beta(1-\nu^2)}$ and $B = \frac{1}{2\beta(1+\nu)}$.\\
+with $A = \frac{1}{\beta(1-\nu^2)}$ and $B = \frac{1}{2\beta(1+\nu)}$.
 
@@
 \end{eqnarray}
-With $\bar{u}$ in the form $\bar{u} = \langle w, \partial_x w, \partial_y w, \partial_{xy} w, \psi_1, \partial_x \psi_1, \partial_y \psi_1, \partial_{xy} \psi_1, \psi_2, \partial_x \psi_2, \partial_y \psi_2, \partial_{xy} \psi_2 \rangle$.
+With $\bar{u}$ in the form $\bar{u} = \langle w, \partial_1 w, \partial_2 w, \partial_{12} w, \psi_1, \partial_1 \psi_1, \partial_2 \psi_1, \partial_{12} \psi_1, \psi_2, \partial_1 \psi_2, \partial_2 \psi_2, \partial_{12} \psi_2 \rangle$.
 
@@
 \subsubsection{Problem P-1E}
-Find a vector function $u$ and a number $\lambda$ such that
+Find a vector function $\bar{u}$ and a number $\lambda$ such that
 \begin{eqnarray}
-	\lambda M{u} & = & K{u}.
+	M\lambda{\bar{u}} & = & K\bar{u}.
 \end{eqnarray}

### 2023-11-07 AppendixA.tex
symbols

@@
 
+\section*{Appendix: Mathematical Preliminaries}
+In this appendix, we provide a brief overview of the mathematical spaces and concepts used throughout the dissertation.
+
+\subsection*{The Space \( L^2 \)}
+Consider a measurable space \( X \). The set of square-integrable functions over \( X \) with respect to a measure \( \mu \) is called the \( L^2 \) space, formally defined as
+\[ L^2(X, \mu) = \{ f: X \to \mathbb{R} \mid \int_X |f|^2 \, d\mu < \infty \}. \]
+
+The inner product in \( L^2 \) space is defined as
+\[ (f,g) = \int_X f(x)g(x) \, d\mu \quad \text{for } f, g \in L^2(X, \mu). \]
+The norm in \( L^2 \) is given by \( ||f|| = (f,f)^{1/2} \) for \( f \in L^2(X, \mu) \). For a comprehensive treatment, see \cite{Rud53}.
+
+\textcolor{red}{***********************************************}
+
+\subsection*{Spaces of Continuous Functions}
+
+\textbf{The Space \( C^m(a,b) \)}\\
+This space consists of functions that are \( m \)-times continuously differentiable in the open interval \( (a, b) \).
+
+\textbf{The Space \( C^m[a,b] \)}\\
+Functions in \( C^m[a,b] \) are \( m \)-times continuously differentiable in \( (a, b) \) and have defined right derivatives at \( a \) and left derivatives at \( b \) up to the \( m \)-th order.
+
+\textbf{The Space \( C_0^m(a,b) \)}\\
+The space \( C_0^m(a,b) \) contains functions from \( C^m[a,b] \) that vanish on the intervals \( [a, \alpha] \) and \( [\beta, b] \) for some \( a < \alpha < \beta < b \).
+
+\textbf{The Spaces \( C^\infty(a,b) \) and \( C^\infty[a,b] \)}\\
+These spaces contain functions that are infinitely differentiable, either on the open interval \( (a, b) \) or on the closed interval \( [a, b] \), respectively.
+
+\textbf{The Space \( C_0^\infty(a,b) \)}\\
+It includes all functions from \( C^\infty(a,b) \) that have compact support within \( (a, b) \).
+
+\subsection*{Weak Derivatives and Sobolev Spaces}
+Weak derivatives allow us to handle functions that are not classically differentiable. These derivatives are defined in a weak sense through the use of test functions.
+
+\textbf{Definition: First Order Weak Derivative}\\
+A function \( v \) is the first order weak derivative of \( u \in L^2(a,b) \) if
+\[ (u, \phi') = -(v, \phi) \quad \text{for all } \phi \in C^\infty_0(a,b). \]
+
+\textbf{Definition: Higher Order Weak Derivative}\\
+Similarly, \( v \) is the \( m \)-th order weak derivative of \( u \) if
+\[ (u, \phi^{(m)}) = (-1)^m(v, \phi) \quad \text{for all } \phi \in C^\infty_0(a,b). \]
+
+\textbf{Sobolev Spaces \( W^m(a,b) \)}\\
+The Sobolev space \( W^m(a,b) \) includes functions in \( L^2(a,b) \) with weak derivatives up to order \( m \). The inner product and norm in \( W^m(a,b) \) are defined as
+\[ (u,v)_m = (u,v) + (Du, Dv) + \dots + (D^m u, D^m v), \]
+\[ ||u||_m = \sqrt{(u,u)_m}. \]
+
+\textbf{Sobolev Spaces \( H^m(a,b) \)}\\
+The space \( H^m(a,b) \) is defined as the closure of \( C^m[a,b] \) in \( W^m(a,b) \) with respect to the Sobolev norm \( ||\cdot||_m \).
+
+\subsection*{Main Results}
+\textbf{Uniqueness of Weak Derivatives}\\
+\begin{thmAH1}
+	The \( m \)-th order weak derivative \( D^{(m)}u \) is uniquely determined by \( u \).
+\end{thmAH1}
+
+\textbf{Inclusion of Continuously Differentiable Functions}\\
+\begin{thmAH2}
+	The space \( C^m(\overline{I}) \) is a subset of \( W^m(I) \). For a function \( u \) in \( C^m(\overline{I}) \), the classical and weak derivatives coincide: \( D^{(m)}u = u^{(m)} \).
+\end{thmAH2}
+
+% Include more theorems, lemmas, or corollaries as needed
+% ...
+
 \end{document}

### 2023-11-07 AppendixB.tex
symbols

@@
 
+\section*{Introduction}
+In this appendix, we delve into the concept of Sobolev spaces, which are fundamental in the study of partial differential equations and variational problems.
+Sobolev spaces generalize the notion of differentiability and integrate the concept of weak derivatives, making them crucial in formulating and solving problems with less smooth solutions.
+
+\section*{One-Dimensional Case}
+Consider the closed interval \([0,\ell]\). We define a partition of this interval into \(n\) subintervals \([x_{k-1},x_k]\), where each \(x_k\) for \(k=0,1,\ldots,n\) is referred to as a node.
+
+\subsection*{Piecewise Linear Basis Functions}
+Let us denote the linear basis functions by \(\phi_i\), where each \(\phi_i\) is associated with a node \(x_i\).
+
+\subsubsection*{Properties}
+\begin{itemize}
+	\item The restriction of \(\phi_i\) to any subinterval is a linear polynomial.
+	\item \(\phi_i \in C^0[0, \ell]\) and \(\phi_i' \in L^2(0, \ell)\).
+	\item \(\phi_i(x_i) = 1\) and \(\phi_i(x_j) = 0\) for \(i \neq j\).
+	\item Each \(\phi_i\) is supported on \([x_{i-1}, x_{i+1}]\), being zero outside this subinterval.
+\end{itemize}
+
+\subsection*{Hermite Cubic Basis Functions}
+The Hermite cubic basis functions ensure continuity of the first derivative across nodes. There are two types of basis functions to cover the function value and the derivative continuity.
+
+\subsubsection*{Type One Properties}
+\begin{itemize}
+	\item Each \(\phi^{(1)}_i\) is a cubic polynomial on its support.
+	\item \(\phi^{(1)}_i \in C^1[0,\ell]\).
+	\item \(\phi^{(1)}_i\) and \((\phi^{(1)}_i)'\) are continuous; \((\phi^{(1)}_i)''\) is piecewise continuous.
+	\item \(\phi^{(1)}_i(x_i) = 1\) and \((\phi^{(1)}_i)'(x_i) = 0\).
+\end{itemize}
+
+\subsubsection*{Type Two Properties}
+\begin{itemize}
+	\item Similar to Type One but designed to ensure that \((\phi^{(2)}_i)'(x_i) = 1\) and \(\phi^{(2)}_i(x_i) = 0\).
+\end{itemize}
+
+\section*{Two-Dimensional Case}
+In the two-dimensional setting, consider a rectangular domain \(\Omega\) with sides of lengths \(a\) and \(b\), divided into rectangular elements by a grid with spacings \(\delta x\) and \(\delta y\).
+
+\subsection*{Piecewise Bi-Linear Basis Functions}
+In two dimensions, basis functions \(\phi_i\) are associated with grid nodes \((x_i, y_i)\) and are bilinear over each rectangular element.
+
+\subsubsection*{Properties}
+\begin{itemize}
+	\item Within each element, \(\phi_i\) is a bilinear function of the form \(a + bx + cy + dxy\).
+	\item For a fixed \(y\), \(\phi_i(\cdot, y)\) is linear in \(x\) and continuous over \([0, a]\); the analogous property holds for fixed \(x\) and varying \(y\).
+	\item At node \((x_i, y_i)\), \(\phi_i\) equals 1 and vanishes at all other nodes.
+	\item The support of \(\phi_i\) consists of the elements sharing the node \((x_i, y_i)\).
+\end{itemize}
+
+\section*{General Properties of Sobolev Spaces}
+\subsection*{Weak Derivatives}
+The concept of weak derivatives allows us to extend the idea of differentiability to functions that may not be differentiable in the classical sense.
+A weak derivative is defined in the distributional sense, by integration by parts, where the test functions come from smooth, compactly supported spaces.
+
+\subsection*{Embedding Theorems}
+Embedding theorems, such as the Sobolev Embedding Theorem, provide the conditions under which Sobolev spaces are contained within other function spaces, or can be continuously injected into them.
+These are crucial in understanding the regularity properties of solutions to PDEs.
+
+\subsection*{Traces}
+In Sobolev spaces, the trace operator allows us to make sense of the restriction of a function to the boundary of a domain, even when the function is not necessarily continuous.
+
+\subsection*{Sobolev Inequalities}
+These inequalities provide bounds on the norms of functions in Sobolev spaces and are essential tools for the analysis of variational problems and PDEs.
+
+\section*{Conclusion}
+Sobolev spaces are instrumental in the mathematical formulation and analysis of a wide variety of problems in science and engineering.
+This appendix provides a foundational overview for understanding these spaces in both one- and two-dimensional contexts.
+
+\section*{References}
+The references section should contain all works cited throughout the appendix and main text. It is crucial to attribute ideas and direct quotations to their original sources.
+
 \end{document}

### 2023-11-07 files/Chapter1/1DModel.tex
symbols

@@
         \rho I\partial_t^2 \phi  &=& V + \partial_x M. \label{eq:1D_Model:EquationOfMotion2}
-    \end{align}
+    \end{align}\label{sym:A}\label{sym:V}\label{sym:Iinertia}\label{sym:M}\label{sym:phiT}
     In~\eqref{eq:1D_Model:EquationOfMotion1} and \eqref{eq:1D_Model:EquationOfMotion2} $\rho$ denotes the density, $A$ is the area of a cross section, $I$ is the area moment of inertia, $M$ is the moment, $V$ is the shear force and $Q$ is an external force acting on the beam.
@@
         M &=& EI\partial_x \phi, \label{eq:1D_Model:ConstitutiveEquations1}\\
-        V &=& AG\kappa^2(\partial_x w - \phi), \label{eq:1D_Model:ConstitutiveEquations2}
+        V &=& AG\kappa^2(\partial_x w - \phi), \label{eq:1D_Model:ConstitutiveEquations2}\label{sym:kappa2T}
     \end{eqnarray}
@@
         =\frac{AG\kappa^2 \ell^2}{EI}.
-    \end{equation*}
+    \end{equation*}\label{sym:alphabeta}
 

### 2023-11-07 files/Chapter1/3DModel.tex
symbols

@@
 \subsection{Equations of motion and constitutive equations} \label{ssec:3D_Model:EquationofMotion+ConstitutiveEquation}
-Consider a vector valued function $u$ defined on domain $\Omega \subset {R}^3$
-where $u$ describes the displacement of $\Omega$ in ${R}^3$.
+Consider a vector valued function $u$ defined on domain $\Omega \subset {R}^3$ \label{sym:Omega} \label{sym:Rn}
+where $u$\label{sym:u} describes the displacement of $\Omega$ in ${R}^3$.
 \subsubsection{Equation of motion}\label{ssec:3D_Model:EquationOfMotion}
@@
 	\rho\partial_t^2 u & = & \textrm{div}T + Q. \label{eq:3D_Model:EM}
-\end{eqnarray}
+\end{eqnarray} \label{sym:rho} \label{sym:partial_diff} \label{sym:T} \label{sym:Q}
 
 In \eqref{eq:3D_Model:EM}, $\rho$ is the density of the elastic body, $T$ is
-the stress tensor with components $\sigma_{ij}$, $Q$ is an external body force
-acting on $\Omega$ and $\textrm{div}T$ is the divergence of the tensor $T$ and
+the stress tensor with components $\sigma_{ij}$\label{sym:sigmaij}, $Q$ is an external body force
+acting on $\Omega$ and $\textrm{div}T$\label{sym:divT} is the divergence of the tensor $T$ and
 represented by
@@
 and rotations are small. Hence the stress tensor $T$ is symmetric. Let
-$\textrm{Tr}(T)$ denote the trace of the stress tensor $T$, that is
+$\textrm{Tr}(T)$\label{sym:TrT} denote the trace of the stress tensor $T$, that is
 \begin{eqnarray}
-	\textrm{Tr}(T) & = & \phi_{11} + \phi_{12} + \phi_{13}. \label{eq:stress_tensor_t}
+	\textrm{Tr}(T) & = & \sigma_{11} + \sigma_{22} + \sigma_{23}. \label{eq:stress_tensor_t}
 \end{eqnarray}
@@
 \subsubsection*{Strain}\label{sssec:3D_Model:Strain}
-Infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$, with components
+Infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$\label{sym:mathcalE}, with components
 \begin{eqnarray}
 	\varepsilon_{ij} = \frac{1}{2}\left( \frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} \right). \label{eq:3D_Model:Strain}
-\end{eqnarray}
+\end{eqnarray}\label{sym:varepsilonij}
 
@@
 
-\subsubsection*{Hooke's law in terms of $E$ and $\nu$}\label{sssec:3D_Model:Hooke'sLaw1}
+\subsubsection*{Hooke's law in terms of $E$ and $\nu$}\label{sssec:3D_Model:Hooke'sLaw1}\label{sym:E} \label{sym:nu}
 \begin{eqnarray}
@@
 Set \[\tau = \frac{t}{t_0},\quad \xi_i = \frac{x_i}{\ell},\quad {u}^*(\xi,\tau) = \frac{1}{\ell}{u}(x,t), \quad Q^{*} = \ell G \kappa^2 Q, \]
-\[ \text{and} \ \,\,\, \sigma_{ij}^*(\xi,\tau) = \frac{1}{G\kappa^2}\sigma_{ij}(x,t),\]
+\[ \text{and} \ \,\,\, \sigma_{ij}^*(\xi,\tau) = \frac{1}{G\kappa^2}\sigma_{ij}(x,t),\]\label{sym:t}\label{sym:G}\label{sym:tau}\label{sym:xi}\label{sym:Qstar}\label{sym:sigmaijstar}\label{sym:ell}\label{sym:kappa2}
 
@@
 	\mathcal{E} = \frac{G \kappa^2}{E} \left[ (1+\nu)T^* - \nu \textrm{Tr}(T^*)I \right]
-\end{eqnarray*}
+\end{eqnarray*}\label{sym:I}
 
@@
 	\gamma= \frac{G\kappa^2}{E}.
-\end{eqnarray*} Using this dimensionless constant,
+\end{eqnarray*}\label{sym:gamma}
+
+Using this dimensionless constant,
 \begin{eqnarray}
@@
 		$\Gamma$.
-\end{enumerate}
+\end{enumerate} \label{sym:n}\label{sym:SigmaGamma}
 
@@
 $\phi$ to equation \eqref{eq:3D_Model:EM-D} and integrating over the domain
-$\Omega$ results in,
+$\Omega$ results in, \label{sym:Cn} \label{sym:phi}
 
@@
 \end{align*}
-\\
 
@@
 	\textrm{Tr}(\Phi) ~dV \label{eq:3D_Model:Bilinear}
-\end{eqnarray}
+\end{eqnarray}\label{sym:b}
 and
@@
 	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}
-\end{eqnarray*}
+\end{eqnarray*}\label{sym:TOmega}
 
@@
 	c(u,\phi) = -b(u,\phi) + (Q,\phi), \label{eq:3D_Model:Problem3D1VEq}
-\end{align}
+\end{align}\label{sym:c}
 for all $\phi \in T(\Omega)$\\

### 2023-11-07 files/Chapter1/PlateModel.tex
symbols

@@
 	Any point on the plate can be described by
-	\[ \bar{x} = x_1 \bar e_1 + x_2 \bar e_2 + x_3 \bar e_3 = q \bar e_r + x_3 \bar e_3. \]
+	\[ \bar{x} = x_1 \bar e_1 + x_2 \bar e_2 + x_3 \bar e_3 = q \bar e_r + x_3 \bar e_3. \] \label{sym:en}
 
@@
 	\begin{eqnarray}
-		\rho h \partial_t^2 w & = & \textrm{div} Q + q \label{eq:P_Model:EM1}\\
+		\rho h \partial_t^2 w & = & \textrm{div} \mathbf{Q} + q \label{eq:P_Model:EM1}\\
 		\rho I \partial_t^2 {\psi} & = & \textrm{div} M - Q \label{P2}\label{eq:P_Model:EM1}
-	\end{eqnarray}
+	\end{eqnarray} \label{sym:bfQ}
 	In these equations $\rho$ denotes the density of the plate, $\displaystyle I = \frac{h^3}{12}$ the length moment of inertia, $M$ the moment density and $Q$ the shear force density.
@@
 	\begin{eqnarray}
-		Q & = & \kappa^2 G h(\nabla w + \psi) \label{eq:P_Model:CE1} \\
+		\mathbf{Q} & = & \kappa^2 G h(\nabla w + \psi) \label{eq:P_Model:CE1} \\
 		M_{11} & = & \frac{1}{2} D \left[2(\partial_1 \psi_1 + \nu \partial_2 \psi_2)\right]  \label{eq:P_Model:CE2}\\
@@
 
-	In classical plate theory, $\psi = -\nabla w$ and the constitutive equation for $Q$ is excluded.
+	In classical plate theory, $\psi = -\nabla w$ and the constitutive equation for $\mathbf{Q}$ is excluded.
 
@@
 	\begin{eqnarray}
-		h \partial_t^2 w & = & \textrm{div} Q + q \label{eq:P_Model:EM1D} \\
+		h \partial_t^2 w & = & \textrm{div} \mathbf{Q} + q \label{eq:P_Model:EM1D} \\
 		I \partial_t^2 {\psi} & = & \textrm{div} M - Q \label{eq:P_Model:EM2D_chap1}
@@
 	\begin{eqnarray}
-		Q & = & h(\nabla w + \psi) \label{eq:P_Model:CE1D}\\
+		\mathbf{Q} & = & h(\nabla w + \psi) \label{eq:P_Model:CE1D}\\
 		M_{11} & = & \frac{1}{2\beta(1-\nu^2)} \left[ 2(\partial_1\psi_1 + \nu \partial_2 \psi_2 \right] \label{eq:P_Model:CE2D}\\
@@
 	Free Edge:
-	\[Mn\cdot n = 0, \ \ Mn\cdot \tau = 0 \ \ \textrm{ and }\ Q\cdot n = 0 \]
+	\[Mn\cdot n = 0, \ \ Mn\cdot \tau = 0 \ \ \textrm{ and }\ \mathbf{Q}\cdot n = 0 \]
 	Soft Supported Edge:
@@
 	\[w = 0,  \ \textrm{ and } \ \psi = \bar{0} \ \textrm{ on } \Sigma_0.\]
-	\[Mn\cdot n = 0,\ \ \ Mn\cdot \tau = 0, \ \textrm{ and } \ Q \cdot n =0 \ \textrm{ on } \partial\Omega\setminus\Sigma_0.\]
+	\[Mn\cdot n = 0,\ \ \ Mn\cdot \tau = 0, \ \textrm{ and } \ \mathbf{Q} \cdot n =0 \ \textrm{ on } \partial\Omega\setminus\Sigma_0.\]
 	with $\tau$ a unit vector perpendicular to $n$.\\
@@
 	\begin{eqnarray*}
-		\int_\Omega h \partial_t^2 w v \ dA & = & \int_\Omega \textrm{div} (Q) v \ dA + \int_\Omega q v \ dA\\
+		\int_\Omega h \partial_t^2 w v \ dA & = & \int_\Omega \textrm{div} (\mathbf{Q}) v \ dA + \int_\Omega q v \ dA\\
 		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & \int_\Omega \textrm{div} (M) \cdot \phi \ dA - \int_\Omega Q \cdot \phi \ dA
@@
 	\begin{eqnarray*}
-		\int_\Omega \textrm{div}(Q) v \ dA & = & - \int_\Omega Q \cdot \nabla v \ dA + \int_{\partial\Omega} (Q\cdot n)v ds,\\
+		\int_\Omega \textrm{div}(\mathbf{Q}) v \ dA & = & - \int_\Omega \mathbf{Q} \cdot \nabla v \ dA + \int_{\partial\Omega} (Q\cdot n)v ds,\\
 		\int_\Omega \textrm{div}(M) \cdot \phi \ dA & = & - \int_\Omega \textrm{Tr} (M \Phi) \ dA + \int_{\partial\Omega} M n \cdot \phi ds.
@@
 	\begin{eqnarray}
-		\int_\Omega h \partial_t^2 w v \ dA & = & - \int_\Omega Q \cdot \nabla v \ dA + \int_\Omega q v \ dA, \label{eq:P_Model:ProblemP1V1}\\
+		\int_\Omega h \partial_t^2 w v \ dA & = & - \int_\Omega \mathbf{Q} \cdot \nabla v \ dA + \int_\Omega q v \ dA, \label{eq:P_Model:ProblemP1V1}\\
 		\int_\Omega I \partial_t^2 \psi \cdot \phi \ dA & = & - b(\phi,v) - \int_\Omega Q \cdot \phi \ dA, \label{eq:P_Model:ProblemP1V2}
@@
 	\begin{eqnarray*}
-		b(u,\phi) & = & \int_\Omega Q \cdot \nabla v \ dA + \int_{\Omega} \textrm{Tr}(M\Phi) \ dA,
+		b(u,\phi) & = & \int_\Omega \mathbf{Q} \cdot \nabla v \ dA + \int_{\Omega} \textrm{Tr}(M\Phi) \ dA,
 	\end{eqnarray*}

### 2023-11-07 files/Chapter2/generalvibrationmodel.tex
symbols

@@
 This chapter discusses theory for the existence and uniqueness of solutions for these type of problems.
-The theoretical basis for modal analysis is also presented.\\
+The theoretical basis for modal analysis is also presented.
 
@@
 The article \cite{VS19} extends this work where $b$ need not be symmetric.
-The article \cite{VV02} is sufficient for the models of this dissertation, while \cite{VS19} is only used where the notation is more convenient and to gain more insight.\\
+The article \cite{VV02} is sufficient for the models of this dissertation, while \cite{VS19} is only used where the notation is more convenient and to gain more insight.
 
 Before the general theory is discussed, a model is presented to be used as an example to show the application of the theory.
-The model is a cantilever Timoshenko beam, denoted by Problem T-2 in Section \ref{ssec:1D_Model:ModelProblems}.\\
+The model is a cantilever Timoshenko beam, denoted by Problem T-2 in Section \ref{ssec:1D_Model:ModelProblems}.
 
@@
 Recall the variational problem for the cantilever beam Problem T-2V, with the test function space $\displaystyle T[0,1] = F_1[0,1] \times F_1[0,1]$.
-To determine the solvability of the problem, the weak variational problem is considered first.\\
+To determine the solvability of the problem, the weak variational problem is considered first.
 
@@
 The inner product for $L^2(0,1)$ yields the inner product $\displaystyle (x_1,y_1) + (x_2,y_2)$ for $X$.
-The idea is to replace the pair $\langle w , \phi \rangle$ by a function $u$ ``of time only" and values $u(t)$ in the space $X$.\\
+The idea is to replace the pair $\langle w , \phi \rangle$ by a function $u$ ``of time only" and values $u(t)$ in the space $X$.
+\label{sym:Ln}
 
@@
 
-The Sobolev space $H^1(0,1)$ is all the functions in $L^2(0,1)$ with at least a first-order weak derivative. $H^1(0,1)$ is complete (see Appendix A).\\
+The Sobolev space $H^1(0,1)$ is all the functions in $L^2(0,1)$ with at least a first-order weak derivative. $H^1(0,1)$ is complete (see Appendix A).\label{sym:Hn}
 
@@
 	\item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
-\end{itemize}
+\end{itemize} \label{sym:Xspace}\label{sym:Wspace}\label{sym:Vspace}\label{sym:norm}
 
@@
 \end{eqnarray}
-while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\\
+while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\label{sym:a} \\
 
@@
 If $f=0$, then $u \in C^1([0,\infty),V)\cap C^2([0,\infty),W)\cap C^\infty((0,\infty),V)$.
-\end{Thm3n}
+\end{Thm3n} \label{Cinfty}
 
@@
 And since $C_0^\infty(0,1)$ is dense in $L_2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L_2(0,1)$.
-Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.\\
+Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.\label{sym:Cinftyzero} \\
 

### 2023-11-07 files/Chapter6/Validity_Timo.tex
symbols

@@
 Specifically, the validity of a cantilever Timoshenko beam model, using a cantilever two-dimensional beam model as a reference.
-This is a discussion and a replication of numerical results of the work done in the article \cite{LVV09}.
+This follows what is done in the article \cite{LVV09}.
+This section discusses the results of the article, focussing on the numerical results.
+Some of the results are replicated with more significant digits, others are extended to be used in the rest of this chapter.
 
@@
 In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
-\textcolor{red}{Give a brief summary of the article here, linking to whatever has already been discussed in the literature review.}
+The authors start by presenting the models.
+These are the same as Problem T-2 and Problem 2D-1 that are defined in Chapter 1.
+The authors also look at the existence and uniqueness of the models, which is covered in Chapter 2 of this dissertation.
+The authors then calculate and compare the eigenvalues and eigenfunctions, which will be discussed in this section.
 
 \subsection{The models}
-The following two models are the focus of this section and the models that are used in the article \cite{LVV09}.
-From section \ref{ssec:1D_Model:ModelProblems}, the cantilever Timoshenko beam model, referred to as Problem T-2.
-From section \ref{ssec:2D_Model:ModelProblem}, the cantilever two-dimensional beam model, referred to as Problem 2D-1.\\
+The cantilever Timoshenko beam model is defined in section \ref{ssec:1D_Model:ModelProblems}, and is referred to as Problem T-2.
+The cantilever two-dimensional beam model is defined in section \ref{ssec:2D_Model:ModelProblem}, and is referred to as Problem 2D-1.
 
@@
 And in section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.
-These can also be obtained to a desired level of accuracy.
 
@@
 In this form, the eigenvalue problem is a system of ordinary differential equations, and can be solved using a numerical method.
+Computer programs like MATLAB provide functions that are able to solve this.
 

### 2023-11-07 table_of_symbols.tex
symbols

\documentclass[main.tex]{subfiles}
\begin{document}

\chapter*{List of Symbols}

The following table provides a list of symbols that will be used throughout this dissertation along with their descriptions:

\noindent
\begin{tabularx}{\textwidth}{cXr}
\toprule
Symbol & Description & First Appearance (Page) \\ 
\midrule
\endhead % Header to be repeated on every page
\( R^n \) & n-dimensional space of real numbers & \pageref{sym:Rn} \\
\( u/w \) & displacement vector & \pageref{sym:u} \\
\( \Omega \) & subset of $R^n$ & \pageref{sym:Omega} \\
\( \rho \) & density & \pageref{sym:rho} \\
\( \partial_x^n \) & n-th partial derivative with respect to $x$ & \pageref{sym:partial_diff} \\
\( \sigma_{ij} \) & element of the stress tensor T & \pageref{sym:sigmaij} \\
\( Q \) & force per unit volume & \pageref{sym:Q} \\
\( \textrm{div}T \) & divergence of T & \pageref{sym:divT} \\
\( \textrm{Tr}(T) \) & Trace of T & \pageref{sym:TrT} \\
\( \mathcal{E} \) & infinitesimal strain tensor & \pageref{sym:mathcalE} \\
\( \varepsilon_{ij} \) & element of the infinitesimal strain tensor $\mathcal{E}$ & \pageref{sym:varepsilonij} \\
\( E \) & Young's modulus & \pageref{sym:E} \\
\( \nu \) & Poisson's ratio & \pageref{sym:nu} \\
\( t \) & time & \pageref{sym:t} \\
\( G \) & shear modulus of elasticity & \pageref{sym:G} \\
\( \tau \) & dimensionless time & \pageref{sym:tau} \\
\( \xi \) & dimensionless space & \pageref{sym:xi} \\
\( Q^* \) & dimensionless force per unit volume & \pageref{sym:Qstar} \\
\( \sigma^*_{ij} \) & dimensionless stress tensor element & \pageref{sym:sigmaijstar} \\
\( \ell \) & dimension representing length & \pageref{sym:ell} \\
\( \kappa^2 \) & some dimensionless constant/shear correction factor & \pageref{sym:kappa2}/\pageref{sym:kappa2T} \\
\( I \) & identity matrix & \pageref{sym:I} \\
\( \gamma \) & a dimensionless constant & \pageref{sym:gamma} \\
\( n \) & a normal vector & \pageref{sym:n} \\
\( \Sigma/\Gamma \) & distinct parts of $\Omega$ & \pageref{sym:SigmaGamma} \\
\( \phi \) & arbitrary vector/rotation of cross-section of Timoshenko beam & \pageref{sym:phi}/\pageref{sym:phiT} \\
\( C^n \) & set of n-times continuously differentiable functions & \pageref{sym:Cn} \\
\( a(\cdot,\cdot),b(\cdot,\cdot),c(\cdot,\cdot) \) & bilinear forms & \pageref{sym:a},\pageref{sym:b},\pageref{sym:c} \\
\( T(\Omega) \) & test function space on $\Omega$ & \pageref{sym:TOmega} \\
\( dV \) & volume integral meassure & \pageref{sym:dV} \\
\( dS \) & surface integral meassure & \pageref{sym:dS} \\
\( dA \) & area integral meassure & \pageref{sym:dA} \\
\( ds \) & line integral meassure & \pageref{sym:ds} \\
\( A \) & area of a cross-section & \pageref{sym:A} \\
\( V \) & shear force & \pageref{sym:V} \\
\( I \) & area moment of inertia & \pageref{sym:Iinertia} \\
\( M \) & moment & \pageref{sym:M} \\
\( \alpha/\beta \) & dimensionless constants & \pageref{sym:alphabeta} \\
\( e_n \) & unit vector in the direction n & \pageref{sym:en} \\
\( \mathbf{Q} \) & constitutive equation for the Reissner-Mindlin plate model & \pageref{sym:bfQ} \\
\( L^n \) & space of n-power Lebesgue integrable functions & \pageref{sym:Ln} \\
\( H^n \) & space of functiontions with weak derivatives up to order n (n'th dimensional Sobolev space) & \pageref{sym:Hn} \\
\( X \) & global space & \pageref{sym:Xspace} \\
\( W \) & inertia space & \pageref{sym:Wspace} \\
\( V \) & energy space & \pageref{sym:Vspace} \\
\( ||\cdot||_X \) & norm in the space $X$ & \pageref{sym:norm} \\
\( C^\infty \) & space of smooth functions & \pageref{sym:Cinfty} \\
\( C^\infty_0 \) & space of smooth functions with compact support & \pageref{sym:Cinftyzero} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\
\( u \) & Displacement vector & \pageref{sym:u} \\

\bottomrule
\end{tabularx}

\end{document}

### 2023-11-08 files/Chapter3/femconvergence.tex
Veranderinge 10-06
symbols

@@
 \begin{document}
-\section{Convergence of eigenvalues in Finite Element Analysis}
+\section{Convergence of eigenvalues and eigenfunctions}
 In this section, the work in the textbook \cite[p.228-236]{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for clarity.\\
@@
 \subsection{General eigenvalue problem}
-Find a function $u \in H$ and number $\lambda \in \mathcal{R}$ such that
+Find a function $u \in H$ and number $\lambda \in R$ such that
 \begin{equation}
@@
 	R(v) = \frac{b(v,v)}{(v,v)} \ \text { for } v \in V.
-\end{equation*}
+\end{equation*} \label{sym:Rayleigh}
 
@@
 
-Consider a interpolation operator $\Pi$. This projection is linear, i.e.
+Consider a interpolation operator $\Pi$.\label{sym:interpolation} This projection is linear, i.e.
 \begin{align*}
@@
 \begin{itemize}
-	\item[] $\mathcal{P}_j(I_e)$: Is the set of all polynomials on the interval $I_e$ of degree at most $j$.
+	\item[] $\mathcal{P}_j(I_e)$: Is the set of all polynomials on the interval $I_e$ of degree at most $j$. \label{sym:poly}
 	\item[] $r(\Pi_e)$: If the range of $\Pi_e$ is contained in $\mathcal{P}_j(I_e)$ and $k<j$ is the largest integer such that $\Pi_e f = f$ for each $f \in \mathcal{P}_j(I_e)$, then $r(\Pi_e) = k$.
@@
 	\begin{equation*}
-		||(\Pi u)^(m) - u^(m)|| \leq C h^{k-m} || u^(k)|| \ \text{ for } m = 0,1,...,k.
+		||(\Pi u)^{(m)} - u^{(m)}|| \leq C h^{k-m} || u^{(k)}|| \ \text{ for } m = 0,1,...,k.
 	\end{equation*}
@@
 Fix $m \in \mathbb{N}$.
-Let $\left\{ \phi_i \in V | i = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
+\label{sym:natural} Let $\left\{ \phi_i \in V | i = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
 Define $S^h := \text{span}\left\{\phi_i \in V | i = 1,2,...,m\right\}$.\\
@@
 
-The space $S^h$ is a finite dimensional subspace of $V$.
+The space $S^h$\label{sym:Sh1} is a finite dimensional subspace of $V$.
 Therefore any subspace of $S^h$ will also be a subspace of $V$.
@@
 \begin{Prop_1}
- $\mu_{m} > 0$ if and only if $\dim S_{m} = m$.
+ $\mu_{m} > 0$ if and only if $\dim S_{m} = m$. \label{sym:mu}
 \end{Prop_1}

### 2023-11-08 table_of_symbols.tex
symbols

@@
 
-The following table provides a list of symbols that will be used throughout this dissertation along with their descriptions:
-
+% Vector Spaces and Related Concepts
 \noindent
+\textbf{Vector Spaces and Related Concepts}\\
 \begin{tabularx}{\textwidth}{cXr}
@@
 \midrule
-\endhead % Header to be repeated on every page
-\( R^n \) & n-dimensional space of real numbers & \pageref{sym:Rn} \\
-\( u/w \) & displacement vector & \pageref{sym:u} \\
-\( \Omega \) & subset of $R^n$ & \pageref{sym:Omega} \\
+\( \mathbb{R}^n \) & n-dimensional space of real numbers & \pageref{sym:Rn} \\
+\( \Omega \) & subset of \( \mathbb{R}^n \), representing a body/reference configuration & \pageref{sym:Omega} \\
+\( C^n \) & set of n-times continuously differentiable functions & \pageref{sym:Cn} \\
+\( L^n \) & space of n-power Lebesgue integrable functions & \pageref{sym:Ln} \\
+\( H^n \) & space of functions with weak derivatives up to order n (n'th dimensional Sobolev space) & \pageref{sym:Hn} \\
+\( C^\infty \) & space of smooth functions & \pageref{sym:Cinfty} \\
+\( C^\infty_0 \) & space of smooth functions with compact support & \pageref{sym:Cinftyzero} \\
+\( \mathcal{P}_j \) & set of all polynomials of degree at most \( j \) & \pageref{sym:poly} \\
+\( \mathbb{N} \) & set of natural numbers \( j \) & \pageref{sym:natural} \\
+\( S^h \) & finite dimensional subspace & \pageref{sym:Sh1} \\
+
+\bottomrule
+\end{tabularx}
+
+% Mathematical Measures and Operations
+\noindent
+\textbf{Mathematical Measures and Operations}\\
+\begin{tabularx}{\textwidth}{cXr}
+\toprule
+Symbol & Description & First Appearance (Page) \\ 
+\midrule
+\( \partial_x^n \) & n-th partial derivative with respect to \( x \) & \pageref{sym:partial_diff} \\
+\( \textrm{div} T \) & divergence of \( T \) & \pageref{sym:divT} \\
+\( \textrm{Tr}(T) \) & Trace of \( T \) & \pageref{sym:TrT} \\
+\( dV \) & volume integral measure & \pageref{sym:dV} \\
+\( dS \) & surface integral measure & \pageref{sym:dS} \\
+\( dA \) & area integral measure & \pageref{sym:dA} \\
+\( ds \) & line integral measure & \pageref{sym:ds} \\
+\( a(\cdot,\cdot), b(\cdot,\cdot), c(\cdot,\cdot) \) & bilinear forms & \pageref{sym:a}, \pageref{sym:b}, \pageref{sym:c} \\
+\( ||\cdot||_X \) & norm in the space \( X \) & \pageref{sym:norm} \\
+\( T(\Omega) \) & test function space on \( \Omega \) & \pageref{sym:TOmega} \\
+\( \mathcal{E}(\cdot) \) & energy function & \pageref{sym:Energy} \\
+\( Pu \) & Projection of the vector u & \pageref{sym:Pu} \\
+\( R(\cdot) \) & Rayleigh quotient & \pageref{sym:Rayleigh} \\
+\( \Pi \) & interpolation operator & \pageref{sym:interpolation} \\
+
+\bottomrule
+\end{tabularx}
+
+% Physical Quantities and Parameters
+\noindent
+\textbf{Physical Quantities and Parameters}\\
+\begin{tabularx}{\textwidth}{cXr}
+\toprule
+Symbol & Description & First Appearance (Page) \\ 
+\midrule
+\( u \) or \( w \) & displacement vector & \pageref{sym:u} \\
 \( \rho \) & density & \pageref{sym:rho} \\
-\( \partial_x^n \) & n-th partial derivative with respect to $x$ & \pageref{sym:partial_diff} \\
-\( \sigma_{ij} \) & element of the stress tensor T & \pageref{sym:sigmaij} \\
+\( \sigma_{ij} \) & element of the stress tensor \( T \) & \pageref{sym:sigmaij} \\
 \( Q \) & force per unit volume & \pageref{sym:Q} \\
-\( \textrm{div}T \) & divergence of T & \pageref{sym:divT} \\
-\( \textrm{Tr}(T) \) & Trace of T & \pageref{sym:TrT} \\
 \( \mathcal{E} \) & infinitesimal strain tensor & \pageref{sym:mathcalE} \\
-\( \varepsilon_{ij} \) & element of the infinitesimal strain tensor $\mathcal{E}$ & \pageref{sym:varepsilonij} \\
+\( \varepsilon_{ij} \) & element of the infinitesimal strain tensor \( \mathcal{E} \) & \pageref{sym:varepsilonij} \\
 \( E \) & Young's modulus & \pageref{sym:E} \\
@@
 \( \ell \) & dimension representing length & \pageref{sym:ell} \\
-\( \kappa^2 \) & some dimensionless constant/shear correction factor & \pageref{sym:kappa2}/\pageref{sym:kappa2T} \\
+\( b \) &  dimension representing width & \pageref{sym:width} \\
+\( h \) & dimension representing height & \pageref{sym:height} \\
+\( \kappa^2 \) & some dimensionless constant/shear correction factor & \pageref{sym:kappa2} \\
 \( I \) & identity matrix & \pageref{sym:I} \\
@@
 \( n \) & a normal vector & \pageref{sym:n} \\
-\( \Sigma/\Gamma \) & distinct parts of $\Omega$ & \pageref{sym:SigmaGamma} \\
-\( \phi \) & arbitrary vector/rotation of cross-section of Timoshenko beam & \pageref{sym:phi}/\pageref{sym:phiT} \\
-\( C^n \) & set of n-times continuously differentiable functions & \pageref{sym:Cn} \\
-\( a(\cdot,\cdot),b(\cdot,\cdot),c(\cdot,\cdot) \) & bilinear forms & \pageref{sym:a},\pageref{sym:b},\pageref{sym:c} \\
-\( T(\Omega) \) & test function space on $\Omega$ & \pageref{sym:TOmega} \\
-\( dV \) & volume integral meassure & \pageref{sym:dV} \\
-\( dS \) & surface integral meassure & \pageref{sym:dS} \\
-\( dA \) & area integral meassure & \pageref{sym:dA} \\
-\( ds \) & line integral meassure & \pageref{sym:ds} \\
+\( \Sigma/\Gamma \) & distinct parts of \( \Omega \) & \pageref{sym:SigmaGamma} \\
+\( \phi \) & arbitrary vector/rotation of cross-section of Timoshenko beam & \pageref{sym:phi} \\
 \( A \) & area of a cross-section & \pageref{sym:A} \\
@@
 \( \alpha/\beta \) & dimensionless constants & \pageref{sym:alphabeta} \\
-\( e_n \) & unit vector in the direction n & \pageref{sym:en} \\
-\( \mathbf{Q} \) & constitutive equation for the Reissner-Mindlin plate model & \pageref{sym:bfQ} \\
-\( L^n \) & space of n-power Lebesgue integrable functions & \pageref{sym:Ln} \\
-\( H^n \) & space of functiontions with weak derivatives up to order n (n'th dimensional Sobolev space) & \pageref{sym:Hn} \\
-\( X \) & global space & \pageref{sym:Xspace} \\
-\( W \) & inertia space & \pageref{sym:Wspace} \\
-\( V \) & energy space & \pageref{sym:Vspace} \\
-\( ||\cdot||_X \) & norm in the space $X$ & \pageref{sym:norm} \\
-\( C^\infty \) & space of smooth functions & \pageref{sym:Cinfty} \\
-\( C^\infty_0 \) & space of smooth functions with compact support & \pageref{sym:Cinftyzero} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
-\( u \) & Displacement vector & \pageref{sym:u} \\
+\( \lambda \) & eigenvalue & \pageref{sym:lambda} \\
+\( \mu \) & eigenvector & \pageref{sym:mu} \\
 

### 2023-11-11 files/Chapter3/dynamicconvergence.tex
symbols
Overview, Chapter 3

@@
 
-In \cite{BV13}, a projection $P$ is defined so that $Pu \in V$. The error is
-then split using this projection. Let $e(t) = Pu(t)- u_h(t)$ and $e_p(t) = u(t)
-	- Pu(t)$ so that
-\begin{eqnarray}
-	e^h(t) = e_p(t) +e(t). \label{Error}
-\end{eqnarray}
-
-According to the authors of~\cite{BV13}, interpolation theory can be used to determine the error $e_p$.
-However to obtain an error estimate for $e$ is not as trivial.
-This is where the use of the Finite Element Analysis comes in.
-
-To simplify the proof, the problem is divided into a semi-discrete problem and a fully discrete problem.
+To simplify the proof, the problem is divided into a semi-discrete problem and a fully discrete problem. The two terms are investigated as seperate problems
+in \cite{BV13}.
 
@@
 
-In \eqref{error_e}, the authors divide the error $e$ into a semi-discrete term
-and a fully discrete term. The two terms are investigated as seperate problems
-in \cite{BV13}.\\
+In \eqref{error_e}, the the error for the semi-discrete problem is the term $[u(t_k)-u_h(t_k)]$ and the term $[u_h(t_k) - u^h_k]$ is the error for the fully disrete appreximation of the semi-discrete approximation.
 
@@
 	\begin{eqnarray*}
-		\Vert u_{h}(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & 7T^{2}\tau^{2}\max\Vert u_{h}^{(4)}\Vert_{W}+7T\tau^{2}\max\Vert u_{h}'''\Vert_{W}\\
+		\Vert u(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & 7T^{2}\tau^{2}\max\Vert u_{h}^{(4)}\Vert_{W}+7T\tau^{2}\max\Vert u_{h}'''\Vert_{W}\\
 		& & + \sqrt{2K_{a}}\tau^{4}\max\Vert u_{h}'''\Vert_{W}
@@
 
-\subsection{Obtaining the error estimate}
-In this section we will show how the error estimate in Theorem 2 is obtained by
-the authors of \cite{BV13}.\\
-
-The following two assumptions are made in \cite{BV13}.
-\subsubsection*{Assumptions}
-\begin{itemize}
-	\item[] \textbf{B1} - The solution $u \in C(J,V)$ of Problem GVar$^h$ has the property that $(Pu) \in C^2(J)$.
-
-	\item[] \textbf{B2} - There exists a subspace $H$ of $V$ and a positive integer $\alpha$ such that if $w \in H$, then $$\inf_{v\in S^{h}}||w-v||_V \leq \hat{C} h^\alpha|||w|||_H,$$ where $|||w|||_H$ is a norm or a semi-norm for $H$.
-\end{itemize}
-
-The projection $P$ in section \eqref{e_est} is defined in \cite{BV13} as
-\begin{eqnarray*}
-	b(u-Pu,v) = 0 \ \ \ \textrm{ for all } v \in V.
-\end{eqnarray*}
-
-From assumption \textbf{B1}, $Pu \in C^2(J)$ and by the definition $P$, $P$ is
-a projection with respect to the inner product $b$.\\
-
-Subtracting \eqref{GV_PB1} from \eqref{DC_E2} gives
-\begin{eqnarray*}
-	c(u''(t)-u''_h(t),v) + a(u'(t)-u'_h(t),v) + b(u(t)-u_h(t),v) = 0
-\end{eqnarray*}
-
-Using the definition of the error $e^h$ while also adding and subtracting
-$Pu(t)$ in the bilinear form $b$, we can write
-\begin{eqnarray*}
-	c(e_h''(t),v) + a(e_h'(t),v) + b(u(t) - Pu(t),v) + b(Pu(t) +u_h(t),v)- = 0.
-\end{eqnarray*}
-
-It then follows from the definitions of the error $e$ and the projection $P$
-that
-\begin{eqnarray*}
-	c(e''(t),v) + a(e'(t),v) + b(e(t),v) = 0
-\end{eqnarray*}
-
-This equation \eqref{DC_E3} is presented in \cite{BV13} as a proposition.
-\newtheorem{DC_Prop1}{Proposition}
-\begin{DC_Prop1}
-	If $u$ is the solution of Problem GVar and $u$ satisfies assumption \textbf{B1}, then
-	\begin{eqnarray}
-		c(e_h''(t),v) + a(e_h'(t),v) + b(e(t),v) = 0 \ \ \ \textrm{ for all } v \in V.
-	\end{eqnarray}
-\end{DC_Prop1}
-
-Using this proposition, the authors of \cite{BV13} derive a generalized error
-estimate for the error $e = Pu - u_h$.
-
-\newtheorem{lem_1}{Lemma}
-\begin{lem_1}
-	If $u$ is the solution of Problem GVar and $u$ satisfies assumption \textbf{B1}, then
-	\begin{eqnarray}
-		\Vert e(t)\Vert_{W} &\leq& \sqrt{2} \biggl( \Vert e(0) \Vert_W + 3T\Vert e'_h(0) \Vert_W + 3 \int_o^T \Vert e'_p(t)\Vert_W\nonumber \\
-		&& + 3K_\alpha T \Vert e_h(0) \Vert_W + 3K_\alpha \int_0^T \Vert e_p(t) \Vert_W \biggr). \label{fundamental_estimate}
-	\end{eqnarray}
-\end{lem_1}
-
-In chapter 2, it was explained that the models of this dissertation have weak
-damping, i.e. $a = 0$. Therefore, the error estimate in Lemma 1 can be
-simplified. This is given in \cite{BV13} as a corollary.
-
-\newtheorem{col_1}{Corollary}
-\begin{col_1}
-	If $u$ is the solution of Problem GVar with $a = 0$ and $u$ satisfies assumption \textbf{B1}, then
-	\begin{eqnarray}
-		\Vert e_(t)\Vert_{W} \leq \sqrt{2} \Vert e(0) \Vert_W + 2T||e'_h(0)||_W + 4\sqrt{T}\max_{t \in [0,T]} \Vert e'_p(t) \Vert_W.
-	\end{eqnarray}
-\end{col_1}
-
-\begin{proof}
-	Assume that there is no damping other than the weak damping, i.e. $a = 0$. The the equation in proposition 1 becomes
-	\begin{eqnarray*}
-		c(e_h''(t),v) + b(e(t),v) = 0 \ \ \ \textrm{ for all } v \in V.
-	\end{eqnarray*}
-
-	If $v \in S^h[0,T]$, then 
-	\begin{eqnarray*}
-		c(e_h''(t),v(t)) + b(e(t),v(t)) = 0.
-	\end{eqnarray*}
-
-	Let $v'(t) = c(t)$, then 
-	\begin{flalign}
-		\frac{d}{dt}\left[\frac{1}{2}c(e,e)-\frac{1}{2}b(v,v)-c(e_h,v) \right] &= c(e',e) - b(e,v)- c(e''_h, v)-c(e_h',v')\nonumber\\
-		&= c(e'_p,e). \label{DC_E4}
-	\end{flalign}
-
-	Choose $v(\tau) = 0$ for some $\tau \in [0,T]$, and integrate \eqref{DC_E4} between $0$ and $\tau$ to obtain
-	\begin{eqnarray*}
-		a
-	\end{eqnarray*}
-
-\end{proof}
-
-\subsubsection{Semi-discrete problem}
-The estimate \eqref{fundamental_estimate} in Lemma 1 is equivalent to
-\begin{eqnarray*}
-	\Vert u(t) - u_h(t) \Vert_{W} &\leq& \sqrt{2} \biggl( \Vert u(0) - u_h(0) \Vert_W + 3T\Vert e'_h(0) \Vert_W + 3 \int_o^T \Vert e'_p(t)\Vert_W\nonumber \\
-	&& + 3K_\alpha T \Vert e_h(0) \Vert_W + 3K_\alpha \int_0^T \Vert e_p(t) \Vert_W \biggr).
-\end{eqnarray*}
-
-Define the projection $P$ such that for any function $u$,
-\begin{eqnarray*}
-	(Pu)(t) = Pu(t) \ \ \ \textrm{ for all } t \in (0,T).
-\end{eqnarray*}
-
-From Theorem 1, it follows that the solution $u$ of Problem GVar satisfies $u
-	\in C^1([0,T]; V) \cap C^2((0,T);V)$. \textcolor{red}{This is a weak assumption
-	made in \cite{BV13}.}\\
-
-\sout{The following is a weak assumption in \cite{BV13}: The solution $u$ of Problem GVar satisfies $u \in C^1([0,T]; V) \cap C^2((0,T);V)$.
-This follows from Theorem 1 and is a necessary assumption in [BSV17].}\\
-
-Let $\Pi$ denote the interpolation operator such that $u_0^h = \Pi u_0$ and
-$u_1^h = \Pi u_1$.
-
-\newtheorem*{DC_Thm4}{Theorem 2}
-\begin{DC_Thm4}
-	Suppose Assumption E2 holds and $u_{0}^{h}=\Pi u_{0}$ and $u_{1}^{h}=\Pi u_{1}.$ If the solution $u$ of Problem $GVar$ satisfies Assumption El, $u(t)\in H$ and $u'(t)\in H$, then
-	\begin{eqnarray*}
-		\Vert u(t)-u_{h}(t)\Vert_{W} & \leq & C_{b} \hat{C}h^{\alpha}|||u(t)|||_{H}+\sqrt{2}C_{b}\hat{C}h^{\alpha}(3T\max|||u'(t)|||_{H}\\
-		& & +3K_{a}T\max|||u(t)|||_{H}+(2+3K_{a}T)|||u_{0}|||_{H} \\
-		& & +3T|||u_{1}|||_{H}) ,
-	\end{eqnarray*} for each $t\in[0, T].$
-\end{DC_Thm4}
-
 \subsection{Fully discrete Galerkin finite element approximation}
+\textcolor{red}{********************HOU VOORLOPIG**********************}
 Consider the time interval $J = [0,T]$. Divide $J$ into $N$ steps with length
@@
 			t_k]$ by $u_k^h$, i.e. $u_h(t_k) = u_k^h$ for each $k$.\\
-
-\sout{The goal the fully-discrete approximation as given by \cite{BV13} is to find an estimate between Problem GVar and Problem GVar$^h$, which can be expressed as}
 
@@
 should also be with respect to the norm of $W$.
-
-\sout{In Theorem 2, Section 3.1.3 it is shown that \cite{BV13} obtained an error estimate for $[u(t_k)-u_h(t_k)]$ with respect to the norm of $W$.
-The authors explain that an estimate for $[u_h(t_k) - u^h_k]$ should also be with respect to the norm $W$ since the dimension of $S^h$ is not fixed and hence the equivalence of the relevant norms cannot be used.}\\
-
-\subsubsection{Notation}
-For any sequence $\{x_k\} \in R_n$,
-For any sequence $\{x_k\} \in R_n$,
-\begin{eqnarray*}
-	\delta_{t}x_{k}& = &\tau^{-1}[x_{k+1}-x_{k}],\\
-	x_{k+\frac{1}{2}} & = & \frac{1}{2}[x_{k+1}+x_{k}].
-\end{eqnarray*}
-
-Let Problem GVar$^h$-D denote the fully discrete form of Problem GVar$^h$.
-\subsubsection*{Problem GVar$^\mathbf{{h}}$-D} Find a sequence
-$\{u_{k}^{h}\}\subset S^{h}$ such that for $k=0,1,2$, . . . , $N-1,$
-\begin{eqnarray}
-	\delta_{t}u_{k}^{h}\ & = & v_{k+\frac{1}{2}},\\
-	c(\delta_{t}v_{k},\ \psi)+a(v_{k+\frac{1}{2}},\ \psi)+b(u_{k+\frac{1}{2}}^{h},\ \psi) & = & \frac{1}{2}([f(t_{k})+f(t_{k+1})],\ \psi)_{X} \nonumber \\ \label{PP}
-\end{eqnarray}
-for each $\psi\in S^{h}$, while $u_{0}^{h}=u_{h}(0)=d^{h}$ and $v_{0}=u_{h}'(0)=v^{h}$.\\
-
-\textcolor{red}{Haal uit************************************************}\\
-The article \cite{BV13} proves the following proposition. This proposition proves that Problem GVar$^h$-D is well defined.
-
-\newtheorem{DC_Prop4}[DC_Prop2]{Proposition}
-\begin{DC_Prop4}
-	Problem $GVar^{h}-D$ has a unique solution for any pair of vectors $d^{h}$ and $v^{h}$ in $S^{h}$.
-\end{DC_Prop4}
-
-In the proof of Proposition 3, the authors of \cite{BV13} show that \eqref{PP}
-in Problem GVar$^h$-D can be rewritten as
-\begin{eqnarray}
-	c(v_k+1,\phi) + \frac{\tau}{2} a(v_{k+1},\phi) + \frac{\tau^2}{4} a(v_{k+1},\phi) & = & c(v_k,\phi) - \frac{\tau}{2} a(v_k,\phi) \nonumber \\  &&
-	- \frac{\tau^2}{4}b(v_k,\phi) - \tau b(u_k,\phi) \nonumber\\
-	&&+\frac{\tau}{2}([f(t_k)+f(t_{k+1})],\phi)_X.\nonumber \\ \label{PPP}
-\end{eqnarray} for each $\phi \in S^h$.\\
-
-Using \eqref{PPP} and the definition of the standard finite element matrices,
-Problem GVar$^h$-D can be reformulated into a algorithm for the Finite Element
-Method. This is the fully discrete form of Problem GVar and is represented in
-Problem FD.\\
-\textcolor{red}{******************************************************}\\
-
-Further results and the standard Finite Element Matrices, let the authors of
-\cite{BV13} rewrite Problem GVar$^\mathbf{{h}}$-D into an algorithm for the
-Finite Element Method. This is represented as Problem FD
-
-\subsubsection*{Problem FD}
-Find a sequence $\{\bar{u}_{k}\}\subset R_{n}$ such that for each $k,$
-\begin{eqnarray*}
-	\bar{u}_{k+1}\ & = & \bar{u}_{k}+\tau\bar{v}_{k+\frac{1}{2}},\\
-	(M + \frac{\tau}{2}C+\frac{\tau^{2}}{4}K)\bar{v}_{k+1} & = & (M- \frac{\tau}{2}C-\frac{\tau^{2}}{4}K)\bar{v}_{k}-\tau K\bar{u}_{k}+\frac{\tau}{2}[F(t_{k})+F(t_{k+1})]
-\end{eqnarray*}
-with $\bar{u}_{0}=\bar{d}$ and $\bar{v}_{0}=\bar{v}.$\\
-
-In this form, the problem is fully discrete. This form also allow the authors
-of \cite{BV13} to obtain an error estimate for the fully-discrete problem.
+\textcolor{red}{********************HOU VOORLOPIG**********************}
 
@@
 
-\textcolor{red}{Haal uit*****************************}\\
+\textcolor{red}{Moontlik hou!}\\
 There error estimate for $[u_h(t_k) - u^h_k]$ can now be determined. Recall that $\tau = \frac{T}{N}$. Subsituting $t = t_k$ and $t = t_k+1$ in Problem GVar$^h$ results in

### 2023-11-11 files/Overview.tex
Overview, Chapter 3

@@
 Using this idea, it is only required to compare the eigenvalues and eigenfunctions of the models to be able to compare the difference between the solutions.
-In Chapter 1, the models of the dissertation is given (they are given in a dimensionless form).
+In Chapter 1, the models of the dissertation are given (in dimensionless form).
 Model problems are then defined by including boundary conditions.
@@
 \subsubsection{Chapter 2}
-First, a variational form for a model problem of a cantilever Timoshenko beam given.
+First, a variational form for a model problem of a cantilever Timoshenko beam is given.
 This model problem in variational form is then extended to complete function spaces, and a weak variational problem is obtained.
@@
 Given a general vibration problem, it is split into two problems by introducing a trial solution.
-It can then be verified that these two problems are the eigenvalue problem and a differential equation.
+It can then be verified that these two problems are the eigenvalue problem and an ordinary differential equation.
 An additional assumption (additional to the assumptions of \cite{VV02}) is introduced by \cite{CVV18}.
-Under this assumption, the eigenvalue problem has infinite many solutions, and the solution of the general vibration problem is an infinite series of the eigenvectors and general Fourier coefficients.
-Solving the differential equation, shows that these Fourier coefficients are periodic and a formal series solution for the general vibration problem (which is a boundary value problem) is obtained.
+Under this assumption, the eigenvalue problem has a complete orthonormal sequence of eigensolutions.
+The solution of the general vibration problem is an infinite series of modal solutions.
 This formal series solution is then shown to also be valid for a initial value problem.
@@
 \subsubsection{Chapter 3}
-\textcolor{red}{Nie seker hoekom prof gese het nie BV13 nie? Ook nie seker hoekom SF97 dood getrek was nie.}
-
 In this chapter, some theory for the Finite Element Method is discussed.
@@
 This theory is presented in the article \cite{BV13}.
-The second part concerns the convergence of the eigenvalues and eigenfunctions of a one-dimensional vibration problem when applying the Finite Element Method.
-This theory is presented in the textbook \cite{SF97}.
+The second part concerns the convergence of the eigenvalues and eigenfunctions of a vibration problem when applying the Finite Element Method.
+This theory is presented in the textbook \cite{SF97}\textcolor{red}{Nie goed genoeg vir dinamiese probleem}.
 
-In the first section, the authors continue with the general vibration problem that is used in Chapter 2.
+In the first part, the authors of \cite{BV13} consider the general vibration problem that is studied in Chapter 2.
 The general vibration problem has a solution as shown in Chapter 2.
-The Galerkin Approximation is derived from the general vibration probelm and is rewritten into a system of ordinary differential using the Finite Element Method.
+The Galerkin Approximation is derived from the general vibration problem and is rewritten into a system of ordinary differential using the Finite Element Method.
 This oridinary differential equation can be proven to have a unique solution.
@@
 The approach of the authors is to calculate the error estimates.
-The error is split into two parts, a semi-discrete and a fully discrete problem.
-Two assumptions are added to the assumptions from Chapter 2.
-Using these assumptions, the authors obtain error estimates for the semi-discrete and fully discrete problems.
 
-The second part of the chapter considers work done in a textbook \cite{SF97}.
+The second part of the chapter considers work done in a textbook \cite{SF97} on eigenvalue problems for elliptic partial differential equations.
 The specific work discussed, covers the convergence of the eigenvalues and eigenfunctions of a one-dimensional vibration problem when applying the Finite Element Method.
@@
 Then using the Rayleigh-quotient, from the Rayleigh-Ritz method, as well as an approximation theorem from \cite{OR97}, the main result is proven.
-The specific work done in this section is updating the notation of the textbook, as well as expanding some results so that the results are easier to understand.
+The specific work done in this section is updating the notation of the textbook, as well as expanding some proofs so that the results are easier to understand.
 
 \subsubsection{Chapter 4}
-This chapter is a focus on the main model theory of this dissertation, the Timoshenko beam theory.
+This chapter is a focus on the main theory of this dissertation, the Timoshenko beam theory.
 The first section is a discussion of modal analysis applied to the Timoshenko beam theory, and specifically a discussion of the article \cite{VV06}.
 In this article, the authors present a method to calculate the exact eigenvalues and eigenfunctions of a Timoshenko beam.
-This method considers the boundary conditions, which differs from most other research.
-Starting with a general eigenvalue problem for a Timoshenko beam model, the authors derive a general solution for this problem.
+Starting with a general eigenvalue problem for a Timoshenko beam model, the authors derive a general solution for the ordinary differential equation.
 The authors then explain the method by hands of an example by applying the method to a cantilever beam model.
-The next sections of this chapter also then looks at examples of applying the method, first to a cantilever beam model, and then to a free-free beam model.
-The examples shows the use of the method, and is preperation for chapter 6 where these results are required for the comparison of the models.
+The next sections of this chapter also then looks at examples of applying the method, first to a cantilever beam model, and then to a pinned-pinned beam model.
 
-The next section is a short discussion on a suspended beam model, afterwards an important article \cite{SP06} is discussed.
+The next section is a short discussion on a suspended beam model, from an important article \cite{SP06}.
 In this article, the authors investigate the validity of the Timoshenko beam theory, by comparing the eigenvalues (natural frequencies) for a physical beam, to a Timoshenko beam and a three-dimensional beam using Finite Element Analysis.
-The authors suspended the beam, and vribrated the beam to induce a free-free beam and measure the natural frequencies.
+The authors report on an experiment with a vibrated a free-free beam measure the natural frequencies.
 These emperical results are then compared to the theoretical results.
 This result, together with the results in chapter 6, give a good picture to the validity of the Timoshenko beam theory.
-Finally the chapter finished by looking at an interesting model of a cantilever beam with a tip-body with elastic interfaces.
+Finally the chapter is concluded by looking at a model of a cantilever beam with a tip-body with elastic interfaces.
 These results combine modal analysis and investigates at the behavior of the model.

### 2023-11-11 table_of_symbols.tex
Overview, Chapter 3

@@
 \midrule
-\( \mathbb{R}^n \) & n-dimensional space of real numbers & \pageref{sym:Rn} \\
-\( \Omega \) & subset of \( \mathbb{R}^n \), representing a body/reference configuration & \pageref{sym:Omega} \\
+\( R^n \) & n-dimensional space of real numbers & \pageref{sym:Rn} \\
+\( \Omega \) & subset of \( R^n \), representing a body/reference configuration & \pageref{sym:Omega} \\
 \( C^n \) & set of n-times continuously differentiable functions & \pageref{sym:Cn} \\
@@
 \( \rho \) & density & \pageref{sym:rho} \\
+\( T \) & stress tensor & \pageref{sym:T} \\
 \( \sigma_{ij} \) & element of the stress tensor \( T \) & \pageref{sym:sigmaij} \\

### 2023-11-12 files/Chapter1/2DModel.tex
symbols
table of symbols

@@
 
-Assume that $\sigma_{3i} = 0$ for $i = 1, 2, 3$\textcolor{red}{;} $\partial_3 u_1 = 0$, $\partial_3 u_2 = 0$ ($u_1$ and $u_2$ are functions of $x_1$ and $x_2$), and the strain component $\varepsilon_{33} = 0$.
+Assume that $\sigma_{3i} = 0$ for $i = 1, 2, 3$; $\partial_3 u_1 = 0$, $\partial_3 u_2 = 0$ ($u_1$ and $u_2$ are functions of $x_1$ and $x_2$), and the strain component $\varepsilon_{33} = 0$.
 Then using the definition of strain
@@
 
-It follows that $u_3$ is a constant on $\Omega$ and $u$ is a vector valued function in $R_2$ with two-dimensional stress and strain.
+It follows that $u_3$ is a constant on $\Omega$ and $u$ is a vector valued function in $R^2$ with two-dimensional stress and strain.
 The out of plane conditions for strain \eqref{plane_stress_neseccary_condition} falls away and Hooke’s law can be written in a two-dimensional form using the stress components (1.2.16) as $\displaystyle T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E})I.$\\
@@
 \begin{eqnarray}
-	T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E}) I. \label{eq:2D_Model:CE}
+	T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{Tr}(\mathcal{E}) I. \label{eq:2D_Model:CE}
 \end{eqnarray}
@@
 \subsection{Model problem}\label{ssec:2D_Model:ModelProblem}
-Suppose $\Omega \subset R_2$ is the reference configuration for a solid executing small vibrations.
+Suppose $\Omega \subset R^2$ is the reference configuration for a solid executing small vibrations.
 The boundary of $\Omega$ consists of two parts $\Sigma$ and $\Gamma$.
@@
 Instead of volume integrals ($dV$) and surface integrals ($dS$), the two-dimensional model has area ($dA$) and line integrals ($ds$).
-Rather than the divergence formula, the divergence form of Green's formula is used to obtain the following result:
+Rather than the divergence formula, the divergence form of Green's formula is used to obtain the following result:\label{sym:dV}\label{sym:dS}\label{sym:dA}\label{sym:ds}
 \begin{eqnarray*}
@@
 \subsubsection{Test functions for problem 2D-1}\label{sssec:2D_Model:TestFunctions2D1}
-The test function space has the same definition of the test function space for Problem 3D-1. But since $\Omega \in R_2$, we have that $T(\Omega) \subset R_2$.
+The test function space has the same definition of the test function space for Problem 3D-1. But since $\Omega \in R^2$, we have that $T(\Omega) \subset R^2$.
 \begin{eqnarray*}
 	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}. 
-\end{eqnarray*}
+\end{eqnarray*}\label{sym:baromega}
 

### 2023-11-12 files/Chapter1/3DModel.tex
table of symbols

@@
 \subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
-Suppose $\Omega \subset R_3$ is the reference configuration for a solid
+Suppose $\Omega \subset R^3$ is the reference configuration for a solid
 executing small vibrations. The boundary of $\Omega$ can be divided into two
@@
 	Tn & = & 0 \quad \textrm{ on } \partial\Omega
-\end{eqnarray*} With $n$ the unit outward normal vector.
+\end{eqnarray*} With $n$ the unit outward normal vector. \label{sym:boundaryOmega}
 
@@
 i.e. $\sigma_{3i} = 0$ for all $i$. From Hooke's Law \eqref{DM_H_E} the
-following equations are obtained:
+following equations are obtained: \label{sym:e_i}
 

### 2023-11-12 files/Chapter1/PlateModel.tex
table of symbols

@@
 This motion can be described by using spherical coordinates.
-Assume that the plate has a two dimensional domain $\Omega \subset R_2$.
+Assume that the plate has a two dimensional domain $\Omega \subset R^2$.
 For $r \geq 0$, the coordinates $x_1$ and $x_2$ can be rewritten as
@@
 	\subsection{Equations of Motion and Constitutive Equations}\label{ssec:P_Model:EquationsOfMotion+ConstitutiveEquation}
-	Consider a Reissner-Mindlin plate with reference configuration $\Omega \in R_2$.
+	Consider a Reissner-Mindlin plate with reference configuration $\Omega \in R^2$.
 Let $u \in \Omega$ define the transverse motion of the plate model and $\psi = \langle \psi_1 \ \psi_2 \rangle$ the angle between the material line and a line perpendicular to the plate.
@@
 	\subsection{Model Problems}\label{ssec:P_Model:ModelProblems}
-	Let $\Omega \subset R_2$ denote reference configuration of the plate model. Following \cite{Wu05}, $\Omega$ is a rectangle.\\
+	Let $\Omega \subset R^2$ denote reference configuration of the plate model. Following \cite{Wu05}, $\Omega$ is a rectangle.\\
 

### 2023-11-12 files/Chapter2/generalvibrationmodel.tex
symbols
table of symbols

@@
 	\item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
-\end{itemize} \label{sym:Xspace}\label{sym:Wspace}\label{sym:Vspace}\label{sym:norm}
+\end{itemize} \label{sym:Xspace}\label{sym:Wspace}\label{sym:Vspace}\label{sym:norm} \label{sym:innerproduct}
 
@@
 If $f=0$, then $u \in C^1([0,\infty),V)\cap C^2([0,\infty),W)\cap C^\infty((0,\infty),V)$.
-\end{Thm3n} \label{Cinfty}
+\end{Thm3n} \label{sym:Cinfty}
 
@@
 \subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
-Find $\lambda \in \mathbb{R}$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
+Find $\lambda \in R$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
 \begin{eqnarray*}
@@
 	 -\int_0^1\alpha \tilde{w}' \psi + \int_0^1\alpha \tilde{\phi} \psi - \int_0^1\frac{1}{\gamma}\tilde{\phi}' \psi' &=& \int_0^1 \lambda \tilde{\phi} \psi .
-\end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$.
+\end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$. \label{sym:lambda}
 
@@
 
-In the article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ a function $u$ given by
+In the article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ a function $u$ given by \label{sym:Energy}
 \begin{eqnarray}
@@
 These comparisons are made in Chapter 4 and 6.
-Being able to express the solutions as a valid series solution, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.
+Being able to express the solutions as valid series solutions, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.
 This is explained in detail in \cite{CVV18}.
@@
 In \cite{CVV18}, the authors consider a beam model and wave equation model for a vibrating string.
-Suppose that for the same initial conditions, $u_b$ and $u_w$ are the exact solution.
+Suppose that for the same initial conditions, $u_b$ and $u_w$ are the exact solutions.
 A comparison of the exact solutions are not possible, but the partial sums can be compared if the bounds for the errors $u_b - u^N_b$ and $u_w - u^N_w$ can be guaranteed.
@@
 \begin{proof}
-	Suppose $f,g \in \mathbb{R}[a,b]$. Then
+	Suppose $f,g \in R[a,b]$. Then
 	\begin{eqnarray}

### 2023-11-12 files/Chapter3/dynamicconvergence.tex
table of symbols

@@
 \section{Introduction}
+\textcolor{red}{1973 is die original, en 1997 is 'n update tot die 1973 met extra voorbeelde, kode en oefeninge. Die 1997 is die die kopie wat ek het. So prof moet se as ek 1973 eerder moet gebruik.}
+
 In this chapter, two important convergence results of the Finite Element Method
@@
 differential equations denoted by Problem ODE. \subsubsection*{Problem ODE}
-Find a function $\bar{u} \in S^h$ such that
+Find a function $\bar{u} \in S^h$ such that \label{sym:baru}
 \begin{eqnarray}
@@
 
-In \eqref{error_e}, the the error for the semi-discrete problem is the term $[u(t_k)-u_h(t_k)]$ and the term $[u_h(t_k) - u^h_k]$ is the error for the fully disrete appreximation of the semi-discrete approximation.
+In \eqref{error_e}, the the error for the semi-discrete problem is the term $u(t_k)-u_h(t_k)$ and the term $u_h(t_k) - u^h_k$ is the error for the fully disrete appreximation of the semi-discrete approximation.
 
 \subsection{Main result}
+\textcolor{red}{************** NIE DIE MAIN RESULT NIE*******************}
 
@@
 \textcolor{red}{********************HOU VOORLOPIG**********************}
+
 Consider the time interval $J = [0,T]$. Divide $J$ into $N$ steps with length
@@
 should also be with respect to the norm of $W$.
+
 \textcolor{red}{********************HOU VOORLOPIG**********************}
+
+\textcolor{red}{Dupliseering maar moontlik beter as werk net voor Main Result, p52}
 

### 2023-11-12 files/Chapter4/CantileverTimo.tex
table of symbols

@@
 
-\subsubsection{Problem Var} Find the functions $w$, $\phi$, $V$ and $\theta$ such that $\langle w(\cdot,t), \phi(\cdot,t) \rangle \in T[0,1] \times C^1[0,1]$, $V(\cdot,t) \in C^1[0,1]$ and $\theta(t) \in \mathbb{R}$ for all $t>0$ and the following equations hold:
+\subsubsection{Problem Var} Find the functions $w$, $\phi$, $V$ and $\theta$ such that $\langle w(\cdot,t), \phi(\cdot,t) \rangle \in T[0,1] \times C^1[0,1]$, $V(\cdot,t) \in C^1[0,1]$ and $\theta(t) \in R$ for all $t>0$ and the following equations hold:
 \begin{align}
@@
 Let $S_0 = \textrm{span}\left\{\delta_0,\delta_1,\delta_2,...,\delta_n\right\}$ and $S = \textrm{span}\left\{\delta_1,\delta_2,\delta_3,...,\delta_n\right\}$.
+\label{sym:span}
 
 \subsubsection{Problem G}
-Find the functions $w^h$, $\phi^h$, $V^h$ and $\theta^h$ such that $w^h(\cdot,t) \in S$,  $\phi^h(\cdot,t),V^h(\cdot,t) \in S_0$ and $\theta^h(t) \in \mathbb{R}$ for all $t>0$ and the following equations hold:
+Find the functions $w^h$, $\phi^h$, $V^h$ and $\theta^h$ such that $w^h(\cdot,t) \in S$,  $\phi^h(\cdot,t),V^h(\cdot,t) \in S_0$ and $\theta^h(t) \in R$ for all $t>0$ and the following equations hold:
 
@@
 \subsubsection{Problem ODE}
-Find the functions $\bar{w} \in S$, $\bar{\phi}, \bar{V} \in S_0$ and $\theta^h \in \mathbb{R}$ such that
+Find the functions $\bar{w} \in S$, $\bar{\phi}, \bar{V} \in S_0$ and $\theta^h \in R$ such that
 \begin{align}

### 2023-11-12 files/Chapter5/2D_FEM.tex
table of symbols

@@
 Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$.
-Denote the elastic body by $\Omega \in R_2$, with $(0,0)$ as the point of reference.
+Denote the elastic body by $\Omega \in R^2$, with $(0,0)$ as the point of reference.
 For a rectangular cross-section, the body $\Omega$ can be described as,
@@
 	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
-\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines (or edges) as follows:
+\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines (or edges) as follows: \label{sym:En}
 

### 2023-11-12 table_of_symbols.tex
table of symbols

@@
 \midrule
+\( \mathbb{N} \) & set of natural numbers \( j \) & \pageref{sym:natural} \\
 \( R^n \) & n-dimensional space of real numbers & \pageref{sym:Rn} \\
-\( \Omega \) & subset of \( R^n \), representing a body/reference configuration & \pageref{sym:Omega} \\
+\( \Omega \) & subset of \( R^n \), usually representing a body/reference configuration & \pageref{sym:Omega} \\
+\( \partial \Omega \) & the boundary of $\Omega$ & \pageref{sym:boundaryOmega} \\
+\( \bar{\Omega} \) & the boundary of $\Omega$ & \pageref{sym:baromega} \\
 \( C^n \) & set of n-times continuously differentiable functions & \pageref{sym:Cn} \\
+\( C^\infty \) & space of smooth functions & \pageref{sym:Cinfty} \\
+\( C^\infty_0 \) & space of smooth functions with compact support & \pageref{sym:Cinftyzero} \\
 \( L^n \) & space of n-power Lebesgue integrable functions & \pageref{sym:Ln} \\
 \( H^n \) & space of functions with weak derivatives up to order n (n'th dimensional Sobolev space) & \pageref{sym:Hn} \\
-\( C^\infty \) & space of smooth functions & \pageref{sym:Cinfty} \\
-\( C^\infty_0 \) & space of smooth functions with compact support & \pageref{sym:Cinftyzero} \\
+\( X \) & global space & \pageref{sym:Xspace} \\
+\( V \) & inertia space & \pageref{sym:Wspace} \\
+\( W \) & energy space & \pageref{sym:Vspace} \\
+\( T(\Omega) \) & test function space on \( \Omega \) & \pageref{sym:TOmega} \\
+\( S^h \) & finite dimensional subspace & \pageref{sym:Sh1} \\
 \( \mathcal{P}_j \) & set of all polynomials of degree at most \( j \) & \pageref{sym:poly} \\
-\( \mathbb{N} \) & set of natural numbers \( j \) & \pageref{sym:natural} \\
-\( S^h \) & finite dimensional subspace & \pageref{sym:Sh1} \\
+\( E_n \) & space spanned by the orthonormal basis vectors $e_i$ & \pageref{sym:En} \\
 
@@
 \midrule
-\( \partial_x^n \) & n-th partial derivative with respect to \( x \) & \pageref{sym:partial_diff} \\
-\( \textrm{div} T \) & divergence of \( T \) & \pageref{sym:divT} \\
-\( \textrm{Tr}(T) \) & Trace of \( T \) & \pageref{sym:TrT} \\
+\( a(\cdot,\cdot), b(\cdot,\cdot), c(\cdot,\cdot) \) & bilinear forms & \pageref{sym:a}, \pageref{sym:b}, \pageref{sym:c} \\
+\( (\cdot, \cdot)_X \) & innerproduct of X & \pageref{sym:innerproduct} \\
+\( ||\cdot||_X \) & norm in the space \( X \) & \pageref{sym:norm} \\
+\( \partial_x^nf \) & n-th partial derivative of f with respect to \( x \) & \pageref{sym:partial_diff} \\
+\( \textrm{div} X \) & divergence of the matrix \( X \) & \pageref{sym:divT} \\
+\( \textrm{Tr}(X) \) & Trace of the matrix \( X \) & \pageref{sym:TrT} \\
+\( \textrm{det}(M) \) & determinant of M & \pageref{sym:determinant} \\
+\( \textrm{span}(\cdot) \) & span of a set & \pageref{sym:span} \\
 \( dV \) & volume integral measure & \pageref{sym:dV} \\
@@
 \( ds \) & line integral measure & \pageref{sym:ds} \\
-\( a(\cdot,\cdot), b(\cdot,\cdot), c(\cdot,\cdot) \) & bilinear forms & \pageref{sym:a}, \pageref{sym:b}, \pageref{sym:c} \\
-\( ||\cdot||_X \) & norm in the space \( X \) & \pageref{sym:norm} \\
-\( T(\Omega) \) & test function space on \( \Omega \) & \pageref{sym:TOmega} \\
 \( \mathcal{E}(\cdot) \) & energy function & \pageref{sym:Energy} \\
-\( Pu \) & Projection of the vector u & \pageref{sym:Pu} \\
 \( R(\cdot) \) & Rayleigh quotient & \pageref{sym:Rayleigh} \\
 \( \Pi \) & interpolation operator & \pageref{sym:interpolation} \\
-
+\( \bar{u} \) & another form explicity showing u is a vector & \pageref{sym:baru} \\
+\( \textrm{RE} \) & abbriviation for the relative error & \pageref{sym:RE} \\
 \bottomrule
@@
 \midrule
+\( \lambda \) & eigenvalue & \pageref{sym:lambda} \\
 \( u \) or \( w \) & displacement vector & \pageref{sym:u} \\
+\( \phi \) & arbitrary vector/rotation of cross-section of Timoshenko beam & \pageref{sym:phi} \\
+\( Q \) & force per unit volume & \pageref{sym:Q} \\
 \( \rho \) & density & \pageref{sym:rho} \\
@@
 \( \sigma_{ij} \) & element of the stress tensor \( T \) & \pageref{sym:sigmaij} \\
-\( Q \) & force per unit volume & \pageref{sym:Q} \\
 \( \mathcal{E} \) & infinitesimal strain tensor & \pageref{sym:mathcalE} \\
@@
 \( t \) & time & \pageref{sym:t} \\
+\( \ell \) & dimension representing length & \pageref{sym:ell} \\
+\( h \) & dimension representing height & \pageref{sym:height} \\
+\( b \) &  dimension representing width & \pageref{sym:width} \\
 \( G \) & shear modulus of elasticity & \pageref{sym:G} \\
+\( A \) & area of a cross-section & \pageref{sym:A} \\
+\( V \) & shear force & \pageref{sym:V} \\
+\( I \) & area moment of inertia & \pageref{sym:Iinertia} \\
+\( M \) & moment & \pageref{sym:M} \\
+\( f^* \) & dimensionless form of f & \pageref{sym:sigmaijstar} \\
 \( \tau \) & dimensionless time & \pageref{sym:tau} \\
 \( \xi \) & dimensionless space & \pageref{sym:xi} \\
-\( Q^* \) & dimensionless force per unit volume & \pageref{sym:Qstar} \\
-\( \sigma^*_{ij} \) & dimensionless stress tensor element & \pageref{sym:sigmaijstar} \\
-\( \ell \) & dimension representing length & \pageref{sym:ell} \\
-\( b \) &  dimension representing width & \pageref{sym:width} \\
-\( h \) & dimension representing height & \pageref{sym:height} \\
+\( \alpha/\beta \) & dimensionless constants & \pageref{sym:alphabeta} \\
 \( \kappa^2 \) & some dimensionless constant/shear correction factor & \pageref{sym:kappa2} \\
@@
 \( \Sigma/\Gamma \) & distinct parts of \( \Omega \) & \pageref{sym:SigmaGamma} \\
-\( \phi \) & arbitrary vector/rotation of cross-section of Timoshenko beam & \pageref{sym:phi} \\
-\( A \) & area of a cross-section & \pageref{sym:A} \\
-\( V \) & shear force & \pageref{sym:V} \\
-\( I \) & area moment of inertia & \pageref{sym:Iinertia} \\
-\( M \) & moment & \pageref{sym:M} \\
-\( \alpha/\beta \) & dimensionless constants & \pageref{sym:alphabeta} \\
-\( \lambda \) & eigenvalue & \pageref{sym:lambda} \\
 \( \mu \) & eigenvector & \pageref{sym:mu} \\
+\( e_i \) & orthonormal basis vector & \pageref{sym:e_i} \\
 

### 2023-11-12 Appendix.tex
appendix

--- 2023-11-12 table_of_symbols.tex
@@
 \begin{document}
+\chapter*{Appendix}
+\addcontentsline{toc}{chapter}{Appendix}
 
-\chapter*{List of Symbols}
+\section*{List of symbols}
+\addcontentsline{toc}{section}{List of symbols}
+
+This list of symbols contain some of the most used symbols in this dissertation.
+The symbols are grouped into three categories: Vector Spaces and Related Concepts, Mathematical Measures and Operations, and Physical Quantities and Parameters.
+The first appearance of each symbol is also listed.
+
+Other symbols that are section specific or that are contextually evident might not be in this list.
 
@@
 \noindent
-\textbf{Vector Spaces and Related Concepts}\\
+\textbf{Vector Spaces and Related Co
+ncepts}\\
 \begin{tabularx}{\textwidth}{cXr}
@@
 
+\section*{Sobolev spaces}
+\addcontentsline{toc}{section}{Sobolev spaces}
+
+\subsection*{The Space $L^2$}
+Consider a measurable space $X$. The set of square integrable functions is called the $L^2$ space.\\
+
+The inner product of $L^2$ is defined as 
+\begin{eqnarray*}
+	(f,g) = \int_X fg \ \ \ \ \textrm { for } f,g \in L2.
+\end{eqnarray*}
+The norm can be defined as $||f|| = (f,f)^{\frac{1}{2}}$ for each $f \in L^2(X)$. For reference, see \cite{Rud53}.
+
+\subsection*{The Space \( L^p \)}
+Consider a measurable space \( X \).
+For a real number \( p \geq 1 \), the set of \( p \)-integrable functions is called the \( L^p \) space.
+A function \( f \) belongs to \( L^p(X) \) if the \( p \)-th power of its absolute value is Lebesgue integrable, that is, if
+\begin{eqnarray*}
+    \int_X |f|^p < \infty.
+\end{eqnarray*}
+
+The \( L^p \) norm (or \( p \)-norm) is defined as
+\begin{eqnarray*}
+    ||f||_p = \left( \int_X |f|^p \right)^{\frac{1}{p}}
+\end{eqnarray*}
+for each \( f \in L^p(X) \).
+
+\subsection*{Continuous function spaces}
+$C^m(a,b)$ is the space of functions with continuous derivatives up to order $m$ over the open interval (a,b).
+
+$C^m[a,b]$ is the space of functions in $C^m(a,b)$, with existing right derivatives at $a$ and existing left derivatives at $b$, up to order m.
+
+$C_0^m(a,b)$ contains all functions $f$ in $C^m[a,b]$ with the property that there exists numbers $a < \alpha < \beta < b$ such that $f$ is zero on $[a,\alpha] \cup [\beta, b]$.
+This property is called compact support.
+
+$C^\infty(a,b)$ contains all functions in $C^m(a,b)$ for all $m$.
+
+$C^\infty[a,b]$ contains all functions in $C^m[a,b]$ for all $m$.
+
+$C_0^\infty(a,b)$ contains all functions in $C_0^m(a,b)$ for all $m$.
+
+\subsection*{First order weak derivative}
+Suppose $u \in L^2(a,b)$ and there exist a $v \in L^2(a,b)$ such that
+\begin{eqnarray*}
+	(u,\phi') = -(v,\phi) \ \textrm{ for each } \phi \in C^{\infty}_0(a,b)
+\end{eqnarray*}
+then $v$ is called the first order weak derivative of $u$ and is denoted by $Du$.
+
+\subsection*{Higher order weak derivative}
+Suppose $u \in L^2(a,b)$ and there exist a $v \in L^2(a,b)$ such that
+\begin{eqnarray*}
+	(u,\phi^{(m)}) = (-1)^{(m)}(v,\phi) \ \textrm{ for each } \phi \in C^{\infty}_0(a,b)
+\end{eqnarray*}
+then $v$ is called the m'th order weak derivative of $u$ and is denoted by $D^{(m)}u$.
+
+\subsection*{Sobolev spaces}
+
+$W^n$ is the space of functions with weak derivatives up to order $n$. There are also special notation $W^{n,p}$ that indicates that the functions are P-intergrable.
+
+$H^n$ is the space of functions with weak derivatives up to order $n$ and the functions are square integrable. (i.e. $H^n = W^{n,2}$)
+
 \end{document}

### 2023-11-12 files/Chapter3/dynamicconvergence.tex
appendix

@@
 Galerkin approximation for second order hyperbolic type problems. The article
-\cite{BV18} extends the work of \cite{BV13} by including general damping and
+\cite{BSV17} extends the work of \cite{BV13} by including general damping and
 damping at the endpoints. For the models in Chapter 1, \cite{BV13} is
-sufficient while \cite{BV18} provides more insight and improved notation.
+sufficient while \cite{BSV17} provides more insight and improved notation.
 

### 2023-11-12 files/Chapter6/Introduction.tex
symbols
appendix

@@
 
-Some examples of values for $\alpha$ and the corresponding height of the beam that can be expected in this chapter, are given in Table \ref{tab:alphaheight} below.
-
-\begin{table}[h]
-	\centering
-	\begin{tabular}{|c|c|}
-		\hline
-		$\alpha$ & $h$\\
-		\hline
-		$100$ & $\approx 0.35$ \\
-		$300$ & $1/5$ \\
-		$1200$ & $1/10$ \\
-		$4800$ & $1/20$ \\
-		$9600$ & $\approx 0.035$ \\
-		$10800$ & $1/30$ \\
-		\hline
-	\end{tabular}
-	\caption{Values of $\alpha$ and the corresponding height of the beam.}
-	\label{tab:alphaheight}
-\end{table}
-
 \subsubsection{Two-dimensional beam}
@@
 
-\subsection{Beam type and plate type problems}
-The investigation of this chapter, and this dissertation focuses on beam-type and plate-type problems. \textcolor{red}{**************expand**********}
-
 \end{document}

### 2023-11-12 files/Overview.tex
appendix

@@
 The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues.
-The authors also consider different shapes of beams, from a short fat beam to a long slender beam.
-The results show that the models compare very well, even for a short and fat beam.
+The authors also consider different shapes of beams, from a short thick beam to a long slender beam.
+The results show that the models compare very well, even for a short and thick beam.
 As the beam gets more slender, the comparison improves.
@@
 But in real-world applications, a beam is a three-dimensional model.
-Therefore it would be more suited to use a three-dimensional model to investigate the validity of the Timoshenko beam theory.
+Therefore it should be more realistic to use a three-dimensional model to investigate the validity of the Timoshenko beam theory.
 This is mentioned by the authors of \cite{LVV09}.
@@
 Again the results so that the comparison relies on the shape of the beams.
-The two-dimensional model compares well to the three-dimensional beam if the beam is not very wide.
+The two-dimensional model compares well to the three-dimensional beam if the beam is not wide.
 
@@
 The results show that the Reissner-Mindlin plate model compares well to the three-dimensional plate model.
-This is also true for a wide plate.
-
-Overall the models compare very well, as long as the shape of the model is realistic.
 
@@
 The in \cite{BV13} the authors prove that this error can be made arbitrarily small by choosing a sufficiently small $h$, such that $u^h \rightarrow u$ as $h \rightarrow 0$.
-\cite{BV18} extends \cite{BV13} to include damping.\\
+\cite{BSV17} extends \cite{BV13} to include damping.\\
 

### 2023-11-13 files/Chapter4/SuspendedBeamModel.tex
chapter 4

@@
 \begin{document}
-\setcounter{chapter}{4}
-\section{Suspended beam model}
+\subsection{Suspended beam model}
+In the article \cite{SP06}, the beam is suspended at both ends.
+The beam is then vibrated and the induced motion causes the beam to transition into a free-free beam.
+This subsection is a short description of the suspended beam model.
+
 The suspended Timoshenko beam model is referred to as Problem T-3 in this \ref{ssec:1D_Model:ModelProblems}.

### 2023-11-13 files/Chapter3/dynamicconvergence.tex
chapter 3 fix

@@
 \section{Introduction}
-\textcolor{red}{1973 is die original, en 1997 is 'n update tot die 1973 met extra voorbeelde, kode en oefeninge. Die 1997 is die die kopie wat ek het. So prof moet se as ek 1973 eerder moet gebruik.}
 
@@
 (FEM) is discussed. The first result looks at the convergence of the Galerkin
-approximation for second order hyperbolic type problems, as presented
-in~\cite{BV13}. The second result, from the textbook~\cite{SF97}, examines the
+approximation for second order hyperbolic type problems (or general vibation problems).
+The papers considered are \cite{BV13} and \cite{BSV17}.
+The second result is from the textbook~\cite{SF73} and examines the
 convergence of eigenvalues and eigenfunctions for a one-dimensional vibration
@@
 
-\section{Convergence of the Galerkin approximation}\label{sec:convergence-of-the-galerkin-approximation}
+\section{Galerkin approximation for second order hyperbolic type problems}\label{sec:convergence-of-the-galerkin-approximation}
 In the article \cite{BV13}, the authors investigate the convergence of the
@@
 
+\subsection{Formulation of the Galerkin approximation}
 \subsubsection*{Problem GVar}
@@
 
-This theorem is presented and proved in \cite{BV13}.
-
 \subsection{System of ordinary differential equations}
@@
 
-Since the set $\{\phi_1, \ \phi_2,...,\phi_n\}$ forms a linearly independent
-basis for $S^h$, the bilinear form $c$ is positive definite on $S^h$.
-Consequently, the matrix $M$ is invertible. The equation \eqref{ODE} can
-therefore be rewritten as $\bar{u}'' + M^{-1}C\bar{u}' + M^{-1}K \bar{u} =
-	M^{-1}F(t)$. Using the theory of linear differential equations, a unique
-solution for Problem ODE can be found, proving Proposition 1.
-
 Proposition 2 provides a link between the solution of Problem ODE and the
@@
 
-Let $u$ be the solution of Problem GVar and $u^h$ be the solution of Problem
-GVar$^h$. The authors of \cite{BV13} define the following error,
-
-Let $u$ be the solution of Problem GVar and $u^h$ be the solution of Problem GVar$^h$.
- The authors of \cite{BV13} define the following error,
+Let $u$ be the solution of Problem GVar and $u^h$ be the solution of Problem GVar$^h$. The authors of \cite{BV13} define the following error,
 \begin{eqnarray}
@@
 
-\subsection{Main result}
-\textcolor{red}{************** NIE DIE MAIN RESULT NIE*******************}
-
-The main result proving the convergence of the solution of the Galerkin
-Approximation is given in \cite{BV13} as follows.
-
-\newtheorem*{DC_Thm5}{Theorem 2}
-\begin{DC_Thm5}
-	{Main Result}\\
-	If $f\in C^{2}([0,T]4,X)$, then
-	\begin{eqnarray*}
-		\Vert u(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & 7T^{2}\tau^{2}\max\Vert u_{h}^{(4)}\Vert_{W}+7T\tau^{2}\max\Vert u_{h}'''\Vert_{W}\\
-		& & + \sqrt{2K_{a}}\tau^{4}\max\Vert u_{h}'''\Vert_{W}
-	\end{eqnarray*}
-	for each $t\in(0,\ T)$.
-\end{DC_Thm5}
-
-The parameter $\tau$ is some number in $(0,T)$. The constant $K_\alpha$ is the
-constant defined in assumption \textbf{A4} of Section 2.2.1.
-
-\subsection{Fully discrete Galerkin finite element approximation}
-\textcolor{red}{********************HOU VOORLOPIG**********************}
-
-Consider the time interval $J = [0,T]$. Divide $J$ into $N$ steps with length
-$\tau = \frac{T}{N}$. Each interval can be expressed as $[t_{k-1}, \ t_k]$ for
-$k = 1,...,N$. Denote the approximation of $u_h$ on the interval $[t_{k-1}, \
-			t_k]$ by $u_k^h$, i.e. $u_h(t_k) = u_k^h$ for each $k$.\\
-
-The error $e(t)$, can now be expressed as
-\begin{eqnarray}
-	e(t_k) = u(t_k) - u^h_k & = & [u(t_k)-u_h(t_k)] + [u_h(t_k) - u^h_k]. \label{error_ek}
-\end{eqnarray}
+\textbf{Fully discrete Galerkin finite element approximation}
 
@@
 
-\textcolor{red}{********************HOU VOORLOPIG**********************}
+A stability result is needed.
 
-\textcolor{red}{Dupliseering maar moontlik beter as werk net voor Main Result, p52}
-
-\subsubsection{Error estimate for the fully discrete problem}
-
-\textcolor{red}{Moontlik hou!}\\
-There error estimate for $[u_h(t_k) - u^h_k]$ can now be determined. Recall that $\tau = \frac{T}{N}$. Subsituting $t = t_k$ and $t = t_k+1$ in Problem GVar$^h$ results in
-\begin{eqnarray*}
-	c( \tau^{-1}[v_{h}(t_{k+1})-v_{h}(t_{k})], \psi)+\frac{1}{2}a([v_{h}(t_{k+1})+v_{h}(t_{k})], \psi)+\frac{1}{2}b([u_{h}(t_{k+1})+u_{h}(t_{k})], \psi) \\
-	=\frac{1}{2}([f(t_{k+1})+f(t_{k})], \psi)_{X}+c(\rho_{k}, \psi)
-\end{eqnarray*}
-where $v_{h}(t)=u_{h}'(t)$ and
-\begin{eqnarray*}
-	\rho_{k}=\tau^{-1}[v_{h}(t_{k+1})-v_{h}(t_{k})]-\frac{1}{2}[v_{h}'(t_{k+1})+v_{h}'(t_{k})].
-\end{eqnarray*}
-
-The authors in \cite{BV13} denote the following errors
-\begin{eqnarray*}
-	e_{k}=u_{h}(t_{k})-u_{k} \ \ \ \ \textrm{ and } \ \ \ \ q_{k}=u_{h}'(t_{k})-v_{k}.
-\end{eqnarray*} In the authors approach, $e_0$ and $q_0$ are zero.
-
-\newtheorem*{DC_Lem3}{Lemma 2}
+\newtheorem*{DC_Lem3}{Lemma}
 \begin{DC_Lem3}
@@
 	\begin{eqnarray*}
-		\max\Vert e_{n}\Vert_{W}^{2}\leq 8T\tau\sum_{n=0}^{N-1}\Vert\epsilon_{n}\Vert_{W}^{2}+2\tau^{4}\Vert\rho_{0}\Vert_{W}^{2}+(8\tau^{2}+2\tau^{4}K_{a})\Vert\sigma_{0}\Vert_{W}^{2}.
+		\max\Vert e_{n}\Vert_{W}^{2}\leq KT\tau
 	\end{eqnarray*}
+	where $K$ depends on $u$, $u_h$ and their derivatives.
 \end{DC_Lem3}
 
-Using this lemma, \cite{BV13} proves the following error estimate.\\
-\textcolor{red}{*************************************}
+Using this lemma, \cite{BV13} prove the finial error estimate.
 
@@
 
-The parameter $\tau$ is some number in $(0,T)$. The constant $K_\alpha$ is the constant defined in assumption \textbf{A4} of Section 2.2.1.
+\subsection{Main result}
+The main result proving the convergence of the solution of the Galerkin
+Approximation is given in \cite{BV13} as follows.
+\newtheorem*{DC_Thm5}{Theorem 2}
+\begin{DC_Thm5}
+	{Main Result}\\
+	If $f\in C^{2}([0,T],X)$, then
+	\begin{eqnarray*}
+		\Vert u(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & K\tau^2
+	\end{eqnarray*}
+	for each $t\in(0,\ T)$.
+\end{DC_Thm5}
+
+The constant $K$ depend on $u_h$ and its derivatives.
 

### 2023-11-13 files/Chapter3/femconvergence.tex
appendix
chapter 3 fix

@@
 \begin{document}
-\section{Convergence of eigenvalues and eigenfunctions}
-In this section, the work in the textbook \cite[p.228-236]{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for clarity.\\
+\section{FEM comparison of eigenvalues and eigenfunctions}
 
@@
 
-The following eigenvalue is given in \cite{SF73}. It is important to note that the problem is limited to one-dimensional problems.
+The following eigenvalue is given in \cite{SF73}.
 
@@
 
+Galerkin approximation for \eqref{GEVP}:
+For $u^h \in S^h$ and $b(u^h, v) = \lambda^h(u^h,v)$ for all $v \in S^h$. For detail, see Chapter 5.
+
 \subsection{Preliminary theory and notation}
+In this section, the work in the textbook \cite[p.228-236]{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for clarity.
+
 Some theory is required before the main results can be proven. The theory is from \cite{SF73}.\\
@@
 
-From the textbook \cite{ORXX}, the following approximation theorem for finite elements is given verbatim:
+From the textbook \cite{OR76}, the following approximation theorem for finite elements is given verbatim:
 \newtheorem*{Interpolation}{Theorem}
@@
 For the requirements of this dissertation, this can be simplified with assumptions.
-The first assumption is a reiteration that the eigenvalue problem is one-dimensional.
 Another assumption is that the basis of $S^h$ consists of polynomials.
@@
 
-This will be referred to as the approximation theorem in this section.\\
+This will be referred to as the approximation theorem in this section.
 
@@
 
-Since $S^h$ is finite dimensional, the ordering of the eigenvalues still hold.
+Since $S^h$ is finite dimensional, the ordering of the eigenvalues remains valid.
 The eigenvalues in the space $S^h$ is denoted as $\lambda_i^h$ with corresponding normalized eigenfunction $u^h_i$ for $i = 1,2,...,m$.\\

### 2023-11-13 files/Chapter3/notes/Using energy methods to compare linear vibration models.tex
chapter 3 fix

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{natbib}

\begin{document}
\section*{Using energy methods to compare linear vibration models}

\textbf{Article: CVV18}\\

\subsection*{Notes:}

In section 2.4.2, we have the series solution for a general vibration problem.\\

Consider the partial sum $u^{N}(t) = \sum_{n=1}^{N} T_{n}(t)w_n$. Let
\begin{eqnarray*}
	u_0^{N} = \sum_{n=1}^{N} A^*_n w_n \ \ \textrm{ and } \ \ u_{1}^{N} =\sum_{n=1}^{N} B^*_n w_n
\end{eqnarray*} where $A^*_n = T_n(0)$ and $B^*_n = T'_n(0)$.\\

\textbf{Question:} When is the formal series solution valid with the initial conditions \[u(0) = u_0, \quad u'(1) = u_1 ?\]\\

The article CVV18 gives the answer to this question using energy norms. But what do we actually want to prove?\\

We have existence of solutions, but now we need to show that later on in the dissertation, we can compare the eigenvalues and eigenvectors of two different dimensional models (actually to compare the solutions of the two models and determine how `close' they are.).\\

If we can show that the series solution is valid with the initial conditions, then it should be possible to compare the two models. Because given a exact position and force applied, the series solution exists. (The models have been disturbed in the exact same way, and the series-solution is valid for this disturbance, hence they can be compared.)\\

Are we trying to prove that we'll be able to compare two different dimensional models (required later on in the dissertation)?\\
\end{document}

### 2023-11-13 files/Overview.tex
chapter 3 fix

@@
 The second part concerns the convergence of the eigenvalues and eigenfunctions of a vibration problem when applying the Finite Element Method.
-This theory is presented in the textbook \cite{SF97}\textcolor{red}{Nie goed genoeg vir dinamiese probleem}.
+This theory is presented in the textbook \cite{SF73}\textcolor{red}{Nie goed genoeg vir dinamiese probleem}.
 
@@
 
-The second part of the chapter considers work done in a textbook \cite{SF97} on eigenvalue problems for elliptic partial differential equations.
-The specific work discussed, covers the convergence of the eigenvalues and eigenfunctions of a one-dimensional vibration problem when applying the Finite Element Method.
+The second part of the chapter considers work done in a textbook \cite{SF73} on eigenvalue problems for elliptic partial differential equations.
+The specific work discussed, covers the convergence of the eigenvalues and eigenfunctions of a general vibration problem when applying the Finite Element Method.
 The authors consider a general eigenvalue problem.
@@
 
-The next section is a short discussion on a suspended beam model, from an important article \cite{SP06}.
+\textcolor{red}{*************Copy van chapter 6******************}
+
+The first section is a discussion of the article \cite{LVV09}.
+In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model.
+The authors compare the models by comparing the eigenvalues and eigenfunctions (see Chapter 2 on modal analysis).
+The two-dimensional model is more complex and there are eigenvalues that are not shared between the models.
+The authors use the mode shapes to match up the eigenvalues.
+The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues.
+The authors also consider different shapes of beams, from a short thick beam to a long slender beam.
+The results show that the models compare very well, even for a short and thick beam.
+As the beam gets more slender, the comparison improves.
+In this section some of the results of the article are discussed and replicated.
+
+\textcolor{red}{*******************************}
+
+The next section is a discussion on the article \cite{SP06}.
 In this article, the authors investigate the validity of the Timoshenko beam theory, by comparing the eigenvalues (natural frequencies) for a physical beam, to a Timoshenko beam and a three-dimensional beam using Finite Element Analysis.
-The authors report on an experiment with a vibrated a free-free beam measure the natural frequencies.
+The authors report on an experiment with forced vibration a free-free beam where the natural frequencies are measured.
 These emperical results are then compared to the theoretical results.
@@
 These results combine modal analysis and investigates at the behavior of the model.
-This section is an example of the usefullness of the Timoshenko beam theory.
 A similar model using realistic two- or three-dimensional model will be very challenging.
@@
 
+\textcolor{red}{*************hou voorlopig******************}
+
 The first section is a discussion of the article \cite{LVV09}.
@@
 In this section some of the results of the article are discussed and replicated.
+
+\textcolor{red}{*******************************}
 
@@
 The second result concerns the convergence of the eigenvalues and eigenfunctions with the Finite Element Method for one-dimensional vibration problems.
-This is a result form the textbook \cite{SF97}.**********
+This is a result form the textbook \cite{SF73}.**********
 
@@
 The second result concerns the convergence of the eigenvalue and eigenfunctions of a one-dimensional second order hyperbolic type problem when applying the Finite Element Method.
-This is presented in the textbook \cite{SF97}.
+This is presented in the textbook \cite{SF73}.
 

### 2023-11-15 files/Chapter5/3D_FEM.tex
symbols
table of symbols
Chapter 6

@@
 	\Omega = \left\{ x \in R^3 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} , \ -\frac{b}{2} \leq x_3 \leq \frac{b}{2}\right \}
-\end{eqnarray*}
+\end{eqnarray*} \label{sym:width}
 Let $\partial \Omega$ denote the boundary of the body. Divide $\partial \Omega$ into the six distinct flat surfaces as follows:
@@
 
-\subsection{System of ordinary differential equations}
+\subsection{System of ordinary differential equations}\label{3d_fem_g}
 Consider the following standard Finite Element Method matrices.

### 2023-11-15 files/Chapter5/PlateModel.tex
table of symbols
Chapter 6

@@
 \begin{eqnarray*}
-	\Omega = \left \{ x \in R_2 \ | \ 0 \leq x_1 \leq 1, \ 0 \leq x_2 \leq b \right \}.
+	\Omega = \left \{ x \in R^2 \ | \ 0 \leq x_1 \leq 1, \ 0 \leq x_2 \leq b \right \}.
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-	c(f,g) & = & h(f_1,g_1)_{\Omega} + I(f_2,g_2)_{R_2} \\
-	b^*(f,g) & = & b(f_2,g_2) + h(\nabla f_1 + f_2, \nabla g_1 + g_2)_{R_2}
+	c(f,g) & = & h(f_1,g_1)_{\Omega} + I(f_2,g_2)_{R^2} \\
+	b^*(f,g) & = & b(f_2,g_2) + h(\nabla f_1 + f_2, \nabla g_1 + g_2)_{R^2}
 \end{eqnarray*}
@@
 	(f_1,g_1)_{\Omega} & = & \iint_\Omega f_1 g_1 \ dA,\\
-	(f,g)_{R_2} & = & \iint_\Omega f \cdot g \ dA.
+	(f,g)_{R^2} & = & \iint_\Omega f \cdot g \ dA.
 \end{eqnarray*}
@@
 Denote the space $X = L^2(0,1)\times L^2(0,1)^2$ as a setting for Problem P-1V.
-A natural inner product for $X$ is $(f,g)_X = (f_1,g_1)_{\Omega} + (f_2,g_2)_{R_2}$.
+A natural inner product for $X$ is $(f,g)_X = (f_1,g_1)_{\Omega} + (f_2,g_2)_{R^2}$.
 Define $W$ as the space $X$ with the inner product $c$ and $V = V_1(0,1) \times V_2(0,1)$
@@
 
-\subsection{System of ordinary differential equations}
+\subsection{System of ordinary differential equations}\label{plate_fem_g}
 The standard FEM matrices $K_{11}$, $K_{12}$, $K_{21}$, $K_{22}$ and $M_F$ where presented in section \ref{ssec:2DFEM:DE}.
-Even though the definition of $R_2$ is different in section \ref{sec:FEM:2D}, the definition of the matrices are the same and are not repeated here.
+Even though the definition of $R^2$ is different in section \ref{sec:FEM:2D}, the definition of the matrices are the same and are not repeated here.
 

### 2023-11-15 files/Chapter6/Validity_2D.tex
summary
table of symbols
Chapter 6

@@
 \section{Validity of a Two-dimensional beam} \label{sec:validity-of-a-2d-beam}
-This section is an extention of section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and the article \cite{LVV09}.
-As seen in the previous section, the two-dimensional model does have some characteristics that are not related to beam-type problems.
-This is also true for the three-dimensional model.
 
-The results in this section will show that the three-dimensional model has a lot of non-beam type eigenvalues.
-It is due to this reason, the authors of \cite{LVV09} suggested to use the two-dimensional model as an intermediate step.
-The the previous section, the validity of a cantilever Timoshenko beam was investigated using a cantilever two-dimensional beam as a reference.
-In this section, the validity of a cantilever two-dimensional beam will be investigated using a cantilever three-dimensional beam as a reference.
+In section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed.
+In this article, the authors investigated the validity of a cantilever Timoshenko beam by comparing it to a cantilever two-dimensional beam.
+In this section, the article is extended and the validity of the cantilever two-dimensional model is investigated.
+
+As mentioned in the introduction of the chapter, a beam is a three-dimensional body and therefore a three-dimensional model is more realistic.
+However the authors of \cite{LVV09} mention that a direct comparison of the one and three-dimensional models will have complexities and they suggest using the two-dimensional model as an intermediate step.
+
+So in this section, the article \cite{LVV09} is extended and the validity of a cantilever two-dimensional beam model is investigated, using a cantilever three-dimensional model as a reference.
 
@@
 \subsection{Calculating the eigenvalues}
-Similar to calculating the eigenvalues of the two-dimensional beam, to calculate the eigenvalues of the three-dimensional beam, the Finite Element Method is used.
 In section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived.
-Section \ref{3dFEM_EP} gives the following eigenvalue problem for the three-dimensional beam:
+Similar to the two-dimensional case in \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the Finite Element Method is used to calculate the eigenvalues of the three-dimensional beam.
+The eigenvalue problem for both models have the same form, but different matrices.
 
-\subsubsection{Problem 2D-1E}
+\subsubsection{Problem 2D-1E and 3D-1E}
 Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
@@
 	K\bar{u} & = & M\lambda{\bar{u}},
-\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices for bi-cubic basis functions. The definition of the matrices are given in section \ref{sec:FEM:2D}.
+\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in section \ref{ssec:2DFEM:DE} for the Problem 2D-1E and section \ref{3d_fem_g} for Problem 3D-1E.
 
-\subsubsection{Problem 3D-1E}
-Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
-\begin{eqnarray}
-	K\bar{u} & = & M\lambda{\bar{u}},
-\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices for tri-cubic basis functions. The definition of the matrices are given in section \ref{sec:FEM:3D}.
-
-\subsubsection{Accuracy of the eigenvalues}
+\subsubsection{Accuracy of the eigenvalues of the three-dimensional model}
 Figure \ref{fig:conv_3d_eig} show the rate of convergence of the first 20 eigenvalues of Problem 3D-1E.
@@
     \begin{adjustbox}{center}
-        \includegraphics[scale=0.7]{Convergence.png}
+        \includegraphics[scale=0.7]{convergence3d.png}
     \end{adjustbox}
@@
 \end{figure}
-\textcolor{red}{Update this figure.}
 
-Similar to the two-dimensional case, the number of elements can be chosen so that at least the first 10 eigenvalues are accurate to 5 significant digits.
+Similar to the two-dimensional case, the number of elements can be chosen so that at least the first 20 eigenvalues are accurate to 4 significant digits.
+
+For the three-dimensional model, obtaining this level of accuracy can be difficult and computationally expensive.
+For the two-dimensional beam in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and the upcoming two-dimensional plate model in section \ref{sec:validity-of-a-plate} it is easier to get 5 significant digits of accuracy.
 
 \subsection{Comparing the mode shapes}
-The method to match up the eigenvalues remains the same as in the previous section.
-Since the three-dimensional model is more complex, there are more mode shapes that do no appear in the Timoshenko model or two-dimensional model.
-The focus remains on beam-type problems, so the mode shapes relating to beam type problems are most important.
+To be able to compare the eigenvalues, the mode shapes of the two models are compared to match up the eigenvalues of the two models.
+This is the same approach as in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}.
+
+As seen in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the two-dimensional model as eigenvalues and eigenvectors that are not related to beam type problems.
+This is also true for the three-dimensional model, and it has even more non-beam type eigenvalues.
+
+The focus of the investigation remains on beam type problems.
+Below are some examples of the mode shapes for beam type eigenvalues, mode shapes for non-beam type eigenvalues that are shared between the two and three-dimensional models and also mode shapes for non-beam type eigenvalues that are only present in the three-dimensional model.
 
@@
 			\end{minipage}
-			\caption{Mode shapes of the displacement $w$ with $h=1/20$.}
+			\caption{Mode shapes of the displacement $u$ with $h=1/20$.}
 			\label{fig:beam-2dv3d}
@@
 			\end{minipage}
-			\caption{Mode shapes of the displacement $w$ with $h=1/20$.}
+			\caption{Mode shapes of the displacement $u$ with $h=1/20$.}
 			\label{fig:nonbeam-2dv3d}
@@
 			\end{minipage}
-			\caption{Mode shapes of the displacement $w$ with $\alpha = 4800$.}
+			\caption{Mode shapes of the displacement $u$ with $h=1/20$.}
 
@@
 \subsection{Comparing the eigenvalues}
-The eigenvalues of the two models can now be compared. Recall from the introduction, that the two-dimensional and three-dimensional models have different paramaters.
+For a realistic comparison of the models, the parameters need to be chosen carefully.
+The parameters are $h$ representing the height of the beam and $b$ representing the width of the beam.
+The two-dimensional model does not have the width parameter.
 
-The two-dimensional model has the single parameter $h$ representing the height of the beam.
-The three-dimensional model has two parameters, $h$ and $b$, representing the height and width of the beam respectively.
-There are thus infinite possibilities for combinations of parameters that can be considered.
-However only a small number of combinations need to be considered to show that the two-dimensional model is a good approximation of the three-dimensional model.
+For $h$, the values used in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} will be used.
+These values covers a range of beam shapes from a short thick beam, to a long slender beam.
+two cases are selected that represents realistic cases.
+For a short and thick beam, consider $h = 1/5$ and for a long and slender beam, consider $h = 1/20$.
 
-For $h$, the values used in the previous section will be used.
-These values covers a range of beam shapes from a short fat beam, to a long slender beam with respect to the length to height ratio.
-For a short and fat beam, consider $h = 1/5$ and for a long and slender beam, consider $h = 1/20$.
+For the parameter $b$, two different cases will be considered.
+The first case is for $b \leq h$, and the $b > h$.
+The distinction of these two cases will become apparent in the results.
+It is important to note that the parameter $b$ will be expressed as a multiple of $h$.
 
-For $b$, two different cases will be considered. The first case is for $b <= h$, and the $b>h$. Incremental increase/decrease of $b$ will then be used to compare the models.
+All of the results will include all the eigenvalues shared between the two-models, including not beam type eigenvalues.
+The non-beam type eigenvalues will be highlighted in grey.
+The non-beam type eigenvalues that are not shared between the two models will be excluded from the results, but the numbering of the eigenvalues will be kept as if they were included.
 
-In all of the tables to follow, the non-beam type eigenvalues that are not present in the two-dimensional model are omitted.
-The beam and non-beam type eigenvalues that both models share are included, with the non-beam type eigenvalues highlighted in grey.
-
-\subsubsection*{Case $b < h$:}
-Intuitively, for this case the two-dimensional model should be a good approximation of the three-dimensional model when considering the shape and definition of the two-dimensional model.
-
-Table \ref{ab:2v3_1} below compares the eigenvalues of the models for a beam with a small length to height ratio of $h=1/5$ with decreasing values of $b$.
+\subsubsection*{Case $b \leq h$:}
+Table \ref{tab:2v3_1} below compares the eigenvalues of the models for a beam with a small length to height ratio of $h=1/5$ with decreasing values of $b$.
 
@@
 \FloatBarrier
-Table \ref{tab:2v3_1} show that the two-dimensional modes compares well to the three-dimensional beam for $b<=h$.
-As the width decreases, the two-dimensional model becomes a better approximation of the three-dimensional model.
-
-Table \ref{tab:2Dv3D_1_breakup} breaks up the maximum relative error for the beam type and non-beam type eigenvalues. The conclusion still holds.
+\label{sym:RE}
 
@@
 
-Table \ref{tab:2v3_2} below is similar to Table \ref{tab:2v3_1} but compares the eigenvalues of the models for a beam with a large length to height ratio of $h=1/20$ with decreasing values of $b$.
+Table \ref{tab:2v3_1} below compares the eigenvalues of the models for a beam with a larger length to height ratio of $h=1/20$ with decreasing values of $b$.
 
@@
 
-Table \ref{tab:2v3_2} shows that the two-dimensional beam compares very well to the three-dimensional beam.
-For this long and slender beam, the two-dimensional model is an exellent approximation, and the approximation improves as the width $b$ decreases.
-
-Table \ref{tab:2v3_2_split} breaks up the maximum relative error for the beam type and non-beam type eigenvalues. The conclusion still holds.
-
 \begin{table}[htbp]
@@
 
-From these results, it is clear that the two-dimensional model compares very well to the three-dimensional model for $b<=h$.
-The two-dimensional model is an excellent approximation for long and slender beams, and the approximation improves as the width $b$ decreases.
+Tables \ref{tab:2v3_1} and \ref{tab:2v3_2} show that the first 20 eigenvalues two-dimensional model compares very well to the matching eigenvalues three-dimensional beam for $b<=h$.
+As the width $b$ decreases, the two-dimensional model becomes a better approximation of the three-dimensional model.
+Also shown is that the slender beam with $h = 1/20$ compares better than the thick beam where $h = 1/5$, event though the case of $h=1/5$ is still a very good comparison.
 
-For applications, very small values of the width $b$ are not always realistic, however the cases $b = h$ and $b=1/2h$ are realistic or close to realistic.
-And for these cases, the two-dimensional model still compare very well.
+The tables also shows that the three-dimensional model has more non-beam type eigenvalues as the width $b$ decreases, as well as when the width $h$ decreases.This is different from the two-dimensional model as seen in \ref{sec:validity-of-a-cantilever-timoshenko-beam}.
+
+Tables \ref{tab:2Dv3D_1_breakup} and \ref{tab:2v3_2_split} breaks up the maximum relative error for the beam type and non-beam type eigenvalues.
+These tables confirm that the the beam type eigenvalues compare very well.
 
 \subsubsection*{Case $b > h$:}
-In this section, the case where $b > h$ is investigated. Similar to the previous case, the two cases of $h = 1/5$ and $h = 1/20 $ are considered, and the width $b$ is increased incrementally.
+First, the case is considered where $h = 1/5$.
 
-\textcolor{red}{Results for $h = 1/5$}
+\FloatBarrier
+\begin{table}[htbp]
+	\scalebox{.8}{
+	\makebox[\textwidth]{
+		\caption{Comparsion of Eigenvalues with $h = 1/5$, with increasing $b$ and $b > h$}
+		\begin{tabular}{|cc|cc|cc||cc|}
+			\hline
+			\multicolumn{8}{|c|}{Eigenvalues} \\
+			\hline
+			\hline
+			i     & {b = 2h} & i     & {b = 4h} & i     & {b = 8h} & j     & 2D \\
+			\hline
+			{1} & 0.12474 					& {1} & 0.12766 & {1} & 0.13036 & 1     & 0.12151 \\
+			{4} & 3.6088 					& {4} & 3.6297 & {5} & 3.7766 & 2     & 3.5460 \\
+			\rowcolor{lightgray}{6} & 7.8091 & {5} & 7.8389 & {9} & 8.9239 & 3     & 7.7311 \\
+			{8} & 20.466 					& {9} & 20.959 & {15} & 21.031 & 4     & 20.255 \\
+			{11} & 56.309					& {18} & 58.149 & {30} & 60.862 & 5     & 56.109 \\
+			\hline
+			\hline
+			\multicolumn{2}{|c|}{Max RE: \  2.6603\%} &\multicolumn{2}{c|}{Max RE: \ 5.0571\%}  & \multicolumn{2}{c|}{Max RE: \  15.428\%} & \multicolumn{2}{c|}{-} \\
+			\hline
+		\end{tabular}%
+		\label{tab:b>h}%
+	}}
+\end{table}
+\FloatBarrier
+
+\FloatBarrier
+\begin{table}[htbp]
+	\centering
+	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/5$}
+	\begin{tabular}{|c|ccc|}
+		\hline
+		\multicolumn{4}{|c|}{Maximum Relative Error} \\
+		\hline
+		\hline
+		& {b = 2h} & {b = 4h} & {b = 8h} \\
+		\hline
+		Beam Type & 2.6603 \% & 5.0571 \% & 8.4712 \% \\
+		Non-Beam Type & 1.0096 \% & 1.3948 \% & 15.428 \% \\
+		\hline
+	\end{tabular}%
+	\label{tab:b>h-split}%
+\end{table}%
+\FloatBarrier
 
@@
 		\end{tabular}%
-		\label{tab:b>h}%
+		\label{tab:b>h_20}%
 	}}
@@
 \FloatBarrier
-
-In Table \ref{tab:b>h}, $h = 1/20$, it is clear that even the beams with a larger lenght to width ratio, the two-dimensional model compares less well to the three-dimensional model as $b$ increases.
-
-Table \ref{tab:b>h-split}, again splits the beam and non-beam type maximum relative errors.
 
@@
 	\end{tabular}%
-	\label{tab:b>h-split}%
+	\label{tab:b>h-split_20}%
 \end{table}%
@@
 
-From these result it is clear the the two-dimensional beam compares less well to the three-dimensional beam if the width $b$ is `too much' larger than the height $h$.
+Tables \ref{tab:b>h} and \ref{tab:b>h_20} show that the two-dimensional model compares less well to the three-dimensional model when $b$ is too much larger than $h$.
+Tables \ref{tab:b>h-split} and \ref{tab:b>h-split_20} show that this is also true for the beam type eigenvalues.
 
-Overall the results show that there are cases where the two-dimensional model compares very well to the three-dimensional model and can be used as a substitute.
-The best case is when the beam has a large length to height ratio, and the width is equal to less than the height.
+For the case of $h=1/5$, it was also more difficult to obtain reliable eigenvalues using a numerical method.
 
-When the width gets larger than the height of the beam, the two-dimensional model starts to compare less well, and the comparison degrades as this difference increases further.
+\subsection{Conclusion}
 
-For practical applications, when cantilever body has a larger width than height, the use of a beam model must be brought into question.
-A different model, like a plate model might be a better choice.
-In the next section, the validity of the Reissner-Mindlin plate mode is investigated using the same methodology used so far in this chapter, and in \cite{LVV09}.
+These results gives a detailed overview of the validity of the cantilever two-dimensional beam compared to the cantilever three-dimensional beam.
+The results show that the two-dimensional beam model compares very well to the three-dimensional beam model for a large range of beam shapes.
+The results shown were chosen to represent realistic cases, and the results are similar for other cases.
+
+The overall conclusion is that the shape of the beam is very important.
+If the width $b$ is equal to or less than the height $h$, the two-dimensional beam model compares very well to the three-dimensional beam model.
+More so when the beam is slender, and less so when the beam is short and thick.
+
+When the width $b$ is larger than the height $h$, the two-dimensional beam the comparison degrades very quickly.
+This is true for both slender and short and thick beams, although with short and thick beams, it is more difficult to obtain reliable eigenvalues using a numerical method.
+
+For practical applications, if $b > h$ the use of a beam model must be brought into question.
+Other models such as a plate model will be better suited as it is a more realistic model.
+In the next section, the validity of the Reissner-Mindlin plate mode is investigated using the same method of this section.
 

### 2023-11-15 files/Chapter6/Validity_Plate.tex
Chapter 6

--- 2023-10-02 files/Chapter6/Validity_Plate.tex
@@
 
-In this section, the validity of a cantilever Reisner-Mindlin plate model is investigated.
-The idea of the model comes from the beam models in the previous section failing to approximate a cantilever elastic body with a width much larger than it's height.
-The process of determining the validity of the model follows the same ideas and methodology as in the previous sections, that is established in \cite{LVV09}.
+In the previous section, section \ref{sec:validity-of-a-2d-beam}, it was shown that for certain applications beam models might not be the appropriate choice.
+The specific application is for models where the body has a larger width than height.
+A suggestion would be a plate model.
 
-Similarly to how the Timoshenko beam theory improves on the Euler-Bernoulli beam theory by including the shear forces, so does the Reissner-Mindlin plate models improve on classic plate models.
-The Reissner-Mindlin plate model is a two-dimensional model, and therefore is it of value to investigate the validity of the model using a three-dimensional plate model as a reference.
+In this section, the validity of a cantilever Reissner-Mindlin plate model is investigated.
+This model is a two-dimensional model.
+So similar to the Timoshenko beam in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, it is of value to investigate the validity of the model using a three-dimensional plate model as a reference.
+
+The same method to validate the model will be used as in sections \ref{sec:validity-of-a-cantilever-timoshenko-beam} and \ref{sec:validity-of-a-2d-beam}.
+A cantilever three-dimensional plate model will be used as a reference, and the eigenvalues and mode shapes of the two models will be compared.
 
@@
 Form section \ref{ssec:P_Model:ModelProblems}, the cantilever Reissner-Mindlin plate model is given, and is referred to as Problem P-1.
-The three-dimensional model is the same as used in the previous section, and is referred to as Problem 3D-1 defined in section \ref{ssec:3D_Model:ModelProblems}.
+The three-dimensional model is the same as used in the previous section (section \ref{sec:validity-of-a-2d-beam}), and is referred to as Problem 3D-1 defined in section \ref{ssec:3D_Model:ModelProblems}.
 
@@
 For the plate model, the Finite Element Method is derived in \ref{sec:FEM:Plate} and for the three-dimensional model, the Finite Element Method is derived in \ref{sec:FEM:3D}.
+The eigenvalue problem for both models have the same form, but the matrices are different
 
-\subsubsection{Problem P-1E}
+\subsubsection{Problem 3D-1E and P-1E}
 Find a vector function $u$ and a number $\lambda$ such that
@@
 	K{u} & = & M\lambda{u}, 
-\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices for bi-cubic basis functions. The definition of the matrices are given in \ref{sec:FEM:Plate}.
-
-\subsubsection{Problem 3D-1E}
-Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
-\begin{eqnarray}
-	K\bar{u} & = & M\lambda{\bar{u}},
-\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices for tri-cubic basis functions. The definition of the matrices are given in section \ref{sec:FEM:3D}.
+\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in section \ref{3d_fem_g} for Problem 3D-1E and section \ref{plate_fem_g} for Problem P-1E.
 
@@
     \begin{adjustbox}{center}
-        \includegraphics[scale=0.7]{Convergence.png}
+        \includegraphics[scale=0.7]{Plate accuracy_no_legend.png}
     \end{adjustbox}
@@
 \end{figure}
-\textcolor{red}{Update this figure.}
 
-The number of elements can be chosen so that at least the first 10 eigenvalues are accurate to 5 significant digits.
+The number of elements can be chosen so that at least the first 20 eigenvalues are accurate to 5 significant digits.
 
 \subsection{Comparing the mode shapes}
-Similar to the previous sections, the mode shapes of the two models are compared, to be able to match up the eigenvalues.
+Similar to the previous sections (section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and section \ref{sec:validity-of-a-2d-beam}), the mode shapes of the two models are compared, to be able to match up the eigenvalues.
 
@@
 \end{figure}\label{fig:plate_mode_shapes}
-
 \FloatBarrier
@@
 \subsection{Comparing the eigenvalues}
-The eigenvalues of the two plate models can now be compared.
-For both the models, there are two parameters to consider for the height $h$ and width $b$.
-For realistic applications, the width of the plate is larger than its height.
+For a realistic comparison of the models, the parameters need to be chosen carefully. Both of the models have a width $h$ and a height $b$ parameter.
 
-For the comparisons, the investigation will consider a plate with small width $b = 0.25$, a plate of width equal to lenght $b = 1$ and a wide plate $1.75$.
-For each case, decreasing values of the height $h$ will be considered.
+Three main cases are considered.
+These cases are $b = 0.25$ for a narrow plate, $b = 1$ for a plate with equal lenght and width and $b = 1.75$ for a wide plate.
+For each of the cases, the thickness of the plate is varied.
+
+\textbf{Remark:} Note that the aim of the results is only to investigate the validity of the cantilever Reissner-Mindlin plate model, and not to investigate weather or not a plate model is more suited over beam model when applied to a body that has a larger width than height.
 
@@
 
-Table \ref{tab:Table_plate_1} shows that the narrow plate model compares well the to three-dimensional model.
-Also note that as the height $h$ decreases, the number of plate type eigenvalues within the first 20 eigenvalues increases.
-
-The next table, table \ref{tab:Table_plate_2}, shows the comparison of the eigenvalues for a plate of width equal to its length, $b = 1$.
-
 \FloatBarrier
@@
 
-Table \ref{tab:Table_plate_2} shows that the plate model compares slightly less well than the case where $b=0.25$, but the comparison is still very good.
-Again it seems that as $h$ decreases, the number of plate-type eigenvalues within the first 20 eigenvalues increases, and in this case there are more than the previous case.
+\FloatBarrier
+\begin{table}[htbp]
+	\scalebox{.8}{
+	\makebox[\textwidth]{
+		\caption{Comparison of eigenvalues with $b = 1.75$, with decreasing values of $h$.}
+		\begin{tabular}{|cccc||cccc||cccc||cccc|}
+			\hline
+			\multicolumn{16}{|c|}{Comparison of Eigenvalues, $b = 1.75$} \\
+			\hline\hline
+			\multicolumn{4}{|c||}{$h = 1/5$}       & \multicolumn{4}{c||}{$h =1/10$}      & \multicolumn{4}{c||}{$h = 1/20$}      & \multicolumn{4}{c|}{$h = 1/30$} \\
+			\hline
+			{i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} & {i} & {3D} & {j} & {Plate} \\
+			\hline
+			1 & 0.13062 & 1 & 0.12939 & 1 & 0.034245 & 1 & 0.034079 & 1 & 0.0086697 & 1 & 0.0086456 & 1 & 0.0038626 & 1 & 0.0038541\\
+			2 & 0.32016 & 2 & 0.31779 & 2 & 0.089872 & 2 & 0.089508 & 2 & 0.023395 & 2 & 0.023323 & 2 & 0.010507 & 2 & 0.010475\\
+			3 & 1.2496 & 3 & 1.2422 & 3 & 0.36964 & 3 & 0.36841 & 3 & 0.098072 & 3 & 0.097745 & 3 & 0.044239 & 3 & 0.044074\\
+			4 & 1.9808 &  & - & 4 & 1.2274 & 4 & 1.2188 & 4 & 0.33233 & 4 & 0.33118 & 4 & 0.15003 & 4 & 0.14964\\
+			5 & 3.7675 & 4 & 3.7086 & 5 & 1.352 & 5 & 1.3465 & 5 & 0.36764 & 5 & 0.36652 & 5 & 0.16657 & 5 & 0.16605\\
+			6 & 4.2021 & 5 & 4.1631 & 6 & 1.6994 & 6 & 1.6894 & 6 & 0.4647 & 6 & 0.4632 & 6 & 0.21059 & 6 & 0.21002\\
+			7 & 5.2022 & 6 & 5.1381 & 7 & 1.9763 &  & - & 7 & 0.79935 & 7 & 0.79606 & 7 & 0.3656 & 7 & 0.36423\\
+			8 & 7.6603 & 7 & 7.9399 & 8 & 2.8259 & 7 & 2.8076 & 8 & 1.2445 & 8 & 1.2411 & 8 & 0.56685 & 8 & 0.56529\\
+			9 & 8.0445 &  & - & 9 & 4.4507 & 8 & 4.4294 & 9 & 1.5708 & 9 & 1.563 & 9 & 0.72384 & 9 & 0.72032\\
+			10 & 9.0791 &  & - & 10 & 5.3923 & 9 & 5.3539 & 10 & 1.9739 &  & - & 10 & 1.1585 & 10 & 1.1545\\
+			11 & 10.135 &  & - & 11 & 7.6371 &  & 0 & 11 & 2.5137 & 10 & 2.5015 & 11 & 1.2513 & 11 & 1.2466\\
+			12 & 12.888 & 8 & 12.736 & 12 & 8.4707 & 10 & 8.3817 & 12 & 2.708 & 11 & 2.6947 & 12 & 1.4005 & 12 & 1.3927\\
+			13 & 14.506 & 9 & 14.302 & 13 & 9.0612 & 11 & 8.9704 & 13 & 3.0153 & 12 & 2.9984 & 13 & 1.4449 & 13 & 1.4393\\
+			14 & 14.892 &  & - & 14 & 9.0682 & & - & 14 & 3.137 & 13 & 3.1246 & 14 & 1.6806 & 14 & 1.6738\\
+			15 & 19.395 &  & - & 15 & 10.018 & 12 & 9.9347 & 15 & 3.6118 & 14 & 3.5928 & 15 & 1.973 &  & -\\
+			16 & 21.265 & 10 & 20.79 & 16 & 10.131 &  & - & 16 & 5.1287 & 15 & 5.0977 & 16 & 2.4081 & 15 & 2.3958\\
+			17 & 22.512 & 11 & 22.038 & 17 & 10.683 & 13 & 10.605 & 17 & 5.6368 & 16 & 5.6009 & 17 & 2.6419 & 16 & 2.6253\\
+			18 & 25.193 & 12 & 24.775 & 18 & 11.806 & 14 & 11.682 & 18 & 6.5069 & 17 & 6.4687 & 18 & 3.0386 & 17 & 3.0189\\
+			19 & 27.783 & 13 & 27.322 & 19 & 14.893 &  & - & 19 & 7.6243 & 18 & 7.6617 & 19 & 3.6563 & 18 & 3.6342\\
+			20 & 28.461 & 14 & 27.851 & 20 & 16.275 & 15 & 16.1 & 20 & 7.7152 &  & - & 20 & 4.3466 & 19 & 4.3267\\
+			\hline
+			\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{3.6499\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{1.0878\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{0.63674\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{0.64798\%} \\
+			\hline
+		\end{tabular}
+		\label{tab:Table_plate_3}
+	}}
+\end{table}
+\FloatBarrier
+
+Overall Tables \ref{tab:Table_plate_1}, \ref{tab:Table_plate_2} and \ref{tab:Table_plate_3} shows that the cantilever Reissner-Mindlin plate model compares very well to the three-dimensional plate.
+The maximum relative error is less than 3.65\% for all cases considered.
+
+There is less of a dramatic change of the comparison when the width of the plate is changed as with the beam model in section \ref{sec:validity-of-a-2d-beam}.
+This could be because the Reissner-Mindlin plate model does consider both the width and the height of the plate, while it is only a two-dimensional model.
+The two-dimensional beam model only considered the height of the beam, and not the width.
+
+Other cases not shown here have also been considered, and the results are similar to the ones shown here. They are therefore not included here, and only worth mentioning.
 

### 2023-11-16 files/Chapter3/femconvergence.tex
small fixes

@@
 \begin{document}
-\section{FEM comparison of eigenvalues and eigenfunctions}
+\section{FEM computation of eigenvalues and eigenfunctions}
 
@@
 Galerkin approximation for \eqref{GEVP}:
+
 For $u^h \in S^h$ and $b(u^h, v) = \lambda^h(u^h,v)$ for all $v \in S^h$. For detail, see Chapter 5.
@@
 \textbf{Rayleigh-Ritz Projection}\\
-If $u \in V$, then $Pu$ is its component in the subspace $S^h$.
+If $u \in V$, then $Pu$ is in the subspace $S^h$.
 \begin{equation*}

### 2023-11-17 files/Chapter4/Validity_Timo.tex
chapter 4
Chapter 4

--- 2023-11-07 files/Chapter6/Validity_Timo.tex
@@
 \begin{document}
-\section{Validity of a Cantilever Timoshenko beam} \label{sec:validity-of-a-cantilever-timoshenko-beam}
+\section{Validity of the model for a cantilever Timoshenko beam} \label{sec:validity-of-a-cantilever-timoshenko-beam}
 
@@
 These are the same as Problem T-2 and Problem 2D-1 that are defined in Chapter 1.
-The authors also look at the existence and uniqueness of the models, which is covered in Chapter 2 of this dissertation.
+The authors also look at the existence and uniqueness of solutions, which is covered in Chapter 2 of this dissertation.
 The authors then calculate and compare the eigenvalues and eigenfunctions, which will be discussed in this section.
@@
 
-As mentioned in the introduction, the height of the two beams can be set to be the same by considering the parameter $\alpha$ for the Timoshenko beam model and the parameter $h$ for the two-dimensional beam model.
+In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
+introduced. The paramater is given here again for convenience,
+\begin{eqnarray*}
+	\alpha = \frac{A\ell^2}{I}.
+\end{eqnarray*}
+
+The model is in a dimensionless form, therefore the length of the beam is $\ell = 1$.
+Since we assumed a square cross-section, the area of the cross-section can be calculated as $\displaystyle A = hb$.
+The area moment of inertia can also be calculated as $\displaystyle I = \frac{h^3b}{12}$.
+
+Substituting these values into the equation for $\alpha$ gives the following relationship between the height of the beam and the parameter $\alpha$,
+\begin{eqnarray}
+	\alpha & = & \frac{12}{h^2}, \label{eq:alpha-h-relationship}
+\end{eqnarray}
+or equivalently,
+\begin{eqnarray}
+	h & = & \sqrt{\frac{12}{\alpha}}. \label{eq:h-alpha-relationship}
+\end{eqnarray}
+
+These equations \eqref{eq:alpha-h-relationship} or \eqref{eq:h-alpha-relationship} describe the relationship between the height of the beam and the parameter $\alpha$.
+Using this relationship, the height of the beam model can be set by considering the value of $\alpha$.
 
@@
 Recall from the introduction, that the investigation is focussed on beam-type problems.
-The two-dimensional model is for an elastic body, and not specific to a beam, like the Timoshenko beam model.
-Therefore there are non-beam type behaviour that can be expected from the two-dimensional model.
-This is also be reflected in the eigenvalues of the two-dimensional model.
+The two-dimensional model is for an eigenvalue problem and and not specific to beam-type applications, like the Timoshenko beam model.
+Therefore there are non-beam type modes that can be expected from the two-dimensional model.
+This is also be reflected in the eigenvalues of the two-dimensional model and therefore eigenvalues irrelevant to beam-type problems exits.
 
@@
 In \cite{LVV09}, the authors compare the mode shapes of the two models, to match up the eigenvalues.
-Recall \textcolor{red}{****} that eigenvalues relating to the mode shapes similar to the mode shapes of the Timoshenko beam, are called beam type eigenvalues.
-The other eigenvalues are called non-beam type eigenvalues.
-This naming convention is used by the authors of \cite{LVV09}.
+Eigenvalues relating to the mode shapes similar to the mode shapes of the Timoshenko beam, are called beam-type eigenvalues.
+The other eigenvalues are called non-beam type eigenvalues by the authors.
 
@@
 For Timoshenko beam theory it is assumed that the cross-sections need not remain perpendicular to the neutral axis of the beam.
-The cross-sections however remain a straight line.\\
+The cross-sections however remain a straight line.
 
-For the two-dimensional beam, the shape of the cross-section can deform into a s-shape.
-This is explained in \cite{LVV09} and a similar figure in \cite{LVV09} is given here.
-This is a difference between the two models that are inherent to their definitions.\\
+For the two-dimensional beam, the shape of the cross-section can deform into a S-shape. This is explained in \cite{LVV09} and a similar figure in \cite{LVV09} is given here.
 
@@
 
-Similarly, figure {fig:phi} directly compares the angle of the cross-section of the Timoshenko beam and the two-dimensional beam.
+Similarly, figure \ref{fig:phi} directly compares the angle of the cross-section of the Timoshenko beam and the two-dimensional beam.
 The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s}.
@@
 These figures are examples that show how similar the mode shapes of the two models are.
-This specific example is for $\alpha = 4800$, which represents a long, narrow beam.
-The authors of \cite{LVV09} obtained similar results for $\alpha=300$, which represents a short and fat beam.
+This specific example is for $\alpha = 4800$, which represents a typical beam.
+The authors of \cite{LVV09} obtained similar results for $\alpha=300$, which represents a short and thick beam.
 
-\subsubsection{Remark:} Note that the overall shape is more important than the actual fit.
+\subsubsection{Remark:} Note that the overall shape is important.
 This is because any multiple of a eigenvector is still an eigenvector.
@@
 \subsection{Comparing the eigenvalues}
-Using this method of comparing the mode shapes, the eigenvalues can now be matched up and compared.
+Using this method of comparing the mode shapes, the eigenvalues can now be matched up and compared. In the tables, Timo refers to the Timoshenko beam and 2D refers to the two-dimensional beam.
 
@@
 
+\begin{table}[!ht]
+	\centering
+	\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
+	\begin{tabular}{|c|c|c||c|c|c|}
+		\hline
+		\multicolumn{3}{|c||}{Results from [LVV09]} & \multicolumn{3}{c|}{Dissertation} \\ \hline \hline
+		~ & 2D & Timo & ~ & 2D & Timo  \\ \hline
+		1 & 0.0317 & 0.0316 & 1 & 0.031713 & 0.031639  \\ 
+		2 & 1.14 & 1.14  & 2 & 1.1413 & 1.1365  \\ 
+		3 & 7.72 & - & 3 & 7.7161 & - \\ 
+		4 & 7.92 & 7.86 &  4 & 7.918 & 7.8617    \\ 
+		5 & 26.2 & 25.9 & 5 & 26.148 & 25.869   \\ 
+		6 & 60.8 & 59.9 & 6 & 60.816 & 59.946  \\ 
+		7 & 69.3 & - & 7 & 69.344 & -  \\ 
+		8 & 115 & 113 &  8 & 115.28 & 113.23   \\ 
+		9 & 192 & 188 &  9 & 191.57 & 187.55   \\ 
+		10 & 192 & - & 10 & 192.03 & -  \\ 
+		11 & 291 & 284 & 11 & 290.76 & 283.81   \\ \hline
+	\end{tabular}\label{Results_LVV09}
+\end{table}
+
+\begin{comment}
 \begin{table}[!ht]
@@
 \end{table}
+\end{comment}
 
@@
 
-This table shows that the eigenvalues compare very well.
+This table shows that the eigenvalues of the Timoshenko model and the two-dimensional model compare very well.
 The non-beam type eigenvalues are highlighted in grey.
-For a short fat beam ($\alpha = 300$), the maximum relative error for the first 20 two-dimensional eigenvalues is just over $3\%$, while for a long thin beam ($\alpha = 10800$), the maximum relative error is just over $1\%$.
+For a short thick beam ($\alpha = 300$), the maximum relative error for the first 20 two-dimensional eigenvalues is just over $3\%$, while for a long thin beam ($\alpha = 10800$), the maximum relative error is just over $1\%$.
 This shows that as the beam becomes longer and thinner, the Timoshenko beam is better approximation of the two-dimensional beam.
@@
 
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-        \begin{axis}[
-            title={Relative Error of Eigenvalues for Different Values of Alpha},
-            xlabel={Eigenvalue},
-            ylabel={Relative Error (\%)},
-            legend pos=north east,
-            grid=major,
-        ]
-        % Alpha = 300
-        \addplot coordinates {
-            (1,0.4875) (2,1.1106) (3,0) (4,1.7895) (5,2.4560) (6,0) (7,2.9630) (8,1.4324) (9,0) (10,2.9530)
-            (11,0.5735) (12,0) (13,0.8375) (14,0.5643) (15,0) (16,0.4757) (17,0) (18,1.1240) (19,0) (20,1.9740)
-        };
-        \addlegendentry{\(\alpha = 300\)}
-
-        % Alpha = 1200
-        \addplot coordinates {
-            (1,0.2337) (2,0.4217) (3,0) (4,0.7198) (5,1.0738) (6,1.4507) (7,0) (8,1.6244) (9,2.1618) (10,0)
-            (11,2.4560) (12,0) (13,2.7265) (14,0) (15,0) (16,5.2392) (17,0) (18,3.2823) (19,3.0864) (20,0)
-        };
-        \addlegendentry{\(\alpha = 1200\)}
-
-        % Alpha = 4800
-        \addplot coordinates {
-            (1,0.1125) (2,0.1661) (3,0.2574) (4,0) (5,0.3824) (6,0.5373) (7,0.7065) (8,0) (9,0.9950) (10,1.0740)
-            (11,0) (12,1.2680) (13,1.4507) (14,0) (15,0) (16,1.8120) (17,0) (18,1.9850) (19,2.1618) (20,0)
-        };
-        \addlegendentry{\(\alpha = 4800\)}
-
-        % Alpha = 10800
-        \addplot coordinates {
-            (1,0.0841) (2,0.1009) (3,0.1287) (4,0.2052) (5,0.3824) (6,0.2817) (7,0.3725) (8,0.4712) (9,0) (10,0.5940)
-            (11,0.7005) (12,0.8140) (13,0.9307) (14,0) (15,0) (16,1.8120) (17,1.2150) (18,1.9850) (19,2.1618) (20,2.8860)
-        };
-        \addlegendentry{\(\alpha = 10800\)}
-
-        \end{axis}
-    \end{tikzpicture}
-    \caption{Plot of the relative error for each eigenvalue and each value of \(\alpha\).}
-    \label{fig:relative_error_plot}
-\end{figure}
-
 \end{document}

### 2023-11-17 files/Chapter6/Validity_Timo.tex
Chapter 6
Chapter 4

@@
 \begin{document}
-\section{Validity of a Cantilever Timoshenko beam} \label{sec:validity-of-a-cantilever-timoshenko-beam}
+\section{Validity of a Cantilever Timoshenko beam} \label{sec:validity-of-a-cantilever-timoshenko-beam_chapter6}
 
@@
 
-Figure \ref{fig:compare:1D+2D} shows the two beams side-by-side.
+Figure \ref{fig:compare:1D+2D_chapter6} shows the two beams side-by-side.
 
@@
 	}
-\end{figure}\label{fig:compare:1D+2D}
+\end{figure}\label{fig:compare:1D+2D_chapter6}
 
@@
     \caption{Rate of convergence of the first 20 eigenvalues.}
-    \label{fig:conv_2d_eig}
+    \label{fig:conv_2d_eig_chapter6}
 \end{figure}
 
-Figure \ref{fig:conv_2d_eig} shows the rate of convergence of the first 20 eigenvalues of the two-dimensional beam. Each color represents a spesific eigenvalue.
+Figure \ref{fig:conv_2d_eig_chapter6} shows the rate of convergence of the first 20 eigenvalues of the two-dimensional beam. Each color represents a spesific eigenvalue.
 
@@
 				\subcaption{2D Beam Type - $\lambda_6 = 21.911$}
-				\label{fig:minipage2}
+				\label{fig:minipage2_chapter6}
 			\end{minipage}
@@
 				\subcaption{Timoshenko - $\lambda_5 = 21.794$}
-				\label{fig:minipage1}
+				\label{fig:minipage1_chapter6}
 			\end{minipage}
@@
 				\subcaption{2D Beam Type - $\lambda_7 = 45.711$}
-				\label{fig:minipage2}
+				\label{fig:minipage2_chapter6}
 			\end{minipage}
@@
 				\subcaption{Timoshenko - $\lambda_6 = 45.390$}
-				\label{fig:minipage1}
+				\label{fig:minipage1_chapter6}
 			\end{minipage}
@@
 				\subcaption{Non-Beam Type - $\lambda_4 = 7.7077$}
-				\label{fig:minipage2}
+				\label{fig:minipage2_chapter6}
 			\end{minipage}
@@
 				\subcaption{Non-Beam Type - $\lambda_8 = 69.344$}
-				\label{fig:minipage1}
+				\label{fig:minipage1_chapter6}
 			\end{minipage}
@@
 \end{tikzpicture}
-	\caption{S-shape deformation of the cross-section of the two-dimensional beam.}\label{fig:s}
+	\caption{S-shape deformation of the cross-section of the two-dimensional beam.}\label{fig:s_chapter6}
 \end{figure}
@@
 
-Note that figure \ref{fig:s} shows an exaggerated example of the deformation of a cross-section.
+Note that figure \ref{fig:s_chapter6} shows an exaggerated example of the deformation of a cross-section.
 The red line shows how the authors of \cite{LVV09} calculated the average rotation of a cross-section of the two-dimensional beam.
@@
 \subsubsection{Direct comparison of mode shapes}
-Figure \ref{fig:w} directly compares a mode shape of the Timoshenko beam to a mode shape of the two-dimensional beam.
+Figure \ref{fig:w_chapter6} directly compares a mode shape of the Timoshenko beam to a mode shape of the two-dimensional beam.
 For the two-dimensional model, the center line of the displacement of the beam is shown.
@@
 			\caption{Comparison of the displacement $w$ mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
-			\label{fig:w}}}
+			\label{fig:w_chapter6}}}
 \end{figure}
@@
 Similarly, figure {fig:phi} directly compares the angle of the cross-section of the Timoshenko beam and the two-dimensional beam.
-The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s}.
+The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s_chapter6}.
 
@@
 			\caption{Comparison of the angle $\phi$ (best fit for 2D Beam) mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
-			\label{fig:phi}}}
+			\label{fig:phi_chapter6}}}
 \end{figure}
@@
 This is because any multiple of a eigenvector is still an eigenvector.
-The mode shapes were specifically scaled to obtain figures \ref{fig:w} and \ref{fig:phi}.
+The mode shapes were specifically scaled to obtain figures \ref{fig:w_chapter6} and \ref{fig:phi_chapter6}.
 
@@
 		11 & 291 & 284 & 0.0241 & 11 & 290.76 & 283.81 &  0.023899  \\ \hline
-	\end{tabular}\label{Results_LVV09}
+	\end{tabular}\label{Results_LVV09_chapter6}
 \end{table}
@@
 	\end{tabular}%
-	\label{tab:Timo}%
+	\label{tab:Timo_chapter6}%
 }

### 2023-11-18 files/Chapter6/Introduction.tex
lvv09 into chapter 4
declaration

@@
 \section{Introduction}
-This chapter is an investigation into the validity of a cantilever Timoshenko beam model and a cantilever Reissner-Mindlin plate model.
-Validity in this context refers to how well the solutions of a model compare to the solutions of a more realistic, higher-dimensional model.
-The investigation and application of the models are restricted to beam-type and plate-type problems.
+Section \ref{sec:validity-of-a-cantilever-timoshenko-beam} is a discussion of the article \cite{LVV09}.
+In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
+In this chapter, the work of the article is extended to investigate the validity of the two-dimensional cantilever beam and a Reisner-Mindlin cantilever plate.
 
@@
 
-Section \ref{sec:validity-of-a-cantilever-timoshenko-beam} is a discussion of the article \cite{LVV09}.
-In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
-This is an investigation into the validity of the Timoshenko beam model.
-The results of the article are replicated and the conclusions are verified.
-This chapter also include extra results to expand and add to the results of the article.
-The results of this section are also used as a referencefor the rest of the chapter.
-
-Section 7.3 extends the work of \cite{LVV09} further to a comparison of a cantilever two-dimensional beam to a cantilever three-dimensional beam.
+Section 6.2 extends the work of \cite{LVV09} further to a comparison of a cantilever two-dimensional beam to a cantilever three-dimensional beam.
 It is an investigation into the validity of the two-dimensional beam model.
-This extention is suggested by the authors of \cite{LVV09}.
-Although a direct comparison between the Timoshenko beam and the three-dimensional beam is preffered, there are complexities involved that makes this comparison difficult.
+This extension is suggested by the authors of \cite{LVV09}.
+Although a direct comparison between the Timoshenko beam and the three-dimensional beam is proffered, there are complexities involved that makes this comparison difficult.
 Some of these complexities are discussed in more detail in the numerical results.
@@
 
-Section 7.4 extends the work of \cite{LVV09} further to plate models.
-This extention follows the same idea as the previous sections, and originates from non-beam type behaviour observed in the three-dimensional beam model in Section 7.3.
+Section 6.3 extends the work of \cite{LVV09} further to plate models.
+This extension follows the same idea as the previous sections, and originates from non-beam type behaviour observed in the three-dimensional beam model in Section 6.2.
 In this section, a cantilever two-dimensional Reisner-Mindlin plate model is compared to a cantilever three-dimensional plate model.
@@
 
-\subsection{Global parameters and configuration}
+\subsubsection{Global parameters and configuration}
 All the models in this dissertation are assumed to be made of the same isotropic material and have a square cross-section. The parameters are as follows:
@@
 We'll use $h$ to describe the height of the beams and plates, and $b$ to describe the width of the beams and plates.
+
+\end{document}
 
@@
 The Reisner-Mindlin plate model is the most different model compared to the rest of the models in this dissertation.
-The Reisner-Mindlin plate model is derived in section \ref{sec:reissnermindlinplate}.
+The Reisner-Mindlin plate model is derived in section \ref{sec:P_Model}.
 The model has two parameters, the height $h$ and the width $b$.
-
-\end{document}

### 2023-11-18 files/Chapter2/generalvibrationmodel.tex
small fixes
chapter 3

@@
 \begin{eqnarray}
-	c(\ddot{u}(t),v) + b(u(t),v) & = & (Q(t),v) \label{eq:existence:PreWV}
-\end{eqnarray} for each $v \in T[0,1]$.\\
+	c(\ddot{u}(t),v) + b(u(t),v) & = & (Q(t),v), \label{eq:existence:PreWV}
+\end{eqnarray} for each $v \in T[0,1]$.
 
-To apply the theory from \cite{VV02}, complete function spaces are required. It is known that $L^2(0,1)$ is a complete function space and hence $X$ is complete.\\
+To apply the theory from \cite{VV02}, complete function spaces are required. It is known that $L^2(0,1)$ is a complete function space and hence $X$ is complete.
 
@@
 It follows that $V(0,1)$ is complete and the product space {$V(0,1)\times V(0,1)$}, denoted by $V$, is complete.
-It is called the energy space.\\
+It is called the energy space.
 
@@
 \end{eqnarray*}
-for all $v\in V$. The initial conditions $u(0) = u_0$ and $\dot{u}(0)=u_1$ must be specified.\\
+for all $v\in V$. The initial conditions $u(0) = u_0$ and $\dot{u}(0)=u_1$ must be specified.
 
-The space X with the inner-product $c$ is denoted by $W$. $W$ is called the inertia space and in Section 2.3 it is shown that $c$ is an inner-product for $W$.\\
+The space X with the inner-product $c$ is denoted by $W$. $W$ is called the inertia space and in Section 2.3 it is shown that $c$ is an inner-product for $W$.
 
@@
 
-The following notation is important for the theory that follows.\\
+The following notation is important for the theory that follows.
 
@@
 	||(h^{-1} u(t+h)-u(t))-u'(t)||_Z \rightarrow 0.
-\end{eqnarray*} Then $u''$ is defined by $u'' = (u')'$.\\
+\end{eqnarray*} Then $u''$ is defined by $u'' = (u')'$.
 
@@
 
-\textbf{Remark} For Problem T-2, $Z$ can be $X$, $W$ or $V$.\\
+\textbf{Remark} For Problem T-2, $Z$ can be $X$, $W$ or $V$.
 
@@
 \end{eqnarray}
-while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\label{sym:a} \\
+while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\label{sym:a}
 
@@
 This theorem allows for a solution of the abstract variational problem Problem GVar, if the assumptions \textbf{A1}-\textbf{A4} is satisfied and the initial values $u_0$ and $u_1$ are admissible.
-It is not always easy to verify that \eqref{bilinear_equation} is satisfied.\\
+It is not always easy to verify that \eqref{bilinear_equation} is satisfied.
 
@@
 Semi-group theory is used in \cite{VV02} to investigate the solvability of Problem IVP and obtain a solution for Problem IVP.
-It is also important to mention that in \cite{VV02}, the authors provide the necessary result that shows the function $F$ is uniquely defined by $f$.\\
+It is also important to mention that in \cite{VV02}, the authors provide the necessary result that shows the function $F$ is uniquely defined by $f$.
 
@@
 It is proved in \cite{VV02} that equation \eqref{author_mapping} is uniquely solvable and hence $\Lambda$ is well defined.
-The proof remains unchanged as presented for $a$ identically zero.\\
+The proof remains unchanged as presented for $a$ identically zero.
 
@@
 From semigroup theory, it follows that $U(t) \in D(A)$ for each $t$.
-Therefore $u(t) \in E_b$ and $u'(t) \in V$ for each $t$.\\
+Therefore $u(t) \in E_b$ and $u'(t) \in V$ for each $t$.
 
@@
 In this section the theory of \cite{VV02} (presented in Section \ref{sec:existence:ExistenceAndUniqueness}) is applied to Problem T-2W.
-This is an continuation of the example from section \ref{sec:existence}.\\
+This is an continuation of the example from section \ref{sec:existence}.
 
@@
 
-To apply the theory, Problem T-2W must satisfy assumptions \textbf{A1}-\textbf{A4} and the initial values must be admissible. We must show that the assumptions are satisfied.\\
+To apply the theory, Problem T-2W must satisfy assumptions \textbf{A1}-\textbf{A4} and the initial values must be admissible. We must show that the assumptions are satisfied.
 
@@
 And since $C_0^\infty(0,1)$ is dense in $L_2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L_2(0,1)$.
-Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.\label{sym:Cinftyzero} \\
+Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.\label{sym:Cinftyzero}
 
@@
 	C_1||x||_X \leq ||x||_W \leq C_2||x||_X \label{C}
-\end{eqnarray} for all $x \in X$.\\
+\end{eqnarray} for all $x \in X$.
 
@@
 
-Chapter 6 is a discussion and extension of the article \cite{LVV09}.
+Sections 4.5 and 6.2 are a discussion and extension of the article \cite{LVV09}.
 This article compares a Timoshenko beam model to a two-dimensional beam model.
@@
 
-These comparisons are made in Chapter 4 and 6.
 Being able to express the solutions as valid series solutions, enable us to compare the different models by only considering the eigenvalues and eigenfunctions of the different models.

### 2023-11-18 files/Chapter3/dynamicconvergence.tex
small fixes
chapter 3

@@
 In this chapter, two important convergence results of the Finite Element Method
-(FEM) is discussed. The first result looks at the convergence of the Galerkin
+(FEM) are discussed. The first result looks at the convergence of the Galerkin
 approximation for second order hyperbolic type problems (or general vibation problems).
-The papers considered are \cite{BV13} and \cite{BSV17}.
+The papers considered for the first result are \cite{BV13} and \cite{BSV17}.
 The second result is from the textbook~\cite{SF73} and examines the
-convergence of eigenvalues and eigenfunctions for a one-dimensional vibration
+convergence of eigenvalues and eigenfunctions for a vibration
 problem, using the Finite Element Method.
@@
 
-In Section 2.2, Problem GVar is presented and identical to the problem in
-\cite{BV13}. The problem is repeated here for convenience.
+In Section 2.2 of this dissertation, Problem GVar is presented. It is identical to the problem in
+\cite{BV13}. For convenience, the problem is repeated here.
 
 \subsection{Formulation of the Galerkin approximation}
+Recall the spaces $V$, $W$ and $X$ from Section \ref{ssec:existence:VariationlApproach} where $V \subset W \subset X$.
+
 \subsubsection*{Problem GVar}
@@
 
-Recall from Chapter 2 that $V$ is the closure of the test function space $T$ in
-the Hilbert space $H$.
-
 \subsubsection*{Problem GVar$^h$}
@@
 \end{eqnarray}
-with the initial values $u_h(0)=u^h_{0}$ and $u'_h(0)=u^h_{1}$. The initial conditions $u^h_{0}$ and $u^h_{1}$ are projections of $u_0$ and $u_1$ into the finite dimensional space $S^h$.
-
-If the function $f$ is continuous, then Problem GVar$^h$ is equivalent to a
-system of second order differential equations. The following theorem from
-\cite{BV13} proves that if $f$ is continuous, then problem Problem GVar$^h$ has
-a unique solution.
-
-\newtheorem{DC_Thm2}{Theorem}
-\begin{DC_Thm2} \label{DC_THM2}
-	If $f \in C(J,X)$, then there exists a unique solution $u_h \in C^2(J)$ for Problem GVar$^h$ for each $u_0^h$ and $u_1^h$ in $S^h$. If $f = 0$ then $u_h \in C^2((-\infty, \infty))$.
-\end{DC_Thm2}
+with the initial values $u_h(0)=u^h_{0}$ and $u'_h(0)=u^h_{1}$. The initial conditions $u^h_{0}$ and $u^h_{1}$ are projections of $u_0$ and $u_1$ in the finite dimensional space $S^h$.
 
 \subsection{System of ordinary differential equations}
+Problem GVar$^h$ is equivalent to a system of second order differential equations.
+
 Consider the standard FEM matrices defined by
@@
 Using these matrices, Problem GVar$^h$ is rewritten as a system of ordinary
-differential equations denoted by Problem ODE. \subsubsection*{Problem ODE}
+differential equations denoted by Problem ODE.
+
+Recall that $u^h(t) = \sum_{k} \bar{u}_k(t)\phi_k$.
+
+\subsubsection*{Problem ODE}
 Find a function $\bar{u} \in S^h$ such that \label{sym:baru}
@@
 
-\subsection{Error estimates}\label{e_est}
-Under the assumptions \textbf{A1}-\textbf{A4} of Section 2 and continuity of $f$, there exists unique solutions for Problem GVar and Problem GVar$^h$.
-The next step is to show that the solution of Problem GVar$^h$ converges to the solution of Problem GVar.
-This is proven the main result of \cite{BV13}.
+The following theorem from \cite{BV13} proves that if $f$ is continuous, then problem Problem GVar$^h$ has a unique solution.
 
-Let $u$ be the solution of Problem GVar and $u^h$ be the solution of Problem GVar$^h$. The authors of \cite{BV13} define the following error,
-\begin{eqnarray}
-	e^h(t) = u(t) - u^h(t). \label{Error}
-\end{eqnarray}
-
-To simplify the proof, the problem is divided into a semi-discrete problem and a fully discrete problem. The two terms are investigated as seperate problems
-in \cite{BV13}.
+\newtheorem{DC_Thm2}{Theorem}
+\begin{DC_Thm2} \label{DC_THM2}
+	If $f \in C(J,X)$, then there exists a unique solution $u_h \in C^2(J)$ for Problem GVar$^h$ for each $u_0^h$ and $u_1^h$ in $S^h$. If $f = 0$ then $u_h \in C^2((-\infty, \infty))$.
+\end{DC_Thm2}
 
@@
 $u_h(t_k) = u_k^h$ for each $k$.
+A finite difference method is used to compute $u^h_k$ for each $k$.
+
+\subsection{Error estimates}\label{e_est}
+In this subsection we consider estimates for the error $u(t_k) - u^h_k$. To simplify the process, the error is divided into errors for the semi-discrete problem and the fully discrete problem.
+
+Under the assumptions \textbf{A1}-\textbf{A4} of Section 2 and continuity of $f$, there exists a unique solution for Problem GVar$^h$.
+The next step is to show that the solution of Problem GVar$^h$ converges to the solution of Problem GVar.
+
+Let $u$ be the solution of Problem GVar and $u^h$ be the solution of Problem GVar$^h$. The authors of \cite{BV13} define the following error,
+\begin{eqnarray}
+	e^h(t) = u(t) - u^h(t). \label{Error}
+\end{eqnarray}
 
@@
 
-\textbf{Fully discrete Galerkin finite element approximation}
+From Theorem 2 of the semi-discrete problem an error estimate for
+$e_k = [u(t_k)-u_h(t_k)]$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $[u_h(t_k) - u^h_k]$.
 
-From Theorem 2 of the semi-discrete problem an error estimate for
-$[u(t_k)-u_h(t_k)]$ with respect to the norm of $W$ was obtained. The authors
-of \cite{BV13} then proceed to obtain an error estimate for $[u_h(t_k) -
-			u^h_k]$. Since the dimension of $S^h$ is not fixed, the equivalence of norms
+Since the dimension of $S^h$ is not fixed, the equivalence of norms
 cannot be used, and therefore this error estimate for $[u_h(t_k) - u^h_k]$

### 2023-11-18 files/Chapter3/femconvergence.tex
chapter 3

@@
 \section{FEM computation of eigenvalues and eigenfunctions}
-
 Let $H$ be a Hilbert space with the inner product $(\cdot,\cdot)$ and induced norm $||\cdot||$.
 Let $V$ be a linear subspace of $H$, with inner product defined by the bilinear form $b(\cdot,\cdot)$.
-It is assumed that this bilinear form $b$ is symmetric.\\
+It is assumed that this bilinear form $b$ is symmetric.
 
-The following eigenvalue is given in \cite{SF73}.
+The following eigenvalue is considered in \cite{SF73}.
 
 \subsection{General eigenvalue problem}
-Find a function $u \in H$ and number $\lambda \in R$ such that
+\subsubsection*{Problem E}
+Find a vector $u \in V$ and number $\lambda \in R$ such that $u \neq 0$ and
 \begin{equation}
 	b(u,v) = \lambda (u,v) \label{GEVP}
-\end{equation} for some $v \in V$.
+\end{equation} for each $v \in V$.
 
-Galerkin approximation for \eqref{GEVP}:
+Consider the Galerkin approximation for \eqref{GEVP}:
+\subsubsection*{Problem $E_h$}
+Find $u^h \in S^h$ such that \[b(u^h, v) = \lambda^h(u^h,v) \textrm{ for all } v \in S^h.\]
 
-For $u^h \in S^h$ and $b(u^h, v) = \lambda^h(u^h,v)$ for all $v \in S^h$. For detail, see Chapter 5.
+For detail, see Chapter 5.
 
 \subsection{Preliminary theory and notation}
-In this section, the work in the textbook \cite[p.228-236]{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for clarity.
+In this section, the work in the textbook \cite[p.228-236]{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for greater clarity.
 
-Some theory is required before the main results can be proven. The theory is from \cite{SF73}.\\
+Some theory is required before the main results can be proven. The theory is from \cite{SF73}.
+
+\subsubsection*{Properties of eigenvalues}
+It is well known that the eigenvalues of a eigenvalue problem such as \eqref{GEVP} form an infinite sequence $(\lambda_i)$.
+Assume that the eigenvalues $\lambda_i$ can be ordered $\lambda_1 \leq \lambda_2 \leq \lambda_3 \leq ...$ and denote the corresponding eigenfunctions $u_i$.
+
+Since any multiple of a eigenfunction is still an eigenfunction, the eigenfunctions can be normalized so that $||u_i|| = 1$ for all $i$.
+
+Fix $m \in \mathbb{N}$.
+\label{sym:natural} Let $\left\{ \phi_i \in V | i = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
+Define $S^h := \text{span}\left\{\phi_i \in V | i = 1,2,...,m\right\}$.
+
+Since $S^h$ is finite dimensional, the ordering of the eigenvalues remains valid.
+The eigenvalues in the space $S^h$ is denoted as $\lambda_i^h$ with corresponding normalized eigenfunction $u^h_i$ for $i = 1,2,...,m$.
+
+The space $S^h$\label{sym:Sh1} is a finite dimensional subspace of $V$.
+Therefore any subspace of $S^h$ will also be a subspace of $V$.
+So the minmax principle applies and a lower bound for the eigenvalues can be found:
+\begin{equation}
+	\lambda_i \leq \lambda_i^h.
+\end{equation}
 
@@
 \textbf{Rayleigh-Ritz Projection}\\
-If $u \in V$, then $Pu$ is in the subspace $S^h$.
+If $u \in V$, then $Pu$ is its projection in the subspace $S^h$.
 \begin{equation*}
@@
 
-For the requirements of this dissertation, this can be simplified with assumptions.
-Another assumption is that the basis of $S^h$ consists of polynomials.
-With these assumptions, the semi-norm $|u|_H$ is equal to the norm $||u||$.
+For the requirements of this dissertation, this can be simplified with an assumption.
+The assumption is that the basis of $S^h$ consists of polynomials.
+With this assumptions, the semi-norm $|u|_H$ is equal to the norm $||u||$.
 This approximation theorem can be rewritten as
@@
 \subsubsection*{Properties of eigenvalues}
+It is well known that the eigenvalues of a eigenvalue problem such as \eqref{GEVP} form an infinite sequence $(\lambda_i)$.
+Assume that the eigenvalues $\lambda_i$ can be ordered $\lambda_1 \leq \lambda_2 \leq \lambda_3 \leq ...$ and denote the corresponding eigenfunctions $u_i$.
 
-It is well known that the eigenvalues of a eigenvalue problem such as \eqref{GEVP} form an infinite sequence $(\lambda_i)$.
-Assume that the eigenvalues $\lambda_i$ can be ordered $\lambda_1 \leq \lambda_2 \leq \lambda_3 \leq ...$ and denote the corresponding eigenfunctions $u_i$.\\
-
-Since any multiple of a eigenfunction is still an eigenfunction, the eigenfunctions can be normalized so that $||u_i|| = 1$ for all $i$.\\
+Since any multiple of a eigenfunction is still an eigenfunction, the eigenfunctions can be normalized so that $||u_i|| = 1$ for all $i$.
 
@@
 \label{sym:natural} Let $\left\{ \phi_i \in V | i = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
-Define $S^h := \text{span}\left\{\phi_i \in V | i = 1,2,...,m\right\}$.\\
+Define $S^h := \text{span}\left\{\phi_i \in V | i = 1,2,...,m\right\}$.
 
 Since $S^h$ is finite dimensional, the ordering of the eigenvalues remains valid.
-The eigenvalues in the space $S^h$ is denoted as $\lambda_i^h$ with corresponding normalized eigenfunction $u^h_i$ for $i = 1,2,...,m$.\\
+The eigenvalues in the space $S^h$ is denoted as $\lambda_i^h$ with corresponding normalized eigenfunction $u^h_i$ for $i = 1,2,...,m$.
 
@@
 \subsection{Estimating the eigenvalues.}
-Let $E_j \in V$ denote the eigenspace spanned by the exact eigenvalues $\left\{u_1,u_2,...,u_j \right\}$ for $j = 1,2,...,m$.\\
+Let $E_j \in V$ denote the eigenspace spanned by the exact eigenvectors $\left\{u_1,u_2,...,u_j \right\}$ for $j = 1,2,...,m$.
 
@@
 \end{equation*} The elements $Py_i$ are the projections of the eigenfunctions $u_i$ into the space $S^h$.
-These projections $Py_i$ are not necessarily equal to $u^h_j \in S^h$, but it can be shown that they are close.\\
+These projections $Py_i$ are not necessarily equal to $u^h_j \in S^h$, but it can be shown that they are close.
 
-Let $B_m = \left\{u \in e_m \ | \ ||u|| = 1 \right\}$ and define $\mu_m = \inf\left\{(Pu,Pu \ | \ u \in B_m)\right\}$.\\
+Let $B_m = \left\{u \in e_m \ | \ ||u|| = 1 \right\}$ and define $\mu_m = \inf\left\{(Pu,Pu \ | \ u \in B_m)\right\}$.
 
-The next steps in the textbook \cite{SF73} contains proofs with multiple results. In an attempt to better understand the results, the proofs are broken up into smaller proofs.\\
+The next steps in the textbook \cite{SF73} contains proofs with multiple results. In an attempt to better understand the results, the proofs are broken up into smaller proofs.
 
@@
 %\newpage
-In the textbook, the authors show that the eigenfunctions are orthogonal. But they do so using matrix representations of the eigenvalue problem. A different method can be used to show this.\\
+In the textbook, the authors show that the eigenfunctions are orthogonal. But they do so using matrix representations of the eigenvalue problem. A different method can be used to show this.
 
@@
 This corollary give a error estimate for the eigenvalues.
-To prove the convergence of the eigenvalues, it is necessary to prove that the error estimate $\sigma_{m}^{h}$ converges to zero as $h \rightarrow 0$.\\
+To prove the convergence of the eigenvalues, it is necessary to prove that the error estimate $\sigma_{m}^{h}$ converges to zero as $h \rightarrow 0$.
 
@@
 
-Proposition \ref{Prop_3} is a result given in \cite{SF73} without explaining how it is derived.\\
+Proposition \ref{Prop_3} is a result given in \cite{SF73} without explaining how it is derived.
 
-Introduce some new notation for ease of writing. For any $u \in E_{m}$, let $u^{*} = \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}$ where $u = \sum_{i=1}^{m} c_{i}u_{i}$.\\
+Introduce some new notation for ease of writing. For any $u \in E_{m}$, let $u^{*} = \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}$ where $u = \sum_{i=1}^{m} c_{i}u_{i}$.
 
@@
 \begin{proof}
-	Consider a set of basis functions $\Phi \subset S^h$ such that $\phi^(k) = 0$ for each $\phi \in \Phi$.\\
+	Consider a set of basis functions $\Phi \subset S^h$ such that $\phi^(k) = 0$ for each $\phi \in \Phi$.
 
-	From the Rayleigh-Ritz Projection, $Pu$ is the closest element in $S^h$ to $u$. In particular, $||u-Pu||\leq ||u-\Pi u||$, where $\Pi u$ is the interpolation of $u$ into $S^h$.\\
+	From the Rayleigh-Ritz Projection, $Pu$ is the closest element in $S^h$ to $u$. In particular, $||u-Pu||\leq ||u-\Pi u||$, where $\Pi u$ is the interpolation of $u$ into $S^h$.
 
@@
 
-The convergence of the eigenvalues are now proved.\\
+The convergence of the eigenvalues are now proved.
 
@@
 It has been shown that the eigenvalues converge to the exact eigenvalues as $h \rightarrow 0$.
-So from this result, it only remains to show that $( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$.\\
+So from this result, it only remains to show that $( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$.
 
@@
 In \cite{SF73}, the authors mention that for repeated eigenvalues, then the eigenfunctions can be chosen so that the main convergence results hold.
-This case is ommited in this dissertation.\\
+This case is ommited in this dissertation.
 
@@
 Therefore (\ref{CV1}) tells us that $Pu_{m}$ is close to $u_{m}^{h}$.
-The estimate for $Pu_{m} - u_{m}^{h}$ will follow from this result.\\
+The estimate for $Pu_{m} - u_{m}^{h}$ will follow from this result.
 
@@
 
-So again using the Approximation Theorem, it follows that $||u_{m} - \beta u_{m}^{h}||\leq Ch^{k}||u^{k}||$.\\
+So again using the Approximation Theorem, it follows that $||u_{m} - \beta u_{m}^{h}||\leq Ch^{k}||u^{k}||$.
 

### 2023-11-18 summary.tex
appendix

@@
 \begin{document}
+
+\textbf{Title} Finite element analysis of multi-dimensional and simplified models for beams and plates
+
+\textbf{Name} Rudi du Toit
+
+\textbf{Supervisor} Prof NFJ van Rensburg
+
+\textbf{Department} Mathematics and Applied Mathematics
+
+\textbf{Degree} MSc Applied Mathematics
+
 \begin{center}
@@
 An example of ongoing research using these theories is the study of suspension bridges.
-The articles \cite{McK99}, \cite{BOC20} are examples of mathematical studies while \cite{SV86} follows an engineering approach.\\
+The articles \cite{Mck99}, \cite{BOC20} are examples of mathematical studies while \cite{SV86} follows an engineering approach.\\
 

### 2023-11-19 files/Chapter3/femconvergence.tex
chapter 32

@@
 \subsubsection*{Problem $E_h$}
-Find $u^h \in S^h$ such that \[b(u^h, v) = \lambda^h(u^h,v) \textrm{ for all } v \in S^h.\]
+Find $u^h \in S^h$ such that $u^h \neq 0$ and \[b(u^h, v) = \lambda^h(u^h,v) \textrm{ for all } v \in S^h.\]
 
@@
 Fix $m \in \mathbb{N}$.
-\label{sym:natural} Let $\left\{ \phi_i \in V | i = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
-Define $S^h := \text{span}\left\{\phi_i \in V | i = 1,2,...,m\right\}$.
+Let $\left\{ \phi_i \in V | i = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
+Define $S^h := \text{span}\left\{\phi_i \in V | i = 1,2,...,m\right\}$ so that $S^h$ is a finite dimensional subspace of V.
+\label{sym:natural} \label{sym:Sh1}
 
-Since $S^h$ is finite dimensional, the ordering of the eigenvalues remains valid.
+The ordering of the eigenvalues remains valid in a finite dimensional space.
 The eigenvalues in the space $S^h$ is denoted as $\lambda_i^h$ with corresponding normalized eigenfunction $u^h_i$ for $i = 1,2,...,m$.
 
-The space $S^h$\label{sym:Sh1} is a finite dimensional subspace of $V$.
-Therefore any subspace of $S^h$ will also be a subspace of $V$.
-So the minmax principle applies and a lower bound for the eigenvalues can be found:
+Also any subspace of $S^h$ will also be a subspace of $V$. So the minmax principle applies and a lower bound for the eigenvalues can be found:
 \begin{equation}

### 2023-11-19 files/Chapter4/Validity_Timo.tex
chapter 4 and overview update

@@
 The authors start by presenting the models.
-These are the same as Problem T-2 and Problem 2D-1 that are defined in Chapter 1.
+These are the same as Problem T-2 and Problem 2D-1 that are defined in Chapter~1.
 The authors also look at the existence and uniqueness of solutions, which is covered in Chapter 2 of this dissertation.
@@
 In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
-introduced. The paramater is given here again for convenience,
+introduced. The paramater is given here again for convenience:
 \begin{eqnarray*}
@@
 The area moment of inertia can also be calculated as $\displaystyle I = \frac{h^3b}{12}$.
-
-Substituting these values into the equation for $\alpha$ gives the following relationship between the height of the beam and the parameter $\alpha$,
-\begin{eqnarray}
-	\alpha & = & \frac{12}{h^2}, \label{eq:alpha-h-relationship}
-\end{eqnarray}
+Substituting these values into the formula for $\alpha$ gives the following relationship between the height of the beam and the parameter $\alpha$: $\displaystyle \alpha = \frac{12}{h^2}$
 or equivalently,
@@
 \end{eqnarray}
-
-These equations \eqref{eq:alpha-h-relationship} or \eqref{eq:h-alpha-relationship} describe the relationship between the height of the beam and the parameter $\alpha$.
  Using this relationship, the height of the beam model can be set by considering the value of $\alpha$.
@@
 \subsubsection{Problem 2D-1E}
-Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
+Find a real number $\lambda$ and a vector $\bar{u} \in R^n$ such that
 \begin{eqnarray}
@@
 
-\subsubsection{Remark:} Note that the overall shape is important.
+\textbf{Remark:} Note that the overall shape is important.
 This is because any multiple of a eigenvector is still an eigenvector.

### 2023-11-23 files/Chapter3/dynamicconvergence.tex
chapter 3

@@
 \subsection{Formulation of the Galerkin approximation}
-Recall the spaces $V$, $W$ and $X$ from Section \ref{ssec:existence:VariationlApproach} where $V \subset W \subset X$.
+Recall the spaces $V$, $W$ and $X$ from Section \ref{sec:existence:ExistenceAndUniqueness} where $V \subset W \subset X$.
 
@@
 necessary. The structure of this section is as follows. First the Galerkin
-approximation is for Problem GVar is derived. Then a equivalent system of
+approximation for Problem GVar is derived. Then an equivalent system of
 ordinary differential equations is derived using the Finite Element Method.
@@
 
+\textcolor{red}{*******NEED COME BACK TO THIS**********}
+
+Let $S^h$ denote a finite dimensional subspace of $V$.
+
+\textcolor{red}{*******NEED COME BACK TO THIS**********}
+
 \subsubsection*{Problem GVar$^h$}
-Given a function $f: J \rightarrow X$, find a function $u_h \in C^2(J)$ such that for each $t\in J$
+Given a function $f: J \rightarrow X$, find a function $u_h \in C^2(J, S^h)$ such that for each $t\in J$
 \begin{eqnarray}
@@
 \subsection{System of ordinary differential equations}
-Problem GVar$^h$ is equivalent to a system of second order differential equations.
-
-Consider the standard FEM matrices defined by
+Problem GVar$^h$ is equivalent to a system of second order differential equations. Consider the standard FEM matrices defined by
 \begin{eqnarray*}
-	K_{ij} & = & b(\phi_j, \phi_i)\\
-	C_{ij} & = & a(\phi_j, \phi_i)\\
-	M_{ij} & = & c(\phi_j, \phi_i)\\
-	F_{i}(t) & = & b(f(t), \phi_i)
-\end{eqnarray*}
+	K_{ij} & = & b(\phi_j, \phi_i),\\
+	C_{ij} & = & a(\phi_j, \phi_i),\\
+	M_{ij} & = & c(\phi_j, \phi_i),\\
+	F_{i}(t) & = & c(f(t), \phi_i),
+\end{eqnarray*} where $\phi_i$ and $\phi_j$ are admissible basis functions.
 
@@
 
-Recall that $u^h(t) = \sum_{k} \bar{u}_k(t)\phi_k$.
+Recall that $u^h(t) = \sum_{k} u_k(t)\phi_k$ where $\bar{u}_k = \left( u_1(t), u_2(t), ...  , u_n(t)\right)$.
 
@@
 \begin{eqnarray}
-	M\bar{u}'' + C \bar{u}' + K\bar{u} = F(t) \ \ \ \textrm{ with } \bar{u}(0) = \bar{u}^h_0 \textrm{ and }  \bar{u}(1) = \bar{u}^h_1 \label{ODE}
+	M\bar{u}'' + C \bar{u}' + K\bar{u} = F(t) \ \ \ \textrm{ with } \bar{u}(0) = \bar{u}_0 \textrm{ and }  \bar{u}(1) = \bar{u}_1 \label{ODE}
 \end{eqnarray}
-The function $F$ is the interpolation of the function $f$ into the discrete space $S^h$.
 
@@
 \begin{DC_Prop3}
-	Suppose $M, K, C, F,\bar{u}^h_0$ and $\bar{u}^h_1$ are defined as above.
-Then, the function $u_{h}$ is a solution of Problem GVar$^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
+	Suppose $M, K, C, F,{u}_0$ and ${u}_1$ are defined as above. Then, the function $u_{h}$ is a solution of Problem GVar$^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
 \end{DC_Prop3}
@@
 Proposition 2 provides a link between the solution of Problem ODE and the
-solution of Problem GVar$^h$.
-
-The following theorem from \cite{BV13} proves that if $f$ is continuous, then problem Problem GVar$^h$ has a unique solution.
+solution of Problem GVar$^h$. Theorem 1 below follows.
 
@@
 \begin{DC_Thm2} \label{DC_THM2}
-	If $f \in C(J,X)$, then there exists a unique solution $u_h \in C^2(J)$ for Problem GVar$^h$ for each $u_0^h$ and $u_1^h$ in $S^h$. If $f = 0$ then $u_h \in C^2((-\infty, \infty))$.
+	If $f \in C(J,X)$, then there exists a unique solution $u_h \in C^2(J, S^h)$ for Problem GVar$^h$ for each $u_0^h$ and $u_1^h$ in $S^h$. If $f = 0$ then $u_h \in C^2((-\infty, \infty))$.
 \end{DC_Thm2}
+
+It is now required to find an approximation for the solution of $\bar{u}$ of Problem ODE.
 
@@
 $u_h(t_k) = u_k^h$ for each $k$.
-A finite difference method is used to compute $u^h_k$ for each $k$.
+(Recall that $u_h(t) = \sum u_i(t)\phi_i$.) A finite difference method is used to compute $u^h_k$ for each $k$.
 
@@
 
+\vspace*{40mm}
+
 The error $e$, can now be expressed as
@@
 From Theorem 2 of the semi-discrete problem an error estimate for
-$e_k = [u(t_k)-u_h(t_k)]$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $[u_h(t_k) - u^h_k]$.
+$e_k = [u(t_k)-u_h(t_k)]$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $e_k = [u_h(t_k) - u^h_k]$.
 
 Since the dimension of $S^h$ is not fixed, the equivalence of norms
-cannot be used, and therefore this error estimate for $[u_h(t_k) - u^h_k]$
+cannot be used, and therefore this error estimate for $e_k = [u_h(t_k) - u^h_k]$
 should also be with respect to the norm of $W$.
 
-A stability result is needed.
+A stability result is derived in \cite{BV13}.
 
@@
 \begin{DC_Lem3}
-	Stability
 	\begin{eqnarray*}
@@
 
-Using this lemma, \cite{BV13} prove the finial error estimate.
+Using this lemma, \cite{BV13} prove the error estimate.
+
+\newtheorem*{DC_Thm5_1}{Theorem 2}
+\begin{DC_Thm5_1}
+	{Main Result}\\
+	If $f\in C^{2}([0,T],X)$, then
+	\begin{eqnarray*}
+		\Vert u(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & K\tau^2
+	\end{eqnarray*}
+	for each $t\in(0,\ T)$.
+\end{DC_Thm5_1}
 

### 2023-11-23 files/Chapter3/femconvergence.tex
chapter 3

@@
 
-The following eigenvalue is considered in \cite{SF73}.
+\subsection{General eigenvalue problem}
 
-\subsection{General eigenvalue problem}
+The following eigenvalue problem is considered in \cite{SF73}.
+
 \subsubsection*{Problem E}
@@
 
-Consider the Galerkin approximation for \eqref{GEVP}:
-\subsubsection*{Problem $E_h$}
+Suppose $E^h$ is a finite dimensional subspace of $V$. Consider the Galerkin approximation for \eqref{GEVP}:
+\subsubsection*{Problem $E^h$}
 Find $u^h \in S^h$ such that $u^h \neq 0$ and \[b(u^h, v) = \lambda^h(u^h,v) \textrm{ for all } v \in S^h.\]
@@
 
+\textcolor{red}{********** need to move this ******************}
+
 \subsection{Preliminary theory and notation}
-In this section, the work in the textbook \cite[p.228-236]{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for greater clarity.
+In this section, the work in the textbook \cite{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for greater clarity.
 
 Some theory is required before the main results can be proven. The theory is from \cite{SF73}.
+
+\textcolor{red}{********** need to move this ******************}
+
+\subsubsection*{Properties of eigenvalues}
+It is well known that the eigenvalues of a eigenvalue problem such as \eqref{GEVP} form an infinite sequence of eigenvalues $(\lambda_i)$.
+Assume that the eigenvectors can be ordered in such a way that $\lambda_1 \leq \lambda_2 \leq \lambda_3 \leq ...$ where $\lambda_i$ are the corresponding eigenvalues.
+
+Since any multiple of a eigenfunction is still an eigenfunction, the eigenfunctions can be normalized so that $||u_i|| = 1$ for all $i$.
+
+Fix $m \in \mathbb{N}$.
+Let $\left\{ \phi_k \in V | k = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
+Define $S^h := \text{span}\left\{\phi_k \in V | k = 1,2,...,m\right\}$ so that $S^h$ is a finite dimensional subspace of V.
+\label{sym:natural} \label{sym:Sh1}
+
+Problem $E^h$ can be written as a matrix eigenvalue problem,
+\begin{eqnarray*}
+	\lambda^nM\bar{u}_n = K\bar{u}_n.
+\end{eqnarray*} The pair $(\lambda^n, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$.
+
+In a finite-dimensional subspace, the ordering of vectors is preserved as it is in the original space.
+Denote the normalized eigenvectors in the space $S^h$ as $u^h_k$ with corresponding eigenvalues $\lambda^h_i$ for $k = 1,2,...,m$.
+
+Also any subspace of $S^h$ will also be a subspace of $V$. So the minmax principle applies and a lower bound for the eigenvalues can be found:
+\begin{equation}
+	\lambda_i \leq \lambda_i^h.
+\end{equation}
 
@@
 Fix $m \in \mathbb{N}$.
-Let $\left\{ \phi_i \in V | i = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
-Define $S^h := \text{span}\left\{\phi_i \in V | i = 1,2,...,m\right\}$ so that $S^h$ is a finite dimensional subspace of V.
+Let $\left\{ \phi_k \in V | k = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
+Define $S^h := \text{span}\left\{\phi_k \in V | k = 1,2,...,m\right\}$ so that $S^h$ is a finite dimensional subspace of V.
 \label{sym:natural} \label{sym:Sh1}
@@
 
+\subsection{Estimating the eigenvalues.}
 \textbf{Rayleigh quotient}
@@
 
-\subsubsection*{Properties of eigenvalues}
-It is well known that the eigenvalues of a eigenvalue problem such as \eqref{GEVP} form an infinite sequence $(\lambda_i)$.
-Assume that the eigenvalues $\lambda_i$ can be ordered $\lambda_1 \leq \lambda_2 \leq \lambda_3 \leq ...$ and denote the corresponding eigenfunctions $u_i$.
-
-Since any multiple of a eigenfunction is still an eigenfunction, the eigenfunctions can be normalized so that $||u_i|| = 1$ for all $i$.
-
-Fix $m \in \mathbb{N}$.
-Let $\left\{ \phi_i \in V | i = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
-Define $S^h := \text{span}\left\{\phi_i \in V | i = 1,2,...,m\right\}$ so that $S^h$ is a finite dimensional subspace of V.
-\label{sym:natural} \label{sym:Sh1}
-
-The ordering of the eigenvalues remains valid in a finite dimensional space.
-The eigenvalues in the space $S^h$ is denoted as $\lambda_i^h$ with corresponding normalized eigenfunction $u^h_i$ for $i = 1,2,...,m$.
-
-Also any subspace of $S^h$ will also be a subspace of $V$. So the minmax principle applies and a lower bound for the eigenvalues can be found:
-\begin{equation}
-	\lambda_i \leq \lambda_i^h.
-\end{equation}
-
-\subsection{Estimating the eigenvalues.}
 Let $E_j \in V$ denote the eigenspace spanned by the exact eigenvectors $\left\{u_1,u_2,...,u_j \right\}$ for $j = 1,2,...,m$.

### 2023-11-23 files/Chapter3/femconvergence.tex
chapter 4

@@
 
-\subsection{Estimating the eigenvalues.}
+\subsection{Estimating the eigenvalues.} \label{sec:est}
 \textbf{Rayleigh quotient}
-\begin{equation*}
-	R(v) = \frac{b(v,v)}{(v,v)} \ \text { for } v \in V.
-\end{equation*} \label{sym:Rayleigh}
+\begin{equation}
+	R(v) = \frac{b(v,v)}{c(v,v)} \ \text { for } v \in V. \label{Rayleigh}
+\end{equation} \label{sym:Rayleigh}
 
@@
 
-Then consider the subspace $S_j$ where
+Then consider the subspace $S_j$ of $S^h$ where
 \begin{equation*}
@@
 \end{equation*} The elements $Py_i$ are the projections of the eigenfunctions $u_i$ into the space $S^h$.
-These projections $Py_i$ are not necessarily equal to $u^h_j \in S^h$, but it can be shown that they are close.
+These projections $Py_i$ are not necessarily equal to $u^h_j \in S^h$, but it can be close.
+The situation is not simple.
+It is possible that $S_j$ is not a subspace of $S^h$.
+Assume that the dimension of $S^h$ is large enough
+
+\vspace{20mm}
+
+(It is possible that $Py_k = 0$ for large $k$.)
 
@@
 
-The next steps in the textbook \cite{SF73} contains proofs with multiple results. In an attempt to better understand the results, the proofs are broken up into smaller proofs.
-
 The first step to obtain estimates for the eigenvalues, it to show that the elements of $B_m$ are linearly independent.
+In the first part we follow the approach in \cite{Zie2000} (A Computable Spectral Theorem - Martin Ziegler - 2000).
+The author introduced the quantity $\mu_m$.
 
@@
 
-\newtheorem{Prop_2}[Prop_1]{Proposition} \label{Prop_2}
+ Recall the definition of the Rayleigh quotient R in \eqref{Rayleigh}.
+
+\newtheorem{Prop_2}[Prop_1]{Proposition}
 \begin{Prop_2}
-	$\lambda^{h}_{m} \leq \max R(Pu) \ \text{ for } u \in B_{m}$\\
+	\label{Prop_2}
+	$\lambda^{h}_{m} \leq \max R(Pu) \ \text{ for } u \in B_{m}$
 \end{Prop_2}
@@
 
-	Take an arbitrary nonzero $v \in S_m$. Then there exists a $Py \in E_m$ such that $v = Py$.\\
+	Take an arbitrary nonzero $v \in S_m$. Then there exists a $Py \in E_m$ such that $v = Py$.
 
@@
 Then there exists a $u \in E_{m}$ such that $Py = v$.
-This $Py$ is the projection into $S_m$ of some $u \in E_m$ (which is also $\displaystyle \frac{1}{||u||}u \in B_m$).\\
+This $Py$ is the projection into $S_m$ of some $u \in E_m$ (which is also $\displaystyle \frac{1}{||u||}u \in B_m$).
 
-	Next a linearity property for $R$ can be proven. 
-	\begin{eqnarray*}
-	R(\frac{1}{||u||}u) &=& \frac{b\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)}{\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)},\\
-						&=& \frac{b(u,u)}{(u,u)},\\
-						&=& R(u).
-	\end{eqnarray*}
+	Next we show that $R(||u||^{-1}u) = R(u)$:
+
+	\[ \frac{b\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)}{c\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)} = \frac{b(u,u)}{c(u,u)} = R(u). \]
+
 	So finally,
@@
 \begin{eqnarray*}
-	b(u_{i},u_{i}) &=& \lambda_{i}( u_{i},u_{i}),\\
-	b(u_{j},u_{j}) &=& \lambda_{j}( u_{j},u_{j}).
+	b(u_{i},u_{i}) &=& \lambda_{i}c(u_{i},u_{i}),\\
+	b(u_{j},u_{j}) &=& \lambda_{j}c(u_{j},u_{j}).
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-	b(u_{i},u_{j}) &=& \lambda_{i}( u_{i},u_{j}),\\
-	b(u_{j},u_{i}) &=& \lambda_{j}( u_{j},u_{i}).
+	b(u_{i},u_{j}) &=& \lambda_{i}c(u_{i},u_{j}),\\
+	b(u_{j},u_{i}) &=& \lambda_{j}c(u_{j},u_{i}).
 \end{eqnarray*}
-Then using the symmetry of $b(\cdot,\cdot)$ and $( \cdot, \cdot )$, and subtracting,
+Then using the symmetry of $b(\cdot,\cdot)$ and $c( \cdot, \cdot )$, and subtracting,
 \begin{eqnarray*}
-	0 &=& (\lambda_{i} - \lambda_{j})( u_{i}, u_{j} )
+	0 &=& (\lambda_{i} - \lambda_{j})c( u_{i}, u_{j} )
 \end{eqnarray*}
-So if $i \neq j$ then $\lambda_{i} \neq \lambda_{j}$.\\
+So if $i \neq j$ then $\lambda_{i} \neq \lambda_{j}$. Therefore $u_{i}$ and $u_{j}$ must be orthogonal.
 
-Therefore $u_{i}$ and $u_{j}$ must be orthogonal. And as mentioned previously, $||u|| = 1$.
+And as mentioned previously, $||u|| = 1$.
 
-\newtheorem{Lem_1}{Lemma} \label{Lem_1}
+The next steps in the textbook \cite{SF73} contains proofs with multiple results. In an attempt to better understand the results, the proofs are broken up into smaller proofs.
+
+\newtheorem{Lem_1}{Lemma} 
 \begin{Lem_1}
-	$\displaystyle \lambda_{m}^{h} \leq \frac{\lambda_{m}}{u_{m}^{h}}$
+	\label{Lem_1}
+	$\displaystyle \lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}$
 \end{Lem_1}
@@
 	\begin{eqnarray*}
-		R(Pu) &=& \frac{b(Pu,Pu)}{(Pu,Pu)},\\
+		R(Pu) &=& \frac{b(Pu,Pu)}{c(Pu,Pu)},\\
 			&=& \frac{b(Pu,Pu)}{||Pu||^{2}},\\
@@
 
-Following Lemma \ref{Lem_1}, and since $\lambda_{i}^{h} \geq \lambda_{i}$ it follows that $0 < \mu_{m}^{h} \leq 1$. It is now possible to define the error estimate as given in \cite{SF73}:
+Following Lemma \ref{Lem_1}, and since $\lambda_{i}^{h} \geq \lambda_{i}$ it follows that $0 < \mu_{m}^{h} \leq 1$. It is now possible to define the `error bound' in \cite{SF73}:
 \begin{eqnarray*}
@@
 
-\newtheorem{Cor_1}{Corollary}
+\newtheorem{Cor_1}{Proposition}
 \begin{Cor_1}
@@
 	Starting with the result of Lemma \ref{Lem_1},
-	\begin{eqnarray*}
-		\lambda_{m}^{h} & \leq & \frac{\lambda_{m}}{\mu_{m}^{h}}\\
-		\lambda_{m}^{h}\mu_{m}^{h}& \leq & \lambda_{m} \\
-		-\lambda_{m}& \leq & -\lambda_{m}^{h}\mu_{m}^{h} \\
-		\lambda_{m}^{h} -\lambda_{m}& \leq & \lambda_{m}^{h} -\lambda_{m}^{h}\mu_{m}^{h}\\
-		\lambda_{m}^{h} -\lambda_{m}& \leq & \lambda_{m}^{h}\sigma_{m}^{h}
-		\end{eqnarray*}
+	\begin{align*}
+		\lambda_{m}^{h} &\leq \frac{\lambda_{m}}{\mu_{m}^{h}} \\
+		\lambda_{m}^{h}\mu_{m}^{h} &\leq \lambda_{m} \\
+		-\lambda_{m} &\leq -\lambda_{m}^{h}\mu_{m}^{h} \\
+		\lambda_{m}^{h} - \lambda_{m} &\leq \lambda_{m}^{h} - \lambda_{m}^{h}\mu_{m}^{h} \\
+		\lambda_{m}^{h} - \lambda_{m} &\leq \lambda_{m}^{h}\sigma_{m}^{h}
+	\end{align*}
 \end{proof}
 
-This corollary give a error estimate for the eigenvalues.
+This result gives an error estimate for the eigenvalues.
 To prove the convergence of the eigenvalues, it is necessary to prove that the error estimate $\sigma_{m}^{h}$ converges to zero as $h \rightarrow 0$.
 
-\newtheorem{Prop_3}[Prop_1]{Proposition} \label{Prop_3}
+\newtheorem{Prop_3}[Prop_1]{Proposition} 
 \begin{Prop_3}
+	\label{Prop_3}
 	$\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}$
@@
 	\begin{eqnarray*}
-		||u - Pu||^{2} &=& ( u - Pu, u - Pu ), \\
-						&=& ( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ), \\
-						&=& 2( u, u ) - 2 ( u, Pu ) + ( Pu, Pu ) - ( u, u ),\\
-						&=& 2( u, u - Pu ) + ( Pu, Pu ) - ( u, u ).\\
+		||u - Pu||^{2} &=& c( u - Pu, u - Pu ), \\
+						&=& c( u, u ) - 2 c( u, Pu ) + c( Pu, Pu ), \\
+						&=& 2c( u, u ) - 2 c( u, Pu ) + c( Pu, Pu ) - c( u, u ),\\
+						&=& 2c( u, u - Pu ) + c( Pu, Pu ) - c( u, u ).\\
 	\end{eqnarray*}
-	Rewriting gives
+	consequently
 	\begin{eqnarray*}
-		( u, u ) - ( Pu, Pu )  & = & 2( u, u - Pu ) - ||u - Pu||^{2}.
+		c( u, u ) - c( Pu, Pu )  & = & 2c( u, u - Pu ) - ||u - Pu||^{2}.
 	\end{eqnarray*}
 
-	Since $u \in B_{m}$, $||u||^{2} = 1$. So then
+	Since $u \in B_{m}$, $||u||^{2} = 1$ and hence
 	\begin{eqnarray*}
-		1 - ||Pu||^{2}  & = & 2( u, u - Pu ) - ||u - Pu||^{2}.
+		1 - ||Pu||^{2}  & = & 2c( u, u - Pu ) - ||u - Pu||^{2}.
 	\end{eqnarray*}
@@
 	\begin{eqnarray*}
-	\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}
+	\sigma_{m}^{h} = \max\left\{ 2c( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}
 	\end{eqnarray*}
@@
 
-\newtheorem{Prop_4}[Prop_1]{Proposition} \label{Prop_4}
+\newtheorem{Prop_4}[Prop_1]{Proposition} 
 \begin{Prop_4}
+	\label{Prop_4}
 	For any $u \in E_{m}$
 		\begin{eqnarray*}
-		( u, u - Pu ) = b(u^{*} - Pu^{*}, u -Pu)
+		c( u, u - Pu ) = b(u^{*} - Pu^{*}, u -Pu)
 		\end{eqnarray*}
@@
 	\begin{eqnarray*}
-	\lambda_{i}( u_{i},u-Pu ) &=&  b(u_{i}, u-Pu),\\
+	\lambda_{i}c( u_{i},u-Pu ) &=&  b(u_{i}, u-Pu),\\
 								&=& b(u_{i}, u-Pu) - b(u-Pu,Pu_{i}) \ \textrm{ (Rayleigh-Ritz Projection)},\\
@@
 	\begin{eqnarray*}
-	\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}\lambda_{i}( u_{i},u-Pu ) &=& \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}b(u_{i}-Pu_{i}, u-Pu),\\
+	\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}\lambda_{i}c( u_{i},u-Pu ) &=& \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}b(u_{i}-Pu_{i}, u-Pu),\\
 								&=& b(\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}-\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}Pu_{i}, u-Pu),\\
@@
 	\end{eqnarray*}
-	Therefore $( u,u-Pu ) = b(u^{*}-Pu^{*}, u-Pu)$.
+	Therefore $c( u,u-Pu ) = b(u^{*}-Pu^{*}, u-Pu)$.
 \end{proof}
@@
 	\begin{eqnarray*}
-		\sigma_{m}^{h} & = & \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}, \\
-					& \leq & \max\left\{ 2( u,u-Pu ) \ | \ u \in B_{m} \right\}. \\
+		\sigma_{m}^{h} & = & \max\left\{ 2c( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}, \\
+					& \leq & \max\left\{ 2c( u,u-Pu ) \ | \ u \in B_{m} \right\}. \\
 	\end{eqnarray*}
@@
 
-	From the Approximation Theorem, is follows that
+	From the Approximation Theorem given at the beginning of section \ref{sec:est}, is follows that
 	\begin{eqnarray*}
@@
 
-\newtheorem{Lem_3}[Lem_1]{Lemma} \label{Lem_3}
+\newtheorem{Lem_3}[Lem_1]{Lemma} 
 \begin{Lem_3}
+	\label{Lem_3}
 	For any $\epsilon >0$ there exists a $\delta > 0$ such that
@@
 
-\newtheorem{Lem_4}[Lem_1]{Lemma} \label{Lem_4}
+\newtheorem{Lem_4}[Lem_1]{Lemma} 
 \begin{Lem_4}
+	\label{Lem_4}
 	There exists a $\delta > 0$ such that for $h < \delta$
@@
 
-	So $\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}$.
+ 	Therefore $\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}$.
 \end{proof}
@@
 	\begin{eqnarray*}
-		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& \lambda_{m}( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h} ) + \lambda_{m}^{h} - \lambda_{m}
+		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& \lambda_{m}c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h} ) + \lambda_{m}^{h} - \lambda_{m}
 		\end{eqnarray*}
@@
 		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& b(u_{m},u_{m}) - 2b(u_{m},u^{h}_{m}) + b(u^{h}_{m},u^{h}_{m}) \\
-										&=& \lambda_{m} ( u_{m}, u_{m} ) - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h}( u_{m}^{h},u_{m}^{h} )\\
-										&=&  \lambda_{m} - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} \\
-										&=& 2\lambda_{m} - 2\lambda_{m} ( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} - \lambda_{m}\\
-										&=& \lambda_{m}( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) + \lambda_{m}^{h} - \lambda_{m}
+										&=& \lambda_{m} c( u_{m}, u_{m} ) - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h}c( u_{m}^{h},u_{m}^{h} )\\
+										&=&  \lambda_{m} - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} \\
+										&=& 2\lambda_{m} - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} - \lambda_{m}\\
+										&=& \lambda_{m}c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) + \lambda_{m}^{h} - \lambda_{m}
 		\end{eqnarray*}
@@
 It has been shown that the eigenvalues converge to the exact eigenvalues as $h \rightarrow 0$.
-So from this result, it only remains to show that $( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$.
+So from this result, it only remains to show that $c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$.
 
@@
 	\begin{eqnarray*}
-	(\lambda_{j}^{h} - \lambda_{m}) ( Pu_{m}, u_{j}^{h}) = \lambda_{m} ( u_{m}-Pu_{m},u_{j}^{h} )
+	(\lambda_{j}^{h} - \lambda_{m}) c( Pu_{m}, u_{j}^{h}) = \lambda_{m} c( u_{m}-Pu_{m},u_{j}^{h} )
 	\end{eqnarray*}
@@
 \begin{proof}
-	Since the term $\lambda_{m}( Pu,u^{h}_{j})$ appears on both sides of the equation, it is only required to show that
+	Since the term $\lambda_{m}c( Pu,u^{h}_{j})$ appears on both sides of the equation, it is only required to show that
 	\begin{eqnarray*}
-		\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& \lambda_{m} ( u, u_{j}^{h} ).	
+		\lambda_{j}^{h}c( Pu, u_{j}^{h} ) &=& \lambda_{m} c( u, u_{j}^{h} ).	
 	\end{eqnarray*}
@@
 	\begin{eqnarray*}
-		\lambda_{j}^{h}( Pu, u_{j}^{h} ) &=& b(Pu,u_{j}^{h})\\
-		\lambda_{m} ( u, u_{j}^{h} ) &=& b(u,u_{j}^{h})
+		\lambda_{j}^{h}c( Pu, u_{j}^{h} ) &=& b(Pu,u_{j}^{h})\\
+		\lambda_{m} c( u, u_{j}^{h} ) &=& b(u,u_{j}^{h})
 	\end{eqnarray*}
@@
 \begin{eqnarray}
-	Pu_{m} &=& \sum_{j=1}^{N} ( P u_{m} ,u_{j}^{h}) u_{j}^{h}. \label{CV1}
+	Pu_{m} &=& \sum_{j=1}^{N} c( P u_{m} ,u_{j}^{h}) u_{j}^{h}. \label{CV1}
 \end{eqnarray}
 
-From Lemma \ref{Lem_6}, it follows that $( P_{m},u_{j}^{h} )$ is small if $\lambda_{m}^{h}$ is not close to $\lambda_{j}$.
+From Lemma \ref{Lem_6}, it follows that $c( P_{m},u_{j}^{h} )$ is small if $\lambda_{m}^{h}$ is not close to $\lambda_{j}$.
 Therefore (\ref{CV1}) tells us that $Pu_{m}$ is close to $u_{m}^{h}$.
@@
 
-To simplify the notation, let $\beta = (Pu_m,Pu_m^h)$.
+To simplify the notation, let $\beta = c(Pu_m,Pu_m^h)$.
 
@@
 \begin{eqnarray*}
-||Pu - \beta u_{m}^{h}||^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2},\\
-				&\leq & \rho^{2} \sum_{j\neq m} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
-				&\leq & \rho^{2} \sum_{j=1}^{N} ( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
+||Pu - \beta u_{m}^{h}||^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2},\\
+				&\leq & \rho^{2} \sum_{j\neq m} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
+				&\leq & \rho^{2} \sum_{j=1}^{N} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
 				& = & \rho^{2} ||u_m - Pu_m||^{2}.\\

### 2023-11-24 files/Chapter3/femconvergence.tex
chapter 3

@@
 
-From the textbook \cite{OR76}, the following approximation theorem for finite elements is given verbatim:
+From the textbook \cite{OR76}, following approximation theorem for finite elements is given verbatim:
 \newtheorem*{Interpolation}{Theorem}
@@
 The first step to obtain estimates for the eigenvalues, it to show that the elements of $B_m$ are linearly independent.
-In the first part we follow the approach in \cite{Zie2000} (A Computable Spectral Theorem - Martin Ziegler - 2000).
+In the first part we follow the approach in \cite{Zie2000} (A Computable Spectral Theorem - Martin Ziegler - 2000 ?).
 The author introduced the quantity $\mu_m$.
@@
 
-\newtheorem{Cor_1}{Proposition}
+\newtheorem{Cor_1}[Prop_1]{Proposition}
 \begin{Cor_1}
@@
 	\begin{align*}
-		\lambda_{m}^{h} &\leq \frac{\lambda_{m}}{\mu_{m}^{h}} \\
-		\lambda_{m}^{h}\mu_{m}^{h} &\leq \lambda_{m} \\
-		-\lambda_{m} &\leq -\lambda_{m}^{h}\mu_{m}^{h} \\
-		\lambda_{m}^{h} - \lambda_{m} &\leq \lambda_{m}^{h} - \lambda_{m}^{h}\mu_{m}^{h} \\
-		\lambda_{m}^{h} - \lambda_{m} &\leq \lambda_{m}^{h}\sigma_{m}^{h}
+		\lambda_{m}^{h} &\leq \frac{\lambda_{m}}{\mu_{m}^{h}}, \\
+		\lambda_{m}^{h}\mu_{m}^{h} &\leq \lambda_{m}. \\
+	\end{align*}
+	This is equivalent to
+	\begin{align*}
+		-\lambda_{m} &\leq -\lambda_{m}^{h}\mu_{m}^{h}. 
+	\end{align*}
+	Add $\lambda_{m}^{h}$ to both sides
+	\begin{align*}
+		\lambda_{m}^{h} - \lambda_{m} &\leq \lambda_{m}^{h} - \lambda_{m}^{h}\mu_{m}^{h}. 
+	\end{align*}
+	And finally using the error bound $\sigma_{m}^{h} = 1 - \mu_{m}^{h}$,
+	\begin{align*}
+		\lambda_{m}^{h} - \lambda_{m} &\leq \lambda_{m}^{h}\sigma_{m}^{h}.
 	\end{align*}
@@
 	\label{Prop_3}
-	$\sigma_{m}^{h} = \max\left\{ 2( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}$
+	$\sigma_{m}^{h} = \max\left\{ 2c( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}$
 \end{Prop_3}
@@
 
-\newtheorem{Lem_2}[Lem_1]{Lemma} \label{Lem_2}
+\newtheorem{Lem_2}[Lem_1]{Lemma} 
 \begin{Lem_2}
+	\label{Lem_2}
 	$\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$
@@
 
-\newtheorem{Prop_5}[Prop_1]{Proposition} \label{Prop_5}
+\newtheorem{Prop_5}[Prop_1]{Proposition} 
 \begin{Prop_5}
+	\label{Prop_5}
 	For any $\epsilon > 0$, there exists a $\delta >0$ such that for $h<\delta$,
@@
 
-\newtheorem{Lem_5}[Lem_1]{Lemma} \label{Lem_5}
+\newtheorem{Lem_5}[Lem_1]{Lemma} 
 \begin{Lem_5}
+	\label{Lem_5}
 	\begin{eqnarray*}
@@
 
-\newtheorem{Lem_6}[Lem_1]{Lemma} \label{Lem_6}
+\newtheorem{Lem_6}[Lem_1]{Lemma} 
 \begin{Lem_6}
+	\label{Lem_6}
 	For all m and j
@@
 
-\newtheorem{Lem_7}[Lem_1]{Lemma} \label{Lem_7}
+\newtheorem{Lem_7}[Lem_1]{Lemma} 
 \begin{Lem_7}
+	\label{Lem_7}
 	\begin{eqnarray*}
@@
 
-\newtheorem{Lem_8}[Lem_1]{Lemma} \label{Lem_8}
+\newtheorem{Lem_8}[Lem_1]{Lemma} 
 \begin{Lem_8}
+	\label{Lem_8}
 	\begin{eqnarray*}
@@
 
-\newtheorem{Lem_9}[Lem_1]{Lemma} \label{Lem_9}
+\newtheorem{Lem_9}[Lem_1]{Lemma} 
 \begin{Lem_9}
+	\label{Lem_9}
 	\begin{eqnarray*}

### 2023-11-25 files/Chapter3/dynamicconvergence.tex
galerkin Timo

@@
 
-\textcolor{red}{*******NEED COME BACK TO THIS**********}
+\textcolor{red}{***************** NEW ********************************}
 
-Let $S^h$ denote a finite dimensional subspace of $V$.
+\subsubsection{*** Example of the Galerkin approximation of a cantilever Timoshenko beam ***}
+Consider the example of the cantilever Timoshenko beam model from Section \ref{sec:existence}. In this section the variational problem Problem T-2V is given in terms of bilinear forms.
 
-\textcolor{red}{*******NEED COME BACK TO THIS**********}
+\subsubsection{Problem T-2V}
+Find a function $u \in T[0,1]$ such that for all $t \in [0,1]$,
+\begin{eqnarray*}
+	c(u''(t),v) + b(u(t),v) & = & (Q(t),v),
+\end{eqnarray*} for each $v \in T[0,1]$.
+
+The interval $[0,1]$ is divided into $n$ equal subintervals $[x_{i}, x_{i+1}]$, each of length $\displaystyle h = \frac{1}{n}$, such that $x_i = ih$ for $i = 0,1,...,n$.
+
+Consider a a set of $n+1$ linear independent, piecewise linear basis functions $\delta_i \in T[0,1]$.
+The subset of these functions that satisfies the boundary conditions are called admissible basis functions.
+For Problem 2-T, the admissible basis functions are ${\delta_i}$ for $i = 1,2,...,n$.
+Define the space $S^h$ as the space spanned by the admissible basis functions, i.e.
+\begin{eqnarray*}
+	S^h = \textrm{span}\{\delta_1, \delta_2, ..., \delta_n\}.
+\end{eqnarray*}
+
+This space $S^h$ is a finite dimensional subspace of $T[0,1]$. Define the following functions $w^h \in S^h$ and $\phi^h \in S^h$ as
+\begin{eqnarray*}
+	w^h(t) & = & \sum_{i=1}^{n} w(x_i^*,t) \delta_i(t),\\
+	\phi^h(t) & = & \sum_{i=1}^{n} w(x_i^*,t) \delta_i(t),
+\end{eqnarray*} where $x^*_i \in [x_i, x_{i+1}]$.
+
+Using these functions, the Galerkin approximation for Problem T-2, referred to as Problem T-2G, can be derived.
+
+\subsubsection{Problem T-2G}
+Find a function $u_h \in S^h$ such that for all $t \in [0,1]$,
+\begin{eqnarray*}
+	c(u''_h(t),v) + b(u_h(t),v) & = & (Q^I(t),v),
+\end{eqnarray*} for each $v \in S^h$, where $u_h = \langle w^h, \phi^h \rangle$. $Q^I$ is a vector of the values of $Q(x^*_i)$ for $i = 0,1,2,...,n$.
+
+This example serves as an illustration of the derivation of the Galerkin approximation and the convention of symbols before the general case is presented.
+Piecewise linear basis functions are used for this example, but other basis functions can be used.
+In Chapter 5, the basis functions used are piecewise cubic Hermite polynomials.
+
+For the general case presented below, $S^h$ is a finite dimensional subspace of $V$.
+
+\textcolor{red}{***************** NEW ********************************}
 

### 2023-11-26 files/Chapter3/dynamicconvergence.tex
Chapter 3

@@
 
-Recall that $u^h(t) = \sum_{k} u_k(t)\phi_k$ where $\bar{u}_k = \left( u_1(t), u_2(t), ...  , u_n(t)\right)$.
+Recall that $u^h(t) = \sum_{k} u_k(t)\phi_k$ where $\bar{u}_k = \left( u_1(t), u_2(t), ...
+, u_n(t)\right)$ where each $\phi_k$ corresponds to a node number $k$.
+More complex cases are treated in Chapter \ref{ch:finite-element-method}.
 
@@
 \begin{DC_Prop2}
-	If $F\in C(J)$, then Problem ODE has a unique solution for each pair of vectors $\bar{u}^h_0$ and $\bar{u}^h_1$
+	If $F\in C(J)$, then Problem ODE has a unique solution for each pair of vectors $\bar{u}_0$ and $\bar{u}_1$
 \end{DC_Prop2}
@@
 \begin{DC_Prop3}
-	Suppose $M, K, C, F,{u}_0$ and ${u}_1$ are defined as above. Then, the function $u_{h}$ is a solution of Problem GVar$^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
+	Suppose $M, K, C, F,\bar{u}_0$ and $\bar{u}_1$ are defined as above. Then, the function $u_{h}$ is a solution of Problem GVar$^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
 \end{DC_Prop3}
@@
 Denote the approximation of $u_h$ on the interval $[t_{k-1}, \ t_k]$ by $u_k^h$, i.e.
-$u_h(t_k) = u_k^h$ for each $k$.
+$u_h(t_k)$ corresponds to $u_k^h$ for each $k$.
 (Recall that $u_h(t) = \sum u_i(t)\phi_i$.) A finite difference method is used to compute $u^h_k$ for each $k$.
@@
 
-\vspace*{40mm}
+In \cite{BV13} it is assumed that there exists a subspace $H$ of $V$ and a positive integer $\alpha$ such that
+\begin{eqnarray*}
+	\inf_{v\in S^{h}}\Vert w-v\Vert_{V}\leq{C}h^{\alpha}|||w|||_{H},
+\end{eqnarray*} for each $w \in H$ where $|||w|||_H$ is a norm or semi-norm for $H$.
 
-The error $e$, can now be expressed as
+\newtheorem*{DC_Thm6_1}{Theorem 2}
+\begin{DC_Thm6_1}
+	If $u(t) \in H$ and $u'(t) \in H$ for each $t$, then
+	\begin{eqnarray*}
+		||e^h(t)||_W & \leq & C h^\alpha \left( |||u(t)||_H + |||u'(t)||_H \right),
+	\end{eqnarray*} for each $t$.
+\end{DC_Thm6_1}
+
+From Theorem 2 for the semi-discrete problem an error estimate for
+$e(t) = [u(t)-u_h(t)]$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $e_k = [u_h(t_k) - u^h_k]$.
+
+The error can then be expressed as
 \begin{eqnarray}
@@
 
-From Theorem 2 of the semi-discrete problem an error estimate for
-$e_k = [u(t_k)-u_h(t_k)]$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $e_k = [u_h(t_k) - u^h_k]$.
-
 Since the dimension of $S^h$ is not fixed, the equivalence of norms
 cannot be used, and therefore this error estimate for $e_k = [u_h(t_k) - u^h_k]$
-should also be with respect to the norm of $W$.
+should also be with respect to the norm of $W$. The local error $e_1$ can be estimated using Taylor polynomials, but then $e_k$ `grows' as $k$ increases.
 
-A stability result is derived in \cite{BV13}.
+A stability result is derived in \cite{BV13}. Recall that $\displaystyle \tau = \frac{T}{N}$.
 
@@
 Using this lemma, \cite{BV13} prove the error estimate.
+The error estimate for the term $[u_h(t_k) - u^h_k]$ with respect to the norm of $W$ as proven by the authors of \cite{BV13} is presented here as Theorem 3.
 
-\newtheorem*{DC_Thm5_1}{Theorem 2}
+\newtheorem*{DC_Thm5_1}{Theorem 3}
 \begin{DC_Thm5_1}
-	{Main Result}\\
 	If $f\in C^{2}([0,T],X)$, then
@@
 
-Recall that $\displaystyle \tau = \frac{T}{N}$. The error estimate for the term
-$[u_h(t_k) - u^h_k]$ with respect to the norm of $W$ as proven by the authors
-of \cite{BV13} is presented here as Theorem 3.
-
+\subsection{Main result}
 Finally, Theorem 2 of the semi-discrete problem and Theorem 3 of the fully
@@
 
-\subsection{Main result}
 The main result proving the convergence of the solution of the Galerkin
 Approximation is given in \cite{BV13} as follows.
-\newtheorem*{DC_Thm5}{Theorem 2}
+\newtheorem*{DC_Thm5}{Theorem 4}
 \begin{DC_Thm5}
@@
 
-The constant $K$ depend on $u_h$ and its derivatives.
+The constant $K$ depend on $u$, $u_h$ and their derivatives.
 

### 2023-11-26 files/Chapter3/dynamicconvergence.tex
Chapter 3

@@
 
-\textcolor{red}{***************** NEW ********************************}
-
-\subsubsection{*** Example of the Galerkin approximation of a cantilever Timoshenko beam ***}
 Consider the example of the cantilever Timoshenko beam model from Section \ref{sec:existence}. In this section the variational problem Problem T-2V is given in terms of bilinear forms.
@@
 
-Consider a a set of $n+1$ linear independent, piecewise linear basis functions $\delta_i \in T[0,1]$.
+Consider a set of $n+1$ linear independent, piecewise linear basis functions $\delta_i$.
 The subset of these functions that satisfies the boundary conditions are called admissible basis functions.
@@
 
-This space $S^h$ is a finite dimensional subspace of $T[0,1]$. Define the following functions $w^h \in S^h$ and $\phi^h \in S^h$ as
+This space $S^h\times S^h$ is a finite dimensional subspace of $T[0,1]$. Define the following functions $w^h \in S^h$ and $\phi^h \in S^h$ as
 \begin{eqnarray*}
@@
 	\phi^h(t) & = & \sum_{i=1}^{n} w(x_i^*,t) \delta_i(t),
-\end{eqnarray*} where $x^*_i \in [x_i, x_{i+1}]$.
+\end{eqnarray*} where $x^*_i \in [x_i, x_{i+1}]$. Then let $u_h = (w^h, \phi^h )$.
 
-Using these functions, the Galerkin approximation for Problem T-2, referred to as Problem T-2G, can be derived.
+Using these functions, the Galerkin approximation for Problem T-2, referred to as Problem T-2V$^h$, can be derived.
 
-\subsubsection{Problem T-2G}
-Find a function $u_h \in S^h$ such that for all $t \in [0,1]$,
+\subsubsection{Problem T-2V$^h$}
+Find a function $u_h \in S^h\times S^h$ such that for all $t \in [0,1]$,
 \begin{eqnarray*}
 	c(u''_h(t),v) + b(u_h(t),v) & = & (Q^I(t),v),
-\end{eqnarray*} for each $v \in S^h$, where $u_h = \langle w^h, \phi^h \rangle$. $Q^I$ is a vector of the values of $Q(x^*_i)$ for $i = 0,1,2,...,n$.
+\end{eqnarray*} for each $v \in S^h\times S^h$, where $u_h = ( w^h, \phi^h )$. $Q^I$ is a vector with elements $Q(x^*_i)$ for $i = 0,1,2,...,n$.
 
@@
 For the general case presented below, $S^h$ is a finite dimensional subspace of $V$.
-
-\textcolor{red}{***************** NEW ********************************}
 

### 2023-11-26 files/Chapter3/femconvergence.tex
chapter 3
Chapter 3

@@
 \section{FEM computation of eigenvalues and eigenfunctions}
-Let $H$ be a Hilbert space with the inner product $(\cdot,\cdot)$ and induced norm $||\cdot||$.
+\textcolor{red}{Change H to W?}
+
+Let $H$ be a Hilbert space with the inner product $c(\cdot,\cdot)$ and induced norm $||\cdot||_{W}$.
 Let $V$ be a linear subspace of $H$, with inner product defined by the bilinear form $b(\cdot,\cdot)$.
-It is assumed that this bilinear form $b$ is symmetric.
+It is assumed that the bilinear form $b$ is symmetric and that the assumptions in Section \ref{sec:existence:ModalAnalysis} holds.
 
-\subsection{General eigenvalue problem}
-
-The following eigenvalue problem is considered in \cite{SF73}.
+The following eigenvalue problem is considered in \cite{SF73}. The same problem was treated in Section \ref{sec:existence:ModalAnalysis}, although the notation differs slightly.
 
@@
 
-Suppose $E^h$ is a finite dimensional subspace of $V$. Consider the Galerkin approximation for \eqref{GEVP}:
+Recall that the eigenvectors can be ordered in such a way that \[\lambda_1 \leq \lambda_2 \leq \lambda_3 \leq ...\] where $\lambda_i$ are the corresponding eigenvalues.
+
+\subsubsection*{Properties of eigenvalues}
+Since any multiple of a eigenfunction is still an eigenfunction, the eigenfunctions can be normalized so that $||u_i||_{W} = 1$ for all $i$.
+
+Let $\left\{ \phi_k \in V \ | \  k = 1,2,...,N_e \right\}$ be a set of linear independent admissible basis functions.
+Define $S^h := \text{span}\left\{\phi_k \in V \ | \ k = 1,2,...,N_e\right\}$ so that $S^h$ is a finite dimensional subspace of V.
+\label{sym:natural} \label{sym:Sh1}
+
+Consider the Galerkin approximation for \eqref{GEVP}:
 \subsubsection*{Problem $E^h$}
@@
 
-For detail, see Chapter 5.
-
-\textcolor{red}{********** need to move this ******************}
-
-\subsection{Preliminary theory and notation}
-In this section, the work in the textbook \cite{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for greater clarity.
-
-Some theory is required before the main results can be proven. The theory is from \cite{SF73}.
-
-\textcolor{red}{********** need to move this ******************}
-
-\subsubsection*{Properties of eigenvalues}
-It is well known that the eigenvalues of a eigenvalue problem such as \eqref{GEVP} form an infinite sequence of eigenvalues $(\lambda_i)$.
-Assume that the eigenvectors can be ordered in such a way that $\lambda_1 \leq \lambda_2 \leq \lambda_3 \leq ...$ where $\lambda_i$ are the corresponding eigenvalues.
-
-Since any multiple of a eigenfunction is still an eigenfunction, the eigenfunctions can be normalized so that $||u_i|| = 1$ for all $i$.
-
-Fix $m \in \mathbb{N}$.
-Let $\left\{ \phi_k \in V | k = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
-Define $S^h := \text{span}\left\{\phi_k \in V | k = 1,2,...,m\right\}$ so that $S^h$ is a finite dimensional subspace of V.
-\label{sym:natural} \label{sym:Sh1}
+For examples, see Chapter 5.
 
 Problem $E^h$ can be written as a matrix eigenvalue problem,
-\begin{eqnarray*}
-	\lambda^nM\bar{u}_n = K\bar{u}_n.
-\end{eqnarray*} The pair $(\lambda^n, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$.
+\begin{eqnarray}
+	\lambda^nM\bar{u}_n = K\bar{u}_n. \label{eq:matrix_eigenvalue}
+\end{eqnarray}
 
-In a finite-dimensional subspace, the ordering of vectors is preserved as it is in the original space.
-Denote the normalized eigenvectors in the space $S^h$ as $u^h_k$ with corresponding eigenvalues $\lambda^h_i$ for $k = 1,2,...,m$.
+Since $N_e$ is never small and usually large to very large, a compute algorithm is required to calculate the eigenvalues (and eigenfunctions) of \eqref{eq:matrix_eigenvalue}.
 
-Also any subspace of $S^h$ will also be a subspace of $V$. So the minmax principle applies and a lower bound for the eigenvalues can be found:
+The pair $(\lambda^n, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$. It is necessary to some of the teory to make the connection.
+
+In $S^h$, the ordering of vectors is the same as in the original space.
+Denote the normalized eigenvectors in the space $S^h$ as $u^h_k$ with corresponding eigenvalues $\lambda^h_k$ for $k = 1,2,...,N_e$.
+
+In section \ref{sec:estimating_the_eigenvalues} it is proved that the error $| \lambda_k^h - \lambda_k|$ is large when $k$ is large.
+It is for example possible that $|\lambda^h_1 - \lambda_1|$ is sufficiently small while $\lambda^h_k$ cannot even be considered an approximation of $\lambda_k$ when $\displaystyle k > \frac{1}{2}N_e$.
+
+Finally, any subspace of $S^h$ will also be a subspace of $V$. So the minmax principle applies and a lower bound for the approximate eigenvalues hold \cite{SF73}:
 \begin{equation}
@@
 
+\textcolor{red}{********* Hou voorlopig hier *************}
 \subsubsection*{Properties of eigenvalues}
@@
 
-Since any multiple of a eigenfunction is still an eigenfunction, the eigenfunctions can be normalized so that $||u_i|| = 1$ for all $i$.
+Since any multiple of a eigenfunction is still an eigenfunction, the eigenfunctions can be normalized so that $||u_i||_{W} = 1$ for all $i$.
 
@@
 \end{equation}
+\textcolor{red}{********* Hou voorlopig hier *************}
 
-\subsection{Estimating the eigenvalues.} \label{sec:est}
-\textbf{Rayleigh quotient}
+\section{Estimating the eigenvalues.} \label{sec:estimating_the_eigenvalues}
+In this section, the work in the textbook \cite{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for greater clarity.
+
+\subsection{Projection of the eigenfunctions}
+
+Some theory is required before the main results can be proven. The theory is from \cite{SF73}.
+
+\subsubsection*{Rayleigh quotient}
 \begin{equation}
@@
 
-\textbf{minmax Principle}\\
-Let T denote the class of subspaces of $V$ that jas dimension $j$. Then
-\begin{equation*}
-	\lambda_j = \min_{s\in T}\max_{v \in S} R(v).
-\end{equation*}
-
-\textbf{Rayleigh-Ritz Projection}\\
+\subsubsection*{Projection}
 If $u \in V$, then $Pu$ is its projection in the subspace $S^h$.
@@
 \end{equation*}
+
+Let $E_j \in V$ denote the eigenspace spanned by the exact eigenvectors $\left\{u_1,u_2,...,u_j \right\}$ for $j = 1,2,...,m$. Clearly $m \leq N_e$.
+
+Consider the subspace $S_j$ of $S^h$ where
+\begin{equation*}
+	S_j = PE_j \ \text{ for } j = 1,2,...,m.
+\end{equation*}
+
+The elements $Pu_j$ are the projections of the eigenfunctions $u_j$ into the space $S^h$.
+These projections $Pu_j$ are not necessarily equal to $u^h \in S^h$.
+In fact, $u^h_j$  can be vastly different from $u_j$.
+The situation is not simple.
+It is possible that $Py_k = 0$ for large $k$ Assume that the dimension of $S^h$ is large enough, substantially larger than $m$.
+
+Let $B_m = \left\{u \in E_m \ | \ ||u||_{W} = 1 \right\}$ and define $\mu_m = \inf\left\{(Pu,Pu \ | \ u \in B_m)\right\}$.
+
+The first step to obtain estimates for the eigenvalues, it to show that the elements of $B_m$ are linearly independent.
+In the first part we follow the approach in \cite{Zie2000}.
+The author introduced the quantity $\mu_m$ above.
+
+\newtheorem{Prop_1}{Proposition}
+\begin{Prop_1}
+ $\mu_{m} > 0$ if and only if $\dim S_{m} = m$. \label{sym:mu}
+\end{Prop_1}
+\begin{proof}
+	To show that the dimension of $S_m = m$, suppose that the elements of $B_m$ are linearly dependent.
+Then there exists a $u \in B_m$ such that $Pu = 0$ and consequently $\mu_m = 0$.
+The result follows from the contra-positive.
+\end{proof}
+
+\subsection{Upper bounds for approximate eigenvalues}
+
+ Recall the definition of the Rayleigh quotient R in \eqref{Rayleigh}.
+
+\newtheorem{Prop_2}[Prop_1]{Proposition}
+\begin{Prop_2}
+	\label{Prop_2}
+	$\lambda^{h}_{m} \leq \max R(Pu) \ \text{ for } u \in B_{m}$
+\end{Prop_2}
+\begin{proof}
+	Since $\dim S_{m} = m$, following from the minmax principle that
+	\begin{equation}
+		\lambda_m^h \leq \max R(v) \ \text{ for } v \in S_m. \label{eq:Prop_2}
+	\end{equation}
+
+	Take an arbitrary nonzero $v \in S_m$. Then there exists a $Py \in E_m$ such that $v = Py$.
+
+	Now we take an arbitrary $v \in S_{m}$, $v \neq 0$.
+Then there exists a $u \in E_{m}$ such that $Py = v$.
+This $Py$ is the projection into $S_m$ of some $u \in E_m$ (which is also $\displaystyle \frac{1}{||u||_{W}}u \in B_m$).
+
+	Next we show that $R(||u||_{W}^{-1}u) = R(u)$:
+
+	\[ \frac{b\left(\frac{1}{||u||_{W}}u,\frac{1}{||u||_{W}}u\right)}{c\left(\frac{1}{||u||_{W}}u,\frac{1}{||u||_{W}}u\right)} = \frac{b(u,u)}{c(u,u)} = R(u). \]
+
+	Finally, from \eqref{eq:Prop_2}
+	\begin{eqnarray*}
+	\lambda_{m}^{h} &\leq & \max R(v) \ \text{ for } \ v \in S_{m},\\
+						&=& \max R(Pu) \ \text{ for } \ u \in E_{m},\\
+						&=& \max R(Pu) \ \text{ for } \ u \in B_{m}.
+	\end{eqnarray*}
+\end{proof}
+
+%\newpage
+In the textbook, the authors show that the eigenfunctions are orthogonal. But they do so using matrix representations of the eigenvalue problem. A different method can be used to show this.
+
+Pick any $i,j \in \mathbb{N}$ such that $i,j \leq m$. Then
+\begin{eqnarray*}
+	b(u_{i},\nu) &=& \lambda_{i}c(u_{i},\nu),\\
+	\textrm{and } b(u_{j},\nu) &=& \lambda_{j}c(u_{j},\nu).
+\end{eqnarray*}
+for each $\nu \in V$. Clearly
+\begin{eqnarray*}
+	b(u_{i},u_{j}) &=& \lambda_{i}c(u_{i},u_{j}),\\
+	\textrm{and } b(u_{j},u_{i}) &=& \lambda_{j}c(u_{j},u_{i}).
+\end{eqnarray*}
+Then using the symmetry of $b(\cdot,\cdot)$ and $c( \cdot, \cdot )$,
+\begin{eqnarray*}
+	0 &=& (\lambda_{i} - \lambda_{j}) c( u_{i}, u_{j} ).
+\end{eqnarray*}
+So if $i \neq j$ then $\lambda_{i} \neq \lambda_{j}$. Therefore $u_{i}$ and $u_{j}$ are orthogonal when $\lambda_i \neq \lambda_j$.
+
+The next steps in the textbook \cite{SF73} contains proofs with multiple results. In an attempt to better understand the results, the proofs are broken up into smaller proofs.
+
+\newtheorem{Lem_1}{Lemma} 
+\begin{Lem_1}
+	\label{Lem_1}
+	$\displaystyle \lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}$
+\end{Lem_1}
+\begin{proof}
+	Consider the linearity of the bilinear form $b$, and fact that any $u \in E_m$ can be expressed as a linear combination $u = \sum_{i=1}^{m} c_{i}u_{i}$. Then
+	\begin{eqnarray*}
+	b(u,u) &=& b\left(\sum_{i=1}^{m} c_{i}u_{i},\sum_{j=1}^{m} c_{j}u_{j}\right),\\
+			&=& \sum_{i=1}^{m} c_{i}\sum_{j=1}^{m} c_{j} b(u_{i},u_{j}).
+	\end{eqnarray*}
+
+	The summation parameters can be merged into a single parameter. Then
+	\begin{eqnarray*}
+		b(u,u)  & = & \sum_{i=1}^{m} c_{i}^{2} \lambda_{i} u_i,\\
+				& \leq & \lambda_{m}\sum_{i=1}^{m} c_{i}^{2} u_i,\\
+				& = & \lambda_{m}||u||_{W}^2.
+	\end{eqnarray*} for all $u \in B_m$.\\
+
+	And since $B_{m} \subset E_{m}$, $b(Pu,Pu) \leq \lambda_{m}$ for all $u\in B_{m}$\\
+
+	Using the Rayleigh quotient, and the definition of $\mu_{m}^{h}$, 
+	\begin{eqnarray*}
+		R(Pu) &=& \frac{b(Pu,Pu)}{c(Pu,Pu)},\\
+			&=& \frac{b(Pu,Pu)}{||Pu||_{W}^{2}},\\
+			&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}.
+	\end{eqnarray*}
+
+	Together with Proposition \ref{Prop_2} it follows that
+	\begin{eqnarray*}
+		\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}.
+	\end{eqnarray*}
+\end{proof}
+
+\subsection{The error bound}
+
+Following Lemma \ref{Lem_1}, and since $\lambda_{i}^{h} \geq \lambda_{i}$ it follows that $0 < \mu_{m}^{h} \leq 1$. It is now possible to define the `error bound' in \cite{SF73}:
+\begin{eqnarray}
+	\sigma_{m}^{h} = 1 - \mu_{m}^{h}. \label{eq:error_bound}
+\end{eqnarray}
+
+\newtheorem{Cor_1}[Prop_1]{Proposition}
+\begin{Cor_1}
+	$0 \leq \sigma_{m}^{h} < 1$ and $\lambda_{m}^{h} - \lambda_{m} \leq \lambda_{m}^{h}\sigma_{m}^{h}$
+\end{Cor_1}
+\begin{proof}
+	Starting with the result of Lemma \ref{Lem_1}, $\lambda_{m}^{h}\mu_{m}^{h} \leq \lambda_{m}$.
+
+	Since $-\lambda_{m} \leq -\lambda_{m}^{h}\mu_{m}^{h}$, it follows that
+	\begin{align*}
+		\lambda_{m}^{h} - \lambda_{m} &\leq \lambda_{m}^{h} - \lambda_{m}^{h}\mu_{m}^{h} = \lambda^h_m(1 - \mu^h_m). 
+	\end{align*}
+\end{proof}
+
+This result gives an error estimate for the eigenvalues.
+To prove the convergence of the eigenvalues, it is necessary to prove that the error estimate $\sigma_{m}^{h}$ converges to zero as $h \rightarrow 0$.
+
+\newtheorem{Prop_3}[Prop_1]{Proposition} 
+\begin{Prop_3}
+	\label{Prop_3}
+	$\sigma_{m}^{h} = \max\left\{ 2c( u,u-Pu )-||u-Pu||_{W}^{2} \ | \ u \in B_{m} \right\}$
+\end{Prop_3}
+\begin{proof}
+	Let $u \in B_{m}$. Then
+	\begin{eqnarray*}
+		||u - Pu||_{W}^{2} &=& c( u - Pu, u - Pu ), \\
+						&=& c( u, u ) - 2 c( u, Pu ) + c( Pu, Pu ), \\
+						&=& 2c( u, u ) - 2 c( u, Pu ) + c( Pu, Pu ) - c( u, u ),\\
+						&=& 2c( u, u - Pu ) + c( Pu, Pu ) - c( u, u ).\\
+	\end{eqnarray*}
+	Consequently,
+	\begin{eqnarray*}
+		c( u, u ) - c( Pu, Pu )  & = & 2c( u, u - Pu ) - ||u - Pu||_{W}^{2}.
+	\end{eqnarray*}
+
+	Since $u \in B_{m}$, $||u||_{W}^{2} = 1$ and hence
+	\begin{eqnarray*}
+		1 - ||Pu||_{W}^{2}  & = & 2c( u, u - Pu ) - ||u - Pu||_{W}^{2}.
+	\end{eqnarray*}
+
+	On the right hand side, $1 - ||Pu||_{W}^{2} \leq 1 - \mu_{m}^{h} = \sigma_{m}^{h}$ for all $u \in B_{m}$. Therefore
+	\begin{eqnarray*}
+	\sigma_{m}^{h} = \max\left\{ 2c( u,u-Pu )-||u-Pu||_{W}^{2} \ | \ u \in B_{m} \right \}.
+	\end{eqnarray*}
+\end{proof}
+
+Proposition \ref{Prop_3} is a result given in \cite{SF73} without explaining how it is derived.
+
+Introduce some new notation for convenience. For any $u \in E_{m}$, let $u^{*} = \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}$ where $u = \sum_{i=1}^{m} c_{i}u_{i}$.
+
+\newtheorem{Prop_4}[Prop_1]{Proposition} 
+\begin{Prop_4}
+	\label{Prop_4}
+	For any $u \in E_{m}$
+		\begin{eqnarray*}
+		c( u, u - Pu ) = b(u^{*} - Pu^{*}, u -Pu)
+		\end{eqnarray*}
+\end{Prop_4}
+\begin{proof}
+	For any $i = 1,2,...,m$,
+	\begin{eqnarray*}
+	\lambda_{i}c( u_{i},u-Pu ) &=&  b(u_{i}, u-Pu),\\
+								&=& b(u_{i}, u-Pu) - b(u-Pu,Pu_{i}) \ \textrm{ (Rayleigh-Ritz Projection)},\\
+								&=&  b(u_{i}, u-Pu) - b(Pu_{i},u-Pu),\\
+								&=&  b(u_{i}-Pu_{i}, u-Pu).
+	\end{eqnarray*}
+	Multiplying by $c_{i}\lambda_{i}^{-1}$ and summation over i gives:
+	\begin{eqnarray*}
+	\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}\lambda_{i}c( u_{i},u-Pu ) &=& \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}b(u_{i}-Pu_{i}, u-Pu),\\
+								&=& b(\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}-\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}Pu_{i}, u-Pu),\\
+										&=& b(u^{*}-Pu^{*}, u-Pu).
+	\end{eqnarray*}
+	Therefore $c( u,u-Pu ) = b(u^{*}-Pu^{*}, u-Pu)$.
+\end{proof}
+
+\newtheorem{Lem_2}[Lem_1]{Lemma} 
+\begin{Lem_2}
+	\label{Lem_2}
+	$\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}||_{W} ||u-Pu||_{W} \ | \ u \in B_{m} \right\}.$
+\end{Lem_2}
+\begin{proof}
+	From Proposition \ref{Prop_3},
+	\begin{eqnarray*}
+		\sigma_{m}^{h} & = & \max\left\{ 2c( u,u-Pu )-||u-Pu||_{W}^{2} \ | \ u \in B_{m} \right\}, \\
+					& \leq & \max\left\{ 2c( u,u-Pu ) \ | \ u \in B_{m} \right\}. \\
+	\end{eqnarray*}
+
+	From Proposition \ref{Prop_4}, 
+	\begin{eqnarray*}
+		\sigma_{m}^{h} = \max\left\{ 2 b(u^{*}-Pu^{*}, u-Pu) \ | \ u \in B_{m} \right\}.
+	\end{eqnarray*}
+
+	Using the Schwartz inequality,
+	\begin{eqnarray*}
+		b(u^{*} - Pu^{*}, u -Pu) & \leq & ||u^{*} - Pu^{*}||_{W}||u -Pu||_{W}.
+	\end{eqnarray*}
+
+	Finally,
+	\begin{eqnarray*}
+		\sigma_{m}^{h} & \leq & \max\left\{ 2||u^{*}- Pu^{*}||_{W} ||u-Pu||_{W} \ | \ u \in B_{m} \right\}.
+	\end{eqnarray*}
+\end{proof}
+
+\subsection{Convergence of the eigenvalues}
+
+\newtheorem{Prop_5}[Prop_1]{Proposition} 
+\begin{Prop_5}
+	\label{Prop_5}
+	For any $\epsilon > 0$, there exists a $\delta >0$ such that for $h<\delta$,
+	\begin{eqnarray*}
+	||u^{*} - Pu^{*}||_{W} < \epsilon \ \textrm{ for each } u \in B_{m},\\
+	||u - Pu||_{W} < \epsilon \ \textrm{ for each } u \in B_{m}.
+	\end{eqnarray*}
+\end{Prop_5}
+\begin{proof}
+	Consider a set of basis functions $\Phi \subset S^h$ such that $\phi^(k) = 0$ for each $\phi \in \Phi$.
+
+	From the Rayleigh-Ritz Projection, $Pu$ is the closest element in $S^h$ to $u$. In particular, $||u-Pu||_{W}\leq ||u-\Pi u||_{W}$, where $\Pi u$ is the interpolation of $u$ into $S^h$.
+
+	\textcolor{red}{Need to fix reference to approximation theorem. Need to wait until section 3.5 is done. The approximation theorem is moved to the end of section 3.5}
+
+	From the Approximation Theorem given at the beginning of section \ref{sec:est}, is follows that
+	\begin{eqnarray*}
+		||u - \Pi u||_{W} \leq Ch^{k}||u^{(k)}||_{W}.
+	\end{eqnarray*}
+
+	So for any $\epsilon > 0$, a $\delta$ can be found such that if $h<\delta$ then
+	\begin{eqnarray*}
+		||u - Pu||_{W} \leq ||u - \Pi u||_{W} \leq \epsilon.
+	\end{eqnarray*}
+	A similar argument for $||u^{*} - Pu^{*}||_{W}$ proves the theorem.
+\end{proof}
+
+\newtheorem{Lem_3}[Lem_1]{Lemma} 
+\begin{Lem_3}
+	\label{Lem_3}
+	For any $\epsilon >0$ there exists a $\delta > 0$ such that
+	\begin{eqnarray}
+	\sigma_{m}^{h} < \epsilon \ \textrm{ if } \ h < \delta. \label{eq:lem3}
+	\end{eqnarray}
+\end{Lem_3}
+\begin{proof}
+	For any $\epsilon > 0$ there exists a $\delta > 0$ such that if $h<\delta$, then
+	\begin{eqnarray*}
+	||u-Pu||_{W} < \epsilon \ \textrm{ for each } \ u \in B_{m}.
+	\end{eqnarray*}
+	This result, together with Lemma \ref{Lem_2} and Proposition \ref{Prop_5} gives the result.
+\end{proof}
+
+\newtheorem{Lem_4}[Lem_1]{Lemma} 
+\begin{Lem_4}
+	\label{Lem_4}
+	There exists a $\delta > 0$ such that for $h < \delta$
+	\begin{eqnarray}
+	\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}. \label{eq:lem4}
+	\end{eqnarray}
+\end{Lem_4}
+\begin{proof}
+	Using Lemma \ref{Lem_3}, choose $\delta$ such that $\sigma_{m}^{h} < \frac{1}{2}$.
+Then (by Lemma \ref{Lem_1}) $\lambda_{m}^{h} < 2\lambda_{m}$ and therefore $\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}$.
+\end{proof}
+
+The convergence of the eigenvalues follows from \eqref{eq:lem3} and \eqref{eq:lem4}.
+
+\section{Convergence of the eigenfunctions}
+The next step is to show the convergence of the eigenfunctions. The problem can be formulated using the following result.
+
+\newtheorem{Lem_5}[Lem_1]{Lemma} 
+\begin{Lem_5}
+	\label{Lem_5}
+	\begin{eqnarray*}
+		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& \lambda_{m}c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h} ) + \lambda_{m}^{h} - \lambda_{m}.
+		\end{eqnarray*}
+\end{Lem_5}
+\begin{proof}
+	\begin{eqnarray*}
+		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& b(u_{m},u_{m}) - 2b(u_{m},u^{h}_{m}) + b(u^{h}_{m},u^{h}_{m}), \\
+										&=& \lambda_{m} c( u_{m}, u_{m} ) - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h}c( u_{m}^{h},u_{m}^{h} ),\\
+										&=&  \lambda_{m} - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h}, \\
+										&=& 2\lambda_{m} - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} - \lambda_{m},\\
+										&=& \lambda_{m}c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) + \lambda_{m}^{h} - \lambda_{m}.
+		\end{eqnarray*}
+\end{proof}
+
+It has been shown that the eigenvalues converge to the exact eigenvalues as $h \rightarrow 0$.
+So from this result, it only remains to show that $c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$.
+
+At this point, another assumption must be made.
+Assume that there are not eigenvalues with multiplicity more than 1.
+In other words, all the eigenvalues correspond only to one eigenfunction.
+In \cite{SF73}, the authors mention that for repeated eigenvalues, then the eigenfunctions can be chosen so that the main convergence results hold.
+This case is ommited in this dissertation.
+
+\newtheorem{Lem_6}[Lem_1]{Lemma} 
+\begin{Lem_6}
+	\label{Lem_6}
+	For all m and j
+	\begin{eqnarray*}
+	(\lambda_{j}^{h} - \lambda_{m}) c( Pu_{m}, u_{j}^{h}) = \lambda_{m} c( u_{m}-Pu_{m},u_{j}^{h} ).
+	\end{eqnarray*}
+\end{Lem_6}
+\begin{proof}
+	Since the term $\lambda_{m}c( Pu,u^{h}_{j})$ appears on both sides of the equation, it is only required to show that
+	\begin{eqnarray*}
+		\lambda_{j}^{h}c( Pu, u_{j}^{h} ) &=& \lambda_{m} c( u, u_{j}^{h} ).	
+	\end{eqnarray*}
+	Since both $u$ and $u_{j}^{h}$ are eigenfunctions, then
+	\begin{eqnarray*}
+		\lambda_{j}^{h}c( Pu, u_{j}^{h} ) &=& b(Pu,u_{j}^{h}),\\
+		\lambda_{m} c( u, u_{j}^{h} ) &=& b(u,u_{j}^{h}).
+	\end{eqnarray*}
+
+	Then equality follows from the definitions of the projection P.
+\end{proof}
+
+The set $\left\{u_{1}^{h},u_{2}^{h},...,u_{N}^{h}\right\}$ forms an orthonormal basis for $S^{h}$. The projection $Pu_{m}$ can be written as:
+\begin{eqnarray}
+	Pu_{m} &=& \sum_{j=1}^{N} c( P u_{m} ,u_{j}^{h}) u_{j}^{h}. \label{CV1}
+\end{eqnarray}
+
+From Lemma \ref{Lem_6}, it follows that $c( P_{m},u_{j}^{h} )$ is small if $\lambda_{m}^{h}$ is not close to $\lambda_{j}$.
+Therefore (\ref{CV1}) tells us that $Pu_{m}$ is close to $u_{m}^{h}$.
+The estimate for $Pu_{m} - u_{m}^{h}$ will follow from this result.
+
+Following the convergence of the eigenvalues, $\exists \rho > 0$ and $\exists \delta > 0$ such that if $h<\delta$,
+\begin{eqnarray}
+|\lambda_{m} - \lambda_{j}^{h}| &>& \rho \ \ \textrm{ for all } \ j = 1,2,...,N.
+\end{eqnarray}
+Therefore
+\begin{eqnarray}
+\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|} &\leq & \rho \ \ \textrm{ for all } \ j = 1,2,...,N.
+\end{eqnarray}
+
+To simplify the notation, let $\beta = c(Pu_m,Pu_m^h)$.
+
+\newtheorem{Lem_7}[Lem_1]{Lemma} 
+\begin{Lem_7}
+	\label{Lem_7}
+	\begin{eqnarray*}
+		||Pu - \beta Pu^h_m||_{W}^{2} &\leq & {\rho}^{2} ||u_{m} - Pu_{m}||_{W}^{2}.
+	\end{eqnarray*}
+\end{Lem_7}
+\begin{comment}
+\begin{proof}
+
+Using Lemma \ref{Lem_6}:
+\begin{eqnarray*}
+||Pu - \beta u_{m}^{h}||_{W}^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2},\\
+				&\leq & \rho^{2} \sum_{j\neq m} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
+				&\leq & \rho^{2} \sum_{j=1}^{N} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
+				& = & \rho^{2} ||u_m - Pu_m||_{W}^{2}.\\
+\end{eqnarray*}
+\end{proof}
+\end{comment}
+
+\newtheorem{Lem_8}[Lem_1]{Lemma} 
+\begin{Lem_8}
+	\label{Lem_8}
+	\begin{eqnarray*}
+		||u_{m} - \beta u_{m}^{h}||_{W} &\leq & \left(1+\rho\right)||u_{m}-Pu_{m}||_{W}.
+	\end{eqnarray*}
+\end{Lem_8}
+\begin{comment}
+\begin{proof}
+	\begin{eqnarray*}
+	||u_{m} - \beta u_{m}^{h}||_{W} & \leq & ||u_{m}-Pu_{m}||_{W} + ||Pu_{m} - \beta u_{m}^{h}||_{W} \\
+				& \leq & \left(1+\rho\right)||u_{m}-Pu_{m}||_{W} \ \ \textrm{ (by Lemma \ref{Lem_7})}
+	\end{eqnarray*}
+\end{proof}
+\end{comment}
+
+The proofs for lemma's \ref{Lem_7} and \ref{Lem_8} are given in \cite{SF73}.\\
+
+So again using the Approximation Theorem, it follows that $||u_{m} - \beta u_{m}^{h}||_{W}\leq Ch^{k}||u^{k}||_{W}$.
+
+\newtheorem{Lem_9}[Lem_1]{Lemma} 
+\begin{Lem_9}
+	\label{Lem_9}
+	\begin{eqnarray*}
+		||u_{m} -  u_{m}^{h}||_{W} &\leq & 2||u_{m}-\beta u^{h}_{m}||_{W}.
+	\end{eqnarray*}
+\end{Lem_9}
+\begin{proof}
+	\begin{eqnarray*}
+	||u_{m} - u_{m}^{h}||_{W} &=& ||u_{m} - \beta u_{m}^{h} + \beta u_{m}^{h} - u_{m}^{h}||_{W}, \\
+						& \leq & ||u_{m} - \beta u_{m}^{h}||_{W} + ||\beta u_{m}^{h} - u_{m}^{h}||_{W}, \\
+						& = & 2||u_{m} - \beta u_{m}^{h}||_{W}.	
+	\end{eqnarray*}
+\end{proof}
+
+Therefore t $||u_{m} -  u_{m}^{h}||_{W} \leq Ch^{k}||u^{k}||_{W}$. So for any $\epsilon >0$ , a $\delta >0$ can be found such that if $h < \delta$, $||u_{m} -  u_{m}^{h}||_{W} < \epsilon$.
 
@@
 The assumption is that the basis of $S^h$ consists of polynomials.
-With this assumptions, the semi-norm $|u|_H$ is equal to the norm $||u||$.
+With this assumptions, the semi-norm $|u|_H$ is equal to the norm $||u||_{W}$.
 This approximation theorem can be rewritten as
@@
 	\begin{equation*}
-		||(\Pi u)^{(m)} - u^{(m)}|| \leq C h^{k-m} || u^{(k)}|| \ \text{ for } m = 0,1,...,k.
+		||(\Pi u)^{(m)} - u^{(m)}||_{W} \leq C h^{k-m} || u^{(k)}||_{W} \ \text{ for } m = 0,1,...,k.
 	\end{equation*}
@@
 This will be referred to as the approximation theorem in this section.
-
-Let $E_j \in V$ denote the eigenspace spanned by the exact eigenvectors $\left\{u_1,u_2,...,u_j \right\}$ for $j = 1,2,...,m$.
-
-Then consider the subspace $S_j$ of $S^h$ where
-\begin{equation*}
-	S_j = PE_j \ \text{ for } j = 1,2,...,m.
-\end{equation*} The elements $Py_i$ are the projections of the eigenfunctions $u_i$ into the space $S^h$.
-These projections $Py_i$ are not necessarily equal to $u^h_j \in S^h$, but it can be close.
-The situation is not simple.
-It is possible that $S_j$ is not a subspace of $S^h$.
-Assume that the dimension of $S^h$ is large enough
-
-\vspace{20mm}
-
-(It is possible that $Py_k = 0$ for large $k$.)
-
-Let $B_m = \left\{u \in e_m \ | \ ||u|| = 1 \right\}$ and define $\mu_m = \inf\left\{(Pu,Pu \ | \ u \in B_m)\right\}$.
-
-The first step to obtain estimates for the eigenvalues, it to show that the elements of $B_m$ are linearly independent.
-In the first part we follow the approach in \cite{Zie2000} (A Computable Spectral Theorem - Martin Ziegler - 2000 ?).
-The author introduced the quantity $\mu_m$.
-
-\newtheorem{Prop_1}{Proposition}
-\begin{Prop_1}
- $\mu_{m} > 0$ if and only if $\dim S_{m} = m$. \label{sym:mu}
-\end{Prop_1}
-\begin{proof}
-	To show that the dimension of $S_m = m$, suppose that the elements of $B_m$ are linearly dependent.
-Then there exists a $u \in B_m$ such that $Pu = 0$ and consequently $\mu_m = 0$.
-The result follows from the contra-positive.
-\end{proof}
-
- Recall the definition of the Rayleigh quotient R in \eqref{Rayleigh}.
-
-\newtheorem{Prop_2}[Prop_1]{Proposition}
-\begin{Prop_2}
-	\label{Prop_2}
-	$\lambda^{h}_{m} \leq \max R(Pu) \ \text{ for } u \in B_{m}$
-\end{Prop_2}
-\begin{proof}
-	Since $\dim S_{m} = m$, following from the minmax principle
-	\begin{equation*}
-		\lambda_m^h \leq \max R(v) \ \text{ for } v \in S_m.
-	\end{equation*}
-
-	Take an arbitrary nonzero $v \in S_m$. Then there exists a $Py \in E_m$ such that $v = Py$.
-
-	Now we take an arbitrary $v \in S_{m}$, $v \neq 0$.
-Then there exists a $u \in E_{m}$ such that $Py = v$.
-This $Py$ is the projection into $S_m$ of some $u \in E_m$ (which is also $\displaystyle \frac{1}{||u||}u \in B_m$).
-
-	Next we show that $R(||u||^{-1}u) = R(u)$:
-
-	\[ \frac{b\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)}{c\left(\frac{1}{||u||}u,\frac{1}{||u||}u\right)} = \frac{b(u,u)}{c(u,u)} = R(u). \]
-
-	So finally,
-	\begin{eqnarray*}
-	\lambda_{m}^{h} &\leq & \max R(v) \ \text{ for } \ v \in S_{m},\\
-						&=& \max R(Pu) \ \text{ for } \ u \in E_{m},\\
-						&=& \max R(Pu) \ \text{ for } \ u \in B_{m}.
-	\end{eqnarray*}
-\end{proof}
-
-%\newpage
-In the textbook, the authors show that the eigenfunctions are orthogonal. But they do so using matrix representations of the eigenvalue problem. A different method can be used to show this.
-
-Pick any $i,j \in \mathbb{N}$ such that $i,j \leq m$. Let $v_{i},v_{j} \in V$ be arbitrary, then
-\begin{eqnarray*}
-	b(u_{i},u_{i}) &=& \lambda_{i}c(u_{i},u_{i}),\\
-	b(u_{j},u_{j}) &=& \lambda_{j}c(u_{j},u_{j}).
-\end{eqnarray*}
-Now pick $u_{i} = u_{j}$ and $u_{j} = u_{i}$. Then
-\begin{eqnarray*}
-	b(u_{i},u_{j}) &=& \lambda_{i}c(u_{i},u_{j}),\\
-	b(u_{j},u_{i}) &=& \lambda_{j}c(u_{j},u_{i}).
-\end{eqnarray*}
-Then using the symmetry of $b(\cdot,\cdot)$ and $c( \cdot, \cdot )$, and subtracting,
-\begin{eqnarray*}
-	0 &=& (\lambda_{i} - \lambda_{j})c( u_{i}, u_{j} )
-\end{eqnarray*}
-So if $i \neq j$ then $\lambda_{i} \neq \lambda_{j}$. Therefore $u_{i}$ and $u_{j}$ must be orthogonal.
-
-And as mentioned previously, $||u|| = 1$.
-
-The next steps in the textbook \cite{SF73} contains proofs with multiple results. In an attempt to better understand the results, the proofs are broken up into smaller proofs.
-
-\newtheorem{Lem_1}{Lemma} 
-\begin{Lem_1}
-	\label{Lem_1}
-	$\displaystyle \lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}$
-\end{Lem_1}
-\begin{proof}
-	Consider the linearity of the bilinear form $b$, and fact that any $u \in E_m$ can be expressed as a linear combination $u = \sum_{i=1}^{m} c_{i}u_{i}$. Then
-	\begin{eqnarray*}
-	b(u,u) &=& b\left(\sum_{i=1}^{m} c_{i}u_{i},\sum_{j=1}^{m} c_{j}u_{j}\right),\\
-			&=& \sum_{i=1}^{m} c_{i}\sum_{j=1}^{m} c_{j} b(u_{i},u_{j}).
-	\end{eqnarray*}
-
-	The summation parameters can be merged into a single parameter. Then
-	\begin{eqnarray*}
-		b(u,u)  & = & \sum_{i=1}^{m} c_{i}^{2} \lambda_{i} u_i,\\
-				& \leq & \lambda_{m}\sum_{i=1}^{m} c_{i}^{2} u_i,\\
-				& = & \lambda_{m}||u||^2.
-	\end{eqnarray*} for all $u \in B_m$.\\
-
-	And since $B_{m} \subset E_{m}$, $b(Pu,Pu) \leq \lambda_{m}$ for all $u\in B_{m}$\\
-
-	Using the Rayleigh quotient, and the definition of $\mu_{m}^{h}$, 
-	\begin{eqnarray*}
-		R(Pu) &=& \frac{b(Pu,Pu)}{c(Pu,Pu)},\\
-			&=& \frac{b(Pu,Pu)}{||Pu||^{2}},\\
-			&\leq & \frac{\lambda_{m}}{\mu_{m}^{h}}.
-	\end{eqnarray*}
-
-	Together with Proposition \ref{Prop_2} it follows that
-	\begin{eqnarray*}
-		\lambda_{m}^{h} \leq \frac{\lambda_{m}}{\mu_{m}^{h}}.
-	\end{eqnarray*}
-\end{proof}
-
-Following Lemma \ref{Lem_1}, and since $\lambda_{i}^{h} \geq \lambda_{i}$ it follows that $0 < \mu_{m}^{h} \leq 1$. It is now possible to define the `error bound' in \cite{SF73}:
-\begin{eqnarray*}
-	\sigma_{m}^{h} = 1 - \mu_{m}^{h}.
-\end{eqnarray*}
-
-\newtheorem{Cor_1}[Prop_1]{Proposition}
-\begin{Cor_1}
-	$0 \leq \sigma_{m}^{h} < 1$ and $\lambda_{m}^{h} - \lambda_{m} \leq \lambda_{m}^{h}\sigma_{m}^{h}$
-\end{Cor_1}
-\begin{proof}
-	Starting with the result of Lemma \ref{Lem_1},
-	\begin{align*}
-		\lambda_{m}^{h} &\leq \frac{\lambda_{m}}{\mu_{m}^{h}}, \\
-		\lambda_{m}^{h}\mu_{m}^{h} &\leq \lambda_{m}. \\
-	\end{align*}
-	This is equivalent to
-	\begin{align*}
-		-\lambda_{m} &\leq -\lambda_{m}^{h}\mu_{m}^{h}. 
-	\end{align*}
-	Add $\lambda_{m}^{h}$ to both sides
-	\begin{align*}
-		\lambda_{m}^{h} - \lambda_{m} &\leq \lambda_{m}^{h} - \lambda_{m}^{h}\mu_{m}^{h}. 
-	\end{align*}
-	And finally using the error bound $\sigma_{m}^{h} = 1 - \mu_{m}^{h}$,
-	\begin{align*}
-		\lambda_{m}^{h} - \lambda_{m} &\leq \lambda_{m}^{h}\sigma_{m}^{h}.
-	\end{align*}
-\end{proof}
-
-This result gives an error estimate for the eigenvalues.
-To prove the convergence of the eigenvalues, it is necessary to prove that the error estimate $\sigma_{m}^{h}$ converges to zero as $h \rightarrow 0$.
-
-\newtheorem{Prop_3}[Prop_1]{Proposition} 
-\begin{Prop_3}
-	\label{Prop_3}
-	$\sigma_{m}^{h} = \max\left\{ 2c( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}$
-\end{Prop_3}
-\begin{proof}
-	Let $u \in B_{m}$. Then
-	\begin{eqnarray*}
-		||u - Pu||^{2} &=& c( u - Pu, u - Pu ), \\
-						&=& c( u, u ) - 2 c( u, Pu ) + c( Pu, Pu ), \\
-						&=& 2c( u, u ) - 2 c( u, Pu ) + c( Pu, Pu ) - c( u, u ),\\
-						&=& 2c( u, u - Pu ) + c( Pu, Pu ) - c( u, u ).\\
-	\end{eqnarray*}
-	consequently
-	\begin{eqnarray*}
-		c( u, u ) - c( Pu, Pu )  & = & 2c( u, u - Pu ) - ||u - Pu||^{2}.
-	\end{eqnarray*}
-
-	Since $u \in B_{m}$, $||u||^{2} = 1$ and hence
-	\begin{eqnarray*}
-		1 - ||Pu||^{2}  & = & 2c( u, u - Pu ) - ||u - Pu||^{2}.
-	\end{eqnarray*}
-
-	On the right hand side, $1 - ||Pu||^{2} \leq 1 - \mu_{m}^{h} = \sigma_{m}^{h}$ for all $u \in B_{m}$. So then it must be that
-	\begin{eqnarray*}
-	\sigma_{m}^{h} = \max\left\{ 2c( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right \}
-	\end{eqnarray*}
-\end{proof}
-
-Proposition \ref{Prop_3} is a result given in \cite{SF73} without explaining how it is derived.
-
-Introduce some new notation for ease of writing. For any $u \in E_{m}$, let $u^{*} = \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}$ where $u = \sum_{i=1}^{m} c_{i}u_{i}$.
-
-\newtheorem{Prop_4}[Prop_1]{Proposition} 
-\begin{Prop_4}
-	\label{Prop_4}
-	For any $u \in E_{m}$
-		\begin{eqnarray*}
-		c( u, u - Pu ) = b(u^{*} - Pu^{*}, u -Pu)
-		\end{eqnarray*}
-\end{Prop_4}
-\begin{proof}
-	For any $i = 1,2,...,m$,
-	\begin{eqnarray*}
-	\lambda_{i}c( u_{i},u-Pu ) &=&  b(u_{i}, u-Pu),\\
-								&=& b(u_{i}, u-Pu) - b(u-Pu,Pu_{i}) \ \textrm{ (Rayleigh-Ritz Projection)},\\
-								&=&  b(u_{i}, u-Pu) - b(Pu_{i},u-Pu),\\
-								&=&  b(u_{i}-Pu_{i}, u-Pu).
-	\end{eqnarray*}
-	Multiplying by $c_{i}\lambda_{i}^{-1}$ and summation over i gives:
-	\begin{eqnarray*}
-	\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}\lambda_{i}c( u_{i},u-Pu ) &=& \sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}b(u_{i}-Pu_{i}, u-Pu),\\
-								&=& b(\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}u_{i}-\sum_{i=1}^{m} c_{i}\lambda_{i}^{-1}Pu_{i}, u-Pu),\\
-										&=& b(u^{*}-Pu^{*}, u-Pu).
-	\end{eqnarray*}
-	Therefore $c( u,u-Pu ) = b(u^{*}-Pu^{*}, u-Pu)$.
-\end{proof}
-
-\newtheorem{Lem_2}[Lem_1]{Lemma} 
-\begin{Lem_2}
-	\label{Lem_2}
-	$\sigma_{m}^{h} \leq \max \left\{2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}$
-\end{Lem_2}
-\begin{proof}
-	From Proposition \ref{Prop_3},
-	\begin{eqnarray*}
-		\sigma_{m}^{h} & = & \max\left\{ 2c( u,u-Pu )-||u-Pu||^{2} \ | \ u \in B_{m} \right\}, \\
-					& \leq & \max\left\{ 2c( u,u-Pu ) \ | \ u \in B_{m} \right\}. \\
-	\end{eqnarray*}
-
-	From Proposition \ref{Prop_4}, 
-	\begin{eqnarray*}
-		\sigma_{m}^{h} = \max\left\{ 2 b(u^{*}-Pu^{*}, u-Pu) \ | \ u \in B_{m} \right\}.
-	\end{eqnarray*}
-
-	Using the Schwartz inequality,
-	\begin{eqnarray*}
-		b(u^{*} - Pu^{*}, u -Pu) & \leq & ||u^{*} - Pu^{*}||||u -Pu||.
-	\end{eqnarray*}
-
-	Finally,
-	\begin{eqnarray*}
-		\sigma_{m}^{h} & \leq & \max\left\{ 2||u^{*}- Pu^{*}|| ||u-Pu|| \ | \ u \in B_{m} \right\}.
-	\end{eqnarray*}
-\end{proof}
-
-\newtheorem{Prop_5}[Prop_1]{Proposition} 
-\begin{Prop_5}
-	\label{Prop_5}
-	For any $\epsilon > 0$, there exists a $\delta >0$ such that for $h<\delta$,
-	\begin{eqnarray*}
-	||u^{*} - Pu^{*}|| < \epsilon \ \textrm{ for each } u \in B_{m}\\
-	||u - Pu|| < \epsilon \ \textrm{ for each } u \in B_{m}
-	\end{eqnarray*}
-\end{Prop_5}
-\begin{proof}
-	Consider a set of basis functions $\Phi \subset S^h$ such that $\phi^(k) = 0$ for each $\phi \in \Phi$.
-
-	From the Rayleigh-Ritz Projection, $Pu$ is the closest element in $S^h$ to $u$. In particular, $||u-Pu||\leq ||u-\Pi u||$, where $\Pi u$ is the interpolation of $u$ into $S^h$.
-
-	From the Approximation Theorem given at the beginning of section \ref{sec:est}, is follows that
-	\begin{eqnarray*}
-		||u - \Pi u|| \leq Ch^{k}||u^{(k)}||
-	\end{eqnarray*}
-
-	So for any $\epsilon > 0$, a $\delta$ can be found such that if $h<\delta$ then
-	\begin{eqnarray*}
-		||u - Pu|| \leq ||u - \Pi u|| \leq \epsilon
-	\end{eqnarray*}
-	A similar argument for $||u^{*} - Pu^{*}||$ proves the theorem.
-\end{proof}
-
-\newtheorem{Lem_3}[Lem_1]{Lemma} 
-\begin{Lem_3}
-	\label{Lem_3}
-	For any $\epsilon >0$ there exists a $\delta > 0$ such that
-	\begin{eqnarray*}
-	\sigma_{m}^{h} < \epsilon \ \textrm{ if } \ h < \delta
-	\end{eqnarray*}
-\end{Lem_3}
-\begin{proof}
-	For any $\epsilon > 0$ there exists a $\delta > 0$ such that if $h<\delta$, then
-	\begin{eqnarray*}
-	||u-Pu|| < \epsilon \ \textrm{ for each } \ u \in B_{m}
-	\end{eqnarray*}
-	This result, together with Lemma \ref{Lem_2} and Proposition \ref{Prop_5} gives the result.
-\end{proof}
-
-\newtheorem{Lem_4}[Lem_1]{Lemma} 
-\begin{Lem_4}
-	\label{Lem_4}
-	There exists a $\delta > 0$ such that for $h < \delta$
-	\begin{eqnarray*}
-	\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}
-	\end{eqnarray*}
-\end{Lem_4}
-\begin{proof}
-	Using Lemma \ref{Lem_3}, choose $\delta$ such that $\sigma_{m}^{h} < \frac{1}{2}$. Then by Lemma \ref{Lem_1} gives that $\lambda_{m}^{h} < 2\lambda_{m}$.\\
-
- 	Therefore $\lambda_{m}^{h} - \lambda_{m} \leq 2\lambda_{m}\sigma_{m}^{h}$.
-\end{proof}
-
-The convergence of the eigenvalues are now proved.
-
-\subsection{Convergence of the eigenfunctions}
-The next step is to show the convergence of the eigenfunctions. The problem can be formulated using the following result.
-
-\newtheorem{Lem_5}[Lem_1]{Lemma} 
-\begin{Lem_5}
-	\label{Lem_5}
-	\begin{eqnarray*}
-		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& \lambda_{m}c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h} ) + \lambda_{m}^{h} - \lambda_{m}
-		\end{eqnarray*}
-\end{Lem_5}
-\begin{proof}
-	\begin{eqnarray*}
-		b(u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) &=& b(u_{m},u_{m}) - 2b(u_{m},u^{h}_{m}) + b(u^{h}_{m},u^{h}_{m}) \\
-										&=& \lambda_{m} c( u_{m}, u_{m} ) - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h}c( u_{m}^{h},u_{m}^{h} )\\
-										&=&  \lambda_{m} - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} \\
-										&=& 2\lambda_{m} - 2\lambda_{m} c( u_{m}, u^{h}_{m} ) + \lambda_{m}^{h} - \lambda_{m}\\
-										&=& \lambda_{m}c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) + \lambda_{m}^{h} - \lambda_{m}
-		\end{eqnarray*}
-\end{proof}
-
-It has been shown that the eigenvalues converge to the exact eigenvalues as $h \rightarrow 0$.
-So from this result, it only remains to show that $c( u_{m}-u_{m}^{h},u_{m}-u_{m}^{h}) \rightarrow 0$ as $h \rightarrow 0$.
-
-At this point, another assumption must be made.
-Assume that there are not eigenvalues with multiplicity more than 1.
-In other words, all the eigenvalues correspond only to one eigenfunction.
-In \cite{SF73}, the authors mention that for repeated eigenvalues, then the eigenfunctions can be chosen so that the main convergence results hold.
-This case is ommited in this dissertation.
-
-\newtheorem{Lem_6}[Lem_1]{Lemma} 
-\begin{Lem_6}
-	\label{Lem_6}
-	For all m and j
-	\begin{eqnarray*}
-	(\lambda_{j}^{h} - \lambda_{m}) c( Pu_{m}, u_{j}^{h}) = \lambda_{m} c( u_{m}-Pu_{m},u_{j}^{h} )
-	\end{eqnarray*}
-\end{Lem_6}
-\begin{proof}
-	Since the term $\lambda_{m}c( Pu,u^{h}_{j})$ appears on both sides of the equation, it is only required to show that
-	\begin{eqnarray*}
-		\lambda_{j}^{h}c( Pu, u_{j}^{h} ) &=& \lambda_{m} c( u, u_{j}^{h} ).	
-	\end{eqnarray*}
-	Since both $u$ and $u_{j}^{h}$ are eigenfunctions, then
-	\begin{eqnarray*}
-		\lambda_{j}^{h}c( Pu, u_{j}^{h} ) &=& b(Pu,u_{j}^{h})\\
-		\lambda_{m} c( u, u_{j}^{h} ) &=& b(u,u_{j}^{h})
-	\end{eqnarray*}
-
-	Then equality follows from the definitions of the projection P.
-\end{proof}
-
-The set $\left\{u_{1}^{h},u_{2}^{h},...,u_{N}^{h}\right\}$ forms an orthonormal basis for $S^{h}$. The projection $Pu_{m}$ can be written as:
-\begin{eqnarray}
-	Pu_{m} &=& \sum_{j=1}^{N} c( P u_{m} ,u_{j}^{h}) u_{j}^{h}. \label{CV1}
-\end{eqnarray}
-
-From Lemma \ref{Lem_6}, it follows that $c( P_{m},u_{j}^{h} )$ is small if $\lambda_{m}^{h}$ is not close to $\lambda_{j}$.
-Therefore (\ref{CV1}) tells us that $Pu_{m}$ is close to $u_{m}^{h}$.
-The estimate for $Pu_{m} - u_{m}^{h}$ will follow from this result.
-
-Following the convergence of the eigenvalues, $\exists \rho > 0$ and $\exists \delta > 0$ such that if $h<\delta$,
-\begin{eqnarray}
-|\lambda_{m} - \lambda_{j}^{h}| &>& \rho \ \ \textrm{ for all } \ j = 1,2,...,N.
-\end{eqnarray}
-Therefore
-\begin{eqnarray}
-\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|} &\leq & \rho \ \ \textrm{ for all } \ j = 1,2,...,N.
-\end{eqnarray}
-
-To simplify the notation, let $\beta = c(Pu_m,Pu_m^h)$.
-
-\newtheorem{Lem_7}[Lem_1]{Lemma} 
-\begin{Lem_7}
-	\label{Lem_7}
-	\begin{eqnarray*}
-		||Pu - \beta Pu^h_m||^{2} &\leq & {\rho}^{2} ||u_{m} - Pu_{m}||^{2}
-	\end{eqnarray*}
-\end{Lem_7}
-\begin{comment}
-\begin{proof}
-
-Using Lemma \ref{Lem_6}:
-\begin{eqnarray*}
-||Pu - \beta u_{m}^{h}||^{2} &=& \sum_{j\neq m} \left(\frac{\lambda_{m}}{|\lambda_{m} - \lambda_{j}^{h}|}\right)^{2} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2},\\
-				&\leq & \rho^{2} \sum_{j\neq m} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
-				&\leq & \rho^{2} \sum_{j=1}^{N} c( u_{m} - Pu_{m} ,u_{j}^{h})^{2}, \\
-				& = & \rho^{2} ||u_m - Pu_m||^{2}.\\
-\end{eqnarray*}
-\end{proof}
-\end{comment}
-
-\newtheorem{Lem_8}[Lem_1]{Lemma} 
-\begin{Lem_8}
-	\label{Lem_8}
-	\begin{eqnarray*}
-		||u_{m} - \beta u_{m}^{h}|| &\leq & \left(1+\rho\right)||u_{m}-Pu_{m}||
-	\end{eqnarray*}
-\end{Lem_8}
-\begin{comment}
-\begin{proof}
-	\begin{eqnarray*}
-	||u_{m} - \beta u_{m}^{h}|| & \leq & ||u_{m}-Pu_{m}|| + ||Pu_{m} - \beta u_{m}^{h}|| \\
-				& \leq & \left(1+\rho\right)||u_{m}-Pu_{m}|| \ \ \textrm{ (by Lemma \ref{Lem_7})}
-	\end{eqnarray*}
-\end{proof}
-\end{comment}
-
-The proofs for lemma's \ref{Lem_7} and \ref{Lem_8} are given in \cite{SF73}.\\
-
-So again using the Approximation Theorem, it follows that $||u_{m} - \beta u_{m}^{h}||\leq Ch^{k}||u^{k}||$.
-
-\newtheorem{Lem_9}[Lem_1]{Lemma} 
-\begin{Lem_9}
-	\label{Lem_9}
-	\begin{eqnarray*}
-		||u_{m} -  u_{m}^{h}|| &\leq & 2||u_{m}-\beta u^{h}_{m}||
-	\end{eqnarray*}
-\end{Lem_9}
-\begin{proof}
-	\begin{eqnarray*}
-	||u_{m} - u_{m}^{h}|| &=& ||u_{m} - \beta u_{m}^{h} + \beta u_{m}^{h} - u_{m}^{h}||, \\
-						& \leq & ||u_{m} - \beta u_{m}^{h}|| + ||\beta u_{m}^{h} - u_{m}^{h}||, \\
-						& = & 2||u_{m} - \beta u_{m}^{h}||.	
-	\end{eqnarray*}
-\end{proof}
-
-Therefore t $||u_{m} -  u_{m}^{h}|| \leq Ch^{k}||u^{k}||$. So for any $\epsilon >0$ , a $\delta >0$ can be found such that if $h < \delta$, $||u_{m} -  u_{m}^{h}|| < \epsilon$.
 \end{document}

### 2023-11-26 files/Chapter5/2D_FEM.tex
Chapter 3

@@
 
-These functions are chosen as bi-cubic functions $\phi_i$.
+These functions are chosen as piecewise Hermite bi-cubic functions $\phi_i$.
 Simpler bi-linear functions can also be used, however the use of the bi-cubic basis functions results in faster convergence and also the benefit of obtaining the derivatives of the solution at the expense of more complexity.
@@
 Consider a set of 
-For this dissertation, we consider bi-cubic basis functions, however bi-linear basis functions can also be used.
+For this dissertation, we consider piecewise Hermite bi-cubic basis functions, however piecewise bi-linear basis functions can also be used.
 

### 2023-11-26 files/Chapter5/3D_FEM.tex
Chapter 3

@@
 
-For the this three-dimensional model, tri-cubix basis functions are used.
-These basis functions are an extension of the Hermite cubic basis functions from the two-dimensional model.
-Although this is more complex than using tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
+For the this three-dimensional model, piecewise Hermite tri-cubic basis functions are used.
+Although this is more complex than using piecwise tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
 
@@
 Consider a set of $n$ linear independent three-dimensional scalar valued functions $\delta_i$.
-In this dissertation, these functions are tri-cubic basis functions (an extension of Hermite cubics from the two-dimensional model into three-dimensions).
+In this dissertation, these functions are piecewise Hermite tri-cubic basis functions (an extension of Hermite cubics from the two-dimensional model into three-dimensions).
 The functions $\delta_i$ satisfying the conditions of the test function space $T(\Omega)$ are called the admissible basis functions.

### 2023-11-29 files/Chapter3/femconvergence.tex
chapter 3

@@
 \begin{equation}
-	b(u,v) = \lambda (u,v) \label{GEVP}
+	b(u,v) = \lambda c(u,v) \label{GEVP}
 \end{equation} for each $v \in V$.
@@
 \subsubsection*{Problem $E^h$}
-Find $u^h \in S^h$ such that $u^h \neq 0$ and \[b(u^h, v) = \lambda^h(u^h,v) \textrm{ for all } v \in S^h.\]
+Find $u^h \in S^h$ such that $u^h \neq 0$ and \[b(u^h, v) = \lambda^h c(u^h,v) \textrm{ for all } v \in S^h.\]
 
@@
 
-The pair $(\lambda^n, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$. It is necessary to some of the teory to make the connection.
+The pair $(\lambda^n, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$. It is necessary to some of the theory to make the connection.
 
@@
 The situation is not simple.
-It is possible that $Py_k = 0$ for large $k$ Assume that the dimension of $S^h$ is large enough, substantially larger than $m$.
+It is possible that $Pu_k = 0$ for large $k$ Assume that the dimension of $S^h$ is large enough, substantially larger than $m$.
 
@@
 	Now we take an arbitrary $v \in S_{m}$, $v \neq 0$.
-Then there exists a $u \in E_{m}$ such that $Py = v$.
-This $Py$ is the projection into $S_m$ of some $u \in E_m$ (which is also $\displaystyle \frac{1}{||u||_{W}}u \in B_m$).
+Then there exists a $u \in E_{m}$ such that $Pu = v$.
+This $Pu$ is the projection into $S_m$ of some $u \in E_m$ (which is also $\displaystyle \frac{1}{||u||_{W}}u \in B_m$).
 
@@
 
-	From the Rayleigh-Ritz Projection, $Pu$ is the closest element in $S^h$ to $u$. In particular, $||u-Pu||_{W}\leq ||u-\Pi u||_{W}$, where $\Pi u$ is the interpolation of $u$ into $S^h$.
+	$Pu$ is the closest element in $S^h$ to $u$. In particular, $||u-Pu||_{W}\leq ||u-\Pi u||_{W}$, where $\Pi u$ is the interpolation of $u$ into $S^h$.
 
@@
 
-Therefore t $||u_{m} -  u_{m}^{h}||_{W} \leq Ch^{k}||u^{k}||_{W}$. So for any $\epsilon >0$ , a $\delta >0$ can be found such that if $h < \delta$, $||u_{m} -  u_{m}^{h}||_{W} < \epsilon$.
+Therefore $||u_{m} -  u_{m}^{h}||_{W} \leq Ch^{k}||u^{k}||_{W}$. So for any $\epsilon >0$ , a $\delta >0$ can be found such that if $h < \delta$, $||u_{m} -  u_{m}^{h}||_{W} < \epsilon$.
 

### 2023-11-30 files/Chapter3/femconvergence.tex
Chapter 3 final

@@
 \section{FEM computation of eigenvalues and eigenfunctions}
-\textcolor{red}{Change H to W?}
-
-Let $H$ be a Hilbert space with the inner product $c(\cdot,\cdot)$ and induced norm $||\cdot||_{W}$.
-Let $V$ be a linear subspace of $H$, with inner product defined by the bilinear form $b(\cdot,\cdot)$.
+Let $W$ be a Hilbert space with the inner product $c(\cdot,\cdot)$ and induced norm $||\cdot||_{W}$.
+In \cite{SF73}, the authors use a Hilbert space $H$, with inner product $(\cdot, \cdot)$ and induced norm $||\cdot||$.
+We remain with the notation that is consistent with this dissertation.
+Let $V$ be a linear subspace of $W$, with inner product defined by the bilinear form $b(\cdot,\cdot)$.
 It is assumed that the bilinear form $b$ is symmetric and that the assumptions in Section \ref{sec:existence:ModalAnalysis} holds.
@@
 
-The pair $(\lambda^n, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$. It is necessary to some of the theory to make the connection.
+The pair $(\lambda^n, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$. It is necessary to understand some of the theory to make the connection.
 
@@
 In section \ref{sec:estimating_the_eigenvalues} it is proved that the error $| \lambda_k^h - \lambda_k|$ is large when $k$ is large.
-It is for example possible that $|\lambda^h_1 - \lambda_1|$ is sufficiently small while $\lambda^h_k$ cannot even be considered an approximation of $\lambda_k$ when $\displaystyle k > \frac{1}{2}N_e$.
+It is for example possible that $|\lambda^h_1 - \lambda_1|$ is sufficiently small while $\lambda^h_k$ cannot even be considered as an approximation for $\lambda_k$ when $\displaystyle k > \frac{1}{2}N_e$.
 
@@
 \end{equation}
-
-\textcolor{red}{********* Hou voorlopig hier *************}
-\subsubsection*{Properties of eigenvalues}
-It is well known that the eigenvalues of a eigenvalue problem such as \eqref{GEVP} form an infinite sequence $(\lambda_i)$.
-Assume that the eigenvalues $\lambda_i$ can be ordered $\lambda_1 \leq \lambda_2 \leq \lambda_3 \leq ...$ and denote the corresponding eigenfunctions $u_i$.
-
-Since any multiple of a eigenfunction is still an eigenfunction, the eigenfunctions can be normalized so that $||u_i||_{W} = 1$ for all $i$.
-
-Fix $m \in \mathbb{N}$.
-Let $\left\{ \phi_k \in V | k = 1,2,...,m \right\}$ be a set of linear independent admissible basis functions.
-Define $S^h := \text{span}\left\{\phi_k \in V | k = 1,2,...,m\right\}$ so that $S^h$ is a finite dimensional subspace of V.
-\label{sym:natural} \label{sym:Sh1}
-
-The ordering of the eigenvalues remains valid in a finite dimensional space.
-The eigenvalues in the space $S^h$ is denoted as $\lambda_i^h$ with corresponding normalized eigenfunction $u^h_i$ for $i = 1,2,...,m$.
-
-Also any subspace of $S^h$ will also be a subspace of $V$. So the minmax principle applies and a lower bound for the eigenvalues can be found:
-\begin{equation}
-	\lambda_i \leq \lambda_i^h.
-\end{equation}
-\textcolor{red}{********* Hou voorlopig hier *************}
 
@@
 
-\newtheorem{Prop_5}[Prop_1]{Proposition} 
-\begin{Prop_5}
-	\label{Prop_5}
-	For any $\epsilon > 0$, there exists a $\delta >0$ such that for $h<\delta$,
+% \newtheorem{Prop_5}[Prop_1]{Proposition} 
+% \begin{Prop_5}
+% 	\label{Prop_5}
+% 	For any $\epsilon > 0$, there exists a $\delta >0$ such that for $h<\delta$,
+% 	\begin{eqnarray*}
+% 	||u^{*} - Pu^{*}||_{W} < \epsilon \ \textrm{ for each } u \in B_{m},\\
+% 	||u - Pu||_{W} < \epsilon \ \textrm{ for each } u \in B_{m}.
+% 	\end{eqnarray*}
+% \end{Prop_5}
+% \begin{proof}
+% 	Consider a set of basis functions $\Phi \subset S^h$ such that $\phi^(k) = 0$ for each $\phi \in \Phi$.
+\subsubsection*{Assumption}
+For any $\epsilon > 0$ there exists a $\delta > 0$ such that if $h<\delta$, then
 \begin{eqnarray*}
-	||u^{*} - Pu^{*}||_{W} < \epsilon \ \textrm{ for each } u \in B_{m},\\
-	||u - Pu||_{W} < \epsilon \ \textrm{ for each } u \in B_{m}.
-	\end{eqnarray*}
-\end{Prop_5}
-\begin{proof}
-	Consider a set of basis functions $\Phi \subset S^h$ such that $\phi^(k) = 0$ for each $\phi \in \Phi$.
-
-	$Pu$ is the closest element in $S^h$ to $u$. In particular, $||u-Pu||_{W}\leq ||u-\Pi u||_{W}$, where $\Pi u$ is the interpolation of $u$ into $S^h$.
-
-	\textcolor{red}{Need to fix reference to approximation theorem. Need to wait until section 3.5 is done. The approximation theorem is moved to the end of section 3.5}
-
-	From the Approximation Theorem given at the beginning of section \ref{sec:est}, is follows that
-	\begin{eqnarray*}
-		||u - \Pi u||_{W} \leq Ch^{k}||u^{(k)}||_{W}.
+||u-Pu||_{W} < \epsilon \ \textrm{ for each } \ u \in B_{m}.
 \end{eqnarray*}
 
-	So for any $\epsilon > 0$, a $\delta$ can be found such that if $h<\delta$ then
-	\begin{eqnarray*}
-		||u - Pu||_{W} \leq ||u - \Pi u||_{W} \leq \epsilon.
-	\end{eqnarray*}
-	A similar argument for $||u^{*} - Pu^{*}||_{W}$ proves the theorem.
-\end{proof}
+\textbf{Remark:} $Pu$ is the closest element in $S^h$ to $u$.
+In particular, $||u-Pu||_{W}\leq ||u-\Pi u||_{W}$, where $\Pi u$ is the interpolant of $u$ in $S^h$.
+The operator $\Pi$ is treated in Section \ref{sec:approximation_theorem}.
 
@@
 \end{Lem_3}
-\begin{proof}
-	For any $\epsilon > 0$ there exists a $\delta > 0$ such that if $h<\delta$, then
-	\begin{eqnarray*}
-	||u-Pu||_{W} < \epsilon \ \textrm{ for each } \ u \in B_{m}.
-	\end{eqnarray*}
-	This result, together with Lemma \ref{Lem_2} and Proposition \ref{Prop_5} gives the result.
-\end{proof}
+
+Substitute the assumption into the estimate for $\sigma^h_m$ in Lemma \ref{Lem_2}.
 
@@
 
-The convergence of the eigenvalues follows from \eqref{eq:lem3} and \eqref{eq:lem4}.
+The convergence of the eigenvalues follows from \eqref{eq:lem3} and \eqref{eq:lem4}. An estimate of the error depends on an estimate for $u - \Pi u$, see Section \ref{sec:approximation_theorem}
 
@@
 
-\subsubsection{The approximation theorem}
-
+\section{The approximation theorem} \label{sec:approximation_theorem}
 Consider a interpolation operator $\Pi$.\label{sym:interpolation} This projection is linear, i.e.
@@
 \end{Interpolation_2}
-
-This will be referred to as the approximation theorem in this section.
 \end{document}

### 2023-12-01 files/Overview.tex
chapter 4 and overview update
Chapter 3 final
Overview

@@
 The second part concerns the convergence of the eigenvalues and eigenfunctions of a vibration problem when applying the Finite Element Method.
-This theory is presented in the textbook \cite{SF73}\textcolor{red}{Nie goed genoeg vir dinamiese probleem}.
+This theory is presented in the textbook \cite{SF73}.
 
@@
 
-\textcolor{red}{*************Copy van chapter 6******************}
-
-The first section is a discussion of the article \cite{LVV09}.
+Section 4.5 is a discussion of the article \cite{LVV09}.
 In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model.
-The authors compare the models by comparing the eigenvalues and eigenfunctions (see Chapter 2 on modal analysis).
+The authors compare the models by comparing the eigenvalues and eigenfunctions.
+(See Chapter 2 on modal analysis).
 The two-dimensional model is more complex and there are eigenvalues that are not shared between the models.
@@
 The results show that the models compare very well, even for a short and thick beam.
-As the beam gets more slender, the comparison improves.
-In this section some of the results of the article are discussed and replicated.
-
-\textcolor{red}{*******************************}
+\textcolor{red}{The results show that the shape of the beam impacts the comparison.
+The comparison improves as the beam gets more slender, but overall the comparisons are very good.}\sout{As the beam gets more slender, the comparison improves.
+In this section some of the results of the article are discussed and replicated.}
 
@@
 
-\textcolor{red}{*************hou voorlopig******************}
-
-The first section is a discussion of the article \cite{LVV09}.
+\sout{The first section is a discussion of the article \cite{LVV09}.
 In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model.
@@
 As the beam gets more slender, the comparison improves.
-In this section some of the results of the article are discussed and replicated.
-
-\textcolor{red}{*******************************}
+In this section some of the results of the article are discussed and replicated.}
 
@@
 The results show that the Reissner-Mindlin plate model compares well to the three-dimensional plate model.
-
-\end{document}
 
@@
 \textcolor{red}{493 Words}
+
+\end{document}
 

### 2023-12-01 files/Overview.tex
overview

@@
 The results show that the models compare very well, even for a short and thick beam.
-\textcolor{red}{The results show that the shape of the beam impacts the comparison.
-The comparison improves as the beam gets more slender, but overall the comparisons are very good.}\sout{As the beam gets more slender, the comparison improves.
+\textcolor{red}{The results improve as the beam gets more slender.
+This shows that the shape of the beam is important.
+The cases covered are realistic to applications.}\sout{As the beam gets more slender, the comparison improves.
 In this section some of the results of the article are discussed and replicated.}
@@
 The authors report on an experiment with forced vibration a free-free beam where the natural frequencies are measured.
-These emperical results are then compared to the theoretical results.
+These empirical results are then compared to the theoretical results.
 This result, together with the results in chapter 6, give a good picture to the validity of the Timoshenko beam theory.
-Finally the chapter is concluded by looking at a model of a cantilever beam with a tip-body with elastic interfaces.
+\sout{Finally the chapter is concluded by looking at a model of a cantilever beam with a tip-body with elastic interfaces.
 These results combine modal analysis and investigates at the behavior of the model.
-A similar model using realistic two- or three-dimensional model will be very challenging.
+A similar model using realistic two- or three-dimensional model will be very challenging.}
 
@@
 \subsubsection{Chapter 6}
-In this chapter, the main comparisons of the models are conducted. All of the sections follow the same idea and struture as the article \cite{LVV09}.
+\textcolor{red}{This chapter is an extension of the work of Section 4.5.
+In Section 4.5, the validity of the Timoshenko beam theory is investigated by comparing a Timoshenko beam model to a two-dimensional beam model.}
 
-\sout{The first section is a discussion of the article \cite{LVV09}.
-In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model.
-The authors compare the models by comparing the eigenvalues and eigenfunctions (see Chapter 2 on modal analysis).
-The two-dimensional model is more complex and there are eigenvalues that are not shared between the models.
-The authors use the mode shapes to match up the eigenvalues.
-The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues.
-The authors also consider different shapes of beams, from a short thick beam to a long slender beam.
-The results show that the models compare very well, even for a short and thick beam.
-As the beam gets more slender, the comparison improves.
-In this section some of the results of the article are discussed and replicated.}
-
-But in real-world applications, a beam is a three-dimensional model.
+In real-world applications, a beam is a three-dimensional model.
 Therefore it should be more realistic to use a three-dimensional model to investigate the validity of the Timoshenko beam theory.
@@
 
+\sout{In this chapter, the main comparisons of the models are conducted. All of the sections follow the same idea and struture as the article \cite{LVV09}.}
+
+\sout{The first section is a discussion of the article \cite{LVV09}.
+In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model.
+The authors compare the models by comparing the eigenvalues and eigenfunctions (see Chapter 2 on modal analysis).
+The two-dimensional model is more complex and there are eigenvalues that are not shared between the models.
+The authors use the mode shapes to match up the eigenvalues.
+The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues.
+The authors also consider different shapes of beams, from a short thick beam to a long slender beam.
+The results show that the models compare very well, even for a short and thick beam.
+As the beam gets more slender, the comparison improves.
+In this section some of the results of the article are discussed and replicated.}
+
 \section{500-word summary}
@@
 The higher dimensional models are a two- and three-dimensional beam and a three-dimensional plate.
-In the first chapter, the models are provided.
+The models are provided in the first chapter
 
@@
 An application of this theory is demonstrated using a cantilever Timoshenko beam.
+\textcolor{red}{Modal analysis is crucial to this dissertation.
+We show that the solution of the general vibration problem is a linear combination of the eigenvalues and eigenfunctions.
+This is the foundation of the comparisons of the models in this dissertation.}
 
@@
 The first result is from an article where the convergence of the Galerkin Approximation is proved.
-A Galerkin Approximation of the general vibration problem is derived.
-Using the Finite Element Method, this Galerkin Approximation is rewritten into an initial value problem, that has a unique solution.
+\sout{A Galerkin Approximation of the general vibration problem is derived.} Using the Finite Element Method, this Galerkin Approximation is rewritten into an initial value problem, that has a unique solution.
 The authors show that there exists error estimates that approximate the error between the general vibration problem and the initial value problem.
 The next result is from a textbook on the convergence of the eigenvalues and eigenvectors of a one-dimensional vibration problem.
-This section rewrites the textbook's results with updated notation, aiming for greater clarity and understanding.
+This is based of work done in a textbook, but the notation is updated and some proofs are expanded.
 
@@
 The method is then applied to a cantilever and a free-free beam model.
-Next is a discussion of an empirical study, that compares the natural frequencies of a physical free-free beam to the theoretical results of the Timoshenko beam theory.
-Finally an extension on a technical report of a cantilever Timoshenko beam with a tip-body and elastic interfaces.
-This model serves as an example of the application of the Timoshenko theory in a complex model and adds to the article by expanding the numerical results.
+\textcolor{red}{Thereafter, the validity of the Timoshenko beam theory is investigated, by comparing a Timoshenko beam model to a two-dimensional beam model.
+The comparison is made by comparing the eigenvalues and eigenvectors.} Next is a discussion of an empirical study, that compares the natural frequencies of a physical free-free beam to the theoretical results of the Timoshenko beam theory.
+\sout{Finally an extension on a technical report of a cantilever Timoshenko beam with a tip-body and elastic interfaces.
+This model serves as an example of the application of the Timoshenko theory in a complex model and adds to the article by expanding the numerical results.}
 
 In the fifth chapter, the Finite Element Method is applied to the two and three-dimensional models of this dissertation.
-The goal of this chapter is to obtain a numerical formula that can be used to calculate the eigenvalues and eigenvectors of the models in preparation for the final chapter where the models are compared.
+The goal of this chapter is to obtain a numerical formula \textcolor{red}{to solve the eigenvalue problems,} \sout{that can be used to calculate the eigenvalues and eigenvectors of the models in} preparation for the final chapter where the models are compared.
 
-The last chapter compares the eigenvalues and eigenvectors of the models.
-The approach is based on an article where a cantilever Timoshenko beam model is compared to a cantilever two-dimensional model.
-The article is discussed and results replicated.
-The article is then extended to a comparison of a two-dimensional model to a three-dimensional model.
-Finally, a cantilever Reissner-Mindlin plate model is compared to a cantilever three-dimensional plate model.
+The last chapter extends the numerical results of the dissertation to a comparison of a two-dimensional model to a three-dimensional beam model and a comparison of a Reissner-Mindlin plate model to a three-dimensional plate model.
 
-\textcolor{red}{493 Words}
+\textcolor{red}{WORD COUNT: 470}
 
@@
 The Galerkin approximation of this general variational problem can be derived, as well as an initial value problem using the standard Finite Element Analysis matrices.
-The article \cite{BV13} derive an error estimate for the solution of the general vartiational problem and the solution to it's Galerkin approximation.
+The article \cite{BV13} derive an error estimate for the solution of the general varitat problem and the solution to it's Galerkin approximation.
 To obtain this error estimate, the authors make two assumptions, and split the problem into a semi-discrete and a fully discrete problem.

### 2023-12-01 code/Timoshenko_beam.py

@@ -1,110 +1,0 @@
-import numpy
-import sympy
-import time
-
-A = sympy.Symbol('A')
-B = sympy.Symbol('B')
-C = sympy.Symbol('C')
-D = sympy.Symbol('D')
-x = sympy.Symbol('x')
-m = sympy.Symbol('m')
-o = sympy.Symbol('o')
-a = sympy.Symbol('a')
-l = sympy.Symbol('l')
-k = sympy.Symbol('k')
-t = sympy.Symbol('t')
-
-class TimoshenkoBeam(object):
-    def __init__(self,alpha) -> None:
-        self.nu = 0.3
-        self.gamma = 1/(2*(1+self.nu))*5/5
-        self.alpha = alpha
-        self.u_0 = None
-        self.u_1 = None
-        self.p_0 = None
-        self.p_1 = None
-
-    @property
-    def delta(self):
-        return 4*self.gamma/(1+self.gamma)**2*self.alpha/l + (1-self.gamma)**2/(1+self.gamma)**2
-
-    @property
-    def omega_squared(self):
-        return 1/2*l*(1+self.gamma)*(self.delta**(1/2)+1)
-
-    @property
-    def mu_squared(self):
-        return 1/2*l*(1+self.gamma)*(self.delta**(1/2)-1)
-
-    @property
-    def theta_squared(self):
-        return 1/2*l*(1+self.gamma)*(1-self.delta**(1/2))
-
-    def u(self, size_of_lam):
-        if size_of_lam == 'less':
-            return A*sympy.sinh(m*x) + B*sympy.cosh(m*x) + C*sympy.sinh(o*x) + D*sympy.cosh(o*x)
-        elif size_of_lam == 'equal':
-            return B + C*sympy.sin(o*x) + D*sympy.cos(o*x)
-        elif size_of_lam == 'greater':
-            return A*sympy.sin(t*x) + B*sympy.cos(t*x) + C*sympy.sin(o*x) + D*sympy.cos(o*x)
-
-    def p(self, size_of_lam):
-        if size_of_lam == 'less':
-            return A*(l+m**2)/(m*sympy.cosh(m*x)) + B*(l+m**2)/(m*sympy.sinh(m*x)) + C*(-l+o**2)/(o*sympy.cosh(o*x)) + D*(l-o**2)/(o*sympy.sinh(o*x))
-        elif size_of_lam == 'equal':
[…]

### 2023-12-01 code/plate_model/PlateCantilever.m
code

@@ -1,0 +1,385 @@
+function [E,wP,xP,yP,size_l] = PlateCantilever(n,h,inum,numEig,d)
+format long g
+m = ceil(n*d);
+
+a = 0;
+b = 1;
+c = 0;
+%alpha = 300;
+deltx = (b-a)/n;
+delty = (d-c)/m;
+
+size_l = (n+1)*(m+1);
+
+nu = 0.3;
+
+kappa_b = (5/6);
+kappa_p = 0.9554;%0.29738*nu + 0.763932;
+
+I = (h^3)/12;
+beta = kappa_b/((2*(1+nu))*I);%*alpha;%0.3846*kappa_p/I
+A = 1/(beta*(1-nu^2));
+B = 1/(2*beta*(1+nu));
+
+[MM,Kxx,Kxy,Kyy,Lx,Ly,Edge] = CalMatrix(n,m,deltx,delty);
+LxT = Lx';
+LyT = Ly';
+Kyx = Kxy';%CHECKED
+O = sparse(size(MM,1),size(MM,2));
+Mu = [MM O O; O I*MM O; O O I*MM];
+Ku = [Kxx+Kyy LxT LyT; h*Lx A*Kxx+B*Kyy+h*MM A*nu*Kyx+B*Kxy; h*Ly A*nu*Kxy+B*Kyx A*Kyy+B*Kxx+h*MM];%The correct one!
+%Ku = [h*(Kxx+Kyy) h*Lx h*Ly; h*LxT A*Kxx+B*Kyy+h*MM A*nu*Kxy+B*Kyx; h*LyT A*nu*Kyx+B*Kxy A*Kyy+B*Kxx+h*MM];
+Mq = [MM O O; O O O; O O O];
+
+F = zeros(size(Mu,1),1);
+F(1:(m+1),1) = -100;
+x = [];
+for i = [0 1 2]
+    x = [x; Edge+(i)*(m+1)*(n+1)];
+end
+
+Mu(x,:) = [];
+Mu(:,x) = [];
+Ku(x,:) = [];
+Ku(:,x) = [];
+Mq(x,:) = [];
+
+[V,D] = eigs(Ku,Mu,numEig,'sm');
+E = diag(D);
+%V = V(:,E>=0);
+%E = E(E>=0);
+
+wP = zeros(inum,(m+1)*(n+1));
+%wP(1,:) = [ueq(1:(m+1)*(n+1)-(m+1),1); zeros(m+1,1)];
+for i = inum:-1:1
+w = V(:,i);
+tic
[…]

### 2023-12-01 code/plate_model/PlateCantileverCubic.m

@@ -1,0 +1,613 @@
+%function [E,wP,xP,yP,size_c] = PlateCantileverCubic(d,n,h,inum,numEig)
+function [E,n,m] = PlateCantileverCubic(d,n,h,inum,numEig)
+format long g
+m = ceil(n*d);
+a = 0;
+b = 1;
+c = 0;
+
+%h = sqrt(12/alpha);
+%d = 1;
+deltx = (b-a)/n;
+delty = (d-c)/m;
+
+size_c = (n+1)*(m+1);
+
+nu = 0.3;
+
+kappa_b = (5/6);
+kappa_p = 0.9554;%0.29738*nu + 0.763932;
+
+I = (h^3)/12;
+beta = kappa_b/((2*(1+nu))*I);%*alpha;%0.3846*kappa_p/I
+A = 1/(beta*(1-nu^2));
+B = 1/(2*beta*(1+nu));
+
+[MM,Kxx,Kxy,Kyy,Lx,Ly,Edge] = CalMatrix(n,m,deltx,delty);
+LxT = Lx';
+LyT = Ly';
+Kyx = Kxy';%CHECKED
+O = sparse(size(MM,1),size(MM,2));
+Mu = [MM O O; O I*MM O; O O I*MM];
+Ku = [Kxx+Kyy LxT LyT; h*Lx A*Kxx+B*Kyy+h*MM A*nu*Kyx+B*Kxy; h*Ly A*nu*Kxy+B*Kyx A*Kyy+B*Kxx+h*MM];%The correct one!
+%Ku = [Kxx+Kyy Lx Ly; h*LxT A*Kxx+B*Kyy+h*MM A*nu*Kxy+B*Kyx; h*LyT A*nu*Kyx+B*Kxy A*Kyy+B*Kxx+h*MM];%The not correct one!
+%Ku = [h*(Kxx+Kyy) h*Lx h*Ly; h*LxT A*Kxx+B*Kyy+h*MM A*nu*Kxy+B*Kyx; h*LyT A*nu*Kyx+B*Kxy A*Kyy+B*Kxx+h*MM];
+Mq = [MM O O; O O O; O O O];
+F = zeros(size(Mu,1),1);
+F(1:(m+1),1) = 0.01;
+x = [];
+
+for i = [0 2 4 6 8 10]
+    x = [x; Edge+(i)*(m+1)*(n+1)];
+end
+Mu(x,:) = [];
[…]

### 2023-12-01 code/three_dimensional_model/Copy_of_CubePC.m

@@ -1,0 +1,2034 @@
+%function [Eig,uxB,uyB,uzB,sz] = Copy_of_CubePC(s,n1,h,inum,numEig)
+function [Eig,n1,n2,n3] = Copy_of_CubePC(s,n1,h,inum,numEig)
+format long g
+warning off;
+method =2;
+
+
+
+%mkdir(strcat('\Plots\',sprintf('%.6f',s)));
+%gpuDevice(1);
+    %mwb = MultiWaitBar(3, 1, '3-Dimensional Beam Eigenvalue Calculator', 'g');
+    %mwb.Update(1, 1, 0, 'Total Progress - Setting parameters');
+    %mwb.Update(2, 1, 0, ['Matrix Creation ' num2str(0) '%']);
+    %mwb.Update(3, 1, 0, 'Plot');
+    %alpha = 1200;
+    %d2 = sqrt(s/alpha);
+    %d1 = sqrt((12*s^2)/(alpha*(1+s^2)));
+    %d1 = sqrt(12/(alpha));
+    d1 = h; 
+    d2 = s; 
+    %d2 = 1; 
+    
+    n2 = ceil(n1*h);
+    if(n2 <= 10)
+        n2 = 6;
+    end
+    n3 = ceil(n2*s);
+    %n3 = ceil(n1/s);
+    if(n3 <= 10)
+        n3 = 6;
+    end
+    %n2 = 3;
+    
+    sz = n1*n2*n3;
+    
+    S = [0 1 0 d1 0 d2]; %Set size of the beam
+    N = [n1 n2 n3]; %Number of elements 
+    Delta = [(S(2)-S(1))/N(1) (S(4)-S(3))/N(2) (S(6)-S(5))/N(3)]; %space step size
+    nu = 0.3;
+    gamma = 1/(2*(1+nu))*5/6
+    %A = 1/(gamma*(1+nu)*(1-2*nu));
+    %B = 1/(2*gamma*(1+nu));
+    for i = inum:-1:50
+        h(i) = figure(i); 
[…]

### 2023-12-01 code/three_dimensional_model/CubePC.m

@@ -1,0 +1,1753 @@
+ function [Eig,uxB,uyB,uzB,sz] = CubePC(s,n1,h,inum,numEig)
+format long g
+warning off;
+%mkdir(strcat('\Plots\',sprintf('%.6f',s)));
+method = 2;
+%gpuDevice(1);
+    mwb = MultiWaitBar(3, 1, '3-Dimensional Beam Eigenvalue Calculator', 'g');
+    mwb.Update(1, 1, 0, 'Total Progress - Setting parameters');
+    mwb.Update(2, 1, 0, ['Matrix Creation ' num2str(0) '%']);
+    %mwb.Update(3, 1, 0, 'Plot');
+    %alpha = 1200;
+    %d2 = sqrt(s/alpha);
+    %d1 = sqrt((12*s^2)/(alpha*(1+s^2)));
+    d1 = h; 
+    d2 = s; 
+    %d2 = 1; 
+    
+    n2 = ceil(n1*h);
+    
+    if(n2 <= 1)
+        n2 = 2;
+    end
+    if(n2 >= 15)
+        n2 = 15;
+    end
+    n3 = ceil(n2*d2);
+    if(n3 <= 1)
+        n3 = 2;
+    end
+    if(n3 >= 15)
+        n3 = 15;
+    end
+    %[n1 n2 n3]
+    %n3 = 30;
+    %n2 = 2;
+    
+    sz = n1*n2*n3;
+    
+    S = [0 1 0 d1 0 d2]; %Set size of the beam
+    N = [n1 n2 n3]; %Number of elements
+    Delta = [(S(2)-S(1))/N(1) (S(4)-S(3))/N(2) (S(6)-S(5))/N(3)]; %space step size
+    
+    gamma = 0.3205;
+    nu = 0.3;
+    f = 0.001;
+    %A = 1/(gamma*(1+nu)*(1-2*nu));
+    %B = 1/(2*gamma*(1+nu));
+    
+    %A = 1/(1-nu^2);
+    %B = 1/(2*gamma*(1+nu));
+    mwb.Update(1, 1, 0.1, 'Total Progress - Creating Matrices');
+    [K11,K12,K13,K22,K23,K33,M0,Dom,E] = Matrices(Delta,N,mwb,method);
[…]

### 2023-12-01 code/timoshenko_Beam/TimoshenkoEig.m

@@ -1,0 +1,240 @@
+function [u,p,Eig] = TimoshenkoEig(alpha)
+syms A;
+syms B;
+syms C;
+syms D;
+syms x;
+syms m;
+syms o;
+syms lam;
+syms k;
+syms a;
+syms t;
+format long;
+
+%gamma = 0.25;
+nu = 0.3;
+gamma = 1/(2*(1+nu))*5/6;
+
+delt = 4*gamma/(1+gamma)^2*alpha/lam + (1-gamma)^2/(1+gamma)^2;
+omega2 = 1/2*lam*(1+gamma)*(delt^(1/2)+1);
+mu2 = 1/2*lam*(1+gamma)*(delt^(1/2)-1);
+theta2 = 1/2*lam*(1+gamma)*(1-delt^(1/2));
+
+
+u = A*sinh(m*x) + B*cosh(m*x) + C*sin(o*x) + D*cos(o*x);
+p = A*((lam+m^2)/m*cosh(m*x)) + B*((lam+m^2)/m*sinh(m*x)) + C*(-(lam-o^2)/o*cos(o*x)) + D*((lam-o^2)/o*sin(o*x));
+
+%u = B + C*sin(o*x) + D*cos(o*x);
+%p = A + B*a*x + C*(-(lam-o^2)/o)*cos(o*x) + D*((lam-o^2)/o)*sin(o*x);
+
+%u = A*sin(t*x) + B*cos(t*x) + C*sin(o*x) + D*cos(o*x);
+%p = A*(-(lam-t^2)/t)*cos(t*x) + B*(lam-t^2)/t*sin(t*x) + C*(-(lam-o^2)/o)*cos(o*x) + D*(lam-o^2)/o*sin(o*x);
+
+
+subs((u),x,0);
+subs((p),x,0);
+
+u = subs(u,[D,C],[-B,A*(lam+m^2)/m*o/(lam-o^2)]);
+p = subs(p,[D,C],[-B,A*(lam+m^2)/m*o/(lam-o^2)]);
+
+%u = subs(u,[B,C],[-D*((lam-o^2)/a),o/lam*(A + k*(-D*((lam-o^2)/a) +D))]);
+%p = subs(p,[B,C],[-D*((lam-o^2)/a),o/lam*(A + k*(-D*((lam-o^2)/a) +D))]);
+
+%u = subs(u,[D,C],[-B,-o/(o^2-lam)*(t^2-lam)/t*A]);
[…]

### 2023-12-01 code/timoshenko_Beam/TimoshenkoEigFree.m

@@ -1,0 +1,159 @@
+function [u,p,Eig] = TimoshenkoEigFree(alpha)
+syms A;
+syms B;
+syms C;
+syms D;
+syms x;
+syms m;
+syms o;
+syms lam;
+syms k;
+syms a;
+syms t;
+format long;
+
+gamma = 0.2829767118;
+
+delt = 4*gamma/(1+gamma)^2*alpha/lam + (1-gamma)^2/(1+gamma)^2;
+omega2 = 1/2*lam*(1+gamma)*(delt^(1/2)+1);
+mu2 = simplifyFraction(1/2*lam*(1+gamma)*(delt^(1/2)-1));
+theta2 = 1/2*lam*(1+gamma)*(1-delt^(1/2));
+
+
+%u = A*sinh(m*x) + B*cosh(m*x) + C*sin(o*x) + D*cos(o*x);
+%p = A*((lam+m^2)/m*cosh(m*x)) + B*((lam+m^2)/m*sinh(m*x)) + C*(-(lam-o^2)/o*cos(o*x)) + D*((lam-o^2)/o*sin(o*x));
+
+%u = B + C*sin(o*x) + D*cos(o*x);
+%p = A + B*a*x + C*(-(lam-o^2)/o)*cos(o*x) + D*((lam-o^2)/o)*sin(o*x);
+
+u = A*sin(t*x) + B*cos(t*x) + C*sin(o*x) + D*cos(o*x);
+p = A*(-(lam-t^2)/t)*cos(t*x) + B*(lam-t^2)/t*sin(t*x) + C*(-(lam-o^2)/o)*cos(o*x) + D*(lam-o^2)/o*sin(o*x);
+
+
+simplify(subs(diff(p),x,0));
+simplify(subs(diff(u) - p,x,0));
+
+%u = subs(u,[D,C],[-((m^2+lam)/(-o^2+lam))*B,o/m*A]);
+%p = subs(p,[D,C],[-((m^2+lam)/(-o^2+lam))*B,o/m*A]);
+
+%u = subs(u,[B,C],[-D*((lam-o^2)/a),o/lam*(A + k*(-D*((lam-o^2)/a) +D))]);
+%p = subs(p,[B,C],[-D*((lam-o^2)/a),o/lam*(A + k*(-D*((lam-o^2)/a) +D))]);
+
+u = subs(u,[D,C],[-B*((t^2-lam)/(o^2-lam)),-A*o/t]);
[…]

### 2023-12-01 code/timoshenko_Beam/TimoshenkoEigSuspended.m

@@ -1,0 +1,188 @@
+function [u,p,Eig] = TimoshenkoEigSuspended()
+format long g;
+syms A;
+syms B;
+syms C;
+syms D;
+syms x;
+syms m;
+syms o;
+syms lam;
+syms k;
+syms a;
+syms t;
+
+%ell = 0.04004;
+%d = 0.01004;
+%b = 0.01009;
+%mass = 0.01143;
+%rho = mass/(ell*d*b);
+%rho = 2817.9111;
+%E = 72666110000;
+%G = 27174810000;
+%nu = E/(2*G)-1;
+%kap = 5*(1+nu)/(6+5*nu);
+%A = ell*d;
+%I = ell*d^3/12;
+
+%k_i = 0;
+%gamma = (G*kap^2)/E;
+%alpha = 12/((d/ell))^2;
+%T = ell*sqrt(rho/(G*kap^2));
+
+%syms w;
+%a = rho/E*(A/I-rho*w^2/(kap^2*G));
+%b = (rho/E*(1+E/(kap^2*G)))^(1/2);
+%lam1 = ((b^4*w^4/4+a*w^2)^(1/2)-b^2*w^2/2)^(1/2);
+%lam2 = ((b^4*w^4/4+a*w^2)^(1/2)+b^2*w^2/2)^(1/2);
+%a1 = (rho*w^2/(kap^2*G)+lam1^2);
+%a2 = (rho*w^2/(kap^2*G)-lam2^2);
+
+delt = 4*gamma/(1+gamma)^2*alpha/lam + (1-gamma)^2/(1+gamma)^2;
+omega2 = 1/2*lam*(1+gamma)*(delt^(1/2)+1);
+mu2 = simplify(1/2*lam*(1+gamma)*(delt^(1/2)-1));
+
+u = A*sinh(m*x) + B*cosh(m*x) + C*sin(o*x) + D*cos(o*x);
+p = A*((lam+m^2)/m*cosh(m*x)) + B*((lam+m^2)/m*sinh(m*x)) + C*(-(lam-o^2)/o*cos(o*x)) + D*((lam-o^2)/o*sin(o*x));
+
+%u = B + C*sin(o*x) + D*cos(o*x);
+%p = A + B*a*x + C*(-(l-o^2)/o)*cos(o*x) + D*((l-o^2)/o)*sin(o*x);
+
+%u = A*sin(t*x) + B*cos(t*x) + C*sin(o*x) + D*cos(o*x);
[…]

### 2023-12-01 code/two_dimensional_model/TwoDimensionalCantilever.m

@@ -1,0 +1,415 @@
+function E = TwoDimensionalCantilever(n,alpha, showGraphs)
+format long g
+%gpuDevice(2)
+beta = 1;
+%alpha = 300;
+gamma = 0.3205;
+nu = 0.3;
+iA = 1/(1-nu^2);
+iB = 1/(2*gamma*(1+nu));
+
+ex = sqrt(12/alpha);
+m = ceil(n*ex);
+
+if(m <= 1)
+    m = 2;
+end
+
+n
+m
+
+a = 0;
+b = 1;
+c = 0;
+d = sqrt(12/alpha);
+deltx = (b-a)/n;
+delty = (d-c)/m;
+
+[MM,Kxx,Kxy,Kyy,D0] = CalMatrix(n,m,deltx,delty);
+Kyx = Kxy';%CHECKED
+
+Admin = (n+1)*(m+1) - (m+1);
+
+K1 = Kxx(1:Admin,1:Admin) + (1-nu)/2*Kyy(1:Admin,1:Admin); 
+K2 = nu*Kyx(1:Admin,1:Admin) + (1-nu)/2*Kxy(1:Admin,1:Admin);
+K3 = nu*Kxy(1:Admin,1:Admin) + (1-nu)/2*Kyx(1:Admin,1:Admin);
+K4 = Kyy(1:Admin,1:Admin) + (1-nu)/2*Kxx(1:Admin,1:Admin);
+MMf = MM(1:Admin,:); 
+MMu = MM(1:Admin,1:Admin);
+Of = sparse(size(MMf,1),size(MMf,2));
+Ou = sparse(size(MMu,1),size(MMu,2));
+
+K = 1/(gamma*(1-nu^2))*[K1 K2; K3 K4];
+Mf = [MMf Of; Of MMf];
+Mu = [MMu Ou; Ou MMu];
+%eig(Mu,K)
+[V,D] = eigs(K,Mu,20,'sm');
+E = diag(D);
+%{
+f = zeros(size(Mf,2));
+f((n+1)*(m+1)+1:(n+1)*(m+1)+(m+1)) = 1;
+
+%f((n+1)*(m+1)+1+ceil((n+1)*(m+1)):(n+1)*(m+1)+(m+1)+ceil((n+1)*(m+1))) = -1;
+
+for i = 20:-1:1
+    w = V(:,i);
+
+    %f = -1/200;
+    %F1 = zeros((n+1)*(m+1),1);
[…]

### 2023-12-01 code/two_dimensional_model/TwoDimensionalCantileverCubic.m

@@ -1,0 +1,520 @@
+function [E, n, m] = TwoDimensionalCantileverCubic(n,alpha,graph)
+format long g
+%gpuDevice(2)
+beta = 1;
+%alpha = 300;
+gamma = 0.3205;
+nu = 0.3; 
+iA = 1/(1-nu^2);
+iB = 1/(2*gamma*(1+nu));
+
+ex = sqrt(12/alpha);
+h=ex
+%ex = h
+m = ceil(n*ex);
+
+if(m <= 1)
+    m = 2;
+end
+%if(m >= 15)
+%    m = 15;
+%end
+%n
+%m = 2
+
+a = 0;
+b = 1;
+c = 0;
+
+%d = sqrt(12/alpha);
+d =h
+deltx = (b-a)/n;
+delty = (d-c)/m;
+
+[MM,Kxx,Kxy,Kyy,D0] = CalMatrix(n,m,deltx,delty);
+Kyx = Kxy';%CHECKED
+All = (n+1)*(m+1);
+
+K1 = Kxx + (1-nu)/2*Kyy; 
+K2 = nu*Kyx + (1-nu)/2*Kxy;
+K3 = nu*Kxy + (1-nu)/2*Kyx;
+K4 = Kyy + (1-nu)/2*Kxx;
+O = sparse(size(MM,1),size(MM,2));%CHECKED
+MMu = [MM O;%CHECKED
+       O MM];%CHECKED
+Mf = MMu;
+K = 1/(gamma*(1-nu^2))*[K1 K2; K3 K4];%CHECKED
+x = [7*All:-1:7*All-(m+1)+1 5*All:-1:5*All-(m+1)+1 3*All:-1:3*All-(m+1)+1 1*All:-1:1*All-(m+1)+1];
+K(x,:) = [];
+K(:,x) = [];
+MMu(x,:) = [];
+MMu(:,x) = [];
+Mf(x,:) = [];
+%CHECKED
+%eig(Mu,K)
+[V,D] = eigs(K,MMu,20,'sm');
+E = diag(D);
+size(K)
+
+if (graph == 1)
+    for i = 1:10
+        w = V(:,i);
+
+        f = -1/200;
+        F1 = zeros((n+1)*(m+1),1);
+        F1(ceil((1+(m+1))/2)) = f;
+        F = zeros(8*(n+1)*(m+1),1);
+        F(4*(n+1)*(m+1)+1:5*(n+1)*(m+1)) = F1;
+
+
+        %ueq = K\MMu*(-w);
+        tic
[…]

### 2023-12-01 files/Overview.tex
spelling mistake and a word counter python app

@@
 An additional assumption (additional to the assumptions of \cite{VV02}) is introduced by \cite{CVV18}.
-Under this assumption, the eigenvalue problem has a complete orthonormal sequence of eigensolutions.
+Under this assumption, the eigenvalue problem has a complete orthonormal sequence of eigen-solutions.
 The solution of the general vibration problem is an infinite series of modal solutions.
@@
 The Galerkin Approximation is derived from the general vibration problem and is rewritten into a system of ordinary differential using the Finite Element Method.
-This oridinary differential equation can be proven to have a unique solution.
+This ordinary differential equation can be proven to have a unique solution.
 The main results of \cite{BV13} shows that this solution of the Galerkin Approximation converges to the solution of the general vibration problem.
@@
 The authors consider a general eigenvalue problem.
-Then using the Rayleigh-quotient, from the Rayleigh-Ritz method, as well as an approximation theorem from \cite{OR97}, the main result is proven.
+Then using the Rayleigh-quotient, from the Rayleigh-Ritz method, as well as an approximation theorem from \cite{OR76}, the main result is proven.
 The specific work done in this section is updating the notation of the textbook, as well as expanding some proofs so that the results are easier to understand.
@@
 For each model, a reference configuration is defined.
-The Galerkin approximation can then be derived and using the Finite Element Method, a system of oridinary differential equations can be obatined.
+The Galerkin approximation can then be derived and using the Finite Element Method, a system of ordinary differential equations can be obtained.
 At this point is it easy to derive a eigenvalue problem for each of the models.

### 2023-12-01 word_count.py

@@ -1,0 +1,18 @@
+# A python script to count the words of a given text string.
+
+
+text = """This dissertation is a literature study that investigates the validity of different linear models in application. Validity in this context refers to how well simplified lower dimensional models compare to more realistic higher dimensional models. This dissertation will investigate the validity of the Timoshenko beam theory and the Reissner-Mindlin plate theory. The higher dimensional models are a two- and three-dimensional beam and a three-dimensional plate. The models are provided in the first chapter
+
+Next, a discussion of the existence and uniqueness of solutions for a general vibration problem. The article discussed provide four assumptions, and prove there exists an infinitesimal generator of a $C_0$-semigroup of contractions, that rewrites the problem into an initial value problem, with a unique solution. The authors then prove this is also a solution of the general vibration problem. An application of this theory is demonstrated using a cantilever Timoshenko beam. \textcolor{red}{Modal analysis is crucial to this dissertation. We show that the solution of the general vibration problem is a linear combination of the eigenvalues and eigenfunctions. This is the foundation of the comparisons of the models in this dissertation.}
+
+Thereafter a discussion of two theoretical results for the Finite Element Method. The first result is from an article where the convergence of the Galerkin Approximation is proved. \sout{A Galerkin Approximation of the general vibration problem is derived.} Using the Finite Element Method, this Galerkin Approximation is rewritten into an initial value problem, that has a unique solution. The authors show that there exists error estimates that approximate the error between the general vibration problem and the initial value problem. The next result is from a textbook on the convergence of the eigenvalues and eigenvectors of a one-dimensional vibration problem. This is based of work done in a textbook, but the notation is updated and some proofs are expanded.
+
[…]

### 2023-12-02 Appendix.tex
Overview

@@
 
+\chapter*{MATLAB Code}
+\addcontentsline{toc}{section}{MATLAB Code}
+\section*{Example code for Timoshenko beam model}
+\lstinputlisting{code/timoshenko_beam/TimoshenkoEig.m}
+
+\section*{Example code for two-dimensional elastic body using bi-cubics}
+\lstinputlisting{code/two_dimensional_model/TwoDimensionalCantileverCubic.m}
+
+\section*{Example code for Reissner-Mindlin plate model using bi-cubics}
+\lstinputlisting{code/plate_model/PlateCantileverCubic.m}
+
+\section*{Example code for three-dimensional elastic body using tri-cubics}
+\lstinputlisting{code/three_dimensional_model/Copy_of_CubePC.m}
+
 \end{document}

### 2023-12-02 files/Overview.tex
Overview

@@
 The results show that the models compare very well, even for a short and thick beam.
-\textcolor{red}{The results improve as the beam gets more slender.
-This shows that the shape of the beam is important.
-The cases covered are realistic to applications.}\sout{As the beam gets more slender, the comparison improves.
-In this section some of the results of the article are discussed and replicated.}
 
@@
 This result, together with the results in chapter 6, give a good picture to the validity of the Timoshenko beam theory.
-\sout{Finally the chapter is concluded by looking at a model of a cantilever beam with a tip-body with elastic interfaces.
-These results combine modal analysis and investigates at the behavior of the model.
-A similar model using realistic two- or three-dimensional model will be very challenging.}
 
@@
 \subsubsection{Chapter 6}
-\textcolor{red}{This chapter is an extension of the work of Section 4.5.
-In Section 4.5, the validity of the Timoshenko beam theory is investigated by comparing a Timoshenko beam model to a two-dimensional beam model.}
+This chapter is an extension of the work of Section 4.5.
+In Section 4.5, the validity of the Timoshenko beam theory is investigated by comparing a Timoshenko beam model to a two-dimensional beam model.
 
@@
 
-\sout{In this chapter, the main comparisons of the models are conducted. All of the sections follow the same idea and struture as the article \cite{LVV09}.}
+The same method is used in this chapter as in Section 4.5.
+The mode shapes are sketched and matched.
+The corresponding eigenvalues can then be matched up and compared.
+The eigenvalues relating to the Reissner-Mindlin plate model are referred to as plate-type eigenvalues.
 
-\sout{The first section is a discussion of the article \cite{LVV09}.
-In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model.
-The authors compare the models by comparing the eigenvalues and eigenfunctions (see Chapter 2 on modal analysis).
-The two-dimensional model is more complex and there are eigenvalues that are not shared between the models.
-The authors use the mode shapes to match up the eigenvalues.
-The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues.
-The authors also consider different shapes of beams, from a short thick beam to a long slender beam.
-The results show that the models compare very well, even for a short and thick beam.
-As the beam gets more slender, the comparison improves.
-In this section some of the results of the article are discussed and replicated.}
+\section{Achievements}
+
+In the first chapter, the models of this dissertation is presented and a dimensionless variational form is derived. The model problems used in the dissertation is also presented.
+
+In the second chapter, we look at the existence and uniqueness of solutions for a general vibration problem.
+All of the models in this dissertation is a special case of this general vibration problem.
+So a cantilever Timoshenko beam model is used as an example of the application of the theory as well as to explain the theory.
+A weak variational form of a cantilever Timoshenko beam model is derived.
+The authors provide four assumptions, and using these assumptions they prove using semi-group theory that the general vibration problem has a unique solution.
+For the example, we show that the four assumptions can be proven for the cantilever Timoshenko beam model.
+
+Then we look at modal analysis.
+Again we use the cantilever Timoshenko beam model as an example.
+A trial solution is chosen and using this trial solution, two problems are obtained.
+The first is the eigenvalue problem and the second is an ordinary differential equation.
+These two problems are solved and substitution then shows that the trial solution is valid.
+This is similar to the separation of variables, but it avoids any division.
+We then discuss a general solution using the same idea.
+The idea of modal analysis is crucial to the dissertation.
+From modal analysis, we can compare the eigenvalues and eigenfunctions of the models, and if they compare well, then the solutions of the models will compare well.
+And since the formal series solution is a linear combination of Fourier Coefficients, we only need to consider the first few eigenvalues.
+
+In the third chapter, two theoretical results are considered for the Finite Element Method.
+The first results is on the convergence of the Galerkin Approximation of a general vibration problem.
+In this section, the results of the article is discussed.
+The results are also given in Theorems with simple notation.
+We then look at a result form a textbook on the convergence of the eigenvalues and eigenfunctions when using the Finite Element Method.
+We discuss the results of the textbook, with some improvements to the notation as well as expanding some results to make it more clear.
+
+In the fourth chapter, we look at our simplest model, the Timoshenko beam model.
+The first result discusses an article that provides a method to determine the exact eigenvalues and eigenfunctions for the Timoshenko beam model.
+We then apply this to a cantilever beam model and a free-free beam model to obtain the eigenvalues and plot the mode shapes.
+We then look at an article that compares a cantilever Timoshenko beam model to a two-dimensional beam model.
+We discuss the results of the article and replicate the results with more significant digits.
+We also include some more results not included in the article, that are used later in Chapter 6.
+We then look at another article that compares the Timoshenko beam theory to results obtained from a measured beam.
+The authors suspended a beam on both ends an vibrated the beam until then endpoints could be considered free.
+They then swept through different frequencies and recorded the natural frequencies of the beam.
+These results are then compared to the theoretical results of a free-free Timoshenko beam.
+We add to the article by giving the model problems for the beams and discuss the results.
+
+The fifth chapter is a preparation chapter for the comparisons of this dissertation.
+In chapter 4, we have a method to obtain the exact eigenvalues and eigenfunctions for the Timoshenko beam theory.
+But a different approach is required for the two- and three-dimensional models.
+In this chapter, we derive the Galerkin Approximation for each of the models.
+We then define a discrete grid of elements on the reference configuration on each of the models.
+Then using piece-wise Hermite cubic basis functions, we derive a matrix representation of the model problems using the standard Finite Element Analysis.
+In this form it is then easy to obtain a matrix representation of the eigenvalue problem for each of the models.
+
+\section{Future Work}
+
+\end{document}
 
@@
 \textcolor{red}{WORD COUNT: 470}
-
-\end{document}
 

### 2023-12-02 files/Overview.tex
Overview

@@
 In this form it is then easy to obtain a matrix representation of the eigenvalue problem for each of the models.
+This is in preparation for the comparisons of the models in Section 4.5 as well as chapter 6.
+
+In the final chapter, we extend the work of Section 4.5 and investigate the validity of the two-dimensional beam model as well as the validity of the Reissner-Mindlin plate model.
+Using the work from chapter 5, a numerical formula is derived to calculate the eigenvalues and eigenvectors of the models.
+This is implemented into some MATLAB code.
+(This was also done to obtain the results in Section 4.5).
+The same structure as Section 4.5 is followed.
+To start, the mode shapes are calculated and plotted.
+These are then compared so that the eigenvalues can be matched up.
+Careful consideration should be taken to the shapes as there are many shapes not relating to beam-type or plate-type problems.
+The results show that the shape of the models impact how well the models compare.
+The cases of the comparisons were chosen so that they represent realistic scenarios for use in application.
 

### 2023-12-02 word_count.py

@@ -1,17 +1,20 @@
 # A python script to count the words of a given text string.
 
 
-text = """This dissertation is a literature study that investigates the validity of different linear models in application. Validity in this context refers to how well simplified lower dimensional models compare to more realistic higher dimensional models. This dissertation will investigate the validity of the Timoshenko beam theory and the Reissner-Mindlin plate theory. The higher dimensional models are a two- and three-dimensional beam and a three-dimensional plate. The models are provided in the first chapter
+text = """In the first chapter, the models of this dissertation is presented and a dimensionless variational form is derived. The model problems used in the dissertation is also presented.
 
-Next, a discussion of the existence and uniqueness of solutions for a general vibration problem. The article discussed provide four assumptions, and prove there exists an infinitesimal generator of a $C_0$-semigroup of contractions, that rewrites the problem into an initial value problem, with a unique solution. The authors then prove this is also a solution of the general vibration problem. An application of this theory is demonstrated using a cantilever Timoshenko beam. \textcolor{red}{Modal analysis is crucial to this dissertation. We show that the solution of the general vibration problem is a linear combination of the eigenvalues and eigenfunctions. This is the foundation of the comparisons of the models in this dissertation.}
+In the second chapter, we look at the existence and uniqueness of solutions for a general vibration problem. All of the models in this dissertation is a special case of this general vibration problem. So a cantilever Timoshenko beam model is used as an example of the application of the theory as well as to explain the theory. A weak variational form of a cantilever Timoshenko beam model is derived. The authors provide four assumptions, and using these assumptions they prove using semi-group theory that the general vibration problem has a unique solution. For the example, we show that the four assumptions can be proven for the cantilever Timoshenko beam model.
 
-Thereafter a discussion of two theoretical results for the Finite Element Method. The first result is from an article where the convergence of the Galerkin Approximation is proved. \sout{A Galerkin Approximation of the general vibration problem is derived.} Using the Finite Element Method, this Galerkin Approximation is rewritten into an initial value problem, that has a unique solution. The authors show that there exists error estimates that approximate the error between the general vibration problem and the initial value problem. The next result is from a textbook on the convergence of the eigenvalues and eigenvectors of a one-dimensional vibration problem. This is based of work done in a textbook, but the notation is updated and some proofs are expanded.
[…]

### 2023-12-03 files/Overview.tex
overview

@@
 
-In the first chapter, the models of this dissertation is presented and a dimensionless variational form is derived. The model problems used in the dissertation is also presented.
+In the first chapter, the models of this dissertation are presented and a dimensionless variational form for each is derived. The model problems for this dissertation are then formulated.
 
-In the second chapter, we look at the existence and uniqueness of solutions for a general vibration problem.
-All of the models in this dissertation is a special case of this general vibration problem.
-So a cantilever Timoshenko beam model is used as an example of the application of the theory as well as to explain the theory.
-A weak variational form of a cantilever Timoshenko beam model is derived.
-The authors provide four assumptions, and using these assumptions they prove using semi-group theory that the general vibration problem has a unique solution.
-For the example, we show that the four assumptions can be proven for the cantilever Timoshenko beam model.
+In the second chapter, two results are investigated.
+This first is on the existence and uniqueness of solutions for vibration problems.
+An article is discussed that proves the existence and uniqueness of solutions for a general vibration problem using semi-group theory and assuming four assumptions.
+All the models in this dissertation is a special case of this general problem, so the theory can be explained and applied to an example.
+The weak variational form for a cantilever Timoshenko beam is derived.
+In this derivation, we also give the definitions of the spaces required.
+The theory is then applied to this example problem.
+We show that the four assumptions can be proven to be true for the cantilever Timoshenko beam model.
 
-Then we look at modal analysis.
-Again we use the cantilever Timoshenko beam model as an example.
-A trial solution is chosen and using this trial solution, two problems are obtained.
-The first is the eigenvalue problem and the second is an ordinary differential equation.
-These two problems are solved and substitution then shows that the trial solution is valid.
-This is similar to the separation of variables, but it avoids any division.
-We then discuss a general solution using the same idea.
-The idea of modal analysis is crucial to the dissertation.
-From modal analysis, we can compare the eigenvalues and eigenfunctions of the models, and if they compare well, then the solutions of the models will compare well.
-And since the formal series solution is a linear combination of Fourier Coefficients, we only need to consider the first few eigenvalues.
+The next result is in Modal Analysis.
+Again the cantilever Timoshenko beam model is used to first explain the theory, before the general case is discussed.
+A trial solution is presented and substituted into the partial differential equations.
+This results into two problems, an eigenvalue problem and an ordinary differential equation.
+These two problems are solved and substitution can confirm then that the trial solutions are indeed solutions.
+The method obtains the same result as separation of variables, but avoids any division.
+Finally a formal series solution for the example is given.
+The general case is then discussed and follows the same idea.
+Modal analysis is crucial for this dissertation.
+For the comparisons later in this dissertation, a method is required to compare the different models.
+Modal analysis shows that is the eigenvalues and eigenfunctions of the models compare well, then the solutions of the models should compare well.
+And since the Fourier Coefficients gets small very fast, it is only required to look at the first few eigenvalues.
 
-In the third chapter, two theoretical results are considered for the Finite Element Method.
-The first results is on the convergence of the Galerkin Approximation of a general vibration problem.
-In this section, the results of the article is discussed.
-The results are also given in Theorems with simple notation.
-We then look at a result form a textbook on the convergence of the eigenvalues and eigenfunctions when using the Finite Element Method.
-We discuss the results of the textbook, with some improvements to the notation as well as expanding some results to make it more clear.
+In the third chapter, two theoretical results for the Finite Element Method is discussed.
+The first result is on the convergence of the Galerkin Approximation.
+The general case contains various symbols rectangularly used in application, so an example of the cantilever Timoshenko beam model is used and the Galerkin Approximation is derived.
+Then the general case is discussed from an article.
+The results from the article are presented in a reduced format to avoid introducing too many new symbols.
+We also present the results in four new Theorems, to present the results of the article in a concise manner.
+
+The second result is on the convergence of the eigenvalues and eigenfunctions when using the Finite Element Method.
+The results are presented in textbook.
+Here we use the notation of the dissertation to present the results.
+The results are also expanded in an attempt to better explain the theory, with a few new parameters also introduced.
+
+In the fourth chapter, we investigate our simplest model, the Timoshenko beam theory.
+First is a discussion of an article that provides a method that allows us to find the exact eigenvalues and eigenfunctions of a Timoshenko beam model.
+A summary of this method is presented.
+It is then applied to two model problems for a cantilever Timoshenko beam and a free-free Timoshenko beam.
+For both model problems, the method is applied and examples of the eigenvalues and mode shapes are given.
+The eigenvalues and mode shape plots are obtained using a computer program, sketching the equation of motion and the using interval division to get the eigenvalues to a desired level of accuracy.
+This is in preparation for the comparison results in the results that follow.
 

### 2023-12-03 word_count.py

@@ -1,21 +1,19 @@
 # A python script to count the words of a given text string.
 
 
-text = """In the first chapter, the models of this dissertation is presented and a dimensionless variational form is derived. The model problems used in the dissertation is also presented.
+text = """
+In the first chapter, the models of this dissertation are presented and a dimensionless variational form for each is derived. The model problems for this dissertation are then formulated.
 
-In the second chapter, we look at the existence and uniqueness of solutions for a general vibration problem. All of the models in this dissertation is a special case of this general vibration problem. So a cantilever Timoshenko beam model is used as an example of the application of the theory as well as to explain the theory. A weak variational form of a cantilever Timoshenko beam model is derived. The authors provide four assumptions, and using these assumptions they prove using semi-group theory that the general vibration problem has a unique solution. For the example, we show that the four assumptions can be proven for the cantilever Timoshenko beam model.
+In the second chapter, two results are investigated. This first is on the existence and uniqueness of solutions for vibration problems. An article is discussed that proves the existence and uniqueness of solutions for a general vibration problem using semi-group theory and assuming four assumptions. All the models in this dissertation is a special case of this general problem, so the theory can be explained and applied to an example. The weak variational form for a cantilever Timoshenko beam is derived. In this derivation, we also give the definitions of the spaces required. The theory is then applied to this example problem. We show that the four assumptions can be proven to be true for the cantilever Timoshenko beam model.
 
-Then we look at modal analysis. Again we use the cantilever Timoshenko beam model as an example. A trial solution is chosen and using this trial solution, two problems are obtained. The first is the eigenvalue problem and the second is an ordinary differential equation. These two problems are solved and substitution then shows that the trial solution is valid. This is similar to the separation of variables, but it avoids any division. We then discuss a general solution using the same idea. The idea of modal analysis is crucial to the dissertation. From modal analysis, we can compare the eigenvalues and eigenfunctions of the models, and if they compare well, then the solutions of the models will compare well. And since the formal series solution is a linear combination of Fourier Coefficients, we only need to consider the first few eigenvalues.
[…]

### 2023-12-03 files/Overview.tex
overview

@@
 
-\section{Achievements}
+\section{Achievements and contributions}
 
@@
 
-In the fourth chapter, we look at our simplest model, the Timoshenko beam model.
-The first result discusses an article that provides a method to determine the exact eigenvalues and eigenfunctions for the Timoshenko beam model.
-We then apply this to a cantilever beam model and a free-free beam model to obtain the eigenvalues and plot the mode shapes.
-We then look at an article that compares a cantilever Timoshenko beam model to a two-dimensional beam model.
-We discuss the results of the article and replicate the results with more significant digits.
-We also include some more results not included in the article, that are used later in Chapter 6.
-We then look at another article that compares the Timoshenko beam theory to results obtained from a measured beam.
-The authors suspended a beam on both ends an vibrated the beam until then endpoints could be considered free.
-They then swept through different frequencies and recorded the natural frequencies of the beam.
-These results are then compared to the theoretical results of a free-free Timoshenko beam.
-We add to the article by giving the model problems for the beams and discuss the results.
+We then investigate the validity of the Timoshenko beam theory.
+This is presented in an article where the cantilever Timoshenko beam theory is compared to a cantilever two-dimensional beam model.
+We apply the method use by the authors to plot the mode shapes.
+These mode shapes are then compared and the eigenvalues are matched up.
+This is required since there are eigenvalues for the two-dimensional model that are not related to beam type eigenvalues.
+The authors make a distinction by referring to the eigenvalues as beam-type eigenvalues and non-beam type eigenvalues.
+For the Timoshenko beam model, the same method and computer program used in this chapter was used.
+For the two-dimensional model, the Finite Element Method is used.
+This is explained more in detail in chapter 5, and in chapter 6.
+The results of the article is replicated, with five significant digits of accuracy (the article use three significant digits of accuracy).
+Also more cases are presented to expand on the article as well as in preparation for the results in chapter 6.
+
+The final result of this chapter looks at a study that compares empirical results from a real world study on the vibrations of a beam to the theoretical results of the Timoshenko beam model.
+We add to the article by including the model problems.
+
+The fifth chapter is preparation for the comparisons of the models in this dissertation.
+In chapter 4, we discussed a method to obtain to obtain the exact solutions for the eigenvalue problem for the Timoshenko beam model.
+For the other models a different approach is required.
+For each of the models, the Galerkin Approximation is derived.
+The reference configuration is the divided into discrete elements.
+We then apply piece-wise Hermite cubic functions and use the Finite Element Method to obtain a initial value problem for each of the models consisting of a system of ordinary differential equations.
+An eigenvalue problem is then derived from this IVP.
+Using a computer program, this eigenvalue problem can be solved and the eigenvalues and eigenvectors can be calculated.
+An investigation into the rate of convergence was conducted to make sure that the results are accurate enough.
 

### 2023-12-03 word_count.py

@@ -10,7 +10,13 @@ The next result is in Modal Analysis. Again the cantilever Timoshenko beam model
 
 In the third chapter, two theoretical results for the Finite Element Method is discussed. The first result is on the convergence of the Galerkin Approximation. The general case contains various symbols rectangularly used in application, so an example of the cantilever Timoshenko beam model is used and the Galerkin Approximation is derived. Then the general case is discussed from an article. The results from the article are presented in a reduced format to avoid introducing too many new symbols. We also present the results in four new Theorems, to present the results of the article in a concise manner.
 
-The second result is on the convergence of the eigenvalues and eigenfunctions when using the Finite Element Method. The results are presented in textbook. Here we use the notation of the dissertation to present the results. The results are also expanded in an attempt to better explain the theory.
+The second result is on the convergence of the eigenvalues and eigenfunctions when using the Finite Element Method. The results are presented in textbook. Here we use the notation of the dissertation to present the results. The results are also expanded in an attempt to better explain the theory, with a few new parameters also introduced.
+
+In the fourth chapter, we investigate our simplest model, the Timoshenko beam theory. First is a discussion of an article that provides a method that allows us to find the exact eigenvalues and eigenfunctions of a Timoshenko beam model. A summary of this method is presented. It is then applied to two model problems for a cantilever Timoshenko beam and a free-free Timoshenko beam. For both model problems, the method is applied and examples of the eigenvalues and mode shapes are given. The eigenvalues and mode shape plots are obtained using a computer program, sketching the equation of motion and the using interval division to get the eigenvalues to a desired level of accuracy. This is in preparation for the comparison results in the results that follow. 
+
[…]

### 2023-12-03 files/Overview.tex
Overview

@@
 
-The fifth chapter is a preparation chapter for the comparisons of this dissertation.
-In chapter 4, we have a method to obtain the exact eigenvalues and eigenfunctions for the Timoshenko beam theory.
-But a different approach is required for the two- and three-dimensional models.
-In this chapter, we derive the Galerkin Approximation for each of the models.
-We then define a discrete grid of elements on the reference configuration on each of the models.
-Then using piece-wise Hermite cubic basis functions, we derive a matrix representation of the model problems using the standard Finite Element Analysis.
-In this form it is then easy to obtain a matrix representation of the eigenvalue problem for each of the models.
-This is in preparation for the comparisons of the models in Section 4.5 as well as chapter 6.
+In the final chapter, the work of section 4.5 is extended.
+The validity of the two-dimensional beam model and the Reissner-Mindlin plate model is investigated.
+Using the work done in chapter 5, the eigenvalue problems for a cantilever two-dimensional beam model, cantilever three-dimensional beam model and a cantilever Reissner-Mindlin plate model is solved using the Finite Element Method and a computer program.
+The same approach as section 4.5 is followed.
+The mode shapes are plotted and the eigenvalues are matched up.
+Careful consideration to the eigenvalues and mode shapes was taken to ensure that the eigenvalues are relevant to beam-type (or plate-type) eigenvalues and mode shapes.
+To investigate the two-dimensional cantilever beam, it is compared to a three-dimensional beam model.
 
-In the final chapter, we extend the work of Section 4.5 and investigate the validity of the two-dimensional beam model as well as the validity of the Reissner-Mindlin plate model.
-Using the work from chapter 5, a numerical formula is derived to calculate the eigenvalues and eigenvectors of the models.
-This is implemented into some MATLAB code.
-(This was also done to obtain the results in Section 4.5).
-The same structure as Section 4.5 is followed.
-To start, the mode shapes are calculated and plotted.
-These are then compared so that the eigenvalues can be matched up.
-Careful consideration should be taken to the shapes as there are many shapes not relating to beam-type or plate-type problems.
-The results show that the shape of the models impact how well the models compare.
-The cases of the comparisons were chosen so that they represent realistic scenarios for use in application.
+The three-dimensional more complex and contains non-beam type eigenvalues that are shared with the two-dimensional model as well as non-beam type eigenvalues that are not present in the two-dimensional model.
+The eigenvalues not present in the two-dimensional model are omitted from the results and all the eigenvalues shared between the models are included with the focus on the beam-type eigenvalues.
+The results shows that the depth of the three-dimensional beam is very important the results.
+The cases considered covers a range of possibilities for realistic beam models for use in practical applications.
+
+Similarly the Reissner-Mindlin plate model is compared to the three-dimensional plat model. The results are restricted to cases where the width of the models
 

### 2023-12-03 word_count.py

@@ -17,6 +17,9 @@ In the fourth chapter, we investigate our simplest model, the Timoshenko beam th
 We then investigate the validity of the Timoshenko beam theory. This is presented in an article where the cantilever Timoshenko beam theory is compared to a cantilever two-dimensional beam model. We apply the method use by the authors to plot the mode shapes. These mode shapes are then compared and the eigenvalues are matched up. This is required since there are eigenvalues for the two-dimensional model that are not related to beam type eigenvalues. The authors make a distinction by referring to the eigenvalues as beam-type eigenvalues and non-beam type eigenvalues. For the Timoshenko beam model, the same method and computer program used in this chapter was used. For the two-dimensional model, the Finite Element Method is used. This is explained more in detail in chapter 5, and in chapter 6. The results of the article is replicated, with five significant digits of accuracy (the article use three significant digits of accuracy). Also more cases are presented to expand on the article as well as in preparation for the results in chapter 6.
 
 The final result of this chapter looks at a study that compares empirical results from a real world study on the vibrations of a beam to the theoretical results of the Timoshenko beam model. We add to the article by including the model problems. 
+
+The fifth chapter is preparation for the comparisons of the models in this dissertation. In chapter 4, we discussed a method to obtain to obtain the exact solutions for the eigenvalue problem for the Timoshenko beam model. For the other models a different approach is required. For each of the models, the Galerkin Approximation is derived. The reference configuration is the divided into discrete elements. We then apply piece-wise Hermite cubic functions and use the Finite Element Method to obtain a initial value problem for each of the models consisting of a system of ordinary differential equations. An eigenvalue problem is then derived from this IVP. Using a computer program, this eigenvalue problem can be solved and the eigenvalues and eigenvectors can be calculated. An investigation into the rate of convergence was conducted to make sure that the results are accurate enough.
+
 """
 
 word_count = len(text.split())

### 2023-12-03 files/Overview.tex
summary

--- 2023-12-03 files/Overview.tex
@@
 
-\section{Achievements}
+\section{Contributions}
 
-In the first chapter, the models of this dissertation are presented and a dimensionless variational form for each is derived. The model problems for this dissertation are then formulated.
+There are four models used in this dissertation. For each of the models, the dimensionless variational form is derived. Also presented are the model problems that are used in this dissertation.
 
-In the second chapter, two results are investigated.
-This first is on the existence and uniqueness of solutions for vibration problems.
-An article is discussed that proves the existence and uniqueness of solutions for a general vibration problem using semi-group theory and assuming four assumptions.
-All the models in this dissertation is a special case of this general problem, so the theory can be explained and applied to an example.
-The weak variational form for a cantilever Timoshenko beam is derived.
-In this derivation, we also give the definitions of the spaces required.
-The theory is then applied to this example problem.
-We show that the four assumptions can be proven to be true for the cantilever Timoshenko beam model.
+The first result investigates the existence and uniqueness of solutions for general vibration problems.
+The article that is discussed proves this result for a general vibration problem, using four assumptions.
+To explain the theory, an example is presented using one of the model problems of the dissertation.
+The cantilever Timoshenko beam model is chosen for the simple boundary conditions, as well as it's recurring importance in this dissertation.
+The weak variational form of the model is derived as well as the function spaces defined.
+This is presented in the same format as the general vibration problem.
+In fact all the models in this dissertation are special cases of this general vibration problem.
+The theory is then applied to this example problem, as a demonstration.
+To apply the theory, the four assumptions are proven to be true.
 
-The next result is in Modal Analysis.
-Again the cantilever Timoshenko beam model is used to first explain the theory, before the general case is discussed.
-A trial solution is presented and substituted into the partial differential equations.
-This results into two problems, an eigenvalue problem and an ordinary differential equation.
-These two problems are solved and substitution can confirm then that the trial solutions are indeed solutions.
-The method obtains the same result as separation of variables, but avoids any division.
-Finally a formal series solution for the example is given.
-The general case is then discussed and follows the same idea.
-Modal analysis is crucial for this dissertation.
-For the comparisons later in this dissertation, a method is required to compare the different models.
-Modal analysis shows that is the eigenvalues and eigenfunctions of the models compare well, then the solutions of the models should compare well.
-And since the Fourier Coefficients gets small very fast, it is only required to look at the first few eigenvalues.
+The next result looks at modal analysis.
+Before the general case is discussed, again the cantilever Timoshenko beam is used to illustrated the concept of modal analysis.A trial solution to the boundary value problem is suggested.
+This trial solution is substituted into the partial differential equation and two problems are obtained.
+The first problem is the eigenvalue problem and the second is an ordinary differential equation.
+The eigenvalue problem can be solved with theory discussed later in the dissertation and the ordinary differential equation can then be solved.
+Substation of these two results into the boundary value problem confirms that the trial solution is correct.
+The same idea is then discussed for the general case.
 
-In the third chapter, two theoretical results for the Finite Element Method is discussed.
-The first result is on the convergence of the Galerkin Approximation.
-The general case contains various symbols rectangularly used in application, so an example of the cantilever Timoshenko beam model is used and the Galerkin Approximation is derived.
-Then the general case is discussed from an article.
-The results from the article are presented in a reduced format to avoid introducing too many new symbols.
-We also present the results in four new Theorems, to present the results of the article in a concise manner.
+We then look at the convergence of the Galerkin Approximation for our general vibration problem.
+The results of the article discussed are updated with improved notation using a different article.
+The general case of the Galerkin approximation use a lot of symbols that are not immediately obvious, so again the cantilever Timoshenko beam model problem is used and the Galerkin Approximation is derived in an attempt to explain some of the conventions.
+The results of the article are then discussed and presented.
+The results are presented in a concise and practical format to reduce the need to define any unnecessary symbols or notation.
+The results are also presented in four theorems, summarizing the results of the article that are important but that are not necessarily presented as a theorem in the article.
 
-The second result is on the convergence of the eigenvalues and eigenfunctions when using the Finite Element Method.
-The results are presented in textbook.
-Here we use the notation of the dissertation to present the results.
-The results are also expanded in an attempt to better explain the theory, with a few new parameters also introduced.
+The next result is on the convergence of the eigenvalues and eigenfunctions of a general vibration problem when using the Finite Element Method.
+The results are from a textbook.
+The results are presented with updated notation, coinciding with the notation used in the dissertation.
+The results are also expanded and extra results are added in an attempt to better explain the theory.
 
-In the fourth chapter, we investigate our simplest model, the Timoshenko beam theory.
-First is a discussion of an article that provides a method that allows us to find the exact eigenvalues and eigenfunctions of a Timoshenko beam model.
-A summary of this method is presented.
-It is then applied to two model problems for a cantilever Timoshenko beam and a free-free Timoshenko beam.
-For both model problems, the method is applied and examples of the eigenvalues and mode shapes are given.
-The eigenvalues and mode shape plots are obtained using a computer program, sketching the equation of motion and the using interval division to get the eigenvalues to a desired level of accuracy.
-This is in preparation for the comparison results in the results that follow.
+We then look at an important result for the Timoshenko beam theory.
+This provides a method to calculate the exact eigenvalues and eigenfunctions for the Timoshenko beam theory.
+Two examples are then used, a cantilever beam and a free-free beam, as an example of the application of the theory.
+The eigenvalues are calculated and the corresponding mode shapes are plotted.
+To obtain these results, the equation of motion is plotted, the isolation intervals are determined and the eigenvalues are then calculated using interval division to a desired level of accuracy.
+The mode shapes can then also be plotted with back substitution.
+These examples are important preparation for the main comparisons of this dissertation.
+We also discuss a result comparing the Timoshenko beam theory to results from an empirical study.
+We add to this article by giving the model problems.
 
-In the fourth chapter, we look at our simplest model, the Timoshenko beam model.
-The first result discusses an article that provides a method to determine the exact eigenvalues and eigenfunctions for the Timoshenko beam model.
-We then apply this to a cantilever beam model and a free-free beam model to obtain the eigenvalues and plot the mode shapes.
-We then look at an article that compares a cantilever Timoshenko beam model to a two-dimensional beam model.
-We discuss the results of the article and replicate the results with more significant digits.
-We also include some more results not included in the article, that are used later in Chapter 6.
-We then look at another article that compares the Timoshenko beam theory to results obtained from a measured beam.
-The authors suspended a beam on both ends an vibrated the beam until then endpoints could be considered free.
-They then swept through different frequencies and recorded the natural frequencies of the beam.
-These results are then compared to the theoretical results of a free-free Timoshenko beam.
-We add to the article by giving the model problems for the beams and discuss the results.
+For the rest of the models in this dissertation, the two- and three-dimensional elastic bodies, and the Reissner-Mindlin plate model, a different approach is required to solve the eigenvalue problems.
+For these models we use the Finite Element Method.
+For each of the models, their reference configurations are given.
+All of the models are assumed to have a square cross-section and in a cantilever configuration.
+This reference configuration is then discretised into a grid of rectangular shaped elements.
+A set of admissable piecewise Hermite cubic functions are then used and each model is rewritten into a Galerkin Approximation.
+We the define the standard Finite Element Method Matrices for each case.
+These are referred to as the mass and stiffness matrices in engineering.
+Finally our boundary value problems are written into a system of ordinary differential equations in a matrix representation.
+At this point is it easy to derive the eigenvalue problem for each of the problems in this matrix form.
+This is in preparation for the main comparisons made in this dissertation.
 
-The fifth chapter is a preparation chapter for the comparisons of this dissertation.
-In chapter 4, we have a method to obtain the exact eigenvalues and eigenfunctions for the Timoshenko beam theory.
-But a different approach is required for the two- and three-dimensional models.
-In this chapter, we derive the Galerkin Approximation for each of the models.
-We then define a discrete grid of elements on the reference configuration on each of the models.
-Then using piece-wise Hermite cubic basis functions, we derive a matrix representation of the model problems using the standard Finite Element Analysis.
-In this form it is then easy to obtain a matrix representation of the eigenvalue problem for each of the models.
-This is in preparation for the comparisons of the models in Section 4.5 as well as chapter 6.
+For our main comparisons, we first look at an article comparing a cantilever Timoshenko beam model to a cantilever two-dimensional model.
+We discuss the article and replicate the results.
+The eigenvalues and eigenfunctions of the Timoshenko beam model is obtained using the exact method already described.
+The eigenvalues and the eigenfunctions for the two-dimensional model are approximated using the Finite Element Method matrix representation of the eigenvalue problem.
+A MATLAB program is written to approximate the eigenvalues and plot the mode shapes.
+The accuracy of this approximation is also investigated by looking at the rate of convergence for different grid sizes.
+Following the article, the eigenvalues are matched up by first comparing the mode shapes of the two models.
+The eigenvalues can then be matched up and also any eigenvalues not relating to beam-type problems can be filtered out.
+Based on the results in modal analysis, only a few eigenvalues need to be considered.
+The relative error between the eigenvalues are then calculated for different shapes of beams.
+The results improve on the article by showing more significant digits and also including some more results.
 
-In the final chapter, we extend the work of Section 4.5 and investigate the validity of the two-dimensional beam model as well as the validity of the Reissner-Mindlin plate model.
-Using the work from chapter 5, a numerical formula is derived to calculate the eigenvalues and eigenvectors of the models.
-This is implemented into some MATLAB code.
-(This was also done to obtain the results in Section 4.5).
-The same structure as Section 4.5 is followed.
-To start, the mode shapes are calculated and plotted.
-These are then compared so that the eigenvalues can be matched up.
-Careful consideration should be taken to the shapes as there are many shapes not relating to beam-type or plate-type problems.
-The results show that the shape of the models impact how well the models compare.
-The cases of the comparisons were chosen so that they represent realistic scenarios for use in application.
+We then extend the results of the article to investigate the validity of a cantilever two-dimensional beam model as well as a cantilever Reissner-Mindlin plate model.
+The same method of the article is followed.
+To investigate the validity of a cantilever two-dimensional model, a cantilever three-dimensional model is considered.
+Since both of the models are not beam models, careful consideration needs to be taken to identify the eigenvalues.
+The same approach is used by comparing the mode shapes.
+For interest, the non-beam type eigenvalues shared between the two models are also included and the rest that the three-dimensional model does not share with the two-dimensional model are omitted.
+A clear distinction is made to show the beam type eigenvalues and the beam type results.
+The shape of the models are also carefully chosen to represent a variety of realistic cases that are interesting.
+The results show that the shape of the models play an important role in how well the models compare.
+An interesting result shows that this comparison is not good when the beam gets too wide.
+We therefore suggest a different model, like a plate model.
+This lead to the introduction of the Reissner-Mindlin plate model into this dissertation.
+The validity of a cantilever Reissner-Mindlin plate model is investigated using the same method.
+The cantilever three-dimensional plate model is again used as the reference model with the restriction that the body is wide.
 
-\section{Future Work}
+\section{Further Research}
+Future work would include the addition of damping into the models.
+A lot of the articles do include results for damping, however the results of the modal analysis (the crucial theory of this dissertation) might not be so trivial to prove.
+
+The use of the Hermite cubic basis functions results in the derivatives of the displacement functions to also be available.
+This brings into question if the stresses of the models can also be compared.
+
+Further improvements to the code can be made.
+Although a lot of effort was put into optimizing the code, this lead to the code being difficult to understand.
+Ideally a refactor and simplification of the code, while maintaining its functionality is desired.
 

### 2023-12-03 summary.tex
summary

@@
 \end{center}
-This dissertation is a literature study, investigating the Finite Element Analysis of multidimensional and simplified beam and plate models.
-The Timoshenko beam and Reissner-Mindlin plate theories are popular theories used in mathematics and engineering.
-An example of ongoing research using these theories is the study of suspension bridges.
-The articles \cite{Mck99}, \cite{BOC20} are examples of mathematical studies while \cite{SV86} follows an engineering approach.\\
 
- This dissertation is a literature study on the Finite Element Analysis 
- \begin{itemize}
-	\item Considering linear mathematical model s for elastic beams and plates.
-	\item Focus is on the one-dimensional Timoshenko beam theory and two-dimensional Reissner-Mindlin plate theory
-	\item Also require two and three-dimensional beam models and a three-dimensional plate model
-	\item Models are used in variational form (Chapter 1)
-	\item Existence and uniqueness of solutions (Chapter 2)
-	\item Convergence of FEM (Chapter 3)
-	\item Chapter 4: - Timoshenko beam theory - Modal analysis - Examples of calculating eigenvalues and eigenvectors - Emperical study - Tipbody model with numerical results.
-	\item Chapter 5: FEM applied to cantilever 3D, 2D and plate elastic bodies
-	\item Chapter 6: Validity of Timo and Reissner-Mindlin Models
-\end{itemize}
+This dissertation is a literature study that investigates the validity of different linear models in application.
+Validity in this context refers to how well simplified lower-dimensional models, such as the Timoshenko beam and Reissner-Mindlin plate models, compare to more realistic higher-dimensional models, including a two-dimensional beam, and three-dimensional beam and plate models.
+The models in this dissertation are all special cases of a general vibration problem.
 
+First, the dissertation examines the existence and uniqueness of the general vibration problem.
+An example is used to to explain the theory, which is then subsequently applied to by proving that the assumptions are satisfied.
+
+Following this, the concept of modal analysis is introduced using an example, before delving into the general case.
+These results on modal analysis are crucial to the dissertation, as they explain that the solutions of the models will compare well if the eigenvalues and eigenfunctions of the models compare well.
+
+The dissertation then explores two theoretical results for the Finite Element Method (FEM).
+The initial result involves an analysis of an article on the convergence of the Galerkin Approximation.
+The findings of the article are reformulated as theorems with simplified notation for clearer presentation
+
+Subsequently, the dissertation reviews results from a textbook regarding the convergence of eigenvalues and eigenfunctions in a general vibration problem when utilizing FEM.
+These results are adapted with updated notation and expanded upon for a more comprehensive explanation of the theory.
+
+Concerning the Timoshenko beam model, the dissertation investigates an article that presents a method to calculate the exact solutions of the eigenvalue problem.
+Two practical examples are provided to illustrate the application of this method.
+Additionally, the dissertation looks at an article that compares the theoretical results of the eigenvalue problem with an empirical study done by the authors.
+
+For the remaining models, the dissertation employs FEM to solve the eigenvalue problems.
+The boundary value problems of each model is rewritten as systems of ordinary differential equations in matrix form using FEM.
+The eigenvalue problems are then derived from this matrix representation.
+Piecewise Hermite cubic basis functions are used, and the solutions of the eigenvalue problems are approximated using MATLAB scripts.
+
+In investigating the validity of simplified models, the dissertation first considers an article comparing the Timoshenko beam model to a two-dimensional beam model.
+The authors method of comparison is discussed, and their results are replicated with a higher degree of accuracy.
+The dissertation then extends this approach to assess the validity of a two-dimensional beam model and a Reissner-Mindlin plate model, using the three-dimensional model as reference.
+The method to compare the models are the same as in the article.
+First the eigenvalues are calculated, sorted and matched by analyzing the corresponding mode shapes.
+The mode shapes are also used to identify eigenvalues specific to beam- and plate-type problems.
+The error can then be calculated.
+Different shapes of beams and plate models are considered that are realistic in application.
+
+The derivation and comparison of the two and three-dimensional models is the main contribution of this dissertation.
 \end{document}

### 2023-12-03 word_count.py

@@ -2,23 +2,23 @@
 
 
 text = """
-In the first chapter, the models of this dissertation are presented and a dimensionless variational form for each is derived. The model problems for this dissertation are then formulated.
+This dissertation is a literature study that investigates the validity of different linear models in application. Validity in this context refers to how well simplified lower-dimensional models, such as the Timoshenko beam and Reissner-Mindlin plate models, compare to more realistic higher-dimensional models, including a two-dimensional beam, and three-dimensional beam and plate models. The models in this dissertation are all special cases of a general vibration problem. 
 
-In the second chapter, two results are investigated. This first is on the existence and uniqueness of solutions for vibration problems. An article is discussed that proves the existence and uniqueness of solutions for a general vibration problem using semi-group theory and assuming four assumptions. All the models in this dissertation is a special case of this general problem, so the theory can be explained and applied to an example. The weak variational form for a cantilever Timoshenko beam is derived. In this derivation, we also give the definitions of the spaces required. The theory is then applied to this example problem. We show that the four assumptions can be proven to be true for the cantilever Timoshenko beam model.
+First, the dissertation examines the existence and uniqueness of the general vibration problem. An example is used to to explain the theory, which is then subsequently applied to by proving that the assumptions are satisfied. 
 
-The next result is in Modal Analysis. Again the cantilever Timoshenko beam model is used to first explain the theory, before the general case is discussed. A trial solution is presented and substituted into the partial differential equations. This results into two problems, an eigenvalue problem and an ordinary differential equation. These two problems are solved and substitution can confirm then that the trial solutions are indeed solutions. The method obtains the same result as separation of variables, but avoids any division. Finally a formal series solution for the example is given. The general case is then discussed and follows the same idea. Modal analysis is crucial for this dissertation. For the comparisons later in this dissertation, a method is required to compare the different models. Modal analysis shows that is the eigenvalues and eigenfunctions of the models compare well, then the solutions of the models should compare well. And since the Fourier Coefficients gets small very fast, it is only required to look at the first few eigenvalues.
+Following this, the concept of modal analysis is introduced using an example, before delving into the general case. These results on modal analysis are crucial to the dissertation, as they explain that the solutions of the models will compare well if the eigenvalues and eigenfunctions of the models compare well.
 
[…]

### 2023-12-04 summary.tex
summary grammer fix

@@
 For the remaining models, the dissertation employs FEM to solve the eigenvalue problems.
-The boundary value problems of each model is rewritten as systems of ordinary differential equations in matrix form using FEM.
+The boundary value problems of each model are rewritten as systems of ordinary differential equations in matrix form using FEM.
 The eigenvalue problems are then derived from this matrix representation.
@@
 The dissertation then extends this approach to assess the validity of a two-dimensional beam model and a Reissner-Mindlin plate model, using the three-dimensional model as reference.
-The method to compare the models are the same as in the article.
+The method to compare the models is the same as in the article.
 First the eigenvalues are calculated, sorted and matched by analyzing the corresponding mode shapes.

### 2024-03-06 article.tex
article

\documentclass[preprint,11pt]{elsarticle}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{draftwatermark}
\usepackage{tabularx} % Required for tables that stretch to text width
\usepackage{booktabs} % For prettier tables
\usepackage{ltablex}
\usepackage{xcolor,cancel,bm,tikz}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage{enumitem}
\usepackage{kantlipsum,graphicx}
\usepackage{multicol,colortbl,multirow}
\usepackage{pgfplots,booktabs,xfrac,floatrow}
\usepackage{color}

\usepackage{setspace}
\setstretch{0.7} % Adjust this value as needed

\setlength{\parindent}{0pt}

\usepackage{geometry}
\geometry{
  left=1in,
  right=1in,
  top=1in,
  bottom=1in,
}

\SetWatermarkText{DRAFT}
\SetWatermarkScale{1}

\journal{Mathematical and Computer Modelling}

\begin{document}

\begin{frontmatter}

\title{Validity of a model for a cantilever two-dimensional beam}

\author{Rudi du Toit}
\address{University of Pretoria, Pretoria, South Africa}

\begin{abstract}
Your abstract here.
\end{abstract}

\begin{keyword}
Vibration \sep Cantilever \sep Beam \sep Three-Dimensional \sep Two-Dimensional
\end{keyword}

\end{frontmatter}

\section{Introduction}
Your introduction here.

\section{Models}

\subsection{Three-dimensional model}
Consider a vector valued displacement function $u \in \Omega \subset R^3$.

\subsubsection*{Equation of motion}\label{ssec:3D_Model:EquationOfMotion}
\begin{eqnarray}
	\rho\partial_t^2 u & = & \textrm{div}T + Q. \label{eq:3D_Model:EM}
\end{eqnarray} \label{sym:rho} \label{sym:partial_diff} \label{sym:T} \label{sym:Q}

Here $\rho$ is the density, $T$ is the stress tensor, and $Q$ is the external 
force per unit volume and $\textrm{div}T$ is the divergence of the tensor $T$ and represented by
\begin{eqnarray}
	\textrm{div}  T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13} \\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23} \\
		\partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
	\end{bmatrix}. \label{eq:3D_Model:divT}
\end{eqnarray}

Assuming only small vibrations, the stress tensor $T$ is symmetric due to small
local displacements and rotations. The trace of the stress tensor $T$ is denoted
\begin{eqnarray}
	\textrm{Tr}(T) & = & \sigma_{11} + \sigma_{22} + \sigma_{23}. \label{eq:stress_tensor_t}
\end{eqnarray}

\subsubsection*{Constitutive Equation}
For an isotropic material, Hooke's law can be written in terms of Young's modulus $E$ and Poisson's ratio $\nu$ as follows.\\

\textbf{Hooke's law}
\begin{eqnarray}
	\mathcal{E} = \left( \frac{1+\nu}{E} \right)T - \frac{\nu}{E}\textrm{Tr}(T)I,  \label{eq:3D_Model:HL}
\end{eqnarray} The components of the strain tensor $\mathcal{E}$ are defined as
\begin{eqnarray}
	\varepsilon_{ij} = \frac{1}{2}\left( \frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} \right). \label{eq:3D_Model:Strain}
\end{eqnarray}\label{sym:varepsilonij}

If the principal stresses $\sigma_i$ are all non-zero, then Hooke's law can be written in an alternative form.\\

\textbf{Hooke's law in the alternative form}
\begin{eqnarray}
	T = \left( \frac{E}{1+\nu} \right)\mathcal{E} + \frac{\nu E}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \label{eq:3D_Model:CE}.
\end{eqnarray}
With $\textrm{Tr}(\mathcal{E}) = \epsilon_{11} + \epsilon_{12} + \epsilon_{13}$ is the trace of the strain operator $\mathcal{E}$.\\

In this form, Hooke's law is the constitutive equation for the three-dimensional model.

\subsection{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
Suppose $\ell$ represents some notable dimension (e.g.the length) of the elastic body 
and $G$ the shear modulus of elasticity.\\

Set \[\tau = \frac{t}{t_0},\quad \xi_i = \frac{x_i}{\ell},\quad {u}^*(\xi,\tau) = \frac{1}{\ell}{u}(x,t), \quad Q^{*} = \ell G \kappa^2 Q, \text{and} \ \,\,\, \sigma_{ij}^*(\xi,\tau) = \frac{1}{G\kappa^2}\sigma_{ij}(x,t),\]\label{sym:t}\label{sym:G}\label{sym:tau}\label{sym:xi}\label{sym:Qstar}\label{sym:sigmaijstar}\label{sym:ell}\label{sym:kappa2}

where $\kappa^2$ is a dimensionless constant and $t_0$ must be specified. Choose \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}} \textrm{ and } \gamma= \frac{G\kappa^2}{E}.\]

Substitution into \eqref{eq:3D_Model:EM} and yields
\begin{eqnarray*}
	\partial_{\tau} u^{*} = \textrm{div}T^* + Q^* \textrm{ where } T^* = \sigma_{i,j}^*(\xi,\tau).
\end{eqnarray*}

The dimensionless forms of \eqref{eq:3D_Model:HL} and \eqref{eq:3D_Model:CE} are
\begin{eqnarray*}
	\mathcal{E} = \frac{G \kappa^2}{E} \left[ (1+\nu)T^* - \nu \textrm{Tr}(T^*)I \right],
\end{eqnarray*}\label{sym:I}

and
\begin{eqnarray*}
	T^* = \frac{E}{G \kappa^2} \left[\left( \frac{1}{1+\nu} \right)\mathcal{E} + \frac{\nu}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \right].
\end{eqnarray*}

Using the dimensionless constant $\gamma$,
\begin{eqnarray}
	\mathcal{E} = \gamma(1+\nu)T^* - \gamma\nu \textrm{Tr}(T^*)I \label{DM_H_E}
\end{eqnarray}
and
\begin{eqnarray}
	T^* = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I. \label{DM_H_T}
\end{eqnarray}

\textbf{Remark} Some of the constants are introduced to simplify the equations and also allow for comparisons to other models such as the Timoshenko beam model.

The original notation is retained for convenience.

\subsubsection*{Equations of motion in dimensionless form}\label{sssec:3D_Model:EquationOfMotionDimensionless}
\begin{eqnarray}
	\partial_t^2 u & = & \textrm{div}T + Q \label{eq:3D_Model:EM-D}
\end{eqnarray}
with
\begin{eqnarray}
	\textrm{div}  T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13} \\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23} \\
		\partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
	\end{bmatrix}.\label{eq:3D_Model:divT-D}
\end{eqnarray}

\subsubsection*{Constitutive equations in dimensionless form}\label{sssec:3D_Model:ConstitutiveEquationsDimensionless}
\begin{eqnarray}
	T = \frac{1}{\gamma(1+\nu)} \mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \label{eq:3D_Model:CE-D}
\end{eqnarray}

\subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
Divide the boundary of $\Omega$ into two distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be considered a model problem for a three-dimensional elastic body. 
The following will be considered a model problem for a three-dimensional elastic body (also for the two-dimensional elastic body).
\begin{enumerate}
	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} is satisfied in $\Omega$;
	\item[] Hooke's law \eqref{eq:3D_Model:CE-D} is satisfied in $\Omega$;
	\item[] The displacement $u = u_\Sigma$ is specified on
		$\Sigma$; The traction $Tn = t_\Gamma$ is specified on
		$\Gamma$.
\end{enumerate} \label{sym:n}\label{sym:SigmaGamma}

\subsubsection{Problem 3D}
Find a vector valued function $u$, satisfying equations
\eqref{eq:3D_Model:EM-D} to \eqref{eq:3D_Model:CE-D} and the following boundary
conditions:\\

Boundary Conditions:
\begin{eqnarray*}
	u & = & 0 \quad \textrm{ on } \Sigma\\
	Tn & = & 0 \quad \textrm{ on } \Gamma
\end{eqnarray*} With $n$ the outward normal vector to $\Omega$. This model problem is a cantilever three-dimensional body.

\subsection{Variational form}\label{ssec:3D_Model:VariationalForm}
Define the bilinear forms
\begin{eqnarray}
	b(u,\phi) = \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dV \label{eq:3D_Model:Bilinear}
\end{eqnarray}\label{sym:b}
and
\begin{eqnarray}
	c(u,\phi) = \int_\Omega~ (\partial^2_t u) \cdot \phi~dV \label{eq:3D_Model:Bilinear_c}
\end{eqnarray}
with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.\\

Also define the integral
\begin{eqnarray}
	(f,g) &=& \int_{\Omega} f\cdot g \ dV \label{eq:3D_Model:Bilinear_int}
\end{eqnarray}

Define the following set of test functions $T(\Omega)$ for Problem 3D:
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}
\end{eqnarray*}\label{sym:TOmega}

The variational problem of Problem 3DV is given as:
\subsubsection{Problem 3DV}\label{sssec:3D_Model:Problem3D1V}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi), \label{eq:3D_Model:Problem3D1VEq}
\end{align}
for all $\phi \in T(\Omega)$\\

\subsection{Plane stress}\label{ssec:3D_Model:PlaneStress}
Stresses acting parallel to a single plane are referred to as plane stress. 
Consider the right-hand orthonormal set $\left\{e_1, e_2, e_3\right\}$. Without
loss of generality, assume the stresses act parallel to the $e_1$-$e_2$ plane
i.e. $\sigma_{3i} = 0$ for all $i$. From Hooke's Law \eqref{DM_H_E} the
following equations are obtained: \label{sym:e_i}

\begin{equation}
	\begin{aligned}
		\varepsilon_{11} & =  \gamma  ( \sigma_{11} - \nu \sigma_{22}) \qquad \qquad \varepsilon_{33} & = & - \gamma \nu (\sigma_{11} + \sigma_{22})          \\
		\varepsilon_{22} & =   \gamma (\sigma_{22} - \nu\sigma_{11}) \qquad \qquad \varepsilon_{12}   & = & \  \gamma (1+\nu) \sigma_{12} \label{strain_comp}
	\end{aligned}
\end{equation}

and a sufficient condition
\begin{eqnarray}
	\varepsilon_{13} =  \varepsilon_{23} = 0.
\end{eqnarray}

After some manipulation, the following stress-strain relations are obtained:
components given in \cite{Fung65}.

\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)} ( \varepsilon_{11} + \nu\varepsilon_{22})\\
		\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)} (\nu \varepsilon_{11} + \varepsilon_{22}).
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray}
		\sigma_{12} & = & \frac{1}{\gamma(1+\nu)} \varepsilon_{12} \label{stress_comp}
	\end{eqnarray}
\end{minipage}\\

Another necessary strain condition for plane stress is found by substituting
$\sigma_{11}$ and $\sigma_{22}$ from \eqref{stress_comp} into
$\varepsilon_{33}$ in \eqref{strain_comp} to obtain
\begin{eqnarray}
	\varepsilon_{33} = -\frac{\nu}{1-\nu} (\varepsilon_{11} + \varepsilon_{22}).\label{plane_stress_neseccary_condition}
\end{eqnarray}

This is known as general plane stress.

\subsection{Two-dimensional model}
Using \cite{Sadd05} as a guide, a special case of general plane stress is considered.

Assume that $\sigma_{3i} = 0$ for $i = 1, 2, 3$; $\partial_3 u_1 = 0$, $\partial_3 u_2 = 0$ ($u_1$ and $u_2$ are functions of $x_1$ and $x_2$), and the strain component $\varepsilon_{33} = 0$. Then using the definition of strain 
\begin{eqnarray}
	\partial_i u_3 = 0 \quad \textrm{ for } i = 1,2,3 \textrm{ on } \Omega.
\end{eqnarray}

It follows that $u_3$ is a constant on $\Omega$ and $u$ is a vector valued function in 
$R^2$ with two-dimensional stress and strain. The out of plane conditions for strain 
\eqref{plane_stress_neseccary_condition} falls away and Hooke’s law can be written in a 
two-dimensional form using the stress components (1.2.16) as 
\[ T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E})I.\]

\subsection{Equations of motion and constitutive equations}\label{ssec:2D_Model:EquationsOfMotion+ConstitutiveEquations}
 The following equations of motion and constitutive equations follow from subsections \ref{ssec:3D_Model:DimensionlessForm} and 1.3.2.
\subsubsection{Equation of motion}\label{sssec:2D_Model:EquationOfMotion}
\begin{eqnarray}
	\partial_t^2 u & = & \textrm{div}T + Q, \label{eq:2D_Model:EM}
\end{eqnarray}
where
\begin{eqnarray}
	\textrm{div} T & = &
	\begin{bmatrix}
		\partial_1 \sigma_{11} + \partial_2 \sigma_{12} \\
		\partial_1 \sigma_{21} + \partial_2 \sigma_{22}
	\end{bmatrix}. \label{eq:2D_Model:DivT}
\end{eqnarray}
\subsubsection{Constitutive equation}\label{sssec:2D_Model:ConstitutiveEquation}
\begin{eqnarray}
	T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{Tr}(\mathcal{E}) I. \label{eq:2D_Model:CE}
\end{eqnarray}

\subsection{Model problem}\label{ssec:2D_Model:ModelProblem}
Divide the boundary of $\Omega$ into two distinct parts, referred to as $\Sigma$ and $\Gamma$.

\subsubsection{Problem 2D}\label{sssec:2D_Model:Problem2D1}
Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:\\

Boundary Conditions:\\
\begin{eqnarray*}
	u & = & 0 \quad \textrm{ on } \Sigma,\\
	Tn & = & 0 \quad \textrm{ on } \Gamma.
\end{eqnarray*} with $n$ the outward unit normal. This model problem is a cantilever two-dimensional body.

\subsection{Variational form}\label{ssec:2D_Model:VariationalForm}
Define the bilinear forms
\begin{eqnarray}
	b(u,\phi) = \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dA \label{eq:2D_Model:Bilinear}
\end{eqnarray}
and
\begin{eqnarray}
	c(u,\phi) = \int_\Omega~ (\partial^2_t u) \cdot \phi~dA \label{eq:2D_Model:Bilinear_c}
\end{eqnarray}
with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.\\
Also define the integral
\begin{eqnarray}
	(f,g) &=& \int_{\Omega} f\cdot g \ dA \label{eq:2D_Model:Bilinear_int}
\end{eqnarray}

\subsubsection{Test functions for Problem 2D}\label{sssec:2D_Model:TestFunctions2D1}
Define the following set of test functions $T(\Omega)$ for Problem 2D:
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}. 
\end{eqnarray*}\label{sym:baromega}

The variational problem of Problem 2D is given as:

\subsubsection{Problem 2DV}\label{sssec:2D_Model:Problem2D1V}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{eq:2D_Model:Problem2D1VEq}
\end{align}
for all $\phi \in T(\Omega)$.\\

\section{Existance and uniqueness of solutions}
The models in this article concern the vibration of elastic bodies. These type of models
have a similar variational form as the wave equation and are called second order hyperbolic
type problems. The articles \cite{VV02} and \cite{VS19} provide existence and uniqueness
results for these type of problems. In \cite{VV02}, it is assumed that $b$ is symmetric. 
\cite{VS19} extends the results of \cite{VV02} to the case where $b$ is not symmetric. For
the models in the article, \cite{VV02} is a sufficient reference.\\

Let $V$, $W$ and $X$ be Hilbert spaces such that $V \subset W \subset X$.
\begin{itemize}
	\item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
	\item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
	\item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
\end{itemize}

Consider a general second order hyperbolic type problem GVar. This general problem is used by the 
authors of \cite{VV02} to prove existence and uniqueness results. The models in this article are 
special cases of this general problem.\\

\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
\begin{eqnarray}
	c(u''(t),v)+a(u'(t),v)+b(u(t),v)= (f(t),v)_{X} \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVar}
\end{eqnarray}
while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\\

The following assumptions are made in \cite{VV02} for the existence results.
\begin{itemize}
	\item[] \textbf{A1} - $V$ is dense in $W$ and $W$ is dense in $X$.

	\item[] \textbf{A2} - There exists a positive constant $C_{W}$ such that $\Vert w\Vert_{X} \leq C_{W}\Vert w\Vert_{W}$ for each $ w\in W$.

	\item[] \textbf{A3} - There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.

	\item[] \textbf{A4} - The bilinear form $a$ is non-negative, symmetric and bounded on $V$, i.e. there exists a positive constant $K_a$ such that for $\displaystyle u,v \in V$, \[|a(u,v)| \leq K_a\Vert u \Vert_V \Vert v \Vert_V.\]
\end{itemize}

Proving that these assumptions are satisfied for the models in this article too much work to 
include in this article. The existence and uniqueness results of \cite{VV02} are used in 
this article without proof.

\section{Modal analysis and comparison of linear models}
Modal analysis is a important concept in the study of vibration of elastic bodies and also 
useful in the comparison of linear models. The following section is a short discussion of 
the basic concepts of modal analysis and how it enables the comparison of linear models.\\

The discussion follows the article \cite{CVV18}, excluding damping. Consider Problem GVar with no damping or external forces.

\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
\begin{eqnarray}
c(u''(t),v)+b(u(t),v) = 0 \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
\end{eqnarray}
with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.\\

Now consider a trial solution $u(t) = T(t)x$ with $x \in V$ and $x \neq 0$. Substituting this trial solution into \eqref{eq:existence:ProblemGVarHom} results in
\begin{eqnarray*}
	b(T(t)x,v) = - c(T''(t)x,v).  \label{eq:existence:ProblemGVarHom:Substitution}
\end{eqnarray*}

Due to the linearity of the bilinear form, this equation can be rewritten as
\begin{eqnarray*}
	T(t)b(x,v) = - T''(t)c(x,v).
\end{eqnarray*}

Dividing both sides by $T(t)$ gives
\begin{eqnarray*}
	b(x,v) = - \frac{T''(t)}{T(t)}c(x,v).
\end{eqnarray*}

Therefore $\displaystyle -\frac{T''(t)}{T(t)}$ must be constant. Suppose that $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. The existence of such a $\lambda$ is uncertain at this point. So we consider the following eigenvalue problem.\\

Find a real number $\lambda$ and a $x \in V$ with $x \neq 0$ such that
\begin{eqnarray*}
	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
\end{eqnarray*}

A solution to the eigenvalue problem consists of an eigenvalue $\lambda$ with corresponding eigenvector $x$.

The article \cite{CVV18} is a convenient reference to show that the eigenvalue problem has a solution if the following assumption, aditional to \textbf{A1}, \textbf{A2}, \textbf{A3} and \textbf{A4},  is satisfied:

\begin{itemize}
	\item[] \textbf{A5} - The embedding of $V$ into $W$ is compact.
\end{itemize}

Using these assumptions, the authors of \cite{CVV18} prove that there exists a complete orthonormal sequence of eigenvectors for the eigenvalue problem with a corresponding sequence of eigenvalues. These eigenvalues are positive and the orthogonality is with respect to the bilinear form $c$. In fact it is also orthogonal with respect to the bilinear form $b$,
\begin{eqnarray*}
	b(x_i, x_j) = \lambda_i c(x_i, x_j) = 0, \ \ \ \ \textrm{ for each } \ i \neq j.
\end{eqnarray*}

Also the sequence of normalized eigenvectors ${x_i}$ forms an orthonormal basis in $W$ and sequence of eigenvalues ${\lambda_i}$ is an infinite sequence with $\lambda_n \rightarrow \infty$ as $n \rightarrow \infty$.

Following these results from \cite{CVV18}, for any $u \in V$, $\displaystyle u = \sum_{i=1}^{\infty} a_i x_i$. These coefficients $a_i$ are generalized Fourier coefficients of $u$ with respect to the eigenvectors $x_i$. Therefore, for any $u \in V$,
\begin{eqnarray*}
	u = \sum_{i=1}^{\infty} a_i x_i. = \sum_{i=1}^{\infty} c(u, x_i)x_i.
\end{eqnarray*}

Now that the eigenvalue problem has many solutions, the following ordinary differentiable equation can be considered,
\begin{eqnarray*}
	T_n'' + \lambda T_n = 0. 
\end{eqnarray*}

Since this differential equation is a simple second order differential equation, $T_n(t)$ has the following possible solutions:
\begin{flalign}
	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda_n > 0, \label{lambda_1}
\end{flalign}

Then combining the solutions of the eigenvalue problem and the differential equation, the formal series solution for the boundary value problem is
\begin{eqnarray}
	u(t) = \sum_{n=1}^{\infty} T_n(t)x_n. \label{eq:1D_Model:ModalAnalysisSeriesSolution}
\end{eqnarray}

\subsection{Validity of series solution}
Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$? To answer this question, we again refer to the article \cite{CVV18}.\\

In the article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ a function $u$ given by \label{sym:Energy}
\begin{eqnarray}
	\mathcal{E} (t) = \frac{1}{2} b(u(t), u(t)) + \frac{1}{2} c(u'(t), u'(t)). \label{eq:1D_Model:ModalAnalysisEnergy}
\end{eqnarray}

Then,
\begin{eqnarray*}
	\mathcal{E}'(t) & = & b(u(t), u'(t)) + c(u'(t), u''(t)),\\
					& = & 0 \ \ \ \ \ \ \ \textrm{ following from \eqref{eq:existence:ProblemGVarHom}}. 
\end{eqnarray*}

Therefore $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$. For the case of weak damping, it can be proved that $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ which is the case of \cite{CVV18}.\\

Denote the partial sum $u^{N}(t) = \sum_{n=1}^{N} T_{n}(t)w_n$. Ideally
\begin{eqnarray*}
	u_0^{N} = \sum_{n=1}^{N} T_n(0) w_n \ \ \textrm{ and } \ \ u_{1}^{N} =\sum_{n=1}^{N} T'_n(0) w_n,
\end{eqnarray*}
but $T_n$ is not uniquely defined by the differential equation.\\

Substitution shows that these partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions for \eqref{eq:existence:ProblemGVarHom} in Problem GVar.\\

The authors then define an error function $u^E_N = u - u^N$. Since both $u$ and $u^N$ satisfies \eqref{eq:existence:ProblemGVarHom}, so does this error function with the following the initial conditions, $u^E_N(0) = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.\\

Let $\mathcal{E}$ denote the energy of the error function $u^E_N$. Since $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$ it follows that, 
\begin{eqnarray}
	||u(t) -  u^N(t)||_V^2 + ||u'(t) - (u^N)'(t)||^2_W = ||u_0 - u^N_0||_V^2 + ||u_1 - u^N_1||_W^2. \label{eq:inequality}
\end{eqnarray}

Now, $u_0$ and $u_1$ are given in Problem GVar. Therefore the generalized Fourier coefficients for $u_0$ and $u_1$ must be used to compute $u_0^N$ and $u_1^N$. These Fourier coefficients are $\displaystyle u_0^N = \sum_{n=1}^{N} b(u_0, w_n)w_n$ and $\displaystyle u_1^N = \sum_{n=1}^{N} c(u_1, w_n)w_n$.

Then $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$. Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$ by \eqref{eq:inequality}.\\

It follows that the partial sums of the series solution converges to the solution $u$ as the initial conditions $u_0^N$ and $u_1^N$ converges to $u_0$ and $u_1$ respectively.

\subsection{Comparison of models}
The results on modal analysis and the validity of the series solution enable the comparison of different linear models. The solution of the model problems can be expressed as a series solution of the eigenvalues and eigenvectors of the models. Therefore the models can be compared by comparing the eigenvalues and eigenvectors of the models.\\

The validity of the series solution also ensures that the comparisons remain valid, no matter the inital distrubance of the models. Suppose that for the same initial conditions, $u_b$ and $u_w$ are the exact solutions. A comparison of the exact solutions are not possible, but the partial sums can be compared if the bounds for the errors $u_b - u^N_b$ and $u_w - u^N_w$ can be guaranteed.

\section{Finite element method}

\subsection{Three-dimensional model}
Consider a cantilever three-dimensional elastic body, with a rectangular cross-section.

\subsubsection*{Reference configuration for rectangular cross-section}
Let $\{e_1,e_2,e_3\}$ be a right-handed orthonormal basis for $R^3$. Denote the elastic body as $\Omega \in R^3$ with $(0,0,0)$ the point of reference. For a rectangular cross-section, the body $\Omega$ can be described as
\begin{eqnarray*}
	\Omega = \left\{ x \in R^3 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} , \ -\frac{b}{2} \leq x_3 \leq \frac{b}{2}\right \}
\end{eqnarray*} \label{sym:width}
Let $\partial \Omega$ denote the boundary of the body. Divide $\partial \Omega$ into the six distinct flat surfaces as follows:

\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\Sigma:& \quad x_1 &= 0\\
		\Gamma_5:& \quad x_1 &= 1\\
		\Gamma_1:& \quad x_3 &= -{b}/{2} 
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\Gamma_2:& \quad x_2 &= -{h}/{2}\\
		\Gamma_3:& \quad x_3 &= {b}/{2}\\
		\Gamma_4:& \quad x_2 &= {h}/{2} 
	\end{eqnarray*}
\end{minipage}

Using this notation, the boundary conditions are similar to the two-dimensional model in section \ref{sssec:2D_Model:RefConf}, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.

\subsubsection{Cantilever elastic body}
Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma$ and free-hanging at all the other sides. This is Problem 3D in section \ref{ssec:3D_Model:ModelProblems}.

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.4mm] (-0.5,1) -- (6.5,1);
		\draw[line width = 0.4mm] (-0.5,-1) -- (6.5,-1);
		\draw[line width = 0.4mm] (6.5,-1) -- (6.5,1);
		\draw[line width = 0.4mm] (-0.5,-1) -- (-0.5,1);

		\draw[line width = 0.4mm] (0.5,1.5) -- (7.5,1.5);
		\draw[line width = 0.4mm] (7.5,-0.5) -- (7.5,1.5);

		\draw[line width = 0.4mm] (-0.5,1) -- (0.5,1.5);
		\draw[line width = 0.4mm] (6.5,1) -- (7.5,1.5);
		\draw[line width = 0.4mm] (6.5,-1) -- (7.5,-0.5);

		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+4});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+2.5});

		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+2});
		\draw[scale=0.5, domain=2:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+2});

		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+1.5});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+1});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+0.5});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-0.5});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-1});
		\draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-1.5});
		\draw[scale=0.5, domain=-3:0, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-2});
		\draw[scale=0.5, domain=-3:1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-2.5});
		\draw[scale=0.5, domain=-3:2, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-3});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-3.5});
		\draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-4});

		%\node at (6.9,1) {$b$};
		%\node at (6.65,0) {$h$};
		%\node at (3.2,-1.2) {$\ell = 1$};

		\draw[line width = 0.1mm,->] (9,1) -- (10,1.6);
		\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
		\draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
		\node at (9.3,1.4) {$e_3$};
		\node at (9.7,0.8) {$e_1$};
		\node at (8.8,1.5) {$e_2$};

		\node at (7.7,0.5) {$h$};
		\draw[-stealth] (7.7,0.7) -- (7.7,1.5);
		\draw (7.6,1.5) -- (7.8,1.5);
		\draw[-stealth] (7.7,0.3) -- (7.7,-0.5);
		\draw (7.6,-0.5) -- (7.8,-0.5);

		\node at (3,-1.2) {$1$};
		\draw[stealth-] (-0.5,-1.2) -- (2.8,-1.2);
		\draw[stealth-] (6.5,-1.2) -- (3.2,-1.2);
		\draw (6.5,-1.3) -- (6.5,-1.1);
		\draw (-0.5,-1.3) -- (-0.5,-1.1);

		\node at (7.2,-0.9) {$b$};
		\draw[stealth-] (7.7,-0.5) -- (7.35,-0.75);
		\draw[stealth-] (6.5,-1.2) -- (7,-0.95);

		\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
		\draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
		\node at (9.7,0.8) {$e_1$};
		\node at (8.8,1.5) {$e_2$};

		\node at (-0.6,0) {$(0,0)$};
		\node at (0,0)[circle,fill,inner sep=1.5pt]{};

		%\node at (-1.4,-1.3) {$(0,-\frac{h}{2},-\frac{b}{2})$};
		%\node at (-1.4,1) {$(0,\frac{h}{2},-\frac{b}{2})$};
		%\node at (0.5,1.8) {$(0,\frac{h}{2},\frac{b}{2})$};

		%\node at (6,-1.3) {$(1,-\frac{h}{2},-\frac{b}{2})$};
		%\node at (6.3,0.7) {$(1,\frac{h}{2},-\frac{b}{2})$};
		%\node at (7.5,1.8) {$(1,\frac{h}{2},\frac{b}{2})$};
		%\node at (8.4,-0.4) {$(1,-\frac{h}{2},\frac{b}{2})$};

	\end{tikzpicture}

\end{figure}

In section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3DV. This general form can now be rewritten as in a model specific form using the reference configuration. For convenience, some of the results from section \ref{sec:3D_Model} are repeated here.

\subsubsection{Problem 3DV}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
\begin{align}
	c(u,\phi) = -b(u,\phi) - (Q,\phi) \label{3DB_20}
\end{align}
for all $\phi \in T(\Omega)$.\\

With the test function space
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C(\Omega) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
\end{eqnarray*}

The bilinear forms and integral function are defined by
\begin{eqnarray}
	b(u,\phi) &=& \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dV,\\
	c(u,\phi) &=& \int_\Omega~ (\partial^2_t u) \cdot \phi~dV, \\
	(f,g) &=& \int_{\Omega} f\cdot g \ dV, \\
\end{eqnarray}
with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.\\

Using the definition of the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten in the following model specific forms: 
\subsubsection*{Constitutive equations}
\begin{eqnarray*}
	\sigma_{11} & = &  \frac{1}{\gamma(1+\nu)}\partial_1 u_1 + \frac{\nu}{\gamma (1+\nu)(1-2\nu)}(\partial_1 u_1 +  \partial_2 u_2 + \partial_3 u_3)\label{3DB_3}\\
	\sigma_{22} & = &  \frac{1}{\gamma(1+\nu)}\partial_2 u_2 + \frac{\nu}{\gamma (1+\nu)(1-2\nu)}(\partial_1 u_1 +  \partial_2 u_2 + \partial_3 u_3)\label{3DB_4}\\
	\sigma_{33} & = &  \frac{1}{\gamma(1+\nu)}\partial_3 u_3 + \frac{\nu}{\gamma (1+\nu)(1-2\nu)}(\partial_1 u_1 +  \partial_2 u_2 + \partial_3 u_3)\label{3DB_5}\\
	\sigma_{23} & = &  \frac{1}{2\gamma(1+\nu)}(\partial_3 u_2 + \partial_2 u_3)\label{3DB_6}\\
	\sigma_{31} & = &  \frac{1}{2\gamma(1+\nu)}(\partial_3 u_1 + \partial_1 u_3)\label{3DB_7}\\
	\sigma_{12} & = &  \frac{1}{2\gamma(1+\nu)}(\partial_2 u_1 + \partial_1 u_2)\label{3DB_8}
\end{eqnarray*}

\subsubsection{Bilinear Form}
\begin{align*}
	b(u,\phi)  &=  \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dV \nonumber\\
	 &=  \int_{\Omega} \sigma_{11} \partial_1\phi_1 + \sigma_{12}\partial_1 \phi_2 + \sigma_{13}\partial_1 \phi_3 + \sigma_{21}\partial_2 \phi_1 + \sigma_{22}\partial_2\phi_2 + \sigma_{23}\partial_2 \phi_3 ~dV
\end{align*}

\subsection{Weak variational form}

\subsubsection{Bilinear form}
Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)\times H^1(0,1)$. Denote $X = L^2(0,1)\times L^2(0,1)\times L^2(0,1)$. The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.

\subsubsection{Problem 3DW}
Find a function $u$ such that for all $t>0$, $u(t) \in V$ and $u''(t) \in W$, satisfying the following equation
\begin{eqnarray}
	c(u,v) + b(u,v) & = & (Q,v) \ \ \ \textrm{ for each } v \in V.
\end{eqnarray}

\subsection{Galerkin approximation}
As mentioned in the previous section, section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised. For this is three-dimensional body, three-dimensional elements shapes are required. The elements used in this dissertation are rectangular prismatic elements. These elements are also known as `brick-shaped' elements and is described in \cite{Wu06}. This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.

Divide the reference configuration $\Omega$ into a grid of rectangular prismatic elements, such that there are $n = n_1 \times n_2 \times n_3$ nodes.

Define a set of $n$-dimensional linear independent basis functions. For the three-dimensional model, the basis functions can be defined by the set
\begin{eqnarray*}
 B = \{\langle\phi_1, 0 , 0\rangle, \langle\phi_2, 0, 0\rangle,...,\langle\phi_{n}, 0, 0 \rangle,\\
	\langle 0,\phi_1 ,0 \rangle,\langle 0 ,\phi_2,0\rangle,...,\langle 0,\phi_{n},0\rangle,\\
	\langle 0,0,\phi_1 \rangle,\langle 0,0,\phi_2\rangle,...,\langle 0,0,\phi_{n}\rangle \}.
\end{eqnarray*}

For the this three-dimensional model, piecewise Hermite tri-cubic basis functions are used. Although this is more complex than using piecwise tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.

Recall that the admissible basis functions, are all the basis functions that satisfies all the conditions of the test function space $T(\Omega)$. Denote the admissible basis functions by $\delta_j$, with each $\delta_j$ a unique element of $B$. The set of admissible basis functions can then be expressed as $A = \left\{\delta_1, \delta_2,... , \delta_k\right\}$ with $k \leq 3n$.

Define the space
\begin{eqnarray*}
	S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right)
\end{eqnarray*}

For each function $u^h \in S^h$, $u^h$ can be expressed as
\begin{eqnarray*}
	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x)
\end{eqnarray*}

Substituting $u^h$ into Problem 3DV, results in the following Galerkin approximation, denoted by Problem 3DG.

\subsubsection{Problem 3DG}
Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
\begin{eqnarray*}
	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I \cdot \phi_i)
\end{eqnarray*} for $i = 1,2,...,k$. $Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$. i.e. $Q^I_{i,j, h} = Q(x_i,x_j, x_h)$ for $i = 1,2,...,n_1$, $j = 1,2,...,n_2$ and $h = 1,2,...,n_3$.

\subsection{System of ordinary differential equations}\label{3d_fem_g}
Consider the following standard Finite Element Method matrices.

\subsubsection{FEM matrices}
\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\mathbf{M}_{ij} & = & \int_{\Omega} \phi_j \phi_i \ dV \ \\
		{K_{11}}_{ij} & = & \int_{\Omega} \partial_1\phi_j \partial_1\phi_i \ dV \  \\
		{K_{12}}_{ij} & = & \int_{\Omega} \partial_1\phi_j \partial_2\phi_i \ dV \ \\
		{K_{13}}_{ij} & = & \int_{\Omega} \partial_1\phi_j \partial_3\phi_i \ dV \ 
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		{K_{22}}_{ij} & = & \int_{\Omega} \partial_2\phi_j \partial_2\phi_i \ dV \  \\
		{K_{23}}_{ij} & = & \int_{\Omega} \partial_2\phi_j \partial_3\phi_i \ dV \ \\
		{K_{33}}_{ij} & = & \int_{\Omega} \partial_3\phi_j \partial_3\phi_i \ dV \ \\
	\end{eqnarray*}
\end{minipage}
for $i,j = 1,2,...,k.$\\

And

\begin{eqnarray*}
	\mathbf{M_f}_{ij} & = & \int_{\Omega} \phi_j \phi_i \ dV
\end{eqnarray*}
for $i = 1,2,...,k$ and for $j = 1,2,...,3n.$\\

The remaining matrices can be defined as
\begin{eqnarray*}
	{K_{21}} & = & {K_{12}}^{T},\\
	{K_{31}} & = & {K_{13}}^{T}, \\
	{K_{32}} & = & {K_{23}}^{T}. \\
\end{eqnarray*}

Define the following matrices:\\
\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\mathbf{K11} & = & \left(C_1 + C_2 \right) K_{11} + C_3 K_{22} + C_3 K_{33}\\
		\mathbf{K12} & = & C_3 K_{12} + C_2 K_{21}\\
		\mathbf{K13} & = & C_3 K_{13} + C_2 K_{31}\\
		\mathbf{K21} & = & C_3 K_{21} + C_2 K_{12}\\
		\mathbf{K22} & = & \left(C_1 + C_2 \right) K_{22} + C_3 K_{11} + C_3 K_{33}
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{0.8\linewidth}
	\begin{eqnarray*}
		\mathbf{K23} & = & C_3 K_{23} + C_2 K_{32}\\
		\mathbf{K31} & = & C_3 K_{31} + C_2 K_{13}\\
		\mathbf{K32} & = & C_3 K_{32} + C_2 K_{23}\\
		\mathbf{K33} & = & \left(C_1 + C_3 \right) K_{33} + C_3 K_{11} + C_3 K_{22}
	\end{eqnarray*}
\end{minipage}\\

with $C_1 = \frac{1}{\gamma(1+\nu)}$, $C_2 =  \frac{\nu}{\gamma (1+\nu)(1-2\nu)}$ and $C_3 =  \frac{1}{2\gamma(1-2\nu)}$.\\

Using the standard FEM matrices and the matrices $K11$ to $K33$, the following concatenated matrices are defined:\\

\begin{eqnarray}
	\begin{aligned}
		K = 
		\begin{bmatrix}
			\mathbf{K11} & \mathbf{K12} & \mathbf{K13}\\
			\mathbf{K21} & \mathbf{K22} & \mathbf{K23}\\
			\mathbf{K31} & \mathbf{K32} & \mathbf{K33}
		\end{bmatrix}
	\end{aligned}
	\ \ \ \ \ \ \ \ \
	\begin{aligned}
		M  = 
		\begin{bmatrix}
			\mathbf{M} & {O} & {O}\\
			{O} & \mathbf{M} & {O}\\
			{O} & {O} & \mathbf{M}
		\end{bmatrix}
	\end{aligned}\label{eq:3DFEM:K+M}
\end{eqnarray}

\begin{eqnarray}
	M_f & = &
	\begin{bmatrix}
		\mathbf{M_f} & {O_f} & {O_f}\\
		{O_f} & \mathbf{M_f} & {O_f}\\
		{O_f} & {O_f} & \mathbf{M_f}
	\end{bmatrix}\label{eq:3DFEM:M}
\end{eqnarray}
The matrices ${O}$ and ${O_f}$ are the zero matrices of the same size as $\mathbf{M}$ and $\mathbf{M_f}$ respectively.\\

Using \eqref{eq:3DFEM:K+M} and \eqref{eq:3DFEM:M}, Problem 3DG is rewritten as a system of ordinary differential equations. This system is referred to as Problem 3DODE

\subsubsection{Problem 3DODE}
Find a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	M\ddot{\bar{u}} & = & K\bar{u} + M_{f}Q^I. \label{3D_M}
\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \partial^i_1u \partial^j_2u \partial^k_3u$ for $i,j,k = 0,1,2,3$.

\subsection{Eigenvalue problem}
The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in section \ref{2dFEM_EP}.

\subsubsection{Problem 3DE}\label{3dFEM_EP}
Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	M\lambda{\bar{u}} & = & K\bar{u}.
\end{eqnarray}

Consider a cantilever two-dimensional elastic body, with a rectangular cross-section.

\subsubsection{Reference configuration for rectangular cross-section}\label{sssec:2D_Model:RefConf}
Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$. Denote the elastic body by $\Omega \in R^2$, with $(0,0)$ as the point of reference. For a rectangular cross-section, the body $\Omega$ can be described as,
\begin{eqnarray*}
	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines (or edges) as follows: \label{sym:En}

\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\Sigma:& \quad x_1 &= 0\\
		\Gamma_3:& \quad x_1 &= 1
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\Gamma_1:& \quad x_2 &= -{h}/{2}\\
		\Gamma_2:& \quad x_2 &= {h}/{2}
	\end{eqnarray*}
\end{minipage}

In this configuration, the body is clamped rigidly to the surface at $x_1 = 0$ denoted as $\Sigma$ and the body is free-hanging on the other boundaries denoted by $\Gamma$.

\subsubsection{Cantilever elastic body}
Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D in section \ref{ssec:2D_Model:ModelProblem}.

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}

		\draw[line width = 0.4mm] (0,0.5) -- (7,0.5);
		\draw[line width = 0.4mm] (0,-0.5) -- (7,-0.5);
		\draw[line width = 0.4mm] (7,-0.5) -- (7,0.5);
		\draw[line width = 0.4mm] (0,-0.5) -- (0,0.5);

		\draw[line width = 0.1mm] (0,1.5) -- (0,-1.5);

		\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.3);
		\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.1);
		\draw[line width = 0.1mm] (0,1.1) -- (-0.2,0.9);
		\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.7);
		\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.5);
		\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.3);
		\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.1);
		\draw[line width = 0.1mm] (0,0.1) -- (-0.2,-0.1);
		\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.3);
		\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.5);
		\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.7);
		\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.9);
		\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1.1);
		\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.3);
		\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.5);

		\node at (7.3,0) {$h$};
		\draw[-stealth] (7.3,0.2) -- (7.3,0.5);
		\draw (7.2,0.5) -- (7.4,0.5);
		\draw[-stealth] (7.3,-0.2) -- (7.3,-0.5);
		\draw (7.2,-0.5) -- (7.4,-0.5);

		\node at (3.5,-0.8) {$1$};
		\draw[stealth-] (0,-0.8) -- (3.3,-0.8);
		\draw[stealth-] (7,-0.8) -- (3.7,-0.8);
		\draw (7,-0.9) -- (7,-0.7);

		\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
		\draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
		\node at (9.7,0.8) {$e_1$};
		\node at (8.8,1.5) {$e_2$};

		\node at (-0.6,0) {$(0,0)$};
		\node at (0,0)[circle,fill,inner sep=1.5pt]{};

		% Add Σ at x_1 = 0
		\node at (-1.4,0) {$\Sigma$};

		% Add Γ₁ at x_2 = -h/2
		\node at (3.5,-1.2) {$\Gamma_1$};

		% Add Γ₂ at x_2 = h/2
		\node at (3.5,0.9) {$\Gamma_2$};

		% Add Γ₃ at x_1 = 1
		\node at (8,0) {$\Gamma_3$};

	\end{tikzpicture}
\end{figure}

In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2DV. Some of the results from section \ref{sec:2D_Model} are repeated here for convenience. Using the reference configuration, these results are rewritten from a general form to a model specific form.

\subsubsection{Problem 2DV}\label{sssec:2D_Model:Problem2D1VChp5}
Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
\begin{align}
	c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{eq:2D_Model:Problem2D1VEqChp5}
\end{align}
for all $\phi \in T(\Omega)$. With the test function space 
\begin{eqnarray*}
	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
\end{eqnarray*}

The bilinear forms and integral function is defined by
\begin{eqnarray}
	b(u,\phi) & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
	\textrm{Tr}(\Phi) ~dA, \label{eq:2D_Model:BilinearChp5}\\
	c(\partial_t^2 u,\phi) & = & \int_\Omega~ (\partial^2_t u) \cdot \phi~dA, \label{eq:2D_Model:Bilinear_cChp5}\\
	(f,g) &=& \int_{\Omega} f\cdot g \ dA, \label{eq:2D_Model:Bilinear_intChp5}
\end{eqnarray}
with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.

Using the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten into a model specific form.

\subsubsection{Constitutive equations:}
\begin{eqnarray}
	\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_1 u_1 + \nu \partial_2 u_2) \label{CE1} \\
	\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_2 u_2 + \nu \partial_1 u_1) \label{CE2} \\
	\sigma_{12} & = & \frac{1}{2\gamma(1+\nu)}(\partial_1 u_2 + \partial_2 u_1) \label{CE3}
\end{eqnarray}

\subsubsection{Bilinear form:}
\begin{align}
	b(u,\phi) & = & \frac{1}{\gamma(1-\nu^2)}\int_{\Omega} (\partial_1 u_1 \partial_1 \phi_1 + \partial_2 u_2 \partial _2 \phi_2 + \nu\partial_1 u_1 \partial_2\phi_2 + \nu \partial_2 u_2 \partial_1 \phi_1 ) \ dA \nonumber\\
	& + & \frac{1}{2\gamma(1+\nu)}\int_{\Omega} (\partial_1 u_2 \partial_1 \phi_2 + \partial_1 u_2 \partial_2 \phi_1 + \partial_2 u_1 \partial_1\phi_2 + \partial_2 u_1 \partial_2\phi_1) \ dA.
\end{align}

\subsection{Weak variational form}
Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)$. Denote $X = L^2(0,1)\times L^2(0,1)$. The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.

\subsubsection{Problem 2DWV}
Find a function $u$ such that $\forall \ t > 0$, $u \in V$ with $\partial_t^2 u \in W$ and
\begin{eqnarray*}
	c(u,v) + b(u,v) & = & (Q,v)
\end{eqnarray*}
for all $v\in V$.

\subsection{Galerkin approximation}\label{2d_FEM_G}
To be able to apply the Finite Element Method to Problem 2DV, the body $\Omega$ needs to be discretised. This is done by dividing the body $\Omega$ into discrete shapes, called elements. There are various types of shapes of elements that can be used. Since the body $\omega$ is has a rectangular cross-section, rectangular elements are the simplest elements to use.

Divide the reference configuration $\Omega$ into a grid of rectangular elements, such that there are $n = n_1\times n_2$ nodes.

Define a set of $n$-dimensional linear independent basis functions. For the two dimensional model, the basis functions can be defined by the set $$B = \left\{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \right\}.$$

These functions are chosen as piecewise Hermite bi-cubic functions $\phi_i$. Simpler bi-linear functions can also be used, however the use of the bi-cubic basis functions results in faster convergence and also the benefit of obtaining the derivatives of the solution at the expense of more complexity.

The subset of basis functions $B$ that satisfies all the conditions of the test function space $T(\Omega)$ are called the admissible basis functions. Denote the admissible basis functions by $\delta_j$, where each $\delta_j$ is a unique element of $B$. The admissible basis functions can be numbered and expressed as the set $A = \left \{\delta_1, \delta_2,..., \delta_k \right\}$ for some $k \leq 2n$.\\

Define the space
\begin{eqnarray*}
S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right).
\end{eqnarray*}

For each function $u^h \in S^h$, $u^h$ can be expressed as
\begin{eqnarray*}
	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x).
\end{eqnarray*}

Substitution of $u^h$ into Problem 2DV, results in the following Galerkin Approximation, denoted by Problem 2DG.

\subsubsection{Problem 2DG}
Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
\begin{eqnarray*}
	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I, \phi_i)
\end{eqnarray*} for $i = 1,2,...,k$. $Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$. i.e. $Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.

\subsection{System of differential equations}\label{ssec:2DFEM:DE}

Consider the following standard Finite Element Method matrices
\subsubsection{FEM matrices}
\noindent\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\mathbf{M}_{j,i} & = & \int_{\Omega} \phi_i \phi_j ~dA \\
		\mathbf{{K}_{11}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_1\phi_j~dA\\
		\mathbf{{K}_{22}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_2\phi_j~dA
	\end{eqnarray*}
\end{minipage}%
\begin{minipage}{.5\linewidth}
	\begin{eqnarray*}
		\mathbf{{K}_{12}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_1\phi_j~dA\\
		\mathbf{{K}_{21}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_2\phi_j~dA
	\end{eqnarray*}
\end{minipage}
for $i,j = 1,2,...,k$.

And 
\begin{eqnarray*}
	{M_{F}}_{j,i} = \int_{\Omega}  \phi_i \phi_j~dA
\end{eqnarray*}

for $i = 1,2,...,k$ and for $j =1,2,...,2n$.

Define the following matrices:
\begin{eqnarray*}
	K_1 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{11}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{22}} \label{eq:2DFEM:K1} \\
	K_2 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{21}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{12}}\label{eq:2DFEM:K2}\\
	K_3 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{12}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{21}}\label{eq:2DFEM:K3}\\
	K_4 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{22}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{11}}\label{eq:2DFEM:K4}
\end{eqnarray*}

Using the standard FEM matrices and matrices $K_1$-$K_4$, the following concatenated matrices are defined.
\begin{eqnarray}
	\begin{aligned}
		K = 
		\begin{bmatrix}
			K1 & K2\\
			K3 & K4
		\end{bmatrix}
	\end{aligned}
	\ \ \ \ \ \ \ \ \
	\begin{aligned}
		M_f = 
		\begin{bmatrix}
			M_{F} & O_{F}\\
			O_{F} & M_{F}
		\end{bmatrix}
	\end{aligned}\label{eq:2DFEM:K+M}
\end{eqnarray}

\begin{eqnarray}
	M = 
	\begin{bmatrix}
		\mathbf{M} & O \\
		O & \mathbf{M}
	\end{bmatrix}\label{eq:2DFEM:M}
\end{eqnarray}

The matrices ${O}$ and ${O_f}$ are the zero matrices of the same size as $\mathbf{M}$ and ${M_f}$ respectively.

Using \eqref{eq:2DFEM:K+M} and \eqref{eq:2DFEM:M}, Problem 2DG is rewritten as a system of ordinary differential equations. This system is referred to as Problem 2DODE.

\subsubsection{Problem 2DODE}
Find a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	M\ddot{\bar{u}} & = & K\bar{u} + M_{f}Q^I.
\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \langle u, \partial_1 u, \partial_2 u, \partial_{12} u \rangle$.

\textbf{Remark} This form of $\bar{u}$ is determined by the use of the bi-cubic basis functions.

\subsection{Eigenvalue problem}\label{2dFEM_EP}
For the eigenvalue problem, assume that there is no external force, $M_{f}Q^I = 0$, so that 
\begin{eqnarray}
		M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
\end{eqnarray}
It is known that a system of ordinary differential equations has a general solution of the form $e^{rt}$. Suppose that $\bar{w} = e^{\lambda t} \bar{u}$ is a solution for \eqref{eq:2DFEM:M2}. In this solution, $\lambda$ is an eigenvalue and $\bar{u}$ a corresponding eigenfunction. Substitution into \eqref{eq:2DFEM:M2} results in
\begin{eqnarray*}
	M\lambda e^{\lambda t}\bar{u} & = & Ke^{\lambda t}\bar{u}.
\end{eqnarray*}
Since $e^{\lambda t} > 0$ for all values of $\lambda t$, we can cancel it from both sides of the equation and formulate the eigenvalue problem Problem 2DE.

\subsubsection{Problem 2DE}
Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	M\lambda{\bar{u}} & = & K\bar{u}.
\end{eqnarray}

\section{Results}

\section{Validity of a model for a cantilever two-dimensional beam} \label{sec:validity-of-a-2d-beam}

In section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed. In this article, the authors investigated the validity of a cantilever Timoshenko beam by comparing it to a cantilever two-dimensional beam. In this section, the article is extended and the validity of the cantilever two-dimensional model is investigated.

As mentioned in the introduction of the chapter, a beam is a three-dimensional body and therefore a three-dimensional model is more realistic. However the authors of \cite{LVV09} mention that a direct comparison of the one and three-dimensional models will have complexities and they suggest using the two-dimensional model as an intermediate step.

So in this section, the article \cite{LVV09} is extended and the validity of a cantilever two-dimensional beam model is investigated, using a cantilever three-dimensional model as a reference.

\subsection{The models}
The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in section \ref{ssec:2D_Model:ModelProblem}. From section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D.

Figure \ref{fig:2Dv3D} shows the two beams side-by-side.

\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{

			\centering
			\begin{minipage}[b]{0.7\linewidth}
				\begin{tikzpicture}
					\draw[line width = 0.3mm] (0,1) -- (7,1);
					\draw[line width = 0.3mm] (0,-1) -- (7,-1);
					\draw[line width = 0.3mm] (7,-1) -- (7,1);
					\draw[line width = 0.3mm] (0,-1) -- (0,1);

					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});

					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

					\draw[scale=0.5, domain=1:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=2:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
					\draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
					\draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

					\node at (7.2,0) {$h$};
					\node at (3.2,-1.2) {$\ell = 1$};
				\end{tikzpicture}
			\end{minipage}
			\begin{minipage}[b]{0.7\linewidth}
				\begin{tikzpicture}
					\draw[line width = 0.3mm] (-0.1,1) -- (6.9,1);
					\draw[line width = 0.3mm] (-0.1,-1) -- (6.9,-1);
					\draw[line width = 0.3mm] (6.9,-1) -- (6.9,1);
					\draw[line width = 0.3mm] (-0.1,-1) -- (-0.1,1);

					\draw[line width = 0.3mm] (0.1,1.1) -- (7.1,1.1);
					\draw[line width = 0.3mm] (7.1,-0.9) -- (7.1,1.1);

					\draw[line width = 0.3mm] (-0.1,1) -- (0.1,1.1);
					\draw[line width = 0.3mm] (6.9,1) -- (7.1,1.1);
					\draw[line width = 0.3mm] (6.9,-1) -- (7.1,-0.9);

					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});

					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

					\draw[scale=0.5, domain=0.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
					\draw[scale=0.5, domain=1.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
					\draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
					\draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
					\draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
					\draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
					\draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
					\draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

					\node at (6.95,1.25) {$b$};
					\node at (6.78,0) {$h$};
					\node at (3.2,-1.2) {$\ell = 1$};
				\end{tikzpicture}

			\end{minipage}
		}
    }
\end{figure}

\subsection{Calculating the eigenvalues}
In section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived. Similar to the two-dimensional case in \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the Finite Element Method is used to calculate the eigenvalues of the three-dimensional beam. The eigenvalue problem for both models have the same form, but different matrices.

\subsubsection{Problem 2DE and 3D-1E}
Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
\begin{eqnarray}
	K\bar{u} & = & M\lambda{\bar{u}},
\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in section \ref{ssec:2DFEM:DE} for the Problem 2DE and section \ref{3d_fem_g} for Problem 3DE.

\subsubsection{Accuracy of the eigenvalues of the three-dimensional model}
Figure \ref{fig:conv_3d_eig} show the rate of convergence of the first 20 eigenvalues of Problem 3DE.

\begin{figure}[H]
    \centering
        \includegraphics[scale=0.7]{files/Chapter6/convergence3d.png}

    \label{fig:conv_3d_eig}
\end{figure}

Similar to the two-dimensional case, the number of elements can be chosen so that at least the first 20 eigenvalues are accurate to 4 significant digits.

For the three-dimensional model, obtaining this level of accuracy can be difficult and computationally expensive. For the two-dimensional beam in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and the upcoming two-dimensional plate model in section \ref{sec:validity-of-a-plate} it is easier to get 5 significant digits of accuracy.

\subsection{Comparing the mode shapes}
To be able to compare the eigenvalues, the mode shapes of the two models are compared to match up the eigenvalues of the two models. This is the same approach as in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}.

As seen in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the two-dimensional model as eigenvalues and eigenvectors that are not related to beam type problems. This is also true for the three-dimensional model, and it has even more non-beam type eigenvalues.

The focus of the investigation remains on beam type problems. Below are some examples of the mode shapes for beam type eigenvalues, mode shapes for non-beam type eigenvalues that are shared between the two and three-dimensional models and also mode shapes for non-beam type eigenvalues that are only present in the three-dimensional model.

\subsubsection{Mode shapes relating to beam type eigenvalues.}
Figure \ref{fig:beam-2dv3d} show some examples of beam type mode shapes for the displacement $u$.

\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{files/Chapter6/3D12.png}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{files/Chapter6/2D3.png}
			\end{minipage}
	    }
    }
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{files/Chapter6/3D22.png}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{files/Chapter6/2D6.png}
			\end{minipage}
	    }
    }
\end{figure}

\subsubsection{Mode shapes relating to non-beam type eigenvalues that are present in the two-dimensional model.}
Figure \ref{fig:nonbeam-2dv3d} show examples of mode shapes relating to non-beam type eigenvalues for the displacement $u$.

\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{files/Chapter6/3D33.png}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{files/Chapter6/2D8.png}
			\end{minipage}
	    }
    }
\end{figure}

\subsubsection{Mode shapes relating to non-beam type eigenvalues that are not present in the two-dimensional model.}
Figure \ref{fig:nonbeam-2dv3d} show examples of mode shapes relating to non-beam type eigenvalues for the displacement $u$ which are not present in the two-dimensional model. These mode shapes only appear in the three-dimensional beam.

\begin{figure}[h!]
	\scalebox{.8}{
		\makebox[\textwidth][c]{
			\centering
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{files/Chapter6/3DNonBeam10.png}
			\end{minipage}
			\begin{minipage}[b]{0.8\linewidth}
				\includegraphics[width=1\linewidth]{files/Chapter6/3DNonBeam11.png}
			\end{minipage}
        }
    }
\end{figure}

\subsection{Comparing the eigenvalues}

For a realistic comparison of the models, the parameters need to be chosen carefully. The parameters are $h$ representing the height of the beam and $b$ representing the width of the beam. The two-dimensional model does not have the width parameter.

For $h$, the values used in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} will be used. These values covers a range of beam shapes from a short thick beam, to a long slender beam. two cases are selected that represents realistic cases. For a short and thick beam, consider $h = 1/5$ and for a long and slender beam, consider $h = 1/20$.

For the parameter $b$, two different cases will be considered. The first case is for $b \leq h$, and the $b > h$. The distinction of these two cases will become apparent in the results. It is important to note that the parameter $b$ will be expressed as a multiple of $h$.

All of the results will include all the eigenvalues shared between the two-models, including not beam type eigenvalues. The non-beam type eigenvalues will be highlighted in grey. The non-beam type eigenvalues that are not shared between the two models will be excluded from the results, but the numbering of the eigenvalues will be kept as if they were included.

\subsubsection*{Case $b \leq h$:}
Table \ref{tab:2v3_1} below compares the eigenvalues of the models for a beam with a small length to height ratio of $h=1/5$ with decreasing values of $b$.

\begin{table}[htbp]
	\scalebox{.8}{
	\makebox[\textwidth]{
		\begin{tabular}{|cc|cc|cc|cc||cc|}
			\hline
			\multicolumn{10}{|c|}{Eigenvalues} \\
			\hline
			\hline
			i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
			\hline
			{2} & 0.12307 & {2} & 0.12234 & {2} & 0.12198 & {3} & 0.12178 & 1     & 0.12151 \\
			{3} & 3.5773 & {5} & 3.5630 & {6} & 3.5558 & {8} & 3.5519 & 2     & 3.5460 \\
			\rowcolor{lightgray}{5} & 7.7799 & {6} & 7.7596 & {8} & 7.7471 & {11} & 7.7401 & 3     & 7.7311 \\
			{8} & 20.334 & {9} & 20.283 & {11} & 20.26 & {14} & 20.247 & 4     & 20.225 \\
			{10} & 56.247 & {12} & 56.173 & {15} & 56.156 & {22} & 56.142 & 5     & 56.109 \\
			\rowcolor{lightgray}{11} & 69.197 & {14} & 69.319 & {17} & 69.281 & {24} & 69.238 & 6     & 69.164 \\
			{14} & 114.03 & {16} & 114.01 & {20} & 114.05 & {29} & 114.06 & 7     & 114.03 \\
			\rowcolor{lightgray}{17} & 187.01 & {19} & 189.14 & {25} & 189.37 & {36} & 189.34 & 8     & 189.17 \\
			{18} & 192.21 & {20} & 192.41 & {26} & 192.58 & {37} & 192.63 & 9     & 192.61 \\
			{21} & 284.76 & {23} & 285.43 & {31} & 285.74 & {42} & 285.84 & 10    & 285.85 \\
			{23} & 327.57 & {26} & 328.24 & {35} & 328.37 & {46} & 328.40 & 11    & 328.40 \\
			\rowcolor{lightgray}{25} & 347.77 & {28} & 356.44 & {36} & 357.30 & {50} & 357.33 & 12    & 357.08 \\
			{27} & 393.69 & {30} & 396.84 & {38} & 397.28 & {53} & 397.37 & 13    & 397.33 \\
			{30} & 434.46 & {34} & 441.05 & {41} & 441.81 & {57} & 441.99 & 14    & 442.00 \\
			\rowcolor{lightgray}{31} & 523.65 & {36} & 534.04 & {43} & 534.17 & {63} & 534.03 & 15    & 533.71 \\
			{34} & 550.51 & {37} & 537.82 & {44} & 538.86 & {64} & 539.06 & 16    & 538.97 \\
			\rowcolor{lightgray}{37} & 590.86 & {41} & 587.43 & {48} & 594.17 & {65} & 595.58 & 17    & 596.06 \\
			{39} & 590.86 & {42} & 600.52 & {49} & 602.25 & {67} & 602.69 & 18    & 602.77 \\
			\rowcolor{lightgray}{42} & 646.21 & {44} & 657.22 & {50} & 658.04 & {71} & 658.06 & 19    & 657.87 \\
			{44} & 711.07 & {46} & 714.62 & {53} & 717.10 & {73} & 717.51 & 20    & 717.37 \\
			\hline
			\hline
			\multicolumn{2}{|c|}{Max RE: \  2.6069\%} &\multicolumn{2}{c|}{Max RE: \ 1.4469\%}  & \multicolumn{2}{c|}{Max RE: \  0.38192\%}  & \multicolumn{2}{c||}{Max RE: \ 0.22301\%}& \multicolumn{2}{c|}{-} \\
			\hline
		\end{tabular}
	    }
    }
\end{table}%

\label{sym:RE}

% Table generated by Excel2LaTeX from sheet 'Sheet2'
\begin{table}[htbp]
	\centering
	\begin{tabular}{|c|cccc|}
		\hline
		\multicolumn{5}{|c|}{Maximum Relative Error} \\
		\hline
		\hline
		& {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
		\hline
		Beam Type & 2.1420 \% & 0.6804 \% & 0.38192 \% & 0.22301 \% \\
		Non-Beam Type & 2.6069 \% & 1.4469 \% & 0.31546 \% & 0.11680 \% \\
		\hline
	\end{tabular}%
	\label{tab:2Dv3D_1_breakup}%
\end{table}%

Table \ref{tab:2v3_1} below compares the eigenvalues of the models for a beam with a larger length to height ratio of $h=1/20$ with decreasing values of $b$.

\begin{table}[ht]
	\scalebox{.8}{
	\makebox[\textwidth]{
	\begin{tabular}{|cc|cc|cc|cc||cc|}
		\hline
		\multicolumn{10}{|c|}{Eigenvalues} \\
		\hline
		\hline
		i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
		\hline
		{2} & 0.008043 & {2} & 0.008029 & {2} & 0.008023 & {3} & 0.00802 & {1} & {0.008013} \\
		{3} & 0.3087 & {4} & 0.30816 & {5} & 0.30794 & {7} & 0.30785 & {2} & {0.30757} \\
		{5} & 2.3357 & {8} & 2.3316 & {9} & 2.3300  & {12} & 2.3293 & {3} & {2.3273} \\
		\rowcolor{lightgray}{8} & 7.7217 & {10} & 7.7156 & {13} & 7.7124 & {16} & 7.7111 & {4} & {7.7077} \\
		{10} & 8.5387 & {11} & 8.5238 & {14} & 8.5182 & {18} & 8.516 & {5} & {8.5086} \\
		{11} & 21.986 & {14} & 21.948 & {18} & 21.934 & {24} & 21.929 & {6} & {21.911} \\
		{14} & 45.863 & {18} & 45.781 & {21} & 45.756 & {30} & 45.746 & {7} & {45.712} \\
		\rowcolor{lightgray}{17} & 69.444 & {19} & 69.408 & {25} & 69.385 & {33} & 69.374 & {8} & {69.344} \\
		{18} & 83.149 & {22} & 82.999 & {27} & 82.960 & {36} & 82.944 & {9} & {82.887} \\
		{21} & 136.44 & {25} & 136.19 & {31} & 136.14 & {42} & 136.12 & {10} & {136.03} \\
		\rowcolor{lightgray}{23} & 192.62 & {27} & 192.62 & {35} & 192.58 & {47} & 192.56 & {11} & {192.48} \\
		{25} & 207.87 & {29} & 207.5 & {36} & 207.43 & {48} & 207.41 & {12} & {207.29} \\
		{27} & 299.14 & {33} & 298.63 & {41} & 298.56 & {55} & 298.53 & {13} & {298.38} \\
		\rowcolor{lightgray}{30} & 376.68 & {35} & 377.01 & {44} & 377.01 & {58} & 376.98 & {14} & {376.83} \\
		{31} & 411.58 & {37} & 410.89 & {46} & 410.83 & {61} & 410.81 & {15} & {410.63} \\
		{34} & 546.15 & {40} & 545.27 & {50} & 545.24 & {66} & 545.23 & {16} & {545.03} \\
		\rowcolor{lightgray}{37} & 620.77 & {42} & 622.02 & {53} & 622.19 & {69} & 622.18 & {17} & {621.95} \\
		{39} & 703.55 & {44} & 702.49 & {54} & 702.29 & {71} & 702.53 & {18} & {702.31} \\
		{42} & 884.27 & {47} & 883.02 & {59} & 883.14 & {82} & 883.19 & {19} & {882.96} \\
		\rowcolor{lightgray}{44} & 923.68 & {49} & 926.88 & {60} & 927.43 & {86} & 927.50 & {20} & {927.18} \\
		\hline
		\hline
		\multicolumn{2}{|c|}{Max RE: \  0.37701\%} &\multicolumn{2}{c|}{Max RE: \ 0.19893\%}  & \multicolumn{2}{c|}{Max RE: \  0.12393\%}  & \multicolumn{2}{c||}{Max RE: \ 0.092843\%}& \multicolumn{2}{c|}{-} \\
		\hline
	\end{tabular}%
	\label{tab:2v3_2}%
    }
}
\end{table}%

\begin{table}[htbp]
	\centering

	\begin{tabular}{|c|cccc|}
		\hline
		\multicolumn{5}{|c|}{Maximum Relative Error} \\
		\hline
		\hline
		& {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
		\hline
		Beam Type & 0.37701 \% & 0.19893 \% & 0.12393 \% & 0.092843 \% \\
		Non-Beam Type & 0.37682 \% & 0.10218 \% & 0.061213 \% & 0.043601 \% \\
		\hline
	\end{tabular}%
	\label{tab:2v3_2_split}%
\end{table}%

Tables \ref{tab:2v3_1} and \ref{tab:2v3_2} show that the first 20 eigenvalues two-dimensional model compares very well to the matching eigenvalues three-dimensional beam for $b<=h$. As the width $b$ decreases, the two-dimensional model becomes a better approximation of the three-dimensional model. Also shown is that the slender beam with $h = 1/20$ compares better than the thick beam where $h = 1/5$, event though the case of $h=1/5$ is still a very good comparison.

The tables also shows that the three-dimensional model has more non-beam type eigenvalues as the width $b$ decreases, as well as when the width $h$ decreases.This is different from the two-dimensional model as seen in \ref{sec:validity-of-a-cantilever-timoshenko-beam}.

Tables \ref{tab:2Dv3D_1_breakup} and \ref{tab:2v3_2_split} breaks up the maximum relative error for the beam type and non-beam type eigenvalues. These tables confirm that the the beam type eigenvalues compare very well.

\subsubsection*{Case $b > h$:}
First, the case is considered where $h = 1/5$.

\begin{table}[htbp]
	\scalebox{.8}{
	\makebox[\textwidth]{
		\begin{tabular}{|cc|cc|cc||cc|}
			\hline
			\multicolumn{8}{|c|}{Eigenvalues} \\
			\hline
			\hline
			i     & {b = 2h} & i     & {b = 4h} & i     & {b = 8h} & j     & 2D \\
			\hline
			{1} & 0.12474 					& {1} & 0.12766 & {1} & 0.13036 & 1     & 0.12151 \\
			{4} & 3.6088 					& {4} & 3.6297 & {5} & 3.7766 & 2     & 3.5460 \\
			\rowcolor{lightgray}{6} & 7.8091 & {5} & 7.8389 & {9} & 8.9239 & 3     & 7.7311 \\
			{8} & 20.466 					& {9} & 20.959 & {15} & 21.031 & 4     & 20.255 \\
			{11} & 56.309					& {18} & 58.149 & {30} & 60.862 & 5     & 56.109 \\
			\hline
			\hline
			\multicolumn{2}{|c|}{Max RE: \  2.6603\%} &\multicolumn{2}{c|}{Max RE: \ 5.0571\%}  & \multicolumn{2}{c|}{Max RE: \  15.428\%} & \multicolumn{2}{c|}{-} \\
			\hline
		\end{tabular}%
		\label{tab:b>h}%
	    }
    }
\end{table}

\begin{table}[htbp]
	\centering

	\begin{tabular}{|c|ccc|}
		\hline
		\multicolumn{4}{|c|}{Maximum Relative Error} \\
		\hline
		\hline
		& {b = 2h} & {b = 4h} & {b = 8h} \\
		\hline
		Beam Type & 2.6603 \% & 5.0571 \% & 8.4712 \% \\
		Non-Beam Type & 1.0096 \% & 1.3948 \% & 15.428 \% \\
		\hline
	\end{tabular}%
	\label{tab:b>h-split}%
\end{table}%

In Table \ref{tab:b>h}, the height of the beam is set to $h=1/20$, which was the best case when $b<h$.

\begin{table}[htbp]
	\scalebox{.8}{
	\makebox[\textwidth]{
		\begin{tabular}{|cc|cc|cc||cc|}
			\hline
			\multicolumn{8}{|c|}{Eigenvalues} \\
			\hline
			\hline
			i     & {b = 2h} & i     & {b = 4h} & i     & {b = 8h} & j     & 2D \\
			\hline
			{2} & 0.008076 & {1} & 0.008162 & {1} & 0.008324 & 1     & 0.008013 \\
			{3} & 0.30995 & {3} & 0.31298 & {3} & 0.31738 & 2     & 0.30757 \\
			{5} & 2.3462 & {5} & 2.3737 & {6} & 2.4116 & 3     & 2.3273 \\
			\rowcolor{lightgray}{8} & 7.7312 & {8} & 7.7471 & {9} & 7.7711 & 4     & 7.7077 \\
			{10} & 8.5841 & {9} & 8.7082 & {10} & 8.7929 & 5     & 8.5086 \\
			{11} & 22.124 & {12} & 22.491 & {14} & 23.222 & 6     & 21.911 \\
			{14} & 46.195 & {14} & 47.003 & {18} & 47.921 & 7     & 45.712 \\
			\rowcolor{lightgray}{17} & 69.454 & {17} & 69.281 & {22} & 72.307 & 8     & 69.344 \\
			{18} & 83.822 & {18} & 85.218 & {24} & 80.607 & 9     & 82.887 \\
			{21} & 137.43 & {21} & 138.58 & {32} & 140.97 & 10    & 136.03 \\
			\hline
			\hline
			\multicolumn{2}{|c|}{Max RE: \  1.1289\%} &\multicolumn{2}{c|}{Max RE: \ 2.8261\%}  & \multicolumn{2}{c|}{Max RE: \  5.9821\%} & \multicolumn{2}{c|}{-} \\
			\hline
		\end{tabular}%
	    }
    }
\end{table}

\begin{table}[htbp]
	\centering

	\begin{tabular}{|c|ccc|}
		\hline
		\multicolumn{4}{|c|}{Maximum Relative Error} \\
		\hline
		\hline
		& {b = 2h} & {b = 4h} & {b = 8h} \\
		\hline
		Beam Type & 1.1289 \% & 2.8261 \% & 5.9821 \% \\
		Non-Beam Type & 0.30521 \% & 0.51096 \% & 4.2734 \% \\
		\hline
	\end{tabular}%
	\label{tab:b>h-split_20}%
\end{table}%

Tables \ref{tab:b>h} and \ref{tab:b>h_20} show that the two-dimensional model compares less well to the three-dimensional model when $b$ is too much larger than $h$. Tables \ref{tab:b>h-split} and \ref{tab:b>h-split_20} show that this is also true for the beam type eigenvalues.

For the case of $h=1/5$, it was also more difficult to obtain reliable eigenvalues using a numerical method.

These results gives a detailed overview of the validity of the cantilever two-dimensional beam compared to the cantilever three-dimensional beam. The results show that the two-dimensional beam model compares very well to the three-dimensional beam model for a large range of beam shapes. The results shown were chosen to represent realistic cases, and the results are similar for other cases.

The overall conclusion is that the shape of the beam is very important. If the width $b$ is equal to or less than the height $h$, the two-dimensional beam model compares very well to the three-dimensional beam model. More so when the beam is slender, and less so when the beam is short and thick.

When the width $b$ is larger than the height $h$, the two-dimensional beam the comparison degrades very quickly. This is true for both slender and short and thick beams, although with short and thick beams, it is more difficult to obtain reliable eigenvalues using a numerical method.

For practical applications, if $b > h$ the use of a beam model must be brought into question. Other models such as a plate model will be better suited as it is a more realistic model. In the next section, the validity of the Reissner-Mindlin plate mode is investigated using the same method of this section.

\section{Conclusion}
his chapter is an extension of the work of Section 4.5. In Section 4.5, the validity of the Timoshenko beam theory is investigated by comparing a Timoshenko beam model to a two-dimensional beam model.

In real-world applications, a beam is a three-dimensional model. Therefore it should be more realistic to use a three-dimensional model to investigate the validity of the Timoshenko beam theory. This is mentioned by the authors of \cite{LVV09}. Their suggestion is to use the two-dimensional model as an intermediate step, to avoid complexities. Therefore the validity of the two-dimensional model is investigated, using a three-dimensional beam model as a reference. Again the results so that the comparison relies on the shape of the beams. The two-dimensional model compares well to the three-dimensional beam if the beam is not wide.

If the width of the beam is very large, the use of a beam model can be questioned. A plate model might be more suited. Therefore the last section of this chapter investigates the validity of the Reissner-Mindlin plate model. The Reissner-Mindlin plate model is compared to a three-dimensional plate model. The results show that the Reissner-Mindlin plate model compares well to the three-dimensional plate model.

The same method is used in this chapter as in Section 4.5. The mode shapes are sketched and matched. The corresponding eigenvalues can then be matched up and compared. The eigenvalues relating to the Reissner-Mindlin plate model are referred to as plate-type eigenvalues.

\section{Contributions}

There are four models used in this dissertation. For each of the models, the dimensionless variational form is derived. Also presented are the model problems that are used in this dissertation.

The first result investigates the existence and uniqueness of solutions for general vibration problems. The article that is discussed proves this result for a general vibration problem, using four assumptions. To explain the theory, an example is presented using one of the model problems of the dissertation. The cantilever Timoshenko beam model is chosen for the simple boundary conditions, as well as it's recurring importance in this dissertation. The weak variational form of the model is derived as well as the function spaces defined. This is presented in the same format as the general vibration problem. In fact all the models in this dissertation are special cases of this general vibration problem. The theory is then applied to this example problem, as a demonstration. To apply the theory, the four assumptions are proven to be true.

The next result looks at modal analysis. Before the general case is discussed, again the cantilever Timoshenko beam is used to illustrated the concept of modal analysis.A trial solution to the boundary value problem is suggested. This trial solution is substituted into the partial differential equation and two problems are obtained. The first problem is the eigenvalue problem and the second is an ordinary differential equation. The eigenvalue problem can be solved with theory discussed later in the dissertation and the ordinary differential equation can then be solved. Substation of these two results into the boundary value problem confirms that the trial solution is correct. The same idea is then discussed for the general case.

We then look at the convergence of the Galerkin Approximation for our general vibration problem. The results of the article discussed are updated with improved notation using a different article. The general case of the Galerkin approximation use a lot of symbols that are not immediately obvious, so again the cantilever Timoshenko beam model problem is used and the Galerkin Approximation is derived in an attempt to explain some of the conventions. The results of the article are then discussed and presented. The results are presented in a concise and practical format to reduce the need to define any unnecessary symbols or notation. The results are also presented in four theorems, summarizing the results of the article that are important but that are not necessarily presented as a theorem in the article.

The next result is on the convergence of the eigenvalues and eigenfunctions of a general vibration problem when using the Finite Element Method. The results are from a textbook. The results are presented with updated notation, coinciding with the notation used in the dissertation. The results are also expanded and extra results are added in an attempt to better explain the theory.

We then look at an important result for the Timoshenko beam theory. This provides a method to calculate the exact eigenvalues and eigenfunctions for the Timoshenko beam theory. Two examples are then used, a cantilever beam and a free-free beam, as an example of the application of the theory. The eigenvalues are calculated and the corresponding mode shapes are plotted. To obtain these results, the equation of motion is plotted, the isolation intervals are determined and the eigenvalues are then calculated using interval division to a desired level of accuracy. The mode shapes can then also be plotted with back substitution. These examples are important preparation for the main comparisons of this dissertation. We also discuss a result comparing the Timoshenko beam theory to results from an empirical study. We add to this article by giving the model problems.

For the rest of the models in this dissertation, the two- and three-dimensional elastic bodies, and the Reissner-Mindlin plate model, a different approach is required to solve the eigenvalue problems. For these models we use the Finite Element Method. For each of the models, their reference configurations are given. All of the models are assumed to have a square cross-section and in a cantilever configuration. This reference configuration is then discretised into a grid of rectangular shaped elements. A set of admissable piecewise Hermite cubic functions are then used and each model is rewritten into a Galerkin Approximation. We the define the standard Finite Element Method Matrices for each case. These are referred to as the mass and stiffness matrices in engineering. Finally our boundary value problems are written into a system of ordinary differential equations in a matrix representation. At this point is it easy to derive the eigenvalue problem for each of the problems in this matrix form. This is in preparation for the main comparisons made in this dissertation.

For our main comparisons, we first look at an article comparing a cantilever Timoshenko beam model to a cantilever two-dimensional model. We discuss the article and replicate the results. The eigenvalues and eigenfunctions of the Timoshenko beam model is obtained using the exact method already described. The eigenvalues and the eigenfunctions for the two-dimensional model are approximated using the Finite Element Method matrix representation of the eigenvalue problem. A MATLAB program is written to approximate the eigenvalues and plot the mode shapes. The accuracy of this approximation is also investigated by looking at the rate of convergence for different grid sizes. Following the article, the eigenvalues are matched up by first comparing the mode shapes of the two models. The eigenvalues can then be matched up and also any eigenvalues not relating to beam-type problems can be filtered out. Based on the results in modal analysis, only a few eigenvalues need to be considered. The relative error between the eigenvalues are then calculated for different shapes of beams. The results improve on the article by showing more significant digits and also including some more results.

We then extend the results of the article to investigate the validity of a cantilever two-dimensional beam model as well as a cantilever Reissner-Mindlin plate model. The same method of the article is followed. To investigate the validity of a cantilever two-dimensional model, a cantilever three-dimensional model is considered. Since both of the models are not beam models, careful consideration needs to be taken to identify the eigenvalues. The same approach is used by comparing the mode shapes. For interest, the non-beam type eigenvalues shared between the two models are also included and the rest that the three-dimensional model does not share with the two-dimensional model are omitted. A clear distinction is made to show the beam type eigenvalues and the beam type results. The shape of the models are also carefully chosen to represent a variety of realistic cases that are interesting. The results show that the shape of the models play an important role in how well the models compare. An interesting result shows that this comparison is not good when the beam gets too wide. We therefore suggest a different model, like a plate model. This lead to the introduction of the Reissner-Mindlin plate model into this dissertation. The validity of a cantilever Reissner-Mindlin plate model is investigated using the same method. The cantilever three-dimensional plate model is again used as the reference model with the restriction that the body is wide.

\section*{References}

\end{document}

### 2024-03-13 article.tex
Draft article template fix

@@
-\documentclass[preprint,11pt]{elsarticle}
-
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{draftwatermark}
-\usepackage{tabularx} % Required for tables that stretch to text width
-\usepackage{booktabs} % For prettier tables
-\usepackage{ltablex}
-\usepackage{xcolor,cancel,bm,tikz}
-\usepackage{hyperref}
-\usepackage{mathtools}
-\usepackage{amsmath,amssymb,amsthm,amsfonts}
-\usepackage{enumitem}
-\usepackage{kantlipsum,graphicx}
-\usepackage{multicol,colortbl,multirow}
-\usepackage{pgfplots,booktabs,xfrac,floatrow}
-\usepackage{color}
-
-\usepackage{setspace}
-\setstretch{0.7} % Adjust this value as needed
-
-\setlength{\parindent}{0pt}
-
-\usepackage{geometry}
-\geometry{
-  left=1in,
-  right=1in,
-  top=1in,
-  bottom=1in,
-}
-
-\SetWatermarkText{DRAFT}
-\SetWatermarkScale{1}
-
-\journal{Mathematical and Computer Modelling}
+% \documentclass[11pt]{elsarticle}
+\input{preamble_article.tex}
+% \usepackage{geometry}
+% \geometry{
+%   left=1in,
+%   right=1in,
+%   top=1in,
+%   bottom=1in,
+% }
 
@@
 \author{Rudi du Toit}
-\address{University of Pretoria, Pretoria, South Africa}
+\address{Department of Mathematics, University of Pretoria, Pretoria, South Africa}
+
+\journal{Applied Mathematics and Computation}
 
 \begin{abstract}
-Your abstract here.
+Beams are wildly used in engineering.
+The the real world, beams are complex three-dimensional objects.
+But often, simplified models are used to study the vibration of beams.
+These simplified models are less complex and computationally less expensive.
+But the validity of these simplified models is not always clear.
+In this article, the validity of a two-dimensional model for a cantilever beam is investigated.
+The two-dimensional model is compared to a three-dimensional model.
 \end{abstract}
@@
 \begin{keyword}
-Vibration \sep Cantilever \sep Beam \sep Three-Dimensional \sep Two-Dimensional
+	Beam \sep Cantilever \sep Two-Dimensional Model \sep Three-Dimensional Model \sep Vibration Problems
 \end{keyword}
@@
 \section{Introduction}
-Your introduction here.
+In the article \cite{LVV09}, the authors investigate the validity of a Timoshenko beam using a two-dimensional model as a reference.
+The two-dimensional model is a simplified model of the Timoshenko beam.
+The authors use the Finite Element Method (FEM) to solve the eigenvalue problem for the two models.
+The results are then compared to determine the validity of the two-dimensional model.
+
+In this article, \cite{LVV09} is extended and the validity of a two-dimensional model is investigated, using a three-dimensional model as a reference.
+Similar to \cite{LVV09}, the investigation focusses on beam-type problems.
+
+The models are presented in a dimensionless variational form.
+It is also explained how the two-dimensional model is derived from the three-dimensional model, as a special case of plane stress.
+The existence and uniqueness of solutions for the two models are briefly discussed.
+
+The concept of modal analysis is then introduced using a general vibration problem.
+From modal analysis, the formal series solution for the vibration problem is obtained.
+This formal series solution is a linear combination of the eigenvectors and eigenvalues of the problem.
+This enables us to compare the solutions of the two models, by only considering a comparison of the eigenvectors and eigenvalues.
+
+Using the Finite Element Method (FEM), a formula for the models are obtained to numerically solve the eigenvalue problem for the two models.
+The eigenvalues are matched up by comparing the mode shapes, and the eigenvalues are then compared.
 
 \section{Models}
-
 \subsection{Three-dimensional model}
@@
 \subsubsection*{Constitutive Equation}
-For an isotropic material, Hooke's law can be written in terms of Young's modulus $E$ and Poisson's ratio $\nu$ as follows.\\
+For an isotropic material, Hooke's law can be written in terms of Young's modulus $E$ and Poisson's ratio $\nu$ as follows.
 
@@
 
-If the principal stresses $\sigma_i$ are all non-zero, then Hooke's law can be written in an alternative form.\\
+If the principal stresses $\sigma_i$ are all non-zero, then Hooke's law can be written in an alternative form.
 
@@
 \end{eqnarray}
-With $\textrm{Tr}(\mathcal{E}) = \epsilon_{11} + \epsilon_{12} + \epsilon_{13}$ is the trace of the strain operator $\mathcal{E}$.\\
+With $\textrm{Tr}(\mathcal{E}) = \epsilon_{11} + \epsilon_{12} + \epsilon_{13}$ is the trace of the strain operator $\mathcal{E}$.
 
@@
 Suppose $\ell$ represents some notable dimension (e.g.the length) of the elastic body 
-and $G$ the shear modulus of elasticity.\\
+and $G$ the shear modulus of elasticity.
 
@@
 
-\textbf{Remark} Some of the constants are introduced to simplify the equations and also allow for comparisons to other models such as the Timoshenko beam model.
+\textbf{Remark} The constants introduced are the same as those in \cite{LVV09}.
+They simplify the equations and allow for comparisons to other models such as the Timoshenko beam model, although that is not covered in this article.
 
@@
 
-\subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
+\subsection{Model problems}\label{ssec:3D_Model}
 Divide the boundary of $\Omega$ into two distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be considered a model problem for a three-dimensional elastic body. 
@@
 \eqref{eq:3D_Model:EM-D} to \eqref{eq:3D_Model:CE-D} and the following boundary
-conditions:\\
+conditions:
 
@@
 \end{eqnarray}
-with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.\\
+with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.
 
@@
 \end{align}
-for all $\phi \in T(\Omega)$\\
+for all $\phi \in T(\Omega)$
 
@@
 	\end{eqnarray}
-\end{minipage}\\
+\end{minipage}
 
@@
 
-\subsection{Two-dimensional model}
-Using \cite{Sadd05} as a guide, a special case of general plane stress is considered.
+\subsection{Two-dimensional model} \label{ssec:2D_Model}
+For the two-dimensional modek, a special case of general plane stress is considered.
 
@@
 \eqref{plane_stress_neseccary_condition} falls away and Hooke’s law can be written in a 
-two-dimensional form using the stress components (1.2.16) as 
+two-dimensional form using the stress components as 
 \[ T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E})I.\]
 
-\subsection{Equations of motion and constitutive equations}\label{ssec:2D_Model:EquationsOfMotion+ConstitutiveEquations}
+\subsection*{Equations of motion and constitutive equations}\label{ssec:2D_Model:EquationsOfMotion+ConstitutiveEquations}
  The following equations of motion and constitutive equations follow from subsections \ref{ssec:3D_Model:DimensionlessForm} and 1.3.2.
@@
 \end{eqnarray}
-\subsubsection{Constitutive equation}\label{sssec:2D_Model:ConstitutiveEquation}
+\subsubsection*{Constitutive equation}\label{sssec:2D_Model:ConstitutiveEquation}
 \begin{eqnarray}
@@
 
-\subsubsection{Problem 2D}\label{sssec:2D_Model:Problem2D1}
-Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:\\
-
-Boundary Conditions:\\
+\subsubsection*{Problem 2D}\label{sssec:2D_Model:Problem2D1}
+Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:
+
+Boundary Conditions:
 \begin{eqnarray*}
@@
 \end{eqnarray}
-with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.\\
+with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.
 Also define the integral
@@
 \end{align}
-for all $\phi \in T(\Omega)$.\\
+for all $\phi \in T(\Omega)$.
 
 \section{Existance and uniqueness of solutions}
-The models in this article concern the vibration of elastic bodies. These type of models
-have a similar variational form as the wave equation and are called second order hyperbolic
-type problems. The articles \cite{VV02} and \cite{VS19} provide existence and uniqueness
-results for these type of problems. In \cite{VV02}, it is assumed that $b$ is symmetric. 
-\cite{VS19} extends the results of \cite{VV02} to the case where $b$ is not symmetric. For
-the models in the article, \cite{VV02} is a sufficient reference.\\
+Our two models, the three-dimensional modela and the two-dimensional model, concern the vibration of elastic bodies.
+These type of models have a similar variational form as the wave equation and are called second order hyperbolic type problems.
+The articles \cite{VV02} and \cite{VS18} provide existence and uniqueness results for these type of problems.
+In \cite{VV02}, it is assumed that $b$ is symmetric.
+\cite{VS18} extends the results of \cite{VV02} to the case where $b$ is not symmetric.
+For the models in the article, \cite{VV02} is a sufficient reference.
 
@@
 authors of \cite{VV02} to prove existence and uniqueness results. The models in this article are 
-special cases of this general problem.\\
+special cases of this general problem.
 
@@
 \end{eqnarray}
-while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\\
+while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.
 
@@
 useful in the comparison of linear models. The following section is a short discussion of 
-the basic concepts of modal analysis and how it enables the comparison of linear models.\\
+the basic concepts of modal analysis and how it enables the comparison of linear models.
 
@@
 \end{eqnarray}
-with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.\\
+with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.
 
@@
 The existence of such a $\lambda$ is uncertain at this point.
-So we consider the following eigenvalue problem.\\
+So we consider the following eigenvalue problem.
 
@@
 Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$?
-To answer this question, we again refer to the article \cite{CVV18}.\\
+To answer this question, we again refer to the article \cite{CVV18}.
 
@@
 
-Therefore $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$. For the case of weak damping, it can be proved that $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ which is the case of \cite{CVV18}.\\
+Therefore $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$. For the case of weak damping, it can be proved that $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ which is the case of \cite{CVV18}.
 
@@
 \end{eqnarray*}
-but $T_n$ is not uniquely defined by the differential equation.\\
-
-Substitution shows that these partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions for \eqref{eq:existence:ProblemGVarHom} in Problem GVar.\\
+but $T_n$ is not uniquely defined by the differential equation.
+
+Substitution shows that these partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions for \eqref{eq:existence:ProblemGVarHom} in Problem GVar.
 
 The authors then define an error function $u^E_N = u - u^N$.
-Since both $u$ and $u^N$ satisfies \eqref{eq:existence:ProblemGVarHom}, so does this error function with the following the initial conditions, $u^E_N(0) = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.\\
+Since both $u$ and $u^N$ satisfies \eqref{eq:existence:ProblemGVarHom}, so does this error function with the following the initial conditions, $u^E_N(0) = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.
 
@@
 
-Then $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$.
-Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$ by \eqref{eq:inequality}.\\
+Then $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$. Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$ by \eqref{eq:inequality}.
 
@@
 The solution of the model problems can be expressed as a series solution of the eigenvalues and eigenvectors of the models.
-Therefore the models can be compared by comparing the eigenvalues and eigenvectors of the models.\\
+Therefore the models can be compared by comparing the eigenvalues and eigenvectors of the models.
 
@@
 
-\section{Finite element method}
-
-\subsection{Three-dimensional model}
+\section{Finite Element Method}
+In the section, the Finite Element Method (FEM) is applied to the models to obtain an eigenvalue problem that can be solved numerically.
+
+\subsection{Two-dimensional model}\label{ssec:2D_Model:FEM}
+Consider a cantilever two-dimensional elastic body, with a rectangular cross-section.
+
+\subsubsection{Reference configuration for rectangular cross-section}\label{sssec:2D_Model:RefConf}
+Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$.
+Denote the elastic body by $\Omega \in R^2$, with $(0,0)$ as the point of reference.
+For a rectangular cross-section, the body $\Omega$ can be described as,
+\begin{eqnarray*}
+	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
+\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines (or edges) as follows: \label{sym:En}
+
+\noindent\begin{minipage}{.5\linewidth}
+	\begin{eqnarray*}
+		\Sigma:& \quad x_1 &= 0\\
+		\Gamma_3:& \quad x_1 &= 1
+	\end{eqnarray*}
+\end{minipage}%
+\begin{minipage}{.5\linewidth}
+	\begin{eqnarray*}
+		\Gamma_1:& \quad x_2 &= -{h}/{2}\\
+		\Gamma_2:& \quad x_2 &= {h}/{2}
+	\end{eqnarray*}
+\end{minipage}
+
+In this configuration, the body is clamped rigidly to the surface at $x_1 = 0$ denoted as $\Sigma$ and the body is free-hanging on the other boundaries denoted by $\Gamma$.
+
+\subsubsection{Cantilever elastic body}
+Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D in section \ref{ssec:2D_Model}.
+
+\FloatBarrier
+
+\begin{figure}[h!]
+	\centering
+	\begin{tikzpicture}
+
+		\draw[line width = 0.4mm] (0,0.5) -- (7,0.5);
+		\draw[line width = 0.4mm] (0,-0.5) -- (7,-0.5);
+		\draw[line width = 0.4mm] (7,-0.5) -- (7,0.5);
+		\draw[line width = 0.4mm] (0,-0.5) -- (0,0.5);
+
+		\draw[line width = 0.1mm] (0,1.5) -- (0,-1.5);
+
+		\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.3);
+		\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.1);
+		\draw[line width = 0.1mm] (0,1.1) -- (-0.2,0.9);
+		\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.7);
+		\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.5);
+		\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.3);
+		\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.1);
+		\draw[line width = 0.1mm] (0,0.1) -- (-0.2,-0.1);
+		\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.3);
+		\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.5);
+		\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.7);
+		\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.9);
+		\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1.1);
+		\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.3);
+		\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.5);
+
+		\node at (7.3,0) {$h$};
+		\draw[-stealth] (7.3,0.2) -- (7.3,0.5);
+		\draw (7.2,0.5) -- (7.4,0.5);
+		\draw[-stealth] (7.3,-0.2) -- (7.3,-0.5);
+		\draw (7.2,-0.5) -- (7.4,-0.5);
+
+		\node at (3.5,-0.8) {$1$};
+		\draw[stealth-] (0,-0.8) -- (3.3,-0.8);
+		\draw[stealth-] (7,-0.8) -- (3.7,-0.8);
+		\draw (7,-0.9) -- (7,-0.7);
+
+		\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
+		\draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
+		\node at (9.7,0.8) {$e_1$};
+		\node at (8.8,1.5) {$e_2$};
+
+		\node at (-0.6,0) {$(0,0)$};
+		\node at (0,0)[circle,fill,inner sep=1.5pt]{};
+
+		% Add Σ at x_1 = 0
+		\node at (-1.4,0) {$\Sigma$};
+
+		% Add Γ₁ at x_2 = -h/2
+		\node at (3.5,-1.2) {$\Gamma_1$};
+
+		% Add Γ₂ at x_2 = h/2
+		\node at (3.5,0.9) {$\Gamma_2$};
+
+		% Add Γ₃ at x_1 = 1
+		\node at (8,0) {$\Gamma_3$};
+
+	\end{tikzpicture}
+\end{figure}
+
+\FloatBarrier
+
+The variational problem for the two dimensional cantilever model is also derived in \ref{ssec:2D_Model} and refered to as Problem 2DV.
+Using the reference configuration, the variational problem can be rewritten into a model specific form.
+
+\subsubsection{Problem 2DV}\label{sssec:2D_Model:Problem2D1VChp5}
+Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
+\begin{align}
+	c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{eq:2D_Model:Problem2D1VEqChp5}
+\end{align}
+for all $\phi \in T(\Omega)$. With the test function space 
+\begin{eqnarray*}
+	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
+\end{eqnarray*}
+
+The bilinear forms and integral function is defined by
+\begin{eqnarray}
+	b(u,\phi) & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
+	\textrm{Tr}(\Phi) ~dA, \label{eq:2D_Model:BilinearChp5}\\
+	c(\partial_t^2 u,\phi) & = & \int_\Omega~ (\partial^2_t u) \cdot \phi~dA, \label{eq:2D_Model:Bilinear_cChp5}\\
+	(f,g) &=& \int_{\Omega} f\cdot g \ dA, \label{eq:2D_Model:Bilinear_intChp5}
+\end{eqnarray}
+with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.
+
+Using the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten into a model specific form.
+
+\subsubsection{Constitutive equations:}
+\begin{eqnarray}
+	\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_1 u_1 + \nu \partial_2 u_2) \label{CE1} \\
+	\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_2 u_2 + \nu \partial_1 u_1) \label{CE2} \\
+	\sigma_{12} & = & \frac{1}{2\gamma(1+\nu)}(\partial_1 u_2 + \partial_2 u_1) \label{CE3}
+\end{eqnarray}
+
+\subsubsection{Bilinear form:}
+\begin{align}
+	b(u,\phi) & = & \frac{1}{\gamma(1-\nu^2)}\int_{\Omega} (\partial_1 u_1 \partial_1 \phi_1 + \partial_2 u_2 \partial _2 \phi_2 + \nu\partial_1 u_1 \partial_2\phi_2 + \nu \partial_2 u_2 \partial_1 \phi_1 ) \ dA \nonumber\\
+	& + & \frac{1}{2\gamma(1+\nu)}\int_{\Omega} (\partial_1 u_2 \partial_1 \phi_2 + \partial_1 u_2 \partial_2 \phi_1 + \partial_2 u_1 \partial_1\phi_2 + \partial_2 u_1 \partial_2\phi_1) \ dA.
+\end{align}
+
+\subsection{Weak variational form}
+Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)$.
+Denote $X = L^2(0,1)\times L^2(0,1)$.
+The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.
+
+\subsubsection{Problem 2DWV}
+Find a function $u$ such that $\forall \ t > 0$, $u \in V$ with $\partial_t^2 u \in W$ and
+\begin{eqnarray*}
+	c(u,v) + b(u,v) & = & (Q,v)
+\end{eqnarray*}
+for all $v\in V$.
+
+\subsection{Galerkin approximation}\label{2d_FEM_G}
+To be able to apply the Finite Element Method to Problem 2DV, the body $\Omega$ needs to be discretised.
+This is done by dividing the body $\Omega$ into discrete shapes, called elements.
+There are various types of shapes of elements that can be used.
+Since the body $\omega$ is has a rectangular cross-section, rectangular elements are the simplest elements to use.
+
+Divide the reference configuration $\Omega$ into a grid of rectangular elements, such that there are $n = n_1\times n_2$ nodes.
+
+Define a set of $n$-dimensional linear independent basis functions.
+For the two dimensional model, the basis functions can be defined by the set $$B = \left\{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \right\}.$$
+
+These functions are chosen as piecewise Hermite bi-cubic functions $\phi_i$.
+Simpler bi-linear functions can also be used, however the use of the bi-cubic basis functions results in faster convergence and also the benefit of obtaining the derivatives of the solution at the expense of more complexity.
+
+The subset of basis functions $B$ that satisfies all the conditions of the test function space $T(\Omega)$ are called the admissible basis functions.
+Denote the admissible basis functions by $\delta_j$, where each $\delta_j$ is a unique element of $B$.
+The admissible basis functions can be numbered and expressed as the set $A = \left \{\delta_1, \delta_2,..., \delta_k \right\}$ for some $k \leq 2n$.\\
+
+Define the space
+\begin{eqnarray*}
+S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right).
+\end{eqnarray*}
+
+For each function $u^h \in S^h$, $u^h$ can be expressed as
+\begin{eqnarray*}
+	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x).
+\end{eqnarray*}
+
+Substitution of $u^h$ into Problem 2DV, results in the following Galerkin Approximation, denoted by Problem 2DG.
+
+\subsubsection{Problem 2DG}
+Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
+\begin{eqnarray*}
+	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I, \phi_i)
+\end{eqnarray*} for $i = 1,2,...,k$.
+$Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$.
+i.e.
+$Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.
+
+\subsection{System of differential equations}\label{ssec:2DFEM:DE}
+
+Consider the following standard Finite Element Method matrices
+\subsubsection{FEM matrices}
+\noindent\begin{minipage}{.5\linewidth}
+	\begin{eqnarray*}
+		\mathbf{M}_{j,i} & = & \int_{\Omega} \phi_i \phi_j ~dA \\
+		\mathbf{{K}_{11}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_1\phi_j~dA\\
+		\mathbf{{K}_{22}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_2\phi_j~dA
+	\end{eqnarray*}
+\end{minipage}%
+\begin{minipage}{.5\linewidth}
+	\begin{eqnarray*}
+		\mathbf{{K}_{12}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_1\phi_j~dA\\
+		\mathbf{{K}_{21}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_2\phi_j~dA
+	\end{eqnarray*}
+\end{minipage}
+for $i,j = 1,2,...,k$.
+
+And 
+\begin{eqnarray*}
+	{M_{F}}_{j,i} = \int_{\Omega}  \phi_i \phi_j~dA
+\end{eqnarray*}
+
+for $i = 1,2,...,k$ and for $j =1,2,...,2n$.
+
+Define the following matrices:
+\begin{eqnarray*}
+	K_1 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{11}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{22}} \label{eq:2DFEM:K1} \\
+	K_2 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{21}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{12}}\label{eq:2DFEM:K2}\\
+	K_3 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{12}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{21}}\label{eq:2DFEM:K3}\\
+	K_4 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{22}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{11}}\label{eq:2DFEM:K4}
+\end{eqnarray*}
+
+Using the standard FEM matrices and matrices $K_1$-$K_4$, the following concatenated matrices are defined.
+\begin{eqnarray}
+	\begin{aligned}
+		K = 
+		\begin{bmatrix}
+			K1 & K2\\
+			K3 & K4
+		\end{bmatrix}
+	\end{aligned}
+	\ \ \ \ \ \ \ \ \
+	\begin{aligned}
+		M_f = 
+		\begin{bmatrix}
+			M_{F} & O_{F}\\
+			O_{F} & M_{F}
+		\end{bmatrix}
+	\end{aligned}\label{eq:2DFEM:K+M}
+\end{eqnarray}
+
+\begin{eqnarray}
+	M = 
+	\begin{bmatrix}
+		\mathbf{M} & O \\
+		O & \mathbf{M}
+	\end{bmatrix}\label{eq:2DFEM:M}
+\end{eqnarray}
+
+The matrices ${O}$ and ${O_f}$ are the zero matrices of the same size as $\mathbf{M}$ and ${M_f}$ respectively.
+
+Using \eqref{eq:2DFEM:K+M} and \eqref{eq:2DFEM:M}, Problem 2DG is rewritten as a system of ordinary differential equations. This system is referred to as Problem 2DODE.
+
+\subsubsection{Problem 2DODE}
+Find a function $\bar{u} \in S^h$ such that
+\begin{eqnarray}
+	M\ddot{\bar{u}} & = & K\bar{u} + M_{f}Q^I.
+\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \langle u, \partial_1 u, \partial_2 u, \partial_{12} u \rangle$.
+
+\textbf{Remark} This form of $\bar{u}$ is determined by the use of the bi-cubic basis functions.
+
+\subsection{Eigenvalue problem}\label{2dFEM_EP}
+For the eigenvalue problem, assume that there is no external force, $M_{f}Q^I = 0$, so that 
+\begin{eqnarray}
+		M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
+\end{eqnarray}
+It is known that a system of ordinary differential equations has a general solution of the form $e^{rt}$.
+Suppose that $\bar{w} = e^{\lambda t} \bar{u}$ is a solution for \eqref{eq:2DFEM:M2}.
+In this solution, $\lambda$ is an eigenvalue and $\bar{u}$ a corresponding eigenfunction.
+Substitution into \eqref{eq:2DFEM:M2} results in
+\begin{eqnarray*}
+	M\lambda e^{\lambda t}\bar{u} & = & Ke^{\lambda t}\bar{u}.
+\end{eqnarray*}
+Since $e^{\lambda t} > 0$ for all values of $\lambda t$, we can cancel it from both sides of the equation and formulate the eigenvalue problem Problem 2DE.
+
+\subsubsection{Problem 2DE}
+Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
+\begin{eqnarray}
+	M\lambda{\bar{u}} & = & K\bar{u}.
+\end{eqnarray}
+
+\subsection{Three-dimensional model} \label{ssec:3D_Model:FEM}
 Consider a cantilever three-dimensional elastic body, with a rectangular cross-section.
@@
 	\Omega = \left\{ x \in R^3 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} , \ -\frac{b}{2} \leq x_3 \leq \frac{b}{2}\right \}
-\end{eqnarray*} \label{sym:width}
+\end{eqnarray*}
 Let $\partial \Omega$ denote the boundary of the body. Divide $\partial \Omega$ into the six distinct flat surfaces as follows:
@@
 
-Using this notation, the boundary conditions are similar to the two-dimensional model in section \ref{sssec:2D_Model:RefConf}, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.
+Using this notation, the boundary conditions are similar to the two-dimensional model, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.
 
@@
 Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma$ and free-hanging at all the other sides.
-This is Problem 3D in section \ref{ssec:3D_Model:ModelProblems}.
+This is Problem 3D in section \ref{ssec:3D_Model}.
 
@@
 
-In section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3DV.
+In section \ref{ssec:3D_Model}, the variational problem for the three-dimensional cantilever model is defined by Problem 3DV.
 This general form can now be rewritten as in a model specific form using the reference configuration.
-For convenience, some of the results from section \ref{sec:3D_Model} are repeated here.
 
@@
 \subsection{Galerkin approximation}
-As mentioned in the previous section, section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised.
 For this is three-dimensional body, three-dimensional elements shapes are required.
@@
 For the this three-dimensional model, piecewise Hermite tri-cubic basis functions are used.
-Although this is more complex than using piecwise tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
+Although this is more complex than using piecwise tri-linear basis functions, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
 
@@
 
-Consider a cantilever two-dimensional elastic body, with a rectangular cross-section.
-
-\subsubsection{Reference configuration for rectangular cross-section}\label{sssec:2D_Model:RefConf}
-Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$.
-Denote the elastic body by $\Omega \in R^2$, with $(0,0)$ as the point of reference.
-For a rectangular cross-section, the body $\Omega$ can be described as,
-\begin{eqnarray*}
-	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
-\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines (or edges) as follows: \label{sym:En}
-
-\noindent\begin{minipage}{.5\linewidth}
-	\begin{eqnarray*}
-		\Sigma:& \quad x_1 &= 0\\
-		\Gamma_3:& \quad x_1 &= 1
-	\end{eqnarray*}
-\end{minipage}%
-\begin{minipage}{.5\linewidth}
-	\begin{eqnarray*}
-		\Gamma_1:& \quad x_2 &= -{h}/{2}\\
-		\Gamma_2:& \quad x_2 &= {h}/{2}
-	\end{eqnarray*}
-\end{minipage}
-
-In this configuration, the body is clamped rigidly to the surface at $x_1 = 0$ denoted as $\Sigma$ and the body is free-hanging on the other boundaries denoted by $\Gamma$.
-
-\subsubsection{Cantilever elastic body}
-Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D in section \ref{ssec:2D_Model:ModelProblem}.
-
-\begin{figure}[h!]
-	\centering
-	\begin{tikzpicture}
-
-		\draw[line width = 0.4mm] (0,0.5) -- (7,0.5);
-		\draw[line width = 0.4mm] (0,-0.5) -- (7,-0.5);
-		\draw[line width = 0.4mm] (7,-0.5) -- (7,0.5);
-		\draw[line width = 0.4mm] (0,-0.5) -- (0,0.5);
-
-		\draw[line width = 0.1mm] (0,1.5) -- (0,-1.5);
-
-		\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.3);
-		\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.1);
-		\draw[line width = 0.1mm] (0,1.1) -- (-0.2,0.9);
-		\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.7);
-		\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.5);
-		\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.3);
-		\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.1);
-		\draw[line width = 0.1mm] (0,0.1) -- (-0.2,-0.1);
-		\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.3);
-		\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.5);
-		\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.7);
-		\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.9);
-		\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1.1);
-		\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.3);
-		\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.5);
-
-		\node at (7.3,0) {$h$};
-		\draw[-stealth] (7.3,0.2) -- (7.3,0.5);
-		\draw (7.2,0.5) -- (7.4,0.5);
-		\draw[-stealth] (7.3,-0.2) -- (7.3,-0.5);
-		\draw (7.2,-0.5) -- (7.4,-0.5);
-
-		\node at (3.5,-0.8) {$1$};
-		\draw[stealth-] (0,-0.8) -- (3.3,-0.8);
-		\draw[stealth-] (7,-0.8) -- (3.7,-0.8);
-		\draw (7,-0.9) -- (7,-0.7);
-
-		\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
-		\draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
-		\node at (9.7,0.8) {$e_1$};
-		\node at (8.8,1.5) {$e_2$};
-
-		\node at (-0.6,0) {$(0,0)$};
-		\node at (0,0)[circle,fill,inner sep=1.5pt]{};
-
-		% Add Σ at x_1 = 0
-		\node at (-1.4,0) {$\Sigma$};
-
-		% Add Γ₁ at x_2 = -h/2
-		\node at (3.5,-1.2) {$\Gamma_1$};
-
-		% Add Γ₂ at x_2 = h/2
-		\node at (3.5,0.9) {$\Gamma_2$};
-
-		% Add Γ₃ at x_1 = 1
-		\node at (8,0) {$\Gamma_3$};
-
-	\end{tikzpicture}
-\end{figure}
-
-In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2DV.
-Some of the results from section \ref{sec:2D_Model} are repeated here for convenience.
-Using the reference configuration, these results are rewritten from a general form to a model specific form.
-
-\subsubsection{Problem 2DV}\label{sssec:2D_Model:Problem2D1VChp5}
-Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
-\begin{align}
-	c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{eq:2D_Model:Problem2D1VEqChp5}
-\end{align}
-for all $\phi \in T(\Omega)$. With the test function space 
-\begin{eqnarray*}
-	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
-\end{eqnarray*}
-
-The bilinear forms and integral function is defined by
-\begin{eqnarray}
-	b(u,\phi) & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
-	\textrm{Tr}(\Phi) ~dA, \label{eq:2D_Model:BilinearChp5}\\
-	c(\partial_t^2 u,\phi) & = & \int_\Omega~ (\partial^2_t u) \cdot \phi~dA, \label{eq:2D_Model:Bilinear_cChp5}\\
-	(f,g) &=& \int_{\Omega} f\cdot g \ dA, \label{eq:2D_Model:Bilinear_intChp5}
-\end{eqnarray}
-with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.
-
-Using the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten into a model specific form.
-
-\subsubsection{Constitutive equations:}
-\begin{eqnarray}
-	\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_1 u_1 + \nu \partial_2 u_2) \label{CE1} \\
-	\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_2 u_2 + \nu \partial_1 u_1) \label{CE2} \\
-	\sigma_{12} & = & \frac{1}{2\gamma(1+\nu)}(\partial_1 u_2 + \partial_2 u_1) \label{CE3}
-\end{eqnarray}
-
-\subsubsection{Bilinear form:}
-\begin{align}
-	b(u,\phi) & = & \frac{1}{\gamma(1-\nu^2)}\int_{\Omega} (\partial_1 u_1 \partial_1 \phi_1 + \partial_2 u_2 \partial _2 \phi_2 + \nu\partial_1 u_1 \partial_2\phi_2 + \nu \partial_2 u_2 \partial_1 \phi_1 ) \ dA \nonumber\\
-	& + & \frac{1}{2\gamma(1+\nu)}\int_{\Omega} (\partial_1 u_2 \partial_1 \phi_2 + \partial_1 u_2 \partial_2 \phi_1 + \partial_2 u_1 \partial_1\phi_2 + \partial_2 u_1 \partial_2\phi_1) \ dA.
-\end{align}
-
-\subsection{Weak variational form}
-Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)$.
-Denote $X = L^2(0,1)\times L^2(0,1)$.
-The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.
-
-\subsubsection{Problem 2DWV}
-Find a function $u$ such that $\forall \ t > 0$, $u \in V$ with $\partial_t^2 u \in W$ and
-\begin{eqnarray*}
-	c(u,v) + b(u,v) & = & (Q,v)
-\end{eqnarray*}
-for all $v\in V$.
-
-\subsection{Galerkin approximation}\label{2d_FEM_G}
-To be able to apply the Finite Element Method to Problem 2DV, the body $\Omega$ needs to be discretised.
-This is done by dividing the body $\Omega$ into discrete shapes, called elements.
-There are various types of shapes of elements that can be used.
-Since the body $\omega$ is has a rectangular cross-section, rectangular elements are the simplest elements to use.
-
-Divide the reference configuration $\Omega$ into a grid of rectangular elements, such that there are $n = n_1\times n_2$ nodes.
-
-Define a set of $n$-dimensional linear independent basis functions.
-For the two dimensional model, the basis functions can be defined by the set $$B = \left\{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \right\}.$$
-
-These functions are chosen as piecewise Hermite bi-cubic functions $\phi_i$.
-Simpler bi-linear functions can also be used, however the use of the bi-cubic basis functions results in faster convergence and also the benefit of obtaining the derivatives of the solution at the expense of more complexity.
-
-The subset of basis functions $B$ that satisfies all the conditions of the test function space $T(\Omega)$ are called the admissible basis functions.
-Denote the admissible basis functions by $\delta_j$, where each $\delta_j$ is a unique element of $B$.
-The admissible basis functions can be numbered and expressed as the set $A = \left \{\delta_1, \delta_2,..., \delta_k \right\}$ for some $k \leq 2n$.\\
-
-Define the space
-\begin{eqnarray*}
-S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right).
-\end{eqnarray*}
-
-For each function $u^h \in S^h$, $u^h$ can be expressed as
-\begin{eqnarray*}
-	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x).
-\end{eqnarray*}
-
-Substitution of $u^h$ into Problem 2DV, results in the following Galerkin Approximation, denoted by Problem 2DG.
-
-\subsubsection{Problem 2DG}
-Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
-\begin{eqnarray*}
-	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I, \phi_i)
-\end{eqnarray*} for $i = 1,2,...,k$.
-$Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$.
-i.e.
-$Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.
-
-\subsection{System of differential equations}\label{ssec:2DFEM:DE}
-
-Consider the following standard Finite Element Method matrices
-\subsubsection{FEM matrices}
-\noindent\begin{minipage}{.5\linewidth}
-	\begin{eqnarray*}
-		\mathbf{M}_{j,i} & = & \int_{\Omega} \phi_i \phi_j ~dA \\
-		\mathbf{{K}_{11}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_1\phi_j~dA\\
-		\mathbf{{K}_{22}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_2\phi_j~dA
-	\end{eqnarray*}
-\end{minipage}%
-\begin{minipage}{.5\linewidth}
-	\begin{eqnarray*}
-		\mathbf{{K}_{12}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_1\phi_j~dA\\
-		\mathbf{{K}_{21}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_2\phi_j~dA
-	\end{eqnarray*}
-\end{minipage}
-for $i,j = 1,2,...,k$.
-
-And 
-\begin{eqnarray*}
-	{M_{F}}_{j,i} = \int_{\Omega}  \phi_i \phi_j~dA
-\end{eqnarray*}
-
-for $i = 1,2,...,k$ and for $j =1,2,...,2n$.
-
-Define the following matrices:
-\begin{eqnarray*}
-	K_1 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{11}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{22}} \label{eq:2DFEM:K1} \\
-	K_2 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{21}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{12}}\label{eq:2DFEM:K2}\\
-	K_3 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{12}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{21}}\label{eq:2DFEM:K3}\\
-	K_4 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{22}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{11}}\label{eq:2DFEM:K4}
-\end{eqnarray*}
-
-Using the standard FEM matrices and matrices $K_1$-$K_4$, the following concatenated matrices are defined.
-\begin{eqnarray}
-	\begin{aligned}
-		K = 
-		\begin{bmatrix}
-			K1 & K2\\
-			K3 & K4
-		\end{bmatrix}
-	\end{aligned}
-	\ \ \ \ \ \ \ \ \
-	\begin{aligned}
-		M_f = 
-		\begin{bmatrix}
-			M_{F} & O_{F}\\
-			O_{F} & M_{F}
-		\end{bmatrix}
-	\end{aligned}\label{eq:2DFEM:K+M}
-\end{eqnarray}
-
-\begin{eqnarray}
-	M = 
-	\begin{bmatrix}
-		\mathbf{M} & O \\
-		O & \mathbf{M}
-	\end{bmatrix}\label{eq:2DFEM:M}
-\end{eqnarray}
-
-The matrices ${O}$ and ${O_f}$ are the zero matrices of the same size as $\mathbf{M}$ and ${M_f}$ respectively.
-
-Using \eqref{eq:2DFEM:K+M} and \eqref{eq:2DFEM:M}, Problem 2DG is rewritten as a system of ordinary differential equations. This system is referred to as Problem 2DODE.
-
-\subsubsection{Problem 2DODE}
-Find a function $\bar{u} \in S^h$ such that
-\begin{eqnarray}
-	M\ddot{\bar{u}} & = & K\bar{u} + M_{f}Q^I.
-\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \langle u, \partial_1 u, \partial_2 u, \partial_{12} u \rangle$.
-
-\textbf{Remark} This form of $\bar{u}$ is determined by the use of the bi-cubic basis functions.
-
-\subsection{Eigenvalue problem}\label{2dFEM_EP}
-For the eigenvalue problem, assume that there is no external force, $M_{f}Q^I = 0$, so that 
-\begin{eqnarray}
-		M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
-\end{eqnarray}
-It is known that a system of ordinary differential equations has a general solution of the form $e^{rt}$.
-Suppose that $\bar{w} = e^{\lambda t} \bar{u}$ is a solution for \eqref{eq:2DFEM:M2}.
-In this solution, $\lambda$ is an eigenvalue and $\bar{u}$ a corresponding eigenfunction.
-Substitution into \eqref{eq:2DFEM:M2} results in
-\begin{eqnarray*}
-	M\lambda e^{\lambda t}\bar{u} & = & Ke^{\lambda t}\bar{u}.
-\end{eqnarray*}
-Since $e^{\lambda t} > 0$ for all values of $\lambda t$, we can cancel it from both sides of the equation and formulate the eigenvalue problem Problem 2DE.
-
-\subsubsection{Problem 2DE}
-Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
-\begin{eqnarray}
-	M\lambda{\bar{u}} & = & K\bar{u}.
-\end{eqnarray}
-
-\section{Results}
+Now Problem 2DE and Problem 3DE can be solved using a computer program. Iterative methods, sparse matrices as well as parallel computing can be used to efficiently solve these problems.
 
 \section{Validity of a model for a cantilever two-dimensional beam} \label{sec:validity-of-a-2d-beam}
-
-In section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed.
-In this article, the authors investigated the validity of a cantilever Timoshenko beam by comparing it to a cantilever two-dimensional beam.
-In this section, the article is extended and the validity of the cantilever two-dimensional model is investigated.
-
 As mentioned in the introduction of the chapter, a beam is a three-dimensional body and therefore a three-dimensional model is more realistic.
@@
 \subsection{The models}
-The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in section \ref{ssec:2D_Model:ModelProblem}.
-From section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D.
-
-Figure \ref{fig:2Dv3D} shows the two beams side-by-side.
-
+Figure \ref{fig:2Dv3D} shows the two beams, Problem 2D and Problem 3D side-by-side.
+
+\FloatBarrier
 \begin{figure}[h!]
@@
 		\makebox[\textwidth][c]{
-
+			\caption{Side-by-side comparison of the beams.}
+			\label{fig:2Dv3D}
 			\centering
@@
 				\end{tikzpicture}
+				\subcaption{Two-Dimensional Elastic Body}
 			\end{minipage}
@@
 					\node at (3.2,-1.2) {$\ell = 1$};
+
 				\end{tikzpicture}
+				\subcaption{Three-Dimensional Elastic Body}
 
@@
 \end{figure}
+\FloatBarrier
 
 \subsection{Calculating the eigenvalues}
-In section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived.
-Similar to the two-dimensional case in \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the Finite Element Method is used to calculate the eigenvalues of the three-dimensional beam.
-The eigenvalue problem for both models have the same form, but different matrices.
-
-\subsubsection{Problem 2DE and 3D-1E}
+In section \ref{ssec:2D_Model:FEM} and \ref{ssec:3D_Model:FEM}, the Finite Element Method for the two-dimensional beam and three-dimensional beam is derived.
+Using this method, the eigenvalue problems can be solved to obtain the eigenvalues and eigenvectors of the two models.
+
+\subsubsection{Problem 2DE and 3DE}
 Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
@@
 
-\subsubsection{Accuracy of the eigenvalues of the three-dimensional model}
-Figure \ref{fig:conv_3d_eig} show the rate of convergence of the first 20 eigenvalues of Problem 3DE.
+\subsubsection{Accuracy of the eigenvalues}
+When solving the eigenvalue problems with a numerical method, the accuracy of the eigenvalues can be established by investigating the rate of convergence.
 
@@
     \centering
+    \begin{adjustbox}{center}
+        \includegraphics[scale=0.7]{files/Chapter4/Convergence.png}
+    \end{adjustbox}
+    \caption{Rate of convergence of the first 20 eigenvalues for Problem 2DE.}
+    \label{fig:conv_2d_eig}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \begin{adjustbox}{center}
         \includegraphics[scale=0.7]{files/Chapter6/convergence3d.png}
-
+    \end{adjustbox}
+    \caption{Rate of convergence of the first 20 eigenvalues for Problem 3DE.}
     \label{fig:conv_3d_eig}
@@
 
-Similar to the two-dimensional case, the number of elements can be chosen so that at least the first 20 eigenvalues are accurate to 4 significant digits.
-
-For the three-dimensional model, obtaining this level of accuracy can be difficult and computationally expensive.
-For the two-dimensional beam in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and the upcoming two-dimensional plate model in section \ref{sec:validity-of-a-plate} it is easier to get 5 significant digits of accuracy.
+Figure \ref{fig:conv_2d_eig} and \ref{fig:conv_3d_eig} shows the rate of convergence of the first 20 eigenvalues of the two-dimensional beam and the three-dimensional beam respectively.
+Each color represents a spesific eigenvalue.
+
+These figures show that the two-dimensional model has a much faster rate of convergence than the three-dimensional model.
+The two-dimensional model also converge faster to a higher accuracy than the three-dimensional model.
+
+Using this, the number of elements can be chosen so that at least the first 10 eigenvalues are accurate to 5 significant digits for the two-dimensional model.
+For the three-dimensional model, obtaining this level of accuracy can be difficult and computationally expensive, but it is possible to get 4 significant digits of accuracy for the first 10 eigenvalues.
 
 \subsection{Comparing the mode shapes}
-To be able to compare the eigenvalues, the mode shapes of the two models are compared to match up the eigenvalues of the two models.
-This is the same approach as in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}.
-
-As seen in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the two-dimensional model as eigenvalues and eigenvectors that are not related to beam type problems.
-This is also true for the three-dimensional model, and it has even more non-beam type eigenvalues.
-
-The focus of the investigation remains on beam type problems.
+To be able to compare the eigenvalues, the mode shapes of the two models are compared to match up the eigenvalues of the two models. This is the same approach as in the article \cite{LVV09}.
+
+When calculating the mode shapes, distinct patterns are observed.
+There are mode shapes that are present in both models, mode shapes that are only present in the three-dimensional model.
+The shared mode shapes also include mode shapes that relate to beam problems.
+These are the mode shapes that are of interest the article \cite{LVV09}.
+
+The focus of the investigation of this article is also on beam type problems.
 Below are some examples of the mode shapes for beam type eigenvalues, mode shapes for non-beam type eigenvalues that are shared between the two and three-dimensional models and also mode shapes for non-beam type eigenvalues that are only present in the three-dimensional model.
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/3D12.png}
+				\subcaption{3D Beam Type - $\lambda_{12} = 2.3293$}
+				\label{fig:minipage2}
 			\end{minipage}
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/2D3.png}
+				\subcaption{2D Beam Type - $\lambda_3 = 2.3273$}
+				\label{fig:minipage1}
 			\end{minipage}
-	    }
-    }
+	}}
 	\scalebox{.8}{
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/3D22.png}
+				\subcaption{3D Beam Type - $\lambda_{24} = 21.929$}
+				\label{fig:minipage2}
 			\end{minipage}
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/2D6.png}
+				\subcaption{2D Beam Type - $\lambda_6 = 21.911$}
+				\label{fig:minipage1}
 			\end{minipage}
-	    }
-    }
+			\caption{Mode shapes of the displacement $u$ with $h=1/20$.}
+			\label{fig:beam-2dv3d}
+	}}
 \end{figure}
+\FloatBarrier
 
@@
 
+\FloatBarrier
 \begin{figure}[h!]
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/3D33.png}
+				\subcaption{3D Non-Beam Type - $\lambda_{33} = 69.374$}
+				\label{fig:minipage2}
 			\end{minipage}
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/2D8.png}
+				\subcaption{2D Non-Beam Type - $\lambda_8 = 69.344$}
+				\label{fig:minipage1}
 			\end{minipage}
-	    }
-    }
+			\caption{Mode shapes of the displacement $u$ with $h=1/20$.}
+			\label{fig:nonbeam-2dv3d}
+	}}
 \end{figure}
+\FloatBarrier
 
@@
 These mode shapes only appear in the three-dimensional beam.
-
+\FloatBarrier
 \begin{figure}[h!]
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/3DNonBeam10.png}
+				\subcaption{Non-2D Type - $\lambda_{10}$}
+				\label{fig:minipage2}
 			\end{minipage}
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/3DNonBeam11.png}
+				\subcaption{Non-2D Type - $\lambda_{11}$}
+				\label{fig:minipage11}
 			\end{minipage}
-        }
-    }
+			\caption{Mode shapes of the displacement $u$ with $h=1/20$.}
+
+	}}
 \end{figure}
+\FloatBarrier
 
 \subsection{Comparing the eigenvalues}
-
 For a realistic comparison of the models, the parameters need to be chosen carefully.
@@
 
-For $h$, the values used in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} will be used.
-These values covers a range of beam shapes from a short thick beam, to a long slender beam.
+For $h$, values are chosen that covers a range of beam shapes from a short thick beam, to a long slender beam.
 two cases are selected that represents realistic cases.
@@
 	\makebox[\textwidth]{
+		\caption{Comparsion of Eigenvalues with $h = 1/5$, with decreasing $b$ and $b < h$.}
 		\begin{tabular}{|cc|cc|cc|cc||cc|}
@@
 			\hline
-		\end{tabular}
-	    }
-    }
+		\end{tabular}%
+		\label{tab:2v3_1}%
+	}}
 \end{table}%
-
+\FloatBarrier
 \label{sym:RE}
@@
 	\centering
+	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/5$.}
 	\begin{tabular}{|c|cccc|}
@@
 	\makebox[\textwidth]{
+	\caption{Comparsion of Eigenvalues with $h = 1/20$, with decreasing $b$ and $b < h$.}
 	\begin{tabular}{|cc|cc|cc|cc||cc|}
@@
 	\label{tab:2v3_2}%
-    }
-}
+}}
 \end{table}%
+\FloatBarrier
 
@@
 	\centering
-
+	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$}
 	\begin{tabular}{|c|cccc|}
@@
 \end{table}%
+\FloatBarrier
 
@@
 
-The tables also shows that the three-dimensional model has more non-beam type eigenvalues as the width $b$ decreases, as well as when the width $h$ decreases.This is different from the two-dimensional model as seen in \ref{sec:validity-of-a-cantilever-timoshenko-beam}.
+The tables also shows that the three-dimensional model has more non-beam type eigenvalues as the width $b$ decreases, as well as when the width $h$ decreases.
 
@@
 
+\FloatBarrier
 \begin{table}[htbp]
@@
 	\makebox[\textwidth]{
+		\caption{Comparsion of Eigenvalues with $h = 1/5$, with increasing $b$ and $b > h$}
 		\begin{tabular}{|cc|cc|cc||cc|}
@@
 		\label{tab:b>h}%
-	    }
-    }
+	}}
 \end{table}
-
+\FloatBarrier
+
+\FloatBarrier
 \begin{table}[htbp]
 	\centering
-
+	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/5$}
 	\begin{tabular}{|c|ccc|}
@@
 	\makebox[\textwidth]{
+		\caption{Comparsion of Eigenvalues with $h = 1/20$, with increasing $b$ and $b > h$}
 		\begin{tabular}{|cc|cc|cc||cc|}
@@
 		\end{tabular}%
-	    }
-    }
+		\label{tab:b>h_20}%
+	}}
 \end{table}
-
+\FloatBarrier
+
+\FloatBarrier
 \begin{table}[htbp]
 	\centering
-
+	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$}
 	\begin{tabular}{|c|ccc|}
@@
 \section{Conclusion}
-his chapter is an extension of the work of Section 4.5. In Section 4.5, the validity of the Timoshenko beam theory is investigated by comparing a Timoshenko beam model to a two-dimensional beam model.
-
-In real-world applications, a beam is a three-dimensional model.
-Therefore it should be more realistic to use a three-dimensional model to investigate the validity of the Timoshenko beam theory.
-This is mentioned by the authors of \cite{LVV09}.
-Their suggestion is to use the two-dimensional model as an intermediate step, to avoid complexities.
-Therefore the validity of the two-dimensional model is investigated, using a three-dimensional beam model as a reference.
-Again the results so that the comparison relies on the shape of the beams.
-The two-dimensional model compares well to the three-dimensional beam if the beam is not wide.
-
-If the width of the beam is very large, the use of a beam model can be questioned.
-A plate model might be more suited.
-Therefore the last section of this chapter investigates the validity of the Reissner-Mindlin plate model.
-The Reissner-Mindlin plate model is compared to a three-dimensional plate model.
-The results show that the Reissner-Mindlin plate model compares well to the three-dimensional plate model.
-
-The same method is used in this chapter as in Section 4.5.
-The mode shapes are sketched and matched.
-The corresponding eigenvalues can then be matched up and compared.
-The eigenvalues relating to the Reissner-Mindlin plate model are referred to as plate-type eigenvalues.
-
-\section{Contributions}
-
-There are four models used in this dissertation. For each of the models, the dimensionless variational form is derived. Also presented are the model problems that are used in this dissertation.
-
-The first result investigates the existence and uniqueness of solutions for general vibration problems.
-The article that is discussed proves this result for a general vibration problem, using four assumptions.
-To explain the theory, an example is presented using one of the model problems of the dissertation.
-The cantilever Timoshenko beam model is chosen for the simple boundary conditions, as well as it's recurring importance in this dissertation.
-The weak variational form of the model is derived as well as the function spaces defined.
-This is presented in the same format as the general vibration problem.
-In fact all the models in this dissertation are special cases of this general vibration problem.
-The theory is then applied to this example problem, as a demonstration.
-To apply the theory, the four assumptions are proven to be true.
-
-The next result looks at modal analysis.
-Before the general case is discussed, again the cantilever Timoshenko beam is used to illustrated the concept of modal analysis.A trial solution to the boundary value problem is suggested.
-This trial solution is substituted into the partial differential equation and two problems are obtained.
-The first problem is the eigenvalue problem and the second is an ordinary differential equation.
-The eigenvalue problem can be solved with theory discussed later in the dissertation and the ordinary differential equation can then be solved.
-Substation of these two results into the boundary value problem confirms that the trial solution is correct.
-The same idea is then discussed for the general case.
-
-We then look at the convergence of the Galerkin Approximation for our general vibration problem.
-The results of the article discussed are updated with improved notation using a different article.
-The general case of the Galerkin approximation use a lot of symbols that are not immediately obvious, so again the cantilever Timoshenko beam model problem is used and the Galerkin Approximation is derived in an attempt to explain some of the conventions.
-The results of the article are then discussed and presented.
-The results are presented in a concise and practical format to reduce the need to define any unnecessary symbols or notation.
-The results are also presented in four theorems, summarizing the results of the article that are important but that are not necessarily presented as a theorem in the article.
-
-The next result is on the convergence of the eigenvalues and eigenfunctions of a general vibration problem when using the Finite Element Method.
-The results are from a textbook.
-The results are presented with updated notation, coinciding with the notation used in the dissertation.
-The results are also expanded and extra results are added in an attempt to better explain the theory.
-
-We then look at an important result for the Timoshenko beam theory.
-This provides a method to calculate the exact eigenvalues and eigenfunctions for the Timoshenko beam theory.
-Two examples are then used, a cantilever beam and a free-free beam, as an example of the application of the theory.
-The eigenvalues are calculated and the corresponding mode shapes are plotted.
-To obtain these results, the equation of motion is plotted, the isolation intervals are determined and the eigenvalues are then calculated using interval division to a desired level of accuracy.
-The mode shapes can then also be plotted with back substitution.
-These examples are important preparation for the main comparisons of this dissertation.
-We also discuss a result comparing the Timoshenko beam theory to results from an empirical study.
-We add to this article by giving the model problems.
-
-For the rest of the models in this dissertation, the two- and three-dimensional elastic bodies, and the Reissner-Mindlin plate model, a different approach is required to solve the eigenvalue problems.
-For these models we use the Finite Element Method.
-For each of the models, their reference configurations are given.
-All of the models are assumed to have a square cross-section and in a cantilever configuration.
-This reference configuration is then discretised into a grid of rectangular shaped elements.
-A set of admissable piecewise Hermite cubic functions are then used and each model is rewritten into a Galerkin Approximation.
-We the define the standard Finite Element Method Matrices for each case.
-These are referred to as the mass and stiffness matrices in engineering.
-Finally our boundary value problems are written into a system of ordinary differential equations in a matrix representation.
-At this point is it easy to derive the eigenvalue problem for each of the problems in this matrix form.
-This is in preparation for the main comparisons made in this dissertation.
-
-For our main comparisons, we first look at an article comparing a cantilever Timoshenko beam model to a cantilever two-dimensional model.
-We discuss the article and replicate the results.
-The eigenvalues and eigenfunctions of the Timoshenko beam model is obtained using the exact method already described.
-The eigenvalues and the eigenfunctions for the two-dimensional model are approximated using the Finite Element Method matrix representation of the eigenvalue problem.
-A MATLAB program is written to approximate the eigenvalues and plot the mode shapes.
-The accuracy of this approximation is also investigated by looking at the rate of convergence for different grid sizes.
-Following the article, the eigenvalues are matched up by first comparing the mode shapes of the two models.
-The eigenvalues can then be matched up and also any eigenvalues not relating to beam-type problems can be filtered out.
-Based on the results in modal analysis, only a few eigenvalues need to be considered.
-The relative error between the eigenvalues are then calculated for different shapes of beams.
-The results improve on the article by showing more significant digits and also including some more results.
-
-We then extend the results of the article to investigate the validity of a cantilever two-dimensional beam model as well as a cantilever Reissner-Mindlin plate model.
-The same method of the article is followed.
-To investigate the validity of a cantilever two-dimensional model, a cantilever three-dimensional model is considered.
-Since both of the models are not beam models, careful consideration needs to be taken to identify the eigenvalues.
-The same approach is used by comparing the mode shapes.
-For interest, the non-beam type eigenvalues shared between the two models are also included and the rest that the three-dimensional model does not share with the two-dimensional model are omitted.
-A clear distinction is made to show the beam type eigenvalues and the beam type results.
-The shape of the models are also carefully chosen to represent a variety of realistic cases that are interesting.
-The results show that the shape of the models play an important role in how well the models compare.
-An interesting result shows that this comparison is not good when the beam gets too wide.
-We therefore suggest a different model, like a plate model.
-This lead to the introduction of the Reissner-Mindlin plate model into this dissertation.
-The validity of a cantilever Reissner-Mindlin plate model is investigated using the same method.
-The cantilever three-dimensional plate model is again used as the reference model with the restriction that the body is wide.
-
-\section*{References}
+In this article, the validity of a two-dimensional cantilever beam model is investigated by comparing it to a three-dimensional cantilever beam model.
+The two models are compared by using the Finite Element Method to obtain the eigenvalues and eigenvectors of the models.
+The eigenvalues are then matched up by considering the mode shapes, and a comparison is made.
+
+The models are presented in a dimensionless variational form. It is also shown how the two-dimensional model can be derived from the three-dimensional model as a special case of plane stress.
+
+The well posedness of the models are not discussed in detail, but the neseccary articles are referenced.
+The idea of modal analysis is explained by a general example.
+Modal analysis is crucial to the comparison of the models, and the application of the comparison of the models is shown in the numerical results of this article.
+
+For both models, the Finite Element Method is applied and a numerical formula is obtained for the eigenvalue problems.
+Using a computer program, the eigenvalues and eigenvectors are obtained for both models.
+
+For the comparison, the eigenvalues are matched up by comparing the mode shapes.
+The results of this article shows that the two-dimensional beam model compares very well to the three-dimensional beam model different shapes of beams.
+The shape of the beam however is crucial to how well the comparison is.
+The two-dimensional model compares best when the three-dimensional beam is thin and long, and less well when the three-dimensional beam is short and thick.
+The two-dimensional model does not compare well to the three-dimensional model when the width $b$ is larger than the height $h$.
+However a better suited model for this case might be a plate model.
+
+\bibliographystyle{elsarticle-harv}
+\bibliography{references}
 

### 2024-03-16 article.tex
fix

@@
 
-\title{Validity of a model for a cantilever two-dimensional beam}
-
-\author{Rudi du Toit}
+\title{Comparison of linear beam theories}
+
+\author{Rudi du Toit\corref{cor1}}
+\ead{u15000258@tuks.co.za}
+\cortext[cor1]{Corresponding author}
+\author{Prof N.F.J. van Rensburg}
 \address{Department of Mathematics, University of Pretoria, Pretoria, South Africa}
@@
 \begin{abstract}
-Beams are wildly used in engineering.
-The the real world, beams are complex three-dimensional objects.
-But often, simplified models are used to study the vibration of beams.
-These simplified models are less complex and computationally less expensive.
-But the validity of these simplified models is not always clear.
-In this article, the validity of a two-dimensional model for a cantilever beam is investigated.
-The two-dimensional model is compared to a three-dimensional model.
+Beams, while commonly used in engineering, are complex three-dimensional objects.
+Simplified models are often used in vibration problems due to their reduced complexity and computational demand.
+However, the accuracy of these models in practical applications is not always certain.
+This article extends previous research to examine a two-dimensional cantilever beam model's validity using modal analysis and the Finite Element Method (FEM), comparing its solutions with those of a three-dimensional model.
+Our findings reveal that the beam's shape is a crucial factor in the model's validity for practical applications.
+For the appropriate beam shapes, the two-dimensional model is a valid approximation of the three-dimensional model.
 \end{abstract}
@@
 \begin{keyword}
-	Beam \sep Cantilever \sep Two-Dimensional Model \sep Three-Dimensional Model \sep Vibration Problems
+	Beams \sep Cantilever Beams \sep Two-Dimensional Models \sep Three-Dimensional Models \sep Vibration Analysis \sep Modal Analysis \sep Finite Element Method
 \end{keyword}
@@
 \section{Introduction}
-In the article \cite{LVV09}, the authors investigate the validity of a Timoshenko beam using a two-dimensional model as a reference.
-The two-dimensional model is a simplified model of the Timoshenko beam.
-The authors use the Finite Element Method (FEM) to solve the eigenvalue problem for the two models.
-The results are then compared to determine the validity of the two-dimensional model.
-
-In this article, \cite{LVV09} is extended and the validity of a two-dimensional model is investigated, using a three-dimensional model as a reference.
-Similar to \cite{LVV09}, the investigation focusses on beam-type problems.
-
-The models are presented in a dimensionless variational form.
-It is also explained how the two-dimensional model is derived from the three-dimensional model, as a special case of plane stress.
-The existence and uniqueness of solutions for the two models are briefly discussed.
-
-The concept of modal analysis is then introduced using a general vibration problem.
-From modal analysis, the formal series solution for the vibration problem is obtained.
-This formal series solution is a linear combination of the eigenvectors and eigenvalues of the problem.
-This enables us to compare the solutions of the two models, by only considering a comparison of the eigenvectors and eigenvalues.
-
-Using the Finite Element Method (FEM), a formula for the models are obtained to numerically solve the eigenvalue problem for the two models.
-The eigenvalues are matched up by comparing the mode shapes, and the eigenvalues are then compared.
-
-\section{Models}
-\subsection{Three-dimensional model}
+In the article \cite{LVV09}, the authors investigate the validity of a cantilever Timoshenko beam model.
+Validity refers to how well the solution of the simplified model compare to a more complex higher dimensional model.
+The reference model in \cite{LVV09} is a two-dimensional cantilever beam model.
+
+In this article, we build upon \cite{LVV09} by further examining the validity of a two-dimensional model for a cantilever beam, using a three-dimensional model as the reference.
+We follow the same methodology as \cite{LVV09}, employing modal analysis and the Finite Element Method (FEM) to compare the two models.
+This extention is motivated by the authors of \cite{LVV09}.
+
+To start, the models are presented in a dimensionless variational form.
+We explain how the two-dimensional model is derived from the three-dimensional model as a special case of plane stress.
+The well-posedness of the two models is not proved in this article, but the necessary existence and uniqueness results from \cite{VV02} are mentioned.
+
+Next we introduce the concept of modal analysis with a general vibration problem.
+Through modal analysis, we derive a formal series solution for the vibration issue, which is a linear combination of the problem's eigenvectors and eigenvalues.
+This approach allows us to compare the solutions of the two models by focusing on a comparison of their eigenvectors and eigenvalues.
+
+We then apply the Finite Element Method (FEM) to the two models and obtain a formula for the models to numerically solve the eigenvalue problem.
+The article \cite{BV13} provides essential convergence results for the FEM in vibration problems.
+The textbook \cite{SF73} also offers insights into the convergence of eigenvalues and eigenfunctions in a vibration problem when using FEM.
+
+Following \cite{LVV09}, by considering the mode shapes, we can match up the eigenvalues and compare them.
+In the comparison, we consider different shapes of beams that are useful in practical applications.
+We find that the shape of the beam significantly influences the validity of the two-dimensional model.
+The results of the comparison are presented in the form of tables and graphs.
+
+\section{Linear mathematical models}
+	\subsection{Three-dimensional theory}
 		Consider a vector valued displacement function $u \in \Omega \subset R^3$.
@@
 		\subsubsection*{Constitutive Equation}
+			\textcolor{red}{************ VOORSTEL om the verkort ************}
+
+			For an isotropic material, Hooke's law can be written in terms of Young's modulus $E$ and Poisson's ratio $\nu$.
+And if the principal stresses $\sigma_i$ are all non-zero, then Hooke's law can be written in the following form:
+			\begin{eqnarray}
+				T = \left( \frac{E}{1+\nu} \right)\mathcal{E} + \frac{\nu E}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \label{eq:3D_Model:CE}.
+			\end{eqnarray} Here $\mathcal{E}$ is the strain tensor and $T$ is the stress tensor.
+
+			In this form, Hooke's law is the constitutive equation for the three-dimensional model.
+
+			\textcolor{red}{************ VOORSTEL ************}
+
 			For an isotropic material, Hooke's law can be written in terms of Young's modulus $E$ and Poisson's ratio $\nu$ as follows.
@@
 
-\subsection{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
-Suppose $\ell$ represents some notable dimension (e.g.the length) of the elastic body 
-and $G$ the shear modulus of elasticity.
+		\subsubsection*{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
+			Suppose $\ell$ represents some notable dimension (e.g.the length) of the elastic body and $G$ the shear modulus of elasticity.
 
@@
 			\textbf{Remark} The constants introduced are the same as those in \cite{LVV09}.
-They simplify the equations and allow for comparisons to other models such as the Timoshenko beam model, although that is not covered in this article.
+			These dimsensionless constants allow for the comparison of the higher dimensional models to the Timoshenko beam model.
 
@@
 
-\subsection{Model problems}\label{ssec:3D_Model}
-Divide the boundary of $\Omega$ into two distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be considered a model problem for a three-dimensional elastic body. 
+		Divide the boundary of $\Omega$ into two distinct parts, referred to as $\Sigma$ and $\Gamma$.
 The following will be considered a model problem for a three-dimensional elastic body (also for the two-dimensional elastic body).
 		\begin{enumerate}
-	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} is satisfied in $\Omega$;
-	\item[] Hooke's law \eqref{eq:3D_Model:CE-D} is satisfied in $\Omega$;
+			\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D}, and Hooke's law is satisfied in $\Omega$;
 			\item[] The displacement $u = u_\Sigma$ is specified on
@@
 
-\subsubsection{Problem 3D}
+		\subsubsection*{Cantilever model}
 			Find a vector valued function $u$, satisfying equations
@@
 				Tn & = & 0 \quad \textrm{ on } \Gamma
-\end{eqnarray*} With $n$ the outward normal vector to $\Omega$. This model problem is a cantilever three-dimensional body.
-
-\subsection{Variational form}\label{ssec:3D_Model:VariationalForm}
+			\end{eqnarray*}
+
+			This will be referred to as \textbf{Problem 3D}.
+
+		\subsection*{Variational form}\label{ssec:3D_Model:VariationalForm}
 			Define the bilinear forms
@@
 
-The variational problem of Problem 3DV is given as:
-\subsubsection{Problem 3DV}\label{sssec:3D_Model:Problem3D1V}
 			Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and
@@
 
-\subsection{Plane stress}\label{ssec:3D_Model:PlaneStress}
+			This will be referred to as \textbf{Problem 3DV}.
+
+	\subsection{Two-dimensional theory}
+		\subsubsection*{General plane stress}
 			Stresses acting parallel to a single plane are referred to as plane stress. 
@@
 
-This is known as general plane stress.
-
-\subsection{Two-dimensional model} \label{ssec:2D_Model}
-For the two-dimensional modek, a special case of general plane stress is considered.
-
+			This is known as general plane stress. The two-dimensional model is a special case of plane stress.
+
+		\subsubsection*{The two dimensional model}
 			Assume that $\sigma_{3i} = 0$ for $i = 1, 2, 3$; $\partial_3 u_1 = 0$, $\partial_3 u_2 = 0$ ($u_1$ and $u_2$ are functions of $x_1$ and $x_2$), and the strain component $\varepsilon_{33} = 0$.
@@
 
-\subsection*{Equations of motion and constitutive equations}\label{ssec:2D_Model:EquationsOfMotion+ConstitutiveEquations}
- The following equations of motion and constitutive equations follow from subsections \ref{ssec:3D_Model:DimensionlessForm} and 1.3.2.
-\subsubsection{Equation of motion}\label{sssec:2D_Model:EquationOfMotion}
+			The equations of motion and constitutive equations follow:
+			\subsubsection*{Equation of motion}\label{sssec:2D_Model:EquationOfMotion}
 			\begin{eqnarray}
@@
 
-\subsection{Model problem}\label{ssec:2D_Model:ModelProblem}
-Divide the boundary of $\Omega$ into two distinct parts, referred to as $\Sigma$ and $\Gamma$.
-
-\subsubsection*{Problem 2D}\label{sssec:2D_Model:Problem2D1}
+		\subsubsection*{Cantilever model}
+
 			Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:
@@
 				Tn & = & 0 \quad \textrm{ on } \Gamma.
-\end{eqnarray*} with $n$ the outward unit normal. This model problem is a cantilever two-dimensional body.
-
-\subsection{Variational form}\label{ssec:2D_Model:VariationalForm}
+			\end{eqnarray*} with $n$ the outward unit normal.
+
+			This will be referred to as \textbf{Problem 2D}.
+
+		\subsubsection*{Variational form}\label{ssec:2D_Model:VariationalForm}
 			Define the bilinear forms
@@
 
-\subsubsection{Test functions for Problem 2D}\label{sssec:2D_Model:TestFunctions2D1}
+			\subsubsection*{Test functions for Problem 2D}\label{sssec:2D_Model:TestFunctions2D1}
 			Define the following set of test functions $T(\Omega)$ for Problem 2D:
@@
 
-The variational problem of Problem 2D is given as:
-
-\subsubsection{Problem 2DV}\label{sssec:2D_Model:Problem2D1V}
 			Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
@@
 			\end{align}
-for all $\phi \in T(\Omega)$.
-
-\section{Existance and uniqueness of solutions}
+			for all $\phi \in T(\Omega)$. This will be referred to as \textbf{Problem 2DV}.
+
+	\subsection{Timoshenko theory}
+		Consider a Timoshenko beam with no damping defined on the interval $[0,\ell]$.
+		Let $w$ represent the transverse displacement and $\phi$ a rotation of the cross-sections of the beam.
+
+		\subsubsection*{Equations of motion}\label{sssec:1D_Model:EquationOfMotion}
+			\begin{eqnarray}
+				\rho A \partial_t^2 w &=& \partial_x V + Q, \label{eq:1D_Model:EquationOfMotion1}\\
+				\rho I\partial_t^2 \phi  &=& V + \partial_x M. \label{eq:1D_Model:EquationOfMotion2}
+			\end{eqnarray}\label{sym:A}\label{sym:V}\label{sym:Iinertia}\label{sym:M}\label{sym:phiT}
+			In~\eqref{eq:1D_Model:EquationOfMotion1} and \eqref{eq:1D_Model:EquationOfMotion2} $\rho$ denotes the density, $A$ is the area of a cross section, $I$ is the area moment of inertia, $M$ is the moment, $V$ is the shear force and $Q$ is an external force acting on the beam.
+
+		\subsubsection*{Constitutive equations}\label{sssec:1D_Model:ConstitutiveEquation}
+			\begin{eqnarray}
+				M &=& EI\partial_x \phi, \label{eq:1D_Model:ConstitutiveEquations1}\\
+				V &=& AG\kappa^2(\partial_x w - \phi), \label{eq:1D_Model:ConstitutiveEquations2}\label{sym:kappa2T}
+			\end{eqnarray}
+			$E$ is Young's modulus, $G$ the shear modulus and $\kappa^2$ the shear correction factor.
+
+		\subsubsection*{Dimensionless form}\label{sssec:1D_Model:DimensionlessForm}
+			As mentioned in the dimensionless form of the three-dimensional model, the same dimensionless scaling can be applied to the Timoshenko beam theory.
+
+			Set \[\tau = \frac{t}{t_0}, \,\, \xi = \frac{x}{\ell}, \,\, w^*(\xi,\tau) = \frac{w(x,t)}{\ell} \ \text{ and } \ \phi^*(\xi, \tau) = \phi(x,t).\]
+
+			The dimensionless forms of the shear force, moment and external force density are \[ V^{*}(\xi,\tau) = \frac{V(x,t)}{AG\kappa^2}, \quad M^{*}(\xi,\tau) = \frac{M(x,t)}{A G\kappa^2 \ell} \,\,\, \ \text{and} \ \,\,\, Q^*(\xi,\tau) = \frac{Q(x,t)\ell}{A G\kappa^2}.\]
+
+			Choose $t_0$ the same as the three-dimensional model, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]
+
+			As in \cite{LVV09} we use the dimensionless constants
+			\begin{equation*}
+				\alpha = \frac{A \ell^2}{I} \,\,\, \text{and} \,\,\, \beta
+				=\frac{AG\kappa^2 \ell^2}{EI}.
+			\end{equation*}\label{sym:alphabeta}
+
+			Interestingly, it turns out that
+			\begin{eqnarray*}
+				\frac{\beta}{\alpha} & = & \gamma
+			\end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in the three-dimensional case.\\
+
+		\subsubsection*{Dimensionless equations of motion}\label{sssec:1D_Model:DimensionlessEquationsOfMotion}
+			\begin{eqnarray}
+				\partial_{t}^{2} w &=& \partial_{x}V + Q, \label{eq:1D_Model:EquationOfMotion1D}\\
+				\frac{1}{\alpha} \partial_{t}^{2} \phi &=& V + \partial_{x}M.\label{eq:1D_Model:EquationOfMotion2D}
+			\end{eqnarray}
+		\subsubsection*{Dimensionless constitutive equations}\label{sssec:1D_Model:DimensionlessConstitutiveEquations}
+			\begin{eqnarray}
+				M &=& \frac{1}{\beta}\partial_x \phi, \label{eq:1D_Model:ConstitutiveEquations1D}\\
+				V &=& \partial_x w-\phi. \label{eq:1D_Model:ConstitutiveEquations2D}
+			\end{eqnarray}
+		The original notation is retained for convenience.
+
+		\subsection{Models and variational forms}
+			\subsubsection*{Bilinear forms and integral}
+				For $f,g \in T[0,1]$, define the bilinear forms
+				\begin{eqnarray}
+					c(f,g) & = & \int_0^1  \partial_t^2 f_1 g_1 + \frac{1}{\alpha}\int_0^1  \partial_t^2 f_2g_2, \label{eq:1D_Model:Bilinear} \\
+					b(f,g) & = &   \int_0^1 (f_1'-f_2)(g_1' - g_2) + \frac{1}{\beta}\int_0^1 f_2' g_2', \label{eq:1D_Model:Bilinear_c}
+				\end{eqnarray}
+				Define the integral
+				\begin{eqnarray}
+				(f,g)
+					&=& \int_{0}^1 fg \label{eq:1D_Model:Bilinear_int}
+				\end{eqnarray} for all $f,g \in L^2(0,1).$\\
+
+				\textbf{Remark}\\
+				$L^2(a,b)$ is the space of all square integrable functions on the interval $(a,b)$.
+The inner product is defined by $\displaystyle (f,g) = \int_a^b fg$, and the induced norm $\displaystyle ||f|| = \int_a^b f^2$.\\
+
+			\subsection*{Pinned-pinned beam}
+				Find functions $w$ and $\phi$ satisfying equations \eqref{eq:1D_Model:EquationOfMotion1D} to \eqref{eq:1D_Model:ConstitutiveEquations2D} and the boundary conditions:
+
+				{Boundary Conditions}\\
+				\begin{eqnarray*}
+					w(0,\cdot) = 0, \ \ &M(0,\cdot) = 0, \label{eq:1D_Model:ProblemT1BC1}\\
+					w(1,\cdot) = 0, \ \ &M(1,\cdot) = 0. \label{eq:1D_Model:ProblemT1BC2}
+				\end{eqnarray*}
+
+				This will be referred to as \textbf{Problem T-1}. Define the set of test functions $T[0,1]$ for Problem T-1 as
+				\begin{eqnarray*}
+					T[0,1] &:=&  \left\{f \in C^1[0,1] \ | \ f(0) = f(1) = 0 \right\} \times C^1[0,1]
+				\end{eqnarray*}
+
+				Then the variational problem for Problem T-1 is given by
+				\subsubsection*{Problem T-1V}\label{sssec:1D_Model:ProblemT1V}
+					Find a function ${u} = \langle w, \phi \rangle$ such that for all $t >0$, ${u} \in  T[0,1]$ satisfying
+					\begin{eqnarray}
+						c(\partial_t^2 u,{\phi}) &=& -b({u},{\phi}) + (Q,{\phi})
+					\end{eqnarray} for each ${\phi} = \langle v, \psi \rangle \in T[0,1]$.
+
+			\subsection*{Cantilever beam}
+				Find functions $w$ and $\phi$ satisfying equations \eqref{eq:1D_Model:EquationOfMotion1D} to \eqref{eq:1D_Model:ConstitutiveEquations2D} and the boundary conditions:
+
+				{Boundary Conditions}\\
+				\begin{eqnarray*}
+					w(0,\cdot) = 0, \ \ &\phi(0,\cdot) = 0, \label{eq:1D_Model:ProblemT2BC1}\\
+					M(1,\cdot) = 0, \ \ &V(1,\cdot) = 0. \label{eq:1D_Model:ProblemT2BC2}
+				\end{eqnarray*}
+
+				This will be referred to as \textbf{Problem T-2}.  Define the set of test functions $T[0,1]$ for Problem T-2 as
+				\begin{eqnarray*}
+					T[0,1] &:=& \left\{g \in C^1[0,1] \ | \ g(0) = 0 \right\} \times \left\{g \in C^1[0,1] \ | \ g(0) = 0 \right\}
+				\end{eqnarray*}
+
+				Then the variational problem for Problem T-2 is given by
+				\subsubsection*{Problem T-2V}\label{sssec:1D_Model:ProblemT1V}
+					Find a function ${u} = \langle w, \phi \rangle$ such that for all $t >0$, ${u} \in  T[0,1]$ satisfying
+					\begin{eqnarray}
+						c(u,{\phi}) &=& -b({u},{\phi}) + (Q,{\phi}) \label{var_form_timo}
+					\end{eqnarray} for each ${\phi} = \langle v, \psi \rangle \in T[0,1]$.
+
+\section{Modal analysis and comparison of linear models}
+
+	\subsection*{Existance and uniqueness of solutions}
 		Our two models, the three-dimensional modela and the two-dimensional model, concern the vibration of elastic bodies.
@@
 
-Proving that these assumptions are satisfied for the models in this article too much work to 
-include in this article. The existence and uniqueness results of \cite{VV02} are used in 
-this article without proof.
-
-\section{Modal analysis and comparison of linear models}
-Modal analysis is a important concept in the study of vibration of elastic bodies and also 
-useful in the comparison of linear models. The following section is a short discussion of 
-the basic concepts of modal analysis and how it enables the comparison of linear models.
+		Proving that these assumptions are satisfied for the models in this article too much work to include in this article.
+The existence and uniqueness results of \cite{VV02} are used in this article without proof.
+
+	\subsection*{Modal Analysis}
+		Modal analysis is a important concept in the study of vibration of elastic bodies and also useful in the comparison of linear models.
+The following section is a short discussion of the basic concepts of modal analysis and how it enables the comparison of linear models.
 
@@
 
-\subsection{Validity of series solution}
+	\subsection*{Validity of series solution}
 		Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$?
@@
 
-Then $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$. Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$ by \eqref{eq:inequality}.
+		Then $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$.
+Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$ by \eqref{eq:inequality}.
 
@@
 
-\subsection{Comparison of models}
+	\subsection*{Comparison of models}
 		The results on modal analysis and the validity of the series solution enable the comparison of different linear models.
@@
 
-\section{Finite Element Method}
-In the section, the Finite Element Method (FEM) is applied to the models to obtain an eigenvalue problem that can be solved numerically.
-
-\subsection{Two-dimensional model}\label{ssec:2D_Model:FEM}
-Consider a cantilever two-dimensional elastic body, with a rectangular cross-section.
-
-\subsubsection{Reference configuration for rectangular cross-section}\label{sssec:2D_Model:RefConf}
+\section{Cantilever two-dimensional model}\label{ssec:2D_Model:FEM}
 Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$.
@@
 In this configuration, the body is clamped rigidly to the surface at $x_1 = 0$ denoted as $\Sigma$ and the body is free-hanging on the other boundaries denoted by $\Gamma$.
-
-\subsubsection{Cantilever elastic body}
-Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D in section \ref{ssec:2D_Model}.
+This is a catilever configuration.
 
@@
 
-\subsection{Weak variational form}
-Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)$.
-Denote $X = L^2(0,1)\times L^2(0,1)$.
-The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.
-
-\subsubsection{Problem 2DWV}
-Find a function $u$ such that $\forall \ t > 0$, $u \in V$ with $\partial_t^2 u \in W$ and
-\begin{eqnarray*}
-	c(u,v) + b(u,v) & = & (Q,v)
-\end{eqnarray*}
-for all $v\in V$.
-
 \subsection{Galerkin approximation}\label{2d_FEM_G}
@@
 
-\subsection{Three-dimensional model} \label{ssec:3D_Model:FEM}
-Consider a cantilever three-dimensional elastic body, with a rectangular cross-section.
-
-\subsubsection*{Reference configuration for rectangular cross-section}
+\section{Cantilever three-dimensional model} \label{ssec:3D_Model:FEM}
 Let $\{e_1,e_2,e_3\}$ be a right-handed orthonormal basis for $R^3$.
@@
 \end{align*}
-
-\subsection{Weak variational form}
-
-\subsubsection{Bilinear form}
-Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)\times H^1(0,1)$.
-Denote $X = L^2(0,1)\times L^2(0,1)\times L^2(0,1)$.
-The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.
-
-\subsubsection{Problem 3DW}
-Find a function $u$ such that for all $t>0$, $u(t) \in V$ and $u''(t) \in W$, satisfying the following equation
-\begin{eqnarray}
-	c(u,v) + b(u,v) & = & (Q,v) \ \ \ \textrm{ for each } v \in V.
-\end{eqnarray}
 
@@
 \section{Conclusion}
-In this article, the validity of a two-dimensional cantilever beam model is investigated by comparing it to a three-dimensional cantilever beam model.
-The two models are compared by using the Finite Element Method to obtain the eigenvalues and eigenvectors of the models.
-The eigenvalues are then matched up by considering the mode shapes, and a comparison is made.
-
-The models are presented in a dimensionless variational form. It is also shown how the two-dimensional model can be derived from the three-dimensional model as a special case of plane stress.
-
-The well posedness of the models are not discussed in detail, but the neseccary articles are referenced.
-The idea of modal analysis is explained by a general example.
-Modal analysis is crucial to the comparison of the models, and the application of the comparison of the models is shown in the numerical results of this article.
-
-For both models, the Finite Element Method is applied and a numerical formula is obtained for the eigenvalue problems.
-Using a computer program, the eigenvalues and eigenvectors are obtained for both models.
-
-For the comparison, the eigenvalues are matched up by comparing the mode shapes.
-The results of this article shows that the two-dimensional beam model compares very well to the three-dimensional beam model different shapes of beams.
-The shape of the beam however is crucial to how well the comparison is.
-The two-dimensional model compares best when the three-dimensional beam is thin and long, and less well when the three-dimensional beam is short and thick.
-The two-dimensional model does not compare well to the three-dimensional model when the width $b$ is larger than the height $h$.
-However a better suited model for this case might be a plate model.
+In this article, we explored the validity of a two-dimensional cantilever beam model by comparing it with a three-dimensional cantilever beam model.
+Using the Finite Element Method, we obtained the eigenvalues and eigenvectors for both models, aligning them through mode shape comparisons.
+
+The models were given in a dimensionless variational form, and we demonstrated how the two-dimensional model could be derived from the three-dimensional model as a specific case of plane stress.
+
+While we did not delve into the well-posedness of the models in detail, we cited necessary references.
+The principle of modal analysis was illustrated with a general example, proving essential for comparing the two models.
+This comparison's application is evident in the numerical results presented in this article.
+
+Applying the Finite Element Method to both models, we developed a numerical formula for solving the eigenvalue problems.
+A computer program was then used to extract the eigenvalues and eigenvectors for each model.
+
+Upon comparing the eigenvalues through mode shapes, our findings suggest that the two-dimensional beam model aligns well with the three-dimensional model for various beam shapes.
+However, the shape of the beam is pivotal to the comparison's accuracy.
+The two-dimensional model shows the best correlation with thin and long three-dimensional beams and less so with short and thick beams.
+Notably, the two-dimensional model does not align well when the beam's width $b$ exceeds its height $h$, suggesting that a plate model may be more appropriate in such cases and can be explored in future work.
 

### 2024-03-16 article.tex
fixe

@@
 	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
-\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines (or edges) as follows: \label{sym:En}
-
-\noindent\begin{minipage}{.5\linewidth}
-	\begin{eqnarray*}
-		\Sigma:& \quad x_1 &= 0\\
-		\Gamma_3:& \quad x_1 &= 1
-	\end{eqnarray*}
-\end{minipage}%
-\begin{minipage}{.5\linewidth}
-	\begin{eqnarray*}
-		\Gamma_1:& \quad x_2 &= -{h}/{2}\\
-		\Gamma_2:& \quad x_2 &= {h}/{2}
-	\end{eqnarray*}
-\end{minipage}
-
-In this configuration, the body is clamped rigidly to the surface at $x_1 = 0$ denoted as $\Sigma$ and the body is free-hanging on the other boundaries denoted by $\Gamma$.
-This is a catilever configuration.
+\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$.
 
@@
 
-The variational problem for the two dimensional cantilever model is also derived in \ref{ssec:2D_Model} and refered to as Problem 2DV.
-Using the reference configuration, the variational problem can be rewritten into a model specific form.
-
-\subsubsection{Problem 2DV}\label{sssec:2D_Model:Problem2D1VChp5}
+ Using the reference configuration, the variational problem Problem 2DV can be rewritten into a model specific form.
+
+\subsubsection*{Problem 2DV}\label{sssec:2D_Model:Problem2D1VChp5}
 Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
@@
 
-\subsubsection{Constitutive equations:}
+\subsubsection*{Constitutive equations:}
 \begin{eqnarray}
@@
 
-\subsubsection{Bilinear form:}
+\subsubsection*{Bilinear form:}
 \begin{align}
@@
 
-\subsection{Galerkin approximation}\label{2d_FEM_G}
-To be able to apply the Finite Element Method to Problem 2DV, the body $\Omega$ needs to be discretised.
-This is done by dividing the body $\Omega$ into discrete shapes, called elements.
-There are various types of shapes of elements that can be used.
-Since the body $\omega$ is has a rectangular cross-section, rectangular elements are the simplest elements to use.
-
-Divide the reference configuration $\Omega$ into a grid of rectangular elements, such that there are $n = n_1\times n_2$ nodes.
-
-Define a set of $n$-dimensional linear independent basis functions.
-For the two dimensional model, the basis functions can be defined by the set $$B = \left\{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \right\}.$$
-
-These functions are chosen as piecewise Hermite bi-cubic functions $\phi_i$.
-Simpler bi-linear functions can also be used, however the use of the bi-cubic basis functions results in faster convergence and also the benefit of obtaining the derivatives of the solution at the expense of more complexity.
-
-The subset of basis functions $B$ that satisfies all the conditions of the test function space $T(\Omega)$ are called the admissible basis functions.
-Denote the admissible basis functions by $\delta_j$, where each $\delta_j$ is a unique element of $B$.
-The admissible basis functions can be numbered and expressed as the set $A = \left \{\delta_1, \delta_2,..., \delta_k \right\}$ for some $k \leq 2n$.\\
+\subsection*{Galerkin approximation}\label{2d_FEM_G}
+To apply the Finite Element Method to Problem 2DV, $\Omega$ must be discretized by dividing it into rectangular elements, suitable for its rectangular cross-section.
+This process involves creating a grid with $n = n_1 \times n_2$ nodes across $\Omega$.
+
+A set of $n$-dimensional linear independent basis functions is defined, particularly for the two-dimensional model, as 
+$$B = \{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \}.$$ 
+These functions, chosen as piecewise Hermite bi-cubic functions $\phi_i$, offer quicker convergence and the ability to derive solution derivatives, despite their increased complexity compared to bi-linear functions.
+
+The subset of basis functions from $B$ that meet the criteria of the test function space $T(\Omega)$ are termed admissible basis functions, denoted by $\delta_j$, where each $\delta_j$ is a distinct element of $B$.
+These can be enumerated and presented as the set
+$$A = \{\delta_1, \delta_2,..., \delta_k \}$$ 
+for some $k \leq 2n$.
 
@@
 
-\subsubsection{Problem 2DG}
+\subsubsection*{Problem 2DG}
 Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
@@
 
-\subsection{System of differential equations}\label{ssec:2DFEM:DE}
-
 Consider the following standard Finite Element Method matrices
-\subsubsection{FEM matrices}
+
 \noindent\begin{minipage}{.5\linewidth}
@@
 
-\subsubsection{Problem 2DODE}
+\subsubsection*{Problem 2DODE}
 Find a function $\bar{u} \in S^h$ such that
@@
 
-\subsection{Eigenvalue problem}\label{2dFEM_EP}
+\subsection*{Eigenvalue problem}\label{2dFEM_EP}
 For the eigenvalue problem, assume that there is no external force, $M_{f}Q^I = 0$, so that 
@@
 
-\subsubsection{Problem 2DE}
+\subsubsection*{Problem 2DE}
 Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
@@
 \end{eqnarray*}
-Let $\partial \Omega$ denote the boundary of the body. Divide $\partial \Omega$ into the six distinct flat surfaces as follows:
-
-\noindent\begin{minipage}{.5\linewidth}
-	\begin{eqnarray*}
-		\Sigma:& \quad x_1 &= 0\\
-		\Gamma_5:& \quad x_1 &= 1\\
-		\Gamma_1:& \quad x_3 &= -{b}/{2} 
-	\end{eqnarray*}
-\end{minipage}%
-\begin{minipage}{.5\linewidth}
-	\begin{eqnarray*}
-		\Gamma_2:& \quad x_2 &= -{h}/{2}\\
-		\Gamma_3:& \quad x_3 &= {b}/{2}\\
-		\Gamma_4:& \quad x_2 &= {h}/{2} 
-	\end{eqnarray*}
-\end{minipage}
-
-Using this notation, the boundary conditions are similar to the two-dimensional model, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.
-
-\subsubsection{Cantilever elastic body}
-Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma$ and free-hanging at all the other sides.
-This is Problem 3D in section \ref{ssec:3D_Model}.
-
+Let $\partial \Omega$ denote the boundary of the body.
+
+\FloatBarrier
 \begin{figure}[h!]
@@
 
-In section \ref{ssec:3D_Model}, the variational problem for the three-dimensional cantilever model is defined by Problem 3DV.
-This general form can now be rewritten as in a model specific form using the reference configuration.
-
-\subsubsection{Problem 3DV}
+\FloatBarrier
+
+This general variational form Problem 3DV can now be rewritten as in a model specific form using the reference configuration.
+
+\subsubsection*{Problem 3DV}
 Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
@@
 
-\subsubsection{Bilinear Form}
+\subsubsection*{Bilinear Form}
 \begin{align*}
@@
 
-\subsection{Galerkin approximation}
-For this is three-dimensional body, three-dimensional elements shapes are required.
-The elements used in this dissertation are rectangular prismatic elements.
-These elements are also known as `brick-shaped' elements and is described in \cite{Wu06}.
-This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.
-
-Divide the reference configuration $\Omega$ into a grid of rectangular prismatic elements, such that there are $n = n_1 \times n_2 \times n_3$ nodes.
-
-Define a set of $n$-dimensional linear independent basis functions. For the three-dimensional model, the basis functions can be defined by the set
+\subsection*{Galerkin approximation}
+For analyzing a three-dimensional body, rectangular prismatic (brick-shaped) elements are used, as detailed in \cite{Wu06}. This choice suits bodies with rectangular cross-sections.
+
+Split $\Omega$ into a grid of these elements, creating $n = n_1 \times n_2 \times n_3$ nodes.
+
+Define $n$-dimensional linear independent basis functions for the three-dimensional model as
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-
-For the this three-dimensional model, piecewise Hermite tri-cubic basis functions are used.
-Although this is more complex than using piecwise tri-linear basis functions, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
-
-Recall that the admissible basis functions, are all the basis functions that satisfies all the conditions of the test function space $T(\Omega)$.
-Denote the admissible basis functions by $\delta_j$, with each $\delta_j$ a unique element of $B$.
-The set of admissible basis functions can then be expressed as $A = \left\{\delta_1, \delta_2,...
-, \delta_k\right\}$ with $k \leq 3n$.
+Employing piecewise Hermite tri-cubic basis functions offers quicker convergence and solution derivatives, albeit with increased complexity compared to tri-linear functions.
+
+Admissible basis functions, satisfying all conditions of $T(\Omega)$, are denoted by $\delta_j$, making up the set $A = \left\{\delta_1, \delta_2,... , \delta_k\right\}$, where $k \leq 3n$.
 
@@
 
-\subsubsection{Problem 3DG}
+\subsubsection*{Problem 3DG}
 Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
@@
 
-\subsection{System of ordinary differential equations}\label{3d_fem_g}
 Consider the following standard Finite Element Method matrices.
 
-\subsubsection{FEM matrices}
 \noindent\begin{minipage}{.5\linewidth}
@@
 
-\subsubsection{Problem 3DODE}
+\subsubsection*{Problem 3DODE}
 Find a function $\bar{u} \in S^h$ such that
@@
 
-\subsection{Eigenvalue problem}
+\subsection*{Eigenvalue problem}
 The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in section \ref{2dFEM_EP}.
 
-\subsubsection{Problem 3DE}\label{3dFEM_EP}
+\subsubsection*{Problem 3DE}\label{3dFEM_EP}
 Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
@@
 \section{Validity of a model for a cantilever two-dimensional beam} \label{sec:validity-of-a-2d-beam}
-As mentioned in the introduction of the chapter, a beam is a three-dimensional body and therefore a three-dimensional model is more realistic.
-However the authors of \cite{LVV09} mention that a direct comparison of the one and three-dimensional models will have complexities and they suggest using the two-dimensional model as an intermediate step.
-
-So in this section, the article \cite{LVV09} is extended and the validity of a cantilever two-dimensional beam model is investigated, using a cantilever three-dimensional model as a reference.
-
-\subsection{The models}
+In this section, we compare the two-dimensional cantilever beam with a three-dimensional cantilever beam.
+
 Figure \ref{fig:2Dv3D} shows the two beams, Problem 2D and Problem 3D side-by-side.
@@
 
-\subsection{Calculating the eigenvalues}
-In section \ref{ssec:2D_Model:FEM} and \ref{ssec:3D_Model:FEM}, the Finite Element Method for the two-dimensional beam and three-dimensional beam is derived.
-Using this method, the eigenvalue problems can be solved to obtain the eigenvalues and eigenvectors of the two models.
-
-\subsubsection{Problem 2DE and 3DE}
-Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
-\begin{eqnarray}
-	K\bar{u} & = & M\lambda{\bar{u}},
-\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in section \ref{ssec:2DFEM:DE} for the Problem 2DE and section \ref{3d_fem_g} for Problem 3DE.
-
-\subsubsection{Accuracy of the eigenvalues}
-When solving the eigenvalue problems with a numerical method, the accuracy of the eigenvalues can be established by investigating the rate of convergence.
-
-\begin{figure}[H]
-    \centering
-    \begin{adjustbox}{center}
-        \includegraphics[scale=0.7]{files/Chapter4/Convergence.png}
-    \end{adjustbox}
-    \caption{Rate of convergence of the first 20 eigenvalues for Problem 2DE.}
-    \label{fig:conv_2d_eig}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \begin{adjustbox}{center}
-        \includegraphics[scale=0.7]{files/Chapter6/convergence3d.png}
-    \end{adjustbox}
-    \caption{Rate of convergence of the first 20 eigenvalues for Problem 3DE.}
-    \label{fig:conv_3d_eig}
-\end{figure}
-
-Figure \ref{fig:conv_2d_eig} and \ref{fig:conv_3d_eig} shows the rate of convergence of the first 20 eigenvalues of the two-dimensional beam and the three-dimensional beam respectively.
-Each color represents a spesific eigenvalue.
-
-These figures show that the two-dimensional model has a much faster rate of convergence than the three-dimensional model.
-The two-dimensional model also converge faster to a higher accuracy than the three-dimensional model.
-
-Using this, the number of elements can be chosen so that at least the first 10 eigenvalues are accurate to 5 significant digits for the two-dimensional model.
-For the three-dimensional model, obtaining this level of accuracy can be difficult and computationally expensive, but it is possible to get 4 significant digits of accuracy for the first 10 eigenvalues.
+\subsection{Calculating the eigenvalues and mode shapes}
+The eigenvalues and mode shapes of the two models are calculated using the computer program.
+The eigenvalues and mode shapes are then compared to determine the accuracy of the two-dimensional model for the cantilever beam.
+The accuracy of the eigenvalues depends on the number of elements employed in the finite element method.
+For the two-dimensional model, accuracy reaches at least five significant digits for the first 10 eigenvalues, while the three-dimensional model achieves at least four significant digits for its first 10 eigenvalues.
 
 \subsection{Comparing the mode shapes}
-To be able to compare the eigenvalues, the mode shapes of the two models are compared to match up the eigenvalues of the two models. This is the same approach as in the article \cite{LVV09}.
-
-When calculating the mode shapes, distinct patterns are observed.
-There are mode shapes that are present in both models, mode shapes that are only present in the three-dimensional model.
-The shared mode shapes also include mode shapes that relate to beam problems.
-These are the mode shapes that are of interest the article \cite{LVV09}.
-
-The focus of the investigation of this article is also on beam type problems.
-Below are some examples of the mode shapes for beam type eigenvalues, mode shapes for non-beam type eigenvalues that are shared between the two and three-dimensional models and also mode shapes for non-beam type eigenvalues that are only present in the three-dimensional model.
-
-\subsubsection{Mode shapes relating to beam type eigenvalues.}
+Following \cite{LVV09}, the mode shapes of the two models are compared.
+As seen in \cite{LVV09}, the eigenvalues of the Timoshenko beam model (beam-type eigenvalues) are all present in the two-dimensional model.
+However not all the eigenvalues of the two-dimensional model are present in the Timoshenko beam model.
+These are called non-beam type eigenvalues.
+
+The same is observed for the three-dimensional model, as there are eigenvalues that are present in the three-dimensional model that are not present in the two-dimensional model.
+
+Therefore it is required to match the eigenvalues of the two models by comparing the mode shapes.
+
+\subsubsection*{Mode shapes relating to beam type eigenvalues.}
 Figure \ref{fig:beam-2dv3d} show some examples of beam type mode shapes for the displacement $u$.
@@
 
-\subsubsection{Mode shapes relating to non-beam type eigenvalues that are present in the two-dimensional model.}
+\subsubsection*{Mode shapes relating to non-beam type eigenvalues that are present in the two-dimensional model.}
 Figure \ref{fig:nonbeam-2dv3d} show examples of mode shapes relating to non-beam type eigenvalues for the displacement $u$.
@@
 
-\subsubsection{Mode shapes relating to non-beam type eigenvalues that are not present in the two-dimensional model.}
+\subsubsection*{Mode shapes relating to non-beam type eigenvalues that are not present in the two-dimensional model.}
 Figure \ref{fig:nonbeam-2dv3d} show examples of mode shapes relating to non-beam type eigenvalues for the displacement $u$ which are not present in the two-dimensional model.
@@
 \subsection{Comparing the eigenvalues}
-For a realistic comparison of the models, the parameters need to be chosen carefully.
-The parameters are $h$ representing the height of the beam and $b$ representing the width of the beam.
-The two-dimensional model does not have the width parameter.
-
-For $h$, values are chosen that covers a range of beam shapes from a short thick beam, to a long slender beam.
-two cases are selected that represents realistic cases.
-For a short and thick beam, consider $h = 1/5$ and for a long and slender beam, consider $h = 1/20$.
-
-For the parameter $b$, two different cases will be considered.
-The first case is for $b \leq h$, and the $b > h$.
-The distinction of these two cases will become apparent in the results.
-It is important to note that the parameter $b$ will be expressed as a multiple of $h$.
-
-All of the results will include all the eigenvalues shared between the two-models, including not beam type eigenvalues.
-The non-beam type eigenvalues will be highlighted in grey.
-The non-beam type eigenvalues that are not shared between the two models will be excluded from the results, but the numbering of the eigenvalues will be kept as if they were included.
+For a realistic comparison of the models, it's crucial to carefully select parameters $h$ and $b$, representing the beam's height and width, respectively, noting that the two-dimensional model lacks the width parameter $b$.
+
+Values for $h$ span a range from short, thick beams ($h = 1/5$) to long, slender beams ($h = 1/20$), capturing two realistic scenarios.
+Regarding $b$, it's considered in two scenarios: when $b \leq h$ and when $b > h$, with $b$ expressed as a multiple of $h$.
+This distinction influences the results.
+
+Results will cover all shared eigenvalues between the models, highlighting non-beam type eigenvalues in grey.
+Non-beam type eigenvalues unique to either model are excluded, but eigenvalue numbering will proceed as if they were included.
 
@@
 
-Tables \ref{tab:2v3_1} and \ref{tab:2v3_2} show that the first 20 eigenvalues two-dimensional model compares very well to the matching eigenvalues three-dimensional beam for $b<=h$.
-As the width $b$ decreases, the two-dimensional model becomes a better approximation of the three-dimensional model.
-Also shown is that the slender beam with $h = 1/20$ compares better than the thick beam where $h = 1/5$, event though the case of $h=1/5$ is still a very good comparison.
-
-The tables also shows that the three-dimensional model has more non-beam type eigenvalues as the width $b$ decreases, as well as when the width $h$ decreases.
-
-Tables \ref{tab:2Dv3D_1_breakup} and \ref{tab:2v3_2_split} breaks up the maximum relative error for the beam type and non-beam type eigenvalues.
-These tables confirm that the the beam type eigenvalues compare very well.
+Tables \ref{tab:2v3_1} and \ref{tab:2v3_2} show that the first 20 eigenvalues of the two-dimensional model closely match those of the three-dimensional beam for $b \leq h$.
+As width $b$ decreases, the two-dimensional model approximates the three-dimensional model more accurately.
+The comparison is notably better for the slender beam with $h = 1/20$ than for the thick beam with $h = 1/5$, though both comparisons are strong.
+
+The tables also indicate an increase in non-beam type eigenvalues in the three-dimensional model as both $b$ and $h$ decrease.
+
+Tables \ref{tab:2Dv3D_1_breakup} and \ref{tab:2v3_2_split} show the maximum relative error for beam type and non-beam type eigenvalues, confirming the close comparison of beam type eigenvalues.
 
@@
 
-Tables \ref{tab:b>h} and \ref{tab:b>h_20} show that the two-dimensional model compares less well to the three-dimensional model when $b$ is too much larger than $h$.
-Tables \ref{tab:b>h-split} and \ref{tab:b>h-split_20} show that this is also true for the beam type eigenvalues.
-
-For the case of $h=1/5$, it was also more difficult to obtain reliable eigenvalues using a numerical method.
-
-These results gives a detailed overview of the validity of the cantilever two-dimensional beam compared to the cantilever three-dimensional beam.
-The results show that the two-dimensional beam model compares very well to the three-dimensional beam model for a large range of beam shapes.
-The results shown were chosen to represent realistic cases, and the results are similar for other cases.
-
-The overall conclusion is that the shape of the beam is very important.
-If the width $b$ is equal to or less than the height $h$, the two-dimensional beam model compares very well to the three-dimensional beam model.
-More so when the beam is slender, and less so when the beam is short and thick.
-
-When the width $b$ is larger than the height $h$, the two-dimensional beam the comparison degrades very quickly.
-This is true for both slender and short and thick beams, although with short and thick beams, it is more difficult to obtain reliable eigenvalues using a numerical method.
-
-For practical applications, if $b > h$ the use of a beam model must be brought into question.
-Other models such as a plate model will be better suited as it is a more realistic model.
-In the next section, the validity of the Reissner-Mindlin plate mode is investigated using the same method of this section.
+Tables \ref{tab:b>h} and \ref{tab:b>h_20} indicate that the two-dimensional model's accuracy declines when $b$ significantly exceeds $h$, a trend also observed for beam type eigenvalues in Tables \ref{tab:b>h-split} and \ref{tab:b>h-split_20}.
+Particularly for $h=1/5$, obtaining reliable eigenvalues numerically was challenging.
+
+These results comprehensively assess the two-dimensional cantilever beam model against the three-dimensional counterpart, demonstrating good agreement across a broad spectrum of beam shapes, especially in scenarios representing realistic cases.
+
+The key takeaway is the critical role of beam shape: the two-dimensional model performs excellently when $b \leq h$, particularly for slender beams, but less so for short, thick beams.
+The model's accuracy rapidly deteriorates as $b$ surpasses $h$, affecting both slender and short, thick beams, with the latter posing challenges in numerical eigenvalue calculation.
+
+For practical applications, a beam model's suitability is questionable when $b > h$, suggesting alternative approaches like plate models for more accurate representation.
+The next section explores the Reissner-Mindlin plate model's validity using a similar analysis.
 

### 2024-03-16 article.tex
Timo added

@@
 \input{preamble_article.tex}
-% \usepackage{geometry}
-% \geometry{
-%   left=1in,
-%   right=1in,
-%   top=1in,
-%   bottom=1in,
-% }
+\usepackage{geometry}
+\geometry{
+  left=1.3in,
+  right=1.4in,
+  top=1.4in,
+  bottom=1.4in,
+}
 
@@
 	Now Problem 2DE and Problem 3DE can be solved using a computer program. Iterative methods, sparse matrices as well as parallel computing can be used to efficiently solve these problems.
+
+\section{Validity of the model for a cantilever Timoshenko beam (CHAPTER 4 of dissertation)} \label{sec:validity-of-a-cantilever-timoshenko-beam}
+
+	In this section, the validity of the Timoshenko beam model is investigated.
+Specifically, the validity of a cantilever Timoshenko beam model, using a cantilever two-dimensional beam model as a reference.
+This follows what is done in the article \cite{LVV09}.
+This section discusses the results of the article, focussing on the numerical results.
+Some of the results are replicated with more significant digits, others are extended to be used in the rest of this chapter.
+
+	The article \cite{LVV09} is titled `Comparison of linear beam theories'.
+In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
+The authors start by presenting the models.
+These are the same as Problem T-2 and Problem 2D-1 that are defined in Chapter~1.
+The authors also look at the existence and uniqueness of solutions, which is covered in Chapter 2 of this dissertation.
+The authors then calculate and compare the eigenvalues and eigenfunctions, which will be discussed in this section.
+
+	\subsection{The models}
+	The cantilever Timoshenko beam model is defined in section \ref{ssec:1D_Model:ModelProblems}, and is referred to as Problem T-2.
+The cantilever two-dimensional beam model is defined in section \ref{ssec:2D_Model:ModelProblem}, and is referred to as Problem 2D-1.
+
+	Figure \ref{fig:compare:1D+2D} shows the two beams side-by-side.
+
+	\begin{figure}[h!]
+		\scalebox{.8}{
+			\makebox[\textwidth][c]{
+				\caption{Side by side comparison of the beams.}
+				\centering
+				\begin{minipage}[b]{0.8\linewidth}
+					\begin{center}
+						\begin{tikzpicture}
+						\draw[line width = 0.4mm] (0,0) -- (6,0);
+
+						\node at (2.7,-0.25) {$\ell = 1$};
+
+						\draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
+						\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
+						\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
+						\draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
+						\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
+						\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
+						\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
+						\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
+						\draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);
+
+						\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
+						\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
+						\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
+						\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
+						\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
+						\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
+						\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
+						\draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
+
+						%\node at (3.2,-0.2) {$\ell = 1$};
+						\end{tikzpicture}
+					\end{center}
+					\subcaption{Timoshenko Cantilever Beam}
+				\end{minipage}
+				\begin{minipage}[b]{0.8\linewidth}
+					\begin{center}
+						\begin{tikzpicture}
+							\draw[line width = 0.4mm] (0,0.2) -- (6,0.2);
+							\draw[line width = 0.4mm] (0,-0.2) -- (6,-0.2);
+							\draw[line width = 0.4mm] (6,-0.2) -- (6,0.2);
+							%\draw[line width = 0.4mm] (0,-0.2) -- (0,0.2);
+
+							%\draw[line width = 0.1mm,->] (6,2) -- (7.4,2);
+							%\draw[line width = 0.1mm,->] (6,2) -- (6,0.9);
+							%\node at (6.7,1.8) {$e_1$};
+							%\node at (5.8,1.4) {$e_2$};
+
+							\node at (6.2,0) {$h$};
+							\node at (2.7,-0.45) {$\ell = 1$};
+
+							\draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
+							\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
+							\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
+							\draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
+							\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
+							\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
+							\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
+							\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
+							\draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);
+
+							\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
+							\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
+							\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
+							\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
+							\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
+							\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
+							\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
+							\draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
+
+							%\node at (3.2,-0.3) {$\ell = 1$};
+
+						\end{tikzpicture}
+					\end{center}
+					\subcaption{Two-Dimensional Cantilever Beam}
+				\end{minipage}
+			}
+		}
+	\end{figure}\label{fig:compare:1D+2D}
+
+	In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
+	introduced. The paramater is given here again for convenience:
+	\begin{eqnarray*}
+		\alpha = \frac{A\ell^2}{I}.
+	\end{eqnarray*}
+
+	The model is in a dimensionless form, therefore the length of the beam is $\ell = 1$.
+Since we assumed a square cross-section, the area of the cross-section can be calculated as $\displaystyle A = hb$.
+The area moment of inertia can also be calculated as $\displaystyle I = \frac{h^3b}{12}$.
+Substituting these values into the formula for $\alpha$ gives the following relationship between the height of the beam and the parameter $\alpha$: $\displaystyle \alpha = \frac{12}{h^2}$
+	or equivalently,
+	\begin{eqnarray}
+		h & = & \sqrt{\frac{12}{\alpha}}. \label{eq:h-alpha-relationship}
+	\end{eqnarray}
+	Using this relationship, the height of the beam model can be set by considering the value of $\alpha$.
+
+	\subsection{Calculating the eigenvalues and eigenvectors}
+	In section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided.
+And in section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.
+
+	For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method.
+In section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived.
+Specifically, section \ref{2dFEM_EP} derived the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.
+
+	\subsubsection{Problem 2D-1E}
+	Find a real number $\lambda$ and a vector $\bar{u} \in R^n$ such that
+	\begin{eqnarray}
+		K\bar{u} & = & M\lambda{\bar{u}},
+	\end{eqnarray} where $M$ and $K$ are the standard Finite Element Method matrices defined in section \ref{sec:FEM:2D}.
+
+	In this form, the eigenvalue problem is a system of ordinary differential equations, and can be solved using a numerical method.
+Computer programs like MATLAB provide functions that are able to solve this.
+
+	\subsubsection{Accuracy of the eigenvalues}
+	Solving \textbf{Problem 2D-1E} with a numerical method, requires a quick investigation into the rate of convergence so that the accuracy of the eigenvalues can be established.
+Chapter \ref{ch:finite-element-theory} provides the necessary theory on the existence of solutions as well as the proof of convergence of the Finite Element Method.
+
+	\begin{figure}[H]
+		\centering
+		\begin{adjustbox}{center}
+			\includegraphics[scale=0.7]{files/Chapter4/Convergence.png}
+		\end{adjustbox}
+		\caption{Rate of convergence of the first 20 eigenvalues.}
+		\label{fig:conv_2d_eig}
+	\end{figure}
+
+	Figure \ref{fig:conv_2d_eig} shows the rate of convergence of the first 20 eigenvalues of the two-dimensional beam. Each color represents a spesific eigenvalue.
+
+	The number of elements are chosen so that at least the first 10 eigenvalues are accurate to 5 significant digits.
+
+	\subsection{Comparing the mode shapes}
+	Recall from the introduction, that the investigation is focussed on beam-type problems.
+The two-dimensional model is for an eigenvalue problem and and not specific to beam-type applications, like the Timoshenko beam model.
+Therefore there are non-beam type modes that can be expected from the two-dimensional model.
+This is also be reflected in the eigenvalues of the two-dimensional model and therefore eigenvalues irrelevant to beam-type problems exits.
+
+	Therefore a method is required to compare and match the eigenvalues of the two models.
+In \cite{LVV09}, the authors compare the mode shapes of the two models, to match up the eigenvalues.
+Eigenvalues relating to the mode shapes similar to the mode shapes of the Timoshenko beam, are called beam-type eigenvalues.
+The other eigenvalues are called non-beam type eigenvalues by the authors.
+
+	\subsubsection{Shapes relating to beam-type eigenvalues}
+	The following figures are examples of beam-type mode shapes for the displacement $w$.
+
+	\begin{figure}[h!]
+		\scalebox{.8}{
+			\makebox[\textwidth][c]{
+				\centering
+				\begin{minipage}[b]{0.8\linewidth}
+					\includegraphics[width=1\linewidth]{files/Chapter4/Beam1.jpg}
+					\subcaption{2D Beam Type - $\lambda_6 = 21.911$}
+					\label{fig:minipage2}
+				\end{minipage}
+				\begin{minipage}[b]{0.8\linewidth}
+					\includegraphics[width=1\linewidth]{files/Chapter4/1DBeam2.png}
+					\subcaption{Timoshenko - $\lambda_5 = 21.794$}
+					\label{fig:minipage1}
+				\end{minipage}
+		}}
+		\scalebox{.8}{
+			\makebox[\textwidth][c]{
+				\begin{minipage}[b]{0.8\linewidth}
+					\includegraphics[width=1\linewidth]{files/Chapter4/Beam2.jpg}
+					\subcaption{2D Beam Type - $\lambda_7 = 45.711$}
+					\label{fig:minipage2}
+				\end{minipage}
+				\begin{minipage}[b]{0.8\linewidth}
+					\includegraphics[width=1\linewidth]{files/Chapter4/1DBeam1.png}
+					\subcaption{Timoshenko - $\lambda_6 = 45.390$}
+					\label{fig:minipage1}
+				\end{minipage}
+				\caption{Modal shapes of the displacement $w$ for the beam-type 2D body and the Timoshenko beam with $\alpha = 4800$ ($h = 1/20$).}
+			}
+		}
+	\end{figure}
+	\FloatBarrier
+
+	\subsubsection{Shapes relating to non-beam type eigenvalues}
+	The following figures are examples of non beam-type mode shapes for the displacement $w$. These mode shapes are not present in the cantilever Timoshenko beam model and are not beam related. 
+	\begin{figure}[h!]
+		\scalebox{.8}{
+			\makebox[\textwidth][c]{
+				\centering
+				\begin{minipage}[b]{0.8\linewidth}
+					\includegraphics[width=1\linewidth]{files/Chapter4/NotBeam1.jpg}
+					\subcaption{Non-Beam Type - $\lambda_4 = 7.7077$}
+					\label{fig:minipage2}
+				\end{minipage}
+				\begin{minipage}[b]{0.8\linewidth}
+					\includegraphics[width=1\linewidth]{files/Chapter4/NotBeam2.jpg}
+					\subcaption{Non-Beam Type - $\lambda_8 = 69.344$}
+					\label{fig:minipage1}
+				\end{minipage}
+				\caption{Modal shapes of the displacement $w$ for the non-beam type 2D body with $h = 1/20$.}
+			}
+		}
+	\end{figure}
+	\FloatBarrier
+
+	\subsubsection{Shape of the cross-sections}
+	The Timoshenko beam theory improve some one-dimensional beam theories such as the Euler-Bernoulli beam theory by also including the effect of shear.
+For Timoshenko beam theory it is assumed that the cross-sections need not remain perpendicular to the neutral axis of the beam.
+The cross-sections however remain a straight line.
+
+	For the two-dimensional beam, the shape of the cross-section can deform into a S-shape. This is explained in \cite{LVV09} and a similar figure in \cite{LVV09} is given here.
+
+	\FloatBarrier
+	\begin{figure}[h!]
+		\centering
+		\begin{tikzpicture}[scale=1.2]
+
+		\draw[line width = 0.4mm] (0,1) -- (7,1);
+		\draw[line width = 0.4mm] (0,-1) -- (7,-1);
+		\draw[line width = 0.4mm] (7,-1) -- (7,1);
+		\draw[line width = 0.4mm] (0,-1) -- (0,1);
+
+		\draw[line width = 0.1mm,dashed] (3.5,1) -- (3.5,-1);
+
+		\draw[thick] plot [smooth,tension=0.9] coordinates{(3.3,1) (3.7,0.5) (3.5,0) (3.3,-0.5) (3.7,-1)};
+
+		\draw[line width = 0.2mm,red] (3.3,1) -- (3.7,-1);
+
+	\end{tikzpicture}
+		\caption{S-shape deformation of the cross-section of the two-dimensional beam.}\label{fig:s}
+	\end{figure}
+	\FloatBarrier
+
+	Note that figure \ref{fig:s} shows an exaggerated example of the deformation of a cross-section.
+The red line shows how the authors of \cite{LVV09} calculated the average rotation of a cross-section of the two-dimensional beam.
+This average rotation can be used to compare the rotation of the cross-section of the two-dimensional beam to the rotation of the cross-section of the Timoshenko beam given by $\phi$.
+
+	\subsubsection{Direct comparison of mode shapes}
+	Figure \ref{fig:w} directly compares a mode shape of the Timoshenko beam to a mode shape of the two-dimensional beam.
+For the two-dimensional model, the center line of the displacement of the beam is shown.
+For the Timoshenko beam, the displacement $w$ is shown.
+
+	\begin{figure}[ht!]
+		\scalebox{.8}{
+			\makebox[\textwidth]{
+				\centering
+				\centering
+				\includegraphics[scale=0.4]{files/Chapter4/1Dv2D.png}
+				\caption{Comparison of the displacement $w$ mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
+				\label{fig:w}}}
+	\end{figure}
+	\FloatBarrier
+
+	Similarly, figure \ref{fig:phi} directly compares the angle of the cross-section of the Timoshenko beam and the two-dimensional beam.
+The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s}.
+
+	\FloatBarrier
+	\begin{figure}[ht!]
+		\scalebox{.8}{
+			\makebox[\textwidth]{
+				\centering
+				\centering
+				\includegraphics[scale=0.4]{files/Chapter4/1Dv2Dphi.png}
+				\caption{Comparison of the angle $\phi$ (best fit for 2D Beam) mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
+				\label{fig:phi}}}
+	\end{figure}
+	\FloatBarrier
+
+	These figures are examples that show how similar the mode shapes of the two models are.
+This specific example is for $\alpha = 4800$, which represents a typical beam.
+The authors of \cite{LVV09} obtained similar results for $\alpha=300$, which represents a short and thick beam.
+
+	\textbf{Remark:} Note that the overall shape is important.
+This is because any multiple of a eigenvector is still an eigenvector.
+The mode shapes were specifically scaled to obtain figures \ref{fig:w} and \ref{fig:phi}.
+
+	\subsection{Comparing the eigenvalues}
+	Using this method of comparing the mode shapes, the eigenvalues can now be matched up and compared. In the tables, Timo refers to the Timoshenko beam and 2D refers to the two-dimensional beam.
+
+	\subsubsection{Some results from [LVV09]}
+	The following table contains results from \cite{LVV09} verbatim to 3 significant digits, as well as the replicated results to 5 significant digits.
+
+	\begin{table}[!ht]
+		\centering
+		\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
+		\begin{tabular}{|c|c|c||c|c|c|}
+			\hline
+			\multicolumn{3}{|c||}{Results from [LVV09]} & \multicolumn{3}{c|}{Dissertation} \\ \hline \hline
+			~ & 2D & Timo & ~ & 2D & Timo  \\ \hline
+			1 & 0.0317 & 0.0316 & 1 & 0.031713 & 0.031639  \\ 
+			2 & 1.14 & 1.14  & 2 & 1.1413 & 1.1365  \\ 
+			3 & 7.72 & - & 3 & 7.7161 & - \\ 
+			4 & 7.92 & 7.86 &  4 & 7.918 & 7.8617    \\ 
+			5 & 26.2 & 25.9 & 5 & 26.148 & 25.869   \\ 
+			6 & 60.8 & 59.9 & 6 & 60.816 & 59.946  \\ 
+			7 & 69.3 & - & 7 & 69.344 & -  \\ 
+			8 & 115 & 113 &  8 & 115.28 & 113.23   \\ 
+			9 & 192 & 188 &  9 & 191.57 & 187.55   \\ 
+			10 & 192 & - & 10 & 192.03 & -  \\ 
+			11 & 291 & 284 & 11 & 290.76 & 283.81   \\ \hline
+		\end{tabular}\label{Results_LVV09}
+	\end{table}
+
+	\begin{comment}
+	\begin{table}[!ht]
+		\centering
+		\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
+		\begin{tabular}{|c|c|c|c||c|c|c|c|}
+			\hline
+			\multicolumn{4}{|c||}{Results from [LVV09]} & \multicolumn{4}{c|}{Dissertation} \\ \hline \hline
+			~ & 2D & Timo & RE & ~ & 2D & Timo & RE  \\ \hline
+			1 & 0.0317 & 0.0316 & 0.00315 & 1 & 0.031713 & 0.031639 & 0.0023407  \\ 
+			2 & 1.14 & 1.14 & $0^*$ & 2 & 1.1413 & 1.1365 &  0.0042050 \\ 
+			3 & 7.72 & - & ~ & 3 & 7.7161 & - &   \\ 
+			4 & 7.92 & 7.86 & 0.00758 & 4 & 7.918 & 7.8617 & 0.0071116    \\ 
+			5 & 26.2 & 25.9 & 0.0115 & 5 & 26.148 & 25.869 & 0.010669  \\ 
+			6 & 60.8 & 59.9 & 0.0148 & 6 & 60.816 & 59.946 & 0.014303  \\ 
+			7 & 69.3 & - & ~ & 7 & 69.344 & - &    \\ 
+			8 & 115 & 113 & 0.0174 & 8 & 115.28 & 113.23 &  0.017787  \\ 
+			9 & 192 & 188 & 0.0208 & 9 & 191.57 & 187.55 &  0.020999  \\ 
+			10 & 192 & - &  & 10 & 192.03 & - &   \\ 
+			11 & 291 & 284 & 0.0241 & 11 & 290.76 & 283.81 &  0.023899  \\ \hline
+		\end{tabular}\label{Results_LVV09}
+	\end{table}
+	\end{comment}
+
+	This table shows that the results obtained in this dissertation are very similar to the results obtained in \cite{LVV09}. This is for a specific case where $\alpha = 1200$.
+
+	In the following table, the eigenvalues for different values of $\alpha$ are compared.
+
+	\begin{table}[h!]
+		\scalebox{.8}{
+		\makebox[\textwidth]{
+		\caption{Eigenvalues of a Timoshenko cantilever beam vs the eigenvalues of a cantilever two-dimensional elastic body. *RE is the relative error.}
+		\begin{tabular}{|cccc||cccc||cccc||cccc|}
+			\hline
+			\multicolumn{16}{|c|}{Comparison of Eigenvalues} \\
+			\hline\hline
+			\multicolumn{4}{|c||}{ $h = 1/5$ or $\alpha = 300$}       & \multicolumn{4}{c||}{$h =1/10$ or $\alpha = 1200$}      & \multicolumn{4}{c||}{$h = 1/20$ or $\alpha = 4800$}      & \multicolumn{4}{c|}{$h = 1/30$ or $\alpha = 10800$} \\
+			\hline
+			{i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} \\
+			\hline
+			{1}&0.12151&1&0.12092&1&0.031713&1&0.031639&1&0.008013&1&0.008004&1&0.003568&1&0.003565\\
+			{2}&3.5460&2&3.5071&2&1.1413&2     & 1.1365 & 2     & 0.30756 & 2     & 0.30705 & 2     & 0.13869 & 2     & 0.13855 \\
+			\cellcolor{lightgray}{3} & \cellcolor{lightgray}{7.7311} &       & {-} & \cellcolor{lightgray}{3}     & \cellcolor{lightgray}{7.7161} &       & {-} & 3     & 2.3273 & 3     & 2.3213 & 3     & 1.0698 & 3     & 1.0683 \\
+			{4} & 20.225 & 3     & 19.869 & 4     & 7.9180 & 3     & 7.8617 & \cellcolor{lightgray}{4}     & \cellcolor{lightgray}{7.7077} &       & {-} & 4     & 4.0140 & 4     & 4.0058 \\
+			{5} & 56.109 & 4     & 54.766 & 5     & 26.148 & 4     & 25.869 & 5     & 8.5086 & 4     & 8.4762 & \cellcolor{lightgray}{5}     & \cellcolor{lightgray}{7.7047} &       & {-} \\
+			\cellcolor{lightgray}{6} & \cellcolor{lightgray}{69.164} &       & {-} & 6     & 60.816 & 5     & 59.946 & 6     & 21.911 & 5     & 21.794 & 6     & 10.655 & 5     & 10.625 \\
+			{7} & 114.03 & 5     & 110.75 & \cellcolor{lightgray}{7}     & \cellcolor{lightgray}{69.344} &       & {-} & 7     & 45.711 & 6     & 45.390 & 7     & 22.975 & 6     & 22.890 \\
+			{8} & {189.17} &  6     & {186.50} & 8     & 115.28 & 6     & 113.23 & \cellcolor{lightgray}{8}     & \cellcolor{lightgray}{69.344} &       & {-} & 8     & 43.113 & 7     & 42.909 \\
+			\cellcolor{lightgray}{9} & \cellcolor{lightgray}{192.61} &      &  & {9}     & {191.57} &   7  & {187.55} & 9     & 82.887 & 7     & 82.154 & \cellcolor{lightgray}{9}     & \cellcolor{lightgray}{69.331} &       & {-} \\
+			{10} & 285.85 & 7     & 277.64 & \cellcolor{lightgray}{10}    & \cellcolor{lightgray}{192.03} &      & {-} & 10    & 136.03 & 8     & 134.58 & 10    & 73.230 & 8     & 72.803 \\
+			{11} & 328.40 & 8     & 330.29 & 11    & 290.76 & 8     & 283.81 & \cellcolor{lightgray}{11}    & \cellcolor{lightgray}{192.48} &       & {-} & 11    & 115.41 & 9     & 114.61 \\
+			\cellcolor{lightgray}{12} & \cellcolor{lightgray}{357.08} &       & {-} & \cellcolor{lightgray}{12}    & \cellcolor{lightgray}{374.45} &       & {-} & 12    & 207.29 & 9     & 204.69 & 12    & 171.61 & 10    & 170.20 \\
+			{13} & 397.33 & 9     & 394.02 & 13    & 413.20 & 9     & 402.27 & 13    & 298.38 & 10    & 294.10 & \cellcolor{lightgray}{13}    & \cellcolor{lightgray}{192.52} &       & {-} \\
+			{14} & 442.00   & 10    & 439.52 & 14    & 558.67 & 10    & 542.65 & \cellcolor{lightgray}{14}    & \cellcolor{lightgray}{376.83} &       & {-} & 14    & 243.56 & 11    & 241.26 \\
+			\cellcolor{lightgray}{15} & \cellcolor{lightgray}{533.71} &       & {-} & \cellcolor{lightgray}{15}    & \cellcolor{lightgray}{614.11} &       & {-} & 15    & 410.63 & 11    & 404.01 & 15    & 332.83 & 12    & 329.28 \\
+			{16} & 538.97 & 11    & 541.55 & 16    & 726.26 & 11    & 704.15 & 16    & 545.03 & 12    & 535.32 & \cellcolor{lightgray}{16}    & \cellcolor{lightgray}{377.16} &       & {-} \\
+			\cellcolor{lightgray}{17} & \cellcolor{lightgray}{596.06} &       & {-} & \cellcolor{lightgray}{17}    & \cellcolor{lightgray}{906.28} &       & {-} & \cellcolor{lightgray}{17}    & \cellcolor{lightgray}{621.95} &       & {-} & 17    & 440.77 & 13    & 435.51 \\
+			{18} & 602.77 & 12    & 596.09 & 18    & 913.69 & 12    & 884.92 & 18    & 702.30 & 13    & 688.64 & 18    & 568.51 & 14    & 561.04 \\
+			\cellcolor{lightgray}{19} & \cellcolor{lightgray}{657.87} &       & {-} & 19    & 1113.7 & 13    & 1080.1 & 19    & 882.95 & 14    & 864.40 & \cellcolor{lightgray}{19}    & \cellcolor{lightgray}{623.05} &       & {-} \\
+			{20} & 717.37 & 13    & 731.74 & \cellcolor{lightgray}{20}    & \cellcolor{lightgray}{1218.0}  &       & {-} & \cellcolor{lightgray}{20}    & \cellcolor{lightgray}{927.18} &       & {-} & 20    & 717.04 & 15    & 706.74 \\
+			\hline
+			\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{3.1718\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{3.1486\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{2.1018\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{1.4361\%} \\
+			\hline
+		\end{tabular}%
+		\label{tab:Timo}%
+	}
+	}
+	\end{table}%
+	\FloatBarrier
+
+	This table shows that the eigenvalues of the Timoshenko model and the two-dimensional model compare very well.
+The non-beam type eigenvalues are highlighted in grey.
+For a short thick beam ($\alpha = 300$), the maximum relative error for the first 20 two-dimensional eigenvalues is just over $3\%$, while for a long thin beam ($\alpha = 10800$), the maximum relative error is just over $1\%$.
+This shows that as the beam becomes longer and thinner, the Timoshenko beam is better approximation of the two-dimensional beam.
+But overall the Timoshenko beam compares very well.
+
+	This table also shows that as the beam gets more narrow, there are less non-beam type eigenvalues within the first few eigenvalues.This would also indicate that the Timoshenko beam would be a better approximation of the two-dimensional beam as the beam gets more narrow since the two-dimensional model behaves `more like a beam'.
 

### 2024-03-17 article.tex
small changes

@@
 		\subsubsection*{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
-			Suppose $\ell$ represents some notable dimension (e.g.the length) of the elastic body and $G$ the shear modulus of elasticity.
-
-			Set \[\tau = \frac{t}{t_0},\quad \xi_i = \frac{x_i}{\ell},\quad {u}^*(\xi,\tau) = \frac{1}{\ell}{u}(x,t), \quad Q^{*} = \ell G \kappa^2 Q, \text{and} \ \,\,\, \sigma_{ij}^*(\xi,\tau) = \frac{1}{G\kappa^2}\sigma_{ij}(x,t),\]\label{sym:t}\label{sym:G}\label{sym:tau}\label{sym:xi}\label{sym:Qstar}\label{sym:sigmaijstar}\label{sym:ell}\label{sym:kappa2}
-
-			where $\kappa^2$ is a dimensionless constant and $t_0$ must be specified. Choose \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}} \textrm{ and } \gamma= \frac{G\kappa^2}{E}.\]
-
-			Substitution into \eqref{eq:3D_Model:EM} and yields
-			\begin{eqnarray*}
-				\partial_{\tau} u^{*} = \textrm{div}T^* + Q^* \textrm{ where } T^* = \sigma_{i,j}^*(\xi,\tau).
-			\end{eqnarray*}
-
-			The dimensionless forms of \eqref{eq:3D_Model:HL} and \eqref{eq:3D_Model:CE} are
-			\begin{eqnarray*}
-				\mathcal{E} = \frac{G \kappa^2}{E} \left[ (1+\nu)T^* - \nu \textrm{Tr}(T^*)I \right],
-			\end{eqnarray*}\label{sym:I}
-
-			and
-			\begin{eqnarray*}
-				T^* = \frac{E}{G \kappa^2} \left[\left( \frac{1}{1+\nu} \right)\mathcal{E} + \frac{\nu}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \right].
-			\end{eqnarray*}
-
-			Using the dimensionless constant $\gamma$,
-			\begin{eqnarray}
-				\mathcal{E} = \gamma(1+\nu)T^* - \gamma\nu \textrm{Tr}(T^*)I \label{DM_H_E}
-			\end{eqnarray}
-			and
-			\begin{eqnarray}
-				T^* = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I. \label{DM_H_T}
-			\end{eqnarray}
-
-			\textbf{Remark} The constants introduced are the same as those in \cite{LVV09}.
-			These dimsensionless constants allow for the comparison of the higher dimensional models to the Timoshenko beam model.
-
-			The original notation is retained for convenience.
+			Let $\ell$ represent a significant dimension (e.g., length) of an elastic body and $G$ the shear modulus. Define dimensionless variables and normalized functions as
+			\[\tau = \frac{t}{t_0},\ \xi_i = \frac{x_i}{\ell},\ u^*(\xi,\tau) = \frac{u(x,t)}{\ell},\ Q^{*} = \ell G \kappa^2 Q,\ \sigma_{ij}^*(\xi,\tau) = \frac{\sigma_{ij}(x,t)}{G\kappa^2},\]
+			where $\kappa^2$ is a dimensionless constant and $\displaystyle t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}$. Let $\displaystyle \gamma= \frac{G\kappa^2}{E}$.
+
+			Substituting these into the equation of motion \eqref{eq:3D_Model:EM} gives
+			\[\partial_{\tau} u^{*} = \text{div}T^* + Q^*,\]
+			where $\displaystyle T^* = \sigma_{i,j}^*(\xi,\tau)$. The dimensionless forms for \eqref{eq:3D_Model:HL} and \eqref{eq:3D_Model:CE} are
+			\[\mathcal{E} = \gamma(1+\nu)T^* - \gamma\nu \text{Tr}(T^*)I,\]
+			\[T^* = \frac{\mathcal{E}}{\gamma(1+\nu)} + \frac{\nu\text{Tr}(\mathcal{E})I}{\gamma(1+\nu)(1-2\nu)}.\]
+
+			The choice of dimensionless constants follow \cite{LVV09} and allows for a comparison between this model and the Timoshenko beam model.
 
@@
 
-			Set \[\tau = \frac{t}{t_0}, \,\, \xi = \frac{x}{\ell}, \,\, w^*(\xi,\tau) = \frac{w(x,t)}{\ell} \ \text{ and } \ \phi^*(\xi, \tau) = \phi(x,t).\]
-
-			The dimensionless forms of the shear force, moment and external force density are \[ V^{*}(\xi,\tau) = \frac{V(x,t)}{AG\kappa^2}, \quad M^{*}(\xi,\tau) = \frac{M(x,t)}{A G\kappa^2 \ell} \,\,\, \ \text{and} \ \,\,\, Q^*(\xi,\tau) = \frac{Q(x,t)\ell}{A G\kappa^2}.\]
-
-			Choose $t_0$ the same as the three-dimensional model, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]
-
-			As in \cite{LVV09} we use the dimensionless constants
-			\begin{equation*}
-				\alpha = \frac{A \ell^2}{I} \,\,\, \text{and} \,\,\, \beta
-				=\frac{AG\kappa^2 \ell^2}{EI}.
-			\end{equation*}\label{sym:alphabeta}
-
-			Interestingly, it turns out that
-			\begin{eqnarray*}
-				\frac{\beta}{\alpha} & = & \gamma
-			\end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in the three-dimensional case.\\
+			Set \[\tau = \frac{t}{t_0},\ \xi = \frac{x}{\ell},\ w^*(\xi,\tau) = \frac{w(x,t)}{\ell},\ \phi^*(\xi, \tau) = \phi(x,t).\]
+
+			Dimensionless shear force, moment, and external force density are \[V^{*} = \frac{V}{AG\kappa^2},\ M^{*} = \frac{M}{A G\kappa^2 \ell},\ Q^* = \frac{Q\ell}{A G\kappa^2}.\]
+
+			Use $\displaystyle t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}$ as before.
+
+			Using the dimensionless constants from \cite{LVV09}, 
+			\[\alpha = \frac{A \ell^2}{I},\ \beta =\frac{AG\kappa^2 \ell^2}{EI},\]
+			with \[\frac{\beta}{\alpha} = \gamma,\] where $\gamma$ is the dimensionless parameter from the three-dimensional model.
 

### 2024-03-21 article.tex
article v2
Article draft final

@@
 
-\author{Rudi du Toit\corref{cor1}}
+\author{R. du Toit\corref{cor1}}
 \ead{u15000258@tuks.co.za}
 \cortext[cor1]{Corresponding author}
-\author{Prof N.F.J. van Rensburg}
+\author{N.F.J. van Rensburg}
 \address{Department of Mathematics, University of Pretoria, Pretoria, South Africa}
@@
 \begin{keyword}
-	Beams \sep Cantilever Beams \sep Two-Dimensional Models \sep Three-Dimensional Models \sep Vibration Analysis \sep Modal Analysis \sep Finite Element Method
+	Beam \sep Cantilever Beam \sep Two-Dimensional Model \sep Three-Dimensional Model \sep Vibration Analysis \sep Modal Analysis \sep Finite Element Method
 \end{keyword}
@@
 
-\section{Linear mathematical models}
+The layout of the paper is as follows:
+\begin{itemize}
+\item Section \ref{sec:LinearMathematicalModels} introduces the linear mathematical models for the three-dimensional, two-dimensional, and Timoshenko beam models.
+\item Section \ref{sec:ModalAnalysis} covers modal analysis, compares linear models, and touches on the models' well-posedness.
+\item Section \ref{ssec:2D_Model:FEM} outlines the variational problem for the two-dimensional model and applies the Finite Element Method to derive an eigenvalue problem.
+\item Section \ref{ssec:3D_Model:FEM} outlines the variational problem for the three-dimensional model and applies the Finite Element Method to derive an eigenvalue problem.
+\item Section \ref{sec:validity-of-a-cantilever-timoshenko-beam} examines the validity of the Timoshenko model for a cantilever beam, drawing on results from \cite{LVV09}.
+\item Section \ref{sec:validity-of-a-2d-beam} expands on \cite{LVV09} to assess the validity of a two-dimensional model for a cantilever beam.
+\item Section \ref{sec:conclusion} concludes the paper.
+\end{itemize}
+
+\section{Linear mathematical models} \label{sec:LinearMathematicalModels}
 	\subsection{Three-dimensional theory}
-		Consider a vector valued displacement function $u \in \Omega \subset R^3$.
+		Consider a vector valued displacement function $u$ defined on $\Omega \subset R^3$.
 
@@
 		\subsubsection*{Constitutive Equation}
-			\textcolor{red}{************ VOORSTEL om the verkort ************}
-
 			For an isotropic material, Hooke's law can be written in terms of Young's modulus $E$ and Poisson's ratio $\nu$.
@@
 
-			\textcolor{red}{************ VOORSTEL ************}
-
-			For an isotropic material, Hooke's law can be written in terms of Young's modulus $E$ and Poisson's ratio $\nu$ as follows.
-
-			\textbf{Hooke's law}
-			\begin{eqnarray}
-				\mathcal{E} = \left( \frac{1+\nu}{E} \right)T - \frac{\nu}{E}\textrm{Tr}(T)I,  \label{eq:3D_Model:HL}
-			\end{eqnarray} The components of the strain tensor $\mathcal{E}$ are defined as
-			\begin{eqnarray}
-				\varepsilon_{ij} = \frac{1}{2}\left( \frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} \right). \label{eq:3D_Model:Strain}
-			\end{eqnarray}\label{sym:varepsilonij}
-
-			If the principal stresses $\sigma_i$ are all non-zero, then Hooke's law can be written in an alternative form.
-
-			\textbf{Hooke's law in the alternative form}
-			\begin{eqnarray}
-				T = \left( \frac{E}{1+\nu} \right)\mathcal{E} + \frac{\nu E}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \label{eq:3D_Model:CE}.
-			\end{eqnarray}
-			With $\textrm{Tr}(\mathcal{E}) = \epsilon_{11} + \epsilon_{12} + \epsilon_{13}$ is the trace of the strain operator $\mathcal{E}$.
-
-			In this form, Hooke's law is the constitutive equation for the three-dimensional model.
-
-		\subsubsection*{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
 			Let $\ell$ represent a significant dimension (e.g., length) of an elastic body and $G$ the shear modulus. Define dimensionless variables and normalized functions as
@@
 
-		\subsubsection*{Equations of motion in dimensionless form}\label{sssec:3D_Model:EquationOfMotionDimensionless}
+		\textbf{Equations of motion in dimensionless form}
 			\begin{eqnarray}
@@
 
-		\subsubsection*{Constitutive equations in dimensionless form}\label{sssec:3D_Model:ConstitutiveEquationsDimensionless}
+		\textbf{Constitutive equations in dimensionless form}
 			\begin{eqnarray}
@@
 			\end{eqnarray}
-
-		Divide the boundary of $\Omega$ into two distinct parts, referred to as $\Sigma$ and $\Gamma$.
-The following will be considered a model problem for a three-dimensional elastic body (also for the two-dimensional elastic body).
-		\begin{enumerate}
-			\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D}, and Hooke's law is satisfied in $\Omega$;
-			\item[] The displacement $u = u_\Sigma$ is specified on
-				$\Sigma$; The traction $Tn = t_\Gamma$ is specified on
-				$\Gamma$.
-		\end{enumerate} \label{sym:n}\label{sym:SigmaGamma}
 
@@
 			Find a vector valued function $u$, satisfying equations
-			\eqref{eq:3D_Model:EM-D} to \eqref{eq:3D_Model:CE-D} and the following boundary
-			conditions:
-
-			Boundary Conditions:
-			\begin{eqnarray*}
-				u & = & 0 \quad \textrm{ on } \Sigma\\
-				Tn & = & 0 \quad \textrm{ on } \Gamma
-			\end{eqnarray*}
-
-			This will be referred to as \textbf{Problem 3D}.
-
-		\subsection*{Variational form}\label{ssec:3D_Model:VariationalForm}
-			Define the bilinear forms
-			\begin{eqnarray}
-				b(u,\phi) = \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
-				\textrm{Tr}(\Phi) ~dV \label{eq:3D_Model:Bilinear}
-			\end{eqnarray}\label{sym:b}
-			and
-			\begin{eqnarray}
-				c(u,\phi) = \int_\Omega~ (\partial^2_t u) \cdot \phi~dV \label{eq:3D_Model:Bilinear_c}
-			\end{eqnarray}
-			with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.
-
-			Also define the integral
-			\begin{eqnarray}
-				(f,g) &=& \int_{\Omega} f\cdot g \ dV \label{eq:3D_Model:Bilinear_int}
-			\end{eqnarray}
-
-			Define the following set of test functions $T(\Omega)$ for Problem 3D:
-			\begin{eqnarray*}
-				T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}
-			\end{eqnarray*}\label{sym:TOmega}
-
-			Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and
-			\begin{align}
-				c(u,\phi) = -b(u,\phi) + (Q,\phi), \label{eq:3D_Model:Problem3D1VEq}
-			\end{align}
-			for all $\phi \in T(\Omega)$
-
-			This will be referred to as \textbf{Problem 3DV}.
+			\eqref{eq:3D_Model:EM-D} to \eqref{eq:3D_Model:CE-D} and the boundary
+			conditions $\displaystyle u = 0$ on part of the boundary and $\displaystyle Tn = 0$ on the rest of the boundary. This will be referred to as \textbf{Problem 3D}.
 
@@
 
-			Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:
-
-			Boundary Conditions:
-			\begin{eqnarray*}
-				u & = & 0 \quad \textrm{ on } \Sigma,\\
-				Tn & = & 0 \quad \textrm{ on } \Gamma.
-			\end{eqnarray*} with $n$ the outward unit normal.
-
+			Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions $u = 0$ on part of the boundary and $Tn = 0$ on the rest of the boundary.
 This will be referred to as \textbf{Problem 2D}.
-
-		\subsubsection*{Variational form}\label{ssec:2D_Model:VariationalForm}
-			Define the bilinear forms
-			\begin{eqnarray}
-				b(u,\phi) = \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
-				\textrm{Tr}(\Phi) ~dA \label{eq:2D_Model:Bilinear}
-			\end{eqnarray}
-			and
-			\begin{eqnarray}
-				c(u,\phi) = \int_\Omega~ (\partial^2_t u) \cdot \phi~dA \label{eq:2D_Model:Bilinear_c}
-			\end{eqnarray}
-			with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.
-			Also define the integral
-			\begin{eqnarray}
-				(f,g) &=& \int_{\Omega} f\cdot g \ dA \label{eq:2D_Model:Bilinear_int}
-			\end{eqnarray}
-
-			\subsubsection*{Test functions for Problem 2D}\label{sssec:2D_Model:TestFunctions2D1}
-			Define the following set of test functions $T(\Omega)$ for Problem 2D:
-			\begin{eqnarray*}
-				T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}. 
-			\end{eqnarray*}\label{sym:baromega}
-
-			Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
-			\begin{align}
-				c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{eq:2D_Model:Problem2D1VEq}
-			\end{align}
-			for all $\phi \in T(\Omega)$. This will be referred to as \textbf{Problem 2DV}.
 
@@
 
-		\subsection{Models and variational forms}
+		\textbf{Models and variational forms}
 			\subsubsection*{Bilinear forms and integral}
@@
 					&=& \int_{0}^1 fg \label{eq:1D_Model:Bilinear_int}
-				\end{eqnarray} for all $f,g \in L^2(0,1).$\\
-
-				\textbf{Remark}\\
+				\end{eqnarray} for all $f,g \in L^2(0,1).$
+
+				\textbf{Remark}
 				$L^2(a,b)$ is the space of all square integrable functions on the interval $(a,b)$.
@@
 
-				{Boundary Conditions}\\
+				{Boundary Conditions}
 				\begin{eqnarray*}
@@
 
-\section{Modal analysis and comparison of linear models}
+\section{Modal analysis and comparison of linear models}\label{sec:ModalAnalysis}
 
@@
 
-\section{Cantilever two-dimensional model}\label{ssec:2D_Model:FEM}
+\section{Cantilever two-dimensional model in variational form}\label{ssec:2D_Model:FEM}
 Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$.
@@
 	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
-\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$.
+\end{eqnarray*} 
+$\partial \Omega$ denotes the boundary of the body.
+$\Sigma$ is the part of the boundary where $x_1 = 0$ and here the boundary condition is $u = 0$.
+$\Gamma$ is the remainder of the boundary where $Tn = 0$.
 
@@
 
- Using the reference configuration, the variational problem Problem 2DV can be rewritten into a model specific form.
-
 \subsubsection*{Problem 2DV}\label{sssec:2D_Model:Problem2D1VChp5}
+The bilinear forms and integral function is defined by
+\begin{eqnarray}
+	b(u,\phi) & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
+	\textrm{Tr}(\Phi) ~dA, \label{eq:2D_Model:BilinearChp5}\\
+	c(\partial_t^2 u,\phi) & = & \int_\Omega~ (\partial^2_t u) \cdot \phi~dA, \label{eq:2D_Model:Bilinear_cChp5}\\
+	(f,g) &=& \int_{\Omega} f\cdot g \ dA, \label{eq:2D_Model:Bilinear_intChp5}
+\end{eqnarray}
+with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.
+
+Define the test function space 
+\begin{eqnarray*}
+	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
+\end{eqnarray*}
+
 Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
@@
 \end{align}
-for all $\phi \in T(\Omega)$. With the test function space 
-\begin{eqnarray*}
-	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
-\end{eqnarray*}
-
-The bilinear forms and integral function is defined by
-\begin{eqnarray}
-	b(u,\phi) & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
-	\textrm{Tr}(\Phi) ~dA, \label{eq:2D_Model:BilinearChp5}\\
-	c(\partial_t^2 u,\phi) & = & \int_\Omega~ (\partial^2_t u) \cdot \phi~dA, \label{eq:2D_Model:Bilinear_cChp5}\\
-	(f,g) &=& \int_{\Omega} f\cdot g \ dA, \label{eq:2D_Model:Bilinear_intChp5}
-\end{eqnarray}
-with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.
-
-Using the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten into a model specific form.
-
-\subsubsection*{Constitutive equations:}
-\begin{eqnarray}
-	\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_1 u_1 + \nu \partial_2 u_2) \label{CE1} \\
-	\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_2 u_2 + \nu \partial_1 u_1) \label{CE2} \\
-	\sigma_{12} & = & \frac{1}{2\gamma(1+\nu)}(\partial_1 u_2 + \partial_2 u_1) \label{CE3}
-\end{eqnarray}
-
-\subsubsection*{Bilinear form:}
-\begin{align}
-	b(u,\phi) & = & \frac{1}{\gamma(1-\nu^2)}\int_{\Omega} (\partial_1 u_1 \partial_1 \phi_1 + \partial_2 u_2 \partial _2 \phi_2 + \nu\partial_1 u_1 \partial_2\phi_2 + \nu \partial_2 u_2 \partial_1 \phi_1 ) \ dA \nonumber\\
-	& + & \frac{1}{2\gamma(1+\nu)}\int_{\Omega} (\partial_1 u_2 \partial_1 \phi_2 + \partial_1 u_2 \partial_2 \phi_1 + \partial_2 u_1 \partial_1\phi_2 + \partial_2 u_1 \partial_2\phi_1) \ dA.
-\end{align}
+for all $\phi \in T(\Omega)$.
 
@@
 
-\section{Cantilever three-dimensional model} \label{ssec:3D_Model:FEM}
+\section{Cantilever three-dimensional model in variational form} \label{ssec:3D_Model:FEM}
 	Let $\{e_1,e_2,e_3\}$ be a right-handed orthonormal basis for $R^3$.
@@
 	\end{eqnarray*}
-	Let $\partial \Omega$ denote the boundary of the body.
+	$\partial \Omega$ denotes the boundary of the body.
+$\Sigma$ is the part of the boundary where $x_1 = 0$ and here the boundary condition is $u = 0$.
+$\Gamma$ is the remainder of the boundary where $Tn = 0$.
 
@@
 
-	This general variational form Problem 3DV can now be rewritten as in a model specific form using the reference configuration.
-
 	\subsubsection*{Problem 3DV}
+	The bilinear forms and integral function is defined by
+	\begin{eqnarray}
+		b(u,\phi) &=& \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
+		\textrm{Tr}(\Phi) ~dV,\\
+		c(u,\phi) &=& \int_\Omega~ (\partial^2_t u) \cdot \phi~dV, \\
+		(f,g) &=& \int_{\Omega} f\cdot g \ dV, \\
+	\end{eqnarray}
+	with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.\\
+
+	The test function space is defined as
+	\begin{eqnarray*}
+		T(\Omega) & = & \left\{ \phi \in C(\Omega) \ | \ \phi = 0 \ \textrm{ on } \ \Sigma \right\}.
+	\end{eqnarray*}
+
 	Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
@@
 
-	With the test function space
-	\begin{eqnarray*}
-		T(\Omega) & = & \left\{ \phi \in C(\Omega) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
-	\end{eqnarray*}
-
-	The bilinear forms and integral function are defined by
-	\begin{eqnarray}
-		b(u,\phi) &=& \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
-		\textrm{Tr}(\Phi) ~dV,\\
-		c(u,\phi) &=& \int_\Omega~ (\partial^2_t u) \cdot \phi~dV, \\
-		(f,g) &=& \int_{\Omega} f\cdot g \ dV, \\
-	\end{eqnarray}
-	with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.\\
-
-	Using the definition of the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten in the following model specific forms: 
-	\subsubsection*{Constitutive equations}
-	\begin{eqnarray*}
-		\sigma_{11} & = &  \frac{1}{\gamma(1+\nu)}\partial_1 u_1 + \frac{\nu}{\gamma (1+\nu)(1-2\nu)}(\partial_1 u_1 +  \partial_2 u_2 + \partial_3 u_3)\label{3DB_3}\\
-		\sigma_{22} & = &  \frac{1}{\gamma(1+\nu)}\partial_2 u_2 + \frac{\nu}{\gamma (1+\nu)(1-2\nu)}(\partial_1 u_1 +  \partial_2 u_2 + \partial_3 u_3)\label{3DB_4}\\
-		\sigma_{33} & = &  \frac{1}{\gamma(1+\nu)}\partial_3 u_3 + \frac{\nu}{\gamma (1+\nu)(1-2\nu)}(\partial_1 u_1 +  \partial_2 u_2 + \partial_3 u_3)\label{3DB_5}\\
-		\sigma_{23} & = &  \frac{1}{2\gamma(1+\nu)}(\partial_3 u_2 + \partial_2 u_3)\label{3DB_6}\\
-		\sigma_{31} & = &  \frac{1}{2\gamma(1+\nu)}(\partial_3 u_1 + \partial_1 u_3)\label{3DB_7}\\
-		\sigma_{12} & = &  \frac{1}{2\gamma(1+\nu)}(\partial_2 u_1 + \partial_1 u_2)\label{3DB_8}
-	\end{eqnarray*}
-
-	\subsubsection*{Bilinear Form}
-	\begin{align*}
-		b(u,\phi)  &=  \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
-		\textrm{Tr}(\Phi) ~dV \nonumber\\
-		&=  \int_{\Omega} \sigma_{11} \partial_1\phi_1 + \sigma_{12}\partial_1 \phi_2 + \sigma_{13}\partial_1 \phi_3 + \sigma_{21}\partial_2 \phi_1 + \sigma_{22}\partial_2\phi_2 + \sigma_{23}\partial_2 \phi_3 ~dV
-	\end{align*}
-
 	\subsection*{Galerkin approximation}
@@
 	\end{eqnarray*} for $i = 1,2,...,k$.
-$Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$.
+$Q^I$ is scalar vector obtained after interpolating the function $Q$ over the brickable grid $\Omega$.
 i.e.
@@
 
-\section{Validity of the model for a cantilever Timoshenko beam (CHAPTER 4 of dissertation)} \label{sec:validity-of-a-cantilever-timoshenko-beam}
-
-	In this section, the validity of the Timoshenko beam model is investigated.
-Specifically, the validity of a cantilever Timoshenko beam model, using a cantilever two-dimensional beam model as a reference.
-This follows what is done in the article \cite{LVV09}.
-This section discusses the results of the article, focussing on the numerical results.
-Some of the results are replicated with more significant digits, others are extended to be used in the rest of this chapter.
-
-	The article \cite{LVV09} is titled `Comparison of linear beam theories'.
-In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
-The authors start by presenting the models.
-These are the same as Problem T-2 and Problem 2D-1 that are defined in Chapter~1.
-The authors also look at the existence and uniqueness of solutions, which is covered in Chapter 2 of this dissertation.
-The authors then calculate and compare the eigenvalues and eigenfunctions, which will be discussed in this section.
-
-	\subsection{The models}
-	The cantilever Timoshenko beam model is defined in section \ref{ssec:1D_Model:ModelProblems}, and is referred to as Problem T-2.
-The cantilever two-dimensional beam model is defined in section \ref{ssec:2D_Model:ModelProblem}, and is referred to as Problem 2D-1.
-
+\section{Validity of the model for a cantilever Timoshenko beam} \label{sec:validity-of-a-cantilever-timoshenko-beam}
+
+	In this section, the validity of a cantilever Timoshenko beam model is investigated.
+This investigation is done in \cite{LVV09}, and is included here with more significant digits and some extended results.
+
+	Recall that the cantilever Timoshenko beam model is referred to as Problem T-2 and the two-dimensional cantilever beam model is referred to as Problem 2D as defined in Section \ref{sec:LinearMathematicalModels}.
 Figure \ref{fig:compare:1D+2D} shows the two beams side-by-side.
+
+	\FloatBarrier
 
@@
 					\end{center}
-					\subcaption{Timoshenko Cantilever Beam}
+					\subcaption{Timoshenko Cantilever Beam (Problem T-2)}
 				\end{minipage}
@@
 					\end{center}
-					\subcaption{Two-Dimensional Cantilever Beam}
+					\subcaption{Two-Dimensional Cantilever Beam (Problem 2D)}
 				\end{minipage}
@@
 
-	In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
-	introduced. The paramater is given here again for convenience:
+	\FloatBarrier
+
+	In introduction of the Timoshenko beam model, the parameter $\alpha$ is introduced. The paramater is given here again for convenience:
 	\begin{eqnarray*}
@@
 
-	\subsection{Calculating the eigenvalues and eigenvectors}
-	In section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided.
-And in section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.
-
-	For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method.
-In section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived.
-Specifically, section \ref{2dFEM_EP} derived the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.
-
-	\subsubsection{Problem 2D-1E}
-	Find a real number $\lambda$ and a vector $\bar{u} \in R^n$ such that
-	\begin{eqnarray}
-		K\bar{u} & = & M\lambda{\bar{u}},
-	\end{eqnarray} where $M$ and $K$ are the standard Finite Element Method matrices defined in section \ref{sec:FEM:2D}.
-
-	In this form, the eigenvalue problem is a system of ordinary differential equations, and can be solved using a numerical method.
-Computer programs like MATLAB provide functions that are able to solve this.
-
-	\subsubsection{Accuracy of the eigenvalues}
-	Solving \textbf{Problem 2D-1E} with a numerical method, requires a quick investigation into the rate of convergence so that the accuracy of the eigenvalues can be established.
-Chapter \ref{ch:finite-element-theory} provides the necessary theory on the existence of solutions as well as the proof of convergence of the Finite Element Method.
-
-	\begin{figure}[H]
-		\centering
-		\begin{adjustbox}{center}
-			\includegraphics[scale=0.7]{files/Chapter4/Convergence.png}
-		\end{adjustbox}
-		\caption{Rate of convergence of the first 20 eigenvalues.}
-		\label{fig:conv_2d_eig}
-	\end{figure}
-
-	Figure \ref{fig:conv_2d_eig} shows the rate of convergence of the first 20 eigenvalues of the two-dimensional beam. Each color represents a spesific eigenvalue.
-
-	The number of elements are chosen so that at least the first 10 eigenvalues are accurate to 5 significant digits.
-
-	\subsection{Comparing the mode shapes}
-	Recall from the introduction, that the investigation is focussed on beam-type problems.
-The two-dimensional model is for an eigenvalue problem and and not specific to beam-type applications, like the Timoshenko beam model.
-Therefore there are non-beam type modes that can be expected from the two-dimensional model.
-This is also be reflected in the eigenvalues of the two-dimensional model and therefore eigenvalues irrelevant to beam-type problems exits.
+	\subsection*{Calculating the eigenvalues and eigenvectors}
+	In the article \cite{VV02} a method for calculating the exact eigenvalues and eigenvectors of the Timoshenko beam is provided.
+For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method, with setup in Section \ref{ssec:2D_Model:FEM}.
+The eigenvalue accuracy depends on the number of elements in the FEM.
+In the two-dimensional model, elements are selected to ensure the first 10 eigenvalues have at least 5 significant digits of accuracy.
+
+	\subsection*{Comparing the mode shapes}
+	Following \cite{LVV09}, the mode shapes of the two-models are compared.
+In the section that follows, we'll show that there are mode shapes that are shared between the models and mode shapes that are unique to the two-dimensional model.
+The authors of \cite{LVV09} refer to the eigenvalues of the Timoshenko beam model as beam-type eigenvalues and the other eigenvalues are referred to as non-beam type eigenvalues.
 
@@
 
-	\subsubsection{Shapes relating to beam-type eigenvalues}
-	The following figures are examples of beam-type mode shapes for the displacement $w$.
+	\subsubsection*{Mode shapes relating to beam-type eigenvalues}
+
+	Figure \ref{fig:beam1} shows examples of beam-type mode shapes for the displacement $w$.
 
@@
 				\caption{Modal shapes of the displacement $w$ for the beam-type 2D body and the Timoshenko beam with $\alpha = 4800$ ($h = 1/20$).}
+				\label{fig:beam1}
 			}
@@
 
-	\subsubsection{Shapes relating to non-beam type eigenvalues}
-	The following figures are examples of non beam-type mode shapes for the displacement $w$. These mode shapes are not present in the cantilever Timoshenko beam model and are not beam related. 
+	\subsubsection*{Mode shapes relating to non beam-type eigenvalues}
+	Figure \ref{fig:beam2} shows examples of non beam-type mode shapes for the displacement $w$. These mode shapes are not present in the cantilever Timoshenko beam model and are not beam related. 
 	\begin{figure}[h!]
@@
 				\caption{Modal shapes of the displacement $w$ for the non-beam type 2D body with $h = 1/20$.}
+				\label{fig:beam2}
 			}
@@
 
-	\subsubsection{Shape of the cross-sections}
+	\subsubsection*{Shape of the cross-section}
 	The Timoshenko beam theory improve some one-dimensional beam theories such as the Euler-Bernoulli beam theory by also including the effect of shear.
@@
 
-	\subsubsection{Direct comparison of mode shapes}
+	\subsubsection*{Direct comparison of mode shapes}
 	Figure \ref{fig:w} directly compares a mode shape of the Timoshenko beam to a mode shape of the two-dimensional beam.
@@
 
-	\subsection{Comparing the eigenvalues}
+	\subsection*{Comparing the eigenvalues}
 	Using this method of comparing the mode shapes, the eigenvalues can now be matched up and compared. In the tables, Timo refers to the Timoshenko beam and 2D refers to the two-dimensional beam.
 
-	\subsubsection{Some results from [LVV09]}
+	\subsubsection*{Some results from \cite{LVV09}}
 	The following table contains results from \cite{LVV09} verbatim to 3 significant digits, as well as the replicated results to 5 significant digits.
@@
 		\centering
-		\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
+		\caption{Results from \cite{LVV09} and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
 		\begin{tabular}{|c|c|c||c|c|c|}
 			\hline
-			\multicolumn{3}{|c||}{Results from [LVV09]} & \multicolumn{3}{c|}{Dissertation} \\ \hline \hline
+			\multicolumn{3}{|c||}{Results from \cite{LVV09}} & \multicolumn{3}{c|}{Dissertation} \\ \hline \hline
 			~ & 2D & Timo & ~ & 2D & Timo  \\ \hline
@@
 		\centering
-		\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
+		\caption{Results from \cite{LVV09} and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
 		\begin{tabular}{|c|c|c|c||c|c|c|c|}
 			\hline
-			\multicolumn{4}{|c||}{Results from [LVV09]} & \multicolumn{4}{c|}{Dissertation} \\ \hline \hline
+			\multicolumn{4}{|c||}{Results from \cite{LVV09}} & \multicolumn{4}{c|}{Dissertation} \\ \hline \hline
 			~ & 2D & Timo & RE & ~ & 2D & Timo & RE  \\ \hline
@@
 
-\subsection{Calculating the eigenvalues and mode shapes}
-The eigenvalues and mode shapes of the two models are calculated using the computer program.
-The eigenvalues and mode shapes are then compared to determine the accuracy of the two-dimensional model for the cantilever beam.
+\subsection*{Calculating the eigenvalues and mode shapes}
  The accuracy of the eigenvalues depends on the number of elements employed in the finite element method.
@@
 
-\subsection{Comparing the mode shapes}
-Following \cite{LVV09}, the mode shapes of the two models are compared.
-As seen in \cite{LVV09}, the eigenvalues of the Timoshenko beam model (beam-type eigenvalues) are all present in the two-dimensional model.
+\subsection*{Comparing the mode shapes}
+Following the same method as \cite{LVV09}, the mode shapes of the two models are compared.
+As seen in \cite{LVV09} and Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the eigenvalues of the Timoshenko beam model (beam-type eigenvalues) are all present in the two-dimensional model.
 However not all the eigenvalues of the two-dimensional model are present in the Timoshenko beam model.
@@
 The same is observed for the three-dimensional model, as there are eigenvalues that are present in the three-dimensional model that are not present in the two-dimensional model.
-
 Therefore it is required to match the eigenvalues of the two models by comparing the mode shapes.
@@
 
-\subsection{Comparing the eigenvalues}
+\subsection*{Comparing the eigenvalues}
 For a realistic comparison of the models, it's crucial to carefully select parameters $h$ and $b$, representing the beam's height and width, respectively, noting that the two-dimensional model lacks the width parameter $b$.
@@
 
-\section{Conclusion}
-In this article, we explored the validity of a two-dimensional cantilever beam model by comparing it with a three-dimensional cantilever beam model.
-Using the Finite Element Method, we obtained the eigenvalues and eigenvectors for both models, aligning them through mode shape comparisons.
+\section{Conclusion} \label{sec:conclusion}
+In this article, we assessed the validity of both a cantilever Timoshenko beam model and a two-dimensional cantilever beam model by comparing their eigenvalues and mode shapes.
+Initially, we evaluated the Timoshenko beam model's validity by comparison with the two-dimensional model, as per the article \cite{LVV09}.
+Subsequently, the validity of the two-dimensional model was examined through comparison with a three-dimensional model.
 
@@
 
-Upon comparing the eigenvalues through mode shapes, our findings suggest that the two-dimensional beam model aligns well with the three-dimensional model for various beam shapes.
-However, the shape of the beam is pivotal to the comparison's accuracy.
+Firstly, the results of \cite{LVV09} is confirmed, showing that the Timsohenko canitlever beam model comapres very well to the two-dimensional model.
+The models compare very well if the beams are long and slender, and good for short and thick beams.
+Extending this to the three-dimensional model, we found that the two-dimensional model aligns well with the three-dimensional model for various beam shapes.
+Again we found that the shape of the beam is pivotal to the comparison's accuracy.
 The two-dimensional model shows the best correlation with thin and long three-dimensional beams and less so with short and thick beams.

### 2024-04-06 Appendix.tex
submition

@@
 \chapter*{MATLAB Code}
+The following are the main code used in this dissertation to obtain the eigenvalues and eigenvectors of the models.
+The code and the dissertation is also available on GitHub at \url{https://github.com/Propagandalf-7/masters}.
+
+The code is optimized for performance, and therefore the presentation of the code is not optimized for readability. The code is also not commented.
+
 \addcontentsline{toc}{section}{MATLAB Code}

### 2024-04-06 article_old.tex

--- 2024-03-16 article.tex
@@
-% \documentclass[11pt]{elsarticle}
-\input{preamble_article.tex}
+\documentclass[preprint,12pt]{elsarticle}
+
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{draftwatermark}
+\usepackage{tabularx} % Required for tables that stretch to text width
+\usepackage{booktabs} % For prettier tables
+\usepackage{ltablex}
+\usepackage{xcolor,cancel,bm,tikz}
+\usepackage{hyperref}
+\usepackage{mathtools}
+\usepackage{amsmath,amssymb,amsthm,amsfonts}
+\usepackage{enumitem}
+\usepackage{kantlipsum,graphicx}
+\usepackage{multicol,colortbl,multirow}
+\usepackage{pgfplots,booktabs,xfrac,floatrow}
+\usepackage{color}
+\usepackage{titlesec}
+\usepackage{natbib}
+
+\titleformat*{\section}{\Large\bfseries}
+\titleformat*{\subsection}{\normalsize\bfseries}
+\titleformat*{\subsubsection}{\normalsize\bfseries}
+\numberwithin{equation}{section}
+
+\usepackage{setspace}
+\setstretch{0.7} % Adjust this value as needed
+
+\setlength{\parindent}{0pt}
+
 \usepackage{geometry}
 \geometry{
-  left=1.3in,
-  right=1.4in,
-  top=1.4in,
-  bottom=1.4in,
-}
+  left=1in,
+  right=1in,
+  top=1in,
+  bottom=1in,
+}
+
+\SetWatermarkText{DRAFT}
+\SetWatermarkScale{1}
+
+\journal{Mathematical and Computer Modelling}
 
@@
 
-\title{Comparison of linear beam theories}
-
-\author{Rudi du Toit\corref{cor1}}
-\ead{u15000258@tuks.co.za}
-\cortext[cor1]{Corresponding author}
-\author{Prof N.F.J. van Rensburg}
-\address{Department of Mathematics, University of Pretoria, Pretoria, South Africa}
-
-\journal{Applied Mathematics and Computation}
+\title{Validity of a model for a cantilever two-dimensional beam}
+
+\author{Rudi du Toit}
+\address{University of Pretoria, Pretoria, South Africa}
 
 \begin{abstract}
-Beams, while commonly used in engineering, are complex three-dimensional objects.
-Simplified models are often used in vibration problems due to their reduced complexity and computational demand.
-However, the accuracy of these models in practical applications is not always certain.
-This article extends previous research to examine a two-dimensional cantilever beam model's validity using modal analysis and the Finite Element Method (FEM), comparing its solutions with those of a three-dimensional model.
-Our findings reveal that the beam's shape is a crucial factor in the model's validity for practical applications.
-For the appropriate beam shapes, the two-dimensional model is a valid approximation of the three-dimensional model.
+Your abstract here.
 \end{abstract}
@@
 \begin{keyword}
-	Beams \sep Cantilever Beams \sep Two-Dimensional Models \sep Three-Dimensional Models \sep Vibration Analysis \sep Modal Analysis \sep Finite Element Method
+Vibration \sep Cantilever \sep Beam \sep Three-Dimensional \sep Two-Dimensional
 \end{keyword}
@@
 \section{Introduction}
-In the article \cite{LVV09}, the authors investigate the validity of a cantilever Timoshenko beam model.
-Validity refers to how well the solution of the simplified model compare to a more complex higher dimensional model.
-The reference model in \cite{LVV09} is a two-dimensional cantilever beam model.
-
-In this article, we build upon \cite{LVV09} by further examining the validity of a two-dimensional model for a cantilever beam, using a three-dimensional model as the reference.
-We follow the same methodology as \cite{LVV09}, employing modal analysis and the Finite Element Method (FEM) to compare the two models.
-This extention is motivated by the authors of \cite{LVV09}.
-
-To start, the models are presented in a dimensionless variational form.
-We explain how the two-dimensional model is derived from the three-dimensional model as a special case of plane stress.
-The well-posedness of the two models is not proved in this article, but the necessary existence and uniqueness results from \cite{VV02} are mentioned.
-
-Next we introduce the concept of modal analysis with a general vibration problem.
-Through modal analysis, we derive a formal series solution for the vibration issue, which is a linear combination of the problem's eigenvectors and eigenvalues.
-This approach allows us to compare the solutions of the two models by focusing on a comparison of their eigenvectors and eigenvalues.
-
-We then apply the Finite Element Method (FEM) to the two models and obtain a formula for the models to numerically solve the eigenvalue problem.
-The article \cite{BV13} provides essential convergence results for the FEM in vibration problems.
-The textbook \cite{SF73} also offers insights into the convergence of eigenvalues and eigenfunctions in a vibration problem when using FEM.
-
-Following \cite{LVV09}, by considering the mode shapes, we can match up the eigenvalues and compare them.
-In the comparison, we consider different shapes of beams that are useful in practical applications.
-We find that the shape of the beam significantly influences the validity of the two-dimensional model.
-The results of the comparison are presented in the form of tables and graphs.
-
-\section{Linear mathematical models}
-	\subsection{Three-dimensional theory}
+Your introduction here.
+
+\section{Models}
+
+\subsection{Three-dimensional model}
 Consider a vector valued displacement function $u \in \Omega \subset R^3$.
@@
 \subsubsection*{Constitutive Equation}
-			\textcolor{red}{************ VOORSTEL om the verkort ************}
-
-			For an isotropic material, Hooke's law can be written in terms of Young's modulus $E$ and Poisson's ratio $\nu$.
-And if the principal stresses $\sigma_i$ are all non-zero, then Hooke's law can be written in the following form:
-			\begin{eqnarray}
-				T = \left( \frac{E}{1+\nu} \right)\mathcal{E} + \frac{\nu E}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \label{eq:3D_Model:CE}.
-			\end{eqnarray} Here $\mathcal{E}$ is the strain tensor and $T$ is the stress tensor.
-
-			In this form, Hooke's law is the constitutive equation for the three-dimensional model.
-
-			\textcolor{red}{************ VOORSTEL ************}
-
-			For an isotropic material, Hooke's law can be written in terms of Young's modulus $E$ and Poisson's ratio $\nu$ as follows.
-
-			\textbf{Hooke's law}
+For an isotropic material, Hooke's law can be written in terms of Young's modulus $E$ and Poisson's ratio $\nu$ as follows.\\
+
+\textit{Hooke's law}
 \begin{eqnarray}
@@
 
-			If the principal stresses $\sigma_i$ are all non-zero, then Hooke's law can be written in an alternative form.
-
-			\textbf{Hooke's law in the alternative form}
+If the principal stresses $\sigma_i$ are all non-zero, then Hooke's law can be written in an alternative form.\\
+
+\textit{Hooke's law in the alternative form}
 \begin{eqnarray}
@@
 \end{eqnarray}
-			With $\textrm{Tr}(\mathcal{E}) = \epsilon_{11} + \epsilon_{12} + \epsilon_{13}$ is the trace of the strain operator $\mathcal{E}$.
+With $\textrm{Tr}(\mathcal{E}) = \epsilon_{11} + \epsilon_{12} + \epsilon_{13}$ is the trace of the strain operator $\mathcal{E}$.\\
 
@@
 
-		\subsubsection*{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
-			Suppose $\ell$ represents some notable dimension (e.g.the length) of the elastic body and $G$ the shear modulus of elasticity.
+\subsection{Dimensionless form} \label{ssec:3D_Model:DimensionlessForm}
+Suppose $\ell$ represents some notable dimension (e.g.the length) of the elastic body 
+and $G$ the shear modulus of elasticity.\\
 
@@
 
-			\textbf{Remark} The constants introduced are the same as those in \cite{LVV09}.
-			These dimsensionless constants allow for the comparison of the higher dimensional models to the Timoshenko beam model.
+\textit{Remark} The constants introduced are the same as those in \cite{LVV09}.
+They simplify the equations and allow for comparisons to other models such as the Timoshenko beam model, although that is not covered in this article.\\
 
@@
 
-		Divide the boundary of $\Omega$ into two distinct parts, referred to as $\Sigma$ and $\Gamma$.
+\subsection{Model problems}\label{ssec:3D_Model:ModelProblems}
+Divide the boundary of $\Omega$ into two distinct parts, referred to as $\Sigma$ and $\Gamma$. The following will be considered a model problem for a three-dimensional elastic body. 
 The following will be considered a model problem for a three-dimensional elastic body (also for the two-dimensional elastic body).
 \begin{enumerate}
-			\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D}, and Hooke's law is satisfied in $\Omega$;
+	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} is satisfied in $\Omega$;
+	\item[] Hooke's law \eqref{eq:3D_Model:CE-D} is satisfied in $\Omega$;
 	\item[] The displacement $u = u_\Sigma$ is specified on
@@
 
-		\subsubsection*{Cantilever model}
+\subsubsection{Problem 3D}
 Find a vector valued function $u$, satisfying equations
 \eqref{eq:3D_Model:EM-D} to \eqref{eq:3D_Model:CE-D} and the following boundary
-			conditions:
+conditions:\\
 
@@
 	Tn & = & 0 \quad \textrm{ on } \Gamma
-			\end{eqnarray*}
-
-			This will be referred to as \textbf{Problem 3D}.
-
-		\subsection*{Variational form}\label{ssec:3D_Model:VariationalForm}
+\end{eqnarray*} With $n$ the outward normal vector to $\Omega$. This model problem is a cantilever three-dimensional body.
+
+\subsection{Variational form}\label{ssec:3D_Model:VariationalForm}
 Define the bilinear forms
@@
 \end{eqnarray}
-			with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.
+with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1+\nu)(1-2\nu)}$.\\
 
@@
 
+The variational problem of Problem 3DV is given as:
+\subsubsection{Problem 3DV}\label{sssec:3D_Model:Problem3D1V}
 Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and
@@
 \end{align}
-			for all $\phi \in T(\Omega)$
-
-			This will be referred to as \textbf{Problem 3DV}.
-
-	\subsection{Two-dimensional theory}
-		\subsubsection*{General plane stress}
+for all $\phi \in T(\Omega)$\\
+
+\subsection{Plane stress}\label{ssec:3D_Model:PlaneStress}
 Stresses acting parallel to a single plane are referred to as plane stress. 
@@
 	\end{eqnarray}
-			\end{minipage}
+\end{minipage}\\
 
@@
 
-			This is known as general plane stress. The two-dimensional model is a special case of plane stress.
-
-		\subsubsection*{The two dimensional model}
+This is known as general plane stress.
+
+\subsection{Two-dimensional model}
+Using \cite{Sadd05} as a guide, a special case of general plane stress is considered. In this special case, a two-dimensional model is obtained.\\
+
 Assume that $\sigma_{3i} = 0$ for $i = 1, 2, 3$; $\partial_3 u_1 = 0$, $\partial_3 u_2 = 0$ ($u_1$ and $u_2$ are functions of $x_1$ and $x_2$), and the strain component $\varepsilon_{33} = 0$.
@@
 
-			The equations of motion and constitutive equations follow:
-			\subsubsection*{Equation of motion}\label{sssec:2D_Model:EquationOfMotion}
+\subsection*{Equations of motion and constitutive equations}\label{ssec:2D_Model:EquationsOfMotion+ConstitutiveEquations}
+ The following equations of motion and constitutive equations follow from subsections \ref{ssec:3D_Model:DimensionlessForm} and 1.3.2.
+\subsubsection{Equation of motion}\label{sssec:2D_Model:EquationOfMotion}
 \begin{eqnarray}
@@
 
-		\subsubsection*{Cantilever model}
-
-			Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:
-
-			Boundary Conditions:
+\subsection{Model problem}\label{ssec:2D_Model:ModelProblem}
+Divide the boundary of $\Omega$ into two distinct parts, referred to as $\Sigma$ and $\Gamma$.
+
+\subsubsection*{Problem 2D}\label{sssec:2D_Model:Problem2D1}
+Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:\\
+
+Boundary Conditions:\\
 \begin{eqnarray*}
@@
 	Tn & = & 0 \quad \textrm{ on } \Gamma.
-			\end{eqnarray*} with $n$ the outward unit normal.
-
-			This will be referred to as \textbf{Problem 2D}.
-
-		\subsubsection*{Variational form}\label{ssec:2D_Model:VariationalForm}
+\end{eqnarray*} with $n$ the outward unit normal. This model problem is a cantilever two-dimensional body.
+
+\subsection{Variational form}\label{ssec:2D_Model:VariationalForm}
 Define the bilinear forms
@@
 \end{eqnarray}
-			with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.
+with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.\\
 Also define the integral
@@
 
-			\subsubsection*{Test functions for Problem 2D}\label{sssec:2D_Model:TestFunctions2D1}
+\subsubsection{Test functions for Problem 2D}\label{sssec:2D_Model:TestFunctions2D1}
 Define the following set of test functions $T(\Omega)$ for Problem 2D:
@@
 
+The variational problem of Problem 2D is given as:
+
+\subsubsection{Problem 2DV}\label{sssec:2D_Model:Problem2D1V}
 Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
@@
 \end{align}
-			for all $\phi \in T(\Omega)$. This will be referred to as \textbf{Problem 2DV}.
-
-	\subsection{Timoshenko theory}
-		Consider a Timoshenko beam with no damping defined on the interval $[0,\ell]$.
-		Let $w$ represent the transverse displacement and $\phi$ a rotation of the cross-sections of the beam.
-
-		\subsubsection*{Equations of motion}\label{sssec:1D_Model:EquationOfMotion}
-			\begin{eqnarray}
-				\rho A \partial_t^2 w &=& \partial_x V + Q, \label{eq:1D_Model:EquationOfMotion1}\\
-				\rho I\partial_t^2 \phi  &=& V + \partial_x M. \label{eq:1D_Model:EquationOfMotion2}
-			\end{eqnarray}\label{sym:A}\label{sym:V}\label{sym:Iinertia}\label{sym:M}\label{sym:phiT}
-			In~\eqref{eq:1D_Model:EquationOfMotion1} and \eqref{eq:1D_Model:EquationOfMotion2} $\rho$ denotes the density, $A$ is the area of a cross section, $I$ is the area moment of inertia, $M$ is the moment, $V$ is the shear force and $Q$ is an external force acting on the beam.
-
-		\subsubsection*{Constitutive equations}\label{sssec:1D_Model:ConstitutiveEquation}
-			\begin{eqnarray}
-				M &=& EI\partial_x \phi, \label{eq:1D_Model:ConstitutiveEquations1}\\
-				V &=& AG\kappa^2(\partial_x w - \phi), \label{eq:1D_Model:ConstitutiveEquations2}\label{sym:kappa2T}
-			\end{eqnarray}
-			$E$ is Young's modulus, $G$ the shear modulus and $\kappa^2$ the shear correction factor.
-
-		\subsubsection*{Dimensionless form}\label{sssec:1D_Model:DimensionlessForm}
-			As mentioned in the dimensionless form of the three-dimensional model, the same dimensionless scaling can be applied to the Timoshenko beam theory.
-
-			Set \[\tau = \frac{t}{t_0}, \,\, \xi = \frac{x}{\ell}, \,\, w^*(\xi,\tau) = \frac{w(x,t)}{\ell} \ \text{ and } \ \phi^*(\xi, \tau) = \phi(x,t).\]
-
-			The dimensionless forms of the shear force, moment and external force density are \[ V^{*}(\xi,\tau) = \frac{V(x,t)}{AG\kappa^2}, \quad M^{*}(\xi,\tau) = \frac{M(x,t)}{A G\kappa^2 \ell} \,\,\, \ \text{and} \ \,\,\, Q^*(\xi,\tau) = \frac{Q(x,t)\ell}{A G\kappa^2}.\]
-
-			Choose $t_0$ the same as the three-dimensional model, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]
-
-			As in \cite{LVV09} we use the dimensionless constants
-			\begin{equation*}
-				\alpha = \frac{A \ell^2}{I} \,\,\, \text{and} \,\,\, \beta
-				=\frac{AG\kappa^2 \ell^2}{EI}.
-			\end{equation*}\label{sym:alphabeta}
-
-			Interestingly, it turns out that
-			\begin{eqnarray*}
-				\frac{\beta}{\alpha} & = & \gamma
-			\end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in the three-dimensional case.\\
-
-		\subsubsection*{Dimensionless equations of motion}\label{sssec:1D_Model:DimensionlessEquationsOfMotion}
-			\begin{eqnarray}
-				\partial_{t}^{2} w &=& \partial_{x}V + Q, \label{eq:1D_Model:EquationOfMotion1D}\\
-				\frac{1}{\alpha} \partial_{t}^{2} \phi &=& V + \partial_{x}M.\label{eq:1D_Model:EquationOfMotion2D}
-			\end{eqnarray}
-		\subsubsection*{Dimensionless constitutive equations}\label{sssec:1D_Model:DimensionlessConstitutiveEquations}
-			\begin{eqnarray}
-				M &=& \frac{1}{\beta}\partial_x \phi, \label{eq:1D_Model:ConstitutiveEquations1D}\\
-				V &=& \partial_x w-\phi. \label{eq:1D_Model:ConstitutiveEquations2D}
-			\end{eqnarray}
-		The original notation is retained for convenience.
-
-		\subsection{Models and variational forms}
-			\subsubsection*{Bilinear forms and integral}
-				For $f,g \in T[0,1]$, define the bilinear forms
-				\begin{eqnarray}
-					c(f,g) & = & \int_0^1  \partial_t^2 f_1 g_1 + \frac{1}{\alpha}\int_0^1  \partial_t^2 f_2g_2, \label{eq:1D_Model:Bilinear} \\
-					b(f,g) & = &   \int_0^1 (f_1'-f_2)(g_1' - g_2) + \frac{1}{\beta}\int_0^1 f_2' g_2', \label{eq:1D_Model:Bilinear_c}
-				\end{eqnarray}
-				Define the integral
-				\begin{eqnarray}
-				(f,g)
-					&=& \int_{0}^1 fg \label{eq:1D_Model:Bilinear_int}
-				\end{eqnarray} for all $f,g \in L^2(0,1).$\\
-
-				\textbf{Remark}\\
-				$L^2(a,b)$ is the space of all square integrable functions on the interval $(a,b)$.
-The inner product is defined by $\displaystyle (f,g) = \int_a^b fg$, and the induced norm $\displaystyle ||f|| = \int_a^b f^2$.\\
-
-			\subsection*{Pinned-pinned beam}
-				Find functions $w$ and $\phi$ satisfying equations \eqref{eq:1D_Model:EquationOfMotion1D} to \eqref{eq:1D_Model:ConstitutiveEquations2D} and the boundary conditions:
-
-				{Boundary Conditions}\\
-				\begin{eqnarray*}
-					w(0,\cdot) = 0, \ \ &M(0,\cdot) = 0, \label{eq:1D_Model:ProblemT1BC1}\\
-					w(1,\cdot) = 0, \ \ &M(1,\cdot) = 0. \label{eq:1D_Model:ProblemT1BC2}
-				\end{eqnarray*}
-
-				This will be referred to as \textbf{Problem T-1}. Define the set of test functions $T[0,1]$ for Problem T-1 as
-				\begin{eqnarray*}
-					T[0,1] &:=&  \left\{f \in C^1[0,1] \ | \ f(0) = f(1) = 0 \right\} \times C^1[0,1]
-				\end{eqnarray*}
-
-				Then the variational problem for Problem T-1 is given by
-				\subsubsection*{Problem T-1V}\label{sssec:1D_Model:ProblemT1V}
-					Find a function ${u} = \langle w, \phi \rangle$ such that for all $t >0$, ${u} \in  T[0,1]$ satisfying
-					\begin{eqnarray}
-						c(\partial_t^2 u,{\phi}) &=& -b({u},{\phi}) + (Q,{\phi})
-					\end{eqnarray} for each ${\phi} = \langle v, \psi \rangle \in T[0,1]$.
-
-			\subsection*{Cantilever beam}
-				Find functions $w$ and $\phi$ satisfying equations \eqref{eq:1D_Model:EquationOfMotion1D} to \eqref{eq:1D_Model:ConstitutiveEquations2D} and the boundary conditions:
-
-				{Boundary Conditions}\\
-				\begin{eqnarray*}
-					w(0,\cdot) = 0, \ \ &\phi(0,\cdot) = 0, \label{eq:1D_Model:ProblemT2BC1}\\
-					M(1,\cdot) = 0, \ \ &V(1,\cdot) = 0. \label{eq:1D_Model:ProblemT2BC2}
-				\end{eqnarray*}
-
-				This will be referred to as \textbf{Problem T-2}.  Define the set of test functions $T[0,1]$ for Problem T-2 as
-				\begin{eqnarray*}
-					T[0,1] &:=& \left\{g \in C^1[0,1] \ | \ g(0) = 0 \right\} \times \left\{g \in C^1[0,1] \ | \ g(0) = 0 \right\}
-				\end{eqnarray*}
-
-				Then the variational problem for Problem T-2 is given by
-				\subsubsection*{Problem T-2V}\label{sssec:1D_Model:ProblemT1V}
-					Find a function ${u} = \langle w, \phi \rangle$ such that for all $t >0$, ${u} \in  T[0,1]$ satisfying
-					\begin{eqnarray}
-						c(u,{\phi}) &=& -b({u},{\phi}) + (Q,{\phi}) \label{var_form_timo}
-					\end{eqnarray} for each ${\phi} = \langle v, \psi \rangle \in T[0,1]$.
-
-\section{Modal analysis and comparison of linear models}
-
-	\subsection*{Existance and uniqueness of solutions}
+for all $\phi \in T(\Omega)$.\\
+
+\section{Existance and uniqueness of solutions}
 Our two models, the three-dimensional modela and the two-dimensional model, concern the vibration of elastic bodies.
 These type of models have a similar variational form as the wave equation and are called second order hyperbolic type problems.
-The articles \cite{VV02} and \cite{VS18} provide existence and uniqueness results for these type of problems.
+The articles \cite{VV02} and \cite{VS19} provide existence and uniqueness results for these type of problems.
 In \cite{VV02}, it is assumed that $b$ is symmetric.
-\cite{VS18} extends the results of \cite{VV02} to the case where $b$ is not symmetric.
-For the models in the article, \cite{VV02} is a sufficient reference.
+\cite{VS19} extends the results of \cite{VV02} to the case where $b$ is not symmetric.
+For the models in the article, \cite{VV02} is a sufficient reference.\\
 
@@
 authors of \cite{VV02} to prove existence and uniqueness results. The models in this article are 
-		special cases of this general problem.
+special cases of this general problem.\\
 
@@
 \end{eqnarray}
-		while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.
+while $u(0)=u_{0},\ \ \ u'(0)=u_{1}$.\\
 
@@
 
-		Proving that these assumptions are satisfied for the models in this article too much work to include in this article.
-The existence and uniqueness results of \cite{VV02} are used in this article without proof.
-
-	\subsection*{Modal Analysis}
-		Modal analysis is a important concept in the study of vibration of elastic bodies and also useful in the comparison of linear models.
-The following section is a short discussion of the basic concepts of modal analysis and how it enables the comparison of linear models.
+Proving that these assumptions are satisfied for the models in this article too much work to 
+include in this article. The existence and uniqueness results of \cite{VV02} are used in 
+this article without proof.
+
+\section{Modal analysis and comparison of linear models}
+Modal analysis is a important concept in the study of vibration of elastic bodies and also 
+useful in the comparison of linear models. The following section is a short discussion of 
+the basic concepts of modal analysis and how it enables the comparison of linear models.\\
 
@@
 \end{eqnarray}
-		with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.
+with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.\\
 
@@
 The existence of such a $\lambda$ is uncertain at this point.
-So we consider the following eigenvalue problem.
+So we consider the following eigenvalue problem.\\
 
@@
 
-	\subsection*{Validity of series solution}
+\subsection{Validity of series solution}
 Consider the following question: When is the formal series solution valid for the vibration problem with initial values $u(0) = u_0$ and $u'(0) = u_1$?
-To answer this question, we again refer to the article \cite{CVV18}.
+To answer this question, we again refer to the article \cite{CVV18}.\\
 
@@
 
-		Therefore $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$. For the case of weak damping, it can be proved that $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ which is the case of \cite{CVV18}.
+Therefore $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$. For the case of weak damping, it can be proved that $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ which is the case of \cite{CVV18}.\\
 
@@
 \end{eqnarray*}
-		but $T_n$ is not uniquely defined by the differential equation.
-
-		Substitution shows that these partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions for \eqref{eq:existence:ProblemGVarHom} in Problem GVar.
+but $T_n$ is not uniquely defined by the differential equation.\\
+
+Substitution shows that these partial sums with initial conditions $u^N(0) = u^N_0$ and $(u^N)'(0) = u^N_1$ are solutions for \eqref{eq:existence:ProblemGVarHom} in Problem GVar.\\
 
 The authors then define an error function $u^E_N = u - u^N$.
-Since both $u$ and $u^N$ satisfies \eqref{eq:existence:ProblemGVarHom}, so does this error function with the following the initial conditions, $u^E_N(0) = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.
+Since both $u$ and $u^N$ satisfies \eqref{eq:existence:ProblemGVarHom}, so does this error function with the following the initial conditions, $u^E_N(0) = u_0 - u^N_0$ and $(u^E_N)'(0) = u_1 - u^N_1$.\\
 
@@
 Then $||u_0 - u^N_0||_V^2 \rightarrow 0$ and $||u_1 - u^N_1||_W^2 \rightarrow 0$ as $N \rightarrow \infty$.
-Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$ by \eqref{eq:inequality}.
+Therefore $\mathcal{E}(t) \rightarrow 0$ as $N \rightarrow \infty$ by \eqref{eq:inequality}.\\
 
@@
 
-	\subsection*{Comparison of models}
+\subsection{Comparison of models}
 The results on modal analysis and the validity of the series solution enable the comparison of different linear models.
 The solution of the model problems can be expressed as a series solution of the eigenvalues and eigenvectors of the models.
-Therefore the models can be compared by comparing the eigenvalues and eigenvectors of the models.
+Therefore the models can be compared by comparing the eigenvalues and eigenvectors of the models.\\
 
@@
 
-\section{Cantilever two-dimensional model}\label{ssec:2D_Model:FEM}
-Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$.
-Denote the elastic body by $\Omega \in R^2$, with $(0,0)$ as the point of reference.
-For a rectangular cross-section, the body $\Omega$ can be described as,
-\begin{eqnarray*}
-	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
-\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$.
-
-\FloatBarrier
-
-\begin{figure}[h!]
-	\centering
-	\begin{tikzpicture}
-
-		\draw[line width = 0.4mm] (0,0.5) -- (7,0.5);
-		\draw[line width = 0.4mm] (0,-0.5) -- (7,-0.5);
-		\draw[line width = 0.4mm] (7,-0.5) -- (7,0.5);
-		\draw[line width = 0.4mm] (0,-0.5) -- (0,0.5);
-
-		\draw[line width = 0.1mm] (0,1.5) -- (0,-1.5);
-
-		\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.3);
-		\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.1);
-		\draw[line width = 0.1mm] (0,1.1) -- (-0.2,0.9);
-		\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.7);
-		\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.5);
-		\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.3);
-		\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.1);
-		\draw[line width = 0.1mm] (0,0.1) -- (-0.2,-0.1);
-		\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.3);
-		\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.5);
-		\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.7);
-		\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.9);
-		\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1.1);
-		\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.3);
-		\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.5);
-
-		\node at (7.3,0) {$h$};
-		\draw[-stealth] (7.3,0.2) -- (7.3,0.5);
-		\draw (7.2,0.5) -- (7.4,0.5);
-		\draw[-stealth] (7.3,-0.2) -- (7.3,-0.5);
-		\draw (7.2,-0.5) -- (7.4,-0.5);
-
-		\node at (3.5,-0.8) {$1$};
-		\draw[stealth-] (0,-0.8) -- (3.3,-0.8);
-		\draw[stealth-] (7,-0.8) -- (3.7,-0.8);
-		\draw (7,-0.9) -- (7,-0.7);
-
-		\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
-		\draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
-		\node at (9.7,0.8) {$e_1$};
-		\node at (8.8,1.5) {$e_2$};
-
-		\node at (-0.6,0) {$(0,0)$};
-		\node at (0,0)[circle,fill,inner sep=1.5pt]{};
-
-		% Add Σ at x_1 = 0
-		\node at (-1.4,0) {$\Sigma$};
-
-		% Add Γ₁ at x_2 = -h/2
-		\node at (3.5,-1.2) {$\Gamma_1$};
-
-		% Add Γ₂ at x_2 = h/2
-		\node at (3.5,0.9) {$\Gamma_2$};
-
-		% Add Γ₃ at x_1 = 1
-		\node at (8,0) {$\Gamma_3$};
-
-	\end{tikzpicture}
-\end{figure}
-
-\FloatBarrier
-
- Using the reference configuration, the variational problem Problem 2DV can be rewritten into a model specific form.
-
-\subsubsection*{Problem 2DV}\label{sssec:2D_Model:Problem2D1VChp5}
-Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
-\begin{align}
-	c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{eq:2D_Model:Problem2D1VEqChp5}
-\end{align}
-for all $\phi \in T(\Omega)$. With the test function space 
-\begin{eqnarray*}
-	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
-\end{eqnarray*}
-
-The bilinear forms and integral function is defined by
-\begin{eqnarray}
-	b(u,\phi) & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
-	\textrm{Tr}(\Phi) ~dA, \label{eq:2D_Model:BilinearChp5}\\
-	c(\partial_t^2 u,\phi) & = & \int_\Omega~ (\partial^2_t u) \cdot \phi~dA, \label{eq:2D_Model:Bilinear_cChp5}\\
-	(f,g) &=& \int_{\Omega} f\cdot g \ dA, \label{eq:2D_Model:Bilinear_intChp5}
-\end{eqnarray}
-with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.
-
-Using the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten into a model specific form.
-
-\subsubsection*{Constitutive equations:}
-\begin{eqnarray}
-	\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_1 u_1 + \nu \partial_2 u_2) \label{CE1} \\
-	\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_2 u_2 + \nu \partial_1 u_1) \label{CE2} \\
-	\sigma_{12} & = & \frac{1}{2\gamma(1+\nu)}(\partial_1 u_2 + \partial_2 u_1) \label{CE3}
-\end{eqnarray}
-
-\subsubsection*{Bilinear form:}
-\begin{align}
-	b(u,\phi) & = & \frac{1}{\gamma(1-\nu^2)}\int_{\Omega} (\partial_1 u_1 \partial_1 \phi_1 + \partial_2 u_2 \partial _2 \phi_2 + \nu\partial_1 u_1 \partial_2\phi_2 + \nu \partial_2 u_2 \partial_1 \phi_1 ) \ dA \nonumber\\
-	& + & \frac{1}{2\gamma(1+\nu)}\int_{\Omega} (\partial_1 u_2 \partial_1 \phi_2 + \partial_1 u_2 \partial_2 \phi_1 + \partial_2 u_1 \partial_1\phi_2 + \partial_2 u_1 \partial_2\phi_1) \ dA.
-\end{align}
-
-\subsection*{Galerkin approximation}\label{2d_FEM_G}
-To apply the Finite Element Method to Problem 2DV, $\Omega$ must be discretized by dividing it into rectangular elements, suitable for its rectangular cross-section.
-This process involves creating a grid with $n = n_1 \times n_2$ nodes across $\Omega$.
-
-A set of $n$-dimensional linear independent basis functions is defined, particularly for the two-dimensional model, as 
-$$B = \{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \}.$$ 
-These functions, chosen as piecewise Hermite bi-cubic functions $\phi_i$, offer quicker convergence and the ability to derive solution derivatives, despite their increased complexity compared to bi-linear functions.
-
-The subset of basis functions from $B$ that meet the criteria of the test function space $T(\Omega)$ are termed admissible basis functions, denoted by $\delta_j$, where each $\delta_j$ is a distinct element of $B$.
-These can be enumerated and presented as the set
-$$A = \{\delta_1, \delta_2,..., \delta_k \}$$ 
-for some $k \leq 2n$.
-
-Define the space
-\begin{eqnarray*}
-S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right).
-\end{eqnarray*}
-
-For each function $u^h \in S^h$, $u^h$ can be expressed as
-\begin{eqnarray*}
-	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x).
-\end{eqnarray*}
-
-Substitution of $u^h$ into Problem 2DV, results in the following Galerkin Approximation, denoted by Problem 2DG.
-
-\subsubsection*{Problem 2DG}
-Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
-\begin{eqnarray*}
-	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I, \phi_i)
-\end{eqnarray*} for $i = 1,2,...,k$.
-$Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$.
-i.e.
-$Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.
-
-Consider the following standard Finite Element Method matrices
-
-\noindent\begin{minipage}{.5\linewidth}
-	\begin{eqnarray*}
-		\mathbf{M}_{j,i} & = & \int_{\Omega} \phi_i \phi_j ~dA \\
-		\mathbf{{K}_{11}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_1\phi_j~dA\\
-		\mathbf{{K}_{22}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_2\phi_j~dA
-	\end{eqnarray*}
-\end{minipage}%
-\begin{minipage}{.5\linewidth}
-	\begin{eqnarray*}
-		\mathbf{{K}_{12}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_1\phi_j~dA\\
-		\mathbf{{K}_{21}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_2\phi_j~dA
-	\end{eqnarray*}
-\end{minipage}
-for $i,j = 1,2,...,k$.
-
-And 
-\begin{eqnarray*}
-	{M_{F}}_{j,i} = \int_{\Omega}  \phi_i \phi_j~dA
-\end{eqnarray*}
-
-for $i = 1,2,...,k$ and for $j =1,2,...,2n$.
-
-Define the following matrices:
-\begin{eqnarray*}
-	K_1 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{11}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{22}} \label{eq:2DFEM:K1} \\
-	K_2 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{21}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{12}}\label{eq:2DFEM:K2}\\
-	K_3 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{12}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{21}}\label{eq:2DFEM:K3}\\
-	K_4 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{22}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{11}}\label{eq:2DFEM:K4}
-\end{eqnarray*}
-
-Using the standard FEM matrices and matrices $K_1$-$K_4$, the following concatenated matrices are defined.
-\begin{eqnarray}
-	\begin{aligned}
-		K = 
-		\begin{bmatrix}
-			K1 & K2\\
-			K3 & K4
-		\end{bmatrix}
-	\end{aligned}
-	\ \ \ \ \ \ \ \ \
-	\begin{aligned}
-		M_f = 
-		\begin{bmatrix}
-			M_{F} & O_{F}\\
-			O_{F} & M_{F}
-		\end{bmatrix}
-	\end{aligned}\label{eq:2DFEM:K+M}
-\end{eqnarray}
-
-\begin{eqnarray}
-	M = 
-	\begin{bmatrix}
-		\mathbf{M} & O \\
-		O & \mathbf{M}
-	\end{bmatrix}\label{eq:2DFEM:M}
-\end{eqnarray}
-
-The matrices ${O}$ and ${O_f}$ are the zero matrices of the same size as $\mathbf{M}$ and ${M_f}$ respectively.
-
-Using \eqref{eq:2DFEM:K+M} and \eqref{eq:2DFEM:M}, Problem 2DG is rewritten as a system of ordinary differential equations. This system is referred to as Problem 2DODE.
-
-\subsubsection*{Problem 2DODE}
-Find a function $\bar{u} \in S^h$ such that
-\begin{eqnarray}
-	M\ddot{\bar{u}} & = & K\bar{u} + M_{f}Q^I.
-\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \langle u, \partial_1 u, \partial_2 u, \partial_{12} u \rangle$.
-
-\textbf{Remark} This form of $\bar{u}$ is determined by the use of the bi-cubic basis functions.
-
-\subsection*{Eigenvalue problem}\label{2dFEM_EP}
-For the eigenvalue problem, assume that there is no external force, $M_{f}Q^I = 0$, so that 
-\begin{eqnarray}
-		M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
-\end{eqnarray}
-It is known that a system of ordinary differential equations has a general solution of the form $e^{rt}$.
-Suppose that $\bar{w} = e^{\lambda t} \bar{u}$ is a solution for \eqref{eq:2DFEM:M2}.
-In this solution, $\lambda$ is an eigenvalue and $\bar{u}$ a corresponding eigenfunction.
-Substitution into \eqref{eq:2DFEM:M2} results in
-\begin{eqnarray*}
-	M\lambda e^{\lambda t}\bar{u} & = & Ke^{\lambda t}\bar{u}.
-\end{eqnarray*}
-Since $e^{\lambda t} > 0$ for all values of $\lambda t$, we can cancel it from both sides of the equation and formulate the eigenvalue problem Problem 2DE.
-
-\subsubsection*{Problem 2DE}
-Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
-\begin{eqnarray}
-	M\lambda{\bar{u}} & = & K\bar{u}.
-\end{eqnarray}
-
-\section{Cantilever three-dimensional model} \label{ssec:3D_Model:FEM}
+\section{Finite element method}
+
+\subsection{Three-dimensional model}
+Consider a cantilever three-dimensional elastic body, with a rectangular cross-section.
+
+\subsubsection*{Reference configuration for rectangular cross-section}
 Let $\{e_1,e_2,e_3\}$ be a right-handed orthonormal basis for $R^3$.
@@
 	\Omega = \left\{ x \in R^3 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} , \ -\frac{b}{2} \leq x_3 \leq \frac{b}{2}\right \}
-	\end{eqnarray*}
-	Let $\partial \Omega$ denote the boundary of the body.
-
-	\FloatBarrier
+\end{eqnarray*} \label{sym:width}
+Let $\partial \Omega$ denote the boundary of the body. Divide $\partial \Omega$ into the six distinct flat surfaces as follows:
+
+\noindent\begin{minipage}{.5\linewidth}
+	\begin{eqnarray*}
+		\Sigma:& \quad x_1 &= 0\\
+		\Gamma_5:& \quad x_1 &= 1\\
+		\Gamma_1:& \quad x_3 &= -{b}/{2} 
+	\end{eqnarray*}
+\end{minipage}%
+\begin{minipage}{.5\linewidth}
+	\begin{eqnarray*}
+		\Gamma_2:& \quad x_2 &= -{h}/{2}\\
+		\Gamma_3:& \quad x_3 &= {b}/{2}\\
+		\Gamma_4:& \quad x_2 &= {h}/{2} 
+	\end{eqnarray*}
+\end{minipage}
+
+Using this notation, the boundary conditions are similar to the two-dimensional model in section \ref{sssec:2D_Model:RefConf}, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.
+
+\subsubsection{Cantilever elastic body}
+Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma$ and free-hanging at all the other sides.
+This is Problem 3D in section \ref{ssec:3D_Model:ModelProblems}.
+
 \begin{figure}[h!]
@@
 
-	\FloatBarrier
-
-	This general variational form Problem 3DV can now be rewritten as in a model specific form using the reference configuration.
-
-	\subsubsection*{Problem 3DV}
+In section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3DV.
+This general form can now be rewritten as in a model specific form using the reference configuration.
+For convenience, some of the results from section \ref{sec:3D_Model} are repeated here.
+
+\subsubsection{Problem 3DV}
 Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
@@
 
-	\subsubsection*{Bilinear Form}
+\subsubsection{Bilinear Form}
 \begin{align*}
@@
 
-	\subsection*{Galerkin approximation}
-	For analyzing a three-dimensional body, rectangular prismatic (brick-shaped) elements are used, as detailed in \cite{Wu06}. This choice suits bodies with rectangular cross-sections.
-
-	Split $\Omega$ into a grid of these elements, creating $n = n_1 \times n_2 \times n_3$ nodes.
-
-	Define $n$-dimensional linear independent basis functions for the three-dimensional model as
+\subsection{Weak variational form}
+
+\subsubsection{Bilinear form}
+Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)\times H^1(0,1)$.
+Denote $X = L^2(0,1)\times L^2(0,1)\times L^2(0,1)$.
+The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.
+
+\subsubsection{Problem 3DW}
+Find a function $u$ such that for all $t>0$, $u(t) \in V$ and $u''(t) \in W$, satisfying the following equation
+\begin{eqnarray}
+	c(u,v) + b(u,v) & = & (Q,v) \ \ \ \textrm{ for each } v \in V.
+\end{eqnarray}
+
+\subsection{Galerkin approximation}
+As mentioned in the previous section, section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised.
+For this is three-dimensional body, three-dimensional elements shapes are required.
+The elements used in this dissertation are rectangular prismatic elements.
+These elements are also known as `brick-shaped' elements and is described in \cite{Wu06}.
+This shape of element is a natural choice for a three-dimensional elastic body with a rectangular cross-section.
+
+Divide the reference configuration $\Omega$ into a grid of rectangular prismatic elements, such that there are $n = n_1 \times n_2 \times n_3$ nodes.
+
+Define a set of $n$-dimensional linear independent basis functions. For the three-dimensional model, the basis functions can be defined by the set
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-	Employing piecewise Hermite tri-cubic basis functions offers quicker convergence and solution derivatives, albeit with increased complexity compared to tri-linear functions.
-
-	Admissible basis functions, satisfying all conditions of $T(\Omega)$, are denoted by $\delta_j$, making up the set $A = \left\{\delta_1, \delta_2,... , \delta_k\right\}$, where $k \leq 3n$.
+
+For the this three-dimensional model, piecewise Hermite tri-cubic basis functions are used.
+Although this is more complex than using piecwise tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
+
+Recall that the admissible basis functions, are all the basis functions that satisfies all the conditions of the test function space $T(\Omega)$.
+Denote the admissible basis functions by $\delta_j$, with each $\delta_j$ a unique element of $B$.
+The set of admissible basis functions can then be expressed as $A = \left\{\delta_1, \delta_2,...
+, \delta_k\right\}$ with $k \leq 3n$.
 
@@
 
-	\subsubsection*{Problem 3DG}
+\subsubsection{Problem 3DG}
 Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
@@
 
+\subsection{System of ordinary differential equations}\label{3d_fem_g}
 Consider the following standard Finite Element Method matrices.
 
+\subsubsection{FEM matrices}
 \noindent\begin{minipage}{.5\linewidth}
@@
 
-	\subsubsection*{Problem 3DODE}
+\subsubsection{Problem 3DODE}
 Find a function $\bar{u} \in S^h$ such that
@@
 
-	\subsection*{Eigenvalue problem}
+\subsection{Eigenvalue problem}
 The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in section \ref{2dFEM_EP}.
 
-	\subsubsection*{Problem 3DE}\label{3dFEM_EP}
+\subsubsection{Problem 3DE}\label{3dFEM_EP}
 Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
@@
 
-	Now Problem 2DE and Problem 3DE can be solved using a computer program. Iterative methods, sparse matrices as well as parallel computing can be used to efficiently solve these problems.
-
-\section{Validity of the model for a cantilever Timoshenko beam (CHAPTER 4 of dissertation)} \label{sec:validity-of-a-cantilever-timoshenko-beam}
-
-	In this section, the validity of the Timoshenko beam model is investigated.
-Specifically, the validity of a cantilever Timoshenko beam model, using a cantilever two-dimensional beam model as a reference.
-This follows what is done in the article \cite{LVV09}.
-This section discusses the results of the article, focussing on the numerical results.
-Some of the results are replicated with more significant digits, others are extended to be used in the rest of this chapter.
-
-	The article \cite{LVV09} is titled `Comparison of linear beam theories'.
-In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam.
-The authors start by presenting the models.
-These are the same as Problem T-2 and Problem 2D-1 that are defined in Chapter~1.
-The authors also look at the existence and uniqueness of solutions, which is covered in Chapter 2 of this dissertation.
-The authors then calculate and compare the eigenvalues and eigenfunctions, which will be discussed in this section.
+Consider a cantilever two-dimensional elastic body, with a rectangular cross-section.
+
+\subsubsection{Reference configuration for rectangular cross-section}\label{sssec:2D_Model:RefConf}
+Let $\{e_1,e_2\}$ be a right-handed orthonormal basis for $R^2$.
+Denote the elastic body by $\Omega \in R^2$, with $(0,0)$ as the point of reference.
+For a rectangular cross-section, the body $\Omega$ can be described as,
+\begin{eqnarray*}
+	\Omega = \left \{ x \in E_2 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} \right \},
+\end{eqnarray*} where $\partial \Omega$ denotes the boundary of $\Omega$. The boundary $\partial \Omega$ can be divided into the four distinct lines (or edges) as follows: \label{sym:En}
+
+\noindent\begin{minipage}{.5\linewidth}
+	\begin{eqnarray*}
+		\Sigma:& \quad x_1 &= 0\\
+		\Gamma_3:& \quad x_1 &= 1
+	\end{eqnarray*}
+\end{minipage}%
+\begin{minipage}{.5\linewidth}
+	\begin{eqnarray*}
+		\Gamma_1:& \quad x_2 &= -{h}/{2}\\
+		\Gamma_2:& \quad x_2 &= {h}/{2}
+	\end{eqnarray*}
+\end{minipage}
+
+In this configuration, the body is clamped rigidly to the surface at $x_1 = 0$ denoted as $\Sigma$ and the body is free-hanging on the other boundaries denoted by $\Gamma$.
+
+\subsubsection{Cantilever elastic body}
+Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D in section \ref{ssec:2D_Model:ModelProblem}.
+
+\begin{figure}[h!]
+	\centering
+	\begin{tikzpicture}
+
+		\draw[line width = 0.4mm] (0,0.5) -- (7,0.5);
+		\draw[line width = 0.4mm] (0,-0.5) -- (7,-0.5);
+		\draw[line width = 0.4mm] (7,-0.5) -- (7,0.5);
+		\draw[line width = 0.4mm] (0,-0.5) -- (0,0.5);
+
+		\draw[line width = 0.1mm] (0,1.5) -- (0,-1.5);
+
+		\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.3);
+		\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.1);
+		\draw[line width = 0.1mm] (0,1.1) -- (-0.2,0.9);
+		\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.7);
+		\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.5);
+		\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.3);
+		\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.1);
+		\draw[line width = 0.1mm] (0,0.1) -- (-0.2,-0.1);
+		\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.3);
+		\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.5);
+		\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.7);
+		\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.9);
+		\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1.1);
+		\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.3);
+		\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.5);
+
+		\node at (7.3,0) {$h$};
+		\draw[-stealth] (7.3,0.2) -- (7.3,0.5);
+		\draw (7.2,0.5) -- (7.4,0.5);
+		\draw[-stealth] (7.3,-0.2) -- (7.3,-0.5);
+		\draw (7.2,-0.5) -- (7.4,-0.5);
+
+		\node at (3.5,-0.8) {$1$};
+		\draw[stealth-] (0,-0.8) -- (3.3,-0.8);
+		\draw[stealth-] (7,-0.8) -- (3.7,-0.8);
+		\draw (7,-0.9) -- (7,-0.7);
+
+		\draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
+		\draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
+		\node at (9.7,0.8) {$e_1$};
+		\node at (8.8,1.5) {$e_2$};
+
+		\node at (-0.6,0) {$(0,0)$};
+		\node at (0,0)[circle,fill,inner sep=1.5pt]{};
+
+		% Add Σ at x_1 = 0
+		\node at (-1.4,0) {$\Sigma$};
+
+		% Add Γ₁ at x_2 = -h/2
+		\node at (3.5,-1.2) {$\Gamma_1$};
+
+		% Add Γ₂ at x_2 = h/2
+		\node at (3.5,0.9) {$\Gamma_2$};
+
+		% Add Γ₃ at x_1 = 1
+		\node at (8,0) {$\Gamma_3$};
+
+	\end{tikzpicture}
+\end{figure}
+
+In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2DV.
+Some of the results from section \ref{sec:2D_Model} are repeated here for convenience.
+Using the reference configuration, these results are rewritten from a general form to a model specific form.
+
+\subsubsection{Problem 2DV}\label{sssec:2D_Model:Problem2D1VChp5}
+Find a function $u$ such that for all $t>0$, $u \in T(\Omega)$ and 
+\begin{align}
+	c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{eq:2D_Model:Problem2D1VEqChp5}
+\end{align}
+for all $\phi \in T(\Omega)$. With the test function space 
+\begin{eqnarray*}
+	T(\Omega) & = & \left\{ \phi \in C^1(\bar{\Omega}) \ | \ \phi = 0 \ \textrm{ on } \ \Gamma \right\}.
+\end{eqnarray*}
+
+The bilinear forms and integral function is defined by
+\begin{eqnarray}
+	b(u,\phi) & = & \int_\Omega~c_1\textrm{Tr}({\cal E}\Phi)+ c_2\textrm{Tr}({\cal E})
+	\textrm{Tr}(\Phi) ~dA, \label{eq:2D_Model:BilinearChp5}\\
+	c(\partial_t^2 u,\phi) & = & \int_\Omega~ (\partial^2_t u) \cdot \phi~dA, \label{eq:2D_Model:Bilinear_cChp5}\\
+	(f,g) &=& \int_{\Omega} f\cdot g \ dA, \label{eq:2D_Model:Bilinear_intChp5}
+\end{eqnarray}
+with $\displaystyle c_1 = \frac{1}{\gamma(1+\nu)}$ and $\displaystyle c_2 = \frac{\nu}{\gamma(1-\nu^2)}$.
+
+Using the reference configuration, the constitutive equations and the bilinear form $b$ can be rewritten into a model specific form.
+
+\subsubsection{Constitutive equations:}
+\begin{eqnarray}
+	\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_1 u_1 + \nu \partial_2 u_2) \label{CE1} \\
+	\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)}(\partial_2 u_2 + \nu \partial_1 u_1) \label{CE2} \\
+	\sigma_{12} & = & \frac{1}{2\gamma(1+\nu)}(\partial_1 u_2 + \partial_2 u_1) \label{CE3}
+\end{eqnarray}
+
+\subsubsection{Bilinear form:}
+\begin{align}
+	b(u,\phi) & = & \frac{1}{\gamma(1-\nu^2)}\int_{\Omega} (\partial_1 u_1 \partial_1 \phi_1 + \partial_2 u_2 \partial _2 \phi_2 + \nu\partial_1 u_1 \partial_2\phi_2 + \nu \partial_2 u_2 \partial_1 \phi_1 ) \ dA \nonumber\\
+	& + & \frac{1}{2\gamma(1+\nu)}\int_{\Omega} (\partial_1 u_2 \partial_1 \phi_2 + \partial_1 u_2 \partial_2 \phi_1 + \partial_2 u_1 \partial_1\phi_2 + \partial_2 u_1 \partial_2\phi_1) \ dA.
+\end{align}
+
+\subsection{Weak variational form}
+Define the inertia space $V$ as the closure of $T(\Omega)$ in $H := H^1(0,1)\times H^1(0,1)$.
+Denote $X = L^2(0,1)\times L^2(0,1)$.
+The inertia space is $W  = X$ with norm $||\cdot||_W = \sqrt{c(\cdot,\cdot)}$.
+
+\subsubsection{Problem 2DWV}
+Find a function $u$ such that $\forall \ t > 0$, $u \in V$ with $\partial_t^2 u \in W$ and
+\begin{eqnarray*}
+	c(u,v) + b(u,v) & = & (Q,v)
+\end{eqnarray*}
+for all $v\in V$.
+
+\subsection{Galerkin approximation}\label{2d_FEM_G}
+To be able to apply the Finite Element Method to Problem 2DV, the body $\Omega$ needs to be discretised.
+This is done by dividing the body $\Omega$ into discrete shapes, called elements.
+There are various types of shapes of elements that can be used.
+Since the body $\omega$ is has a rectangular cross-section, rectangular elements are the simplest elements to use.
+
+Divide the reference configuration $\Omega$ into a grid of rectangular elements, such that there are $n = n_1\times n_2$ nodes.
+
+Define a set of $n$-dimensional linear independent basis functions.
+For the two dimensional model, the basis functions can be defined by the set $$B = \left\{\langle\phi_1, 0\rangle, \langle\phi_2, 0\rangle,...,\langle\phi_{n}, 0 \rangle,\langle 0,\phi_1\rangle,\langle 0 ,\phi_2\rangle,...,\langle 0,\phi_{n}\rangle \right\}.$$
+
+These functions are chosen as piecewise Hermite bi-cubic functions $\phi_i$.
+Simpler bi-linear functions can also be used, however the use of the bi-cubic basis functions results in faster convergence and also the benefit of obtaining the derivatives of the solution at the expense of more complexity.
+
+The subset of basis functions $B$ that satisfies all the conditions of the test function space $T(\Omega)$ are called the admissible basis functions.
+Denote the admissible basis functions by $\delta_j$, where each $\delta_j$ is a unique element of $B$.
+The admissible basis functions can be numbered and expressed as the set $A = \left \{\delta_1, \delta_2,..., \delta_k \right\}$ for some $k \leq 2n$.\\
+
+Define the space
+\begin{eqnarray*}
+S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right).
+\end{eqnarray*}
+
+For each function $u^h \in S^h$, $u^h$ can be expressed as
+\begin{eqnarray*}
+	u^h = \sum_{i = 1}^{k} u_i(t) \delta_{i}(x).
+\end{eqnarray*}
+
+Substitution of $u^h$ into Problem 2DV, results in the following Galerkin Approximation, denoted by Problem 2DG.
+
+\subsubsection{Problem 2DG}
+Find a function $u^h$ such that for all $t>0$, $u^h \in S^h$ and
+\begin{eqnarray*}
+	(u^h, \phi_i) & = & -b(u^h,\phi_i) + (Q^I, \phi_i)
+\end{eqnarray*} for $i = 1,2,...,k$.
+$Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$.
+i.e.
+$Q^I_{i,j} = Q(x_i,x_j)$ for $i = 1,2,...,n_1$ and $j = 1,2,...,n_2$.
+
+\subsection{System of differential equations}\label{ssec:2DFEM:DE}
+
+Consider the following standard Finite Element Method matrices
+\subsubsection{FEM matrices}
+\noindent\begin{minipage}{.5\linewidth}
+	\begin{eqnarray*}
+		\mathbf{M}_{j,i} & = & \int_{\Omega} \phi_i \phi_j ~dA \\
+		\mathbf{{K}_{11}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_1\phi_j~dA\\
+		\mathbf{{K}_{22}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_2\phi_j~dA
+	\end{eqnarray*}
+\end{minipage}%
+\begin{minipage}{.5\linewidth}
+	\begin{eqnarray*}
+		\mathbf{{K}_{12}}_{j,i} & = & \int_{\Omega} \partial_2\phi_i \partial_1\phi_j~dA\\
+		\mathbf{{K}_{21}}_{j,i} & = & \int_{\Omega} \partial_1\phi_i \partial_2\phi_j~dA
+	\end{eqnarray*}
+\end{minipage}
+for $i,j = 1,2,...,k$.
+
+And 
+\begin{eqnarray*}
+	{M_{F}}_{j,i} = \int_{\Omega}  \phi_i \phi_j~dA
+\end{eqnarray*}
+
+for $i = 1,2,...,k$ and for $j =1,2,...,2n$.
+
+Define the following matrices:
+\begin{eqnarray*}
+	K_1 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{11}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{22}} \label{eq:2DFEM:K1} \\
+	K_2 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{21}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{12}}\label{eq:2DFEM:K2}\\
+	K_3 & = & \frac{\nu}{\gamma(1-\nu^2)} \mathbf{K_{12}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{21}}\label{eq:2DFEM:K3}\\
+	K_4 & = & \frac{1}{\gamma(1-\nu^2)} \mathbf{K_{22}} + \frac{1}{2\gamma(1+\nu)}\mathbf{K_{11}}\label{eq:2DFEM:K4}
+\end{eqnarray*}
+
+Using the standard FEM matrices and matrices $K_1$-$K_4$, the following concatenated matrices are defined.
+\begin{eqnarray}
+	\begin{aligned}
+		K = 
+		\begin{bmatrix}
+			K1 & K2\\
+			K3 & K4
+		\end{bmatrix}
+	\end{aligned}
+	\ \ \ \ \ \ \ \ \
+	\begin{aligned}
+		M_f = 
+		\begin{bmatrix}
+			M_{F} & O_{F}\\
+			O_{F} & M_{F}
+		\end{bmatrix}
+	\end{aligned}\label{eq:2DFEM:K+M}
+\end{eqnarray}
+
+\begin{eqnarray}
+	M = 
+	\begin{bmatrix}
+		\mathbf{M} & O \\
+		O & \mathbf{M}
+	\end{bmatrix}\label{eq:2DFEM:M}
+\end{eqnarray}
+
+The matrices ${O}$ and ${O_f}$ are the zero matrices of the same size as $\mathbf{M}$ and ${M_f}$ respectively.
+
+Using \eqref{eq:2DFEM:K+M} and \eqref{eq:2DFEM:M}, Problem 2DG is rewritten as a system of ordinary differential equations. This system is referred to as Problem 2DODE.
+
+\subsubsection{Problem 2DODE}
+Find a function $\bar{u} \in S^h$ such that
+\begin{eqnarray}
+	M\ddot{\bar{u}} & = & K\bar{u} + M_{f}Q^I.
+\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \langle u, \partial_1 u, \partial_2 u, \partial_{12} u \rangle$.
+
+\textbf{Remark} This form of $\bar{u}$ is determined by the use of the bi-cubic basis functions.
+
+\subsection{Eigenvalue problem}\label{2dFEM_EP}
+For the eigenvalue problem, assume that there is no external force, $M_{f}Q^I = 0$, so that 
+\begin{eqnarray}
+		M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
+\end{eqnarray}
+It is known that a system of ordinary differential equations has a general solution of the form $e^{rt}$.
+Suppose that $\bar{w} = e^{\lambda t} \bar{u}$ is a solution for \eqref{eq:2DFEM:M2}.
+In this solution, $\lambda$ is an eigenvalue and $\bar{u}$ a corresponding eigenfunction.
+Substitution into \eqref{eq:2DFEM:M2} results in
+\begin{eqnarray*}
+	M\lambda e^{\lambda t}\bar{u} & = & Ke^{\lambda t}\bar{u}.
+\end{eqnarray*}
+Since $e^{\lambda t} > 0$ for all values of $\lambda t$, we can cancel it from both sides of the equation and formulate the eigenvalue problem Problem 2DE.
+
+\subsubsection{Problem 2DE}
+Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
+\begin{eqnarray}
+	M\lambda{\bar{u}} & = & K\bar{u}.
+\end{eqnarray}
+
+\section{Results}
+
+\section{Validity of a model for a cantilever two-dimensional beam} \label{sec:validity-of-a-2d-beam}
+
+In section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed.
+In this article, the authors investigated the validity of a cantilever Timoshenko beam by comparing it to a cantilever two-dimensional beam.
+In this section, the article is extended and the validity of the cantilever two-dimensional model is investigated.
+
+As mentioned in the introduction of the chapter, a beam is a three-dimensional body and therefore a three-dimensional model is more realistic.
+However the authors of \cite{LVV09} mention that a direct comparison of the one and three-dimensional models will have complexities and they suggest using the two-dimensional model as an intermediate step.
+
+So in this section, the article \cite{LVV09} is extended and the validity of a cantilever two-dimensional beam model is investigated, using a cantilever three-dimensional model as a reference.
 
 \subsection{The models}
-	The cantilever Timoshenko beam model is defined in section \ref{ssec:1D_Model:ModelProblems}, and is referred to as Problem T-2.
-The cantilever two-dimensional beam model is defined in section \ref{ssec:2D_Model:ModelProblem}, and is referred to as Problem 2D-1.
-
-	Figure \ref{fig:compare:1D+2D} shows the two beams side-by-side.
+The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in section \ref{ssec:2D_Model:ModelProblem}.
+From section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D.
+
+Figure \ref{fig:2Dv3D} shows the two beams side-by-side.
 
@@
 		\makebox[\textwidth][c]{
-				\caption{Side by side comparison of the beams.}
-				\centering
-				\begin{minipage}[b]{0.8\linewidth}
-					\begin{center}
-						\begin{tikzpicture}
-						\draw[line width = 0.4mm] (0,0) -- (6,0);
-
-						\node at (2.7,-0.25) {$\ell = 1$};
-
-						\draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
-						\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
-						\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
-						\draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
-						\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
-						\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
-						\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
-						\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
-						\draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);
-
-						\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
-						\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
-						\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
-						\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
-						\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
-						\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
-						\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
-						\draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
-
-						%\node at (3.2,-0.2) {$\ell = 1$};
-						\end{tikzpicture}
-					\end{center}
-					\subcaption{Timoshenko Cantilever Beam}
-				\end{minipage}
-				\begin{minipage}[b]{0.8\linewidth}
-					\begin{center}
-						\begin{tikzpicture}
-							\draw[line width = 0.4mm] (0,0.2) -- (6,0.2);
-							\draw[line width = 0.4mm] (0,-0.2) -- (6,-0.2);
-							\draw[line width = 0.4mm] (6,-0.2) -- (6,0.2);
-							%\draw[line width = 0.4mm] (0,-0.2) -- (0,0.2);
-
-							%\draw[line width = 0.1mm,->] (6,2) -- (7.4,2);
-							%\draw[line width = 0.1mm,->] (6,2) -- (6,0.9);
-							%\node at (6.7,1.8) {$e_1$};
-							%\node at (5.8,1.4) {$e_2$};
-
-							\node at (6.2,0) {$h$};
-							\node at (2.7,-0.45) {$\ell = 1$};
-
-							\draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
-							\draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
-							\draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
-							\draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
-							\draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
-							\draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
-							\draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
-							\draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
-							\draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);
-
-							\draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
-							\draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
-							\draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
-							\draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
-							\draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
-							\draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
-							\draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
-							\draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
-
-							%\node at (3.2,-0.3) {$\ell = 1$};
-
-						\end{tikzpicture}
-					\end{center}
-					\subcaption{Two-Dimensional Cantilever Beam}
-				\end{minipage}
-			}
-		}
-	\end{figure}\label{fig:compare:1D+2D}
-
-	In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
-	introduced. The paramater is given here again for convenience:
-	\begin{eqnarray*}
-		\alpha = \frac{A\ell^2}{I}.
-	\end{eqnarray*}
-
-	The model is in a dimensionless form, therefore the length of the beam is $\ell = 1$.
-Since we assumed a square cross-section, the area of the cross-section can be calculated as $\displaystyle A = hb$.
-The area moment of inertia can also be calculated as $\displaystyle I = \frac{h^3b}{12}$.
-Substituting these values into the formula for $\alpha$ gives the following relationship between the height of the beam and the parameter $\alpha$: $\displaystyle \alpha = \frac{12}{h^2}$
-	or equivalently,
-	\begin{eqnarray}
-		h & = & \sqrt{\frac{12}{\alpha}}. \label{eq:h-alpha-relationship}
-	\end{eqnarray}
-	Using this relationship, the height of the beam model can be set by considering the value of $\alpha$.
-
-	\subsection{Calculating the eigenvalues and eigenvectors}
-	In section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided.
-And in section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.
-
-	For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method.
-In section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived.
-Specifically, section \ref{2dFEM_EP} derived the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.
-
-	\subsubsection{Problem 2D-1E}
-	Find a real number $\lambda$ and a vector $\bar{u} \in R^n$ such that
-	\begin{eqnarray}
-		K\bar{u} & = & M\lambda{\bar{u}},
-	\end{eqnarray} where $M$ and $K$ are the standard Finite Element Method matrices defined in section \ref{sec:FEM:2D}.
-
-	In this form, the eigenvalue problem is a system of ordinary differential equations, and can be solved using a numerical method.
-Computer programs like MATLAB provide functions that are able to solve this.
-
-	\subsubsection{Accuracy of the eigenvalues}
-	Solving \textbf{Problem 2D-1E} with a numerical method, requires a quick investigation into the rate of convergence so that the accuracy of the eigenvalues can be established.
-Chapter \ref{ch:finite-element-theory} provides the necessary theory on the existence of solutions as well as the proof of convergence of the Finite Element Method.
-
-	\begin{figure}[H]
-		\centering
-		\begin{adjustbox}{center}
-			\includegraphics[scale=0.7]{files/Chapter4/Convergence.png}
-		\end{adjustbox}
-		\caption{Rate of convergence of the first 20 eigenvalues.}
-		\label{fig:conv_2d_eig}
-	\end{figure}
-
-	Figure \ref{fig:conv_2d_eig} shows the rate of convergence of the first 20 eigenvalues of the two-dimensional beam. Each color represents a spesific eigenvalue.
-
-	The number of elements are chosen so that at least the first 10 eigenvalues are accurate to 5 significant digits.
-
-	\subsection{Comparing the mode shapes}
-	Recall from the introduction, that the investigation is focussed on beam-type problems.
-The two-dimensional model is for an eigenvalue problem and and not specific to beam-type applications, like the Timoshenko beam model.
-Therefore there are non-beam type modes that can be expected from the two-dimensional model.
-This is also be reflected in the eigenvalues of the two-dimensional model and therefore eigenvalues irrelevant to beam-type problems exits.
-
-	Therefore a method is required to compare and match the eigenvalues of the two models.
-In \cite{LVV09}, the authors compare the mode shapes of the two models, to match up the eigenvalues.
-Eigenvalues relating to the mode shapes similar to the mode shapes of the Timoshenko beam, are called beam-type eigenvalues.
-The other eigenvalues are called non-beam type eigenvalues by the authors.
-
-	\subsubsection{Shapes relating to beam-type eigenvalues}
-	The following figures are examples of beam-type mode shapes for the displacement $w$.
-
-	\begin{figure}[h!]
-		\scalebox{.8}{
-			\makebox[\textwidth][c]{
-				\centering
-				\begin{minipage}[b]{0.8\linewidth}
-					\includegraphics[width=1\linewidth]{files/Chapter4/Beam1.jpg}
-					\subcaption{2D Beam Type - $\lambda_6 = 21.911$}
-					\label{fig:minipage2}
-				\end{minipage}
-				\begin{minipage}[b]{0.8\linewidth}
-					\includegraphics[width=1\linewidth]{files/Chapter4/1DBeam2.png}
-					\subcaption{Timoshenko - $\lambda_5 = 21.794$}
-					\label{fig:minipage1}
-				\end{minipage}
-		}}
-		\scalebox{.8}{
-			\makebox[\textwidth][c]{
-				\begin{minipage}[b]{0.8\linewidth}
-					\includegraphics[width=1\linewidth]{files/Chapter4/Beam2.jpg}
-					\subcaption{2D Beam Type - $\lambda_7 = 45.711$}
-					\label{fig:minipage2}
-				\end{minipage}
-				\begin{minipage}[b]{0.8\linewidth}
-					\includegraphics[width=1\linewidth]{files/Chapter4/1DBeam1.png}
-					\subcaption{Timoshenko - $\lambda_6 = 45.390$}
-					\label{fig:minipage1}
-				\end{minipage}
-				\caption{Modal shapes of the displacement $w$ for the beam-type 2D body and the Timoshenko beam with $\alpha = 4800$ ($h = 1/20$).}
-			}
-		}
-	\end{figure}
-	\FloatBarrier
-
-	\subsubsection{Shapes relating to non-beam type eigenvalues}
-	The following figures are examples of non beam-type mode shapes for the displacement $w$. These mode shapes are not present in the cantilever Timoshenko beam model and are not beam related. 
-	\begin{figure}[h!]
-		\scalebox{.8}{
-			\makebox[\textwidth][c]{
-				\centering
-				\begin{minipage}[b]{0.8\linewidth}
-					\includegraphics[width=1\linewidth]{files/Chapter4/NotBeam1.jpg}
-					\subcaption{Non-Beam Type - $\lambda_4 = 7.7077$}
-					\label{fig:minipage2}
-				\end{minipage}
-				\begin{minipage}[b]{0.8\linewidth}
-					\includegraphics[width=1\linewidth]{files/Chapter4/NotBeam2.jpg}
-					\subcaption{Non-Beam Type - $\lambda_8 = 69.344$}
-					\label{fig:minipage1}
-				\end{minipage}
-				\caption{Modal shapes of the displacement $w$ for the non-beam type 2D body with $h = 1/20$.}
-			}
-		}
-	\end{figure}
-	\FloatBarrier
-
-	\subsubsection{Shape of the cross-sections}
-	The Timoshenko beam theory improve some one-dimensional beam theories such as the Euler-Bernoulli beam theory by also including the effect of shear.
-For Timoshenko beam theory it is assumed that the cross-sections need not remain perpendicular to the neutral axis of the beam.
-The cross-sections however remain a straight line.
-
-	For the two-dimensional beam, the shape of the cross-section can deform into a S-shape. This is explained in \cite{LVV09} and a similar figure in \cite{LVV09} is given here.
-
-	\FloatBarrier
-	\begin{figure}[h!]
-		\centering
-		\begin{tikzpicture}[scale=1.2]
-
-		\draw[line width = 0.4mm] (0,1) -- (7,1);
-		\draw[line width = 0.4mm] (0,-1) -- (7,-1);
-		\draw[line width = 0.4mm] (7,-1) -- (7,1);
-		\draw[line width = 0.4mm] (0,-1) -- (0,1);
-
-		\draw[line width = 0.1mm,dashed] (3.5,1) -- (3.5,-1);
-
-		\draw[thick] plot [smooth,tension=0.9] coordinates{(3.3,1) (3.7,0.5) (3.5,0) (3.3,-0.5) (3.7,-1)};
-
-		\draw[line width = 0.2mm,red] (3.3,1) -- (3.7,-1);
-
-	\end{tikzpicture}
-		\caption{S-shape deformation of the cross-section of the two-dimensional beam.}\label{fig:s}
-	\end{figure}
-	\FloatBarrier
-
-	Note that figure \ref{fig:s} shows an exaggerated example of the deformation of a cross-section.
-The red line shows how the authors of \cite{LVV09} calculated the average rotation of a cross-section of the two-dimensional beam.
-This average rotation can be used to compare the rotation of the cross-section of the two-dimensional beam to the rotation of the cross-section of the Timoshenko beam given by $\phi$.
-
-	\subsubsection{Direct comparison of mode shapes}
-	Figure \ref{fig:w} directly compares a mode shape of the Timoshenko beam to a mode shape of the two-dimensional beam.
-For the two-dimensional model, the center line of the displacement of the beam is shown.
-For the Timoshenko beam, the displacement $w$ is shown.
-
-	\begin{figure}[ht!]
-		\scalebox{.8}{
-			\makebox[\textwidth]{
-				\centering
-				\centering
-				\includegraphics[scale=0.4]{files/Chapter4/1Dv2D.png}
-				\caption{Comparison of the displacement $w$ mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
-				\label{fig:w}}}
-	\end{figure}
-	\FloatBarrier
-
-	Similarly, figure \ref{fig:phi} directly compares the angle of the cross-section of the Timoshenko beam and the two-dimensional beam.
-The average rotation of the cross-section of the two-dimensional beam's mode shape is calculated as shown in figure \ref{fig:s}.
-
-	\FloatBarrier
-	\begin{figure}[ht!]
-		\scalebox{.8}{
-			\makebox[\textwidth]{
-				\centering
-				\centering
-				\includegraphics[scale=0.4]{files/Chapter4/1Dv2Dphi.png}
-				\caption{Comparison of the angle $\phi$ (best fit for 2D Beam) mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)}
-				\label{fig:phi}}}
-	\end{figure}
-	\FloatBarrier
-
-	These figures are examples that show how similar the mode shapes of the two models are.
-This specific example is for $\alpha = 4800$, which represents a typical beam.
-The authors of \cite{LVV09} obtained similar results for $\alpha=300$, which represents a short and thick beam.
-
-	\textbf{Remark:} Note that the overall shape is important.
-This is because any multiple of a eigenvector is still an eigenvector.
-The mode shapes were specifically scaled to obtain figures \ref{fig:w} and \ref{fig:phi}.
-
-	\subsection{Comparing the eigenvalues}
-	Using this method of comparing the mode shapes, the eigenvalues can now be matched up and compared. In the tables, Timo refers to the Timoshenko beam and 2D refers to the two-dimensional beam.
-
-	\subsubsection{Some results from [LVV09]}
-	The following table contains results from \cite{LVV09} verbatim to 3 significant digits, as well as the replicated results to 5 significant digits.
-
-	\begin{table}[!ht]
-		\centering
-		\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
-		\begin{tabular}{|c|c|c||c|c|c|}
-			\hline
-			\multicolumn{3}{|c||}{Results from [LVV09]} & \multicolumn{3}{c|}{Dissertation} \\ \hline \hline
-			~ & 2D & Timo & ~ & 2D & Timo  \\ \hline
-			1 & 0.0317 & 0.0316 & 1 & 0.031713 & 0.031639  \\ 
-			2 & 1.14 & 1.14  & 2 & 1.1413 & 1.1365  \\ 
-			3 & 7.72 & - & 3 & 7.7161 & - \\ 
-			4 & 7.92 & 7.86 &  4 & 7.918 & 7.8617    \\ 
-			5 & 26.2 & 25.9 & 5 & 26.148 & 25.869   \\ 
-			6 & 60.8 & 59.9 & 6 & 60.816 & 59.946  \\ 
-			7 & 69.3 & - & 7 & 69.344 & -  \\ 
-			8 & 115 & 113 &  8 & 115.28 & 113.23   \\ 
-			9 & 192 & 188 &  9 & 191.57 & 187.55   \\ 
-			10 & 192 & - & 10 & 192.03 & -  \\ 
-			11 & 291 & 284 & 11 & 290.76 & 283.81   \\ \hline
-		\end{tabular}\label{Results_LVV09}
-	\end{table}
-
-	\begin{comment}
-	\begin{table}[!ht]
-		\centering
-		\caption{Results from [LVV09] and results obtained in this dissertation. $0^*$ indicates a 0 as a result of rounding. $\alpha = 1200$.}
-		\begin{tabular}{|c|c|c|c||c|c|c|c|}
-			\hline
-			\multicolumn{4}{|c||}{Results from [LVV09]} & \multicolumn{4}{c|}{Dissertation} \\ \hline \hline
-			~ & 2D & Timo & RE & ~ & 2D & Timo & RE  \\ \hline
-			1 & 0.0317 & 0.0316 & 0.00315 & 1 & 0.031713 & 0.031639 & 0.0023407  \\ 
-			2 & 1.14 & 1.14 & $0^*$ & 2 & 1.1413 & 1.1365 &  0.0042050 \\ 
-			3 & 7.72 & - & ~ & 3 & 7.7161 & - &   \\ 
-			4 & 7.92 & 7.86 & 0.00758 & 4 & 7.918 & 7.8617 & 0.0071116    \\ 
-			5 & 26.2 & 25.9 & 0.0115 & 5 & 26.148 & 25.869 & 0.010669  \\ 
-			6 & 60.8 & 59.9 & 0.0148 & 6 & 60.816 & 59.946 & 0.014303  \\ 
-			7 & 69.3 & - & ~ & 7 & 69.344 & - &    \\ 
-			8 & 115 & 113 & 0.0174 & 8 & 115.28 & 113.23 &  0.017787  \\ 
-			9 & 192 & 188 & 0.0208 & 9 & 191.57 & 187.55 &  0.020999  \\ 
-			10 & 192 & - &  & 10 & 192.03 & - &   \\ 
-			11 & 291 & 284 & 0.0241 & 11 & 290.76 & 283.81 &  0.023899  \\ \hline
-		\end{tabular}\label{Results_LVV09}
-	\end{table}
-	\end{comment}
-
-	This table shows that the results obtained in this dissertation are very similar to the results obtained in \cite{LVV09}. This is for a specific case where $\alpha = 1200$.
-
-	In the following table, the eigenvalues for different values of $\alpha$ are compared.
-
-	\begin{table}[h!]
-		\scalebox{.8}{
-		\makebox[\textwidth]{
-		\caption{Eigenvalues of a Timoshenko cantilever beam vs the eigenvalues of a cantilever two-dimensional elastic body. *RE is the relative error.}
-		\begin{tabular}{|cccc||cccc||cccc||cccc|}
-			\hline
-			\multicolumn{16}{|c|}{Comparison of Eigenvalues} \\
-			\hline\hline
-			\multicolumn{4}{|c||}{ $h = 1/5$ or $\alpha = 300$}       & \multicolumn{4}{c||}{$h =1/10$ or $\alpha = 1200$}      & \multicolumn{4}{c||}{$h = 1/20$ or $\alpha = 4800$}      & \multicolumn{4}{c|}{$h = 1/30$ or $\alpha = 10800$} \\
-			\hline
-			{i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} \\
-			\hline
-			{1}&0.12151&1&0.12092&1&0.031713&1&0.031639&1&0.008013&1&0.008004&1&0.003568&1&0.003565\\
-			{2}&3.5460&2&3.5071&2&1.1413&2     & 1.1365 & 2     & 0.30756 & 2     & 0.30705 & 2     & 0.13869 & 2     & 0.13855 \\
-			\cellcolor{lightgray}{3} & \cellcolor{lightgray}{7.7311} &       & {-} & \cellcolor{lightgray}{3}     & \cellcolor{lightgray}{7.7161} &       & {-} & 3     & 2.3273 & 3     & 2.3213 & 3     & 1.0698 & 3     & 1.0683 \\
-			{4} & 20.225 & 3     & 19.869 & 4     & 7.9180 & 3     & 7.8617 & \cellcolor{lightgray}{4}     & \cellcolor{lightgray}{7.7077} &       & {-} & 4     & 4.0140 & 4     & 4.0058 \\
-			{5} & 56.109 & 4     & 54.766 & 5     & 26.148 & 4     & 25.869 & 5     & 8.5086 & 4     & 8.4762 & \cellcolor{lightgray}{5}     & \cellcolor{lightgray}{7.7047} &       & {-} \\
-			\cellcolor{lightgray}{6} & \cellcolor{lightgray}{69.164} &       & {-} & 6     & 60.816 & 5     & 59.946 & 6     & 21.911 & 5     & 21.794 & 6     & 10.655 & 5     & 10.625 \\
-			{7} & 114.03 & 5     & 110.75 & \cellcolor{lightgray}{7}     & \cellcolor{lightgray}{69.344} &       & {-} & 7     & 45.711 & 6     & 45.390 & 7     & 22.975 & 6     & 22.890 \\
-			{8} & {189.17} &  6     & {186.50} & 8     & 115.28 & 6     & 113.23 & \cellcolor{lightgray}{8}     & \cellcolor{lightgray}{69.344} &       & {-} & 8     & 43.113 & 7     & 42.909 \\
-			\cellcolor{lightgray}{9} & \cellcolor{lightgray}{192.61} &      &  & {9}     & {191.57} &   7  & {187.55} & 9     & 82.887 & 7     & 82.154 & \cellcolor{lightgray}{9}     & \cellcolor{lightgray}{69.331} &       & {-} \\
-			{10} & 285.85 & 7     & 277.64 & \cellcolor{lightgray}{10}    & \cellcolor{lightgray}{192.03} &      & {-} & 10    & 136.03 & 8     & 134.58 & 10    & 73.230 & 8     & 72.803 \\
-			{11} & 328.40 & 8     & 330.29 & 11    & 290.76 & 8     & 283.81 & \cellcolor{lightgray}{11}    & \cellcolor{lightgray}{192.48} &       & {-} & 11    & 115.41 & 9     & 114.61 \\
-			\cellcolor{lightgray}{12} & \cellcolor{lightgray}{357.08} &       & {-} & \cellcolor{lightgray}{12}    & \cellcolor{lightgray}{374.45} &       & {-} & 12    & 207.29 & 9     & 204.69 & 12    & 171.61 & 10    & 170.20 \\
-			{13} & 397.33 & 9     & 394.02 & 13    & 413.20 & 9     & 402.27 & 13    & 298.38 & 10    & 294.10 & \cellcolor{lightgray}{13}    & \cellcolor{lightgray}{192.52} &       & {-} \\
-			{14} & 442.00   & 10    & 439.52 & 14    & 558.67 & 10    & 542.65 & \cellcolor{lightgray}{14}    & \cellcolor{lightgray}{376.83} &       & {-} & 14    & 243.56 & 11    & 241.26 \\
-			\cellcolor{lightgray}{15} & \cellcolor{lightgray}{533.71} &       & {-} & \cellcolor{lightgray}{15}    & \cellcolor{lightgray}{614.11} &       & {-} & 15    & 410.63 & 11    & 404.01 & 15    & 332.83 & 12    & 329.28 \\
-			{16} & 538.97 & 11    & 541.55 & 16    & 726.26 & 11    & 704.15 & 16    & 545.03 & 12    & 535.32 & \cellcolor{lightgray}{16}    & \cellcolor{lightgray}{377.16} &       & {-} \\
-			\cellcolor{lightgray}{17} & \cellcolor{lightgray}{596.06} &       & {-} & \cellcolor{lightgray}{17}    & \cellcolor{lightgray}{906.28} &       & {-} & \cellcolor{lightgray}{17}    & \cellcolor{lightgray}{621.95} &       & {-} & 17    & 440.77 & 13    & 435.51 \\
-			{18} & 602.77 & 12    & 596.09 & 18    & 913.69 & 12    & 884.92 & 18    & 702.30 & 13    & 688.64 & 18    & 568.51 & 14    & 561.04 \\
-			\cellcolor{lightgray}{19} & \cellcolor{lightgray}{657.87} &       & {-} & 19    & 1113.7 & 13    & 1080.1 & 19    & 882.95 & 14    & 864.40 & \cellcolor{lightgray}{19}    & \cellcolor{lightgray}{623.05} &       & {-} \\
-			{20} & 717.37 & 13    & 731.74 & \cellcolor{lightgray}{20}    & \cellcolor{lightgray}{1218.0}  &       & {-} & \cellcolor{lightgray}{20}    & \cellcolor{lightgray}{927.18} &       & {-} & 20    & 717.04 & 15    & 706.74 \\
-			\hline
-			\multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{3.1718\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{3.1486\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{2.1018\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{1.4361\%} \\
-			\hline
-		\end{tabular}%
-		\label{tab:Timo}%
-	}
-	}
-	\end{table}%
-	\FloatBarrier
-
-	This table shows that the eigenvalues of the Timoshenko model and the two-dimensional model compare very well.
-The non-beam type eigenvalues are highlighted in grey.
-For a short thick beam ($\alpha = 300$), the maximum relative error for the first 20 two-dimensional eigenvalues is just over $3\%$, while for a long thin beam ($\alpha = 10800$), the maximum relative error is just over $1\%$.
-This shows that as the beam becomes longer and thinner, the Timoshenko beam is better approximation of the two-dimensional beam.
-But overall the Timoshenko beam compares very well.
-
-	This table also shows that as the beam gets more narrow, there are less non-beam type eigenvalues within the first few eigenvalues.This would also indicate that the Timoshenko beam would be a better approximation of the two-dimensional beam as the beam gets more narrow since the two-dimensional model behaves `more like a beam'.
-
-\section{Validity of a model for a cantilever two-dimensional beam} \label{sec:validity-of-a-2d-beam}
-In this section, we compare the two-dimensional cantilever beam with a three-dimensional cantilever beam.
-
-Figure \ref{fig:2Dv3D} shows the two beams, Problem 2D and Problem 3D side-by-side.
-
-\FloatBarrier
-\begin{figure}[h!]
-	\scalebox{.8}{
-		\makebox[\textwidth][c]{
-			\caption{Side-by-side comparison of the beams.}
-			\label{fig:2Dv3D}
+
 			\centering
@@
 				\end{tikzpicture}
-				\subcaption{Two-Dimensional Elastic Body}
 			\end{minipage}
@@
 					\node at (3.2,-1.2) {$\ell = 1$};
-
 				\end{tikzpicture}
-				\subcaption{Three-Dimensional Elastic Body}
 
@@
 \end{figure}
-\FloatBarrier
-
-\subsection{Calculating the eigenvalues and mode shapes}
-The eigenvalues and mode shapes of the two models are calculated using the computer program.
-The eigenvalues and mode shapes are then compared to determine the accuracy of the two-dimensional model for the cantilever beam.
-The accuracy of the eigenvalues depends on the number of elements employed in the finite element method.
-For the two-dimensional model, accuracy reaches at least five significant digits for the first 10 eigenvalues, while the three-dimensional model achieves at least four significant digits for its first 10 eigenvalues.
+
+\subsection{Calculating the eigenvalues}
+In section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived.
+Similar to the two-dimensional case in \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the Finite Element Method is used to calculate the eigenvalues of the three-dimensional beam.
+The eigenvalue problem for both models have the same form, but different matrices.
+
+\subsubsection{Problem 2DE and 3D-1E}
+Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
+\begin{eqnarray}
+	K\bar{u} & = & M\lambda{\bar{u}},
+\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in section \ref{ssec:2DFEM:DE} for the Problem 2DE and section \ref{3d_fem_g} for Problem 3DE.
+
+\subsubsection{Accuracy of the eigenvalues of the three-dimensional model}
+Figure \ref{fig:conv_3d_eig} show the rate of convergence of the first 20 eigenvalues of Problem 3DE.
+
+\begin{figure}[H]
+    \centering
+        \includegraphics[scale=0.7]{files/Chapter6/convergence3d.png}
+
+    \label{fig:conv_3d_eig}
+\end{figure}
+
+Similar to the two-dimensional case, the number of elements can be chosen so that at least the first 20 eigenvalues are accurate to 4 significant digits.
+
+For the three-dimensional model, obtaining this level of accuracy can be difficult and computationally expensive.
+For the two-dimensional beam in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and the upcoming two-dimensional plate model in section \ref{sec:validity-of-a-plate} it is easier to get 5 significant digits of accuracy.
 
 \subsection{Comparing the mode shapes}
-Following \cite{LVV09}, the mode shapes of the two models are compared.
-As seen in \cite{LVV09}, the eigenvalues of the Timoshenko beam model (beam-type eigenvalues) are all present in the two-dimensional model.
-However not all the eigenvalues of the two-dimensional model are present in the Timoshenko beam model.
-These are called non-beam type eigenvalues.
-
-The same is observed for the three-dimensional model, as there are eigenvalues that are present in the three-dimensional model that are not present in the two-dimensional model.
-
-Therefore it is required to match the eigenvalues of the two models by comparing the mode shapes.
-
-\subsubsection*{Mode shapes relating to beam type eigenvalues.}
+To be able to compare the eigenvalues, the mode shapes of the two models are compared to match up the eigenvalues of the two models.
+This is the same approach as in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}.
+
+As seen in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the two-dimensional model as eigenvalues and eigenvectors that are not related to beam type problems.
+This is also true for the three-dimensional model, and it has even more non-beam type eigenvalues.
+
+The focus of the investigation remains on beam type problems.
+Below are some examples of the mode shapes for beam type eigenvalues, mode shapes for non-beam type eigenvalues that are shared between the two and three-dimensional models and also mode shapes for non-beam type eigenvalues that are only present in the three-dimensional model.
+
+\subsubsection{Mode shapes relating to beam type eigenvalues.}
 Figure \ref{fig:beam-2dv3d} show some examples of beam type mode shapes for the displacement $u$.
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/3D12.png}
-				\subcaption{3D Beam Type - $\lambda_{12} = 2.3293$}
-				\label{fig:minipage2}
 			\end{minipage}
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/2D3.png}
-				\subcaption{2D Beam Type - $\lambda_3 = 2.3273$}
-				\label{fig:minipage1}
 			\end{minipage}
-	}}
+	    }
+    }
 	\scalebox{.8}{
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/3D22.png}
-				\subcaption{3D Beam Type - $\lambda_{24} = 21.929$}
-				\label{fig:minipage2}
 			\end{minipage}
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/2D6.png}
-				\subcaption{2D Beam Type - $\lambda_6 = 21.911$}
-				\label{fig:minipage1}
 			\end{minipage}
-			\caption{Mode shapes of the displacement $u$ with $h=1/20$.}
-			\label{fig:beam-2dv3d}
-	}}
+	    }
+    }
 \end{figure}
-\FloatBarrier
-
-\subsubsection*{Mode shapes relating to non-beam type eigenvalues that are present in the two-dimensional model.}
+
+\subsubsection{Mode shapes relating to non-beam type eigenvalues that are present in the two-dimensional model.}
 Figure \ref{fig:nonbeam-2dv3d} show examples of mode shapes relating to non-beam type eigenvalues for the displacement $u$.
 
-\FloatBarrier
 \begin{figure}[h!]
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/3D33.png}
-				\subcaption{3D Non-Beam Type - $\lambda_{33} = 69.374$}
-				\label{fig:minipage2}
 			\end{minipage}
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/2D8.png}
-				\subcaption{2D Non-Beam Type - $\lambda_8 = 69.344$}
-				\label{fig:minipage1}
 			\end{minipage}
-			\caption{Mode shapes of the displacement $u$ with $h=1/20$.}
-			\label{fig:nonbeam-2dv3d}
-	}}
+	    }
+    }
 \end{figure}
-\FloatBarrier
-
-\subsubsection*{Mode shapes relating to non-beam type eigenvalues that are not present in the two-dimensional model.}
+
+\subsubsection{Mode shapes relating to non-beam type eigenvalues that are not present in the two-dimensional model.}
 Figure \ref{fig:nonbeam-2dv3d} show examples of mode shapes relating to non-beam type eigenvalues for the displacement $u$ which are not present in the two-dimensional model.
 These mode shapes only appear in the three-dimensional beam.
-\FloatBarrier
+
 \begin{figure}[h!]
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/3DNonBeam10.png}
-				\subcaption{Non-2D Type - $\lambda_{10}$}
-				\label{fig:minipage2}
 			\end{minipage}
@@
 				\includegraphics[width=1\linewidth]{files/Chapter6/3DNonBeam11.png}
-				\subcaption{Non-2D Type - $\lambda_{11}$}
-				\label{fig:minipage11}
 			\end{minipage}
-			\caption{Mode shapes of the displacement $u$ with $h=1/20$.}
-
-	}}
+        }
+    }
 \end{figure}
-\FloatBarrier
 
 \subsection{Comparing the eigenvalues}
-For a realistic comparison of the models, it's crucial to carefully select parameters $h$ and $b$, representing the beam's height and width, respectively, noting that the two-dimensional model lacks the width parameter $b$.
-
-Values for $h$ span a range from short, thick beams ($h = 1/5$) to long, slender beams ($h = 1/20$), capturing two realistic scenarios.
-Regarding $b$, it's considered in two scenarios: when $b \leq h$ and when $b > h$, with $b$ expressed as a multiple of $h$.
-This distinction influences the results.
-
-Results will cover all shared eigenvalues between the models, highlighting non-beam type eigenvalues in grey.
-Non-beam type eigenvalues unique to either model are excluded, but eigenvalue numbering will proceed as if they were included.
+
+For a realistic comparison of the models, the parameters need to be chosen carefully.
+The parameters are $h$ representing the height of the beam and $b$ representing the width of the beam.
+The two-dimensional model does not have the width parameter.
+
+For $h$, the values used in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} will be used.
+These values covers a range of beam shapes from a short thick beam, to a long slender beam.
+two cases are selected that represents realistic cases.
+For a short and thick beam, consider $h = 1/5$ and for a long and slender beam, consider $h = 1/20$.
+
+For the parameter $b$, two different cases will be considered.
+The first case is for $b \leq h$, and the $b > h$.
+The distinction of these two cases will become apparent in the results.
+It is important to note that the parameter $b$ will be expressed as a multiple of $h$.
+
+All of the results will include all the eigenvalues shared between the two-models, including not beam type eigenvalues.
+The non-beam type eigenvalues will be highlighted in grey.
+The non-beam type eigenvalues that are not shared between the two models will be excluded from the results, but the numbering of the eigenvalues will be kept as if they were included.
 
@@
 	\makebox[\textwidth]{
-		\caption{Comparsion of Eigenvalues with $h = 1/5$, with decreasing $b$ and $b < h$.}
 		\begin{tabular}{|cc|cc|cc|cc||cc|}
@@
 			\hline
-		\end{tabular}%
-		\label{tab:2v3_1}%
-	}}
+		\end{tabular}
+	    }
+    }
 \end{table}%
-\FloatBarrier
+
 \label{sym:RE}
@@
 	\centering
-	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/5$.}
 	\begin{tabular}{|c|cccc|}
@@
 	\makebox[\textwidth]{
-	\caption{Comparsion of Eigenvalues with $h = 1/20$, with decreasing $b$ and $b < h$.}
 	\begin{tabular}{|cc|cc|cc|cc||cc|}
@@
 	\label{tab:2v3_2}%
-}}
+    }
+}
 \end{table}%
-\FloatBarrier
 
@@
 	\centering
-	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$}
+
 	\begin{tabular}{|c|cccc|}
@@
 \end{table}%
-\FloatBarrier
-
-Tables \ref{tab:2v3_1} and \ref{tab:2v3_2} show that the first 20 eigenvalues of the two-dimensional model closely match those of the three-dimensional beam for $b \leq h$.
-As width $b$ decreases, the two-dimensional model approximates the three-dimensional model more accurately.
-The comparison is notably better for the slender beam with $h = 1/20$ than for the thick beam with $h = 1/5$, though both comparisons are strong.
-
-The tables also indicate an increase in non-beam type eigenvalues in the three-dimensional model as both $b$ and $h$ decrease.
-
-Tables \ref{tab:2Dv3D_1_breakup} and \ref{tab:2v3_2_split} show the maximum relative error for beam type and non-beam type eigenvalues, confirming the close comparison of beam type eigenvalues.
+
+Tables \ref{tab:2v3_1} and \ref{tab:2v3_2} show that the first 20 eigenvalues two-dimensional model compares very well to the matching eigenvalues three-dimensional beam for $b<=h$.
+As the width $b$ decreases, the two-dimensional model becomes a better approximation of the three-dimensional model.
+Also shown is that the slender beam with $h = 1/20$ compares better than the thick beam where $h = 1/5$, event though the case of $h=1/5$ is still a very good comparison.
+
+The tables also shows that the three-dimensional model has more non-beam type eigenvalues as the width $b$ decreases, as well as when the width $h$ decreases.This is different from the two-dimensional model as seen in \ref{sec:validity-of-a-cantilever-timoshenko-beam}.
+
+Tables \ref{tab:2Dv3D_1_breakup} and \ref{tab:2v3_2_split} breaks up the maximum relative error for the beam type and non-beam type eigenvalues.
+These tables confirm that the the beam type eigenvalues compare very well.
 
@@
 
-\FloatBarrier
 \begin{table}[htbp]
@@
 	\makebox[\textwidth]{
-		\caption{Comparsion of Eigenvalues with $h = 1/5$, with increasing $b$ and $b > h$}
 		\begin{tabular}{|cc|cc|cc||cc|}
@@
 		\label{tab:b>h}%
-	}}
+	    }
+    }
 \end{table}
-\FloatBarrier
-
-\FloatBarrier
+
 \begin{table}[htbp]
 	\centering
-	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/5$}
+
 	\begin{tabular}{|c|ccc|}
@@
 \end{table}%
-\FloatBarrier
 
@@
 	\makebox[\textwidth]{
-		\caption{Comparsion of Eigenvalues with $h = 1/20$, with increasing $b$ and $b > h$}
 		\begin{tabular}{|cc|cc|cc||cc|}
@@
 		\end{tabular}%
-		\label{tab:b>h_20}%
-	}}
+	    }
+    }
 \end{table}
-\FloatBarrier
-
-\FloatBarrier
+
 \begin{table}[htbp]
 	\centering
-	\caption{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$}
+
 	\begin{tabular}{|c|ccc|}
@@
 \end{table}%
-\FloatBarrier
-
-Tables \ref{tab:b>h} and \ref{tab:b>h_20} indicate that the two-dimensional model's accuracy declines when $b$ significantly exceeds $h$, a trend also observed for beam type eigenvalues in Tables \ref{tab:b>h-split} and \ref{tab:b>h-split_20}.
-Particularly for $h=1/5$, obtaining reliable eigenvalues numerically was challenging.
-
-These results comprehensively assess the two-dimensional cantilever beam model against the three-dimensional counterpart, demonstrating good agreement across a broad spectrum of beam shapes, especially in scenarios representing realistic cases.
-
-The key takeaway is the critical role of beam shape: the two-dimensional model performs excellently when $b \leq h$, particularly for slender beams, but less so for short, thick beams.
-The model's accuracy rapidly deteriorates as $b$ surpasses $h$, affecting both slender and short, thick beams, with the latter posing challenges in numerical eigenvalue calculation.
-
-For practical applications, a beam model's suitability is questionable when $b > h$, suggesting alternative approaches like plate models for more accurate representation.
-The next section explores the Reissner-Mindlin plate model's validity using a similar analysis.
+
+Tables \ref{tab:b>h} and \ref{tab:b>h_20} show that the two-dimensional model compares less well to the three-dimensional model when $b$ is too much larger than $h$.
+Tables \ref{tab:b>h-split} and \ref{tab:b>h-split_20} show that this is also true for the beam type eigenvalues.
+
+For the case of $h=1/5$, it was also more difficult to obtain reliable eigenvalues using a numerical method.
+
+These results gives a detailed overview of the validity of the cantilever two-dimensional beam compared to the cantilever three-dimensional beam.
+The results show that the two-dimensional beam model compares very well to the three-dimensional beam model for a large range of beam shapes.
+The results shown were chosen to represent realistic cases, and the results are similar for other cases.
+
+The overall conclusion is that the shape of the beam is very important.
+If the width $b$ is equal to or less than the height $h$, the two-dimensional beam model compares very well to the three-dimensional beam model.
+More so when the beam is slender, and less so when the beam is short and thick.
+
+When the width $b$ is larger than the height $h$, the two-dimensional beam the comparison degrades very quickly.
+This is true for both slender and short and thick beams, although with short and thick beams, it is more difficult to obtain reliable eigenvalues using a numerical method.
+
+For practical applications, if $b > h$ the use of a beam model must be brought into question.
+Other models such as a plate model will be better suited as it is a more realistic model.
+In the next section, the validity of the Reissner-Mindlin plate mode is investigated using the same method of this section.
 
 \section{Conclusion}
-In this article, we explored the validity of a two-dimensional cantilever beam model by comparing it with a three-dimensional cantilever beam model.
-Using the Finite Element Method, we obtained the eigenvalues and eigenvectors for both models, aligning them through mode shape comparisons.
-
-The models were given in a dimensionless variational form, and we demonstrated how the two-dimensional model could be derived from the three-dimensional model as a specific case of plane stress.
-
-While we did not delve into the well-posedness of the models in detail, we cited necessary references.
-The principle of modal analysis was illustrated with a general example, proving essential for comparing the two models.
-This comparison's application is evident in the numerical results presented in this article.
-
-Applying the Finite Element Method to both models, we developed a numerical formula for solving the eigenvalue problems.
-A computer program was then used to extract the eigenvalues and eigenvectors for each model.
-
-Upon comparing the eigenvalues through mode shapes, our findings suggest that the two-dimensional beam model aligns well with the three-dimensional model for various beam shapes.
-However, the shape of the beam is pivotal to the comparison's accuracy.
-The two-dimensional model shows the best correlation with thin and long three-dimensional beams and less so with short and thick beams.
-Notably, the two-dimensional model does not align well when the beam's width $b$ exceeds its height $h$, suggesting that a plate model may be more appropriate in such cases and can be explored in future work.
-
-\bibliographystyle{elsarticle-harv}
-\bibliography{references}
+his chapter is an extension of the work of Section 4.5. In Section 4.5, the validity of the Timoshenko beam theory is investigated by comparing a Timoshenko beam model to a two-dimensional beam model.
+
+In real-world applications, a beam is a three-dimensional model.
+Therefore it should be more realistic to use a three-dimensional model to investigate the validity of the Timoshenko beam theory.
+This is mentioned by the authors of \cite{LVV09}.
+Their suggestion is to use the two-dimensional model as an intermediate step, to avoid complexities.
+Therefore the validity of the two-dimensional model is investigated, using a three-dimensional beam model as a reference.
+Again the results so that the comparison relies on the shape of the beams.
+The two-dimensional model compares well to the three-dimensional beam if the beam is not wide.
+
+If the width of the beam is very large, the use of a beam model can be questioned.
+A plate model might be more suited.
+Therefore the last section of this chapter investigates the validity of the Reissner-Mindlin plate model.
+The Reissner-Mindlin plate model is compared to a three-dimensional plate model.
+The results show that the Reissner-Mindlin plate model compares well to the three-dimensional plate model.
+
+The same method is used in this chapter as in Section 4.5.
+The mode shapes are sketched and matched.
+The corresponding eigenvalues can then be matched up and compared.
+The eigenvalues relating to the Reissner-Mindlin plate model are referred to as plate-type eigenvalues.
+
+\section{Contributions}
+
+There are four models used in this dissertation. For each of the models, the dimensionless variational form is derived. Also presented are the model problems that are used in this dissertation.
+
+The first result investigates the existence and uniqueness of solutions for general vibration problems.
+The article that is discussed proves this result for a general vibration problem, using four assumptions.
+To explain the theory, an example is presented using one of the model problems of the dissertation.
+The cantilever Timoshenko beam model is chosen for the simple boundary conditions, as well as it's recurring importance in this dissertation.
+The weak variational form of the model is derived as well as the function spaces defined.
+This is presented in the same format as the general vibration problem.
+In fact all the models in this dissertation are special cases of this general vibration problem.
+The theory is then applied to this example problem, as a demonstration.
+To apply the theory, the four assumptions are proven to be true.
+
+The next result looks at modal analysis.
+Before the general case is discussed, again the cantilever Timoshenko beam is used to illustrated the concept of modal analysis.A trial solution to the boundary value problem is suggested.
+This trial solution is substituted into the partial differential equation and two problems are obtained.
+The first problem is the eigenvalue problem and the second is an ordinary differential equation.
+The eigenvalue problem can be solved with theory discussed later in the dissertation and the ordinary differential equation can then be solved.
+Substation of these two results into the boundary value problem confirms that the trial solution is correct.
+The same idea is then discussed for the general case.
+
+We then look at the convergence of the Galerkin Approximation for our general vibration problem.
+The results of the article discussed are updated with improved notation using a different article.
+The general case of the Galerkin approximation use a lot of symbols that are not immediately obvious, so again the cantilever Timoshenko beam model problem is used and the Galerkin Approximation is derived in an attempt to explain some of the conventions.
+The results of the article are then discussed and presented.
+The results are presented in a concise and practical format to reduce the need to define any unnecessary symbols or notation.
+The results are also presented in four theorems, summarizing the results of the article that are important but that are not necessarily presented as a theorem in the article.
+
+The next result is on the convergence of the eigenvalues and eigenfunctions of a general vibration problem when using the Finite Element Method.
+The results are from a textbook.
+The results are presented with updated notation, coinciding with the notation used in the dissertation.
+The results are also expanded and extra results are added in an attempt to better explain the theory.
+
+We then look at an important result for the Timoshenko beam theory.
+This provides a method to calculate the exact eigenvalues and eigenfunctions for the Timoshenko beam theory.
+Two examples are then used, a cantilever beam and a free-free beam, as an example of the application of the theory.
+The eigenvalues are calculated and the corresponding mode shapes are plotted.
+To obtain these results, the equation of motion is plotted, the isolation intervals are determined and the eigenvalues are then calculated using interval division to a desired level of accuracy.
+The mode shapes can then also be plotted with back substitution.
+These examples are important preparation for the main comparisons of this dissertation.
+We also discuss a result comparing the Timoshenko beam theory to results from an empirical study.
+We add to this article by giving the model problems.
+
+For the rest of the models in this dissertation, the two- and three-dimensional elastic bodies, and the Reissner-Mindlin plate model, a different approach is required to solve the eigenvalue problems.
+For these models we use the Finite Element Method.
+For each of the models, their reference configurations are given.
+All of the models are assumed to have a square cross-section and in a cantilever configuration.
+This reference configuration is then discretised into a grid of rectangular shaped elements.
+A set of admissable piecewise Hermite cubic functions are then used and each model is rewritten into a Galerkin Approximation.
+We the define the standard Finite Element Method Matrices for each case.
+These are referred to as the mass and stiffness matrices in engineering.
+Finally our boundary value problems are written into a system of ordinary differential equations in a matrix representation.
+At this point is it easy to derive the eigenvalue problem for each of the problems in this matrix form.
+This is in preparation for the main comparisons made in this dissertation.
+
+For our main comparisons, we first look at an article comparing a cantilever Timoshenko beam model to a cantilever two-dimensional model.
+We discuss the article and replicate the results.
+The eigenvalues and eigenfunctions of the Timoshenko beam model is obtained using the exact method already described.
+The eigenvalues and the eigenfunctions for the two-dimensional model are approximated using the Finite Element Method matrix representation of the eigenvalue problem.
+A MATLAB program is written to approximate the eigenvalues and plot the mode shapes.
+The accuracy of this approximation is also investigated by looking at the rate of convergence for different grid sizes.
+Following the article, the eigenvalues are matched up by first comparing the mode shapes of the two models.
+The eigenvalues can then be matched up and also any eigenvalues not relating to beam-type problems can be filtered out.
+Based on the results in modal analysis, only a few eigenvalues need to be considered.
+The relative error between the eigenvalues are then calculated for different shapes of beams.
+The results improve on the article by showing more significant digits and also including some more results.
+
+We then extend the results of the article to investigate the validity of a cantilever two-dimensional beam model as well as a cantilever Reissner-Mindlin plate model.
+The same method of the article is followed.
+To investigate the validity of a cantilever two-dimensional model, a cantilever three-dimensional model is considered.
+Since both of the models are not beam models, careful consideration needs to be taken to identify the eigenvalues.
+The same approach is used by comparing the mode shapes.
+For interest, the non-beam type eigenvalues shared between the two models are also included and the rest that the three-dimensional model does not share with the two-dimensional model are omitted.
+A clear distinction is made to show the beam type eigenvalues and the beam type results.
+The shape of the models are also carefully chosen to represent a variety of realistic cases that are interesting.
+The results show that the shape of the models play an important role in how well the models compare.
+An interesting result shows that this comparison is not good when the beam gets too wide.
+We therefore suggest a different model, like a plate model.
+This lead to the introduction of the Reissner-Mindlin plate model into this dissertation.
+The validity of a cantilever Reissner-Mindlin plate model is investigated using the same method.
+The cantilever three-dimensional plate model is again used as the reference model with the restriction that the body is wide.
+
+\section*{References}
+\bibliographystyle{plainnat}
+\bibliography{references.bib}
 

### 2024-04-07 files/Chapter1/1DModel.tex
appendix
review exam report

@@
     In this section we introduce the Timoshenko beam theory for the transverse vibration of a uniform beam.
-    For a reference of the model~\cite{Inm94}, and~\cite{Fu65} were used.\\
+    For a reference of the model~\cite{Timo21}, and~\cite{Fung65} were used.\\
 
@@
     \subsubsection*{Equations of motion}\label{sssec:1D_Model:EquationOfMotion}
-    \begin{align}
+    \begin{eqnarray}
         \rho A \partial_t^2 w &=& \partial_x V + Q, \label{eq:1D_Model:EquationOfMotion1}\\
         \rho I\partial_t^2 \phi  &=& V + \partial_x M. \label{eq:1D_Model:EquationOfMotion2}
-    \end{align}\label{sym:A}\label{sym:V}\label{sym:Iinertia}\label{sym:M}\label{sym:phiT}
+    \end{eqnarray}\label{sym:A}\label{sym:V}\label{sym:Iinertia}\label{sym:M}\label{sym:phiT}
     In~\eqref{eq:1D_Model:EquationOfMotion1} and \eqref{eq:1D_Model:EquationOfMotion2} $\rho$ denotes the density, $A$ is the area of a cross section, $I$ is the area moment of inertia, $M$ is the moment, $V$ is the shear force and $Q$ is an external force acting on the beam.
@@
     \subsubsection*{Dimensionless form}\label{sssec:1D_Model:DimensionlessForm}
-    As mentioned in subsection \ref{ssec:3D_Model:DimensionlessForm}, the same dimensionless scaling is used for all the models in this dissertation.\\
+    As mentioned in Subsection \ref{ssec:3D_Model:DimensionlessForm}, the same dimensionless scaling is used for all the models in this dissertation.\\
 
@@
 
-    Choose $t_0$ the same as in subsection \ref{ssec:3D_Model:DimensionlessForm}, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]
+    Choose $t_0$ the same as in Subsection \ref{ssec:3D_Model:DimensionlessForm}, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]
 
@@
         \frac{\beta}{\alpha} & = & \gamma
-    \end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in subsection \ref{ssec:3D_Model:DimensionlessForm}.\\
+    \end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in Subsection \ref{ssec:3D_Model:DimensionlessForm}.\\
 
-    \textbf{Remark} Recall that in subsection \ref{ssec:3D_Model:DimensionlessForm} the constant $G\kappa^2$ was used for the scaling of the stresses.
+    \textbf{Remark} Recall that in Subsection \ref{ssec:3D_Model:DimensionlessForm} the constant $G\kappa^2$ was used for the scaling of the stresses.
 

### 2024-04-07 files/Chapter1/2DModel.tex
review exam report

@@
 \subsubsection{Problem 2D-1}\label{sssec:2D_Model:Problem2D1}
-Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:\\
+Find a vector valued function $u$, satisfying equations \eqref{eq:2D_Model:EM} to \eqref{eq:2D_Model:CE} and the boundary conditions:
 
-Boundary Conditions:\\
 \begin{eqnarray*}
@@
 \subsection{Variational form}\label{ssec:2D_Model:VariationalForm}
-The steps to derive the variational form is almost identical to the case of the three-dimensional case. Therefore it is not shown again and only the differences are discussed. \\
+The steps to derive the variational form is almost identical to the three-dimensional case. Therefore it is not shown again and only the differences are discussed. \\
 
@@
  Applications are continued in Chapter 5 and 6.
-In Chapter 5, the finite element analysis is applied to a cantilever beam to solve the eigenvalue problem.
+In Chapter 5, the finite element method is applied to a cantilever beam to solve the eigenvalue problem.
 In Chapter 6, a cantilever beam in used in the comparison of our linear models.

### 2024-04-07 files/Chapter1/PlateModel.tex
review exam report

@@
 	\begin{eqnarray*}
-		{\psi} = \langle \psi_1 \  \psi_2\rangle = \langle \sin\phi \cos \theta \ \ \sin\phi \sin \theta\rangle.
+		{\psi} = \langle \psi_1, \ \psi_2\rangle = \langle \sin\phi \cos \theta, \ \sin\phi \sin \theta\rangle.
 	\end{eqnarray*}
@@
 	\begin{eqnarray*}
-		{\psi} = \langle \psi_1 \  \psi_2\rangle = \langle \phi \cos \theta \ \ \phi \sin \theta \rangle.
+		{\psi} = \langle \psi_1, \  \psi_2\rangle = \langle \phi \cos \theta, \ \phi \sin \theta \rangle.
 	\end{eqnarray*}
@@
 	Consider a Reissner-Mindlin plate with reference configuration $\Omega \in R^2$.
-Let $u \in \Omega$ define the transverse motion of the plate model and $\psi = \langle \psi_1 \ \psi_2 \rangle$ the angle between the material line and a line perpendicular to the plate.
+Let $u \in \Omega$ define the transverse motion of the plate model and $\psi = \langle \psi_1, \ \psi_2 \rangle$ the angle between the material line and a line perpendicular to the plate.
 
@@
 The parameter $q$ is an external force acting on the plate.
+$\mathbf{Q}$ is defined as part of the constitutive equations below.
 The moment density is defined as
@@
 	\subsubsection{Remark}
-	Similar to the model in section \ref{ssec:3D_Model:DimensionlessForm}, the constant $G$ is introduced to allow for the comparison of models in later chapters.
+	Similar to the model in Section \ref{ssec:3D_Model:DimensionlessForm}, the constant $G$ is introduced to allow for the comparison of models in later chapters.
 It will also be required that $\kappa$ is the same for the beam and plate models.
+
+	For convienience, the original notation is used for the dimensionless form.
 
@@
 
-	Some commonly used boundary (or edge) conditions are:\\
+	Some commonly used boundary (or edge) conditions are:
 
@@
 	\subsection{Model Problems}\label{ssec:P_Model:ModelProblems}
-	Let $\Omega \subset R^2$ denote reference configuration of the plate model. Following \cite{Wu05}, $\Omega$ is a rectangle.\\
+	Let $\Omega \subset R^2$ denote reference configuration of the plate model. Following \cite{Wu06}, $\Omega$ is a rectangle.
 
@@
 In this configuration, the plate is clamped at one edge and free hanging at the rest of the boundary.
-With out loss of generality, assume that the plate is clamped on the edge $\Sigma_0$.\\
+Without loss of generality, assume that the plate is clamped on the edge $\Sigma_0$.
 
-	Find functions $w$ and $\psi$ satisfying equations \eqref{eq:P_Model:EM1D} to \eqref{eq:P_Model:CE4D_chap1}, the boundary conditions.\\
+	Find functions $w$ and $\psi$ satisfying equations \eqref{eq:P_Model:EM1D} to \eqref{eq:P_Model:CE4D_chap1} and the boundary conditions:
 
-	Boundary Conditions\\
 	\[w = 0,  \ \textrm{ and } \ \psi = \bar{0} \ \textrm{ on } \Sigma_0.\]
 	\[Mn\cdot n = 0,\ \ \ Mn\cdot \tau = 0, \ \textrm{ and } \ \mathbf{Q} \cdot n =0 \ \textrm{ on } \partial\Omega\setminus\Sigma_0.\]
-	with $\tau$ a unit vector perpendicular to $n$.\\
+	with $\tau$ a unit vector perpendicular to $n$.
 
@@
 	Consider a plate model that is rigidly clamped on $\partial \Omega$.
-Find functions $w$ and $\psi$ satisfying equations \eqref{eq:P_Model:EM1D} to \eqref{eq:P_Model:CE4D_chap1}, the boundary conditions.\\
+Find functions $w$ and $\psi$ satisfying equations \eqref{eq:P_Model:EM1D} to \eqref{eq:P_Model:CE4D_chap1} and the boundary conditions:\\
 
-	Boundary Conditions\\
 	\[w = 0,  \ \textrm{ and } \ \psi = \bar{0} \ \textrm{ on } \partial \Omega.\]
@@
 	\subsection{Variational Form}\label{ssec:P_Model:VariationalForm}
-	Let $v \in C_2^1[0,1]$ and $w \in C^1[0,1] \times C^1[0,1]$ such that $w$ is a vector valued function. Multiplication these functions to \eqref{eq:P_Model:EM1D} and \eqref{eq:P_Model:EM2D} yields:
+	Let $v \in C_2^1[0,1]$ and $w \in C^1[0,1] \times C^1[0,1]$ such that $w$ is a vector valued function.
+Multiplication these artitrary functions to \eqref{eq:P_Model:EM1D} and \eqref{eq:P_Model:EM2D_chap1} yields:
 	\begin{eqnarray*}
@@
 
-	Following from Green's Formulas, similar to section \ref{ssec:3D_Model:VariationalForm}, 
+	Following from Green's Formulas, similar to Section \ref{ssec:3D_Model:VariationalForm}, 
 	\begin{eqnarray*}
@@
 
-	The variational form can be given as
+	The variational form is given as
 	\begin{align}
@@
  Applications are continued in Chapter 5 and 6.
-In Chapter 5, the finite element analysis is applied to a cantilever plate to solve the eigenvalue problem.
-In Chapter 6, a cantilever plate in used in the comparison of our linear models.
+In Chapter 5, the finite element method is applied to a cantilever plate to solve the eigenvalue problem.
+In Chapter 6, a cantilever plate in used in the comparison of the linear models.
 \end{document}

### 2024-04-07 files/Chapter2/generalvibrationmodel.tex
galerkin Timo
review exam report

@@
 
-In this chapter we consider the work done by the authors of \cite{VV02} and \cite{VS19}.
+In this chapter we consider the work done by the authors of \cite{VV02} and \cite{VS18}.
 In these articles the authors prove the existence and uniqueness of solutions for general second order hyperbolic type problems.
@@
 The article \cite{VV02} concerns the case of a symmetric bilinear form $b$.
-The article \cite{VS19} extends this work where $b$ need not be symmetric.
-The article \cite{VV02} is sufficient for the models of this dissertation, while \cite{VS19} is only used where the notation is more convenient and to gain more insight.
+The article \cite{VS18} extends this work where $b$ need not be symmetric.
+The article \cite{VV02} is sufficient for the models of this dissertation, while \cite{VS18} is only used where the notation is more convenient and to gain more insight.
 
@@
 \begin{eqnarray}
-	u(t)(x) = \langle w(x,t), \phi(x,t) \rangle \label{def_of_u}
+	u(t)(x) = \langle w(x,t), \phi(x,t) \rangle. \label{def_of_u}
 \end{eqnarray}
@@
 
-The space X with the inner-product $c$ is denoted by $W$. $W$ is called the inertia space and in Section 2.3 it is shown that $c$ is an inner-product for $W$.
+The space X equipped with the inner-product $c$ is denoted by $W$. $W$ is called the inertia space and in Section 2.3 it is shown that $c$ is an inner-product for $W$.
 
@@
 
-As mentioned before, ideas and notation from \cite{VS19} are also used.
+As mentioned before, ideas and notation from \cite{VS18} are also used.
 
@@
 
-This general variational form is applicable in all the models in this dissertation.
+This general variational form is applicable to all the models in this dissertation.
 In \cite{VV02}, a more general form is given that includes the possibility for damping terms in the models.
@@
 
-As mentioned, in the models of this dissertation, the bilinear form $a$ is identically zero. This automatically satisfy the weak damping condition and hence Theorem 2 may be applied.
+As mentioned, in the models of this dissertation, the bilinear form $a$ is identically zero. This automatically satisfies the weak damping condition and hence Theorem 2 may be applied.
 
@@
 So it follows that $C_0^\infty(0,1) \subset V(0,1) \subset H^1(0,1)$.
-And since $C_0^\infty(0,1)$ is dense in $L_2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L_2(0,1)$.
-Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.\label{sym:Cinftyzero}
+And since $C_0^\infty(0,1)$ is dense in $L^2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L^2(0,1)$.
+Therefore $V(0,1)\times V(0,1)$ is dense in $X = L^2(0,1) \times L^2(0,1)$.\label{sym:Cinftyzero}
 
@@
 \end{eqnarray*}
-From this, the following inequalities can be obtained:
+From this and the definition of the $X$ norm, the following inequalities can be obtained:
 \begin{eqnarray*}
@@
 
-Consider the partial differential equations of a pinned-pinned Timoshenko beam, obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}:
+Consider the partial differential equations of a pinned-pinned Timoshenko beam, obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations2D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion2D}:
 \begin{eqnarray}
@@
 	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
-	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
+	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}, \label{eq:1D_Model:ProblemT1E2}
 \end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.
@@
 \end{eqnarray*} 
-Substitution show that these solutions does indeed satisfy the differential equations \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} with the boundary conditions.
+Substitution show that these solutions do indeed satisfy the differential equations \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} with the boundary conditions.
 These solutions are the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (and consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.
@@
 	 -\int_0^1\alpha \tilde{w}' \psi + \int_0^1\alpha \tilde{\phi} \psi - \int_0^1\frac{1}{\gamma}\tilde{\phi}' \psi' &=& \int_0^1 \lambda \tilde{\phi} \psi .
-\end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$. \label{sym:lambda}
+\end{eqnarray*} for each $\langle v, \ \psi\rangle \in T[0,1]$. \label{sym:lambda}
 
@@
 \begin{eqnarray*}
-	u = \sum_{i=1}^{\infty} a_i x_i. = \sum_{i=1}^{\infty} c(u, x_i)x_i.
+	u = \sum_{i=1}^{\infty} a_i x_i = \sum_{i=1}^{\infty} c(u, x_i)x_i.
 \end{eqnarray*}
@@
 
-In the article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ a function $u$ given by \label{sym:Energy}
+In the article, the validity of the series solution is proved using energy norms, where the energy $\mathcal{E}$ of the function $u$ given by \label{sym:Energy}
 \begin{eqnarray}
@@
 
-Therfore $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$. For the case of weak damping, it can be proved that $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ which is the case of \cite{CVV18}.
+Therefore $\mathcal{E}(t) = \mathcal{E}(0)$ for all $t>0$. For the case of weak damping, it can be proved that $\mathcal{E}(t) \leq \mathcal{E}(0)$ for all $t>0$ which is the case of \cite{CVV18}.
 
@@
 Suppose that for the same initial conditions, $u_b$ and $u_w$ are the exact solutions.
-A comparison of the exact solutions are not possible, but the partial sums can be compared if the bounds for the errors $u_b - u^N_b$ and $u_w - u^N_w$ can be guaranteed.
+A comparison of the exact solutions is not possible, but the partial sums can be compared if the bounds for the errors $u_b - u^N_b$ and $u_w - u^N_w$ can be guaranteed.
 

### 2024-04-07 files/Chapter3/dynamicconvergence.tex
chapter 3
Chapter 3 final
submition
review exam report

@@
 	S^h = \textrm{span}\{\delta_1, \delta_2, ..., \delta_n\}.
-\end{eqnarray*}
+\end{eqnarray*} \label{sym:span}
 
@@
 	c(u''_h(t),v) + b(u_h(t),v) & = & (Q^I(t),v),
-\end{eqnarray*} for each $v \in S^h\times S^h$, where $u_h = ( w^h, \phi^h )$. $Q^I$ is a vector with elements $Q(x^*_i)$ for $i = 0,1,2,...,n$.
+\end{eqnarray*} for each $v \in S^h\times S^h$. For each $t$, $Q^I(t)$ is the interpolant of $Q(t)$ in $S^h$.
 
@@
 
-Under the assumptions \textbf{A1}-\textbf{A4} of Section 2 and continuity of $f$, there exists a unique solution for Problem GVar$^h$.
+Under the assumptions \textbf{A1}-\textbf{A4} of Chapter 2 and continuity of $f$, there exists a unique solution for Problem GVar$^h$.
 The next step is to show that the solution of Problem GVar$^h$ converges to the solution of Problem GVar.
@@
 From Theorem 2 for the semi-discrete problem an error estimate for
-$e(t) = [u(t)-u_h(t)]$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $e_k = [u_h(t_k) - u^h_k]$.
+$e(t) = u(t)-u_h(t)$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $e_k = u_h(t_k) - u^h_k$.
 
@@
 Since the dimension of $S^h$ is not fixed, the equivalence of norms
-cannot be used, and therefore this error estimate for $e_k = [u_h(t_k) - u^h_k]$
+cannot be used, and therefore this error estimate for $e_k = u_h(t_k) - u^h_k$
 should also be with respect to the norm of $W$. The local error $e_1$ can be estimated using Taylor polynomials, but then $e_k$ `grows' as $k$ increases.
@@
 Using this lemma, \cite{BV13} prove the error estimate.
-The error estimate for the term $[u_h(t_k) - u^h_k]$ with respect to the norm of $W$ as proven by the authors of \cite{BV13} is presented here as Theorem 3.
+The error estimate for the term $u_h(t_k) - u^h_k$ with respect to the norm of $W$ as proven by the authors of \cite{BV13} is presented here as Theorem 3.
 
@@
 	\begin{eqnarray*}
-		\Vert u(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & K\tau^2
+		\Vert u_h(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & K\tau^2
 	\end{eqnarray*}

### 2024-04-07 files/Chapter3/femconvergence.tex
review exam report

@@
 \begin{eqnarray}
-	\lambda^nM\bar{u}_n = K\bar{u}_n. \label{eq:matrix_eigenvalue}
+	\lambda^hM\bar{u}_n = K\bar{u}_n. \label{eq:matrix_eigenvalue}
 \end{eqnarray}
@@
 
-The pair $(\lambda^n, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$. It is necessary to understand some of the theory to make the connection.
+The pair $(\lambda^h, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$. It is necessary to understand some of the theory to make the connection.
 
@@
 \section{Estimating the eigenvalues.} \label{sec:estimating_the_eigenvalues}
-In this section, the work in the textbook \cite{SF73} is discussed. The results are the same as given in the textbook, how ever the proofs are expanded for greater clarity.
+In this section, the work in the textbook \cite{SF73} is discussed. The results are the same as given in the textbook, however the proofs are expanded for greater clarity.
 
@@
 The assumption is that the basis of $S^h$ consists of polynomials.
-With this assumptions, the semi-norm $|u|_H$ is equal to the norm $||u||_{W}$.
+With these assumptions, the semi-norm $|u|_H$ is equal to the norm $||u||_{W}$.
 This approximation theorem can be rewritten as

### 2024-04-07 files/Chapter4/CantileverBeam.tex
review exam report

@@
 The eigenvalue problem of Problem T-3 is denoted by Problem T-3E.
-This section serves as an example of the application of the theory from [VV02].\\
+This section serves as an example of the application of the theory from \cite{VV06}.\\
 
 Consider the general solutions of the eigenvalue problem for the three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$.
-Imposing the boundary conditions $x = 0$ results the following constants:
+Imposing the boundary conditions $x = 0$ results in the following constants:
 \begin{align}

### 2024-04-07 files/Chapter4/FreeFreeTimo.tex
review exam report

@@
 \begin{document}
-\section{Free-free timoshenko beam}\label{sec:Timo:Free}
+\section{Free-free Timoshenko beam}\label{sec:Timo:Free}
 Consider a free-free Timoshenko beam model (Problem T-4 in section \ref{ssec:1D_Model:ModelProblems}).The eigenvalue problem of Problem T-4 is denoted by Problem T-4E.
@@
 Consider the general solutions of the eigenvalue problem for the three cases $\lambda < \alpha$, $\lambda = \alpha$ and $\lambda > \alpha$.
-Imposing the boundary conditions $x = 0$ results the following:
+Imposing the boundary conditions $x = 0$ results in the following:
 

### 2024-04-07 files/Chapter4/ModalAnalysisTimo.tex
table of symbols
review exam report

@@
 \section{Introduction}
-An example of modal analysis on a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}.
-In this chapter, more general theory for modal analysis of te Timoshenko beam theory is discussed, as well as more examples of the application of the theory.
+An example of modal analysis of a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}.
+In this chapter, more general theory for modal analysis of the Timoshenko beam theory is discussed, as well as more examples of the application of the theory.
 
@@
 The authors of \cite{VV06} first derive a general solution for the system of ordinary differential equations \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2}.
-In \cite{VV06} the authors show that for the Timoshenko models in this dissertation $\lambda$ non-negative.
-Assume that the solution is of the form $\langle u, \phi \rangle = e^{mx}\bar{w}$ where $m\in \mathbb{R}$ or $m\in \mathbb{C}$.
+In \cite{VV06} the authors show that for the Timoshenko models in this dissertation that $\lambda$ is non-negative.
+Assume that the solution is of the form $\langle u, \phi \rangle = e^{mx}\bar{w}$ where $m\in R$ or $m\in C$.
 Substitution into \eqref{eq:Timo:EigenvalueProblem1} and \eqref{eq:Timo:EigenvalueProblem2} yields:
@@
 
-Let $A$ denote the coefficient matrix of \eqref{eq:Timo:SolutionEigenvalueProblem}. For a nontrivial solution of $\bar{w}$, it is required that the determinant of matrix $A$ is $0$.
+Let $A$ denote the coefficient matrix of \eqref{eq:Timo:SolutionEigenvalueProblem}. For a nontrivial solution $\bar{w}$, it is required that the determinant of matrix $A$ is $0$.
 \begin{align*}
 \textrm{det}(A)=m^{4}+\lambda(1+\gamma)m^{2}+\gamma\lambda(\lambda-\alpha)=0. \label{TE7}
-\end{align*}
+\end{align*} \label{sym:determinant}
 
@@
 
-The authors of \cite{VV06} provide a detailed example of the application of the above strategy to for determining the eigenvalues and eigenvectors.
+The authors of \cite{VV06} provide a detailed example of the application of the above strategy for determining the eigenvalues and eigenvectors.
 The example used is a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}.
@@
 Each of the solutions corresponds to a eigenvalue with a unique vector $\bar{b}$.
-The eigefunctions can then be obtained by substituting the vector $\bar{b}$ into the general solution for $u$ and $\phi$.
+The eigenfunctions can then be obtained by substituting the vector $\bar{b}$ into the general solution for $u$ and $\phi$.
 

### 2024-04-07 files/Chapter4/SP06.tex
Chapter 4 + 5 review
symbols
Overview, Chapter 3
table of symbols
chapter 4
review exam report

@@
 The natural frequencies of the Timoshenko beam theory was obtained by using frequency equations from an article by Levison and Cooke \cite{LC81}.
-In theoretical approach of the three-dimensional beam, two methods were considered.
+In the theoretical approach of the three-dimensional beam, two methods were considered.
 A commercial finite elements method (ANSYS), and a resonant ultrasound spectroscopy (RUS) technique.
@@
 \begin{eqnarray*}
-	\Omega := \left\{ \bar{x} = \langle x,y,z \rangle \in \mathbb{R} \ | \ 0 \leq x \leq 1, \ -\frac{h}{2} \leq y, z \leq \frac{h}{2}  \right\}
+	\Omega := \left\{ \bar{x} = \langle x,y,z \rangle \in R \ | \ 0 \leq x \leq 1, \ -\frac{h}{2} \leq y, z \leq \frac{h}{2}  \right\}
 \end{eqnarray*}
 
-with $h$ the height and width of the beam. $\partial \Omega$ denotes the boundary of $\Omega$. \\
+with $h$ the height and width of the beam. $\partial \Omega$ denotes the boundary of $\Omega$. \label{sym:height} \\
 
@@
 \end{eqnarray*} with $n$ a outward normal vector.
+
+\subfile{./SuspendedBeamModel.tex}
 
@@
 \subsection{Results from SP06}
-The following table contains relevant results are obtained by \cite{SP06}. 
+The following table contains relevant results obtained by \cite{SP06}. 
 % Table generated by Excel2LaTeX from sheet 'Sheet1'
@@
 
+\end{document}
+
 \textcolor{red}{Onseker oor die***************}\\
@@
 \textcolor{red}{Onseker oor die***************}
-\end{document}
 

### 2024-04-07 files/Chapter4/SuspendedBeamModel.tex
review exam report

@@
 
-Let $\langle w^* \ \phi^*\rangle$ represent the solution of the model problem, and $\langle w^e \ \phi^e \rangle$ the solution to the equilibrium problem.
-Define $\langle w \ \phi\rangle = \langle(w^*-w^e) \ \ (\phi^*-\phi^e)\rangle$ such that it represents the deviation of the beam from the equilibrium solution.
-Substitution verifies that $\langle w \ \phi\rangle$ satisfies the partial differential equation and boundary conditions.\\
+Let $\langle w^*, \ \phi^*\rangle$ represent the solution of the model problem, and $\langle w^e, \ \phi^e \rangle$ the solution to the equilibrium problem.
+Define $\langle w, \ \phi\rangle = \langle(w^*-w^e), \ (\phi^*-\phi^e)\rangle$ such that it represents the deviation of the beam from the equilibrium solution.
+Substitution verifies that $\langle w, \ \phi\rangle$ satisfies the partial differential equation and boundary conditions.\\
 

### 2024-04-07 files/Chapter4/Validity_Timo.tex
review exam report

@@
 In section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived.
-Specifically, section \ref{2dFEM_EP} derived the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.
+Specifically, section \ref{2dFEM_EP} derives the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.
 
@@
 For a short thick beam ($\alpha = 300$), the maximum relative error for the first 20 two-dimensional eigenvalues is just over $3\%$, while for a long thin beam ($\alpha = 10800$), the maximum relative error is just over $1\%$.
-This shows that as the beam becomes longer and thinner, the Timoshenko beam is better approximation of the two-dimensional beam.
+This shows that as the beam becomes longer and thinner, the Timoshenko beam is a better approximation of the two-dimensional beam.
 But overall the Timoshenko beam compares very well.

### 2024-04-07 final_seminar/main.tex
review exam report

\documentclass[8pt]{beamer}
\usetheme{metropolis} % Use the Metropolis theme
\usepackage{pgfplots}

\title{Comparison of linear beam models}
\author{Rudi du Toit}
\date{September 1, 2023}
\institute{University of Pretoria}

\begin{document}

% Redefine the title page template
\setbeamertemplate{title page}{
    \begin{center}
        \usebeamercolor[fg]{titlegraphic}\inserttitlegraphic\par
        \vskip0.25em%
        {\fontsize{14}{16}\selectfont\usebeamerfont{title}\usebeamercolor[fg]{title}\inserttitle\par}% Increase the font size of the title
        \ifx\insertsubtitle\@empty%
        \else%
        \vskip0.25em%
        {\fontsize{12}{14}\selectfont\usebeamerfont{subtitle}\usebeamercolor[fg]{subtitle}\insertsubtitle\par}% Increase the font size of the subtitle
        \fi%     
        \vskip1em\par
        \usebeamerfont{author}\insertauthor\par
        \vskip1em\par
        \usebeamerfont{institute}\insertinstitute\par
        \vskip1em%
        \includegraphics[width=0.2\linewidth]{logo-up.jpg}\par % Include the logo here
        \vskip1em\par
        \usebeamerfont{date}\insertdate\par
        \vfill
    \end{center}
}

\begin{frame}[plain]
\titlepage
\end{frame}

\begin{frame}{Introduction}
    \begin{itemize}
        \item Beams are widely used in engineering.
        \item A three-dimensional beam model would be most realistic representation of a real world beam.
        \item Three-dimensional beams are complex and require a lot of compute power, especially when using multiple beams in a single structure.
        \item Therefore simplified beam models are used, like the Timoshenko beam model.
        \item When in application is a Timoshenko beam a suitable replacement for a three-dimensional beam?
    \end{itemize}
\end{frame}

\begin{frame}{Introduction}
    \begin{itemize}
        \item Vibration problems are common in beam models.
        \item The validity of a Timoshenko beam model in application is an important consideration.
        \item Validity refers to how well the solution of a model compares to a more realistic, higher dimensional model.
    \end{itemize}
\end{frame}

\end{document}

### 2024-04-07 final_seminar/title_and_abstract.tex
review exam report

\documentclass{article}
\usepackage{lipsum} % for generating dummy text

\title{Finite element analysis of multi-dimensional and simplified models for beams and plates}
\author{Rudi du Toit}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
    Beams are fundamental structural elements in engineering. They are used in a wide range of applications, from bridges to buildings. Simplified models are often used in vibration problems due to their reduced complexity and computational demand. However, the accuracy of these models in practical applications is not always certain. In this presentation, we look at the validity of the Timoshenko beam model as well as the validity of the two-dimensional model. We use modal analysis and the Finite Element Method (FEM) to compare the models' natural frequencies and mode shapes to those of a more realistic three-dimensional model.
\end{abstract}

\end{document}

### 2024-04-07 files/Chapter5/2D_FEM.tex
plate model

@@
 The goal of this chapter is to obtain an algorithm that can be used to calculate the eigenvalues and eigenvectors for the models.
-This is in preparation of chapter 6, where the eigenvalues and eigenvectors of the models are compared.
+This is in preparation of Chapter 6, where the eigenvalues and eigenvectors of the models are compared.
 
-In chapter 4, a method was discussed to obtain the eigenvalues and eigenvectors for the Timoshenko beam model.
+In Chapter 4, a method was discussed to obtain the eigenvalues and eigenvectors for the Timoshenko beam model.
 Therefore it is not necessary to apply the Finite Element Method on the Timoshenko model to obtain the eigenvalues and eigenvectors.
@@
 \begin{eqnarray*}
-S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right).
+S^h & = & \textrm{span}\left\{\delta_i \ | \ i = 1,2,...,k \right\}.
 \end{eqnarray*}
@@
 
-The matrices ${O}$ and ${O_f}$ are the zero matrices of the same size as $\mathbf{M}$ and ${M_f}$ respectively.
+The matrices ${O}$ and ${O_F}$ are the zero matrices of the same size as $\mathbf{M}$ and ${M_f}$ respectively.
 

### 2024-04-07 files/Chapter5/3D_FEM.tex
plate model

@@
 \begin{align}
-	c(u,\phi) = -b(u,\phi) - (Q,\phi) \label{3DB_20}
+	c(u,\phi) = -b(u,\phi) + (Q,\phi) \label{3DB_20}
 \end{align}
@@
 As mentioned in the previous section, section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised.
-For this is three-dimensional body, three-dimensional elements shapes are required.
+For this three-dimensional body, three-dimensional elements shapes are required.
 The elements used in this dissertation are rectangular prismatic elements.
@@
 
-For the this three-dimensional model, piecewise Hermite tri-cubic basis functions are used.
+For this three-dimensional model, piecewise Hermite tri-cubic basis functions are used.
 Although this is more complex than using piecwise tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
@@
 \begin{eqnarray*}
-	S^h & = & \textrm{span}\left(\left\{\delta_i \ | \ i = 1,2,...,k \right\} \right)
+	S^h & = & \textrm{span}\left\{\delta_i \ | \ i = 1,2,...,k \right\}
 \end{eqnarray*}
@@
 \end{eqnarray*} for $i = 1,2,...,k$.
-$Q^I$ is scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$.
-i.e.
+$Q^I$ is a scalar vector obtained after interpolating the function $Q$ over the rectangular grid $\Omega$, i.e.
 $Q^I_{i,j, h} = Q(x_i,x_j, x_h)$ for $i = 1,2,...,n_1$, $j = 1,2,...,n_2$ and $h = 1,2,...,n_3$.
@@
 \end{minipage}
+
 for $i,j = 1,2,...,k.$\\
@@
 	M\ddot{\bar{u}} & = & K\bar{u} + M_{f}Q^I. \label{3D_M}
-\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \partial^i_1u \partial^j_2u \partial^k_3u$ for $i,j,k = 0,1,2,3$.
+\end{eqnarray} With $\bar{u}$ in the form $\bar{u} = \langle \partial^i_1u, \ \partial^j_2u, \ \partial^k_3u \rangle$ for $i,j,k = 0,1,2,3$.
 

### 2024-04-07 article.tex
changes
Section capital

@@
 	\subsection*{Eigenvalue problem}
-	The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in section \ref{2dFEM_EP}.
+	The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in Section \ref{2dFEM_EP}.
 
@@
 
-\end{document}
+\end{document}`'

### 2024-04-07 article_old.tex
Section capital

@@
 
-Using this notation, the boundary conditions are similar to the two-dimensional model in section \ref{sssec:2D_Model:RefConf}, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.
+Using this notation, the boundary conditions are similar to the two-dimensional model in Section \ref{sssec:2D_Model:RefConf}, where the body is clamped rigidly at $\Sigma$, and free-hanging on the other sides denoted by $\Gamma$.
 
@@
 Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma$ and free-hanging at all the other sides.
-This is Problem 3D in section \ref{ssec:3D_Model:ModelProblems}.
+This is Problem 3D in Section \ref{ssec:3D_Model:ModelProblems}.
 
@@
 
-In section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3DV.
+In Section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3DV.
 This general form can now be rewritten as in a model specific form using the reference configuration.
-For convenience, some of the results from section \ref{sec:3D_Model} are repeated here.
+For convenience, some of the results from Section \ref{sec:3D_Model} are repeated here.
 
@@
 \subsection{Galerkin approximation}
-As mentioned in the previous section, section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised.
+As mentioned in the previous section, Section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised.
 For this is three-dimensional body, three-dimensional elements shapes are required.
@@
 For the this three-dimensional model, piecewise Hermite tri-cubic basis functions are used.
-Although this is more complex than using piecwise tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
+Although this is more complex than using piecwise tri-linear basis functions, as mentioned in Section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
 
@@
 \subsection{Eigenvalue problem}
-The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in section \ref{2dFEM_EP}.
+The derivation and form of the eigenvalue problem for the three-dimensional elastic body is similar to the two-dimensional model given in Section \ref{2dFEM_EP}.
 
@@
 \subsubsection{Cantilever elastic body}
-Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D in section \ref{ssec:2D_Model:ModelProblem}.
+Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D in Section \ref{ssec:2D_Model:ModelProblem}.
 
@@
 
-In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2DV.
-Some of the results from section \ref{sec:2D_Model} are repeated here for convenience.
+In Section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2DV.
+Some of the results from Section \ref{sec:2D_Model} are repeated here for convenience.
 Using the reference configuration, these results are rewritten from a general form to a model specific form.
@@
 
-In section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed.
+In Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed.
 In this article, the authors investigated the validity of a cantilever Timoshenko beam by comparing it to a cantilever two-dimensional beam.
@@
 \subsection{The models}
-The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in section \ref{ssec:2D_Model:ModelProblem}.
-From section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D.
+The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in Section \ref{ssec:2D_Model:ModelProblem}.
+From Section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D.
 
@@
 \subsection{Calculating the eigenvalues}
-In section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived.
+In Section \ref{sec:FEM:3D}, the Finite Element Method for the three-dimensional beam is derived.
 Similar to the two-dimensional case in \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the Finite Element Method is used to calculate the eigenvalues of the three-dimensional beam.
@@
 	K\bar{u} & = & M\lambda{\bar{u}},
-\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in section \ref{ssec:2DFEM:DE} for the Problem 2DE and section \ref{3d_fem_g} for Problem 3DE.
+\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in Section \ref{ssec:2DFEM:DE} for the Problem 2DE and Section \ref{3d_fem_g} for Problem 3DE.
 
@@
 For the three-dimensional model, obtaining this level of accuracy can be difficult and computationally expensive.
-For the two-dimensional beam in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and the upcoming two-dimensional plate model in section \ref{sec:validity-of-a-plate} it is easier to get 5 significant digits of accuracy.
+For the two-dimensional beam in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and the upcoming two-dimensional plate model in Section \ref{sec:validity-of-a-plate} it is easier to get 5 significant digits of accuracy.
 
@@
 To be able to compare the eigenvalues, the mode shapes of the two models are compared to match up the eigenvalues of the two models.
-This is the same approach as in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}.
-
-As seen in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the two-dimensional model as eigenvalues and eigenvectors that are not related to beam type problems.
+This is the same approach as in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}.
+
+As seen in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the two-dimensional model as eigenvalues and eigenvectors that are not related to beam type problems.
 This is also true for the three-dimensional model, and it has even more non-beam type eigenvalues.
@@
 
-For $h$, the values used in section \ref{sec:validity-of-a-cantilever-timoshenko-beam} will be used.
+For $h$, the values used in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam} will be used.
 These values covers a range of beam shapes from a short thick beam, to a long slender beam.

### 2024-04-07 files/Chapter1/1DModel.tex
Section capital

@@
     \subsubsection*{Dimensionless form}\label{sssec:1D_Model:DimensionlessForm}
-    As mentioned in Subsection \ref{ssec:3D_Model:DimensionlessForm}, the same dimensionless scaling is used for all the models in this dissertation.\\
+    As mentioned in SubSection \ref{ssec:3D_Model:DimensionlessForm}, the same dimensionless scaling is used for all the models in this dissertation.\\
 
@@
 
-    Choose $t_0$ the same as in Subsection \ref{ssec:3D_Model:DimensionlessForm}, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]
+    Choose $t_0$ the same as in SubSection \ref{ssec:3D_Model:DimensionlessForm}, i.e. \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]
 
@@
         \frac{\beta}{\alpha} & = & \gamma
-    \end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in Subsection \ref{ssec:3D_Model:DimensionlessForm}.\\
+    \end{eqnarray*} where $\gamma$ is the dimensionless parameter defined in SubSection \ref{ssec:3D_Model:DimensionlessForm}.\\
 
-    \textbf{Remark} Recall that in Subsection \ref{ssec:3D_Model:DimensionlessForm} the constant $G\kappa^2$ was used for the scaling of the stresses.
+    \textbf{Remark} Recall that in SubSection \ref{ssec:3D_Model:DimensionlessForm} the constant $G\kappa^2$ was used for the scaling of the stresses.
 

### 2024-04-07 files/Chapter1/3DModel.tex
Section capital

@@
-\documentclass[../../main.tex]{subfiles}
+\documentclass[../../main.tex]{subfiles}ite{VS18}
 \begin{document}
 \section{Model problem for a three-dimensional elastic solid} \label{sec:3D_Model}
-In this section we introduces the linear theory for a three-dimensional elastic
+In this section we introduce the linear theory for a three-dimensional elastic
 solid. The textbook of Fung \cite{Fung65} is used with some changes in the
@@
 
-The equation of motion and constitutive equation are given in subsection
+The equation of motion and constitutive equation are given in Subsection
 \ref{ssec:3D_Model:EquationOfMotion}. The dimensionless form of the equation of
-motion and constitutive equation are derived in subsection
+motion and constitutive equation are derived in Subsection
 \ref{ssec:3D_Model:DimensionlessForm}. Model problems are presented in
-subsection \ref{ssec:3D_Model:ModelProblems}. The variational form for the
-vibration problem is given in section \ref{ssec:3D_Model:VariationalForm}.
-Plane stress is discussed in section \ref{ssec:3D_Model:PlaneStress}
+SubSection \ref{ssec:3D_Model:ModelProblems}. The variational form for the
+vibration problem is given in Section \ref{ssec:3D_Model:VariationalForm}.
+Plane stress is discussed in Section \ref{ssec:3D_Model:PlaneStress}
 
@@
 \subsubsection*{Strain}\label{sssec:3D_Model:Strain}
-Infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$\label{sym:mathcalE}, with components
+The infinitesimal strain tensor is defined on $\Omega$ as $\mathcal{E}$\label{sym:mathcalE}, with components
 \begin{eqnarray}
@@
 \end{eqnarray}
-$\textrm{Tr}(\mathcal{E}) = \epsilon_{11} + \epsilon_{12} + \epsilon_{13}$ is the trace of the strain operator $\mathcal{E}$.\\
+$\textrm{Tr}(\mathcal{E}) = \varepsilon_{11} + \varepsilon_{12} + \varepsilon_{13}$ is the trace of the strain operator $\mathcal{E}$.\\
 
@@
 derived in this subsection. Suppose $\ell$ represents some notable dimension
-(e.g.the length) of the elastic body and $G$ the shear modulus of elasticity.\\
+(e.g. the length) of the elastic body and $G$ the shear modulus of elasticity.\\
 
@@
 where $\kappa^2$ is a dimensionless constant and $t_0$ must be specified. A
-convenient choice for $t_0$ (see section \ref{sec:1D_Model}) is \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]
+convenient choice for $t_0$ (see Section \ref{sec:1D_Model}) is \[t_0 = \ell\sqrt{\frac{\rho}{G\kappa^2}}.\]
 
-Substitution into \eqref{eq:3D_Model:EM} and yields
+Substitution into \eqref{eq:3D_Model:EM} yields
 \begin{eqnarray*}
-	\partial_{\tau} u^{*} = \textrm{div}T^* + Q^*.
+	\partial_{\tau} u^{*} = \textrm{div}T^* + Q^*,
 \end{eqnarray*}
-where $T^* = \sigma_{i,j}^*(\xi,\tau)$.\\
+where $T^* = \sigma_{i,j}^*(\xi,\tau)$.
 
 The dimensionless form of \eqref{eq:3D_Model:HL} and \eqref{eq:3D_Model:CE} are
-\begin{eqnarray*}
-	\mathcal{E} = \frac{G \kappa^2}{E} \left[ (1+\nu)T^* - \nu \textrm{Tr}(T^*)I \right]
-\end{eqnarray*}\label{sym:I}
-
+\begin{eqnarray}
+	\mathcal{E} = \frac{G \kappa^2}{E} \left[ (1+\nu)T^* - \nu \textrm{Tr}(T^*)I \right] \label{sym:E_2}
+\end{eqnarray}\label{sym:I}
 and
-\begin{eqnarray*}
-	T^* = \frac{E}{G \kappa^2} \left[\left( \frac{1}{1+\nu} \right)\mathcal{E} + \frac{\nu}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \right]
-\end{eqnarray*}
+\begin{eqnarray}
+	T^* = \frac{E}{G \kappa^2} \left[\left( \frac{1}{1+\nu} \right)\mathcal{E} + \frac{\nu}{(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I \right]. \label{sym:T_2}
+\end{eqnarray}
 
@@
 
-Using this dimensionless constant,
+Using this dimensionless constant, \eqref{sym:E_2} and \eqref{sym:T_2} becomes
 \begin{eqnarray}
@@
 \textbf{Remark} The constant $G\kappa^2$ is introduced to allow for comparisons of the models in later chapters.
-The constant comes from the Timoshenko beam theory and is explained in section \ref{sec:1D_Model} \\
+The constant comes from the Timoshenko beam theory and is explained in Section \ref{sec:1D_Model} \\
 
-In the rest of section 1.2 the original notation is retained for convenience.
+In the rest of Section 1.2 the original notation is retained for convenience.
 
@@
 
-\subsubsection*{Constitutive equations in dimensionless form}\label{sssec:3D_Model:ConstitutiveEquationsDimensionless}
+\subsubsection*{Constitutive equation in dimensionless form}\label{sssec:3D_Model:ConstitutiveEquationsDimensionless}
 \begin{eqnarray}
@@
 \begin{enumerate}
-	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} is satisfied in $\Omega$;
+	\item[] The equations of motion \eqref{eq:3D_Model:EM-D} and \eqref{eq:3D_Model:divT-D} are satisfied in $\Omega$;
 	\item[] Hooke's law \eqref{eq:3D_Model:CE-D} is satisfied in $\Omega$;
@@
 
-Boundary Conditions:
 \begin{eqnarray*}
@@
 	Tn & = & 0 \quad \textrm{ on } \Gamma
-\end{eqnarray*} With $n$ the outward normal vector to $\Omega$.
+\end{eqnarray*} with $n$ the outward normal vector to $\Omega$.
 
@@
 
-Boundary Conditions:
 \begin{eqnarray*}
 	Tn & = & 0 \quad \textrm{ on } \partial\Omega
-\end{eqnarray*} With $n$ the unit outward normal vector. \label{sym:boundaryOmega}
+\end{eqnarray*} with $n$ the unit outward normal vector. \label{sym:boundaryOmega}
 
@@
 Let $\phi \in C({\Omega})$ be an arbitrary vector valued function. Multiplying
-$\phi$ to equation \eqref{eq:3D_Model:EM-D} and integrating over the domain
+$\phi$ with equation \eqref{eq:3D_Model:EM-D} and integrating over the domain
 $\Omega$ results in, \label{sym:Cn} \label{sym:phi}
@@
 \end{align}\label{sym:c}
-for all $\phi \in T(\Omega)$\\
+for all $\phi \in T(\Omega)$.\\
 
 The well-posedness of the model is treated in Chapter 2, where Korn's
-inequality is presented. Applications are continued in Chapter 4, 5 and 6. In
+inequality is presented. Applications are continued in Chapters 4, 5 and 6. In
 Chapter 4, a free-free three-dimensional beam is discussed as part of an
@@
 cantilever beam to solve the eigenvalue problem. In Chapter 6, a cantilever
-beam in used in the comparison of our linear models.
+beam is used in the comparison of the linear models.
 
@@
 	\begin{eqnarray*}
-		\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)} ( \varepsilon_{11} + \nu\varepsilon_{22})\\
+		\sigma_{11} & = & \frac{1}{\gamma(1-\nu^2)} ( \varepsilon_{11} + \nu\varepsilon_{22}),\\
 		\sigma_{22} & = & \frac{1}{\gamma(1-\nu^2)} (\nu \varepsilon_{11} + \varepsilon_{22}).
@@
 	\begin{eqnarray}
-		\sigma_{12} & = & \frac{1}{\gamma(1+\nu)} \varepsilon_{12} \label{stress_comp}
+		\sigma_{12} & = & \frac{1}{\gamma(1+\nu)} \varepsilon_{12}, \label{stress_comp}
 	\end{eqnarray}
@@
 This is known as general plane stress. In this dissertation only a special case
-of general plane stress is considered in section \ref{sec:2D_Model}.
+of general plane stress is considered in Section \ref{sec:2D_Model}.
 

### 2024-04-07 files/Chapter4/CantileverBeam.tex
Section capital

@@
 \section{Cantilever beam} \label{sec:Timo:Cantilever}
-Consider a cantilever Timoshenko beam model (Problem T-3 as defined in section \ref{ssec:1D_Model:ModelProblems}).
+Consider a cantilever Timoshenko beam model (Problem T-3 as defined in Section \ref{ssec:1D_Model:ModelProblems}).
 The eigenvalue problem of Problem T-3 is denoted by Problem T-3E.

### 2024-04-07 files/Chapter4/CantileverTimo.tex
Section capital

@@
 \subsection{The model problem}
-Consider the dimensionless equations of motion \ref{eq:1D_Model:EquationOfMotion1D} and \ref{eq:1D_Model:EquationOfMotion2D} and constitutive equations \ref{eq:1D_Model:ConstitutiveEquations1D} and \ref{eq:1D_Model:ConstitutiveEquations2D} of a Timoshenko beam, as given in section \ref{sec:1D_Model}.
+Consider the dimensionless equations of motion \ref{eq:1D_Model:EquationOfMotion1D} and \ref{eq:1D_Model:EquationOfMotion2D} and constitutive equations \ref{eq:1D_Model:ConstitutiveEquations1D} and \ref{eq:1D_Model:ConstitutiveEquations2D} of a Timoshenko beam, as given in Section \ref{sec:1D_Model}.
 The model in [DBVXX] adds two damping terms to these equations.

### 2024-04-07 files/Chapter4/FreeFreeTimo.tex
Section capital

@@
 \section{Free-free Timoshenko beam}\label{sec:Timo:Free}
-Consider a free-free Timoshenko beam model (Problem T-4 in section \ref{ssec:1D_Model:ModelProblems}).The eigenvalue problem of Problem T-4 is denoted by Problem T-4E.
+Consider a free-free Timoshenko beam model (Problem T-4 in Section \ref{ssec:1D_Model:ModelProblems}).The eigenvalue problem of Problem T-4 is denoted by Problem T-4E.
 Similar to the previous section, this section serves as an example of the application of the theory from [VV02].\\

### 2024-04-07 files/Chapter4/ModalAnalysisTimo.tex
Section capital

@@
 \section{Introduction}
-An example of modal analysis of a Timoshenko beam is given in section \ref{sec:existence:ModalAnalysis}.
+An example of modal analysis of a Timoshenko beam is given in Section \ref{sec:existence:ModalAnalysis}.
 In this chapter, more general theory for modal analysis of the Timoshenko beam theory is discussed, as well as more examples of the application of the theory.
@@
 
-Recall from section \ref{sec:1D_Model}, $u$ represents the transverse motion of the beam, $\phi$ is the angle of rotation of the cross-section of the beam, $\alpha$ and $\gamma$ are dimensionless constants defined in section 1.5 and $\lambda$ represents the eigenvalue.
+Recall from Section \ref{sec:1D_Model}, $u$ represents the transverse motion of the beam, $\phi$ is the angle of rotation of the cross-section of the beam, $\alpha$ and $\gamma$ are dimensionless constants defined in section 1.5 and $\lambda$ represents the eigenvalue.
 
@@
 The authors of \cite{VV06} provide a detailed example of the application of the above strategy for determining the eigenvalues and eigenvectors.
-The example used is a pinned-pinned beam, the same model as in section \ref{subsec:Timoshenko_Modal_Analsis}.
+The example used is a pinned-pinned beam, the same model as in Section \ref{subsec:Timoshenko_Modal_Analsis}.
 
@@
 
-A rigourous proof of the above results can be found in \cite{VV06}. These results also prove the Theorem 1 presented in section \ref{subsec:Timoshenko_Modal_Analsis}.
+A rigourous proof of the above results can be found in \cite{VV06}. These results also prove the Theorem 1 presented in Section \ref{subsec:Timoshenko_Modal_Analsis}.
 

### 2024-04-07 files/Chapter4/SP06.tex
Section capital

@@
 The authors of \cite{SP06} do not formulate the models in the article.
-Consider Problem T-4 from section \ref{ssec:1D_Model:ModelProblems} for the free-free Timoshenko beam and Problem 3D-2 from section \ref{ssec:3D_Model:ModelProblems} for the free-free three-dimensional beam.
+Consider Problem T-4 from Section \ref{ssec:1D_Model:ModelProblems} for the free-free Timoshenko beam and Problem 3D-2 from Section \ref{ssec:3D_Model:ModelProblems} for the free-free three-dimensional beam.
 The boundary conditions and reference configurations of the model problems are given below.
@@
 In [LC81], a single frequency equation for the free-free beam is given.
-From the work in section \ref{sec:Timo:EigenvalueProblem}, it has been shown that there can be up to three-different frequency equations depending on $\alpha$.
+From the work in Section \ref{sec:Timo:EigenvalueProblem}, it has been shown that there can be up to three-different frequency equations depending on $\alpha$.
 As the $\alpha$ for this beam is very small, the eigenvalues 9 and above will not be considered in this dissertation.\\

### 2024-04-07 files/Chapter4/SuspendedBeamModel.tex
Section capital

@@
 The beam is suspended at both endpoints by linear springs.
-The boundary conditions of Problem T-3 as given in section \ref{ssec:1D_Model:ModelProblems} can be rewritten by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations2D}.
+The boundary conditions of Problem T-3 as given in Section \ref{ssec:1D_Model:ModelProblems} can be rewritten by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations2D}.
 

### 2024-04-07 files/Chapter4/Validity_Timo.tex
Section capital

@@
 \subsection{The models}
-The cantilever Timoshenko beam model is defined in section \ref{ssec:1D_Model:ModelProblems}, and is referred to as Problem T-2.
-The cantilever two-dimensional beam model is defined in section \ref{ssec:2D_Model:ModelProblem}, and is referred to as Problem 2D-1.
+The cantilever Timoshenko beam model is defined in Section \ref{ssec:1D_Model:ModelProblems}, and is referred to as Problem T-2.
+The cantilever two-dimensional beam model is defined in Section \ref{ssec:2D_Model:ModelProblem}, and is referred to as Problem 2D-1.
 
@@
 
-In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
+In the derivation of the Timoshenko beam model in Section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
 introduced. The paramater is given here again for convenience:
@@
 \subsection{Calculating the eigenvalues and eigenvectors}
-In section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided.
-And in section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.
+In Section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided.
+And in Section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.
 
 For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method.
-In section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived.
-Specifically, section \ref{2dFEM_EP} derives the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.
+In Section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived.
+Specifically, Section \ref{2dFEM_EP} derives the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.
 
@@
 	K\bar{u} & = & M\lambda{\bar{u}},
-\end{eqnarray} where $M$ and $K$ are the standard Finite Element Method matrices defined in section \ref{sec:FEM:2D}.
+\end{eqnarray} where $M$ and $K$ are the standard Finite Element Method matrices defined in Section \ref{sec:FEM:2D}.
 

### 2024-04-07 files/Chapter5/2D_FEM.tex
Section capital

@@
 \begin{itemize}
-	\item[] Section \ref{sec:FEM:2D} FEM for a cantilever two-dimensional elastic body. This is problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
-	\item[] Section \ref{sec:FEM:3D} FEM for a cantilever three-dimensional elastic body. This is problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.
-	\item[] Section \ref{sec:FEM:Plate} FEM for a cantilever Reissner-Mindlin plate. This is problem P-1 in section \ref{ssec:P_Model:ModelProblems}.
+	\item[] Section \ref{sec:FEM:2D} FEM for a cantilever two-dimensional elastic body. This is problem 2D-1 in Section \ref{ssec:2D_Model:ModelProblem}.
+	\item[] Section \ref{sec:FEM:3D} FEM for a cantilever three-dimensional elastic body. This is problem 3D-1 in Section \ref{ssec:3D_Model:ModelProblems}.
+	\item[] Section \ref{sec:FEM:Plate} FEM for a cantilever Reissner-Mindlin plate. This is problem P-1 in Section \ref{ssec:P_Model:ModelProblems}.
 \end{itemize}
@@
 \subsubsection{Cantilever elastic body}
-Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem}.
+Consider a two-dimensional elastic body clamped rigidly to a surface at $x_1 = 0$. The body is free-hanging on the other boundaries. This is Problem 2D-1 in Section \ref{ssec:2D_Model:ModelProblem}.
 \FloatBarrier
@@
 
-In section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2D-1V.
-Some of the results from section \ref{sec:2D_Model} are repeated here for convenience.
+In Section \ref{ssec:2D_Model:VariationalForm} the variational problem for the two dimensional cantilever model is derived and refered to as Problem 2D-1V.
+Some of the results from Section \ref{sec:2D_Model} are repeated here for convenience.
 Using the reference configuration, these results are rewritten from a general form to a model specific form.

### 2024-04-07 files/Chapter5/3D_FEM.tex
Section capital

@@
 Consider a three-dimensional elastic body with rectangular cross-section, rigidly clamped to a surface at attached at the side $\Sigma$ and free-hanging at all the other sides.
-This is Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.
+This is Problem 3D-1 in Section \ref{ssec:3D_Model:ModelProblems}.
 \FloatBarrier
@@
 
-In section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3D-1V.
+In Section \ref{ssec:3D_Model:VariationalForm}, the variational problem for the three-dimensional cantilever model is defined by Problem 3D-1V.
 This general form can now be rewritten as in a model specific form using the reference configuration.
-For convenience, some of the results from section \ref{sec:3D_Model} are repeated here.
+For convenience, some of the results from Section \ref{sec:3D_Model} are repeated here.
 
@@
 \subsection{Galerkin approximation}
-As mentioned in the previous section, section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised.
+As mentioned in the previous section, Section \ref{2d_FEM_G}, the body $\Omega$ needs to be descritised.
 For this three-dimensional body, three-dimensional elements shapes are required.
@@
 For this three-dimensional model, piecewise Hermite tri-cubic basis functions are used.
-Although this is more complex than using piecwise tri-linear basis functions, as mentioned in section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
+Although this is more complex than using piecwise tri-linear basis functions, as mentioned in Section \ref{2d_FEM_G}, the tri-cubic basis functions ensure faster convergence and also the derivatives of the solutions.
 

### 2024-04-07 files/Chapter5/PlateModel.tex
Chapter 3
Section capital

@@
 Let $\left\{e_1,e_2\right\}$ be a right-handed orthonormal basis for $R^2$.
-Although this basis seems identical to the two-dimensional beam in section \ref{sssec:2D_Model:RefConf}, it is fact different.
+Although this basis seems identical to the two-dimensional beam in Section \ref{sssec:2D_Model:RefConf}, it is fact different.
 It would be more appropriate to use $e_1$ and $e_3$ for this plate model.
@@
 Consider a rectangular Reissner-Mindlin plate clamped rigidly to a surface at $\Sigma$ and free hanging on the remaining edges.
-This plate model is presented in section \ref{ssec:P_Model:ModelProblems} as Problem P-1.
+This plate model is presented in Section \ref{ssec:P_Model:ModelProblems} as Problem P-1.
 
@@
 
-In section \ref{ssec:P_Model:ModelProblems} the variational problem for the cantilever Reissner-Mindlin plate is defined by Problem P-1V.
-For convenience, the relevant results from section \ref{ssec:P_Model:ModelProblems} are repeated.
+In Section \ref{ssec:P_Model:ModelProblems} the variational problem for the cantilever Reissner-Mindlin plate is defined by Problem P-1V.
+For convenience, the relevant results from Section \ref{ssec:P_Model:ModelProblems} are repeated.
 
@@
 \subsection{Galerkin approximation}
-To discretise the body $\Omega$, the same shapes as in section \ref{ssec:2D_Model:Galerkin} are used.
+To discretise the body $\Omega$, the same shapes as in Section \ref{ssec:2D_Model:Galerkin} are used.
 
@@
 
-These basis functions are bi-cubic basis functions.
+These basis functions are piecewise Hermite bi-cubic basis functions.
 
@@
 \subsection{System of ordinary differential equations}\label{plate_fem_g}
-The standard FEM matrices $K_{11}$, $K_{12}$, $K_{21}$, $K_{22}$ and $M_F$ where presented in section \ref{ssec:2DFEM:DE}.
-Even though the definition of $R^2$ is different in section \ref{sec:FEM:2D}, the definition of the matrices are the same and are not repeated here.
+The standard FEM matrices $K_{11}$, $K_{12}$, $K_{21}$, $K_{22}$ and $M_F$ where presented in Section \ref{ssec:2DFEM:DE}.
+Even though the definition of $R^2$ is different in Section \ref{sec:FEM:2D}, the definition of the matrices are the same and are not repeated here.
 
@@
 
-The equation \eqref{Plate_FEM_M} is the same form as in section \ref{2dFEM_EP} for the two-dimensional elastic body.
+The equation \eqref{Plate_FEM_M} is the same form as in Section \ref{2dFEM_EP} for the two-dimensional elastic body.
 Therefore the derivation of the eigenvalue problem is identical.

### 2024-04-07 files/Chapter6/Introduction.tex
Section capital

@@
 \subsubsection{Timoshenko beam}
-In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
+In the derivation of the Timoshenko beam model in Section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is 
 introduced. The paramater is given here again for convenience,
@@
 
-This special case of plane stress, simplifies the three-dimensional model (see section \ref{sec:2D_Model} In application, this two-dimensional beam can be interpreted as a vertical slice of the three-dimensional beam, where the width of the slice is infinitesimally small.
+This special case of plane stress, simplifies the three-dimensional model (see Section \ref{sec:2D_Model} In application, this two-dimensional beam can be interpreted as a vertical slice of the three-dimensional beam, where the width of the slice is infinitesimally small.
 Therefore there is no width parameter $b$ for the two-dimensional beam.
@@
 The Reisner-Mindlin plate model is the most different model compared to the rest of the models in this dissertation.
-The Reisner-Mindlin plate model is derived in section \ref{sec:P_Model}.
+The Reisner-Mindlin plate model is derived in Section \ref{sec:P_Model}.
 The model has two parameters, the height $h$ and the width $b$.

### 2024-04-07 files/Chapter6/Validity_2D.tex
declaration
Section capital

@@
 \begin{document}
-\section{Validity of a Two-dimensional beam} \label{sec:validity-of-a-2d-beam}
+\section{Validity of a model for a cantilever two-dimensional beam} \label{sec:validity-of-a-2d-beam}
 
-In section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed.
+In Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the article \cite{LVV09} was discussed.
 In this article, the authors investigated the validity of a cantilever Timoshenko beam by comparing it to a cantilever two-dimensional beam.
@@
 \subsection{The models}
-The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in section \ref{ssec:2D_Model:ModelProblem}.
-From section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D-1.
+The two-dimensional model is the same model as used in the previous section, Problem T-2 defined in Section \ref{ssec:2D_Model:ModelProblem}.
+From Section \ref{ssec:3D_Model:ModelProblems}, the cantilever three-dimensional model, referred to as Problem 3D-1.
 
@@
 	K\bar{u} & = & M\lambda{\bar{u}},
-\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in section \ref{ssec:2DFEM:DE} for the Problem 2D-1E and section \ref{3d_fem_g} for Problem 3D-1E.
+\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in Section \ref{ssec:2DFEM:DE} for the Problem 2D-1E and Section \ref{3d_fem_g} for Problem 3D-1E.
 
@@
 To be able to compare the eigenvalues, the mode shapes of the two models are compared to match up the eigenvalues of the two models.
-This is the same approach as in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}.
+This is the same approach as in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}.
 
-As seen in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the two-dimensional model as eigenvalues and eigenvectors that are not related to beam type problems.
+As seen in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, the two-dimensional model as eigenvalues and eigenvectors that are not related to beam type problems.
 This is also true for the three-dimensional model, and it has even more non-beam type eigenvalues.
@@
 
-\subsection{Conclusion}
-
 These results gives a detailed overview of the validity of the cantilever two-dimensional beam compared to the cantilever three-dimensional beam.

### 2024-04-07 files/Chapter6/Validity_Plate.tex
Section capital

@@
 \begin{document}
-\section{Validity of a Reissner-Mindlin plate} \label{sec:validity-of-a-plate}
+\section{Validity of a model for a cantilever Reissner-Mindlin plate} \label{sec:validity-of-a-plate}
 
-In the previous section, section \ref{sec:validity-of-a-2d-beam}, it was shown that for certain applications beam models might not be the appropriate choice.
+In the previous section, Section \ref{sec:validity-of-a-2d-beam}, it was shown that for certain applications beam models might not be the appropriate choice.
 The specific application is for models where the body has a larger width than height.
@@
 This model is a two-dimensional model.
-So similar to the Timoshenko beam in section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, it is of value to investigate the validity of the model using a three-dimensional plate model as a reference.
+So similar to the Timoshenko beam in Section \ref{sec:validity-of-a-cantilever-timoshenko-beam}, it is of value to investigate the validity of the model using a three-dimensional plate model as a reference.
 
@@
 \subsection{The models}
-Form section \ref{ssec:P_Model:ModelProblems}, the cantilever Reissner-Mindlin plate model is given, and is referred to as Problem P-1.
-The three-dimensional model is the same as used in the previous section (section \ref{sec:validity-of-a-2d-beam}), and is referred to as Problem 3D-1 defined in section \ref{ssec:3D_Model:ModelProblems}.
+Form Section \ref{ssec:P_Model:ModelProblems}, the cantilever Reissner-Mindlin plate model is given, and is referred to as Problem P-1.
+The three-dimensional model is the same as used in the previous section (Section \ref{sec:validity-of-a-2d-beam}), and is referred to as Problem 3D-1 defined in Section \ref{ssec:3D_Model:ModelProblems}.
 
@@
 	K{u} & = & M\lambda{u}, 
-\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in section \ref{3d_fem_g} for Problem 3D-1E and section \ref{plate_fem_g} for Problem P-1E.
+\end{eqnarray} where $K$ and $M$ are the standard Finite Element Method matrices defined in Section \ref{3d_fem_g} for Problem 3D-1E and Section \ref{plate_fem_g} for Problem P-1E.
 
@@
 \subsection{Comparing the mode shapes}
-Similar to the previous sections (section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and section \ref{sec:validity-of-a-2d-beam}), the mode shapes of the two models are compared, to be able to match up the eigenvalues.
+Similar to the previous sections (Section \ref{sec:validity-of-a-cantilever-timoshenko-beam} and Section \ref{sec:validity-of-a-2d-beam}), the mode shapes of the two models are compared, to be able to match up the eigenvalues.
 
@@
 
-There is less of a dramatic change of the comparison when the width of the plate is changed as with the beam model in section \ref{sec:validity-of-a-2d-beam}.
+There is less of a dramatic change of the comparison when the width of the plate is changed as with the beam model in Section \ref{sec:validity-of-a-2d-beam}.
 This could be because the Reissner-Mindlin plate model does consider both the width and the height of the plate, while it is only a two-dimensional model.

### 2024-04-07 files/Chapter6/Validity_Timo.tex
Section capital

@@
 \subsection{Calculating the eigenvalues and eigenvectors}
-In section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided.
-And in section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.
+In Section \ref{sec:Timo:EigenvalueProblem} a method for calculating the eigenvalues and eigenvectors of the Timoshenko beam is provided.
+And in Section \ref{sec:Timo:Cantilever}, the eigenvalues and eigenvectors of a cantilever Timoshenko beam are calculated as an example.
 
 For the two-dimensional beam, the eigenvalues and eigenvectors are calculated using the Finite Element Method.
-In section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived.
-Specifically, section \ref{2dFEM_EP} derived the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.
+In Section \ref{sec:FEM:2D}, the Finite Element Method for a cantilever two-dimensional beam is derived.
+Specifically, Section \ref{2dFEM_EP} derived the eigenvalue problem for the two-dimensional beam using the Finite Element Method, called Problem 2D-1E.
 

### 2024-04-07 files/Chapter7/Beam-Main_Rig_2.tex
Section capital

@@
 \subsection{The models}
-Consider the cantilever Timoshenko beam model problem Problem T-2 from section \ref{ssec:1D_Model:ModelProblems} and the cantilever two-dimensional beam model problem Problem 2D-1 from section \ref{ssec:2D_Model:ModelProblem}.\\
+Consider the cantilever Timoshenko beam model problem Problem T-2 from Section \ref{ssec:1D_Model:ModelProblems} and the cantilever two-dimensional beam model problem Problem 2D-1 from Section \ref{ssec:2D_Model:ModelProblem}.\\
 
@@
 The parameter $h$ is the height of the two-dimensional beam.
-Recall the dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ from section \ref{sssec:1D_Model:DimensionlessForm}.
+Recall the dimensionless constant $\displaystyle \alpha = \frac{A \ell^2}{I}$ from Section \ref{sssec:1D_Model:DimensionlessForm}.
 For the Timoshenko beam model with a rectangular cross-section, the area moment of inertial is
@@
 This method also allows for the eigenvalues to be obtained to a desired level of accuracy (using a numerical method such as interval division).
-In this dissertation, \cite{VV06} is discussed in section \ref{sec:Timo:EigenvalueProblem}.\\
+In this dissertation, \cite{VV06} is discussed in Section \ref{sec:Timo:EigenvalueProblem}.\\
 
@@
 \subsection{The models}
-Consider a cantilever two-dimensional beam, referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.\\
+Consider a cantilever two-dimensional beam, referred to as Problem 2D-1 in Section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in Section \ref{ssec:3D_Model:ModelProblems}.\\
 

### 2024-04-07 files/Chapter7/Beam.tex
Section capital

@@
 \subsection{The models}
-Recall the cantilever Timoshenko beam model from section \ref{ssec:1D_Model:ModelProblems}, referred to as Problem T-2 and the cantilever two-dimensional beam model from section \ref{ssec:2D_Model:ModelProblem}, referred to as Problem 2D-1.
+Recall the cantilever Timoshenko beam model from Section \ref{ssec:1D_Model:ModelProblems}, referred to as Problem T-2 and the cantilever two-dimensional beam model from Section \ref{ssec:2D_Model:ModelProblem}, referred to as Problem 2D-1.
 In \cite{LVV09} it is assumed that the beams have a rectangular cross-section.\\
@@
 To calculate the eigenvalues and eigenfunctions of the Timoshenko beam, the authors of \cite{LVV09} use the article \cite{VV06}.
-This article was discussed in section \ref{sec:Timo:EigenvalueProblem} in this dissertation.
+This article was discussed in Section \ref{sec:Timo:EigenvalueProblem} in this dissertation.
 Using this article, the eigenvalues for the Timoshenko beam model can be numerically calculated to a desired accuracy level.
@@
 A different approach is needed for the two-dimensional beam.
-The Finite Element Method is applied to the eigenvalue problem described in section \ref{sec:FEM:2D}.
+The Finite Element Method is applied to the eigenvalue problem described in Section \ref{sec:FEM:2D}.
 The following shows the rate of convergence of the first 20 eigenvalues using FEM and bi-cubic basis functions.
@@
 
-The models for the two-dimensional and three-dimensional beams are defined in section \ref{ssec:2D_Model:ModelProblem} and \ref{ssec:3D_Model:ModelProblems} respectively.
+The models for the two-dimensional and three-dimensional beams are defined in Section \ref{ssec:2D_Model:ModelProblem} and \ref{ssec:3D_Model:ModelProblems} respectively.
 These models are elastic bodies and not specifically beam models.
@@
 \subsection{The models}
-Recall a cantilever two-dimensional beam, referred to as Problem 2D-1 in section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in section \ref{ssec:3D_Model:ModelProblems}.\\
+Recall a cantilever two-dimensional beam, referred to as Problem 2D-1 in Section \ref{ssec:2D_Model:ModelProblem} and a cantilever three-dimensional beam, referred to as Problem 3D-1 in Section \ref{ssec:3D_Model:ModelProblems}.\\
 
@@
 Similar to how the eigenvalues and eigenfunctions of the two-dimensional model calculated in the previous section, the eigenvalues and eigenfunctions can be calculated for the three-dimensional model.
-The numerical formula to calculate the eigenvalues and eigenfunctions are derived in section \ref{sec:FEM:3D}.\\
+The numerical formula to calculate the eigenvalues and eigenfunctions are derived in Section \ref{sec:FEM:3D}.\\
 

### 2024-04-07 files/Chapter7/Introduction.tex
Section capital

@@
 \subsubsection{Timoshenko beam}
-In the derivation of the Timoshenko beam model in section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is introduced.
+In the derivation of the Timoshenko beam model in Section \ref{subsec:equationsofmotion+constitutiveequation}, the parameter $\alpha$ is introduced.
 \begin{eqnarray*}
@@
 The two-dimensional plate model is the most different model from the rest of the models.
-The two-dimensional plate model is a Reissner-Mindlin plate model, and is derived in section \ref{sec:reissnermindlinplate}.
+The two-dimensional plate model is a Reissner-Mindlin plate model, and is derived in Section \ref{sec:reissnermindlinplate}.
 The model has two parameters, the height $h$ and the width $b$.

### 2024-04-07 files/Chapter5/PlateModel.tex
final small changes

@@
 \subsection{Galerkin approximation}
-To discretise the body $\Omega$, the same shapes as in Section \ref{ssec:2D_Model:Galerkin} are used.
+To discretise the body $\Omega$, the same shapes as in Section \ref{2d_FEM_G} are used.
 
@@
 \begin{eqnarray*}
-	w^h = \sum_{i = 1}^{k} w_i(t) \delta^*_{i}(x)
+	w^h = \sum_{i = 1}^{k} w_i(t) \delta^1_{i}(x)
 \end{eqnarray*} and $\psi^h$ can be expressed as
 \begin{eqnarray*}
-	\psi^h = \sum_{i = 1}^{k} \psi_i(t) \delta_{i}(x)
+	\psi^h = \sum_{i = 1}^{k} \psi_i(t) \delta^2_{i}(x)
 \end{eqnarray*}
@@
 
-The equation \eqref{Plate_FEM_M} is the same form as in Section \ref{2dFEM_EP} for the two-dimensional elastic body.
+The equation \eqref{Plate_FEM_M} is in the same form as in Section \ref{2dFEM_EP} for the two-dimensional elastic body.
 Therefore the derivation of the eigenvalue problem is identical.

### 2024-04-07 files/Chapter6/Validity_2D.tex
final small changes

@@
 
-All of the results will include all the eigenvalues shared between the two-models, including not beam type eigenvalues.
+All of the results will include all the eigenvalues shared between the two-models, including non-beam type eigenvalues.
 The non-beam type eigenvalues will be highlighted in grey.
@@
 
-Tables \ref{tab:2v3_1} and \ref{tab:2v3_2} show that the first 20 eigenvalues two-dimensional model compares very well to the matching eigenvalues three-dimensional beam for $b<=h$.
+Tables \ref{tab:2v3_1} and \ref{tab:2v3_2} show that the first 20 eigenvalues of the two-dimensional model compares very well to the matching eigenvalues of the three-dimensional beam for $b \leq h$.
 As the width $b$ decreases, the two-dimensional model becomes a better approximation of the three-dimensional model.
@@
 
-Tables \ref{tab:b>h} and \ref{tab:b>h_20} show that the two-dimensional model compares less well to the three-dimensional model when $b$ is too much larger than $h$.
+Tables \ref{tab:b>h} and \ref{tab:b>h_20} show that the two-dimensional model compares not as well to the three-dimensional model when $b$ is larger than $h$.
 Tables \ref{tab:b>h-split} and \ref{tab:b>h-split_20} show that this is also true for the beam type eigenvalues.
@@
 
-These results gives a detailed overview of the validity of the cantilever two-dimensional beam compared to the cantilever three-dimensional beam.
+These results give a detailed overview of the validity of the cantilever two-dimensional beam compared to the cantilever three-dimensional beam.
 The results show that the two-dimensional beam model compares very well to the three-dimensional beam model for a large range of beam shapes.

### 2024-04-07 files/Chapter6/Validity_Plate.tex
final small changes

@@
 
-In the previous section, Section \ref{sec:validity-of-a-2d-beam}, it was shown that for certain applications beam models might not be the appropriate choice.
+In the previous section it was shown that for certain applications beam models might not be the appropriate choice.
 The specific application is for models where the body has a larger width than height.
@@
 
-Overall Tables \ref{tab:Table_plate_1}, \ref{tab:Table_plate_2} and \ref{tab:Table_plate_3} shows that the cantilever Reissner-Mindlin plate model compares very well to the three-dimensional plate.
+Overall Tables \ref{tab:Table_plate_1}, \ref{tab:Table_plate_2} and \ref{tab:Table_plate_3} show that the cantilever Reissner-Mindlin plate model compares very well to the three-dimensional plate.
 The maximum relative error is less than 3.65\% for all cases considered.

### 2024-04-07 files/Overview.tex
final small changes

@@
 The other models are a two-dimensional elastic beam model, three-dimensional elastic beam and plate models and a Reissner-Mindlin plate model.
-The aim in this dissertation to validate the use of the Timoshenko beam model and the Reissner-Mindlin plate model in applications.
+The aim in this dissertation is to validate the use of the Timoshenko beam model and the Reissner-Mindlin plate model in applications.
 These models are simplified one-dimensional beam and two-dimensional plate models.
-But more realistic models exists, such as a two-dimensional and three-dimensional beam model and a three-dimensional plate model.
+But more realistic models exist, such as a two-dimensional and three-dimensional beam model and a three-dimensional plate model.
 Using modal analysis (see Chapter 2), it is shown that the solutions of the models can be represented as a linear combination of the modal solutions.
@@
 Finally the concept of modal analysis is introduced, which is fundamental to this dissertation.
-First idea of modal analysis is explained by hands of another example, again using a cantilever Timoshenko beam.
+First the idea of modal analysis is explained by hands of another example, again using a cantilever Timoshenko beam.
 Then the general case is discussed that follows the article \cite{CVV18}.
@@
 Therefore the validity of the two-dimensional model is investigated, using a three-dimensional beam model as a reference.
-Again the results so that the comparison relies on the shape of the beams.
+Again the results show that the comparison relies on the shape of the beams.
 The two-dimensional model compares well to the three-dimensional beam if the beam is not wide.
@@
 The eigenvalue problem can be solved with theory discussed later in the dissertation and the ordinary differential equation can then be solved.
-Substation of these two results into the boundary value problem confirms that the trial solution is correct.
+Substitution of these two results into the boundary value problem confirms that the trial solution is correct.
 The same idea is then discussed for the general case.

### 2024-04-09 final_seminar/main.tex
seminar v1

@@
 
-\title{Comparison of linear beam models}
+\usepackage[style=authoryear,backend=biber]{biblatex}
+\addbibresource{../references.bib}
+
+\title{Finite element analysis of multi-dimensional and simplified models for beams and plates}
 \author{Rudi du Toit}
-\date{September 1, 2023}
+\date{\today}
 \institute{University of Pretoria}
@@
 
+\section{Introduction}
     \begin{frame}{Introduction}
+        Beams are fundamental structural elements in engineering. They are used in a wide range of applications, from bridges to buildings.
+        \pause
+
+        Simplified models are often used in vibration problems due to their reduced complexity and computational demand.
+However, the accuracy of these models in practical applications is not always certain.
+        \pause
+
+        In this presentation, we look at the validity of the Timoshenko beam model as well as the validity of the two-dimensional model.
+We use modal analysis and the Finite Element Method (FEM) to compare the models' natural frequencies and mode shapes to those of a more realistic three-dimensional model.
+    \end{frame}
+
+    \begin{frame}{Structure of the presentation}
+        \tableofcontents
+    \end{frame}
+
+\section{Theory}
+    \subsection{General vibration problem}
+        \begin{frame}{General vibration problem}
+        \end{frame}
+
+    \subsection{Existence and uniqueness of solutions}
+        \begin{frame}{Existence and uniqueness of solutions}
+        \end{frame}
+
+    \subsection{Modal Analysis}
+        \begin{frame}{Modal Analysis}
+            General vibration problem:
+
+            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
+            \begin{eqnarray}
+                c(u''(t),v)+b(u(t),v) = 0 \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
+            \end{eqnarray}
+            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.
+
+            \only<2->{
+            Trial solution:
+
+            $u(t) = T(t)x$ with $x \in V$ and $x \neq 0$}
+        \end{frame}
+
+        \begin{frame}{Modal Analysis}
+           Substituting trial solution into \eqref{eq:existence:ProblemGVarHom}:
+           \begin{eqnarray*}
+                b(T(t)x,v) = - c(T''(t)x,v).  \label{eq:existence:ProblemGVarHom:Substitution}
+            \end{eqnarray*}
+
+            Due to the linearity of the bilinear form, this equation can be rewritten as
+            \begin{eqnarray*}
+                T(t)b(x,v) = - T''(t)c(x,v).
+            \end{eqnarray*}
+
+            \only<1>{
+            Dividing both sides by $T(t)$ gives
+            \begin{eqnarray*}
+                b(x,v) = - \frac{T''(t)}{T(t)}c(x,v).
+            \end{eqnarray*}}
+
+            \only<2>{
+            Dividing both sides by $T(t)$ gives
+            \begin{eqnarray*}
+                b(x,v) = - \frac{T''(t)}{T(t)}c(x,v) \implies  \frac{T''(t)}{T(t)} \ \ \ \textrm{must be constant.}
+            \end{eqnarray*}}
+        \end{frame}
+
+        \begin{frame}{Modal Analysis}
+            Set $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$.
+
+            At this point we do not yet know if such a $\lambda$ exists.
+
+            \only<2->{
+            Eigenvalue Problem:
+
+            Find a real number $\lambda$ and a $x \in V$ with $x \neq 0$ such that
+            \begin{eqnarray*}
+                b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
+            \end{eqnarray*}}
+
+         \end{frame}
+
+         \begin{frame}{Modal Analysis}
+            \only<1->{
+            Eigenvalue Problem:
+
+            Find a real number $\lambda$ and a $x \in V$ with $x \neq 0$ such that
+            \begin{eqnarray*}
+                b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
+            \end{eqnarray*}}
+
+            *******************CHECK THIS*******************
+            Existence of a solution is presented in the article [\cite{CVV18}]\footfullcite{CVV18}
+
+        \end{frame}
+
+        \begin{frame}{Modal Analysis}
+            Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
             \begin{itemize}
-        \item Beams are widely used in engineering.
-        \item A three-dimensional beam model would be most realistic representation of a real world beam.
-        \item Three-dimensional beams are complex and require a lot of compute power, especially when using multiple beams in a single structure.
-        \item Therefore simplified beam models are used, like the Timoshenko beam model.
-        \item When in application is a Timoshenko beam a suitable replacement for a three-dimensional beam?
+                \item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
+                \item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
+                \item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
             \end{itemize}
@@
 
-\begin{frame}{Introduction}
+        \begin{frame}{Modal Analysis}
             \begin{itemize}
-        \item Vibration problems are common in beam models.
-        \item The validity of a Timoshenko beam model in application is an important consideration.
-        \item Validity refers to how well the solution of a model compares to a more realistic, higher dimensional model.
+                \item[] \textbf{A1} - $V$ is dense in $W$ and $W$ is dense in $X$.
+
+                \item[] \textbf{A2} - There exists a positive constant $C_{W}$ such that $\Vert w\Vert_{X} \leq C_{W}\Vert w\Vert_{W}$ for each $ w\in W$.
+
+                \item[] \textbf{A3} - There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
+
+                \item[] \textbf{A4} - The bilinear form $a$ is non-negative, symmetric and bounded on $V$, i.e.
+there exists a positive constant $K_a$ such that for $\displaystyle u,v \in V$, \[|a(u,v)| \leq K_a\Vert u \Vert_V \Vert v \Vert_V.\]
+
+                \item[] \textbf{A5} - The embedding of $V$ into $W$ is compact.
             \end{itemize}
@@
 
+         \begin{frame}{Modal Analysis}
+            Formal series solution for the general vibration problem:
+            \begin{eqnarray}
+                u(t) = \sum_{n=1}^{\infty} T_n(t)x_n. \label{eq:1D_Model:ModalAnalysisSeriesSolution}
+            \end{eqnarray}
+            with 
+            \begin{flalign}
+                T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda_n > 0, \label{lambda_1}
+            \end{flalign}
+         \end{frame}
+
+\section{Models}
+    \subsection{Timoshenko cantilever beam}
+        \begin{frame}{Models - Timoshenko cantilever beam}
+            \begin{columns}[T] % align columns
+                \begin{column}{.6\textwidth}
+                    \only<1->{ % Frame 1: Equations of motion
+                    Equations of motion
+                    \begin{eqnarray*}
+                        \partial_{t}^{2} w &=& \partial_{x}V + Q,\\
+                        \frac{1}{\alpha} \partial_{t}^{2} \phi &=& V + \partial_{x}M.
+                    \end{eqnarray*}
+                    % Frame 1: Constitutive equations
+                    Constitutive equations
+                    \begin{eqnarray*}
+                        M &=& \frac{1}{\beta}\partial_x \phi,\\
+                        V &=& \partial_x w-\phi.
+                    \end{eqnarray*}
+                    }
+                \end{column}
+
+                \begin{column}{.4\textwidth}
+                    \only<2->{% Frame 2: Parameter descriptions
+                    \textbf{Description:}
+                    \begin{itemize}
+                        \item[-] \( w \): Displacement
+                        \item[-] \( \phi \): Angle of rotation of the cross-sections
+                        \item[-] \( M \): Bending moment
+                        \item[-] \( V \): Shear force
+                        \item[-] \( Q \): External distributed load
+                        \item[-] \( \alpha, \beta \): Dimensionless constants
+                    \end{itemize}}
+                \end{column}
+            \end{columns}
+        \end{frame}
+
+        \begin{frame}{Models - Timoshenko cantilever beam}
+            \begin{figure}[h!]
+                \centering
+                \begin{tikzpicture}
+
+                    \draw[line width = 0.4mm] (0,0) -- (6,0);
+                    \node at (2.7,-0.25) {$\ell = 1$};
+
+                    \draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
+                    \draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
+                    \draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
+                    \draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
+                    \draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
+                    \draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
+                    \draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
+                    \draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
+                    \draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);
+                    \draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
+                    \draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
+                    \draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
+                    \draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
+                    \draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
+                    \draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
+                    \draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
+                    \draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
+
+                    % Adding points 0 and 1
+                    \node at (0,-0.35) {0};
+                    \node at (6,-0.35) {1};
+
+                \end{tikzpicture}
+                \caption{A cantilever Timoshenko beam.}
+            \end{figure}
+
+            Boundary conditions for a cantilever beam
+            \begin{eqnarray*}
+                w(0,\cdot) = 0, &\phi(0,\cdot) = 0,\\
+                M(1,\cdot) = 0, &V(1,\cdot) = 0.
+            \end{eqnarray*}
+        \end{frame}
+
+    \subsection{Two-dimensional cantilever beam}
+        \begin{frame}{Models - Two-dimensional cantilever beam}
+            \begin{columns}[T] % align columns
+                \begin{column}{.6\textwidth}
+                    \only<1->{ % Frame 1: Equations of motion
+                        Equations of motion
+                        \begin{eqnarray*}
+                            \partial_t^2 u & = & \textrm{div}T + Q,
+                        \end{eqnarray*}
+                        with
+                        \begin{eqnarray*}
+                            \textrm{div} T & = &
+                            \begin{bmatrix}
+                                \partial_1 \sigma_{11} + \partial_2 \sigma_{12} \\
+                                \partial_1 \sigma_{21} + \partial_2 \sigma_{22}
+                            \end{bmatrix}.
+                        \end{eqnarray*}
+                    }
+                    \only<1->{ % Frame 1: Constitutive equations
+                        Constitutive equations
+                        \begin{eqnarray*}
+                            T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E}) I
+                        \end{eqnarray*}
+                    }
+                \end{column}
+
+                \begin{column}{.4\textwidth}
+                    \only<2->{ % Frame 2: Parameter descriptions
+                        \textbf{Description:}
+                        \begin{itemize}
+                            \item[-] \( u \): Displacement vector in 2D
+                            \item[-] \( T \): Stress tensor
+                            \item[-] \( Q \): External distributed load in 2D
+                            \item[-] \( \mathcal{E} \): Young's modulus
+                            \item[-] \( \nu \): Poisson's ratio
+                            \item[-] \( \gamma \): Dimensionless constant
+                        \end{itemize}
+                    }
+                \end{column}
+            \end{columns}
+        \end{frame}
+
+        \begin{frame}{Models - Two-dimensional cantilever beam}
+            \begin{figure}[h!]
+                \centering
+                \begin{tikzpicture}
+
+                    \draw[line width = 0.4mm] (0,0.5) -- (7,0.5);
+                    \draw[line width = 0.4mm] (0,-0.5) -- (7,-0.5);
+                    \draw[line width = 0.4mm] (7,-0.5) -- (7,0.5);
+                    \draw[line width = 0.4mm] (0,-0.5) -- (0,0.5);
+
+                    \draw[line width = 0.1mm] (0,1.5) -- (0,-1.5);
+
+                    \draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.3);
+                    \draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.1);
+                    \draw[line width = 0.1mm] (0,1.1) -- (-0.2,0.9);
+                    \draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.7);
+                    \draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.5);
+                    \draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.3);
+                    \draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.1);
+                    \draw[line width = 0.1mm] (0,0.1) -- (-0.2,-0.1);
+                    \draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.3);
+                    \draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.5);
+                    \draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.7);
+                    \draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.9);
+                    \draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1.1);
+                    \draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.3);
+                    \draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.5);
+
+                    \node at (7.3,0) {$h$};
+                    \draw[-stealth] (7.3,0.2) -- (7.3,0.5);
+                    \draw (7.2,0.5) -- (7.4,0.5);
+                    \draw[-stealth] (7.3,-0.2) -- (7.3,-0.5);
+                    \draw (7.2,-0.5) -- (7.4,-0.5);
+
+                    \node at (3.5,-0.8) {$1$};
+                    \draw[stealth-] (0,-0.8) -- (3.3,-0.8);
+                    \draw[stealth-] (7,-0.8) -- (3.7,-0.8);
+                    \draw (7,-0.9) -- (7,-0.7);
+
+                    \draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
+                    \draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
+                    \node at (9.7,0.8) {$e_1$};
+                    \node at (8.8,1.5) {$e_2$};
+
+                    \node at (-0.6,0) {$(0,0)$};
+                    \node at (0,0)[circle,fill,inner sep=1.5pt]{};
+
+                \end{tikzpicture}
+                \caption{A cantilever two-dimensional elastic body.}
+            \end{figure}
+
+            % Placeholder for boundary conditions of 2D cantilever
+            Boundary Conditions:
+            \begin{eqnarray*}
+                u & = & 0 \quad \textrm{ where } x_1 = 0\\
+                Tn & = & 0 \quad \textrm{ on the rest of the body }
+            \end{eqnarray*} With $n$ the outward normal vector to $\Omega$.
+        \end{frame}
+
+    \subsection{Three-dimensional cantilever beam}
+        \begin{frame}{Models - Three-dimensional cantilever beam}
+            \begin{columns}[T] % align columns
+                \begin{column}{.6\textwidth}
+                    \only<1->{ % Frame 1: Equations of motion
+                        Equations of motion
+                        \begin{eqnarray*}
+                            \partial_t^2 u & = & \textrm{div}T + Q
+                        \end{eqnarray*}
+                        with
+                        \begin{eqnarray*}
+                            \textrm{div}  T & = &
+                            \begin{bmatrix}
+                                \partial_1 \sigma_{11} + \partial_2 \sigma_{12} + \partial_3 \sigma_{13} \\
+                                \partial_1 \sigma_{21} + \partial_2 \sigma_{22} + \partial_3 \sigma_{23} \\
+                                \partial_1 \sigma_{31} + \partial_2 \sigma_{32} + \partial_3 \sigma_{33}
+                            \end{bmatrix}.\label{eq:3D_Model:divT-D}
+                        \end{eqnarray*}
+                    }
+                    \only<1->{ % Frame 1: Constitutive equations
+                        Constitutive equations
+                        \begin{eqnarray*}
+                            T = \frac{1}{\gamma(1+\nu)} \mathcal{E} + \frac{\nu}{\gamma(1+\nu)(1-2\nu)}\textrm{Tr}(\mathcal{E})I
+                        \end{eqnarray*}
+                    }
+                \end{column}
+
+                \begin{column}{.4\textwidth}
+                    \only<2->{ % Frame 2: Parameter descriptions
+                        \textbf{Description:}
+                        \begin{itemize}
+                            \item[-] \( u \): Displacement vector in 2D
+                            \item[-] \( T \): Stress tensor
+                            \item[-] \( Q \): External distributed load in 2D
+                            \item[-] \( \mathcal{E} \): Young's modulus
+                            \item[-] \( \nu \): Poisson's ratio
+                            \item[-] \( \gamma \): Dimensionless constant
+                        \end{itemize}
+                    }
+                \end{column}
+            \end{columns}
+        \end{frame}
+
+        \begin{frame}{Models - Three-dimensional cantilever beam}
+            \begin{figure}[h!]
+                \centering
+                \begin{tikzpicture}[scale=0.58]
+
+                    \draw[line width = 0.4mm] (-0.5,1) -- (6.5,1);
+                    \draw[line width = 0.4mm] (-0.5,-1) -- (6.5,-1);
+                    \draw[line width = 0.4mm] (6.5,-1) -- (6.5,1);
+                    \draw[line width = 0.4mm] (-0.5,-1) -- (-0.5,1);
+
+                    \draw[line width = 0.4mm] (0.5,1.5) -- (7.5,1.5);
+                    \draw[line width = 0.4mm] (7.5,-0.5) -- (7.5,1.5);
+
+                    \draw[line width = 0.4mm] (-0.5,1) -- (0.5,1.5);
+                    \draw[line width = 0.4mm] (6.5,1) -- (7.5,1.5);
+                    \draw[line width = 0.4mm] (6.5,-1) -- (7.5,-0.5);
+
+                    \draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+4});
+                    \draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+3.5});
+                    \draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+3});
+                    \draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+2.5});
+
+                    \draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+2});
+                    \draw[scale=0.5, domain=2:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+2});
+
+                    \draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+1.5});
+                    \draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+1});
+                    \draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x+0.5});
+                    \draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x});
+                    \draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-0.5});
+                    \draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-1});
+                    \draw[scale=0.5, domain=-3:-1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-1.5});
+                    \draw[scale=0.5, domain=-3:0, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-2});
+                    \draw[scale=0.5, domain=-3:1, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-2.5});
+                    \draw[scale=0.5, domain=-3:2, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-3});
+                    \draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-3.5});
+                    \draw[scale=0.5, domain=-3:3, smooth, variable=\x,dotted] plot ({\x}, {0.5*\x-4});
+
+                    %\node at (6.9,1) {$b$};
+                    %\node at (6.65,0) {$h$};
+                    %\node at (3.2,-1.2) {$\ell = 1$};
+
+                    \draw[line width = 0.1mm,->] (9,1) -- (10,1.6);
+                    \draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
+                    \draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
+                    \node at (9.3,1.4) {$e_3$};
+                    \node at (9.7,0.8) {$e_1$};
+                    \node at (8.8,1.5) {$e_2$};
+
+                    \node at (7.7,0.5) {$h$};
+                    \draw[-stealth] (7.7,0.7) -- (7.7,1.5);
+                    \draw (7.6,1.5) -- (7.8,1.5);
+                    \draw[-stealth] (7.7,0.3) -- (7.7,-0.5);
+                    \draw (7.6,-0.5) -- (7.8,-0.5);
+
+                    \node at (3,-1.2) {$1$};
+                    \draw[stealth-] (-0.5,-1.2) -- (2.8,-1.2);
+                    \draw[stealth-] (6.5,-1.2) -- (3.2,-1.2);
+                    \draw (6.5,-1.3) -- (6.5,-1.1);
+                    \draw (-0.5,-1.3) -- (-0.5,-1.1);
+
+                    \node at (7.2,-0.9) {$b$};
+                    \draw[stealth-] (7.7,-0.5) -- (7.35,-0.75);
+                    \draw[stealth-] (6.5,-1.2) -- (7,-0.95);
+
+                    \draw[line width = 0.1mm,->] (9,1) -- (10.4,1);
+                    \draw[line width = 0.1mm,->] (9,1) -- (9,2.1);
+                    \node at (9.7,0.8) {$e_1$};
+                    \node at (8.8,1.5) {$e_2$};
+
+                    \node at (-0.6,0) {$(0,0)$};
+                    \node at (0,0)[circle,fill,inner sep=1.5pt]{};
+
+                    %\node at (-1.4,-1.3) {$(0,-\frac{h}{2},-\frac{b}{2})$};
+                    %\node at (-1.4,1) {$(0,\frac{h}{2},-\frac{b}{2})$};
+                    %\node at (0.5,1.8) {$(0,\frac{h}{2},\frac{b}{2})$};
+
+                    %\node at (6,-1.3) {$(1,-\frac{h}{2},-\frac{b}{2})$};
+                    %\node at (6.3,0.7) {$(1,\frac{h}{2},-\frac{b}{2})$};
+                    %\node at (7.5,1.8) {$(1,\frac{h}{2},\frac{b}{2})$};
+                    %\node at (8.4,-0.4) {$(1,-\frac{h}{2},\frac{b}{2})$};
+
+                \end{tikzpicture}
+                \caption{Cantilever Three-Dimensional Elastic Body with Rectangular Cross-Section.}
+            \end{figure} 
+            Boundary Conditions:
+            \begin{eqnarray*}
+                u & = & 0 \quad \textrm{ where } x_1 = 0\\
+                Tn & = & 0 \quad \textrm{ on the rest of the body }
+            \end{eqnarray*} With $n$ the outward normal vector to $\Omega$.
+        \end{frame}
+
+\section{Literature study}
+    \subsection{Comparison of linear beam theories}
+        \begin{frame}{Literature study - Comparison of linear beam theories}
+            Consider the article [\cite{LVV09}]\footfullcite{LVV09}
+        \end{frame}
+
+    \subsection{Empirical comparison of beams}
+        \begin{frame}{Literature study - Empirical comparison of beams}
+            Consider the article [\cite{SP06}]\footfullcite{SP06}
+        \end{frame}
+
+\section{Numerical Results}
+    \subsection{Finite Element Analysis}
+        \begin{frame}{FEM}
+        \end{frame}
+
+        \begin{frame}{Eigenvalue problem - Timoshenko model}
+            General eigenvalue problem for the Timoshenko beam model:
+
+            Find functions $u$ and $\phi$ and a real number $\lambda$ satisfying the following equations
+            \begin{eqnarray}
+            -u'' + \phi' &=& \lambda u, \label{eq:Timo:EigenvalueProblem1}\\
+            -\alpha u' + \alpha\phi - \frac{1}{\gamma}\phi'' &=& \lambda\phi.\label{eq:Timo:EigenvalueProblem2}
+            \end{eqnarray}
+
+            The solution to this problem is presented in the article [\cite{VV06}]\footfullcite{VV06}.
+
+            \begin{itemize}
+                \item[-] Provides a method to calculate the exact eigenvalues.
+                \item[-] Uses a cantilever beam as an example in the article.
+                \item[-] Eigenvalues can be numerically obtained to any degree of accuracy.
+            \end{itemize}
+
+        \end{frame}
+
+        \begin{frame}{Eigenvalue problem - Two and Three-dimensional models}
+            General eigenvalue problem for the two- and three-dimensional models:
+
+                For the eigenvalue problem, assume that $M_{f}Q^I = 0$ so that 
+            \begin{eqnarray}
+                    M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
+            \end{eqnarray}
+
+            Not so simple to compute the eigenvalues and eigenfunctions.
+
+            Need to use a numerical method like FEM to approximate the eigenvalues and eigenvectors.
+
+        \end{frame}
+
+    \subsection{Validity of the Timoshenko beam model}
+        \begin{frame}{Validity of the Timoshenko beam model}
+        \end{frame}
+
+    \subsection{Validity of the two-dimensional beam model}
+        \begin{frame}{Validity of the two-dimensional beam model}
+        \end{frame}
+
+        \begin{frame}{Eigenvalue problem - FEM}
+            \centering
+            \includegraphics[scale=0.45]{Convergence.png} \\ % Adjust scale as needed
+            \footnotesize Rate of convergence of the first 20 eigenvalues.
+            \label{fig:conv}
+        \end{frame}
+
+        \begin{frame}{Comparison of two and three-dimensional models}
+            \centering
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{Beam1.jpg}
+                \\ 2D Beam Type - $\lambda_6 = 21.911$
+                \label{fig:minipage2}
+            \end{minipage}
+            \hfill
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{1DBeam2.png}
+                \\ Timoshenko - $\lambda_5 = 21.794$
+                \label{fig:minipage1}
+            \end{minipage}
+            \vspace{1em}
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{Beam2.jpg}
+                \\ 2D Beam Type - $\lambda_7 = 45.711$
+                \label{fig:minipage4}
+            \end{minipage}
+            \hfill
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{1DBeam1.png}
+                \\ Timoshenko - $\lambda_6 = 45.390$
+                \label{fig:minipage3}
+            \end{minipage}
+            \\ Modal shapes of the displacement $w$ for the beam-type 2D body and the Timoshenko beam with $\alpha = 4800$ ($h = 1/20$).
+        \end{frame}
+
+        \begin{frame}{Comparison of two and three-dimensional models}
+            \centering
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{NotBeam1.jpg}
+                \\ Non-Beam Type - $\lambda_4 = 7.7077$
+                \label{fig:nonbeam1}
+            \end{minipage}
+            \hfill
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{NotBeam2.jpg}
+                \\ Non-Beam Type - $\lambda_8 = 69.344$
+                \label{fig:nonbeam2}
+            \end{minipage}
+            \\ Modal shapes of the displacement $w$ for the non-beam type 2D body with $h = 1/20$.
+        \end{frame}
+
+        \begin{frame}{Comparison of two and three-dimensional models}
+            \centering
+            \footnotesize
+            \renewcommand{\arraystretch}{0.8}
+            Results from [LVV09] and results obtained. $0^a$ indicates a 0 due to rounding. $\alpha = 1200$
+
+            \begin{tabular}{cccc|cccc}
+                \hline
+                & \multicolumn{3}{c}{[LVV09]} & & \multicolumn{3}{c}{Dissertation} \\
+
+                & 2D & Timo & RE & & 2D & Timo & RE \\
+                \hline
+                1 & 0.0317 & 0.0316 & 0.00315 & 1 & 0.031713 & 0.031639 & 0.0023407 \\
+                2 & 1.14 & 1.14 & $0^a$ & 2 & 1.1413 & 1.1365 & 0.0042050 \\
+                3 & 7.72 & - & - & 3 & 7.7161 & - & - \\
+                4 & 7.92 & 7.86 & 0.00758 & 4 & 7.918 & 7.8617 & 0.0071116 \\
+                5 & 26.2 & 25.9 & 0.0115 & 5 & 26.148 & 25.869 & 0.010669 \\
+                6 & 60.8 & 59.9 & 0.0148 & 6 & 60.816 & 59.946 & 0.014303 \\
+                7 & 69.3 & - & - & 7 & 69.344 & - & - \\
+                8 & 115 & 113 & 0.0174 & 8 & 115.28 & 113.23 & 0.017787 \\
+                9 & 192 & 188 & 0.0208 & 9 & 191.57 & 187.55 & 0.020999 \\
+                10 & 192 & - & - & 10 & 192.03 & - & - \\
+                11 & 291 & 284 & 0.0241 & 11 & 290.76 & 283.81 & 0.023899 \\
+                \hline
+            \end{tabular}
+
+        \end{frame}
+
+        \begin{frame}{Eigenvalue problem - FEM}
+            \centering
+            \includegraphics[scale=0.45]{Result.png} \\ % Adjust scale as needed
+            \footnotesize Rate of convergence of the first 20 eigenvalues.
+            \label{fig:conv}
+        \end{frame}
+
+        \begin{frame}{Comparison of Eigenvalues across Different Parameters}
+            \centering
+            \footnotesize
+            \renewcommand{\arraystretch}{0.8}
+            \resizebox{\textwidth}{!}{%
+            \begin{tabular}{|cccc||cccc||cccc||cccc|}
+                \hline
+                \multicolumn{16}{|c|}{Comparison of Eigenvalues} \\
+                \hline\hline
+                \multicolumn{4}{|c||}{ $h = 1/5$ or $\alpha = 300$} & \multicolumn{4}{c||}{$h =1/10$ or $\alpha = 1200$} & \multicolumn{4}{c||}{$h = 1/20$ or $\alpha = 4800$} & \multicolumn{4}{c|}{$h = 1/30$ or $\alpha = 10800$} \\
+                \hline
+
+                {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} \\
+                \hline
+                {1}&0.12151&1&0.12092&1&0.031713&1&0.031639&1&0.008013&1&0.008004&1&0.003568&1&0.003565\\
+                {2}&3.5460&2&3.5071&2&1.1413&2     & 1.1365 & 2     & 0.30756 & 2     & 0.30705 & 2     & 0.13869 & 2     & 0.13855 \\
+                {3} & {7.7311} &       & {-} & {3}     & {7.7161} &       & {-} & 3     & 2.3273 & 3     & 2.3213 & 3     & 1.0698 & 3     & 1.0683 \\
+                {4} & 20.225 & 3     & 19.869 & 4     & 7.9180 & 3     & 7.8617 & {4}     & {7.7077} &       & {-} & 4     & 4.0140 & 4     & 4.0058 \\
+                {5} & 56.109 & 4     & 54.766 & 5     & 26.148 & 4     & 25.869 & 5     & 8.5086 & 4     & 8.4762 & {5}     & {7.7047} &       & {-} \\
+                {6} & {69.164} &       & {-} & 6     & 60.816 & 5     & 59.946 & 6     & 21.911 & 5     & 21.794 & 6     & 10.655 & 5     & 10.625 \\
+                {7} & 114.03 & 5     & 110.75 & {7}     & {69.344} &       & {-} & 7     & 45.711 & 6     & 45.390 & 7     & 22.975 & 6     & 22.890 \\
+                {8} & {189.17} &  6     & {186.50} & 8     & 115.28 & 6     & 113.23 & {8}     & {69.344} &       & {-} & 8     & 43.113 & 7     & 42.909 \\
+                {9} & {192.61} &      &  & {9}     & {191.57} &   7  & {187.55} & 9     & 82.887 & 7     & 82.154 & {9}     & {69.331} &       & {-} \\
+                {10} & 285.85 & 7     & 277.64 & {10}    & {192.03} &      & {-} & 10    & 136.03 & 8     & 134.58 & 10    & 73.230 & 8     & 72.803 \\
+                {11} & 328.40 & 8     & 330.29 & 11    & 290.76 & 8     & 283.81 & {11}    & {192.48} &       & {-} & 11    & 115.41 & 9     & 114.61 \\
+                {12} & {357.08} &       & {-} & {12}    & {374.45} &       & {-} & 12    & 207.29 & 9     & 204.69 & 12    & 171.61 & 10    & 170.20 \\
+                {13} & 397.33 & 9     & 394.02 & 13    & 413.20 & 9     & 402.27 & 13    & 298.38 & 10    & 294.10 & {13}    & {192.52} &       & {-} \\
+                {14} & 442.00   & 10    & 439.52 & 14    & 558.67 & 10    & 542.65 & {14}    & {376.83} &       & {-} & 14    & 243.56 & 11    & 241.26 \\
+                {15} & {533.71} &       & {-} & {15}    & {614.11} &       & {-} & 15    & 410.63 & 11    & 404.01 & 15    & 332.83 & 12    & 329.28 \\
+                {16} & 538.97 & 11    & 541.55 & 16    & 726.26 & 11    & 704.15 & 16    & 545.03 & 12    & 535.32 & {16}    & {377.16} &       & {-} \\
+                {17} & {596.06} &       & {-} & {17}    & {906.28} &       & {-} & {17}    & {621.95} &       & {-} & 17    & 440.77 & 13    & 435.51 \\
+                {18} & 602.77 & 12    & 596.09 & 18    & 913.69 & 12    & 884.92 & 18    & 702.30 & 13    & 688.64 & 18    & 568.51 & 14    & 561.04 \\
+                {19} & {657.87} &       & {-} & 19    & 1113.7 & 13    & 1080.1 & 19    & 882.95 & 14    & 864.40 & {19}    & {623.05} &       & {-} \\
+                {20} & 717.37 & 13    & 731.74 & {20}    & {1218.0}  &       & {-} & {20}    & {927.18} &       & {-} & 20    & 717.04 & 15    & 706.74 \\
+                \hline
+                \multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{3.1718\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{3.1486\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{2.1018\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{1.4361\%} \\
+                \hline
+            \end{tabular}}
+        \end{frame}
+
+        \begin{frame}{Three-Dimensional model vs Two-Dimensional model}
+            \centering
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{3D12.png}
+                \\ 3D Beam Type - $\lambda_{12} = 2.3293$
+                \label{fig:minipage2}
+            \end{minipage}
+            \hfill
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{2D3.png}
+                \\ 2D Beam Type - $\lambda_3 = 2.3273$
+                \label{fig:minipage1}
+            \end{minipage}
+
+            \vspace{1em} % spacing between the rows
+
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{3D22.png}
+                \\ 3D Beam Type - $\lambda_{24} = 21.929$
+                \label{fig:minipage4}
+            \end{minipage}
+            \hfill
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{2D6.png}
+                \\ 2D Beam Type - $\lambda_6 = 21.911$
+                \label{fig:minipage3}
+            \end{minipage}
+
+            Mode shapes of the displacement \( w \) with \( h=1/20 \).
+
+        \end{frame}
+
+        \begin{frame}{Three-Dimensional model}
+            \centering
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{3D33.png}
+                \\ 3D Non-Beam Type - $\lambda_{33} = 69.374$
+                \label{fig:minipage6}
+            \end{minipage}
+            \hfill
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{2D8.png}
+                \\ 2D Non-Beam Type - $\lambda_8 = 69.344$
+                \label{fig:minipage5}
+            \end{minipage}
+
+            \vspace{1em} % spacing between the rows
+
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{3DNonBeam10.png}
+                \\ Non-2D Type - $\lambda_{10}$
+                \label{fig:minipage8}
+            \end{minipage}
+            \hfill
+            \begin{minipage}[b]{0.45\textwidth}
+                \includegraphics[width=\textwidth]{3DNonBeam11.png}
+                \\ Non-2D Type - $\lambda_{11}$
+                \label{fig:minipage7}
+            \end{minipage}
+
+            Mode shapes of the displacement \( w \) with \( \alpha = 4800 \).
+        \end{frame}
+
+\section{Conclusion}
+    \begin{frame}{Conclusion}
+    \end{frame}
+
+    \begin{frame}{References}
+        \printbibliography[heading=bibintoc, title={References}]
+    \end{frame}
+
 \end{document}

### 2024-04-10 final_seminar/main.tex
seminar

@@
 \usepackage{pgfplots}
-
+\usepackage{caption,subcaption}
 \usepackage[style=authoryear,backend=biber]{biblatex}
@@
         \begin{frame}{General vibration problem}
+            \textbf{General vibration problem:}
+
+            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
+            \begin{eqnarray}
+                c(u''(t),v)+a(u'(t),v)+b(u(t),v) = (f(t),v) \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
+            \end{eqnarray}
+            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.
         \end{frame}
@@
         \begin{frame}{Existence and uniqueness of solutions}
+            Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
+            \begin{itemize}
+                \item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
+                \item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
+                \item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
+            \end{itemize}
+        \end{frame}
+
+        \begin{frame}{Existence and uniqueness of solutions}
+            The following assumptions are made in \cite{VV02} for the existence results.
+            \begin{itemize}
+                \item[] \textbf{A1} - $V$ is dense in $W$ and $W$ is dense in $X$.
+
+                \item[] \textbf{A2} - There exists a positive constant $C_{W}$ such that $\Vert w\Vert_{X} \leq C_{W}\Vert w\Vert_{W}$ for each $ w\in W$.
+
+                \item[] \textbf{A3} - There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
+
+                \item[] \textbf{A4} - The bilinear form $a$ is non-negative, symmetric and bounded on $V$, i.e.
+there exists a positive constant $K_a$ such that for $\displaystyle u,v \in V$, \[|a(u,v)| \leq K_a\Vert u \Vert_V \Vert v \Vert_V.\]
+            \end{itemize}
+        \end{frame}
+
+        \begin{frame}{Existence and uniqueness of solutions}
+            \newtheorem{Thmx}{Theorem}
+            \begin{Thmx}
+                Suppose assumptions \textbf{A1}-\textbf{A4} hold. If, for $u_0 \in V$ and $u_1 \in V$, there exists some $y \in W$ such that
+                \begin{eqnarray}
+                    b(u_0,v) + a(u_1,v) = c(y,v) \ \ \ \ \textrm{ for all } \ v \in V, \label{bilinear_equation}
+                \end{eqnarray}
+                then for each $f \in C^1(J,X)$, there exists a unique solution $u \in C^1(J,V)\cap C^2(J,W)$ for Problem GVar.
+            \end{Thmx}
+
+            This theorem allows for a solution of the abstract variational problem Problem GVar, if the assumptions \textbf{A1}-\textbf{A4} is satisfied and the initial values $u_0$ and $u_1$ are admissible.
+It is not always easy to verify that \eqref{bilinear_equation} is satisfied.
         \end{frame}
@@
         \begin{frame}{Modal Analysis}
-            General vibration problem:
+            \textbf{General vibration problem:}
 
@@
 
-            *******************CHECK THIS*******************
             Existence of a solution is presented in the article [\cite{CVV18}]\footfullcite{CVV18}
 
-        \end{frame}
-
-        \begin{frame}{Modal Analysis}
-            Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
-            \begin{itemize}
-                \item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
-                \item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
-                \item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
-            \end{itemize}
         \end{frame}
@@
     \subsection{Finite Element Analysis}
-        \begin{frame}{FEM}
+        \begin{frame}{Eigenvalue problem - Two and Three-dimensional models}
+            General eigenvalue problem for the two- and three-dimensional models:
+
+                For the eigenvalue problem, assume that $M_{f}Q^I = 0$ so that 
+            \begin{eqnarray}
+                    M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
+            \end{eqnarray}
+
+            Not so simple to compute the eigenvalues and eigenfunctions.
+
+            Need to use a numerical method like FEM to approximate the eigenvalues and eigenvectors.
+
         \end{frame}
@@
 
-        \begin{frame}{Eigenvalue problem - Two and Three-dimensional models}
-            General eigenvalue problem for the two- and three-dimensional models:
+        \begin{frame}{FEM}
+        \end{frame}
 
-                For the eigenvalue problem, assume that $M_{f}Q^I = 0$ so that 
-            \begin{eqnarray}
-                    M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
-            \end{eqnarray}
+        \begin{frame}{Accuracy of the Eigenvalues}
+            \centering
+            \includegraphics[scale=0.3]{Convergence.png} \\ % Adjust scale as needed
+            \footnotesize Rate of convergence of the first 20 eigenvalues.
 
-            Not so simple to compute the eigenvalues and eigenfunctions.
-
-            Need to use a numerical method like FEM to approximate the eigenvalues and eigenvectors.
-
+            \centering
+            \includegraphics[scale=0.3]{convergence3d.png} \\ % Adjust scale as needed
+            \footnotesize Rate of convergence of the first 20 eigenvalues.
         \end{frame}
@@
         \begin{frame}{Validity of the Timoshenko beam model}
-        \end{frame}
+            \begin{center}
+                \begin{minipage}[b]{0.45\linewidth}
+                    \centering
+                    \begin{tikzpicture}[scale=0.7]
+                        \draw[line width = 0.4mm] (0,0.2) -- (6,0.2);
+                                    \draw[line width = 0.4mm] (0,-0.2) -- (6,-0.2);
+                                    \draw[line width = 0.4mm] (6,-0.2) -- (6,0.2);
 
-    \subsection{Validity of the two-dimensional beam model}
-        \begin{frame}{Validity of the two-dimensional beam model}
-        \end{frame}
+                                    \node at (6.2,0) {$h$};
+                                    \node at (2.7,-0.45) {$\ell = 1$};
 
-        \begin{frame}{Eigenvalue problem - FEM}
+                                    \draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
+                                    \draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
+                                    \draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
+                                    \draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
+                                    \draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
+                                    \draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
+                                    \draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
+                                    \draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
+                                    \draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);
+
+                                    \draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
+                                    \draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
+                                    \draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
+                                    \draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
+                                    \draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
+                                    \draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
+                                    \draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
+                                    \draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
+                    \end{tikzpicture}
+                    \captionof{figure}{Two-Dimensional Beam}
+                \end{minipage}
+                \hfill
+                \begin{minipage}[b]{0.45\linewidth}
                     \centering
-            \includegraphics[scale=0.45]{Convergence.png} \\ % Adjust scale as needed
-            \footnotesize Rate of convergence of the first 20 eigenvalues.
-            \label{fig:conv}
+                    \begin{tikzpicture}[scale=0.7]
+                        \draw[line width = 0.4mm] (0,0) -- (6,0);
+                                \node at (2.7,-0.25) {$\ell = 1$};
+
+                                \draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
+                                \draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
+                                \draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
+                                \draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
+                                \draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
+                                \draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
+                                \draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
+                                \draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
+                                \draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);
+
+                                \draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
+                                \draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
+                                \draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
+                                \draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
+                                \draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
+                                \draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
+                                \draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
+                                \draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
+                    \end{tikzpicture}
+                    \captionof{figure}{Timoshenko Beam}
+                \end{minipage}
+            \end{center}
         \end{frame}
@@
             \footnotesize
-            \renewcommand{\arraystretch}{0.8}
+            \renewcommand{\arraystretch}{0.9}
             Results from [LVV09] and results obtained. $0^a$ indicates a 0 due to rounding. $\alpha = 1200$
@@
             \end{tabular}}
+        \end{frame}
+
+    \subsection{Validity of the Two-dimensional beam model}
+        \begin{frame}{Validity of the Two-dimensional beam model}
+            \begin{center}
+                \begin{minipage}[b]{0.45\linewidth}
+                    \centering
+                    \begin{tikzpicture}[scale=0.6]
+                        \draw[line width = 0.3mm] (-0.1,1) -- (6.9,1);
+                        \draw[line width = 0.3mm] (-0.1,-1) -- (6.9,-1);
+                        \draw[line width = 0.3mm] (6.9,-1) -- (6.9,1);
+                        \draw[line width = 0.3mm] (-0.1,-1) -- (-0.1,1);
+
+                        \draw[line width = 0.3mm] (0.1,1.1) -- (7.1,1.1);
+                        \draw[line width = 0.3mm] (7.1,-0.9) -- (7.1,1.1);
+
+                        \draw[line width = 0.3mm] (-0.1,1) -- (0.1,1.1);
+                        \draw[line width = 0.3mm] (6.9,1) -- (7.1,1.1);
+                        \draw[line width = 0.3mm] (6.9,-1) -- (7.1,-0.9);
+
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
+
+                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
+                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
+                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
+
+                        \draw[scale=0.5, domain=0.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
+                        \draw[scale=0.5, domain=1.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
+                        \draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
+
+                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
+                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
+                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
+                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
+                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
+                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
+                        \draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
+                        \draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});
+
+                        \node at (6.95,1.25) {$b$};
+                        \node at (6.78,0) {$h$};
+                        \node at (3.2,-1.2) {$\ell = 1$};
+                    \end{tikzpicture}
+                    \captionof{figure}{Three-Dimensional Beam}
+                \end{minipage}
+                \hfill
+                \begin{minipage}[b]{0.45\linewidth}
+                    \centering
+                    \begin{tikzpicture}[scale=0.6]
+                        \draw[line width = 0.3mm] (0,1) -- (7,1);
+                        \draw[line width = 0.3mm] (0,-1) -- (7,-1);
+                        \draw[line width = 0.3mm] (7,-1) -- (7,1);
+                        \draw[line width = 0.3mm] (0,-1) -- (0,1);
+
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
+
+                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
+                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
+
+                        \draw[scale=0.5, domain=1:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
+                        \draw[scale=0.5, domain=2:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});
+
+                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
+                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
+                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
+                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
+                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
+                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
+                        \draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
+                        \draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
+                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});
+
+                        \node at (7.2,0) {$h$};
+                        \node at (3.2,-1.2) {$\ell = 1$};
+                    \end{tikzpicture}
+                    \captionof{figure}{Two-dimensional Beam}
+                \end{minipage}
+            \end{center}
         \end{frame}

### 2024-04-11 final_seminar/main.tex
speech

@@
 
-\title{Finite element analysis of multi-dimensional and simplified models for beams and plates}
+\title{Finite element analysis of multi-dimensional and simplified models for beams}
 \author{Rudi du Toit}
@@
 \institute{University of Pretoria}
+
+\newcommand{\footfullcitenonumber}[1]{
+  \footnotetext{\fullcite{#1}}
+}
 
@@
         \begin{frame}{General vibration problem}
+            Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
+            \begin{itemize}
+                \item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
+                \item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
+                \item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
+            \end{itemize}
+            \only<2->{
+            The bilinear forms $a$, $b$ and $c$ are defined as $a = (\cdot,\cdot)_X$,$b = (\cdot,\cdot)_V$ and $c = (\cdot,\cdot)_W$.
+            }
+
+            \only<3>{
             \textbf{General vibration problem:}
@@
             \end{eqnarray}
-            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.
+            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.}
+
+            \only<4->{
+            \textbf{General vibration problem:}
+
+            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
+            \begin{eqnarray}
+                c(u''(t),v)+b(u(t),v) = (f(t),v) \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
+            \end{eqnarray}
+            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.}
+
+            \footfullcitenonumber{VV02}
         \end{frame}
@@
     \subsection{Existence and uniqueness of solutions}
-        \begin{frame}{Existence and uniqueness of solutions}
-            Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
-            \begin{itemize}
-                \item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
-                \item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
-                \item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
-            \end{itemize}
-        \end{frame}
+
+        In [\cite{VV02}] the authors present results for the existence and uniqueness of solutions to the general vibration problem. The following assumptions are made for the existence results.
 
@@
             \end{itemize}
+            \footfullcitenonumber{VV02}
         \end{frame}
@@
 It is not always easy to verify that \eqref{bilinear_equation} is satisfied.
+
+            \footfullcitenonumber{VV02}
         \end{frame}
@@
                     \begin{tikzpicture}[scale=0.6]
-                        \draw[line width = 0.3mm] (0,1) -- (7,1);
+                        \draw[line width = 0.3mm] (0,1) -- (7,1);~
                         \draw[line width = 0.3mm] (0,-1) -- (7,-1);

### 2024-04-15 final_seminar/main.tex
order change and added datat

@@
 \usepackage[style=authoryear,backend=biber]{biblatex}
+\usepackage[table]{xcolor}
 \addbibresource{../references.bib}
@@
 
-\section{Theory}
-    \subsection{General vibration problem}
-        \begin{frame}{General vibration problem}
-            Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
-            \begin{itemize}
-                \item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
-                \item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
-                \item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
-            \end{itemize}
-            \only<2->{
-            The bilinear forms $a$, $b$ and $c$ are defined as $a = (\cdot,\cdot)_X$,$b = (\cdot,\cdot)_V$ and $c = (\cdot,\cdot)_W$.
-            }
-
-            \only<3>{
-            \textbf{General vibration problem:}
-
-            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
-            \begin{eqnarray}
-                c(u''(t),v)+a(u'(t),v)+b(u(t),v) = (f(t),v) \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
-            \end{eqnarray}
-            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.}
-
-            \only<4->{
-            \textbf{General vibration problem:}
-
-            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
-            \begin{eqnarray}
-                c(u''(t),v)+b(u(t),v) = (f(t),v) \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
-            \end{eqnarray}
-            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.}
-
-            \footfullcitenonumber{VV02}
-        \end{frame}
-
-    \subsection{Existence and uniqueness of solutions}
-
-        In [\cite{VV02}] the authors present results for the existence and uniqueness of solutions to the general vibration problem. The following assumptions are made for the existence results.
-
-        \begin{frame}{Existence and uniqueness of solutions}
-            The following assumptions are made in \cite{VV02} for the existence results.
-            \begin{itemize}
-                \item[] \textbf{A1} - $V$ is dense in $W$ and $W$ is dense in $X$.
-
-                \item[] \textbf{A2} - There exists a positive constant $C_{W}$ such that $\Vert w\Vert_{X} \leq C_{W}\Vert w\Vert_{W}$ for each $ w\in W$.
-
-                \item[] \textbf{A3} - There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
-
-                \item[] \textbf{A4} - The bilinear form $a$ is non-negative, symmetric and bounded on $V$, i.e.
-there exists a positive constant $K_a$ such that for $\displaystyle u,v \in V$, \[|a(u,v)| \leq K_a\Vert u \Vert_V \Vert v \Vert_V.\]
-            \end{itemize}
-            \footfullcitenonumber{VV02}
-        \end{frame}
-
-        \begin{frame}{Existence and uniqueness of solutions}
-            \newtheorem{Thmx}{Theorem}
-            \begin{Thmx}
-                Suppose assumptions \textbf{A1}-\textbf{A4} hold. If, for $u_0 \in V$ and $u_1 \in V$, there exists some $y \in W$ such that
-                \begin{eqnarray}
-                    b(u_0,v) + a(u_1,v) = c(y,v) \ \ \ \ \textrm{ for all } \ v \in V, \label{bilinear_equation}
-                \end{eqnarray}
-                then for each $f \in C^1(J,X)$, there exists a unique solution $u \in C^1(J,V)\cap C^2(J,W)$ for Problem GVar.
-            \end{Thmx}
-
-            This theorem allows for a solution of the abstract variational problem Problem GVar, if the assumptions \textbf{A1}-\textbf{A4} is satisfied and the initial values $u_0$ and $u_1$ are admissible.
-It is not always easy to verify that \eqref{bilinear_equation} is satisfied.
-
-            \footfullcitenonumber{VV02}
-        \end{frame}
-
-    \subsection{Modal Analysis}
-        \begin{frame}{Modal Analysis}
-            \textbf{General vibration problem:}
-
-            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
-            \begin{eqnarray}
-                c(u''(t),v)+b(u(t),v) = 0 \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
-            \end{eqnarray}
-            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.
-
-            \only<2->{
-            Trial solution:
-
-            $u(t) = T(t)x$ with $x \in V$ and $x \neq 0$}
-        \end{frame}
-
-        \begin{frame}{Modal Analysis}
-           Substituting trial solution into \eqref{eq:existence:ProblemGVarHom}:
-           \begin{eqnarray*}
-                b(T(t)x,v) = - c(T''(t)x,v).  \label{eq:existence:ProblemGVarHom:Substitution}
-            \end{eqnarray*}
-
-            Due to the linearity of the bilinear form, this equation can be rewritten as
-            \begin{eqnarray*}
-                T(t)b(x,v) = - T''(t)c(x,v).
-            \end{eqnarray*}
-
-            \only<1>{
-            Dividing both sides by $T(t)$ gives
-            \begin{eqnarray*}
-                b(x,v) = - \frac{T''(t)}{T(t)}c(x,v).
-            \end{eqnarray*}}
-
-            \only<2>{
-            Dividing both sides by $T(t)$ gives
-            \begin{eqnarray*}
-                b(x,v) = - \frac{T''(t)}{T(t)}c(x,v) \implies  \frac{T''(t)}{T(t)} \ \ \ \textrm{must be constant.}
-            \end{eqnarray*}}
-        \end{frame}
-
-        \begin{frame}{Modal Analysis}
-            Set $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$.
-
-            At this point we do not yet know if such a $\lambda$ exists.
-
-            \only<2->{
-            Eigenvalue Problem:
-
-            Find a real number $\lambda$ and a $x \in V$ with $x \neq 0$ such that
-            \begin{eqnarray*}
-                b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
-            \end{eqnarray*}}
-
-         \end{frame}
-
-         \begin{frame}{Modal Analysis}
-            \only<1->{
-            Eigenvalue Problem:
-
-            Find a real number $\lambda$ and a $x \in V$ with $x \neq 0$ such that
-            \begin{eqnarray*}
-                b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
-            \end{eqnarray*}}
-
-            Existence of a solution is presented in the article [\cite{CVV18}]\footfullcite{CVV18}
-
-        \end{frame}
-
-        \begin{frame}{Modal Analysis}
-            \begin{itemize}
-                \item[] \textbf{A1} - $V$ is dense in $W$ and $W$ is dense in $X$.
-
-                \item[] \textbf{A2} - There exists a positive constant $C_{W}$ such that $\Vert w\Vert_{X} \leq C_{W}\Vert w\Vert_{W}$ for each $ w\in W$.
-
-                \item[] \textbf{A3} - There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
-
-                \item[] \textbf{A4} - The bilinear form $a$ is non-negative, symmetric and bounded on $V$, i.e.
-there exists a positive constant $K_a$ such that for $\displaystyle u,v \in V$, \[|a(u,v)| \leq K_a\Vert u \Vert_V \Vert v \Vert_V.\]
-
-                \item[] \textbf{A5} - The embedding of $V$ into $W$ is compact.
-            \end{itemize}
-         \end{frame}
-
-         \begin{frame}{Modal Analysis}
-            Formal series solution for the general vibration problem:
-            \begin{eqnarray}
-                u(t) = \sum_{n=1}^{\infty} T_n(t)x_n. \label{eq:1D_Model:ModalAnalysisSeriesSolution}
-            \end{eqnarray}
-            with 
-            \begin{flalign}
-                T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda_n > 0, \label{lambda_1}
-            \end{flalign}
+\section{Literature study}
+    \subsection{Comparison of linear beam theories}
+        \begin{frame}{Literature study - Comparison of linear beam theories}
+            Consider the article \textit{Comparison of linear beam theories} [\cite{LVV09}]
+
+            \footfullcite{LVV09}
+        \end{frame}
+
+        \begin{frame}{Detailed Comparison: Timoshenko Beam Model vs. Two-Dimensional Model}
+
+            \textbf{Objective of Comparison:}
+            \begin{itemize}
+              \item To validate the efficacy of the Timoshenko beam theory against a more comprehensive two-dimensional model, which accounts for plane stress conditions and detailed stress distribution across the beam's cross-section.
+            \end{itemize}
+
+            \textbf{Methodology:}
+            \begin{itemize}
+              \item Utilized finite element methods to calculate natural frequencies and modes, providing a direct comparison of results from both models.
+              \item Both models analyzed under the same boundary conditions and loading scenarios to ensure consistency in comparison.
+            \end{itemize}
+
+            \textbf{Key Findings:}
+            \begin{itemize}
+              \item \textbf{Close Agreement}: Timoshenko model results closely match those from the two-dimensional model, with most eigenvalues showing less than 3\% deviation.
+              \item \textbf{Model Reliability}: Demonstrates high reliability of the Timoshenko model for predicting beam behavior under various loading conditions, particularly for lower vibration modes.
+            \end{itemize}
+
+        \end{frame}
+
+        \begin{frame}
+            \textbf{Model Advantages:}
+            \begin{itemize}
+              \item \textbf{Timoshenko Model}: Offers significant improvements in accuracy over simpler models like Euler-Bernoulli, especially in scenarios where beam lengths are relatively short and shear deformations cannot be ignored.
+              \item \textbf{Two-Dimensional Model}: Provides a more rigorous analysis by accounting for two-dimensional stress effects, which are important for comprehensive structural analyses.
+            \end{itemize}
+
+            \textbf{Practical Implications:}
+            \begin{itemize}
+              \item \textbf{Engineering Applications}: Timoshenko model is particularly advantageous for practical engineering applications, providing a good balance between computational efficiency and accuracy.
+              \item \textbf{Advanced Analyses}: For critical engineering tasks where detailed stress distribution is crucial, the two-dimensional model serves as a more suitable analytical tool.
+            \end{itemize}
+
+            \textbf{Conclusions and Recommendations:}
+            \begin{itemize}
+              \item \textbf{Preferred Use of Timoshenko Model}: Recommended for most practical engineering applications involving beams, where it strikes an optimal balance between accuracy and simplicity.
+              \item \textbf{When to Use Two-Dimensional Model}: Advisable for in-depth structural analyses where precise stress distribution is required, such as in complex assemblies or where materials with varying properties are involved.
+              \item This comparison serves as an intermediate step towards the more comprehensive analysis involving the comparison of two-dimensional and three-dimensional models.
+            \end{itemize}
+
+            \end{frame}
+
+    \subsection{Empirical comparison of beams}
+        \begin{frame}{Literature study - Empirical comparison of beams}
+            Consider the article \textit{On the valid frequency range of Timoshenko beam theory} [\cite{SP06}]\footfullcite{SP06}
+        \end{frame}
+
+        \begin{frame}{Setup and Testing Method}
+            \textbf{Objective:}
+            \begin{itemize}
+                \item To validate the frequency predictions of Timoshenko beam theory (TBT) for different end conditions and frequencies.
+            \end{itemize}
+
+            \textbf{Methodology:}
+            \begin{itemize}
+                \item Experimental setup involved a short free-free beam of near-square cross-section.
+                \item Beam dimensions: Length = 40.047 mm, Breadth = 10.097 mm, Depth = 10.047 mm.
+                \item Beam material: Aluminum alloy, with properties determined via resonant ultrasound spectroscopy (RUS).
+                \item Comparisons made with experimental observations, commercial finite element (ANSYS) predictions, and RUS technique predictions.
+                \item Finite element analysis used 20-node brick elements, and TBT predictions were calculated using specific frequency equations.
+            \end{itemize}
+
+            \textbf{Key Setup Features:}
+            \begin{itemize}
+                \item The experimental beam was suspended and excited by two carbon-fibre loops attached to piezoelectric transducers.
+                \item Resonant frequencies detected by sweeping the frequency range with a network analyzer.
+            \end{itemize}
+        \end{frame}
+
+        \begin{frame}{Numerical Results and Discussion}
+            \textbf{Results Summary:}
+            \begin{itemize}
+                \item Excellent agreement between measured, ANSYS, and RUS frequencies below the cut-off frequency.
+                \item Above the cut-off frequency, TBT predictions deviate increasingly from measured and simulated frequencies.
+            \end{itemize}
+
+            \textbf{Discussion:}
+            \begin{itemize}
+                \item For free-free end conditions, discrepancies arise above the cut-off frequency, suggesting limitations in the TBT's applicability.
+                \item TBT predictions were increasingly inaccurate for higher modes (n >= 8), exceeding the typical engineering tolerance.
+            \end{itemize}
+
+            \textbf{Conclusion:}
+            \begin{itemize}
+                \item The study suggests a cut-off frequency as a reasonable upper bound for TBT predictions.
+                \item This research serves as an intermediate step, setting the stage for further comparison between two-dimensional and three-dimensional models.
+            \end{itemize}
         \end{frame}
@@
 
-\section{Literature study}
-    \subsection{Comparison of linear beam theories}
-        \begin{frame}{Literature study - Comparison of linear beam theories}
-            Consider the article [\cite{LVV09}]\footfullcite{LVV09}
-        \end{frame}
-
-    \subsection{Empirical comparison of beams}
-        \begin{frame}{Literature study - Empirical comparison of beams}
-            Consider the article [\cite{SP06}]\footfullcite{SP06}
+\section{Theory}
+    \subsection{General vibration problem}
+        \begin{frame}{General vibration problem}
+            Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
+            \begin{itemize}
+                \item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
+                \item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
+                \item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
+            \end{itemize}
+            \only<2->{
+            The bilinear forms $a$, $b$ and $c$ are defined as $a = (\cdot,\cdot)_X$,$b = (\cdot,\cdot)_V$ and $c = (\cdot,\cdot)_W$.
+            }
+
+            \only<3>{
+            \textbf{General vibration problem:}
+
+            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
+            \begin{eqnarray}
+                c(u''(t),v)+a(u'(t),v)+b(u(t),v) = (f(t),v) \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
+            \end{eqnarray}
+            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.}
+
+            \only<4->{
+            \textbf{General vibration problem:}
+
+            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
+            \begin{eqnarray}
+                c(u''(t),v)+b(u(t),v) = (f(t),v) \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
+            \end{eqnarray}
+            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.}
+
+            \footfullcitenonumber{VV02}
+        \end{frame}
+
+    \subsection{Existence and uniqueness of solutions}
+        \begin{frame}{Existence and uniqueness of solutions}
+            In [\cite{VV02}] the authors present results for the existence and uniqueness of solutions to the general vibration problem. The following assumptions are made for the existence results.
+
+            \begin{itemize}
+                \item[] \textbf{A1} - $V$ is dense in $W$ and $W$ is dense in $X$.
+
+                \item[] \textbf{A2} - There exists a positive constant $C_{W}$ such that $\Vert w\Vert_{X} \leq C_{W}\Vert w\Vert_{W}$ for each $ w\in W$.
+
+                \item[] \textbf{A3} - There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
+
+                \item[] \textbf{A4} - The bilinear form $a$ is non-negative, symmetric and bounded on $V$, i.e.
+there exists a positive constant $K_a$ such that for $\displaystyle u,v \in V$, \[|a(u,v)| \leq K_a\Vert u \Vert_V \Vert v \Vert_V.\]
+            \end{itemize}
+            \footfullcitenonumber{VV02}
+        \end{frame}
+
+        \begin{frame}{Existence and uniqueness of solutions}
+            \newtheorem{Thmx}{Theorem}
+            \begin{Thmx}
+                Suppose assumptions \textbf{A1}-\textbf{A4} hold. If, for $u_0 \in V$ and $u_1 \in V$, there exists some $y \in W$ such that
+                \begin{eqnarray}
+                    b(u_0,v) + a(u_1,v) = c(y,v) \ \ \ \ \textrm{ for all } \ v \in V, \label{bilinear_equation}
+                \end{eqnarray}
+                then for each $f \in C^1(J,X)$, there exists a unique solution $u \in C^1(J,V)\cap C^2(J,W)$ for Problem GVar.
+            \end{Thmx}
+
+            This theorem allows for a solution of the abstract variational problem Problem GVar, if the assumptions \textbf{A1}-\textbf{A4} is satisfied and the initial values $u_0$ and $u_1$ are admissible.
+It is not always easy to verify that \eqref{bilinear_equation} is satisfied.
+
+            \footfullcitenonumber{VV02}
+        \end{frame}
+
+    \subsection{Modal Analysis}
+        \begin{frame}{Modal Analysis}
+            \textbf{General vibration problem:}
+
+            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
+            \begin{eqnarray}
+                c(u''(t),v)+b(u(t),v) = 0 \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
+            \end{eqnarray}
+            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.
+
+            \only<2->{
+            Trial solution:
+
+            $u(t) = T(t)x$ with $x \in V$ and $x \neq 0$}
+        \end{frame}
+
+        \begin{frame}{Modal Analysis}
+           Substituting trial solution into \eqref{eq:existence:ProblemGVarHom}:
+           \begin{eqnarray*}
+                b(T(t)x,v) = - c(T''(t)x,v).  \label{eq:existence:ProblemGVarHom:Substitution}
+            \end{eqnarray*}
+
+            Due to the linearity of the bilinear form, this equation can be rewritten as
+            \begin{eqnarray*}
+                T(t)b(x,v) = - T''(t)c(x,v).
+            \end{eqnarray*}
+
+            \only<1>{
+            Dividing both sides by $T(t)$ gives
+            \begin{eqnarray*}
+                b(x,v) = - \frac{T''(t)}{T(t)}c(x,v).
+            \end{eqnarray*}}
+
+            \only<2>{
+            Dividing both sides by $T(t)$ gives
+            \begin{eqnarray*}
+                b(x,v) = - \frac{T''(t)}{T(t)}c(x,v) \implies  \frac{T''(t)}{T(t)} \ \ \ \textrm{must be constant.}
+            \end{eqnarray*}}
+
+            \only<3->{
+                Set $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$.
+
+            At this point we do not yet know if such a $\lambda$ exists.
+            }
+        \end{frame}
+
+        \begin{frame}{Modal Analysis}
+            Eigenvalue Problem:
+
+            Find a real number $\lambda$ and a $x \in V$ with $x \neq 0$ such that
+            \begin{eqnarray*}
+                b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
+            \end{eqnarray*}
+
+            Ordinary differential equation for $T(t)$:
+            \begin{eqnarray}
+                T''(t)  + \lambda T(t) = 0. \label{eq:1D_Model:ModalAnalysisODE}
+            \end{eqnarray}
+         \end{frame}
+
+        \begin{frame}{Modal Analysis}
+            Assumptions:
+            \begin{itemize}
+                \item[] \textbf{A1} - $V$ is dense in $W$ and $W$ is dense in $X$.
+
+                \item[] \textbf{A2} - There exists a positive constant $C_{W}$ such that $\Vert w\Vert_{X} \leq C_{W}\Vert w\Vert_{W}$ for each $ w\in W$.
+
+                \item[] \textbf{A3} - There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
+
+                \item[] \textbf{A4} - The bilinear form $a$ is non-negative, symmetric and bounded on $V$, i.e.
+there exists a positive constant $K_a$ such that for $\displaystyle u,v \in V$, \[|a(u,v)| \leq K_a\Vert u \Vert_V \Vert v \Vert_V.\]
+
+                \item[] \alert{\textbf{A5} - The embedding of $V$ into $W$ is compact.} [\cite{CVV18}]
+            \end{itemize}
+            \footfullcite{CVV18}
+        \end{frame}
+
+        \begin{frame}{Modal Analysis}
+
+            ***************Verduideliking********************
+
+            Solutions for the Eigenvalue Problem:
+            \begin{eqnarray*}
+                u = \sum_{i=1}^{\infty} a_i x_i = \sum_{i=1}^{\infty} c(u, x_i)x_i.
+            \end{eqnarray*}
+
+            Solutions for the Ordinary Differential Equation:
+            \begin{flalign}
+                T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda_n > 0, \label{lambda_1}
+            \end{flalign}
+
+            Formal series solution for the general vibration problem:
+            \begin{eqnarray}
+                u(t) = \sum_{n=1}^{\infty} T_n(t)x_n.
+            \end{eqnarray}
         \end{frame}
@@
 
+        \begin{frame}
+            \begin{table}[htbp]
+                \scalebox{.8}{
+                \makebox[\textwidth]{
+                    \begin{tabular}{|cc|cc|cc|cc||cc|}
+                        \hline
+                        \multicolumn{10}{|c|}{Eigenvalues for $b \leq h$} \\
+                        \hline
+                        \hline
+                        i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
+                        \hline
+                        {2} & 0.12307 & {2} & 0.12234 & {2} & 0.12198 & {3} & 0.12178 & 1     & 0.12151 \\
+                        {3} & 3.5773 & {5} & 3.5630 & {6} & 3.5558 & {8} & 3.5519 & 2     & 3.5460 \\
+                        \rowcolor{lightgray}{5} & 7.7799 & {6} & 7.7596 & {8} & 7.7471 & {11} & 7.7401 & 3     & 7.7311 \\
+                        {8} & 20.334 & {9} & 20.283 & {11} & 20.26 & {14} & 20.247 & 4     & 20.225 \\
+                        {10} & 56.247 & {12} & 56.173 & {15} & 56.156 & {22} & 56.142 & 5     & 56.109 \\
+                        \rowcolor{lightgray}{11} & 69.197 & {14} & 69.319 & {17} & 69.281 & {24} & 69.238 & 6     & 69.164 \\
+                        {14} & 114.03 & {16} & 114.01 & {20} & 114.05 & {29} & 114.06 & 7     & 114.03 \\
+                        \rowcolor{lightgray}{17} & 187.01 & {19} & 189.14 & {25} & 189.37 & {36} & 189.34 & 8     & 189.17 \\
+                        {18} & 192.21 & {20} & 192.41 & {26} & 192.58 & {37} & 192.63 & 9     & 192.61 \\
+                        {21} & 284.76 & {23} & 285.43 & {31} & 285.74 & {42} & 285.84 & 10    & 285.85 \\
+                        {23} & 327.57 & {26} & 328.24 & {35} & 328.37 & {46} & 328.40 & 11    & 328.40 \\
+                        \rowcolor{lightgray}{25} & 347.77 & {28} & 356.44 & {36} & 357.30 & {50} & 357.33 & 12    & 357.08 \\
+                        {27} & 393.69 & {30} & 396.84 & {38} & 397.28 & {53} & 397.37 & 13    & 397.33 \\
+                        {30} & 434.46 & {34} & 441.05 & {41} & 441.81 & {57} & 441.99 & 14    & 442.00 \\
+                        \rowcolor{lightgray}{31} & 523.65 & {36} & 534.04 & {43} & 534.17 & {63} & 534.03 & 15    & 533.71 \\
+                        {34} & 550.51 & {37} & 537.82 & {44} & 538.86 & {64} & 539.06 & 16    & 538.97 \\
+                        \rowcolor{lightgray}{37} & 590.86 & {41} & 587.43 & {48} & 594.17 & {65} & 595.58 & 17    & 596.06 \\
+                        {39} & 590.86 & {42} & 600.52 & {49} & 602.25 & {67} & 602.69 & 18    & 602.77 \\
+                        \rowcolor{lightgray}{42} & 646.21 & {44} & 657.22 & {50} & 658.04 & {71} & 658.06 & 19    & 657.87 \\
+                        {44} & 711.07 & {46} & 714.62 & {53} & 717.10 & {73} & 717.51 & 20    & 717.37 \\
+                        \hline
+                        \hline
+                        \multicolumn{2}{|c|}{Max RE: \  2.6069\%} &\multicolumn{2}{c|}{Max RE: \ 1.4469\%}  & \multicolumn{2}{c|}{Max RE: \  0.38192\%}  & \multicolumn{2}{c||}{Max RE: \ 0.22301\%}& \multicolumn{2}{c|}{-} \\
+                        \hline
+                    \end{tabular}%
+                    \label{tab:2v3_1}%
+                }}
+            \end{table}%
+        \end{frame}
+
+        \begin{frame}
+            \begin{table}[htbp]
+                \centering
+                \begin{tabular}{|c|cccc|}
+                    \hline
+                    \multicolumn{5}{|c|}{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/5$.} \\
+                    \hline
+                    \hline
+                    & {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
+                    \hline
+                    Beam Type & 2.1420 \% & 0.6804 \% & 0.38192 \% & 0.22301 \% \\
+                    Non-Beam Type & 2.6069 \% & 1.4469 \% & 0.31546 \% & 0.11680 \% \\
+                    \hline
+                \end{tabular}%
+                \label{tab:2Dv3D_1_breakup}%
+            \end{table}%
+        \end{frame}
+
+        \begin{frame}
+            \begin{table}[ht]
+                \scalebox{.8}{
+                \makebox[\textwidth]{
+                \begin{tabular}{|cc|cc|cc|cc||cc|}
+                    \hline
+                    \multicolumn{10}{|c|}{Comparsion of Eigenvalues with $h = 1/20$, with decreasing $b$ and $b < h$.} \\
+                    \hline
+                    \hline
+                    i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
+                    \hline
+                    {2} & 0.008043 & {2} & 0.008029 & {2} & 0.008023 & {3} & 0.00802 & {1} & {0.008013} \\
+                    {3} & 0.3087 & {4} & 0.30816 & {5} & 0.30794 & {7} & 0.30785 & {2} & {0.30757} \\
+                    {5} & 2.3357 & {8} & 2.3316 & {9} & 2.3300  & {12} & 2.3293 & {3} & {2.3273} \\
+                    \rowcolor{lightgray}{8} & 7.7217 & {10} & 7.7156 & {13} & 7.7124 & {16} & 7.7111 & {4} & {7.7077} \\
+                    {10} & 8.5387 & {11} & 8.5238 & {14} & 8.5182 & {18} & 8.516 & {5} & {8.5086} \\
+                    {11} & 21.986 & {14} & 21.948 & {18} & 21.934 & {24} & 21.929 & {6} & {21.911} \\
+                    {14} & 45.863 & {18} & 45.781 & {21} & 45.756 & {30} & 45.746 & {7} & {45.712} \\
+                    \rowcolor{lightgray}{17} & 69.444 & {19} & 69.408 & {25} & 69.385 & {33} & 69.374 & {8} & {69.344} \\
+                    {18} & 83.149 & {22} & 82.999 & {27} & 82.960 & {36} & 82.944 & {9} & {82.887} \\
+                    {21} & 136.44 & {25} & 136.19 & {31} & 136.14 & {42} & 136.12 & {10} & {136.03} \\
+                    \rowcolor{lightgray}{23} & 192.62 & {27} & 192.62 & {35} & 192.58 & {47} & 192.56 & {11} & {192.48} \\
+                    {25} & 207.87 & {29} & 207.5 & {36} & 207.43 & {48} & 207.41 & {12} & {207.29} \\
+                    {27} & 299.14 & {33} & 298.63 & {41} & 298.56 & {55} & 298.53 & {13} & {298.38} \\
+                    \rowcolor{lightgray}{30} & 376.68 & {35} & 377.01 & {44} & 377.01 & {58} & 376.98 & {14} & {376.83} \\
+                    {31} & 411.58 & {37} & 410.89 & {46} & 410.83 & {61} & 410.81 & {15} & {410.63} \\
+                    {34} & 546.15 & {40} & 545.27 & {50} & 545.24 & {66} & 545.23 & {16} & {545.03} \\
+                    \rowcolor{lightgray}{37} & 620.77 & {42} & 622.02 & {53} & 622.19 & {69} & 622.18 & {17} & {621.95} \\
+                    {39} & 703.55 & {44} & 702.49 & {54} & 702.29 & {71} & 702.53 & {18} & {702.31} \\
+                    {42} & 884.27 & {47} & 883.02 & {59} & 883.14 & {82} & 883.19 & {19} & {882.96} \\
+                    \rowcolor{lightgray}{44} & 923.68 & {49} & 926.88 & {60} & 927.43 & {86} & 927.50 & {20} & {927.18} \\
+                    \hline
+                    \hline
+                    \multicolumn{2}{|c|}{Max RE: \  0.37701\%} &\multicolumn{2}{c|}{Max RE: \ 0.19893\%}  & \multicolumn{2}{c|}{Max RE: \  0.12393\%}  & \multicolumn{2}{c||}{Max RE: \ 0.092843\%}& \multicolumn{2}{c|}{-} \\
+                    \hline
+                \end{tabular}%
+                \label{tab:2v3_2}%
+            }}
+            \end{table}%
+        \end{frame}
+
+        \begin{frame}
+            \begin{table}[htbp]
+                \centering
+                \begin{tabular}{|c|cccc|}
+                    \hline
+                    \multicolumn{5}{|c|}{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$} \\
+                    \hline
+                    \hline
+                    & {b = h} & {b = 1/2h} & {b = 1/4h} & {b = 1/8h} \\
+                    \hline
+                    Beam Type & 0.37701 \% & 0.19893 \% & 0.12393 \% & 0.092843 \% \\
+                    Non-Beam Type & 0.37682 \% & 0.10218 \% & 0.061213 \% & 0.043601 \% \\
+                    \hline
+                \end{tabular}%
+                \label{tab:2v3_2_split}%
+            \end{table}%
+        \end{frame}
+
+        \begin{frame}
+            \begin{table}[htbp]
+                \scalebox{.8}{
+                \makebox[\textwidth]{
+                    \begin{tabular}{|cc|cc|cc||cc|}
+                        \hline
+                        \multicolumn{8}{|c|}{Comparsion of Eigenvalues with $h = 1/20$, with increasing $b$ and $b > h$} \\
+                        \hline
+                        \hline
+                        i     & {b = 2h} & i     & {b = 4h} & i     & {b = 8h} & j     & 2D \\
+                        \hline
+                        {2} & 0.008076 & {1} & 0.008162 & {1} & 0.008324 & 1     & 0.008013 \\
+                        {3} & 0.30995 & {3} & 0.31298 & {3} & 0.31738 & 2     & 0.30757 \\
+                        {5} & 2.3462 & {5} & 2.3737 & {6} & 2.4116 & 3     & 2.3273 \\
+                        \rowcolor{lightgray}{8} & 7.7312 & {8} & 7.7471 & {9} & 7.7711 & 4     & 7.7077 \\
+                        {10} & 8.5841 & {9} & 8.7082 & {10} & 8.7929 & 5     & 8.5086 \\
+                        {11} & 22.124 & {12} & 22.491 & {14} & 23.222 & 6     & 21.911 \\
+                        {14} & 46.195 & {14} & 47.003 & {18} & 47.921 & 7     & 45.712 \\
+                        \rowcolor{lightgray}{17} & 69.454 & {17} & 69.281 & {22} & 72.307 & 8     & 69.344 \\
+                        {18} & 83.822 & {18} & 85.218 & {24} & 80.607 & 9     & 82.887 \\
+                        {21} & 137.43 & {21} & 138.58 & {32} & 140.97 & 10    & 136.03 \\
+                        \hline
+                        \hline
+                        \multicolumn{2}{|c|}{Max RE: \  1.1289\%} &\multicolumn{2}{c|}{Max RE: \ 2.8261\%}  & \multicolumn{2}{c|}{Max RE: \  5.9821\%} & \multicolumn{2}{c|}{-} \\
+                        \hline
+                    \end{tabular}%
+                    \label{tab:b>h_20}%
+                }}
+            \end{table}
+        \end{frame}
+
+        \begin{frame}
+            \begin{table}[htbp]
+                \centering
+                \begin{tabular}{|c|ccc|}
+                    \hline
+                    \multicolumn{4}{|c|}{Maximum relative error for beam type and non-beam type eigenvalues for $h = 1/20$} \\
+                    \hline
+                    \hline
+                    & {b = 2h} & {b = 4h} & {b = 8h} \\
+                    \hline
+                    Beam Type & 1.1289 \% & 2.8261 \% & 5.9821 \% \\
+                    Non-Beam Type & 0.30521 \% & 0.51096 \% & 4.2734 \% \\
+                    \hline
+                \end{tabular}%
+                \label{tab:b>h-split_20}%
+            \end{table}%
+        \end{frame}
+
 \section{Conclusion}

### 2024-04-16 final_seminar/main.tex
final

@@
 
+            \textbf{Objective of Comparison:}
+            \begin{itemize}
+              \item To validate the efficacy of the Timoshenko beam theory against a more realistic two-dimensional model.
+            \end{itemize}
+
+            \textbf{Methodology:}
+            \begin{itemize}
+              \item Use modal analysis and the Finite Element Method (FEM) to calculate natural frequencies and modes, providing a direct comparison of results from both models.
+            \end{itemize}
+
+            \textbf{Key Findings:}
+            \begin{itemize}
+              \item Timoshenko model results closely match those from the two-dimensional model, with most eigenvalues showing less than 3\% deviation, depending on the shape of the beam.
+              \item The shape of the beams significantly influences the accuracy of the Timoshenko model.
+            \end{itemize}
+
             \footfullcite{LVV09}
@@
 
-        \begin{frame}{Detailed Comparison: Timoshenko Beam Model vs. Two-Dimensional Model}
-
-            \textbf{Objective of Comparison:}
-            \begin{itemize}
-              \item To validate the efficacy of the Timoshenko beam theory against a more comprehensive two-dimensional model, which accounts for plane stress conditions and detailed stress distribution across the beam's cross-section.
-            \end{itemize}
-
-            \textbf{Methodology:}
-            \begin{itemize}
-              \item Utilized finite element methods to calculate natural frequencies and modes, providing a direct comparison of results from both models.
-              \item Both models analyzed under the same boundary conditions and loading scenarios to ensure consistency in comparison.
-            \end{itemize}
-
-            \textbf{Key Findings:}
-            \begin{itemize}
-              \item \textbf{Close Agreement}: Timoshenko model results closely match those from the two-dimensional model, with most eigenvalues showing less than 3\% deviation.
-              \item \textbf{Model Reliability}: Demonstrates high reliability of the Timoshenko model for predicting beam behavior under various loading conditions, particularly for lower vibration modes.
-            \end{itemize}
-
-        \end{frame}
-
-        \begin{frame}
-            \textbf{Model Advantages:}
-            \begin{itemize}
-              \item \textbf{Timoshenko Model}: Offers significant improvements in accuracy over simpler models like Euler-Bernoulli, especially in scenarios where beam lengths are relatively short and shear deformations cannot be ignored.
-              \item \textbf{Two-Dimensional Model}: Provides a more rigorous analysis by accounting for two-dimensional stress effects, which are important for comprehensive structural analyses.
-            \end{itemize}
-
-            \textbf{Practical Implications:}
-            \begin{itemize}
-              \item \textbf{Engineering Applications}: Timoshenko model is particularly advantageous for practical engineering applications, providing a good balance between computational efficiency and accuracy.
-              \item \textbf{Advanced Analyses}: For critical engineering tasks where detailed stress distribution is crucial, the two-dimensional model serves as a more suitable analytical tool.
-            \end{itemize}
+        \begin{frame}{Literature study - Comparison of linear beam theories}
 
@@
             \begin{itemize}
-              \item \textbf{Preferred Use of Timoshenko Model}: Recommended for most practical engineering applications involving beams, where it strikes an optimal balance between accuracy and simplicity.
-              \item \textbf{When to Use Two-Dimensional Model}: Advisable for in-depth structural analyses where precise stress distribution is required, such as in complex assemblies or where materials with varying properties are involved.
-              \item This comparison serves as an intermediate step towards the more comprehensive analysis involving the comparison of two-dimensional and three-dimensional models.
+              \item For practical applications, the Timoshenko beam model is a suitable approximation for two-dimensional model.
+              \item This article excluded damping.
+              \item This comparison serves as an intermediate step towards the more comprehensive analysis involving the comparison of Timoshenko beam model and a three-dimensional model.
+A direct comparison is preferred but this will introduce additional complexities.
+            \end{itemize}
+
+            \textbf{In this presentation:}
+            \begin{itemize}
+              \item We will replicate the results of this article using the Finite Element Method (FEM) and modal analysis.
+              \item We will improve the results by increasing the accuracy to 5 significant digits.
+              \item We extent the article to also include the comparison of the two-dimensional model with a three-dimensional model.
             \end{itemize}
@@
         \begin{frame}{Literature study - Empirical comparison of beams}
-            Consider the article \textit{On the valid frequency range of Timoshenko beam theory} [\cite{SP06}]\footfullcite{SP06}
-        \end{frame}
-
-        \begin{frame}{Setup and Testing Method}
+            Consider the article \textit{On the valid frequency range of Timoshenko beam theory} [\cite{SP06}]
+
             \textbf{Objective:}
             \begin{itemize}
-                \item To validate the frequency predictions of Timoshenko beam theory (TBT) for different end conditions and frequencies.
+                \item To validate the frequency predictions of Timoshenko beam theory for different end conditions and frequencies.
             \end{itemize}
@@
 
+            \footfullcite{SP06}
+        \end{frame}
+
+        \begin{frame}{Setup and Testing Method}
+
             \textbf{Key Setup Features:}
@@
             \end{itemize}
+
+            \begin{figure}[h!]
+                \centering
+                \begin{tikzpicture}[scale=0.8]
+
+                    \draw[line width = 0.25mm] (2,0) -- (7,2);
+                    \draw[line width = 0.25mm] (2,1) -- (7,3);
+                    \draw[line width = 0.25mm] (1,1) -- (6,3);
+
+                    \draw[line width = 0.25mm] (2,0) -- (2,1);
+                    \draw[line width = 0.25mm] (1,0) -- (1,1);
+                    \draw[line width = 0.25mm] (2,0) -- (1,0);
+                    \draw[line width = 0.25mm] (2,1) -- (1,1);
+
+                    \draw[line width = 0.25mm] (6,3) -- (7,3);
+                    \draw[line width = 0.25mm] (7,3) -- (7,2);
+
+                    \draw(2.1,0) parabola (2.5,4);
+                    \draw(1,0.1) parabola (0.6,4);
+
+                    \draw(6.9,1.9) parabola (7.4,4.9);
+                    \draw[line width = 0.15mm] (5.7,2.9) -- (5.5,4.9);
+
+                \end{tikzpicture}
+            \end{figure} 
         \end{frame}
@@
                 \item Excellent agreement between measured, ANSYS, and RUS frequencies below the cut-off frequency.
-                \item Above the cut-off frequency, TBT predictions deviate increasingly from measured and simulated frequencies.
-            \end{itemize}
-
-            \textbf{Discussion:}
-            \begin{itemize}
-                \item For free-free end conditions, discrepancies arise above the cut-off frequency, suggesting limitations in the TBT's applicability.
-                \item TBT predictions were increasingly inaccurate for higher modes (n >= 8), exceeding the typical engineering tolerance.
-            \end{itemize}
-
-            \textbf{Conclusion:}
-            \begin{itemize}
-                \item The study suggests a cut-off frequency as a reasonable upper bound for TBT predictions.
-                \item This research serves as an intermediate step, setting the stage for further comparison between two-dimensional and three-dimensional models.
-            \end{itemize}
+            \end{itemize}
+
+            \textbf{Some results from the article:}
+            \begin{table}[htbp]
+                \makebox[\textwidth]{
+                \begin{tabular}{||c|c|cc|cc|c||}
+                    \hline
+                    {n} & {Measured} & {3D FEM} & {\% Error} & {Timoshenko Beam} & {\% Error} & Side \\
+                    \hline
+                    1     & 27359.6 & 27417.6 & 0,21\% & 27407.1 & 0,17\% & Flexible \\
+                            & 27423.8 & 27515.6 & 0,33\% & 27505.3 & 0,30\% & Stiff \\
+                    2     & 60862   & 60882.0 & 0,03\% & 60851.1 & -0,02\% & Flexible \\
+                           & 61098.3 & 61022.0 & -0,12\% & 60992.1 & -0,17\% & Stiff \\
+                    3     & 97609.5 & 97734.4 & 0,13\% & 97796.0 & 0,19\% & Flexible \\
+                          & 97852.4 & 97881.5 & 0,03\% & 97945.4 & 0,09\% & Stiff \\
+                    4     & 161494 & 131658 & 0,12\% & 132277 & 0,60\% & Flexible \\
+                          & 131732 & 131675 & -0,04\% & 132308 & 0,44\% & Stiff \\
+                    5     & 161352 & 161390 & 0,02\% & 163547 & 1,36\% & Stiff \\
+                          & 161538 & 161517 & -0,01\% & 163611 & 1,31\% & Flexible \\
+                    6     & 165183 & 164887 & -0,18\% & 169108 & 2,38\% & Stiff \\
+                          & 165598 & 165398 & -0,12\% & 169634 & 2,44\% & Flexible \\
+                    7     & 194863 & 194933 & 0,04\% & 202352 & 3,84\% & Flexible \\
+                             & 194973 & 195032 & 0,03\% & 202115 & 3,66\% & Stiff \\
+                    8     & 195869 & 195977 & 0,06\% & 203319 & 3,80\% & Stiff \\
+                          & 195908 & 196097 & 0,10\% & 203518 & 3,88\% & Flexible \\
+                    9     & 213501 &       &       & 241202 & 12,97\% & Flexible \\
+                          & 213635 &       &       & 241067 & 12,84\% & Stiff \\
+              {10 and 11} & 220556 &       &       & 247954 & 12,42\% & Flexible \\
+                          & 220702 &       &       & 281542 & 27,57\% & Flexible \\
+                          & 221010 &       &       & 247782 & 12,11\% & Stiff \\
+                          & 221092 &       &       & 281408 & 27,28\% & Stiff \\
+                    \hline
+                \end{tabular}%
+            }
+            \end{table}%
         \end{frame}
@@
 
-            \only<2>{
+            \only<2->{
             Dividing both sides by $T(t)$ gives
@@
 
-            ***************Verduideliking********************
-
-            Solutions for the Eigenvalue Problem:
+            Using these assumptions, the authors prove that there exists a complete orthonormal sequence of eigenvectors for the eigenvalue problem with a corresponding sequence of eigenvalues.
+These eigenvalues are positive and the orthogonality is with respect to the bilinear form $c$.
+Also the sequence of normalized eigenvectors ${x_i}$ forms an orthonormal basis in $W$ and sequence of eigenvalues ${\lambda_i}$ is an infinite sequence with $\lambda_n \rightarrow \infty$ as $n \rightarrow \infty$.
+
+            Following these results, for any $u \in V$, $\displaystyle u = \sum_{i=1}^{\infty} a_i x_i$.
+These coefficients $a_i$ are generalized Fourier coefficients of $u$ with respect to the eigenvectors $x_i$.
+Therefore, for any $u \in V$,
             \begin{eqnarray*}
@@
 
-            Solutions for the Ordinary Differential Equation:
+            Now that the eigenvalue problem has many solutions, the following ordinary differentiable equation can be considered,
+            \begin{eqnarray*}
+                T_n'' + \lambda T_n = 0. 
+            \end{eqnarray*}
+        \end{frame}
+
+        \begin{frame}
+            Since this differential equation is a simple second order differential equation, $T_n(t)$ has the following possible solutions:
             \begin{flalign}
@@
 
-            Formal series solution for the general vibration problem:
+            Then combining the solutions of the eigenvalue problem and the differential equation, the formal series solution for the boundary value problem is
             \begin{eqnarray}
-                u(t) = \sum_{n=1}^{\infty} T_n(t)x_n.
+                u(t) = \sum_{n=1}^{\infty} T_n(t)x_n. \label{eq:1D_Model:ModalAnalysisSeriesSolution}
             \end{eqnarray}
+
         \end{frame}
@@
     \subsection{Finite Element Analysis}
-        \begin{frame}{Eigenvalue problem - Two and Three-dimensional models}
-            General eigenvalue problem for the two- and three-dimensional models:
-
-                For the eigenvalue problem, assume that $M_{f}Q^I = 0$ so that 
-            \begin{eqnarray}
-                    M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
-            \end{eqnarray}
-
-            Not so simple to compute the eigenvalues and eigenfunctions.
-
-            Need to use a numerical method like FEM to approximate the eigenvalues and eigenvectors.
-
-        \end{frame}
-
         \begin{frame}{Eigenvalue problem - Timoshenko model}
@@
             \end{itemize}
+
+        \end{frame}
+
+        \begin{frame}{Eigenvalue problem - Two and Three-dimensional models}
+            General eigenvalue problem for the two- and three-dimensional models:
+
+                For the eigenvalue problem, assume that $M_{f}Q^I = 0$ so that 
+            \begin{eqnarray}
+                    M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
+            \end{eqnarray}
+
+            Not so simple to compute the eigenvalues and eigenfunctions.
+
+            Need to use a numerical method like FEM to approximate the eigenvalues and eigenvectors.
 

### 2024-04-17 final_seminar/main.tex
presentation

@@
         Beams are fundamental structural elements in engineering. They are used in a wide range of applications, from bridges to buildings.
-        \pause
 
@@
 However, the accuracy of these models in practical applications is not always certain.
-        \pause
 
@@
             \begin{itemize}
-              \item Timoshenko model results closely match those from the two-dimensional model, with most eigenvalues showing less than 3\% deviation, depending on the shape of the beam.
+              \item Timoshenko model results closely match those from the two-dimensional model, especially for the first ten eigenvalues.
               \item The shape of the beams significantly influences the accuracy of the Timoshenko model.
@@
         \begin{frame}{Models - Three-dimensional cantilever beam}
+            Assume that $\sigma_{3i} = 0$ for $i = 1, 2, 3$; $\partial_3 u_1 = 0$, $\partial_3 u_2 = 0$ ($u_1$ and $u_2$ are functions of $x_1$ and $x_2$), and the strain component $\varepsilon_{33} = 0$.
+Then using the definition of strain
+            \begin{eqnarray}
+                \partial_i u_3 = 0 \quad \textrm{ for } i = 1,2,3 \textrm{ on } \Omega.
+            \end{eqnarray}
+
+            It follows that $u_3$ is a constant on $\Omega$ and $u$ is a vector valued function in $R^2$ with two-dimensional stress and strain.
+The out of plane conditions for strain \eqref{plane_stress_neseccary_condition} falls away and Hooke’s law can be written in a two-dimensional form using the stress components (1.2.16) as $\displaystyle T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E})I.$\\
+
+        \end{frame}
+
+        \begin{frame}{Models - Three-dimensional cantilever beam}
             \begin{figure}[h!]
@@
             Find a real number $\lambda$ and a $x \in V$ with $x \neq 0$ such that
-            \begin{eqnarray*}
+            \begin{eqnarray}
                 b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
-            \end{eqnarray*}
+            \end{eqnarray}
 

### 2024-04-18 final_seminar/main.tex
everything except a concludion

@@
                 \item[-] Uses a cantilever beam as an example in the article.
-                \item[-] Eigenvalues can be numerically obtained to any degree of accuracy.
-            \end{itemize}
-
-        \end{frame}
-
-        \begin{frame}{Eigenvalue problem - Two and Three-dimensional models}
-            General eigenvalue problem for the two- and three-dimensional models:
-
-                For the eigenvalue problem, assume that $M_{f}Q^I = 0$ so that 
+                \item[-] Eigenvalues can be numerically obtained to specified degree of accuracy.
+            \end{itemize}
+
+        \end{frame}
+
+        \begin{frame}{Finite Element Method}
+            It is not trivial to solve the eigenvalue problem for the cantilever two- and three-dimensional beams.
+The Finite Element Method (FEM) can be used to approximate the eigenvalues and eigenvectors.
+
+            We descrise our beams into a finite number of elements and nodes.
+For the two-dimensional beam, we can use a grid of rectangular shaped elements.
+For the three-dimensional beam, we can use a grid of cuboid or brick shaped elements.
+
+            We can also choose our basis functions. In this presentation, bi-cubic and tri-cubic basis function 
+            are used. These have the advantage over bi-linear and tri-linear basis function in that they provide faster convergence of the eigenvalues, although they are more complex to program.
+        \end{frame}
+
+        \begin{frame}{Eigenvalue problem - Two-dimensional and three-dimensional model}
+            \textbf{Eigenvalue problem}
+
+            Find a real number $\lambda$ and a function $\bar{u} \in S^h$ such that
             \begin{eqnarray}
-                    M\ddot{\bar{u}} & = & K\bar{u}.\label{eq:2DFEM:M2}
+                M\lambda{\bar{u}} & = & K\bar{u}.
             \end{eqnarray}
 
-            Not so simple to compute the eigenvalues and eigenfunctions.
-
-            Need to use a numerical method like FEM to approximate the eigenvalues and eigenvectors.
-
-        \end{frame}
-
-        \begin{frame}{FEM}
+            \begin{itemize}
+                \item $M$ and $K$ are the mass and stiffness matrices. They are derived from the standard Finite Element Matrices.
+                \item In this form, the eigenvalue problem is a system of ordinary differential equations.
+                \item It is possible to solve this system of equations using standard numerical methods.
+            \end{itemize}
+
         \end{frame}
@@
             \includegraphics[scale=0.3]{Convergence.png} \\ % Adjust scale as needed
-            \footnotesize Rate of convergence of the first 20 eigenvalues.
+            \footnotesize Rate of convergence of the first 20 eigenvalues for the two-dimensional beam.
 
@@
             \includegraphics[scale=0.3]{convergence3d.png} \\ % Adjust scale as needed
-            \footnotesize Rate of convergence of the first 20 eigenvalues.
-        \end{frame}
-
-    \subsection{Validity of the Timoshenko beam model}
+            \footnotesize Rate of convergence of the first 20 eigenvalues for the three-dimensional beam.
+        \end{frame}
+
+\section{Validity of the Timoshenko beam model}
     \begin{frame}{Validity of the Timoshenko beam model}
@@
         \renewcommand{\arraystretch}{0.9}
-            Results from [LVV09] and results obtained. $0^a$ indicates a 0 due to rounding. $\alpha = 1200$
+        Results from \cite{LVV09} and results obtained. $0^a$ indicates a 0 due to rounding. Height to lenght ratio of 1 to 10.
 
@@
             \hline
-                & \multicolumn{3}{c}{[LVV09]} & & \multicolumn{3}{c}{Dissertation} \\
+            & \multicolumn{3}{c}{[LVV09]} & & \multicolumn{3}{c}{Master Dissertation} \\
 
@@
 
-        \end{frame}
-
-        \begin{frame}{Eigenvalue problem - FEM}
-            \centering
-            \includegraphics[scale=0.45]{Result.png} \\ % Adjust scale as needed
-            \footnotesize Rate of convergence of the first 20 eigenvalues.
-            \label{fig:conv}
-        \end{frame}
+        \footfullcite{LVV09}
+    \end{frame}
+
+    % \begin{frame}{Eigenvalue problem - FEM}
+    %     \centering
+    %     \includegraphics[scale=0.45]{Result.png} \\ % Adjust scale as needed
+    %     \footnotesize Rate of convergence of the first 20 eigenvalues.
+    %     \label{fig:conv}
+    % \end{frame}
 
@@
 
-    \subsection{Validity of the Two-dimensional beam model}
+\section{Validity of the Two-dimensional beam model}
     \begin{frame}{Validity of the Two-dimensional beam model}
@@
                     \hline
-                        \multicolumn{10}{|c|}{Eigenvalues for $b \leq h$} \\
+                    \multicolumn{10}{|c|}{{Comparsion of Eigenvalues with $h = 1/5$, with decreasing $b$ and $b < h$.} \\
                     \hline

### 2024-04-18 final_seminar/main.tex
presentaion

@@
 
-\section{Validity of the Timoshenko beam model}
-    \begin{frame}{Validity of the Timoshenko beam model}
+    \subsection{Validity of the Timoshenko beam}
+        \begin{frame}{Validity of the Timoshenko beam - Visual representation}
             \begin{center}
@@
             \end{center}
-    \end{frame}
-
-    \begin{frame}{Comparison of two and three-dimensional models}
+
+            \only<2->{
+                Parameters:
+
+                For the Timoshenko beam model we do not have a direct parameter for the height.
+
+                Recall the dimensionless constant $\alpha$ in the Timoshenko beam model. In the derivation of the dimensionless form, the following relation was obtained:
+
+                \[ \alpha = \frac{A\ell^2}{I}\]
+
+                Where $A$ is the area of the cross-section, $\ell$ is the length of the beam and $I$ is the area moment of inertia.
+            }
+
+            \only<3->{
+                \[A = hb, \ I = \frac{h^3b}{12} \implies h = \sqrt{\frac{12}{\alpha}}\]
+            }
+
+        \end{frame}
+
+        \begin{frame}{Validity of the Timoshenko beam - Beam type mode shapes}
             \centering
@@
 
-    \begin{frame}{Comparison of two and three-dimensional models}
+        \begin{frame}{Validity of the Timoshenko beam - Non-beam type mode shapes}
             \centering
@@
 
-    \begin{frame}{Comparison of two and three-dimensional models}
+        \begin{frame}{Validity of the Timoshenko beam - Direct comparison of displacement mode shapes}
+            \centering
+            \includegraphics[scale=0.2]{1Dv2D.png} % Adjust scale as needed
+            \par
+            \footnotesize Comparison of the displacement $w$ mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)
+        \end{frame}
+
+        \begin{frame}{Validity of the Timoshenko beam - Direct comparison of rotation mode shapes}
+            \centering
+            \includegraphics[scale=0.2]{1Dv2Dphi.png} % Adjust scale as needed
+            \par
+            \footnotesize Comparison of the angle $\phi$ (best fit for 2D Beam) mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)
+
+            \begin{figure}[h!]
+                \centering
+                \begin{tikzpicture}[scale=0.4]
+
+                \draw[line width = 0.4mm] (0,1) -- (7,1);
+                \draw[line width = 0.4mm] (0,-1) -- (7,-1);
+                \draw[line width = 0.4mm] (7,-1) -- (7,1);
+                \draw[line width = 0.4mm] (0,-1) -- (0,1);
+
+                \draw[line width = 0.1mm,dashed] (3.5,1) -- (3.5,-1);
+
+                \draw[thick] plot [smooth,tension=0.9] coordinates{(3.3,1) (3.7,0.5) (3.5,0) (3.3,-0.5) (3.7,-1)};
+
+                \draw[line width = 0.2mm,red] (3.3,1) -- (3.7,-1);
+
+            \end{tikzpicture}
+                \caption{S-shape deformation of the cross-section of the two-dimensional beam.}\label{fig:s}
+            \end{figure}
+        \end{frame}
+
+        \begin{frame}{Validity of the Timoshenko beam - Results from article}
             \centering
@@
 
-    \begin{frame}{Comparison of Eigenvalues across Different Parameters}
+        \begin{frame}{Validity of the Timoshenko beam - Results for different beam shapes}
             \centering
@@
             \end{tabular}}
-    \end{frame}
-
-\section{Validity of the Two-dimensional beam model}
+
+            \only<2->{
+                \textbf{Conclusion for the Timoshenko beam model:}
+                \begin{itemize}
+                    \item The Timoshenko beam model compares well with the two-dimensional beam model.
+                    \item The shape of the beam influences how well the Timoshenko beam model compares to the two-dimensional beam model.
+                    \item The results of the article are confirmed.
+                    \item The case of a height to length ration of 1 to 20 is the best case we have tested.
+                \end{itemize}
+            }
+
+        \end{frame}
+
+    \subsection{Validity of the Two-dimensional beam model}
         \begin{frame}{Validity of the Two-dimensional beam model}
@@
 
+        \begin{frame}{}
+
+        \end{frame}
+
         \begin{frame}
@@
                         \hline
-                    \multicolumn{10}{|c|}{{Comparsion of Eigenvalues with $h = 1/5$, with decreasing $b$ and $b < h$.} \\
+                        \multicolumn{10}{|c|}{Comparsion of Eigenvalues with $h = 1/5$, with decreasing $b$ and $b < h$.} \\
                         \hline
@@
     \begin{frame}{Conclusion}
+        \begin{itemize}
+            \item 
+        \end{itemize}
+
+        \textbf{Future Work:}
+        \begin{itemize}
+            \item Include damping in the models.
+        \end{itemize}
+
     \end{frame}

### 2024-04-19 final_seminar/main.tex
conclusion

@@
     \begin{frame}{Conclusion}
-        \begin{itemize}
-            \item 
+        \textbf{What we have done:}
+        \begin{itemize}
+            \item Literature study on two articles.
+            \item Presented three different models for a beam, each a different dimension.
+            \item Looked at the well-posedness of the models.
+            \item Looked into Modal Analysis, which forms the basis of the comparisons.
+            \item Quickly discussed the Finite Element Method.
+            \item Looked at the validity of the Timoshenko beam model. Part of the literature study.
+            \item Extended the investigation to the validity of the two-dimensional beam model.
+        \end{itemize}
+
+        \textbf{Conclusion}
+        \begin{itemize}
+            \item We verified the results of the article.
+            \item Shown that the Timoshenko cantilever beam model is a good approximation to the two-dimensional cantilever beam. The shape is important.
+            \item Shown that the two-dimensional cantilever beam is a good approximation to the three-dimensional cantilever beam.
+            \item The shape of the beams are very important to how well the models compare.
+            \item Showed results for various shapes, that can be considered realistic for practical applications of a beam.
         \end{itemize}
@@
             \item Include damping in the models.
+            \item Expand to plate models (this is done in my masters)
+            \item Investigate the effect of different distrubances on the models.
         \end{itemize}

### 2024-04-19 final_seminar/main.tex
final

--- 2024-04-18 final_seminar/main.tex
@@
         \vskip1em%
-        \includegraphics[width=0.2\linewidth]{logo-up.jpg}\par % Include the logo here
+        \includegraphics[width=0.4\linewidth]{logo-up.jpg}\par % Include the logo here
         \vskip1em\par
@@
 
-            \only<3>{
+            \only<3->{
             \textbf{General vibration problem:}
@@
                 c(u''(t),v)+a(u'(t),v)+b(u(t),v) = (f(t),v) \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
-            \end{eqnarray}
-            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.}
-
-            \only<4->{
-            \textbf{General vibration problem:}
-
-            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
-            \begin{eqnarray}
-                c(u''(t),v)+b(u(t),v) = (f(t),v) \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
             \end{eqnarray}
@@
                 \begin{itemize}
-                    \item The Timoshenko beam model compares well with the two-dimensional beam model.
+                    \item The Timoshenko beam model compares well with the two-dimensional beam model. It is a suitable model to use instead of the two-dimensional beam model.
                     \item The shape of the beam influences how well the Timoshenko beam model compares to the two-dimensional beam model.
                     \item The results of the article are confirmed.
-                    \item The case of a height to length ration of 1 to 20 is the best case we have tested.
-                \end{itemize}
-            }
-
-        \end{frame}
-
-    \subsection{Validity of the Two-dimensional beam model}
-        \begin{frame}{Validity of the Two-dimensional beam model}
+                \end{itemize}
+            }
+
+        \end{frame}
+
+    \subsection{Validity of the Two-dimensional beam}
+        \begin{frame}{Validity of the Two-dimensional beam - Visual representation}
             \begin{center}
@@
 
-        \begin{frame}{Three-Dimensional model vs Two-Dimensional model}
+        \begin{frame}{Validity of the Two-dimensional beam- Beam type mode shapes}
             \centering
@@
 
-        \begin{frame}{Three-Dimensional model}
+        \begin{frame}{Validity of the Two-dimensional beam - Non-beam type mode shapes}
             \centering
@@
 
-        \begin{frame}{}
-
-        \end{frame}
-
-        \begin{frame}
+        \begin{frame}{Validity of the Two-dimensional beam - Comparison short thick beam}
             \begin{table}[htbp]
@@
 
-        \begin{frame}
+        \begin{frame}{Validity of the Two-dimensional beam - Comparison short thick beam}
             \begin{table}[htbp]
@@
 
-        \begin{frame}
+        \begin{frame}{Validity of the Two-dimensional beam - Comparison long slender beam}
             \begin{table}[ht]
@@
 
-        \begin{frame}
+        \begin{frame}{Validity of the Two-dimensional beam - Comparison long slender beam}
             \begin{table}[htbp]
@@
 
-        \begin{frame}
+        \begin{frame}{Validity of the Two-dimensional beam - depth larger than height}
             \begin{table}[htbp]
@@
 
+        \begin{frame}{Conclusion for the Two-dimensional model}
+            \textbf{Conclusion for the Two-dimensional model:}
+            \begin{itemize}
+                \item The two-dimensional model compares well with the three-dimensional model, given that the depth of the beam is not larger than the height.
+                \item Again a long and slender beam does compare better than a short and thick beam.
+                \item For body shapes where the depth is larger than the height, the two-dimensional model is not a good approximation to the three-dimensional model and another model should be considered.
+            \end{itemize}
+        \end{frame}
+
 \section{Conclusion}
     \begin{frame}{Conclusion}
-        \begin{itemize}
-            \item 
+        \textbf{What we have done:}
+        \begin{itemize}
+            \item Gave a summary of two articles, one that formed the basis of the comparison that we investigated
+            \item Presented three different models of a beam, each a different dimension.
+            \item Mentioned the well-posedness of the models.
+            \item Briefly discussed modal analysis, and how it can be used to compare the models.
+            \item Discussed at the validity of the Timoshenko beam model as part of the literature of the first article.
+            \item Extended the investigation to the validity of the two-dimensional beam model.
+        \end{itemize}
+
+    \end{frame}
+    \begin{frame}{Conclusion}
+        \textbf{Conclusion}
+        \begin{itemize}
+            \item Discussed and verified the results of the article.
+            \item Shown that the Timoshenko cantilever beam model is a good approximation to the two-dimensional cantilever beam.
+            \item Shown that the two-dimensional cantilever beam is a good approximation to the three-dimensional cantilever beam.
+            \item Shown that shape of the beams are very important to how well the models compare. The shapes that we looked at can be considered realistic beam shapes that is used in applications.
         \end{itemize}
@@
             \item Include damping in the models.
-        \end{itemize}
-
+            \item Expand to plate models (this is done in my masters)
+            \item Investigate the effect of different distrubances on the models.
+        \end{itemize}
     \end{frame}
